### 2019-06-13 eck2019syntheticprediction.tex
first commit; notes on synthetic prediction; some merging of initial documents

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\usepackage{geometry}
\geometry{margin=1in}

\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Hist}{\mathcal{H}}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\indep}{\perp\!\!\!\perp}

\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\Var}{Var}

\title{Synthetic prediction methods for minimizing post shock forecasting error}
\author{Daniel J. Eck and Soheil Eshghi}
\date{May 2019}

\begin{document}

\maketitle
\begin{abstract}
    We seek to develop a forecasting methodology for time series data that is 
    thought to have undergone a shock which has origins that have not been 
    previously observed.  We still can provide credible forecasts for a time 
    series in the presence of such systematic shocks by drawing from disparate 
    time series that have undergone similar shocks for which post-shock 
    outcome data is recorded.  These disparate time series are assumed to have 
    mechanistic similarities to the time series under study but are otherwise 
    independent (Granger noncausal).  The inferential goal of our forecasting 
    methodology is to supplement observed time series data with post-shock 
    data from the disparate time series in order to minimize average forecast 
    risk. 
\end{abstract}

\section{Setting}
Suppose that an analyst is interested in forecasting a real-valued time series 
$y_1, y_2, \ldots$.  Given each time point $t \geq 1$, let $\x_t$ be the 
(possibly multivariate) information variable vector revealed prior to the 
observation of $y_t$.  To gauge the performance of a procedure that produces forecasts 
$\{\hat y_t, t= 1,2,\ldots\}$ given time horizon $T$, we consider the average 
forecast risk
$$
  R_T = \frac{1}{T}\sum_{t=1}^T\E(y_t - \hat y_t)^2
$$
in our analyses.

\section{Dynamic panel model}
\label{sec:dpm}
We consider a dynamic panel data model similar with autoregressive structure.  
For simplicity, we will consider the following simplified version with one covariate:
\begin{equation} \label{DPM}
  y_{i,t} = \eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i \x_{i,t} 
    + \varepsilon_{i,t}, 
\end{equation}
where $i = 1,\ldots,J+1$ and $t = 1,\ldots,T$ and $D_{i,t} = 1(t > T_i^*)$, 
$T_i^* < T$.  For simplicity we will assume that $T_i^* = T$ for all $i = 1$,
$\ldots$, $J$.  We will consider a simple random effects structure where 
\begin{align*}
  \eta_i &\overset{iid}{\sim} N(0, \sigma_\eta^2), 
    \qquad i = 1,\ldots J+1, \\
  \alpha_i &\overset{iid}{\sim} N(\mu_\alpha, \sigma_\alpha^2), 
    \qquad i = 1,\ldots J+1, \\
  \phi_i &\overset{iid}{\sim} U(-1,1), 
    \qquad i = 1,\ldots J+1, \\
  \theta_i &\overset{iid}{\sim} U(-1,1), 
    \qquad i = 1,\ldots J+1, \\
  \varepsilon_{i,t} &\overset{iid}{\sim} N(0, \sigma^2), 
    \qquad i = 1,\ldots J+1;\; t = 1, \ldots T, \\
  \eta &\indep \alpha \indep \phi \indep \theta \indep \varepsilon;
\end{align*}
Without loss of generality, we will suppose that we want to forecast for 
$y_{1, T^* + 1}$ where we have no observations for $y_{1,t}, t > T^*$. 
Inference about the random effects parameters is not of interest in this  
forecasting context.  Conditional on all regression parameters 
(except $\alpha$?), previous responses, and covariates, model \eqref{DPM} 
has distribution
$$
  y_{i,t} 
    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i\x_{i,t}, \sigma^2).
$$
All parameters will be estimated with OLS. In particular, let 
$\hat{\alpha}_i$, $i = 2,\ldots,J+1$ be the OLS estimate of $\alpha_i$ 
and define the adjusted $\alpha$ plugin estimator for time series $i=1$ by,
\begin{equation} \label{adjusted}
  \hat{\alpha}_{\text{adj}} = \frac{1}{J}\sum_{i=2}^{J+1}\hat{\alpha}_i
\end{equation}
where the $\hat{\alpha}_i$s are MLEs of all of the $\alpha_i$s.  
We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for the unknown 
$\alpha_1$ term for which no meaningful estimation information otherwise 
exists.

Consider the candidate forecasts: 
\begin{align*}
  &\text{Forecast 1}: \hat y_{1,T^*+1}^1 = \hat\eta_1 
    + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1}, \\
  &\text{Forecast 2}: \hat y_{1,T^*+1}^2 = \hat\eta_1 
    + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} + \hat{\alpha}_{\text{adj}},
\end{align*}
where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are MLEs of 
$\eta_1$, $\phi_1$, and $\theta_1$ respectively.  
The two forecasts do not differ in their predictions for 
$y_{t}$, $t = 1,\ldots T^*$.  They only differ in predicting $y_{T^*+1}$.  \\

{\bf We want to determine when either $\hat y_{1,T^*+1}^1$ or 
$\hat y_{1,T^*+1}^2$ minimizes the average forecast risk.}

The two forecasts do not differ in their predictions for 
$y_{t}$, $t = 1,\ldots T^*$.  They only differ in predicting 
$y_{T^*+1}$.  The forecast risk for $y_{T+1,2}$ is: 
\begin{align*}
  %&R_{T^*+1, 2} - R_{T^*, 2} = 
  &\E(\hat y_{1,T^*+1}^2 - y_{1,T^*+1}^2)^2 \\
  &\qquad= \E\left\{ \hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} 
    + \hat{\alpha}_{\text{adj}}
      - (\eta_1 + \phi_1 y_{1,T^*} + \theta_1 \x_{1,T^*+1} + \alpha_1 + \varepsilon_{1,T^*+1}) \right\}^2 \\
  &\qquad= \E\left\{ (\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1}     
      -\eta_1 - \phi_1 y_{1,T^*} - \theta_1 \x_{1,T^*+1} - \alpha_1 - \varepsilon_{1,T^*+1}) 
        + \hat{\alpha}_{\text{adj}} \right\}^2 \\      
  &\qquad= R_{T, 1} + \E(\hat{\alpha}_{\text{adj}}^2) - 2\E\left\{(\hat\eta_1 + \hat\phi_1 y_{1,T^*} 
    + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} - \theta_1 \x_{1,T^*+1} - \alpha_1 - \varepsilon_{1,T^*+1})
      \hat{\alpha}_{\text{adj}} \right\} \\
  &\qquad= R_{T, 1} + \E(\hat{\alpha}_{\text{adj}}^2) - 2\E(\hat{\alpha}_{\text{adj}})\E(\alpha_1) 
    - 2\E\left\{(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
      - \theta_1 \x_{1,T^*+1})\hat{\alpha}_{\text{adj}} \right\} \\
  &\qquad= R_{T, 1} + \Var(\hat{\alpha}_{\text{adj}}) - \mu_{\alpha}^2 
    - 2\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
      - \theta_1 \x_{1,T^*+1}\right)\mu_{\alpha},
\end{align*}
where 
$$
  \E(\hat{\alpha}_{\text{adj}}) = \E\left\{\E(\hat{\alpha}_{\text{adj}}| \Hist )\right\}
    = \E\left(\frac{1}{J}\sum_{i=2}^{J+1}\alpha_i\right) 
    = \mu_{\alpha},
$$
and 
$$
  \Hist = \{(\eta_i, \phi_i, \theta_i, \alpha_i, \x_{i,t}, y_{i,t}); 
    i = 2,\ldots,J+1, t = 1,\ldots,T\}.
$$
Define
$$
  \Hist_1 = \{\eta_1, \phi_1, \theta_1, \alpha_1, \x_{1,T^*+1}, (\x_{1,t}, y_{1,t});  
    t = 1,\ldots,T^*\}.
$$
Notice that 
\begin{align*}
  &\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
    - \theta_1 \x_{1,T^*+1}\right) \\
  &\qquad= \E\left\{\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
    - \theta_1 \x_{1,T^*+1}\right)|\Hist\cup\Hist_1\right\} = 0,
\end{align*}
(\textbf{is the above true?}) and that 
\begin{align*}
  \Var(\hat{\alpha}_{\text{adj}}) &= \E\left\{\Var(\hat{\alpha}_{\text{adj}}|\Hist)\right\} 
    + \Var\left\{\E(\hat{\alpha}_{\text{adj}}|\Hist)\right\} \\
  &= \E\left\{\Var(\hat{\alpha}_{\text{adj}}|\Hist)\right\} + \frac{\sigma_{\alpha}^2}{J} \\
  &= \frac{1}{J^2} \sum_{i=2}^{J+1} \E\left\{\Var(\hat{\alpha}_j|\Hist)\right\} + \frac{\sigma_{\alpha}^2}{J} \\
  &= \frac{1}{J^2(T-1)}\sum_{i=2}^{J+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_j)s_{\alpha_j}^2}\right\} 
    + \frac{\sigma_{\alpha}^2}{J},
\end{align*}
where $s_{e,j}^2$ is the estimated variance of model $j$, $R^2_{\alpha_j}$ is 
the multiple $R^2$ obtained from regressing the shock indicator $D$ on the 
other regressors, and $s_j^2$ is... .

Forecast 2 has lower forecast risk than Forecast 1 when,  
\begin{equation} \label{risk}
  \Var(\hat{\alpha}_{\text{adj}}) - \mu_{\alpha}^2 
    - 2\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
      - \theta_1 \x_{1,T^*+1}\right)\mu_{\alpha} < 0.
\end{equation}
Putting everything together, we see that \eqref{risk} is equivalent to
$$
  \frac{1}{J^2(T-1)}\sum_{i=2}^{J+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_j)s_{\alpha_j}^2}\right\} 
    + \frac{\sigma_{\alpha}^2}{J} < \mu_{\alpha}^2.
$$
Forecast 2 is preferable to Forecast 1 asymptotically in both $T$ and $J$ 
whenever $\mu_{\alpha} \neq 0$. In finite samples, Forecast 2 is preferable to 
Forecast 1 when the $\mu_{\alpha}$ is large relative to its variability and 
overall regression variability.

\section{Synthetic prediction via by synthetic control method}

{\bf Taken from Soheil's notes (begin).}
Assume we have covariate-observation pairs $(y_i, \x_i)$ for $n$ points, and 
that $\x_1$, the covariates of the intervened unit, lies within the convex hull 
of $(\x_i)_{i=1}^n$. One way to match covariates is to pick a vector $\w$ such 
that $\w'1=1$ and $\norm{\x_1 - \X\w}$, where $\X$ is the matrix of available 
covariates (arranged in column form), is minimized.

One can incorporate a notion of locality by penalizing the use of covariates 
far from the covariates of interest, through incorporating the following term 
in either a constraint or as part of the objective:
$\sum_{i=1}^n \w_i \norm{\x_1 - \x_i}$.

The use of the transformed linear model (linking covariates to observations of 
outcomes) to create the counterfactual show our belief in the model 
specification. Under these conditions, the prediction of the model for the 
outcome at covariates $\x_i$ based on all other observed covariates $\x_{-i}$ 
(if it is within the convex hull) should closely match its observed outcome.  
Any discrepancy should make us less confident in the observation of the 
outcome (if we hold the model specification to be correct), so we would want 
$y_i$ to play less of a role in the creation of the counterfactual in that 
scenario.  Thus, we will put an upper limit on $\w_i$, the weight assigned to 
the covariate-observation pair by a function of the discrepancy between $y_1$ 
and the created synthetic prediction for it $\hat{y}_i$ from $\x_{-i}$.  
{\bf Taken from Soheil's notes (end).} \\

%The question of how to minimize variance in the $Yw$ can be addressed in 
%multiple ways. One is to incorporate the weighted sample variance 
%(weighted by $w$) into a constraint or as part of the objective.  However, 
%this is not the right way to address this issue, as it abstracts out the 
%dependence on the covariates. Thus, it is likely that we will need to create a 
%covariate-weighted variance measure for the synthetic controls.
%{\bf Taken from Soheil's notes (end).}

Prediction via this synthetic control method can be applied to the dynamic 
panel models in Section~\ref{sec:dpm}.  In this case, the individual level 
shock effects $\alpha_i$ are correlated with the covariate information 
$\x_i$.  We consider the model 
\begin{equation} \label{shockmodel}
  \alpha_{i} = \mu_{\alpha_i} + \beta\x_i + \gamma_{i}
\end{equation}
for the shock effects, where $\gamma_{i}$ are iid with 
$\E(\gamma_i) = 0$ and $\Var(\gamma_i) = \sigma^2_\gamma$ and are 
independent of all other random effects.  
The specification in \eqref{shockmodel} can be substitutes into the dynamic 
panel model \eqref{DPM} which yields,
\begin{align*} 
  y_{i,t} &= \eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i \x_{i,t} 
    + \varepsilon_{i,t} \\
  &= \eta_i + (\mu_{\alpha_i} + \beta\x_i + \gamma_{i})D_{i,t} 
    + \phi_i y_{i,t-1} + \theta_i \x_{i,t} + \varepsilon_{i,t} \\
  &= (\eta_i + \mu_{\alpha_i}D_{i,t}) + \phi_i y_{i,t-1} 
    + (\theta_i + \beta D_{i,t})\x_{i,t} + (\gamma_{i}D_{i,t} 
    + \varepsilon_{i,t}) \\
  &= \tilde\eta_i + \phi_i y_{i,t-1} + \tilde\beta_{i,t}\x_{i,t} + \tilde\varepsilon_{i,t},
\end{align*}
where $\tilde\eta_i \sim N(\mu_{\alpha_i},\sigma^2_\eta)$ 
and $\tilde\varepsilon_{i,t} \sim N(0, \sigma^2 + D_{i,t}\sigma^2_\gamma)$.

\end{document}

### 2019-08-22 eck2019syntheticprediction.tex
fixed typo
Adding in comments on the synthetic control notes
I added some notation and formalized the optimization problem. I also put in notes with some questions.

@@
 \usepackage{geometry}
+\usepackage[usenames]{color}
 \geometry{margin=1in}
@@
 \newcommand{\X}{\textbf{X}}
+\newcommand{\Y}{\textbf{Y}}
 \newcommand{\Hist}{\mathcal{H}}
@@
 \DeclareMathOperator{\Var}{Var}
+
+\newcommand\red[1]{{\color{red}#1}}
 
@@
 The two forecasts do not differ in their predictions for 
-$y_{t}$, $t = 1,\ldots T^*$.  They only differ in predicting 
+$y_{t}$, $t = 1,\ldots T^*$. \red{repetition.}  They only differ in predicting 
 $y_{T^*+1}$.  The forecast risk for $y_{T+1,2}$ is: 
@@
 
-\section{Synthetic prediction via by synthetic control method}
+\section{Synthetic prediction via synthetic control method}
 
@@
 
+This leads to the following optimization problem:
+\begin{align*}
+\min_{\w} ~~~& \norm{\x_1 - \X\w}\\
+\text{s.t.}~~~& \w'1=1,\\
+& \sum_{i=1}^n \w_i\norm{\x_1 - \x_i} \leq \delta, \\
+& \text{Var}(\Y\w)\leq \gamma,
+\end{align*}
+with $\delta$ and $\gamma$ being rightsizing parameters.
+
+We can simplify the above using the following assumptions:
+
+\ldots
+\red{Once I have time I will write these out so that e can extract the fixed values mostly to one side.}
+
+\red{The rest is kind of bad as is, to be honest, and hard to justify.
+I still think we should weigh down the ones that are pretty far from the expected value, but it's not clear why the variance condition above will not be enough and we have to do a prediction model for all $(n-1)-$ tuples.
+Any ideas?}
+
 The use of the transformed linear model (linking covariates to observations of 
@@
 the covariate-observation pair by a function of the discrepancy between $y_1$ 
-and the created synthetic prediction for it $\hat{y}_i$ from $\x_{-i}$.  
+and the created synthetic prediction for it $\hat{y}_i$ from $\x_{-i}$, i.e.,
+
 {\bf Taken from Soheil's notes (end).} \\

### 2019-11-26 Notes-on-synthetic-prediction.tex
reorganized content; generalized regression result; moved synthetic weighting notes to a separate document

--- 2019-08-22 eck2019syntheticprediction.tex
@@
 \usepackage{amsmath}
+\usepackage{natbib}
 
@@
 
-\section{Dynamic panel model}
+\section{Motivating example: Dynamic panel model}
 \label{sec:dpm}
-We consider a dynamic panel data model similar with autoregressive structure.  
-For simplicity, we will consider the following simplified version with one covariate:
+
+To fix ideas we consider a dynamic panel data model with autoregressive 
+structure in \citet{blundell1998initial} without present time period covariate 
+information and with a single covariate.  We consider an additional shock 
+effect whose presence is given by the binary variable $D_{i,t}$.  Our dynamic 
+panel model is  
 \begin{equation} \label{DPM}
@@
 \end{align*}
-Without loss of generality, we will suppose that we want to forecast for 
-$y_{1, T^* + 1}$ where we have no observations for $y_{1,t}, t > T^*$. 
-Inference about the random effects parameters is not of interest in this  
-forecasting context.  Conditional on all regression parameters 
+
+Our first goal is to evaluate the forecast risk of competing forecasts which 
+offer predicts for $y_{1, T^* + 1}$, the response observed after the first 
+post shock time period for subject 1.  The difficulty in this forecast stems 
+from not observing $\alpha_1$ and not having any readily infromation available 
+to estimate it directly.  We show that there is a balance between $\mu_\alpha$ 
+and $\sigma_\alpha^2$ that allows us to lower the forecast risk for 
+$y_{1, T^* + 1}$ by incorporating what is known about the other $\alpha_i$s 
+when such information is available.
+
+Conditional on all regression parameters 
 (except $\alpha$?), previous responses, and covariates, model \eqref{DPM} 
@@
 $$
-All parameters will be estimated with OLS. In particular, let 
+All parameters in this model will be estimated with OLS. In particular, let 
 $\hat{\alpha}_i$, $i = 2,\ldots,J+1$ be the OLS estimate of $\alpha_i$ 
@@
 $\eta_1$, $\phi_1$, and $\theta_1$ respectively.  
-The two forecasts do not differ in their predictions for 
+The first forecast ignores the information about the distribution of 
+$\alpha_1$ while the second forecast incorporates an estimate of $\mu_\alpha$ 
+that is obtained from the other individual forecasts under study.  
+Note that the two forecasts do not differ in their predictions for 
 $y_{t}$, $t = 1,\ldots T^*$.  They only differ in predicting $y_{T^*+1}$.  \\
 
-{\bf We want to determine when either $\hat y_{1,T^*+1}^1$ or 
-$\hat y_{1,T^*+1}^2$ minimizes the average forecast risk.}
+We want to determine when either $\hat y_{1,T^*+1}^1$ or $\hat y_{1,T^*+1}^2$ 
+minimizes the forecast risk for $\hat y_{1,T^*+1}$.
 
-The two forecasts do not differ in their predictions for 
-$y_{t}$, $t = 1,\ldots T^*$. \red{repetition.}  They only differ in predicting 
-$y_{T^*+1}$.  The forecast risk for $y_{T+1,2}$ is: 
+The forecast risk for $y_{T+1,2}$ is: 
 \begin{align*}
@@
 
+\bibliographystyle{plainnat}
+\bibliography{synthetic-prediction-notes}
+
 \end{document}

### 2019-11-26 eck2019syntheticprediction.tex
reorganized content; generalized regression result; moved synthetic weighting notes to a separate document

--- 2019-06-13 eck2019syntheticprediction.tex
@@
 \usepackage{amsmath}
+\usepackage{natbib}
 
 \usepackage{geometry}
+\usepackage[usenames]{color}
 \geometry{margin=1in}
@@
 
-\title{Synthetic prediction methods for minimizing post shock forecasting error}
-\author{Daniel J. Eck and Soheil Eshghi}
+\newcommand\red[1]{{\color{red}#1}}
+
+\title{Minimizing post shock forecasting error using disparate information}
+\author{Daniel J. Eck}
 \date{May 2019}
@@
 \label{sec:dpm}
-We consider a dynamic panel data model similar with autoregressive structure.  
-For simplicity, we will consider the following simplified version with one covariate:
+
+To fix ideas we consider a similar dynamic panel data model with autoregressive 
+structure in \citet{blundell1998initial} %without past time period covariate 
+%information and with a single present time covariate.  
+We consider an additional shock effect whose presence is given by the binary 
+variable $D_{i,t}$.  Our dynamic panel model is  
 \begin{equation} \label{DPM}
-  y_{i,t} = \eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i \x_{i,t} 
-    + \varepsilon_{i,t}, 
+  y_{i,t} = \eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i' \x_{i,t} + 
+    \beta_i' \x_{i,t-1} + \varepsilon_{i,t},  
 \end{equation}
 where $i = 1,\ldots,J+1$ and $t = 1,\ldots,T$ and $D_{i,t} = 1(t > T_i^*)$, 
-$T_i^* < T$.  For simplicity we will assume that $T_i^* = T$ for all $i = 1$,
-$\ldots$, $J$.  We will consider a simple random effects structure where 
+$T_i^* < T$.  We will consider a simple random effects structure where,  
+%\begin{align*}
+%  \eta_i &\overset{iid}{\sim} N(0, \sigma_\eta^2), 
+%    \qquad i = 1,\ldots J+1, \\
+%  \alpha_i &\overset{iid}{\sim} N(\mu_\alpha, \sigma_\alpha^2), 
+%    \qquad i = 1,\ldots J+1, \\
+%  \phi_i &\overset{iid}{\sim} U(-1,1), 
+%    \qquad i = 1,\ldots J+1, \\
+%  \theta_i &\overset{iid}{\sim} N(0, \Sigma_\theta), 
+%    \qquad i = 1,\ldots J+1, \\
+%  \beta_i &\overset{iid}{\sim} N(0, \Sigma_\beta), 
+%    \qquad i = 1,\ldots J+1, \\
+%  \varepsilon_{i,t} &\overset{iid}{\sim} N(0, \sigma^2), 
+%    \qquad i = 1,\ldots J+1;\; t = 1, \ldots T, \\
+%  \eta &\indep \alpha \indep \phi \indep \theta \indep \varepsilon;
+%\end{align*}
 \begin{align*}
-  \eta_i &\overset{iid}{\sim} N(0, \sigma_\eta^2), 
+  \eta_i &\overset{iid}{\sim} \eta,\; \text{where}\; \E(\eta) = 0,\; \Var(\eta) = \sigma_\eta^2, 
     \qquad i = 1,\ldots J+1, \\
-  \alpha_i &\overset{iid}{\sim} N(\mu_\alpha, \sigma_\alpha^2), 
+  \alpha_i &\overset{iid}{\sim} \alpha,\; \text{where}\; \E(\alpha) = \mu_\alpha,\; 
+    \Var(\alpha) = \sigma_\alpha^2, \qquad i = 1,\ldots J+1, \\
+  \phi_i &\overset{iid}{\sim} \phi,\; \text{where}\; |\phi| < 1, 
     \qquad i = 1,\ldots J+1, \\
-  \phi_i &\overset{iid}{\sim} U(-1,1), 
-    \qquad i = 1,\ldots J+1, \\
-  \theta_i &\overset{iid}{\sim} U(-1,1), 
-    \qquad i = 1,\ldots J+1, \\
+  \theta_i &\overset{iid}{\sim} \theta,\; \text{where}\; \E(\theta) = 0,\; 
+    \Var(\theta) = \Sigma_\theta^2, \qquad i = 1,\ldots J+1, \\
+  \beta_i &\overset{iid}{\sim} \beta,\; \text{where}\; \E(\beta) = 0,\; 
+    \Var(\beta) = \Sigma_\beta^2, \qquad i = 1,\ldots J+1, \\    
   \varepsilon_{i,t} &\overset{iid}{\sim} N(0, \sigma^2), 
@@
 \end{align*}
-Without loss of generality, we will suppose that we want to forecast for 
-$y_{1, T^* + 1}$ where we have no observations for $y_{1,t}, t > T^*$. 
-Inference about the random effects parameters is not of interest in this  
-forecasting context.  Conditional on all regression parameters 
-(except $\alpha$?), previous responses, and covariates, model \eqref{DPM} 
-has distribution
+
+Our first goal is to evaluate the forecast risk of competing forecasts which 
+offer predicts for $y_{1, T_1^* + 1}$, the response observed after the first 
+post shock time period for subject 1.  The difficulty in this forecast stems 
+from not observing $\alpha_1$ and not having any readily infromation available 
+to estimate it directly.  We show that there is a balance between $\mu_\alpha$ 
+and $\sigma_\alpha^2$ that allows us to lower the forecast risk for 
+$y_{1, T_1^* + 1}$ by incorporating what is known about the other $\alpha_i$s 
+when such information is available.
+
+Conditional on all regression parameters, previous responses, and covariates, 
+model \eqref{DPM} has distribution 
 $$
   y_{i,t} 
-    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i\x_{i,t}, \sigma^2).
+    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
+      + \beta_i'\x_{i,t-1}, \sigma^2).
 $$
-All parameters will be estimated with OLS. In particular, let 
-$\hat{\alpha}_i$, $i = 2,\ldots,J+1$ be the OLS estimate of $\alpha_i$ 
-and define the adjusted $\alpha$ plugin estimator for time series $i=1$ by,
+All parameters in this model will be estimated with OLS using historical data. 
+In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, J+1$ be the OLS estimate 
+of $\alpha_i$ and define the adjusted $\alpha$ plugin estimator for time 
+series $i=1$ by,
 \begin{equation} \label{adjusted}
@@
 \begin{align*}
-  &\text{Forecast 1}: \hat y_{1,T^*+1}^1 = \hat\eta_1 
-    + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1}, \\
-  &\text{Forecast 2}: \hat y_{1,T^*+1}^2 = \hat\eta_1 
-    + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} + \hat{\alpha}_{\text{adj}},
+  &\text{Forecast 1}: \hat y_{1,T_1^*+1}^1 = \hat\eta_1 
+    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
+    + \hat\beta_1'\x_{1,T_1^*}, \\
+  &\text{Forecast 2}: \hat y_{1,T_1^*+1}^2 = \hat\eta_1 
+    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
+    + \hat\beta_1'\x_{1,T_1^*} + \hat{\alpha}_{\text{adj}},
 \end{align*}
-where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are MLEs of 
-$\eta_1$, $\phi_1$, and $\theta_1$ respectively.  
-The two forecasts do not differ in their predictions for 
-$y_{t}$, $t = 1,\ldots T^*$.  They only differ in predicting $y_{T^*+1}$.  \\
+where $\hat\eta_1$, $\hat\phi_1$, $\hat\theta_1$, and $\hat\beta_1$ are MLEs 
+of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$ respectively.  
+The first forecast ignores the information about the distribution of 
+$\alpha_1$ while the second forecast incorporates an estimate of $\mu_\alpha$ 
+that is obtained from the other individual forecasts under study.  
+Note that the two forecasts do not differ in their predictions for 
+$y_{1,t}$, $t = 1,\ldots T_1^*$.  They only differ in predicting 
+$y_{1,T_1^*+1}$.  We want to determine when either $\hat y_{1,T_1^*+1}^1$ or 
+$\hat y_{1,T_1^*+1}^2$ minimizes the forecast risk for $\hat y_{1,T_1^*+1}$.  
+Let $R_{T_1^*+1, k} = \E(\hat y_{1,T_1^*+1}^k - y_{1,T_1^*+1}^k)^2$, 
+where $k = 1,2$.  \\
 
-{\bf We want to determine when either $\hat y_{1,T^*+1}^1$ or 
-$\hat y_{1,T^*+1}^2$ minimizes the average forecast risk.}
-
-The two forecasts do not differ in their predictions for 
-$y_{t}$, $t = 1,\ldots T^*$.  They only differ in predicting 
-$y_{T^*+1}$.  The forecast risk for $y_{T+1,2}$ is: 
+The forecast risk for $y_{1,T^*_1+1}^2$ is: 
 \begin{align*}
-  %&R_{T^*+1, 2} - R_{T^*, 2} = 
-  &\E(\hat y_{1,T^*+1}^2 - y_{1,T^*+1}^2)^2 \\
-  &\qquad= \E\left\{ \hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} 
-    + \hat{\alpha}_{\text{adj}}
-      - (\eta_1 + \phi_1 y_{1,T^*} + \theta_1 \x_{1,T^*+1} + \alpha_1 + \varepsilon_{1,T^*+1}) \right\}^2 \\
-  &\qquad= \E\left\{ (\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1}     
-      -\eta_1 - \phi_1 y_{1,T^*} - \theta_1 \x_{1,T^*+1} - \alpha_1 - \varepsilon_{1,T^*+1}) 
-        + \hat{\alpha}_{\text{adj}} \right\}^2 \\      
-  &\qquad= R_{T, 1} + \E(\hat{\alpha}_{\text{adj}}^2) - 2\E\left\{(\hat\eta_1 + \hat\phi_1 y_{1,T^*} 
-    + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} - \theta_1 \x_{1,T^*+1} - \alpha_1 - \varepsilon_{1,T^*+1})
-      \hat{\alpha}_{\text{adj}} \right\} \\
-  &\qquad= R_{T, 1} + \E(\hat{\alpha}_{\text{adj}}^2) - 2\E(\hat{\alpha}_{\text{adj}})\E(\alpha_1) 
-    - 2\E\left\{(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
-      - \theta_1 \x_{1,T^*+1})\hat{\alpha}_{\text{adj}} \right\} \\
-  &\qquad= R_{T, 1} + \Var(\hat{\alpha}_{\text{adj}}) - \mu_{\alpha}^2 
-    - 2\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
-      - \theta_1 \x_{1,T^*+1}\right)\mu_{\alpha},
+  &R_{T_1^*+1, 2} = \E(\hat y_{1,T_1^*+1}^2 - y_{1,T_1^*+1}^2)^2 \\
+    &\qquad= \E\left\{ \hat\eta_1 + \hat\phi_1 y_{1,T_1^*} 
+      + \hat\theta_1'\x_{1,T_1^*+1} + \hat\beta_1'\x_{1,T_1^*} 
+      + \hat{\alpha}_{\text{adj}}\right. \\
+        &\qquad\qquad\left.- (\eta_1 + \phi_1 y_{1,T_1^*} + \theta_1'\x_{1,T_1^*+1} 
+          + \beta_1'\x_{1,T_1^*} + \alpha_1 + \varepsilon_{1,T_1^*+1}) \right\}^2 \\
+    &\qquad= \E\left\{ (\hat\eta_1 + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
+      + \hat\beta_1'\x_{1,T_1^*} - \eta_1 - \phi_1 y_{1,T_1^*}\right. \\ 
+        &\qquad\qquad\left.- \theta_1'\x_{1,T_1^*+1} - \beta_1'\x_{1,T_1^*} 
+          - \alpha_1 - \varepsilon_{1,T_1^*+1}) + \hat{\alpha}_{\text{adj}} \right\}^2 \\      
+    &\qquad= R_{T_1^*+1, 1} + \E(\hat{\alpha}_{\text{adj}}^2) - 2\E\left\{(\hat\eta_1 
+      + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1}\right. \\
+        &\qquad\qquad\left. + \hat\beta_1'\x_{1,T_1^*} - \eta_1 - \phi_1 y_{1,T_1^*} 
+          - \theta_1'\x_{1,T_1^*+1} - \beta_1'\x_{1,T_1^*} - \alpha_1 
+          - \varepsilon_{1,T_1^*+1})\hat{\alpha}_{\text{adj}} \right\} \\
+    &\qquad= R_{T_1^*+1, 1} + \E(\hat{\alpha}_{\text{adj}}^2) 
+      - 2\E(\hat{\alpha}_{\text{adj}})\E(\alpha_1) \\
+      &\qquad\qquad- 2\E\left\{(\hat\eta_1 + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
+        + \hat\beta_1'\x_{1,T_1^*} - \eta_1 - \phi_1 y_{1,T_1^*} 
+        - \theta_1'\x_{1,T_1^*+1} - \beta_1'\x_{1,T_1^*})\hat{\alpha}_{\text{adj}} \right\} \\
+    &\qquad= R_{T_1^*+1, 1} + \Var(\hat{\alpha}_{\text{adj}}) - \mu_{\alpha}^2 \\
+      &\qquad\qquad- 2\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T_1^*} 
+        + \hat\theta_1'\x_{1,T_1^*+1} + \hat\beta_1'\x_{1,T_1^*} - \eta_1 - \phi_1 y_{1,T_1^*} 
+        - \theta_1'\x_{1,T_1^*+1} - \beta_1'\x_{1,T_1^*}\right)\mu_{\alpha},
 \end{align*}
@@
 $$
-  \Hist = \{(\eta_i, \phi_i, \theta_i, \alpha_i, \x_{i,t}, y_{i,t}); 
-    i = 2,\ldots,J+1, t = 1,\ldots,T\}.
+  \Hist = \{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \x_{i,t}, y_{i,t}); 
+    t = 1,\ldots,T_i, i = 2,\ldots,J+1\}.
 $$
@@
 $$
-  \Hist_1 = \{\eta_1, \phi_1, \theta_1, \alpha_1, \x_{1,T^*+1}, (\x_{1,t}, y_{1,t});  
-    t = 1,\ldots,T^*\}.
+  \Hist_1 = \{\eta_1, \phi_1, \theta_1, \beta_1, \alpha_1, 
+    \x_{1,T_1^*+1}, (\x_{1,t}, y_{1,t});  t = 1,\ldots,T_1^*\},
 $$
-Notice that 
+and observe that 
 \begin{align*}
-  &\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
-    - \theta_1 \x_{1,T^*+1}\right) \\
-  &\qquad= \E\left\{\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
-    - \theta_1 \x_{1,T^*+1}\right)|\Hist\cup\Hist_1\right\} = 0,
+  &\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
+    + \hat\beta_1'\x_{1,T_1^*} - \eta_1 - \phi_1 y_{1,T_1^*} 
+    - \theta_1'\x_{1,T_1^*+1} - \beta_1'\x_{1,T_1^*}\right) \\
+  &= \E\left\{\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T_1^*} 
+    + \hat\theta_1'\x_{1,T_1^*+1} + \hat\beta_1'\x_{1,T_1^*} - \eta_1 
+    - \phi_1 y_{1,T_1^*} - \theta_1'\x_{1,T_1^*+1} 
+    - \beta_1'\x_{1,T_1^*}\right)|\Hist_1\right\} \\
+  &= 0,
 \end{align*}
-(\textbf{is the above true?}) and that 
+and that 
 \begin{align*}
-  \Var(\hat{\alpha}_{\text{adj}}) &= \E\left\{\Var(\hat{\alpha}_{\text{adj}}|\Hist)\right\} 
+  &\Var(\hat{\alpha}_{\text{adj}}) = \E\left\{\Var(\hat{\alpha}_{\text{adj}}|\Hist)\right\} 
     + \Var\left\{\E(\hat{\alpha}_{\text{adj}}|\Hist)\right\} \\
-  &= \E\left\{\Var(\hat{\alpha}_{\text{adj}}|\Hist)\right\} + \frac{\sigma_{\alpha}^2}{J} \\
-  &= \frac{1}{J^2} \sum_{i=2}^{J+1} \E\left\{\Var(\hat{\alpha}_j|\Hist)\right\} + \frac{\sigma_{\alpha}^2}{J} \\
-  &= \frac{1}{J^2(T-1)}\sum_{i=2}^{J+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_j)s_{\alpha_j}^2}\right\} 
+    %= \E\left\{\Var(\hat{\alpha}_{\text{adj}}|\Hist)\right\} 
+    %+ \frac{\sigma_{\alpha}^2}{J} \\
+  &\qquad= \frac{1}{J^2} \sum_{i=2}^{J+1} \E\left\{\Var(\hat{\alpha}_i|\Hist)\right\} 
+    + \frac{\sigma_{\alpha}^2}{J} \\
+  &\qquad= \frac{1}{J^2(T-1)}\sum_{i=2}^{J+1} 
+    \E\left\{\frac{s_{e,i}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
       + \frac{\sigma_{\alpha}^2}{J},
 \end{align*}
-where $s_{e,j}^2$ is the estimated variance of model $j$, $R^2_{\alpha_j}$ is 
+where $s_{e,i}^2$ is the estimated variance of model $i$, $R^2_{\alpha_i}$ is 
 the multiple $R^2$ obtained from regressing the shock indicator $D$ on the 
-other regressors, and $s_j^2$ is... .
+other regressors, and $s_{\alpha_i}^2$ is... .
 
 Forecast 2 has lower forecast risk than Forecast 1 when,  
-\begin{equation} \label{risk}
-  \Var(\hat{\alpha}_{\text{adj}}) - \mu_{\alpha}^2 
-    - 2\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1 \x_{1,T^*+1} -\eta_1 - \phi_1 y_{1,T^*} 
-      - \theta_1 \x_{1,T^*+1}\right)\mu_{\alpha} < 0.
-\end{equation}
-Putting everything together, we see that \eqref{risk} is equivalent to
+$
+  \Var(\hat{\alpha}_{\text{adj}}) 
+    %- 2\E\left(\hat\eta_1 + \hat\phi_1 y_{1,T^*} + \hat\theta_1'\x_{1,T^*+1} 
+    %+ \hat\beta_1'\x_{1,T^*} - \eta_1 - \phi_1 y_{1,T^*} - \theta_1'\x_{1,T^*+1}
+    %- \beta_1'\x_{1,T^*}\right)\mu_{\alpha} 
+    < \mu_{\alpha}^2.
+$
+Putting everything together, we see that Forecast 2 has lower forecast risk 
+than Forecast 1 when 
 $$
-  \frac{1}{J^2(T-1)}\sum_{i=2}^{J+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_j)s_{\alpha_j}^2}\right\} 
+  \frac{1}{J^2(T-1)}\sum_{i=2}^{J+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
     + \frac{\sigma_{\alpha}^2}{J} < \mu_{\alpha}^2.
@@
 
-\section{Synthetic prediction via by synthetic control method}
-
-{\bf Taken from Soheil's notes (begin).}
-Assume we have covariate-observation pairs $(y_i, \x_i)$ for $n$ points, and 
-that $\x_1$, the covariates of the intervened unit, lies within the convex hull 
-of $(\x_i)_{i=1}^n$. One way to match covariates is to pick a vector $\w$ such 
-that $\w'1=1$ and $\norm{\x_1 - \X\w}$, where $\X$ is the matrix of available 
-covariates (arranged in column form), is minimized.
-
-One can incorporate a notion of locality by penalizing the use of covariates 
-far from the covariates of interest, through incorporating the following term 
-in either a constraint or as part of the objective:
-$\sum_{i=1}^n \w_i \norm{\x_1 - \x_i}$.
-
-The use of the transformed linear model (linking covariates to observations of 
-outcomes) to create the counterfactual show our belief in the model 
-specification. Under these conditions, the prediction of the model for the 
-outcome at covariates $\x_i$ based on all other observed covariates $\x_{-i}$ 
-(if it is within the convex hull) should closely match its observed outcome.  
-Any discrepancy should make us less confident in the observation of the 
-outcome (if we hold the model specification to be correct), so we would want 
-$y_i$ to play less of a role in the creation of the counterfactual in that 
-scenario.  Thus, we will put an upper limit on $\w_i$, the weight assigned to 
-the covariate-observation pair by a function of the discrepancy between $y_1$ 
-and the created synthetic prediction for it $\hat{y}_i$ from $\x_{-i}$.  
-{\bf Taken from Soheil's notes (end).} \\
-
-%The question of how to minimize variance in the $Yw$ can be addressed in 
-%multiple ways. One is to incorporate the weighted sample variance 
-%(weighted by $w$) into a constraint or as part of the objective.  However, 
-%this is not the right way to address this issue, as it abstracts out the 
-%dependence on the covariates. Thus, it is likely that we will need to create a 
-%covariate-weighted variance measure for the synthetic controls.
-%{\bf Taken from Soheil's notes (end).}
-
-Prediction via this synthetic control method can be applied to the dynamic 
-panel models in Section~\ref{sec:dpm}.  In this case, the individual level 
-shock effects $\alpha_i$ are correlated with the covariate information 
-$\x_i$.  We consider the model 
-\begin{equation} \label{shockmodel}
-  \alpha_{i} = \mu_{\alpha_i} + \beta\x_i + \gamma_{i}
-\end{equation}
-for the shock effects, where $\gamma_{i}$ are iid with 
-$\E(\gamma_i) = 0$ and $\Var(\gamma_i) = \sigma^2_\gamma$ and are 
-independent of all other random effects.  
-The specification in \eqref{shockmodel} can be substitutes into the dynamic 
-panel model \eqref{DPM} which yields,
-\begin{align*} 
-  y_{i,t} &= \eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i \x_{i,t} 
-    + \varepsilon_{i,t} \\
-  &= \eta_i + (\mu_{\alpha_i} + \beta\x_i + \gamma_{i})D_{i,t} 
-    + \phi_i y_{i,t-1} + \theta_i \x_{i,t} + \varepsilon_{i,t} \\
-  &= (\eta_i + \mu_{\alpha_i}D_{i,t}) + \phi_i y_{i,t-1} 
-    + (\theta_i + \beta D_{i,t})\x_{i,t} + (\gamma_{i}D_{i,t} 
-    + \varepsilon_{i,t}) \\
-  &= \tilde\eta_i + \phi_i y_{i,t-1} + \tilde\beta_{i,t}\x_{i,t} + \tilde\varepsilon_{i,t},
-\end{align*}
-where $\tilde\eta_i \sim N(\mu_{\alpha_i},\sigma^2_\eta)$ 
-and $\tilde\varepsilon_{i,t} \sim N(0, \sigma^2 + D_{i,t}\sigma^2_\gamma)$.
+\bibliographystyle{plainnat}
+\bibliography{synthetic-prediction-notes}
 

### 2019-11-26 eck2019syntheticprediction.tex
updated Introduction and references

@@
 \usepackage[utf8]{inputenc}
+
 \usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amsfonts}
+%\usepackage{amscd}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{mathtools}
 \usepackage{natbib}
+\usepackage{url}
 
@@
 
+\newtheorem{cor}{Corollary}
+\newtheorem{lem}{Lemma}
+\newtheorem{thm}{Theorem}
+\newtheorem{defn}{Definition}
+\newtheorem{prop}{Proposition}
+
 \newcommand\red[1]{{\color{red}#1}}
@@
 \begin{abstract}
-    We seek to develop a forecasting methodology for time series data that is 
+    We develop a forecasting methodology for time series data that is 
     thought to have undergone a shock which has origins that have not been 
@@
 
+\section{Introduction}
+The technique of combining forecasts to lower forecast error has a rich 
+history \citep{bates1969combination, mundlak1978pooling, 
+  timmermann2006forecast, granger2014forecasting}.  
+The Introduction of \citet{timmermann2006forecast} provided several reasons 
+for combining forecasts.  In particular: 
+1) the information set underlying individual forecasts is often unobserved to 
+the forecast user; 2) different individual forecasts may be very differently 
+affected by non-stationarities and model misspecifications; 3) different 
+individual forecasts may be motivated by different loss functions 
+\citep[and references therein]{timmermann2006forecast}.
+
+In this article we propse a new setting for the classic forecast combination 
+problem.  We will suppose that a time series of interest has recently 
+undergone a structural shock that is not similar to anything observed in its 
+past, and we desire reliable post-shock forecasts in this setting.  It is 
+unlikely that any forecast that previously gave successful predictions for  
+the time series of interest will be able to accomondate the recent structural 
+shock.  However, it may be the case that disparate time series have previously 
+undergone similar structural shocks.  When this is so, one may be able to 
+aggreagate the post-shock information from these disparate time series to aid 
+the post-shock forecast for the time series under investigation.
+
 \section{Setting}
-Suppose that an analyst is interested in forecasting a real-valued time series 
-$y_1, y_2, \ldots$.  Given each time point $t \geq 1$, let $\x_t$ be the 
-(possibly multivariate) information variable vector revealed prior to the 
-observation of $y_t$.  To gauge the performance of a procedure that produces forecasts 
-$\{\hat y_t, t= 1,2,\ldots\}$ given time horizon $T$, we consider the average 
-forecast risk
+
+We will suppose that an analyst has time series data ($y_{i,t}$,$\x_{i,t}$), 
+$t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a 
+scalar response and $\x_{i,t}$ is a vector of covariates that revealed prior 
+to the observation of $y_{1,t}$.  Suppose that the analyst is interested in 
+forecasting $y_{1,t}$, the first time series in the collection.
+%$y_1, y_2, \ldots$.  
+%Given each time point $t \geq 1$, let $\x_{1,t}$ be a vector of covariates 
+%revealed prior to the observation of $y_{1,t}$.  
+To gauge the performance of a procedure that produces forecasts 
+$\{\hat y_{1,t}, t= 1,2,\ldots\}$ given time horizon $T_1$, we consider the 
+average forecast risk
 $$
-  R_T = \frac{1}{T}\sum_{t=1}^T\E(y_t - \hat y_t)^2
+  R_T = \frac{1}{T}\sum_{t=1}^T\E(\hat y_{1,t} - y_{1,t})^2
 $$
@@
 \end{equation}
-where $i = 1,\ldots,J+1$ and $t = 1,\ldots,T$ and $D_{i,t} = 1(t > T_i^*)$, 
-$T_i^* < T$.  We will consider a simple random effects structure where,  
+where $t = 1,\ldots,T_i$, $i = 1,\ldots, n+1$, and $D_{i,t} = 1(t > T_i^*)$, 
+$T_i^* < T_i$.  We will consider a simple random effects structure where,  
 %\begin{align*}
 %  \eta_i &\overset{iid}{\sim} N(0, \sigma_\eta^2), 
-%    \qquad i = 1,\ldots J+1, \\
+%    \qquad i = 1,\ldots n+1, \\
 %  \alpha_i &\overset{iid}{\sim} N(\mu_\alpha, \sigma_\alpha^2), 
-%    \qquad i = 1,\ldots J+1, \\
+%    \qquad i = 1,\ldots n+1, \\
 %  \phi_i &\overset{iid}{\sim} U(-1,1), 
-%    \qquad i = 1,\ldots J+1, \\
+%    \qquad i = 1,\ldots n+1, \\
 %  \theta_i &\overset{iid}{\sim} N(0, \Sigma_\theta), 
-%    \qquad i = 1,\ldots J+1, \\
+%    \qquad i = 1,\ldots n+1, \\
 %  \beta_i &\overset{iid}{\sim} N(0, \Sigma_\beta), 
-%    \qquad i = 1,\ldots J+1, \\
+%    \qquad i = 1,\ldots n+1, \\
 %  \varepsilon_{i,t} &\overset{iid}{\sim} N(0, \sigma^2), 
-%    \qquad i = 1,\ldots J+1;\; t = 1, \ldots T, \\
+%    \qquad i = 1,\ldots n+1;\; t = 1, \ldots T, \\
 %  \eta &\indep \alpha \indep \phi \indep \theta \indep \varepsilon;
@@
   \eta_i &\overset{iid}{\sim} \eta,\; \text{where}\; \E(\eta) = 0,\; \Var(\eta) = \sigma_\eta^2, 
-    \qquad i = 1,\ldots J+1, \\
+    \qquad i = 1,\ldots n+1, \\
   \alpha_i &\overset{iid}{\sim} \alpha,\; \text{where}\; \E(\alpha) = \mu_\alpha,\; 
-    \Var(\alpha) = \sigma_\alpha^2, \qquad i = 1,\ldots J+1, \\
+    \Var(\alpha) = \sigma_\alpha^2, \qquad i = 1,\ldots n+1, \\
   \phi_i &\overset{iid}{\sim} \phi,\; \text{where}\; |\phi| < 1, 
-    \qquad i = 1,\ldots J+1, \\
+    \qquad i = 1,\ldots n+1, \\
   \theta_i &\overset{iid}{\sim} \theta,\; \text{where}\; \E(\theta) = 0,\; 
-    \Var(\theta) = \Sigma_\theta^2, \qquad i = 1,\ldots J+1, \\
+    \Var(\theta) = \Sigma_\theta^2, \qquad i = 1,\ldots n+1, \\
   \beta_i &\overset{iid}{\sim} \beta,\; \text{where}\; \E(\beta) = 0,\; 
-    \Var(\beta) = \Sigma_\beta^2, \qquad i = 1,\ldots J+1, \\    
+    \Var(\beta) = \Sigma_\beta^2, \qquad i = 1,\ldots n+1, \\    
   \varepsilon_{i,t} &\overset{iid}{\sim} N(0, \sigma^2), 
-    \qquad i = 1,\ldots J+1;\; t = 1, \ldots T, \\
+    \qquad t = 1, \ldots T_i,\; i = 1,\ldots n+1; \\
   \eta &\indep \alpha \indep \phi \indep \theta \indep \varepsilon;
@@
 Conditional on all regression parameters, previous responses, and covariates, 
-model \eqref{DPM} has distribution 
+the response variable $y_{i,t}$ in model \eqref{DPM} has distribution 
 $$
@@
 $$
-All parameters in this model will be estimated with OLS using historical data. 
-In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, J+1$ be the OLS estimate 
-of $\alpha_i$ and define the adjusted $\alpha$ plugin estimator for time 
-series $i=1$ by,
+All parameters in this model will be estimated with ordinary least squares 
+(OLS) using historical data.  In particular, let $\hat{\alpha}_i$, 
+$i = 2, \ldots, n+1$ be the OLS estimate of $\alpha_i$ and define the 
+adjusted $\alpha$ plugin estimator for time series $i=1$ by,
 \begin{equation} \label{adjusted}
-  \hat{\alpha}_{\text{adj}} = \frac{1}{J}\sum_{i=2}^{J+1}\hat{\alpha}_i
+  \hat{\alpha}_{\text{adj}} = \frac{1}{n}\sum_{i=2}^{n+1}\hat{\alpha}_i
 \end{equation}
-where the $\hat{\alpha}_i$s are MLEs of all of the $\alpha_i$s.  
-We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for the unknown 
-$\alpha_1$ term for which no meaningful estimation information otherwise 
-exists.
+where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of all of 
+the $\alpha_i$s.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
+the unknown $\alpha_1$ term for which no meaningful estimation information 
+otherwise exists.
 
@@
 \end{align*}
-where $\hat\eta_1$, $\hat\phi_1$, $\hat\theta_1$, and $\hat\beta_1$ are MLEs 
-of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$ respectively.  
+where $\hat\eta_1$, $\hat\phi_1$, $\hat\theta_1$, and $\hat\beta_1$ are all 
+OLS estimators of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$ respectively.  
 The first forecast ignores the information about the distribution of 
@@
 $\hat y_{1,T_1^*+1}^2$ minimizes the forecast risk for $\hat y_{1,T_1^*+1}$.  
-Let $R_{T_1^*+1, k} = \E(\hat y_{1,T_1^*+1}^k - y_{1,T_1^*+1}^k)^2$, 
-where $k = 1,2$.  \\
+Let $R_{T_1^*+1, k} = \E(\hat y_{1,T_1^*+1}^k - y_{1,T_1^*+1}^k)^2$, where 
+$k = 1,2$ and define the parameter sets 
+\begin{equation}
+\begin{split}
+  \Hist &= \{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \x_{i,t}, y_{i,t}); 
+    t = 1,\ldots,T_i, i = 2,\ldots,n+1\}, \\
+  \Hist_1 &= \{(\eta_1, \phi_1, \theta_1, \beta_1, \alpha_1, 
+    \x_{1,T_1^*+1}, \x_{1,t}, y_{1,t});  t = 1,\ldots,T_1^*\}.
+\label{Hist}
+\end{split}
+\end{equation}
+Proposition~\ref{prop:R1R2} states when the incorporation of disparate 
+information improves forecasting.
 
-The forecast risk for $y_{1,T^*_1+1}^2$ is: 
+\begin{prop}
+We have that $R_{T_1^*+1, 2} < R_{T_1^*+1, 1}$ when 
+$\Var(\hat{\alpha}_{\text{adj}}) < \mu_{\alpha}^2$.
+\label{prop:R1R2}
+\end{prop}
+
+\begin{proof}
+The forecast risk for $y_{1,T^*_1+1}^2$ is
 \begin{align*}
@@
   \E(\hat{\alpha}_{\text{adj}}) = \E\left\{\E(\hat{\alpha}_{\text{adj}}| \Hist )\right\}
-    = \E\left(\frac{1}{J}\sum_{i=2}^{J+1}\alpha_i\right) 
+    = \E\left(\frac{1}{n}\sum_{i=2}^{n+1}\alpha_i\right) 
     = \mu_{\alpha},
 $$
-and 
-$$
-  \Hist = \{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \x_{i,t}, y_{i,t}); 
-    t = 1,\ldots,T_i, i = 2,\ldots,J+1\}.
-$$
-Define
-$$
-  \Hist_1 = \{\eta_1, \phi_1, \theta_1, \beta_1, \alpha_1, 
-    \x_{1,T_1^*+1}, (\x_{1,t}, y_{1,t});  t = 1,\ldots,T_1^*\},
-$$
-and observe that 
+and $\Hist$ defined in \eqref{Hist}.  Observe that 
 \begin{align*}
@@
     - \beta_1'\x_{1,T_1^*}\right)|\Hist_1\right\} \\
-  &= 0,
+  &= 0.
 \end{align*}
-and that 
-\begin{align*}
+Therefore,
+$$
+  R_{T_1^*+1, 2} = R_{T_1^*+1, 1} + \Var(\hat{\alpha}_{\text{adj}}) - \mu_{\alpha}^2,
+$$ 
+and we have that $R_{T_1^*+1, 2} < R_{T_1^*+1, 1}$ when 
+$\Var(\hat{\alpha}_{\text{adj}}) < \mu_{\alpha}^2$.
+\end{proof}
+
+When we estimate all of the parameters via OLS we can write 
+$\Var(\hat{\alpha}_{\text{adj}})$ as
+\begin{equation}
+\begin{split}
   &\Var(\hat{\alpha}_{\text{adj}}) = \E\left\{\Var(\hat{\alpha}_{\text{adj}}|\Hist)\right\} 
@@
     %= \E\left\{\Var(\hat{\alpha}_{\text{adj}}|\Hist)\right\} 
-    %+ \frac{\sigma_{\alpha}^2}{J} \\
-  &\qquad= \frac{1}{J^2} \sum_{i=2}^{J+1} \E\left\{\Var(\hat{\alpha}_i|\Hist)\right\} 
-    + \frac{\sigma_{\alpha}^2}{J} \\
-  &\qquad= \frac{1}{J^2(T-1)}\sum_{i=2}^{J+1} 
+    %+ \frac{\sigma_{\alpha}^2}{n} \\
+  &\qquad= \frac{1}{n^2} \sum_{i=2}^{n+1} \E\left\{\Var(\hat{\alpha}_i|\Hist)\right\} 
+    + \frac{\sigma_{\alpha}^2}{n} \\
+  &\qquad= \frac{1}{n^2(T-1)}\sum_{i=2}^{n+1} 
     \E\left\{\frac{s_{e,i}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
-      + \frac{\sigma_{\alpha}^2}{J},
-\end{align*}
+      + \frac{\sigma_{\alpha}^2}{n},
+\label{reg}
+\end{split}
+\end{equation}
 where $s_{e,i}^2$ is the estimated variance of model $i$, $R^2_{\alpha_i}$ is 
@@
 
-Forecast 2 has lower forecast risk than Forecast 1 when,  
+Propostion~\ref{prop:R1R2} states that Forecast 2 has lower forecast risk 
+than Forecast 1 when  
 $
@@
 $
-Putting everything together, we see that Forecast 2 has lower forecast risk 
-than Forecast 1 when 
+Combining this result with \eqref{reg}, we see that Forecast 2 has lower 
+forecast risk than Forecast 1 when 
 $$
-  \frac{1}{J^2(T-1)}\sum_{i=2}^{J+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
-    + \frac{\sigma_{\alpha}^2}{J} < \mu_{\alpha}^2.
+  \frac{1}{n^2(T-1)}\sum_{i=2}^{n+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
+    + \frac{\sigma_{\alpha}^2}{n} < \mu_{\alpha}^2.
 $$
-Forecast 2 is preferable to Forecast 1 asymptotically in both $T$ and $J$ 
+Forecast 2 is preferable to Forecast 1 asymptotically in both $T$ and $n$ 
 whenever $\mu_{\alpha} \neq 0$. In finite samples, Forecast 2 is preferable to 

### 2019-11-27 Rcode/supplemental_materials.Rmd
editted main text; added goals; added initial simulations

---
title: "Post shock prediction simulations"
author: "Daniel Eck"
date: "November 26, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We load in the R packages that we need.

```{r, message=FALSE}
library(matrixStats)
library(parallel)
library(doParallel)
library(foreach)
library(tidyverse)
```

## Simulations with simple model

```{r, echo = FALSE}
simstudy_normal <- function(n = 20, T = 20, mu.alpha = 2, 
                     sigma.alpha = 2, sigma.X = 1, sigma = 1){

  Tstar <- floor(T/2)
  eta <- rnorm(n+1)
  theta <- rnorm(n+1)
  theta <- theta / as.vector(sqrt(crossprod(theta)))
  beta <- rnorm(n+1)
  beta <- beta / as.vector(sqrt(crossprod(beta)))
  beta.X <- rnorm(n+1)
  beta.X <- beta.X / as.vector(sqrt(crossprod(beta.X)))
  alpha <- rnorm(n+1, mean = mu.alpha, sd = sigma.alpha)

  X <- matrix(0, nrow = T+1, ncol = n+1)
  X[1, ] <- rnorm(n+1)
  Y <- matrix(0, nrow = T+1, ncol = n+1)
  Y[1, ] <- rnorm(n+1)

  for(i in 2:(T+1)){
    X[i, ] <- beta.X * X[i-1, ] + rnorm(n+1, sd = sigma.X)
    Y[i, ] <- eta + theta * Y[i-1, ] + beta * X[i, ] + 
      alpha * ifelse(i-1 > Tstar, 1, 0) + rnorm(n+1, sd = sigma) 
  }

  mu.alpha.hat <- rep(0, n)
  for(j in 2:(n+1)){
    m1 <- lm(Y[2:(T+1), j] ~ 1 + Y[1:T, j] + X[2:(T+1), j] + ifelse(1:T > Tstar,1,0))
    mu.alpha.hat[j-1] <- coefficients(m1)[4]
  }

  alpha.hat <- mean(mu.alpha.hat)
  #alpha.hat
  #sd(mu.alpha.hat) / sqrt(length(mu.alpha.hat))

  m1 <- lm(Y[2:(Tstar+1), 1] ~ 1 + Y[1:Tstar, 1] + X[2:(Tstar+1), 1])
  beta.hat <- coefficients(m1)
  Ypred.original <- as.vector(beta.hat %*% c(1, Y[Tstar+1,1], X[Tstar+2,1]))
  Ypred.adjusted <- Ypred.original + alpha.hat

  R.original <- (Ypred.original - Y[Tstar+2,1])^2
  R.adjusted <- (Ypred.adjusted - Y[Tstar+2,1])^2

  c(R.original, R.adjusted)
}
```

We set the random seed and declare the number of cores that our multicore implementation will use.

```{r}
ncores <- detectCores() - 1
registerDoParallel(cores = ncores)
set.seed(13)
RNGkind("L'Ecuyer-CMRG")
nsim <- 2e3
```

## Simple model simulations with normal errors

Combinations

```{r simsetup}
ns <- c(5, 1:4 * 10)
Ts <- c(1:4 * 10)
mus <- 1:5 / 2
sds <- 1:4
sim_params <- expand.grid(list(ns = ns, Ts = Ts, mus = mus, sds = sds))
```

```{r basicsims, cache = TRUE}
system.time({
  output_basic <- lapply(1:nrow(sim_params), FUN = function(j){
      n <- sim_params[j, 1]
      T <- sim_params[j, 2]
      mu.alpha <- sim_params[j, 3]
      sigma.alpha <- sim_params[j, 4]
      out <- foreach(i = 1:nsim, .combine = rbind) %dopar% {
        return(simstudy_normal(n = n, T = T, mu.alpha = mu.alpha, 
        sigma.alpha = sigma.alpha, sigma.X = 1, sigma = 1))
      }
      out
  })
})
```

```{r basicsims_ferror}
dat_basic <- cbind(sim_params, do.call(rbind, lapply(output_basic, colMeans)), 
  do.call(rbind, lapply(output_basic, function(x) colSds(x) / sqrt(nsim) )))
colnames(dat_basic)[5:8] <- c("mean_noadj", "mean_adj", "sd_noadj", "sd_adj") 
ggplot(dat_basic, aes(x = mus, y = mean_noadj - mean_adj, 
  group = as.factor(sds), color = as.factor(sds))) + 
  labs(title="Performance of adjustment via disparate information", 
    subtitle = "(rows increase in T, columns increase in n)",
    x ="shock means", y = "error without adjusting minus error after adjusting", 
    color = "shock sd") +
  geom_line() + geom_hline(yintercept = 0, color = "red") +
  theme_minimal() + 
  scale_x_continuous(breaks=c(1,2), minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = NULL) + 
  facet_grid(Ts ~ ns)
```

```{r, eval = FALSE, echo = FALSE}
n = 20 
T = 20
sigma.X = 1
sigma = 1
simstudy_gamma <- function(n = 20, T = 20, mu.alpha = 2, shape = 2, scale = 5, 
  neg = TRUE, sigma.X = 1, sigma = 1){

  Tstar <- floor(T/2)
  eta <- rnorm(n+1)
  theta <- rnorm(n+1)
  theta <- theta / as.vector(sqrt(crossprod(theta)))
  beta <- rnorm(n+1)
  beta <- beta / as.vector(sqrt(crossprod(beta)))
  beta.X <- rnorm(n+1)
  beta.X <- beta.X / as.vector(sqrt(crossprod(beta.X)))

  neg <- ifelse(neg, 1, -1)
  alpha <- mu.alpha + shape*scale*neg - 
    neg*rgamma(n = n+1, shape = shape, scale = scale)

  X <- matrix(0, nrow = T+1, ncol = n+1)
  X[1, ] <- rnorm(n+1)
  Y <- matrix(0, nrow = T+1, ncol = n+1)
  Y[1, ] <- rnorm(n+1)

  for(i in 2:(T+1)){
    X[i, ] <- beta.X * X[i-1, ] + rnorm(n+1, sd = sigma.X)
    Y[i, ] <- eta + theta * Y[i-1, ] + beta * X[i, ] + 
      alpha * ifelse(i-1 > Tstar, 1, 0) + rnorm(n+1, sd = sigma) 
  }

  mu.alpha.hat <- rep(0, n)
  for(j in 2:(n+1)){
    m1 <- lm(Y[2:(T+1), j] ~ 1 + Y[1:T, j] + X[2:(T+1), j] + ifelse(1:T > Tstar,1,0))
    mu.alpha.hat[j-1] <- coefficients(m1)[4]
  }

  alpha.hat <- mean(mu.alpha.hat)
  #alpha.hat
  #sd(mu.alpha.hat) / sqrt(length(mu.alpha.hat))

  m1 <- lm(Y[2:(Tstar+1), 1] ~ 1 + Y[1:Tstar, 1] + X[2:(Tstar+1), 1])
  beta.hat <- coefficients(m1)
  Ypred.original <- as.vector(beta.hat %*% c(1, Y[Tstar+1,1], X[Tstar+2,1]))
  Ypred.adjusted <- Ypred.original + alpha.hat

  R.original <- (Ypred.original - Y[Tstar+2,1])^2
  R.adjusted <- (Ypred.adjusted - Y[Tstar+2,1])^2

  c(R.original, R.adjusted)
}

test2 <- sapply(1:n.sim, FUN = function(j) 
  simstudy_gamma(n = 100, T = 100,  mu.alpha = 2, shape = 2, scale = 4, 
    neg = FALSE, sigma.X = 1, sigma = 1))
rowMeans(test2) # average forecast error for each forecast
rowSds(test2) / sqrt(n.sim) # Monte Carlo standard errors corresponding to the above averages

mean(apply(test2, 2, which.min) - 1) # proportion that adjusting wins
diffs2 <- apply(test2, 2, diff)

# average reduction achieved from adjustment
mean(diffs2)

# Monte Carlo standard error corresponding to the above average
sd(diffs2) / sqrt(n.sim) 
```

### 2019-11-27 eck2019syntheticprediction.tex
editted main text; added goals; added initial simulations

@@
 
+\allowdisplaybreaks
+
 \title{Minimizing post shock forecasting error using disparate information}
 \author{Daniel J. Eck}
-\date{May 2019}
 
@@
 
+{\bf Things to do}: \\
+
+  - get regression model interpretation of $\Var(\hat\alpha_j)$. \\
+
+  - simulations for simple model with normal errors; model with normal 
+    errors and $p > 1$; model where shock effect is Gamma. \\
+
+  - get references on time series pooling. \\
+
+  - investigate orthogonal parameterizations of regression model 
+    matrices in order to isolate estimation of $\Var(\hat\alpha_j)$, 
+    so that the asymptotic estimate of $\Var(\hat\alpha_j)$ is independent 
+    of other terms. \\
+
+  - expand method to weighted cases when the shock effect depends on the 
+    measured covariates. \\
+
+  - get a real dataset. \\
+
 \section{Introduction}
@@
 The Introduction of \citet{timmermann2006forecast} provided several reasons 
-for combining forecasts.  In particular: 
+for combining forecasts.  In particular, combining forecasts may be 
+beneficial when: 
 1) the information set underlying individual forecasts is often unobserved to 
@@
 \citep[and references therein]{timmermann2006forecast}.
+The setting for the forecast combination problem is that there are 
+competing forecasts for a single time series.  In this setting, one may 
+desire combining forecasts as a method for lowering overall forecast error.
 
-In this article we propse a new setting for the classic forecast combination 
+In this article we propse a new setting for the forecast combination 
 problem.  We will suppose that a time series of interest has recently 
@@
 $$
-in our analyses.
-
-\section{Dynamic panel model}
-\label{sec:dpm}
-
-To fix ideas we consider a similar dynamic panel data model with autoregressive 
-structure in \citet{blundell1998initial} %without past time period covariate 
+in our analyses. In this article, we consider a similar dynamic panel data 
+model with autoregressive structure to that in \citet{blundell1998initial}. 
+%without past time period covariate 
 %information and with a single present time covariate.  
-We consider an additional shock effect whose presence is given by the binary 
-variable $D_{i,t}$.  Our dynamic panel model is  
+Our dynamic panel model includes an additional shock effect whose presence 
+or absence is given by the binary variable $D_{i,t}$.  Our dynamic panel 
+model is 
 \begin{equation} \label{DPM}
@@
 where $t = 1,\ldots,T_i$, $i = 1,\ldots, n+1$, and $D_{i,t} = 1(t > T_i^*)$, 
-$T_i^* < T_i$.  We will consider a simple random effects structure where,  
+$T_i^* < T_i$.  We will consider the following random effects structure:  
 %\begin{align*}
@@
     \qquad t = 1, \ldots T_i,\; i = 1,\ldots n+1; \\
-  \eta &\indep \alpha \indep \phi \indep \theta \indep \varepsilon;
+  \eta &\indep \alpha \indep \phi \indep \theta \indep \varepsilon.
 \end{align*}
+
+Throughout the rest of this article we show that the collection of 
+disparate time series $\{y_{i,t}, t = 2,\ldots,T_i, i = 1,\ldots,n\}$ has 
+the potential to improve the forecasts for $y_{1, t}$ when $t > T_1^*$ 
+and no observations arre made for these time periods.
+
+\section{Adjustment via disparate infromation in dynamic panel model}
 
@@
 offer predicts for $y_{1, T_1^* + 1}$, the response observed after the first 
-post shock time period for subject 1.  The difficulty in this forecast stems 
-from not observing $\alpha_1$ and not having any readily infromation available 
-to estimate it directly.  We show that there is a balance between $\mu_\alpha$ 
+post shock time period for out ime series of interest.  
+The difficulty in this forecast stems from not observing $\alpha_1$ and not 
+having any readily infromation available to estimate it directly from 
+model \eqref{DPM}.  We show that there is a balance between $\mu_\alpha$ 
 and $\sigma_\alpha^2$ that allows us to lower the forecast risk for 
@@
 
-Consider the candidate forecasts: 
+It is important to note that the adjustment $\hat{\alpha}_{\text{adj}}$ 
+is a consistent estimator of $\mu_\alpha$, it is not an unbiased 
+estimator for $\alpha_1$, nor does it converge to $\alpha_1$.  
+Despite these inferential shortcomings, adjustment of the forecast for 
+$y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}_{\text{adj}}$ has 
+the potential to lower forecast risk in settings where $\mu_\alpha$ is 
+large relative to $\sigma_\alpha$.
+
+We will consider the candidate 
+forecasts: 
 \begin{align*}

### 2019-11-27 Rcode/simstudy.R

@@ -1,0 +1,83 @@
+
+
+
+simstudy <- function(J = 20, T = 20, mu.alpha = 4, 
+  sigma.alpha = 1, sigma.X = 1, sigma = 1){
+
+  Tstar <- floor(T/2)
+  eta <- rnorm(J+1)
+  theta <- rnorm(J+1)
+  theta <- theta / as.vector(sqrt(crossprod(theta)))
+  beta <- rnorm(J+1)
+  beta <- beta / as.vector(sqrt(crossprod(beta)))
+  beta.X <- rnorm(J+1)
+  beta.X <- beta.X / as.vector(sqrt(crossprod(beta.X)))
+  alpha <- rnorm(J+1, mean = mu.alpha, sd = sigma.alpha)
+
+  X <- matrix(0, nrow = T+1, ncol = J+1)
+  X[1, ] <- rnorm(J+1)
+  Y <- matrix(0, nrow = T+1, ncol = J+1)
+  Y[1, ] <- rnorm(J+1)
+
+  for(i in 2:(T+1)){
+    X[i, ] <- beta.X * X[i-1, ] + rnorm(J+1, sd = sigma.X)
+    Y[i, ] <- eta + theta * Y[i-1, ] + beta * X[i, ] + alpha * ifelse(i-1 > Tstar, 1, 0) + rnorm(J+1, sd = sigma) 
+  }
+
+  mu.alpha.hat <- rep(0, J)
+  for(j in 2:(J+1)){
+    m1 <- lm(Y[2:(T+1), j] ~ 1 + Y[1:T, j] + X[2:(T+1), j] + ifelse(1:T > Tstar,1,0))
+    mu.alpha.hat[j-1] <- coefficients(m1)[4]
+  }
+
+  alpha.hat <- mean(mu.alpha.hat)
+  #alpha.hat
+  #sd(mu.alpha.hat) / sqrt(length(mu.alpha.hat))
+
+  m1 <- lm(Y[2:(Tstar+1), 1] ~ 1 + Y[1:Tstar, 1] + X[2:(Tstar+1), 1])
+  beta.hat <- coefficients(m1)
+  Ypred.original <- as.vector(beta.hat %*% c(1, Y[Tstar+1,1], X[Tstar+2,1]))
+  Ypred.adjusted <- Ypred.original + alpha.hat
+
+  R.original <- (Ypred.original - Y[Tstar+2,1])^2
[…]

### 2020-02-11 eck2020SCMpred.tex
updated synthetic control notes that borrow from Soheils direction

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{url}

\usepackage{geometry}
\usepackage[usenames]{color}
\geometry{margin=1in}

\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\Hist}{\mathcal{H}}
\newcommand{\Tstar}{T^{\textstyle{*}}}
\newcommand{\Wstar}{W^{\textstyle{*}}}
\newcommand{\WstarI}{W^{I^{\textstyle{*}}}}
\newcommand{\WstarN}{W^{N^{\textstyle{*}}}}
\newcommand{\wstar}{w^{\textstyle{*}}}
\newcommand{\wstarI}{w^{I^{\textstyle{*}}}}
\newcommand{\wstarN}{w^{N^{\textstyle{*}}}}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\indep}{\perp\!\!\!\perp}

\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\Var}{Var}

\newtheorem{cor}{Corollary}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{prop}{Proposition}

\newcommand\red[1]{{\color{red}#1}}

\allowdisplaybreaks

\title{Sythetic prediction of treatment effects before they are implemented}
\author{Daniel J. Eck and Soheil Eshghi}

\begin{document}

\maketitle

\begin{abstract}
The synthetic control method (SCM) is a powerful methodology for evaluating the effects of treatments over time. In this article we reformulate SCM so that it can estimate treatment effects before they are implemented. 
\end{abstract}

\section{Introduction}

\cite{athey2017state} state that SCM is ``arguably the most important innovation in the policy evaluation literature in the last 15 years.'' We reformulate the synthetic control method \citep{abadie2010synthetic} as a tool to estimate multiple counterfactual with the aim of estimating what a treatment effect would be.

\section{Background on SCM}
What follows is adapted from \cite{abadie2010synthetic}: \\

Let $Y_{it}^N$ be the counterfactual outcome for subject $i$ at time point $t$ in the absence of treatment for subjects $i = 1,\ldots, n+1$, $t = 1,\ldots, T_i$.  Let $Y_{it}^I$ be the counterfactual outcome that would be observed for subject $i$ at time $t$ if subject $i$ is exposed to the treatment. We let $\Tstar_i$ be the time that the treatment is assigned to subject $i$ where $T_i = \infty$ for subjects that do not receive the treatment. It is assumed that $Y_{it}^N = Y_{it}^I$ for all $t < \Tstar_i$.

Let $\alpha_{it} = Y_{it}^I - Y_{it}^N$ be the treatment effect for individual $i$ at time period $t$, and let $D_{it}$ be an indicator that is 1 if individual $i$ is given the treatment and $t \geq \Tstar_i$. The observed outcome is 
$$
  Y_{it} = Y_{it}^N + \alpha_{it}D_{it}.
$$

In SCM the goal is to estimate $\alpha_{1\Tstar_1+1}, \ldots, \alpha_{1T_1}$ since subject $1$ is the only individual who receives the treatment. To achieve this goal we need to estimate $Y_{1t}^N$ for all $t > \Tstar_1$ since $Y_{1t}^I$ is observed over this time period. Suppose that $Y_{it}^N$ can be represented as a factor model,
$$
  Y_{it}^N = \delta_t + \theta_t'Z_i + \lambda_t'\mu_i + \varepsilon_{it}, 
$$
where $\delta_t$ is an unknown common factor with constant factor loadings across units, $Z_i \in \R^p$ is a vector of observed covariates (not affected by the treatment), $\theta_t \in \R^p$ is a vector of unknown parameters, $\lambda_t \R^F$ is a  vector of unobserved common factors, $\mu_i \in \R^F$ is a vector of unknown factor loadings, and the error terms $\varepsilon_{it}$ are unobserved errors with $E(\varepsilon_{it}) = 0$.

Let $W = (w_2,\ldots, w_{n+1}) \in \R^n$ be a vector of weights that satisfy $\sum_{i=2}^{n+1}w_i = 1$ and $w_i \geq 0$ for all $i = 2,\ldots, n+1$. The value of the outcome variable for each synthetic control indexed by $W$ is
$$
  \sum_{i=2}^{n+1}w_i Y_{it} = \delta_t + \theta_t'\sum_{i=2}^{n+1}w_iZ_i + \lambda_t'\sum_{i=2}^{n+1} w_i\mu_i + \sum_{i=2}^{n+1} w_i\varepsilon_{it},
$$
and this synthetic control is then used to construct an estimate of the intervention effect,
$$
  \widehat{\alpha}_{1t} = Y_{1t} - \sum_{i=2}^{n+1}w_i Y_{it}.
$$

The outcome variable of interest is observed for $T_i$ periods, $t = 1,\ldots,T_i$, for the subject affected by the intervention, $Y_{1t}$, and the unaffected subjects, $Y_{it}$, $i = 2,\ldots, n+1$. Let $K_i \in \R^{\Tstar_i}$ define a linear combination of preintervention outcomes: $\bar{Y}_i^K = \sum_{t=1}^{\Tstar_i}k_tY_{it}$. Consider $M$ such linear combinations $K_1, \ldots, K_M$, and let $\X_1 = (Z_1', \bar{Y}_1^{K_1}, \ldots, \bar{Y}_1^{K_M} )' \in \R^{k}$, $k = p + M$, be a vector of preintervention characteristics for the exposed subject. Similarly $\X_o \in \R^{k \times n}$ is a matrix containing the same variables for the unaffected subjects. That is, the $i$th column of $\X_o$ is $(Z_i',Y_i^{K_1},\ldots,Y_i^{K_M})'$ (assuming that $T_i = T$ for all $i$). The vector $\Wstar$ is chosen to minimize some distance, $\|\X_1 - \X_o W\|$. \cite{abadie2010synthetic} proposed using $\|\X_1 - \X_oW\|_V = \sqrt{(\X_1 - \X_oW)'V(\X_1 - \X_oW)}$, where $V \in \R^{k \times k}$ is some symmetric and positive semidefinite matrix. %If the relationship between the outcome variable and the explanatory variables in $\X_1$ and $\X_o$ is highly nonlinear and the support of the explanatory variables is large, interpolation biases may be severe.

\section{Synthetic prediction of treatment effect}

Here we ``reverse'' SCM and use it as a methodology for constructing both the intervention and the nonintervention for subject 1 at future time periods. In this context we suppose that we have $\Tstar_1$ preintervention observations of $Y_{1t}^N$ and no observations of $Y_{1t}$ for $t > \Tstar_1$. We aim to estimate $\alpha_{1t}$ for $t = \Tstar_1 + 1,\ldots, T_1$. We achieve this by using SCM to estimate $Y_{1t}^I$ and $Y_{1t}^N$ for$t = \Tstar_1 + 1,\ldots, T_1$.

We will now allow for two donor pools to estimate both counterfactuals $Y_{1t}^N$ and $Y_{1t}^I$ for $t > \Tstar_1$. We will let $n_I$ and $n_N = n - n_I$ be the number of subjects in the donor pool used to estimate $Y_{1t}^I$ and $Y_{1t}^N$ respectively. We estimate $Y_{1t}^I$ using data from the first donor pool. In this pool, we suppose that we have $\Tstar_i$ observations of $Y_{it}^N$ and $T_i - \Tstar_i$ postintervention observations of $Y_{it}^I$ for subjects $i = 2,\ldots,n_I+1$. We estimate $Y_{1t}^N$ using data from the second donor pool. In this pool, we suppose that we have $T_1 + 1$ observations of $Y_{it}^N$ %and $T_i - \Tstar_i$ postintervention observations of $Y_{it}^I$ 
for subjects $i = n_I+2,\ldots,n+1$. %where $T_i - \Tstar_i$ is allowed to equal 0.
Not all of the subjects are assumed to follow the same timelines as subject 1 in this context. We make the following assumption to ensure that the treatment assignments from subjects $2,\ldots,n+1$ do not interfere with the treatment effect on subject $1$.

\vspace*{0.5cm}
\noindent\textbf{Assumption 1 (Independence)} We assume that $(Y_{1t}^N,Y_{1t}^I,Z_1)$, $t = 1,\ldots,\Tstar_1$ are all independent of $(Y_{it}^N, Y_{it}^I, Z_i)$, $t = 1,\ldots,T_i$, $i = 2,\ldots,n+1$. 
\vspace*{0.5cm}

For now, we estimate the treatment effect $\alpha_{1\Tstar_1+1}$, the treatment effect for the first time period in which no counterfactuals $Y_{1t}^I$ or $Y_{1t}^N$ are observed.

Let $\X_1 = (Z_1', \bar{Y}_1^{K_1}, \ldots, \bar{Y}_1^{K_M} )' \in \R^{k}$, $k = p + M$, be a vector of preintervention characteristics for subject 1. Let $\X_o^I \in \R^{k \times n_I}$ be a matrix containing the same variables for the $n_I$ subjects belonging to the first donor pool. That is, the $i$th column of $\X_o^I$ is $(Z_i',Y_i^{K_1},\ldots,Y_i^{K_M})'$ (assuming that $T_i = T$ for all $i = 2,\ldots,n_I+1$). The vector $\WstarI$ is chosen so that  
$$
  \WstarI = \text{argmin}_{W} \sqrt{(\X_1 - \X_o^IW)'V(\X_1 - \X_o^IW)},
$$
where $V \in \R^{k \times k}$ is some symmetric and positive semidefinite matrix. Similarly, let $\X_o^N \in \R^{k \times n_N}$ be a matrix containing the same variables for the $n_N$ subjects belonging to the second donor pool. That is, the $i$th column of $\X_o^N$ is $(Z_i',Y_i^{K_1},\ldots,Y_i^{K_M})'$ (assuming that $T_i = T$ for all $i = n_I+2,\ldots,n+1$). The vector $\WstarN$ is chosen so that  
$$
  \WstarN = \text{argmin}_{W} \sqrt{(\X_1 - \X_o^NW)'V(\X_1 - \X_o^NW)}.
$$
To ensure that both donor pools can reliably estimate the treatment effect $\alpha_{1,\Tstar_1+1}$ we assume that no treatment selection bias exists.

\vspace*{0.5cm}
\noindent\textbf{Assumption 2 (No selection bias)} We assume that $(Y_{it}^N,Y_{it}^I) \indep D_{it}$ for all $t = 1,\ldots,T_i$ and all subjects $i = 1,\ldots n+1$.
\vspace*{0.5cm}

Under assumptions 1 and 2 we propose estimating $\alpha_{1,\Tstar_1+1}$ with 
$$
  \widehat{\alpha}_{1,\Tstar_1+1} = \sum_{i=2}^{n_I + 1} \wstarI_i Y_{i\Tstar_i+1} - \sum_{i=n_I + 2}^{n + 1} \wstarN_i Y_{i\Tstar_i+1}.
$$

\section*{Notes}
{\bf Taken from Soheil's notes (begin).}
Assume we have covariate-observation pairs $(y_i, \x_i)$ for $n$ points, and 
that $\x_1$, the covariates of the intervened unit, lies within the convex hull 
of $(\x_i)_{i=1}^n$. One way to match covariates is to pick a vector $\w$ such 
that $\w'1=1$ and $\norm{\x_1 - \X\w}$, where $\X$ is the matrix of available 
covariates (arranged in column form), is minimized.

One can incorporate a notion of locality by penalizing the use of covariates 
far from the covariates of interest, through incorporating the following term 
in either a constraint or as part of the objective:
$\sum_{i=1}^n \w_i \norm{\x_1 - \x_i}$.

This leads to the following optimization problem:
\begin{align*}
\min_{\w} ~~~& \norm{\x_1 - \X\w}\\
\text{s.t.}~~~& \w'1=1,\\
& \sum_{i=1}^n \w_i\norm{\x_1 - \x_i} \leq \delta, \\
& \text{Var}(\Y\w)\leq \gamma,
\end{align*}
with $\delta$ and $\gamma$ being rightsizing parameters.

We can simplify the above using the following assumptions:

\ldots
\red{Once I have time I will write these out so that e can extract the fixed values mostly to one side.}

\red{The rest is kind of bad as is, to be honest, and hard to justify. I still think we should weigh down the ones that are pretty far from the expected value, but it's not clear why the variance condition above will not be enough and we have to do a prediction model for all $(n-1)-$ tuples. Any ideas?}

The use of the transformed linear model (linking covariates to observations of 
outcomes) to create the counterfactual show our belief in the model 
specification. Under these conditions, the prediction of the model for the 
outcome at covariates $\x_i$ based on all other observed covariates $\x_{-i}$ 
(if it is within the convex hull) should closely match its observed outcome.  
Any discrepancy should make us less confident in the observation of the 
outcome (if we hold the model specification to be correct), so we would want 
$y_i$ to play less of a role in the creation of the counterfactual in that 
scenario.  Thus, we will put an upper limit on $\w_i$, the weight assigned to 
the covariate-observation pair by a function of the discrepancy between $y_1$ 
and the created synthetic prediction for it $\hat{y}_i$ from $\x_{-i}$, i.e.,

{\bf Taken from Soheil's notes (end).} \\

\bibliographystyle{plainnat}
\bibliography{synthetic-prediction-notes}

\end{document}

### 2020-02-26 eck2019syntheticprediction.tex
updated synthetic control notes that borrow from Soheils direction
updated MS

@@
 
+\newcommand{\R}{\mathbb{R}}
 \newcommand{\w}{\textbf{w}}
@@
 
+  - more general panel model where covariates may be different. \\
+
   - get references on time series pooling. \\
@@
 
-  - get a real dataset. \\
+  - get a real dataset. Air conditiong units in hot humid summer vs salt sales 
+  	in very icy/snoy winters and portable generators for hurricane/fires/tornados  \\
 
@@
 \end{equation}
-where $t = 1,\ldots,T_i$, $i = 1,\ldots, n+1$, and $D_{i,t} = 1(t > T_i^*)$, 
-$T_i^* < T_i$.  We will consider the following random effects structure:  
+$t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = 1(t > T_i^*)$, 
+$T_i^* < T_i$ and $\x_{i,t} \in \R^{p}$, $p \geq 1$.  We will consider 
+the following random effects structure:  
 %\begin{align*}
@@
   &\qquad= \frac{1}{n^2} \sum_{i=2}^{n+1} \E\left\{\Var(\hat{\alpha}_i|\Hist)\right\} 
-    + \frac{\sigma_{\alpha}^2}{n} \\
-  &\qquad= \frac{1}{n^2(T-1)}\sum_{i=2}^{n+1} 
-    \E\left\{\frac{s_{e,i}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
-      + \frac{\sigma_{\alpha}^2}{n},
+    + \frac{\sigma_{\alpha}^2}{n}. %\\
+%  &\qquad= \frac{1}{n^2(T-1)}\sum_{i=2}^{n+1} 
+%    \E\left\{\frac{s_{e,i}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
+%      + \frac{\sigma_{\alpha}^2}{n},
 \label{reg}
@@
 \end{equation}
-where $s_{e,i}^2$ is the estimated variance of model $i$, $R^2_{\alpha_i}$ is 
-the multiple $R^2$ obtained from regressing the shock indicator $D$ on the 
-other regressors, and $s_{\alpha_i}^2$ is... .
-
+%where $s_{e,i}^2$ is the estimated variance of model $i$, $R^2_{\alpha_i}$ is 
+%the multiple $R^2$ obtained from regressing the shock indicator $D$ on the 
+%other regressors, and $s_{\alpha_i}^2$ is... .
 Propostion~\ref{prop:R1R2} states that Forecast 2 has lower forecast risk 
@@
 forecast risk than Forecast 1 when 
+%$$
+%  \frac{1}{n^2(T-1)}\sum_{i=2}^{n+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
+%    + \frac{\sigma_{\alpha}^2}{n} < \mu_{\alpha}^2.
+%$$
 $$
-  \frac{1}{n^2(T-1)}\sum_{i=2}^{n+1} \E\left\{\frac{s_{e,j}^2}{(1-R^2_i)s_{\alpha_i}^2}\right\} 
+  \frac{1}{n^2} \sum_{i=2}^{n+1} \E\left\{\Var(\hat{\alpha}_i|\Hist)\right\} 
     + \frac{\sigma_{\alpha}^2}{n} < \mu_{\alpha}^2.

### 2020-05-18 manuscript/manuscript.tex
added manuscript folder with Jileis recent edits

\documentclass[11pt]{article}

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{tikz}
% margin setup
\geometry{margin=1in}

% function definition
\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\Hist}{\mathcal{H}}
\def\mbf#1{\mathbf{#1}} % bold but not italic
\def\ind#1{\mathrm{1}(#1)} % indicator function
\newcommand{\simiid}{\stackrel{iid}{\sim}} % IID 
\def\where{\text{ where }} % where
\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
\def\mrm#1{\mathrm{#1}} % remove math
\newcommand{\reals}{\mathbb{R}} % Real number symbol
\def\t#1{\tilde{#1}} % tilde
\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
\def\v#1{\mbi{#1}} % Vector notation
\def\mc#1{\mathcal{#1}} % mathical
\DeclareMathOperator*{\argmax}{arg\,max} % arg max
\DeclareMathOperator*{\argmin}{arg\,min} % arg min
\def\E#1{\mathrm{E}(#1)} % Expectation symbol
\def\var#1{\mathrm{Var}(#1)} % Variance symbol
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
\newcommand\red[1]{{\color{red}#1}}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert} % A norm with 1 argument
\DeclareMathOperator{\Var}{Var} % Variance symbol

\newtheorem{cor}{Corollary}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{prop}{Proposition}
\theoremstyle{definition}
\newtheorem{remark}{Remark}
\hypersetup{
  linkcolor  = blue,
  citecolor  = blue,
  urlcolor   = magenta,
  colorlinks = true,
} % color setup

% proof to proposition 
\newenvironment{proof-of-proposition}[1][{}]{\noindent{\bf
    Proof of Proposition {#1}}
  \hspace*{.5em}}{\qed\bigskip\\}
% general proof of corollary
  \newenvironment{proof-of-corollary}[1][{}]{\noindent{\bf
    Proof of Corollary {#1}}
  \hspace*{.5em}}{\qed\bigskip\\}
% general proof of lemma
  \newenvironment{proof-of-lemma}[1][{}]{\noindent{\bf
    Proof of Lemma {#1}}
  \hspace*{.5em}}{\qed\bigskip\\}

\allowdisplaybreaks

% title
\title{Minimizing post shock forecasting error using disparate information}
\author{Jilei Lin\thanks{jileil2@ilinois.edu}}
\author{Ziyu Liu\thanks{ziyuliu3@illinois.edu}}
\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
\affil{Department of Statistics, University of Illinois at Urbana-Champaign}

%%% New version of \caption puts things in smaller type, single-spaced 
%%% and indents them to set them off more from the text.
\makeatletter
\long\def\@makecaption#1#2{
  \vskip 0.8ex
  \setbox\@tempboxa\hbox{\small {\bf #1:} #2}
  \parindent 1.5em  %% How can we use the global value of this???
  \dimen0=\hsize
  \advance\dimen0 by -3em
  \ifdim \wd\@tempboxa >\dimen0
  \hbox to \hsize{
    \parindent 0em
    \hfil 
    \parbox{\dimen0}{\def\baselinestretch{0.96}\small
      {\bf #1.} #2
      %%\unhbox\@tempboxa
    } 
    \hfil}
  \else \hbox to \hsize{\hfil \box\@tempboxa \hfil}
  \fi
}
\makeatother

\begin{document}

\begin{center}
  \textbf{Note}
\end{center}

Things to do:
\begin{enumerate}
  \item Literature review and introduction (We need a literature review for existing methods that are similar/different but close enough methods.  Possible searches include pooling, time series pooling, bayesian time series, bayesian autoregression)
  \item Explore bootstrapping
  \item Data analysis
\end{enumerate}

In R, \texttt{optim} function in \texttt{base} and \texttt{Rsolnp} package may be helpful for solving the minimization problems in synthetic control methods.

\begin{center}
  \textbf{Updates in this version}
\end{center}

\begin{enumerate}
  \item The manuscript is revised according to the comments and unnecessary parts are deleted.
  \item Parametric bootstrap for AR(1) is added in Section  3.3 with some references added.
  \item A couple of references are added in the introduction but more to be added.
\end{enumerate}

% table of contents
\tableofcontents

\newpage

\maketitle
\begin{abstract}
    We develop a forecasting methodology for time series data that has 
    undergone a shock. We still can provide credible forecasts for a time 
    series in the presence of such systematic shocks by drawing from disparate 
    time series that have undergone similar shocks for which post-shock 
    outcome data is recorded.  These disparate time series are assumed to have 
    mechanistic similarities to the time series under study but are otherwise 
    independent (Granger noncausal).  The inferential goal of our forecasting 
    methodology is to supplement observed time series data with post-shock 
    data from the disparate time series in order to minimize average forecast 
    risk. 
\end{abstract}

\section{Introduction}
The technique of combining forecasts to lower forecast error has a rich 
history \citep{bates1969combination, mundlak1978pooling, 
  timmermann2006forecast, granger2014forecasting}.  
The Introduction of \citet{timmermann2006forecast} provided several reasons 
for combining forecasts.  In particular, combining forecasts may be 
beneficial when: 
1) the information set underlying individual forecasts is often unobserved to 
the forecast user; 2) different individual forecasts may be very differently 
affected by non-stationarities and model misspecifications; 3) different 
individual forecasts may be motivated by different loss functions 
\citep[and references therein]{timmermann2006forecast}.
The setting for the forecast combination problem is that there are 
competing forecasts for a single time series.  In this setting, one may 
desire combining forecasts as a method for lowering overall forecast error.

In this article we provide forecasting adjustment techniques with the goal 
of lowering overall forecast error when the time series under study has 
undergone a structural shock.
%In this article we propose a new setting for the forecast combination 
%problem.  We will suppose that a time series of interest has recently 
%undergone a structural shock that is not similar to anything observed in its 
%past, and we desire reliable post-shock forecasts in this setting.  
It is unlikely that any forecast that previously gave successful predictions 
for the time series of interest will be able to accommodate the 
structural shock.  Therefore the traditional forecast combination framework 
may not be of any help. However, all is not lost in this setting. It may be 
the case that there exists disparate time series that have previously 
undergone similar structural shocks.  When this is so, one may be able to 
aggregate the post-shock information from these disparate time series to 
aid the post-shock forecast for the time series under investigation.

We develop and compare aggregation techniques in this post-shock setting and 
investigate settings for when they do and do not decrease mean squared 
prediction error. We assume a simple auto regressive data generating process 
with a general random effects structure. The main idea is to first average 
the estimated shock effects from the disparate time series and then add 
the averaged estimated shock effect to the present forecast. When these 
time series are independent and the mean of shock effect distribution is 
large relative to its variance then this technique will reduce mean squared 
prediction error under the assumed model. Note that this methodology is not 
motivated with the goal of unbiased, asymptotically unbiased, or consistent 
estimation for the shock-effect of the time series under study. We consider 
three aggregation techniques: simple averaging, inverse-variance weighted 
averaging, and similarity weighting. The latter technique is similar to 
the weighting in synthetic control methodology \citep{abadie2010synthetic}.

\vspace{.3cm}

\emph{\textcolor{red}{More to be added ...}}

\vspace{.3cm}

Time-series pooling methodology is one of the main methods to deal this problem. The literature of time-series pooling is mainly related to pooling cross-sectional data. In this setting, estimation of parameters is usually based on merging from different time series using various pooling techniques.  For example, \citet{zellner1991forecasting} assumes the coefficient vectors of different time series are the same so that the time series can be merged to estimate parameters once in forecasting turning point of GDP growth rate in practice. \emph{\textcolor{red}{More to be added ...}}

Modern research in ``combining'' forecasts from disparate time series have taken perspectives from distinct fields.  \citet{lee2020estimation} constructed a Bayesian hierarchical model  to estimate posterior parameters for Richards model to improve predictive precision of COVID-19 infection trajectories for different countries. Though a Bayesian hierarchical approach can be a solution for our problem by setting up prior for shock-effects, the analysis is sensitive to the prior and the hierarchical model setup, and conditions for predictive improvement are generally hard to know. \citet{plessen2020integrated} employs a data-mining approach to take COVID-19 data from different countries as input to predict \emph{global} net daily infections  and deaths of COVID-19 from clustering. However, the fit is poor due to tremendous volatility of COVID-19 data, and perhaps a lack of random structure in his model. \emph{\textcolor{red}{More to be added ...}}

\begin{figure}[t]
  \begin{center}
    \includegraphics[height = 8cm]{comp.pdf}
    \caption{A comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series and that the shock time is at $T_1^* = 125$.}\label{figure1}
  \end{center}  
  \vspace{-.6cm}
\end{figure}

%The question is then how to estimate the shock effects and improve the 
%prediction? This paper proposes three estimators, the adjustment estimator, weighted adjustment estimator, and inverse-variance weighted estimators. Section (to be updated) discusses properties of those estimators. Section (to be updated) compares the  interplay between prediction risk and different shock effects estimators. Section (to be updated) conducts simulation to justify our claims and certain properties that cannot be found analytically.

\section{Setting}
\label{setting}
We will suppose that an analyst has time series data ($y_{i,t}$,$\x_{i,t}$), 
$t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a 
scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to 
the analyst prior to the observation of $y_{1,t}$.  Suppose that the analyst 
is interested in forecasting $y_{1,t}$, the first time series in the 
collection.
%$y_1, y_2, \ldots$.  
%Given each time point $t \geq 1$, let $\x_{1,t}$ be a vector of covariates 
%revealed prior to the observation of $y_{1,t}$.  
To gauge the performance of a procedure that produces forecasts 
$\{\hat y_{1,t}, t= 1,2,\ldots\}$ given time horizon $T_1$, we consider the 
average forecast risk
$$
  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2
$$
in our analyses. In this article, we consider a similar dynamic panel data 
model with autoregressive structure to that in \citet{blundell1998initial}. 
%without past time period covariate 
%information and with a single present time covariate.  
Our dynamic panel model includes an additional shock effect whose presence 
or absence is given by the binary variable $D_{i,t}$, the details of this model 
are in the next section.

Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology. This figure depicts a time-series that experienced a ``shock'' at time point $T_1^* = 125$. It is supposed that the researcher does not have any information beyond $T_1^*$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded. Similarity in this context means that the shock effects are random variables that from a common distribution.
%As we can see, the purple line provides a better prediction than the red line in this particular example. But we will justify later that consideration of estimated shock-effects will improve the prediction under certain conditions.
In this example, the mean of the estimated shock effects is taken as a shock-effect estimator for the time series under study. Forecasts are then made by adding this shock-effect estimator to the estimated response values obtained from the process that ignores the shock. It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect. We evaluate the performance of this post-shock prediction methodology throughout this article; we outline situations for when it is expected to work and when it is not.

%Section \ref{properties} will provide a more detailed treatment about when our proposed estimators in Section \ref{constructionofestimators} will improve the prediction under various model setups in Section \ref{modelsetup}. More examples will be provided using Monte Carlo simulations in Section \ref{simulation}.

\subsection{Model Setup}

\label{modelsetup}

In this section, we will describe the assumed dynamic panel models for which 
post-shock aggregated estimators are provided. The basic structure of these models 
are the same, the differences between them lie in the setup of the shock effect 
distribution.

The model $\mc{M}_1$ is defined as
\begin{align}
\mc{M}_1 \colon y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t}+ \beta_i'\mbf{x}_{i, t-1} + \varepsilon_{i,t}\label{equation1}
\end{align}
for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = 1(t > T_i^*)$, 
$T_i^* < T_i$ and $\x_{i,t} \in \R^{p}$, $p \geq 1$.  We assume that the 
$\mbf{x}_{i,t}$'s are fixed and $T_i^*$s are known. The random effects structure for $\mc{M}_1$ is:
\begin{align*}
  \eta_i &\simiid  \eta ,\where \E{\eta} = 0, \var{\eta} = \sigma^2_{\eta}, \qquad i = 1, \ldots, n+1,\\
  \phi_i &\simiid \phi, \where |\phi|<1, \qquad i = 1, \ldots, n+1, \\
   \theta_i &\simiid \theta, \where \E{\theta}=\mu_{\theta}, \var{\theta}=\Sigma_{\theta}^2, \qquad i = 1, \ldots, n + 1, \\
\beta_i &\simiid \beta, \where \E{\beta}=\mu_{\beta}, \var{\beta}=\Sigma_{\beta}^2, \qquad i = 1, \ldots, n+1,\\
\varepsilon_{i,t} &\simiid \normal{0}{\sigma^2}, \qquad t=1, \ldots, T_i, \; i = 1, \ldots, n+1,\\
\alpha_i &\simiid  \normal{\mu_{\alpha}}{\sigma^2_{\alpha}}, \qquad  i = 1, \ldots, n+1; \\
\eta &\indep  \alpha_i \indep \phi \indep \theta \indep \varepsilon_{i,t}.
\end{align*}
Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
for $i = 1, \ldots, n+1$.  %Although synthesizing information from disparate time series assumes similarities of shock effects, shock effects may differ in terms of their means in practice. 
We also consider a model where the shock effects are linear functions of covariates and 
lagged covariates with an additional additive mean-zero error.
%Additionally, $\mc{M}_1$ can be further improved in the sense that the shock effects may depend on the covariates around the shock time points, i.e., $T_i^*$ for $i = 1, \ldots, n+1$. 
%$\mc{M}_2$ can be constructed to accommodate those issues by imposing additional structures on the means of $\alpha_i$ as in (\ref{model2}) for $i = 1, \ldots, n+1$.
The random effects structure for this model (model $\mc{M}_2$) is:
\begin{align}
\mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t}+ \beta_i'\mbf{x}_{i, t-1} + \varepsilon_{i,t}\\[.2cm]
  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}+\t{\varepsilon}_{i, T_i},
\end{array}\label{model2}
\end{align}
for $i = 1, \ldots, n+1$, where the added random effects are
\begin{align*}
\t{\varepsilon}_{i} &\simiid  \normal{0}{\sigma^2_{\alpha}}, \qquad  i = 1, \ldots, n+1; \\
\eta &\indep  \alpha_i \indep \phi \indep \theta \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
\end{align*}
%and $\delta_i$ and $\gamma_i$ will be discussed shortly. 
We further define 
$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T_i^*-1}$. 
We will investigate post-shock aggregated estimators in $\mc{M}_2$ 
in settings where $\delta_i$ and $\gamma_i$ are either fixed or random. 
We let $\mc{M}_{21}$ denote model $\mc{M}_{2}$ with $\gamma_i = \gamma$ 
and $\delta_i = \delta$ for $i= 1, \ldots, n+1$, 
where $\gamma$ and $\delta$ are fixed unknown parameters.
We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects 
structure for $\gamma$ and $\delta$:
\begin{align*}
\begin{array}{c}
  \gamma_i \overset{iid}{\sim} \mrm{E}(\gamma) = \mu_\gamma, \var{\gamma} = \Sigma_\gamma \\
  \delta_i \overset{iid}{\sim} \mrm{E}(\delta) = \mu_\delta, \var{\delta} = \Sigma_\delta
\end{array}
   \quad \text{ with } \quad  \delta_i  \indep \t{\varepsilon}_{i} \quad  \text{ and } \quad \gamma_i  \indep \t{\varepsilon}_{i}.
\end{align*}
Note that $\delta_i$ and $\gamma_i$ may be dependent. We further define the parameter sets
\begin{align}
  \begin{array}{lll}
     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\}.\\
    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 1\}.\label{parameter},
  \end{array}
\end{align}
where $\Theta$ and $\Theta_1$ can adapt to $\mc{M}_1$ by dropping $\delta_i$ and 
$\gamma_i$. We assume this for notational simplicity.

\subsection{Forecast}
\label{forecast}
In this section we show how post-shock aggregate estimators improve upon standard 
forecasts that do not account for the shock effect.
%The interest of this study lies in comparing how consideration of shock effects 
%improves the prediction. 
More formally, we will consider the following candidate forecasts: 
\begin{align*}
  &\text{Forecast 1}: \hat y_{1,T_1^*+1}^1 = \hat\eta_1 
    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
    + \hat\beta_1'\x_{1,T_1^*}, \\
  &\text{Forecast 2}: \hat y_{1,T_1^*+1}^2 = \hat\eta_1 
    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
    + \hat\beta_1'\x_{1,T_1^*} + \hat{\alpha},
\end{align*}
where $\hat\eta_1$, $\hat\phi_1$, $\hat\theta_1$, and $\hat\beta_1$ are all 
OLS estimators of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$ respectively, 
and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$. 
The first forecast ignores the presence of $\alpha_1$ while the second forecast 
incorporates an estimate of $\alpha_1$ that is obtained from the other individual 
forecasts under study. 
%Under $\mc{M}_1$ (Section \ref{modelsetup}), $\E{\alpha_1} = \mu_{\alpha}$.

Note that the two forecasts do not differ in their predictions for 
$y_{1,t}$, $t = 1,\ldots T_1^*$, they only differ in predicting 
$y_{1,T_1^*+1}$. Throughout the rest of this article we show that the collection of 
disparate time series $\{y_{i,t}, t = 2,\ldots,T_i, i = 1,\ldots,n\}$ has 
the potential to improve the forecasts for $y_{1, t}$ when $t > T_1^*$ under different 
circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$. 
It is important to note that in general $\hat{\alpha}$ 
is not a consistent estimator of the unobserved $\alpha_1$ nor does it converge 
to $\alpha_1$.  Despite these inferential shortcomings, adjustment of the forecast 
for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has 
the potential to lower forecast risk under several conditions corresponding to 
different estimators of $\alpha_1$. % which will be discussed shortly.

\subsection{Construction of shock effects estimators}
\label{constructionofestimators}

We now construct the aggregate estimators of the shock effects that appear in 
Forecast 2. We use these to forecast response values $y_{1, t}$ when 
$t > T_1^*$, i.e., the time series of interest after the shock time where we 
assume that $T_1^*$ is known.  %Notice that the shock effect 
%for time series $1$ is typically unobserved. But we can gather knowledge from 
%disparate time series to construct some sort of estimators that may be helpful for 
%estimating $\E{\alpha_1}$. 
First, we introduce the procedures of parameter estimation for 
$\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
Conditional on all regression parameters, previous responses, and covariates, 
the response variable $y_{i,t}$ in $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ 
has distribution 
$$
  y_{i,t} 
    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
      + \beta_i'\x_{i,t-1}, \sigma^2).
$$
For $i = 2, \ldots, n$, all parameters in this model will be estimated with ordinary least squares 
(OLS) using historical data of $t = 1, \ldots, n_i$. For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$. In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate 
of $\alpha_i$.  Note that parameter estimation 
for $\mc{M}_1$ is identically the same as $\mc{M}_{21}$ and $\mc{M}_{22}$.

Second, we introduce the candidate estimators for $\alpha_1$. Define the 
\emph{adjustment estimator} for time series $i=1$ by,
\begin{equation} \label{adjusted}
  \hat{\alpha}_{\text{adj}} = \frac{1}{n}\sum_{i=2}^{n+1}\hat{\alpha}_i,
\end{equation}
where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of all of 
the $\alpha_i$s.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
the unknown $\alpha_1$ term for which no meaningful estimation information 
otherwise exists. It is intuitive that $\hat{\alpha}_{\rm adj}$ should perform 
well under $\mc{M}_1$ where we assume that $\alpha_i$'s share the same mean 
for $i= 1, \ldots, n+1$. However, it can also be shown that 
$\hat{\alpha}_{\rm adj}$ may be less favorable in $\mc{M}_{21}$ 
and $\mc{M}_{22}$, which will be discussed in detail in Section \ref{properties}.

We also consider the \emph{inverse-variance weighted estimator} 
in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i$. 
The inverse-variance weighted estimator is defined as 
\begin{align*}
  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{U}_i)_{22}^{-1},
\end{align*}
 $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
and $\mbf{U}_i$ is the design matrix for OLS with respect to time series 
for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
is required and the numerator and denominator terms are dependent in general. 
%It is hard to evaluate its expectation and variance. 
%But it is clear 
%that $\hat{\alpha}_{\rm IVW}$ will generally not be unbiased. 
However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in 
practical settings. %when the change 
%point is not symmetric and/or there are some series with small or large number 
%of time points recorded. We will then investigate the performance of this 
%estimator in simulation (Section \ref{simulation}).
We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ 
and $\var{\hat{\alpha}_{\rm IVW}}$, empirical performance of 
$\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation 
(see Section \ref{simulation}).

%More importantly, we introduce the backgrounds and procedures of constructing \emph{weighted-adjustment estimator} as follows. 
We now motivate a \emph{weighted-adjustment estimator} for model $\mc{M}_{21}$ 
and $\mc{M}_{22}$. Our weighted-adjustment estimator is inspired by the 
weighting techniques in synthetic control methodology (SCM) developed 
in \cite{abadie2010synthetic}. 
%we intend to construct a weighted adjustment estimator by using similar but 
%different methods. 
However, our weighted-adjustment estimator is not a causal estimator and 
our estimation premise is a reversal of that in SCM. 
%The case study of \citet{abadie2010synthetic} in essence observes the data and 
%estimates the effect of policy. 
Our objective is in predicting a post-shock response $y_{1,T_1^*+1}$ that is not yet 
observed using disparate time series whose post-shock responses are observed.
%However, the idea of merging information from  similar events (i.e., time series in our 
%study) to improve the solutions for the problem of interest should be the same.

We use similar notation as that in \cite{abadie2010synthetic} to motivate 
our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
\begin{align*}
  \mbf{X}_1 = \begin{pmatrix}
    \mbf{x}_{1, T_1^*-1} \\ \mbf{x}_{1, T_1^*}
  \end{pmatrix} \quad 
  \text{ and } \quad \mbf{X}_0 = \begin{pmatrix}
    \mbf{x}_{2, T_2^*-1} & \cdots & \mbf{x}_{n+1, T_{n+1}^*-1} \\
    \mbf{x}_{2, T_2^*} & \cdots & \mbf{x}_{n+1, T_{n+1}^*} 
  \end{pmatrix},
\end{align*}
where $\mbf{X}_1$ is $2 \times 1$ and $\mbf{X}_0$ is $2\times n$. 
Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that
\begin{align}
 \mbf{X}_1=\mbf{X}_0 \mbf{W}  \quad i.e., \quad \mbf{x}_{1, T_1^*-1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*-1} \text{ and } \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*}.\label{SCM}
\end{align}
Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
\begin{align}
    (\mbf{x}_{2, T_2^*-1} & \cdots \mbf{x}_{n+1, T_{n+1}^*-1}, \ldots, 
    \mbf{x}_{2, T_2^*},  \cdots  \mbf{x}_{n+1, T_{n+1}^*}). \label{convexhull}
\end{align}
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
\begin{align}
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mbf{X}_1-\mbf{X}_0\mbf{W}}. 
  \label{W}
\end{align}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
  \begin{align*}
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}.
  \end{align*}
%Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock-effects. 
Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.

\begin{remark}
% Though in Section \ref{modelsetup} we assume $\mbf{x}_{i,t}\in \reals^p$ and bases construction for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$  on this fact, we will shortly show that the covariates need not be of the same dimension across disparate time series. 
In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta, \beta \in \reals^p$. 
 % We can insert $\mathbf{0}$ into the covariates of disparate time series for the parts that they do not share. For example, suppose $\mathbf{x}_{2, t}, \mathbf{x}_{2, t-1}\in \reals^{p-1}$ and $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}\in \reals^p$ are the covariates for time series 2 and 3. Assume that the $p$th column of $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}$ is the part they do not share. In this case, we can let $\mathbf{x}^{adj}_{2, t}=(\mathbf{x}_{2, t}, \mathbf{0})$, $\mathbf{x}^{adj}_{2, t-1}=(\mathbf{x}_{2, t-1}, \mathbf{0})$ to satisfy the $p$-dimension requirement. 
However, it is not necessary that the all $p$ covariates are important for every time series under study. The regression coefficients $\theta$ and $\beta$ are nuisance parameters that are not of primary importance. 
% In this regard, OLS estimations in software can reparameterize the design matrix.  Of course, the column space of the design matrix does not change compared to the one in original dimension. Thus, the least squares estimators do not change. In other words, OLS estimation need no adjustment. The generalization may only apply to the construction of weighted-adjustment  estimator $\hat{\alpha}_{\rm wadj}$.
It will be understood that structural 0s in $\mbf{x}_{i,t}$ correspond to variables that are unimportant. 
\end{remark}

\section{Forecast risk and properties of shock-effects estimators}
\label{properties}

In this section, we discuss the properties that are related to forecast-risk reduction. In discussion of risk, it is useful to derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.  The expression for the expectations are attached as follow\footnote{The formal justification can be found in Section \ref{exp}.}.

 \begin{enumerate}[label = (\roman*)]
    \item Under $\mc{M}_{1}$, $\E{\hat{\alpha}_{\rm adj}}=\E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha}$.
    \item Under $\mc{M}_{21}$, 
    \begin{align*}
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*} + \frac{1}{n} \sum_{i=2}^{n+2} \gamma' \mbf{x}_{i, T_i^*-1} 
      \quad \text{ and } \quad 
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*} + \gamma' \mbf{x}_{1, T_1^*-1}
    \end{align*}
    \item Under $\mc{M}_{22}$,
    \begin{align*}
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*} + \frac{1}{n} \sum_{i=2}^{n+2}  \mu_{\gamma}'\mbf{x}_{i, T_i^*-1} 
      \quad \text{ and } \quad 
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*} + \mu_{\gamma}' \mbf{x}_{1, T_1^*-1}
    \end{align*}
  \end{enumerate}

Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$. Notice that under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$ (see distributional details of $\alpha_1$ in Section \ref{modelsetup}). Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$. Thus, we collect these results  as the following proposition.

\begin{prop}
\label{unbiased} 
\quad 
\begin{enumerate}[label = (\roman*)]
  \item Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$. Under $\mc{M}_{21}$ and $\mc{M}_{22}$, $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ in general.
  \item Suppose that $\mbf{W}^*$ satisfies (\ref{SCM}). Under $\mc{M}_{1}$, $\mc{M}_{21}$ and $\mc{M}_{22}$, $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
\end{enumerate}
\end{prop}

Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple risk-reduction conditions and invoke a method of comparison, although our primary interest is in reducing forecast risk. % for $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm wadj}$ to reduce risk, and make it more clear with respect to when one is better than the other. 
These conditions will be discussed in Section \ref{conditions} and Section \ref{comparisons}. Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below\footnote{The formal justification can be found in Section \ref{var}}.

\begin{enumerate}[label = (\roman*)]
  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
\begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
\end{align*}
\item Under $\mc{M}_{22}$, 
\begin{align*}
\var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}\var{\alpha_i}\\
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
  + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i}
\end{align*}
\end{enumerate}
Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ 
because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our auto regressive model formulation.  Under $\mc{M}_{22}$, the expression for $\var{\alpha_i}$ is not of closed form because $\gamma_i$ and $\delta_i$ may be dependent when they are placed in a random-effects model. We investigate comparisons between the variability of these estimators in Section \ref{comparisons}.%, we will show under some circumstances, it is possible to compare the variances for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$.

As Section \ref{conditions} and \ref{comparisons} detailed the conditions for risk-reduction and comparisons, they usually involve fixed quantities related to variance and expectation. To make use of those properties in practice, estimation is required. Section \ref{varbootstrap} will introduce a general procedure of \emph{parametric bootstrap} under the context of the problem to attain this purpose.

\subsection{Conditions for risk-reduction for shock-effects estimators}
\label{conditions}

In this section we will discuss the conditions for risk reduction for individual shock-effects estimators under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$. %The reason is that if the estimator of $\alpha_1$ turns out to be an unbiased estimator of $\E{\alpha_1}$, the conditions get  simplified.

\subsubsection{Conditions under $\mc{M}_1$}
 \label{conditionsmodel1}

Recall that Proposition \ref{unbiased} implies that the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ are unbiased for $\E{\alpha_1}$ under $\mc{M}_1$. With this result, we will have  the following propositions that specify the conditions that are necessary for risk reduction.

\begin{prop}
\label{proprisk}Under $\mc{M}_1$,
\begin{enumerate}[label = (\roman*)]
  \item  $R_{T_1^*+1, 2} < R_{T_1^*+1, 1}$ when 
$\Var(\hat{\alpha}_{\rm adj}) < \mu_{\alpha}^2$.
  \item if $\mbf{W}^*$ satisfies (\ref{SCM}), $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm wadj}}<\mu_{\alpha}^2$. 
\end{enumerate}
\end{prop}

Proposition \ref{proprisk} tells that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties. Recalling from variance expression at the beginning of Section \ref{properties}, Proposition \ref{proprisk} shows that the risk-reduction condition is
\begin{align}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2 \label{riskconditionadj}
\end{align}

In terms of the adjustment estimator, $\hat{\alpha}_{\rm adj}$, (\ref{riskconditionadj}) implies two facts: (1) Forecast 2 is preferable to Forecast 1 asymptotically in $n$ 
whenever $\mu_{\alpha} \neq 0$; (2) In finite pool of time series, Forecast 2 is preferable to 
Forecast 1 when the $\mu_{\alpha}$ is large relative to its variability and 
overall regression variability.   %This result is also intuitive. For example, if  $\mu_{\alpha}$ is large, Forecast 1 will definitely work poor because large  $\mu_{\alpha}$ implies shock effects that cannot be ignored.  See Section \ref{forecast} for forecast formulation for details.

For the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$, if  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}. From Proposition \ref{proprisk} and variance expression of $\hat{\alpha}_{\rm wadj}$, the following is the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$.
\begin{align*}
\var{\hat{\alpha}_{\rm wadj}}
 = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
\end{align*}
In this case, Forecast 2 is preferable to Forecast 1 when $\mu_{\alpha}$ is large relative to the \emph{weighted sum of variances for shock effects for other time series} and overall regression variability.  However, the above criteria are generally difficult to evaluate in practice due to the term $\hat{\alpha}_{\rm wadj}$. Section  \ref{varbootstrap} will provide a detailed treatment about how to deal with these technical inequalities in practice.

\subsubsection{Conditions under $\mc{M}_{21}$ and $\mc{M}_{22}$}
\label{conditionsm2122}
The $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$. %It is a more reasonable and general model since it is often the case that shock-effects differ by means among disparate time series in practice. $\mc{M}_{22}$  further adds the random effect structure of $\delta$ and $\gamma$ to  $\mc{M}_{21}$ for generalization.
However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$. %From Proposition \ref{varprop}, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$  will be as in Proposition \ref{propriskwadj2}. 
We now state conditions for risk reduction.

\begin{prop}
\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}), under $\mc{M}_{21}$ and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$. 
\end{prop}

Based on Proposition \ref{propriskwadj2}, we can obtain a similar inequality as in Section \ref{conditionsmodel1} as below
\begin{align*}
\var{\hat{\alpha}_{\rm wadj}}
 = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i} < (\E{\alpha_1})^2,
\end{align*}
where $\var{\alpha_i}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$. The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.

Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally. Hence, Proposition \ref{proprisk} no longer  holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$. But, as an alternative, we can derive similar conditions as below. By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
\begin{align*}
 \E{\alpha_1^2}= \var{\alpha_1}+(\E{\alpha_1})^2
 &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
\end{align*}
Therefore, the above inequality will simply to 
\begin{align*}
 (\E{\alpha_1})^2
 &>\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
\end{align*}
Note that since $\hat{\alpha}_{\rm adj}$ is biased for $\E{\alpha_1}$, the bias term $(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2$ will become complicated and  simplification yields no insightful results.

As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$. In other words, $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$. That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.

Topics of  evaluation of these inequalities in practice can be found in Section \ref{varbootstrap}. As conditions of risk-reduction for individual estimators are obtained, a natural question arises --- which one is better? It will be discussed in Section \ref{comparisons}.

\subsection{Comparisons among estimators}

\label{comparisons}

In comparing  shock-effects estimators, we would assume that the risk-reduction conditions are satisfied as in Section \ref{conditions}.

Denote the risk-reduction quantity for the adjustment estimator as $\Delta_{\rm adj}$, the one for inverse-weighted estimator as $\Delta_{\rm IVW}$, and the one for weighted-adjustment estimator as $\Delta_{\rm wadj}$. As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration. For example, if we find that $\Delta_{\rm wadj}>\Delta_{\rm adj}$ and $\Delta_{\rm wadj}>\Delta_{\rm IVW}$, the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ is the most favorable.

According to  discussion in Section \ref{conditionsm2122}, we know that under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, the risk-reduction quantity for $\hat{\alpha}_{\rm IVW}$ is
\begin{align*}
  \Delta_{\rm IVW} = (\E{\alpha_1})^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2.
\end{align*}
From discussions in Section \ref{conditions}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ differ across models, we will discuss in different cases accordingly.

\subsubsection{Under $\mc{M}_{1}$}

From Proposition \ref{proprisk}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
\begin{align*}
  \Delta_{\rm adj} 
  = \mu_{\alpha}^2 -\var{\hat{\alpha}_{\rm adj}}
\quad   \text{ and } \quad 
  \Delta_{\rm wadj} 
  = \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}.
\end{align*}
Under the framework of $\mc{M}_1$, the risk-reduction quantity  for $\hat{\alpha}_{\rm IVW}$ is
\begin{align*}
  \Delta_{\rm IVW} = \mu_{\alpha}^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2.
\end{align*}
In other words, when $\var{\hat{\alpha}_{\rm wadj}}<\var{\hat{\alpha}_{\rm adj}}$ and $\hat{\alpha}_{\rm wadj} < \var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2$, we would prefer $\hat{\alpha}_{\rm wadj}$ as the best estimator. Other conditions for voting the other estimators as the best one follow similarly.

\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}

According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
\begin{align*}
  \Delta_{\rm adj} 
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
\quad   \text{ and } \quad 
  \Delta_{\rm wadj} 
  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
\end{align*}
In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
\begin{align*}
 \Delta_{\rm IVW} 
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
\end{align*}

For the case of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ , we can derive the following inequality for $\hat{\alpha}_{\rm wadj}$ to be favored over $\hat{\alpha}_{\rm adj}$.
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  -\var{\hat{\alpha}_{\rm wadj}} + \big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2> 0.
\end{align*}

 What insights can we gain from this inequality? We can analyze this inequality from two perspectives. 
 \begin{enumerate}
   \item If it turns out to be fact that the variance of the weighted-adjustment estimator is greater than that of adjustment estimator, we should be aware that  the compromise for variance because of using $\hat{\alpha}_{\rm wadj}$ shouldn't exceed the squared bias, i.e., $\big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2$.
   \item If instead the variance of $\hat{\alpha}_{\rm wadj}$ is smaller than that of $\hat{\alpha}_{\rm adj}$, the above inequality should always hold because $\big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2>0$ under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
 \end{enumerate}

 These are some analytical results for comparison studies among estimators of $\alpha_1$. Next, we will detail a framework for estimation of risk-reduction  quantities using non-parametric bootstrap such that the above inequalities can be  analyzed numerically in practice.

\subsection{Parametric bootstrap for risk-reduction evaluation problems}

In this section, we present a parametric bootstrap procedure for our AR(1) model (see Section \ref{modelsetup}) in approximating the distribution of our shock-effect estimators. In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).

\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model.

In the usual setup of AR($p$) model, the unobserved errors are assumed to be \emph{identically} and \emph{independently distributed}. In other words, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. As in the standard bootstrap, the asymptotic accuracy for OLS parameter estimation is guaranteed under the order of $O(T^{-1/2})$ almost surely, where $T$ is the length of the time series \citep{berkowitz2000recent}. \citet{bose1988edgeworth} showed that it can be further improved to $o(T^{-1/2})$ almost surely under some regularity conditions. Nevertheless, the pseudo time series generated by this procedure are not stationary.

\citet{politis1994stationary} invented the stationary bootstrap method for \emph{strictly stationary} and \emph{weakly dependent} time series. However, the asymptotic accuracy of this procedure to OLS estimation is not known. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$, the parameter of the geometric distribution; this issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to \citet{berkowitz2000recent}. It is up to the user in selecting which procedure to choose but under \emph{different} assumptions on the time-series.

The procedures of bootstrapping AR(1) can be outline as
\begin{enumerate}
  \item From the observed fitted AR(1) model, we have a sample of residuals $\hat{\varepsilon}_{i, t}$'s for $i = 2, \ldots, n+1$ and $t=1, \ldots, T_i$. 
  \item For the $b$th step of bootstrapping, we sampling with replacement from $\hat{\varepsilon}_{i, t}$'s to obtain  the bootstrapped residuals $\hat{\varepsilon}_{i, t}^b$'s.
  \item Pluging $\hat{\varepsilon}_{i, t}^*$ into the original model yields a sample of ``bootstrapped'' response $y_{i, t}^b$'s.
  \item  Compute the estimate of the shock-effects $\hat{\alpha}_i^{b}$ using OLS.
  \item Compute the $\hat{\alpha}_{\rm adj}^{b}$, $\hat{\alpha}_{\rm wadj}^{b}$, and $\hat{\alpha}_{\rm IVW}^{b}$. 
  \item Compute the sample mean, and sample variance of $\hat{\alpha}_{\rm adj}^{b}$, $\hat{\alpha}_{\rm wadj}^{b}$, and $\hat{\alpha}_{\rm IVW}^{b}$.
\end{enumerate}
Note that the estimates yielded by above procedure will provide an approximation for parameters involved in the risk-reduction conditions in Sections \ref{conditions} and \ref{comparisons}. In particular $\overline{\hat{\alpha}_{\rm wadj}}$, the sample mean of $\hat{\alpha}_{\rm wadj}^{b}$, will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}. Therefore, we can judge whether to use a shock-effect estimator, and choose between  shock-effect estimators by this method.

\section{Simulation}

\label{simulation}

\section{Supplementary Materials}

\subsection{Proofs}

\label{proofs}

\subsubsection{Justification of Expectation of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
\label{exp}

The building block for the following proof is the fact that least squares is conditionally unbiased conditioned on $\Theta$.

\noindent \textbf{Case I: under $\mc{M}_{1}$:} It follows that  under $\mc{M}_{1}$ (see Section \ref{modelsetup}),
\begin{align*}
\E{\hat{\alpha}_{\rm adj}} =\frac{1}{n}  \sum_{i=2}^{n+1} \E{\E{\hat{\alpha}_i|\Theta}} = \mu_{\alpha} 
\quad \text{ and } \quad \E{\hat{\alpha}_{\rm wadj}}&= \sum_{i=2}^{n+1} w_i^* \E{\E{\hat{\alpha}_i|\Theta}}= \sum_{i=2}^{n+1} w_i^*\mu_{\alpha}= \mu_{\alpha}.
\end{align*}
where we used the fact that $\sum_{i=2}^{n+1} w_i=1$.

\noindent \textbf{Case II: under $\mc{M}_{21}$ and $\mc{M}_{22}$:} Since $\E{\tilde{\varepsilon}_{i, T_i}}=0$, $\E{\hat{\tilde{\alpha}}_{i}}=\E{\tilde{\alpha}_{i}}=\E{\alpha_{i}}$, it follows that
  \begin{align*}
   \E{\hat{\alpha}_{\rm wadj}}= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}
   &= \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right)\\
   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}\right]\bigg\}\\
   &=\mu_{\alpha}+\mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}\right]\bigg\}.\tag{$\mbf{W}\in \mc{W}$}
   \end{align*}
Similarly,
  \begin{align*}
   \E{\hat{\alpha}_{\rm adj}}
   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \E{\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}}.
   \end{align*}

\subsubsection{Justification of Variance of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
\label{var}

Notice that under the setting of OLS, the design matrix for $\mc{M}_2$ is the same as the one for $\mc{M}_1$. Therefore, it follows that
  \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \E{\var{\hat{\alpha}_{\rm wadj}|\Theta}} + \var{\E{\hat{\alpha}_{\rm wadj}|\Theta}} \\
  &=\mrm{E} \left\{\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\} +\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
\end{align*}
Under $\mc{M}_{21}$ where $\delta_i=\delta$ and $\gamma_i=\gamma$ are fixed unknown parameters,  we will have
  \begin{align}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma^2(\mbf{U}'_i\mbf{U}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
\end{align}
Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \gamma_i \indep \varepsilon_{i,t}$, we have
 \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
  + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i}
\end{align*}
For the adjustment estimator, we simply replace $\mbf{W}^*$ with $1/n\mbf{1}_n$. Thus, under $\mc{M}_{21}$ we have 
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
\end{align*}
Under $\mc{M}_{22}$, we shall have
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}\var{\alpha_i}.
\end{align*}
Notice that $\mc{M}_{1}$ differs from $\mc{M}_{21}$ only by its mean parameterization of $\alpha$ (see Section \ref{modelsetup}). In other words, the variances of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ under $\mc{M}_1$ are the same for those under $\mc{M}_{21}$.

\subsection{Proofs for lemmas and propositions}

\begin{proof-of-proposition}[\ref{unbiased}] The proof for unbiasedness follows immediately from discussions related to expectation in Section \ref{properties}. For the biasedness of  $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$, we write the bias term for $\hat{\alpha}_{\rm adj}$ as below.
\begin{align*}
  \mrm{Bias}(\hat{\alpha}_{\rm adj}) = 
  \begin{cases}
       \frac{1}{n} \sum_{i=2}^{n+1} \delta'(\mbf{x}_{i, T_i^*}-n\mbf{x}_{1, T_1^*}) +  \frac{1}{n} \sum_{i=2}^{n+1} \gamma'(\mbf{x}_{i, T_i^*-1}-n\mbf{x}_{1, T_1^*-1}) & \text{ for } \mc{M}_{21}\\
    \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}'(\mbf{x}_{i, T_i^*}-n\mbf{x}_{1, T_1^*}) +  \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\gamma}'(\mbf{x}_{i, T_i^*-1}-n\mbf{x}_{1, T_1^*-1}) & \text{ for }\mc{M}_{22}
  \end{cases}.
\end{align*}
But it may be unbiased in some special circumstances when the above bias turns out to be 0. \end{proof-of-proposition}

\begin{lem}
  \label{risklemma} The forecast risk difference is $R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2$ for all estimators of $\alpha_1$ that are independent of $\Theta_1$ (see Section \ref{modelsetup}).
\end{lem}

\begin{proof-of-lemma}[\ref{risklemma}]
  Define 
  \begin{align*}
    C(\Theta_1) =\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} + \hat{\beta}_1'\mbf{x}_{1, T_1^*}-(\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}+\beta_1'\mbf{x}_{1,T_1^*}),
  \end{align*}
  where $\Theta_1$ is as defined in (\ref{parameter}). Notice that
  \begin{align*}
    R_{T_1^*+1,1}= \mrm{E}\big\{\big(C(\Theta_1)-\alpha_1\big)^2\big\}
    \qquad \text{ and } 
    \qquad  R_{T_1^*+1,2}= \mrm{E}\big\{\big(C(\Theta_1)+\hat{\alpha}-\alpha_1\big)^2\big\}.
  \end{align*}
  It follows that
  \begin{align*}
    R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-2\E{C(\Theta_1)\hat{\alpha}}-\E{\hat{\alpha}-\alpha_1}^2.
  \end{align*}
  Assuming $\mbf{S}=(\mbf{1}_n, \mbf{y}_{1,t-1}, \mbf{x}_{1}, \mbf{x}_{1,t-1})$ has full rank, under OLS setting, $\hat{\eta}_1$, $\hat{\phi}_1$, $\hat{\theta}_1$, and $\hat{\beta}_1$ are unbiased estimators of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$, respectively under conditioning of $\Theta_1$. Since we assume $\hat{\alpha}$ is independent of $\Theta_1$, through the method of iterated expectation,
  \begin{align*}
    \E{C(\Theta_1)\hat{\alpha}}=\mrm{E}\big\{\hat{\alpha}\cdot \E{C(\Theta_1)\mid \Theta_1}\}=0.
  \end{align*}
  It follows that
  \begin{align*}
    R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2,
  \end{align*}
  which finishes the proof.
\end{proof-of-lemma}

\begin{proof-of-proposition}[\ref{proprisk}] The proofs are arranged into two separate parts as below.

 \textbf{Proof for statement (i):} Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$ because
  \begin{align*}
   E\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
   = \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}
   &= \frac{1}{n}\sum_{i=2}^{n+1}\E{\E{\hat{\alpha}_i\mid \Theta}}\\
   &=  \frac{1}{n}\sum_{i=2}^{n+1}\E{\alpha_i}
   = \mu_{\alpha}=\E{\alpha_1},
  \end{align*}
  where we used the fact that OLS estimator is unbiased when the design matrix $\mbf{U}_i$ is of full rank for all $i = 2, \ldots, n+1$. Because $\alpha_1\indep \varepsilon_{i,t}$, $\E{\hat{\alpha}_{\rm adj}\alpha_1}=\E{\hat{\alpha}_{\rm adj}}\E{\alpha_1}=(\E{\hat{\alpha}_{\rm adj}})^2$. By Lemma \ref{risklemma}, 
    \begin{align*}
    R_{T_1^*+1,1}-R_{T_1^*+1,2}
    &=\E{\alpha_1^2}-\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
   & =\E{\alpha_1^2}-\E{\alpha_1^2}- \E{\hat{\alpha}_{\rm adj}^2}+2\E{\hat{\alpha}_{\rm adj}\alpha_1} \\
   &= \mu_{\alpha}^2 - \var{\hat{\alpha}_{\rm adj}} 
  \end{align*}
  Therefore, as long as we have $\var{\hat{\alpha}_{\rm adj}}<\mu_{\alpha}^2$, we will achieve the risk reduction.

 \textbf{Proof for statement (ii):} By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\mu_{\alpha}$ holds for $\mc{M}_{1}$. Then, similar proof of statement (i) will proves the Proposition.
\end{proof-of-proposition}

\begin{proof-of-proposition}[\ref{propriskwadj2}]
  By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ holds for $\mc{M}_{21}$ and $\mc{M}_{22}$. Then, similar proof of Proposition \ref{propriskadj} will proves the Proposition.
\end{proof-of-proposition}

\bibliographystyle{plainnat}
\bibliography{synthetic-prediction-notes}

\end{document}

### 2020-05-18 manuscript/comp.R
rendered pdf file

@@ -1,0 +1,74 @@
+# require
+require('tikzDevice')
+# set seed
+set.seed(2017)
+# parameter setup
+n = 40; T = 250; mu.alpha = 200; sigma.alpha = 100; sigma.X = 100; sigma = 100
+
+# T* is the shock time point
+Tstar <- floor(T / 2)
+# random effects
+eta <- rnorm(n + 1)
+# with normalization
+theta <- rnorm(n + 1)
+theta <- theta / as.vector(sqrt(crossprod(theta)))
+beta <- rnorm(n + 1)
+beta <- beta / as.vector(sqrt(crossprod(beta)))
+beta.X <- rnorm(n + 1)
+beta.X <- beta.X / as.vector(sqrt(crossprod(beta.X)))
+alpha <- rnorm(n + 1, mean = mu.alpha, sd = sigma.alpha)
+
+# T: time points; n: different time series
+X <- matrix(0, nrow = T + 1, ncol = n + 1)
+X[1, ] <- rnorm(n + 1)
+Y <- matrix(0, nrow = T + 1, ncol = n + 1)
+Y[1,] <- rnorm(n + 1)
+
+# i represents for time -- T
+for(i in 2:(T + 1)){
+  X[i,] <- beta.X * X[i - 1,] + rnorm(n + 1, sd = sigma.X)
+  Y[i, ] <- eta + theta * Y[i - 1,] + beta * X[i,] + 
+    alpha * ifelse(i - 1 > Tstar, 1, 0) + rnorm(n + 1, sd = sigma) 
+}
+
+# compute mu alpha hat
+mu.alpha.hat <- rep(0, n)
+for (j in 2:(n + 1)){
+  # OLS Regression
+  m1 <- lm(Y[2:(T + 1), j] ~ 1 + Y[1:T, j] + X[2:(T + 1), j] + ifelse(1:T > Tstar, 1, 0))
+  # find alpha hat
+  mu.alpha.hat[j - 1] <- coefficients(m1)[4]
+}
+
+alpha.hat <- mean(mu.alpha.hat)
+# alpha.hat
+# sd(mu.alpha.hat) / sqrt(length(mu.alpha.hat))
+
+# compute estimate for Tstar without post shock
+m1 <- lm(Y[2:(Tstar + 1), 1] ~ 1 + Y[1:Tstar, 1] + X[2:(Tstar + 1), 1])
+beta.hat <- coefficients(m1)
[…]

### 2020-05-19 CP_2020.Rmd
added CP analysis script; still in progress

---
title: "ConocoPhillips2020"
author: "Daniel J. Eck"
date: "5/9/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus (COVID-19) recession. Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020. Conoco Phillips is chosen for this analysis because it is a large oil and gas resources [company](http://www.conocophillips.com/about-us/how-energy-works/) with a relatively recent [initial public offering](http://www.conocophillips.com/about-us/our-history/2009-1990/). Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices ([Source](https://www.sciencedirect.com/science/article/pii/S014098830900245X?casa_token=Qi1OhieqW5sAAAAA:tzbKY-_SggD1Han_qWic9qVhiKHwO3YaEDrhi2bBEsozISXaX60paUH87QS2eonuKwak_W8QrA)), and our chosen time frame represents the onset of a significant economic down turn, coupled with OPEC decreasing the global price of oil the Sunday before trading resumes on Monday, March 9th [Source](https://www.cnbc.com/2020/03/08/saudi-arabia-to-hike-oil-output-above-10-million-bpd-in-april-after-opec-deal-collapse.html). Conoco Philips is particularly interesting because it is a young company with no stock information before 1990, thus we use separate companies to estimate the March 9th shock effect.

The current recession followed an inversion of the yield curve, an event that signals that recessions are more likely ([St. Louis Fed](https://files.stlouisfed.org/files/htdocs/publications/economic-synopses/2018/11/30/does-the-yield-curve-really-forecast-recession.pdf), [San Francisco Fed](https://www.frbsf.org/economic-research/files/el2018-07.pdf?source=post_page---------------------------), [Damir Tonik](https://onlinelibrary.wiley.com/doi/pdf/10.1002/jcaf.22400?casa_token=ONwrV5ApkhkAAAAA:Qgh2e8QFSEniGLvPbzST_p1o2PregqnrCoNQrwjSK47iNcySWPHZQOf1_F342Vzog-ayXtpPukAnuMc)). We investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock. We also consider previous OPEC oil supply shocks.

We will borrow from the literature on oil price forecasting to establish appropriate time horizons, forecasting and nowcasting models, and donor pools of disparate time series. Recessions that occured before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 ([Source](https://www.federalreserve.gov/PUBS/ifdp/2011/1022/ifdp1022.htm)). We will use a simple AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months ([Source](https://www.federalreserve.gov/PUBS/ifdp/2011/1022/ifdp1022.htm)). We will consider 30 pre-shock trading days and we will nowcast the immediate shock effect and the shock effect over a future five trading day window. All estimates will be adjusted for inflation: https://www.usinflationcalculator.com

<!-- is strong evidence that recursively estimated AR and ARMA models have lower MSPE than the no-change forecast for predicting real oil prices, especially at horizons of 1 and 3 months. At longer horizons, the no-change forecast of the real price of oil typically is the predictor with the lowest MSPE. These results are robust to the use of real time data ([Source](https://www.federalreserve.gov/PUBS/ifdp/2011/1022/ifdp1022.htm)).  We will use these findings on oil prices as guidelines for constructing time horizons for our AR models, our time horizons will be 30 trading days centered at the reported time of the shock. -->

<!-- # October 22, 1998 - Conoco officially separates from DuPont  -->
<!-- # in the largest IPO in history at that time - nearly $4.4 billion.  -->
<!-- # Conoco stock begins trading again, using a new symbol, "COC,"  -->
<!-- # that honors the name it had held for so many years -  -->
<!-- # Continental Oil Company. -->
<!-- # http://www.conocophillips.com/about-us/our-history/2009-1990/ -->

<!-- # Baron's article on worisome future (written 02/26/2020) -->
<!-- # https://www.barrons.com/articles/energy-companies-find-it-harder-to-cover-their-rich-dividends-51582755434?siteid=yhoof2&yptr=yahoo -->

<!-- # Coronavirus recession began on Feb 20, 2020 -->
<!-- # https://en.wikipedia.org/wiki/Coronavirus_recession -->

We load in the relevant R packages

```{r, message = FALSE}
library(data.table)
library(tidyverse)
library(tseries)
library(quantmod)
```

and load in relevant datasets with some mild preprocessing.

```{r loadCOP, message = "FALSE"}
## Conoco Phillips
getSymbols('COP', from = "2000-01-01")
COP <- as.data.frame(COP)
COP <- COP %>% mutate(Date = rownames(COP))

## Exxon Mobile
getSymbols('XOM', from = "1970-01-01")
XOM <- as.data.frame(XOM)
XOM <- XOM %>% mutate(Date = rownames(XOM))

## Chevron
getSymbols('CVX', from = "1970-01-01")
CVX <- as.data.frame(CVX)
CVX <- CVX %>% mutate(Date = rownames(CVX))

## S&P 500
getSymbols('^GSPC', from = "1970-01-01")
GSPC <- as.data.frame(GSPC)
GSPC <- GSPC %>% mutate(Date = rownames(GSPC))
```

#### Tuesday, September 11, 2001

Here is the 1 day nowcast with S&P 500:

```{r}
## September 11th (no trading from T-F); 1 day nowcast
COP_close <- COP %>% select(COP.Close, Date) %>% 
  rename(COP_Close = COP.Close)
GSPC_close <- GSPC %>% select(GSPC.Close, Date) %>% 
  rename(GSPC_Close = GSPC.Close)
COP_close <- merge(COP_close, GSPC_close)
Y <- COP_close$COP_Close[-1]
COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
start <- which(COP_close$Date == "2001-09-10")
start_day <- as.numeric(1:nrow(COP_close) > start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-29):(start+1), ]
dim(COP_close_small)
m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                 data = COP_close_small)
summary(m_COP_9_11)
alpha_9_11_1 <- summary(m_COP_9_11)$coef[3,1:2]
alpha_9_11_1 #-1.97 (0.41) in 2020 dollars
```

Here is the 1 day nowcast without S&P 500:

```{r}
m_COP_9_11 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
summary(m_COP_9_11)
alpha_9_11_1_no <- summary(m_COP_9_11)$coef[3,1:2]
alpha_9_11_1_no #-1.56 (0.33) in 2020 dollars
```

Here is the 5 day nowcast with S&P 500:

```{r}
COP_close_small <- COP_close[(start-29):(start+5), ]
m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                 data = COP_close_small)
summary(m_COP_9_11)
alpha_9_11_5 <- summary(m_COP_9_11)$coef[3,1:2]
alpha_9_11_5 #-2.19 (0.46) in 2020 dollars
```

Here is the 5 day nowcast without S&P 500:

```{r}
COP_close_small <- COP_close[(start-29):(start+5), ]
m_COP_9_11 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
summary(m_COP_9_11)
alpha_9_11_5_no <- summary(m_COP_9_11)$coef[3,1:2]
alpha_9_11_5_no #-1.55 (0.28) in 2020 dollars
```

#### Monday, September 8th, 2008
<!-- https://www.democracynow.org/2008/9/8/headlines -->

In the weekend before trading began, the United States announced its takeover of Fannie May and Freddie Mac [Source](https://www.treasury.gov/press-center/press-releases/Pages/hp1129.aspx), and it was reported that the nation’s unemployment rate reached five-year highs. It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt [Source](https://www.marketwatch.com/story/lehman-folds-with-record-613-billion-debt).

Here is the 1 day nowcast with S&P 500:

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2008-09-08")
start_day <- as.numeric(1:nrow(COP_close) >= start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
dim(COP_close_small)
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
summary(m_COP_9_08_08)
alpha_9_08_08_1 <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_1 #-6.95 (1.98) in 2020 dollars
```

Here is the 1 day nowcast without S&P 500:

```{r}
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
summary(m_COP_9_08_08)
alpha_9_08_08_1_no <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_1_no #-6.94 (1.94) in 2020 dollars
```

Here is the 5 day nowcast with S&P 500:

```{r}
COP_close_small <- COP_close[(start-30):(start+4), ]
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
summary(m_COP_9_08_08)
alpha_9_08_08_5 <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_5 #-4.20 (1.61) in 2020 dollars
```

Here is the 5 day nowcast with S&P 500:

```{r}
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
summary(m_COP_9_08_08)
alpha_9_08_08_5_no <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_5_no #-4.14 (1.58) in 2020 dollars
```

#### Thursday, November 27, 2014

During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver [Source pg 19](http://pubdocs.worldbank.org/en/339801451407117632/PRN01Mar2015OilPrices.pdf). It is documented that oil prices fall as OPEC opts not to cut production [Source](https://www.cnbc.com/2014/11/27/saudi-oil-minister-says-opec-will-not-cut-oil-production-reuters.html) on November 27th, 2014. This date will serve as our change point when we estimate a shock effect for Conoco Phillips stock.

Here is the 1 day nowcast with S&P 500:

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2014-11-26")
start_day <- as.numeric(1:nrow(COP_close) >= start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
dim(COP_close_small)
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                    data = COP_close_small)
summary(m_COP_11_27_14)
alpha_11_27_14_1 <- summary(m_COP_11_27_14)$coef[3,1:2]
alpha_11_27_14_1 #-5.68 (1.06) in 2020 dollars
```

Here is the 1 day nowcast without S&P 500:

```{r}
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
summary(m_COP_11_27_14)
alpha_11_27_14_1_no <- summary(m_COP_11_27_14)$coef[3,1:2]
alpha_11_27_14_1_no #-5.26 (0.97) in 2020 dollars
```

Here is the 5 day nowcast with S&P 500:

```{r}
COP_close_small <- COP_close[(start-30):(start+4), ]
dim(COP_close_small)
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                    data = COP_close_small)
summary(m_COP_11_27_14)
alpha_11_27_14_5 <- summary(m_COP_11_27_14)$coef[3,1:2]
alpha_11_27_14_5 #-2.69 (0.94) in 2020 dollars
```

Here is the 5 day nowcast without S&P 500:

```{r}
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
summary(m_COP_11_27_14)
alpha_11_27_14_5_no <- summary(m_COP_11_27_14)$coef[3,1:2]
alpha_11_27_14_5_no #-1.23 (0.65) in 2020 dollars
```

```{r}
mat <- rbind(
c(-1.97, 0.41, -1.56, 0.33, -2.19, 0.46, -1.55, 0.28),
c(-6.95, 1.98, -6.94, 1.94, -4.20, 1.61, -4.14, 1.58),
c(-5.68, 1.06, -5.26, 0.97, -2.69, 0.94, -1.23, 0.65)
)
colnames(mat) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no",
                   "a_5","sd_a_5","a_5_no","sd_a_5_no")
rownames(mat) <- c("y2001", "y2008", "y2014")
```

#### The March 9th, 2020 shock effect:

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2020-03-06")
start_day <- as.numeric(1:nrow(COP_close) >= start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
dim(COP_close_small)
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
summary(m_COP_03_09_20)
alpha_03_09_20_1 <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_1 #-10.51414
```

Here is the 5 day shock effect

```{r}
COP_close_small <- COP_close[(start-30):(start+4), ]
dim(COP_close_small)
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
summary(m_COP_03_09_20)
alpha_03_09_20_5 <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_5 #-5.333522
```

```{r, eval = FALSE, echo = FALSE}
## tests
adf.test(dat_COP[50:200, ]$Close)
adf.test(dat_COP[100:210, ]$Close)
adf.test(dat_COP[100:207, ]$mkt_Close)
adf.test(dat_COP[211:252, ]$Close)
adf.test(dat_COP[211:252, ]$mkt_Close)

Box.test(dat_COP[100:210, ]$Close, lag=20, type="Ljung-Box")
kpss.test(dat_COP[100:210, ]$Close, null="Trend")
acf(dat_COP[100:210, ]$Close)

## one level of differencing may be preferred
fit <- arima(x = dat_COP[181:241, ]$Y, order = c(1, 0, 0), 
      xreg = dat_COP[181:241, ]$mkt_Close)
fit

## the post-shock model
fit2 <- arima(x = dat_COP[211:252, ]$Y, order = c(1, 0, 0), 
      xreg = dat_COP[211:252, ]$mkt_Close)
fit2
```

### 2020-05-19 CP_2020.Rmd
minor edit to data analysis

@@
 dim(COP_close_small)
+```
+
+Here is the 1 day nowcast with S&P 500:
+
+```{r}
 m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
@@
 alpha_03_09_20_1 <- summary(m_COP_03_09_20)$coef[3,1:2]
-alpha_03_09_20_1 #-10.51414
+alpha_03_09_20_1 #-10.51414 (1.62901)
 ```
 
-Here is the 5 day shock effect
+Here is the 1 day nowcast without S&P 500:
+
+```{r}
+m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
+summary(m_COP_03_09_20)
+alpha_03_09_20_1_no <- summary(m_COP_03_09_20)$coef[3,1:2]
+alpha_03_09_20_1_no #-10.533756 (1.617991)
+```
+
+Here is the 5 day shock effect with S&P 500:
 
@@
 alpha_03_09_20_5 <- summary(m_COP_03_09_20)$coef[3,1:2]
-alpha_03_09_20_5 #-5.333522
+alpha_03_09_20_5 #-5.333522 (2.077089)
+```
+
+Here is the 5 day shock effect without S&P 500:
+
+```{r}
+m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
+summary(m_COP_03_09_20)
+alpha_03_09_20_5_no <- summary(m_COP_03_09_20)$coef[3,1:2]
+alpha_03_09_20_5_no #-5.314242 (2.031455)
 ```

### 2020-05-20 manuscript/comp.tex
edit of literture review, parametric bootstrap, and Figure 1

% Created by tikzDevice version 0.12.3 on 2020-05-18 21:52:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,289.08);
\begin{scope}
\path[clip] ( 48.00, 48.00) rectangle (554.16,277.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 66.75,172.95) --
	( 68.63,152.47) --
	( 70.51,145.69) --
	( 72.39,140.03) --
	( 74.28,104.28) --
	( 76.16,151.54) --
	( 78.04,154.95) --
	( 79.92,133.81) --
	( 81.80,175.35) --
	( 83.69,166.88) --
	( 85.57,125.70) --
	( 87.45,170.76) --
	( 89.33,129.50) --
	( 91.22,171.48) --
	( 93.10,157.93) --
	( 94.98,132.20) --
	( 96.86,134.97) --
	( 98.74,121.20) --
	(100.63,132.31) --
	(102.51,167.74) --
	(104.39,139.43) --
	(106.27,161.95) --
	(108.15,118.76) --
	(110.04,173.04) --
	(111.92,101.84) --
	(113.80,132.79) --
	(115.68,156.33) --
	(117.57,121.16) --
	(119.45,173.74) --
	(121.33,100.01) --
	(123.21,122.32) --
	(125.09,136.35) --
	(126.98,148.45) --
	(128.86, 99.38) --
	(130.74,159.11) --
	(132.62,177.96) --
	(134.51,146.68) --
	(136.39, 99.65) --
	(138.27,141.14) --
	(140.15,113.97) --
	(142.03, 56.48) --
	(143.92,137.78) --
	(145.80,157.07) --
	(147.68,135.25) --
	(149.56,140.67) --
	(151.45,155.40) --
	(153.33,144.28) --
	(155.21,109.64) --
	(157.09,161.65) --
	(158.97,120.57) --
	(160.86,134.53) --
	(162.74,187.79) --
	(164.62,127.58) --
	(166.50,140.39) --
	(168.39,128.19) --
	(170.27,170.09) --
	(172.15,121.23) --
	(174.03,147.74) --
	(175.91,166.20) --
	(177.80,152.19) --
	(179.68, 95.16) --
	(181.56,137.35) --
	(183.44,180.08) --
	(185.32,152.17) --
	(187.21,170.34) --
	(189.09,168.84) --
	(190.97,130.81) --
	(192.85, 95.27) --
	(194.74,162.93) --
	(196.62,138.78) --
	(198.50,138.61) --
	(200.38,173.02) --
	(202.26,167.54) --
	(204.15,162.63) --
	(206.03,148.90) --
	(207.91,177.00) --
	(209.79,135.59) --
	(211.68,142.01) --
	(213.56,146.72) --
	(215.44,147.34) --
	(217.32,137.83) --
	(219.20,161.38) --
	(221.09,135.23) --
	(222.97,113.76) --
	(224.85,132.15) --
	(226.73,152.10) --
	(228.62,133.70) --
	(230.50,142.92) --
	(232.38,137.94) --
	(234.26, 80.23) --
	(236.14,128.05) --
	(238.03,140.12) --
	(239.91,113.33) --
	(241.79,135.32) --
	(243.67,145.57) --
	(245.56,148.21) --
	(247.44,181.13) --
	(249.32,123.87) --
	(251.20,167.03) --
	(253.08,176.92) --
	(254.97,146.67) --
	(256.85,137.49) --
	(258.73,148.71) --
	(260.61,158.20) --
	(262.49,144.01) --
	(264.38,140.56) --
	(266.26,134.50) --
	(268.14,164.72) --
	(270.02,113.97) --
	(271.91,173.50) --
	(273.79,131.97) --
	(275.67,135.32) --
	(277.55,143.59) --
	(279.43,134.00) --
	(281.32,182.28) --
	(283.20,134.50) --
	(285.08,136.30) --
	(286.96,121.98) --
	(288.85,170.76) --
	(290.73,168.83) --
	(292.61,130.32) --
	(294.49,130.95) --
	(296.37,167.83) --
	(298.26,106.18) --
	(300.14,158.89) --
	(302.02,221.32) --
	(303.90,262.43) --
	(305.79,181.52) --
	(307.67,221.00) --
	(309.55,219.36) --
	(311.43,223.97) --
	(313.31,225.88) --
	(315.20,172.43) --
	(317.08,211.80) --
	(318.96,229.45) --
	(320.84,222.24) --
	(322.73,252.46) --
	(324.61,190.77) --
	(326.49,224.11) --
	(328.37,194.35) --
	(330.25,184.33) --
	(332.14,175.51) --
	(334.02,208.94) --
	(335.90,208.16) --
	(337.78,210.48) --
	(339.67,204.77) --
	(341.55,200.42) --
	(343.43,207.20) --
	(345.31,194.28) --
	(347.19,175.97) --
	(349.08,221.82) --
	(350.96,230.52) --
	(352.84,206.54) --
	(354.72,213.96) --
	(356.60,241.92) --
	(358.49,206.43) --
	(360.37,254.17) --
	(362.25,205.63) --
	(364.13,199.30) --
	(366.02,207.87) --
	(367.90,210.32) --
	(369.78,198.03) --
	(371.66,248.03) --
	(373.54,206.39) --
	(375.43,246.52) --
	(377.31,210.82) --
	(379.19,232.38) --
	(381.07,213.29) --
	(382.96,237.01) --
	(384.84,208.79) --
	(386.72,192.52) --
	(388.60,236.32) --
	(390.48,175.56) --
	(392.37,250.12) --
	(394.25,185.69) --
	(396.13,231.06) --
	(398.01,191.78) --
	(399.90,226.76) --
	(401.78,199.54) --
	(403.66,165.06) --
	(405.54,255.85) --
	(407.42,210.34) --
	(409.31,199.91) --
	(411.19,229.86) --
	(413.07,203.76) --
	(414.95,231.64) --
	(416.84,230.77) --
	(418.72,190.26) --
	(420.60,203.84) --
	(422.48,209.53) --
	(424.36,220.43) --
	(426.25,173.24) --
	(428.13,209.84) --
	(430.01,159.64) --
	(431.89,251.30) --
	(433.77,197.02) --
	(435.66,216.20) --
	(437.54,224.42) --
	(439.42,193.29) --
	(441.30,213.98) --
	(443.19,172.72) --
	(445.07,245.00) --
	(446.95,192.05) --
	(448.83,235.97) --
	(450.71,204.00) --
	(452.60,164.26) --
	(454.48,238.03) --
	(456.36,185.07) --
	(458.24,227.07) --
	(460.13,222.82) --
	(462.01,212.73) --
	(463.89,268.60) --
	(465.77,192.34) --
	(467.65,239.77) --
	(469.54,202.33) --
	(471.42,231.75) --
	(473.30,220.58) --
	(475.18,187.28) --
	(477.07,206.99) --
	(478.95,199.08) --
	(480.83,226.56) --
	(482.71,221.75) --
	(484.59,227.59) --
	(486.48,203.00) --
	(488.36,227.21) --
	(490.24,209.56) --
	(492.12,221.87) --
	(494.01,245.38) --
	(495.89,236.19) --
	(497.77,241.22) --
	(499.65,231.39) --
	(501.53,253.76) --
	(503.42,191.19) --
	(505.30,203.77) --
	(507.18,247.46) --
	(509.06,219.46) --
	(510.94,214.21) --
	(512.83,191.34) --
	(514.71,248.79) --
	(516.59,197.34) --
	(518.47,220.12) --
	(520.36,259.69) --
	(522.24,240.39) --
	(524.12,221.17) --
	(526.00,214.51) --
	(527.88,259.99) --
	(529.77,220.91) --
	(531.65,215.72) --
	(533.53,233.07) --
	(535.41,219.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.98, 48.00) -- (533.53, 48.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.98, 48.00) -- ( 62.98, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.09, 48.00) -- (157.09, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.20, 48.00) -- (251.20, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.31, 48.00) -- (345.31, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.42, 48.00) -- (439.42, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (533.53, 48.00) -- (533.53, 42.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.98, 26.40) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (157.09, 26.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (251.20, 26.40) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (345.31, 26.40) {150};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (439.42, 26.40) {200};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (533.53, 26.40) {250};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 55.58) -- ( 48.00,270.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 55.58) -- ( 42.00, 55.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 98.61) -- ( 42.00, 98.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,141.64) -- ( 42.00,141.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,184.67) -- ( 42.00,184.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,227.69) -- ( 42.00,227.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,270.72) -- ( 42.00,270.72);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 55.58) {$-400$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 98.61) {$-200$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,141.64) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,184.67) {200};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,227.69) {400};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,270.72) {600};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 48.00) --
	(554.16, 48.00) --
	(554.16,277.08) --
	( 48.00,277.08) --
	( 48.00, 48.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (301.08,  2.40) {Time $T$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,162.54) {Response};
\end{scope}
\begin{scope}
\path[clip] ( 48.00, 48.00) rectangle (554.16,277.08);
\definecolor{drawColor}{RGB}{255,106,106}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 66.75,142.83) --
	( 68.63,140.13) --
	( 70.51,141.93) --
	( 72.39,141.91) --
	( 74.28,142.43) --
	( 76.16,146.39) --
	( 78.04,141.61) --
	( 79.92,141.14) --
	( 81.80,143.78) --
	( 83.69,140.06) --
	( 85.57,141.28) --
	( 87.45,144.25) --
	( 89.33,140.02) --
	( 91.22,143.17) --
	( 93.10,140.45) --
	( 94.98,141.62) --
	( 96.86,143.92) --
	( 98.74,143.18) --
	(100.63,144.99) --
	(102.51,143.92) --
	(104.39,140.49) --
	(106.27,143.03) --
	(108.15,141.75) --
	(110.04,144.93) --
	(111.92,140.19) --
	(113.80,146.77) --
	(115.68,143.66) --
	(117.57,141.45) --
	(119.45,144.73) --
	(121.33,140.27) --
	(123.21,146.15) --
	(125.09,144.70) --
	(126.98,143.27) --
	(128.86,141.92) --
	(130.74,146.15) --
	(132.62,140.59) --
	(134.51,139.83) --
	(136.39,141.78) --
	(138.27,147.01) --
	(140.15,142.91) --
	(142.03,145.16) --
	(143.92,150.29) --
	(145.80,143.35) --
	(147.68,141.31) --
	(149.56,142.82) --
	(151.45,142.93) --
	(153.33,141.23) --
	(155.21,142.28) --
	(157.09,144.73) --
	(158.97,141.28) --
	(160.86,144.80) --
	(162.74,143.76) --
	(164.62,139.14) --
	(166.50,144.55) --
	(168.39,142.11) --
	(170.27,143.40) --
	(172.15,140.31) --
	(174.03,144.97) --
	(175.91,141.97) --
	(177.80,140.53) --
	(179.68,141.81) --
	(181.56,146.17) --
	(183.44,143.43) --
	(185.32,139.06) --
	(187.21,142.38) --
	(189.09,140.37) --
	(190.97,141.03) --
	(192.85,143.88) --
	(194.74,146.77) --
	(196.62,140.46) --
	(198.50,143.03) --
	(200.38,141.89) --
	(202.26,140.44) --
	(204.15,139.71) --
	(206.03,141.07) --
	(207.91,142.19) --
	(209.79,139.86) --
	(211.68,142.89) --
	(213.56,142.17) --
	(215.44,142.86) --
	(217.32,142.40) --
	(219.20,143.71) --
	(221.09,141.02) --
	(222.97,142.74) --
	(224.85,145.76) --
	(226.73,143.65) --
	(228.62,141.79) --
	(230.50,143.50) --
	(232.38,142.42) --
	(234.26,142.91) --
	(236.14,147.76) --
	(238.03,143.33) --
	(239.91,142.66) --
	(241.79,145.02) --
	(243.67,143.33) --
	(245.56,142.23) --
	(247.44,142.51) --
	(249.32,139.83) --
	(251.20,143.91) --
	(253.08,140.91) --
	(254.97,139.48) --
	(256.85,142.03) --
	(258.73,142.30) --
	(260.61,142.42) --
	(262.49,141.41) --
	(264.38,142.28) --
	(266.26,143.37) --
	(268.14,143.80) --
	(270.02,141.46) --
	(271.91,145.00) --
	(273.79,140.14) --
	(275.67,144.39) --
	(277.55,142.54) --
	(279.43,143.15) --
	(281.32,143.33) --
	(283.20,139.76) --
	(285.08,143.03) --
	(286.96,142.39) --
	(288.85,144.66) --
	(290.73,140.34) --
	(292.61,139.93) --
	(294.49,143.71) --
	(296.37,143.28) --
	(298.26,140.41) --
	(300.14,145.43) --
	(302.02,140.85) --
	(303.90,136.75) --
	(305.79,132.94) --
	(307.67,139.42) --
	(309.55,135.87) --
	(311.43,136.63) --
	(313.31,135.78) --
	(315.20,135.92) --
	(317.08,140.12) --
	(318.96,136.56) --
	(320.84,134.76) --
	(322.73,135.54) --
	(324.61,133.98) --
	(326.49,138.52) --
	(328.37,135.72) --
	(330.25,138.98) --
	(332.14,139.33) --
	(334.02,140.22) --
	(335.90,136.88) --
	(337.78,137.21) --
	(339.67,136.66) --
	(341.55,137.15) --
	(343.43,138.26) --
	(345.31,136.84) --
	(347.19,138.24) --
	(349.08,139.43) --
	(350.96,136.01) --
	(352.84,135.41) --
	(354.72,136.89) --
	(356.60,136.87) --
	(358.49,134.00) --
	(360.37,138.00) --
	(362.25,133.77) --
	(364.13,137.44) --
	(366.02,136.97) --
	(367.90,136.64) --
	(369.78,136.51) --
	(371.66,138.07) --
	(373.54,134.02) --
	(375.43,137.34) --
	(377.31,134.24) --
	(379.19,137.50) --
	(381.07,134.80) --
	(382.96,138.20) --
	(384.84,133.93) --
	(386.72,136.89) --
	(388.60,138.15) --
	(390.48,134.68) --
	(392.37,139.28) --
	(394.25,133.59) --
	(396.13,139.33) --
	(398.01,135.30) --
	(399.90,137.96) --
	(401.78,135.47) --
	(403.66,137.90) --
	(405.54,140.60) --
	(407.42,133.45) --
	(409.31,136.69) --
	(411.19,137.22) --
	(413.07,135.30) --
	(414.95,137.11) --
	(416.84,134.45) --
	(418.72,135.26) --
	(420.60,139.07) --
	(422.48,137.43) --
	(424.36,137.15) --
	(426.25,136.50) --
	(428.13,140.82) --
	(430.01,138.00) --
	(431.89,141.05) --
	(433.77,133.05) --
	(435.66,137.92) --
	(437.54,136.77) --
	(439.42,135.43) --
	(441.30,139.49) --
	(443.19,136.51) --
	(445.07,140.20) --
	(446.95,134.28) --
	(448.83,139.11) --
	(450.71,134.98) --
	(452.60,137.08) --
	(454.48,141.67) --
	(456.36,134.46) --
	(458.24,139.63) --
	(460.13,134.69) --
	(462.01,135.78) --
	(463.89,137.05) --
	(465.77,131.53) --
	(467.65,138.29) --
	(469.54,134.65) --
	(471.42,137.65) --
	(473.30,135.03) --
	(475.18,136.76) --
	(477.07,138.74) --
	(478.95,137.36) --
	(480.83,138.23) --
	(482.71,135.82) --
	(484.59,135.95) --
	(486.48,135.89) --
	(488.36,136.74) --
	(490.24,135.40) --
	(492.12,136.77) --
	(494.01,135.94) --
	(495.89,133.46) --
	(497.77,134.48) --
	(499.65,134.68) --
	(501.53,135.56) --
	(503.42,134.09) --
	(505.30,139.32) --
	(507.18,138.00) --
	(509.06,133.98) --
	(510.94,136.16) --
	(512.83,136.35) --
	(514.71,138.27) --
	(516.59,133.84) --
	(518.47,137.50) --
	(520.36,136.90) --
	(522.24,132.66) --
	(524.12,134.57) --
	(526.00,136.61) --
	(527.88,136.86) --
	(529.77,132.70) --
	(531.65,135.88) --
	(533.53,136.61) --
	(535.41,134.54);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 66.75,142.83) --
	( 68.63,140.13) --
	( 70.51,141.93) --
	( 72.39,141.91) --
	( 74.28,142.43) --
	( 76.16,146.39) --
	( 78.04,141.61) --
	( 79.92,141.14) --
	( 81.80,143.78) --
	( 83.69,140.06) --
	( 85.57,141.28) --
	( 87.45,144.25) --
	( 89.33,140.02) --
	( 91.22,143.17) --
	( 93.10,140.45) --
	( 94.98,141.62) --
	( 96.86,143.92) --
	( 98.74,143.18) --
	(100.63,144.99) --
	(102.51,143.92) --
	(104.39,140.49) --
	(106.27,143.03) --
	(108.15,141.75) --
	(110.04,144.93) --
	(111.92,140.19) --
	(113.80,146.77) --
	(115.68,143.66) --
	(117.57,141.45) --
	(119.45,144.73) --
	(121.33,140.27) --
	(123.21,146.15) --
	(125.09,144.70) --
	(126.98,143.27) --
	(128.86,141.92) --
	(130.74,146.15) --
	(132.62,140.59) --
	(134.51,139.83) --
	(136.39,141.78) --
	(138.27,147.01) --
	(140.15,142.91) --
	(142.03,145.16) --
	(143.92,150.29) --
	(145.80,143.35) --
	(147.68,141.31) --
	(149.56,142.82) --
	(151.45,142.93) --
	(153.33,141.23) --
	(155.21,142.28) --
	(157.09,144.73) --
	(158.97,141.28) --
	(160.86,144.80) --
	(162.74,143.76) --
	(164.62,139.14) --
	(166.50,144.55) --
	(168.39,142.11) --
	(170.27,143.40) --
	(172.15,140.31) --
	(174.03,144.97) --
	(175.91,141.97) --
	(177.80,140.53) --
	(179.68,141.81) --
	(181.56,146.17) --
	(183.44,143.43) --
	(185.32,139.06) --
	(187.21,142.38) --
	(189.09,140.37) --
	(190.97,141.03) --
	(192.85,143.88) --
	(194.74,146.77) --
	(196.62,140.46) --
	(198.50,143.03) --
	(200.38,141.89) --
	(202.26,140.44) --
	(204.15,139.71) --
	(206.03,141.07) --
	(207.91,142.19) --
	(209.79,139.86) --
	(211.68,142.89) --
	(213.56,142.17) --
	(215.44,142.86) --
	(217.32,142.40) --
	(219.20,143.71) --
	(221.09,141.02) --
	(222.97,142.74) --
	(224.85,145.76) --
	(226.73,143.65) --
	(228.62,141.79) --
	(230.50,143.50) --
	(232.38,142.42) --
	(234.26,142.91) --
	(236.14,147.76) --
	(238.03,143.33) --
	(239.91,142.66) --
	(241.79,145.02) --
	(243.67,143.33) --
	(245.56,142.23) --
	(247.44,142.51) --
	(249.32,139.83) --
	(251.20,143.91) --
	(253.08,140.91) --
	(254.97,139.48) --
	(256.85,142.03) --
	(258.73,142.30) --
	(260.61,142.42) --
	(262.49,141.41) --
	(264.38,142.28) --
	(266.26,143.37) --
	(268.14,143.80) --
	(270.02,141.46) --
	(271.91,145.00) --
	(273.79,140.14) --
	(275.67,144.39) --
	(277.55,142.54) --
	(279.43,143.15) --
	(281.32,143.33) --
	(283.20,139.76) --
	(285.08,143.03) --
	(286.96,142.39) --
	(288.85,144.66) --
	(290.73,140.34) --
	(292.61,139.93) --
	(294.49,143.71) --
	(296.37,143.28) --
	(298.26,140.41) --
	(300.14,194.20) --
	(302.02,189.62) --
	(303.90,185.53) --
	(305.79,181.72) --
	(307.67,188.20) --
	(309.55,184.65) --
	(311.43,185.40) --
	(313.31,184.56) --
	(315.20,184.70) --
	(317.08,188.90) --
	(318.96,185.34) --
	(320.84,183.53) --
	(322.73,184.32) --
	(324.61,182.76) --
	(326.49,187.29) --
	(328.37,184.50) --
	(330.25,187.76) --
	(332.14,188.11) --
	(334.02,189.00) --
	(335.90,185.66) --
	(337.78,185.99) --
	(339.67,185.43) --
	(341.55,185.92) --
	(343.43,187.03) --
	(345.31,185.62) --
	(347.19,187.02) --
	(349.08,188.21) --
	(350.96,184.78) --
	(352.84,184.18) --
	(354.72,185.67) --
	(356.60,185.65) --
	(358.49,182.77) --
	(360.37,186.77) --
	(362.25,182.54) --
	(364.13,186.22) --
	(366.02,185.75) --
	(367.90,185.41) --
	(369.78,185.28) --
	(371.66,186.84) --
	(373.54,182.80) --
	(375.43,186.12) --
	(377.31,183.02) --
	(379.19,186.28) --
	(381.07,183.58) --
	(382.96,186.97) --
	(384.84,182.70) --
	(386.72,185.67) --
	(388.60,186.93) --
	(390.48,183.46) --
	(392.37,188.06) --
	(394.25,182.37) --
	(396.13,188.11) --
	(398.01,184.08) --
	(399.90,186.74) --
	(401.78,184.24) --
	(403.66,186.67) --
	(405.54,189.37) --
	(407.42,182.23) --
	(409.31,185.46) --
	(411.19,186.00) --
	(413.07,184.08) --
	(414.95,185.89) --
	(416.84,183.23) --
	(418.72,184.04) --
	(420.60,187.85) --
	(422.48,186.21) --
	(424.36,185.93) --
	(426.25,185.27) --
	(428.13,189.59) --
	(430.01,186.78) --
	(431.89,189.83) --
	(433.77,181.83) --
	(435.66,186.69) --
	(437.54,185.54) --
	(439.42,184.20) --
	(441.30,188.26) --
	(443.19,185.29) --
	(445.07,188.98) --
	(446.95,183.06) --
	(448.83,187.89) --
	(450.71,183.76) --
	(452.60,185.86) --
	(454.48,190.44) --
	(456.36,183.23) --
	(458.24,188.40) --
	(460.13,183.47) --
	(462.01,184.56) --
	(463.89,185.83) --
	(465.77,180.31) --
	(467.65,187.07) --
	(469.54,183.42) --
	(471.42,186.43) --
	(473.30,183.81) --
	(475.18,185.53) --
	(477.07,187.52) --
	(478.95,186.14) --
	(480.83,187.00) --
	(482.71,184.60) --
	(484.59,184.73) --
	(486.48,184.66) --
	(488.36,185.52) --
	(490.24,184.18) --
	(492.12,185.54) --
	(494.01,184.71) --
	(495.89,182.24) --
	(497.77,183.25) --
	(499.65,183.46) --
	(501.53,184.33) --
	(503.42,182.87) --
	(505.30,188.10) --
	(507.18,186.77) --
	(509.06,182.75) --
	(510.94,184.94) --
	(512.83,185.13) --
	(514.71,187.05) --
	(516.59,182.61) --
	(518.47,186.28) --
	(520.36,185.68) --
	(522.24,181.44) --
	(524.12,183.35) --
	(526.00,185.39) --
	(527.88,185.63) --
	(529.77,181.48) --
	(531.65,184.66) --
	(533.53,185.38) --
	(535.41,183.31);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (298.26, 55.58) -- (298.26,270.72);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,196.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,189.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,206.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,189.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,168.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,154.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,222.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,169.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,198.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,201.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,175.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,186.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,164.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,212.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,202.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,181.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,162.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,221.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,193.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,216.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,190.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,176.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,192.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,184.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,224.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,181.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,185.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,188.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,187.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,186.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,184.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,227.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,193.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,191.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,169.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,192.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,195.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,184.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,192.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,174.59) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.84,137.34) -- (320.84,186.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (318.31,141.72) --
	(320.84,137.34) --
	(323.37,141.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.37,181.74) --
	(320.84,186.12) --
	(318.31,181.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.55,190.42) -- (292.61,190.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.23,187.89) --
	(292.61,190.42) --
	(288.23,192.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (373.54,158.80) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i=226.72$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (270.02,187.92) {$\hat{\alpha}_i$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (354.72, 63.76) {shock time point $T^*_1$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.98,270.72) rectangle (206.60,234.72);
\definecolor{drawColor}{RGB}{255,106,106}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 71.98,258.72) -- ( 89.98,258.72);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 71.98,246.72) -- ( 89.98,246.72);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 98.98,255.28) {$\hat{Y}$ without shock effects};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 98.98,243.28) {$\hat{Y}$ with shock effects};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-05-20 manuscript/manuscript.tex
minor edit to manuscript
made minor edit to the manuscript
edit of literture review, parametric bootstrap, and Figure 1

@@
 \usepackage{caption}
+\usepackage{float}
 \usepackage{tikz}
+\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
 % margin setup
@@
 Possible searches include pooling, time series pooling, bayesian time series, bayesian autoregression)
-  \item Explore bootstrapping
   \item Data analysis
 \end{enumerate}
-
-In R, \texttt{optim} function in \texttt{base} and \texttt{Rsolnp} package may be helpful for solving the minimization problems in synthetic control methods.
 
@@
 \begin{enumerate}
-  \item The manuscript is revised according to the comments and unnecessary parts are deleted.
-  \item Parametric bootstrap for AR(1) is added in Section  3.3 with some references added.
-  \item A couple of references are added in the introduction but more to be added.
+  \item Figure 1 is updated.
+  \item Some introductions for forecast combination are added in Paragraph 2. Literature review for time-series pooling in cross-sectional (panel) data is rewritten and more to be added.
+  \item The procedure for parametric bootstrap is rewritten.
+  \item Technical details for SCM method are updated.
+  \item SCM code is written using \texttt{Rsolnp} package.
 \end{enumerate}
@@
 
+Forecast combination is a general term for a plethora of  methods for combining forecasts, e.g., (1) model averaging \citep{newbold2002forecast, timmermann2006forecast, hansen2008least}, (2) model selection \citep{lee2015model,greenaway2020multistep}, (3) time-series pooling \citep{mundlak1978pooling,zellner1991forecasting, lee2020estimation,plessen2020integrated}.
+Model averaging typically selects weights for models based on minimizing various loss functions whereas model selection chooses the model through minimization of those loss functions, see for example, \citet{fosten2019panel}.
+Time-series pooling is a broad topic for borrowing information from multiple time series for prediction improvement and is the focus of this paper.
+Before discussion of time-series pooling literature, we will first introduce the problem statement of our study.
+
 In this article we provide forecasting adjustment techniques with the goal 
@@
 
-\vspace{.3cm}
+ The literature of time-series pooling is mainly related to pooling cross-sectional panel data \citep{mundlak1978pooling, zellner1991forecasting, fosten2019panel}.
+The issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded.
+\citet{baltagi2008forecasting} showed that homogeneity approach often outperform   heterogeneity one in mean squared forecast error; while heterogeneity approach is more general to accommodate differences among units.
 
-\emph{\textcolor{red}{More to be added ...}}
-
-\vspace{.3cm}
-
-Time-series pooling methodology is one of the main methods to deal this problem.
-The literature of time-series pooling is mainly related to pooling cross-sectional data.
-In this setting, estimation of parameters is usually based on merging from different time series using various pooling techniques.
-For example, \citet{zellner1991forecasting} assumes the coefficient vectors of different time series are the same so that the time series can be merged to estimate parameters once in forecasting turning point of GDP growth rate in practice.
-\emph{\textcolor{red}{More to be added ...}}
-
-Modern research in ``combining'' forecasts from disparate time series have taken perspectives from distinct fields.
+Modern researches in ``combining'' forecasts from disparate time series have taken perspectives from distinct fields.
 \citet{lee2020estimation} constructed a Bayesian hierarchical model  to estimate posterior parameters for Richards model to improve predictive precision of COVID-19 infection trajectories for different countries.
@@
 \emph{\textcolor{red}{More to be added ...}}
-
-\begin{figure}[t]
-  \begin{center}
-    \includegraphics[height = 8cm]{comp.pdf}
-    \caption{A comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series and that the shock time is at $T_1^* = 125$.}\label{figure1}
-  \end{center}  
-  \vspace{-.6cm}
-\end{figure}
 
@@
 \label{setting}
+
 We will suppose that an analyst has time series data ($y_{i,t}$,$\x_{i,t}$), 
@@
 are in the next section.
+
+\begin{figure}[H]
+  \begin{center}
+    \includegraphics[height = 8cm]{comp.pdf}
+    \caption{A comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series and that the shock time is at $T_1^* = 125$.
+The dots represent least square estimate $\hat{\alpha}_i$ from disparate time series.
+Two model differs by an adjustment $\hat{\alpha}=\frac{1}{n}\sum_{i=1}^n \hat{\alpha}_i$.}\label{figure1}
+  \end{center}  
+  \vspace{-.6cm}
+\end{figure}
 
@@
 our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
-$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 
+$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 
 $i = 2, \ldots, n+1$. Construct
@@
     \mbf{x}_{1, T_1^*-1} \\ \mbf{x}_{1, T_1^*}
-  \end{pmatrix} \quad 
-  \text{ and } \quad \mbf{X}_0 = \begin{pmatrix}
-    \mbf{x}_{2, T_2^*-1} & \cdots & \mbf{x}_{n+1, T_{n+1}^*-1} \\
-    \mbf{x}_{2, T_2^*} & \cdots & \mbf{x}_{n+1, T_{n+1}^*} 
-  \end{pmatrix},
+  \end{pmatrix}
+  \quad \text{ and }
+  \quad  \hat{\mbf{X}}_1(\mbf{W})
+  = w_2\begin{pmatrix}
+     \mbf{x}_{2, T_2^*-1} \\
+      \mbf{x}_{2, T_2^*}
+   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
+     \mbf{x}_{n+1, T_{n+1}^*} \\
+      \mbf{x}_{n+1, T_{n+1}^*}
+   \end{pmatrix} .
 \end{align*}
-where $\mbf{X}_1$ is $2 \times 1$ and $\mbf{X}_0$ is $2\times n$. 
-Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
+where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
 Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
-$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that
+$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that
 \begin{align}
- \mbf{X}_1=\mbf{X}_0 \mbf{W}  \quad i.e., \quad \mbf{x}_{1, T_1^*-1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*-1} \text{ and } \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*}.\label{SCM}
+ \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*-1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*-1} \text{ and } \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*}.\label{SCM}
 \end{align}
  Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
-\begin{align}
-    (\mbf{x}_{2, T_2^*-1} & \cdots \mbf{x}_{n+1, T_{n+1}^*-1}, \ldots, 
-    \mbf{x}_{2, T_2^*},  \cdots  \mbf{x}_{n+1, T_{n+1}^*}). \label{convexhull}
-\end{align}
+ \begin{align*}
+   \left\{ \begin{pmatrix}
+     \mbf{x}_{2, T_2^*-1} \\
+      \mbf{x}_{2, T_2^*}
+   \end{pmatrix}, \ldots, \begin{pmatrix}
+     \mbf{x}_{n+1, T_{n+1}^*} \\
+      \mbf{x}_{n+1, T_{n+1}^*}
+   \end{pmatrix} \right\}.
+ \end{align*}
 %It is a reasonable assumption that the pool of time series that we are considering 
@@
 \begin{align}
-  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mbf{X}_1-\mbf{X}_0\mbf{W}}. 
+  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})\big)}_{2p}. 
   \label{W}
@@
 
-The procedures of bootstrapping AR(1) can be outline as
-\begin{enumerate}
-  \item From the observed fitted AR(1) model, we have a sample of residuals $\hat{\varepsilon}_{i, t}$'s for $i = 2, \ldots, n+1$ and $t=1, \ldots, T_i$. 
-  \item For the $b$th step of bootstrapping, we sampling with replacement from $\hat{\varepsilon}_{i, t}$'s to obtain  the bootstrapped residuals $\hat{\varepsilon}_{i, t}^b$'s.
-  \item Pluging $\hat{\varepsilon}_{i, t}^*$ into the original model yields a sample of ``bootstrapped'' response $y_{i, t}^b$'s.
-  \item  Compute the estimate of the shock-effects $\hat{\alpha}_i^{b}$ using OLS.
-  \item Compute the $\hat{\alpha}_{\rm adj}^{b}$, $\hat{\alpha}_{\rm wadj}^{b}$, and $\hat{\alpha}_{\rm IVW}^{b}$. 
-  \item Compute the sample mean, and sample variance of $\hat{\alpha}_{\rm adj}^{b}$, $\hat{\alpha}_{\rm wadj}^{b}$, and $\hat{\alpha}_{\rm IVW}^{b}$.
-\end{enumerate}
-Note that the estimates yielded by above procedure will provide an approximation for parameters involved in the risk-reduction conditions in Sections \ref{conditions} and \ref{comparisons}.
+\vspace{.2cm}
+\begin{algorithm}[H]
+\SetAlgoLined \label{boots}
+
+\SetKwInOut{Input}{Input}
+\Input{$B$ --  the number of parametric bootstraps  \\ $S_i= \{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ -- the collection of  residuals for $t = 1,\ldots, T_i$ \\ $\mc{P}_i$ -- the fitted AR(1) model for $i = 2, \ldots, n+1$
+
+}
+
+\KwResult{The sample mean, and sample variance of bootstrapped adjustment estimator, inverse-variance weighted estimator, and weighted-adjustment estimator.}
+
+  \For{$b = 1:B$}{
+  \For{$i = 2, \ldots, n+1$}{
+  Sample with replacement from $S_{i}$ to obtain $S_{i}^{(b)}\coloneqq \{\hat{\varepsilon}_{i, t}^{(b)} \colon t = 1, \ldots, T_i\}$
+
+  Plug $S_{i}^{(b)}$ into $\mc{P}_i$ to generate the bootstrapped response $\mbf{Y}_i^{(b)}$
+
+  Compute $\hat{\alpha}_i^{(b)}$ based on OLS estimation of AR(1) with $\mbf{Y}_i^{(b)}$ and covariates from $\mc{P}_i$
+  }
+    Compute $\hat{\alpha}_{\rm adj}^{(b)}$, $\hat{\alpha}_{\rm wadj}^{(b)}$, and $\hat{\alpha}_{\rm IVW}^{(b)}$ 
+  }
+   Compute the sample mean, and sample variance of $\hat{\alpha}_{\rm adj}^{(b)}$, $\hat{\alpha}_{\rm wadj}^{(b)}$, and $\hat{\alpha}_{\rm IVW}^{(b)}$.
+ \caption{Parametric bootstrap for approximation for  mean and  variance of shock-effect estimators of $\alpha_1$.}
+\end{algorithm}
+\vspace{.2cm}
+
+The procedures of bootstrapping AR(1) can be outline as in Algorithm \ref{boots}.
+We stress that the $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for  $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are i.i.d.
+since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$ (see Section \ref{modelsetup}), and it is \emph{not} absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$.
+Therefore, this parametric bootstrap framework will work for us.
+
+The estimates yielded by Algorithm \ref{boots} provides an approximation for parameters involved in the risk-reduction conditions in Sections \ref{conditions} and \ref{comparisons}.
 In particular $\overline{\hat{\alpha}_{\rm wadj}}$, the sample mean of $\hat{\alpha}_{\rm wadj}^{b}$, will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}.

### 2020-05-20 manuscript/comp.R

@@ -53,7 +53,7 @@ Ypred.adjusted <- Ypred.original + alpha.hat * as.matrix(ifelse(2:(T + 1) > Tsta
 # set working directory
 setwd('/Users/mac/Desktop/Research/Post-Shock Prediction/')
 # figure setting
-tikz('comp.tex', standAlone = TRUE, width = 5.5, height = 3)
+tikz('comp.tex', standAlone = TRUE, width = 8, height = 4)
 # plot
 par(mar = c(4, 4, 1, 2))
 # original
@@ -64,7 +64,18 @@ matplot(2:(T + 1), cbind(Y[2:(T + 1), 1], Ypred.original, Ypred.adjusted),
         type = 'l')
 # add shock
 segments(x0 = Tstar, y0 = -400, y1 = 600, col = 'deepskyblue', lty = 2, lwd = 2)
-text(x = Tstar + 40, y = -350, 'shock time point $T^*_1$')
+points(x = rep(125, 40), y = mu.alpha.hat, col = 'magenta')
+# add arrows
+arrows(x0 = 137, y0 = Ypred.original[165],
+       y1 = Ypred.adjusted[165],  code = 3, length = 0.07)
+arrows(x0 = 114, x1 = 122, y0 = alpha.hat, code = 2, length = 0.07)
+# \hat{\alpha}
+text(x = 165, y = mean(c(Ypred.original[165], Ypred.adjusted[165])) - 2, 
+     labels = '$\\displaystyle \\hat{\\alpha} = \\frac{1}{n}\\sum_{i=1}^{n} \\hat{\\alpha}_i=226.72$')
+# alpha_i
+text(x = 110, y = alpha.hat, labels = '$\\hat{\\alpha}_i$')
+# shock time points
+text(x = Tstar + 30, y = -350, 'shock time point $T^*_1$')
 # legends
 legend(x = 0, y = 600, 
        col = c('indianred1', 'magenta'),
@@ -72,3 +83,6 @@ legend(x = 0, y = 600,
        c('$\\hat{Y}$ without shock effects', '$\\hat{Y}$ with shock effects'))
 # output
 dev.off()
+
+
+

### 2020-05-20 CP_2020.Rmd

--- 2020-05-19 CP_2020.Rmd
@@
 ---
-title: "ConocoPhillips2020"
+title: "Conoco Phillips 2020"
 author: "Daniel J. Eck"
@@
 Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices ([Source](https://www.sciencedirect.com/science/article/pii/S014098830900245X?casa_token=Qi1OhieqW5sAAAAA:tzbKY-_SggD1Han_qWic9qVhiKHwO3YaEDrhi2bBEsozISXaX60paUH87QS2eonuKwak_W8QrA)), and our chosen time frame represents the onset of a significant economic down turn, coupled with OPEC decreasing the global price of oil the Sunday before trading resumes on Monday, March 9th [Source](https://www.cnbc.com/2020/03/08/saudi-arabia-to-hike-oil-output-above-10-million-bpd-in-april-after-opec-deal-collapse.html).
-Conoco Philips is particularly interesting because it is a young company with no stock information before 1990, thus we use separate companies to estimate the March 9th shock effect.
+Furthermore, fear of and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
+Major events include the SXSW festival being cancelled as trading closed on March 6th [Source](https://www.cnn.com/world/live-news/coronavirus-outbreak-03-06-20-intl-hnk/h_a8875b987d5086f165e9284304f7c77e),
+<!-- Cornavirus fear began taking ahold of the stock market in late February to early March https://www.cnn.com/world/live-news/coronavirus-outbreak-03-06-20-intl-hnk/h_82c5c28377848e2d8f728f498a08f4f7 -->
+New York declared a state of emergency on March 7th [Source](https://www.governor.ny.gov/news/novel-coronavirus-briefing-governor-cuomo-declares-state-emergency-contain-spread-virus), and by Sunday, March 8th, eight states have declared a state of emergency while Italy placed 16 million people in quarantine [Source](https://www.newsweek.com/what-us-states-have-declared-state-emergency-amid-coronavirus-outbreak-1491299).
 
-The current recession followed an inversion of the yield curve, an event that signals that recessions are more likely ([St.
+<!-- Jim Jim Tankersley,  https://www.nytimes.com/2020/03/09/podcasts/coronavirus-stock-market-crash.html
+-->
+
+<!-- Conoco Philips is particularly interesting because it is a young company with no stock information before 1990, thus we use separate companies to estimate the March 9th shock effect.-->
+
+Economic indicators forecasted our recession before the coronavirus pandemic began.
+The current recession followed an inversion of the yield curve that first happend back in March 22, 2019 [Source](https://apnews.com/a0af7de008924d789c6d2bddc1ee9168).
+An inversion of the yield curve is an event that signals that recessions are more likely ([St.
 Louis Fed](https://files.stlouisfed.org/files/htdocs/publications/economic-synopses/2018/11/30/does-the-yield-curve-really-forecast-recession.pdf), [San Francisco Fed](https://www.frbsf.org/economic-research/files/el2018-07.pdf?source=post_page---------------------------), [Damir Tonik](https://onlinelibrary.wiley.com/doi/pdf/10.1002/jcaf.22400?casa_token=ONwrV5ApkhkAAAAA:Qgh2e8QFSEniGLvPbzST_p1o2PregqnrCoNQrwjSK47iNcySWPHZQOf1_F342Vzog-ayXtpPukAnuMc)).
-We investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
+
+In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
 We also consider previous OPEC oil supply shocks.
-
-We will borrow from the literature on oil price forecasting to establish appropriate time horizons, forecasting and nowcasting models, and donor pools of disparate time series.
+We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models.
 Recessions that occured before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 ([Source](https://www.federalreserve.gov/PUBS/ifdp/2011/1022/ifdp1022.htm)).
@@
 This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months ([Source](https://www.federalreserve.gov/PUBS/ifdp/2011/1022/ifdp1022.htm)).
-We will consider 30 pre-shock trading days and we will nowcast the immediate shock effect and the shock effect over a future five trading day window.
-All estimates will be adjusted for inflation: https://www.usinflationcalculator.com
+We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window.
+All estimates will be adjusted for inflation using the inflation calculator at https://www.usinflationcalculator.com.
 
@@
 We will use these findings on oil prices as guidelines for constructing time horizons for our AR models, our time horizons will be 30 trading days centered at the reported time of the shock.
+-->
+
+Our donor pool will consist of Conoco Phillips shock effects observed on September 11th, 2001, September 8th, 2008, and November 27, 2014.
+The first two shock effects were observed during recessions that were predicated by an inversion of the yiled curve, and the third was an OPEC induced supply side shock effect.
+Some other notable shock effects were not included in this analysis because the conditions preceding them are not simialar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects ([1987 Source](https://www.nber.org/chapters/c10958.pdf), [2011 Source](https://www.latimes.com/world/la-xpm-2011-aug-06-la-fi-us-debt-downgrade-20110806-story.html), [2015 Source](https://www.nytimes.com/2015/08/25/business/dealbook/daily-stock-market-activity.html)).
+<!-- 
+October 19, 1987: https://www.nber.org/chapters/c10958.pdf
+@article{shiller1988portfolio,
+  title={Portfolio insurance and other investor fashions as factors in the 1987 stock market crash},
+  author={Shiller, Robert J},
+  journal={NBER Macroeconomics Annual},
+  volume={3},
+  pages={287--297},
+  year={1988},
+  publisher={MIT Press}
+}
+
+August 24th, 2015: https://www.nytimes.com/2015/08/25/business/dealbook/daily-stock-market-activity.html
+
+August 8th, 2011, US Credit rating downgraded: https://www.latimes.com/world/la-xpm-2011-aug-06-la-fi-us-debt-downgrade-20110806-story.html
 -->
@@
 
-```{r, message = FALSE}
+```{r, message = FALSE, warning = FALSE}
 library(data.table)
@@
 
-```{r loadCOP, message = "FALSE"}
+```{r loadCOP, message = FALSE, warning = FALSE}
 ## Conoco Phillips
@@
 
-## Exxon Mobile
-getSymbols('XOM', from = "1970-01-01")
-XOM <- as.data.frame(XOM)
-XOM <- XOM %>% mutate(Date = rownames(XOM))
-
-## Chevron
-getSymbols('CVX', from = "1970-01-01")
-CVX <- as.data.frame(CVX)
-CVX <- CVX %>% mutate(Date = rownames(CVX))
-
 ## S&P 500
@@
 GSPC <- GSPC %>% mutate(Date = rownames(GSPC))
+
+## Exxon Mobile
+#getSymbols('XOM', from = "1970-01-01")
+#XOM <- as.data.frame(XOM)
+#XOM <- XOM %>% mutate(Date = rownames(XOM))
+
+## Chevron
+#getSymbols('CVX', from = "1970-01-01")
+#CVX <- as.data.frame(CVX)
+#CVX <- CVX %>% mutate(Date = rownames(CVX))
 ```
@@
 start <- which(COP_close$Date == "2001-09-10")
-start_day <- as.numeric(1:nrow(COP_close) > start)
+## change to equality
+start_day <- as.numeric(1:nrow(COP_close) == start + 1)
 COP_close <- COP_close %>% mutate(start_day = start_day)
 COP_close_small <- COP_close[(start-29):(start+1), ]
-dim(COP_close_small)
 m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                  data = COP_close_small)
-summary(m_COP_9_11)
 alpha_9_11_1 <- summary(m_COP_9_11)$coef[3,1:2]
@@
 m_COP_9_11 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-summary(m_COP_9_11)
 alpha_9_11_1_no <- summary(m_COP_9_11)$coef[3,1:2]
@@
                  data = COP_close_small)
-summary(m_COP_9_11)
 alpha_9_11_5 <- summary(m_COP_9_11)$coef[3,1:2]
-alpha_9_11_5 #-2.19 (0.46) in 2020 dollars
+             #constant: -2.19 (0.46) in 2020 dollars
+alpha_9_11_5 #-1.17 (0.54) in 2020 dollars
 ```
@@
 m_COP_9_11 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-summary(m_COP_9_11)
 alpha_9_11_5_no <- summary(m_COP_9_11)$coef[3,1:2]
-alpha_9_11_5_no #-1.55 (0.28) in 2020 dollars
+                #constant: -1.55 (0.28) in 2020 dollars
+alpha_9_11_5_no #-1.59 (0.52) in 2020 dollars
 ```
@@
 start <- which(COP_close$Date == "2008-09-08")
-start_day <- as.numeric(1:nrow(COP_close) >= start)
+## change to equality
+start_day <- as.numeric(1:nrow(COP_close) == start)
 COP_close <- COP_close %>% mutate(start_day = start_day)
 COP_close_small <- COP_close[(start-30):(start), ]
-dim(COP_close_small)
 m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                     data = COP_close_small)
-summary(m_COP_9_08_08)
 alpha_9_08_08_1 <- summary(m_COP_9_08_08)$coef[3,1:2]
@@
 m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-summary(m_COP_9_08_08)
 alpha_9_08_08_1_no <- summary(m_COP_9_08_08)$coef[3,1:2]
@@
                     data = COP_close_small)
-summary(m_COP_9_08_08)
 alpha_9_08_08_5 <- summary(m_COP_9_08_08)$coef[3,1:2]
-alpha_9_08_08_5 #-4.20 (1.61) in 2020 dollars
+                #constant: -4.20 (1.61) in 2020 dollars
+alpha_9_08_08_5 # -6.28 (2.00) in 2020 dollars
 ```
@@
 m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-summary(m_COP_9_08_08)
 alpha_9_08_08_5_no <- summary(m_COP_9_08_08)$coef[3,1:2]
-alpha_9_08_08_5_no #-4.14 (1.58) in 2020 dollars
+                   #constant: -4.14 (1.58) in 2020 dollars
+alpha_9_08_08_5_no #-6.26 (1.94) 
 ```
@@
 start <- which(COP_close$Date == "2014-11-26")
-start_day <- as.numeric(1:nrow(COP_close) >= start)
+start_day <- as.numeric(1:nrow(COP_close) == start)
+## change to equality
 COP_close <- COP_close %>% mutate(start_day = start_day)
 COP_close_small <- COP_close[(start-30):(start), ]
-dim(COP_close_small)
 m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                     data = COP_close_small)
-summary(m_COP_11_27_14)
 alpha_11_27_14_1 <- summary(m_COP_11_27_14)$coef[3,1:2]
@@
 m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-summary(m_COP_11_27_14)
 alpha_11_27_14_1_no <- summary(m_COP_11_27_14)$coef[3,1:2]
@@
 COP_close_small <- COP_close[(start-30):(start+4), ]
-dim(COP_close_small)
 m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                     data = COP_close_small)
-summary(m_COP_11_27_14)
 alpha_11_27_14_5 <- summary(m_COP_11_27_14)$coef[3,1:2]
-alpha_11_27_14_5 #-2.69 (0.94) in 2020 dollars
+                 #constant: -2.69 (0.94) in 2020 dollars
+alpha_11_27_14_5 #-5.43 (1.01) in 2020 dollars
 ```
@@
 m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-summary(m_COP_11_27_14)
 alpha_11_27_14_5_no <- summary(m_COP_11_27_14)$coef[3,1:2]
-alpha_11_27_14_5_no #-1.23 (0.65) in 2020 dollars
-```
-
-```{r}
-mat <- rbind(
-c(-1.97, 0.41, -1.56, 0.33, -2.19, 0.46, -1.55, 0.28),
-c(-6.95, 1.98, -6.94, 1.94, -4.20, 1.61, -4.14, 1.58),
-c(-5.68, 1.06, -5.26, 0.97, -2.69, 0.94, -1.23, 0.65)
-)
-colnames(mat) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no",
-                   "a_5","sd_a_5","a_5_no","sd_a_5_no")
-rownames(mat) <- c("y2001", "y2008", "y2014")
+                    #constant:-1.23 (0.65) in 2020 dollars
+alpha_11_27_14_5_no #-5.26 (0.99) in 2020 dollars
 ```
@@
 start <- which(COP_close$Date == "2020-03-06")
-start_day <- as.numeric(1:nrow(COP_close) >= start)
+## change to equality
+start_day <- as.numeric(1:nrow(COP_close) == start)
 COP_close <- COP_close %>% mutate(start_day = start_day)
 COP_close_small <- COP_close[(start-30):(start), ]
-dim(COP_close_small)
+```
+
+Here is the 1 day nowcast with S&P 500:
+
+```{r}
 m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                     data = COP_close_small)
-summary(m_COP_03_09_20)
 alpha_03_09_20_1 <- summary(m_COP_03_09_20)$coef[3,1:2]
-alpha_03_09_20_1 #-10.51414
+alpha_03_09_20_1 #-10.51414 (1.62901)
 ```
 
-Here is the 5 day shock effect
+Here is the 1 day nowcast without S&P 500:
+
+```{r}
+m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
+alpha_03_09_20_1_no <- summary(m_COP_03_09_20)$coef[3,1:2]
+alpha_03_09_20_1_no #-10.533756 (1.617991)
+```
+
+Here is the 5 day shock effect with S&P 500:
 
@@
 COP_close_small <- COP_close[(start-30):(start+4), ]
-dim(COP_close_small)
 m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                     data = COP_close_small)
-summary(m_COP_03_09_20)
 alpha_03_09_20_5 <- summary(m_COP_03_09_20)$coef[3,1:2]
-alpha_03_09_20_5 #-5.333522
+                 #constant: -5.333522 (2.077089)
+alpha_03_09_20_5 #-10.714979 (1.775454)
 ```
 
-```{r, eval = FALSE, echo = FALSE}
-## tests
-adf.test(dat_COP[50:200, ]$Close)
-adf.test(dat_COP[100:210, ]$Close)
-adf.test(dat_COP[100:207, ]$mkt_Close)
-adf.test(dat_COP[211:252, ]$Close)
-adf.test(dat_COP[211:252, ]$mkt_Close)
+Here is the 5 day shock effect without S&P 500:
 
-Box.test(dat_COP[100:210, ]$Close, lag=20, type="Ljung-Box")
-kpss.test(dat_COP[100:210, ]$Close, null="Trend")
-acf(dat_COP[100:210, ]$Close)
+```{r}
+m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
+alpha_03_09_20_5_no <- summary(m_COP_03_09_20)$coef[3,1:2]
+                    #constant: -5.314242 (2.031455)
+alpha_03_09_20_5_no #-10.668604 (1.754461)
+```
 
-## one level of differencing may be preferred
-fit <- arima(x = dat_COP[181:241, ]$Y, order = c(1, 0, 0), 
-      xreg = dat_COP[181:241, ]$mkt_Close)
-fit
+## Shock effect estimators
 
-## the post-shock model
-fit2 <- arima(x = dat_COP[211:252, ]$Y, order = c(1, 0, 0), 
-      xreg = dat_COP[211:252, ]$mkt_Close)
-fit2
+We first obtain the inflation-adjusted shock effect estimators from all of the above analyses.
+
+```{r}
+a_estimates <- rbind(
+c(-1.97, 0.41, -1.56, 0.33, -1.17, 0.54, -1.59, 0.52),
+c(-6.95, 1.98, -6.94, 1.94, -6.28, 2.00, -6.26, 1.94),
+c(-5.68, 1.06, -5.26, 0.97, -5.43, 1.01, -5.26, 0.99)
+)
+colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no",
+                   "a_5","sd_a_5","a_5_no","sd_a_5_no")
+rownames(a_estimates) <- c("y2001", "y2008", "y2014")
 ```
+
+We now compute four shock effect estimators.
+We compute the adjustment estimator that averages the estimated shock effects and the inverse variance weighted adjustment estimator, these two estimators are computed with and without the September 11th, 2001 shock effect.
+We consider analyses without the September 11th, 2001 shock effect because the stock market was closed for the week following the terrorist attack, so immediate post shock data was not actually observed.
+
+```{r}
+a_adj <- colMeans(a_estimates[,1:4 * 2 -1 ])
+a_adj_no911 <- colMeans(a_estimates[-1,1:4 * 2 -1 ])
+weights <- rbind(
+(1 / a_estimates[,1:4 * 2])[1, ] / colSums(1 / a_estimates[,1:4 * 2]),
+(1 / a_estimates[,1:4 * 2])[2, ] / colSums(1 / a_estimates[,1:4 * 2]),
+(1 / a_estimates[,1:4 * 2])[3, ] / colSums(1 / a_estimates[,1:4 * 2])
+)
+a_adj_IVW <- colSums(weights * a_estimates[,1:4 * 2 -1 ])
+weights_no911 <- rbind(
+(1 / a_estimates[-1,1:4 * 2])[1, ] / colSums(1 / a_estimates[-1,1:4 * 2]),
+(1 / a_estimates[-1,1:4 * 2])[2, ] / colSums(1 / a_estimates[-1,1:4 * 2])
+)
+a_adj_IVW_no911 <- colSums(weights_no911 * a_estimates[-1,1:4 * 2 -1 ])
+```
+
+Here are the estimators:
+
+```{r}
+shock_effects <- rbind(a_adj, a_adj_no911, 
+                       a_adj_IVW, a_adj_IVW_no911)
+shock_effects
+```
+
+Interesting to note that the March 9th, 2020 shock effect is closely approximated by the additive effect of the recession diven shock on September 8th, 2008 and the OPEC supply driven shock on November 27, 2014.
+
+```{r}
+additive <- colSums(a_estimates[-1,1:4 * 2 -1])
+additive
+```
+
+## Post-shock forecasts
+
+```{r}
+COP_close <- COP_close %>% select(-"start_day")
+start <- which(COP_close$Date == "2020-03-06")
+#start_day <- as.numeric(1:nrow(COP_close) >= start)
+#COP_close <- COP_close %>% mutate(start_day = start_day)
+COP_close_small <- COP_close[(start-30):(start), ]
+```
+
+Here is the 1 day nowcast with S&P 500:
+
+```{r}
+m_COP_03_06_20 <- lm(Y ~ COP_Close + GSPC_Close, 
+                     data = COP_close_small[-nrow(COP_close_small), ])
+preds <- predict(m_COP_03_06_20)
+Yhat_nothing_1 <- 0.933928 * 46.96604 -7.462690 + 0.003267 * 3023.94
+Yhat_adj_1 <- Yhat_nothing_1 + shock_effects[, 1]
+Yhat_adj_additive_1 <- Yhat_nothing_1 + additive[1]
+
+## doing nothing completely misses the mark
+Yhat_nothing_1 - COP_close_small$Y[nrow(COP_close_small)]
+
+## adjustment gets closer
+Yhat_adj_1 - COP_close_small$Y[nrow(COP_close_small)]
+
+## additive effect does well
+Yhat_adj_additive_1 - COP_close_small$Y[nrow(COP_close_small)]
+```
+
+```{r}
+COP_close_small$id <- 1:nrow(COP_close_small)
+mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
+             c(Yhat_adj_1, Yhat_adj_additive_1))
+colnames(mat) <- c("id", "Yhat_adj")
+dat <- as.data.frame(mat)
+ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
+  labs(title = "Conoco Phillips forecasting (with S&P 500)", 
+       x = "Day", y = "Close price (in USD)") +
+  geom_point() + 
+  geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:6) + 
+  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values, Yhat_nothing_1)), 
+            col = "blue") +
+  theme_minimal()
+```
+
+Here is the 1 day nowcast without S&P 500:
+
+```{r}
+m_COP_03_06_20 <- lm(Y ~ COP_Close, 
+                     data = COP_close_small[-nrow(COP_close_small), ])
+summary(m_COP_03_06_20)
+preds <- predict(m_COP_03_06_20)
+Yhat_nothing_1_no <- -1.25682 + 1.01170 * 47.00149 
+Yhat_adj_1_no <- Yhat_nothing_1_no + shock_effects[, 2]
+Yhat_adj_additive_1_no <- Yhat_nothing_1_no + additive[2]
+
+## doing nothing misses the mark
+Yhat_nothing_1_no - COP_close_small$Y[nrow(COP_close_small)]
+
+## adjustment gets closer
+Yhat_adj_1_no - COP_close_small$Y[nrow(COP_close_small)]
+
+## additive effect does well
+Yhat_adj_additive_1_no - COP_close_small$Y[nrow(COP_close_small)]
+```
+
+```{r}
+COP_close_small$id <- 1:nrow(COP_close_small)
+mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
+             c(Yhat_adj_1,  Yhat_adj_additive_1_no))
+colnames(mat) <- c("id", "Yhat_adj")
+dat <- as.data.frame(mat)
+ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
+  labs(title = "Conoco Phillips forecasting (without S&P 500)", 
+       x = "Day", y = "Close price (in USD)") +
+  geom_point() + 
+  geom_point(data = dat, aes(x = id, y = Yhat_adj), 
+                             col = 2, pch = 2:6) + 
+  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values,
+                              Yhat_nothing_1_no)), 
+            col = "blue") +
+  theme_minimal()
+```

### 2020-05-21 CP_2020.Rmd
updated plots

@@
   geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:6) + 
+  geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing_1), 
+             aes(x = x, y = y), col = "blue", cex = 1.5) + 
   geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values, Yhat_nothing_1)), 
             col = "blue") + 
+    annotate("text", x=1, y=seq(from = 47, to = 39,length.out=6), 
+             label=c("no adjustment","mean adjustment",
+                     "mean adjustment (no 9/11)","IVW adjustment",
+                     "IVW adjustment (no 9/11)", "aggregate adjustment"), 
+             hjust=0) + 
+    annotate("point", x = 0, y=seq(from = 47, to = 39,length.out=6), 
+             pch = c(16,2:6),
+             color = c("blue","red","red","red","red","red")) +
   theme_minimal()
@@
                              col = 2, pch = 2:6) + 
+  geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing_1_no), 
+             aes(x = x, y = y), col = "blue", cex = 1.5) + 
   geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values,
@@
             col = "blue") +
+      annotate("text", x=1, y=seq(from = 47, to = 39,length.out=6), 
+             label=c("no adjustment","mean adjustment",
+                     "mean adjustment (no 9/11)","IVW adjustment",
+                     "IVW adjustment (no 9/11)", "aggregate adjustment"), 
+             hjust=0) + 
+    annotate("point", x = 0, y=seq(from = 47, to = 39,length.out=6), 
+             pch = c(16,2:6),
+             color = c("blue","red","red","red","red","red")) +
   theme_minimal()

### 2020-05-22 manuscript/manuscript.tex
added comments to draft of manuscript

@@
 \section{Introduction}
-The technique of combining forecasts to lower forecast error has a rich 
-history \citep{bates1969combination, mundlak1978pooling, 
-  timmermann2006forecast, granger2014forecasting}.  
-The Introduction of \citet{timmermann2006forecast} provided several reasons 
-for combining forecasts.  In particular, combining forecasts may be 
-beneficial when: 
-1) the information set underlying individual forecasts is often unobserved to 
-the forecast user; 2) different individual forecasts may be very differently 
-affected by non-stationarities and model misspecifications; 3) different 
-individual forecasts may be motivated by different loss functions 
-\citep[and references therein]{timmermann2006forecast}.
-The setting for the forecast combination problem is that there are 
-competing forecasts for a single time series.  In this setting, one may 
-desire combining forecasts as a method for lowering overall forecast error.
 
-Forecast combination is a general term for a plethora of  methods for combining forecasts, e.g., (1) model averaging \citep{newbold2002forecast, timmermann2006forecast, hansen2008least}, (2) model selection \citep{lee2015model,greenaway2020multistep}, (3) time-series pooling \citep{mundlak1978pooling,zellner1991forecasting, lee2020estimation,plessen2020integrated}.
-Model averaging typically selects weights for models based on minimizing various loss functions whereas model selection chooses the model through minimization of those loss functions, see for example, \citet{fosten2019panel}.
-Time-series pooling is a broad topic for borrowing information from multiple time series for prediction improvement and is the focus of this paper.
-Before discussion of time-series pooling literature, we will first introduce the problem statement of our study.
+In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
+It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.
+However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study.
+One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error.
+%When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.
 
-In this article we provide forecasting adjustment techniques with the goal 
-of lowering overall forecast error when the time series under study has 
-undergone a structural shock.
-%In this article we propose a new setting for the forecast combination 
-%problem.  We will suppose that a time series of interest has recently 
-%undergone a structural shock that is not similar to anything observed in its 
-%past, and we desire reliable post-shock forecasts in this setting.  
-It is unlikely that any forecast that previously gave successful predictions 
-for the time series of interest will be able to accommodate the 
-structural shock.  Therefore the traditional forecast combination framework 
-may not be of any help. However, all is not lost in this setting. It may be 
-the case that there exists disparate time series that have previously 
-undergone similar structural shocks.  When this is so, one may be able to 
-aggregate the post-shock information from these disparate time series to 
-aid the post-shock forecast for the time series under investigation.
+Improving forecasts through forecast combination has a rich history \citep{bates1969combination, mundlak1978pooling, timmermann2006forecast, granger2014forecasting}.  
+%\citet{timmermann2006forecast} provided several reasons for combining forecasts.
+In particular, combining forecasts may be beneficial when: 1) the information set underlying individual forecasts is often unobserved to the forecast user; 2) different individual forecasts may be very differently affected by non-stationarity and model misspecifications; 3) different individual forecasts may be motivated by different loss functions \citep[and references therein]{timmermann2006forecast}.
+The classical setting for the forecast combination problem is when there are competing forecasts for a single time series.
+%In this setting, one may desire combining forecasts as a method for lowering overall forecast error.
+%\textbf{Integrate this paragraph into the next paragraph.}
+\textbf{The following list of methods needs to fall in the forecast combination literature, not the time series pooling literature}.
+In this setting there are a plethora of methods for combining forecasts, e.g., (1) model averaging \citep{newbold2002forecast, timmermann2006forecast, hansen2008least}, (2) model selection \citep{lee2015model, greenaway2020multistep}, (3) time-series pooling \citep{mundlak1978pooling, zellner1991forecasting, lee2020estimation, plessen2020integrated}.
+Model averaging typically selects weights for models based on minimizing various loss functions whereas model selection chooses the model through minimization of those loss functions, see for example, \citet{fosten2019panel} \textbf{I do not think that this reference belongs here}.
+Classical forecast combination may fail when forecasting in the presence of structural shocks.
 
-We develop and compare aggregation techniques in this post-shock setting and 
-investigate settings for when they do and do not decrease mean squared 
-prediction error. We assume a simple auto regressive data generating process 
-with a general random effects structure. The main idea is to first average 
-the estimated shock effects from the disparate time series and then add 
-the averaged estimated shock effect to the present forecast. When these 
-time series are independent and the mean of shock effect distribution is 
-large relative to its variance then this technique will reduce mean squared 
-prediction error under the assumed model. Note that this methodology is not 
-motivated with the goal of unbiased, asymptotically unbiased, or consistent 
-estimation for the shock-effect of the time series under study. We consider 
-three aggregation techniques: simple averaging, inverse-variance weighted 
-averaging, and similarity weighting. The latter technique is similar to 
-the weighting in synthetic control methodology \citep{abadie2010synthetic}.
+%Time-series pooling is a broad topic for borrowing information from multiple time series for prediction improvement and is the focus of this paper.
+\textbf{Need to mention that these methods may fail or be irrelevant in the presence of shock effects.}
 
+In our post-shock setting we combine estimated quantities from different time series with the aim of lowering forecast error for a single time series under study.
+Our techniques are similar to those in time-series pooling and data integration.
 The literature of time-series pooling is mainly related to pooling cross-sectional panel data \citep{mundlak1978pooling, zellner1991forecasting, fosten2019panel}.
@@
 \citet{baltagi2008forecasting} showed that homogeneity approach often outperform  heterogeneity one in mean squared forecast error; while heterogeneity approach is more general to accommodate differences among units.
+\textbf{How does this relevant to what we are doing?}
 
-Modern researches in ``combining'' forecasts from disparate time series have taken perspectives from distinct fields.
-\citet{lee2020estimation} constructed a Bayesian hierarchical model  to estimate posterior parameters for Richards model to improve predictive precision of COVID-19 infection trajectories for different countries.
-Though a Bayesian hierarchical approach can be a solution for our problem by setting up prior for shock-effects, the analysis is sensitive to the prior and the hierarchical model setup, and conditions for predictive improvement are generally hard to know.
-\citet{plessen2020integrated} employs a data-mining approach to take COVID-19 data from different countries as input to predict \emph{global} net daily infections  and deaths of COVID-19 from clustering.
-However, the fit is poor due to tremendous volatility of COVID-19 data, and perhaps a lack of random structure in his model.
-\emph{\textcolor{red}{More to be added ...}}
+Data integration for forecasting is a broad area of research including ideas from many areas.
+\citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model
+to improve predictive precision of COVID-19 infection trajectories for different countries.
+A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
+%, and conditions for predictive improvement are generally hard to know. 
+\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering.
+However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
+\textbf{Mention synthetic intervention paper here, stress the importance of carefully constructing the donor pool.}  \emph{\textcolor{red}{More to be added ...}}
+
+%Therefore the traditional forecast combination framework may not be of any help.  
+%The Bayesian hierarchical approach of \citet{lee2020estimation} may be too sensitive to prior and the hierarchical parametric model setup.
+
+\textbf{Need more of a transition to what we do here and why it is good.}
+We develop and compare aggregation techniques in this post-shock setting and investigate settings for when they do and do not decrease mean squared prediction error.
+We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure.
+The main idea is to first average the estimated shock effects from the disparate time series and then add the averaged estimated shock effect to the present forecast.
+When these time series are independent and the mean of shock effect distribution is large relative to its variance then this technique will reduce mean squared prediction error under the assumed model.
+Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock-effect of the time series under study.
+We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting.
+The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
+
+\vspace*{0.25cm}\textbf{Need to discuss our example and our simulation results.}
 
@@
 $$
-in our analyses. In this article, we consider a similar dynamic panel data 
-model with autoregressive structure to that in \citet{blundell1998initial}. 
+in our analyses. In this article, we consider a dynamic panel data 
+model with autoregressive structure similar to that in \citet{blundell1998initial}. 
 %without past time period covariate 
@@
 The dots represent least square estimate $\hat{\alpha}_i$ from disparate time series.
-Two model differs by an adjustment $\hat{\alpha}=\frac{1}{n}\sum_{i=1}^n \hat{\alpha}_i$.}\label{figure1}
+Two model differs by an adjustment $\hat{\alpha}=\frac{1}{n}\sum_{i=1}^n \hat{\alpha}_i$.
+\textbf{The picture needs to be made more clear.
+Remove $\hat{\alpha}_i$ and state what those points are in the caption.
+Label the true (unknown to us) shock effect $\alpha_1$.}}\label{figure1}
   \end{center}  
@@
 The first forecast ignores the presence of $\alpha_1$ while the second forecast 
-incorporates an estimate of $\alpha_1$ that is obtained from the other individual 
-forecasts under study. 
+incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study. 
 %Under $\mc{M}_1$ (Section \ref{modelsetup}), $\E{\alpha_1} = \mu_{\alpha}$.
@@
 In discussion of risk, it is useful to derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.
-The expression for the expectations are attached as follow\footnote{The formal justification can be found in Section \ref{exp}.}.
+The expression for the expectations are as follow,
 
@@
       \quad \text{ and } \quad 
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*} + \gamma' \mbf{x}_{1, T_1^*-1}
+       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*} + \gamma' \mbf{x}_{1, T_1^*-1}.
     \end{align*}
@@
       \quad \text{ and } \quad 
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*} + \mu_{\gamma}' \mbf{x}_{1, T_1^*-1}
+       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*} + \mu_{\gamma}' \mbf{x}_{1, T_1^*-1}.
     \end{align*}
   \end{enumerate}
-
+Formal justification for these results can be found in Appendix.
 Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$.
@@
 These conditions will be discussed in Section \ref{conditions} and Section \ref{comparisons}.
-Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below\footnote{The formal justification can be found in Section \ref{var}}.
+Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below
 
@@
   &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
-  + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i}
+  + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i}.
 \end{align*}
 \end{enumerate}
+Formal justification for these results can be found in Appendix.
 Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$
@@
 To make use of those properties in practice, estimation is required.
-Section \ref{varbootstrap} will introduce a general procedure of \emph{parametric bootstrap} under the context of the problem to attain this purpose.
+Section \ref{varbootstrap} will introduce a general procedure of parametric bootstrap under the context of the problem to attain this purpose.
 
@@
 Topics of  evaluation of these inequalities in practice can be found in Section \ref{varbootstrap}. 
-As conditions of risk-reduction for individual estimators are obtained, a natural question arises --- which one is better?
-It will be discussed in Section \ref{comparisons}.
+We will discuss comparisons of adjustment estimators in the the next Section.
+%As conditions of risk-reduction for individual estimators are obtained, a natural question arises --- which one is better? It will be discussed in Section \ref{comparisons}.
 
@@
 
- What insights can we gain from this inequality? We can analyze this inequality from two perspectives. 
+%What insights can we gain from this inequality? 
+We analyze this inequality from two perspectives. 
  \begin{enumerate}
@@
  These are some analytical results for comparison studies among estimators of $\alpha_1$.
-Next, we will detail a framework for estimation of risk-reduction  quantities using non-parametric bootstrap such that the above inequalities can be  analyzed numerically in practice.
+Next, we will detail a framework for estimation of risk-reduction  quantities using a parametric bootstrap routine.
+Therefore, the above inequalities can be analyzed numerically in practice.
 
 \subsection{Parametric bootstrap for risk-reduction evaluation problems}
+\label{varbootstrap}
+
+\textbf{I am not sure if all of this is necessary. This is a nice summary of the literature but I think that we only need the results that motivate our bootstrap procedure.}
 
 In this section, we present a parametric bootstrap procedure for our AR(1) model (see Section \ref{modelsetup}) in approximating the distribution of our shock-effect estimators.
-In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives.
+%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives.
 In the second step, we detail the procedure of boostrapping AR(1).
-
-\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}.
+%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}.
 However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model.
-
-In the usual setup of AR($p$) model, the unobserved errors are assumed to be \emph{identically} and \emph{independently distributed}.
-In other words, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}.
-As in the standard bootstrap, the asymptotic accuracy for OLS parameter estimation is guaranteed under the order of $O(T^{-1/2})$ almost surely, where $T$ is the length of the time series \citep{berkowitz2000recent}.
+In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed.
+In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}.
+The asymptotic accuracy for OLS parameter estimation is guaranteed under the order of $O(T^{-1/2})$ almost surely, where $T$ is the length of the time series \citep{berkowitz2000recent}.
 \citet{bose1988edgeworth} showed that it can be further improved to $o(T^{-1/2})$ almost surely under some regularity conditions.
@@
 
-\citet{politis1994stationary} invented the stationary bootstrap method for \emph{strictly stationary} and \emph{weakly dependent} time series.
+\citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series.
 However, the asymptotic accuracy of this procedure to OLS estimation is not known.
-Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$, the parameter of the geometric distribution; this issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.
+Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$, the parameter of the geometric distribution (\textbf{what does this mean, what is the geometric distribution in this context?}).
+This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.
 More work related to bootstrapping time series  can be referred to \citet{berkowitz2000recent}.
-It is up to the user in selecting which procedure to choose but under \emph{different} assumptions on the time-series.
+It is up to the user in selecting which procedure to choose but under different assumptions on the time-series.
+
+\textbf{We do not need to rewrite bootstrap algorithms that exist in the literature.
+We only need to write our algorithm.
+Emphasis needs to be placed on $T_i^*$being known, the pre and post $T_i^*$ sampling needs to be made explicit.}
 
@@
 Therefore, we can judge whether to use a shock-effect estimator, and choose between  shock-effect estimators by this method.
+
+\textbf{We should include a brief simulation which shows that our bootstrap procedure works.}
 
@@
  \textbf{Proof for statement (ii):} By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\mu_{\alpha}$ holds for $\mc{M}_{1}$.
-Then, similar proof of statement (i) will proves the Proposition.
+The remainder of the proof follows a similar argument to the proof of statement (i).
 \end{proof-of-proposition}
@@
   By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ holds for $\mc{M}_{21}$ and $\mc{M}_{22}$.
-Then, similar proof of Proposition \ref{propriskadj} will proves the Proposition.
+The remainder of the proof follows a similar argument to the proof of Proposition \ref{propriskadj} (\textbf{Fix this problematic reference}).
 \end{proof-of-proposition}

### 2020-05-28 manuscript/comp.tex
edit of manuscript and addition of simulation codes

@@
-% Created by tikzDevice version 0.12.3 on 2020-05-18 21:52:26
+% Created by tikzDevice version 0.12.3 on 2020-05-27 15:30:26
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 66.75,172.95) --
-	( 68.63,152.47) --
-	( 70.51,145.69) --
-	( 72.39,140.03) --
-	( 74.28,104.28) --
-	( 76.16,151.54) --
-	( 78.04,154.95) --
-	( 79.92,133.81) --
-	( 81.80,175.35) --
-	( 83.69,166.88) --
-	( 85.57,125.70) --
-	( 87.45,170.76) --
-	( 89.33,129.50) --
-	( 91.22,171.48) --
-	( 93.10,157.93) --
-	( 94.98,132.20) --
-	( 96.86,134.97) --
-	( 98.74,121.20) --
-	(100.63,132.31) --
-	(102.51,167.74) --
-	(104.39,139.43) --
-	(106.27,161.95) --
-	(108.15,118.76) --
-	(110.04,173.04) --
-	(111.92,101.84) --
-	(113.80,132.79) --
-	(115.68,156.33) --
-	(117.57,121.16) --
-	(119.45,173.74) --
-	(121.33,100.01) --
-	(123.21,122.32) --
-	(125.09,136.35) --
-	(126.98,148.45) --
-	(128.86, 99.38) --
-	(130.74,159.11) --
-	(132.62,177.96) --
-	(134.51,146.68) --
-	(136.39, 99.65) --
-	(138.27,141.14) --
-	(140.15,113.97) --
-	(142.03, 56.48) --
-	(143.92,137.78) --
-	(145.80,157.07) --
-	(147.68,135.25) --
-	(149.56,140.67) --
-	(151.45,155.40) --
-	(153.33,144.28) --
-	(155.21,109.64) --
-	(157.09,161.65) --
-	(158.97,120.57) --
-	(160.86,134.53) --
-	(162.74,187.79) --
-	(164.62,127.58) --
-	(166.50,140.39) --
-	(168.39,128.19) --
-	(170.27,170.09) --
-	(172.15,121.23) --
-	(174.03,147.74) --
-	(175.91,166.20) --
-	(177.80,152.19) --
-	(179.68, 95.16) --
-	(181.56,137.35) --
-	(183.44,180.08) --
-	(185.32,152.17) --
-	(187.21,170.34) --
-	(189.09,168.84) --
-	(190.97,130.81) --
-	(192.85, 95.27) --
-	(194.74,162.93) --
-	(196.62,138.78) --
-	(198.50,138.61) --
-	(200.38,173.02) --
-	(202.26,167.54) --
-	(204.15,162.63) --
-	(206.03,148.90) --
-	(207.91,177.00) --
-	(209.79,135.59) --
-	(211.68,142.01) --
-	(213.56,146.72) --
-	(215.44,147.34) --
-	(217.32,137.83) --
-	(219.20,161.38) --
-	(221.09,135.23) --
-	(222.97,113.76) --
-	(224.85,132.15) --
-	(226.73,152.10) --
-	(228.62,133.70) --
-	(230.50,142.92) --
-	(232.38,137.94) --
-	(234.26, 80.23) --
-	(236.14,128.05) --
-	(238.03,140.12) --
-	(239.91,113.33) --
-	(241.79,135.32) --
-	(243.67,145.57) --
-	(245.56,148.21) --
-	(247.44,181.13) --
-	(249.32,123.87) --
-	(251.20,167.03) --
-	(253.08,176.92) --
-	(254.97,146.67) --
-	(256.85,137.49) --
-	(258.73,148.71) --
-	(260.61,158.20) --
-	(262.49,144.01) --
-	(264.38,140.56) --
-	(266.26,134.50) --
-	(268.14,164.72) --
-	(270.02,113.97) --
-	(271.91,173.50) --
-	(273.79,131.97) --
-	(275.67,135.32) --
-	(277.55,143.59) --
-	(279.43,134.00) --
-	(281.32,182.28) --
-	(283.20,134.50) --
-	(285.08,136.30) --
-	(286.96,121.98) --
-	(288.85,170.76) --
-	(290.73,168.83) --
-	(292.61,130.32) --
-	(294.49,130.95) --
-	(296.37,167.83) --
-	(298.26,106.18) --
-	(300.14,158.89) --
-	(302.02,221.32) --
-	(303.90,262.43) --
-	(305.79,181.52) --
-	(307.67,221.00) --
-	(309.55,219.36) --
-	(311.43,223.97) --
-	(313.31,225.88) --
-	(315.20,172.43) --
-	(317.08,211.80) --
-	(318.96,229.45) --
-	(320.84,222.24) --
-	(322.73,252.46) --
-	(324.61,190.77) --
-	(326.49,224.11) --
-	(328.37,194.35) --
-	(330.25,184.33) --
-	(332.14,175.51) --
-	(334.02,208.94) --
-	(335.90,208.16) --
-	(337.78,210.48) --
-	(339.67,204.77) --
-	(341.55,200.42) --
-	(343.43,207.20) --
-	(345.31,194.28) --
-	(347.19,175.97) --
-	(349.08,221.82) --
-	(350.96,230.52) --
-	(352.84,206.54) --
-	(354.72,213.96) --
-	(356.60,241.92) --
-	(358.49,206.43) --
-	(360.37,254.17) --
-	(362.25,205.63) --
-	(364.13,199.30) --
-	(366.02,207.87) --
-	(367.90,210.32) --
-	(369.78,198.03) --
-	(371.66,248.03) --
-	(373.54,206.39) --
-	(375.43,246.52) --
-	(377.31,210.82) --
-	(379.19,232.38) --
-	(381.07,213.29) --
-	(382.96,237.01) --
-	(384.84,208.79) --
-	(386.72,192.52) --
-	(388.60,236.32) --
-	(390.48,175.56) --
-	(392.37,250.12) --
-	(394.25,185.69) --
-	(396.13,231.06) --
-	(398.01,191.78) --
-	(399.90,226.76) --
-	(401.78,199.54) --
-	(403.66,165.06) --
-	(405.54,255.85) --
-	(407.42,210.34) --
-	(409.31,199.91) --
-	(411.19,229.86) --
-	(413.07,203.76) --
-	(414.95,231.64) --
-	(416.84,230.77) --
-	(418.72,190.26) --
-	(420.60,203.84) --
-	(422.48,209.53) --
-	(424.36,220.43) --
-	(426.25,173.24) --
-	(428.13,209.84) --
-	(430.01,159.64) --
-	(431.89,251.30) --
-	(433.77,197.02) --
-	(435.66,216.20) --
-	(437.54,224.42) --
-	(439.42,193.29) --
-	(441.30,213.98) --
-	(443.19,172.72) --
-	(445.07,245.00) --
-	(446.95,192.05) --
-	(448.83,235.97) --
-	(450.71,204.00) --
-	(452.60,164.26) --
-	(454.48,238.03) --
-	(456.36,185.07) --
-	(458.24,227.07) --
-	(460.13,222.82) --
-	(462.01,212.73) --
-	(463.89,268.60) --
-	(465.77,192.34) --
-	(467.65,239.77) --
-	(469.54,202.33) --
-	(471.42,231.75) --
-	(473.30,220.58) --
-	(475.18,187.28) --
-	(477.07,206.99) --
-	(478.95,199.08) --
-	(480.83,226.56) --
-	(482.71,221.75) --
-	(484.59,227.59) --
-	(486.48,203.00) --
-	(488.36,227.21) --
-	(490.24,209.56) --
-	(492.12,221.87) --
-	(494.01,245.38) --
-	(495.89,236.19) --
-	(497.77,241.22) --
-	(499.65,231.39) --
-	(501.53,253.76) --
-	(503.42,191.19) --
-	(505.30,203.77) --
-	(507.18,247.46) --
-	(509.06,219.46) --
-	(510.94,214.21) --
-	(512.83,191.34) --
-	(514.71,248.79) --
-	(516.59,197.34) --
-	(518.47,220.12) --
-	(520.36,259.69) --
-	(522.24,240.39) --
-	(524.12,221.17) --
-	(526.00,214.51) --
-	(527.88,259.99) --
-	(529.77,220.91) --
-	(531.65,215.72) --
-	(533.53,233.07) --
-	(535.41,219.94);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,150.94) --
+	( 75.27,164.79) --
+	( 78.11,157.49) --
+	( 80.95,165.92) --
+	( 83.79,166.40) --
+	( 86.63,141.84) --
+	( 89.47,150.09) --
+	( 92.31,143.93) --
+	( 95.15,141.05) --
+	( 97.99,145.70) --
+	(100.83,139.65) --
+	(103.67,178.59) --
+	(106.51,163.76) --
+	(109.35,143.77) --
+	(112.19,137.72) --
+	(115.03,164.14) --
+	(117.87,143.58) --
+	(120.71,166.91) --
+	(123.55,163.52) --
+	(126.40,145.84) --
+	(129.24,155.56) --
+	(132.08,140.91) --
+	(134.92,146.00) --
+	(137.76,155.61) --
+	(140.60,151.70) --
+	(143.44,158.08) --
+	(146.28,157.50) --
+	(149.12,162.02) --
+	(151.96,166.12) --
+	(154.80,159.26) --
+	(157.64,149.45) --
+	(160.48,145.98) --
+	(163.32,156.42) --
+	(166.16,141.35) --
+	(169.00,146.25) --
+	(171.84,165.79) --
+	(174.68,133.16) --
+	(177.52,164.74) --
+	(180.36,158.63) --
+	(183.20,174.39) --
+	(186.04,136.64) --
+	(188.88,142.35) --
+	(191.72,165.33) --
+	(194.56,177.10) --
+	(197.41,169.75) --
+	(200.25,166.95) --
+	(203.09,116.51) --
+	(205.93,139.49) --
+	(208.77,140.86) --
+	(211.61,181.44) --
+	(214.45,157.88) --
+	(217.29,160.28) --
+	(220.13,161.32) --
+	(222.97,174.87) --
+	(225.81,148.01) --
+	(228.65,118.11) --
+	(231.49,167.94) --
+	(234.33,167.87) --
+	(237.17,178.18) --
+	(240.01,165.32) --
+	(242.85,151.88) --
+	(245.69,151.67) --
+	(248.53,151.92) --
+	(251.37,128.89) --
+	(254.21,159.78) --
+	(257.05,144.18) --
+	(259.89,155.47) --
+	(262.73,164.76) --
+	(265.57,152.05) --
+	(268.42,138.91) --
+	(271.26,143.64) --
+	(274.10,141.06) --
+	(276.94,166.61) --
+	(279.78,177.14) --
+	(282.62,143.52) --
+	(285.46,129.06) --
+	(288.30,134.98) --
+	(291.14,126.11) --
+	(293.98,179.60) --
+	(296.82,162.55) --
+	(299.66,178.83) --
+	(302.50,133.78) --
+	(305.34,124.87) --
+	(308.18,142.06) --
+	(311.02,157.78) --
+	(313.86,132.62) --
+	(316.70,148.93) --
+	(319.54,130.16) --
+	(322.38,152.67) --
+	(325.22,156.53) --
+	(328.06,145.81) --
+	(330.90,145.85) --
+	(333.74,164.04) --
+	(336.59,162.10) --
+	(339.43,137.37) --
+	(342.27,177.60) --
+	(345.11,138.08) --
+	(347.95,158.99) --
+	(350.79,145.39) --
+	(353.63,165.05) --
+	(356.47,136.95) --
+	(359.31,166.26) --
+	(362.15,151.18) --
+	(364.99,143.86) --
+	(367.83,154.91) --
+	(370.67,151.74) --
+	(373.51,154.30) --
+	(376.35,126.88) --
+	(379.19,135.58) --
+	(382.03,152.86) --
+	(384.87,171.42) --
+	(387.71,136.46) --
+	(390.55,130.68) --
+	(393.39,141.79) --
+	(396.23,146.31) --
+	(399.07,119.63) --
+	(401.91,132.99) --
+	(404.75,143.78) --
+	(407.60,169.91) --
+	(410.44,180.48) --
+	(413.28,132.66) --
+	(416.12,158.14) --
+	(418.96,163.74) --
+	(421.80,167.20) --
+	(424.64,169.82) --
+	(427.48,208.40);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.98, 48.00) -- (533.53, 48.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75, 48.00) -- (492.81, 48.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.98, 48.00) -- ( 62.98, 42.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75, 48.00) -- ( 66.75, 42.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.09, 48.00) -- (157.09, 42.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.77, 48.00) -- (208.77, 42.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.20, 48.00) -- (251.20, 42.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.79, 48.00) -- (350.79, 42.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.31, 48.00) -- (345.31, 42.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.81, 48.00) -- (492.81, 42.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.42, 48.00) -- (439.42, 42.00);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 66.75, 26.40) {0};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (533.53, 48.00) -- (533.53, 42.00);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (208.77, 26.40) {50};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.98, 26.40) {0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (350.79, 26.40) {100};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (157.09, 26.40) {50};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 26.40) {150};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (251.20, 26.40) {100};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 56.55) -- ( 48.00,265.51);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (345.31, 26.40) {150};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 56.55) -- ( 42.00, 56.55);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (439.42, 26.40) {200};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 86.40) -- ( 42.00, 86.40);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (533.53, 26.40) {250};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,116.25) -- ( 42.00,116.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 55.58) -- ( 48.00,270.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,146.10) -- ( 42.00,146.10);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 55.58) -- ( 42.00, 55.58);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,175.96) -- ( 42.00,175.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 98.61) -- ( 42.00, 98.61);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,205.81) -- ( 42.00,205.81);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,141.64) -- ( 42.00,141.64);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,235.66) -- ( 42.00,235.66);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,184.67) -- ( 42.00,184.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,265.51) -- ( 42.00,265.51);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,227.69) -- ( 42.00,227.69);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 56.55) {-6};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,270.72) -- ( 42.00,270.72);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 86.40) {-4};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 55.58) {$-400$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,116.25) {-2};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 98.61) {$-200$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,146.10) {0};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,141.64) {0};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,175.96) {2};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,184.67) {200};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,205.81) {4};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,227.69) {400};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,235.66) {6};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,270.72) {600};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,265.51) {8};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 66.75,142.83) --
-	( 68.63,140.13) --
-	( 70.51,141.93) --
-	( 72.39,141.91) --
-	( 74.28,142.43) --
-	( 76.16,146.39) --
-	( 78.04,141.61) --
-	( 79.92,141.14) --
-	( 81.80,143.78) --
-	( 83.69,140.06) --
-	( 85.57,141.28) --
-	( 87.45,144.25) --
-	( 89.33,140.02) --
-	( 91.22,143.17) --
-	( 93.10,140.45) --
-	( 94.98,141.62) --
-	( 96.86,143.92) --
-	( 98.74,143.18) --
-	(100.63,144.99) --
-	(102.51,143.92) --
-	(104.39,140.49) --
-	(106.27,143.03) --
-	(108.15,141.75) --
-	(110.04,144.93) --
-	(111.92,140.19) --
-	(113.80,146.77) --
-	(115.68,143.66) --
-	(117.57,141.45) --
-	(119.45,144.73) --
-	(121.33,140.27) --
-	(123.21,146.15) --
-	(125.09,144.70) --
-	(126.98,143.27) --
-	(128.86,141.92) --
-	(130.74,146.15) --
-	(132.62,140.59) --
-	(134.51,139.83) --
-	(136.39,141.78) --
-	(138.27,147.01) --
-	(140.15,142.91) --
-	(142.03,145.16) --
-	(143.92,150.29) --
-	(145.80,143.35) --
-	(147.68,141.31) --
-	(149.56,142.82) --
-	(151.45,142.93) --
-	(153.33,141.23) --
-	(155.21,142.28) --
-	(157.09,144.73) --
-	(158.97,141.28) --
-	(160.86,144.80) --
-	(162.74,143.76) --
-	(164.62,139.14) --
-	(166.50,144.55) --
-	(168.39,142.11) --
-	(170.27,143.40) --
-	(172.15,140.31) --
-	(174.03,144.97) --
-	(175.91,141.97) --
-	(177.80,140.53) --
-	(179.68,141.81) --
-	(181.56,146.17) --
-	(183.44,143.43) --
-	(185.32,139.06) --
-	(187.21,142.38) --
-	(189.09,140.37) --
-	(190.97,141.03) --
-	(192.85,143.88) --
-	(194.74,146.77) --
-	(196.62,140.46) --
-	(198.50,143.03) --
-	(200.38,141.89) --
-	(202.26,140.44) --
-	(204.15,139.71) --
-	(206.03,141.07) --
-	(207.91,142.19) --
-	(209.79,139.86) --
-	(211.68,142.89) --
-	(213.56,142.17) --
-	(215.44,142.86) --
-	(217.32,142.40) --
-	(219.20,143.71) --
-	(221.09,141.02) --
-	(222.97,142.74) --
-	(224.85,145.76) --
-	(226.73,143.65) --
-	(228.62,141.79) --
-	(230.50,143.50) --
-	(232.38,142.42) --
-	(234.26,142.91) --
-	(236.14,147.76) --
-	(238.03,143.33) --
-	(239.91,142.66) --
-	(241.79,145.02) --
-	(243.67,143.33) --
-	(245.56,142.23) --
-	(247.44,142.51) --
-	(249.32,139.83) --
-	(251.20,143.91) --
-	(253.08,140.91) --
-	(254.97,139.48) --
-	(256.85,142.03) --
-	(258.73,142.30) --
-	(260.61,142.42) --
-	(262.49,141.41) --
-	(264.38,142.28) --
-	(266.26,143.37) --
-	(268.14,143.80) --
-	(270.02,141.46) --
-	(271.91,145.00) --
-	(273.79,140.14) --
-	(275.67,144.39) --
-	(277.55,142.54) --
-	(279.43,143.15) --
-	(281.32,143.33) --
-	(283.20,139.76) --
-	(285.08,143.03) --
-	(286.96,142.39) --
-	(288.85,144.66) --
-	(290.73,140.34) --
-	(292.61,139.93) --
-	(294.49,143.71) --
-	(296.37,143.28) --
-	(298.26,140.41) --
-	(300.14,145.43) --
-	(302.02,140.85) --
-	(303.90,136.75) --
-	(305.79,132.94) --
-	(307.67,139.42) --
-	(309.55,135.87) --
-	(311.43,136.63) --
-	(313.31,135.78) --
-	(315.20,135.92) --
-	(317.08,140.12) --
-	(318.96,136.56) --
-	(320.84,134.76) --
-	(322.73,135.54) --
-	(324.61,133.98) --
-	(326.49,138.52) --
-	(328.37,135.72) --
-	(330.25,138.98) --
-	(332.14,139.33) --
-	(334.02,140.22) --
-	(335.90,136.88) --
-	(337.78,137.21) --
-	(339.67,136.66) --
-	(341.55,137.15) --
-	(343.43,138.26) --
-	(345.31,136.84) --
-	(347.19,138.24) --
-	(349.08,139.43) --
-	(350.96,136.01) --
-	(352.84,135.41) --
-	(354.72,136.89) --
-	(356.60,136.87) --
-	(358.49,134.00) --
-	(360.37,138.00) --
-	(362.25,133.77) --
-	(364.13,137.44) --
-	(366.02,136.97) --
-	(367.90,136.64) --
-	(369.78,136.51) --
-	(371.66,138.07) --
-	(373.54,134.02) --
-	(375.43,137.34) --
-	(377.31,134.24) --
-	(379.19,137.50) --
-	(381.07,134.80) --
-	(382.96,138.20) --
-	(384.84,133.93) --
-	(386.72,136.89) --
-	(388.60,138.15) --
-	(390.48,134.68) --
-	(392.37,139.28) --
-	(394.25,133.59) --
-	(396.13,139.33) --
-	(398.01,135.30) --
-	(399.90,137.96) --
-	(401.78,135.47) --
-	(403.66,137.90) --
-	(405.54,140.60) --
-	(407.42,133.45) --
-	(409.31,136.69) --
-	(411.19,137.22) --
-	(413.07,135.30) --
-	(414.95,137.11) --
-	(416.84,134.45) --
-	(418.72,135.26) --
-	(420.60,139.07) --
-	(422.48,137.43) --
-	(424.36,137.15) --
-	(426.25,136.50) --
-	(428.13,140.82) --
-	(430.01,138.00) --
-	(431.89,141.05) --
-	(433.77,133.05) --
-	(435.66,137.92) --
-	(437.54,136.77) --
-	(439.42,135.43) --
-	(441.30,139.49) --
-	(443.19,136.51) --
-	(445.07,140.20) --
-	(446.95,134.28) --
-	(448.83,139.11) --
-	(450.71,134.98) --
-	(452.60,137.08) --
-	(454.48,141.67) --
-	(456.36,134.46) --
-	(458.24,139.63) --
-	(460.13,134.69) --
-	(462.01,135.78) --
-	(463.89,137.05) --
-	(465.77,131.53) --
-	(467.65,138.29) --
-	(469.54,134.65) --
-	(471.42,137.65) --
-	(473.30,135.03) --
-	(475.18,136.76) --
-	(477.07,138.74) --
-	(478.95,137.36) --
-	(480.83,138.23) --
-	(482.71,135.82) --
-	(484.59,135.95) --
-	(486.48,135.89) --
-	(488.36,136.74) --
-	(490.24,135.40) --
-	(492.12,136.77) --
-	(494.01,135.94) --
-	(495.89,133.46) --
-	(497.77,134.48) --
-	(499.65,134.68) --
-	(501.53,135.56) --
-	(503.42,134.09) --
-	(505.30,139.32) --
-	(507.18,138.00) --
-	(509.06,133.98) --
-	(510.94,136.16) --
-	(512.83,136.35) --
-	(514.71,138.27) --
-	(516.59,133.84) --
-	(518.47,137.50) --
-	(520.36,136.90) --
-	(522.24,132.66) --
-	(524.12,134.57) --
-	(526.00,136.61) --
-	(527.88,136.86) --
-	(529.77,132.70) --
-	(531.65,135.88) --
-	(533.53,136.61) --
-	(535.41,134.54);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,150.71) --
+	( 75.27,152.99) --
+	( 78.11,153.34) --
+	( 80.95,153.46) --
+	( 83.79,154.87) --
+	( 86.63,154.01) --
+	( 89.47,150.03) --
+	( 92.31,152.38) --
+	( 95.15,151.57) --
+	( 97.99,152.37) --
+	(100.83,152.36) --
+	(103.67,150.86) --
+	(106.51,156.31) --
+	(109.35,153.24) --
+	(112.19,151.49) --
+	(115.03,151.36) --
+	(117.87,153.65) --
+	(120.71,151.38) --
+	(123.55,152.92) --
+	(126.40,153.78) --
+	(129.24,151.96) --
+	(132.08,152.95) --
+	(134.92,151.02) --
+	(137.76,151.57) --
+	(140.60,152.69) --
+	(143.44,152.68) --
+	(146.28,153.09) --
+	(149.12,152.91) --
+	(151.96,153.40) --
+	(154.80,153.72) --
+	(157.64,154.05) --
+	(160.48,150.47) --
+	(163.32,151.15) --
+	(166.16,154.68) --
+	(169.00,150.91) --
+	(171.84,152.67) --
+	(174.68,154.71) --
+	(177.52,150.54) --
+	(180.36,152.87) --
+	(183.20,154.34) --
+	(186.04,155.31) --
+	(188.88,151.72) --
+	(191.72,150.98) --
+	(194.56,153.67) --
+	(197.41,154.62) --
+	(200.25,153.87) --
+	(203.09,154.64) --
+	(205.93,147.78) --
+	(208.77,151.29) --
+	(211.61,149.62) --
+	(214.45,154.76) --
+	(217.29,154.96) --
+	(220.13,152.57) --
+	(222.97,154.38) --
+	(225.81,154.97) --
+	(228.65,151.07) --
+	(231.49,147.57) --
+	(234.33,153.88) --
+	(237.17,154.51) --
+	(240.01,156.10) --
+	(242.85,153.60) --
+	(245.69,152.48) --
+	(248.53,152.70) --
+	(251.37,150.55) --
+	(254.21,150.42) --
+	(257.05,153.27) --
+	(259.89,150.70) --
+	(262.73,154.55) --
+	(265.57,152.18) --
+	(268.42,153.01) --
+	(271.26,149.72) --
+	(274.10,153.84) --
+	(276.94,151.75) --
+	(279.78,152.74) --
+	(282.62,153.59) --
+	(285.46,151.51) --
+	(288.30,150.68) --
+	(291.14,149.01) --
+	(293.98,151.89) --
+	(296.82,154.30) --
+	(299.66,153.42) --
+	(302.50,155.56) --
+	(305.34,151.16) --
+	(308.18,147.57) --
+	(311.02,152.92) --
+	(313.86,151.71) --
+	(316.70,150.02) --
+	(319.54,152.22) --
+	(322.38,150.09) --
+	(325.22,153.11) --
+	(328.06,152.16) --
+	(330.90,151.37) --
+	(333.74,150.41) --
+	(336.59,154.30) --
+	(339.43,152.44) --
+	(342.27,151.58) --
+	(345.11,154.49) --
+	(347.95,149.53) --
+	(350.79,154.05) --
+	(353.63,151.10) --
+	(356.47,153.07) --
+	(359.31,150.01) --
+	(362.15,155.43) --
+	(364.99,152.12) --
+	(367.83,150.94) --
+	(370.67,152.10) --
+	(373.51,151.70) --
+	(376.35,154.23) --
+	(379.19,148.51) --
+	(382.03,151.49) --
+	(384.87,151.86) --
+	(387.71,153.13) --
+	(390.55,150.34) --
+	(393.39,150.97) --
+	(396.23,151.09) --
+	(399.07,151.14) --
+	(401.91,148.35) --
+	(404.75,150.18) --
+	(407.60,150.74) --
+	(410.44,154.68) --
+	(413.28,156.36) --
+	(416.12,149.02) --
+	(418.96,152.85) --
+	(421.80,153.32) --
+	(424.64,153.53) --
+	(427.48,154.47);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 66.75,142.83) --
-	( 68.63,140.13) --
-	( 70.51,141.93) --
-	( 72.39,141.91) --
-	( 74.28,142.43) --
-	( 76.16,146.39) --
-	( 78.04,141.61) --
-	( 79.92,141.14) --
-	( 81.80,143.78) --
-	( 83.69,140.06) --
-	( 85.57,141.28) --
-	( 87.45,144.25) --
-	( 89.33,140.02) --
-	( 91.22,143.17) --
-	( 93.10,140.45) --
-	( 94.98,141.62) --
-	( 96.86,143.92) --
-	( 98.74,143.18) --
-	(100.63,144.99) --
-	(102.51,143.92) --
-	(104.39,140.49) --
-	(106.27,143.03) --
-	(108.15,141.75) --
-	(110.04,144.93) --
-	(111.92,140.19) --
-	(113.80,146.77) --
-	(115.68,143.66) --
-	(117.57,141.45) --
-	(119.45,144.73) --
-	(121.33,140.27) --
-	(123.21,146.15) --
-	(125.09,144.70) --
-	(126.98,143.27) --
-	(128.86,141.92) --
-	(130.74,146.15) --
-	(132.62,140.59) --
-	(134.51,139.83) --
-	(136.39,141.78) --
-	(138.27,147.01) --
-	(140.15,142.91) --
-	(142.03,145.16) --
-	(143.92,150.29) --
-	(145.80,143.35) --
-	(147.68,141.31) --
-	(149.56,142.82) --
-	(151.45,142.93) --
-	(153.33,141.23) --
-	(155.21,142.28) --
-	(157.09,144.73) --
-	(158.97,141.28) --
-	(160.86,144.80) --
-	(162.74,143.76) --
-	(164.62,139.14) --
-	(166.50,144.55) --
-	(168.39,142.11) --
-	(170.27,143.40) --
-	(172.15,140.31) --
-	(174.03,144.97) --
-	(175.91,141.97) --
-	(177.80,140.53) --
-	(179.68,141.81) --
-	(181.56,146.17) --
-	(183.44,143.43) --
-	(185.32,139.06) --
-	(187.21,142.38) --
-	(189.09,140.37) --
-	(190.97,141.03) --
-	(192.85,143.88) --
-	(194.74,146.77) --
-	(196.62,140.46) --
-	(198.50,143.03) --
-	(200.38,141.89) --
-	(202.26,140.44) --
-	(204.15,139.71) --
-	(206.03,141.07) --
-	(207.91,142.19) --
-	(209.79,139.86) --
-	(211.68,142.89) --
-	(213.56,142.17) --
-	(215.44,142.86) --
-	(217.32,142.40) --
-	(219.20,143.71) --
-	(221.09,141.02) --
-	(222.97,142.74) --
-	(224.85,145.76) --
-	(226.73,143.65) --
-	(228.62,141.79) --
-	(230.50,143.50) --
-	(232.38,142.42) --
-	(234.26,142.91) --
-	(236.14,147.76) --
-	(238.03,143.33) --
-	(239.91,142.66) --
-	(241.79,145.02) --
-	(243.67,143.33) --
-	(245.56,142.23) --
-	(247.44,142.51) --
-	(249.32,139.83) --
-	(251.20,143.91) --
-	(253.08,140.91) --
-	(254.97,139.48) --
-	(256.85,142.03) --
-	(258.73,142.30) --
-	(260.61,142.42) --
-	(262.49,141.41) --
-	(264.38,142.28) --
-	(266.26,143.37) --
-	(268.14,143.80) --
-	(270.02,141.46) --
-	(271.91,145.00) --
-	(273.79,140.14) --
-	(275.67,144.39) --
-	(277.55,142.54) --
-	(279.43,143.15) --
-	(281.32,143.33) --
-	(283.20,139.76) --
-	(285.08,143.03) --
-	(286.96,142.39) --
-	(288.85,144.66) --
-	(290.73,140.34) --
-	(292.61,139.93) --
-	(294.49,143.71) --
-	(296.37,143.28) --
-	(298.26,140.41) --
-	(300.14,194.20) --
-	(302.02,189.62) --
-	(303.90,185.53) --
-	(305.79,181.72) --
-	(307.67,188.20) --
-	(309.55,184.65) --
-	(311.43,185.40) --
-	(313.31,184.56) --
-	(315.20,184.70) --
-	(317.08,188.90) --
-	(318.96,185.34) --
-	(320.84,183.53) --
-	(322.73,184.32) --
-	(324.61,182.76) --
-	(326.49,187.29) --
-	(328.37,184.50) --
-	(330.25,187.76) --
-	(332.14,188.11) --
-	(334.02,189.00) --
-	(335.90,185.66) --
-	(337.78,185.99) --
-	(339.67,185.43) --
-	(341.55,185.92) --
-	(343.43,187.03) --
-	(345.31,185.62) --
-	(347.19,187.02) --
-	(349.08,188.21) --
-	(350.96,184.78) --
-	(352.84,184.18) --
-	(354.72,185.67) --
-	(356.60,185.65) --
-	(358.49,182.77) --
-	(360.37,186.77) --
-	(362.25,182.54) --
-	(364.13,186.22) --
-	(366.02,185.75) --
-	(367.90,185.41) --
-	(369.78,185.28) --
-	(371.66,186.84) --
-	(373.54,182.80) --
-	(375.43,186.12) --
-	(377.31,183.02) --
-	(379.19,186.28) --
-	(381.07,183.58) --
-	(382.96,186.97) --
-	(384.84,182.70) --
-	(386.72,185.67) --
-	(388.60,186.93) --
-	(390.48,183.46) --
-	(392.37,188.06) --
-	(394.25,182.37) --
-	(396.13,188.11) --
-	(398.01,184.08) --
-	(399.90,186.74) --
-	(401.78,184.24) --
-	(403.66,186.67) --
-	(405.54,189.37) --
-	(407.42,182.23) --
-	(409.31,185.46) --
-	(411.19,186.00) --
-	(413.07,184.08) --
-	(414.95,185.89) --
-	(416.84,183.23) --
-	(418.72,184.04) --
-	(420.60,187.85) --
-	(422.48,186.21) --
-	(424.36,185.93) --
-	(426.25,185.27) --
-	(428.13,189.59) --
-	(430.01,186.78) --
-	(431.89,189.83) --
-	(433.77,181.83) --
-	(435.66,186.69) --
-	(437.54,185.54) --
-	(439.42,184.20) --
-	(441.30,188.26) --
-	(443.19,185.29) --
-	(445.07,188.98) --
-	(446.95,183.06) --
-	(448.83,187.89) --
-	(450.71,183.76) --
-	(452.60,185.86) --
-	(454.48,190.44) --
-	(456.36,183.23) --
-	(458.24,188.40) --
-	(460.13,183.47) --
-	(462.01,184.56) --
-	(463.89,185.83) --
-	(465.77,180.31) --
-	(467.65,187.07) --
-	(469.54,183.42) --
-	(471.42,186.43) --
-	(473.30,183.81) --
-	(475.18,185.53) --
-	(477.07,187.52) --
-	(478.95,186.14) --
-	(480.83,187.00) --
-	(482.71,184.60) --
-	(484.59,184.73) --
-	(486.48,184.66) --
-	(488.36,185.52) --
-	(490.24,184.18) --
-	(492.12,185.54) --
-	(494.01,184.71) --
-	(495.89,182.24) --
-	(497.77,183.25) --
-	(499.65,183.46) --
-	(501.53,184.33) --
-	(503.42,182.87) --
-	(505.30,188.10) --
-	(507.18,186.77) --
-	(509.06,182.75) --
-	(510.94,184.94) --
-	(512.83,185.13) --
-	(514.71,187.05) --
-	(516.59,182.61) --
-	(518.47,186.28) --
-	(520.36,185.68) --
-	(522.24,181.44) --
-	(524.12,183.35) --
-	(526.00,185.39) --
-	(527.88,185.63) --
-	(529.77,181.48) --
-	(531.65,184.66) --
-	(533.53,185.38) --
-	(535.41,183.31);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,150.71) --
+	( 75.27,152.99) --
+	( 78.11,153.34) --
+	( 80.95,153.46) --
+	( 83.79,154.87) --
+	( 86.63,154.01) --
+	( 89.47,150.03) --
+	( 92.31,152.38) --
+	( 95.15,151.57) --
+	( 97.99,152.37) --
+	(100.83,152.36) --
+	(103.67,150.86) --
+	(106.51,156.31) --
+	(109.35,153.24) --
+	(112.19,151.49) --
+	(115.03,151.36) --
+	(117.87,153.65) --
+	(120.71,151.38) --
+	(123.55,152.92) --
+	(126.40,153.78) --
+	(129.24,151.96) --
+	(132.08,152.95) --
+	(134.92,151.02) --
+	(137.76,151.57) --
+	(140.60,152.69) --
+	(143.44,152.68) --
+	(146.28,153.09) --
+	(149.12,152.91) --
+	(151.96,153.40) --
+	(154.80,153.72) --
+	(157.64,154.05) --
+	(160.48,150.47) --
+	(163.32,151.15) --
+	(166.16,154.68) --
+	(169.00,150.91) --
+	(171.84,152.67) --
+	(174.68,154.71) --
+	(177.52,150.54) --
+	(180.36,152.87) --
+	(183.20,154.34) --
+	(186.04,155.31) --
+	(188.88,151.72) --
+	(191.72,150.98) --
+	(194.56,153.67) --
+	(197.41,154.62) --
+	(200.25,153.87) --
+	(203.09,154.64) --
+	(205.93,147.78) --
+	(208.77,151.29) --
+	(211.61,149.62) --
+	(214.45,154.76) --
+	(217.29,154.96) --
+	(220.13,152.57) --
+	(222.97,154.38) --
+	(225.81,154.97) --
+	(228.65,151.07) --
+	(231.49,147.57) --
+	(234.33,153.88) --
+	(237.17,154.51) --
+	(240.01,156.10) --
+	(242.85,153.60) --
+	(245.69,152.48) --
+	(248.53,152.70) --
+	(251.37,150.55) --
+	(254.21,150.42) --
+	(257.05,153.27) --
+	(259.89,150.70) --
+	(262.73,154.55) --
+	(265.57,152.18) --
+	(268.42,153.01) --
+	(271.26,149.72) --
+	(274.10,153.84) --
+	(276.94,151.75) --
+	(279.78,152.74) --
+	(282.62,153.59) --
+	(285.46,151.51) --
+	(288.30,150.68) --
+	(291.14,149.01) --
+	(293.98,151.89) --
+	(296.82,154.30) --
+	(299.66,153.42) --
+	(302.50,155.56) --
+	(305.34,151.16) --
+	(308.18,147.57) --
+	(311.02,152.92) --
+	(313.86,151.71) --
+	(316.70,150.02) --
+	(319.54,152.22) --
+	(322.38,150.09) --
+	(325.22,153.11) --
+	(328.06,152.16) --
+	(330.90,151.37) --
+	(333.74,150.41) --
+	(336.59,154.30) --
+	(339.43,152.44) --
+	(342.27,151.58) --
+	(345.11,154.49) --
+	(347.95,149.53) --
+	(350.79,154.05) --
+	(353.63,151.10) --
+	(356.47,153.07) --
+	(359.31,150.01) --
+	(362.15,155.43) --
+	(364.99,152.12) --
+	(367.83,150.94) --
+	(370.67,152.10) --
+	(373.51,151.70) --
+	(376.35,154.23) --
+	(379.19,148.51) --
+	(382.03,151.49) --
+	(384.87,151.86) --
+	(387.71,153.13) --
+	(390.55,150.34) --
+	(393.39,150.97) --
+	(396.23,151.09) --
+	(399.07,151.14) --
+	(401.91,148.35) --
+	(404.75,150.18) --
+	(407.60,150.74) --
+	(410.44,154.68) --
+	(413.28,156.36) --
+	(416.12,149.02) --
+	(418.96,152.85) --
+	(421.80,153.32) --
+	(424.64,153.53) --
+	(427.48,232.35);
 \definecolor{drawColor}{RGB}{0,191,255}
 
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (298.26, 55.58) -- (298.26,270.72);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (424.64, 56.48) -- (424.64,268.60);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,196.47) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,189.77) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,225.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,206.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,189.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,235.83) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,168.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,199.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,154.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,243.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,222.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,238.37) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,169.47) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,227.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,198.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,201.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,175.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,231.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,186.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.34) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,164.51) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,237.93) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,212.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,243.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,202.61) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,219.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,181.94) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,162.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,211.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,221.82) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,242.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,193.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,222.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,216.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,190.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,241.35) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,176.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.35) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,192.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,184.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,221.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,224.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,219.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,181.45) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,216.79) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,185.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,268.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,188.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,172.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,187.45) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,186.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,212.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,184.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,245.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,227.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,251.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,193.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,246.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,191.68) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,240.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,169.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,250.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,192.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,242.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,195.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,199.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,184.13) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,239.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,192.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,224.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.26,174.59) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,175.75) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.68,154.47) -- (441.68,232.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.15,158.85) --
+	(441.68,154.47) --
+	(444.21,158.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.21,227.97) --
+	(441.68,232.35) --
+	(439.15,227.97);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.84,137.34) -- (320.84,186.12);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.16,135.51) -- (433.16,208.40);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (318.31,141.72) --
-	(320.84,137.34) --
-	(323.37,141.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.63,139.89) --
+	(433.16,135.51) --
+	(435.69,139.89);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.37,181.74) --
-	(320.84,186.12) --
-	(318.31,181.74);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.69,204.02) --
+	(433.16,208.40) --
+	(430.63,204.02);
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.55,190.42) -- (292.61,190.42);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81,190.91) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$5.22};
+\definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.23,187.89) --
-	(292.61,190.42) --
-	(288.23,192.94);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (470.08,147.93) {$\alpha = 4.88$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (373.54,158.80) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i=226.72$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 83.82) {shock time point $T^*_1 + 1$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (270.02,187.92) {$\hat{\alpha}_i$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,205.90) {$y_{T_1^*+1}$};
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (354.72, 63.76) {shock time point $T^*_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,229.85) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.98,270.72) rectangle (206.60,234.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,232.35) -- (427.48,232.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,229.82) --
+	(427.48,232.35) --
+	(423.10,234.88);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,208.40) -- (427.48,208.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,205.87) --
+	(427.48,208.40) --
+	(423.10,210.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,232.35) rectangle (212.08,196.35);
 \definecolor{drawColor}{RGB}{255,106,106}
 
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 71.98,258.72) -- ( 89.98,258.72);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,220.35) -- ( 93.75,220.35);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 71.98,246.72) -- ( 89.98,246.72);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,208.35) -- ( 93.75,208.35);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 98.98,255.28) {$\hat{Y}$ without shock effects};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,216.91) {$\hat{y}_{t}^{1}$ without shock effects};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 98.98,243.28) {$\hat{Y}$ with shock effects};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,204.91) {$\hat{y}_{t}^{2}$ with shock effects};
 \end{scope}

### 2020-05-28 manuscript/manuscript.tex
edit of manuscript and addition of simulation codes

@@
   citecolor  = blue,
-  urlcolor   = magenta,
+  urlcolor   = blue,
   colorlinks = true,
@@
 \begin{enumerate}
-  \item Figure 1 is updated.
-  \item Some introductions for forecast combination are added in Paragraph 2. Literature review for time-series pooling in cross-sectional (panel) data is rewritten and more to be added.
-  \item The procedure for parametric bootstrap is rewritten.
-  \item Technical details for SCM method are updated.
-  \item SCM code is written using \texttt{Rsolnp} package.
+  \item Figure 1 is revised accordingly.
+  \item The synthetic intervention paper and comment are added in the introduction. Other parts haven't been revised.
+  \item Parametric bootstrap is updated with additional comments. 
+  \item The background for Example section is written.
+  \item SCM.R for SCM method and sim.R for simulation are added in Github.
 \end{enumerate}
@@
 However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
-\textbf{Mention synthetic intervention paper here, stress the importance of carefully constructing the donor pool.}  \emph{\textcolor{red}{More to be added ...}}
+From a machine learning perspective, \citet{agarwal2020two} proposed a model-free synthetic intervention  method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
+Among those methodologies, they share the implicit assumption that candidates  from donor pool should be similar.
+In other words, caution should be dedicated to the construction of donor pool; otherwise, the result will be expected not to be  robust to the noise introduced by the insimilar ones.
+\emph{\textcolor{red}{More to be added ...}}
 
@@
     \includegraphics[height = 8cm]{comp.pdf}
-    \caption{A comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series and that the shock time is at $T_1^* = 125$.
-The dots represent least square estimate $\hat{\alpha}_i$ from disparate time series.
-Two model differs by an adjustment $\hat{\alpha}=\frac{1}{n}\sum_{i=1}^n \hat{\alpha}_i$.
-\textbf{The picture needs to be made more clear.
-Remove $\hat{\alpha}_i$ and state what those points are in the caption.
-Label the true (unknown to us) shock effect $\alpha_1$.}}\label{figure1}
+    \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 4.88$.
+The figure is a comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series, and that the shock time is at $T_1^* +1=126$.
+The magenta dots represent least square estimate $\hat{\alpha}_i$ from disparate time series.
+The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=5.22$.
+It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
   \end{center}  
@@
 Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology.
-This figure depicts a time-series that experienced a ``shock'' at time point $T_1^* = 125$.
-It is supposed that the researcher does not have any information beyond $T_1^*$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded.
+This figure depicts a time-series that experienced a ``shock'' at time point $T_1^*+1 = 126$.
+It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded.
 Similarity in this context means that the shock effects are random variables that from a common distribution.
@@
 \end{align}
-for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = 1(t > T_i^*)$, 
+for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = 1(t = T_i^* + 1)$, 
 $T_i^* < T_i$ and $\x_{i,t} \in \R^{p}$, $p \geq 1$.  We assume that the 
@@
   y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t}+ \beta_i'\mbf{x}_{i, t-1} + \varepsilon_{i,t}\\[.2cm]
-  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}+\t{\varepsilon}_{i, T_i},
+  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}+\t{\varepsilon}_{i},
 \end{array}\label{model2}
@@
 We further define 
-$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T_i^*-1}$. 
+$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T_i^*}$. 
 We will investigate post-shock aggregated estimators in $\mc{M}_2$ 
@@
  \mbf{X}_1 = \begin{pmatrix}
-    \mbf{x}_{1, T_1^*-1} \\ \mbf{x}_{1, T_1^*}
+    \mbf{x}_{1, T_1^*} \\ \mbf{x}_{1, T_1^*+1}
   \end{pmatrix}
@@
   = w_2\begin{pmatrix}
-     \mbf{x}_{2, T_2^*-1} \\
-      \mbf{x}_{2, T_2^*}
+     \mbf{x}_{2, T_2^*} \\
+      \mbf{x}_{2, T_2^*+1}
    \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
      \mbf{x}_{n+1, T_{n+1}^*} \\
-      \mbf{x}_{n+1, T_{n+1}^*}
+      \mbf{x}_{n+1, T_{n+1}^*+1}
    \end{pmatrix} .
@@
 \begin{align}
- \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*-1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*-1} \text{ and } \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*}.\label{SCM}
+ \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
 \end{align}
@@
    \left\{ \begin{pmatrix}
-     \mbf{x}_{2, T_2^*-1} \\
-      \mbf{x}_{2, T_2^*}
+     \mbf{x}_{2, T_2^*} \\
+      \mbf{x}_{2, T_2^*+1}
    \end{pmatrix}, \ldots, \begin{pmatrix}
      \mbf{x}_{n+1, T_{n+1}^*} \\
-      \mbf{x}_{n+1, T_{n+1}^*}
+      \mbf{x}_{n+1, T_{n+1}^*+1}
    \end{pmatrix} \right\}.
@@
     \begin{align*}
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*} + \frac{1}{n} \sum_{i=2}^{n+2} \gamma' \mbf{x}_{i, T_i^*-1} 
+      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1} + \frac{1}{n} \sum_{i=2}^{n+2} \gamma' \mbf{x}_{i, T_i^*} 
       \quad \text{ and } \quad 
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*} + \gamma' \mbf{x}_{1, T_1^*-1}.
+       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} + \gamma' \mbf{x}_{1, T_1^*}.
     \end{align*}
@@
     \begin{align*}
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*} + \frac{1}{n} \sum_{i=2}^{n+2}  \mu_{\gamma}'\mbf{x}_{i, T_i^*-1} 
+      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1} + \frac{1}{n} \sum_{i=2}^{n+2}  \mu_{\gamma}'\mbf{x}_{i, T_i^*} 
       \quad \text{ and } \quad 
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*} + \mu_{\gamma}' \mbf{x}_{1, T_1^*-1}.
+       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} + \mu_{\gamma}' \mbf{x}_{1, T_1^*}.
     \end{align*}
@@
 
-\textbf{I am not sure if all of this is necessary. This is a nice summary of the literature but I think that we only need the results that motivate our bootstrap procedure.}
-
 In this section, we present a parametric bootstrap procedure for our AR(1) model (see Section \ref{modelsetup}) in approximating the distribution of our shock-effect estimators.
@@
 In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}.
-The asymptotic accuracy for OLS parameter estimation is guaranteed under the order of $O(T^{-1/2})$ almost surely, where $T$ is the length of the time series \citep{berkowitz2000recent}.
-\citet{bose1988edgeworth} showed that it can be further improved to $o(T^{-1/2})$ almost surely under some regularity conditions.
+\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.
 Nevertheless, the pseudo time series generated by this procedure are not stationary.
 
-\citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series.
-However, the asymptotic accuracy of this procedure to OLS estimation is not known.
-Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$, the parameter of the geometric distribution (\textbf{what does this mean, what is the geometric distribution in this context?}).
+\citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
+This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$, where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$\footnote{for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$}; and the sampling stops when $N$ observations are reached.
+Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d.
+discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d.
+geometric random variables with parameter $p$.
+However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}.
+Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$.
 This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.
-More work related to bootstrapping time series  can be referred to \citet{berkowitz2000recent}.
+More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}.
 It is up to the user in selecting which procedure to choose but under different assumptions on the time-series.
-
-\textbf{We do not need to rewrite bootstrap algorithms that exist in the literature.
-We only need to write our algorithm.
-Emphasis needs to be placed on $T_i^*$being known, the pre and post $T_i^*$ sampling needs to be made explicit.}
 
@@
 \SetKwInOut{Input}{Input}
-\Input{$B$ --  the number of parametric bootstraps  \\ $S_i= \{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ -- the collection of  residuals for $t = 1,\ldots, T_i$ \\ $\mc{P}_i$ -- the fitted AR(1) model for $i = 2, \ldots, n+1$
-
+\Input{$B$ --  the number of parametric bootstraps  \\  $\{(y_{i,t}, \mbf{x}_{i,t})\colon i = 2,\ldots, n+1, t = 0, \ldots, T_i\}$ -- the data\\ $\{T_i^* \colon i = 1, \ldots, n+1\}$ -- the time point just before the shock\\$\{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ -- the collection of  residuals for $t = 1,\ldots, T_i$ \\ $\{\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_i, \hat{\theta}_i, \hat{\beta}_i\colon i = 2, \ldots, n+1\}$ -- the OLS estimates \\
 }
@@
   \For{$i = 2, \ldots, n+1$}{
-  Sample with replacement from $S_{i}$ to obtain $S_{i}^{(b)}\coloneqq \{\hat{\varepsilon}_{i, t}^{(b)} \colon t = 1, \ldots, T_i\}$
-
-  Plug $S_{i}^{(b)}$ into $\mc{P}_i$ to generate the bootstrapped response $\mbf{Y}_i^{(b)}$
-
-  Compute $\hat{\alpha}_i^{(b)}$ based on OLS estimation of AR(1) with $\mbf{Y}_i^{(b)}$ and covariates from $\mc{P}_i$
+
+    Sample with replacement from $\{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ to obtain $\{\hat{\varepsilon}_{i, t}^{(b)} \colon t = 1, \ldots, T_i\}$
+
+     Define $y_{i,0}^{(b)}=y_{i,0}$
+
+    \For{$t = 1,\ldots, T_i$}{
+
+     Compute $y_{i,t}^{(b)}=\hat{\eta}_i +\hat{\alpha}_i 1(t=T_i^*+1)+\hat{\phi}_iy_{i,t-1}^{(b)}+\theta_i'\mbf{x}_{i,t} + \beta_i'\mbf{x}_{i, t-1}+\hat{\varepsilon}_{i,t}^{(b)}$
     }
-    Compute $\hat{\alpha}_{\rm adj}^{(b)}$, $\hat{\alpha}_{\rm wadj}^{(b)}$, and $\hat{\alpha}_{\rm IVW}^{(b)}$ 
+    Compute $\hat{\alpha}_i^{(b)}$ based on OLS estimation of (\ref{equation1}) with $\{(y_{i,t}^{(b)}, \mbf{x}_{i,t}) \colon t= 0, \ldots, T_i\}$
   }
-   Compute the sample mean, and sample variance of $\hat{\alpha}_{\rm adj}^{(b)}$, $\hat{\alpha}_{\rm wadj}^{(b)}$, and $\hat{\alpha}_{\rm IVW}^{(b)}$.
+   Compute the $b$th shock-effect estimate $\hat{\alpha}^{(b)}_{\rm est}$ for $\mrm{est} \in \{\mrm{adj}, \mrm{wadj}, \mrm{IVW}\}$
+  }
+   Compute the sample mean, and sample variance of $\{\hat{\alpha}_{\rm est}^{(b)} \colon b = 1, \ldots, B\}$ for $\mrm{est} \in \{\mrm{adj}, \mrm{wadj}, \mrm{IVW}\}$
  \caption{Parametric bootstrap for approximation for  mean and  variance of shock-effect estimators of $\alpha_1$.}
@@
 The estimates yielded by Algorithm \ref{boots} provides an approximation for parameters involved in the risk-reduction conditions in Sections \ref{conditions} and \ref{comparisons}.
-In particular $\overline{\hat{\alpha}_{\rm wadj}}$, the sample mean of $\hat{\alpha}_{\rm wadj}^{b}$, will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}.
+The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$  and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally if we assume the regularity conditions outlined in  \citet{bose1988edgeworth}.
+The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
+\begin{align*}
+  \overline{\hat{\alpha}_{\mrm{wadj}}} \mid \Theta 
+  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)} \mid \Theta 
+  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)} \mid \Theta 
+  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i \mid \Theta=\E{\hat{\alpha}_{\rm wadj}|\Theta},
+\end{align*}
+The case for the sample variance of the bootstrapped weighted adjustment estimator would be similar.
+The same line of analysis holds for   adjustment estimator as well since  it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$ (see Section \ref{modelsetup}).
+Nevertheless, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is not a linear combination of OLS estimates with random weights.
+It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$.
+We would claim that Algorithm \ref{boots} only provides an \emph{approximation} for the case of $\hat{\alpha}_{\rm IVW}$.
+
+In particular $\overline{\hat{\alpha}_{\rm wadj}}$, the sample mean of $\hat{\alpha}_{\rm wadj}^{(b)}$, will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}.
 Therefore, we can judge whether to use a shock-effect estimator, and choose between  shock-effect estimators by this method.
 
-\textbf{We should include a brief simulation which shows that our bootstrap procedure works.}
+We \emph{stress} that the above approximation is conditioned on $\Theta$.
+Under a random-effect structure (see Section \ref{modelsetup}), every true shock effect of a time series in reality is only an observed value from a population.
+  For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$.
+
+The simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.
 
@@
 \label{simulation}
+
+\subsection{Parametric bootstrap simulation}
+\label{parametricbootstrapsimulation}
+
+In this section, we present the simulation for the parametric bootstrap procedure for AR(1) outlined in Section \ref{varbootstrap}.
+The simulation is only provided for the adjustment estimator and weighted adjustment estimator since the weights for inverse-variance estimator are random and the true values of its moments are unknown.
+
+\begin{center}
+  \begin{tabular}{l|cccccc}
+    & \multicolumn{6}{c}{Time series}\\
+    & 1 & 2 & 3 & 4 & 5 & 6\\
+   Length $T_i$ & 77 & 93 & 72 & 71 & 73 & 50 \\
+   Shock Time  $T_i^*+1$ & 20 & 39 & 45 & 52 & 59 & 11 \\
+   Autoregressive parameter $\phi_i$ & 0.540 & 0.961 & 0.654 & 0.547 & 0.266 & 0.197 
+  \end{tabular}
+\end{center}
+
+\section{Example}
+
+In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus (COVID-19) recession.
+Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020.
+We will detail how we  combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price without adjustment for the shock.
+The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool, and (4) nowcast.
+Section \ref{background} provides the justification for the first three steps.
+Section \ref{results} discusses the result of our forecast.
+
+\subsection{Background}
+\label{background}
+ Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo} and with a relatively recent initial public offering \citep{conocohist}.
+Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with OPEC decreasing the global price of oil the Sunday before trading resumes on Monday, March 9th \citep{cnbc}.
+Furthermore, fear of and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
+Major events include the SXSW festival being cancelled as trading closed on March 6th \citep{cnn}.
+New York declared a state of emergency on March 7th \citep{nygov}, and by Sunday, March 8th, eight states have declared a state of emergency while Italy placed 16 million people in quarantine \citep{newsweek}.
+
+Economic indicators forecasted our recession before the coronavirus pandemic began.
+The current recession followed an inversion of the yield curve that first happened back in March 22, 2019 \citep{ap}.
+An inversion of the yield curve is an event that signals that recessions are more likely \citep{fed, frbsf, tokic2019yield}.
+In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
+We also consider previous OPEC oil supply shocks.
+We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models.
+Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}.
+
+\subsubsection*{(1) AR(1) model and Time window}
+
+ We will use a simple AR(1) model to forecast Conoco Phillips stock price.
+This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months \citep{alquist2013forecasting}.
+We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window.
+All estimates will be adjusted for inflation using the inflation calculator at \url{https://www.usinflationcalculator.com}.
+The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects.
+All the parameters are estimated using OLS.
+
+\subsubsection*{(2) Selection of covariates}
+
+We perform two lines of analyses with one incorporating the price of S\&P 500 index and one without to justify our choice of covariate.
+Since the stock price of a company implies its value provided the number of shares is unchanged, the price of S\&P 500 index in the recession can partially represent the overall status of the economy.
+Therefore, using the price of S\&P 500 index as the covariate can possibly improve the precision of the OLS estimates for shock-effects that are unique to Conoco Phillips.
+The rationale for inclusion of the price of S\&P 500 index is similar to that of market return in capital asset pricing model (CAPM).
+
+\subsubsection*{(3) Construction of donor pool}
+
+Our donor pool will consist of Conoco Phillips shock effects observed on September 11th, 2001, September 8th, 2008, and November 27, 2014.
+The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve, and the third was an OPEC induced supply side shock effect.
+The reasons for those three shocks are
+\begin{enumerate}
+  \item On September 11th, 2001, Islamic extremist al-Qaeda  committed a series of four terrorist attacks  against U.S.
+It triggers negative percussions on the U.S.
+economy with falling stock prices, increased unemployment rates, and falling U.S.
+dollar \citep{nytimes911, history}.
+  \item On September 8th, 2008, the United States announced its takeover of Fannie May and Freddie Mac \citep{UST}, and it was reported that the nation’s unemployment rate reached five-year highs.
+It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt \citep{lehman}.
+  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{CNBC2014}.
+During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors.
+During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}.
+\end{enumerate}
+
+Some other notable shock effects were not included in this analysis because the conditions preceding them are not similar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects \citep{shiller1988portfolio, latimes, nytimes}.
+
+\subsection{Results}
+\label{results}
 
@@
    &= \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right)\\
-   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}\right]\bigg\}\\
-   &=\mu_{\alpha}+\mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}\right]\bigg\}.\tag{$\mbf{W}\in \mc{W}$}
+   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}\right]\bigg\}\\
+   &=\mu_{\alpha}+\mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}\right]\bigg\}.\tag{$\mbf{W}\in \mc{W}$}
    \end{align*}
@@
    \E{\hat{\alpha}_{\rm adj}}
-   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \E{\delta_{i}'\mbf{x}_{i, T_i^*}+\gamma_i'\mbf{x}_{i, T^*_i-1}}.
+   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \E{\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}}.
    \end{align*}
@@
   \begin{cases}
-       \frac{1}{n} \sum_{i=2}^{n+1} \delta'(\mbf{x}_{i, T_i^*}-n\mbf{x}_{1, T_1^*}) +  \frac{1}{n} \sum_{i=2}^{n+1} \gamma'(\mbf{x}_{i, T_i^*-1}-n\mbf{x}_{1, T_1^*-1}) & \text{ for } \mc{M}_{21}\\
-    \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}'(\mbf{x}_{i, T_i^*}-n\mbf{x}_{1, T_1^*}) +  \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\gamma}'(\mbf{x}_{i, T_i^*-1}-n\mbf{x}_{1, T_1^*-1}) & \text{ for }\mc{M}_{22}
+       \frac{1}{n} \sum_{i=2}^{n+1} \delta'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1}) +  \frac{1}{n} \sum_{i=2}^{n+1} \gamma'(\mbf{x}_{i, T_i^*}-n\mbf{x}_{1, T_1^*}) & \text{ for } \mc{M}_{21}\\
+    \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1}) +  \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\gamma}'(\mbf{x}_{i, T_i^*}-n\mbf{x}_{1, T_1^*}) & \text{ for }\mc{M}_{22}
   \end{cases}.
@@
   By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ holds for $\mc{M}_{21}$ and $\mc{M}_{22}$.
-The remainder of the proof follows a similar argument to the proof of Proposition \ref{propriskadj} (\textbf{Fix this problematic reference}).
+The remainder of the proof follows a similar argument to the proof of Proposition \ref{proprisk} (\textbf{Fix this problematic reference}).
 \end{proof-of-proposition}

### 2020-05-28 manuscript/sim.R

@@ -1,0 +1,263 @@
+# Bootstrap Simulation
+set.seed(2014)
+# parameter setup
+n <- 5 # pool size
+T <- sample(50:100, size = 6) # Time Length
+Tstar <- c() # Shock Time Points
+for (t in T) {
+ Tstar <- c(Tstar, sample(3:t, size = 1))
+}
+phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters
+
+# parameter 
+mu.alpha <- 10; sigma.alpha <- 1; sigma <- 1
+
+# construction of design matrix and shock effects
+X <- c()
+alpha <- c()
+delta <- c()
+gamma <- c()
+for (i in 1:(n + 1)) {
+  Ti <- T[i]
+  Tstari <- Tstar[i]
+  X[[i]] <- rnorm(Ti + 1) 
+  # parameter setup
+  delta[i] <- rnorm(1)
+  gamma[i] <- rnorm(1)
+  epsilontildei <- rnorm(n = 1, sd = sigma.alpha)
+  # alpha
+  alpha <- c(alpha, mu.alpha + delta[i] * X[[i]][Tstari + 1] + 
+               gamma[i] * X[[i]][Tstari] + epsilontildei)
+}
+
+mu.alpha + delta[1] * X[[i]][Tstar[1] + 1] + gamma[1] * X[[i]][Tstar[1]]
+
+# generation of yit
+Y <- c()
+for (i in 1:(n + 1)) {
+  
+  # initial value
+  yi0 <- rnorm(1)
+  
+  # setup
+  Tstari <- Tstar[i]
+  alphai <- alpha[i]
+  phii <- phi[i]
+  xi <- X[[i]]
+  
+  # parameter setup
+  thetai <- rnorm(1)
+  betai <- rnorm(1)
+  etai <- rnorm(1)
+  
+  yi <- yi0
+  for (t in 2:(T[i] + 1)) {
+    epsilonit <- rnorm(n = 1, sd = sigma)
+    yi <- c(yi, etai + alphai * ifelse(t == Tstari + 2, yes = 1, no = 0) +
+              phii * yi[t - 1] + thetai * xi[t] + betai * xi[t - 1] + epsilonit)
+  }
+  
+  Y[[i]] <- yi
+}
+
+# OLS
+# this function returns the W^* estimated by synthetic control method (SCM)
+scm <- function(X, Tstar) {
+  # X is a list of covariates for disparate time series
[…]

### 2020-05-28 CP_2020.Rmd

--- 2020-05-20 CP_2020.Rmd
@@
 
-Our donor pool will consist of Conoco Phillips shock effects observed on September 11th, 2001, September 8th, 2008, and November 27, 2014.
-The first two shock effects were observed during recessions that were predicated by an inversion of the yiled curve, and the third was an OPEC induced supply side shock effect.
-Some other notable shock effects were not included in this analysis because the conditions preceding them are not simialar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects ([1987 Source](https://www.nber.org/chapters/c10958.pdf), [2011 Source](https://www.latimes.com/world/la-xpm-2011-aug-06-la-fi-us-debt-downgrade-20110806-story.html), [2015 Source](https://www.nytimes.com/2015/08/25/business/dealbook/daily-stock-market-activity.html)).
+Our donor pool will consist of Conoco Phillips shock effects observed on September 11th, 2001, March 18th, 2008, many days in September and October of 2008, and November 27, 2014.
+The September 11th, 2001 and the 2008 shock effects were observed during recessions that were predicated by an inversion of the yield curve, and the November 27, 2014 shock was an OPEC induced supply side shock effect.
+<!--Some other notable shock effects were not included in this analysis because the conditions preceding them are not simialar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects ([1987 Source](https://www.nber.org/chapters/c10958.pdf), [2011 Source](https://www.latimes.com/world/la-xpm-2011-aug-06-la-fi-us-debt-downgrade-20110806-story.html), [2015 Source](https://www.nytimes.com/2015/08/25/business/dealbook/daily-stock-market-activity.html)).
+-->
 <!-- 
@@
 
+## Brent Crude prices
+Brent_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/brent-daily_csv/data/d93216330ab2c27aae3d177b2f0f0921/brent-daily_csv.csv") %>%
+  rename(Oil_Close = Price)
+
+## WTI Crude prices
+WTI_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/wti-daily_csv/data/c414c9d375ec3c8f9d7c276d866fb2a4/wti-daily_csv.csv") %>%
+  rename(WTI_Close = Price)
+
+## inflation adjustment
+getSymbols("CPIAUCSL", src='FRED')
+avg.cpi <- apply.yearly(CPIAUCSL, mean)
+inflation_adj <- as.numeric(avg.cpi['2020'])/avg.cpi
+inflation_adj <- as.data.frame(inflation_adj)
+colnames(inflation_adj) <- c("dollars_2020")
+inflation_adj <- inflation_adj %>% mutate(year = 1947:2020)
+```
+
+```{r, echo = FALSE, eval = FALSE}
 ## Exxon Mobile
@@
 
-Here is the 1 day nowcast with S&P 500:
+Here is the estimated shock effect 1 day in the future with covariates:
 
@@
 COP_close <- merge(COP_close, GSPC_close)
+COP_close <- merge(COP_close, WTI_Crude)
 Y <- COP_close$COP_Close[-1]
@@
 start <- which(COP_close$Date == "2001-09-10")
-## change to equality
 start_day <- as.numeric(1:nrow(COP_close) == start + 1)
@@
 COP_close_small <- COP_close[(start-29):(start+1), ]
-m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
+m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                  data = COP_close_small)
-alpha_9_11_1 <- summary(m_COP_9_11)$coef[3,1:2]
-alpha_9_11_1 #-1.97 (0.41) in 2020 dollars
+alpha_9_11 <- summary(m_COP_9_11)$coef[3,1:2] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
+alpha_9_11
 ```
 
-Here is the 1 day nowcast without S&P 500:
+Here is the estimated shock effect 1 day in the future without covariates:
 
 ```{r}
-m_COP_9_11 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_9_11_1_no <- summary(m_COP_9_11)$coef[3,1:2]
-alpha_9_11_1_no #-1.56 (0.33) in 2020 dollars
+m_COP_9_11_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
+alpha_9_11_no <- summary(m_COP_9_11_no)$coef[3,1:2] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
+alpha_9_11_no
 ```
 
-Here is the 5 day nowcast with S&P 500:
+#### 2008 shock effects
+<!-- https://www.democracynow.org/2008/9/8/headlines -->
+
+The first 4 major shocks of 2008 were proceeded by unprecedented failures in the financial sector that rattled markets, oil prices, and Conoco Phillips stock alike.
+The March 8th, September 12th, and September 26th shock effects were proceeded by the bailouts or failures of Bear Stearns, Lehman Brothers, and Washington Mutual financial institutions.
+The September 8th shock effect was proceeded by Fannie Mae and Freddie Mac being placed in conservatorship.
+
+We first find the Baer Stearns shock effect. Here is the estimated shock effect 1 day in the future with covariates:
 
 ```{r}
-COP_close_small <- COP_close[(start-29):(start+5), ]
-m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
+COP_close <- COP_close %>% select(-"start_day")
+start <- which(COP_close$Date == "2008-03-18")
+start_day <- as.numeric(1:nrow(COP_close) == start)
+COP_close <- COP_close %>% mutate(start_day = start_day)
+COP_close_small <- COP_close[(start-29):(start+1), ]
+m_COP_3_18 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                  data = COP_close_small)
-alpha_9_11_5 <- summary(m_COP_9_11)$coef[3,1:2]
-             #constant: -2.19 (0.46) in 2020 dollars
-alpha_9_11_5 #-1.17 (0.54) in 2020 dollars
+alpha_3_18 <- summary(m_COP_3_18)$coef[3,1:2] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
+alpha_3_18
 ```
 
-Here is the 5 day nowcast without S&P 500:
+Here is the estimated shock effect 1 day in the future without covariates:
 
 ```{r}
-COP_close_small <- COP_close[(start-29):(start+5), ]
-m_COP_9_11 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_9_11_5_no <- summary(m_COP_9_11)$coef[3,1:2]
-                #constant: -1.55 (0.28) in 2020 dollars
-alpha_9_11_5_no #-1.59 (0.52) in 2020 dollars
+m_COP_3_18_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
+alpha_3_18_no <- summary(m_COP_3_18_no)$coef[3,1:2] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
+alpha_3_18_no
 ```
 
-#### Monday, September 8th, 2008
-<!-- https://www.democracynow.org/2008/9/8/headlines -->
+We now find the September shock effects. We estimate the financial instistution failures as if they are all the same.
 
-In the weekend before trading began, the United States announced its takeover of Fannie May and Freddie Mac [Source](https://www.treasury.gov/press-center/press-releases/Pages/hp1129.aspx), and it was reported that the nation’s unemployment rate reached five-year highs.
+```{r}
+COP_close <- COP_close %>% select(-"start_day")
+COP_close[which(COP_close$COP_Close - COP_close$Y >= 3.5), ][2:4, ]
+start <- which(COP_close$COP_Close - COP_close$Y >= 3.5)[2:4]
+start_day <- as.numeric(1:nrow(COP_close) %in% start)
+COP_close <- COP_close %>% mutate(start_day = start_day)
+COP_close_small <- COP_close[
+  which(COP_close$Date == "2008-07-28"):which(COP_close$Date == "2008-09-26"), ]
+m_COP_Sept_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
+                 data = COP_close_small)
+alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3,1:2] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
+alpha_Sept_08
+```
+
+Here is the estimated shock effect 1 day in the future without covariates:
+
+```{r}
+m_COP_Sept_08_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
+alpha_Sept_08_no <- summary(m_COP_Sept_08_no)$coef[3,1:2] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
+alpha_Sept_08_no
+```
+
+<!-- In the weekend before trading began, the United States announced its takeover of Fannie May and Freddie Mac [Source](https://www.treasury.gov/press-center/press-releases/Pages/hp1129.aspx), and it was reported that the nation’s unemployment rate reached five-year highs.
 It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt [Source](https://www.marketwatch.com/story/lehman-folds-with-record-613-billion-debt).
@@
 COP_close <- COP_close %>% select(-"start_day")
-start <- which(COP_close$Date == "2008-09-08")
+#start <- which(COP_close$Date == "2008-09-08")
+start <- which(COP_close$Date == "2008-09-12")
+
 ## change to equality
@@
 ```
-
-Here is the 5 day nowcast with S&P 500:
-
-```{r}
-COP_close_small <- COP_close[(start-30):(start+4), ]
-m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
-                    data = COP_close_small)
-alpha_9_08_08_5 <- summary(m_COP_9_08_08)$coef[3,1:2]
-                #constant: -4.20 (1.61) in 2020 dollars
-alpha_9_08_08_5 # -6.28 (2.00) in 2020 dollars
-```
-
-Here is the 5 day nowcast with S&P 500:
-
-```{r}
-m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_9_08_08_5_no <- summary(m_COP_9_08_08)$coef[3,1:2]
-                   #constant: -4.14 (1.58) in 2020 dollars
-alpha_9_08_08_5_no #-6.26 (1.94) 
-```
+-->
 
@@
 start_day <- as.numeric(1:nrow(COP_close) == start)
-## change to equality
 COP_close <- COP_close %>% mutate(start_day = start_day)
@@
                     data = COP_close_small)
-alpha_11_27_14_1 <- summary(m_COP_11_27_14)$coef[3,1:2]
-alpha_11_27_14_1 #-5.68 (1.06) in 2020 dollars
+alpha_11_27_14 <- summary(m_COP_11_27_14)$coef[3,1:2] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
+alpha_11_27_14
 ```
 
-Here is the 1 day nowcast without S&P 500:
+Here is the estimated shock effect 1 day in the future without covariates:
 
@@
 m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_11_27_14_1_no <- summary(m_COP_11_27_14)$coef[3,1:2]
-alpha_11_27_14_1_no #-5.26 (0.97) in 2020 dollars
-```
-
-Here is the 5 day nowcast with S&P 500:
-
-```{r}
-COP_close_small <- COP_close[(start-30):(start+4), ]
-m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
-                    data = COP_close_small)
-alpha_11_27_14_5 <- summary(m_COP_11_27_14)$coef[3,1:2]
-                 #constant: -2.69 (0.94) in 2020 dollars
-alpha_11_27_14_5 #-5.43 (1.01) in 2020 dollars
-```
-
-Here is the 5 day nowcast without S&P 500:
-
-```{r}
-m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_11_27_14_5_no <- summary(m_COP_11_27_14)$coef[3,1:2]
-                    #constant:-1.23 (0.65) in 2020 dollars
-alpha_11_27_14_5_no #-5.26 (0.99) in 2020 dollars
+alpha_11_27_14_no <- summary(m_COP_11_27_14)$coef[3,1:2]  * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
+alpha_11_27_14_no
 ```
@@
                     data = COP_close_small)
-alpha_03_09_20_1 <- summary(m_COP_03_09_20)$coef[3,1:2]
-alpha_03_09_20_1 #-10.51414 (1.62901)
+alpha_03_09_20 <- summary(m_COP_03_09_20)$coef[3,1:2]
+alpha_03_09_20 #-10.51414 (1.62901)
 ```
@@
 m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_03_09_20_1_no <- summary(m_COP_03_09_20)$coef[3,1:2]
-alpha_03_09_20_1_no #-10.533756 (1.617991)
-```
-
-Here is the 5 day shock effect with S&P 500:
-
-```{r}
-COP_close_small <- COP_close[(start-30):(start+4), ]
-m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
-                    data = COP_close_small)
-alpha_03_09_20_5 <- summary(m_COP_03_09_20)$coef[3,1:2]
-                 #constant: -5.333522 (2.077089)
-alpha_03_09_20_5 #-10.714979 (1.775454)
-```
-
-Here is the 5 day shock effect without S&P 500:
-
-```{r}
-m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_03_09_20_5_no <- summary(m_COP_03_09_20)$coef[3,1:2]
-                    #constant: -5.314242 (2.031455)
-alpha_03_09_20_5_no #-10.668604 (1.754461)
+alpha_03_09_20_no <- summary(m_COP_03_09_20)$coef[3,1:2]
+alpha_03_09_20_no #-10.533756 (1.617991)
 ```
@@
 ```{r}
-a_estimates <- rbind(
-c(-1.97, 0.41, -1.56, 0.33, -1.17, 0.54, -1.59, 0.52),
-c(-6.95, 1.98, -6.94, 1.94, -6.28, 2.00, -6.26, 1.94),
-c(-5.68, 1.06, -5.26, 0.97, -5.43, 1.01, -5.26, 0.99)
-)
-colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no",
-                   "a_5","sd_a_5","a_5_no","sd_a_5_no")
-rownames(a_estimates) <- c("y2001", "y2008", "y2014")
+
+a_estimates <- rbind( c(alpha_9_11, alpha_9_11_no),
+  c(alpha_3_18, alpha_3_18_no),
+  c(alpha_Sept_08, alpha_Sept_08_no),
+  c(alpha_11_27_14, alpha_11_27_14_no))
+colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no")
+rownames(a_estimates) <- c("y2001", "my2008", "sy2008", "y2014")
 ```
@@
 ```{r}
-a_adj <- colMeans(a_estimates[,1:4 * 2 -1 ])
-a_adj_no911 <- colMeans(a_estimates[-1,1:4 * 2 -1 ])
+a_adj <- colMeans(a_estimates[, c(1,3)])
+a_adj_no911 <- colMeans(a_estimates[-1, c(1,3)])
 weights <- rbind(
-(1 / a_estimates[,1:4 * 2])[1, ] / colSums(1 / a_estimates[,1:4 * 2]),
-(1 / a_estimates[,1:4 * 2])[2, ] / colSums(1 / a_estimates[,1:4 * 2]),
-(1 / a_estimates[,1:4 * 2])[3, ] / colSums(1 / a_estimates[,1:4 * 2])
+(1 / a_estimates[, c(2,4)])[1, ] / colSums(1 / a_estimates[, c(2,4)]),
+(1 / a_estimates[, c(2,4)])[2, ] / colSums(1 / a_estimates[, c(2,4)]),
+(1 / a_estimates[, c(2,4)])[3, ] / colSums(1 / a_estimates[, c(2,4)]),
+(1 / a_estimates[, c(2,4)])[4, ] / colSums(1 / a_estimates[, c(2,4)])
 )
-a_adj_IVW <- colSums(weights * a_estimates[,1:4 * 2 -1 ])
+a_adj_IVW <- colSums(weights * a_estimates[, c(1,3)])
 weights_no911 <- rbind(
-(1 / a_estimates[-1,1:4 * 2])[1, ] / colSums(1 / a_estimates[-1,1:4 * 2]),
-(1 / a_estimates[-1,1:4 * 2])[2, ] / colSums(1 / a_estimates[-1,1:4 * 2])
+(1 / a_estimates[-1, c(2,4)])[1, ] / colSums(1 / a_estimates[-1, c(2,4)]),
+(1 / a_estimates[-1, c(2,4)])[2, ] / colSums(1 / a_estimates[-1, c(2,4)]),
+(1 / a_estimates[-1, c(2,4)])[3, ] / colSums(1 / a_estimates[-1, c(2,4)])
 )
-a_adj_IVW_no911 <- colSums(weights_no911 * a_estimates[-1,1:4 * 2 -1 ])
+a_adj_IVW_no911 <- colSums(weights_no911 * a_estimates[-1, c(1,3)])
 ```
@@
 
-Interesting to note that the March 9th, 2020 shock effect is closely approximated by the additive effect of the recession diven shock on September 8th, 2008 and the OPEC supply driven shock on November 27, 2014.
+Interesting to note that the March 9th, 2020 shock effect is closely approximated by the additive effect of the average of the 2008 recession diven shocks and the OPEC supply driven shock on November 27, 2014.
 
 ```{r}
-additive <- colSums(a_estimates[-1,1:4 * 2 -1])
+additive <- colMeans(a_estimates[c(2,3), c(1,3)]) + a_estimates[4, c(1,3)]
 additive
@@
 ```{r}
-m_COP_03_06_20 <- lm(Y ~ COP_Close + GSPC_Close, 
+m_COP_03_06_20 <- lm(Y ~ COP_Close + GSPC_Close + WTI_Close, 
                      data = COP_close_small[-nrow(COP_close_small), ])
 preds <- predict(m_COP_03_06_20)
-Yhat_nothing_1 <- 0.933928 * 46.96604 -7.462690 + 0.003267 * 3023.94
-Yhat_adj_1 <- Yhat_nothing_1 + shock_effects[, 1]
-Yhat_adj_additive_1 <- Yhat_nothing_1 + additive[1]
+summary(m_COP_03_06_20)
+Yhat_nothing <- -2.430990 + 1.045492 * 47.01888 + 
+  0.003063 * 3023.94 + -0.210924 * 45.90
+Yhat_adj <- Yhat_nothing + shock_effects[, 1]
+Yhat_adj_additive <- Yhat_nothing + additive[1]
 
 ## doing nothing completely misses the mark
-Yhat_nothing_1 - COP_close_small$Y[nrow(COP_close_small)]
+Yhat_nothing - COP_close_small$Y[nrow(COP_close_small)]
 
 ## adjustment gets closer
-Yhat_adj_1 - COP_close_small$Y[nrow(COP_close_small)]
+Yhat_adj - COP_close_small$Y[nrow(COP_close_small)]
 
 ## additive effect does well
-Yhat_adj_additive_1 - COP_close_small$Y[nrow(COP_close_small)]
+Yhat_adj_additive - COP_close_small$Y[nrow(COP_close_small)]
 ```
@@
 mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
-             c(Yhat_adj_1, Yhat_adj_additive_1))
+             c(Yhat_adj, Yhat_adj_additive))
 colnames(mat) <- c("id", "Yhat_adj")
@@
   geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:6) + 
-  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values, Yhat_nothing_1)), 
+  geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing), 
+             aes(x = x, y = y), col = "blue", cex = 1.5) + 
+  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values, Yhat_nothing)), 
             col = "blue") + 
+    annotate("text", x=1, y=seq(from = 47, to = 39,length.out=6), 
+             label=c("no adjustment","mean adjustment",
+                     "mean adjustment (no 9/11)","IVW adjustment",
+                     "IVW adjustment (no 9/11)", "aggregate adjustment"), 
+             hjust=0) + 
+    annotate("point", x = 0, y=seq(from = 47, to = 39,length.out=6), 
+             pch = c(16,2:6),
+             color = c("blue","red","red","red","red","red")) +
   theme_minimal()
@@
 
-Here is the 1 day nowcast without S&P 500:
+Here is the 1 day nowcast without covariates:
 
@@
 preds <- predict(m_COP_03_06_20)
-Yhat_nothing_1_no <- -1.25682 + 1.01170 * 47.00149 
-Yhat_adj_1_no <- Yhat_nothing_1_no + shock_effects[, 2]
-Yhat_adj_additive_1_no <- Yhat_nothing_1_no + additive[2]
+Yhat_nothing_no <- -1.25682 + 1.01170 * 47.00149
+Yhat_adj_no <- Yhat_nothing_no + shock_effects[, 2]
+Yhat_adj_additive_no <- Yhat_nothing_no + additive[2]
 
 ## doing nothing misses the mark
-Yhat_nothing_1_no - COP_close_small$Y[nrow(COP_close_small)]
+Yhat_nothing_no - COP_close_small$Y[nrow(COP_close_small)]
 
 ## adjustment gets closer
-Yhat_adj_1_no - COP_close_small$Y[nrow(COP_close_small)]
+Yhat_adj_no - COP_close_small$Y[nrow(COP_close_small)]
 
 ## additive effect does well
-Yhat_adj_additive_1_no - COP_close_small$Y[nrow(COP_close_small)]
+Yhat_adj_additive_no - COP_close_small$Y[nrow(COP_close_small)]
 ```
@@
 mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
-             c(Yhat_adj_1,  Yhat_adj_additive_1_no))
+             c(Yhat_adj,  Yhat_adj_additive_no))
 colnames(mat) <- c("id", "Yhat_adj")
@@
                              col = 2, pch = 2:6) + 
+  geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing_no), 
+             aes(x = x, y = y), col = "blue", cex = 1.5) + 
   geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values,
-                              Yhat_nothing_1_no)), 
+                              Yhat_nothing_no)), 
             col = "blue") +
+      annotate("text", x=1, y=seq(from = 47, to = 39,length.out=6), 
+             label=c("no adjustment","mean adjustment",
+                     "mean adjustment (no 9/11)","IVW adjustment",
+                     "IVW adjustment (no 9/11)", "aggregate adjustment"), 
+             hjust=0) + 
+    annotate("point", x = 0, y=seq(from = 47, to = 39,length.out=6), 
+             pch = c(16,2:6),
+             color = c("blue","red","red","red","red","red")) +
   theme_minimal()

### 2020-06-02 CP_2020.Rmd
updated example; updated bootstrap; fixed some references; still need to do more

@@
 ## September 11th (no trading from T-F); 1 day nowcast
-COP_close <- COP %>% select(COP.Close, Date) %>% 
+COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% 
   rename(COP_Close = COP.Close)
-GSPC_close <- GSPC %>% select(GSPC.Close, Date) %>% 
+GSPC_close <- GSPC %>% dplyr::select(GSPC.Close, Date) %>% 
   rename(GSPC_Close = GSPC.Close)
@@
 The first 4 major shocks of 2008 were proceeded by unprecedented failures in the financial sector that rattled markets, oil prices, and Conoco Phillips stock alike.
-The March 8th, September 12th, and September 26th shock effects were proceeded by the bailouts or failures of Bear Stearns, Lehman Brothers, and Washington Mutual financial institutions.
+The September 12th and September 26th shock effects were proceeded by the bailouts or failures of Lehman Brothers and Washington Mutual financial institutions.
 The September 8th shock effect was proceeded by Fannie Mae and Freddie Mac being placed in conservatorship.
-
-We first find the Baer Stearns shock effect. Here is the estimated shock effect 1 day in the future with covariates:
-
-```{r}
-COP_close <- COP_close %>% select(-"start_day")
-start <- which(COP_close$Date == "2008-03-18")
-start_day <- as.numeric(1:nrow(COP_close) == start)
-COP_close <- COP_close %>% mutate(start_day = start_day)
-COP_close_small <- COP_close[(start-29):(start+1), ]
-m_COP_3_18 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
-                 data = COP_close_small)
-alpha_3_18 <- summary(m_COP_3_18)$coef[3,1:2] * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
-alpha_3_18
-```
-
-Here is the estimated shock effect 1 day in the future without covariates:
-
-```{r}
-m_COP_3_18_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_3_18_no <- summary(m_COP_3_18_no)$coef[3,1:2] * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
-alpha_3_18_no
-```
 
@@
 ```{r}
-COP_close <- COP_close %>% select(-"start_day")
-COP_close[which(COP_close$COP_Close - COP_close$Y >= 3.5), ][2:4, ]
-start <- which(COP_close$COP_Close - COP_close$Y >= 3.5)[2:4]
-start_day <- as.numeric(1:nrow(COP_close) %in% start)
-COP_close <- COP_close %>% mutate(start_day = start_day)
+#COP_close <- COP_close %>% dplyr::select(-"start_day")
+COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% 
+  rename(COP_Close = COP.Close)
+COP_close <- merge(COP_close, GSPC_close)
+COP_close <- merge(COP_close, WTI_Crude)
+Y <- COP_close$COP_Close[-1]
+COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
+start_09_08_08 <- which(COP_close$Date == "2008-09-08")
+start_09_12_08 <- which(COP_close$Date == "2008-09-12")
+start_09_26_08 <- which(COP_close$Date == "2008-09-26")
+start_day_09_08_08 <- as.numeric(1:nrow(COP_close) %in% start_09_08_08)
+start_day_09_12_08 <- as.numeric(1:nrow(COP_close) %in% start_09_12_08)
+start_day_09_26_08 <- as.numeric(1:nrow(COP_close) %in% start_09_26_08)
+COP_close <- COP_close %>% mutate(start_day_09_08_08 = start_day_09_08_08, 
+                                  start_day_09_12_08 = start_day_09_12_08, 
+                                  start_day_09_26_08 = start_day_09_26_08)
 COP_close_small <- COP_close[
   which(COP_close$Date == "2008-07-28"):which(COP_close$Date == "2008-09-26"), ]
-m_COP_Sept_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
+m_COP_Sept_08 <- lm(Y ~ COP_Close + start_day_09_08_08 + start_day_09_12_08 + 
+                      start_day_09_26_08 + GSPC_Close + WTI_Close, 
                  data = COP_close_small)
-alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3,1:2] * 
+alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3:5,1:2] * 
   inflation_adj$dollars_2020[inflation_adj$year == 2008] 
@@
 ```{r}
-m_COP_Sept_08_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_Sept_08_no <- summary(m_COP_Sept_08_no)$coef[3,1:2] * 
+m_COP_Sept_08_no <- lm(Y ~ COP_Close + start_day_09_08_08 + start_day_09_12_08 + 
+                      start_day_09_26_08, data = COP_close_small)
+alpha_Sept_08_no <- summary(m_COP_Sept_08_no)$coef[3:5,1:2] * 
   inflation_adj$dollars_2020[inflation_adj$year == 2008] 
@@
 ```
-
-<!-- In the weekend before trading began, the United States announced its takeover of Fannie May and Freddie Mac [Source](https://www.treasury.gov/press-center/press-releases/Pages/hp1129.aspx), and it was reported that the nation’s unemployment rate reached five-year highs.
-It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt [Source](https://www.marketwatch.com/story/lehman-folds-with-record-613-billion-debt).
-
-Here is the 1 day nowcast with S&P 500:
-
-```{r}
-COP_close <- COP_close %>% select(-"start_day")
-#start <- which(COP_close$Date == "2008-09-08")
-start <- which(COP_close$Date == "2008-09-12")
-
-## change to equality
-start_day <- as.numeric(1:nrow(COP_close) == start)
-COP_close <- COP_close %>% mutate(start_day = start_day)
-COP_close_small <- COP_close[(start-30):(start), ]
-m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
-                    data = COP_close_small)
-alpha_9_08_08_1 <- summary(m_COP_9_08_08)$coef[3,1:2]
-alpha_9_08_08_1 #-6.95 (1.98) in 2020 dollars
-```
-
-Here is the 1 day nowcast without S&P 500:
-
-```{r}
-m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_9_08_08_1_no <- summary(m_COP_9_08_08)$coef[3,1:2]
-alpha_9_08_08_1_no #-6.94 (1.94) in 2020 dollars
-```
--->
 
@@
 ```{r}
-COP_close <- COP_close %>% select(-"start_day")
+COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% 
+  rename(COP_Close = COP.Close)
+COP_close <- merge(COP_close, GSPC_close)
+COP_close <- merge(COP_close, WTI_Crude)
+Y <- COP_close$COP_Close[-1]
+COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
 start <- which(COP_close$Date == "2014-11-26")
@@
 ```{r}
-COP_close <- COP_close %>% select(-"start_day")
+COP_close <- COP_close %>% dplyr::select(-"start_day")
 start <- which(COP_close$Date == "2020-03-06")
@@
 ```{r}
-
 a_estimates <- rbind( c(alpha_9_11, alpha_9_11_no),
-  c(alpha_3_18, alpha_3_18_no),
-  c(alpha_Sept_08, alpha_Sept_08_no),
+  cbind(alpha_Sept_08, alpha_Sept_08_no),
   c(alpha_11_27_14, alpha_11_27_14_no))
 colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no")
-rownames(a_estimates) <- c("y2001", "my2008", "sy2008", "y2014")
+rownames(a_estimates) <- c("y2001","s8y2008","s12y2008","s26y2008","y2014")
 ```
@@
 (1 / a_estimates[, c(2,4)])[3, ] / colSums(1 / a_estimates[, c(2,4)]),
-(1 / a_estimates[, c(2,4)])[4, ] / colSums(1 / a_estimates[, c(2,4)])
+(1 / a_estimates[, c(2,4)])[4, ] / colSums(1 / a_estimates[, c(2,4)]),
+(1 / a_estimates[, c(2,4)])[5, ] / colSums(1 / a_estimates[, c(2,4)])
 )
@@
 (1 / a_estimates[-1, c(2,4)])[2, ] / colSums(1 / a_estimates[-1, c(2,4)]),
-(1 / a_estimates[-1, c(2,4)])[3, ] / colSums(1 / a_estimates[-1, c(2,4)])
+(1 / a_estimates[-1, c(2,4)])[3, ] / colSums(1 / a_estimates[-1, c(2,4)]),
+(1 / a_estimates[-1, c(2,4)])[4, ] / colSums(1 / a_estimates[-1, c(2,4)])
 )
@@
 ```{r}
-additive <- colMeans(a_estimates[c(2,3), c(1,3)]) + a_estimates[4, c(1,3)]
+additive <- colMeans(a_estimates[2:4, c(1,3)]) + a_estimates[4, c(1,3)]
 additive

### 2020-06-02 manuscript/manuscript.tex
updated example; updated bootstrap; fixed some references; still need to do more

@@
 To gauge the performance of a procedure that produces forecasts 
-$\{\hat y_{1,t}, t= 1,2,\ldots\}$ given time horizon $T_1$, we consider the 
-average forecast risk
+$\{\hat y_{1,t}, t= 1,2,\ldots\}$ given time horizon $T_1$, 
+we consider forecast risk in the form of root mean squared error
 $$
-  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2
+  R_T = \sqrt{\frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2}
 $$
-in our analyses. In this article, we consider a dynamic panel data 
+in our analyses. \textbf{Let's switch to root mean squared error, this metric is often used in forecasting articles.} In this article, we consider a dynamic panel data 
 model with autoregressive structure similar to that in \citet{blundell1998initial}. 
@@
 
-\subsection{Parametric bootstrap for risk-reduction evaluation problems}
+\subsection{Bootstrap for risk-reduction evaluation problems}
 \label{varbootstrap}
 
-In this section, we present a parametric bootstrap procedure for our AR(1) model (see Section \ref{modelsetup}) in approximating the distribution of our shock-effect estimators.
+In this section, we present a bootstrap procedure 
+%(see Section \ref{modelsetup}) 
+that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice.
+Our procedure involves the resampling of residuals in the separate OLS fits.
+This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
 %NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives.
@@
 However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model.
-In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed.
+%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed.
 In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}.
 \citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.
-Nevertheless, the pseudo time series generated by this procedure are not stationary.
-
+However, the pseudo time series generated by this procedure are not stationary.
+(\textbf{Is this necessary to state?
+There needs to be a rationale fro why this is not a problem.})
+
+\textbf{I think that our bootstrap procedure should first sample the disparate time series without replacement, and then estimate the parameters in each resampled time series.}
+The formal steps of our bootstrap procedures are outlined in the Supplementary Materials, the intuition for our procedure is as follows: let $B$ be the bootstrap sample size and initialize $y_{i,0}$ for all $i = 2,\ldots,n+1$.
+At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i = 2,\ldots,n+1$.
+Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$.
+We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
+%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
+%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$.
+Therefore, this parametric bootstrap framework will work for us.
+Once can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
+
+Let 
+$
+  \overline{\hat{\alpha}_{\mrm{aadj}}} 
+    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
+$, 
+$
+  \overline{\hat{\alpha}_{\mrm{wadj}}} 
+    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
+$, 
+and 
+$
+  \overline{\hat{\alpha}_{\mrm{IVW}}} 
+    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
+$
+The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold.
+The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below.
+As $B \to \infty$,
+\begin{align*}
+  \overline{\hat{\alpha}_{\mrm{wadj}}}
+  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
+  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
+  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
+  =\E{\hat{\alpha}_{\rm wadj}|\Theta},
+\end{align*}
+The case for the sample variance of the bootstrapped weighted adjustment estimator is similar.
+The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$.
+However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is a linear combination of OLS estimates with random weights.
+It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$.
+We claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.
+
+%In particular $\overline{\hat{\alpha}_{\rm wadj}}$ will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}.
+Therefore, we can judge whether to use a shock-effect estimator, and choose between shock-effect estimators by this method.
+
+We stress that the above approximation is conditioned on $\Theta$ and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
+%Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population.
+For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$.
+Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.
+
+\section{Simulation}
+
+\label{simulation}
+
+\subsection{Parametric bootstrap simulation}
+\label{parametricbootstrapsimulation}
+
+%In this section, we present the simulation for the parametric bootstrap procedure for AR(1) outlined in Section \ref{varbootstrap}.
+The simulation is only provided for the adjustment estimator and weighted adjustment estimator since the weights for inverse-variance estimator are random and the true values of its moments are unknown.
+
+%\begin{center}
+%  \begin{tabular}{l|cccccc}
+%    & \multicolumn{6}{c}{Time series}\\
+%    & 1 & 2 & 3 & 4 & 5 & 6\\
+%   Length $T_i$ & 77 & 93 & 72 & 71 & 73 & 50 \\
+%   Shock Time  $T_i^*+1$ & 20 & 39 & 45 & 52 & 59 & 11 \\
+%   Autoregressive parameter $\phi_i$ & 0.540 & 0.961 & 0.654 & 0.547 & 0.266 & 0.197 
+%  \end{tabular}
+%\end{center}
+
+\section{Forecasting Conoco Phillips stock in the presence of shocks}
+
+In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus (COVID-19) recession.
+Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020.
+We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustment for the shock.
+The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool, and (4) nowcast.
+Section \ref{background} provides the justification for the first three steps.
+Section \ref{results} discusses the result of our forecast.
+
+\subsection{Background}
+\label{background}
+
+ Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo}. %and with a relatively recent initial public offering \citep{conocohist}. 
+Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}.
+Furthermore, fear of and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
+Major events include the SXSW festival being cancelled as trading closed on March 6th \citep{wang2020impact}.
+New York declared a state of emergency on March 7th \citep{nygov}, and by Sunday, March 8th, eight states have declared a state of emergency \citep{alonso2020state} while Italy placed 16 million people in quarantine \citep{sjodin2020only}.
+
+Economic indicators forecasted our recession before the coronavirus pandemic began.
+The current recession followed an inversion of the yield curve that first happened back in March, 2019 \citep{tokic2019yield}.
+An inversion of the yield curve is an event that signals that recessions are more likely \citep{andolfatto2018yield, bauer2018economic}.
+In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
+We also consider previous OPEC oil supply shocks.
+We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models.
+Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}.
+
+\subsubsection*{(1) AR(1) model and Time window}
+
+ We will use a simple AR(1) model to forecast Conoco Phillips stock price.
+This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months \citep{alquist2013forecasting}.
+We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window.
+All estimates will be adjusted for inflation.
+The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects.
+All the parameters are estimated using OLS.
+
+\subsubsection*{(2) Selection of covariates}
+
+We perform two lines of analyses with one incorporating the price of S\&P 500 index and one without to justify our choice of covariate.
+Since the stock price of a company implies its value provided the number of shares is unchanged, the price of S\&P 500 index in the recession can partially represent the overall status of the economy.
+Therefore, using the price of S\&P 500 index as the covariate can possibly improve the precision of the OLS estimates for shock-effects that are unique to Conoco Phillips.
+The rationale for inclusion of the price of S\&P 500 index is similar to that of market return in capital asset pricing model (CAPM).
+(\textbf{Need reference for the CAPM}.)
+
+\subsubsection*{(3) Construction of donor pool}
+
+Our donor pool will consist of Conoco Phillips shock effects observed after September 11th, 2001, %March 18th, 2008, 
+several events in September, 2008, and November 27, 2014.
+The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}.
+The reasons for those three shocks are
+\begin{enumerate}
+  \item On September 11th, 2001, Islamic extremist al-Qaeda committed a series of terrorist attacks against the United States of America \citep{braniff2011towards}.
+In addition to the tragic loss of life, this triggered negative repercussions on the U.S.
+and world economies with falling stock prices and a falling U.S.
+dollar \citep{floyd2001terror}.
+Moreover, trading was closed until September 17, 2001 \citep{johnston2006impact}.
+  %\item In heavy trading on Tuesday, March 18 \citep{shorter2008bear}
+  \item On September 8th, 2008, the United States announced its takeover of Fannie May and Freddie Mac \citep{UST}, and it was reported that the nation’s unemployment rate reached five-year highs.
+It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt \citep{lehman}.
+  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}.
+During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors.
+During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}.
+\end{enumerate}
+
+%Some other notable shock effects were not included in this analysis because the conditions preceding them are not similar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects \citep{shiller1988portfolio, latimes, nytimes}.
+
+\subsection{Results}
+\label{results}
+
+\section{Discussion}
+
+Our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series.
 \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
@@
 
-\vspace{.2cm}
-\begin{algorithm}[H]
-\SetAlgoLined \label{boots}
-
-\SetKwInOut{Input}{Input}
-\Input{$B$ --  the number of parametric bootstraps  \\  $\{(y_{i,t}, \mbf{x}_{i,t})\colon i = 2,\ldots, n+1, t = 0, \ldots, T_i\}$ -- the data\\ $\{T_i^* \colon i = 1, \ldots, n+1\}$ -- the time point just before the shock\\$\{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ -- the collection of  residuals for $t = 1,\ldots, T_i$ \\ $\{\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_i, \hat{\theta}_i, \hat{\beta}_i\colon i = 2, \ldots, n+1\}$ -- the OLS estimates \\
-}
-
-\KwResult{The sample mean, and sample variance of bootstrapped adjustment estimator, inverse-variance weighted estimator, and weighted-adjustment estimator.}
-
-  \For{$b = 1:B$}{
-  \For{$i = 2, \ldots, n+1$}{
-
-    Sample with replacement from $\{\hat{\varepsilon}_{i, t} \colon t = 1, \ldots, T_i\}$ to obtain $\{\hat{\varepsilon}_{i, t}^{(b)} \colon t = 1, \ldots, T_i\}$
-
-     Define $y_{i,0}^{(b)}=y_{i,0}$
-
-    \For{$t = 1,\ldots, T_i$}{
-
-     Compute $y_{i,t}^{(b)}=\hat{\eta}_i +\hat{\alpha}_i 1(t=T_i^*+1)+\hat{\phi}_iy_{i,t-1}^{(b)}+\theta_i'\mbf{x}_{i,t} + \beta_i'\mbf{x}_{i, t-1}+\hat{\varepsilon}_{i,t}^{(b)}$
-    }
-    Compute $\hat{\alpha}_i^{(b)}$ based on OLS estimation of (\ref{equation1}) with $\{(y_{i,t}^{(b)}, \mbf{x}_{i,t}) \colon t= 0, \ldots, T_i\}$
-  }
-   Compute the $b$th shock-effect estimate $\hat{\alpha}^{(b)}_{\rm est}$ for $\mrm{est} \in \{\mrm{adj}, \mrm{wadj}, \mrm{IVW}\}$
-  }
-   Compute the sample mean, and sample variance of $\{\hat{\alpha}_{\rm est}^{(b)} \colon b = 1, \ldots, B\}$ for $\mrm{est} \in \{\mrm{adj}, \mrm{wadj}, \mrm{IVW}\}$
- \caption{Parametric bootstrap for approximation for  mean and  variance of shock-effect estimators of $\alpha_1$.}
-\end{algorithm}
-\vspace{.2cm}
-
-The procedures of bootstrapping AR(1) can be outline as in Algorithm \ref{boots}.
-We stress that the $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for  $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are i.i.d.
-since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$ (see Section \ref{modelsetup}), and it is \emph{not} absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$.
-Therefore, this parametric bootstrap framework will work for us.
-
-The estimates yielded by Algorithm \ref{boots} provides an approximation for parameters involved in the risk-reduction conditions in Sections \ref{conditions} and \ref{comparisons}.
-The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$  and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally if we assume the regularity conditions outlined in  \citet{bose1988edgeworth}.
-The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
-\begin{align*}
-  \overline{\hat{\alpha}_{\mrm{wadj}}} \mid \Theta 
-  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)} \mid \Theta 
-  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)} \mid \Theta 
-  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i \mid \Theta=\E{\hat{\alpha}_{\rm wadj}|\Theta},
-\end{align*}
-The case for the sample variance of the bootstrapped weighted adjustment estimator would be similar.
-The same line of analysis holds for   adjustment estimator as well since  it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$ (see Section \ref{modelsetup}).
-Nevertheless, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is not a linear combination of OLS estimates with random weights.
-It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$.
-We would claim that Algorithm \ref{boots} only provides an \emph{approximation} for the case of $\hat{\alpha}_{\rm IVW}$.
-
-In particular $\overline{\hat{\alpha}_{\rm wadj}}$, the sample mean of $\hat{\alpha}_{\rm wadj}^{(b)}$, will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}.
-Therefore, we can judge whether to use a shock-effect estimator, and choose between  shock-effect estimators by this method.
-
-We \emph{stress} that the above approximation is conditioned on $\Theta$.
-Under a random-effect structure (see Section \ref{modelsetup}), every true shock effect of a time series in reality is only an observed value from a population.
-  For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$.
-
-The simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.
-
-\section{Simulation}
-
-\label{simulation}
-
-\subsection{Parametric bootstrap simulation}
-\label{parametricbootstrapsimulation}
-
-In this section, we present the simulation for the parametric bootstrap procedure for AR(1) outlined in Section \ref{varbootstrap}.
-The simulation is only provided for the adjustment estimator and weighted adjustment estimator since the weights for inverse-variance estimator are random and the true values of its moments are unknown.
-
-\begin{center}
-  \begin{tabular}{l|cccccc}
-    & \multicolumn{6}{c}{Time series}\\
-    & 1 & 2 & 3 & 4 & 5 & 6\\
-   Length $T_i$ & 77 & 93 & 72 & 71 & 73 & 50 \\
-   Shock Time  $T_i^*+1$ & 20 & 39 & 45 & 52 & 59 & 11 \\
-   Autoregressive parameter $\phi_i$ & 0.540 & 0.961 & 0.654 & 0.547 & 0.266 & 0.197 
-  \end{tabular}
-\end{center}
-
-\section{Example}
-
-In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus (COVID-19) recession.
-Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020.
-We will detail how we  combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price without adjustment for the shock.
-The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool, and (4) nowcast.
-Section \ref{background} provides the justification for the first three steps.
-Section \ref{results} discusses the result of our forecast.
-
-\subsection{Background}
-\label{background}
- Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo} and with a relatively recent initial public offering \citep{conocohist}.
-Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with OPEC decreasing the global price of oil the Sunday before trading resumes on Monday, March 9th \citep{cnbc}.
-Furthermore, fear of and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
-Major events include the SXSW festival being cancelled as trading closed on March 6th \citep{cnn}.
-New York declared a state of emergency on March 7th \citep{nygov}, and by Sunday, March 8th, eight states have declared a state of emergency while Italy placed 16 million people in quarantine \citep{newsweek}.
-
-Economic indicators forecasted our recession before the coronavirus pandemic began.
-The current recession followed an inversion of the yield curve that first happened back in March 22, 2019 \citep{ap}.
-An inversion of the yield curve is an event that signals that recessions are more likely \citep{fed, frbsf, tokic2019yield}.
-In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
-We also consider previous OPEC oil supply shocks.
-We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models.
-Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}.
-
-\subsubsection*{(1) AR(1) model and Time window}
-
- We will use a simple AR(1) model to forecast Conoco Phillips stock price.
-This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months \citep{alquist2013forecasting}.
-We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window.
-All estimates will be adjusted for inflation using the inflation calculator at \url{https://www.usinflationcalculator.com}.
-The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects.
-All the parameters are estimated using OLS.
-
-\subsubsection*{(2) Selection of covariates}
-
-We perform two lines of analyses with one incorporating the price of S\&P 500 index and one without to justify our choice of covariate.
-Since the stock price of a company implies its value provided the number of shares is unchanged, the price of S\&P 500 index in the recession can partially represent the overall status of the economy.
-Therefore, using the price of S\&P 500 index as the covariate can possibly improve the precision of the OLS estimates for shock-effects that are unique to Conoco Phillips.
-The rationale for inclusion of the price of S\&P 500 index is similar to that of market return in capital asset pricing model (CAPM).
-
-\subsubsection*{(3) Construction of donor pool}
-
-Our donor pool will consist of Conoco Phillips shock effects observed on September 11th, 2001, September 8th, 2008, and November 27, 2014.
-The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve, and the third was an OPEC induced supply side shock effect.
-The reasons for those three shocks are
-\begin{enumerate}
-  \item On September 11th, 2001, Islamic extremist al-Qaeda  committed a series of four terrorist attacks  against U.S.
-It triggers negative percussions on the U.S.
-economy with falling stock prices, increased unemployment rates, and falling U.S.
-dollar \citep{nytimes911, history}.
-  \item On September 8th, 2008, the United States announced its takeover of Fannie May and Freddie Mac \citep{UST}, and it was reported that the nation’s unemployment rate reached five-year highs.
-It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt \citep{lehman}.
-  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{CNBC2014}.
-During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors.
-During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}.
-\end{enumerate}
-
-Some other notable shock effects were not included in this analysis because the conditions preceding them are not similar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects \citep{shiller1988portfolio, latimes, nytimes}.
-
-\subsection{Results}
-\label{results}
-
-\section{Supplementary Materials}
+\section{Appendix}
 
@@
   By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ holds for $\mc{M}_{21}$ and $\mc{M}_{22}$.
-The remainder of the proof follows a similar argument to the proof of Proposition \ref{proprisk} (\textbf{Fix this problematic reference}).
+The remainder of the proof follows a similar argument to the proof of Proposition \ref{proprisk}.
 \end{proof-of-proposition}

### 2020-06-03 CP_2020.Rmd
updates to data analysis; removed table of contents; updated checklist

@@
 COP_close_small <- COP_close[(start-29):(start+1), ]
+COP_close_small[, 2:5] <- COP_close_small[, 2:5] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
 m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                  data = COP_close_small)
-alpha_9_11 <- summary(m_COP_9_11)$coef[3,1:2] * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
+alpha_9_11 <- summary(m_COP_9_11)$coef[3,1:2] 
 alpha_9_11
@@
 m_COP_9_11_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_9_11_no <- summary(m_COP_9_11_no)$coef[3,1:2] * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
+alpha_9_11_no <- summary(m_COP_9_11_no)$coef[3,1:2]
 alpha_9_11_no
@@
   which(COP_close$Date == "2008-07-28"):which(COP_close$Date == "2008-09-26"), ]
+COP_close_small[, 2:5] <- COP_close_small[, 2:5] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
 m_COP_Sept_08 <- lm(Y ~ COP_Close + start_day_09_08_08 + start_day_09_12_08 + 
@@
                  data = COP_close_small)
-alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3:5,1:2] * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
+alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3:5,1:2] 
 alpha_Sept_08
@@
                       start_day_09_26_08, data = COP_close_small)
-alpha_Sept_08_no <- summary(m_COP_Sept_08_no)$coef[3:5,1:2] * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
+alpha_Sept_08_no <- summary(m_COP_Sept_08_no)$coef[3:5,1:2] 
 alpha_Sept_08_no
@@
 COP_close_small <- COP_close[(start-30):(start), ]
-m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
+COP_close_small[, 2:5] <- COP_close_small[, 2:5] * 
+  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
+m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close  + WTI_Close,
                     data = COP_close_small)
-alpha_11_27_14 <- summary(m_COP_11_27_14)$coef[3,1:2] * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
+alpha_11_27_14 <- summary(m_COP_11_27_14)$coef[3,1:2] 
 alpha_11_27_14
@@
 m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_11_27_14_no <- summary(m_COP_11_27_14)$coef[3,1:2]  * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
+alpha_11_27_14_no <- summary(m_COP_11_27_14)$coef[3,1:2]  
 alpha_11_27_14_no
@@
 start <- which(COP_close$Date == "2020-03-06")
-## change to equality
 start_day <- as.numeric(1:nrow(COP_close) == start)
@@
 
-Here is the 1 day nowcast with S&P 500:
+Here is the 1 day nowcast with covariates:
 
 ```{r}
-m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
+m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close  + WTI_Close, 
                     data = COP_close_small)
 alpha_03_09_20 <- summary(m_COP_03_09_20)$coef[3,1:2]
-alpha_03_09_20 #-10.51414 (1.62901)
+alpha_03_09_20 #-11.31712 (1.90208)
 ```
 
-Here is the 1 day nowcast without S&P 500:
+Here is the 1 day nowcast without covariates:
 
@@
   c(alpha_11_27_14, alpha_11_27_14_no))
-colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no")
+a_estimates[, c(2,4)] <- a_estimates[, c(2,4)]^2
+colnames(a_estimates) <- c("a_1","var_a_1","a_1_no","var_a_1_no")
 rownames(a_estimates) <- c("y2001","s8y2008","s12y2008","s26y2008","y2014")
@@
 Interesting to note that the March 9th, 2020 shock effect is closely approximated by the additive effect of the average of the 2008 recession diven shocks and the OPEC supply driven shock on November 27, 2014.
+We first compute the additive adjustment estimator.
 
 ```{r}
+## Additive adjustment
 additive <- colMeans(a_estimates[2:4, c(1,3)]) + a_estimates[4, c(1,3)]
 additive
+```
+
+We now compute the additive IVW adjustment estimator.
+
+```{r}
+weights_additive <- rbind(
+(1 / a_estimates[, c(2,4)])[1, ] / colSums(1 / a_estimates[1:4, c(2,4)]),
+(1 / a_estimates[, c(2,4)])[2, ] / colSums(1 / a_estimates[1:4, c(2,4)]),
+(1 / a_estimates[, c(2,4)])[3, ] / colSums(1 / a_estimates[1:4, c(2,4)]),
+(1 / a_estimates[, c(2,4)])[4, ] / colSums(1 / a_estimates[1:4, c(2,4)])
+)
+a_adj_IVW_additive <- colSums(weights_additive * a_estimates[1:4, c(1,3)])
+weights_no911_additive <- rbind(
+(1 / a_estimates[2:4, c(2,4)])[1, ] / colSums(1 / a_estimates[2:4, c(2,4)]),
+(1 / a_estimates[2:4, c(2,4)])[2, ] / colSums(1 / a_estimates[2:4, c(2,4)]),
+(1 / a_estimates[2:4, c(2,4)])[3, ] / colSums(1 / a_estimates[2:4, c(2,4)])
+)
+a_adj_IVW_no911_additive <- 
+  colSums(weights_no911_additive * a_estimates[2:4, c(1,3)])
+
+## Additive IVW adjustment
+additive_IVW <- as.numeric(a_adj_IVW_additive[1] + a_estimates[5, 1])
+additive_IVW
+
+## Additive IVW adjustment without covariates
+additive_IVW_no <- as.numeric(a_adj_IVW_additive[2] + a_estimates[5, 1])
+additive_IVW_no
+
+## Additive IVW adjustment without 911
+additive_IVW_no911 <- as.numeric(a_adj_IVW_no911_additive[1] + a_estimates[5, 1])
+additive_IVW_no911
+
+## Additive IVW adjustment without 911 and covariates
+additive_IVW_no911_no <- as.numeric(a_adj_IVW_no911_additive[2] + a_estimates[5, 1])
+additive_IVW_no911_no
 ```
@@
 
-Here is the 1 day nowcast with S&P 500:
+Here is the 1 day nowcast with covariates:
 
@@
 Yhat_adj_additive <- Yhat_nothing + additive[1]
+Yhat_adj_additive_IVW <- Yhat_nothing + additive_IVW
+Yhat_adj_additive_IVW_no911 <- Yhat_nothing + additive_IVW_no911
 
@@
 
-## additive effect does well
+## additive effect does well with standard adjustment
 Yhat_adj_additive - COP_close_small$Y[nrow(COP_close_small)]
+
+## additive effect does well with IVW adjustment
+Yhat_adj_additive_IVW - COP_close_small$Y[nrow(COP_close_small)]
+Yhat_adj_additive_IVW_no911 - COP_close_small$Y[nrow(COP_close_small)]
 ```
@@
 mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
-             c(Yhat_adj, Yhat_adj_additive))
+             c(Yhat_adj, Yhat_adj_additive, Yhat_adj_additive_IVW_no911))
 colnames(mat) <- c("id", "Yhat_adj")
@@
 ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
-  labs(title = "Conoco Phillips forecasting (with S&P 500)", 
-       x = "Day", y = "Close price (in USD)") +
+  labs(title = "Conoco Phillips forecasting", 
+       x = "Day", y = "Closing price (in USD)") +
   geom_point() + 
-  geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:6) + 
+  geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:7) + 
   geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing), 
@@
             col = "blue") + 
-    annotate("text", x=1, y=seq(from = 47, to = 39,length.out=6), 
+    annotate("text", x=1, y=seq(from = 47, to = 38,length.out=7), 
              label=c("no adjustment","mean adjustment",
                      "mean adjustment (no 9/11)","IVW adjustment",
-                     "IVW adjustment (no 9/11)", "aggregate adjustment"), 
+                     "IVW adjustment (no 9/11)", "aggregate adjustment", 
+                     "aggregate IVW adjustment"), 
              hjust=0) + 
-    annotate("point", x = 0, y=seq(from = 47, to = 39,length.out=6), 
-             pch = c(16,2:6),
-             color = c("blue","red","red","red","red","red")) +
+    annotate("point", x = 0, y=seq(from = 47, to = 38,length.out=7), 
+             pch = c(16,2:7),
+             color = c("blue","red","red","red","red","red","red")) +
   theme_minimal()
@@
 Yhat_adj_additive_no <- Yhat_nothing_no + additive[2]
+Yhat_adj_additive_IVW_no <- Yhat_nothing + additive_IVW_no
+Yhat_adj_additive_IVW_no911_no <- Yhat_nothing + additive_IVW_no911_no
 
@@
 Yhat_adj_additive_no - COP_close_small$Y[nrow(COP_close_small)]
+
+## additive effect does well with IVW adjustment
+Yhat_adj_additive_IVW_no - COP_close_small$Y[nrow(COP_close_small)]
+Yhat_adj_additive_IVW_no911_no - COP_close_small$Y[nrow(COP_close_small)]
 ```
@@
 mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
-             c(Yhat_adj,  Yhat_adj_additive_no))
+             c(Yhat_adj,  Yhat_adj_additive_no, Yhat_adj_additive_IVW_no911_no))
 colnames(mat) <- c("id", "Yhat_adj")
@@
 ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
-  labs(title = "Conoco Phillips forecasting (without S&P 500)", 
-       x = "Day", y = "Close price (in USD)") +
+  labs(title = "Conoco Phillips forecasting (without covariates)", 
+       x = "Day", y = "Closing price (in USD)") +
   geom_point() + 
   geom_point(data = dat, aes(x = id, y = Yhat_adj), 
-                             col = 2, pch = 2:6) + 
+                             col = 2, pch = 2:7) + 
   geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing_no), 
@@
             col = "blue") +
-      annotate("text", x=1, y=seq(from = 47, to = 39,length.out=6), 
+      annotate("text", x=1, y=seq(from = 47, to = 38,length.out=7), 
              label=c("no adjustment","mean adjustment",
                      "mean adjustment (no 9/11)","IVW adjustment",
-                     "IVW adjustment (no 9/11)", "aggregate adjustment"), 
+                     "IVW adjustment (no 9/11)", "aggregate adjustment",
+                     "aggregate IVW adjustment"), 
              hjust=0) + 
-    annotate("point", x = 0, y=seq(from = 47, to = 39,length.out=6), 
-             pch = c(16,2:6),
-             color = c("blue","red","red","red","red","red")) +
+    annotate("point", x = 0, y=seq(from = 47, to = 38,length.out=7), 
+             pch = c(16,2:7),
+             color = c("blue","red","red","red","red","red","red")) +
   theme_minimal()

### 2020-06-03 manuscript/manuscript.tex
updates to data analysis; removed table of contents; updated checklist

@@
 \begin{enumerate}
-  \item Literature review and introduction (We need a literature review for existing methods that are similar/different but close enough methods.
-Possible searches include pooling, time series pooling, bayesian time series, bayesian autoregression)
-  \item Data analysis
+  \item Literature review and introduction. Need more references, need to mention synthetic interventions in the introduction or the discussion.
+  \item Need to mention possible generalizations in the Discussion.
+  \item Need to add weighted adjustment estimator to the data analysis.
+  \item Need to add simulations. 
+  \item Update abstract.
 \end{enumerate}
@@
 \begin{enumerate}
-  \item Figure 1 is revised accordingly.
   \item The synthetic intervention paper and comment are added in the introduction. Other parts haven't been revised.
-  \item Parametric bootstrap is updated with additional comments. 
-  \item The background for Example section is written.
   \item SCM.R for SCM method and sim.R for simulation are added in Github.
+  \item Data analysis references are fixed. The structure is organized better.
 \end{enumerate}
@@
 % table of contents
-\tableofcontents
+%\tableofcontents
 
@@
 $\{\hat y_{1,t}, t= 1,2,\ldots\}$ given time horizon $T_1$, 
-we consider forecast risk in the form of root mean squared error
+we consider forecast risk in the form of root mean squared error (RMSE),
 $$
-  R_T = \sqrt{\frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2}
+  R_T = \sqrt{\frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2},
 $$
@@
 
-\begin{figure}[H]
+\begin{figure}
   \begin{center}
@@
 
-In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus (COVID-19) recession.
+In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession.
 Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020.
 We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustment for the shock.
-The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool, and (4) nowcast.
-Section \ref{background} provides the justification for the first three steps.
+The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool, and (4) forecast.
+%Section \ref{background} provides the justification for the first three steps.
 Section \ref{results} discusses the result of our forecast.
 
-\subsection{Background}
-\label{background}
+%\subsection{Background}
+%\label{background}
 
@@
 In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
-We also consider previous OPEC oil supply shocks.
+We also consider previous OPEC oil supply shocks \citep{mensi2014opec}.
 We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models.
 Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}.
-
-\subsubsection*{(1) AR(1) model and Time window}
-
+In this analysis we make the following considerations:
+
+\begin{enumerate}
+\item[(1)] {\bf AR(1) model and time window}.
 We will use a simple AR(1) model to forecast Conoco Phillips stock price.
@@
 All the parameters are estimated using OLS.
-
-\subsubsection*{(2) Selection of covariates}
-
-We perform two lines of analyses with one incorporating the price of S\&P 500 index and one without to justify our choice of covariate.
-Since the stock price of a company implies its value provided the number of shares is unchanged, the price of S\&P 500 index in the recession can partially represent the overall status of the economy.
-Therefore, using the price of S\&P 500 index as the covariate can possibly improve the precision of the OLS estimates for shock-effects that are unique to Conoco Phillips.
-The rationale for inclusion of the price of S\&P 500 index is similar to that of market return in capital asset pricing model (CAPM).
-(\textbf{Need reference for the CAPM}.)
-
-\subsubsection*{(3) Construction of donor pool}
-
-Our donor pool will consist of Conoco Phillips shock effects observed after September 11th, 2001, %March 18th, 2008, 
+\item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
+\item[(3)] {\bf Construction of donor pool}. Our donor pool will consist of Conoco Phillips shock effects observed after September 11th, 2001, %March 18th, 2008, 
 several events in September, 2008, and November 27, 2014.
 The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}.
-The reasons for those three shocks are
+The reasons for those three shocks are:
   \begin{enumerate}
@@
 Moreover, trading was closed until September 17, 2001 \citep{johnston2006impact}.
-  %\item In heavy trading on Tuesday, March 18 \citep{shorter2008bear}
-  \item On September 8th, 2008, the United States announced its takeover of Fannie May and Freddie Mac \citep{UST}, and it was reported that the nation’s unemployment rate reached five-year highs.
-It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt \citep{lehman}.
+  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets.
+The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}.
+Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
   \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}.
@@
   \end{enumerate}
+\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
+\end{enumerate}
+
+%Since the stock price of a company implies its value provided the number of shares is unchanged, the price of S\&P 500 index in the recession can partially represent the overall status of the economy.
+Therefore, using the price of S\&P 500 index as the covariate can possibly improve the precision of the OLS estimates for shock-effects that are unique to Conoco Phillips.
+The rationale for inclusion of the price of S\&P 500 index is similar to that of market return in capital asset pricing model (CAPM).
+(\textbf{Need reference for the CAPM}.)
+
+% INTEREST RATES AND OIL RELATIONSHIP: This paper shows that in the short term both gold and crude oil prices positively influence each other.
+Interest rates have a negative influence on the future gold prices and a positive influence on the future crude oil prices.
+In the long run, a relationship exists whereby interest rates influence the US dollar, which in turn influences international crude oil prices.
+When the Federal Reserve Board (Fed) lowers interest rates to boost the economy, market expectations for oil demand change and, as a result, crude oil prices fluctuate \citep{wang2013dynamic}.
 
@@
 
-\subsection{Results}
-\label{results}
+%\subsection{Results}
+%\label{results}
+
+{\bf Jilei, can you add the weighted adjustment estimator to this analysis?}
+We estimate the five shock effects mentioned above using OLS and then construct $\hat{\alpha}_{\text{adj}}$ and $\hat{\alpha}_{\text{IVW}}$ from these estimates.
+We also consider estimation without the September 11th, 2001 shock effect since there was a week long delay in trading due to the terrorist attack.
+We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
+The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[height = 8cm]{CPtimeseries.png}
+    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. The blue line displays the }
+    \label{Fig:CP}
+  \end{center}  
+  \vspace{-.6cm}
+\end{figure}
+
+We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
+The unadjusted forecast had an RMSE of 12.24, 
+the use of $\hat{\alpha}_{\text{adj}}$ had an RMSE of 6.85,
+the use of $\hat{\alpha}_{\text{adj}}$ without September 11th had an RMSE of 5.96,
+the use of $\hat{\alpha}_{\text{IVW}}$ had an RMSE of 9.37,
+and the use of $\hat{\alpha}_{\text{IVW}}$ without September 11th had an RMSE of 6.15.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$ estimators for the demand and supply shock effects without September 11th has an RMSE of 0.80. 
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects without September 11th has an RMSE of 0.023.
+
+We also see that additive estimators do extremely well.
+However, these additive estimators are retrospective but their is some apriori justification for their use.
+\citet{kilian2009not} study the effect that different supply and demand shocks have on oil prices through a vector auto regressive model.
+Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.
+%This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.
 
@@
 Our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series.
-\citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
+%I AM NOT SURE HOW MUCH OF THE FOLLOWING IS NEEDED: \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
 This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$, where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$\footnote{for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$}; and the sampling stops when $N$ observations are reached.

### 2020-06-03 Rcode/sim.R
addition of simulation codes and tables and some alterations for the sim.R

@@ -170,7 +170,8 @@ ols.est.alphahat <- function(Tstar, Y, X) {
   names(est) <- c('adj', 'wadj', 'IVW')
   
   # output
-  return(list(alphahat = alphahat, est = est, Tstar = Tstar, X = X, Y = Y, lmod = lmod, res = res))
+  return(list(alphahat = alphahat, est = est, Tstar = Tstar, X = X, Y = Y, 
+              lmod = lmod, res = res, Wstar = W, se = se))
   
 }
 
@@ -248,18 +249,14 @@ for (i in 1:3) {
 }
 
 # experiment 
-Bs <- c(100, 1000, 10000)
-means <- matrix(0, nrow = 3, ncol = 3)
-vars <- matrix(0, nrow = 3, ncol = 3)
-for (i in 1:3) {
-  bootsamp <- boots(B = Bs[i], ols = ols)
-  for (j in 1:3) {
-    means[i, j] <- mean(bootsamp[[j]])
-    vars[i, j] <- var(bootsamp[[j]])
-  }
+# risk conditions
+means <- c()
+vars <- c()
+for (j in 1:3) {
+  means <- c(means, mean(bootsamp[[j]]))
+  vars <- c(vars, var(bootsamp[[j]]))
 }
-colnames(means) <- colnames(vars) <- c('adj', 'wadj', 'IVW')
-rownames(means) <- rownames(vars) <- c('B = 100', 'B = 1000', 'B = 10000')
+names(means) <- names(vars) <- c('adj', 'wadj', 'IVW')
 
 
 # risk-reduction conditions evaluation
@@ -269,15 +266,15 @@ risk.reduction <- function(means, vars) {
   rr.IVW <- (means['wadj']) ^ 2 - vars['IVW'] - (means['IVW'] - means['wadj']) ^ 2
   est <- c(rr.adj, rr.wadj, rr.IVW)
   names(est) <- c('adj', 'wadj', 'IVW')
-  return(list(usable = which(est > 0), best = which.max(est)))
+  return(list(usable = ifelse(est > 0, yes = 1, no = 0), best = which.max(est)))
 }
-risk.reduction(means = means[3,], vars = vars[3,])
+risk.reduction(means = means, vars = vars)
 # in this case adj is the best
 
 # nowcasting 
[…]

### 2020-06-03 Rcode/sim.study.R

@@ -1,0 +1,611 @@
+# OLS
+# this function returns the W^* estimated by synthetic control method (SCM)
+scm <- function(X, Tstar) {
+  # X is a list of covariates for disparate time series
+  # X[[1]] should be the covariate of the time series to predict
+  # X[[p]] for p = 2,...,n+1 are covariates for time series pool
+  
+  # T^* is a vector of shock-effects time points
+  # shock effect point must be > 2
+  
+  # package for constrained optiminization
+  require('Rsolnp')
+  
+  # number of time series for pool
+  n <- length(X) - 1
+  
+  # covariate for time series for prediction
+  X1 <- X[[1]][c(Tstar[1], Tstar[1] + 1), , drop = FALSE]
+  
+  # covariates for time series pool
+  X0 <- c()
+  for (i in 1:n) {
+    X0[[i]] <- X[[i + 1]][c(Tstar[i + 1], Tstar[i + 1] + 1), ,drop = FALSE]
+  }
+  
+  # objective function
+  weightedX0 <- function(W) {
+    # W is a vector of weight of the same length of X0
+    n <- length(W)
+    p <- ncol(X1)
+    XW <- matrix(0, nrow = 2, ncol = p)
+    for (i in 1:n) {
+      XW <- XW + W[i] * X0[[i]]
+    }
+    norm <- as.numeric(crossprod(matrix(X1 - XW)))
+    return(norm)
+  }
+  
+  # constraint for W
+  Wcons <- function(W) sum(W) - 1
+  
+  
+  # optimization
+  solnp(par = rep(1/n, n), fun = weightedX0, eqfun = Wcons, eqB = 0, 
+        LB = rep(0, n), UB = rep(1, n), control = list(trace = 0))
+}
+ols.est.alphahat <- function(Tstar, Y, X) {
+  
+  n <- length(Y) - 1
+  T <- c()
+  for (i in 1:(n + 1)) {
+    T <- c(T, length(Y[[i]]) - 1)
+  }
+  
+  # empty
+  alphahat <- c()
+  se <- c()
+  res <- c()
+  lmod <- c()
+  
+  
[…]

### 2020-06-03 manuscript/manuscript.tex
changed Figure 2; made edits discussed in meeting

@@
 \begin{align*}
-\t{\varepsilon}_{i} &\simiid  \normal{0}{\sigma^2_{\alpha}}, \qquad  i = 1, \ldots, n+1; \\
+\t{\varepsilon}_{i} &\simiid  \E{\t{\varepsilon}}=0, \var{\t{\varepsilon}}=\sigma^2_{\alpha}, \qquad i = 1, \ldots, n+1,\\
 \eta &\indep  \alpha_i \indep \phi \indep \theta \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
@@
 We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustment for the shock.
-The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool, and (4) forecast.
+The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool.
 %Section \ref{background} provides the justification for the first three steps.
@@
   \end{enumerate}
-\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
+%\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
 \end{enumerate}
@@
 We also consider estimation without the September 11th, 2001 shock effect since there was a week long delay in trading due to the terrorist attack.
-We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
-The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
 
@@
 and the use of $\hat{\alpha}_{\text{IVW}}$ without September 11th had an RMSE of 6.15.
+
+We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
+The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
 The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$ estimators for the demand and supply shock effects without September 11th has an RMSE of 0.80.
@@
 
-We also see that additive estimators do extremely well.
-However, these additive estimators are retrospective but their is some apriori justification for their use.
-\citet{kilian2009not} study the effect that different supply and demand shocks have on oil prices through a vector auto regressive model.
+These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect.
+There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.
+Our apriori justification comes from \citet{kilian2009not} who study the effect that different supply and demand shocks have on oil prices through a vector auto regressive model.
 Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.

### 2020-06-04 Rcode/sim.R
addition of non-parametric bootstrap in simulation

@@ -183,7 +183,7 @@ est <- ols.est.alphahat(Tstar = Tstar, Y = Y, X = X)$est
 ols <- ols.est.alphahat(Tstar = Tstar, Y = Y, X = X)
 
 # Bootstrap
-B <- 10000
+B <- 1000
 
 # function based on ols object
 boots <- function(B, ols) {
@@ -235,6 +235,60 @@ boots <- function(B, ols) {
   return(list(adj = alphahat.adj.B, wadj = alphahat.wadj.B, IVW = alphahat.IVW.B))
 }
 
+# function based on ols object
+boots.mix <- function(B, ols) {
+  # extract
+  est <- ols$est
+  res <- ols$res
+  Tstar <- ols$Tstar
+  Y <- ols$Y
+  X <- ols$X
+  lmod <- ols$lmod
+  p <- ncol(X[[1]])
+  n <- length(ols$Y) - 1
+  
+  alphahat.adj.B <- c()
+  alphahat.wadj.B <- c()
+  alphahat.IVW.B <- c()
+  
+  for (b in 1:B) {
+    Yb <- Xb <- Tstarb <- c();
+    Yb[[1]] <- Y[[1]]; Xb[[1]] <- X[[1]]; Tstarb <- Tstar[1]
+    pool <- sample(2:(n + 1), size = n, replace = TRUE)
+    for (i in 1:n) {
+      
+      # setup
+      index <- pool[i]
+      Ti <- length(Y[[index]]) - 1
+      resit <- base::sample(res[[index - 1]], replace = TRUE)
+      yitb <- Y[[index]][1]
+      Tstari <- Tstar[index]
+      lmodi <- lmod[[index - 1]]
+      xi <- X[[index]][-1,]
+      xilag <- X[[index]][-(Ti + 1), ]
+      
+      # parameter
+      etahati <- coef(lmodi)[1]
+      alphahati <- coef(lmodi)[2]
+      phihati <- coef(lmodi)[3]
+      thetahati <- coef(lmodi)[4:(4 + p - 1)]
+      betahati <- coef(lmodi)[(4 + p):(3 + 2 * p)]
+      
+      for (t in 1:Ti) {
+        yitb <- c(yitb, etahati + alphahati * ifelse(t == Tstari + 1, yes = 1, no = 0) +
[…]

### 2020-06-04 Rcode/sim.study.R

@@ -161,6 +161,62 @@ boots <- function(B, ols) {
   return(list(adj = alphahat.adj.B, wadj = alphahat.wadj.B, IVW = alphahat.IVW.B))
 }
 
+# function based on ols object
+boots.mix <- function(B, ols) {
+  # extract
+  est <- ols$est
+  res <- ols$res
+  Tstar <- ols$Tstar
+  Y <- ols$Y
+  X <- ols$X
+  lmod <- ols$lmod
+  p <- ncol(X[[1]])
+  n <- length(ols$Y) - 1
+  
+  alphahat.adj.B <- c()
+  alphahat.wadj.B <- c()
+  alphahat.IVW.B <- c()
+  
+  for (b in 1:B) {
+    Yb <- Xb <- Tstarb <- c();
+    Yb[[1]] <- Y[[1]]; Xb[[1]] <- X[[1]]; Tstarb <- Tstar[1]
+    pool <- sample(2:(n + 1), size = n, replace = TRUE)
+    for (i in 1:n) {
+      
+      # setup
+      index <- pool[i]
+      Ti <- length(Y[[index]]) - 1
+      coefitb <- coef(lmod[[index - 1]])
+      resit <- base::sample(res[[index - 1]], replace = TRUE)
+      yitb <- Y[[index]][1]
+      Tstari <- Tstar[index]
+      lmodi <- lmod[[index - 1]]
+      xi <- X[[index]][-1,]
+      xilag <- X[[index]][-(Ti + 1), ]
+      
+      # parameter
+      etahati <- coef(lmodi)[1]
+      alphahati <- coef(lmodi)[2]
+      phihati <- coef(lmodi)[3]
+      thetahati <- coef(lmodi)[4:(4 + p - 1)]
+      betahati <- coef(lmodi)[(4 + p):(3 + 2 * p)]
+      
+      for (t in 1:Ti) {
+        yitb <- c(yitb, etahati + alphahati * ifelse(t == Tstari + 1, yes = 1, no = 0) +
+                    phihati * yitb[t] + thetahati %*% xi[t, ] + betahati %*% xilag[t, ] + resit[t])
+      }
+      Yb[[i + 1]] <- yitb
+      Xb[[i + 1]] <- X[[index]]
+      Tstarb[[i + 1]] <- Tstari
+    }
+    olsb <- ols.est.alphahat(Tstar = Tstarb, Y = Yb, X = Xb)
[…]

### 2020-06-04 CP_2020.Rmd
updated data analysis; removed 911; added Bear Stearns

@@
 
-Our donor pool will consist of Conoco Phillips shock effects observed on September 11th, 2001, March 18th, 2008, many days in September and October of 2008, and November 27, 2014.
-The September 11th, 2001 and the 2008 shock effects were observed during recessions that were predicated by an inversion of the yield curve, and the November 27, 2014 shock was an OPEC induced supply side shock effect.
+Our donor pool will consist of Conoco Phillips shock effects observed on March 17th, 2008, many days in September and October of 2008, and November 27, 2014.
+The 2008 shock effects were observed during recessions that were predicated by an inversion of the yield curve, and the November 27, 2014 shock was an OPEC induced supply side shock effect.
 <!--Some other notable shock effects were not included in this analysis because the conditions preceding them are not simialar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects ([1987 Source](https://www.nber.org/chapters/c10958.pdf), [2011 Source](https://www.latimes.com/world/la-xpm-2011-aug-06-la-fi-us-debt-downgrade-20110806-story.html), [2015 Source](https://www.nytimes.com/2015/08/25/business/dealbook/daily-stock-market-activity.html)).
@@
 
-#### Tuesday, September 11, 2001
+#### Monday, March 17th, 2008
 
@@
 ```{r}
-## September 11th (no trading from T-F); 1 day nowcast
+## March 17th; 1 day nowcast
 COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% 
@@
 COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
-start <- which(COP_close$Date == "2001-09-10")
-start_day <- as.numeric(1:nrow(COP_close) == start + 1)
+start <- which(COP_close$Date == "2008-03-14")
+start_day <- as.numeric(1:nrow(COP_close) == start)
 COP_close <- COP_close %>% mutate(start_day = start_day)
-COP_close_small <- COP_close[(start-29):(start+1), ]
+COP_close_small <- COP_close[(start-30):start, ]
 COP_close_small[, 2:5] <- COP_close_small[, 2:5] * 
-  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
-m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
+  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
+m_COP_3_17 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                  data = COP_close_small)
-alpha_9_11 <- summary(m_COP_9_11)$coef[3,1:2] 
-alpha_9_11
+alpha_3_17 <- summary(m_COP_3_17)$coef[3,1:2] 
+alpha_3_17
 ```
@@
 ```{r}
-m_COP_9_11_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
-alpha_9_11_no <- summary(m_COP_9_11_no)$coef[3,1:2]
-alpha_9_11_no
+m_COP_3_17_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
+alpha_3_17_no <- summary(m_COP_3_17_no)$coef[3,1:2] 
+alpha_3_17_no
 ```
 
-#### 2008 shock effects
+#### 2008 September shock effects
 <!-- https://www.democracynow.org/2008/9/8/headlines -->
 
-The first 4 major shocks of 2008 were proceeded by unprecedented failures in the financial sector that rattled markets, oil prices, and Conoco Phillips stock alike.
+The first 3 major shocks in September, 2008 were proceeded by failures in the financial sector that rattled markets, oil prices, and Conoco Phillips stock alike.
 The September 12th and September 26th shock effects were proceeded by the bailouts or failures of Lehman Brothers and Washington Mutual financial institutions.
@@
 ```{r}
-a_estimates <- rbind( c(alpha_9_11, alpha_9_11_no),
+a_estimates <- rbind( c(alpha_3_17, alpha_3_17_no),
   cbind(alpha_Sept_08, alpha_Sept_08_no),
@@
 colnames(a_estimates) <- c("a_1","var_a_1","a_1_no","var_a_1_no")
-rownames(a_estimates) <- c("y2001","s8y2008","s12y2008","s26y2008","y2014")
+rownames(a_estimates) <- c("m2008","s8y2008","s12y2008","s26y2008","y2014")
 ```
 
-We now compute four shock effect estimators.
-We compute the adjustment estimator that averages the estimated shock effects and the inverse variance weighted adjustment estimator, these two estimators are computed with and without the September 11th, 2001 shock effect.
-We consider analyses without the September 11th, 2001 shock effect because the stock market was closed for the week following the terrorist attack, so immediate post shock data was not actually observed.
+We now compute shock effect estimators. We compute the adjustment estimator that averages the estimated shock effects and the inverse variance weighted adjustment estimator.
 
@@
 a_adj <- colMeans(a_estimates[, c(1,3)])
-a_adj_no911 <- colMeans(a_estimates[-1, c(1,3)])
 weights <- rbind(
@@
 a_adj_IVW <- colSums(weights * a_estimates[, c(1,3)])
-weights_no911 <- rbind(
-(1 / a_estimates[-1, c(2,4)])[1, ] / colSums(1 / a_estimates[-1, c(2,4)]),
-(1 / a_estimates[-1, c(2,4)])[2, ] / colSums(1 / a_estimates[-1, c(2,4)]),
-(1 / a_estimates[-1, c(2,4)])[3, ] / colSums(1 / a_estimates[-1, c(2,4)]),
-(1 / a_estimates[-1, c(2,4)])[4, ] / colSums(1 / a_estimates[-1, c(2,4)])
-)
-a_adj_IVW_no911 <- colSums(weights_no911 * a_estimates[-1, c(1,3)])
 ```
@@
 ```{r}
-shock_effects <- rbind(a_adj, a_adj_no911, 
-                       a_adj_IVW, a_adj_IVW_no911)
+shock_effects <- rbind(a_adj, a_adj_IVW)
 shock_effects
@@
 ## Additive adjustment
-additive <- colMeans(a_estimates[2:4, c(1,3)]) + a_estimates[4, c(1,3)]
+additive <- colMeans(a_estimates[1:4, c(1,3)]) + a_estimates[5, c(1,3)]
 additive
@@
 a_adj_IVW_additive <- colSums(weights_additive * a_estimates[1:4, c(1,3)])
-weights_no911_additive <- rbind(
-(1 / a_estimates[2:4, c(2,4)])[1, ] / colSums(1 / a_estimates[2:4, c(2,4)]),
-(1 / a_estimates[2:4, c(2,4)])[2, ] / colSums(1 / a_estimates[2:4, c(2,4)]),
-(1 / a_estimates[2:4, c(2,4)])[3, ] / colSums(1 / a_estimates[2:4, c(2,4)])
-)
-a_adj_IVW_no911_additive <- 
-  colSums(weights_no911_additive * a_estimates[2:4, c(1,3)])
 
@@
 additive_IVW_no
-
-## Additive IVW adjustment without 911
-additive_IVW_no911 <- as.numeric(a_adj_IVW_no911_additive[1] + a_estimates[5, 1])
-additive_IVW_no911
-
-## Additive IVW adjustment without 911 and covariates
-additive_IVW_no911_no <- as.numeric(a_adj_IVW_no911_additive[2] + a_estimates[5, 1])
-additive_IVW_no911_no
 ```
@@
 Yhat_adj_additive_IVW <- Yhat_nothing + additive_IVW
-Yhat_adj_additive_IVW_no911 <- Yhat_nothing + additive_IVW_no911
 
@@
 Yhat_adj_additive_IVW - COP_close_small$Y[nrow(COP_close_small)]
-Yhat_adj_additive_IVW_no911 - COP_close_small$Y[nrow(COP_close_small)]
 ```
+
+Here is a plot without additive adjustment estimators included:
 
@@
 mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
-             c(Yhat_adj, Yhat_adj_additive, Yhat_adj_additive_IVW_no911))
+             c(Yhat_adj))
 colnames(mat) <- c("id", "Yhat_adj")
@@
   geom_point() + 
-  geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:7) + 
+  geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:3) + 
   geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing), 
@@
             col = "blue") + 
-    annotate("text", x=1, y=seq(from = 47, to = 38,length.out=7), 
+    annotate("text", x=1, y=seq(from = 45, to = 40, length.out=3), 
+             label=c("no adjustment","mean adjustment","IVW adjustment"), 
+             hjust=0) + 
+    annotate("point", x = 0, y=seq(from = 45, to = 40, length.out=3), 
+             pch = c(16, 2:3),
+             color = c("blue","red","red")) +
+  theme_minimal()
+```
+
+Here is a plot with additive adjustment estimators included:
+
+```{r}
+COP_close_small$id <- 1:nrow(COP_close_small)
+mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
+             c(Yhat_adj, Yhat_adj_additive, Yhat_adj_additive_IVW))
+colnames(mat) <- c("id", "Yhat_adj")
+dat <- as.data.frame(mat)
+ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
+  labs(title = "Conoco Phillips forecasting", 
+       x = "Day", y = "Closing price (in USD)") +
+  geom_point() + 
+  geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:5) + 
+  geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing), 
+             aes(x = x, y = y), col = "blue", cex = 1.5) + 
+  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values, Yhat_nothing)), 
+            col = "blue") + 
+    annotate("text", x=1, y=seq(from = 47, to = 40,length.out=5), 
              label=c("no adjustment","mean adjustment",
-                     "mean adjustment (no 9/11)","IVW adjustment",
-                     "IVW adjustment (no 9/11)", "aggregate adjustment", 
+                     "IVW adjustment", "aggregate adjustment", 
                      "aggregate IVW adjustment"), 
              hjust=0) + 
-    annotate("point", x = 0, y=seq(from = 47, to = 38,length.out=7), 
-             pch = c(16,2:7),
-             color = c("blue","red","red","red","red","red","red")) +
+    annotate("point", x = 0, y=seq(from = 47, to = 40,length.out=5), 
+             pch = c(16,2:5),
+             color = c("blue","red","red","red","red")) +
   theme_minimal()
@@
 Yhat_adj_additive_IVW_no <- Yhat_nothing + additive_IVW_no
-Yhat_adj_additive_IVW_no911_no <- Yhat_nothing + additive_IVW_no911_no
 
@@
 Yhat_adj_additive_IVW_no - COP_close_small$Y[nrow(COP_close_small)]
-Yhat_adj_additive_IVW_no911_no - COP_close_small$Y[nrow(COP_close_small)]
 ```
@@
 mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
-             c(Yhat_adj,  Yhat_adj_additive_no, Yhat_adj_additive_IVW_no911_no))
+             c(Yhat_adj_no,  Yhat_adj_additive_no, Yhat_adj_additive_IVW_no))
 colnames(mat) <- c("id", "Yhat_adj")
@@
   geom_point(data = dat, aes(x = id, y = Yhat_adj), 
-                             col = 2, pch = 2:7) + 
+                             col = 2, pch = 2:5) + 
   geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing_no), 
@@
             col = "blue") +
-      annotate("text", x=1, y=seq(from = 47, to = 38,length.out=7), 
-             label=c("no adjustment","mean adjustment",
-                     "mean adjustment (no 9/11)","IVW adjustment",
-                     "IVW adjustment (no 9/11)", "aggregate adjustment",
-                     "aggregate IVW adjustment"), 
+      annotate("text", x=1, y=seq(from = 47, to = 40,length.out=5), 
+             label=c("no adjustment","mean adjustment","IVW adjustment",
+                     "aggregate adjustment","aggregate IVW adjustment"), 
              hjust=0) + 
-    annotate("point", x = 0, y=seq(from = 47, to = 38,length.out=7), 
-             pch = c(16,2:7),
-             color = c("blue","red","red","red","red","red","red")) +
+    annotate("point", x = 0, y=seq(from = 47, to = 40,length.out=5), 
+             pch = c(16,2:5),
+             color = c("blue","red","red","red","red")) +
   theme_minimal()

### 2020-06-06 manuscript/fig2.tex
updated data analysis, discussions, tables for parametric bootstrap

% Created by tikzDevice version 0.12.3 on 2020-06-05 08:57:46
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,361.35);
\begin{scope}
\path[clip] ( 31.71, 30.69) rectangle (500.39,338.69);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 53.81) --
	(500.39, 53.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71,151.88) --
	(500.39,151.88);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71,249.96) --
	(500.39,249.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] (121.74, 30.69) --
	(121.74,338.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (259.18, 30.69) --
	(259.18,338.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (396.62, 30.69) --
	(396.62,338.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,102.85) --
	(500.39,102.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,200.92) --
	(500.39,200.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,299.00) --
	(500.39,299.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 53.02, 30.69) --
	( 53.02,338.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (190.46, 30.69) --
	(190.46,338.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (327.90, 30.69) --
	(327.90,338.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (465.34, 30.69) --
	(465.34,338.69);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.76,324.69) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.50,309.20) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.25,310.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.99,303.80) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.74,307.73) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.48,293.41) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.23,290.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.97,264.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.71,287.03) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.46,283.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.20,279.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (217.95,278.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (231.69,286.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (245.43,296.64) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (259.18,287.42) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (272.92,285.46) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.67,282.32) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (300.41,291.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (314.16,288.01) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (327.90,283.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (341.64,263.49) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (355.39,238.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.13,212.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (382.88,172.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (396.62,185.42) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (410.37,193.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (424.11,182.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (437.85,195.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.60,178.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (465.34,155.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (479.09, 44.69) circle (  1.96);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.63) --
	(481.73, 87.05) --
	(476.44, 87.05) --
	(479.09, 91.63);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 91.18) -- (481.86, 91.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 88.41) -- (479.09, 93.96);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.20) -- (481.05, 90.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 90.12) -- (481.05, 86.20);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (479.09,141.49) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.76,313.70) --
	( 80.50,313.67) --
	( 94.25,302.10) --
	(107.99,304.27) --
	(121.74,297.06) --
	(135.48,299.42) --
	(149.23,290.97) --
	(162.97,283.99) --
	(176.71,258.33) --
	(190.46,290.13) --
	(204.20,281.01) --
	(217.95,276.50) --
	(231.69,274.52) --
	(245.43,289.86) --
	(259.18,300.87) --
	(272.92,286.25) --
	(286.67,282.81) --
	(300.41,276.99) --
	(314.16,288.22) --
	(327.90,280.06) --
	(341.64,273.21) --
	(355.39,252.42) --
	(369.13,229.35) --
	(382.88,199.60) --
	(396.62,163.01) --
	(410.37,175.15) --
	(424.11,190.38) --
	(437.85,181.33) --
	(451.60,180.97) --
	(465.34,175.47) --
	(479.09,141.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,148.08) {$\hat{y}_{1, T_1^* + 1}^{1}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,131.74) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm adj}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,115.39) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm IVW}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76, 99.04) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm wadj}$};

\path[fill=fillColor] ( 53.02,151.88) circle (  1.96);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,138.59) --
	( 55.66,134.01) --
	( 50.37,134.01) --
	( 53.02,138.59);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.24,119.19) -- ( 55.79,119.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,116.42) -- ( 53.02,121.97);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.05,100.88) -- ( 54.98,104.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.05,104.81) -- ( 54.98,100.88);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,361.35);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 99.81) {40};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,197.89) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,295.97) {60};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,361.35);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 53.02, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (190.46, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (327.90, 19.68) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (465.34, 19.68) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (266.05,  7.64) {Day};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,184.69) {Closing Stock price (in USD)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.32] at (266.05,346.76) {Conoco Phillips Stock Forecasting (2020--01--24 to 2020--03--09)};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-06-06 manuscript/manuscript.tex
updated data analysis, discussions, tables for parametric bootstrap

@@
 \usepackage{tikz}
+\usepackage{multirow}
 \usepackage[linesnumbered, ruled,vlined]{algorithm2e}
@@
 \begin{enumerate}
-  \item The synthetic intervention paper and comment are added in the introduction. Other parts haven't been revised.
-  \item SCM.R for SCM method and sim.R for simulation are added in Github.
-  \item Data analysis references are fixed. The structure is organized better.
+  \item Remark for non-uniqueness of $\mathbf{W}^*$ is added in Section \ref{properties}.
+  \item Generalizations are added in Section 6
+  \item Data analysis is updated with results of weighted adjustment estimators
+  \item Some preliminary setup of the simulation is added in Section 4.
 \end{enumerate}
@@
 %which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
-\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
+We stress that $\mathbf{W}^*$ may not be unique. \cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
 so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
@@
 
+\begin{remark}
+  In Section \ref{constructionofestimators}, we note that $\mathbf{W}^*$ may not be unique.
+However, Proposition \ref{proprisk} and \ref{propriskwadj2} will hold for  every $\hat{\alpha}_{\rm wadj}$ using  $\mathbf{W}^*$ that satisfies (\ref{SCM}).
+\end{remark}
+
 \subsection{Bootstrap for risk-reduction evaluation problems}
@@
 \citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.
-However, the pseudo time series generated by this procedure are not stationary.
-(\textbf{Is this necessary to state?
-There needs to be a rationale fro why this is not a problem.})
 
@@
 
+In this section, we provide experiments that vary across variance of $\alpha_i$, $y_{i,t}$, and donor pool size $n$ using two bootstrap techniques with one conditioned on the donor pool and one without.
+We implement our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
+We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers.
+It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
+Moreover, $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
+
 %In this section, we present the simulation for the parametric bootstrap procedure for AR(1) outlined in Section \ref{varbootstrap}.
@@
 \section{Forecasting Conoco Phillips stock in the presence of shocks}
-
+\label{forecasting}
 In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession.
@@
 %\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
+We assume that the five shocks are independent of the shock that Conoco Phillips  experienced on 2020-03-09.
 \end{enumerate}
@@
 
-{\bf Jilei, can you add the weighted adjustment estimator to this analysis?}
-We estimate the five shock effects mentioned above using OLS and then construct $\hat{\alpha}_{\text{adj}}$ and $\hat{\alpha}_{\text{IVW}}$ from these estimates.
-We also consider estimation without the September 11th, 2001 shock effect since there was a week long delay in trading due to the terrorist attack.
+\vspace{-.3cm}
+\begin{table}[H]
+  \caption{Some basic summary statistics of the covariates and response} \vspace{.4cm} \label{table1}
+  \begin{center}
+    \begin{tabular}{ccrrrrrr}
+       &    & \multicolumn{2}{c}{S\&P 500} & \multicolumn{2}{c}{WTI}  & \multicolumn{2}{c}{$y_{i,t}$} \\
+     Time series & $T_i^*+1$ & Mean & SD  &  Mean & SD  & Mean & SD  \\
+             \hline 
+2020 Mar.  &  03--09 & 3239.11 & 139.28 & 50.36 & 3.13 & 55.35 & 6.37 \\ 
+  2008 Mar.  & 03--17 & 1341.03 & 29.50 & 98.82 & 7.01 & 60.59 & 2.28 \\ 
+ \multirow{3}{*}{2008 Sep.}
+ & $T_3^* +1 = \text{09--08}$ & \multirow{3}{*}{1504.50}  & \multirow{3}{*}{43.44}  & \multirow{3}{*}{134.46} & \multirow{3}{*}{10.24} & \multirow{3}{*}{71.20}  & \multirow{3}{*}{4.11}  \\ 
+ & $T_4^* +1 = \text{09--12}$ \\
+   & $T_5^* +1 = \text{09--26}$ \\
+\\
+  2014 Nov.  & 11--27 & 2179.99 & 66.99 & 85.70 & 3.38 & 76.99 & 1.90 \\ 
+    \end{tabular}
+  \end{center}  \vspace{-.3cm}
+\end{table}
+
+Table \ref{table1} presents some basic summary statistics for the covaraites and response for the time series of interest (stock price of Conoco Phillips in 2020 March) and the donor pool.
+Note that there are three shock-effects nested in the time series 2008 September.
+This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool.
+Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.
+
+We computed 3 shock-effect estimates.
+Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$.
+For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
+\begin{align*}
+ \mathbf{W}^*= (0.000,0.000, 0.949, 0.000, 0.051) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 23.496.
+\end{align*}
+Note that the norm is computed using the $k$-dimensional Euclidean metric.
+Table \ref{table1} that contains some basic summary statistics for the units and range of the covariates can provide some information about the performance of the fit.
+The fit is acceptable.
+According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately.
+
+$\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (2008--09--08) and $\alpha_5$ (2014--11--27) according to the setup of $\mc{M}_2$.
+That is, the shock that Conoco Phillips experienced in 2020-03-09 is similar to the shock induced by the placement of Fannie May and Freddie Mac, and the one caused by oil supply shock on 2014--11--27.
+It is consistent with discussion at the beginning of the section.
+\begin{table}[H]
+  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
+  \begin{center}
+    \begin{tabular}{lrrr}
+      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
+      \hline 
+    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
+    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
+    Risk-reduction proposition & 1 & 1 & 1 \\
+    Best shock-effect estimator & 0 & 0 & 1
+    \end{tabular}
+  \end{center}  
+\end{table}
+\vspace{-.5cm}
+
+Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
+Note that this parametric bootstrap procedure is conditioned  on the  donor pool.
+Table \ref{table2} tells that all three proposed  shock-effect estimators are usable in the sense that the forecast employing them is better than the one without; and the $\hat{\alpha}_{\rm wadj}$ is the best in terms of the estimated risk-reduction quantity.
+Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
 
@@
   \begin{center}
-    \includegraphics[height = 8cm]{CPtimeseries.png}
-    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. The blue line displays the }
+    \includegraphics[height = 9cm]{fig2.pdf}
+    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price.}
     \label{Fig:CP}
@@
 
-We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
-The unadjusted forecast had an RMSE of 12.24, 
-the use of $\hat{\alpha}_{\text{adj}}$ had an RMSE of 6.85,
-the use of $\hat{\alpha}_{\text{adj}}$ without September 11th had an RMSE of 5.96,
-the use of $\hat{\alpha}_{\text{IVW}}$ had an RMSE of 9.37,
-and the use of $\hat{\alpha}_{\text{IVW}}$ without September 11th had an RMSE of 6.15.
+We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
+The unadjusted forecast has an RMSE of 9.870 whereas 
+the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of 4.475,  4.432, and 4.741, respectively.
+Therefore, results proposed by Table \ref{table2} are verified with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without, and that $\hat{\alpha}_{\rm wadj}$ is the best with lowest RMSE.
 
@@
 The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$ estimators for the demand and supply shock effects without September 11th has an RMSE of 0.80.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects without September 11th has an RMSE of 0.023.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects without September 11th have  RMSEs of $1.341$, $1.677$, and $0.661$, respectively.
 
@@
 
+Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models.
+First, the model can be extended to AR($p$) for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
+The model for $\alpha_i$ in $\mc{M}_2$ may be generalized to $\alpha_i = \mu_{\alpha} + \delta_i' \mathbf{x}_{i, T_i^*+1} + \cdots + \gamma_i \mathbf{x}_{i, T_i^* -(p+1)} + \tilde{\varepsilon}_{i}$ with some proper simple adjustments for SCM method.
+Second, multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent.
+This generalization was adopted in Section \ref{forecasting}.
+In this case, the variance expressions proposed in Section \ref{properties} will not work.
+However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
+Third, though it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions with existing first and second moments.
+Fourth, the covariates in the model for $\alpha_i$ in $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
+It is because in the derivation such dependence is not used.
+
 \section{Appendix}

### 2020-06-06 Rcode/dataanalysis.R

@@ -1,0 +1,480 @@
+# load packages
+library("data.table")
+library("tidyverse")
+library("tseries")
+library("quantmod")
+library('Rsolnp')
+library('msos')
+library('tikzDevice')
+library('xtable')
+
+## Conoco Phillips
+getSymbols('COP', from = "2000-01-01")
+COP <- as.data.frame(COP)
+COP <- COP %>% mutate(Date = rownames(COP))
+
+## S&P 500
+getSymbols('^GSPC', from = "1970-01-01")
+GSPC <- as.data.frame(GSPC)
+GSPC <- GSPC %>% mutate(Date = rownames(GSPC))
+
+## Brent Crude prices
+Brent_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/brent-daily_csv/data/d93216330ab2c27aae3d177b2f0f0921/brent-daily_csv.csv") %>%
+  rename(Oil_Close = Price)
+
+## WTI Crude prices
+WTI_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/wti-daily_csv/data/c414c9d375ec3c8f9d7c276d866fb2a4/wti-daily_csv.csv") %>%
+  rename(WTI_Close = Price)
+
+## inflation adjustment
+getSymbols("CPIAUCSL", src='FRED')
+avg.cpi <- apply.yearly(CPIAUCSL, mean)
+inflation_adj <- as.numeric(avg.cpi['2020'])/avg.cpi
+inflation_adj <- as.data.frame(inflation_adj)
+colnames(inflation_adj) <- c("dollars_2020")
+inflation_adj <- inflation_adj %>% mutate(year = 1947:2020)
+
+
+# Data Preparation
+COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% rename(COP_Close = COP.Close)
+GSPC_close <- GSPC %>% dplyr::select(GSPC.Close, Date) %>% rename(GSPC_Close = GSPC.Close)
+COP_close <- merge(COP_close, GSPC_close)
+COP_close <- merge(COP_close, WTI_Crude)
+
+# response
+Y <- COP_close$COP_Close[-1]
+
+# data frame
+COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
+
+# lagged covariates
+WTI_Close_lag1 <- COP_close$WTI_Close[-nrow(COP_close)]
+GSPC_Close_lag1 <- COP_close$GSPC_Close[-nrow(COP_close)]
+# re-input
[…]

### 2020-06-06 Rcode/sim.study.R

@@ -264,7 +264,7 @@ nowcast.alpha <- function(X, Y, Tstar, best = c('adj', 'wadj', 'IVW')) {
 sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma, 
                                     sigma.alpha, sigma.delta.gamma, 
                                     p, B, n, scale, np = c(TRUE, FALSE)) {
-  T <- sample(50:100, size = n + 1, replace = TRUE) # Time Length
+  T <- round(rgamma(n = n + 1, shape = 10, scale = 5)) # Time Length
   Tstar <- c() # Shock Time Points
   for (t in T) {
     Tstar <- c(Tstar, sample(3:(t - 1), size = 1))
@@ -384,7 +384,7 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
 sim.study.normal.normalX <- function(mu.gamma.delta, mu.alpha, sigma, 
                                      sigma.alpha, sigma.delta.gamma, 
                                      p, B, n, mean, sd, np = c(TRUE, FALSE)) {
-  T <- sample(50:100, size = n + 1, replace = TRUE) # Time Length
+  T <- round(rgamma(n = n + 1, shape = 10, scale = 5)) # Time Length
   Tstar <- c() # Shock Time Points
   for (t in T) {
     Tstar <- c(Tstar, sample(3:(t - 1), size = 1))
@@ -738,3 +738,76 @@ table <- cbind(table.bias, table.dist, table.consistency)
 require('xtable')
 xtable(table, digits = 3)
 
+
+
+
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+# 8 cores -- use 7
+ncores <- detectCores() - 1
+registerDoParallel(cores = ncores)
+set.seed(2020)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 200
+
+# parameter setup
+ns <- c(5, 10, 15, 25)
+sigma.delta.gamma.alphas <- c(0.01, 0.1, 1, 10)
+sim_params <- expand.grid(list(sigma.delta.gamma.alphas = sigma.delta.gamma.alphas, ns = ns))
+
+# simulation time
+system.time(
+  output <- lapply(1:nrow(sim_params), FUN = function(j) {
+    # parameters
+    sigma.delta.gamma.alpha <- sim_params[j, 1]
+    n <- sim_params[j, 2]
[…]

### 2020-06-07 manuscript/manuscript.tex
updated abstract and edits to RMSE

@@
   \item Literature review and introduction. Need more references, need to mention synthetic interventions in the introduction or the discussion.
-  \item Need to mention possible generalizations in the Discussion.
-  \item Need to add weighted adjustment estimator to the data analysis.
   \item Need to add simulations. 
-  \item Update abstract.
 \end{enumerate}
@@
   \item Some preliminary setup of the simulation is added in Section 4.
+  \item RMSE is changed to MSE.
+  \item Abstract is updated
 \end{enumerate}
@@
 \begin{abstract}
-    We develop a forecasting methodology for time series data that has 
-    undergone a shock. We still can provide credible forecasts for a time 
-    series in the presence of such systematic shocks by drawing from disparate 
+    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate 
     time series that have undergone similar shocks for which post-shock 
-    outcome data is recorded.  These disparate time series are assumed to have 
-    mechanistic similarities to the time series under study but are otherwise 
-    independent (Granger noncausal).  The inferential goal of our forecasting 
-    methodology is to supplement observed time series data with post-shock 
-    data from the disparate time series in order to minimize average forecast 
-    risk. 
+    outcome is recorded.
+Three shock-effects estimators were constructed for minimizing average forecast risk.
+We proposed conditions when our methodology works, and which estimator is the best in average forecast risk reduction.
+Parametric bootstrap procedures are provided for such realization.
+Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
 \end{abstract}
@@
 $\{\hat y_{1,t}, t= 1,2,\ldots\}$ given time horizon $T_1$, 
-we consider forecast risk in the form of root mean squared error (RMSE),
+we consider forecast risk in the form of  mean squared error (MSE),
 $$
-  R_T = \sqrt{\frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2},
+  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2,
 $$
-in our analyses. \textbf{Let's switch to root mean squared error, this metric is often used in forecasting articles.} In this article, we consider a dynamic panel data 
+in our analyses. In this article, we consider a dynamic panel data 
 model with autoregressive structure similar to that in \citet{blundell1998initial}. 
@@
 %\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
-We assume that the five shocks are independent of the shock that Conoco Phillips  experienced on 2020-03-09.
+We assume that the five shocks are independent of the shock that Conoco Phillips  experienced on 2020-03-09. The covariates and response of time series in the donor pool are adjusted for inflation.
 \end{enumerate}
@@
     Risk-reduction proposition & 1 & 1 & 1 \\
-    Best shock-effect estimator & 0 & 0 & 1
+    Best shock-effect estimator & 0 & 1 & 0
     \end{tabular}
@@
 
-Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
+Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
 Note that this parametric bootstrap procedure is conditioned  on the  donor pool.
@@
 We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
-The unadjusted forecast has an RMSE of 9.870 whereas 
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of 4.475,  4.432, and 4.741, respectively.
-Therefore, results proposed by Table \ref{table2} are verified with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without, and that $\hat{\alpha}_{\rm wadj}$ is the best with lowest RMSE.
+The unadjusted forecast has an MSE of 97.422 whereas 
+the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  MSE of 20.028,  19.647, and 22.477, respectively.
+Therefore, results proposed by Table \ref{table2} are verified with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without, and that $\hat{\alpha}_{\rm wadj}$ is the best with lowest MSE.
 
@@
 The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects without September 11th have  RMSEs of $1.341$, $1.677$, and $0.661$, respectively.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  MSEs of $1.797$, $2.812$, and $0.437$, respectively.
 
@@
 \section{Discussion}
+
+Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models.
+First, the model can be extended to AR($p$) for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
+The model for $\alpha_i$ in $\mc{M}_2$ may be generalized to $\alpha_i = \mu_{\alpha} + \delta_i' \mathbf{x}_{i, T_i^*+1} + \cdots + \gamma_i \mathbf{x}_{i, T_i^* -(p+1)} + \tilde{\varepsilon}_{i}$ with some proper simple adjustments for SCM method.
+
+Second, multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent.
+This generalization was adopted in Section \ref{forecasting}.
+In this case, the variance expressions proposed in Section \ref{properties} will not work.
+However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
+
+Third, though it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions with existing first and second moments.
+Fourth, the covariates in the model for $\alpha_i$ in $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
+It is because in the derivation such dependence is not used.
+Fifth, the metric used in construction of $\hat{\alpha}_{\rm wadj}$ may be replaced with other complete metrics.
 
@@
 
-Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models.
-First, the model can be extended to AR($p$) for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
-The model for $\alpha_i$ in $\mc{M}_2$ may be generalized to $\alpha_i = \mu_{\alpha} + \delta_i' \mathbf{x}_{i, T_i^*+1} + \cdots + \gamma_i \mathbf{x}_{i, T_i^* -(p+1)} + \tilde{\varepsilon}_{i}$ with some proper simple adjustments for SCM method.
-Second, multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent.
-This generalization was adopted in Section \ref{forecasting}.
-In this case, the variance expressions proposed in Section \ref{properties} will not work.
-However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
-Third, though it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions with existing first and second moments.
-Fourth, the covariates in the model for $\alpha_i$ in $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
-It is because in the derivation such dependence is not used.
-
 \section{Appendix}

### 2020-06-07 Rcode/dataanalysis.R

@@ -194,6 +194,8 @@ for (i in 1:5) {
 }
 
 # SCM
+
+# Euclidean metric
 # objective function
 weightedX0 <- function(W) {
   # W is a vector of weight of the same length of X0
@@ -220,6 +222,28 @@ weightedX0(round(outs$pars, digits = 3))
 # weighted adjustment estimator
 alpha_wadj <- sum(Wstar * estimates[,1])
  
+# Mahalanobis Distance metric
+Sigmahat <- cov(TS1[, c(3, 7, 4, 6)])
+weightedX0.M <- function(W) {
+  # W is a vector of weight of the same length of X0
+  n <- length(W)
+  p <- ncol(X1)
+  XW <- matrix(0, nrow = 2, ncol = p)
+  for (i in 1:n) {
+    XW <- XW + W[i] * X0[[i]]
+  }
+  norm <- as.numeric(matrix(X1 - XW, nrow = 1) %*% solve(Sigmahat) %*% matrix(X1 - XW))
+  return(norm)
+}
+# optimization
+outs.M <- solnp(par = rep(1/n, n), fun = weightedX0.M, eqfun = Wcons, eqB = 0, LB = rep(0, n), UB = rep(1, n))
+Wstar.M <- outs.M$pars
+# objective function
+sqrt(weightedX0.M(round(outs.M$pars, digits = 3)))
+# weighted adjustment estimator
+alpha_wadj.M <- sum(Wstar.M * estimates[,1])
+
+
 
 # Parametric Bootstrap Estimation
 
@@ -426,13 +450,13 @@ Yhat_additive <- c(alpha.adj.additive + Yhat_nothing, alpha.IVW.additive + Yhat_
                    alpha.wadj.additive + Yhat_nothing)
 
 ## doing nothing completely misses the mark
-Yhat_nothing - TS1$Y[nrow(TS1)]
+(Yhat_nothing - TS1$Y[nrow(TS1)]) ^ 2
 
 ## adjustment gets closer
-Yhat_adj - TS1$Y[nrow(TS1)]
+(Yhat_adj - TS1$Y[nrow(TS1)]) ^ 2
 
 ## additive effect does well
-Yhat_additive - TS1$Y[nrow(TS1)]
+(Yhat_additive - TS1$Y[nrow(TS1)]) ^ 2
 
 
 # plot data

### 2020-06-07 Rcode/sim.study.R

@@ -811,3 +811,47 @@ result[, c(11:16 + 2)]
 pred <- result[, -c(1:4 + 2, 11:16 + 2)]
 # xtable
 xtable(pred, digits = 3)
+
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+# 8 cores -- use 7
+ncores <- detectCores() - 1
+registerDoParallel(cores = ncores)
+set.seed(2020)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 200
+
+# parameter setup
+ns <- c(5, 10, 15, 25)
+sigma.delta.gamma.alphas <- c(0.01, 0.1, 1, 10)
+sim_params <- expand.grid(list(sigma.delta.gamma.alphas = sigma.delta.gamma.alphas, ns = ns))
+
+# simulation time
+system.time(
+  output <- lapply(1:nrow(sim_params), FUN = function(j) {
+    # parameters
+    sigma.delta.gamma.alpha <- sim_params[j, 1]
+    n <- sim_params[j, 2]
+    # %do% evaluates sequentially
+    # %dopar% evaluates in parallel
+    # .combine results
+    out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+      # result
+      study <- sim.study.normal.gammaX(mu.gamma.delta = 2, 
+                                       mu.alpha = 10, sigma = 1, 
+                                       sigma.alpha = sigma.delta.gamma.alpha,
+                                       sigma.delta.gamma = sigma.delta.gamma.alpha, 
+                                       p = 2, B = 500, scale = 10, 
+                                       n = n, np = TRUE)
+      result <- c(study$bias, study$dist, study$consistency, study$rmse)
+      return(result)
+    }
+    # return results
+    out
+  })
+)
+

### 2020-06-07 manuscript/manuscript.tex
additional explanation to data analysis results with COVID-19

@@
 
+However, from another perspective, this phenomenon can be explained by the fact that the donor pool is not constructed to be similar enough to the time series of interest.
+The shock on 2020-03-09 occurred with the pandemic caused by  COVID-19.
+It is difficult to find available stock market time series data that were generated under a similar setting.
+
 \section{Discussion}

### 2020-06-07 manuscript/manuscript.tex
some edit at the end of introduction

@@
 From a machine learning perspective, \citet{agarwal2020two} proposed a model-free synthetic intervention  method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
-Among those methodologies, they share the implicit assumption that candidates  from donor pool should be similar.
-In other words, caution should be dedicated to the construction of donor pool; otherwise, the result will be expected not to be  robust to the noise introduced by the insimilar ones.
-\emph{\textcolor{red}{More to be added ...}}
 
@@
 
-\textbf{Need more of a transition to what we do here and why it is good.}
-We develop and compare aggregation techniques in this post-shock setting and investigate settings for when they do and do not decrease mean squared prediction error.
+Up to the scale of the shock, it is very unlikely that the above mentioned  statistical models or machine learning methods will work ideally since they are trained on the time series data that do not experience such a shock.
+To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration.
 We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure.
-The main idea is to first average the estimated shock effects from the disparate time series and then add the averaged estimated shock effect to the present forecast.
-When these time series are independent and the mean of shock effect distribution is large relative to its variance then this technique will reduce mean squared prediction error under the assumed model.
-Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock-effect of the time series under study.
+The main idea is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, to the original forecast at the known shock time point.
+
 We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting.
 The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-
-\vspace*{0.25cm}\textbf{Need to discuss our example and our simulation results.}
+We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three.
+The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap.
+Our simulation results show that  bootstrap estimation and the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
+In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020-03-09, the proposed three aggregation techniques work decently well.
+We now motivate our aggregation techniques.
+
+% Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock-effect of the time series under study.
 
@@
 
+For the use of our methodologies, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the unsimilar ones.
+
 \section{Appendix}

### 2020-06-07 manuscript/manuscript.tex
some edit at the end of introduction
addition of parametric and non-parametric bootstrap result

@@
   \item Abstract is updated
+  \item Edit the end of the introduction
 \end{enumerate}
@@
 Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models.
+
 First, the model can be extended to AR($p$) for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
@@
 
-Our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series.
-%I AM NOT SURE HOW MUCH OF THE FOLLOWING IS NEEDED: \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
-This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$, where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$\footnote{for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$}; and the sampling stops when $N$ observations are reached.
-Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d.
+Sixth, our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series.
+The pseudo-time series generated by parametric bootstrap is not stationary.
+Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
+This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$\footnote{The collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d.
 discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d.
-geometric random variables with parameter $p$.
+geometric random variables with parameter $p$.}, where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$\footnote{For $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$.}; and the sampling stops when $N$ observations are reached.
 However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}.
@@
 
-For the use of our methodologies, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the unsimilar ones.
+For the use of our methodology, caution should be dedicated to the construction of donor pool.
+Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest.
 

### 2020-06-08 manuscript/manuscript.tex
corrected R codes for simulation and updated manuscript for simulation

@@
 
-\textbf{I think that our bootstrap procedure should first sample the disparate time series without replacement, and then estimate the parameters in each resampled time series.}
-The formal steps of our bootstrap procedures are outlined in the Supplementary Materials, the intuition for our procedure is as follows: let $B$ be the bootstrap sample size and initialize $y_{i,0}$ for all $i = 2,\ldots,n+1$.
-At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i = 2,\ldots,n+1$.
+To specify, there are two possible parametric bootstrap procedures for our methods, one conditioned on donor pool and the other  without.
+We first illustrate the simpler parametric bootstrap conditioned on the donor pool.
+The formal steps of it are outlined in the Supplementary Materials, the intuition for our procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool.
+initialize $y_{i,0}$ for all $i \in I$.
+At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$.
 Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$.
@@
 
+The parametric bootstrap without conditioning on the donor pool differs from the one with in the step that the former performs a non-parametric bootstrap by sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^*$.
+Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^*$.
+
 Let 
 $
-  \overline{\hat{\alpha}_{\mrm{aadj}}} 
+  \overline{\hat{\alpha}_{\mrm{adj}}} 
     = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
@@
 
-We stress that the above approximation is conditioned on $\Theta$ and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
+We stress that the above approximation is conditioned on $\Theta$ and the donor pool, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
 %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population.
 For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$.
+For parametric bootstrap without conditioning on the donor pool but conditioned on $\Theta$, we stress that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold.
 Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.
@@
 
-\subsection{Parametric bootstrap simulation}
-\label{parametricbootstrapsimulation}
-
-In this section, we provide experiments that vary across variance of $\alpha_i$, $y_{i,t}$, and donor pool size $n$ using two bootstrap techniques with one conditioned on the donor pool and one without.
+In this section, we provide justification for our methods based on simulation examples.
 We implement our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
+$\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
 We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers.
 It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
-Moreover, $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
+Moreover, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
+We consider $p=2$ and $\mu_{\alpha}=10$.
+In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\gamma}$ and $\sigma_{\delta}$ in the model $\delta_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\delta}\mathbf{I}_p}$, and $\gamma_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\gamma}\mathbf{I}_p}$.
+
+\subsection{Parametric bootstrap simulation for risk-reduction propositions}
+\label{parametricbootstrapsimulation}
+
+In this section, we provide justification for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}).
+We will compare the result of using parametric bootstrap conditioned on the donor pool with the one without using the parameter setup discussed in Section \ref{simulation}.
+
+Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions.
+We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation.
+Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise.
+Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table.
+\begin{center}
+  \begin{center}
+      \begin{tabular}{cc|c|c}
+        \hline
+        & & \multicolumn{2}{c}{Decision} \\
+        & & Accept $\hat{\alpha}$ & Reject $\hat{\alpha}$ \\ 
+                \hline
+     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
+      \cline{3-4}
+      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
+      \hline
+      \end{tabular}
+  \end{center}
+\end{center}
+We report 1 for risk-reduction propositions to be consistent and 0 otherwise.
+
+\subsection{Simulation for prediction}
+
+In this section, we report prediction results for our methods in the simulation.
+Specifically, we are interested in the distance between $\alpha_1$ and our shock-effect estimators, and the distance between $y_{1,T_1^*+1}$ and $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$.
 
@@
 Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest.
+We recommend using parametric bootstrap without conditioning on the donor pool when the donor pool size $n$ is large, and the one conditioned on the donor pool when $n$ is small.
 

### 2020-06-08 Rcode/sim.study.R

@@ -292,12 +292,14 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   }
   
   # E(alpha1)
-  Ealpha1 <- mu.alpha + delta[[1]] %*% X[[1]][Tstar[1] + 1, ] + gamma[[1]] %*% X[[1]][Tstar[1], ]
+  Ealpha1 <- mu.alpha + matrix(mu.gamma.delta, nrow = 1, ncol = p) %*% X[[1]][Tstar[1] + 1, ] + 
+    matrix(mu.gamma.delta, nrow = 1, ncol = p) %*% X[[1]][Tstar[1], ]
   
   # E(alpha_adj)
   alphas.2.np1 <- c()
   for (i in 2:(n + 1)) {
-    alphas.2.np1 <- c(alphas.2.np1, mu.alpha + delta[[i]] %*% X[[i]][Tstar[i] + 1, ] + gamma[[i]] %*% X[[i]][Tstar[i], ])
+    alphas.2.np1 <- c(alphas.2.np1, mu.alpha + matrix(mu.gamma.delta, nrow = 1, ncol = p) %*% X[[i]][Tstar[i] + 1, ] + 
+                        matrix(mu.gamma.delta, nrow = 1, ncol = p) %*% X[[i]][Tstar[i], ])
   }
   Ealpha.adj <- mean(alphas.2.np1)
   
@@ -363,6 +365,7 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   # yhats
   yhat2s <- sapply(c('adj', 'wadj', 'IVW'), function(d) nowcast.alpha(X = X, Y = Y, Tstar = Tstar, best = d)[[1]])
   yhat1 <- nowcast.alpha(X = X, Y = Y, Tstar = Tstar, best = 'wadj')[[2]]
+  names(yhat1) <- 'no'
   names(yhat2s) <- c('adj', 'wadj', 'IVW')
   
   # comparison
@@ -373,10 +376,10 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   consistency <- ifelse(truth == guess, yes = 1, no = 0)
   
   # risk
-  rmse <- sqrt(abs(Y[[1]][Tstar[1] + 2] - yhat2s) ^ 2)
+  rmse <- sqrt(abs(Y[[1]][Tstar[1] + 2] - c(yhat1, yhat2s)) ^ 2)
   
   # output
[…]

### 2020-06-08 Rcode/sim.study.R
one minor change to sim.study.R

@@ -686,7 +686,7 @@ system.time(
                                        sigma.delta.gamma = sigma.delta.gamma.alpha, 
                                        p = 2, B = 500, scale = 10, 
                                        n = n, np = FALSE)
-      result <- c(study$bias, study$dist, study$consistency, study$rmse)
+      result <- c(study$bias, study$dist, study$guess, study$consistency, study$rmse)
       return(result)
     }
   # return results
@@ -757,7 +757,7 @@ system.time(
                                        sigma.delta.gamma = sigma.delta.gamma.alpha, 
                                        p = 2, B = 500, scale = 10, 
                                        n = n, np = TRUE)
-      result <- c(study$bias, study$dist, study$consistency, study$rmse)
+      result <- c(study$bias, study$dist, study$guess, study$consistency, study$rmse)
       return(result)
     }
     # return results

### 2020-06-09 manuscript/manuscript.tex
made a round of updates to the manuscript

@@
 % title
-\title{Minimizing post shock forecasting error using disparate information}
+\title{Minimizing post-shock forecasting error using disparate information}
 \author{Jilei Lin\thanks{jileil2@ilinois.edu}}
@@
 \begin{abstract}
-    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate 
-    time series that have undergone similar shocks for which post-shock 
-    outcome is recorded.
+    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded.
 Three shock-effects estimators were constructed for minimizing average forecast risk.
 We proposed conditions when our methodology works, and which estimator is the best in average forecast risk reduction.
-Parametric bootstrap procedures are provided for such realization.
+Bootstrap procedures are provided to estimate the variability of our shock effect estimators and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed.
 Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
@@
 However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
-From a machine learning perspective, \citet{agarwal2020two} proposed a model-free synthetic intervention  method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
+%From a machine learning perspective,
+\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
+They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
 
@@
 
-We will suppose that an analyst has time series data ($y_{i,t}$,$\x_{i,t}$), 
-$t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a 
-scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to 
-the analyst prior to the observation of $y_{1,t}$.  Suppose that the analyst 
-is interested in forecasting $y_{1,t}$, the first time series in the 
-collection.
+We will suppose that an analyst has time series data ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
+Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection.
 %$y_1, y_2, \ldots$.  
@@
 %revealed prior to the observation of $y_{1,t}$.
-To gauge the performance of a procedure that produces forecasts 
-$\{\hat y_{1,t}, t= 1,2,\ldots\}$ given time horizon $T_1$, 
-we consider forecast risk in the form of  mean squared error (MSE),
+
+We will suppose that specific interest is in forecasts to made after the occurrence of a structural shock.
+To gauge the performance of forecasts, we consider forecast risk in the form of mean squared error (MSE),
 $$
@@
 $$
-in our analyses. In this article, we consider a dynamic panel data 
-model with autoregressive structure similar to that in \citet{blundell1998initial}. 
-%without past time period covariate 
-%information and with a single present time covariate.  
-Our dynamic panel model includes an additional shock effect whose presence 
-or absence is given by the binary variable $D_{i,t}$, the details of this model 
-are in the next section.
+and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.
+
+%The forecast consists of three steps: (1) pick a model, (2) selection of covariates, (3) choices of donor pool.
+Our post-shock prediction methodology will consist of selecting covariates $x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$.
+In this article, we consider a dynamic panel data model with autoregressive structure similar to that in \citet{blundell1998initial}.
+Our dynamic panel model includes an additional shock effect whose presence or absence is given by the binary variable $D_{i,t}$, and we will assume that the donor pool time series are independent of the time series under study.
+The details of this model are in the next section.
 
@@
 \beta_i &\simiid \beta, \where \E{\beta}=\mu_{\beta}, \var{\beta}=\Sigma_{\beta}^2, \qquad i = 1, \ldots, n+1,\\
+\alpha_i &\simiid \alpha, \where \E{\alpha}=\mu_{\alpha}, \var{\alpha}=\sigma_{\alpha}^2, \qquad  i = 1, \ldots, n+1; \\
 \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2}, \qquad t=1, \ldots, T_i, \; i = 1, \ldots, n+1,\\
-\alpha_i &\simiid  \normal{\mu_{\alpha}}{\sigma^2_{\alpha}}, \qquad  i = 1, \ldots, n+1; \\
 \eta &\indep  \alpha_i \indep \phi \indep \theta \indep \varepsilon_{i,t}.
@@
 
-In this section, we present a bootstrap procedure 
-%(see Section \ref{modelsetup}) 
-that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice.
+In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice.
 Our procedure involves the resampling of residuals in the separate OLS fits.
@@
 
-To specify, there are two possible parametric bootstrap procedures for our methods, one conditioned on donor pool and the other  without.
-We first illustrate the simpler parametric bootstrap conditioned on the donor pool.
-The formal steps of it are outlined in the Supplementary Materials, the intuition for our procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool.
+To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement and the other without any resampling of the donor pool.
+We first illustrate the simple bootstrap without resampling the donor pool.
+The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool.
 initialize $y_{i,0}$ for all $i \in I$.
@@
 
-The parametric bootstrap without conditioning on the donor pool differs from the one with in the step that the former performs a non-parametric bootstrap by sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^*$.
+The bootstrap based on resampling the donor pool with replacement is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^*$.
 Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^*$.
+Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$.
+When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however, if the constraints used to obtain $\mathbf{W}^*$ are binding then our bootstrap procedure needs to be modified \citep{li2019statistical}.
+The subsampling method in Section 4 of \citet{li2019statistical} can be adapted to our post-shock setting when the constraints are binding.
 
@@
 
-\subsection{Parametric bootstrap simulation for risk-reduction propositions}
+\subsection{Bootstrap simulation for risk-reduction propositions}
 \label{parametricbootstrapsimulation}
@@
         & & \multicolumn{2}{c}{Decision} \\
-        & & Accept $\hat{\alpha}$ & Reject $\hat{\alpha}$ \\ 
+        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
                 \hline
@@
 In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession.
-Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020.
-We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustment for the shock.
-The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool.
+Specific interest is in predictions made after March 6, 2020, the Friday before the stock market crash on March 9, 2020.
+We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustments for the shock.
 %Section \ref{background} provides the justification for the first three steps.
@@
 \item[(1)] {\bf AR(1) model and time window}.
-We will use a simple AR(1) model to forecast Conoco Phillips stock price.
-This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months \citep{alquist2013forecasting}.
+We will use an AR(1) model to forecast Conoco Phillips stock price.
+This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.
 We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window.
@@
 \item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
-\item[(3)] {\bf Construction of donor pool}. Our donor pool will consist of Conoco Phillips shock effects observed after September 11th, 2001, %March 18th, 2008, 
-several events in September, 2008, and November 27, 2014.
+\item[(3)] {\bf Construction of donor pool}.
+Our donor pool will consist of Conoco Phillips shock effects observed on March 14, 2008, several events in September, 2008, and November 27, 2014.
 The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}.
@@
   \begin{enumerate}
-  \item On September 11th, 2001, Islamic extremist al-Qaeda committed a series of terrorist attacks against the United States of America \citep{braniff2011towards}.
-In addition to the tragic loss of life, this triggered negative repercussions on the U.S.
-and world economies with falling stock prices and a falling U.S.
-dollar \citep{floyd2001terror}.
-Moreover, trading was closed until September 17, 2001 \citep{johnston2006impact}.
+  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities.
+On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank.
+The day of the announcement, the stocks of other major Wall Street firms tumbled (including Conoco Phillips).
+These concerns then spilled over into the broader universe of stocks \citep{shorter2008bear}.
+%In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
   \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets.
@@
 %\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
-We assume that the five shocks are independent of the shock that Conoco Phillips  experienced on 2020-03-09. The covariates and response of time series in the donor pool are adjusted for inflation.
 \end{enumerate}
@@
 
-%Some other notable shock effects were not included in this analysis because the conditions preceding them are not similar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects \citep{shiller1988portfolio, latimes, nytimes}.
-
 %\subsection{Results}
@@
 
-\vspace{-.3cm}
-\begin{table}[H]
-  \caption{Some basic summary statistics of the covariates and response} \vspace{.4cm} \label{table1}
-  \begin{center}
-    \begin{tabular}{ccrrrrrr}
-       &    & \multicolumn{2}{c}{S\&P 500} & \multicolumn{2}{c}{WTI}  & \multicolumn{2}{c}{$y_{i,t}$} \\
-     Time series & $T_i^*+1$ & Mean & SD  &  Mean & SD  & Mean & SD  \\
-             \hline 
-2020 Mar.  &  03--09 & 3239.11 & 139.28 & 50.36 & 3.13 & 55.35 & 6.37 \\ 
-  2008 Mar.  & 03--17 & 1341.03 & 29.50 & 98.82 & 7.01 & 60.59 & 2.28 \\ 
- \multirow{3}{*}{2008 Sep.}
- & $T_3^* +1 = \text{09--08}$ & \multirow{3}{*}{1504.50}  & \multirow{3}{*}{43.44}  & \multirow{3}{*}{134.46} & \multirow{3}{*}{10.24} & \multirow{3}{*}{71.20}  & \multirow{3}{*}{4.11}  \\ 
- & $T_4^* +1 = \text{09--12}$ \\
-   & $T_5^* +1 = \text{09--26}$ \\
-\\
-  2014 Nov.  & 11--27 & 2179.99 & 66.99 & 85.70 & 3.38 & 76.99 & 1.90 \\ 
-    \end{tabular}
-  \end{center}  \vspace{-.3cm}
-\end{table}
-
-Table \ref{table1} presents some basic summary statistics for the covaraites and response for the time series of interest (stock price of Conoco Phillips in 2020 March) and the donor pool.
-Note that there are three shock-effects nested in the time series 2008 September.
-This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool.
-Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.
-
+%\vspace{-.3cm}
+%\begin{table}[H]
+%  \caption{Some basic summary statistics of the covariates and response} \vspace{.4cm} \label{table1}
+%  \begin{center}
+%    \begin{tabular}{ccrrrrrr}
+%       &    & \multicolumn{2}{c}{S\&P 500} & \multicolumn{2}{c}{WTI}  & \multicolumn{2}{c}{$y_{i,t}$} \\
+%     Time series & $T_i^*+1$ & Mean & SD  &  Mean & SD  & Mean & SD  \\
+%             \hline 
+%2020 Mar.  &  03--09 & 3239.11 & 139.28 & 50.36 & 3.13 & 55.35 & 6.37 \\ 
+%  2008 Mar.  & 03--14 & 1341.03 & 29.50 & 98.82 & 7.01 & 60.59 & 2.28 \\ 
+% \multirow{3}{*}{2008 Sep.}
+% & $T_3^* +1 = \text{09--08}$ & \multirow{3}{*}{1504.50}  & \multirow{3}{*}{43.44}  & \multirow{3}{*}{134.46} & \multirow{3}{*}{10.24} & \multirow{3}{*}{71.20}  & \multirow{3}{*}{4.11}  \\ 
+% & $T_4^* +1 = \text{09--12}$ \\
+%   & $T_5^* +1 = \text{09--26}$ \\
+%\\
+%  2014 Nov.  & 11--27 & 2179.99 & 66.99 & 85.70 & 3.38 & 76.99 & 1.90 \\ 
+%    \end{tabular}
+%  \end{center}  \vspace{-.3cm}
+%\end{table}
+
+%Table \ref{table1} presents some basic summary statistics for the covariates and response for the time series of interest (stock price of Conoco Phillips in 2020 March) and the donor pool.
+
+We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020.
+The covariates and response of time series in the donor pool are adjusted for inflation.
+Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent.
 We computed 3 shock-effect estimates.
@@
 Note that the norm is computed using the $k$-dimensional Euclidean metric.
-Table \ref{table1} that contains some basic summary statistics for the units and range of the covariates can provide some information about the performance of the fit.
 The fit is acceptable.
 According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately.
-
-$\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (2008--09--08) and $\alpha_5$ (2014--11--27) according to the setup of $\mc{M}_2$.
-That is, the shock that Conoco Phillips experienced in 2020-03-09 is similar to the shock induced by the placement of Fannie May and Freddie Mac, and the one caused by oil supply shock on 2014--11--27.
-It is consistent with discussion at the beginning of the section.
+The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (September 8, 2008) and $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.
+
 \begin{table}[H]
@@
     Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
-    Risk-reduction proposition & 1 & 1 & 1 \\
-    Best shock-effect estimator & 0 & 1 & 0
+    Risk-reduction proposition & 1 & 1 & 1
+%    Best shock-effect estimator & 0 & 1 & 0
     \end{tabular}
@@
 We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
-The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
+The supply shock donor pool consists of the November 27, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
 The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  MSEs of $1.797$, $2.812$, and $0.437$, respectively.
-
 These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect.
@@
 However, from another perspective, this phenomenon can be explained by the fact that the donor pool is not constructed to be similar enough to the time series of interest.
-The shock on 2020-03-09 occurred with the pandemic caused by  COVID-19.
+The shock(s) on March 9, 2020 in the midst of the COVID-19 pandemic and oil production volatility.
 It is difficult to find available stock market time series data that were generated under a similar setting.
@@
 Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models.
-
-First, the model can be extended to AR($p$) for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
-The model for $\alpha_i$ in $\mc{M}_2$ may be generalized to $\alpha_i = \mu_{\alpha} + \delta_i' \mathbf{x}_{i, T_i^*+1} + \cdots + \gamma_i \mathbf{x}_{i, T_i^* -(p+1)} + \tilde{\varepsilon}_{i}$ with some proper simple adjustments for SCM method.
-
-Second, multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent.
-This generalization was adopted in Section \ref{forecasting}.
+Our simple AR(1) model can be extended to AR($p$) settings %for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
+Similarly, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors.
+Moreover, the functional form for the mean function can be extended beyond the linear regression model under $\mc{M}_2$.
+Multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent.
+As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
+%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool.
+%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.
+%This generalization was adopted in Section \ref{forecasting}.
 In this case, the variance expressions proposed in Section \ref{properties} will not work.
 However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
-
-Third, though it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions with existing first and second moments.
-Fourth, the covariates in the model for $\alpha_i$ in $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
-It is because in the derivation such dependence is not used.
-Fifth, the metric used in construction of $\hat{\alpha}_{\rm wadj}$ may be replaced with other complete metrics.
-
-Sixth, our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series.
+Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions with existing first and second moments.
+The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
+We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts.
+An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.
+
+Our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series.
 The pseudo-time series generated by parametric bootstrap is not stationary.
@@
 It is up to the user in selecting which procedure to choose but under different assumptions on the time-series.
+\textbf{Include footnotes in main text; also use either time series or time-series but not both}.
 

### 2020-06-09 manuscript/fig2.tex
addition of more references to introduction, error fixing in dataanalysis. R(not adjust for inflation for 2008-Sep time series), and other updates in the manuscript (see 1st page)

@@
-% Created by tikzDevice version 0.12.3 on 2020-06-05 08:57:46
+% Created by tikzDevice version 0.12.3 on 2020-06-09 17:22:19
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.63) --
-	(481.73, 87.05) --
-	(476.44, 87.05) --
-	(479.09, 91.63);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.16) --
+	(481.73, 86.58) --
+	(476.44, 86.58) --
+	(479.09, 91.16);
 \definecolor{drawColor}{RGB}{0,191,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 91.18) -- (481.86, 91.18);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 87.98) -- (481.86, 87.98);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 88.41) -- (479.09, 93.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.20) -- (479.09, 90.75);
 \definecolor{drawColor}{RGB}{238,99,99}

### 2020-06-09 manuscript/manuscript.tex
addition of more references to introduction, error fixing in dataanalysis. R(not adjust for inflation for 2008-Sep time series), and other updates in the manuscript (see 1st page)

@@
 \begin{enumerate}
-  \item Literature review and introduction. Need more references, need to mention synthetic interventions in the introduction or the discussion.
   \item Need to add simulations. 
@@
 \begin{enumerate}
-  \item Remark for non-uniqueness of $\mathbf{W}^*$ is added in Section \ref{properties}.
-  \item Generalizations are added in Section 6
-  \item Data analysis is updated with results of weighted adjustment estimators
-  \item Some preliminary setup of the simulation is added in Section 4.
-  \item RMSE is changed to MSE.
-  \item Abstract is updated
-  \item Edit the end of the introduction
+  \item Proposition for uniqueness of $\mathbf{W}^*$ is added.
+  \item Introduction is revised with additional references.
+  \item Data analysis is revised by fixing previous coding error.
+  \item Simulation description is updated.
+  \item Discussion is revised according to comments.
 \end{enumerate}
@@
 %\textbf{Integrate this paragraph into the next paragraph.}
-\textbf{The following list of methods needs to fall in the forecast combination literature, not the time series pooling literature}.
-In this setting there are a plethora of methods for combining forecasts, e.g., (1) model averaging \citep{newbold2002forecast, timmermann2006forecast, hansen2008least}, (2) model selection \citep{lee2015model, greenaway2020multistep}, (3) time-series pooling \citep{mundlak1978pooling, zellner1991forecasting, lee2020estimation, plessen2020integrated}.
-Model averaging typically selects weights for models based on minimizing various loss functions whereas model selection chooses the model through minimization of those loss functions, see for example, \citet{fosten2019panel} \textbf{I do not think that this reference belongs here}.
-Classical forecast combination may fail when forecasting in the presence of structural shocks.
+In this setting there are a plethora of methods for combining forecasts, e.g., model averaging \citep{newbold2002forecast, hendry2004pooling, koop2004forecasting, timmermann2006forecast, eklund2007forecast, hansen2008least}, model selection \citep{swanson1997model, swanson2001choosing, lee2015model}, and other various methods \citep{pesaran2011forecast,li2014forecasting}.
+Forecast encompassing methods are developed to test whether competing forecasts are suitable for combinations \citep{newbold2002forecast, fang2003forecasting}.
 
@@
 
-In our post-shock setting we combine estimated quantities from different time series with the aim of lowering forecast error for a single time series under study.
+% In our post-shock setting we combine estimated quantities from different time series with the aim of lowering forecast error for a single time series under study.
 Our techniques are similar to those in time-series pooling and data integration.
@@
 Data integration for forecasting is a broad area of research including ideas from many areas.
+Time-series pooling methods are a popular data integration method for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.
+However, the issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded.
 \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model
@@
 %which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
-We stress that $\mathbf{W}^*$ may not be unique. \cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
+\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
 so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
@@
 This model somehow accounts for the impact of past information on the shock-effects.
+ We further define
+\begin{align*}
+  \mathbf{V} = \Big(\mrm{vec}\big((\mathbf{x}_{2, T_2^*}, \mathbf{x}_{2, T_2^*+1})\big), \ldots, \mrm{vec}\big((\mathbf{x}_{n+1, T_2^*}, \mathbf{x}_{n+1, T_2^*+1})\big)\Big).
+\end{align*}
+Note that $\mathbf{V}$ is $2p \times n$. Then, the following proposition details some conditions when $\mathbf{W}^*$ is unique.
+\begin{prop}
+  \label{uniqueness} If $\mathbf{V}$ has full rank and it exists some $\mathbf{W}$ satisfies (\ref{SCM}), the solution to  (\ref{W}) is unique.
+\end{prop} 
+If the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$.
+However, when $2p < n$, $\mathbf{W}^*$ may not be unique.
+
 Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
@@
 \begin{remark}
-  In Section \ref{constructionofestimators}, we note that $\mathbf{W}^*$ may not be unique.
+  In Section \ref{constructionofestimators}, we noted that $\mathbf{W}^*$ may not be unique if $2p < n$.
 However, Proposition \ref{proprisk} and \ref{propriskwadj2} will hold for  every $\hat{\alpha}_{\rm wadj}$ using  $\mathbf{W}^*$ that satisfies (\ref{SCM}).
@@
 
-The bootstrap based on resampling the donor pool with replacement is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^*$.
-Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^*$.
+The bootstrap based on resampling the donor pool with replacement is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$.
+Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$.
 Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$.
@@
   \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
-  =\E{\hat{\alpha}_{\rm wadj}|\Theta},
+  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
 \end{align*}
@@
 In this section, we provide justification for our methods based on simulation examples.
-We implement our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
+We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
+We consider $p=13$ and $\mu_{\alpha}=10$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.
+
+Parameter setup of our simulations are detailed as below.
 $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
 We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers.
+This process is repeated until $T_i > 2p + 3$ for all $i\in \{1, \ldots, n + 1\}$ to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
 It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
 Moreover, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
-We consider $p=2$ and $\mu_{\alpha}=10$.
+
 In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\gamma}$ and $\sigma_{\delta}$ in the model $\delta_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\delta}\mathbf{I}_p}$, and $\gamma_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\gamma}\mathbf{I}_p}$.
+We used 200 replications of Monte Carlo simulations and $B = 500$ for computation; and report means and standard errors for estimated quantities accordingly.
 
@@
 We report 1 for risk-reduction propositions to be consistent and 0 otherwise.
+Recall that in Section \ref{comparisons}, we could estimate the risk-reduction quantities, and therefore select the best estimator with the maximum risk-reduction quantities.
+It is also possible to confirm whether this decision is true in a simulation setting.
+Similarly, we report 1 for the decision of selecting the best shock-effect estimators  to be consistent and 0 otherwise.
+
+In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\gamma}= \sigma_{\delta}=\sigma_{\alpha} \in  \{0.01, 0.1, 1, 10\}$ where we fix $\sigma$ to 1.
+The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown.
+It is shown in Table ?
+that as the donor pool size increases, the bias and consistency results improve with more precision.
+In contrast, the result gets poorer as  the variance of $\alpha_i$ increases.
+It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$.
+Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates.
+But it is reversed in the random design case.
 
@@
 Specifically, we are interested in the distance between $\alpha_1$ and our shock-effect estimators, and the distance between $y_{1,T_1^*+1}$ and $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$.
+
+In the first experiment, Table ?
+shows similar results to  Section  \ref{parametricbootstrapsimulation} that the prediction and distance to $\alpha_1$ gets better as $n$ increases but worser when the variance of $\alpha_i$ gets larger.
 
@@
 The covariates and response of time series in the donor pool are adjusted for inflation.
-Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent.
+Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in Appendix \ref{smfda}.
 We computed 3 shock-effect estimates.
@@
     Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
-    Risk-reduction proposition & 1 & 1 & 1
-%    Best shock-effect estimator & 0 & 1 & 0
+    Risk-reduction proposition & 1 & 1 & 1\\
+    Risk reduction & 28.126 & 28.179 & 25.834
     \end{tabular}
@@
 Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
+The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator.
 Note that this parametric bootstrap procedure is conditioned  on the  donor pool.
@@
 The unadjusted forecast has an MSE of 97.422 whereas 
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  MSE of 20.028,  19.647, and 22.477, respectively.
-Therefore, results proposed by Table \ref{table2} are verified with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without, and that $\hat{\alpha}_{\rm wadj}$ is the best with lowest MSE.
-
-We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
+the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  MSE of 19.599,  19.647, and 19.484, respectively.
+Therefore, results proposed by Table \ref{table2} are verified with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
+However, the risk-reduction quantities are inconsistent with the reality.
+The empirical MSE votes for $\hat{\alpha}_{\text{IVW}}$ though the estimates of  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ are fairly close shown by Figure~\ref{Fig:CP}.
+
+We also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
 The supply shock donor pool consists of the November 27, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  MSEs of $1.797$, $2.812$, and $0.437$, respectively.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  MSEs of $1.962$, $2.812$, and $1.354$, respectively.
 These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect.
@@
 Our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series.
-The pseudo-time series generated by parametric bootstrap is not stationary.
+The pseudo time series generated by parametric bootstrap is not stationary.
 Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
-This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$\footnote{The collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d.
+This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$ where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$; for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$.
+The sampling stops when $N$ observations are reached.
+Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d.
 discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d.
-geometric random variables with parameter $p$.}, where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$\footnote{For $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$.}; and the sampling stops when $N$ observations are reached.
+geometric random variables with parameter $p$.
 However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}.
@@
 More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}.
-It is up to the user in selecting which procedure to choose but under different assumptions on the time-series.
-\textbf{Include footnotes in main text; also use either time series or time-series but not both}.
+It is up to the user in selecting which procedure to choose but under different assumptions on the time series.
 
@@
 
-\subsection{Proofs for lemmas and propositions}
+\subsubsection{Proofs for lemmas and propositions}
+
+\begin{proof-of-proposition}[\ref{uniqueness}]
+  The proof of \citet{li2019statistical} in Appendix A.2 and A.3 adapts easily to Proposition \ref{uniqueness}.
+\end{proof-of-proposition}
 
@@
 
+\subsection{Supplementary materials for data analysis}
+\label{smfda}
+The independence of estimated shock-effects are further tested using likelihood ratio test (LRT) based on their estimated covariance matrix. The estimated covariance matrix is
+\begin{align*}
+  \hat{\mathbf{\Sigma}}=\left(\begin{array}{rrr}
+    4.012 & 0.362 & -0.062 \\
+    0.362 & 3.894 & -0.029 \\
+    -0.062 & -0.029 & 3.927
+  \end{array}\right).
+\end{align*}
+with degrees of freedoms 35.
+Using LRT for independence between blocks of random variables \citep[Section 10.2]{msos}, the LRT test statistic is $0.304$ with $p$-value of 0.581.
+Therefore, we do not reject  the null hypothesis that the three estimated shock-effects are independent.
+
 \bibliographystyle{plainnat}

### 2020-06-09 Rcode/sim.study.R

@@ -160,7 +160,6 @@ boots <- function(B, ols) {
   }
   return(list(adj = alphahat.adj.B, wadj = alphahat.wadj.B, IVW = alphahat.IVW.B))
 }
-
 # function based on ols object
 boots.mix <- function(B, ols) {
   # extract
@@ -216,7 +215,6 @@ boots.mix <- function(B, ols) {
   }
   return(list(adj = alphahat.adj.B, wadj = alphahat.wadj.B, IVW = alphahat.IVW.B))
 }
-
 # risk condition
 risk.reduction <- function(means, vars) {
   rr.adj <- (means['wadj']) ^ 2 - vars['adj'] - (means['adj'] - means['wadj']) ^ 2
@@ -226,8 +224,6 @@ risk.reduction <- function(means, vars) {
   names(est) <- c('adj', 'wadj', 'IVW')
   return(list(usable = ifelse(est > 0, yes = 1, no = 0), best = which.max(est)))
 }
-
-# nowcasting 
 # nowcasting 
 nowcast.alpha <- function(X, Y, Tstar, best = c('adj', 'wadj', 'IVW')) {
   # set up
@@ -259,12 +255,14 @@ nowcast.alpha <- function(X, Y, Tstar, best = c('adj', 'wadj', 'IVW')) {
   return(list(yhat2 = yhat2, yhat1 = yhat1, alpha1est = ols$est[best]))
 }
 
-
 # simulation study normal
 sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma, 
                                     sigma.alpha, sigma.delta.gamma, 
                                     p, B, n, scale, np = c(TRUE, FALSE)) {
   T <- round(rgamma(n = n + 1, shape = 10, scale = 5)) # Time Length
+  while(min(T) <= 3 + 2 * p) {
+    T <- round(rgamma(n = n + 1, shape = 10, scale = 5))
+  }
   Tstar <- c() # Shock Time Points
   for (t in T) {
     Tstar <- c(Tstar, sample(3:(t - 1), size = 1))
@@ -340,9 +338,9 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   
   # bootstrap samples
   if (np == TRUE) {
-    bootsamp <- boots.mix(B = 1000, ols = ols)
+    bootsamp <- boots.mix(B = B, ols = ols)
   } else {
[…]

### 2020-06-12 manuscript/fig2.tex
Revisions to abstract, introduction, simulation, data analysis, and discussions.

@@
-% Created by tikzDevice version 0.12.3 on 2020-06-09 17:22:19
+% Created by tikzDevice version 0.12.3 on 2020-06-11 18:44:46
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.16) --
-	(481.73, 86.58) --
-	(476.44, 86.58) --
-	(479.09, 91.16);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.25) --
+	(481.73, 86.67) --
+	(476.44, 86.67) --
+	(479.09, 91.25);
 \definecolor{drawColor}{RGB}{0,191,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 87.98) -- (481.86, 87.98);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 88.07) -- (481.86, 88.07);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.20) -- (479.09, 90.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.29) -- (479.09, 90.84);
 \definecolor{drawColor}{RGB}{238,99,99}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.20) -- (481.05, 90.12);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.29) -- (481.05, 90.21);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 90.12) -- (481.05, 86.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 90.21) -- (481.05, 86.29);
 \definecolor{drawColor}{RGB}{238,130,238}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,148.08) {$\hat{y}_{1, T_1^* + 1}^{1}$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.42] at ( 66.76,176.41) {$\hat{y}_{1, T_1^* + 1}^{1}$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,131.74) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm adj}$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.42] at ( 66.76,150.25) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm adj}$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,115.39) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm IVW}$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.42] at ( 66.76,124.10) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm IVW}$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76, 99.04) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm wadj}$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.42] at ( 66.76, 97.94) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm wadj}$};
 
-\path[fill=fillColor] ( 53.02,151.88) circle (  1.96);
+\path[fill=fillColor] ( 53.02,181.31) circle (  2.50);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,138.59) --
-	( 55.66,134.01) --
-	( 50.37,134.01) --
-	( 53.02,138.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,159.04) --
+	( 56.38,153.21) --
+	( 49.65,153.21) --
+	( 53.02,159.04);
 \definecolor{drawColor}{RGB}{0,191,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.24,119.19) -- ( 55.79,119.19);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.48,129.00) -- ( 56.55,129.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,116.42) -- ( 53.02,121.97);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,125.47) -- ( 53.02,132.53);
 \definecolor{drawColor}{RGB}{238,99,99}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.05,100.88) -- ( 54.98,104.81);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.52,100.35) -- ( 55.51,105.34);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.05,104.81) -- ( 54.98,100.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.52,105.34) -- ( 55.51,100.35);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.32] at (266.05,346.76) {Conoco Phillips Stock Forecasting (2020--01--24 to 2020--03--09)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.32] at (266.05,346.76) {Conoco Phillips Stock Forecasting (2020 January 24th to 2020 March 9th)};
 \end{scope}

### 2020-06-12 manuscript/manuscript.tex
Revisions to abstract, introduction, simulation, data analysis, and discussions.

@@
 \begin{enumerate}
-  \item Proposition for uniqueness of $\mathbf{W}^*$ is added.
-  \item Introduction is revised with additional references.
-  \item Data analysis is revised by fixing previous coding error.
-  \item Simulation description is updated.
-  \item Discussion is revised according to comments.
+  \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
 \end{enumerate}
@@
 Bootstrap procedures are provided to estimate the variability of our shock effect estimators and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed.
+The risk-reduction conditions are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well.
 Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
@@
 One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error.
+Then, we discuss some frequently used methodologies that may be applied in this situation.
 %When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.
@@
 
-Data integration for forecasting is a broad area of research including ideas from many areas.
-Time-series pooling methods are a popular data integration method for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.
-However, the issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded.
-\citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model
+As alternatives to forecast combination, data integration and time series pooling for forecasting is a broad domain of research including ideas from many areas.
+Time-series pooling methods are frequently used for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.
+Recent researches in data integration have investigated versatile methods to combine knowledge from multiple datasets for better prediction, whose ideas are similar to ours.
+For instance, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model
 to improve predictive precision of COVID-19 infection trajectories for different countries.
@@
 
-Up to the scale of the shock, it is very unlikely that the above mentioned  statistical models or machine learning methods will work ideally since they are trained on the time series data that do not experience such a shock.
+Up to the scale of the shock, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock.
 To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration.
@@
 The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap.
-Our simulation results show that  bootstrap estimation and the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
-In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020-03-09, the proposed three aggregation techniques work decently well.
+These propositions are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well, using estimates from bootstrap procedures.
+Our simulation results show that the proposed bootstrap estimation and the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
+In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well.
 We now motivate our aggregation techniques.
@@
 \end{align*}
-Note that $\mathbf{V}$ is $2p \times n$. Then, the following proposition details some conditions when $\mathbf{W}^*$ is unique.
 \begin{prop}
@@
 \end{prop} 
-If the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$.
+Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.
+Note that $\mathbf{V}$ is $2p \times n$.
+Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$.
 However, when $2p < n$, $\mathbf{W}^*$ may not be unique.
-
-Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
-and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.
 
@@
 
-In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice.
+In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, and checks the underlying conditions of our risk reduction results in practice.
 Our procedure involves the resampling of residuals in the separate OLS fits.
@@
 To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement and the other without any resampling of the donor pool.
-We first illustrate the simple bootstrap without resampling the donor pool.
+We denote them by $\mc{B}_1$ and  $\mc{B}_2$, respectively.
+We first illustrate the simple $\mc{B}_2$.
 The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool.
-initialize $y_{i,0}$ for all $i \in I$.
+Initialize $y_{i,0}$ for all $i \in I$.
 At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$.
@@
 Therefore, this parametric bootstrap framework will work for us.
-Once can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
-
-The bootstrap based on resampling the donor pool with replacement is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$.
+One can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
+
+$\mc{B}_1$ is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$.
 Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$.
 Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$.
-When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however, if the constraints used to obtain $\mathbf{W}^*$ are binding then our bootstrap procedure needs to be modified \citep{li2019statistical}.
-The subsampling method in Section 4 of \citet{li2019statistical} can be adapted to our post-shock setting when the constraints are binding.
+
+%When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however,
+
+$\mc{B}_1$ takes the perspective of treating the donor-pool candidates to be random while $\mc{B}_2$ takes them as fixed.
+Therefore, it is possible that $\mc{B}_1$ can improve precision of $\mc{B}_2$.
+Notice that $\mathbf{W}^*$ is random in $\mc{B}_1$.
+It is likely that  $\mc{B}_1$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ since $\mathbf{W}^*$ may possibly take values on the boundary of the parameter space \citep{andrews2000inconsistency}.
+For example, $w_i^*=0$ for some $i \in \{2, \ldots, n+1\}$.
+The subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$ and $m/n \to 0$ as $n \to \infty$.
+However, we may leave its mathematical justification for future research.
+Note that this problem will not occur under  $\mc{B}_2$ because  if $w_i^*=0$ for some $i$, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.
 
@@
 The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$.
-However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is a linear combination of OLS estimates with random weights.
+However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because its weights are random.
 It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$.
-We claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.
+We would only claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.
 
@@
 
-We stress that the above approximation is conditioned on $\Theta$ and the donor pool, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
+We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_2$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
 %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population.
 For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$.
-For parametric bootstrap without conditioning on the donor pool but conditioned on $\Theta$, we stress that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold.
+For $\mc{B}_1$ but conditioned on $\Theta$, we stress that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold.
 Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.
@@
 
-In this section, we provide justification for our methods based on simulation examples.
+In this section, we provide justification for our methods based on Monte Carlo simulation examples.
 We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
@@
 $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
-We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers.
-This process is repeated until $T_i > 2p + 3$ for all $i\in \{1, \ldots, n + 1\}$ to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
-It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
-Moreover, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
+We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers.
+If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.
+It is set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
+Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
+However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$.
+In that case, we do not consider such $b$ in computations of means and variances.
+Additionally, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
 
@@
     Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
-    Risk-reduction proposition & 1 & 1 & 1\\
-    Risk reduction & 28.126 & 28.179 & 25.834
     \end{tabular}
@@
 Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
+Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $28.031$, $28.084$, and $25.748$, respectively.
 The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator.
 Note that this parametric bootstrap procedure is conditioned  on the  donor pool.
-Table \ref{table2} tells that all three proposed  shock-effect estimators are usable in the sense that the forecast employing them is better than the one without; and the $\hat{\alpha}_{\rm wadj}$ is the best in terms of the estimated risk-reduction quantity.
 Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
@@
 We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
-The unadjusted forecast has an MSE of 97.422 whereas 
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  MSE of 19.599,  19.647, and 19.484, respectively.
-Therefore, results proposed by Table \ref{table2} are verified with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
+The unadjusted forecast has an RMSE of 19.680 dollars whereas 
+the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $4.441$, and $4.423$ dollars, respectively.
+Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
 However, the risk-reduction quantities are inconsistent with the reality.
@@
 
-We also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
-The supply shock donor pool consists of the November 27, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  MSEs of $1.962$, $2.812$, and $1.354$, respectively.
+The phenomenon that the true shock effect is not recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ can be due to that the donor pool is not constructed to be similar enough to the time series of interest.
+The shock(s) on March 9, 2020 is(are) in the midst of the COVID-19 pandemic and oil production volatility.
+It is difficult to find available stock market time series data that were generated under a similar setting.
+
+From another perspective, it is possible that the stock of Conoco Phillips actually experienced multiple shocks on 2020 March 9th.
+For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector auto regressive model.
+Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.
+Motivated by his study, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
+The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.382$, $1.657$, and $1.145$ dollars, respectively.
 These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect.
-There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.
-Our apriori justification comes from \citet{kilian2009not} who study the effect that different supply and demand shocks have on oil prices through a vector auto regressive model.
-Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.
+%There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.
 %This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.
-
-However, from another perspective, this phenomenon can be explained by the fact that the donor pool is not constructed to be similar enough to the time series of interest.
-The shock(s) on March 9, 2020 in the midst of the COVID-19 pandemic and oil production volatility.
-It is difficult to find available stock market time series data that were generated under a similar setting.
 
@@
 Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest.
-We recommend using parametric bootstrap without conditioning on the donor pool when the donor pool size $n$ is large, and the one conditioned on the donor pool when $n$ is small.
+We recommend using $\mc{B}_1$ when the donor pool size $n$ is large, and $\mc{B}_2$ when $n$ is small.
 

### 2020-06-12 Rcode/dataanalysis.R

@@ -64,7 +64,7 @@ start_day_20080317 <- as.numeric(1:nrow(COP_close) == start)
 COP_close <- COP_close %>% mutate(start_day_20080317 = start_day_20080317)
 TS2 <- COP_close[(start-30):start, ]
 # inflation adjustment
-TS2[, 2:7] <- COP_close_small[, 2:7] * inflation_adj$dollars_2020[inflation_adj$year == 2008] 
+TS2[, 2:7] <- TS2[, 2:7] * inflation_adj$dollars_2020[inflation_adj$year == 2008] 
 m_COP_3_17 <- lm(Y ~ COP_Close + start_day_20080317 + GSPC_Close + WTI_Close + WTI_Close_lag1 + GSPC_Close_lag1, 
                  data = TS2)
 alpha_3_17 <- summary(m_COP_3_17)$coef[3,1:2] 
@@ -128,7 +128,7 @@ lrindcov <- function(cov, cols, v){
 # not significant => Independence
 lrindcov(vcov(m_COP_Sept_08)[3:5, 3:5], cols = list(1, 2, 3), v = df.residual(m_COP_Sept_08))
 
-
+xtable(vcov(m_COP_Sept_08)[3:5, 3:5])
 
 #### Thursday, November 27, 2014
 
@@ -350,7 +350,6 @@ for (b in 1:B) {
   alphas[[2]] <- c(alphas[[2]], sum(alphahatsb * weights / sum(weights)))
   alphas[[3]] <- c(alphas[[3]], sum(Wstar * alphahatsb))
 }
-
 # Parameters
 means <- c()
 vars <- c()
@@ -367,7 +366,9 @@ risk.reduction <- function(means, vars) {
   rr.IVW <- (means['wadj']) ^ 2 - vars['IVW'] - (means['IVW'] - means['wadj']) ^ 2
   est <- c(rr.adj, rr.wadj, rr.IVW)
   names(est) <- c('adj', 'wadj', 'IVW')
-  return(list(usable = ifelse(est > 0, yes = 1, no = 0), best = which.max(est)))
+  return(list(usable = ifelse(est > 0, yes = 1, no = 0), 
+              best = which.max(est),
+              rr = est))
 }
 risk.reduction(means = means, vars = vars) 
 
@@ -418,7 +419,7 @@ alpha.adj.additive <- mean(estimates[1:4, 1]) + estimates[5, 1]
 
 # IVW estimator
 weights <- (1 / estimates[1:4,2]) / sum(1 / estimates[1:4, 2])
[…]

### 2020-06-12 Rcode/sim.study.R

@@ -259,10 +259,8 @@ nowcast.alpha <- function(X, Y, Tstar, best = c('adj', 'wadj', 'IVW')) {
 sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma, 
                                     sigma.alpha, sigma.delta.gamma, 
                                     p, B, n, scale, np = c(TRUE, FALSE)) {
-  T <- round(rgamma(n = n + 1, shape = 10, scale = 5)) # Time Length
-  while(min(T) <= 3 + 2 * p) {
-    T <- round(rgamma(n = n + 1, shape = 10, scale = 5))
-  }
+  T <- round(rgamma(n = n + 1, shape = 15, scale = 10)) # Time Length
+  T[which(T < 90)] <- 90
   Tstar <- c() # Shock Time Points
   for (t in T) {
     Tstar <- c(Tstar, sample(3:(t - 1), size = 1))
@@ -344,8 +342,8 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   }
   
   # Bias
-  bias <- c(abs(mean(bootsamp[[1]]) - Ealpha.adj), 
-              abs(mean(bootsamp[[2]]) - Ealpha1))
+  bias <- c(abs(mean(bootsamp[[1]], na.rm = TRUE) - Ealpha.adj), 
+              abs(mean(bootsamp[[2]], na.rm = TRUE) - Ealpha1))
   names(bias) <- c('E.adj', 'E.wadj')
   
   # Distance
@@ -355,8 +353,8 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   means <- c()
   vars <- c()
   for (j in 1:3) {
-    means <- c(means, mean(bootsamp[[j]]))
-    vars <- c(vars, var(bootsamp[[j]]))
+    means <- c(means, mean(bootsamp[[j]], na.rm = TRUE))
+    vars <- c(vars, var(bootsamp[[j]], na.rm = TRUE))
   }
   names(means) <- names(vars) <- c('adj', 'wadj', 'IVW')
   
@@ -388,7 +386,8 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
 sim.study.normal.normalX <- function(mu.gamma.delta, mu.alpha, sigma, 
                                      sigma.alpha, sigma.delta.gamma, 
[…]

### 2020-06-14 manuscript/manuscript.tex
major revision to discussion, and minor edits to abstract, introduction, methodology, data analysis, and simulation

@@
 Three shock-effects estimators were constructed for minimizing average forecast risk.
-We proposed conditions when our methodology works, and which estimator is the best in average forecast risk reduction.
-Bootstrap procedures are provided to estimate the variability of our shock effect estimators and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed.
-The risk-reduction conditions are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well.
+We proposed conditions when our methodology works and estimators for risk-reduction quantities.
+Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed.
+The risk-reduction conditions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best.
 Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
@@
 The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap.
-These propositions are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well, using estimates from bootstrap procedures.
-Our simulation results show that the proposed bootstrap estimation and the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
+These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best, using estimates from bootstrap procedures.
+Our Monte Carlo simulation results show that  the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
+Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large.
 In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well.
@@
 Next, we will detail a framework for estimation of risk-reduction  quantities using a parametric bootstrap routine.
-Therefore, the above inequalities can be analyzed numerically in practice.
+Therefore, the above inequalities can be analyzed numerically and risk-reduction quantities can be estimated using plug-in estimators in practice.
 
@@
 
-In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, and checks the underlying conditions of our risk reduction results in practice.
+In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction results, and estimate risk-reduction using plug-in approach in practice.
 Our procedure involves the resampling of residuals in the separate OLS fits.
@@
 
-To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement and the other without any resampling of the donor pool.
-We denote them by $\mc{B}_1$ and  $\mc{B}_2$, respectively.
-We first illustrate the simple $\mc{B}_2$.
+To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement (\emph{unconditional} on donor pool) and the other without any resampling of the donor pool (\emph{conditional} on donor pool).
+We denote them by $\mc{B}_u$ and  $\mc{B}_c$, respectively.
+We first illustrate the simple $\mc{B}_c$.
 The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool.
@@
 
-$\mc{B}_1$ is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$.
+$\mc{B}_u$ is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$.
 Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$.
 Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$.
+We would assume $\mathbf{W}^*$ is non-degenerate (i.e., no zero weights) in the population when using $\mc{B}_u$.
+See Section \ref{discussion} for discussions.
 
@@
 
-$\mc{B}_1$ takes the perspective of treating the donor-pool candidates to be random while $\mc{B}_2$ takes them as fixed.
-Therefore, it is possible that $\mc{B}_1$ can improve precision of $\mc{B}_2$.
-Notice that $\mathbf{W}^*$ is random in $\mc{B}_1$.
-It is likely that  $\mc{B}_1$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ since $\mathbf{W}^*$ may possibly take values on the boundary of the parameter space \citep{andrews2000inconsistency}.
-For example, $w_i^*=0$ for some $i \in \{2, \ldots, n+1\}$.
-The subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$ and $m/n \to 0$ as $n \to \infty$.
-However, we may leave its mathematical justification for future research.
-Note that this problem will not occur under  $\mc{B}_2$ because  if $w_i^*=0$ for some $i$, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.
-
-Let 
+Now, we discuss some consistency results for $\mc{B}_c$ conditioned on $\Theta_1$. Let 
 $
@@
 
-We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_2$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
+We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_c$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
 %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population.
 For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$.
-For $\mc{B}_1$ but conditioned on $\Theta$, we stress that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold.
+For $\mc{B}_u$ but conditioned on $\Theta$, we emphasize that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold.
 Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.
@@
 But it is reversed in the random design case.
+Moreover, notice that the consistency for voting the best estimator works poor when $n$ is small but improves significantly when $n$ is large.
 
@@
 We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
-The unadjusted forecast has an RMSE of 19.680 dollars whereas 
+The unadjusted forecast has an RMSE of 9.870 dollars whereas 
 the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $4.441$, and $4.423$ dollars, respectively.
@@
 The empirical MSE votes for $\hat{\alpha}_{\text{IVW}}$ though the estimates of  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ are fairly close shown by Figure~\ref{Fig:CP}.
+It is consistent with the finding in Section \ref{parametricbootstrapsimulation} that voting for best estimator with estimated risk-reduction quantities is very likely to be inconsistent with the truth when the donor pool size $n$ is small.
 
@@
 \section{Discussion}
+\label{discussion}
 
@@
 
-Our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series.
+Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series.
 The pseudo time series generated by parametric bootstrap is not stationary.
@@
 More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}.
-It is up to the user in selecting which procedure to choose but under different assumptions on the time series.
+It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.
+
+In terms of the use of our bootstrap procedure, we caution that the bootstrapping residuals in OLS estimation may not provide valid inference in high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}.
+Recall that in Section \ref{varbootstrap}, we proposed two possible bootstrap procedures, $\mc{B}_u$  and $\mc{B}_c$.
+There are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_c$.
+$\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
+In contrast $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
+Therefore, it is possible that $\mc{B}_u$ can improve precision of $\mc{B}_2$.
+In this study, for the use of $\mc{B}_u$, we assume $\mathbf{W}^*$ is non-degenerate in the population with taking zero weight.
+However, it is likely that $\mathbf{W}^*$ may possibly take values on the boundary of $\mc{W}$, in which case $\mc{B}_u$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
+For example, $w_i^*=0$ for some $i \in \{2, \ldots, n+1\}$.
+In this regard, the subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$.
+But we may leave its mathematical justification for future research.
+Note that this problem will not occur under  $\mc{B}_c$ because  if $w_i^*=0$ for some $i$, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.
+That being said, if in practice users detect the boundary case (e.g., $\mathbf{W}^*$ in Section \ref{forecasting}), they are not recommended to use $\mc{B}_u$.
+Besides, we  recommend using $\mc{B}_c$ when the donor pool size $n$ is small.
+When $n$ is large, the selection would be more up to how users think of the philosophical differences between $\mc{B}_u$ and $\mc{B}_c$ up to application of interest, and the problems that  $\mc{B}_u$ may fail.
 
 For the use of our methodology, caution should be dedicated to the construction of donor pool.
-Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest.
-We recommend using $\mc{B}_1$ when the donor pool size $n$ is large, and $\mc{B}_2$ when $n$ is small.
+If the donor pool includes some individuals that are not similar to the time series of interest, the result will possibly not be robust to the introduced noises.
+Additionally, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large.
+It is  due to the fact that plug-in estimation of  risk-reduction quantities gains more precision when $n$ becomes large.
 

### 2020-06-14 Rcode/sim.study.R

@@ -560,7 +560,7 @@ ncores <- detectCores() - 1
 registerDoParallel(cores = ncores)
 set.seed(2020)
 RNGkind("L'Ecuyer-CMRG")
-nsim <- 200
+nsim <- 260
 
 # parameter setup
 ns <- c(5, 10, 15, 25)
@@ -593,19 +593,90 @@ system.time(
   })
 )
 
-sim.study.normal.gammaX(mu.gamma.delta = 2, 
-                        mu.alpha = 10, sigma = 1, 
-                        sigma.alpha = 1,
-                        sigma.delta.gamma = 1, 
-                        p = 13, B = 500, scale = 10, 
-                        n = n, np = FALSE)
-
 # store results
 # load packages
 require('readxl')
 require('writexl')
 setwd('/Users/mac/Desktop/Research/Post-Shock Prediction/')
 write_xlsx(lapply(output, as.data.frame), 'parametricnsigma.xlsx')
+
+
+# collect results
+result <- c()
+nnas <- c()
+for (i in 1:16) {
+  table <- output[[i]]
+  
+  # means and sds
+  means <- apply(table, 2, function(x) mean(x, na.rm = TRUE))
+  sds <- apply(table, 2, function(x) sd(x, na.rm = TRUE))
+  
+  # check how many effective rows
+  nna <- length(which(apply(output[[i]], 1, FUN = function(x) anyNA(x)) == FALSE))
+  nnas <- c(nnas, nna)
+  
+  result.i <- c()
+  for (j in 1:16) {
+    result.i <- cbind(result.i, paste0(round(means[j], digits = 3), 
+                                       ' (', round(sds[j] / sqrt(nna), 
+                                                   digits = 3), ')'))
+  }
+  result <- rbind(result, result.i)
+}
+result <- cbind(sim_params[, c(2,1)], result)
+rownames(result) <- 1:16
+# results
+riskprop <- result[, c(1:4, 8:14)]
+pred <- result[, -c(3:4, 8:14)]
+# xtable
+require('xtable')
+xtable(riskprop)
+xtable(pred)
+
+
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+# 8 cores -- use 7
+ncores <- detectCores() - 1
+registerDoParallel(cores = ncores)
+set.seed(2020)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 260
[…]

### 2020-06-16 manuscript/manuscript.tex
revision to sim.study.R and manuscript

@@
 However, when $2p < n$, $\mathbf{W}^*$ may not be unique.
+If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there are infinitely many solutions to (\ref{SCM}).
+The issue of non-uniqueness is further discussed in Section \ref{discussion}.
 
@@
 \subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}
-
+\label{section322}
 According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
@@
 
-%In particular $\overline{\hat{\alpha}_{\rm wadj}}$ will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}.
-Therefore, we can judge whether to use a shock-effect estimator, and choose between shock-effect estimators by this method.
-
 We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_c$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
@@
 
+In particular, $\overline{\hat{\alpha}_{\rm wadj}}$ will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}.
+Therefore, we can estimate the risk-reduction quantities in Section \ref{comparisons} using the estimates from the parametric bootstrap.
+For example, the $\Delta_{\rm adj}$ and its estimator $\hat{\Delta}_{\rm adj}$ are
+\begin{align*}
+  \Delta_{\rm adj} 
+  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
+  \hat{\Delta}_{\rm adj} 
+ & = (\overline{\hat{\alpha}_{\rm wadj}})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\overline{\hat{\alpha}_{\rm adj}}-\overline{\hat{\alpha}_{\rm wadj}})^2,
+\end{align*}
+where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance for $\hat{\alpha}_{\rm adj}$.
+Suppose the $\hat{\Delta}_{\rm wadj}$ and $\hat{\Delta}_{\rm IVW}$ are estimators for $\Delta_{\rm wadj}$ and $\Delta_{\rm IVW}$, respectively.
+Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}_{\rm est}>0$ for $\text{est} \in \{\text{adj}, \text{wadj}, \text{IVW}\}$, and  the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities.
+
 \section{Simulation}
@@
 If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.
-It is set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
+Moreover, $T_i^*$ is randomly selected from $2p + 4$ to $T_i-1$.
+Those are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
 Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
@@
 
-In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\gamma}$ and $\sigma_{\delta}$ in the model $\delta_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\delta}\mathbf{I}_p}$, and $\gamma_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\gamma}\mathbf{I}_p}$.
+In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
 We used 200 replications of Monte Carlo simulations and $B = 500$ for computation; and report means and standard errors for estimated quantities accordingly.
@@
 
-In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\gamma}= \sigma_{\delta}=\sigma_{\alpha} \in  \{0.01, 0.1, 1, 10\}$ where we fix $\sigma$ to 1.
+In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{1, 5, 10, 25, 100\}$ where we fix $\sigma$ to 1.
 The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown.
@@
 
+Under the setup of our model, non-uniqueness of $\mathbf{W}^*$ would not be a problem.
+It is because all risk-reduction propositions and other properties established will still hold.
+However, non-uniqueness may not be desirable in other model setup.
+For example, consider the model where $\alpha_i$ is assumed to be not identically distributed, the size of  donor pool to be 2, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$ with $\var{\alpha_2}\neq \var{\alpha_3}$.
+In this scenario, the procedure of trying to recover $\alpha_1$ will fail since the resulting $\alpha_1$ will be different with different variances for $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
+If the non-uniqueness is of concern, users may select the weight that optimizes some objective function.
+For instance, in the example just discussed, users may select the weight that minimizes the estimated variance of $\hat{\alpha}_{\rm wadj}$.
+
 Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series.
-The pseudo time series generated by parametric bootstrap is not stationary.
+The pseudo time series generated by our proposed parametric bootstrap is not stationary.
 Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
@@
 Therefore, it is possible that $\mc{B}_u$ can improve precision of $\mc{B}_2$.
-In this study, for the use of $\mc{B}_u$, we assume $\mathbf{W}^*$ is non-degenerate in the population with taking zero weight.
-However, it is likely that $\mathbf{W}^*$ may possibly take values on the boundary of $\mc{W}$, in which case $\mc{B}_u$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-For example, $w_i^*=0$ for some $i \in \{2, \ldots, n+1\}$.
+
+In this study, for the use of $\mc{B}_u$, we assume $\mathbf{W}^*$ is non-degenerate in the population without taking zero weight.
+Recall that in Section \ref{constructionofestimators} we note that if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there will be infinitely many solutions to $\mathbf{W}^*$.
+In the simulation setup, we consider $2p >n$ such that the assumption can be reasonably satisfied.
+However, in the application, it is likely that $\mathbf{W}^*$ may  take values on the boundary of $\mc{W}$, in which case $\mc{B}_u$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
 In this regard, the subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$.
 But we may leave its mathematical justification for future research.
-Note that this problem will not occur under  $\mc{B}_c$ because  if $w_i^*=0$ for some $i$, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.
-That being said, if in practice users detect the boundary case (e.g., $\mathbf{W}^*$ in Section \ref{forecasting}), they are not recommended to use $\mc{B}_u$.
-Besides, we  recommend using $\mc{B}_c$ when the donor pool size $n$ is small.
-When $n$ is large, the selection would be more up to how users think of the philosophical differences between $\mc{B}_u$ and $\mc{B}_c$ up to application of interest, and the problems that  $\mc{B}_u$ may fail.
+Note that this problem will not occur under  $\mc{B}_c$ because  if $w_i^*=0$ for some $i$ and the weights are known, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.
+Some recommendations for selection between  $\mc{B}_u$ and $\mc{B}_c$ are as below.
+
+If in practice users detect the boundary case (e.g., $\mathbf{W}^*$ in Section \ref{forecasting}), they are not recommended to use $\mc{B}_u$.
+Moreover, if $2p < n$, $\mc{B}_u$ is also not recommended since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
+Additionally, we  recommend using $\mc{B}_c$ when the donor pool size $n$ is small.
+When $n$ is large and $2p > n$, the selection would be more up to how users think of the philosophical differences between $\mc{B}_u$ and $\mc{B}_c$ up to application of interest, and the problems that  $\mc{B}_u$ may fail.
 
@@
 If the donor pool includes some individuals that are not similar to the time series of interest, the result will possibly not be robust to the introduced noises.
-Additionally, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large.
+Moreover, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large.
 It is  due to the fact that plug-in estimation of  risk-reduction quantities gains more precision when $n$ becomes large.

### 2020-06-16 Rcode/sim.study.R

@@ -224,6 +224,14 @@ risk.reduction <- function(means, vars) {
   names(est) <- c('adj', 'wadj', 'IVW')
   return(list(usable = ifelse(est > 0, yes = 1, no = 0), best = which.max(est)))
 }
+risk.reduction2 <- function(est, vars) {
+  rr.adj <- (est['wadj']) ^ 2 - vars['adj'] - (est['adj'] - est['wadj']) ^ 2
+  rr.wadj <- (est['wadj']) ^ 2 - vars['wadj']
+  rr.IVW <- (est['wadj']) ^ 2 - vars['IVW'] - (est['IVW'] - est['wadj']) ^ 2
+  rest <- c(rr.adj, rr.wadj, rr.IVW)
+  names(rest) <- c('adj', 'wadj', 'IVW')
+  return(list(usable = ifelse(rest > 0, yes = 1, no = 0), best = which.max(rest)))
+}
 # nowcasting 
 nowcast.alpha <- function(X, Y, Tstar, best = c('adj', 'wadj', 'IVW')) {
   # set up
@@ -263,7 +271,7 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   T[which(T < 90)] <- 90
   Tstar <- c() # Shock Time Points
   for (t in T) {
-    Tstar <- c(Tstar, sample(3:(t - 1), size = 1))
+    Tstar <- c(Tstar, sample((2 * p + 3 + 1):(t - 1), size = 1))
   }
   phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters
 
@@ -383,174 +391,6 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   return(result)
 }
 
-sim.study.normal.normalX <- function(mu.gamma.delta, mu.alpha, sigma, 
-                                     sigma.alpha, sigma.delta.gamma, 
-                                     p, B, n, mean, sd, np = c(TRUE, FALSE)) {
-  T <- round(rgamma(n = n + 1, shape = 15, scale = 10)) # Time Length
-  T[which(T < 90)] <- 90
-  Tstar <- c() # Shock Time Points
-  for (t in T) {
-    Tstar <- c(Tstar, sample(3:(t - 1), size = 1))
-  }
-  phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters
-  
[…]

### 2020-06-26 manuscript/manuscript.tex
revision to manuscript in discussions and bootstrap section and minor revision to data analysis (and code) in switching to sample estimate of expectations

@@
   \item Need to add simulations. 
+  \item $\mu_{\alpha}=2$, $X_{i,t}\sim \Gamma(1,2)$, $\delta_i, \gamma_i \sim \normal{1}{0.5}$
+  \item $\sigma=10$ for the base case.
+  \item $\sigma_{\alpha}= (5, 10, 25, 50, 100)$
+  \item $\sigma= (5, 10, 25, 50, 100)$
 \end{enumerate}
@@
 One can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
-
 $\mc{B}_u$ is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$.
 Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$.
-Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$.
-We would assume $\mathbf{W}^*$ is non-degenerate (i.e., no zero weights) in the population when using $\mc{B}_u$.
-See Section \ref{discussion} for discussions.
 
@@
 
-Now, we discuss some consistency results for $\mc{B}_c$ conditioned on $\Theta_1$. Let 
+Now, we discuss some consistency results for $\mc{B}_c$ conditioned on $\Theta_1$.
+The bootstrap is aimed for estimating $\mrm{Var}(\hat{\alpha}_{\rm adj})$, $\mrm{Var}(\hat{\alpha}_{\rm wadj})$, and $\mrm{Var}(\hat{\alpha}_{\rm IVW})$.
+The consistency results will be similar to the counterparts in sample mean.
+Therefore, we will briefly discuss the proof for the sample mean case and adapt it to the variance case.
+Let
 $
@@
 \end{align*}
-The case for the sample variance of the bootstrapped weighted adjustment estimator is similar.
 The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$.
@@
 
-In particular, $\overline{\hat{\alpha}_{\rm wadj}}$ will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}.
-Therefore, we can estimate the risk-reduction quantities in Section \ref{comparisons} using the estimates from the parametric bootstrap.
+Recall that  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ from Proposition \ref{unbiased}.
+Given the bootstrapped estimates of the variance, we can estimate the risk-reduction quantities in Section \ref{comparisons} using the estimates from the parametric bootstrap.
 For example, the $\Delta_{\rm adj}$ and its estimator $\hat{\Delta}_{\rm adj}$ are
@@
   \hat{\Delta}_{\rm adj} 
- & = (\overline{\hat{\alpha}_{\rm wadj}})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\overline{\hat{\alpha}_{\rm adj}}-\overline{\hat{\alpha}_{\rm wadj}})^2,
+ & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
 \end{align*}
@@
 Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}_{\rm est}>0$ for $\text{est} \in \{\text{adj}, \text{wadj}, \text{IVW}\}$, and  the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities.
+Next, we discuss some potential problems of the bootstrap procedures.
+
+In terms of the use of our bootstrap procedure, we caution that the bootstrapping residuals in OLS estimation may not provide valid inference in moderate or high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}; see alternatives for residual bootstrapping in linear models in \citet{el2018can}.
+
+Recall that $\mathbf{W}^*$  may not be unique if the conditions in Proposition \ref{uniqueness} are not satisfied.
+Under the setup of our model, non-uniqueness of $\mathbf{W}^*$ would not be a problem for inferential purposes.
+It is because all risk-reduction propositions and other properties established will still hold.
+However, non-uniqueness may not be desirable in other model setup.
+For example, consider the model where $\alpha_i$ is assumed to be not identically distributed, the size of  donor pool to be 2, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$ with $\var{\alpha_2}\neq \var{\alpha_3}$.
+In this scenario, the procedure of trying to recover $\alpha_1$ will fail since the resulting $\alpha_1$ will be different with different variances for $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
+If the non-uniqueness is of concern, users may select the weight that optimizes some objective function.
+For instance, in the example just discussed, users may select the weight that minimizes the estimated variance of $\hat{\alpha}_{\rm wadj}$.
+
+There are some issues in using $\mc{B}_u$ when $\mathbf{W}^*$ falls in the boundary of the parameter space. See detailed discussions in Section \ref{discussion}.
 
@@
       \hline 
-    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
     Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
@@
 Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
-Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $28.031$, $28.084$, and $25.748$, respectively.
+Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $28.914$, $28.988$, and $26.444$, respectively.
 The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator.
@@
 
-Under the setup of our model, non-uniqueness of $\mathbf{W}^*$ would not be a problem.
-It is because all risk-reduction propositions and other properties established will still hold.
-However, non-uniqueness may not be desirable in other model setup.
-For example, consider the model where $\alpha_i$ is assumed to be not identically distributed, the size of  donor pool to be 2, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$ with $\var{\alpha_2}\neq \var{\alpha_3}$.
-In this scenario, the procedure of trying to recover $\alpha_1$ will fail since the resulting $\alpha_1$ will be different with different variances for $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
-If the non-uniqueness is of concern, users may select the weight that optimizes some objective function.
-For instance, in the example just discussed, users may select the weight that minimizes the estimated variance of $\hat{\alpha}_{\rm wadj}$.
-
 Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series.
@@
 
-In terms of the use of our bootstrap procedure, we caution that the bootstrapping residuals in OLS estimation may not provide valid inference in high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}.
 Recall that in Section \ref{varbootstrap}, we proposed two possible bootstrap procedures, $\mc{B}_u$  and $\mc{B}_c$.
@@
 In contrast $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
-Therefore, it is possible that $\mc{B}_u$ can improve precision of $\mc{B}_2$.
 
@@
 However, in the application, it is likely that $\mathbf{W}^*$ may  take values on the boundary of $\mc{W}$, in which case $\mc{B}_u$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
+For example, if $\mathbf{W}^*$ is observed to fall in the boundary, $\mc{B}_u$ will fail.
+Moreover, if $2p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
 In this regard, the subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$.
@@
 Note that this problem will not occur under  $\mc{B}_c$ because  if $w_i^*=0$ for some $i$ and the weights are known, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.
-Some recommendations for selection between  $\mc{B}_u$ and $\mc{B}_c$ are as below.
-
-If in practice users detect the boundary case (e.g., $\mathbf{W}^*$ in Section \ref{forecasting}), they are not recommended to use $\mc{B}_u$.
-Moreover, if $2p < n$, $\mc{B}_u$ is also not recommended since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
-Additionally, we  recommend using $\mc{B}_c$ when the donor pool size $n$ is small.
-When $n$ is large and $2p > n$, the selection would be more up to how users think of the philosophical differences between $\mc{B}_u$ and $\mc{B}_c$ up to application of interest, and the problems that  $\mc{B}_u$ may fail.
 

### 2020-06-26 Rcode/dataanalysis.R

@@ -371,6 +371,19 @@ risk.reduction <- function(means, vars) {
               rr = est))
 }
 risk.reduction(means = means, vars = vars) 
+# sample version
+risk.reduction2 <- function(est, vars) {
+  rr.adj <- (est['wadj']) ^ 2 - vars['adj'] - (est['adj'] - est['wadj']) ^ 2
+  rr.wadj <- (est['wadj']) ^ 2 - vars['wadj']
+  rr.IVW <- (est['wadj']) ^ 2 - vars['IVW'] - (est['IVW'] - est['wadj']) ^ 2
+  rest <- c(rr.adj, rr.wadj, rr.IVW)
+  names(rest) <- c('adj', 'wadj', 'IVW')
+  return(list(usable = ifelse(rest > 0, yes = 1, no = 0), best = which.max(rest), rr = rest))
+}
+est <- c(alpha_adj, alpha_wadj, alpha_IVW)
+names(est) <- c('adj', 'wadj', 'IVW')
+risk.reduction2(est = est, vars = vars) 
+
 
 
 # A function of descriptive statistics

### 2020-06-26 Rcode/sim.study.R

@@ -179,6 +179,8 @@ boots.mix <- function(B, ols) {
   for (b in 1:B) {
     Yb <- Xb <- Tstarb <- c();
     Yb[[1]] <- Y[[1]]; Xb[[1]] <- X[[1]]; Tstarb <- Tstar[1]
+    
+    # main difference from boots function
     pool <- sample(2:(n + 1), size = n, replace = TRUE)
     for (i in 1:n) {
       
@@ -230,7 +232,7 @@ risk.reduction2 <- function(est, vars) {
   rr.IVW <- (est['wadj']) ^ 2 - vars['IVW'] - (est['IVW'] - est['wadj']) ^ 2
   rest <- c(rr.adj, rr.wadj, rr.IVW)
   names(rest) <- c('adj', 'wadj', 'IVW')
-  return(list(usable = ifelse(rest > 0, yes = 1, no = 0), best = which.max(rest)))
+  return(list(usable = ifelse(rest > 0, yes = 1, no = 0), best = which.max(rest), rr = rest))
 }
 # nowcasting 
 nowcast.alpha <- function(X, Y, Tstar, best = c('adj', 'wadj', 'IVW')) {
@@ -261,6 +263,92 @@ nowcast.alpha <- function(X, Y, Tstar, best = c('adj', 'wadj', 'IVW')) {
   
   # output
   return(list(yhat2 = yhat2, yhat1 = yhat1, alpha1est = ols$est[best]))
+}
+
+# double bootstrap
+## main function for double bootstrap
+ddboots <- function(B, K, ols, np) {
+  
+  # extract
+  est <- ols$est
+  res <- ols$res
+  Tstar <- ols$Tstar
+  Y <- ols$Y
+  X <- ols$X
+  lmod <- ols$lmod
+  p <- ncol(X[[1]])
+  n <- length(ols$Y) - 1
+  
+  # Distribution of Risk-Reduction
+  RR.adj <- c()
+  RR.wadj <- c()
+  RR.IVW <- c()
+  
+  # FIRST BOOTSTRAP
+  
+  for (b in 1:B) {
+    
+    # setup
+    Yb <- Xb <- Tstarb <- c();
+    Yb[[1]] <- Y[[1]]; Xb[[1]] <- X[[1]]; Tstarb <- Tstar[1]
+    
+    # non-parametric bootstrap or not of the donor pool
+    if (np == TRUE) {
[…]

### 2020-06-28 manuscript/fig2.tex
revisions to data analysis

@@
-% Created by tikzDevice version 0.12.3 on 2020-06-11 18:44:46
+% Created by tikzDevice version 0.12.3 on 2020-06-28 18:03:01
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.29) -- (481.05, 90.21);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 81.21) -- (481.05, 85.13);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 90.21) -- (481.05, 86.29);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 85.13) -- (481.05, 81.21);
 \definecolor{drawColor}{RGB}{238,130,238}

### 2020-06-28 manuscript/manuscript.tex
revisions to data analysis

@@
 \begin{align*}
- \mathbf{W}^*= (0.000,0.000, 0.949, 0.000, 0.051) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 23.496.
+ \mathbf{W}^*= (0.000,0.000, 0.000, 0.000, 1.000) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 1314.04.
 \end{align*}
 Note that the norm is computed using the $k$-dimensional Euclidean metric.
-The fit is acceptable.
-According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately.
-The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (September 8, 2008) and $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.
+The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is very similar to $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.
 
@@
       \hline 
-    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
+    Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
+    Leave-one-out consistency & 0.000 & 0.800 & 0.000
     \end{tabular}
@@
 
-Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
-Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $28.914$, $28.988$, and $26.444$, respectively.
+Using the parametric bootstrap conditioned on the donor pool proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
+Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $34.565$, $34.880$, and $34.139$, respectively.
 The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator.
-Note that this parametric bootstrap procedure is conditioned  on the  donor pool.
+Moreover, the leave-one-out consistency of the risk-reduction propositions are 0.000, 0.800, and 0.000 for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$, respectively.
+It implies that we should only use the propositions for $\hat{\alpha}_{\text{wadj}}$.
 Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
@@
 The unadjusted forecast has an RMSE of 9.870 dollars whereas 
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $4.441$, and $4.423$ dollars, respectively.
+the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $3.924$, and $4.423$ dollars, respectively.
 Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
-However, the risk-reduction quantities are inconsistent with the reality.
-The empirical MSE votes for $\hat{\alpha}_{\text{IVW}}$ though the estimates of  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ are fairly close shown by Figure~\ref{Fig:CP}.
-It is consistent with the finding in Section \ref{parametricbootstrapsimulation} that voting for best estimator with estimated risk-reduction quantities is very likely to be inconsistent with the truth when the donor pool size $n$ is small.
+Moreover, the risk-reduction quantities are consistent with the reality as well.
+The results are also consistent with leave-one-out consistency for $\hat{\alpha}_{\text{wadj}}$ in that it  reduces the risk.
 
@@
 The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.382$, $1.657$, and $1.145$ dollars, respectively.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.382$, $2.468$, and $1.145$ dollars, respectively.
 These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect.

### 2020-06-28 Rcode/dataanalysis.R

@@ -184,7 +184,7 @@ alpha_IVW <- sum(weights * estimates[, 1])
 
 # weighted adjustment estimator
 Tstar.Date <- c("2020-03-05", "2008-03-13", "2008-09-05", "2008-09-11", "2008-09-25",  "2014-11-25")
-Tstar <- which(COP_close$Date %in% Tstar.Date)
+Tstar <- sapply(Tstar.Date, function(x) which(COP_close$Date == x))
 # X1
 X1 <- as.matrix(COP_close[c(Tstar[1], Tstar[1] + 1), c(3, 4)])
 # X0
@@ -197,6 +197,34 @@ for (i in 1:5) {
 
 # Euclidean metric
 # objective function
+
+scmm <- function(X1, X0) {
+  weightedX0 <- function(W) {
+    # W is a vector of weight of the same length of X0
+    n <- length(W)
+    p <- ncol(X1)
+    XW <- matrix(0, nrow = 2, ncol = p)
+    for (i in 1:n) {
+      XW <- XW + W[i] * X0[[i]]
+    }
+    norm <- as.numeric(crossprod(matrix(X1 - XW)))
+    return(norm)
+  }
+  # constraint for W
+  Wcons <- function(W) sum(W) - 1
+  n <- length(X0)
+  # optimization
+  outs <- solnp(par = rep(1/n, n), fun = weightedX0, eqfun = Wcons, eqB = 0, LB = rep(0, n), UB = rep(1, n))
+  
+  # output weights
+  Wstar <- outs$pars
+  
+  return(Wstar)
+}
+
+# objective function is not 0; the fit may not be good
+Wstar <- scmm(X1 = X1, X0 = X0)
+
 weightedX0 <- function(W) {
   # W is a vector of weight of the same length of X0
   n <- length(W)
@@ -210,40 +238,16 @@ weightedX0 <- function(W) {
 }
 # constraint for W
 Wcons <- function(W) sum(W) - 1
-n <- 5
+n <- length(X0)
 # optimization
 outs <- solnp(par = rep(1/n, n), fun = weightedX0, eqfun = Wcons, eqB = 0, LB = rep(0, n), UB = rep(1, n))
 
 # output weights
 Wstar <- outs$pars
-# objective function is not 0; the fit may not be good
 weightedX0(round(outs$pars, digits = 3))
[…]

### 2020-06-28 Rcode/sim.study.R

@@ -351,10 +351,80 @@ ddboots <- function(B, K, ols, np) {
   return(list(adj = RR.adj, wadj = RR.wadj, IVW = RR.IVW))
 }
 
+cv <- function(k, X, Y, Tstar, np, B) {
+  # k must <= n
+  # X is a list of n + 1 objects
+  n <- length(X) - 1
+  
+  # if n <= k
+  if (n <= k) {
+    draw <- 1:n
+    k <- n
+  } else {
+    draw <- sample(1:n, size = k, replace = TRUE)
+  }
+  
+  c1 <- c()
+  c2 <- c()
+  
+  for (i in 1:k) {
+    X.i <- c(X[draw[i] + 1], X[-c(1, draw[i] + 1)])
+    Y.i <- c(Y[draw[i] + 1], Y[-c(1, draw[i] + 1)])
+    Tstar.i <- c(Tstar[draw[i] + 1], Tstar[-c(1, draw[i] + 1)])
+    
+    # ols object
+    ols.i <- ols.est.alphahat(Tstar = Tstar.i, Y = Y.i, X = X.i)
+    
+    # estimates
+    alphahat.i <- ols.i$alphahat
+    est.i <- ols.i$est
+    
+    # bootstrap samples
+    if (np == TRUE) {
+      bootsamp <- boots.mix(B = B, ols = ols.i)
+    } else {
+      bootsamp <- boots(B = B, ols = ols.i)
+    }
+    
+    # risk conditions
+    vars.i <- c()
+    for (j in 1:3) {
+      vars.i <- c(vars.i, var(bootsamp[[j]], na.rm = TRUE))
+    }
+    names(vars.i) <- c('adj', 'wadj', 'IVW')
+    
+    # yhats
+    yhat2s <- sapply(c('adj', 'wadj', 'IVW'), function(d) nowcast.alpha(X = X.i, Y = Y.i, Tstar = Tstar.i, best = d)[[1]])
+    yhat1 <- nowcast.alpha(X = X.i, Y = Y.i, Tstar = Tstar.i, best = 'wadj')[[2]]
+    names(yhat1) <- 'no'
+    names(yhat2s) <- c('adj', 'wadj', 'IVW')
+    
+    # truth
+    truth <- ifelse(as.numeric(abs(Y.i[[1]][Tstar.i[1] + 2] - yhat1)) - as.numeric(abs(Y.i[[1]][Tstar.i[1] + 2] - yhat2s)) > 0,
+                    yes = 1, no = 0) 
[…]

### 2020-07-03 manuscript/manuscript.tex
addition of Section 3.4 and many revisions to abstract, intro, and Section 3.3, 4, 5, 6

@@
 \def\ind#1{\mathrm{1}(#1)} % indicator function
-\newcommand{\simiid}{\stackrel{iid}{\sim}} % IID 
+\newcommand{\simiid}{\stackrel{iid}{\sim}} %[] IID 
 \def\where{\text{ where }} % where
@@
   \item Need to add simulations. 
-  \item $\mu_{\alpha}=2$, $X_{i,t}\sim \Gamma(1,2)$, $\delta_i, \gamma_i \sim \normal{1}{0.5}$
-  \item $\sigma=10$ for the base case.
-  \item $\sigma_{\alpha}= (5, 10, 25, 50, 100)$
-  \item $\sigma= (5, 10, 25, 50, 100)$
 \end{enumerate}
@@
   \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
+  \item Addition of Section 3.4
 \end{enumerate}
@@
 Three shock-effects estimators were constructed for minimizing average forecast risk.
-We proposed conditions when our methodology works and estimators for risk-reduction quantities.
+We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities.
 Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed.
-The risk-reduction conditions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best.
+The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best.
+Leave-one-out cross validation with $k$ random  draws is proposed to estimate consistency of risk-reduction propositions and best consistency of voting the best shock-estimators, prospectively informing users the probabilities that this prospective evaluation is consistent with the reality.
 Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
@@
 The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three.
-The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap.
+We provide risk-reduction propositions that detail the conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three.
+The involved parameters in the risk-reduction propositions and risk-reduction quantities are estimated by parametric bootstrap.
 These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best, using estimates from bootstrap procedures.
+Furthermore, to inform the credibility of this prospective evaluation, we propose a leave-one-out cross validation with $k$ random draws to estimate the consistency of the risk-reduction propositions and best consistency of voting the best shock-effect estimators prospectively (see Definition \ref{consistency} and \ref{best consistency}), which tell the probabilities that the prospective evaluation is consistent with the reality.
 Our Monte Carlo simulation results show that  the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
@@
 \begin{align*}
-  \Delta_{\rm adj} 
+  \Delta(\hat{\alpha}_{\rm adj})
   = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
 \quad   \text{ and } \quad 
-  \Delta_{\rm wadj} 
+  \Delta(\hat{\alpha}_{\rm wadj})
   = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
@@
 \begin{align*}
- \Delta_{\rm IVW} 
+ \Delta(\hat{\alpha}_{\rm IVW})
   = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
@@
 
-In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction results, and estimate risk-reduction using plug-in approach in practice.
+In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction using plug-in approach in practice.
 Our procedure involves the resampling of residuals in the separate OLS fits.
@@
 \begin{align*}
-  \Delta_{\rm adj} 
+  \Delta(\hat{\alpha}_{\rm adj})
   &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
-  \hat{\Delta}_{\rm adj} 
+  \hat{\Delta}(\hat{\alpha}_{\rm adj})
  & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
 \end{align*}
-where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance for $\hat{\alpha}_{\rm adj}$.
-Suppose the $\hat{\Delta}_{\rm wadj}$ and $\hat{\Delta}_{\rm IVW}$ are estimators for $\Delta_{\rm wadj}$ and $\Delta_{\rm IVW}$, respectively.
-Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}_{\rm est}>0$ for $\text{est} \in \{\text{adj}, \text{wadj}, \text{IVW}\}$, and  the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities.
-Next, we discuss some potential problems of the bootstrap procedures.
+where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance for $\hat{\Delta}(\hat{\alpha}_{\rm adj})$.
+
+Suppose we have a pool of shock-effect estimators, $\mc{A}$, e.g., $\mc{A}= \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ in our study.
+We can determine which one is the best shock-effect estimator.
+Suppose the $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ and $\hat{\Delta}(\hat{\alpha}_{\rm IVW})$ are estimators for $\Delta(\hat{\alpha}_{\rm wadj}) $ and $\Delta(\hat{\alpha}_{\rm IVW})$, respectively.
+Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}(\hat{\alpha})>0$ for $\hat{\alpha}\in \mc{A}$.
+Besides, we can also select the best shock-effect estimator accordingly.
+Define
+\begin{align}
+	\hat{\alpha}_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \hat{\Delta}(\hat{\alpha}) \quad \text{ and } \quad  \alpha_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \Delta(\hat{\alpha}). \label{best}
+\end{align}
+That is, the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities whereas $\alpha_{\rm best}$ is the true best shock-effect estimator given observed post-shock response.
+See more discussions in Section \ref{loocv}.
 
@@
 There are some issues in using $\mc{B}_u$ when $\mathbf{W}^*$ falls in the boundary of the parameter space. See detailed discussions in Section \ref{discussion}.
+
+\subsection{Leave-one-out cross validation with $k$ random draws}
+\label{loocv}
+
+In this section, we introduce a powerful procedure for rendering prospective evaluations of the applicability of the proposed methods.
+First, we introduce the concept of consistency.
+Second, we detail the leave-one-out cross-validation with $k$ random draws to realize the estimation prospectively.
+
+Our risk-reduction propositions methodologies can be evaluated by \emph{consistency}.
+Risk-reduction propositions are decision-making procedures that might commit a type of error, which is similar to Type I or Type II error in a hypothesis test.
+Let $\hat{\alpha}$ be an estimator of $\alpha_1$ and $\delta_{\hat{\alpha}}$ is the corresponding risk-reduction proposition.
+If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) so that it make the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be \emph{inconsistent}.
+If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) so that it make the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be \emph{consistent}.
+These situations are depicted in the following table.
+\begin{center}
+  \begin{center}
+      \begin{tabular}{cc|c|c}
+        \hline
+        & & \multicolumn{2}{c}{Decision} \\
+        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
+                \hline
+     \multirow{2}{*}{Truth}  & $\Delta(\hat{\alpha})>0$ & Consistent & Inconsistent\\
+      \cline{3-4}
+      & $\Delta(\hat{\alpha})<0$  & Inconsistent & Consistent \\
+      \hline
+      \end{tabular}
+  \end{center}
+\end{center}
+Similar definitions can be adapted to the best shock-effect estimators.
+
+In this setting, judging whether $\delta_{\alpha}$ is consistent can be treated as a Bernoulli trial that reports 1 if $\delta_{\alpha}$ is consistent, and reports 0 if $\delta_{\alpha}$ is inconsistent.
+It is also true for selecting the best shock-effect estimator.
+It motivates us to define
+\begin{align*}
+	\mc{C}(\delta_{\alpha}) 
+	= I(\delta_{\hat{\alpha}} \text{ is consistent})
+ \quad \text{ and } \quad  	
+ \mc{C}(\mc{A}) 
+	= I(\hat{\alpha}_{\rm best} = \alpha_{\rm best})
+\end{align*}
+where $I(\cdot)$ is an indicator function, $\mc{A}$ is the pool of shock-effect estimators, $\alpha_{\rm best}$ is the true best shock-effect estimator, and $\hat{\alpha}_{\rm best}$ is the best shock-effect estimator selected by the maximum estimated risk-reduction,   see Section \ref{varbootstrap}.
+Then, we can define consistency and best consistency as in Definition \ref{consistency} and \ref{best consistency}.
+
+\begin{defn}
+\normalfont 	\label{consistency}The \emph{consistency} of 	the risk-reduction proposition $\delta_{\hat{\alpha}}$ is $\E{\mc{C}(\delta_{\hat{\alpha}})}$.
+\end{defn}
+
+\begin{defn}
+	\normalfont  \label{best consistency}Given $\mc{A}$ the pool of shock-effect estimators, the \emph{best consistency} is $\E{\mc{C}(\mc{A})}$.
+\end{defn}
+Consistency and best consistency are important parameters for users to evaluate the effectiveness of our risk-reduction propositions and estimated risk-reduction.
+If $\E{\mc{C}(\delta_{\hat{\alpha}})} > 0.5$, we  claim that $\delta_{\hat{\alpha}}$ is better than a random guess.
+If $\E{\mc{C}(\mc{A})} > 1/ |\mc{A}|$, we claim that the procedure of selecting the best shock-effect estimators is better than a random guess.
+Note that $\mc{C}(\delta_{\hat{\alpha}})$
+ and $\mc{C}(\mc{A})$ generally can be known only if the post-shock response is observed.
+But it is only feasible in a retrospective finding.
+It is even more difficult to construct a random sample to estimate $\E{\mc{C}(\delta_{\hat{\alpha}})}$ or $\E{\mc{C}(\mc{A})}$.
+Nevertheless, it is possible to estimate them using the procedure \emph{leave-one-out cross validation (LOOCV)}.
+
+Our proposed LOOCV tailors the standard LOOCV to our application.
+See details of standard LOOCV in Section 7.10 of \citet{hastie2009elements}.
+Recall in Section \ref{modelsetup} that we are given the data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining is those of the donor pool.
+For $m^{\rm th}$ iteration of LOOCV, where $m = \{1, \ldots, n\}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$.
+Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, for $\hat{\alpha}\in \mc{A}$, we can compute the consistency and best consistency as $\mc{C} ^{(-m)}(\delta_{\hat{\alpha}})$ and $\mc{C} ^{(-m)}(\mc{A})$  using the estimation procedures in Section \ref{varbootstrap}.
+The the LOOCV estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$  and $\E{\mc{C}(\mc{A})}$ are
+\begin{align*}
+	 \bar{\mc{C}}(\delta_{\hat{\alpha}})= \frac{1}{n} \sum_{m = 1}^n \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})
+	 \quad \text{ and } \quad \bar{\mc{C}}(\mc{A})= \frac{1}{n} \sum_{m = 1}^n \mc{C} ^{(-m)}(\mc{A}).
+\end{align*}
+Note that to satisfy $\mc{M}_{2}$ in Section \ref{modelsetup}, the candidates from donor pool has to be assumed to be mutually independent.
+Based on this assumption, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively \citep[Page 222]{msos}.
+
+However, LOOCV can be very computationally intensive when $n$ is large.
+In an analog to $k$-fold cross-validation as remedies for ordinary LOOCV, we propose a similar procedure \emph{LOOCV with $k$ random draws} to alleviate the computation burden.
+LOOCV with $k$ random draws differs in the selection of indices.
+The algorithms are outlined as follows.
+If $n \leq  k$, we set $k$ to be $n$.
+If $n > k$, we randomly sample without replacement $k$ elements from $\{1, \ldots, n\}$ to gather them into $\mc{J}$.
+For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$.
+The LOOCV with $k$ random draws estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$  and $\E{\mc{C}(\mc{A})}$ are
+\begin{align*}
+	 \bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})
+	 \quad \text{ and } \quad \bar{\mc{C}}^{(k)}(\mc{A})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\mc{A}).
+\end{align*}
+Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}^{}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively.
+The estimation bias should decrease as $k \to n$.
+In practice, $k=5$ or $k=10$ can be typical choices for LOOCV with $k$ random draws.
 
@@
 In that case, we do not consider such $b$ in computations of means and variances.
-Additionally, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
+Additionally, we generated the covariates from $\Gamma(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
 
 In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
-We used 200 replications of Monte Carlo simulations and $B = 500$ for computation; and report means and standard errors for estimated quantities accordingly.
+We used $30$ replications of Monte Carlo simulations and $B = 200$ for computation; and report means and standard errors for estimated quantities accordingly.
+$k=5$ is set up for LOOCV with $k$ random draws.
 
@@
 
-Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions.
-We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation.
-Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise.
-Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table.
-\begin{center}
-  \begin{center}
-      \begin{tabular}{cc|c|c}
-        \hline
-        & & \multicolumn{2}{c}{Decision} \\
-        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
-                \hline
-     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
-      \cline{3-4}
-      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
-      \hline
-      \end{tabular}
-  \end{center}
-\end{center}
-We report 1 for risk-reduction propositions to be consistent and 0 otherwise.
-Recall that in Section \ref{comparisons}, we could estimate the risk-reduction quantities, and therefore select the best estimator with the maximum risk-reduction quantities.
-It is also possible to confirm whether this decision is true in a simulation setting.
-Similarly, we report 1 for the decision of selecting the best shock-effect estimators  to be consistent and 0 otherwise.
-
-In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{1, 5, 10, 25, 100\}$ where we fix $\sigma$ to 1.
-The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown.
-It is shown in Table ?
-that as the donor pool size increases, the bias and consistency results improve with more precision.
-In contrast, the result gets poorer as  the variance of $\alpha_i$ increases.
-It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$.
-Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates.
-But it is reversed in the random design case.
-Moreover, notice that the consistency for voting the best estimator works poor when $n$ is small but improves significantly when $n$ is large.
+In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma$ to $10$.
+From Table ?, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we can observe that $\delta_{\hat{\alpha}}$ is highly consistent for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small.
+It is because when $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal.
+Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
+Nevertheless, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the $\delta_{\hat{\alpha}}$  become more inconsistent for $\hat{\alpha}\in \mc{A}$.
+It is to be expected since the bootstrap estimates become more biased.
+However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$.
+Fixing $\sigma_{\alpha}$, we can observe that $\delta_{\hat{\alpha}}$ becomes more consistent when $n$ increases.
+It is due to the robustness gain in estimation when $n$ increases.
+
+In this setting, comparing Table ? with Table ??, we can see that $\mc{B}_u$ does not differ a lot from $\mc{B}_c$.
 
@@
     Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
-    Leave-one-out consistency & 0.000 & 0.800 & 0.000
     \end{tabular}
@@
 
-Using the parametric bootstrap conditioned on the donor pool proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
+Using $\mc{B}_c$ proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
 Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $34.565$, $34.880$, and $34.139$, respectively.
 The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator.
-Moreover, the leave-one-out consistency of the risk-reduction propositions are 0.000, 0.800, and 0.000 for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$, respectively.
-It implies that we should only use the propositions for $\hat{\alpha}_{\text{wadj}}$.
-Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
+LOOCV with $k$ random draws was not implemented since the effective $n$ is $3$, a number too small to provide a credible estimation.
+We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
 
@@
 Moreover, the risk-reduction quantities are consistent with the reality as well.
-The results are also consistent with leave-one-out consistency for $\hat{\alpha}_{\text{wadj}}$ in that it  reduces the risk.
 
@@
 Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models.
-Our simple AR(1) model can be extended to AR($p$) settings %for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
-Similarly, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors.
-Moreover, the functional form for the mean function can be extended beyond the linear regression model under $\mc{M}_2$.
+Our simple AR(1) model can be extended to AR($p$) settings.
+%for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
+Moreover, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors.
+Similarly, LOOCV with $k$ random draws can be adapted to AR($p$).
+Besides, the functional form for the mean function for $y_{i,t}$ can be extended beyond the linear regression model under $\mc{M}_2$.
 Multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent.
 As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
+But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
 %This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool.
@@
 $\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
+In contrast, $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
 
@@
 
+Double bootstrap can be another general bootstrap alternative to the one proposed in Section \ref{varbootstrap}.
+For example, for $\mc{B}_u$, double bootstrap adds another layer of residual bootstrap between the donor pool non-parametric bootstrap and the original residual bootstrap.
+It enables an estimation for distribution of $\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
+In the framework of double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, we can check whether non-parametric 95\% confidence intervals contain 0.
+Likewise, we can compare two shock-effect estimators by checking whether their 95\% confidence intervals of risk-reduction overlap though an exhaustive ranking may not be feasible.
+We have attempted Monte Carlo simulations using the same setting in Section \ref{simulation} for the double bootstrap procedure, the results of which are quite similar to those of Section \ref{varbootstrap}.
+
 For the use of our methodology, caution should be dedicated to the construction of donor pool.
@@
 Moreover, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large.
-It is  due to the fact that plug-in estimation of  risk-reduction quantities gains more precision when $n$ becomes large.
+It is  due to the fact that plug-in estimation of  risk-reduction quantities in Section \ref{varbootstrap} gains more precision when $n$ becomes large.
 

### 2020-07-03 Rcode/dataanalysis.R

@@ -158,7 +158,6 @@ COP_close <- COP_close %>% mutate(start_day_20200309 = start_day_20200309)
 # time window
 TS1 <- COP_close[(start-30):(start), ]
 
-
 # shock-effect estimate
 m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day_20200309 + GSPC_Close + WTI_Close + WTI_Close_lag1 + GSPC_Close_lag1, 
                      data = TS1)
@@ -186,11 +185,12 @@ alpha_IVW <- sum(weights * estimates[, 1])
 Tstar.Date <- c("2020-03-05", "2008-03-13", "2008-09-05", "2008-09-11", "2008-09-25",  "2014-11-25")
 Tstar <- sapply(Tstar.Date, function(x) which(COP_close$Date == x))
 # X1
-X1 <- as.matrix(COP_close[c(Tstar[1], Tstar[1] + 1), c(3, 4)])
+X1 <- as.matrix(TS1[c(nrow(TS1) - 1, nrow(TS1)), c(3, 4)])
+# X1 <- as.matrix(COP_close[c(Tstar[1], Tstar[1] + 1), c(3, 4)])
 # X0
 X0 <- c()
 for (i in 1:5) {
-  X0[[i]] <- as.matrix(COP_close[c(Tstar[i + 1], Tstar[i + 1] + 1), c(3, 4)])
+ X0[[i]] <- as.matrix(COP_close[c(Tstar[i + 1], Tstar[i + 1] + 1), c(3, 4)])
 }
 
 # SCM
@@ -354,6 +354,7 @@ for (b in 1:B) {
   alphas[[2]] <- c(alphas[[2]], sum(alphahatsb * weights / sum(weights)))
   alphas[[3]] <- c(alphas[[3]], sum(Wstar * alphahatsb))
 }
+
 # Parameters
 means <- c()
 vars <- c()
@@ -377,423 +378,6 @@ names(est) <- c('adj', 'wadj', 'IVW')
 risk.reduction2(est = est, vars = vars) 
 
 
-# round 1
-Tstar.1 <- Tstar[-1]
-X1.1 <- as.matrix(COP_close[c(Tstar.1[1], Tstar.1[1] + 1), c(3, 4)])
-# X0
-X0.1 <- c()
-n <- length(Tstar.1) - 1
-for (i in 1:n) {
[…]

### 2020-07-03 Rcode/sim.study.R

@@ -361,7 +361,7 @@ cv <- function(k, X, Y, Tstar, np, B) {
     draw <- 1:n
     k <- n
   } else {
-    draw <- sample(1:n, size = k, replace = TRUE)
+    draw <- sample(1:n, size = k, replace = FALSE)
   }
   
   c1 <- c()
@@ -986,4 +986,150 @@ require('xtable')
 xtable(riskprop)
 xtable(pred)
 
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+# 8 cores -- use 7
+ncores <- detectCores() - 1
+registerDoParallel(cores = ncores)
+set.seed(2020)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 100
+# parameter setup
+sigma <- c(5, 10, 25, 50, 100)
+sigma.alphas <- c(5, 10, 25, 50, 100)
+sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, sigma = sigma))
+
+# simulation time
+system.time(
+  output <- lapply(1:nrow(sim_params), FUN = function(j) {
+    # parameters
+    sigma.alpha <- sim_params[j, 1]
+    sigma <- sim_params[j, 2]
+    # %do% evaluates sequentially
+    # %dopar% evaluates in parallel
+    # .combine results
+    out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+      # result
+      study <- sim.study.normal.gammaX(mu.gamma.delta = 1, 
+                                       mu.alpha = 2, sigma = sigma, 
+                                       sigma.alpha = sigma.alpha,
+                                       sigma.delta.gamma = 0.5, 
+                                       p = 13, B = 100, scale = 2, k = 5,
+                                       n = 10, np = FALSE)
+      return(study)
+    }
+    # return results
+    out
+  })
+)
+
+# store results
+# load packages
+require('readxl')
+require('writexl')
+setwd('/Users/mac/Desktop/Research/Post-Shock Prediction/')
+write_xlsx(lapply(output, as.data.frame), 'parametricssigma.xlsx')
+
+
+result <- c()
+for (i in 1:nrow(sim_params)) {
+  table <- output[[i]]
+  # means and sds
+  means <- apply(table, 2, function(x) mean(x))
+  sds <- apply(table, 2, function(x) sd(x))
+  result.i <- c()
+  for (j in 1:20) {
+    result.i <- cbind(result.i, paste0(round(means[j], digits = 3), 
[…]

### 2020-07-07 manuscript/manuscript.tex
addition of simulation discussions

@@
 % margin setup
-\geometry{margin=1in}
+\geometry{margin=0.8in}
 
@@
 
-Things to do:
-\begin{enumerate}
-  \item Need to add simulations. 
-\end{enumerate}
-
 \begin{center}
@@
   \item Addition of Section 3.4
+  \item A major addition of content to simulation.
 \end{enumerate}
@@
 \end{align}
-for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = 1(t = T_i^* + 1)$, 
+for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = I(t = T_i^* + 1)$, 
 $T_i^* < T_i$ and $\x_{i,t} \in \R^{p}$, $p \geq 1$.  We assume that the 
@@
 \end{align*}
-Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}^{}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively.
+Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively.
 The estimation bias should decrease as $k \to n$.
@@
 We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
-We consider $p=13$ and $\mu_{\alpha}=10$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.
-
-Parameter setup of our simulations are detailed as below.
+We consider $p=13$ and $\mu_{\alpha}=2$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.
+Parameter setup of our simulations is detailed as below.
 $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
@@
 Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
-However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$.
-In that case, we do not consider such $b$ in computations of means and variances.
 Additionally, we generated the covariates from $\Gamma(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
+Last, we set $\gamma_i, \delta_i\simiid  \normal{1}{0.5}$ and $\theta_i, \beta_i \sim \normal{0}{1}$.
 
@@
 
-In this section, we provide justification for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}).
-We will compare the result of using parametric bootstrap conditioned on the donor pool with the one without using the parameter setup discussed in Section \ref{simulation}.
+In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}).
+We will compare $\mc{B}_c$ with $\mc{B}_u$.
 
 In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma$ to $10$.
-From Table ?, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we can observe that $\delta_{\hat{\alpha}}$ is highly consistent for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small.
-It is because when $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal.
+Note that $\E{\E{\alpha_1}}=54$, where the last expectation is operated under the density of the covariates.
+In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.
+
+\begin{table}[t]
+\caption{30 Monte Carlo simulations for $\mc{B}_c$ with varying $n$ and $\sigma_{\alpha}$ (risk-reduction propositions $\delta_{\hat{\alpha}}$)} \vspace{.2cm} \label{table1}
+\begin{center}
+\begin{tabular}{cc|ccc|cccc}
+ $n$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ &  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.15cm]
+  \hline
+  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.90 (0.02) & 0.89 (0.03) & 0.35 (0.04) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.89 (0.03) & 0.89 (0.03) & 0.37 (0.05) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.78 (0.03) & 0.83 (0.03) & 0.78 (0.03) & 0.44 (0.05) \\ 
+  & 50  & 0.90 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.66 (0.04) & 0.65 (0.04) & 0.65 (0.04) & 0.45 (0.06) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.80 (0.07) & 0.57 (0.04) & 0.53 (0.04) & 0.57 (0.04) & 0.49 (0.05) \\[.3cm]  
+  \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.92 (0.02) & 0.91 (0.02) & 0.25 (0.03) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.89 (0.03) & 0.89 (0.02) & 0.29 (0.03) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.75 (0.03) & 0.78 (0.03) & 0.77 (0.04) & 0.3 (0.04) \\ 
+  & 50  & 0.83 (0.07) & 1 (0) & 0.80 (0.07) & 0.59 (0.04) & 0.63 (0.04) & 0.59 (0.04) & 0.37 (0.05) \\ 
+  & 100  & 0.80 (0.07) & 0.93 (0.05) & 0.80 (0.07) & 0.47 (0.04) & 0.51 (0.04) & 0.46 (0.04) & 0.41 (0.05) \\[.3cm]  
+  \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.93 (0.02) & 0.91 (0.02) & 0.31 (0.05) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.02) & 0.89 (0.03) & 0.87 (0.02) & 0.31 (0.04) \\ 
+ & 25  & 1 (0) & 1 (0) & 1 (0) & 0.75 (0.03) & 0.78 (0.03) & 0.76 (0.03) & 0.37 (0.04) \\ 
+  & 50  & 0.933 (0.05) & 1 (0) & 0.9 (0.06) & 0.61 (0.04) & 0.69 (0.03) & 0.64 (0.04) & 0.41 (0.04) \\ 
+  & 100  & 0.67 (0.09) & 1 (0) & 0.63 (0.09) & 0.55 (0.04) & 0.51 (0.04) & 0.55 (0.04) & 0.47 (0.04) \\[.3cm]  
+  \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.94 (0.02) & 0.95 (0.02) & 0.29 (0.04) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.91 (0.02) & 0.93 (0.02) & 0.30 (0.04) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.78 (0.04) & 0.79 (0.04) & 0.77 (0.04) & 0.31 (0.04) \\ 
+  & 50  & 0.90 (0.06) & 1 (0) & 0.9 (0.06) & 0.57 (0.04) & 0.60 (0.04) & 0.58 (0.04) & 0.34 (0.04) \\ 
+    & 100  & 0.83 (0.07) & 1 (0) & 0.80 (0.07) & 0.49 (0.04) & 0.48 (0.04) & 0.50 (0.04) & 0.39 (0.03) \\ 
+\end{tabular}  
+\end{center}
+ \vspace{-.5cm}
+\end{table}
+
+ Table \ref{table1} shows the results, with the 3rd to 5th column representing the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ (i.e., guess of $\delta_{\hat{\alpha}}$), and the 6th to 9th columns representing the LOOCV consistency and best consistency following notations in Section \ref{loocv}.
+First, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we  observe that $\delta_{\hat{\alpha}}$ is highly consistent for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small  from Table \ref{table1}.
+The reasons can be explained as follows.
+When $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal according to construction of $\hat{\alpha}_{\rm wadj}$ in Section \ref{constructionofestimators}.
 Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
-Nevertheless, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the $\delta_{\hat{\alpha}}$  become more inconsistent for $\hat{\alpha}\in \mc{A}$.
+However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the $\delta_{\hat{\alpha}}$  become more inconsistent for $\hat{\alpha}\in \mc{A}$.
 It is to be expected since the bootstrap estimates become more biased.
 However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$.
-Fixing $\sigma_{\alpha}$, we can observe that $\delta_{\hat{\alpha}}$ becomes more consistent when $n$ increases.
+Second, fixing $\sigma_{\alpha}$, we can observe that $\delta_{\hat{\alpha}}$ becomes more consistent when $n$ increases.
 It is due to the robustness gain in estimation when $n$ increases.
 
-In this setting, comparing Table ? with Table ??, we can see that $\mc{B}_u$ does not differ a lot from $\mc{B}_c$.
+\begin{table}[t]
+    \caption{30 Monte Carlo simulations for $\mc{B}_c$ with varying $\sigma$ and $\sigma_{\alpha}$} \label{table2} \vspace{-.2cm}
+  \begin{center}
+\begin{tabular}{cc|ccc|cccc}
+ $\sigma$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ &  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.15cm]
+  \hline
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.99 (0.01) & 0.99 (0.01) & 0.99 (0.01) & 0.4 (0.04) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.95 (0.02) & 0.92 (0.02) & 0.46 (0.04) \\ 
+    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.83 (0.03) & 0.89 (0.02) & 0.83 (0.03) & 0.43 (0.04) \\ 
+   & 50  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.67 (0.04) & 0.69 (0.03) & 0.67 (0.04) & 0.38 (0.04) \\ 
+    & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.77 (0.08) & 0.52 (0.04) & 0.51 (0.04) & 0.51 (0.05) & 0.51 (0.05) \\[.3cm] 
+    \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.93 (0.02) & 0.93 (0.02) & 0.27 (0.03) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 0.37 (0.04) \\ 
+    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.78 (0.03) & 0.82 (0.03) & 0.79 (0.03) & 0.29 (0.04) \\ 
+    & 50  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.66 (0.04) & 0.67 (0.04) & 0.66 (0.04) & 0.32 (0.04) \\ 
+    & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.54 (0.05) & 0.54 (0.04) & 0.55 (0.04) & 0.43 (0.05) \\[.3cm] 
+    \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 1 (0) & 0.78 (0.03) & 0.77 (0.03) & 0.79 (0.03) & 0.22 (0.03) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.81 (0.03) & 0.79 (0.03) & 0.81 (0.03) & 0.21 (0.03) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.72 (0.03) & 0.77 (0.03) & 0.71 (0.03) & 0.25 (0.04) \\ 
+    & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.57 (0.04) & 0.52 (0.04) & 0.35 (0.04) \\ 
+    & 100  & 0.9 (0.06) & 1 (0) & 0.87 (0.06) & 0.54 (0.04) & 0.54 (0.04) & 0.56 (0.04) & 0.39 (0.05) \\[.3cm] 
+    \multirow{5}{*}{50} & 5  & 0.83 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.54 (0.04) & 0.57 (0.04) & 0.55 (0.04) & 0.19 (0.03) \\ 
+    & 10  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.53 (0.04) & 0.55 (0.05) & 0.53 (0.04) & 0.23 (0.03) \\ 
+    & 25  & 0.73 (0.08) & 0.8 (0.07) & 0.73 (0.08) & 0.58 (0.04) & 0.58 (0.04) & 0.57 (0.04) & 0.21 (0.03) \\ 
+    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.04) & 0.53 (0.04) & 0.6 (0.04) & 0.29 (0.05) \\ 
+    & 100  & 0.5 (0.09) & 0.73 (0.08) & 0.53 (0.09) & 0.51 (0.05) & 0.48 (0.05) & 0.51 (0.05) & 0.31 (0.04) \\[.3cm] 
+    \multirow{5}{*}{100} & 5  & 0.43 (0.09) & 0.37 (0.09) & 0.43 (0.09) & 0.47 (0.04) & 0.47 (0.04) & 0.47 (0.04) & 0.19 (0.03) \\ 
+    & 10  & 0.63 (0.09) & 0.6 (0.09) & 0.67 (0.09) & 0.51 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 0.23 (0.03) \\ 
+    & 25  & 0.57 (0.09) & 0.6 (0.09) & 0.57 (0.09) & 0.51 (0.04) & 0.53 (0.04) & 0.49 (0.04) & 0.21 (0.04) \\ 
+    & 50  & 0.53 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.47 (0.04) & 0.49 (0.05) & 0.49 (0.05) & 0.19 (0.03) \\ 
+    & 100  & 0.63 (0.09) & 0.63 (0.09) & 0.63 (0.09) & 0.43 (0.04) & 0.41 (0.04) & 0.45 (0.04) & 0.17 (0.03) \\ 
+\end{tabular}
+  \end{center}  
+   \vspace{-.5cm}
+\end{table}
+
+Interestingly, we observe different patterns of $\bar{\mc{C}}^{(k)}(\mc{A})$ as opposed to $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$: (1) as $n$ increases, $\bar{\mc{C}}^{(k)}(\mc{A})$ decreases; and (2) as $\sigma_{\alpha}$ increases, $\bar{\mc{C}}^{(k)}(\mc{A})$ increases.
+It is possible  when $n$ is small or $\sigma_{\alpha}$ is large, the differences among $\hat{\Delta}(\hat{\alpha})$ for  $\hat{\alpha}\in \mc{A}$ are large so that the ranking gains more precision.
+It is because in these situations, the estimation of bootstrap estimates is less precise so that the variance of $\hat{\Delta}(\hat{\alpha})$ is larger.
+
+Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down.
+Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$.
+But it is not present for $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ since we applied the fact  $\hat{\alpha}_{\rm wadj}$ is unbiased for $\E{\alpha_1}$ from Proposition \ref{unbiased}.
+Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative.
+Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of consistencies between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
+For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.90 \times 0.66 = 0.594$ from table \ref{table1}.
+In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.
+
+In the second experiment, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n$ to $10$.
+Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.
+
+From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}(\mc{A})$ will  decrease, which is a pattern similar to one shown in the first experiment.
+Furthermore, as $\sigma$ increases fixing $\sigma_{\alpha}$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}(\mc{A})$ decrease as well.
+Note that the consistency or best consistency  hinges on the estimation of the parameters.
+Since $\hat{\alpha}_{\rm wadj}$  is a linear combination of OLS estimates, as $\sigma$ increases, $\var{\hat{\alpha}_{\rm wadj}}$ increases as well.
+Therefore, $\hat{\alpha}_{\rm wadj}$ become more volatile and its estimation of $\E{\alpha_1}$ can be less reliable.
+Those reasons can explain  why an increase of $\sigma_{\alpha}$ contributes to a decrease of  $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}(\mc{A})$.
+
+With respect to averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases.
+It is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
+The reasons can be outlined as below.
+Recall in Section \ref{conditionsm2122}, the conditions of risk-reduction propositions involve $(\E{\alpha_1})^2 > \var{\hat{\alpha}} + (\E{\hat{\alpha}}-\E{\alpha_1})^2$ for $\hat{\alpha}\in \mc{A}$, where we note that those parameters are \emph{true} ones but not estimated ones.
+Notice that $\var{\hat{\alpha}}$ is  a function of $\sigma$ since $\hat{\alpha}$ is estimated by OLS.
+Therefore, it explains the reason why the increase of $\sigma$ would result in a decrease of averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ since the conditions are not likely to hold when  $\var{\hat{\alpha}}$ increases.
+
+\begin{table}[t]
+ \caption{30 Monte Carlo simulation with varying $n$ and $\sigma_{\alpha}$ (distance to $y_{1, T_1^*+1}$)} \label{table3}
+ \begin{center}
+\begin{tabular}{cc|cccc}
+  $n$   & $\sigma_{\alpha}$  & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.3cm]  
+  \hline
+  \multirow{5}{*}{5} & 5  & 51.92 (4.04) & 19.23 (2.55) & 20.64 (2.76) & 19.36 (2.52) \\ 
+  & 10  &  52.58 (4.35) & 21.565 (2.58) & 23.38 (2.86) & 21.72 (2.50) \\ 
+  & 25  &  55.02 (5.84) & 30.30 (3.59) & 31.99 (4.36) & 30.20 (3.50) \\ 
+  & 50  & 64.42 (8.11) & 50.00 (5.78) & 52.56 (6.92) & 49.55 (5.70) \\ 
+  & 100  & 91.51 (13.20) & 94.27 (10.41) & 97.26 (12.57) & 93.61 (10.27) \\[.3cm]  
+  \multirow{5}{*}{10} & 5 & 52.34 (4.00) & 17.23 (2.96) & 18.55 (2.84) & 17.39 (2.95) \\ 
+  & 10 &  52.59 (4.05) & 19.02 (3.24) & 20.95 (3.14) & 19.23 (3.24) \\ 
+  & 25 & 54.07 (4.97) & 27.66 (4.55) & 31.79 (4.47) & 27.85 (4.61) \\ 
+  & 50 &  60.32 (7.53) & 47.70 (7.04) & 52.97 (7.54) & 47.78 (7.17) \\ 
+  & 100 & 85.60 (12.99) & 89.86 (12.82) & 100.74 (13.61) & 90.40 (12.91) \\[.3cm]  
+  \multirow{5}{*}{15} & 5 & 49.86 (4.01) & 18.07 (2.88) & 18.38 (2.71) & 18.04 (2.88) \\ 
+  & 10 & 48.73 (4.30) & 19.45 (2.97) & 19.35 (2.86) & 19.32 (3.00) \\ 
+  & 25 &  47.06 (5.13) & 26.16 (3.31) & 26.81 (3.13) & 26.23 (3.33) \\ 
+  & 50 &  48.75 (6.86) & 40.27 (4.43) & 42.09 (4.49) & 40.77 (4.38) \\ 
+  & 100 &  64.29 (11.11) & 68.85 (8.27) & 74.08 (8.72) & 69.91 (8.14) \\[.3cm]  
+  \multirow{5}{*}{25} & 5 & 57.60 (6.94) & 21.58 (5.90) & 20.00 (5.86) & 21.58 (5.90) \\ 
+  & 10 &  56.80 (7.01) & 22.20 (5.97) & 20.47 (5.89) & 22.22 (5.97) \\ 
+  & 25 &  56.58 (7.49) & 28.96 (6.49) & 27.06 (6.19) & 29.03 (6.48) \\ 
+  & 50 &  64.33 (8.75) & 47.16 (8.28) & 46.30 (7.26) & 47.35 (8.26) \\ 
+  & 100 & 95.61 (13.02) & 90.10 (13.29) & 86.81 (11.75) & 90.55 (13.23) \\ 
+\end{tabular}	
+ \end{center}
+ \vspace{-.5cm}
+\end{table}
+
+Simulation for $\mc{B}_u$ with the same parameter setup as that of $\mc{B}_c$ are implemented. See table \ref{table6} and table \ref{table7} for results. Comparing table \ref{table1}
+ and table \ref{table6} yields that when $n$ is small ($n = 5$ or $n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_c$ with statistical evidence.
+For other situations, $\mc{B}_u$  and $\mc{B}_c$  are rather similar.
+It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool.
+Concerning  table \ref{table2} and table \ref{table7}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_c$  when $\sigma$ increases.
+It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$.
+However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_c$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$.
+In conclusion, $\mc{B}_u$ is better than $\mc{B}_c$ when the signal of the covariates is strong and $n$ is small; otherwise, they are similar.
+See more discussions for differences between $\mc{B}_u$ and $\mc{B}_c$ in Section \ref{discussion}.
 
 \subsection{Simulation for prediction}
+\label{simulationforprediction}
+
+\begin{table}[t]
+ \caption{30 Monte Carlo simulation with varying $n$ and $\sigma_{\alpha}$ (distance to $y_{1, T_1^*+1}$)} \label{table4}
+ \begin{center}
+\begin{tabular}{cc|cccc}
+  $\sigma$   & $\sigma_{\alpha}$  & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.3cm]  
+  \hline
+ \multirow{5}{*}{5}  & 5  & 53.27 (2.59) & 10.91 (1.70) & 11.77 (1.55) & 10.8 (1.69) \\ 
+   & 10  & 50.86 (3.83) & 18.06 (2.18) & 17.26 (2.17) & 18.25 (2.17) \\ 
+    & 25  & 60.52 (3.97) & 16.09 (2.40) & 19.83 (3.05) & 15.87 (2.38) \\ 
+     & 50  & 54.65 (6.95) & 51.79 (6.87) & 53.83 (7.26) & 52.6 (6.91) \\ 
+     & 100  & 104.73 (13.00) & 88.31 (12.16) & 88.88 (12.63) & 86.72 (12.35) \\[.3cm] 
+   \multirow{5}{*}{10}  & 5  & 58.17 (4.18) & 18.17 (2.61) & 16.59 (2.39) & 18.09 (2.63) \\ 
+    & 10  & 52.81 (4.07) & 19.05 (2.49) & 19.67 (2.66) & 18.95 (2.53) \\ 
+     & 25  & 61.53 (5.69) & 28.55 (4.07) & 31.82 (4.27) & 28.76 (4.07) \\ 
+     & 50  & 56.31 (8.03) & 47.33 (4.89) & 41.44 (4.39) & 46.86 (4.79) \\ 
+     & 100  & 84.38 (11.62) & 82.91 (11.77) & 84.5 (12.39) & 84.3 (11.93) \\[.3cm] 
+   \multirow{5}{*}{25}  & 5  & 56.35 (6.1) & 25.54 (4.06) & 30.49 (4.61) & 25.94 (4.02) \\ 
+     & 10  & 49.8 (5.24) & 25.04 (4.38) & 26.74 (3.64) & 24.86 (4.38) \\ 
+     & 25  & 54.21 (6.51) & 44.17 (6.66) & 43.41 (6.95) & 43.89 (6.63) \\ 
+     & 50  & 66.51 (7.86) & 46.19 (8.04) & 44.83 (9.31) & 46.54 (8.27) \\ 
+     & 100  & 109.21 (13.29) & 78.47 (12.45) & 83.99 (12.00) & 78.57 (12.75) \\[.3cm] 
+   \multirow{5}{*}{50}  & 5  & 75.29 (10.75) & 63.51 (8.30) & 64.25 (8.88) & 63.32 (8.40) \\ 
+     & 10  & 57.59 (6.00) & 48.51 (8.32) & 50.58 (8.63) & 48.08 (8.36) \\ 
+     & 25  & 77.21 (12.03) & 54.73 (9.47) & 54.76 (10.24) & 54.2 (9.62) \\ 
+     & 50  & 90.48 (10.21) & 68.88 (9.20) & 68.28 (10.48) & 68.8 (9.28) \\ 
+     & 100  & 111.09 (17.54) & 102.47 (16.68) & 110.15 (15.87) & 101.53 (16.52) \\[.3cm] 
+   \multirow{5}{*}{100}  & 5  & 214.07 (67.40) & 195.46 (67.65) & 197.51 (68.45) & 196.58 (67.51) \\ 
+     & 10  & 120.85 (15.39) & 114.79 (15.51) & 119.19 (15.75) & 114.02 (15.74) \\ 
+     & 25  & 97.84 (13.75) & 95.02 (14.88) & 100.04 (16.94) & 96.23 (14.71) \\ 
+     & 50  & 141.22 (24.51) & 136.11 (25.73) & 150.62 (27.62) & 135.26 (25.39) \\ 
+     & 100  & 95.53 (12.80) & 103.01 (14.12) & 103.31 (16.27) & 105.79 (14.32) \\
+\end{tabular}	
+ \end{center}
+  \vspace{-.5cm}
+\end{table}
 
 In this section, we report prediction results for our methods in the simulation.
-Specifically, we are interested in the distance between $\alpha_1$ and our shock-effect estimators, and the distance between $y_{1,T_1^*+1}$ and $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$.
-
-In the first experiment, Table ?
-shows similar results to  Section  \ref{parametricbootstrapsimulation} that the prediction and distance to $\alpha_1$ gets better as $n$ increases but worser when the variance of $\alpha_i$ gets larger.
+Specifically, we are interested in the distance between the true response $y_{1,T_1^*+1}$ and the adjusted forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$.
+
+In the first experiment, table \ref{table3} shows that similar to Section \ref{parametricbootstrapsimulation}, as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
+When $\sigma_{\alpha}= 5, 10, 25$, forecasts using $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are always better than the original forecast significantly.
+But it does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
+It is reasonable in that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
+Nevertheless, unlike what is detected in Section \ref{parametricbootstrapsimulation}, no statistical evidence has been found to support the claim that $n$ matters in prediction.
+In other words, $n$ matters in producing reliable decision-making of $\delta_{\hat{\alpha}}$  rather than reliable prediction.
+
+Note that there is no statistical evidence supporting for differences among $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
+This observation corresponds to the fact that $\bar{\mc{C}}(\mc{A})$ is small and following analysis in Section \ref{parametricbootstrapsimulation}.
+When their performances do not differ much, the precision of ranking is small.
+In this scenario, for a more reasonable statistical inference, one may opt for a double bootstrap instead to approximate the distribution of $\Delta(\hat{\alpha})$ and compare estimators by checking whether their 95\% confidence intervals overlap.
+See more details in Section \ref{discussion}.
+
+In the second experiment, table \ref{table4} shows similar results for prediction to those in the first expeirment, for the case of varying $\sigma_{\alpha}$ but fixing $\sigma$, and the case of varying $\sigma$ but fixing $\sigma_{\alpha}$.
+When $\sigma$ increases with fixing $\sigma_{\alpha}$, it is likely that the degree of variation of $y_{1,t}$ exceeds the extent of adjustment improvement $\hat{\alpha}$ can contribute to for $\hat{\alpha}\in \mc{A}$.
+It can be confirmed by looking into  the case of $\sigma= 50, 100$ as opposed to the case for $\sigma= 5, 10, 25$ where adjusted forecasts outperform original forecasts.
+Adjusted forecasts can be worse than original forecast if the variation of $y_{i,t}$ is large and the signal of the covariates is very small.
+See for the case  of $\sigma=100$ and $\sigma_{\alpha}=100$ in table \ref{table4}.
 
@@
 \begin{table}[H]
-  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
+  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table5}
   \begin{center}
@@
 In contrast, $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
+For other differences,  Section \ref{parametricbootstrapsimulation} shows that $\mc{B}_u$ is better than $\mc{B}_c$ when the signal of the covariates is strong and $n$ is small; otherwise, they are quite similar.
 
@@
 
+\subsection{Simulations tables for $\mc{B}_u$}
+\label{simulationappendix}
+
+\begin{table}[H]
+\caption{30 Monte Carlo simulations  for $\mc{B}_u$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table6}
+\begin{center}
+\begin{tabular}{cc|ccc|cccc}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{4}{|c}{LOOCV with $k$ random draws}  \\ 
+ $n$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ &  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.15cm]
+  \hline
+  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.96 (0.02) & 0.92 (0.02) & 0.36 (0.05) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.90 (0.02) & 0.92 (0.02) & 0.90 (0.02) & 0.40 (0.04) \\ 
+    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.80 (0.02) & 0.81 (0.02) & 0.80 (0.03) & 0.43 (0.04) \\ 
+    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.87 (0.06) & 0.55 (0.05) & 0.57 (0.05) & 0.55 (0.05) & 0.38 (0.05) \\ 
+    & 100  & 0.47 (0.09) & 0.73 (0.08) & 0.47 (0.09) & 0.48 (0.05) & 0.48 (0.04) & 0.46 (0.04) & 0.37 (0.05) \\[.3cm] 
+    \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.95 (0.02) & 0.95 (0.02) & 0.33 (0.04) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.91 (0.03) & 0.92 (0.03) & 0.33 (0.04) \\ 
+    & 25  & 0.90 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.77 (0.04) & 0.79 (0.04) & 0.75 (0.05) & 0.31 (0.04) \\ 
+    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.55 (0.04) & 0.64 (0.04) & 0.55 (0.05) & 0.31 (0.04) \\ 
+    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.53 (0.04) & 0.53 (0.05) & 0.51 (0.04) & 0.33 (0.04) \\[.3cm] 
+    \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.93 (0.02) & 0.92 (0.02) & 0.31 (0.05) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.92 (0.02) & 0.30 (0.03) \\ 
+   & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.83 (0.03) & 0.83 (0.03) & 0.35 (0.04) \\ 
+  & 50  & 0.90 (0.06) & 0.93 (0.05) & 0.90 (0.06) & 0.71 (0.03) & 0.67 (0.04) & 0.69 (0.04) & 0.33 (0.04) \\ 
+    & 100  & 0.70 (0.09) & 0.73 (0.08) & 0.70 (0.09) & 0.54 (0.05) & 0.61 (0.04) & 0.54 (0.05) & 0.31 (0.05) \\[.3cm] 
+   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.90 (0.03) & 0.91 (0.03) & 0.90 (0.03) & 0.27 (0.04) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 0.30 (0.03) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.73 (0.03) & 0.74 (0.04) & 0.73 (0.03) & 0.29 (0.03) \\ 
+    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.83 (0.07) & 0.55 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 0.29 (0.04) \\ 
+    & 100  & 0.77 (0.08) & 0.73 (0.08) & 0.77 (0.08) & 0.48 (0.05) & 0.49 (0.04) & 0.49 (0.05) & 0.31 (0.05) \\ 
+\end{tabular}
+   \end{center}
+      \vspace{-.5cm}
+\end{table}
+
+\begin{table}[H]
+\caption{30 Monte Carlo simulations  for $\mc{B}_u$ with varying $\sigma$ and $\sigma_{\alpha}$} \label{table7}
+\begin{center}
+\begin{tabular}{cc|ccc|cccc}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{4}{|c}{LOOCV with $k$ random draws}  \\ 
+ $\sigma$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ &  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.3cm]
+  \hline
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.99 (0.01) & 0.99 (0.01) & 0.99 (0.01) & 0.39 (0.05) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.97 (0.01) & 0.97 (0.01) & 0.97 (0.01) & 0.34 (0.04) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.81 (0.04) & 0.82 (0.04) & 0.81 (0.04) & 0.29 (0.04) \\ 
+    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.57 (0.05) & 0.67 (0.04) & 0.57 (0.05) & 0.34 (0.04) \\ 
+    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.51 (0.04) & 0.53 (0.05) & 0.50 (0.04) & 0.35 (0.05) \\[.3cm] 
+   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.95 (0.02) & 0.95 (0.02) & 0.33 (0.04) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.91 (0.03) & 0.92 (0.03) & 0.33 (0.04) \\ 
+    & 25  & 0.90 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.77 (0.04) & 0.79 (0.04) & 0.75 (0.05) & 0.31 (0.04) \\ 
+    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.55 (0.04) & 0.64 (0.04) & 0.55 (0.05) & 0.31 (0.04) \\ 
+    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.53 (0.04) & 0.53 (0.05) & 0.51 (0.04) & 0.33 (0.04) \\[.3cm] 
+   \multirow{5}{*}{25}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.79 (0.04) & 0.78 (0.04) & 0.77 (0.04) & 0.19 (0.04) \\ 
+    & 10  & 0.97 (0.03) & 0.97 (0.03) & 0.97 (0.03) & 0.75 (0.04) & 0.75 (0.04) & 0.73 (0.05) & 0.20 (0.04) \\ 
+   & 25  & 0.90 (0.06) & 0.93 (0.05) & 0.90 (0.06) & 0.66 (0.05) & 0.69 (0.05) & 0.66 (0.05) & 0.30 (0.05) \\ 
+    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.80 (0.07) & 0.55 (0.05) & 0.64 (0.05) & 0.55 (0.05) & 0.34 (0.05) \\ 
+    & 100  & 0.60 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.48 (0.04) & 0.52 (0.04) & 0.47 (0.04) & 0.31 (0.04) \\[.3cm] 
+   \multirow{5}{*}{50}  & 5  & 0.73 (0.08) & 0.73 (0.08) & 0.77 (0.08) & 0.57 (0.05) & 0.57 (0.05) & 0.58 (0.05) & 0.24 (0.04) \\ 
+    & 10  & 0.73 (0.08) & 0.73 (0.08) & 0.73 (0.08) & 0.55 (0.05) & 0.55 (0.05) & 0.55 (0.05) & 0.23 (0.03) \\ 
+    & 25  & 0.77 (0.08) & 0.70 (0.09) & 0.73 (0.08) & 0.48 (0.05) & 0.51 (0.05) & 0.47 (0.05) & 0.24 (0.04) \\ 
+    & 50  & 0.77 (0.08) & 0.73 (0.08) & 0.73 (0.08) & 0.46 (0.05) & 0.53 (0.04) & 0.47 (0.05) & 0.25 (0.04) \\ 
+    & 100  & 0.57 (0.09) & 0.70 (0.09) & 0.57 (0.09) & 0.46 (0.05) & 0.49 (0.03) & 0.45 (0.05) & 0.33 (0.05) \\[.3cm] 
+  \multirow{5}{*}{100}  & 5  & 0.63 (0.09) & 0.60 (0.09) & 0.63 (0.09) & 0.46 (0.05) & 0.52 (0.04) & 0.48 (0.05) & 0.23 (0.04) \\ 
+    & 10  & 0.60 (0.09) & 0.60 (0.09) & 0.63 (0.09) & 0.46 (0.05) & 0.53 (0.04) & 0.46 (0.05) & 0.24 (0.04) \\ 
+    & 25  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.45 (0.05) & 0.54 (0.04) & 0.47 (0.05) & 0.21 (0.04) \\ 
+    & 50  & 0.57 (0.09) & 0.53 (0.09) & 0.57 (0.09) & 0.49 (0.04) & 0.54 (0.04) & 0.47 (0.05) & 0.23 (0.03) \\ 
+    & 100  & 0.43 (0.09) & 0.53 (0.09) & 0.43 (0.09) & 0.52 (0.05) & 0.55 (0.03) & 0.51 (0.05) & 0.27 (0.04) \\
+\end{tabular}
+   \end{center}
+   \vspace{-.5cm}
+\end{table}
+
+\newpage
+
 \bibliographystyle{plainnat}

### 2020-07-09 manuscript/manuscript.tex
updated manuscript; comments are provided; next steps are provided

--- 2020-06-28 manuscript/manuscript.tex
@@
 
-Things to do:
-\begin{enumerate}
-  \item Need to add simulations. 
-  \item $\mu_{\alpha}=2$, $X_{i,t}\sim \Gamma(1,2)$, $\delta_i, \gamma_i \sim \normal{1}{0.5}$
-  \item $\sigma=10$ for the base case.
-  \item $\sigma_{\alpha}= (5, 10, 25, 50, 100)$
-  \item $\sigma= (5, 10, 25, 50, 100)$
-\end{enumerate}
-
 \begin{center}
@@
 \begin{enumerate}
-  \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
+  \item Revisions to the manuscript.
+  \item Detailed comments for further revisions are included.
+  \item The Supplementary Materials document has been expanded. More comments are included in that document.
+  \item The fixed donor pool bootstrap procedure (previously called $B_c$) is moved to the Supplementary Materials document.
+  \item Commentary about bootstrap consistency is removed, I do not think that it is necessary.
+  \item The ``best estimator'' materials are removed, this procedure did not perform too well.
 \end{enumerate}
+
+\noindent{\bf Things to do}: We also need a simulation corresponding to model $\mc{M}_1$ in which we investigate the performance of all adjustment estimators.
+We should also do a very small simulation that checks whether or not the weighted adjustment estimator does well when we expect $\mathbf{W}^*$ to be on the boundary.
 
@@
 One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error.
-Then, we discuss some frequently used methodologies that may be applied in this situation.
+%Then, we discuss some frequently used methodologies that may be applied in this situation.
 %When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.
@@
 
-As alternatives to forecast combination, data integration and time series pooling for forecasting is a broad domain of research including ideas from many areas.
+Data integration and time series pooling for forecasting is a broad domain of research including ideas from many areas.
 Time-series pooling methods are frequently used for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.
-Recent researches in data integration have investigated versatile methods to combine knowledge from multiple datasets for better prediction, whose ideas are similar to ours.
+Recent developments in data integration have investigated versatile methods to combine knowledge from multiple datasets for better prediction.
+%whose ideas are similar to ours.
 For instance, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
 to improve predictive precision of COVID-19 infection trajectories for different countries.
-A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
+A similar setup may be appropriate for post-shock prediction but may be too dependent upon model specification for the shock distribution.
 %, and conditions for predictive improvement are generally hard to know. 
@@
 
-Up to the scale of the shock, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock.
+Up to the scale of the shock, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock (\textbf{What does Up to the scale of the shock mean?
+Why will the model-free technique not work ideally?}).
 To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration.
 We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure.
-The main idea is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, to the original forecast at the known shock time point.
+The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point.
 
@@
 The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three.
-The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap.
-These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best, using estimates from bootstrap procedures.
-Our Monte Carlo simulation results show that  the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
+We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast, and estimate risk-reduction quantities to find the best technique out of the three.
+The involved parameters in the risk-reduction propositions and risk-reduction quantities are estimated by parametric bootstrap.
+These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed.
+Furthermore, to inform the credibility of this prospective evaluation, we propose a leave-one-out cross validation with $k$ random draws to estimate the performance of the risk-reduction propositions and best consistency of voting the best shock-effect estimators prospectively.
+Our Monte Carlo simulation results show that the risk-reduction conditions are highly consistent when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
 Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large.
-In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well.
+We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a shock on March 9th, 2020.
+The proposed three aggregation techniques work much better than no adjustment in this example.
+We also use this example to demonstrate settings in which the shock-effect may be decomposed into separate estimable parts.
 We now motivate our aggregation techniques.
@@
 Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology.
-This figure depicts a time-series that experienced a ``shock'' at time point $T_1^*+1 = 126$.
+This figure depicts a time-series that experienced a shock at time point $T_1^*+1 = 126$.
 It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded.
@@
 
-We use similar notation as that in \cite{abadie2010synthetic} to motivate 
-our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
-$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 
+We use similar notation as that in \cite{abadie2010synthetic} to motivate our weighted-adjustment estimator. Consider a $\mbf{W} \in \R^n$ weight vector 
+$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 
 $i = 2, \ldots, n+1$. Construct
@@
  \mbf{X}_1 = \begin{pmatrix}
-    \mbf{x}_{1, T_1^*} \\ \mbf{x}_{1, T_1^*+1}
-  \end{pmatrix}
-  \quad \text{ and }
-  \quad  \hat{\mbf{X}}_1(\mbf{W})
-  = w_2\begin{pmatrix}
-     \mbf{x}_{2, T_2^*} \\
-      \mbf{x}_{2, T_2^*+1}
-   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
-     \mbf{x}_{n+1, T_{n+1}^*} \\
-      \mbf{x}_{n+1, T_{n+1}^*+1}
-   \end{pmatrix} .
-\end{align*}
-where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
+    \mbf{x}_{1, T_1^*}' \\ \mbf{x}_{1, T_1^*+1}'
+  \end{pmatrix},
+  \quad  
+  \mbf{X} = \begin{pmatrix}
+  	\mbf{x}_{2, T_2^*}' \\
+    \mbf{x}_{2, T_2^*+1}' \\
+    \vdots \\
+  	\mbf{x}_{1, T_{n+1}^*}' \\
+    \mbf{x}_{2, T_{n+1}^*+1}'
+  \end{pmatrix},
+  \quad \text{and} \quad 
+  \hat{\mbf{X}}_1(\mbf{W}) 
+    = (\mbf{W}' \otimes \mbf{I}_2) \mbf{X}
+\end{align*}
+where $\otimes$ is the kronecker product, $\mbf{I}_2$ is the identity matrix with two rows, $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{2 \times p}$.
+Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$.
 Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
-$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that
+$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that
 \begin{align}
@@
    \left\{ \begin{pmatrix}
-     \mbf{x}_{2, T_2^*} \\
-      \mbf{x}_{2, T_2^*+1}
+     \mbf{x}_{2, T_2^*}' \\
+      \mbf{x}_{2, T_2^*+1}'
    \end{pmatrix}, \ldots, \begin{pmatrix}
-     \mbf{x}_{n+1, T_{n+1}^*} \\
-      \mbf{x}_{n+1, T_{n+1}^*+1}
+     \mbf{x}_{n+1, T_{n+1}^*}' \\
+      \mbf{x}_{n+1, T_{n+1}^*+1}'
    \end{pmatrix} \right\}.
@@
       w^*_2 & \cdots & w^*_{n+1}
-    \end{pmatrix}.
+    \end{pmatrix}'.
   \end{align*}
@@
 If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there are infinitely many solutions to (\ref{SCM}).
-The issue of non-uniqueness is further discussed in Section \ref{discussion}.
+The issue of non-uniqueness is further discussed in Section \ref{varbootstrap}.
 
@@
 
-As Section \ref{conditions} and \ref{comparisons} detailed the conditions for risk-reduction and comparisons, they usually involve fixed quantities related to variance and expectation.
+Sections \ref{conditions} and \ref{comparisons} detail conditions needed for risk-reduction and comparisons of adjustment estimators.
+These conditions involve variances and expectations which may be difficult to compute in practice.
 To make use of those properties in practice, estimation is required.
-Section \ref{varbootstrap} will introduce a general procedure of parametric bootstrap under the context of the problem to attain this purpose.
-
-\subsection{Conditions for risk-reduction for shock-effects estimators}
+Sections \ref{varbootstrap} and \ref{loocv} introduce  parametric bootstrap and leave-one-out cross validation procedures which prospectively estimate the conditions necessary for risk-reduction without observation of the post-shock response for the time series under study.
+Our simulations test these procedures.
+
+\subsection{Risk-reduction conditions for shock-effects estimators}
 \label{conditions}
@@
 
-In terms of the adjustment estimator, $\hat{\alpha}_{\rm adj}$, (\ref{riskconditionadj}) implies two facts: (1) Forecast 2 is preferable to Forecast 1 asymptotically in $n$ 
-whenever $\mu_{\alpha} \neq 0$; (2) In finite pool of time series, Forecast 2 is preferable to 
-Forecast 1 when the $\mu_{\alpha}$ is large relative to its variability and 
-overall regression variability.
+Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$; (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
 %This result is also intuitive.
@@
 For the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$, if  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}.
-From Proposition \ref{proprisk} and variance expression of $\hat{\alpha}_{\rm wadj}$, the following is the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$.
+From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
 \begin{align*}
@@
 \end{align*}
-In this case, Forecast 2 is preferable to Forecast 1 when $\mu_{\alpha}$ is large relative to the \emph{weighted sum of variances for shock effects for other time series} and overall regression variability.
+In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.
 However, the above criteria are generally difficult to evaluate in practice due to the term $\hat{\alpha}_{\rm wadj}$.
-Section  \ref{varbootstrap} will provide a detailed treatment about how to deal with these technical inequalities in practice.
+Sections \ref{varbootstrap} and \ref{loocv} will provide a detailed treatment about how to deal with these technical inequalities in practice.
 
@@
 \label{conditionsm2122}
-The $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
+
+The shock-effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
 %It is a more reasonable and general model since it is often the case that shock-effects differ by means among disparate time series in practice.
@@
 %From Proposition \ref{varprop}, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$  will be as in Proposition \ref{propriskwadj2}.
-We now state conditions for risk reduction.
+We now state conditions for risk-reduction.
 
@@
 \end{align*}
-where $\var{\alpha_i}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$. The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.
-
+where $\var{\alpha_i}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$.
+The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.
 Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally.
 Hence, Proposition \ref{proprisk} no longer holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.
-But, as an alternative, we can derive similar conditions as below.
+
+As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting.
 By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
@@
   &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
-  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
-\end{align*}
-Therefore, the above inequality will simply to 
-\begin{align*}
- (\E{\alpha_1})^2
- &>\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
-\end{align*}
+  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
+\end{align*}
+The above inequality simplifies to 
+\begin{equation} \label{ineq}
+ (\E{\alpha_1})^2 >\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
+\end{equation}
 Note that since $\hat{\alpha}_{\rm adj}$ is biased for $\E{\alpha_1}$, the bias term $(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2$ will become complicated and simplification yields no insightful results.
+We can however estimate \eqref{ineq} using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
 
@@
 That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
-
-Topics of  evaluation of these inequalities in practice can be found in Section \ref{varbootstrap}. 
-We will discuss comparisons of adjustment estimators in the the next Section.
+Evaluation of these inequalities in practice can be found in Sections \ref{varbootstrap} and \ref{loocv}.
+We will discuss comparisons of adjustment estimators in the the next section.
 %As conditions of risk-reduction for individual estimators are obtained, a natural question arises --- which one is better? It will be discussed in Section \ref{comparisons}.
@@
 
-Denote the risk-reduction quantity for the adjustment estimator as $\Delta_{\rm adj}$, the one for inverse-weighted estimator as $\Delta_{\rm IVW}$, and the one for weighted-adjustment estimator as $\Delta_{\rm wadj}$.
-As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration.
+Denote the risk-reduction quantities for adjustment estimators as $\Delta_{\rm adj}$, $\Delta_{\rm IVW}$, and $\Delta_{\rm wadj}$, respectively for standard adjustment, inverse-variance weighted estimator, and weighted-adjustment estimato.
+%As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration.
 For example, if we find that $\Delta_{\rm wadj}>\Delta_{\rm adj}$ and $\Delta_{\rm wadj}>\Delta_{\rm IVW}$, the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ is the most favorable.
-
 According to  discussion in Section \ref{conditionsm2122}, we know that under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, the risk-reduction quantity for $\hat{\alpha}_{\rm IVW}$ is
@@
 \begin{align*}
- \Delta_{\rm IVW} 
+ \Delta(\hat{\alpha}_{\rm IVW})
   = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
 \end{align*}
-
-For the case of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ , we can derive the following inequality for $\hat{\alpha}_{\rm wadj}$ to be favored over $\hat{\alpha}_{\rm adj}$.
+For the case of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$, we can derive the following inequality for $\hat{\alpha}_{\rm wadj}$ to be favored over $\hat{\alpha}_{\rm adj}$,
  \begin{align*}
@@
 \end{align*}
-
  %What insights can we gain from this inequality? 
-We analyze this inequality from two perspectives. 
+We analyze this inequality from two perspectives:
  \begin{enumerate}
@@
 
-In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction results, and estimate risk-reduction using plug-in approach in practice.
+In this section, we present bootstrap procedures that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction using plug-in approach in practice.
 Our procedure involves the resampling of residuals in the separate OLS fits.
@@
 \citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.
-
-To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement (\emph{unconditional} on donor pool) and the other without any resampling of the donor pool (\emph{conditional} on donor pool).
+(\textbf{Does our framework satisfy these regularity conditions?
+If so, then mention this.
+If not, then remove this reference.})
+
+Our bootstrap procedure is as follows: Let $B$ be the bootstrap sample size.
+At iteration $b$, first resample the indicies $I = \{2, \ldots, n+1\}$ of the donor pool without replacement to form $I^{(b)}$.
+Initialize $y_{i,0}$ for all $i \in I^{(b)}$.
+Then, resample the residuals under models $\mc{M}_1$, $\mc{M}_{21}$, or $\mc{M}_{22}$ and obtain shock-effect estimators for each of the disparate time series for all $i \in I^{(b)}$.
+These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, $b = 1,\ldots,B$.
+We can then estimate distributional quantities of our shock-effect estimators under our considered models with the bootstrap sample $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
+An algorithmic formulation of this bootstrap procedure and a fixed donor pool bootstrap procedure are outlined in the Supplementary Materials.
+%To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement (\emph{unconditional} on donor pool) and the other without any resampling of the donor pool (\emph{conditional} on donor pool).
 We denote them by $\mc{B}_u$ and  $\mc{B}_c$, respectively.
@@
 We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
-%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$.
-Therefore, this parametric bootstrap framework will work for us.
 One can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
@@
 
-Now, we discuss some consistency results for $\mc{B}_c$ conditioned on $\Theta_1$.
+%Now, we discuss some consistency results for $\mc{B}_c$ conditioned on $\Theta_1$.
 The bootstrap is aimed for estimating $\mrm{Var}(\hat{\alpha}_{\rm adj})$, $\mrm{Var}(\hat{\alpha}_{\rm wadj})$, and $\mrm{Var}(\hat{\alpha}_{\rm IVW})$.
@@
 Let
-$
-  \overline{\hat{\alpha}_{\mrm{adj}}} 
-    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
-$, 
-$
-  \overline{\hat{\alpha}_{\mrm{wadj}}} 
-    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
-$, 
-and 
-$
-  \overline{\hat{\alpha}_{\mrm{IVW}}} 
-    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
-$
-The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold.
+%$
+%  \overline{\hat{\alpha}_{\mrm{adj}}} 
+%    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
+%$, 
+%$
+%  \overline{\hat{\alpha}_{\mrm{wadj}}} 
+%    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
+%$, 
+%and 
+%$
+%  \overline{\hat{\alpha}_{\mrm{IVW}}} 
+%    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
+%$
+%The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold.
 The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below.
 As $B \to \infty$,
-\begin{align*}
-  \overline{\hat{\alpha}_{\mrm{wadj}}}
-  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
-  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
-  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
-  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
-\end{align*}
-The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$.
+%\begin{align*}
+%  \overline{\hat{\alpha}_{\mrm{wadj}}}
+%  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
+%  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
+%  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
+%  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
+%\end{align*}
+%The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$.
 However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because its weights are random.
@@
 
-We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_c$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
-%Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population.
-For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$.
+%We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_c$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
 For $\mc{B}_u$ but conditioned on $\Theta$, we emphasize that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold.
@@
 
+We will explicitly use these bootstrapped samples of shock-effect estimators to check the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
 Recall that  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ from Proposition \ref{unbiased}.
-Given the bootstrapped estimates of the variance, we can estimate the risk-reduction quantities in Section \ref{comparisons} using the estimates from the parametric bootstrap.
-For example, the $\Delta_{\rm adj}$ and its estimator $\hat{\Delta}_{\rm adj}$ are
-\begin{align*}
-  \Delta_{\rm adj} 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
-  \hat{\Delta}_{\rm adj} 
- & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
-\end{align*}
-where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance for $\hat{\alpha}_{\rm adj}$.
-Suppose the $\hat{\Delta}_{\rm wadj}$ and $\hat{\Delta}_{\rm IVW}$ are estimators for $\Delta_{\rm wadj}$ and $\Delta_{\rm IVW}$, respectively.
-Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}_{\rm est}>0$ for $\text{est} \in \{\text{adj}, \text{wadj}, \text{IVW}\}$, and  the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities.
-Next, we discuss some potential problems of the bootstrap procedures.
-
-In terms of the use of our bootstrap procedure, we caution that the bootstrapping residuals in OLS estimation may not provide valid inference in moderate or high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}; see alternatives for residual bootstrapping in linear models in \citet{el2018can}.
-
+Our bootstrap procedure estimates the variance of our adjustment estimators.
+We can then estimate the risk-reduction quantities in Section \ref{comparisons}.
+For example, we can estimate $\Delta_{\rm adj}$ under model $\mc{M}_{21}$ or $\mc{M}_{22}$ with
+\begin{align*}
+%  \Delta(\hat{\alpha}_{\rm adj})
+  %&= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
+  \hat{\Delta}(\hat{\alpha}_{\rm adj}) & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
+\end{align*}
+where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance estimator for $\Var(\hat{\alpha}_{\rm adj})$.
+
+%Suppose we have a pool of shock-effect estimators, $\mc{A}$, e.g., $\mc{A}= \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ in our study.
+We can determine which one is the best shock-effect estimator.
+Suppose the $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ and $\hat{\Delta}(\hat{\alpha}_{\rm IVW})$ are estimators for $\Delta(\hat{\alpha}_{\rm wadj}) $ and $\Delta(\hat{\alpha}_{\rm IVW})$, respectively.
+Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}(\hat{\alpha})>0$ for $\hat{\alpha}\in \mc{A}$.
+Besides, we can also select the best shock-effect estimator accordingly.
+Define
+%\begin{align}
+%	\hat{\alpha}_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \hat{\Delta}(\hat{\alpha}) \quad \text{ and } \quad  \alpha_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \Delta(\hat{\alpha}).
+\label{best}
+%\end{align}
+%That is, the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities whereas $\alpha_{\rm best}$ is the true best shock-effect estimator given observed post-shock response.
+See more discussions in Section \ref{loocv}.
+
+We stress that the our bootstrap approximations cannot alleviate the inherent bias of using our adjustment estimators as surrogates for $\alpha_1$.
+We caution that the bootstrapping residuals in OLS estimation may not provide valid inference in moderate or high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}; see alternatives for residual bootstrapping in linear models in \citet{el2018can}.
 Recall that $\mathbf{W}^*$  may not be unique if the conditions in Proposition \ref{uniqueness} are not satisfied.
 Under the setup of our model, non-uniqueness of $\mathbf{W}^*$ would not be a problem for inferential purposes.
-It is because all risk-reduction propositions and other properties established will still hold.
-However, non-uniqueness may not be desirable in other model setup.
+This is because all risk-reduction propositions and other properties established will still hold.
+However, non-uniqueness may not be desirable in other model setups.
 For example, consider the model where $\alpha_i$ is assumed to be not identically distributed, the size of  donor pool to be 2, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$ with $\var{\alpha_2}\neq \var{\alpha_3}$.
@@
 For instance, in the example just discussed, users may select the weight that minimizes the estimated variance of $\hat{\alpha}_{\rm wadj}$.
-
-There are some issues in using $\mc{B}_u$ when $\mathbf{W}^*$ falls in the boundary of the parameter space. See detailed discussions in Section \ref{discussion}.
-
-\section{Simulation}
-
-\label{simulation}
-
-In this section, we provide justification for our methods based on Monte Carlo simulation examples.
-We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
-We consider $p=13$ and $\mu_{\alpha}=10$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.
-
-Parameter setup of our simulations are detailed as below.
-$\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
-We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers.
-If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.
-Moreover, $T_i^*$ is randomly selected from $2p + 4$ to $T_i-1$.
-Those are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
-Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
-However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$.
-In that case, we do not consider such $b$ in computations of means and variances.
-Additionally, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
-
-In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
-We used 200 replications of Monte Carlo simulations and $B = 500$ for computation; and report means and standard errors for estimated quantities accordingly.
-
-\subsection{Bootstrap simulation for risk-reduction propositions}
-\label{parametricbootstrapsimulation}
-
-In this section, we provide justification for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}).
-We will compare the result of using parametric bootstrap conditioned on the donor pool with the one without using the parameter setup discussed in Section \ref{simulation}.
-
-Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions.
-We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation.
-Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise.
-Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table.
+%There are some issues in using $\mc{B}_u$ when $\mathbf{W}^*$ falls in the boundary of the parameter space. See detailed discussions in Section \ref{discussion}.
+
+\subsection{Leave-one-out cross validation}
+\label{loocv}
+
+In this section, we adapt leave-one-out cross validation (LOOCV) to our estimation context in order to provide prospective evaluations of our adjustment techniques.
+Our proposed LOOCV procedure has its roots in Section 7.10 of \citet{hastie2009elements} (\textbf{Is this true?}).
+Recall in Section \ref{modelsetup} that we are given the data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining observations form the donor pool.
+For iteration $m \in \{1,\ldots,n\}$ of our LOOCV procedure, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}_m, t = 1, \ldots, T_{i}\}$, where $\mc{I}_m=\{2, \ldots, n+1\} \setminus \{m+1\}$.
+Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, we can evaluate the performance of our adjustment estimators and the original forecast made without adjustment.
+
+LOOCV can be very computationally intensive when $n$ is large, especially when combined with bootstrapping.
+To alleviate these concerns we can perform LOOCV with a random subset of $k \leq n$ iterations selected without replacement.
+In this setting, we let $\mc{J}$ be the randomly sampled indicies.
+For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$.
+We find that $k=5$ or $k=10$ iterations of LOOCV performs well.
+
+We now outline how LOOCV can be used to prospectively assess the performance of adjustment estimators.
+Let $\mc{A}$ be the set of adjustment estimators.
+For each $\hat{\alpha} \in \mc{A}$, let $\delta_{\hat{\alpha}} = 1(\hat\Delta(\hat{\alpha})>0)$ be a decision rule where $1(\cdot)$ is the indicator function and a $1$ corresponds to the decision to use adjustment estimator $\hat\alpha$.
+\textbf{Jilei, check these results and make sure that $\hat\Delta$ and $\Delta$ are used correctly.} If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) so that it make the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be incorrect.
+If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) so that it make the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be correct.
+These situations are depicted in the following table: \vspace*{0.3cm}
+
 \begin{center}
@@
         & & \multicolumn{2}{c}{Decision} \\
-        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
+        & & $\delta_{\hat{\alpha}} = 1$ & $\delta_{\hat{\alpha}} = 0$ \\ 
                 \hline
-     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
+     \multirow{2}{*}{Truth}  & $\Delta(\hat{\alpha})>0$ & Correct & Incorrect \\
       \cline{3-4}
-      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
+      & $\Delta(\hat{\alpha})<0$  & Incorrect & Correct \\
       \hline
@@
 \end{center}
-We report 1 for risk-reduction propositions to be consistent and 0 otherwise.
-Recall that in Section \ref{comparisons}, we could estimate the risk-reduction quantities, and therefore select the best estimator with the maximum risk-reduction quantities.
-It is also possible to confirm whether this decision is true in a simulation setting.
-Similarly, we report 1 for the decision of selecting the best shock-effect estimators  to be consistent and 0 otherwise.
-
-In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{1, 5, 10, 25, 100\}$ where we fix $\sigma$ to 1.
-The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown.
-It is shown in Table ?
-that as the donor pool size increases, the bias and consistency results improve with more precision.
-In contrast, the result gets poorer as  the variance of $\alpha_i$ increases.
-It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$.
-Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates.
-But it is reversed in the random design case.
-Moreover, notice that the consistency for voting the best estimator works poor when $n$ is small but improves significantly when $n$ is large.
-
-\subsection{Simulation for prediction}
-
-In this section, we report prediction results for our methods in the simulation.
-Specifically, we are interested in the distance between $\alpha_1$ and our shock-effect estimators, and the distance between $y_{1,T_1^*+1}$ and $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$.
-
-In the first experiment, Table ?
-shows similar results to  Section  \ref{parametricbootstrapsimulation} that the prediction and distance to $\alpha_1$ gets better as $n$ increases but worser when the variance of $\alpha_i$ gets larger.
-
-%In this section, we present the simulation for the parametric bootstrap procedure for AR(1) outlined in Section \ref{varbootstrap}.
-The simulation is only provided for the adjustment estimator and weighted adjustment estimator since the weights for inverse-variance estimator are random and the true values of its moments are unknown.
-
-%\begin{center}
-%  \begin{tabular}{l|cccccc}
-%    & \multicolumn{6}{c}{Time series}\\
-%    & 1 & 2 & 3 & 4 & 5 & 6\\
-%   Length $T_i$ & 77 & 93 & 72 & 71 & 73 & 50 \\
-%   Shock Time  $T_i^*+1$ & 20 & 39 & 45 & 52 & 59 & 11 \\
-%   Autoregressive parameter $\phi_i$ & 0.540 & 0.961 & 0.654 & 0.547 & 0.266 & 0.197 
-%  \end{tabular}
-%\end{center}
+%Similar definitions can be adapted to the best shock-effect estimators. 
+\vspace*{0.3cm}
+
+We will use 
+$
+	\mc{C}(\delta_{\hat\alpha}) 
+	= I(\delta_{\hat{\alpha}} \text{ is correct})
+ %\quad \text{ and } \quad  	
+ %\mc{C}(\mc{A}) 
+%	= I(\hat{\alpha}_{\rm best} = \alpha_{\rm best})
+$
+as a metric that evaluates the performance of forecasts made with the adjustment estimator $\hat\alpha$.
+If $\E{\mc{C}(\delta_{\hat{\alpha}})} > 0.5$, we claim that $\delta_{\hat{\alpha}}$ is better than random guessing.
+Note that $\mc{C}(\delta_{\hat{\alpha}})$ can generally be computed only when the post-shock response is observed.
+However, it is possible to estimate $\E{\mc{C}(\delta_{\hat{\alpha}})}$ using LOOCV.
+%For each $\hat{\alpha}\in \mc{A}$ we can compute the consistency as $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ using the estimation procedures in Section \ref{varbootstrap}.
+The LOOCV estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$ are
+\begin{equation} \label{loocvm}
+	 \bar{\mc{C}}(\delta_{\hat{\alpha}})= \frac{1}{n} \sum_{m = 1}^n \mc{C}^{(-m)}(\delta_{\hat{\alpha}})
+	\end{equation}
+where $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ is computed with respect to donor pool with index set $\mc{I}_m$ and the $m+1$ time series is treated as the series of interest.
+The mutual independence assumption in model setup $\mc{M}_{2}$ implies that $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
+\textbf{Jilei, what does almost unbiased mean?
+Can you clarify?} The LOOCV with $k$ random draws estimates $\E{\mc{C}(\delta_{\hat{\alpha}})}$ as
+\begin{equation} \label{loocvk}
+	 \bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})	,
+\end{equation}
+where $\mc{J}$ is the set of the $k$ randomly sampled indicies.
+%Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively.
+The estimation bias should decrease as $k \to n$.
+
+\section{Numerical Examples}
+\label{simulation}
+
+\subsection{Modeling setup}
+
+In this section we provide justification for our methods based on Monte Carlo simulation.
+We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
+We consider $p=13$ and $\mu_{\alpha}=2$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.
+Parameter setup of our simulations is detailed as follows: the $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
+We sampled $T_i$'s independently from  $\text{Gamma}(15, 10)$ that are further rounded to integers, where the minimum allowable value of $T_i$ is fixed to be 90.
+We will randomly draw $T_i^*$ from $\{2p + 4, \ldots, T_i-1\}$.
+The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
+Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
+Additionally, we generated the covariates from $\text{Gamma}(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
+Last, we set $\gamma_i, \delta_i\simiid  \normal{1}{0.5}$ and $\theta_i, \beta_i \sim \normal{0}{1}$.
+We will consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
+We choose a Monte Carlo sample size of $30$ replications and a bootstrap sample size of $B = 200$ for computation.
+Means and standard errors for estimated quantities will be recorded.
+Our LOOCV procedure will consider $k=5$ random draws.
+\textbf{Jilei, can you briefly describe how bootstrapping and LOOCV are used together?}
+
+\subsection{Performance metrics}
+
+Our adjustment estimators will be evaluated by multiple criteria.
+\textbf{Jilei, can you include guess in this section?
+Also, could you explain what guess is in the appropriate section, either here or in Section 3.3?} We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
+We will also consider the magnitude of the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ from the realized post-shock response $y_{1,T_1^*+1}$.
+The first two metrics can combine to assess our forecasting methodology prospectively while the latter requires the realization of the post-shock response $y_{1,T_1^*+1}$.
+
+\subsection{Monte Carlo results}
+\label{parametricbootstrapsimulation}
+
+In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}).
+Two simulation setups are investigated.
+
+In the first simulation setup, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$.
+Note that $\E{\E{\alpha_1}}=54$, where the last expectation is operated under the density of the covariates.
+In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.
+Results are displayed in Table~\ref{table1}.
+
+In the second simulation setup, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n=10$.
+Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.
+Results are displayed in Table~\ref{table2}.
+
+\vspace*{0.5cm} \textbf{Jilei, please add a description of the simulation results.} \vspace{0.5cm}
+
+\begin{table}[h]
+\caption{30 Monte Carlo simulations with varying $n$ and $\sigma_{\alpha}$ \textbf{Jilei, can we get the predictions to fit in this table? A smaller text size might work}} \vspace{.3cm} \label{table1}
+\begin{center}
+\begin{tabular}{cc|ccc|ccc}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c}{LOOCV with $k$ random draws}  \\ 
+ $n$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ \\[.15cm] %&  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.15cm]
+  \hline
+  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.96 (0.02) & 0.92 (0.02) \\ %& 0.36 (0.05) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.90 (0.02) & 0.92 (0.02) & 0.90 (0.02) \\ %& 0.40 (0.04) \\ 
+    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.80 (0.02) & 0.81 (0.02) & 0.80 (0.03) \\ %& 0.43 (0.04) \\ 
+    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.87 (0.06) & 0.55 (0.05) & 0.57 (0.05) & 0.55 (0.05) \\% & 0.38 (0.05) \\ 
+    & 100  & 0.47 (0.09) & 0.73 (0.08) & 0.47 (0.09) & 0.48 (0.05) & 0.48 (0.04) & 0.46 (0.04) \\[.3cm] % & 0.37 (0.05) \\[.3cm] 
+    \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.95 (0.02) & 0.95 (0.02) \\ %& 0.33 (0.04) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.91 (0.03) & 0.92 (0.03) \\ %& 0.33 (0.04) \\ 
+    & 25  & 0.90 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.77 (0.04) & 0.79 (0.04) & 0.75 (0.05) \\ %& 0.31 (0.04) \\ 
+    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.55 (0.04) & 0.64 (0.04) & 0.55 (0.05) \\ %& 0.31 (0.04) \\ 
+    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.53 (0.04) & 0.53 (0.05) & 0.51 (0.04) \\[.3cm] %& 0.33 (0.04) \\[.3cm] 
+    \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.93 (0.02) & 0.92 (0.02) \\ %& 0.31 (0.05) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.92 (0.02) \\ %& 0.30 (0.03) \\ 
+   & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.83 (0.03) & 0.83 (0.03) \\ %& 0.35 (0.04) \\ 
+  & 50  & 0.90 (0.06) & 0.93 (0.05) & 0.90 (0.06) & 0.71 (0.03) & 0.67 (0.04) & 0.69 (0.04) \\ %& 0.33 (0.04) \\ 
+    & 100  & 0.70 (0.09) & 0.73 (0.08) & 0.70 (0.09) & 0.54 (0.05) & 0.61 (0.04) & 0.54 (0.05) \\[.3cm] %& 0.31 (0.05) \\[.3cm] 
+   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.90 (0.03) & 0.91 (0.03) & 0.90 (0.03) \\ %& 0.27 (0.04) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) \\ %& 0.30 (0.03) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.73 (0.03) & 0.74 (0.04) & 0.73 (0.03) \\ %& 0.29 (0.03) \\ 
+    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.83 (0.07) & 0.55 (0.05) & 0.56 (0.05) & 0.55 (0.05) \\ %& 0.29 (0.04) \\ 
+    & 100  & 0.77 (0.08) & 0.73 (0.08) & 0.77 (0.08) & 0.48 (0.05) & 0.49 (0.04) & 0.49 (0.05) \\ %& 0.31 (0.05) \\ 
+\end{tabular}
+   \end{center}
+      \vspace{-.5cm}
+\end{table}
+
+\begin{table}[h]
+\caption{30 Monte Carlo simulations with varying $\sigma$ and $\sigma_{\alpha}$ \textbf{Jilei, can we get the predictions to fit in this table? A smaller text size might work}} \label{table2}
+\begin{center}
+\begin{tabular}{cc|ccc|ccc}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c}{LOOCV with $k$ random draws}  \\ 
+ $\sigma$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$  \\[.3cm] %&  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.3cm]
+  \hline
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.99 (0.01) & 0.99 (0.01) & 0.99 (0.01) \\ %& 0.39 (0.05) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.97 (0.01) & 0.97 (0.01) & 0.97 (0.01) \\ %& 0.34 (0.04) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.81 (0.04) & 0.82 (0.04) & 0.81 (0.04) \\% & 0.29 (0.04) \\ 
+    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.57 (0.05) & 0.67 (0.04) & 0.57 (0.05) \\% & 0.34 (0.04) \\ 
+    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.51 (0.04) & 0.53 (0.05) & 0.50 (0.04) \\[.3cm] %& 0.35 (0.05) \\[.3cm] 
+   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.95 (0.02) & 0.95 (0.02) \\ %& 0.33 (0.04) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.91 (0.03) & 0.92 (0.03) \\ %& 0.33 (0.04) \\ 
+    & 25  & 0.90 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.77 (0.04) & 0.79 (0.04) & 0.75 (0.05) \\ %& 0.31 (0.04) \\ 
+    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.55 (0.04) & 0.64 (0.04) & 0.55 (0.05) \\ %& 0.31 (0.04) \\ 
+    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.53 (0.04) & 0.53 (0.05) & 0.51 (0.04) \\[.3cm] %& 0.33 (0.04) \\[.3cm] 
+   \multirow{5}{*}{25}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.79 (0.04) & 0.78 (0.04) & 0.77 (0.04) \\ %& 0.19 (0.04) \\ 
+    & 10  & 0.97 (0.03) & 0.97 (0.03) & 0.97 (0.03) & 0.75 (0.04) & 0.75 (0.04) & 0.73 (0.05) \\ %& 0.20 (0.04) \\ 
+   & 25  & 0.90 (0.06) & 0.93 (0.05) & 0.90 (0.06) & 0.66 (0.05) & 0.69 (0.05) & 0.66 (0.05) \\ %& 0.30 (0.05) \\ 
+    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.80 (0.07) & 0.55 (0.05) & 0.64 (0.05) & 0.55 (0.05) \\ %& 0.34 (0.05) \\ 
+    & 100  & 0.60 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.48 (0.04) & 0.52 (0.04) & 0.47 (0.04) \\[.3cm] % & 0.31 (0.04) \\[.3cm] 
+   \multirow{5}{*}{50}  & 5  & 0.73 (0.08) & 0.73 (0.08) & 0.77 (0.08) & 0.57 (0.05) & 0.57 (0.05) & 0.58 (0.05) \\ %& 0.24 (0.04) \\ 
+    & 10  & 0.73 (0.08) & 0.73 (0.08) & 0.73 (0.08) & 0.55 (0.05) & 0.55 (0.05) & 0.55 (0.05) \\ %& 0.23 (0.03) \\ 
+    & 25  & 0.77 (0.08) & 0.70 (0.09) & 0.73 (0.08) & 0.48 (0.05) & 0.51 (0.05) & 0.47 (0.05) \\ %& 0.24 (0.04) \\ 
+    & 50  & 0.77 (0.08) & 0.73 (0.08) & 0.73 (0.08) & 0.46 (0.05) & 0.53 (0.04) & 0.47 (0.05) \\ %& 0.25 (0.04) \\ 
+    & 100  & 0.57 (0.09) & 0.70 (0.09) & 0.57 (0.09) & 0.46 (0.05) & 0.49 (0.03) & 0.45 (0.05) \\[.3cm] %& 0.33 (0.05) \\[.3cm] 
+  \multirow{5}{*}{100}  & 5  & 0.63 (0.09) & 0.60 (0.09) & 0.63 (0.09) & 0.46 (0.05) & 0.52 (0.04) & 0.48 (0.05) \\ %& 0.23 (0.04) \\ 
+    & 10  & 0.60 (0.09) & 0.60 (0.09) & 0.63 (0.09) & 0.46 (0.05) & 0.53 (0.04) & 0.46 (0.05) \\ %& 0.24 (0.04) \\ 
+    & 25  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.45 (0.05) & 0.54 (0.04) & 0.47 (0.05) \\ %& 0.21 (0.04) \\ 
+    & 50  & 0.57 (0.09) & 0.53 (0.09) & 0.57 (0.09) & 0.49 (0.04) & 0.54 (0.04) & 0.47 (0.05) \\ %& 0.23 (0.03) \\ 
+    & 100  & 0.43 (0.09) & 0.53 (0.09) & 0.43 (0.09) & 0.52 (0.05) & 0.55 (0.03) & 0.51 (0.05) \\ %& 0.27 (0.04) \\
+\end{tabular}
+   \end{center}
+   \vspace{-.5cm}
+\end{table}
+
+%\subsection{Simulation for prediction}
+%\label{simulationforprediction}
+
+\begin{table}[t]
+ \caption{30 Monte Carlo simulation with varying $n$ and $\sigma_{\alpha}$ (distance to $y_{1, T_1^*+1}$). \textbf{Jilei, which simulation setting do these results correspond to?}} \label{table3}
+ \begin{center}
+\begin{tabular}{cc|cccc}
+  $\sigma$   & $\sigma_{\alpha}$  & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.3cm]  
+  \hline
+ \multirow{5}{*}{5}  & 5  & 53.27 (2.59) & 10.91 (1.70) & 11.77 (1.55) & 10.8 (1.69) \\ 
+   & 10  & 50.86 (3.83) & 18.06 (2.18) & 17.26 (2.17) & 18.25 (2.17) \\ 
+    & 25  & 60.52 (3.97) & 16.09 (2.40) & 19.83 (3.05) & 15.87 (2.38) \\ 
+     & 50  & 54.65 (6.95) & 51.79 (6.87) & 53.83 (7.26) & 52.6 (6.91) \\ 
+     & 100  & 104.73 (13.00) & 88.31 (12.16) & 88.88 (12.63) & 86.72 (12.35) \\[.3cm] 
+   \multirow{5}{*}{10}  & 5  & 58.17 (4.18) & 18.17 (2.61) & 16.59 (2.39) & 18.09 (2.63) \\ 
+    & 10  & 52.81 (4.07) & 19.05 (2.49) & 19.67 (2.66) & 18.95 (2.53) \\ 
+     & 25  & 61.53 (5.69) & 28.55 (4.07) & 31.82 (4.27) & 28.76 (4.07) \\ 
+     & 50  & 56.31 (8.03) & 47.33 (4.89) & 41.44 (4.39) & 46.86 (4.79) \\ 
+     & 100  & 84.38 (11.62) & 82.91 (11.77) & 84.5 (12.39) & 84.3 (11.93) \\[.3cm] 
+   \multirow{5}{*}{25}  & 5  & 56.35 (6.1) & 25.54 (4.06) & 30.49 (4.61) & 25.94 (4.02) \\ 
+     & 10  & 49.8 (5.24) & 25.04 (4.38) & 26.74 (3.64) & 24.86 (4.38) \\ 
+     & 25  & 54.21 (6.51) & 44.17 (6.66) & 43.41 (6.95) & 43.89 (6.63) \\ 
+     & 50  & 66.51 (7.86) & 46.19 (8.04) & 44.83 (9.31) & 46.54 (8.27) \\ 
+     & 100  & 109.21 (13.29) & 78.47 (12.45) & 83.99 (12.00) & 78.57 (12.75) \\[.3cm] 
+   \multirow{5}{*}{50}  & 5  & 75.29 (10.75) & 63.51 (8.30) & 64.25 (8.88) & 63.32 (8.40) \\ 
+     & 10  & 57.59 (6.00) & 48.51 (8.32) & 50.58 (8.63) & 48.08 (8.36) \\ 
+     & 25  & 77.21 (12.03) & 54.73 (9.47) & 54.76 (10.24) & 54.2 (9.62) \\ 
+     & 50  & 90.48 (10.21) & 68.88 (9.20) & 68.28 (10.48) & 68.8 (9.28) \\ 
+     & 100  & 111.09 (17.54) & 102.47 (16.68) & 110.15 (15.87) & 101.53 (16.52) \\[.3cm] 
+   \multirow{5}{*}{100}  & 5  & 214.07 (67.40) & 195.46 (67.65) & 197.51 (68.45) & 196.58 (67.51) \\ 
+     & 10  & 120.85 (15.39) & 114.79 (15.51) & 119.19 (15.75) & 114.02 (15.74) \\ 
+     & 25  & 97.84 (13.75) & 95.02 (14.88) & 100.04 (16.94) & 96.23 (14.71) \\ 
+     & 50  & 141.22 (24.51) & 136.11 (25.73) & 150.62 (27.62) & 135.26 (25.39) \\ 
+     & 100  & 95.53 (12.80) & 103.01 (14.12) & 103.31 (16.27) & 105.79 (14.32) \\
+\end{tabular}	
+ \end{center}
+  \vspace{-.5cm}
+\end{table}
+
+\textbf{Jilei, please integrate these results with a revised description of the results for the bootstrap procedure.}
+In the first experiment, table \ref{table3} shows that similar to Section \ref{parametricbootstrapsimulation}, as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
+When $\sigma_{\alpha}= 5, 10, 25$, forecasts using $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are always better than the original forecast significantly.
+But it does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
+It is reasonable in that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
+Nevertheless, unlike what is detected in Section \ref{parametricbootstrapsimulation}, no statistical evidence has been found to support the claim that $n$ matters in prediction.
+In other words, $n$ matters in producing reliable decision-making of $\delta_{\hat{\alpha}}$  rather than reliable prediction.
+
+Note that there is no statistical evidence supporting for differences among $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
+This observation corresponds to the fact that $\bar{\mc{C}}(\mc{A})$ is small and following analysis in Section \ref{parametricbootstrapsimulation}.
+When their performances do not differ much, the precision of ranking is small.
+In this scenario, for a more reasonable statistical inference, one may opt for a double bootstrap instead to approximate the distribution of $\Delta(\hat{\alpha})$ and compare estimators by checking for overlap of percentile intervals at some desirable error threshold.
+See more details in the Discussion.
+
+%In the second experiment, table \ref{table4} shows similar results for prediction to those in the first expeirment, for the case of varying $\sigma_{\alpha}$ but fixing $\sigma$, and the case of varying $\sigma$ but fixing $\sigma_{\alpha}$.
+When $\sigma$ increases with fixing $\sigma_{\alpha}$, it is likely that the degree of variation of $y_{1,t}$ exceeds the extent of adjustment improvement $\hat{\alpha}$ can contribute to for $\hat{\alpha}\in \mc{A}$.
+It can be confirmed by looking into  the case of $\sigma= 50, 100$ as opposed to the case for $\sigma= 5, 10, 25$ where adjusted forecasts outperform original forecasts.
+Adjusted forecasts can be worse than original forecast if the variation of $y_{i,t}$ is large and the signal of the covariates is very small.
+See for the case  of $\sigma=100$ and $\sigma_{\alpha}=100$ in table \ref{table4}.
 
@@
   \end{enumerate}
-%\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
 \end{enumerate}
-
-%Since the stock price of a company implies its value provided the number of shares is unchanged, the price of S\&P 500 index in the recession can partially represent the overall status of the economy.
-Therefore, using the price of S\&P 500 index as the covariate can possibly improve the precision of the OLS estimates for shock-effects that are unique to Conoco Phillips.
-The rationale for inclusion of the price of S\&P 500 index is similar to that of market return in capital asset pricing model (CAPM).
-(\textbf{Need reference for the CAPM}.)
-
-% INTEREST RATES AND OIL RELATIONSHIP: This paper shows that in the short term both gold and crude oil prices positively influence each other.
-Interest rates have a negative influence on the future gold prices and a positive influence on the future crude oil prices.
-In the long run, a relationship exists whereby interest rates influence the US dollar, which in turn influences international crude oil prices.
-When the Federal Reserve Board (Fed) lowers interest rates to boost the economy, market expectations for oil demand change and, as a result, crude oil prices fluctuate \citep{wang2013dynamic}.
-
-%\subsection{Results}
-%\label{results}
-
-%\vspace{-.3cm}
-%\begin{table}[H]
-%  \caption{Some basic summary statistics of the covariates and response} \vspace{.4cm} \label{table1}
-%  \begin{center}
-%    \begin{tabular}{ccrrrrrr}
-%       &    & \multicolumn{2}{c}{S\&P 500} & \multicolumn{2}{c}{WTI}  & \multicolumn{2}{c}{$y_{i,t}$} \\
-%     Time series & $T_i^*+1$ & Mean & SD  &  Mean & SD  & Mean & SD  \\
-%             \hline 
-%2020 Mar.  &  03--09 & 3239.11 & 139.28 & 50.36 & 3.13 & 55.35 & 6.37 \\ 
-%  2008 Mar.  & 03--14 & 1341.03 & 29.50 & 98.82 & 7.01 & 60.59 & 2.28 \\ 
-% \multirow{3}{*}{2008 Sep.}
-% & $T_3^* +1 = \text{09--08}$ & \multirow{3}{*}{1504.50}  & \multirow{3}{*}{43.44}  & \multirow{3}{*}{134.46} & \multirow{3}{*}{10.24} & \multirow{3}{*}{71.20}  & \multirow{3}{*}{4.11}  \\ 
-% & $T_4^* +1 = \text{09--12}$ \\
-%   & $T_5^* +1 = \text{09--26}$ \\
-%\\
-%  2014 Nov.  & 11--27 & 2179.99 & 66.99 & 85.70 & 3.38 & 76.99 & 1.90 \\ 
-%    \end{tabular}
-%  \end{center}  \vspace{-.3cm}
-%\end{table}
-
-%Table \ref{table1} presents some basic summary statistics for the covariates and response for the time series of interest (stock price of Conoco Phillips in 2020 March) and the donor pool.
 
@@
 The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.382$, $2.468$, and $1.145$ dollars, respectively.
-These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect.
+These additive adjustment estimators do extremely well.
 %There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.
@@
 
-Recall that in Section \ref{varbootstrap}, we proposed two possible bootstrap procedures, $\mc{B}_u$  and $\mc{B}_c$.
-There are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_c$.
-$\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
-
-In this study, for the use of $\mc{B}_u$, we assume $\mathbf{W}^*$ is non-degenerate in the population without taking zero weight.
-Recall that in Section \ref{constructionofestimators} we note that if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there will be infinitely many solutions to $\mathbf{W}^*$.
-In the simulation setup, we consider $2p >n$ such that the assumption can be reasonably satisfied.
-However, in the application, it is likely that $\mathbf{W}^*$ may  take values on the boundary of $\mc{W}$, in which case $\mc{B}_u$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-For example, if $\mathbf{W}^*$ is observed to fall in the boundary, $\mc{B}_u$ will fail.
-Moreover, if $2p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
-In this regard, the subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$.
+In this manuscript, we have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.
+Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $2p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
+However, in applications, it is likely that $\mathbf{W}^*$ may take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
+\textbf{Jilei, in the previous sentence is it likely that bootstrapping will fail in applications or is it possible that bootstrapping will fail in applications?} %Moreover, when $2p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
+The subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$.
 But we may leave its mathematical justification for future research.
-Note that this problem will not occur under  $\mc{B}_c$ because  if $w_i^*=0$ for some $i$ and the weights are known, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.
+
+Double bootstrap can be another general bootstrap alternative to the one proposed in Section \ref{varbootstrap}.
+The double bootstrap procedure adds another layer of residual bootstrapping between resampling of the donor pool and the resampling of the residuals.
+This procedure enables estimation of the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
+In the framework of double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, we can check whether a bootstrap percentile interval contain 0 at a desired error threshold.
+We have attempted Monte Carlo simulations using the same setting in Section \ref{simulation} for the double bootstrap procedure, the results of which are quite similar to those of Section \ref{varbootstrap}.
 
@@
 Moreover, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large.
-It is  due to the fact that plug-in estimation of  risk-reduction quantities gains more precision when $n$ becomes large.
+It is  due to the fact that plug-in estimation of  risk-reduction quantities in Section \ref{varbootstrap} gains more precision when $n$ becomes large.
 
 \section{Appendix}
-
-\subsection{Proofs}
-
 \label{proofs}
 
-\subsubsection{Justification of Expectation of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
+\subsection{Justification of Expectation of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
 \label{exp}
@@
 
-\subsubsection{Justification of Variance of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
+\subsection{Justification of Variance of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
 \label{var}
@@
 
-\subsubsection{Proofs for lemmas and propositions}
+\subsection{Proofs for lemmas and propositions}
 
@@
 
-\subsection{Supplementary materials for data analysis}
-\label{smfda}
-The independence of estimated shock-effects are further tested using likelihood ratio test (LRT) based on their estimated covariance matrix. The estimated covariance matrix is
-\begin{align*}
-  \hat{\mathbf{\Sigma}}=\left(\begin{array}{rrr}
-    4.012 & 0.362 & -0.062 \\
-    0.362 & 3.894 & -0.029 \\
-    -0.062 & -0.029 & 3.927
-  \end{array}\right).
-\end{align*}
-with degrees of freedoms 35.
-Using LRT for independence between blocks of random variables \citep[Section 10.2]{msos}, the LRT test statistic is $0.304$ with $p$-value of 0.581.
-Therefore, we do not reject  the null hypothesis that the three estimated shock-effects are independent.
-
 \bibliographystyle{plainnat}

### 2020-07-15 manuscript/manuscript.tex
revisions to manuscript and simulations results in table.pdf

@@
 \begin{enumerate}
-  \item Revisions to the manuscript.
-  \item Detailed comments for further revisions are included.
-  \item The Supplementary Materials document has been expanded. More comments are included in that document.
-  \item The fixed donor pool bootstrap procedure (previously called $B_c$) is moved to the Supplementary Materials document.
-  \item Commentary about bootstrap consistency is removed, I do not think that it is necessary.
-  \item The ``best estimator'' materials are removed, this procedure did not perform too well.
+  \item Revisions to the manuscript (mainly in Simulations and Discussions). The comments are addressed as well.
 \end{enumerate}
-
-\noindent{\bf Things to do}: We also need a simulation corresponding to model $\mc{M}_1$ in which we investigate the performance of all adjustment estimators.
-We should also do a very small simulation that checks whether or not the weighted adjustment estimator does well when we expect $\mathbf{W}^*$ to be on the boundary.
 
@@
 They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
+However, the model-free perspective seeks for a perfect fit on the past data.
+If the work of \citet{agarwal2020two} were adapted to post-shock setting by treating structural shocks as "interventions", the prediction would have been only a guess.
+Though their methods are quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
 
@@
 
-Up to the scale of the shock, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock (\textbf{What does Up to the scale of the shock mean?
-Why will the model-free technique not work ideally?}).
+Overall, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock.
 To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration.
@@
     \vdots \\
-  	\mbf{x}_{1, T_{n+1}^*}' \\
-    \mbf{x}_{2, T_{n+1}^*+1}'
+  	\mbf{x}_{n+1, T_{n+1}^*}' \\
+    \mbf{x}_{n+1, T_{n+1}^*+1}'
   \end{pmatrix},
@@
 In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}.
-\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.
-(\textbf{Does our framework satisfy these regularity conditions?
-If so, then mention this.
-If not, then remove this reference.})
 
@@
 We can then estimate distributional quantities of our shock-effect estimators under our considered models with the bootstrap sample $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-An algorithmic formulation of this bootstrap procedure and a fixed donor pool bootstrap procedure are outlined in the Supplementary Materials.
+We denote this procedure by $\mc{B}_u$, and another procedure, which fixes the donor pool without sampling the donor pool without replacement, as $\mc{B}_f$.
+An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in the Supplementary Materials.
 %To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement (\emph{unconditional} on donor pool) and the other without any resampling of the donor pool (\emph{conditional} on donor pool).
@@
 We can then estimate the risk-reduction quantities in Section \ref{comparisons}.
-For example, we can estimate $\Delta_{\rm adj}$ under model $\mc{M}_{21}$ or $\mc{M}_{22}$ with
+For example, we can estimate $\Delta(\hat{\alpha}_{\rm adj})$ under model $\mc{M}_{21}$ or $\mc{M}_{22}$ with
 \begin{align*}
@@
 In this section, we adapt leave-one-out cross validation (LOOCV) to our estimation context in order to provide prospective evaluations of our adjustment techniques.
-Our proposed LOOCV procedure has its roots in Section 7.10 of \citet{hastie2009elements} (\textbf{Is this true?}).
+Our proposed LOOCV procedure has its roots in Section 7.10 of \citet{hastie2009elements}.
 Recall in Section \ref{modelsetup} that we are given the data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining observations form the donor pool.
@@
 To alleviate these concerns we can perform LOOCV with a random subset of $k \leq n$ iterations selected without replacement.
-In this setting, we let $\mc{J}$ be the randomly sampled indicies.
+In this setting, we let $\mc{J}$ be the randomly sampled indices.
 For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$.
+Based on the new donor pool, we compute $\delta_{\hat{\alpha}}$ using bootstrap procedures outlined in Section \ref{varbootstrap}.
+In other words, $k$ times of bootstrapping are nested in a LOOCV procedure.
 We find that $k=5$ or $k=10$ iterations of LOOCV performs well.
@@
 Let $\mc{A}$ be the set of adjustment estimators.
-For each $\hat{\alpha} \in \mc{A}$, let $\delta_{\hat{\alpha}} = 1(\hat\Delta(\hat{\alpha})>0)$ be a decision rule where $1(\cdot)$ is the indicator function and a $1$ corresponds to the decision to use adjustment estimator $\hat\alpha$.
-\textbf{Jilei, check these results and make sure that $\hat\Delta$ and $\Delta$ are used correctly.} If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) so that it make the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be incorrect.
-If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) so that it make the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be correct.
+For each $\hat{\alpha} \in \mc{A}$, let $\delta_{\hat{\alpha}} = I(\hat\Delta(\hat{\alpha})>0)$ be a decision rule where $I(\cdot)$ is the indicator function and a $1$ corresponds to the decision to use adjustment estimator $\hat\alpha$.
+If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported 1 (0, respectively) so that it make the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be incorrect.
+If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported 0 (1, respectively) so that it make the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be correct.
 These situations are depicted in the following table: \vspace*{0.3cm}
@@
 \begin{equation} \label{loocvm}
-	 \bar{\mc{C}}(\delta_{\hat{\alpha}})= \frac{1}{n} \sum_{m = 1}^n \mc{C}^{(-m)}(\delta_{\hat{\alpha}})
+	 \bar{\mc{C}}(\delta_{\hat{\alpha}})= \frac{1}{n} \sum_{m = 1}^n \mc{C}^{(-m)}(\delta_{\hat{\alpha}}),
 	\end{equation}
@@
 The mutual independence assumption in model setup $\mc{M}_{2}$ implies that $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
-\textbf{Jilei, what does almost unbiased mean?
-Can you clarify?} The LOOCV with $k$ random draws estimates $\E{\mc{C}(\delta_{\hat{\alpha}})}$ as
+The LOOCV with $k$ random draws estimates $\E{\mc{C}(\delta_{\hat{\alpha}})}$ as
 \begin{equation} \label{loocvk}
@@
 Our LOOCV procedure will consider $k=5$ random draws.
-\textbf{Jilei, can you briefly describe how bootstrapping and LOOCV are used together?}
+Recall in Section \ref{loocv} that $k$ times of bootstrap are nested in a LOOCV with $k$ random draws.
+It implies that $B(k+1)$ times of bootstrap replications are required for each Monte Carlo simulation.
 
@@
 Our adjustment estimators will be evaluated by multiple criteria.
-\textbf{Jilei, can you include guess in this section?
-Also, could you explain what guess is in the appropriate section, either here or in Section 3.3?} We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
+We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the \emph{guess}, with 1 suggesting $\hat{\alpha}$ reduces the risk according to our bootstrap estimation and 0 the converse.
+We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
 We will also consider the magnitude of the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ from the realized post-shock response $y_{1,T_1^*+1}$.
@@
 In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}).
+We mainly discuss simulations under $\mc{M}_2$ (see Section \ref{modelsetup}) for $\mc{B}_u$ and $\mc{B}_f$ (see Section \ref{varbootstrap}) with comparisons to those under $\mc{M}_1$ whose results are listed in Section 3 in Supplementary Materials.
 Two simulation setups are investigated.
@@
 
-\vspace*{0.5cm} \textbf{Jilei, please add a description of the simulation results.} \vspace{0.5cm}
-
 \begin{table}[h]
-\caption{30 Monte Carlo simulations with varying $n$ and $\sigma_{\alpha}$ \textbf{Jilei, can we get the predictions to fit in this table? A smaller text size might work}} \vspace{.3cm} \label{table1}
+\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table1}
 \begin{center}
-\begin{tabular}{cc|ccc|ccc}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c}{LOOCV with $k$ random draws}  \\ 
- $n$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ \\[.15cm] %&  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.15cm]
+\resizebox{\textwidth-1.2cm}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
+ $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
   \hline
-  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.96 (0.02) & 0.92 (0.02) \\ %& 0.36 (0.05) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.90 (0.02) & 0.92 (0.02) & 0.90 (0.02) \\ %& 0.40 (0.04) \\ 
-    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.80 (0.02) & 0.81 (0.02) & 0.80 (0.03) \\ %& 0.43 (0.04) \\ 
-    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.87 (0.06) & 0.55 (0.05) & 0.57 (0.05) & 0.55 (0.05) \\% & 0.38 (0.05) \\ 
-    & 100  & 0.47 (0.09) & 0.73 (0.08) & 0.47 (0.09) & 0.48 (0.05) & 0.48 (0.04) & 0.46 (0.04) \\[.3cm] % & 0.37 (0.05) \\[.3cm] 
-    \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.95 (0.02) & 0.95 (0.02) \\ %& 0.33 (0.04) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.91 (0.03) & 0.92 (0.03) \\ %& 0.33 (0.04) \\ 
-    & 25  & 0.90 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.77 (0.04) & 0.79 (0.04) & 0.75 (0.05) \\ %& 0.31 (0.04) \\ 
-    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.55 (0.04) & 0.64 (0.04) & 0.55 (0.05) \\ %& 0.31 (0.04) \\ 
-    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.53 (0.04) & 0.53 (0.05) & 0.51 (0.04) \\[.3cm] %& 0.33 (0.04) \\[.3cm] 
-    \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.93 (0.02) & 0.92 (0.02) \\ %& 0.31 (0.05) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.92 (0.02) \\ %& 0.30 (0.03) \\ 
-   & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.83 (0.03) & 0.83 (0.03) \\ %& 0.35 (0.04) \\ 
-  & 50  & 0.90 (0.06) & 0.93 (0.05) & 0.90 (0.06) & 0.71 (0.03) & 0.67 (0.04) & 0.69 (0.04) \\ %& 0.33 (0.04) \\ 
-    & 100  & 0.70 (0.09) & 0.73 (0.08) & 0.70 (0.09) & 0.54 (0.05) & 0.61 (0.04) & 0.54 (0.05) \\[.3cm] %& 0.31 (0.05) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.90 (0.03) & 0.91 (0.03) & 0.90 (0.03) \\ %& 0.27 (0.04) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) \\ %& 0.30 (0.03) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.73 (0.03) & 0.74 (0.04) & 0.73 (0.03) \\ %& 0.29 (0.03) \\ 
-    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.83 (0.07) & 0.55 (0.05) & 0.56 (0.05) & 0.55 (0.05) \\ %& 0.29 (0.04) \\ 
-    & 100  & 0.77 (0.08) & 0.73 (0.08) & 0.77 (0.08) & 0.48 (0.05) & 0.49 (0.04) & 0.49 (0.05) \\ %& 0.31 (0.05) \\ 
-\end{tabular}
+ \multirow{5}{*}{5}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.96 (0.01) & 0.92 (0.02) & 65.47 (4.77) & 19.92 (3.57) & 21.86 (3.99) & 20.27 (3.62) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.9 (0.02) & 0.92 (0.02) & 0.9 (0.02) & 65.67 (4.9) & 20.66 (3.74) & 22.92 (4.2) & 21.1 (3.75) \\ 
+    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.8 (0.02) & 0.81 (0.02) & 0.8 (0.03) & 66.29 (5.83) & 27.98 (4.21) & 30.3 (4.87) & 28.3 (4.18) \\ 
+    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.87 (0.06) & 0.55 (0.05) & 0.57 (0.04) & 0.55 (0.05) & 70.59 (7.46) & 43.1 (6.19) & 46.31 (6.8) & 43.07 (6.16) \\ 
+    & 100  & 0.47 (0.09) & 0.73 (0.08) & 0.47 (0.09) & 0.48 (0.04) & 0.48 (0.04) & 0.46 (0.04) & 89.82 (10.49) & 76.74 (11.42) & 79.78 (12.26) & 76.69 (11.33) \\[.3cm]  
+   \multirow{5}{*}{10}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.95 (0.02) & 0.95 (0.02) & 55.66 (4.28) & 16.36 (2.48) & 17.51 (2.41) & 16.6 (2.45) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.03) & 0.92 (0.02) & 55.91 (4.71) & 18.28 (2.85) & 19.38 (2.88) & 18.44 (2.83) \\ 
+    & 25  & 0.9 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.77 (0.04) & 0.79 (0.04) & 0.75 (0.04) & 59.43 (6.1) & 29.01 (4.24) & 32.1 (4.3) & 28.84 (4.26) \\ 
+    & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.55 (0.04) & 0.64 (0.04) & 0.55 (0.04) & 69.34 (9.45) & 52.52 (6.75) & 58.05 (7.28) & 52.28 (6.76) \\ 
+    & 100  & 0.63 (0.09) & 0.7 (0.09) & 0.63 (0.09) & 0.53 (0.04) & 0.53 (0.05) & 0.51 (0.04) & 104.19 (15.88) & 99.93 (12.83) & 113.77 (13.42) & 99.57 (12.81) \\[.3cm]  
+   \multirow{5}{*}{15}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.93 (0.02) & 0.92 (0.02) & 51.78 (2.74) & 12.66 (2.48) & 13.89 (2.48) & 12.64 (2.49) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.92 (0.02) & 51.82 (3.04) & 13.93 (2.52) & 16 (2.63) & 14.05 (2.53) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.83 (0.03) & 0.83 (0.03) & 51.94 (4.56) & 21.27 (2.93) & 24.49 (3.69) & 21.75 (2.92) \\ 
+    & 50  & 0.9 (0.06) & 0.93 (0.05) & 0.9 (0.06) & 0.71 (0.03) & 0.67 (0.04) & 0.69 (0.04) & 55.22 (7.06) & 35.85 (4.63) & 42.72 (5.93) & 36.41 (4.71) \\ 
+    & 100  & 0.7 (0.09) & 0.73 (0.08) & 0.7 (0.09) & 0.54 (0.05) & 0.61 (0.04) & 0.54 (0.05) & 76.44 (10.75) & 67.79 (8.77) & 79.49 (11.44) & 68.57 (8.96) \\[.3cm]  
+   \multirow{5}{*}{25}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.9 (0.03) & 0.91 (0.02) & 0.9 (0.03) & 62.23 (6.88) & 21.29 (5.9) & 19.29 (5.88) & 21.34 (5.93) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.02) & 0.87 (0.03) & 61.28 (7.09) & 22.96 (5.91) & 20.81 (5.89) & 23.02 (5.94) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.73 (0.03) & 0.74 (0.04) & 0.73 (0.03) & 61.9 (7.5) & 30.04 (6.46) & 28.76 (6.46) & 30.17 (6.48) \\ 
+    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.83 (0.07) & 0.55 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 67.46 (9.23) & 45.5 (8.55) & 47.38 (8.62) & 45.67 (8.58) \\ 
+    & 100  & 0.77 (0.08) & 0.73 (0.08) & 0.77 (0.08) & 0.48 (0.05) & 0.49 (0.04) & 0.49 (0.05) & 91.08 (14.54) & 81.72 (14.24) & 85.72 (15.39) & 82.3 (14.24) \\ 
+\end{tabular}}
    \end{center}
@@
 
-\begin{table}[h]
-\caption{30 Monte Carlo simulations with varying $\sigma$ and $\sigma_{\alpha}$ \textbf{Jilei, can we get the predictions to fit in this table? A smaller text size might work}} \label{table2}
+First, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we  observe from Table \ref{table1} that the decision making of $\delta_{\hat{\alpha}}$ is nearly correct  for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small  from Table \ref{table1}.
+The reasons can be explained as follows.
+When $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal according to construction of $\hat{\alpha}_{\rm wadj}$ in Section \ref{constructionofestimators}.
+Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
+However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the $\delta_{\hat{\alpha}}$  become more incorrect for $\hat{\alpha}\in \mc{A}$.
+It is to be expected since the bootstrap estimates become more biased.
+However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$.
+Second, fixing $\sigma_{\alpha}$, we can observe that the correctness of $\delta_{\hat{\alpha}}$ increases when $n$ increases.
+It is due to the robustness gain in estimation when $n$ increases.
+
+Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down.
+Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$.
+But it is not present for $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ since we applied the fact  $\hat{\alpha}_{\rm wadj}$ is unbiased for $\E{\alpha_1}$ from Proposition \ref{unbiased} in plugging it in with replacing $\E{\alpha_1}$.
+Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative.
+Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of consistencies between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
+For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.90 \times 0.66 = 0.594$ from table \ref{table1}.
+In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.
+
+From columns related to distance to $y_{1, T_1^*+1}$ in Table \ref{table1}, as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
+When $\sigma_{\alpha}= 5, 10, 25$, forecasts using $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are always better than the original forecast significantly.
+But it does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
+It is reasonable in that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
+Nevertheless, no statistical evidence has been found to support the claim that $n$ matters in prediction.
+In other words, $n$ matters in producing reliable decision-making of $\delta_{\hat{\alpha}}$  rather than reliable prediction.
+
+\begin{table}[H]
+\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table2}
 \begin{center}
-\begin{tabular}{cc|ccc|ccc}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c}{LOOCV with $k$ random draws}  \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$  \\[.3cm] %&  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.3cm]
+\resizebox{\textwidth-1.2cm}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
+ $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
   \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.99 (0.01) & 0.99 (0.01) & 0.99 (0.01) \\ %& 0.39 (0.05) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.97 (0.01) & 0.97 (0.01) & 0.97 (0.01) \\ %& 0.34 (0.04) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.81 (0.04) & 0.82 (0.04) & 0.81 (0.04) \\% & 0.29 (0.04) \\ 
-    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.57 (0.05) & 0.67 (0.04) & 0.57 (0.05) \\% & 0.34 (0.04) \\ 
-    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.51 (0.04) & 0.53 (0.05) & 0.50 (0.04) \\[.3cm] %& 0.35 (0.05) \\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.95 (0.02) & 0.95 (0.02) \\ %& 0.33 (0.04) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.91 (0.03) & 0.92 (0.03) \\ %& 0.33 (0.04) \\ 
-    & 25  & 0.90 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.77 (0.04) & 0.79 (0.04) & 0.75 (0.05) \\ %& 0.31 (0.04) \\ 
-    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.77 (0.08) & 0.55 (0.04) & 0.64 (0.04) & 0.55 (0.05) \\ %& 0.31 (0.04) \\ 
-    & 100  & 0.63 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.53 (0.04) & 0.53 (0.05) & 0.51 (0.04) \\[.3cm] %& 0.33 (0.04) \\[.3cm] 
-   \multirow{5}{*}{25}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.79 (0.04) & 0.78 (0.04) & 0.77 (0.04) \\ %& 0.19 (0.04) \\ 
-    & 10  & 0.97 (0.03) & 0.97 (0.03) & 0.97 (0.03) & 0.75 (0.04) & 0.75 (0.04) & 0.73 (0.05) \\ %& 0.20 (0.04) \\ 
-   & 25  & 0.90 (0.06) & 0.93 (0.05) & 0.90 (0.06) & 0.66 (0.05) & 0.69 (0.05) & 0.66 (0.05) \\ %& 0.30 (0.05) \\ 
-    & 50  & 0.77 (0.08) & 0.80 (0.07) & 0.80 (0.07) & 0.55 (0.05) & 0.64 (0.05) & 0.55 (0.05) \\ %& 0.34 (0.05) \\ 
-    & 100  & 0.60 (0.09) & 0.70 (0.09) & 0.63 (0.09) & 0.48 (0.04) & 0.52 (0.04) & 0.47 (0.04) \\[.3cm] % & 0.31 (0.04) \\[.3cm] 
-   \multirow{5}{*}{50}  & 5  & 0.73 (0.08) & 0.73 (0.08) & 0.77 (0.08) & 0.57 (0.05) & 0.57 (0.05) & 0.58 (0.05) \\ %& 0.24 (0.04) \\ 
-    & 10  & 0.73 (0.08) & 0.73 (0.08) & 0.73 (0.08) & 0.55 (0.05) & 0.55 (0.05) & 0.55 (0.05) \\ %& 0.23 (0.03) \\ 
-    & 25  & 0.77 (0.08) & 0.70 (0.09) & 0.73 (0.08) & 0.48 (0.05) & 0.51 (0.05) & 0.47 (0.05) \\ %& 0.24 (0.04) \\ 
-    & 50  & 0.77 (0.08) & 0.73 (0.08) & 0.73 (0.08) & 0.46 (0.05) & 0.53 (0.04) & 0.47 (0.05) \\ %& 0.25 (0.04) \\ 
-    & 100  & 0.57 (0.09) & 0.70 (0.09) & 0.57 (0.09) & 0.46 (0.05) & 0.49 (0.03) & 0.45 (0.05) \\[.3cm] %& 0.33 (0.05) \\[.3cm] 
-  \multirow{5}{*}{100}  & 5  & 0.63 (0.09) & 0.60 (0.09) & 0.63 (0.09) & 0.46 (0.05) & 0.52 (0.04) & 0.48 (0.05) \\ %& 0.23 (0.04) \\ 
-    & 10  & 0.60 (0.09) & 0.60 (0.09) & 0.63 (0.09) & 0.46 (0.05) & 0.53 (0.04) & 0.46 (0.05) \\ %& 0.24 (0.04) \\ 
-    & 25  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.45 (0.05) & 0.54 (0.04) & 0.47 (0.05) \\ %& 0.21 (0.04) \\ 
-    & 50  & 0.57 (0.09) & 0.53 (0.09) & 0.57 (0.09) & 0.49 (0.04) & 0.54 (0.04) & 0.47 (0.05) \\ %& 0.23 (0.03) \\ 
-    & 100  & 0.43 (0.09) & 0.53 (0.09) & 0.43 (0.09) & 0.52 (0.05) & 0.55 (0.03) & 0.51 (0.05) \\ %& 0.27 (0.04) \\
-\end{tabular}
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.97 (0.01) & 0.97 (0.01) & 0.97 (0.01) & 49.95 (2.46) & 12.36 (1.71) & 11.71 (1.55) & 12.13 (1.71) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.92 (0.02) & 0.92 (0.02) & 51.25 (2.88) & 13.14 (1.88) & 14.55 (1.7) & 12.84 (1.87) \\ 
+  & 25  & 0.97 (0.03) & 1 (0) & 1 (0) & 0.81 (0.03) & 0.84 (0.03) & 0.81 (0.03) & 54.85 (4.6) & 19.32 (3.07) & 20.87 (3.45) & 19.75 (3.13) \\ 
+  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.59 (0.04) & 0.62 (0.03) & 0.58 (0.04) & 60.57 (8.15) & 43.17 (5.49) & 47.62 (5.88) & 43.59 (5.63) \\ 
+  & 100  & 0.67 (0.09) & 0.63 (0.09) & 0.67 (0.09) & 0.45 (0.04) & 0.49 (0.04) & 0.49 (0.04) & 71.15 (10.52) & 72.15 (9.61) & 80.17 (9.52) & 71.7 (9.57) \\[.3cm] 
+ \multirow{5}{*}{10} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.91 (0.02) & 0.91 (0.02) & 0.91 (0.02) & 48.65 (3.85) & 18.3 (2.4) & 19.78 (2.31) & 18.64 (2.39) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.9 (0.02) & 0.93 (0.02) & 0.91 (0.02) & 52.46 (4.4) & 16.52 (3.06) & 15.86 (3.18) & 16.46 (3.06) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.79 (0.04) & 0.81 (0.03) & 0.8 (0.04) & 64.81 (4.93) & 24.85 (3.5) & 24.78 (3.7) & 24.94 (3.58) \\ 
+  & 50  & 0.87 (0.06) & 0.9 (0.06) & 0.87 (0.06) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 65.69 (6.74) & 40.16 (5.47) & 37.29 (5.35) & 39.44 (5.49) \\ 
+  & 100  & 0.63 (0.09) & 0.67 (0.09) & 0.63 (0.09) & 0.43 (0.04) & 0.47 (0.03) & 0.43 (0.04) & 67.98 (10.7) & 65.69 (8.35) & 78.45 (9.42) & 67.75 (8.58) \\[.3cm] 
+ \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.73 (0.03) & 0.74 (0.03) & 0.73 (0.03) & 58.32 (7.69) & 39.37 (7.46) & 39.16 (7.89) & 39.6 (7.47) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.71 (0.04) & 0.73 (0.05) & 0.73 (0.04) & 65.93 (5.72) & 33.34 (5.91) & 34.04 (5.49) & 33.05 (5.89) \\ 
+ & 25  & 0.9 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.67 (0.04) & 0.68 (0.03) & 0.66 (0.04) & 56.05 (7.5) & 39.49 (5.25) & 35.65 (4.98) & 39.73 (5.26) \\ 
+  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.59 (0.04) & 0.62 (0.04) & 0.59 (0.04) & 60.85 (7.93) & 46.55 (6.83) & 47.97 (7.4) & 47.23 (6.73) \\ 
+  & 100  & 0.67 (0.09) & 0.7 (0.09) & 0.63 (0.09) & 0.53 (0.05) & 0.53 (0.04) & 0.53 (0.05) & 95.21 (12.76) & 98.68 (11.57) & 99.87 (13.28) & 98.77 (11.61) \\[.3cm] 
+   \multirow{5}{*}{50} & 5  & 0.77 (0.08) & 0.7 (0.09) & 0.77 (0.08) & 0.6 (0.04) & 0.61 (0.03) & 0.61 (0.04) & 71.05 (8.49) & 52.9 (8.7) & 57.45 (9.57) & 53.05 (8.59) \\ 
+    & 10  & 0.63 (0.09) & 0.63 (0.09) & 0.63 (0.09) & 0.57 (0.04) & 0.57 (0.05) & 0.57 (0.04) & 68.23 (7.38) & 44.22 (5.95) & 55.53 (6.2) & 44.63 (5.86) \\ 
+  & 25  & 0.73 (0.08) & 0.67 (0.09) & 0.77 (0.08) & 0.55 (0.04) & 0.55 (0.04) & 0.57 (0.04) & 69.78 (10.51) & 63.97 (9.49) & 68.82 (9.79) & 64.33 (9.47) \\ 
+  & 50  & 0.83 (0.07) & 0.8 (0.07) & 0.83 (0.07) & 0.55 (0.04) & 0.51 (0.05) & 0.55 (0.04) & 64.9 (11.37) & 66.61 (10.07) & 73.22 (10.92) & 67.06 (9.99) \\ 
+  & 100  & 0.47 (0.09) & 0.53 (0.09) & 0.47 (0.09) & 0.49 (0.04) & 0.51 (0.04) & 0.49 (0.04) & 92.78 (12) & 73.61 (11.81) & 78.33 (10.92) & 74.37 (11.63) \\[.3cm] 
+ \multirow{5}{*}{100} & 5  & 0.5 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.49 (0.05) & 0.48 (0.04) & 0.47 (0.05) & 125.13 (15.27) & 104.01 (14.95) & 100.33 (13.71) & 105.4 (14.95) \\ 
+    & 10  & 0.4 (0.09) & 0.4 (0.09) & 0.37 (0.09) & 0.49 (0.03) & 0.51 (0.05) & 0.51 (0.04) & 106.46 (14.76) & 101.82 (14.64) & 110.6 (14.95) & 98.85 (14.69) \\ 
+  & 25  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.49 (0.04) & 0.48 (0.04) & 0.51 (0.04) & 142.91 (16.43) & 132.29 (18.34) & 146.26 (17.96) & 132.06 (18.25) \\ 
+  & 50  & 0.57 (0.09) & 0.57 (0.09) & 0.57 (0.09) & 0.5 (0.05) & 0.5 (0.05) & 0.49 (0.04) & 114.36 (15.46) & 93 (16.26) & 95.41 (15.89) & 91.92 (15.98) \\ 
+    & 100  & 0.33 (0.09) & 0.3 (0.09) & 0.3 (0.09) & 0.49 (0.05) & 0.49 (0.05) & 0.48 (0.05) & 150.5 (20.71) & 148.07 (17.57) & 151.26 (17.18) & 148.96 (17.71) \\ 
+\end{tabular}}
    \end{center}
@@
 
-%\subsection{Simulation for prediction}
-%\label{simulationforprediction}
-
-\begin{table}[t]
- \caption{30 Monte Carlo simulation with varying $n$ and $\sigma_{\alpha}$ (distance to $y_{1, T_1^*+1}$). \textbf{Jilei, which simulation setting do these results correspond to?}} \label{table3}
+From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will  decrease, which is a pattern similar to the one shown in the first experiment.
+Furthermore, as $\sigma$ increases fixing $\sigma_{\alpha}$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases as well.
+Note that the correctness  hinges on the estimation of the parameters.
+Since $\hat{\alpha}_{\rm wadj}$  is a linear combination of OLS estimates, as $\sigma$ increases, $\var{\hat{\alpha}_{\rm wadj}}$ increases as well.
+Therefore, $\hat{\alpha}_{\rm wadj}$ become more volatile and its estimation of $\E{\alpha_1}$ can be less reliable.
+Those reasons can explain  why an increase of $\sigma_{\alpha}$ contributes to a decrease of  $\bar{\mc{C}}(\delta_{\hat{\alpha}})$.
+We observe similar patterns for distance to $y_{1, T_1^*+1}$ as well.
+When $\sigma$ increases with fixing $\sigma_{\alpha}$, it is likely that the degree of variation of $y_{1,t}$ exceeds the extent of adjustment improvement $\hat{\alpha}$ can contribute to for $\hat{\alpha}\in \mc{A}$.
+
+With respect to averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases.
+It is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
+The reasons can be outlined as below.
+Recall in Section \ref{conditionsm2122}, the conditions of risk-reduction propositions involve $(\E{\alpha_1})^2 > \var{\hat{\alpha}} + (\E{\hat{\alpha}}-\E{\alpha_1})^2$ for $\hat{\alpha}\in \mc{A}$, where we note that those parameters are \emph{true} ones but not estimated ones.
+Notice that $\var{\hat{\alpha}}$ is  an increasing function of $\sigma$ since $\hat{\alpha}$ is estimated by OLS.
+Therefore, it explains the reason why the increase of $\sigma$ would result in a decrease of averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ since the inequality is not likely to hold when  $\var{\hat{\alpha}}$ increases.
+
+\begin{table}[H]
+\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table3}
 \begin{center}
-\begin{tabular}{cc|cccc}
-  $\sigma$   & $\sigma_{\alpha}$  & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.3cm]  
+\resizebox{\textwidth-1.2cm}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
+ $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}} $  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
   \hline
- \multirow{5}{*}{5}  & 5  & 53.27 (2.59) & 10.91 (1.70) & 11.77 (1.55) & 10.8 (1.69) \\ 
-   & 10  & 50.86 (3.83) & 18.06 (2.18) & 17.26 (2.17) & 18.25 (2.17) \\ 
-    & 25  & 60.52 (3.97) & 16.09 (2.40) & 19.83 (3.05) & 15.87 (2.38) \\ 
-     & 50  & 54.65 (6.95) & 51.79 (6.87) & 53.83 (7.26) & 52.6 (6.91) \\ 
-     & 100  & 104.73 (13.00) & 88.31 (12.16) & 88.88 (12.63) & 86.72 (12.35) \\[.3cm] 
-   \multirow{5}{*}{10}  & 5  & 58.17 (4.18) & 18.17 (2.61) & 16.59 (2.39) & 18.09 (2.63) \\ 
-    & 10  & 52.81 (4.07) & 19.05 (2.49) & 19.67 (2.66) & 18.95 (2.53) \\ 
-     & 25  & 61.53 (5.69) & 28.55 (4.07) & 31.82 (4.27) & 28.76 (4.07) \\ 
-     & 50  & 56.31 (8.03) & 47.33 (4.89) & 41.44 (4.39) & 46.86 (4.79) \\ 
-     & 100  & 84.38 (11.62) & 82.91 (11.77) & 84.5 (12.39) & 84.3 (11.93) \\[.3cm] 
-   \multirow{5}{*}{25}  & 5  & 56.35 (6.1) & 25.54 (4.06) & 30.49 (4.61) & 25.94 (4.02) \\ 
-     & 10  & 49.8 (5.24) & 25.04 (4.38) & 26.74 (3.64) & 24.86 (4.38) \\ 
-     & 25  & 54.21 (6.51) & 44.17 (6.66) & 43.41 (6.95) & 43.89 (6.63) \\ 
-     & 50  & 66.51 (7.86) & 46.19 (8.04) & 44.83 (9.31) & 46.54 (8.27) \\ 
-     & 100  & 109.21 (13.29) & 78.47 (12.45) & 83.99 (12.00) & 78.57 (12.75) \\[.3cm] 
-   \multirow{5}{*}{50}  & 5  & 75.29 (10.75) & 63.51 (8.30) & 64.25 (8.88) & 63.32 (8.40) \\ 
-     & 10  & 57.59 (6.00) & 48.51 (8.32) & 50.58 (8.63) & 48.08 (8.36) \\ 
-     & 25  & 77.21 (12.03) & 54.73 (9.47) & 54.76 (10.24) & 54.2 (9.62) \\ 
-     & 50  & 90.48 (10.21) & 68.88 (9.20) & 68.28 (10.48) & 68.8 (9.28) \\ 
-     & 100  & 111.09 (17.54) & 102.47 (16.68) & 110.15 (15.87) & 101.53 (16.52) \\[.3cm] 
-   \multirow{5}{*}{100}  & 5  & 214.07 (67.40) & 195.46 (67.65) & 197.51 (68.45) & 196.58 (67.51) \\ 
-     & 10  & 120.85 (15.39) & 114.79 (15.51) & 119.19 (15.75) & 114.02 (15.74) \\ 
-     & 25  & 97.84 (13.75) & 95.02 (14.88) & 100.04 (16.94) & 96.23 (14.71) \\ 
-     & 50  & 141.22 (24.51) & 136.11 (25.73) & 150.62 (27.62) & 135.26 (25.39) \\ 
-     & 100  & 95.53 (12.80) & 103.01 (14.12) & 103.31 (16.27) & 105.79 (14.32) \\
-\end{tabular}	
+  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.9 (0.02) & 0.89 (0.02) & 51.92 (4.04) & 19.23 (2.55) & 20.64 (2.76) & 19.36 (2.52) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.89 (0.02) & 0.89 (0.02) & 52.58 (4.35) & 21.57 (2.58) & 23.38 (2.86) & 21.72 (2.5) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.78 (0.03) & 0.83 (0.02) & 0.79 (0.03) & 55.01 (5.84) & 30.3 (3.59) & 31.98 (4.36) & 30.2 (3.5) \\ 
+  & 50  & 0.9 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.66 (0.04) & 0.65 (0.04) & 0.65 (0.04) & 64.42 (8.11) & 50 (5.78) & 52.56 (6.92) & 49.55 (5.7) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.8 (0.07) & 0.57 (0.04) & 0.53 (0.04) & 0.57 (0.04) & 91.51 (13.2) & 94.26 (10.41) & 97.26 (12.57) & 93.61 (10.27) \\[.3cm] 
+  \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.92 (0.02) & 0.91 (0.02) & 52.34 (4) & 17.23 (2.96) & 18.54 (2.83) & 17.39 (2.95) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.89 (0.02) & 0.89 (0.02) & 52.59 (4.04) & 19.02 (3.24) & 20.95 (3.13) & 19.23 (3.24) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.75 (0.03) & 0.78 (0.03) & 0.77 (0.03) & 54.07 (4.97) & 27.66 (4.55) & 31.79 (4.47) & 27.84 (4.61) \\ 
+  & 50  & 0.83 (0.07) & 1 (0) & 0.8 (0.07) & 0.59 (0.04) & 0.63 (0.04) & 0.59 (0.04) & 60.32 (7.53) & 47.7 (7.04) & 52.97 (7.54) & 47.78 (7.17) \\ 
+  & 100  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.47 (0.04) & 0.51 (0.04) & 0.46 (0.04) & 85.6 (12.99) & 89.85 (12.82) & 100.74 (13.61) & 90.4 (12.91) \\[.3cm] 
+  \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.93 (0.02) & 0.91 (0.02) & 49.85 (4.01) & 18.07 (2.88) & 18.38 (2.71) & 18.04 (2.88) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.02) & 0.89 (0.02) & 0.87 (0.02) & 48.73 (4.3) & 19.45 (2.97) & 19.35 (2.86) & 19.32 (2.99) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.75 (0.03) & 0.78 (0.03) & 0.76 (0.03) & 47.06 (5.13) & 26.16 (3.31) & 26.81 (3.13) & 26.23 (3.33) \\ 
+  & 50  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.61 (0.04) & 0.69 (0.03) & 0.64 (0.04) & 48.75 (6.86) & 40.27 (4.43) & 42.09 (4.49) & 40.77 (4.38) \\ 
+  & 100  & 0.67 (0.09) & 1 (0) & 0.63 (0.09) & 0.55 (0.04) & 0.51 (0.04) & 0.55 (0.04) & 64.29 (11.11) & 68.85 (8.27) & 74.08 (8.72) & 69.91 (8.14) \\[.3cm] 
+  \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.94 (0.02) & 0.95 (0.02) & 57.6 (6.94) & 21.58 (5.9) & 20 (5.86) & 21.58 (5.9) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.91 (0.02) & 0.93 (0.02) & 56.8 (7.01) & 22.2 (5.97) & 20.47 (5.89) & 22.22 (5.97) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.78 (0.04) & 0.79 (0.04) & 0.77 (0.04) & 56.58 (7.49) & 28.96 (6.49) & 27.06 (6.19) & 29.03 (6.48) \\ 
+ & 50  & 0.9 (0.06) & 1 (0) & 0.9 (0.06) & 0.57 (0.04) & 0.6 (0.04) & 0.58 (0.04) & 64.33 (8.75) & 47.16 (8.28) & 46.3 (7.26) & 47.35 (8.25) \\ 
+     & 100  & 0.83 (0.07) & 1 (0) & 0.8 (0.07) & 0.49 (0.04) & 0.48 (0.04) & 0.5 (0.04) & 95.61 (13.02) & 90.1 (13.29) & 86.81 (11.75) & 90.55 (13.23) \\
+\end{tabular}}
    \end{center}
@@
 
-\textbf{Jilei, please integrate these results with a revised description of the results for the bootstrap procedure.}
-In the first experiment, table \ref{table3} shows that similar to Section \ref{parametricbootstrapsimulation}, as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
-When $\sigma_{\alpha}= 5, 10, 25$, forecasts using $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are always better than the original forecast significantly.
-But it does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
-It is reasonable in that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
-Nevertheless, unlike what is detected in Section \ref{parametricbootstrapsimulation}, no statistical evidence has been found to support the claim that $n$ matters in prediction.
-In other words, $n$ matters in producing reliable decision-making of $\delta_{\hat{\alpha}}$  rather than reliable prediction.
-
-Note that there is no statistical evidence supporting for differences among $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
-This observation corresponds to the fact that $\bar{\mc{C}}(\mc{A})$ is small and following analysis in Section \ref{parametricbootstrapsimulation}.
-When their performances do not differ much, the precision of ranking is small.
-In this scenario, for a more reasonable statistical inference, one may opt for a double bootstrap instead to approximate the distribution of $\Delta(\hat{\alpha})$ and compare estimators by checking for overlap of percentile intervals at some desirable error threshold.
-See more details in the Discussion.
-
-%In the second experiment, table \ref{table4} shows similar results for prediction to those in the first expeirment, for the case of varying $\sigma_{\alpha}$ but fixing $\sigma$, and the case of varying $\sigma$ but fixing $\sigma_{\alpha}$.
-When $\sigma$ increases with fixing $\sigma_{\alpha}$, it is likely that the degree of variation of $y_{1,t}$ exceeds the extent of adjustment improvement $\hat{\alpha}$ can contribute to for $\hat{\alpha}\in \mc{A}$.
-It can be confirmed by looking into  the case of $\sigma= 50, 100$ as opposed to the case for $\sigma= 5, 10, 25$ where adjusted forecasts outperform original forecasts.
-Adjusted forecasts can be worse than original forecast if the variation of $y_{i,t}$ is large and the signal of the covariates is very small.
-See for the case  of $\sigma=100$ and $\sigma_{\alpha}=100$ in table \ref{table4}.
+\begin{table}[H]
+\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table4}
+\begin{center}
+\resizebox{\textwidth-1.2cm}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
+ $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
+  \hline
+  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.99 (0.01) & 0.99 (0.01) & 0.99 (0.01) & 53.27 (2.59) & 10.91 (1.7) & 11.77 (1.55) & 10.8 (1.69) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.95 (0.02) & 0.92 (0.02) & 50.86 (3.83) & 18.06 (2.18) & 17.26 (2.17) & 18.25 (2.17) \\ 
+  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.83 (0.03) & 0.89 (0.02) & 0.83 (0.03) & 60.52 (3.97) & 16.09 (2.4) & 19.83 (3.05) & 15.87 (2.38) \\ 
+  & 50  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.67 (0.04) & 0.69 (0.03) & 0.67 (0.04) & 54.65 (6.95) & 51.79 (6.87) & 53.83 (7.26) & 52.6 (6.91) \\ 
+  & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.77 (0.08) & 0.52 (0.04) & 0.51 (0.04) & 0.51 (0.05) & 104.73 (13) & 88.31 (12.16) & 88.88 (12.63) & 86.72 (12.35) \\[.3cm] 
+  \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.93 (0.02) & 0.93 (0.02) & 58.17 (4.18) & 18.17 (2.61) & 16.59 (2.39) & 18.09 (2.63) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 52.81 (4.07) & 19.05 (2.49) & 19.67 (2.66) & 18.95 (2.53) \\ 
+  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.78 (0.03) & 0.82 (0.03) & 0.79 (0.03) & 61.53 (5.69) & 28.55 (4.07) & 31.82 (4.27) & 28.76 (4.07) \\ 
+  & 50  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.66 (0.04) & 0.67 (0.04) & 0.66 (0.04) & 56.31 (8.03) & 47.33 (4.89) & 41.44 (4.39) & 46.86 (4.79) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.54 (0.05) & 0.54 (0.04) & 0.55 (0.04) & 84.38 (11.62) & 82.91 (11.77) & 84.5 (12.39) & 84.3 (11.93) \\[.3cm] 
+  \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 1 (0) & 0.78 (0.03) & 0.77 (0.03) & 0.79 (0.03) & 56.35 (6.1) & 25.54 (4.06) & 30.49 (4.61) & 25.94 (4.02) \\ 
+   & 10  & 1 (0) & 1 (0) & 1 (0) & 0.81 (0.03) & 0.79 (0.03) & 0.81 (0.03) & 49.8 (5.24) & 25.04 (4.38) & 26.74 (3.64) & 24.86 (4.38) \\ 
+  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.72 (0.03) & 0.77 (0.03) & 0.71 (0.03) & 54.21 (6.51) & 44.17 (6.66) & 43.41 (6.95) & 43.89 (6.63) \\ 
+  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.57 (0.04) & 0.52 (0.04) & 66.51 (7.86) & 46.19 (8.04) & 44.83 (9.31) & 46.54 (8.27) \\ 
+  & 100  & 0.9 (0.06) & 1 (0) & 0.87 (0.06) & 0.54 (0.04) & 0.54 (0.04) & 0.56 (0.04) & 109.21 (13.29) & 78.47 (12.45) & 83.99 (12) & 78.57 (12.75)\\[.3cm] 
+  \multirow{5}{*}{50} & 5  & 0.83 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.54 (0.04) & 0.57 (0.04) & 0.55 (0.04) & 75.29 (10.75) & 63.51 (8.3) & 64.25 (8.88) & 63.32 (8.4) \\ 
+  & 10  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.53 (0.04) & 0.55 (0.05) & 0.53 (0.04) & 57.59 (6) & 48.51 (8.32) & 50.58 (8.63) & 48.08 (8.36) \\ 
+  & 25  & 0.73 (0.08) & 0.8 (0.07) & 0.73 (0.08) & 0.58 (0.04) & 0.58 (0.04) & 0.57 (0.04) & 77.21 (12.03) & 54.73 (9.47) & 54.76 (10.24) & 54.2 (9.62) \\ 
+  & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.04) & 0.53 (0.04) & 0.6 (0.04) & 90.48 (10.21) & 68.88 (9.2) & 68.28 (10.48) & 68.8 (9.28) \\ 
+  & 100  & 0.5 (0.09) & 0.73 (0.08) & 0.53 (0.09) & 0.51 (0.05) & 0.48 (0.05) & 0.51 (0.05) & 111.09 (17.54) & 102.47 (16.68) & 110.15 (15.87) & 101.53 (16.52) \\[.3cm] 
+  \multirow{5}{*}{100} & 5  & 0.43 (0.09) & 0.37 (0.09) & 0.43 (0.09) & 0.47 (0.04) & 0.47 (0.04) & 0.47 (0.04) & 214.07 (67.4) & 195.46 (67.65) & 197.51 (68.45) & 196.58 (67.51) \\ 
+  & 10  & 0.63 (0.09) & 0.6 (0.09) & 0.67 (0.09) & 0.51 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 120.85 (15.39) & 114.79 (15.51) & 119.19 (15.75) & 114.02 (15.74) \\ 
+  & 25  & 0.57 (0.09) & 0.6 (0.09) & 0.57 (0.09) & 0.51 (0.04) & 0.53 (0.04) & 0.49 (0.04) & 97.84 (13.75) & 95.02 (14.88) & 100.04 (16.94) & 96.23 (14.71) \\ 
+  & 50  & 0.53 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.47 (0.04) & 0.49 (0.05) & 0.49 (0.05) & 141.22 (24.51) & 136.11 (25.73) & 150.62 (27.62) & 135.26 (25.39) \\ 
+  & 100  & 0.63 (0.09) & 0.63 (0.09) & 0.63 (0.09) & 0.43 (0.04) & 0.41 (0.04) & 0.45 (0.04) & 95.53 (12.8) & 103.01 (14.12) & 103.31 (16.27) & 105.79 (14.32) \\
+\end{tabular}}
+   \end{center}
+      \vspace{-.5cm}
+\end{table}
+
+Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented. See table \ref{table3} and table \ref{table4} for results. Comparing table \ref{table1}
+ and table \ref{table2} yields that when $n$ is small ($n = 5$ or $n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
+For other situations, $\mc{B}_u$  and $\mc{B}_f$  are rather similar.
+It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool.
+Concerning  table \ref{table2} and table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
+It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$.
+However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_f$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$.
+In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is small; otherwise, they are similar.
+See more discussions for differences between $\mc{B}_u$ and $\mc{B}_f$ in Section \ref{discussion}.
+
+ Simulation results of $\mc{M}_1$ are listed in Section 3 in Supplementary Materials.
+Its results are very similar to those of $\mc{M}_2$ except for the difference among estimators.
+The results show that in many situations, $\hat{\alpha}_{\rm adj}$ is better than $\hat{\alpha}_{\rm IVW}$, which is in turn better than $\hat{\alpha}_{\rm wadj}$ with statistical evidence; in other situations, they are mostly the same without statistical significance.
+Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
+Therefore, similarity weighting may not be informative when the model for $\alpha_i$ is identified wrongly.
+Under $\mc{M}_1$, simple averaging aimed for a reduction of variance or inverse-variance weighting targeting on reducing negative effects from varying time lengths may work better.
 
@@
 Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $2p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
-However, in applications, it is likely that $\mathbf{W}^*$ may take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-\textbf{Jilei, in the previous sentence is it likely that bootstrapping will fail in applications or is it possible that bootstrapping will fail in applications?} %Moreover, when $2p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
-The subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$.
-But we may leave its mathematical justification for future research.
+However, in applications, it is possible that $\mathbf{W}^*$ may take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
+Moreover, when $2p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
+However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
+Note that there are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_f$.
+$\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
+In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
 

### 2020-07-15 Rcode/sim.study.R

@@ -422,9 +422,10 @@ cv <- function(k, X, Y, Tstar, np, B) {
 }
 
 # simulation study normal
-sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma, 
-                                    sigma.alpha, sigma.delta.gamma, 
-                                    p, B, n, k, scale, np = c(TRUE, FALSE)) {
+sim.study.normal.gammaX <- function(mu.gamma.delta = 1, mu.alpha, sigma, 
+                                    sigma.alpha, sigma.delta.gamma = 0.5, 
+                                    p, B, n, k, scale, np = c(TRUE, FALSE),
+                                    model = 2) {
   T <- round(rgamma(n = n + 1, shape = 15, scale = 10)) # Time Length
   T[which(T < 90)] <- 90
   Tstar <- c() # Shock Time Points
@@ -433,37 +434,56 @@ sim.study.normal.gammaX <- function(mu.gamma.delta, mu.alpha, sigma,
   }
   phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters
 
-  
-  # construction of design matrix and shock effects
   X <- c()
   alpha <- c()
-  delta <- c()
-  gamma <- c()
-  for (i in 1:(n + 1)) {
-    Ti <- T[i]
-    Tstari <- Tstar[i]
-    X[[i]] <- matrix(rgamma(n = p * (Ti + 1), shape = 1, scale = scale), ncol = p, byrow = T) 
-    # matrix(rnorm(n = (Ti + 1) * p), ncol = p, byrow = T)
-    # parameter setup
-    delta[[i]] <- matrix(rnorm(p, mean = mu.gamma.delta, sd = sigma.delta.gamma), nrow = 1)
-    gamma[[i]] <- matrix(rnorm(p, mean = mu.gamma.delta, sd = sigma.delta.gamma), nrow = 1)
-    epsilontildei <- rnorm(n = 1, sd = sigma.alpha)
-    # alpha
-    alpha <- c(alpha, mu.alpha + delta[[i]] %*% X[[i]][Tstari + 1, ] + 
-                 gamma[[i]] %*% X[[i]][Tstari, ] + epsilontildei)
+  if (model == 2) {
+    # construction of design matrix and shock effects
+    delta <- c()
+    gamma <- c()
+    for (i in 1:(n + 1)) {
+      Ti <- T[i]
+      Tstari <- Tstar[i]
[…]

### 2020-07-20 manuscript/manuscript.tex
Overhauled Introduction and Discussion; made minor edits; still need to edit the main text

@@
 \author{Jilei Lin\thanks{jileil2@ilinois.edu}}
-\author{Ziyu Liu\thanks{ziyuliu3@illinois.edu}}
 \author{Daniel J. Eck\thanks{dje13@illinois.edu}}
@@
 
-\begin{center}
-  \textbf{Note}
-\end{center}
-
-\begin{center}
-  \textbf{Updates in this version}
-\end{center}
-
-\begin{enumerate}
-  \item Revisions to the manuscript (mainly in Simulations and Discussions). The comments are addressed as well.
-\end{enumerate}
-
-% table of contents
-%\tableofcontents
-
-\newpage
-
 \maketitle
@@
 The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best.
-Leave-one-out cross validation with $k$ random  draws is proposed to estimate consistency of risk-reduction propositions and best consistency of voting the best shock-estimators, prospectively informing users the probabilities that this prospective evaluation is consistent with the reality.
+Leave-one-out cross validation is proposed to estimate consistency of risk-reduction propositions and best consistency of voting the best shock-estimators, prospectively informing users of the probabilities that this prospective evaluation is consistent with the reality.
 Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
@@
 In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock. 
-It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.
+%It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.
 However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study.
-One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error.
-%Then, we discuss some frequently used methodologies that may be applied in this situation.
-%When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.
-
-Improving forecasts through forecast combination has a rich history \citep{bates1969combination, mundlak1978pooling, timmermann2006forecast, granger2014forecasting}.  
-%\citet{timmermann2006forecast} provided several reasons for combining forecasts.
-In particular, combining forecasts may be beneficial when: 1) the information set underlying individual forecasts is often unobserved to the forecast user; 2) different individual forecasts may be very differently affected by non-stationarity and model misspecifications; 3) different individual forecasts may be motivated by different loss functions \citep[and references therein]{timmermann2006forecast}.
-The classical setting for the forecast combination problem is when there are competing forecasts for a single time series.
-%In this setting, one may desire combining forecasts as a method for lowering overall forecast error.
-%\textbf{Integrate this paragraph into the next paragraph.}
-In this setting there are a plethora of methods for combining forecasts, e.g., model averaging \citep{newbold2002forecast, hendry2004pooling, koop2004forecasting, timmermann2006forecast, eklund2007forecast, hansen2008least}, model selection \citep{swanson1997model, swanson2001choosing, lee2015model}, and other various methods \citep{pesaran2011forecast,li2014forecasting}.
-Forecast encompassing methods are developed to test whether competing forecasts are suitable for combinations \citep{newbold2002forecast, fang2003forecasting}.
-
-%Time-series pooling is a broad topic for borrowing information from multiple time series for prediction improvement and is the focus of this paper.
-\textbf{Need to mention that these methods may fail or be irrelevant in the presence of shock effects.}
-
-% In our post-shock setting we combine estimated quantities from different time series with the aim of lowering forecast error for a single time series under study.
-Our techniques are similar to those in time-series pooling and data integration.
-The literature of time-series pooling is mainly related to pooling cross-sectional panel data \citep{mundlak1978pooling, zellner1991forecasting, fosten2019panel}.
-The issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded.
-\citet{baltagi2008forecasting} showed that homogeneity approach often outperform  heterogeneity one in mean squared forecast error; while heterogeneity approach is more general to accommodate differences among units.
-\textbf{How does this relevant to what we are doing?}
-
-Data integration and time series pooling for forecasting is a broad domain of research including ideas from many areas.
-Time-series pooling methods are frequently used for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.
-Recent developments in data integration have investigated versatile methods to combine knowledge from multiple datasets for better prediction.
-%whose ideas are similar to ours.
-For instance, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
-to improve predictive precision of COVID-19 infection trajectories for different countries.
-A similar setup may be appropriate for post-shock prediction but may be too dependent upon model specification for the shock distribution.
-%, and conditions for predictive improvement are generally hard to know. 
-  \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering.
-However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
-%From a machine learning perspective,
-\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
-They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
-However, the model-free perspective seeks for a perfect fit on the past data.
-If the work of \citet{agarwal2020two} were adapted to post-shock setting by treating structural shocks as "interventions", the prediction would have been only a guess.
-Though their methods are quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
+The core idea of our methodology is to sensibly combine similar shock effects that have occurred in the past which arose from disparate time-series, and then add them to the present forecast.
+Our method of combining disparate shock effects embraces ideas from time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, and synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, clements2019measuring}.
+%, and nowcasting \citep{matheson2010nowcasting, fosten2019panel}.
+%baltagi2008econometric
+
+In our post-shocking setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
+The researcher must therefore move beyond the modeling paradigm that they were previously working under to accommodate this new shockas in judgement forecasting \citep{monti2008forecast, svensson2005monetary}.
+In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past.
+Construction of the donor pool that forms this panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
+As in SCM, care is needed when forming the donor pool of disparate time series.
+However, there are key differences between our framework and SCM.
+We assume that the disparate time series are independent from the time series under study before the timing of the shock.
+We also assume that the shock-effects for each disparate time series are independent realizations from some unknown distribution.
+
+We estimate the shock-effects that are present in the disparate time series for which post-shock responses are observed.
+We then aggregate these estimated shock-effects and use this aggregated estimate as an estimator for the shock-effect in the time series of interest.
+This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest.
+Shock-effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
+The context in \cite{clements2019measuring} allowed for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
+We offer no such consistency guarantee here.
+In our context, the yet to observed shock-effect of interest is a realization from a random process that can only be partially explained by the realizations of the disparate time series.
 
@@
 %The Bayesian hierarchical approach of \citet{lee2020estimation} may be too sensitive to prior and the hierarchical parametric model setup.
-
 Overall, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock.
-To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration.
-We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure.
-The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point.
-
+
+In this paper, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure.
+Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
+However, our model formulation is more general than \cite{ramaswamy1993empirical} and our donor pool is formed from independent time series.
+%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point.
 We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting.
 The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast, and estimate risk-reduction quantities to find the best technique out of the three.
-The involved parameters in the risk-reduction propositions and risk-reduction quantities are estimated by parametric bootstrap.
-These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed.
-Furthermore, to inform the credibility of this prospective evaluation, we propose a leave-one-out cross validation with $k$ random draws to estimate the performance of the risk-reduction propositions and best consistency of voting the best shock-effect estimators prospectively.
-Our Monte Carlo simulation results show that the risk-reduction conditions are highly consistent when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases.
-Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large.
-We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a shock on March 9th, 2020.
-The proposed three aggregation techniques work much better than no adjustment in this example.
+These adjustment strategies all ``incorrectly'' target the mean of the shock-effect distribution.
+However, such an estimation strategy can reduce mean squared error (MSE) when variation in the shock-effect distribution is small relative to the mean.
+We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast.
+The involved parameters in the risk-reduction propositions and risk-reduction quantities can be estimated by a residual bootstrap procedure that we develop within.
+%These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed.
+We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock-effect adjustment estimators without.
+This prospective assessment does not require the observation of the post-shock response.
+Our Monte Carlo simulation results show that the risk-reduction conditions are highly consistent when the model for the shock effects is identified well with appropriate covariates under a fixed design.
+We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020.
+We show that our proposed adjustment estimators yield much better results than no adjustment in this setting.
 We also use this example to demonstrate settings in which the shock-effect may be decomposed into separate estimable parts.
-We now motivate our aggregation techniques.
+We now motivate our framework for post-shock forecasting.
 
@@
 Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of consistencies between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
-For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.90 \times 0.66 = 0.594$ from table \ref{table1}.
+For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.83 \times 0.55 = 0.457$ from Table \ref{table1}.
 In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.
@@
 The covariates and response of time series in the donor pool are adjusted for inflation.
-Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in Appendix \ref{smfda}.
-We computed 3 shock-effect estimates.
-Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$.
-For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
-\begin{align*}
- \mathbf{W}^*= (0.000,0.000, 0.000, 0.000, 1.000) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 1314.04.
-\end{align*}
-Note that the norm is computed using the $k$-dimensional Euclidean metric.
-The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is very similar to $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.
+Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Supplementary Materials.
+Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
+For $\hat{\alpha}_{\rm wadj}$, we observe that
+$
+  \mathbf{W}^*= (0.000,0.000, 0.000, 0.000, 1.000)
+$
+and 
+$
+  \norm{\mrm{vec}\left(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\right)}_{4} = 1314.04.
+$
+Note that the norm is computed using the $k$-dimensional Euclidean metric. The solution $\mathbf{W}^*$ suggests that the shock effect of interest is replicated by the November 27, 2014 shock effect.
 
@@
 
-Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models.
-Our simple AR(1) model can be extended to AR($p$) settings.
+We developed methodology for forecasting post-shock response values after the occurrence of a structural.
+Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock-effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock-effect estimator to the original forecast.
+We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock-effect settings.
+The model that we verify these claims under is a simple AR(1) model.
+Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
 %for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
+
 Moreover, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors.
-Similarly, LOOCV with $k$ random draws can be adapted to AR($p$).
-Besides, the functional form for the mean function for $y_{i,t}$ can be extended beyond the linear regression model under $\mc{M}_2$.
-Multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent.
+The functional form of the mean function in our considered models can be extended beyond the linear regression model.
+Multiple shock-effects can be nested within a time series; and time series in the donor pool can be dependent.
 As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
@@
 However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
-Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions with existing first and second moments.
+Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that second moments exist.
 The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
@@
 
-In this manuscript, we have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.
+We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.
 Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $2p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
@@
 
-Double bootstrap can be another general bootstrap alternative to the one proposed in Section \ref{varbootstrap}.
-The double bootstrap procedure adds another layer of residual bootstrapping between resampling of the donor pool and the resampling of the residuals.
-This procedure enables estimation of the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
-In the framework of double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, we can check whether a bootstrap percentile interval contain 0 at a desired error threshold.
-We have attempted Monte Carlo simulations using the same setting in Section \ref{simulation} for the double bootstrap procedure, the results of which are quite similar to those of Section \ref{varbootstrap}.
-
-For the use of our methodology, caution should be dedicated to the construction of donor pool.
-If the donor pool includes some individuals that are not similar to the time series of interest, the result will possibly not be robust to the introduced noises.
-Moreover, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large.
-It is  due to the fact that plug-in estimation of  risk-reduction quantities in Section \ref{varbootstrap} gains more precision when $n$ becomes large.
+%Double bootstrap can also be employed as an alternative to the bootstrap procedure proposed in Section \ref{varbootstrap}. 
+A double bootstrap procedure with similar steps to the bootstrap technique in Section~\ref{varbootstrap} can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
+The double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, can check whether a bootstrap percentile interval of resampled estimates of $\Delta(\hat{\alpha})$ contain 0 at a desired error threshold.
+We investigated such a double bootstrap procedure and found that it produced inferences that were similar to those produced using the bootstrap techniques developed in the main text.
+
+There have been several recent time series pooling methods developed for forecasting COVID-19 cases.
+\citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries.
+A similar setup may be appropriate for post-shock prediction but may be too dependent upon model specification for the shock distribution.
+\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach.
+However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
+\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
+They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
+Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
 

### 2020-07-20 manuscript/manuscript.tex
edited main text; looks good

@@
 We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities.
-Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed.
+Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock forecasts before the post-shock response is observed.
 The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best.
@@
 In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
-%It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.
-However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study.
-The core idea of our methodology is to sensibly combine similar shock effects that have occurred in the past which arose from disparate time-series, and then add them to the present forecast.
-Our method of combining disparate shock effects embraces ideas from time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, and synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, clements2019measuring}.
-%, and nowcasting \citep{matheson2010nowcasting, fosten2019panel}.
-%baltagi2008econometric
-
-In our post-shocking setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
-The researcher must therefore move beyond the modeling paradigm that they were previously working under to accommodate this new shockas in judgement forecasting \citep{monti2008forecast, svensson2005monetary}.
+The core idea of our methodology is to sensibly aggregate similar past realized shock-effects which arose from disparate time-series, and then incorporate the aggregated shock-effect estimator into the present forecast.
+Our method of combining disparate shock effects embraces ideas from time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, clements2019measuring}.
+We study this methodology in the context of additive shock-effects in linear autoregressive models.
+
+In our post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
+The researcher must therefore move beyond the modeling paradigm that they were previously working under to accommodate this new shock, as in judgement forecasting \citep{monti2008forecast, svensson2005monetary}.
 In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past.
-Construction of the donor pool that forms this panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
+Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
 As in SCM, care is needed when forming the donor pool of disparate time series.
@@
 
-In this paper, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure.
+In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure.
 Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
@@
 The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-These adjustment strategies all ``incorrectly'' target the mean of the shock-effect distribution.
+These adjustment strategies all target the mean of the shock-effect distribution.
 However, such an estimation strategy can reduce mean squared error (MSE) when variation in the shock-effect distribution is small relative to the mean.
@@
 
-We will suppose that an analyst has time series data ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
+We will suppose that a researcher has time series data ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
 Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection.
@@
 %The forecast consists of three steps: (1) pick a model, (2) selection of covariates, (3) choices of donor pool.
-Our post-shock prediction methodology will consist of selecting covariates $x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$.
+Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$.
 In this article, we consider a dynamic panel data model with autoregressive structure similar to that in \citet{blundell1998initial}.
@@
 It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect.
-We evaluate the performance of this post-shock prediction methodology throughout this article; we outline situations for when it is expected to work and when it is not.
+We evaluate the performance of this post-shock forecasting methodology throughout this article; we outline situations for when it is expected to work and when it is not.
 
@@
 \end{align*}
-where $\hat\eta_1$, $\hat\phi_1$, $\hat\theta_1$, and $\hat\beta_1$ are all 
-OLS estimators of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$ respectively, 
-and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$. 
+where $\hat\eta_1$, $\hat\phi_1$, $\hat\theta_1$, and $\hat\beta_1$ are all ordinary least squares (OLS) estimators of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$ respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
 The first forecast ignores the presence of $\alpha_1$ while the second forecast 
@@
 circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
+We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response.
 It is important to note that in general $\hat{\alpha}$
@@
   \hat{\mbf{X}}_1(\mbf{W}) 
-    = (\mbf{W}' \otimes \mbf{I}_2) \mbf{X}
+    = (\mbf{W}' \otimes \mbf{I}_2) \mbf{X},
 \end{align*}
@@
 Under $\mc{M}_{22}$, the expression for $\var{\alpha_i}$ is not of closed form because $\gamma_i$ and $\delta_i$ may be dependent when they are placed in a random-effects model.
-We investigate comparisons between the variability of these estimators in Section \ref{comparisons}.%, we will show under some circumstances, it is possible to compare the variances for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$.
-
-Sections \ref{conditions} and \ref{comparisons} detail conditions needed for risk-reduction and comparisons of adjustment estimators.
+
+Section \ref{conditions} details conditions needed for risk-reduction and comparisons of adjustment estimators.
 These conditions involve variances and expectations which may be difficult to compute in practice.
@@
 From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
-\begin{align*}
+\begin{equation} \label{varwadj}
 \var{\hat{\alpha}_{\rm wadj}}
  = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
-\end{align*}
+\end{equation}
 In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.
@@
 \end{prop}
-
-Based on Proposition \ref{propriskwadj2}, we can obtain a similar inequality as in Section \ref{conditionsmodel1} as below
+Under Proposition \ref{propriskwadj2}, we can obtain a risk-reduction inequality that is similar to \eqref{varwadj},
 \begin{align*}
@@
 \end{equation}
-Note that since $\hat{\alpha}_{\rm adj}$ is biased for $\E{\alpha_1}$, the bias term $(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2$ will become complicated and simplification yields no insightful results.
-We can however estimate \eqref{ineq} using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
+We estimate \eqref{ineq} using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
+
+%A simple mean-squares decomposition produces the following inequality for assessing the favorability of $\hat{\alpha}_{\rm wadj}$ to $\hat{\alpha}_{\rm adj}$ under models $\mc{M}_{21}$ and $\mc{M}_{22}$,
+% \begin{align*}
+%  \var{\hat{\alpha}_{\rm adj}} 
+%  -\var{\hat{\alpha}_{\rm wadj}} + \big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2> 0.
+%\end{align*}
+
+%If it turns out to be fact that the variance of the weighted-adjustment estimator is greater than that of adjustment estimator, we should be aware that  the compromise for variance because of using $\hat{\alpha}_{\rm wadj}$ shouldn't exceed the squared bias, i.e., $\big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2$.
 
 As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$.
-In other words, $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$.
+We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$.
 That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
-Evaluation of these inequalities in practice can be found in Sections \ref{varbootstrap} and \ref{loocv}.
-We will discuss comparisons of adjustment estimators in the the next section.
-%As conditions of risk-reduction for individual estimators are obtained, a natural question arises --- which one is better? It will be discussed in Section \ref{comparisons}.
-
-\subsection{Comparisons among estimators}
-
-\label{comparisons}
-
-In comparing  shock-effects estimators, we would assume that the risk-reduction conditions are satisfied as in Section \ref{conditions}.
-
-Denote the risk-reduction quantities for adjustment estimators as $\Delta_{\rm adj}$, $\Delta_{\rm IVW}$, and $\Delta_{\rm wadj}$, respectively for standard adjustment, inverse-variance weighted estimator, and weighted-adjustment estimato.
-%As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration.
+Methods for assessing these inequalities in practice are developed in Sections \ref{varbootstrap} and \ref{loocv}.
+%We will discuss comparisons of adjustment estimators in the the next section.
+
+%%%%%%%%%%% Commenting out Section 3.2 %%%%%%%%%%%%
+%\subsection{Comparisons among estimators}
+%\label{comparisons}
+
+%In comparing  shock-effects estimators, we would assume that the risk-reduction conditions are satisfied as in Section \ref{conditions}.
+
+%Denote the risk-reduction quantities for adjustment estimators as $\Delta_{\rm adj}$, $\Delta_{\rm IVW}$, and $\Delta_{\rm wadj}$, respectively for standard adjustment, inverse-variance weighted estimator, and weighted-adjustment estimato.
+%%%As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration.
 For example, if we find that $\Delta_{\rm wadj}>\Delta_{\rm adj}$ and $\Delta_{\rm wadj}>\Delta_{\rm IVW}$, the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ is the most favorable.
-According to  discussion in Section \ref{conditionsm2122}, we know that under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, the risk-reduction quantity for $\hat{\alpha}_{\rm IVW}$ is
-\begin{align*}
-  \Delta_{\rm IVW} = (\E{\alpha_1})^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2.
-\end{align*}
-From discussions in Section \ref{conditions}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ differ across models, we will discuss in different cases accordingly.
-
-\subsubsection{Under $\mc{M}_{1}$}
-
-From Proposition \ref{proprisk}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
-\begin{align*}
-  \Delta_{\rm adj} 
-  = \mu_{\alpha}^2 -\var{\hat{\alpha}_{\rm adj}}
-\quad   \text{ and } \quad 
-  \Delta_{\rm wadj} 
-  = \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}.
-\end{align*}
-Under the framework of $\mc{M}_1$, the risk-reduction quantity  for $\hat{\alpha}_{\rm IVW}$ is
-\begin{align*}
-  \Delta_{\rm IVW} = \mu_{\alpha}^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2.
-\end{align*}
-In other words, when $\var{\hat{\alpha}_{\rm wadj}}<\var{\hat{\alpha}_{\rm adj}}$ and $\hat{\alpha}_{\rm wadj} < \var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2$, we would prefer $\hat{\alpha}_{\rm wadj}$ as the best estimator.
+%According to  discussion in Section \ref{conditionsm2122}, we know that under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, the risk-reduction quantity for $\hat{\alpha}_{\rm IVW}$ is
+%\begin{align*}
+%  \Delta_{\rm IVW} = (\E{\alpha_1})^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2.
+%\end{align*}
+%From discussions in Section \ref{conditions}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ differ across models, we will discuss in different cases accordingly.
+
+%\subsubsection{Under $\mc{M}_{1}$}
+
+%From Proposition \ref{proprisk}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
+%\begin{align*}
+%  \Delta_{\rm adj} 
+%  = \mu_{\alpha}^2 -\var{\hat{\alpha}_{\rm adj}}
+%\quad   \text{ and } \quad 
+%  \Delta_{\rm wadj} 
+%  = \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}.
+%\end{align*}
+%Under the framework of $\mc{M}_1$, the risk-reduction quantity  for $\hat{\alpha}_{\rm IVW}$ is
+%\begin{align*}
+%  \Delta_{\rm IVW} = \mu_{\alpha}^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2.
+%\end{align*}
+%In other words, when $\var{\hat{\alpha}_{\rm wadj}}<\var{\hat{\alpha}_{\rm adj}}$ and $\hat{\alpha}_{\rm wadj} < \var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2$, we would prefer $\hat{\alpha}_{\rm wadj}$ as the best estimator.
 Other conditions for voting the other estimators as the best one follow similarly.
 
-\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}
-\label{section322}
-According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
-\begin{align*}
-  \Delta(\hat{\alpha}_{\rm adj})
-  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
-\quad   \text{ and } \quad 
-  \Delta(\hat{\alpha}_{\rm wadj})
-  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
-\end{align*}
-In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
-\begin{align*}
- \Delta(\hat{\alpha}_{\rm IVW})
-  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
-\end{align*}
-For the case of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$, we can derive the following inequality for $\hat{\alpha}_{\rm wadj}$ to be favored over $\hat{\alpha}_{\rm adj}$,
- \begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  -\var{\hat{\alpha}_{\rm wadj}} + \big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2> 0.
-\end{align*}
- %What insights can we gain from this inequality? 
-We analyze this inequality from two perspectives:
- \begin{enumerate}
-   \item If it turns out to be fact that the variance of the weighted-adjustment estimator is greater than that of adjustment estimator, we should be aware that  the compromise for variance because of using $\hat{\alpha}_{\rm wadj}$ shouldn't exceed the squared bias, i.e., $\big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2$.
-   \item If instead the variance of $\hat{\alpha}_{\rm wadj}$ is smaller than that of $\hat{\alpha}_{\rm adj}$, the above inequality should always hold because $\big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2>0$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.
- \end{enumerate}
-
- These are some analytical results for comparison studies among estimators of $\alpha_1$.
+%\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}
+%\label{section322}
+
+%According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
+%\begin{align*}
+%  \Delta(\hat{\alpha}_{\rm adj})
+%  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
+%\quad   \text{ and } \quad 
+%  \Delta(\hat{\alpha}_{\rm wadj})
+%  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
+%\end{align*}
+%In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
+%\begin{align*}
+% \Delta(\hat{\alpha}_{\rm IVW})
+%  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
+%\end{align*}
+
+% These are some analytical results for comparison studies among estimators of $\alpha_1$.
 Next, we will detail a framework for estimation of risk-reduction  quantities using a parametric bootstrap routine.
@@
 
-\begin{remark}
-  In Section \ref{constructionofestimators}, we noted that $\mathbf{W}^*$ may not be unique if $2p < n$.
+%\begin{remark}
+%  In Section \ref{constructionofestimators}, we noted that $\mathbf{W}^*$ may not be unique if $2p < n$.
 However, Proposition \ref{proprisk} and \ref{propriskwadj2} will hold for  every $\hat{\alpha}_{\rm wadj}$ using  $\mathbf{W}^*$ that satisfies (\ref{SCM}).
-\end{remark}
+%\end{remark}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Our bootstrap procedure is as follows: Let $B$ be the bootstrap sample size.
+Our first bootstrap procedure is as follows: Let $B$ be the bootstrap sample size.
 At iteration $b$, first resample the indicies $I = \{2, \ldots, n+1\}$ of the donor pool without replacement to form $I^{(b)}$.
@@
 We can then estimate distributional quantities of our shock-effect estimators under our considered models with the bootstrap sample $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-We denote this procedure by $\mc{B}_u$, and another procedure, which fixes the donor pool without sampling the donor pool without replacement, as $\mc{B}_f$.
+We denote this procedure by $\mc{B}_u$.
+We motivate a second bootstrap procedure $\mc{B}_f$ which treats the the donor pool as fixed, and not a realization from an infinite super-population.
+Therefore, there is no resampling of the donor pool in $\mc{B}_f$, it is otherwise similar to $\mc{B}_u$.
 An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in the Supplementary Materials.
-%To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement (\emph{unconditional} on donor pool) and the other without any resampling of the donor pool (\emph{conditional} on donor pool).
-We denote them by $\mc{B}_u$ and  $\mc{B}_c$, respectively.
-We first illustrate the simple $\mc{B}_c$.
-The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool.
-Initialize $y_{i,0}$ for all $i \in I$.
-At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$.
-Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$.
-We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-One can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
-$\mc{B}_u$ is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$.
-Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$.
-
-%When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however,
-
-%Now, we discuss some consistency results for $\mc{B}_c$ conditioned on $\Theta_1$.
-The bootstrap is aimed for estimating $\mrm{Var}(\hat{\alpha}_{\rm adj})$, $\mrm{Var}(\hat{\alpha}_{\rm wadj})$, and $\mrm{Var}(\hat{\alpha}_{\rm IVW})$.
-The consistency results will be similar to the counterparts in sample mean.
-Therefore, we will briefly discuss the proof for the sample mean case and adapt it to the variance case.
-Let
-%$
-%  \overline{\hat{\alpha}_{\mrm{adj}}} 
-%    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
-%$, 
-%$
-%  \overline{\hat{\alpha}_{\mrm{wadj}}} 
-%    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
-%$, 
-%and 
-%$
-%  \overline{\hat{\alpha}_{\mrm{IVW}}} 
-%    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
-%$
-%The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold.
-The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below.
-As $B \to \infty$,
-%\begin{align*}
-%  \overline{\hat{\alpha}_{\mrm{wadj}}}
-%  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
-%  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
-%  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
-%  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
-%\end{align*}
-%The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$.
-However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because its weights are random.
-It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$.
-We would only claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.
-
-%We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_c$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$.
-For $\mc{B}_u$ but conditioned on $\Theta$, we emphasize that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold.
-Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.
 
@@
 Our bootstrap procedure estimates the variance of our adjustment estimators.
-We can then estimate the risk-reduction quantities in Section \ref{comparisons}.
+We can then estimate the risk-reduction propositions and inequalities.
 For example, we can estimate $\Delta(\hat{\alpha}_{\rm adj})$ under model $\mc{M}_{21}$ or $\mc{M}_{22}$ with
@@
 Our adjustment estimators will be evaluated by multiple criteria.
-We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the \emph{guess}, with 1 suggesting $\hat{\alpha}$ reduces the risk according to our bootstrap estimation and 0 the converse.
+We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the \emph{guess}, with 1 indicating that $\hat{\alpha}$ provides risk-reduction over the simple no-adjustment forecast, and 0 indicates the converse.
 We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
@@
 
-In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}).
-We mainly discuss simulations under $\mc{M}_2$ (see Section \ref{modelsetup}) for $\mc{B}_u$ and $\mc{B}_f$ (see Section \ref{varbootstrap}) with comparisons to those under $\mc{M}_1$ whose results are listed in Section 3 in Supplementary Materials.
+In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities.
+We mainly discuss simulations under $\mc{M}_2$ (see Section \ref{modelsetup}) for $\mc{B}_u$ and $\mc{B}_f$ (see Section \ref{varbootstrap}) with comparisons to those under $\mc{M}_1$ whose results are listed in Section 3 in the Supplementary Materials.
 Two simulation setups are investigated.
@@
 Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
-However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the $\delta_{\hat{\alpha}}$  become more incorrect for $\hat{\alpha}\in \mc{A}$.
+However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the decision rule $\delta_{\hat{\alpha}}$  becomes unreliable for $\hat{\alpha}\in \mc{A}$.
 It is to be expected since the bootstrap estimates become more biased.
@@
 Nevertheless, no statistical evidence has been found to support the claim that $n$ matters in prediction.
-In other words, $n$ matters in producing reliable decision-making of $\delta_{\hat{\alpha}}$  rather than reliable prediction.
+In other words, the size of the donor pool matters for producing reliable decision-making of $\delta_{\hat{\alpha}}$ rather than reliable prediction.
 
@@
 With respect to averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases.
-It is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
+This is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
 The reasons can be outlined as below.
@@
 In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is small; otherwise, they are similar.
-See more discussions for differences between $\mc{B}_u$ and $\mc{B}_f$ in Section \ref{discussion}.
-
- Simulation results of $\mc{M}_1$ are listed in Section 3 in Supplementary Materials.
-Its results are very similar to those of $\mc{M}_2$ except for the difference among estimators.
-The results show that in many situations, $\hat{\alpha}_{\rm adj}$ is better than $\hat{\alpha}_{\rm IVW}$, which is in turn better than $\hat{\alpha}_{\rm wadj}$ with statistical evidence; in other situations, they are mostly the same without statistical significance.
+%See more discussions for differences between $\mc{B}_u$ and $\mc{B}_f$ in Section \ref{discussion}.
+
+ Simulation results corresponding to model $\mc{M}_1$ are listed in Section 3 in Supplementary Materials.
+Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$, except for the difference among estimators.
+The results show that in many situations, $\hat{\alpha}_{\rm adj}$ is better than $\hat{\alpha}_{\rm IVW}$, which is in turn better than $\hat{\alpha}_{\rm wadj}$ with statistical siginificance; in other situations, they are mostly the same without statistical significance.
 Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
@@
 
-\begin{table}[H]
-  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table5}
-  \begin{center}
-    \begin{tabular}{lrrr}
-      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
-      \hline 
-    Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
-    \end{tabular}
-  \end{center}  
-\end{table}
-\vspace{-.5cm}
-
-Using $\mc{B}_c$ proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
-Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $34.565$, $34.880$, and $34.139$, respectively.
-The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator.
-LOOCV with $k$ random draws was not implemented since the effective $n$ is $3$, a number too small to provide a credible estimation.
+%\begin{table}[H]
+%  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table5}
+%  \begin{center}
+%    \begin{tabular}{lrrr}
+%      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
+ %     \hline 
+ %   Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
+ %   \end{tabular}
+ % \end{center}  
+%\end{table}
+%\vspace{-.5cm}
+
+Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
+Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $34.565$, $34.880$, and $34.139$, respectively.
 We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
@@
 \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries.
-A similar setup may be appropriate for post-shock prediction but may be too dependent upon model specification for the shock distribution.
+A similar setup may be appropriate for post-shock forecasting but may be too dependent upon model specification for the shock distribution.
 \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach.

### 2020-07-22 manuscript/manuscript.tex
revisions to manuscript with typos fixed and simulations of model 1

@@
 \title{Minimizing post-shock forecasting error using disparate information}
-\author{Jilei Lin\thanks{jileil2@ilinois.edu}}
+\author{Jilei Lin\thanks{jileil2@ilinois.edu} }
 \author{Daniel J. Eck\thanks{dje13@illinois.edu}}
@@
 \begin{abstract}
-    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded.
+    We developed a forecasting methodology for providing credible forecasts for the time series data that have undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded.
 Three shock-effects estimators were constructed for minimizing average forecast risk.
@@
 Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock forecasts before the post-shock response is observed.
-The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best.
-Leave-one-out cross validation is proposed to estimate consistency of risk-reduction propositions and best consistency of voting the best shock-estimators, prospectively informing users of the probabilities that this prospective evaluation is consistent with the reality.
+The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well.
+Leave-one-out cross validation is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality.
 Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
@@
 %These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed.
-We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock-effect adjustment estimators without.
+We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock-effect adjustment estimators.
 This prospective assessment does not require the observation of the post-shock response.
-Our Monte Carlo simulation results show that the risk-reduction conditions are highly consistent when the model for the shock effects is identified well with appropriate covariates under a fixed design.
+Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.
 We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020.
@@
 
-We will suppose that specific interest is in forecasts to made after the occurrence of a structural shock.
+We will suppose that specific interest is in forecasting the response after the occurrence of a structural shock.
 To gauge the performance of forecasts, we consider forecast risk in the form of mean squared error (MSE),
@@
 
-Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology.
-This figure depicts a time-series that experienced a shock at time point $T_1^*+1 = 126$.
+Figure \ref{figure1} provides a simple intuition of the practical usefulness of our proposed methodology.
+This figure depicts a time series that experienced a shock at time point $T_1^*+1 = 126$.
 It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded.
@@
 In this section, we will describe the assumed dynamic panel models for which 
-post-shock aggregated estimators are provided. The basic structure of these models 
+post-shock aggregated estimators are provided. The basic structures of these models 
 are the same, the differences between them lie in the setup of the shock effect 
@@
 $\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T_i^*}$. 
-We will investigate post-shock aggregated estimators in $\mc{M}_2$ 
+We will investigate the post-shock aggregated estimators in $\mc{M}_2$ 
 in settings where $\delta_i$ and $\gamma_i$ are either fixed or random. 
@@
 We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects 
-structure for $\gamma$ and $\delta$:
+structure for $\gamma_i$ and $\delta_i$:
 \begin{align*}
@@
   \begin{array}{lll}
-     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\}.\\
-    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 1\}.\label{parameter},
+     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
+    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
   \end{array}
@@
 Note that the two forecasts do not differ in their predictions for 
-$y_{1,t}$, $t = 1,\ldots T_1^*$, they only differ in predicting 
+$y_{1,t}$, $t = 1,\ldots T_1^*$. Instead, they only differ in predicting 
 $y_{1,T_1^*+1}$. Throughout the rest of this article we show that the collection of 
@@
 We now construct the aggregate estimators of the shock effects that appear in 
-Forecast 2. We use these to forecast response values $y_{1, t}$ when 
-$t > T_1^*$, i.e., the time series of interest after the shock time where we 
-assume that $T_1^*$ is known.  %Notice that the shock effect 
+Forecast 2 (see Section \ref{forecast}). We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.  %Notice that the shock effect 
 %for time series $1$ is typically unobserved. But we can gather knowledge from 
@@
 of $\alpha_i$.  Note that parameter estimation 
-for $\mc{M}_1$ is identically the same as $\mc{M}_{21}$ and $\mc{M}_{22}$.
+for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
 
 Second, we introduce the candidate estimators for $\alpha_1$. Define the 
-\emph{adjustment estimator} for time series $i=1$ by,
+\emph{adjustment estimator} for time series $i=1$ by
 \begin{equation} \label{adjusted}
@@
 where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of all of 
-the $\alpha_i$s.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
+the $\alpha_i$s for $i = 2, \ldots, n+1$.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
 the unknown $\alpha_1$ term for which no meaningful estimation information 
@@
 \end{align*}
- $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
+where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
 $\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
@@
 We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ 
-and $\var{\hat{\alpha}_{\rm IVW}}$, empirical performance of 
+and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of 
 $\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation 
@@
 \end{align*}
-where $\otimes$ is the kronecker product, $\mbf{I}_2$ is the identity matrix with two rows, $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{2 \times p}$.
+where $\otimes$ is the Kronecker product, $\mbf{I}_2$ is the identity matrix with two rows, and $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{2 \times p}$.
 Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$.
@@
 \begin{align}
- \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
+ \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
 \end{align}
@@
 In discussion of risk, it is useful to derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.
-The expression for the expectations are as follow,
+The expressions for the expectations are as follow,
 
@@
 
-Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple risk-reduction conditions and invoke a method of comparison, although our primary interest is in reducing forecast risk.
+Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple risk-reduction conditions, and more importantly motivates a bootstrap estimation for evaluation of these conditions.
 % for $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm wadj}$ to reduce risk, and make it more clear with respect to when one is better than the other.
-These conditions will be discussed in Section \ref{conditions} and Section \ref{comparisons}.
-Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below
+These conditions and bootstrap will be discussed in Section \ref{conditions} and \ref{varbootstrap}, respectively.
+Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below.
 
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2 \label{riskconditionadj}
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
 \end{align}
 
-Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$; (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
+Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$ (see Forecast in Section \ref{forecast}); (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
 %This result is also intuitive.
@@
 In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.
-However, the above criteria are generally difficult to evaluate in practice due to the term $\hat{\alpha}_{\rm wadj}$.
-Sections \ref{varbootstrap} and \ref{loocv} will provide a detailed treatment about how to deal with these technical inequalities in practice.
+However, the above criteria are generally difficult to evaluate in practice due to the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.
+
+In fact, we can extend checking risk-reduction conditions to verifying the sign of risk-reduction quantities for generalization.
+For an adjustment estimator $\hat{\alpha}$, the risk-reduction quantity is defined as  $\Delta(\hat{\alpha})=R_{T_1^*+1,1}-R_{T_1^*+1,2}$.
+If $\Delta(\hat{\alpha})>0$, $\hat{\alpha}$ will improve the Forecast 1.
+In this context, according to Proposition \ref{proprisk}, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$.
+Sections \ref{varbootstrap} and \ref{loocv} will provide a detailed treatment about how to checking the sign  in practice.
 
@@
 \end{equation}
-We estimate \eqref{ineq} using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
 
@@
 That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
-Methods for assessing these inequalities in practice are developed in Sections \ref{varbootstrap} and \ref{loocv}.
-%We will discuss comparisons of adjustment estimators in the the next section.
+Therefore, using the generalization mentioned in Section \ref{conditionsmodel1}, under $\mc{M}_2$, it can be shown that the risk-reduction quantities are
+\begin{align*}
+  \Delta(\hat{\alpha}_{\rm adj}) 
+  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2\\
+  \Delta(\hat{\alpha}_{\rm IVW}) 
+  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2\\
+  \Delta(\hat{\alpha}_{\rm wadj}) 
+  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}},
+\end{align*}
+where we estimate $\Delta(\hat{\alpha})$  using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
 
@@
 
-In this section, we present bootstrap procedures that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction using plug-in approach in practice.
+In this section, we present bootstrap procedures that approximate the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction quantity using plug-in approach in practice.
 Our procedure involves the resampling of residuals in the separate OLS fits.
-This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
+This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processe.
 %NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives.
@@
 Then, resample the residuals under models $\mc{M}_1$, $\mc{M}_{21}$, or $\mc{M}_{22}$ and obtain shock-effect estimators for each of the disparate time series for all $i \in I^{(b)}$.
-These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, $b = 1,\ldots,B$.
-We can then estimate distributional quantities of our shock-effect estimators under our considered models with the bootstrap sample $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
+These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
+We can then estimate distributional quantities of our shock-effect estimators under our considered models with the bootstrap samples $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
 We denote this procedure by $\mc{B}_u$.
@@
 Therefore, there is no resampling of the donor pool in $\mc{B}_f$, it is otherwise similar to $\mc{B}_u$.
-An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in the Supplementary Materials.
+An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in Section 2 in the Supplementary Materials.
 
@@
 For iteration $m \in \{1,\ldots,n\}$ of our LOOCV procedure, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}_m, t = 1, \ldots, T_{i}\}$, where $\mc{I}_m=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, we can evaluate the performance of our adjustment estimators and the original forecast made without adjustment.
+Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, we can evaluate the performance of our adjustment estimators and the original forecast made without adjustment (i.e., Forecast 1 in Section \ref{forecast}).
 
@@
 For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Based on the new donor pool, we compute $\delta_{\hat{\alpha}}$ using bootstrap procedures outlined in Section \ref{varbootstrap}.
+Based on the new donor pool, we estimate relevant parameters using bootstrap procedures outlined in Section \ref{varbootstrap}.
 In other words, $k$ times of bootstrapping are nested in a LOOCV procedure.
@@
 	\end{equation}
-where $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ is computed with respect to donor pool with index set $\mc{I}_m$ and the $m+1$ time series is treated as the series of interest.
+where $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ is computed with respect to donor pool with index set $\mc{I}_m$ and the $m+1$ time series is treated as the time series of interest.
 The mutual independence assumption in model setup $\mc{M}_{2}$ implies that $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
@@
 The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
-Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
+Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
 Additionally, we generated the covariates from $\text{Gamma}(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
@@
 We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
-We will also consider the magnitude of the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ from the realized post-shock response $y_{1,T_1^*+1}$.
+We will also consider the Euclidean distance between the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ and the realized post-shock response $y_{1,T_1^*+1}$.
 The first two metrics can combine to assess our forecasting methodology prospectively while the latter requires the realization of the post-shock response $y_{1,T_1^*+1}$.
@@
 Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative.
-Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of consistencies between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
+Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of correctness between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
 For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.83 \times 0.55 = 0.457$ from Table \ref{table1}.
@@
 
-From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will  decrease, which is a pattern similar to the one shown in the first experiment.
+From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$   decreases, which is a pattern similar to the one shown in the first experiment.
 Furthermore, as $\sigma$ increases fixing $\sigma_{\alpha}$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases as well.
@@
 
-With respect to averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases.
+With respect to averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases.
 This is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
@@
 Notice that $\var{\hat{\alpha}}$ is  an increasing function of $\sigma$ since $\hat{\alpha}$ is estimated by OLS.
-Therefore, it explains the reason why the increase of $\sigma$ would result in a decrease of averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ since the inequality is not likely to hold when  $\var{\hat{\alpha}}$ increases.
+Therefore, it explains the reason why the increase of $\sigma$ would result in a decrease of averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ since the inequality is not likely to hold when  $\var{\hat{\alpha}}$ increases.
 
@@
 
-Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented. See table \ref{table3} and table \ref{table4} for results. Comparing table \ref{table1}
- and table \ref{table2} yields that when $n$ is small ($n = 5$ or $n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
+Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented. See Table \ref{table3} and Table \ref{table4} for results. Comparing Table \ref{table1}
+ and Table \ref{table2} yields that when $n$ is small ($n = 5$ or $n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
 For other situations, $\mc{B}_u$  and $\mc{B}_f$  are rather similar.
 It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool.
-Concerning  table \ref{table2} and table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
+Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
 It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$.
@@
 Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$, except for the difference among estimators.
-The results show that in many situations, $\hat{\alpha}_{\rm adj}$ is better than $\hat{\alpha}_{\rm IVW}$, which is in turn better than $\hat{\alpha}_{\rm wadj}$ with statistical siginificance; in other situations, they are mostly the same without statistical significance.
+The results show that (1) the performance of $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are nearly the same and (2) in many situations, $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are  better than $\hat{\alpha}_{\rm wadj}$; in other situations, they are mostly the same.
 Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
 Therefore, similarity weighting may not be informative when the model for $\alpha_i$ is identified wrongly.
-Under $\mc{M}_1$, simple averaging aimed for a reduction of variance or inverse-variance weighting targeting on reducing negative effects from varying time lengths may work better.
+Under $\mc{M}_1$, simple averaging, aimed for a reduction of variance, or inverse-variance weighting, targeting on reducing negative effects from varying time lengths, may work better.
 
@@
 Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo}. %and with a relatively recent initial public offering \citep{conocohist}. 
-Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}.
-Furthermore, fear of and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
+Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control on the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}.
+Furthermore, fear and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
 Major events include the SXSW festival being cancelled as trading closed on March 6th \citep{wang2020impact}.
@@
 The current recession followed an inversion of the yield curve that first happened back in March, 2019 \citep{tokic2019yield}.
-An inversion of the yield curve is an event that signals that recessions are more likely \citep{andolfatto2018yield, bauer2018economic}.
+An inversion of the yield curve is an event that signals likely recessions \citep{andolfatto2018yield, bauer2018economic}.
 In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
@@
 \item[(3)] {\bf Construction of donor pool}.
-Our donor pool will consist of Conoco Phillips shock effects observed on March 14, 2008, several events in September, 2008, and November 27, 2014.
+Our donor pool  consists of Conoco Phillips shock effects observed on March 14, 2008, several events in September, 2008, and November 27, 2014.
 The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}.
@@
 The covariates and response of time series in the donor pool are adjusted for inflation.
-Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Supplementary Materials.
+Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials.
 Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
@@
 
-Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}.
+Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}.
+The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.531, 0.479, and 0.970, respectively.
 Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $34.565$, $34.880$, and $34.139$, respectively.
@@
 
-We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
+We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, and they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
 The unadjusted forecast has an RMSE of 9.870 dollars whereas 
@@
 
-We developed methodology for forecasting post-shock response values after the occurrence of a structural.
+We developed methodology for forecasting post-shock response values after the occurrence of a structural shock.
 Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock-effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock-effect estimator to the original forecast.
 We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock-effect settings.
-The model that we verify these claims under is a simple AR(1) model.
+The model, under which we verify these claims, is a simple AR(1) model.
 Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
@@
 However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
-Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that second moments exist.
+Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its first and second moments exist.
 The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
@@
 However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
+Nevertheless, it does not seriously compromise the inference according to our simulation results in Section 4 in the Supplementary Materials.
 Note that there are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_f$.

### 2020-07-22 Rcode/sim.study.R

@@ -226,8 +226,12 @@ risk.reduction <- function(means, vars) {
   names(est) <- c('adj', 'wadj', 'IVW')
   return(list(usable = ifelse(est > 0, yes = 1, no = 0), best = which.max(est)))
 }
-risk.reduction2 <- function(est, vars) {
-  rr.adj <- (est['wadj']) ^ 2 - vars['adj'] - (est['adj'] - est['wadj']) ^ 2
+risk.reduction2 <- function(est, vars, model = 2) {
+  if (model == 2) {
+    rr.adj <- (est['wadj']) ^ 2 - vars['adj'] - (est['adj'] - est['wadj']) ^ 2
+  } else if (model == 1) {
+    rr.adj <- (est['wadj']) ^ 2 - vars['adj'] 
+  }
   rr.wadj <- (est['wadj']) ^ 2 - vars['wadj']
   rr.IVW <- (est['wadj']) ^ 2 - vars['IVW'] - (est['IVW'] - est['wadj']) ^ 2
   rest <- c(rr.adj, rr.wadj, rr.IVW)
@@ -559,12 +563,12 @@ sim.study.normal.gammaX <- function(mu.gamma.delta = 1, mu.alpha, sigma,
   names(bias) <- c('E.adj', 'E.wadj')
       
   # comparison
-  guess <- risk.reduction2(est = est, vars = vars)$usable
+  guess <- risk.reduction2(est = est, vars = vars, model = model)$usable
   consistency <- ifelse(truth == guess, yes = 1, no = 0)
       
   # best consistency
   best.consistency <- ifelse(which.min(abs(Y[[1]][Tstar[1] + 2] - yhat2s)) == 
-                                   risk.reduction2(est = est, vars = vars)$best, yes = 1, no = 0)
+                                   risk.reduction2(est = est, vars = vars, model = model)$best, yes = 1, no = 0)
   
   # cv consistency
   cv.consistency <- cv(k = k, X = X, Y = Y, Tstar = Tstar, np = np, B = B)
@@ -1199,6 +1203,7 @@ system.time(
     out
   })
 )
+
 
 
 # store results

### 2020-07-23 manuscript/manuscript.tex
made one minor change suggested by Jilei

@@
 Moreover, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors.
-The functional form of the mean function in our considered models can be extended beyond the linear regression model.
-Multiple shock-effects can be nested within a time series; and time series in the donor pool can be dependent.
+The functional form of the mean function for $y_{i,t}$ in our considered models can be extended beyond the linear regression model.
+Multiple shock-effects can be nested within a time series, and the time series in the donor pool can be dependent.
 As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.

### 2020-07-23 manuscript/manuscript.tex
changes to supplements and and discussions

--- 2020-07-22 manuscript/manuscript.tex
@@
 Our procedure involves the resampling of residuals in the separate OLS fits.
-This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processe.
+This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid process.
 %NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives.
@@
 Our first bootstrap procedure is as follows: Let $B$ be the bootstrap sample size.
-At iteration $b$, first resample the indicies $I = \{2, \ldots, n+1\}$ of the donor pool without replacement to form $I^{(b)}$.
+At iteration $b$, first resample the indices $I = \{2, \ldots, n+1\}$ of the donor pool with replacement to form $I^{(b)}$ with cardinality $n$, where we note that the elements of $I^{(b)}$ may not be unique in terms of their  indices in the donor pool.
 Initialize $y_{i,0}$ for all $i \in I^{(b)}$.
@@
 
+The resulting shock-effect estimates are $\hat{\alpha}_{\rm adj}=-5.433$, $\hat{\alpha}_{\rm wadj}= -5.945$, and $\hat{\alpha}_{\rm IVW}=-5.446$.
 Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}.
@@
 Moreover, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors.
-The functional form of the mean function in our considered models can be extended beyond the linear regression model.
 Multiple shock-effects can be nested within a time series; and time series in the donor pool can be dependent.
@@
 Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series.
-The pseudo time series generated by our proposed parametric bootstrap is not stationary.
-Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
+If the data are subject to heteroskedasticity of unknown form, bootstrapping tuples of regressands and regressors proposed by \citet{freedman1981bootstrapping} is robust in this situation with asymptotic validity in autoregressive models established by \citet{gonccalves2004bootstrapping}.
+If serial correlation exists in the data, various block bootstrapping procedures \citep{kunsch1989jackknife, liu1992moving} can be possible reasonable alternatives.
+Note that the pseudo time series generated by our proposed parametric bootstrap is not stationary.
+If stationarity is of concern, one can be referred to the stationary bootstrap invented \citet{politis1994stationary} for stationary and weakly dependent time series.
+Nevertheless, it was shown that approximation accuracy may be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.
+More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, \citet{berkowitz2000recent}, and Chapter 12 in \citet{kilian2017structural}.
+It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.
+
+% \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
 This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$ where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$; for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$.
@@
 This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.
-More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}.
-It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.
 

### 2020-07-24 manuscript/manuscript.tex
Added to Introduction; more is needed

@@
 
-In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
+In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock in real-time.
+Standard forecasting methods may not allow users to explore the consequences that structural shocks have on baseline forecasts \citep{baumeister2014real}.
+All is not lost in this setting, one may be able to supplement the present forecast with past data that contains similar structural shocks.
 The core idea of our methodology is to sensibly aggregate similar past realized shock-effects which arose from disparate time-series, and then incorporate the aggregated shock-effect estimator into the present forecast.
-Our method of combining disparate shock effects embraces ideas from time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, clements2019measuring}.
-We study this methodology in the context of additive shock-effects in linear autoregressive models.
-
-In our post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
+Our method of combining disparate shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, expectation shocks \citep{croushore2006data, clements2019measuring}.
+
+We study the post-shock forecasting problem in the context of additive shock-effects in linear autoregressive models.
+In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
 The researcher must therefore move beyond the modeling paradigm that they were previously working under to accommodate this new shock, as in judgement forecasting \citep{monti2008forecast, svensson2005monetary}.
+One method for estimating the shock-effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}.
+Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}.
+{\bf Need to explore more}
+
 In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past.
@@
 In our context, the yet to observed shock-effect of interest is a realization from a random process that can only be partially explained by the realizations of the disparate time series.
+
+{\bf Note}: Forecasting scenario methodology \citep{baumeister2014real, kilian2017structural}:
 

### 2020-07-27 manuscript/manuscript.tex
changes to introductions and revisions to Dave comments

@@
 
-In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock in real-time.
+In this study, we investigate reliable forecasting for  time series that are to undergone a structural shock, which is not observed before, at a known time point.
+In this scenario, currently available forecasting methodologies are likely to fail since those  forecasts are trained on the data without any knowledge about the shock.
+It is a general problem that has many real-life implications for forecasting under unprecedented events.
+For example, an investor may be interested in forecasting the stock price of a company tomorrow after he  knew related news about an event that signals recessions today but he or she do not have available recent data for reliable prediction.
+Or, companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis but they only have recent sales data for which the company is operating well.
+Nevertheless, it is still possible to do reliable forecasting by borrowing knowledge from similar disparate time-series in the sense that they experienced similar shocks in the past.
+
+To formalize, we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock in real-time.
 Standard forecasting methods may not allow users to explore the consequences that structural shocks have on baseline forecasts \citep{baumeister2014real}.
@@
 for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
+We emphasize that $\alpha_i$s are random variables but the OLS estimation is conditioned on the their realizations from some distribution.
 
@@
 It will be understood that structural 0s in $\mbf{x}_{i,t}$ correspond to variables that are unimportant. 
+\end{remark}
+
+\begin{remark}
+  From Bayesian perspective, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as Bayes rules that minimize the posterior expected losses under different unknown loss functions.
 \end{remark}
@@
 If serial correlation exists in the data, various block bootstrapping procedures \citep{kunsch1989jackknife, liu1992moving} can be possible reasonable alternatives.
-Note that the pseudo time series generated by our proposed parametric bootstrap is not stationary.
-If stationarity is of concern, one can be referred to the stationary bootstrap invented \citet{politis1994stationary} for stationary and weakly dependent time series.
-Nevertheless, it was shown that approximation accuracy may be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.
+Note that the pseudo time series generated by our proposed parametric bootstrap are not stationary.
+If stationarity is of concern, one can be referred to the stationary bootstrap invented by \citet{politis1994stationary} for stationary and weakly dependent time series.
+Nevertheless, it was shown that approximation accuracy might be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.
 More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, \citet{berkowitz2000recent}, and Chapter 12 in \citet{kilian2017structural}.

### 2020-07-28 manuscript/manuscript.tex
updated Introduction; made minor edits

--- 2020-07-24 manuscript/manuscript.tex
@@
     We developed a forecasting methodology for providing credible forecasts for the time series data that have undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded.
-Three shock-effects estimators were constructed for minimizing average forecast risk.
+Three shock effects estimators were constructed for minimizing average forecast risk.
 We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities.
@@
 
-In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock in real-time.
+We provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock in real-time.
 Standard forecasting methods may not allow users to explore the consequences that structural shocks have on baseline forecasts \citep{baumeister2014real}.
-All is not lost in this setting, one may be able to supplement the present forecast with past data that contains similar structural shocks.
-The core idea of our methodology is to sensibly aggregate similar past realized shock-effects which arose from disparate time-series, and then incorporate the aggregated shock-effect estimator into the present forecast.
-Our method of combining disparate shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, expectation shocks \citep{croushore2006data, clements2019measuring}.
-
-We study the post-shock forecasting problem in the context of additive shock-effects in linear autoregressive models.
+This is a general problem that has many real life applications.
+For example, one may be interested in forecasting the stock price of a company tomorrow after hearing terrible or great news about the company in after hours trading.
+Companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis, but they only have recent sales data for which the company is operating well.
+All is not lost in this setting, one may be able to supplement the present forecast with past data borrowed from disparate time series which contain similar structural shocks.
+The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from disparate time series, and then incorporate the aggregated shock effect estimator into the present forecast.
+Our method of combining disparate shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, jforecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
+
+We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models.
 In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
-The researcher must therefore move beyond the modeling paradigm that they were previously working under to accommodate this new shock, as in judgement forecasting \citep{monti2008forecast, svensson2005monetary}.
-One method for estimating the shock-effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}.
+The researcher must therefore move beyond the modeling paradigm that they were previously working under to accommodate this new shock \citep{monti2008forecast, svensson2005monetary}.
+One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}.
 Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}.
-{\bf Need to explore more}
+On the other hand, our methodology allows for the inclusion of outside data sources into this conditional forecasting context provided that the shock effects are all thought to arise from a similar data generating process.
 
@@
 We assume that the disparate time series are independent from the time series under study before the timing of the shock.
-We also assume that the shock-effects for each disparate time series are independent realizations from some unknown distribution.
-
-We estimate the shock-effects that are present in the disparate time series for which post-shock responses are observed.
-We then aggregate these estimated shock-effects and use this aggregated estimate as an estimator for the shock-effect in the time series of interest.
+We also assume that the shock effects for each disparate time series are independent realizations from some unknown distribution.
+
+We estimate the shock effects that are present in the disparate time series for which post-shock responses are observed.
+We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest.
 This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest.
-Shock-effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
+shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
 The context in \cite{clements2019measuring} allowed for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
-We offer no such consistency guarantee here.
-In our context, the yet to observed shock-effect of interest is a realization from a random process that can only be partially explained by the realizations of the disparate time series.
-
-{\bf Note}: Forecasting scenario methodology \citep{baumeister2014real, kilian2017structural}:
+There is no consistency guarantee here.
+In our context, the yet to observed shock effect of interest is a realization from a random process that can only be partially explained by the realizations of the disparate time series.
+Therefore, the shock effect of interest can not be estimated consistently.
 
@@
 The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-These adjustment strategies all target the mean of the shock-effect distribution.
-However, such an estimation strategy can reduce mean squared error (MSE) when variation in the shock-effect distribution is small relative to the mean.
+Our auto regressive model will consider present day and lagged covariates to better motivate similarity weighting.
+The considered adjustment strategies all target the mean of the shock effect distribution.
+However, such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean.
 We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast.
@@
 %These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed.
-We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock-effect adjustment estimators.
+We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators.
 This prospective assessment does not require the observation of the post-shock response.
@@
 We show that our proposed adjustment estimators yield much better results than no adjustment in this setting.
-We also use this example to demonstrate settings in which the shock-effect may be decomposed into separate estimable parts.
+We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts.
 We now motivate our framework for post-shock forecasting.
 
-% Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock-effect of the time series under study.
+% Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock effect of the time series under study.
 
@@
 and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.
+Specific emphasis will be given to post-shock prediction where forecasts methods only differ at one future time point.
+In this setting we will consider the magnitude $|\E{\hat y_{1,t} - y_{1,t}}|$.
 
@@
 %As we can see, the purple line provides a better prediction than the red line in this particular example.
-But we will justify later that consideration of estimated shock-effects will improve the prediction under certain conditions.
-In this example, the mean of the estimated shock effects is taken as a shock-effect estimator for the time series under study.
-Forecasts are then made by adding this shock-effect estimator to the estimated response values obtained from the process that ignores the shock.
-It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect.
+But we will justify later that consideration of estimated shock effects will improve the prediction under certain conditions.
+In this example, the mean of the estimated shock effects is taken as a shock effect estimator for the time series under study.
+Forecasts are then made by adding this shock effect estimator to the estimated response values obtained from the process that ignores the shock.
+It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock effect.
 We evaluate the performance of this post-shock forecasting methodology throughout this article; we outline situations for when it is expected to work and when it is not.
@@
 To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock.
-This model somehow accounts for the impact of past information on the shock-effects.
+This model somehow accounts for the impact of past information on the shock effects.
  We further define
@@
 
-\section{Forecast risk and properties of shock-effects estimators}
+\begin{remark}
+  Our forecasting premise and estimation construction shares similarities with Bayesian viewpoints.
+From a Bayesian perspective, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as attempts to estimate the Bayes rule $\mathrm{E}\left(\alpha|\eta,\phi,\theta,\beta,\x,y,\delta,\gamma\right)$.
+\end{remark}
+
+\section{Forecast risk and properties of shock effects estimators}
 \label{properties}
@@
 
-\subsection{Risk-reduction conditions for shock-effects estimators}
+\subsection{Risk-reduction conditions for shock effects estimators}
 \label{conditions}
 
-In this section we will discuss the conditions for risk reduction for individual shock-effects estimators under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
+In this section we will discuss the conditions for risk reduction for individual shock effects estimators under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
 %The reason is that if the estimator of $\alpha_1$ turns out to be an unbiased estimator of $\E{\alpha_1}$, the conditions get  simplified.
@@
 
-The shock-effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
-%It is a more reasonable and general model since it is often the case that shock-effects differ by means among disparate time series in practice.
+The shock effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
+%It is a more reasonable and general model since it is often the case that shock effects differ by means among disparate time series in practice.
 $\mc{M}_{22}$  further adds the random effect structure of $\delta$ and $\gamma$ to  $\mc{M}_{21}$ for generalization.
@@
 
-%In comparing  shock-effects estimators, we would assume that the risk-reduction conditions are satisfied as in Section \ref{conditions}.
+%In comparing  shock effects estimators, we would assume that the risk-reduction conditions are satisfied as in Section \ref{conditions}.
 
@@
 
-In this section, we present bootstrap procedures that approximate the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction quantity using plug-in approach in practice.
+In this section, we present bootstrap procedures that approximate the distribution of our shock effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction quantity using plug-in approach in practice.
 Our procedure involves the resampling of residuals in the separate OLS fits.
-This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid process.
-%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives.
-In the second step, we detail the procedure of boostrapping AR(1).
-%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}.
-However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model.
-%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed.
-In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}.
+This procedure has its origins in Section 6 of \citet{efron1986bootstrap} and Chapter 12 of \cite{kilian2017structural}.
+Our procedure involves the resampling of the residuals which are assumed to be the realizations of an iid process.
 
@@
 Initialize $y_{i,0}$ for all $i \in I^{(b)}$.
-Then, resample the residuals under models $\mc{M}_1$, $\mc{M}_{21}$, or $\mc{M}_{22}$ and obtain shock-effect estimators for each of the disparate time series for all $i \in I^{(b)}$.
+Then, resample the residuals under models $\mc{M}_1$, $\mc{M}_{21}$, or $\mc{M}_{22}$ and obtain shock effect estimators for each of the disparate time series for all $i \in I^{(b)}$.
 These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-We can then estimate distributional quantities of our shock-effect estimators under our considered models with the bootstrap samples $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
+We can then estimate distributional quantities of our shock effect estimators under our considered models with the bootstrap samples $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
 We denote this procedure by $\mc{B}_u$.
@@
 
-We will explicitly use these bootstrapped samples of shock-effect estimators to check the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
+We will explicitly use these bootstrapped samples of shock effect estimators to check the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
 Recall that  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ from Proposition \ref{unbiased}.
@@
 
-%Suppose we have a pool of shock-effect estimators, $\mc{A}$, e.g., $\mc{A}= \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ in our study.
-We can determine which one is the best shock-effect estimator.
+%Suppose we have a pool of shock effect estimators, $\mc{A}$, e.g., $\mc{A}= \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ in our study.
+We can determine which one is the best shock effect estimator.
 Suppose the $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ and $\hat{\Delta}(\hat{\alpha}_{\rm IVW})$ are estimators for $\Delta(\hat{\alpha}_{\rm wadj}) $ and $\Delta(\hat{\alpha}_{\rm IVW})$, respectively.
 Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}(\hat{\alpha})>0$ for $\hat{\alpha}\in \mc{A}$.
-Besides, we can also select the best shock-effect estimator accordingly.
+Besides, we can also select the best shock effect estimator accordingly.
 Define
@@
 %\end{align}
-%That is, the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities whereas $\alpha_{\rm best}$ is the true best shock-effect estimator given observed post-shock response.
+%That is, the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities whereas $\alpha_{\rm best}$ is the true best shock effect estimator given observed post-shock response.
 See more discussions in Section \ref{loocv}.
@@
 \end{center}
-%Similar definitions can be adapted to the best shock-effect estimators. 
+%Similar definitions can be adapted to the best shock effect estimators. 
 \vspace*{0.3cm}
@@
 The covariates and response of time series in the donor pool are adjusted for inflation.
-Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials.
+Note that there are three shock effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials.
 Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
@@
 
-The resulting shock-effect estimates are $\hat{\alpha}_{\rm adj}=-5.433$, $\hat{\alpha}_{\rm wadj}= -5.945$, and $\hat{\alpha}_{\rm IVW}=-5.446$.
+The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-5.433$, $\hat{\alpha}_{\rm wadj}= -5.945$, and $\hat{\alpha}_{\rm IVW}=-5.446$.
 Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}.
@@
 We developed methodology for forecasting post-shock response values after the occurrence of a structural shock.
-Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock-effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock-effect estimator to the original forecast.
-We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock-effect settings.
+Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
+We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings.
 The model, under which we verify these claims, is a simple AR(1) model.
@@
 Moreover, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors.
-Multiple shock-effects can be nested within a time series; and time series in the donor pool can be dependent.
+Multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
 As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
 But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
-%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool.
+%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock effects in the donor pool.
 %Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.
@@
 In this case, the variance expressions proposed in Section \ref{properties} will not work.
-However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
+However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
 Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its first and second moments exist.

### 2020-07-28 manuscript/manuscript.tex
changes to introductions, remarks discussions

@@
 This is a general problem that has many real life applications.
-For example, one may be interested in forecasting the stock price of a company tomorrow after hearing terrible or great news about the company in after hours trading.
+For example, one may be interested in forecasting the stock price of a company tomorrow after hearing terrible or great news about the company  after hours trading.
 Companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis, but they only have recent sales data for which the company is operating well.
@@
 The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from disparate time series, and then incorporate the aggregated shock effect estimator into the present forecast.
-Our method of combining disparate shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, jforecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
+Our method of combining disparate shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
 
@@
 In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
-The researcher must therefore move beyond the modeling paradigm that they were previously working under to accommodate this new shock \citep{monti2008forecast, svensson2005monetary}.
+The researcher must therefore move beyond the modeling paradigm under which he or she was previously working  to accommodate this new shock \citep{monti2008forecast, svensson2005monetary}.
 One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}.
 Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}.
-On the other hand, our methodology allows for the inclusion of outside data sources into this conditional forecasting context provided that the shock effects are all thought to arise from a similar data generating process.
+On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects are all thought to arise from a similar data generating process.
+For further differences of assumptions on shocks, our methodology allows for \emph{unprecedented} shocks and no observation of past shocks.
 
@@
 This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest.
-shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
+Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
 The context in \cite{clements2019measuring} allowed for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
@@
   Our forecasting premise and estimation construction shares similarities with Bayesian viewpoints.
-From a Bayesian perspective, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as attempts to estimate the Bayes rule $\mathrm{E}\left(\alpha|\eta,\phi,\theta,\beta,\x,y,\delta,\gamma\right)$.
+From a Bayesian perspective, if we assign a prior $\pi$ to $\alpha_1$, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as the Bayes rules with respect to $\pi$ under different loss functions.
+If the sampling distribution of the data and $\pi$ are known, it is possible to compute the Bayes risks of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ with respect to $\pi$, and thus enable comparisons among them.
+Additionally, from Lemma 20.3 \citep{marden}, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are admissible among the set of Bayes rules with respect to $\pi$ under corresponding loss functions.
 \end{remark}
@@
 The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
+Recall that the modeling equation of $\alpha_i$ includes present day and lagged covariates.
+It can be also generalized to the one with $q$ lags covariates.
+In that case, based same assumptions in Section \ref{constructionofestimators}, a sufficient condition for $\mbf{W}^*$ to be unique is $p(q+1) \geq n$.
 We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts.
@@
 Nevertheless, it does not seriously compromise the inference according to our simulation results in Section 4 in the Supplementary Materials.
+In fact, one can avoid this issue by increasing lagged number 1 to $q$ in the modeling equation of $\alpha_i$ to some $q$ such that $p(q+1) \geq n$, mentioned previously.
+
 Note that there are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_f$.
@@
   \begin{align*}
-   E\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
+   \mrm{E}\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
    = \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}

### 2020-08-05 Rcode/comp.R
changes by deletion of covariates and revision by comments

@@ -13,24 +13,18 @@ eta <- rnorm(n + 1)
 phi <- runif(n + 1, 0, .1)
 theta <- rnorm(n + 1)
 theta <- theta / as.vector(sqrt(crossprod(theta)))
-beta <- rnorm(n + 1)
-beta <- beta / as.vector(sqrt(crossprod(beta)))
-beta.X <- rnorm(n + 1)
-beta.X <- beta.X / as.vector(sqrt(crossprod(beta.X)))
 alpha <- rnorm(n + 1, mean = mu.alpha, sd = sigma.alpha)
 # T: time points; n: different time series
-X <- matrix(0, nrow = T + 1, ncol = n + 1)
-X[1, ] <- rnorm(n + 1)
+X <- matrix(rnorm((n + 1) * (T + 1), sd = sigma.X), nrow = T + 1, ncol = n + 1)
 Y <- matrix(0, nrow = T + 1, ncol = n + 1)
 Y[1,] <- rnorm(n + 1)
 
 # i represents for time -- T
 for(i in 2:(T + 1)){
-  X[i,] <- beta.X * X[i - 1,] + rnorm(n + 1, sd = sigma.X)
   if (i - 2 == Tstar) {
-    Y[i, ] <- eta + phi * Y[i - 1,] + beta * X[i,]  + rnorm(n + 1, sd = sigma) + alpha
+    Y[i, ] <- eta + phi * Y[i - 1,] + theta * X[i,]  + rnorm(n + 1, sd = sigma) + alpha
   } else {
-    Y[i, ] <- eta + phi * Y[i - 1,] + beta * X[i,]  + rnorm(n + 1, sd = sigma)
+    Y[i, ] <- eta + phi * Y[i - 1,] + theta * X[i,]  + rnorm(n + 1, sd = sigma)
     } 
 }
 
@@ -44,7 +38,6 @@ for (j in 2:(n + 1)){
   mu.alpha.hat[j - 1] <- coefficients(m1)[4]
   se[j - 1] <- summary(m1)$coef[4, 2]
 }
-
 alpha.hat <- mean(mu.alpha.hat)
 
 # sum(mu.alpha.hat / se ^ 2) /  (sum(1 / se ^ 2))
@@ -64,12 +57,12 @@ scm <- function(X, Tstar) {
   n <- length(X) - 1
   
   # covariate for time series for prediction
[…]

### 2020-08-05 Rcode/dataanalysis.R

@@ -65,7 +65,7 @@ COP_close <- COP_close %>% mutate(start_day_20080317 = start_day_20080317)
 TS2 <- COP_close[(start-30):start, ]
 # inflation adjustment
 TS2[, 2:7] <- TS2[, 2:7] * inflation_adj$dollars_2020[inflation_adj$year == 2008] 
-m_COP_3_17 <- lm(Y ~ COP_Close + start_day_20080317 + GSPC_Close + WTI_Close + WTI_Close_lag1 + GSPC_Close_lag1, 
+m_COP_3_17 <- lm(Y ~ COP_Close + start_day_20080317 + GSPC_Close + WTI_Close, 
                  data = TS2)
 alpha_3_17 <- summary(m_COP_3_17)$coef[3,1:2] 
 # shock-effects
@@ -92,8 +92,7 @@ TS3 <- COP_close[which(COP_close$Date == "2008-07-28"):which(COP_close$Date == "
 TS3[, 2:7] <- TS3[, 2:7] * inflation_adj$dollars_2020[inflation_adj$year == 2008] 
 # AR(1)
 m_COP_Sept_08 <- lm(Y ~ COP_Close + start_day_09_08_08 + start_day_09_12_08 + 
-                      start_day_09_26_08 + GSPC_Close + WTI_Close +
-                      WTI_Close_lag1 + GSPC_Close_lag1, data = TS3)
+                      start_day_09_26_08 + GSPC_Close + WTI_Close, data = TS3)
 alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3:5,1:2] 
 cov2cor(vcov(m_COP_Sept_08)[3:5, 3:5])
 # shock-effects
@@ -141,7 +140,7 @@ TS4 <- COP_close[(start - 30):start,]
 # adjust for inflation
 TS4[, 2:7] <- TS4[, 2:7] * inflation_adj$dollars_2020[inflation_adj$year == 2014] 
 # AR(1)
-m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day_20141127 + GSPC_Close + WTI_Close + WTI_Close_lag1 + GSPC_Close_lag1,
+m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day_20141127 + GSPC_Close + WTI_Close,
                      data = TS4)
 alpha_11_27_14 <- summary(m_COP_11_27_14)$coef[3,1:2] 
 # shock-effects
[…]

### 2020-08-05 Rcode/sim.study.R

@@ -15,12 +15,12 @@ scm <- function(X, Tstar) {
   n <- length(X) - 1
   
   # covariate for time series for prediction
-  X1 <- X[[1]][c(Tstar[1], Tstar[1] + 1), , drop = FALSE]
+  X1 <- X[[1]][Tstar[1] + 1, , drop = FALSE]
   
   # covariates for time series pool
   X0 <- c()
   for (i in 1:n) {
-    X0[[i]] <- X[[i + 1]][c(Tstar[i + 1], Tstar[i + 1] + 1), ,drop = FALSE]
+    X0[[i]] <- X[[i + 1]][Tstar[i + 1] + 1, , drop = FALSE]
   }
   
   # objective function
@@ -28,7 +28,7 @@ scm <- function(X, Tstar) {
     # W is a vector of weight of the same length of X0
     n <- length(W)
     p <- ncol(X1)
-    XW <- matrix(0, nrow = 2, ncol = p)
+    XW <- matrix(0, nrow = 1, ncol = p)
     for (i in 1:n) {
       XW <- XW + W[i] * X0[[i]]
     }
@@ -44,6 +44,7 @@ scm <- function(X, Tstar) {
   solnp(par = rep(1/n, n), fun = weightedX0, eqfun = Wcons, eqB = 0, 
         LB = rep(0, n), UB = rep(1, n), control = list(trace = 0))
 }
+
 ols.est.alphahat <- function(Tstar, Y, X) {
   
   n <- length(Y) - 1
@@ -69,11 +70,10 @@ ols.est.alphahat <- function(Tstar, Y, X) {
     
     # lag
     yilag <- Y[[i]][-(Ti + 1)]
-    xilag <- X[[i]][-(Ti + 1), ]
     
     # OLS
     lmodi <- lm(yi ~ 1 + ifelse(1:Ti == Tstari + 1, yes = 1, no = 0) + 
-                  yilag + xi + xilag)
+                  yilag + xi)
     
     # find estimates
     alphahat <- c(alphahat, coef(lmodi)[2])
@@ -138,18 +138,16 @@ boots <- function(B, ols) {
       Tstari <- Tstar[i]
       lmodi <- lmod[[i - 1]]
       xi <- X[[i]][-1,]
-      xilag <- X[[i]][-(Ti + 1), ]
       
       # parameter
       etahati <- coef(lmodi)[1]
[…]

### 2020-08-05 manuscript/alphahist.tex
changes by deletion of covariates and revision by comments

% Created by tikzDevice version 0.12.3.1 on 2020-08-05 11:58:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,252.94);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (301.08,  2.40) {$\hat{\alpha}_i$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,144.47) {Frequency};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75, 48.00) -- (535.41, 48.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75, 48.00) -- ( 66.75, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.70, 48.00) -- (133.70, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65, 48.00) -- (200.65, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.60, 48.00) -- (267.60, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56, 48.00) -- (334.56, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.51, 48.00) -- (401.51, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.46, 48.00) -- (468.46, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.41, 48.00) -- (535.41, 42.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 66.75, 26.40) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (133.70, 26.40) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (200.65, 26.40) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (267.60, 26.40) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (334.56, 26.40) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (401.51, 26.40) {7};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (468.46, 26.40) {8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (535.41, 26.40) {9};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 55.15) -- ( 48.00,233.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 55.15) -- ( 42.00, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 80.67) -- ( 42.00, 80.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,106.19) -- ( 42.00,106.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,131.71) -- ( 42.00,131.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,157.23) -- ( 42.00,157.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,182.76) -- ( 42.00,182.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,208.28) -- ( 42.00,208.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,233.80) -- ( 42.00,233.80);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 55.15) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 80.67) {1};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,106.19) {2};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,131.71) {3};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,157.23) {4};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,182.76) {5};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,208.28) {6};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,233.80) {7};
\end{scope}
\begin{scope}
\path[clip] ( 48.00, 48.00) rectangle (554.16,240.94);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.25, 55.15) -- (167.18, 85.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.18, 85.07) -- (188.30,106.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65,220.75) -- (213.70,233.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65,118.55) -- (234.13,152.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.13,152.02) -- (239.34,157.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.46, 55.15) -- (267.60, 83.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.60, 83.29) -- (301.08,116.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (301.08,116.77) -- (334.56,150.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56,150.24) -- (368.03,183.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.66, 55.15) -- (368.03, 81.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (368.03, 81.52) -- (401.51,114.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.87, 55.15) -- (443.87, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.46, 79.74) -- (469.39, 80.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75, 55.15) --
	(100.22, 55.15) --
	(100.22, 80.67) --
	( 66.75, 80.67) --
	( 66.75, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.22, 55.15) --
	(133.70, 55.15) --
	(133.70,106.19) --
	(100.22,106.19) --
	(100.22, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.70, 55.15) --
	(167.18, 55.15) --
	(167.18,106.19) --
	(133.70,106.19) --
	(133.70, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.18, 55.15) --
	(200.65, 55.15) --
	(200.65,106.19) --
	(167.18,106.19) --
	(167.18, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65, 55.15) --
	(234.13, 55.15) --
	(234.13,233.80) --
	(200.65,233.80) --
	(200.65, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.13, 55.15) --
	(267.60, 55.15) --
	(267.60,157.23) --
	(234.13,157.23) --
	(234.13, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.60, 55.15) --
	(301.08, 55.15) --
	(301.08,131.71) --
	(267.60,131.71) --
	(267.60, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (301.08, 55.15) --
	(334.56, 55.15) --
	(334.56,208.28) --
	(301.08,208.28) --
	(301.08, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56, 55.15) --
	(368.03, 55.15) --
	(368.03,208.28) --
	(334.56,208.28) --
	(334.56, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (368.03, 55.15) --
	(401.51, 55.15) --
	(401.51,157.23) --
	(368.03,157.23) --
	(368.03, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.51, 55.15) --
	(434.98, 55.15) --
	(434.98, 80.67) --
	(401.51, 80.67) --
	(401.51, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.98, 55.15) --
	(468.46, 55.15) --
	(468.46, 55.15) --
	(434.98, 55.15) --
	(434.98, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.46, 55.15) --
	(501.94, 55.15) --
	(501.94, 80.67) --
	(468.46, 80.67) --
	(468.46, 55.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.94, 55.15) --
	(535.41, 55.15) --
	(535.41, 80.67) --
	(501.94, 80.67) --
	(501.94, 55.15);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.27, 48.00) -- (282.27,240.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.44,226.14) -- (285.62,226.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.00,228.67) --
	(285.62,226.14) --
	(290.00,223.61);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (368.03,223.64) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$5.22};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-05 manuscript/comp.tex
changes by deletion of covariates and revision by comments

@@
-% Created by tikzDevice version 0.12.3 on 2020-05-27 15:30:26
+% Created by tikzDevice version 0.12.3.1 on 2020-08-05 11:58:05
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,252.94);
 \begin{scope}
-\path[clip] ( 48.00, 48.00) rectangle (554.16,277.08);
+\path[clip] ( 48.00, 48.00) rectangle (554.16,240.94);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,150.94) --
-	( 75.27,164.79) --
-	( 78.11,157.49) --
-	( 80.95,165.92) --
-	( 83.79,166.40) --
-	( 86.63,141.84) --
-	( 89.47,150.09) --
-	( 92.31,143.93) --
-	( 95.15,141.05) --
-	( 97.99,145.70) --
-	(100.83,139.65) --
-	(103.67,178.59) --
-	(106.51,163.76) --
-	(109.35,143.77) --
-	(112.19,137.72) --
-	(115.03,164.14) --
-	(117.87,143.58) --
-	(120.71,166.91) --
-	(123.55,163.52) --
-	(126.40,145.84) --
-	(129.24,155.56) --
-	(132.08,140.91) --
-	(134.92,146.00) --
-	(137.76,155.61) --
-	(140.60,151.70) --
-	(143.44,158.08) --
-	(146.28,157.50) --
-	(149.12,162.02) --
-	(151.96,166.12) --
-	(154.80,159.26) --
-	(157.64,149.45) --
-	(160.48,145.98) --
-	(163.32,156.42) --
-	(166.16,141.35) --
-	(169.00,146.25) --
-	(171.84,165.79) --
-	(174.68,133.16) --
-	(177.52,164.74) --
-	(180.36,158.63) --
-	(183.20,174.39) --
-	(186.04,136.64) --
-	(188.88,142.35) --
-	(191.72,165.33) --
-	(194.56,177.10) --
-	(197.41,169.75) --
-	(200.25,166.95) --
-	(203.09,116.51) --
-	(205.93,139.49) --
-	(208.77,140.86) --
-	(211.61,181.44) --
-	(214.45,157.88) --
-	(217.29,160.28) --
-	(220.13,161.32) --
-	(222.97,174.87) --
-	(225.81,148.01) --
-	(228.65,118.11) --
-	(231.49,167.94) --
-	(234.33,167.87) --
-	(237.17,178.18) --
-	(240.01,165.32) --
-	(242.85,151.88) --
-	(245.69,151.67) --
-	(248.53,151.92) --
-	(251.37,128.89) --
-	(254.21,159.78) --
-	(257.05,144.18) --
-	(259.89,155.47) --
-	(262.73,164.76) --
-	(265.57,152.05) --
-	(268.42,138.91) --
-	(271.26,143.64) --
-	(274.10,141.06) --
-	(276.94,166.61) --
-	(279.78,177.14) --
-	(282.62,143.52) --
-	(285.46,129.06) --
-	(288.30,134.98) --
-	(291.14,126.11) --
-	(293.98,179.60) --
-	(296.82,162.55) --
-	(299.66,178.83) --
-	(302.50,133.78) --
-	(305.34,124.87) --
-	(308.18,142.06) --
-	(311.02,157.78) --
-	(313.86,132.62) --
-	(316.70,148.93) --
-	(319.54,130.16) --
-	(322.38,152.67) --
-	(325.22,156.53) --
-	(328.06,145.81) --
-	(330.90,145.85) --
-	(333.74,164.04) --
-	(336.59,162.10) --
-	(339.43,137.37) --
-	(342.27,177.60) --
-	(345.11,138.08) --
-	(347.95,158.99) --
-	(350.79,145.39) --
-	(353.63,165.05) --
-	(356.47,136.95) --
-	(359.31,166.26) --
-	(362.15,151.18) --
-	(364.99,143.86) --
-	(367.83,154.91) --
-	(370.67,151.74) --
-	(373.51,154.30) --
-	(376.35,126.88) --
-	(379.19,135.58) --
-	(382.03,152.86) --
-	(384.87,171.42) --
-	(387.71,136.46) --
-	(390.55,130.68) --
-	(393.39,141.79) --
-	(396.23,146.31) --
-	(399.07,119.63) --
-	(401.91,132.99) --
-	(404.75,143.78) --
-	(407.60,169.91) --
-	(410.44,180.48) --
-	(413.28,132.66) --
-	(416.12,158.14) --
-	(418.96,163.74) --
-	(421.80,167.20) --
-	(424.64,169.82) --
-	(427.48,208.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,141.91) --
+	( 75.27,148.65) --
+	( 78.11,138.04) --
+	( 80.95,120.32) --
+	( 83.79,144.55) --
+	( 86.63,128.04) --
+	( 89.47,158.74) --
+	( 92.31,142.28) --
+	( 95.15,144.24) --
+	( 97.99,150.16) --
+	(100.83,129.86) --
+	(103.67,156.20) --
+	(106.51,161.19) --
+	(109.35,150.66) --
+	(112.19,143.27) --
+	(115.03,126.88) --
+	(117.87,118.05) --
+	(120.71,139.15) --
+	(123.55,135.40) --
+	(126.40,140.74) --
+	(129.24,149.36) --
+	(132.08,115.48) --
+	(134.92,139.71) --
+	(137.76,114.03) --
+	(140.60,125.67) --
+	(143.44,139.07) --
+	(146.28,144.69) --
+	(149.12,130.89) --
+	(151.96,140.09) --
+	(154.80,126.64) --
+	(157.64,111.23) --
+	(160.48,121.82) --
+	(163.32,149.80) --
+	(166.16,149.85) --
+	(169.00,139.78) --
+	(171.84,158.01) --
+	(174.68,141.87) --
+	(177.52,133.42) --
+	(180.36,131.05) --
+	(183.20,129.40) --
+	(186.04,142.69) --
+	(188.88,144.63) --
+	(191.72,130.06) --
+	(194.56,121.56) --
+	(197.41,118.55) --
+	(200.25,119.73) --
+	(203.09,140.14) --
+	(205.93,137.20) --
+	(208.77,125.79) --
+	(211.61,150.02) --
+	(214.45,134.16) --
+	(217.29,137.62) --
+	(220.13,143.96) --
+	(222.97,145.02) --
+	(225.81,137.14) --
+	(228.65,147.61) --
+	(231.49,162.41) --
+	(234.33,138.41) --
+	(237.17,162.38) --
+	(240.01,127.19) --
+	(242.85,125.12) --
+	(245.69,134.60) --
+	(248.53,134.89) --
+	(251.37,158.83) --
+	(254.21,122.69) --
+	(257.05,117.16) --
+	(259.89,147.80) --
+	(262.73,138.62) --
+	(265.57,123.35) --
+	(268.42,140.39) --
+	(271.26,137.29) --
+	(274.10,148.46) --
+	(276.94,135.80) --
+	(279.78,134.54) --
+	(282.62,139.54) --
+	(285.46,143.03) --
+	(288.30,143.37) --
+	(291.14,107.15) --
+	(293.98,121.09) --
+	(296.82,144.70) --
+	(299.66,143.32) --
+	(302.50,149.80) --
+	(305.34,113.62) --
+	(308.18,139.96) --
+	(311.02,134.15) --
+	(313.86,130.85) --
+	(316.70,135.42) --
+	(319.54,131.11) --
+	(322.38,145.18) --
+	(325.22,143.55) --
+	(328.06,141.15) --
+	(330.90,125.31) --
+	(333.74,129.29) --
+	(336.59,118.52) --
+	(339.43,146.06) --
+	(342.27,140.93) --
+	(345.11,151.97) --
+	(347.95,136.60) --
+	(350.79,114.01) --
+	(353.63,120.33) --
+	(356.47,142.22) --
+	(359.31,130.73) --
+	(362.15,138.80) --
+	(364.99,114.92) --
+	(367.83,152.60) --
+	(370.67,139.26) --
+	(373.51,137.13) --
+	(376.35,140.56) --
+	(379.19,149.07) --
+	(382.03,151.38) --
+	(384.87,153.12) --
+	(387.71,126.88) --
+	(390.55,137.55) --
+	(393.39,137.71) --
+	(396.23,129.83) --
+	(399.07,123.04) --
+	(401.91,117.89) --
+	(404.75,132.35) --
+	(407.60,141.10) --
+	(410.44,137.00) --
+	(413.28,143.73) --
+	(416.12,131.05) --
+	(418.96,129.54) --
+	(421.80,129.16) --
+	(424.64,128.38) --
+	(427.48,164.19);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[clip] (  0.00,  0.00) rectangle (578.16,252.94);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 56.55) -- ( 48.00,265.51);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 67.43) -- ( 48.00,190.54);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 56.55) -- ( 42.00, 56.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 67.43) -- ( 42.00, 67.43);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 86.40) -- ( 42.00, 86.40);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,128.99) -- ( 42.00,128.99);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,116.25) -- ( 42.00,116.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,190.54) -- ( 42.00,190.54);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,146.10) -- ( 42.00,146.10);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 67.43) {-5};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,175.96) -- ( 42.00,175.96);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,128.99) {0};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,205.81) -- ( 42.00,205.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,235.66) -- ( 42.00,235.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,265.51) -- ( 42.00,265.51);
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 56.55) {-6};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 86.40) {-4};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,116.25) {-2};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,146.10) {0};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,175.96) {2};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,205.81) {4};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,235.66) {6};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,265.51) {8};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,190.54) {5};
 
@@
 	(554.16, 48.00) --
-	(554.16,277.08) --
-	( 48.00,277.08) --
+	(554.16,240.94) --
+	( 48.00,240.94) --
 	( 48.00, 48.00);
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[clip] (  0.00,  0.00) rectangle (578.16,252.94);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,162.54) {Response};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,144.47) {Response};
 \end{scope}
 \begin{scope}
-\path[clip] ( 48.00, 48.00) rectangle (554.16,277.08);
+\path[clip] ( 48.00, 48.00) rectangle (554.16,240.94);
 \definecolor{drawColor}{RGB}{255,106,106}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,150.71) --
-	( 75.27,152.99) --
-	( 78.11,153.34) --
-	( 80.95,153.46) --
-	( 83.79,154.87) --
-	( 86.63,154.01) --
-	( 89.47,150.03) --
-	( 92.31,152.38) --
-	( 95.15,151.57) --
-	( 97.99,152.37) --
-	(100.83,152.36) --
-	(103.67,150.86) --
-	(106.51,156.31) --
-	(109.35,153.24) --
-	(112.19,151.49) --
-	(115.03,151.36) --
-	(117.87,153.65) --
-	(120.71,151.38) --
-	(123.55,152.92) --
-	(126.40,153.78) --
-	(129.24,151.96) --
-	(132.08,152.95) --
-	(134.92,151.02) --
-	(137.76,151.57) --
-	(140.60,152.69) --
-	(143.44,152.68) --
-	(146.28,153.09) --
-	(149.12,152.91) --
-	(151.96,153.40) --
-	(154.80,153.72) --
-	(157.64,154.05) --
-	(160.48,150.47) --
-	(163.32,151.15) --
-	(166.16,154.68) --
-	(169.00,150.91) --
-	(171.84,152.67) --
-	(174.68,154.71) --
-	(177.52,150.54) --
-	(180.36,152.87) --
-	(183.20,154.34) --
-	(186.04,155.31) --
-	(188.88,151.72) --
-	(191.72,150.98) --
-	(194.56,153.67) --
-	(197.41,154.62) --
-	(200.25,153.87) --
-	(203.09,154.64) --
-	(205.93,147.78) --
-	(208.77,151.29) --
-	(211.61,149.62) --
-	(214.45,154.76) --
-	(217.29,154.96) --
-	(220.13,152.57) --
-	(222.97,154.38) --
-	(225.81,154.97) --
-	(228.65,151.07) --
-	(231.49,147.57) --
-	(234.33,153.88) --
-	(237.17,154.51) --
-	(240.01,156.10) --
-	(242.85,153.60) --
-	(245.69,152.48) --
-	(248.53,152.70) --
-	(251.37,150.55) --
-	(254.21,150.42) --
-	(257.05,153.27) --
-	(259.89,150.70) --
-	(262.73,154.55) --
-	(265.57,152.18) --
-	(268.42,153.01) --
-	(271.26,149.72) --
-	(274.10,153.84) --
-	(276.94,151.75) --
-	(279.78,152.74) --
-	(282.62,153.59) --
-	(285.46,151.51) --
-	(288.30,150.68) --
-	(291.14,149.01) --
-	(293.98,151.89) --
-	(296.82,154.30) --
-	(299.66,153.42) --
-	(302.50,155.56) --
-	(305.34,151.16) --
-	(308.18,147.57) --
-	(311.02,152.92) --
-	(313.86,151.71) --
-	(316.70,150.02) --
-	(319.54,152.22) --
-	(322.38,150.09) --
-	(325.22,153.11) --
-	(328.06,152.16) --
-	(330.90,151.37) --
-	(333.74,150.41) --
-	(336.59,154.30) --
-	(339.43,152.44) --
-	(342.27,151.58) --
-	(345.11,154.49) --
-	(347.95,149.53) --
-	(350.79,154.05) --
-	(353.63,151.10) --
-	(356.47,153.07) --
-	(359.31,150.01) --
-	(362.15,155.43) --
-	(364.99,152.12) --
-	(367.83,150.94) --
-	(370.67,152.10) --
-	(373.51,151.70) --
-	(376.35,154.23) --
-	(379.19,148.51) --
-	(382.03,151.49) --
-	(384.87,151.86) --
-	(387.71,153.13) --
-	(390.55,150.34) --
-	(393.39,150.97) --
-	(396.23,151.09) --
-	(399.07,151.14) --
-	(401.91,148.35) --
-	(404.75,150.18) --
-	(407.60,150.74) --
-	(410.44,154.68) --
-	(413.28,156.36) --
-	(416.12,149.02) --
-	(418.96,152.85) --
-	(421.80,153.32) --
-	(424.64,153.53) --
-	(427.48,154.47);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,137.81) --
+	( 75.27,136.65) --
+	( 78.11,143.49) --
+	( 80.95,137.43) --
+	( 83.79,130.64) --
+	( 86.63,140.10) --
+	( 89.47,133.95) --
+	( 92.31,138.95) --
+	( 95.15,138.13) --
+	( 97.99,134.38) --
+	(100.83,138.70) --
+	(103.67,136.65) --
+	(106.51,142.33) --
+	(109.35,140.08) --
+	(112.19,140.76) --
+	(115.03,135.30) --
+	(117.87,131.53) --
+	(120.71,134.31) --
+	(123.55,136.31) --
+	(126.40,138.07) --
+	(129.24,138.68) --
+	(132.08,133.35) --
+	(134.92,135.06) --
+	(137.76,137.42) --
+	(140.60,132.08) --
+	(143.44,134.84) --
+	(146.28,141.15) --
+	(149.12,136.50) --
+	(151.96,137.75) --
+	(154.80,136.26) --
+	(157.64,132.36) --
+	(160.48,135.15) --
+	(163.32,133.44) --
+	(166.16,135.02) --
+	(169.00,137.46) --
+	(171.84,137.44) --
+	(174.68,138.85) --
+	(177.52,137.64) --
+	(180.36,136.64) --
+	(183.20,136.98) --
+	(186.04,135.19) --
+	(188.88,135.00) --
+	(191.72,137.46) --
+	(194.56,133.62) --
+	(197.41,136.58) --
+	(200.25,133.35) --
+	(203.09,137.85) --
+	(205.93,138.76) --
+	(208.77,132.56) --
+	(211.61,136.25) --
+	(214.45,135.48) --
+	(217.29,136.00) --
+	(220.13,134.15) --
+	(222.97,138.92) --
+	(225.81,140.34) --
+	(228.65,137.72) --
+	(231.49,138.74) --
+	(234.33,140.75) --
+	(237.17,137.08) --
+	(240.01,139.13) --
+	(242.85,132.23) --
+	(245.69,135.17) --
+	(248.53,135.31) --
+	(251.37,134.56) --
+	(254.21,137.20) --
+	(257.05,135.96) --
+	(259.89,133.73) --
+	(262.73,140.13) --
+	(265.57,133.33) --
+	(268.42,134.06) --
+	(271.26,136.71) --
+	(274.10,138.64) --
+	(276.94,143.32) --
+	(279.78,136.35) --
+	(282.62,136.03) --
+	(285.46,138.94) --
+	(288.30,139.04) --
+	(291.14,138.48) --
+	(293.98,133.60) --
+	(296.82,137.06) --
+	(299.66,135.32) --
+	(302.50,136.59) --
+	(305.34,139.19) --
+	(308.18,132.33) --
+	(311.02,130.50) --
+	(313.86,133.96) --
+	(316.70,137.48) --
+	(319.54,136.37) --
+	(322.38,135.54) --
+	(325.22,141.95) --
+	(328.06,137.28) --
+	(330.90,136.24) --
+	(333.74,135.82) --
+	(336.59,129.34) --
+	(339.43,131.63) --
+	(342.27,137.63) --
+	(345.11,139.18) --
+	(347.95,141.59) --
+	(350.79,135.78) --
+	(353.63,132.71) --
+	(356.47,132.87) --
+	(359.31,137.75) --
+	(362.15,135.79) --
+	(364.99,140.06) --
+	(367.83,133.34) --
+	(370.67,138.30) --
+	(373.51,137.87) --
+	(376.35,138.13) --
+	(379.19,134.63) --
+	(382.03,136.24) --
+	(384.87,143.24) --
+	(387.71,134.81) --
+	(390.55,133.80) --
+	(393.39,135.75) --
+	(396.23,137.51) --
+	(399.07,135.80) --
+	(401.91,130.45) --
+	(404.75,132.80) --
+	(407.60,136.90) --
+	(410.44,137.73) --
+	(413.28,138.35) --
+	(416.12,138.71) --
+	(418.96,134.35) --
+	(421.80,137.02) --
+	(424.64,137.94) --
+	(427.48,134.70);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,150.71) --
-	( 75.27,152.99) --
-	( 78.11,153.34) --
-	( 80.95,153.46) --
-	( 83.79,154.87) --
-	( 86.63,154.01) --
-	( 89.47,150.03) --
-	( 92.31,152.38) --
-	( 95.15,151.57) --
-	( 97.99,152.37) --
-	(100.83,152.36) --
-	(103.67,150.86) --
-	(106.51,156.31) --
-	(109.35,153.24) --
-	(112.19,151.49) --
-	(115.03,151.36) --
-	(117.87,153.65) --
-	(120.71,151.38) --
-	(123.55,152.92) --
-	(126.40,153.78) --
-	(129.24,151.96) --
-	(132.08,152.95) --
-	(134.92,151.02) --
-	(137.76,151.57) --
-	(140.60,152.69) --
-	(143.44,152.68) --
-	(146.28,153.09) --
-	(149.12,152.91) --
-	(151.96,153.40) --
-	(154.80,153.72) --
-	(157.64,154.05) --
-	(160.48,150.47) --
-	(163.32,151.15) --
-	(166.16,154.68) --
-	(169.00,150.91) --
-	(171.84,152.67) --
-	(174.68,154.71) --
-	(177.52,150.54) --
-	(180.36,152.87) --
-	(183.20,154.34) --
-	(186.04,155.31) --
-	(188.88,151.72) --
-	(191.72,150.98) --
-	(194.56,153.67) --
-	(197.41,154.62) --
-	(200.25,153.87) --
-	(203.09,154.64) --
-	(205.93,147.78) --
-	(208.77,151.29) --
-	(211.61,149.62) --
-	(214.45,154.76) --
-	(217.29,154.96) --
-	(220.13,152.57) --
-	(222.97,154.38) --
-	(225.81,154.97) --
-	(228.65,151.07) --
-	(231.49,147.57) --
-	(234.33,153.88) --
-	(237.17,154.51) --
-	(240.01,156.10) --
-	(242.85,153.60) --
-	(245.69,152.48) --
-	(248.53,152.70) --
-	(251.37,150.55) --
-	(254.21,150.42) --
-	(257.05,153.27) --
-	(259.89,150.70) --
-	(262.73,154.55) --
-	(265.57,152.18) --
-	(268.42,153.01) --
-	(271.26,149.72) --
-	(274.10,153.84) --
-	(276.94,151.75) --
-	(279.78,152.74) --
-	(282.62,153.59) --
-	(285.46,151.51) --
-	(288.30,150.68) --
-	(291.14,149.01) --
-	(293.98,151.89) --
-	(296.82,154.30) --
-	(299.66,153.42) --
-	(302.50,155.56) --
-	(305.34,151.16) --
-	(308.18,147.57) --
-	(311.02,152.92) --
-	(313.86,151.71) --
-	(316.70,150.02) --
-	(319.54,152.22) --
-	(322.38,150.09) --
-	(325.22,153.11) --
-	(328.06,152.16) --
-	(330.90,151.37) --
-	(333.74,150.41) --
-	(336.59,154.30) --
-	(339.43,152.44) --
-	(342.27,151.58) --
-	(345.11,154.49) --
-	(347.95,149.53) --
-	(350.79,154.05) --
-	(353.63,151.10) --
-	(356.47,153.07) --
-	(359.31,150.01) --
-	(362.15,155.43) --
-	(364.99,152.12) --
-	(367.83,150.94) --
-	(370.67,152.10) --
-	(373.51,151.70) --
-	(376.35,154.23) --
-	(379.19,148.51) --
-	(382.03,151.49) --
-	(384.87,151.86) --
-	(387.71,153.13) --
-	(390.55,150.34) --
-	(393.39,150.97) --
-	(396.23,151.09) --
-	(399.07,151.14) --
-	(401.91,148.35) --
-	(404.75,150.18) --
-	(407.60,150.74) --
-	(410.44,154.68) --
-	(413.28,156.36) --
-	(416.12,149.02) --
-	(418.96,152.85) --
-	(421.80,153.32) --
-	(424.64,153.53) --
-	(427.48,232.35);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,137.81) --
+	( 75.27,136.65) --
+	( 78.11,143.49) --
+	( 80.95,137.43) --
+	( 83.79,130.64) --
+	( 86.63,140.10) --
+	( 89.47,133.95) --
+	( 92.31,138.95) --
+	( 95.15,138.13) --
+	( 97.99,134.38) --
+	(100.83,138.70) --
+	(103.67,136.65) --
+	(106.51,142.33) --
+	(109.35,140.08) --
+	(112.19,140.76) --
+	(115.03,135.30) --
+	(117.87,131.53) --
+	(120.71,134.31) --
+	(123.55,136.31) --
+	(126.40,138.07) --
+	(129.24,138.68) --
+	(132.08,133.35) --
+	(134.92,135.06) --
+	(137.76,137.42) --
+	(140.60,132.08) --
+	(143.44,134.84) --
+	(146.28,141.15) --
+	(149.12,136.50) --
+	(151.96,137.75) --
+	(154.80,136.26) --
+	(157.64,132.36) --
+	(160.48,135.15) --
+	(163.32,133.44) --
+	(166.16,135.02) --
+	(169.00,137.46) --
+	(171.84,137.44) --
+	(174.68,138.85) --
+	(177.52,137.64) --
+	(180.36,136.64) --
+	(183.20,136.98) --
+	(186.04,135.19) --
+	(188.88,135.00) --
+	(191.72,137.46) --
+	(194.56,133.62) --
+	(197.41,136.58) --
+	(200.25,133.35) --
+	(203.09,137.85) --
+	(205.93,138.76) --
+	(208.77,132.56) --
+	(211.61,136.25) --
+	(214.45,135.48) --
+	(217.29,136.00) --
+	(220.13,134.15) --
+	(222.97,138.92) --
+	(225.81,140.34) --
+	(228.65,137.72) --
+	(231.49,138.74) --
+	(234.33,140.75) --
+	(237.17,137.08) --
+	(240.01,139.13) --
+	(242.85,132.23) --
+	(245.69,135.17) --
+	(248.53,135.31) --
+	(251.37,134.56) --
+	(254.21,137.20) --
+	(257.05,135.96) --
+	(259.89,133.73) --
+	(262.73,140.13) --
+	(265.57,133.33) --
+	(268.42,134.06) --
+	(271.26,136.71) --
+	(274.10,138.64) --
+	(276.94,143.32) --
+	(279.78,136.35) --
+	(282.62,136.03) --
+	(285.46,138.94) --
+	(288.30,139.04) --
+	(291.14,138.48) --
+	(293.98,133.60) --
+	(296.82,137.06) --
+	(299.66,135.32) --
+	(302.50,136.59) --
+	(305.34,139.19) --
+	(308.18,132.33) --
+	(311.02,130.50) --
+	(313.86,133.96) --
+	(316.70,137.48) --
+	(319.54,136.37) --
+	(322.38,135.54) --
+	(325.22,141.95) --
+	(328.06,137.28) --
+	(330.90,136.24) --
+	(333.74,135.82) --
+	(336.59,129.34) --
+	(339.43,131.63) --
+	(342.27,137.63) --
+	(345.11,139.18) --
+	(347.95,141.59) --
+	(350.79,135.78) --
+	(353.63,132.71) --
+	(356.47,132.87) --
+	(359.31,137.75) --
+	(362.15,135.79) --
+	(364.99,140.06) --
+	(367.83,133.34) --
+	(370.67,138.30) --
+	(373.51,137.87) --
+	(376.35,138.13) --
+	(379.19,134.63) --
+	(382.03,136.24) --
+	(384.87,143.24) --
+	(387.71,134.81) --
+	(390.55,133.80) --
+	(393.39,135.75) --
+	(396.23,137.51) --
+	(399.07,135.80) --
+	(401.91,130.45) --
+	(404.75,132.80) --
+	(407.60,136.90) --
+	(410.44,137.73) --
+	(413.28,138.35) --
+	(416.12,138.71) --
+	(418.96,134.35) --
+	(421.80,137.02) --
+	(424.64,137.94) --
+	(427.48,198.96);
 \definecolor{drawColor}{RGB}{0,191,255}
 
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (424.64, 56.48) -- (424.64,268.60);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (424.64, 55.15) -- (424.64,233.80);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,189.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,225.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,212.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,176.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,235.83) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,199.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,243.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,181.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,238.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,227.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.99) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,231.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,187.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,237.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,243.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,219.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,187.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,211.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,166.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,242.97) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,222.68) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,165.90) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,241.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,179.34) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,169.71) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,233.80) circle (  2.25);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,221.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,219.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,163.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,216.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.09) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,268.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,188.70) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,172.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,210.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,212.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.23) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,245.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,176.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,251.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,179.09) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,246.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,240.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,178.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,250.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.34) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,242.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,199.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,239.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,158.42) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,224.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,175.75) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.68,134.70) -- (441.68,198.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.68,154.47) -- (441.68,232.35);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.15,139.08) --
+	(441.68,134.70) --
+	(444.21,139.08);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.15,158.85) --
-	(441.68,154.47) --
-	(444.21,158.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.21,227.97) --
-	(441.68,232.35) --
-	(439.15,227.97);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.21,194.58) --
+	(441.68,198.96) --
+	(439.15,194.58);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.16,135.51) -- (433.16,208.40);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.16,112.36) -- (433.16,164.19);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.63,139.89) --
-	(433.16,135.51) --
-	(435.69,139.89);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.63,116.74) --
+	(433.16,112.36) --
+	(435.69,116.74);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.69,204.02) --
-	(433.16,208.40) --
-	(430.63,204.02);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.69,159.81) --
+	(433.16,164.19) --
+	(430.63,159.81);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81,190.91) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$5.22};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81,164.33) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$5.22};
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (470.08,147.93) {$\alpha = 4.88$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (470.08,122.17) {$\alpha = 4.21$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 83.82) {shock time point $T^*_1 + 1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 77.15) {shock time point $T^*_1 + 1$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,205.90) {$y_{T_1^*+1}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,161.69) {$y_{T_1^*+1}$};
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,229.85) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,196.46) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,232.35) -- (427.48,232.35);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,198.96) -- (427.48,198.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,229.82) --
-	(427.48,232.35) --
-	(423.10,234.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,196.43) --
+	(427.48,198.96) --
+	(423.10,201.49);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,208.40) -- (427.48,208.40);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,164.19) -- (427.48,164.19);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,205.87) --
-	(427.48,208.40) --
-	(423.10,210.93);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,161.66) --
+	(427.48,164.19) --
+	(423.10,166.72);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,232.35) rectangle (212.08,196.35);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,198.96) rectangle (212.08,162.96);
 \definecolor{drawColor}{RGB}{255,106,106}
 
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,220.35) -- ( 93.75,220.35);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,186.96) -- ( 93.75,186.96);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,208.35) -- ( 93.75,208.35);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,174.96) -- ( 93.75,174.96);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,216.91) {$\hat{y}_{t}^{1}$ without shock effects};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,183.51) {$\hat{y}_{t}^{1}$ without shock effects};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,204.91) {$\hat{y}_{t}^{2}$ with shock effects};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,171.51) {$\hat{y}_{t}^{2}$ with shock effects};
 \end{scope}

### 2020-08-05 manuscript/fig2.tex
addition of Section 3.4 and many revisions to abstract, intro, and Section 3.3, 4, 5, 6
changes by deletion of covariates and revision by comments

@@
-% Created by tikzDevice version 0.12.3 on 2020-06-28 18:03:01
+% Created by tikzDevice version 0.12.3.1 on 2020-08-05 10:48:56
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.25) --
-	(481.73, 86.67) --
-	(476.44, 86.67) --
-	(479.09, 91.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 92.09) --
+	(481.73, 87.51) --
+	(476.44, 87.51) --
+	(479.09, 92.09);
 \definecolor{drawColor}{RGB}{0,191,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 88.07) -- (481.86, 88.07);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 89.61) -- (481.86, 89.61);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.29) -- (479.09, 90.84);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 86.84) -- (479.09, 92.39);
 \definecolor{drawColor}{RGB}{238,99,99}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 81.21) -- (481.05, 85.13);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 83.03) -- (481.05, 86.95);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 85.13) -- (481.05, 81.21);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.95) -- (481.05, 83.03);
 \definecolor{drawColor}{RGB}{238,130,238}

### 2020-08-05 manuscript/manuscript.tex
changes by deletion of covariates and revision by comments

@@
 \usepackage{float}
+\usepackage[caption = false]{subfig}
 \usepackage{tikz}
@@
 Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
-However, our model formulation is more general than \cite{ramaswamy1993empirical} and our donor pool is formed from independent time series.
+However, our model formulation is more general than \cite{ramaswamy1993empirical}.
+In our model, the donor pool can consist of dependent time series but time series within the donor pool should be independent of the time series of interest.
+However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method.
 %The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point.
@@
 
+\begin{figure}[H]
+  \begin{center}
+    \subfloat[A comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series, and that the shock time is at $T_1^* +1=126$.
+The magenta dots represent least square estimate $\hat{\alpha}_i$ from disparate time series.
+The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=5.22$.
+It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.]{\includegraphics[height = 7cm]{comp.pdf}}\\
+     \subfloat[Histogram for $\hat{\alpha}_i$ for $i = 2, \ldots, n+1$]{\includegraphics[height = 7cm]{alphahist.pdf}}
+  \end{center}
+     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 4.21$.
+(a) presents the comparison of the prediction without adjustment and one with.
+(b) shows the histogram for the $\alpha_i$s used in estimating shock $\alpha_1$.}\label{figure1}
+\end{figure}
+
 \section{Setting}
@@
 The details of this model are in the next section.
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[height = 8cm]{comp.pdf}
-    \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 4.88$.
-The figure is a comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series, and that the shock time is at $T_1^* +1=126$.
-The magenta dots represent least square estimate $\hat{\alpha}_i$ from disparate time series.
-The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=5.22$.
-It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
-  \end{center}  
-  \vspace{-.6cm}
-\end{figure}
 
@@
 
-The model $\mc{M}_1$ is defined as
+Let $I(\cdot)$ be an indicator function, $T_i$ be the time length of the time series $i$ for $i = 1, \ldots, n+1$, and $T_i^*$ be the time point just before the one when the shock is \emph{known} to occur, with $T_i^* < T_i$.
+For $t= 1, \ldots, T_i$ and $i = 1, \ldots, n+1$, the model $\mc{M}_1$ is defined as
 \begin{align}
-\mc{M}_1 \colon y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t}+ \beta_i'\mbf{x}_{i, t-1} + \varepsilon_{i,t}\label{equation1}
+\mc{M}_1 \colon y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\label{equation1}
 \end{align}
-for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = I(t = T_i^* + 1)$, 
-$T_i^* < T_i$ and $\x_{i,t} \in \R^{p}$, $p \geq 1$.  We assume that the 
-$\mbf{x}_{i,t}$'s are fixed and $T_i^*$s are known. The random effects structure for $\mc{M}_1$ is:
-\begin{align*}
-  \eta_i &\simiid  \eta ,\where \E{\eta} = 0, \var{\eta} = \sigma^2_{\eta}, \qquad i = 1, \ldots, n+1,\\
-  \phi_i &\simiid \phi, \where |\phi|<1, \qquad i = 1, \ldots, n+1, \\
-   \theta_i &\simiid \theta, \where \E{\theta}=\mu_{\theta}, \var{\theta}=\Sigma_{\theta}^2, \qquad i = 1, \ldots, n + 1, \\
-\beta_i &\simiid \beta, \where \E{\beta}=\mu_{\beta}, \var{\beta}=\Sigma_{\beta}^2, \qquad i = 1, \ldots, n+1,\\
-\alpha_i &\simiid \alpha, \where \E{\alpha}=\mu_{\alpha}, \var{\alpha}=\sigma_{\alpha}^2, \qquad  i = 1, \ldots, n+1; \\
-\varepsilon_{i,t} &\simiid \normal{0}{\sigma^2}, \qquad t=1, \ldots, T_i, \; i = 1, \ldots, n+1,\\
-\eta &\indep  \alpha_i \indep \phi \indep \theta \indep \varepsilon_{i,t}.
+ where $D_{i,t} = I(t = T_i^* + 1)$ 
+and $\x_{i,t} \in \R^{p}$ with $p \geq 1$.  We assume that the 
+$\mbf{x}_{i,t}$'s are fixed. Let $|x|$ denote the absolute value of $x$ for $x\in \reals$. For $i = 1, \ldots, n+1$ and $t=1, \ldots, T_i$, the random effects structure for $\mc{M}_1$ is:
+\begin{align*}
+  \eta_i &\simiid  \; \E{\eta_i} = 0, \var{\eta_i} = \sigma^2_{\eta}\\
+  \phi_i &\simiid \; |\phi_i|<1, \\
+   \theta_i &\simiid  \; \E{\theta_i}=\mu_{\theta}, \var{\theta_i}=\Sigma_{\theta}^2 \\
+\alpha_i &\simiid \; \E{\alpha_i}=\mu_{\alpha}, \var{\alpha_i}=\sigma_{\alpha}^2, \\
+\varepsilon_{i,t} &\simiid \; \E{\varepsilon_{i,t}} =0, \var{\varepsilon_{i,t}}=\sigma^2 \where \sigma > 0 ,  \\
+\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t}.
 \end{align*}
@@
 for $i = 1, \ldots, n+1$.  %Although synthesizing information from disparate time series assumes similarities of shock effects, shock effects may differ in terms of their means in practice. 
-We also consider a model where the shock effects are linear functions of covariates and 
-lagged covariates with an additional additive mean-zero error.
+We also consider a model where the shock effects are linear functions of covariates with an additional additive mean-zero error.
 %Additionally, $\mc{M}_1$ can be further improved in the sense that the shock effects may depend on the covariates around the shock time points, i.e., $T_i^*$ for $i = 1, \ldots, n+1$. 
 %$\mc{M}_2$ can be constructed to accommodate those issues by imposing additional structures on the means of $\alpha_i$ as in (\ref{model2}) for $i = 1, \ldots, n+1$.
-The random effects structure for this model (model $\mc{M}_2$) is:
+For $i = 1, \ldots, n+1$, the random effects structure for this model (model $\mc{M}_2$) is:
 \begin{align}
 \mc{M}_2 \colon \begin{array}{l}
-  y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t}+ \beta_i'\mbf{x}_{i, t-1} + \varepsilon_{i,t}\\[.2cm]
-  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}+\t{\varepsilon}_{i},
+  y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
+  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+ \t{\varepsilon}_{i},
 \end{array}\label{model2}
 \end{align}
-for $i = 1, \ldots, n+1$, where the added random effects are
-\begin{align*}
-\t{\varepsilon}_{i} &\simiid  \E{\t{\varepsilon}}=0, \var{\t{\varepsilon}}=\sigma^2_{\alpha}, \qquad i = 1, \ldots, n+1,\\
-\eta &\indep  \alpha_i \indep \phi \indep \theta \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
+ where the added random effects are
+\begin{align*}
+\t{\varepsilon}_{i} &\simiid  \E{\t{\varepsilon}}=0, \var{\t{\varepsilon}}=\sigma^2_{\alpha} \where \sigma_{\alpha}>0\\
+\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
 \end{align*}
@@
 We further define 
-$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T_i^*}$. 
+$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}$. 
 We will investigate the post-shock aggregated estimators in $\mc{M}_2$ 
-in settings where $\delta_i$ and $\gamma_i$ are either fixed or random. 
-We let $\mc{M}_{21}$ denote model $\mc{M}_{2}$ with $\gamma_i = \gamma$ 
-and $\delta_i = \delta$ for $i= 1, \ldots, n+1$, 
-where $\gamma$ and $\delta$ are fixed unknown parameters.
+in settings where $\delta_i$ is either fixed or random. 
+We let $\mc{M}_{21}$ denote model $\mc{M}_{2}$ with $\delta_i = \delta$ for $i= 1, \ldots, n+1$, 
+where $\delta$ is a  fixed unknown parameter.
 We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects 
-structure for $\gamma_i$ and $\delta_i$:
-\begin{align*}
-\begin{array}{c}
-  \gamma_i \overset{iid}{\sim} \mrm{E}(\gamma) = \mu_\gamma, \var{\gamma} = \Sigma_\gamma \\
-  \delta_i \overset{iid}{\sim} \mrm{E}(\delta) = \mu_\delta, \var{\delta} = \Sigma_\delta
-\end{array}
-   \quad \text{ with } \quad  \delta_i  \indep \t{\varepsilon}_{i} \quad  \text{ and } \quad \gamma_i  \indep \t{\varepsilon}_{i}.
-\end{align*}
-Note that $\delta_i$ and $\gamma_i$ may be dependent. We further define the parameter sets
+structure for $\delta_i$:
+\begin{align*}
+\delta_i \overset{iid}{\sim}\;  \mrm{E}(\delta) = \mu_\delta, \var{\delta} = \Sigma_\delta
+   \quad \text{ with } \quad  \delta_i  \indep \t{\varepsilon}_{i}.
+\end{align*}
+We further define the parameter sets
 \begin{align}
   \begin{array}{lll}
-     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
-    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
+     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
+    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
   \end{array}
 \end{align}
-where $\Theta$ and $\Theta_1$ can adapt to $\mc{M}_1$ by dropping $\delta_i$ and 
-$\gamma_i$. We assume this for notational simplicity.
+where $\Theta$ and $\Theta_1$ can adapt to $\mc{M}_1$ by dropping $\delta_i$. We assume this for notational simplicity.
 
@@
     + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
-    + \hat\beta_1'\x_{1,T_1^*}, \\
+    , \\
   &\text{Forecast 2}: \hat y_{1,T_1^*+1}^2 = \hat\eta_1 
     + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
-    + \hat\beta_1'\x_{1,T_1^*} + \hat{\alpha},
-\end{align*}
-where $\hat\eta_1$, $\hat\phi_1$, $\hat\theta_1$, and $\hat\beta_1$ are all ordinary least squares (OLS) estimators of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$ respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
+    + \hat{\alpha},
+\end{align*}
+where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all ordinary least squares (OLS) estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
 The first forecast ignores the presence of $\alpha_1$ while the second forecast 
@@
 $y_{1,T_1^*+1}$. Throughout the rest of this article we show that the collection of 
-disparate time series $\{y_{i,t}, t = 2,\ldots,T_i, i = 1,\ldots,n\}$ has 
+disparate time series $\{y_{i,t}, t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$ has 
 the potential to improve the forecasts for $y_{1, t}$ when $t > T_1^*$ under different 
 circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response.
-It is important to note that in general $\hat{\alpha}$
+Improvement will be  measured by \emph{risk-reduction quantity}, which is the difference between the risk of Forecast 1 and Forecast 2.
+We will return to the theoretical details of risk-reduction quantity in Section \ref{properties}.
+
+We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response. It is important to note that in general $\hat{\alpha}$ 
 is not a consistent estimator of the unobserved $\alpha_1$ nor does it converge 
@@
     \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
-      + \beta_i'\x_{i,t-1}, \sigma^2).
+      , \sigma^2).
 $$
-For $i = 2, \ldots, n$, all parameters in this model will be estimated with ordinary least squares 
-(OLS) using historical data of $t = 1, \ldots, n_i$.
+For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares 
+(OLS) using historical data of $t = 1, \ldots, T_i$.
 For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$.
@@
 We also consider the \emph{inverse-variance weighted estimator} 
-in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i$. 
+in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i=2, \ldots, n+1$. 
 The inverse-variance weighted estimator is defined as 
@@
 \begin{align*}
- \mbf{X}_1 = \begin{pmatrix}
-    \mbf{x}_{1, T_1^*}' \\ \mbf{x}_{1, T_1^*+1}'
-  \end{pmatrix},
+ \mbf{X}_1 = \mbf{x}_{1, T_1^*+1}',
   \quad  
   \mbf{X} = \begin{pmatrix}
-  	\mbf{x}_{2, T_2^*}' \\
     \mbf{x}_{2, T_2^*+1}' \\
     \vdots \\
-  	\mbf{x}_{n+1, T_{n+1}^*}' \\
     \mbf{x}_{n+1, T_{n+1}^*+1}'
@@
   \hat{\mbf{X}}_1(\mbf{W}) 
-    = (\mbf{W}' \otimes \mbf{I}_2) \mbf{X},
-\end{align*}
-where $\otimes$ is the Kronecker product, $\mbf{I}_2$ is the identity matrix with two rows, and $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{2 \times p}$.
-Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$.
+    = \mbf{W}'\mbf{X},
+\end{align*}
+where $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{1 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 
 Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
@@
 \begin{align}
- \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
+ \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
 \end{align}
@@
  \begin{align*}
-   \left\{ \begin{pmatrix}
-     \mbf{x}_{2, T_2^*}' \\
-      \mbf{x}_{2, T_2^*+1}'
-   \end{pmatrix}, \ldots, \begin{pmatrix}
-     \mbf{x}_{n+1, T_{n+1}^*}' \\
-      \mbf{x}_{n+1, T_{n+1}^*+1}'
-   \end{pmatrix} \right\}.
+   \left\{ \mbf{x}_{2, T_2^*+1}', \ldots, \mbf{x}_{n+1, T_{n+1}^*+1}' \right\}.
  \end{align*}
@@
 \begin{align}
-  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})\big)}_{2p}. 
+  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})}_{p}. 
   \label{W}
@@
 \begin{align*}
-  \mathbf{V} = \Big(\mrm{vec}\big((\mathbf{x}_{2, T_2^*}, \mathbf{x}_{2, T_2^*+1})\big), \ldots, \mrm{vec}\big((\mathbf{x}_{n+1, T_2^*}, \mathbf{x}_{n+1, T_2^*+1})\big)\Big).
+  \mathbf{V} = (\mathbf{x}_{2, T_2^*+1}, \ldots,\mathbf{x}_{n+1, T_{n+1}^*+1}).
 \end{align*}
@@
 Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.
-Note that $\mathbf{V}$ is $2p \times n$.
-Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$.
-However, when $2p < n$, $\mathbf{W}^*$ may not be unique.
-If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there are infinitely many solutions to (\ref{SCM}).
+Note that $\mathbf{V}$ is $p \times n$.
+Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $p \geq n$.
+However, when $p < n$, $\mathbf{W}^*$ may not be unique.
+If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $p < n$, there are infinitely many solutions to (\ref{SCM}).
 The issue of non-uniqueness is further discussed in Section \ref{varbootstrap}.
@@
 % Though in Section \ref{modelsetup} we assume $\mbf{x}_{i,t}\in \reals^p$ and bases construction for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$  on this fact, we will shortly show that the covariates need not be of the same dimension across disparate time series.
-In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta, \beta \in \reals^p$. 
+In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
  % We can insert $\mathbf{0}$ into the covariates of disparate time series for the parts that they do not share.
@@
 However, it is not necessary that the all $p$ covariates are important for every time series under study.
-The regression coefficients $\theta$ and $\beta$ are nuisance parameters that are not of primary importance.
+The regression coefficients $\theta_i$ are nuisance parameters that are not of primary importance.
 % In this regard, OLS estimations in software can reparameterize the design matrix.
@@
 The generalization may only apply to the construction of weighted-adjustment  estimator $\hat{\alpha}_{\rm wadj}$.
-It will be understood that structural 0s in $\mbf{x}_{i,t}$ correspond to variables that are unimportant. 
+It will be understood that structural 0s in $\theta_i$ correspond to variables that are unimportant. 
 \end{remark}
@@
 If the sampling distribution of the data and $\pi$ are known, it is possible to compute the Bayes risks of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ with respect to $\pi$, and thus enable comparisons among them.
-Additionally, from Lemma 20.3 \citep{marden}, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are admissible among the set of Bayes rules with respect to $\pi$ under corresponding loss functions.
+Additionally, from Theorem 2.4 in Chapter 5 of \cite{lehmann2006theory}, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are admissible if they are unique with probability one.
 \end{remark}
@@
     \begin{align*}
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1} + \frac{1}{n} \sum_{i=2}^{n+2} \gamma' \mbf{x}_{i, T_i^*} 
+      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1} 
       \quad \text{ and } \quad 
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} + \gamma' \mbf{x}_{1, T_1^*}.
+       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} .
     \end{align*}
@@
     \begin{align*}
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{2} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1} + \frac{1}{n} \sum_{i=2}^{n+2}  \mu_{\gamma}'\mbf{x}_{i, T_i^*} 
+      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1}
       \quad \text{ and } \quad 
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} + \mu_{\gamma}' \mbf{x}_{1, T_1^*}.
+       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} .
     \end{align*}
@@
 \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}\var{\alpha_i}\\
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
   \var{\hat{\alpha}_{\rm wadj}} 
   &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
-  + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i}.
+  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
 \end{align*}
@@
 \var{\hat{\alpha}_{\rm wadj}}
- = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i} < (\E{\alpha_1})^2,
-\end{align*}
-where $\var{\alpha_i}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$.
+ = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}) < (\E{\alpha_1})^2,
+\end{align*}
+where $\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$.
 The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.
@@
 where $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ is computed with respect to donor pool with index set $\mc{I}_m$ and the $m+1$ time series is treated as the time series of interest.
-The mutual independence assumption in model setup $\mc{M}_{2}$ implies that $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
 The LOOCV with $k$ random draws estimates $\E{\mc{C}(\delta_{\hat{\alpha}})}$ as
@@
 The estimation bias should decrease as $k \to n$.
+
+\begin{remark}
+  Note that we allow the time series within the donor pool to be dependent but donor pool should be independent of the time series of interest.
+However, if we assume the mutual  independence structure, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
+In other words, mutual independence assumption is not related to  $\E{\mc{C}(\delta_{\hat{\alpha}})}$ (i.e., the intrinsic correctness) but its estimation.
+\end{remark}
 
@@
 $
-  \norm{\mrm{vec}\left(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\right)}_{4} = 1314.04.
+  \norm{\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)}_{2} = 900.13.
 $
@@
 
-The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-5.433$, $\hat{\alpha}_{\rm wadj}= -5.945$, and $\hat{\alpha}_{\rm IVW}=-5.446$.
+The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-5.348$, $\hat{\alpha}_{\rm wadj}= -5.761$, and $\hat{\alpha}_{\rm IVW}=-5.290$.
 Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}.
-The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.531, 0.479, and 0.970, respectively.
-Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $34.565$, $34.880$, and $34.139$, respectively.
+The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.567, 0.499, and 1.006, respectively.
+Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $32.452$, $32.690$, and $31.960$, respectively.
 We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
@@
 The unadjusted forecast has an RMSE of 9.870 dollars whereas 
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $3.924$, and $4.423$ dollars, respectively. 
+the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.522$, $4.109$, and $3.581$ dollars, respectively. 
 Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
@@
 The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.382$, $2.468$, and $1.145$ dollars, respectively.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.136$, $2.421$, and $0.818$ dollars, respectively.
 These additive adjustment estimators do extremely well.
@@
 
-Moreover, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors.
-Multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
+Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
 As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
@@
 The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
-Recall that the modeling equation of $\alpha_i$ includes present day and lagged covariates.
-It can be also generalized to the one with $q$ lags covariates.
-In that case, based same assumptions in Section \ref{constructionofestimators}, a sufficient condition for $\mbf{W}^*$ to be unique is $p(q+1) \geq n$.
 We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts.
 An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.
+Although our work is developed for  time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated \emph{unbiasedly}, and an additive shock-effect structure.
 
@@
 We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.
-Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $2p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
+Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
 However, in applications, it is possible that $\mathbf{W}^*$ may take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-Moreover, when $2p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
+Moreover, when $p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
 However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
 Nevertheless, it does not seriously compromise the inference according to our simulation results in Section 4 in the Supplementary Materials.
-In fact, one can avoid this issue by increasing lagged number 1 to $q$ in the modeling equation of $\alpha_i$ to some $q$ such that $p(q+1) \geq n$, mentioned previously.
 
@@
    &= \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right)\\
-   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}\right]\bigg\}\\
-   &=\mu_{\alpha}+\mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}\right]\bigg\}.\tag{$\mbf{W}\in \mc{W}$}
+   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}\right]\bigg\}\\
+   &=\mu_{\alpha}+ \mu_{\delta}' \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}\tag{$\mbf{W}\in \mc{W}$}
+   \\
+   &=\mu_{\alpha}+  \mu_{\delta}'\mbf{x}_{1, T_1^*+1}. \tag{from (\ref{SCM})}
    \end{align*}
@@
    \E{\hat{\alpha}_{\rm adj}}
-   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \E{\delta_{i}'\mbf{x}_{i, T_i^*+1}+\gamma_i'\mbf{x}_{i, T^*_i}}.
+   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \mu_{\delta}'  \mbf{x}_{i, T_i^*+1}.
    \end{align*}
@@
 \end{align*}
-Under $\mc{M}_{21}$ where $\delta_i=\delta$ and $\gamma_i=\gamma$ are fixed unknown parameters,  we will have
+Under $\mc{M}_{21}$ where $\delta_i=\delta$ are fixed unknown parameters,  we will have
   \begin{align}
@@
   &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
-  + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i}
+  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
 \end{align*}
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}\var{\alpha_i}.
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
 \end{align*}
@@
   \begin{cases}
-       \frac{1}{n} \sum_{i=2}^{n+1} \delta'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1}) +  \frac{1}{n} \sum_{i=2}^{n+1} \gamma'(\mbf{x}_{i, T_i^*}-n\mbf{x}_{1, T_1^*}) & \text{ for } \mc{M}_{21}\\
-    \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1}) +  \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\gamma}'(\mbf{x}_{i, T_i^*}-n\mbf{x}_{1, T_1^*}) & \text{ for }\mc{M}_{22}
+       \frac{1}{n} \sum_{i=2}^{n+1} \delta'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1})  & \text{ for } \mc{M}_{21}\\
+    \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1})  & \text{ for }\mc{M}_{22}
   \end{cases}.
@@
 \begin{lem}
-  \label{risklemma} The forecast risk difference is $R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2$ for all estimators of $\alpha_1$ that are independent of $\Theta_1$ (see Section \ref{modelsetup}).
+  \label{risklemma} The forecast risk reduction is $R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2$ for all estimators of $\alpha_1$ that are independent of $\Theta_1$ (see Section \ref{modelsetup}).
 \end{lem}
@@
   \begin{align*}
-    C(\Theta_1) =\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} + \hat{\beta}_1'\mbf{x}_{1, T_1^*}-(\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}+\beta_1'\mbf{x}_{1,T_1^*}),
+    C(\Theta_1) =\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} -(\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}),
   \end{align*}
@@
   \end{align*}
-  Assuming $\mbf{S}=(\mbf{1}_n, \mbf{y}_{1,t-1}, \mbf{x}_{1}, \mbf{x}_{1,t-1})$ has full rank, under OLS setting, $\hat{\eta}_1$, $\hat{\phi}_1$, $\hat{\theta}_1$, and $\hat{\beta}_1$ are unbiased estimators of $\eta_1$, $\phi_1$, $\theta_1$, and $\beta_1$, respectively under conditioning of $\Theta_1$.
+  Assuming $\mbf{S}=(\mbf{1}_n, \mbf{y}_{1,t-1}, \mbf{x}_{1})$ has full rank, under OLS setting, $\hat{\eta}_1$, $\hat{\phi}_1$, and $\hat{\theta}_1$ are unbiased estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively under conditioning of $\Theta_1$.
 Since we assume $\hat{\alpha}$ is independent of $\Theta_1$, through the method of iterated expectation,

### 2020-08-06 manuscript/manuscript.tex
addressed Forrest and Karl Oskar edits; I left a few small comments

@@
 Three shock effects estimators were constructed for minimizing average forecast risk.
-We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities.
-Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock forecasts before the post-shock response is observed.
-The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well.
+We proposed risk-reduction propositions providing conditions when our methodology works.
+Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential prospective success of post-shock forecasts.
+%The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well.
     Leave-one-out cross validation is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality.
@@
 In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
-The researcher must therefore move beyond the modeling paradigm under which he or she was previously working  to accommodate this new shock \citep{monti2008forecast, svensson2005monetary}.
+In this setting, the additive shock effect is a random effect that is parameterized in the autoregressive model.
+The shock effect is then estimated using ordinary least squares (OLS).
+The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}.
 One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}.
@@
 However, there are key differences between our framework and SCM.
-We assume that the disparate time series are independent from the time series under study before the timing of the shock.
+We assume that the disparate time series are independent from the time series under study before the timing of the shock {\bf Jilei, can weaken this assumption?}.
 We also assume that the shock effects for each disparate time series are independent realizations from some unknown distribution.
@@
 The context in \cite{clements2019measuring} allowed for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
-There is no consistency guarantee here.
-In our context, the yet to observed shock effect of interest is a realization from a random process that can only be partially explained by the realizations of the disparate time series.
-Therefore, the shock effect of interest can not be estimated consistently.
+In our context, the yet to observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the disparate time series.
 
@@
 post-shock aggregated estimators are provided. The basic structures of these models 
-are the same, the differences between them lie in the setup of the shock effect 
-distribution.
+are the same for all time-series in the analysis, the differences between them lie in the setup of the shock effect distribution.
 
@@
 \end{align*}
-where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all ordinary least squares (OLS) estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
+where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all OLS estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
 The first forecast ignores the presence of $\alpha_1$ while the second forecast 
@@
  \end{align*}
+{\bf Jilei, can you add clarity to this point? It is hard to see why this works on the first viewing.}
 %It is a reasonable assumption that the pool of time series that we are considering 
@@
 \label{forecasting}
-In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession.
+
+We demonstrate our post-shock forecasting methodology on a time series of Conoco Phillips share prices after the occurrence of a structural shock.
+Conoco Phillips is a large oil and gas resources company \citep{conocowhatwedo}.
+The particular post-shock response that we predict happened after trading ended on Friday March 6th, 2020 and before trading began on Monday March 9th, 2020.
+It is reasonable that the timing of this shock is known, several events occurred over the trading weekend which had an impact on stock markets and the oil markets.
+For example, Russia and OPEC began a battle for global oil price control on Sunday, March 8th \citep{sukhankin2020russian}, and several US states began declaring state of emergencies in response to the evolving coronavirus pandemic \citep{nygov, alonso2020state}.
+In this analysis we make the following design considerations:
+
+%In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession.
 Specific interest is in predictions made after March 6, 2020, the Friday before the stock market crash on March 9, 2020.
@@
 
-Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo}. %and with a relatively recent initial public offering \citep{conocohist}. 
-Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control on the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}.
+%Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo}. %and with a relatively recent initial public offering \citep{conocohist}. 
+%Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control on the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}.
 Furthermore, fear and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
@@
 
-Economic indicators forecasted our recession before the coronavirus pandemic began.
+%Economic indicators forecasted our recession before the coronavirus pandemic began.
 The current recession followed an inversion of the yield curve that first happened back in March, 2019 \citep{tokic2019yield}.
@@
 Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}.
-In this analysis we make the following considerations:
 
 \begin{enumerate}
-\item[(1)] {\bf AR(1) model and time window}.
+\item[(1)] {\bf Selection of model}.
 We will use an AR(1) model to forecast Conoco Phillips stock price.
 This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.
-We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window.
+For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect.
 All estimates will be adjusted for inflation.
@@
 \item[(3)] {\bf Construction of donor pool}.
-Our donor pool  consists of Conoco Phillips shock effects observed on March 14, 2008, several events in September, 2008, and November 27, 2014.
-The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}.
-The reasons for those three shocks are:
-  \begin{enumerate}
-  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities.
+Our donor pool consists of Conoco Phillips shock effects observed in the past.
+We consider shock effects which occurred on March 14, 2008, several days in September, 2008, and November 27, 2014.
+The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession.
+In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}.
+These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Mac in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}.
+The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}.
+%The reasons for those three shocks are.
+%  \begin{enumerate}
+%  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities.
 On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank.
@@
 %In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
-  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets.
+%  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets.
 The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}.
 Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
-  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}.
+%  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}.
 During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors.
 During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}.
-  \end{enumerate}
+%  \end{enumerate}
 \end{enumerate}
@@
 The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.567, 0.499, and 1.006, respectively.
-Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $32.452$, $32.690$, and $31.960$, respectively.
+%Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $32.452$, $32.690$, and $31.960$, respectively.
 We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
@@
 We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, and they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
-The unadjusted forecast has an RMSE of 9.870 dollars whereas 
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.522$, $4.109$, and $3.581$ dollars, respectively. 
-Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
+The unadjusted forecast misses the post-shock response by 9.870 dollars whereas 
+the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $4.522$, $4.109$, and $3.581$ dollars, respectively. 
+%Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
 Moreover, the risk-reduction quantities are consistent with the reality as well.
-
-The phenomenon that the true shock effect is not recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ can be due to that the donor pool is not constructed to be similar enough to the time series of interest.
-The shock(s) on March 9, 2020 is(are) in the midst of the COVID-19 pandemic and oil production volatility.
+The true shock effect is not fully recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$.
+This may be a result of a poorly constructed donor pool.
+The shock on March 9th, 2020 is in the midst of the COVID-19 pandemic and oil production volatility.
 It is difficult to find available stock market time series data that were generated under a similar setting.
+In any event, the shock on March 9th, 2020 was the largest price shock to Conoco Phillips shares by a wide margin, even after adjusting for inflation.
 

### 2020-08-09 manuscript/alphahist.tex
addition of simulation results

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-05 11:58:06
+% Created by tikzDevice version 0.12.3.1 on 2020-08-08 20:35:31
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 66.75, 26.40) {2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 66.75, 26.40) {7};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (133.70, 26.40) {3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (133.70, 26.40) {8};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (200.65, 26.40) {4};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (200.65, 26.40) {9};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (267.60, 26.40) {5};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (267.60, 26.40) {10};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (334.56, 26.40) {6};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (334.56, 26.40) {11};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (401.51, 26.40) {7};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (401.51, 26.40) {12};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (468.46, 26.40) {8};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (468.46, 26.40) {13};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (535.41, 26.40) {9};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (535.41, 26.40) {14};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.25, 55.15) -- (167.18, 85.07);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.11, 55.15) -- (133.70, 79.74);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.18, 85.07) -- (188.30,106.19);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.70, 79.74) -- (167.18,113.22);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65,220.75) -- (213.70,233.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65,146.69) -- (234.13,180.17);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.65,118.55) -- (234.13,152.02);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.31, 55.15) -- (234.13, 77.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.13,152.02) -- (239.34,157.23);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.13, 77.96) -- (267.60,111.44);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.46, 55.15) -- (267.60, 83.29);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.60,111.44) -- (287.88,131.71);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.60, 83.29) -- (301.08,116.77);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (301.08,144.91) -- (334.56,178.39);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (301.08,116.77) -- (334.56,150.24);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (313.52, 55.15) -- (334.56, 76.19);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56,150.24) -- (368.03,183.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56,178.39) -- (364.44,208.28);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.66, 55.15) -- (368.03, 81.52);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.56, 76.19) -- (368.03,109.66);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (368.03, 81.52) -- (401.51,114.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (368.03,109.66) -- (401.51,143.14);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.87, 55.15) -- (443.87, 55.15);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.72, 55.15) -- (434.98, 74.41);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.46, 79.74) -- (469.39, 80.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.93, 55.15) -- (535.41, 72.63);
 
@@
 	(133.70, 55.15) --
-	(133.70,106.19) --
-	(100.22,106.19) --
+	(133.70, 80.67) --
+	(100.22, 80.67) --
 	(100.22, 55.15);
@@
 	(167.18, 55.15) --
-	(167.18,106.19) --
-	(133.70,106.19) --
+	(167.18,131.71) --
+	(133.70,131.71) --
 	(133.70, 55.15);
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.27, 48.00) -- (282.27,240.94);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.53, 48.00) -- (282.53,240.94);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.44,226.14) -- (285.62,226.14);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.70,226.14) -- (285.88,226.14);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.00,228.67) --
-	(285.62,226.14) --
-	(290.00,223.61);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.26,228.67) --
+	(285.88,226.14) --
+	(290.26,223.61);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (368.03,223.64) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$5.22};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (374.73,223.64) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$10.22};
 \end{scope}

### 2020-08-09 manuscript/comp.tex
addition of simulation results

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-05 11:58:05
+% Created by tikzDevice version 0.12.3.1 on 2020-08-08 20:33:27
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,141.91) --
-	( 75.27,148.65) --
-	( 78.11,138.04) --
-	( 80.95,120.32) --
-	( 83.79,144.55) --
-	( 86.63,128.04) --
-	( 89.47,158.74) --
-	( 92.31,142.28) --
-	( 95.15,144.24) --
-	( 97.99,150.16) --
-	(100.83,129.86) --
-	(103.67,156.20) --
-	(106.51,161.19) --
-	(109.35,150.66) --
-	(112.19,143.27) --
-	(115.03,126.88) --
-	(117.87,118.05) --
-	(120.71,139.15) --
-	(123.55,135.40) --
-	(126.40,140.74) --
-	(129.24,149.36) --
-	(132.08,115.48) --
-	(134.92,139.71) --
-	(137.76,114.03) --
-	(140.60,125.67) --
-	(143.44,139.07) --
-	(146.28,144.69) --
-	(149.12,130.89) --
-	(151.96,140.09) --
-	(154.80,126.64) --
-	(157.64,111.23) --
-	(160.48,121.82) --
-	(163.32,149.80) --
-	(166.16,149.85) --
-	(169.00,139.78) --
-	(171.84,158.01) --
-	(174.68,141.87) --
-	(177.52,133.42) --
-	(180.36,131.05) --
-	(183.20,129.40) --
-	(186.04,142.69) --
-	(188.88,144.63) --
-	(191.72,130.06) --
-	(194.56,121.56) --
-	(197.41,118.55) --
-	(200.25,119.73) --
-	(203.09,140.14) --
-	(205.93,137.20) --
-	(208.77,125.79) --
-	(211.61,150.02) --
-	(214.45,134.16) --
-	(217.29,137.62) --
-	(220.13,143.96) --
-	(222.97,145.02) --
-	(225.81,137.14) --
-	(228.65,147.61) --
-	(231.49,162.41) --
-	(234.33,138.41) --
-	(237.17,162.38) --
-	(240.01,127.19) --
-	(242.85,125.12) --
-	(245.69,134.60) --
-	(248.53,134.89) --
-	(251.37,158.83) --
-	(254.21,122.69) --
-	(257.05,117.16) --
-	(259.89,147.80) --
-	(262.73,138.62) --
-	(265.57,123.35) --
-	(268.42,140.39) --
-	(271.26,137.29) --
-	(274.10,148.46) --
-	(276.94,135.80) --
-	(279.78,134.54) --
-	(282.62,139.54) --
-	(285.46,143.03) --
-	(288.30,143.37) --
-	(291.14,107.15) --
-	(293.98,121.09) --
-	(296.82,144.70) --
-	(299.66,143.32) --
-	(302.50,149.80) --
-	(305.34,113.62) --
-	(308.18,139.96) --
-	(311.02,134.15) --
-	(313.86,130.85) --
-	(316.70,135.42) --
-	(319.54,131.11) --
-	(322.38,145.18) --
-	(325.22,143.55) --
-	(328.06,141.15) --
-	(330.90,125.31) --
-	(333.74,129.29) --
-	(336.59,118.52) --
-	(339.43,146.06) --
-	(342.27,140.93) --
-	(345.11,151.97) --
-	(347.95,136.60) --
-	(350.79,114.01) --
-	(353.63,120.33) --
-	(356.47,142.22) --
-	(359.31,130.73) --
-	(362.15,138.80) --
-	(364.99,114.92) --
-	(367.83,152.60) --
-	(370.67,139.26) --
-	(373.51,137.13) --
-	(376.35,140.56) --
-	(379.19,149.07) --
-	(382.03,151.38) --
-	(384.87,153.12) --
-	(387.71,126.88) --
-	(390.55,137.55) --
-	(393.39,137.71) --
-	(396.23,129.83) --
-	(399.07,123.04) --
-	(401.91,117.89) --
-	(404.75,132.35) --
-	(407.60,141.10) --
-	(410.44,137.00) --
-	(413.28,143.73) --
-	(416.12,131.05) --
-	(418.96,129.54) --
-	(421.80,129.16) --
-	(424.64,128.38) --
-	(427.48,164.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,119.70) --
+	( 75.27,124.71) --
+	( 78.11,116.82) --
+	( 80.95,103.64) --
+	( 83.79,121.66) --
+	( 86.63,109.38) --
+	( 89.47,132.22) --
+	( 92.31,119.97) --
+	( 95.15,121.43) --
+	( 97.99,125.83) --
+	(100.83,110.73) --
+	(103.67,130.32) --
+	(106.51,134.04) --
+	(109.35,126.21) --
+	(112.19,120.71) --
+	(115.03,108.51) --
+	(117.87,101.94) --
+	(120.71,117.64) --
+	(123.55,114.85) --
+	(126.40,118.83) --
+	(129.24,125.24) --
+	(132.08,100.04) --
+	(134.92,118.06) --
+	(137.76, 98.96) --
+	(140.60,107.61) --
+	(143.44,117.58) --
+	(146.28,121.77) --
+	(149.12,111.50) --
+	(151.96,118.34) --
+	(154.80,108.34) --
+	(157.64, 96.87) --
+	(160.48,104.75) --
+	(163.32,125.56) --
+	(166.16,125.60) --
+	(169.00,118.11) --
+	(171.84,131.67) --
+	(174.68,119.66) --
+	(177.52,113.38) --
+	(180.36,111.62) --
+	(183.20,110.39) --
+	(186.04,120.28) --
+	(188.88,121.72) --
+	(191.72,110.88) --
+	(194.56,104.55) --
+	(197.41,102.32) --
+	(200.25,103.20) --
+	(203.09,118.38) --
+	(205.93,116.19) --
+	(208.77,107.70) --
+	(211.61,125.73) --
+	(214.45,113.93) --
+	(217.29,116.50) --
+	(220.13,121.22) --
+	(222.97,122.01) --
+	(225.81,116.15) --
+	(228.65,123.94) --
+	(231.49,134.95) --
+	(234.33,117.09) --
+	(237.17,134.93) --
+	(240.01,108.75) --
+	(242.85,107.21) --
+	(245.69,114.25) --
+	(248.53,114.47) --
+	(251.37,132.28) --
+	(254.21,105.40) --
+	(257.05,101.28) --
+	(259.89,124.08) --
+	(262.73,117.25) --
+	(265.57,105.89) --
+	(268.42,118.56) --
+	(271.26,116.26) --
+	(274.10,124.57) --
+	(276.94,115.15) --
+	(279.78,114.21) --
+	(282.62,117.93) --
+	(285.46,120.53) --
+	(288.30,120.78) --
+	(291.14, 93.84) --
+	(293.98,104.20) --
+	(296.82,121.77) --
+	(299.66,120.74) --
+	(302.50,125.57) --
+	(305.34, 98.65) --
+	(308.18,118.24) --
+	(311.02,113.92) --
+	(313.86,111.47) --
+	(316.70,114.87) --
+	(319.54,111.66) --
+	(322.38,122.13) --
+	(325.22,120.92) --
+	(328.06,119.13) --
+	(330.90,107.34) --
+	(333.74,110.31) --
+	(336.59,102.29) --
+	(339.43,122.78) --
+	(342.27,118.97) --
+	(345.11,127.18) --
+	(347.95,115.75) --
+	(350.79, 98.94) --
+	(353.63,103.64) --
+	(356.47,119.92) --
+	(359.31,111.38) --
+	(362.15,117.39) --
+	(364.99, 99.61) --
+	(367.83,127.65) --
+	(370.67,117.72) --
+	(373.51,116.14) --
+	(376.35,118.69) --
+	(379.19,125.02) --
+	(382.03,126.74) --
+	(384.87,128.03) --
+	(387.71,108.51) --
+	(390.55,116.45) --
+	(393.39,116.57) --
+	(396.23,110.71) --
+	(399.07,105.66) --
+	(401.91,101.83) --
+	(404.75,112.58) --
+	(407.60,119.09) --
+	(410.44,116.04) --
+	(413.28,121.05) --
+	(416.12,111.62) --
+	(418.96,110.49) --
+	(421.80,110.21) --
+	(424.64,109.63) --
+	(427.48,182.07);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 67.43) -- ( 48.00,190.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 64.28) -- ( 48.00,201.67);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 67.43) -- ( 42.00, 67.43);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 64.28) -- ( 42.00, 64.28);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,128.99) -- ( 42.00,128.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,110.08) -- ( 42.00,110.08);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,190.54) -- ( 42.00,190.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,155.88) -- ( 42.00,155.88);
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 67.43) {-5};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,201.67) -- ( 42.00,201.67);
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,128.99) {0};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 64.28) {-5};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,190.54) {5};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,110.08) {0};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,155.88) {5};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,201.67) {10};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,137.81) --
-	( 75.27,136.65) --
-	( 78.11,143.49) --
-	( 80.95,137.43) --
-	( 83.79,130.64) --
-	( 86.63,140.10) --
-	( 89.47,133.95) --
-	( 92.31,138.95) --
-	( 95.15,138.13) --
-	( 97.99,134.38) --
-	(100.83,138.70) --
-	(103.67,136.65) --
-	(106.51,142.33) --
-	(109.35,140.08) --
-	(112.19,140.76) --
-	(115.03,135.30) --
-	(117.87,131.53) --
-	(120.71,134.31) --
-	(123.55,136.31) --
-	(126.40,138.07) --
-	(129.24,138.68) --
-	(132.08,133.35) --
-	(134.92,135.06) --
-	(137.76,137.42) --
-	(140.60,132.08) --
-	(143.44,134.84) --
-	(146.28,141.15) --
-	(149.12,136.50) --
-	(151.96,137.75) --
-	(154.80,136.26) --
-	(157.64,132.36) --
-	(160.48,135.15) --
-	(163.32,133.44) --
-	(166.16,135.02) --
-	(169.00,137.46) --
-	(171.84,137.44) --
-	(174.68,138.85) --
-	(177.52,137.64) --
-	(180.36,136.64) --
-	(183.20,136.98) --
-	(186.04,135.19) --
-	(188.88,135.00) --
-	(191.72,137.46) --
-	(194.56,133.62) --
-	(197.41,136.58) --
-	(200.25,133.35) --
-	(203.09,137.85) --
-	(205.93,138.76) --
-	(208.77,132.56) --
-	(211.61,136.25) --
-	(214.45,135.48) --
-	(217.29,136.00) --
-	(220.13,134.15) --
-	(222.97,138.92) --
-	(225.81,140.34) --
-	(228.65,137.72) --
-	(231.49,138.74) --
-	(234.33,140.75) --
-	(237.17,137.08) --
-	(240.01,139.13) --
-	(242.85,132.23) --
-	(245.69,135.17) --
-	(248.53,135.31) --
-	(251.37,134.56) --
-	(254.21,137.20) --
-	(257.05,135.96) --
-	(259.89,133.73) --
-	(262.73,140.13) --
-	(265.57,133.33) --
-	(268.42,134.06) --
-	(271.26,136.71) --
-	(274.10,138.64) --
-	(276.94,143.32) --
-	(279.78,136.35) --
-	(282.62,136.03) --
-	(285.46,138.94) --
-	(288.30,139.04) --
-	(291.14,138.48) --
-	(293.98,133.60) --
-	(296.82,137.06) --
-	(299.66,135.32) --
-	(302.50,136.59) --
-	(305.34,139.19) --
-	(308.18,132.33) --
-	(311.02,130.50) --
-	(313.86,133.96) --
-	(316.70,137.48) --
-	(319.54,136.37) --
-	(322.38,135.54) --
-	(325.22,141.95) --
-	(328.06,137.28) --
-	(330.90,136.24) --
-	(333.74,135.82) --
-	(336.59,129.34) --
-	(339.43,131.63) --
-	(342.27,137.63) --
-	(345.11,139.18) --
-	(347.95,141.59) --
-	(350.79,135.78) --
-	(353.63,132.71) --
-	(356.47,132.87) --
-	(359.31,137.75) --
-	(362.15,135.79) --
-	(364.99,140.06) --
-	(367.83,133.34) --
-	(370.67,138.30) --
-	(373.51,137.87) --
-	(376.35,138.13) --
-	(379.19,134.63) --
-	(382.03,136.24) --
-	(384.87,143.24) --
-	(387.71,134.81) --
-	(390.55,133.80) --
-	(393.39,135.75) --
-	(396.23,137.51) --
-	(399.07,135.80) --
-	(401.91,130.45) --
-	(404.75,132.80) --
-	(407.60,136.90) --
-	(410.44,137.73) --
-	(413.28,138.35) --
-	(416.12,138.71) --
-	(418.96,134.35) --
-	(421.80,137.02) --
-	(424.64,137.94) --
-	(427.48,134.70);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,116.65) --
+	( 75.27,115.78) --
+	( 78.11,120.87) --
+	( 80.95,116.36) --
+	( 83.79,111.31) --
+	( 86.63,118.35) --
+	( 89.47,113.78) --
+	( 92.31,117.49) --
+	( 95.15,116.88) --
+	( 97.99,114.09) --
+	(100.83,117.31) --
+	(103.67,115.79) --
+	(106.51,120.01) --
+	(109.35,118.34) --
+	(112.19,118.84) --
+	(115.03,114.78) --
+	(117.87,111.97) --
+	(120.71,114.04) --
+	(123.55,115.53) --
+	(126.40,116.84) --
+	(129.24,117.29) --
+	(132.08,113.33) --
+	(134.92,114.60) --
+	(137.76,116.36) --
+	(140.60,112.38) --
+	(143.44,114.43) --
+	(146.28,119.13) --
+	(149.12,115.67) --
+	(151.96,116.60) --
+	(154.80,115.49) --
+	(157.64,112.59) --
+	(160.48,114.67) --
+	(163.32,113.39) --
+	(166.16,114.57) --
+	(169.00,116.38) --
+	(171.84,116.37) --
+	(174.68,117.42) --
+	(177.52,116.52) --
+	(180.36,115.78) --
+	(183.20,116.03) --
+	(186.04,114.70) --
+	(188.88,114.55) --
+	(191.72,116.39) --
+	(194.56,113.53) --
+	(197.41,115.73) --
+	(200.25,113.33) --
+	(203.09,116.67) --
+	(205.93,117.35) --
+	(208.77,112.74) --
+	(211.61,115.48) --
+	(214.45,114.91) --
+	(217.29,115.30) --
+	(220.13,113.92) --
+	(222.97,117.48) --
+	(225.81,118.53) --
+	(228.65,116.58) --
+	(231.49,117.34) --
+	(234.33,118.84) --
+	(237.17,116.11) --
+	(240.01,117.63) --
+	(242.85,112.50) --
+	(245.69,114.69) --
+	(248.53,114.79) --
+	(251.37,114.23) --
+	(254.21,116.19) --
+	(257.05,115.27) --
+	(259.89,113.61) --
+	(262.73,118.37) --
+	(265.57,113.31) --
+	(268.42,113.85) --
+	(271.26,115.83) --
+	(274.10,117.26) --
+	(276.94,120.74) --
+	(279.78,115.56) --
+	(282.62,115.32) --
+	(285.46,117.49) --
+	(288.30,117.56) --
+	(291.14,117.14) --
+	(293.98,113.51) --
+	(296.82,116.09) --
+	(299.66,114.80) --
+	(302.50,115.74) --
+	(305.34,117.67) --
+	(308.18,112.57) --
+	(311.02,111.21) --
+	(313.86,113.78) --
+	(316.70,116.40) --
+	(319.54,115.57) --
+	(322.38,114.95) --
+	(325.22,119.73) --
+	(328.06,116.25) --
+	(330.90,115.48) --
+	(333.74,115.16) --
+	(336.59,110.34) --
+	(339.43,112.05) --
+	(342.27,116.51) --
+	(345.11,117.67) --
+	(347.95,119.46) --
+	(350.79,115.14) --
+	(353.63,112.85) --
+	(356.47,112.97) --
+	(359.31,116.60) --
+	(362.15,115.14) --
+	(364.99,118.32) --
+	(367.83,113.32) --
+	(370.67,117.01) --
+	(373.51,116.69) --
+	(376.35,116.89) --
+	(379.19,114.28) --
+	(382.03,115.47) --
+	(384.87,120.69) --
+	(387.71,114.41) --
+	(390.55,113.66) --
+	(393.39,115.12) --
+	(396.23,116.42) --
+	(399.07,115.15) --
+	(401.91,111.17) --
+	(404.75,112.92) --
+	(407.60,115.97) --
+	(410.44,116.59) --
+	(413.28,117.05) --
+	(416.12,117.32) --
+	(418.96,114.07) --
+	(421.80,116.06) --
+	(424.64,116.75) --
+	(427.48,114.33);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,137.81) --
-	( 75.27,136.65) --
-	( 78.11,143.49) --
-	( 80.95,137.43) --
-	( 83.79,130.64) --
-	( 86.63,140.10) --
-	( 89.47,133.95) --
-	( 92.31,138.95) --
-	( 95.15,138.13) --
-	( 97.99,134.38) --
-	(100.83,138.70) --
-	(103.67,136.65) --
-	(106.51,142.33) --
-	(109.35,140.08) --
-	(112.19,140.76) --
-	(115.03,135.30) --
-	(117.87,131.53) --
-	(120.71,134.31) --
-	(123.55,136.31) --
-	(126.40,138.07) --
-	(129.24,138.68) --
-	(132.08,133.35) --
-	(134.92,135.06) --
-	(137.76,137.42) --
-	(140.60,132.08) --
-	(143.44,134.84) --
-	(146.28,141.15) --
-	(149.12,136.50) --
-	(151.96,137.75) --
-	(154.80,136.26) --
-	(157.64,132.36) --
-	(160.48,135.15) --
-	(163.32,133.44) --
-	(166.16,135.02) --
-	(169.00,137.46) --
-	(171.84,137.44) --
-	(174.68,138.85) --
-	(177.52,137.64) --
-	(180.36,136.64) --
-	(183.20,136.98) --
-	(186.04,135.19) --
-	(188.88,135.00) --
-	(191.72,137.46) --
-	(194.56,133.62) --
-	(197.41,136.58) --
-	(200.25,133.35) --
-	(203.09,137.85) --
-	(205.93,138.76) --
-	(208.77,132.56) --
-	(211.61,136.25) --
-	(214.45,135.48) --
-	(217.29,136.00) --
-	(220.13,134.15) --
-	(222.97,138.92) --
-	(225.81,140.34) --
-	(228.65,137.72) --
-	(231.49,138.74) --
-	(234.33,140.75) --
-	(237.17,137.08) --
-	(240.01,139.13) --
-	(242.85,132.23) --
-	(245.69,135.17) --
-	(248.53,135.31) --
-	(251.37,134.56) --
-	(254.21,137.20) --
-	(257.05,135.96) --
-	(259.89,133.73) --
-	(262.73,140.13) --
-	(265.57,133.33) --
-	(268.42,134.06) --
-	(271.26,136.71) --
-	(274.10,138.64) --
-	(276.94,143.32) --
-	(279.78,136.35) --
-	(282.62,136.03) --
-	(285.46,138.94) --
-	(288.30,139.04) --
-	(291.14,138.48) --
-	(293.98,133.60) --
-	(296.82,137.06) --
-	(299.66,135.32) --
-	(302.50,136.59) --
-	(305.34,139.19) --
-	(308.18,132.33) --
-	(311.02,130.50) --
-	(313.86,133.96) --
-	(316.70,137.48) --
-	(319.54,136.37) --
-	(322.38,135.54) --
-	(325.22,141.95) --
-	(328.06,137.28) --
-	(330.90,136.24) --
-	(333.74,135.82) --
-	(336.59,129.34) --
-	(339.43,131.63) --
-	(342.27,137.63) --
-	(345.11,139.18) --
-	(347.95,141.59) --
-	(350.79,135.78) --
-	(353.63,132.71) --
-	(356.47,132.87) --
-	(359.31,137.75) --
-	(362.15,135.79) --
-	(364.99,140.06) --
-	(367.83,133.34) --
-	(370.67,138.30) --
-	(373.51,137.87) --
-	(376.35,138.13) --
-	(379.19,134.63) --
-	(382.03,136.24) --
-	(384.87,143.24) --
-	(387.71,134.81) --
-	(390.55,133.80) --
-	(393.39,135.75) --
-	(396.23,137.51) --
-	(399.07,135.80) --
-	(401.91,130.45) --
-	(404.75,132.80) --
-	(407.60,136.90) --
-	(410.44,137.73) --
-	(413.28,138.35) --
-	(416.12,138.71) --
-	(418.96,134.35) --
-	(421.80,137.02) --
-	(424.64,137.94) --
-	(427.48,198.96);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,116.65) --
+	( 75.27,115.78) --
+	( 78.11,120.87) --
+	( 80.95,116.36) --
+	( 83.79,111.31) --
+	( 86.63,118.35) --
+	( 89.47,113.78) --
+	( 92.31,117.49) --
+	( 95.15,116.88) --
+	( 97.99,114.09) --
+	(100.83,117.31) --
+	(103.67,115.79) --
+	(106.51,120.01) --
+	(109.35,118.34) --
+	(112.19,118.84) --
+	(115.03,114.78) --
+	(117.87,111.97) --
+	(120.71,114.04) --
+	(123.55,115.53) --
+	(126.40,116.84) --
+	(129.24,117.29) --
+	(132.08,113.33) --
+	(134.92,114.60) --
+	(137.76,116.36) --
+	(140.60,112.38) --
+	(143.44,114.43) --
+	(146.28,119.13) --
+	(149.12,115.67) --
+	(151.96,116.60) --
+	(154.80,115.49) --
+	(157.64,112.59) --
+	(160.48,114.67) --
+	(163.32,113.39) --
+	(166.16,114.57) --
+	(169.00,116.38) --
+	(171.84,116.37) --
+	(174.68,117.42) --
+	(177.52,116.52) --
+	(180.36,115.78) --
+	(183.20,116.03) --
+	(186.04,114.70) --
+	(188.88,114.55) --
+	(191.72,116.39) --
+	(194.56,113.53) --
+	(197.41,115.73) --
+	(200.25,113.33) --
+	(203.09,116.67) --
+	(205.93,117.35) --
+	(208.77,112.74) --
+	(211.61,115.48) --
+	(214.45,114.91) --
+	(217.29,115.30) --
+	(220.13,113.92) --
+	(222.97,117.48) --
+	(225.81,118.53) --
+	(228.65,116.58) --
+	(231.49,117.34) --
+	(234.33,118.84) --
+	(237.17,116.11) --
+	(240.01,117.63) --
+	(242.85,112.50) --
+	(245.69,114.69) --
+	(248.53,114.79) --
+	(251.37,114.23) --
+	(254.21,116.19) --
+	(257.05,115.27) --
+	(259.89,113.61) --
+	(262.73,118.37) --
+	(265.57,113.31) --
+	(268.42,113.85) --
+	(271.26,115.83) --
+	(274.10,117.26) --
+	(276.94,120.74) --
+	(279.78,115.56) --
+	(282.62,115.32) --
+	(285.46,117.49) --
+	(288.30,117.56) --
+	(291.14,117.14) --
+	(293.98,113.51) --
+	(296.82,116.09) --
+	(299.66,114.80) --
+	(302.50,115.74) --
+	(305.34,117.67) --
+	(308.18,112.57) --
+	(311.02,111.21) --
+	(313.86,113.78) --
+	(316.70,116.40) --
+	(319.54,115.57) --
+	(322.38,114.95) --
+	(325.22,119.73) --
+	(328.06,116.25) --
+	(330.90,115.48) --
+	(333.74,115.16) --
+	(336.59,110.34) --
+	(339.43,112.05) --
+	(342.27,116.51) --
+	(345.11,117.67) --
+	(347.95,119.46) --
+	(350.79,115.14) --
+	(353.63,112.85) --
+	(356.47,112.97) --
+	(359.31,116.60) --
+	(362.15,115.14) --
+	(364.99,118.32) --
+	(367.83,113.32) --
+	(370.67,117.01) --
+	(373.51,116.69) --
+	(376.35,116.89) --
+	(379.19,114.28) --
+	(382.03,115.47) --
+	(384.87,120.69) --
+	(387.71,114.41) --
+	(390.55,113.66) --
+	(393.39,115.12) --
+	(396.23,116.42) --
+	(399.07,115.15) --
+	(401.91,111.17) --
+	(404.75,112.92) --
+	(407.60,115.97) --
+	(410.44,116.59) --
+	(413.28,117.05) --
+	(416.12,117.32) --
+	(418.96,114.07) --
+	(421.80,116.06) --
+	(424.64,116.75) --
+	(427.48,207.97);
 \definecolor{drawColor}{RGB}{0,191,255}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,189.66) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,212.78) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,218.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,176.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,191.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.49) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.83) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,181.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,194.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,230.23) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.56) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,213.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,213.37) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,187.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,199.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,187.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.49) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,211.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,166.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,184.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,165.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,179.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,169.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,186.22) circle (  2.25);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,213.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.56) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,163.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,181.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,214.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,188.70) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,200.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.75) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,210.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,216.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,176.55) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,191.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,179.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.23) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.75) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,178.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,192.70) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,211.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,220.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.21) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,158.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,178.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.83) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.68,134.70) -- (441.68,198.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.00,114.33) -- (436.00,207.97);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.15,139.08) --
-	(441.68,134.70) --
-	(444.21,139.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.47,118.72) --
+	(436.00,114.33) --
+	(438.53,118.72);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.21,194.58) --
-	(441.68,198.96) --
-	(439.15,194.58);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.53,203.59) --
+	(436.00,207.97) --
+	(433.47,203.59);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (487.13,158.65) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$10.22};
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.16,112.36) -- (433.16,164.19);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.40,114.33) -- (427.48,114.33);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.63,116.74) --
-	(433.16,112.36) --
-	(435.69,116.74);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.86,116.86) --
+	(427.48,114.33) --
+	(431.86,111.81);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.69,159.81) --
-	(433.16,164.19) --
-	(430.63,159.81);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (498.49,111.84) {$\hat{y}^{1}_{T_1^*+1} = 0.46$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 70.86) {shock time point $T^*_1 + 1$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,179.57) {$y_{T_1^*+1}$};
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81,164.33) {$\displaystyle \hat{\alpha} = \frac{1}{n}\sum_{i=1}^{n} \hat{\alpha}_i= \;$5.22};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,205.47) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,207.97) -- (427.48,207.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,205.44) --
+	(427.48,207.97) --
+	(423.10,210.50);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (470.08,122.17) {$\alpha = 4.21$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,182.07) -- (427.48,182.07);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 77.15) {shock time point $T^*_1 + 1$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,179.54) --
+	(427.48,182.07) --
+	(423.10,184.60);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,161.69) {$y_{T_1^*+1}$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,207.97) rectangle (212.08,171.97);
+\definecolor{drawColor}{RGB}{255,106,106}
+
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,195.97) -- ( 93.75,195.97);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,196.46) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,198.96) -- (427.48,198.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,196.43) --
-	(427.48,198.96) --
-	(423.10,201.49);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,183.97) -- ( 93.75,183.97);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,164.19) -- (427.48,164.19);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,192.53) {$\hat{y}_{t}^{1}$ without shock effects};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,161.66) --
-	(427.48,164.19) --
-	(423.10,166.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,198.96) rectangle (212.08,162.96);
-\definecolor{drawColor}{RGB}{255,106,106}
-
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,186.96) -- ( 93.75,186.96);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,174.96) -- ( 93.75,174.96);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,183.51) {$\hat{y}_{t}^{1}$ without shock effects};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,171.51) {$\hat{y}_{t}^{2}$ with shock effects};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,180.53) {$\hat{y}_{t}^{2}$ with shock effects};
 \end{scope}

### 2020-08-09 manuscript/manuscript.tex
addition of simulation results

@@
 However, there are key differences between our framework and SCM.
-We assume that the disparate time series are independent from the time series under study before the timing of the shock {\bf Jilei, can weaken this assumption?}.
-We also assume that the shock effects for each disparate time series are independent realizations from some unknown distribution.
+We assume that the disparate time series are independent from the time series under study before the timing of the shock.
+We also assume that the shock effects for each disparate time series are independent realizations from some unknown distribution with existing first and second moments.
 
@@
 The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-Our auto regressive model will consider present day and lagged covariates to better motivate similarity weighting.
+Our auto regressive model will consider present day covariates to better motivate similarity weighting.
 The considered adjustment strategies all target the mean of the shock effect distribution.
@@
   \begin{center}
-    \subfloat[A comparison between forecast without considering shock effects and the one uses simple averaging given $n=40$ disparate time series, and that the shock time is at $T_1^* +1=126$.
-The magenta dots represent least square estimate $\hat{\alpha}_i$ from disparate time series.
-The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=5.22$.
-It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.]{\includegraphics[height = 7cm]{comp.pdf}}\\
-     \subfloat[Histogram for $\hat{\alpha}_i$ for $i = 2, \ldots, n+1$]{\includegraphics[height = 7cm]{alphahist.pdf}}
+    \subfloat{\includegraphics[height = 7cm]{comp.pdf}}\\
+     \subfloat{\includegraphics[height = 7cm]{alphahist.pdf}}
   \end{center}
      \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 4.21$.
-(a) presents the comparison of the prediction without adjustment and one with.
-(b) shows the histogram for the $\alpha_i$s used in estimating shock $\alpha_1$.}\label{figure1}
+(a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given $n=40$ disparate time series.
+(b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.
+The magenta dots represent $\hat{\alpha}_i$ from disparate time series.
+The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=10.22$.
+It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
 \end{figure}
@@
 \end{align}
- Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
+Note that (\ref{SCM}) tries to find $\mbf{W}^*$ such that $\mbf{x}_{1, T_1^*+1}$ is a convex combination of $\mbf{x}_{i, T_i^*+1}$ for $i = 2, \ldots, n+1$ with weights $\mbf{W}^*$.
+Therefore, $\mbf{W}^*$ should exist as long as $\mbf{X}_1$ falls in the convex hull of
  \begin{align*}
@@
  \end{align*}
-{\bf Jilei, can you add clarity to this point? It is hard to see why this works on the first viewing.}
 %It is a reasonable assumption that the pool of time series that we are considering 
@@
 We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
-We consider $p=13$ and $\mu_{\alpha}=2$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.
+We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}.
 Parameter setup of our simulations is detailed as follows: the $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
 We sampled $T_i$'s independently from  $\text{Gamma}(15, 10)$ that are further rounded to integers, where the minimum allowable value of $T_i$ is fixed to be 90.
-We will randomly draw $T_i^*$ from $\{2p + 4, \ldots, T_i-1\}$.
+We will randomly draw $T_i^*$ from $\{p + 4, \ldots, T_i-1\}$.
 The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
@@
 Additionally, we generated the covariates from $\text{Gamma}(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
-Last, we set $\gamma_i, \delta_i\simiid  \normal{1}{0.5}$ and $\theta_i, \beta_i \sim \normal{0}{1}$.
+Last, we set $\gamma_i, \delta_i\simiid  \normal{1}{0.5}$ and $\theta_i \sim \normal{0}{1}$.
 We will consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
@@
 In the first simulation setup, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$.
-Note that $\E{\E{\alpha_1}}=54$, where the last expectation is operated under the density of the covariates.
+Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates.
 In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.
@@
   \hline
- \multirow{5}{*}{5}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.96 (0.01) & 0.92 (0.02) & 65.47 (4.77) & 19.92 (3.57) & 21.86 (3.99) & 20.27 (3.62) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.9 (0.02) & 0.92 (0.02) & 0.9 (0.02) & 65.67 (4.9) & 20.66 (3.74) & 22.92 (4.2) & 21.1 (3.75) \\ 
-    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.8 (0.02) & 0.81 (0.02) & 0.8 (0.03) & 66.29 (5.83) & 27.98 (4.21) & 30.3 (4.87) & 28.3 (4.18) \\ 
-    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.87 (0.06) & 0.55 (0.05) & 0.57 (0.04) & 0.55 (0.05) & 70.59 (7.46) & 43.1 (6.19) & 46.31 (6.8) & 43.07 (6.16) \\ 
-    & 100  & 0.47 (0.09) & 0.73 (0.08) & 0.47 (0.09) & 0.48 (0.04) & 0.48 (0.04) & 0.46 (0.04) & 89.82 (10.49) & 76.74 (11.42) & 79.78 (12.26) & 76.69 (11.33) \\[.3cm]  
-   \multirow{5}{*}{10}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.95 (0.02) & 0.95 (0.02) & 55.66 (4.28) & 16.36 (2.48) & 17.51 (2.41) & 16.6 (2.45) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.03) & 0.92 (0.02) & 55.91 (4.71) & 18.28 (2.85) & 19.38 (2.88) & 18.44 (2.83) \\ 
-    & 25  & 0.9 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.77 (0.04) & 0.79 (0.04) & 0.75 (0.04) & 59.43 (6.1) & 29.01 (4.24) & 32.1 (4.3) & 28.84 (4.26) \\ 
-    & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.55 (0.04) & 0.64 (0.04) & 0.55 (0.04) & 69.34 (9.45) & 52.52 (6.75) & 58.05 (7.28) & 52.28 (6.76) \\ 
-    & 100  & 0.63 (0.09) & 0.7 (0.09) & 0.63 (0.09) & 0.53 (0.04) & 0.53 (0.05) & 0.51 (0.04) & 104.19 (15.88) & 99.93 (12.83) & 113.77 (13.42) & 99.57 (12.81) \\[.3cm]  
-   \multirow{5}{*}{15}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.93 (0.02) & 0.92 (0.02) & 51.78 (2.74) & 12.66 (2.48) & 13.89 (2.48) & 12.64 (2.49) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.92 (0.02) & 51.82 (3.04) & 13.93 (2.52) & 16 (2.63) & 14.05 (2.53) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.83 (0.03) & 0.83 (0.03) & 51.94 (4.56) & 21.27 (2.93) & 24.49 (3.69) & 21.75 (2.92) \\ 
-    & 50  & 0.9 (0.06) & 0.93 (0.05) & 0.9 (0.06) & 0.71 (0.03) & 0.67 (0.04) & 0.69 (0.04) & 55.22 (7.06) & 35.85 (4.63) & 42.72 (5.93) & 36.41 (4.71) \\ 
-    & 100  & 0.7 (0.09) & 0.73 (0.08) & 0.7 (0.09) & 0.54 (0.05) & 0.61 (0.04) & 0.54 (0.05) & 76.44 (10.75) & 67.79 (8.77) & 79.49 (11.44) & 68.57 (8.96) \\[.3cm]  
-   \multirow{5}{*}{25}  & 5  & 1 (0) & 1 (0) & 1 (0) & 0.9 (0.03) & 0.91 (0.02) & 0.9 (0.03) & 62.23 (6.88) & 21.29 (5.9) & 19.29 (5.88) & 21.34 (5.93) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.02) & 0.87 (0.03) & 61.28 (7.09) & 22.96 (5.91) & 20.81 (5.89) & 23.02 (5.94) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.73 (0.03) & 0.74 (0.04) & 0.73 (0.03) & 61.9 (7.5) & 30.04 (6.46) & 28.76 (6.46) & 30.17 (6.48) \\ 
-    & 50  & 0.83 (0.07) & 0.87 (0.06) & 0.83 (0.07) & 0.55 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 67.46 (9.23) & 45.5 (8.55) & 47.38 (8.62) & 45.67 (8.58) \\ 
-    & 100  & 0.77 (0.08) & 0.73 (0.08) & 0.77 (0.08) & 0.48 (0.05) & 0.49 (0.04) & 0.49 (0.05) & 91.08 (14.54) & 81.72 (14.24) & 85.72 (15.39) & 82.3 (14.24) \\ 
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.91 (0.02) & 0.9 (0.03) & 53.23 (4.1) & 15.88 (2.1) & 16.78 (2.37) & 15.82 (2.07) \\ 
+    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.89 (0.03) & 0.9 (0.03) & 0.89 (0.03) & 53.01 (4.47) & 17.83 (2.38) & 19.56 (2.56) & 17.61 (2.36) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.74 (0.04) & 0.81 (0.04) & 0.75 (0.04) & 53.38 (5.92) & 26.44 (3.8) & 29.06 (4) & 26.11 (3.75) \\ 
+    & 50  & 0.83 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.64 (0.05) & 0.59 (0.05) & 61.68 (7.73) & 46 (6.31) & 47.3 (7.14) & 45.25 (6.32) \\ 
+    & 100  & 0.7 (0.09) & 0.87 (0.06) & 0.7 (0.09) & 0.53 (0.05) & 0.54 (0.05) & 0.53 (0.06) & 85.68 (12.95) & 87.25 (11.86) & 87.07 (13.63) & 85.65 (12.02)\\[.3cm] 
+   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
+    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
+    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
+   \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 51.11 (3.05) & 14.94 (2.36) & 14.09 (2.37) & 15.09 (2.35) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.91 (0.02) & 52.34 (3.19) & 15.64 (2.73) & 15.29 (2.74) & 15.89 (2.68) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.73 (0.04) & 0.76 (0.04) & 0.73 (0.04) & 56.03 (5.2) & 25.49 (3.85) & 27.38 (3.87) & 25.27 (3.84) \\ 
+    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.56 (0.04) & 0.6 (0.04) & 0.57 (0.04) & 71.37 (7.76) & 47.25 (6.42) & 52.06 (6.57) & 46.41 (6.43) \\ 
+    & 100  & 0.63 (0.09) & 0.67 (0.09) & 0.63 (0.09) & 0.52 (0.04) & 0.42 (0.04) & 0.53 (0.04) & 111.91 (13.83) & 92.95 (12.34) & 103.13 (12.74) & 91.07 (12.37) \\[.3cm] 
+   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.94 (0.02) & 0.93 (0.02) & 47.79 (2.93) & 14.83 (1.72) & 14.83 (2.04) & 14.76 (1.72) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.91 (0.02) & 0.89 (0.03) & 47.93 (3.25) & 16.55 (1.89) & 17.55 (2.12) & 16.53 (1.88) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.82 (0.03) & 0.83 (0.03) & 49.78 (5.01) & 26.42 (3.38) & 29.11 (3.4) & 26.45 (3.35) \\ 
+    & 50  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.64 (0.05) & 0.63 (0.05) & 0.64 (0.05) & 62.64 (7.4) & 48.84 (6.4) & 52.67 (6.28) & 48.8 (6.35) \\ 
+    & 100  & 0.83 (0.07) & 0.8 (0.07) & 0.83 (0.07) & 0.57 (0.05) & 0.59 (0.05) & 0.59 (0.05) & 103.37 (12.23) & 97.81 (12.52) & 102.4 (12.49) & 97.63 (12.45) \\
 \end{tabular}}
@@
 
-Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down.
+Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down, though they  follow similar patterns.
 Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$.
@@
 Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of correctness between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
-For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.83 \times 0.55 = 0.457$ from Table \ref{table1}.
+For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.83 \times 0.59 = 0.490$ from Table \ref{table1}.
 In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.
@@
   \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.97 (0.01) & 0.97 (0.01) & 0.97 (0.01) & 49.95 (2.46) & 12.36 (1.71) & 11.71 (1.55) & 12.13 (1.71) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.92 (0.02) & 0.92 (0.02) & 51.25 (2.88) & 13.14 (1.88) & 14.55 (1.7) & 12.84 (1.87) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 1 (0) & 0.81 (0.03) & 0.84 (0.03) & 0.81 (0.03) & 54.85 (4.6) & 19.32 (3.07) & 20.87 (3.45) & 19.75 (3.13) \\ 
-  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.59 (0.04) & 0.62 (0.03) & 0.58 (0.04) & 60.57 (8.15) & 43.17 (5.49) & 47.62 (5.88) & 43.59 (5.63) \\ 
-  & 100  & 0.67 (0.09) & 0.63 (0.09) & 0.67 (0.09) & 0.45 (0.04) & 0.49 (0.04) & 0.49 (0.04) & 71.15 (10.52) & 72.15 (9.61) & 80.17 (9.52) & 71.7 (9.57) \\[.3cm] 
- \multirow{5}{*}{10} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.91 (0.02) & 0.91 (0.02) & 0.91 (0.02) & 48.65 (3.85) & 18.3 (2.4) & 19.78 (2.31) & 18.64 (2.39) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.9 (0.02) & 0.93 (0.02) & 0.91 (0.02) & 52.46 (4.4) & 16.52 (3.06) & 15.86 (3.18) & 16.46 (3.06) \\ 
-  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.79 (0.04) & 0.81 (0.03) & 0.8 (0.04) & 64.81 (4.93) & 24.85 (3.5) & 24.78 (3.7) & 24.94 (3.58) \\ 
-  & 50  & 0.87 (0.06) & 0.9 (0.06) & 0.87 (0.06) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 65.69 (6.74) & 40.16 (5.47) & 37.29 (5.35) & 39.44 (5.49) \\ 
-  & 100  & 0.63 (0.09) & 0.67 (0.09) & 0.63 (0.09) & 0.43 (0.04) & 0.47 (0.03) & 0.43 (0.04) & 67.98 (10.7) & 65.69 (8.35) & 78.45 (9.42) & 67.75 (8.58) \\[.3cm] 
- \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.73 (0.03) & 0.74 (0.03) & 0.73 (0.03) & 58.32 (7.69) & 39.37 (7.46) & 39.16 (7.89) & 39.6 (7.47) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.71 (0.04) & 0.73 (0.05) & 0.73 (0.04) & 65.93 (5.72) & 33.34 (5.91) & 34.04 (5.49) & 33.05 (5.89) \\ 
- & 25  & 0.9 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.67 (0.04) & 0.68 (0.03) & 0.66 (0.04) & 56.05 (7.5) & 39.49 (5.25) & 35.65 (4.98) & 39.73 (5.26) \\ 
-  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.59 (0.04) & 0.62 (0.04) & 0.59 (0.04) & 60.85 (7.93) & 46.55 (6.83) & 47.97 (7.4) & 47.23 (6.73) \\ 
-  & 100  & 0.67 (0.09) & 0.7 (0.09) & 0.63 (0.09) & 0.53 (0.05) & 0.53 (0.04) & 0.53 (0.05) & 95.21 (12.76) & 98.68 (11.57) & 99.87 (13.28) & 98.77 (11.61) \\[.3cm] 
-   \multirow{5}{*}{50} & 5  & 0.77 (0.08) & 0.7 (0.09) & 0.77 (0.08) & 0.6 (0.04) & 0.61 (0.03) & 0.61 (0.04) & 71.05 (8.49) & 52.9 (8.7) & 57.45 (9.57) & 53.05 (8.59) \\ 
-    & 10  & 0.63 (0.09) & 0.63 (0.09) & 0.63 (0.09) & 0.57 (0.04) & 0.57 (0.05) & 0.57 (0.04) & 68.23 (7.38) & 44.22 (5.95) & 55.53 (6.2) & 44.63 (5.86) \\ 
-  & 25  & 0.73 (0.08) & 0.67 (0.09) & 0.77 (0.08) & 0.55 (0.04) & 0.55 (0.04) & 0.57 (0.04) & 69.78 (10.51) & 63.97 (9.49) & 68.82 (9.79) & 64.33 (9.47) \\ 
-  & 50  & 0.83 (0.07) & 0.8 (0.07) & 0.83 (0.07) & 0.55 (0.04) & 0.51 (0.05) & 0.55 (0.04) & 64.9 (11.37) & 66.61 (10.07) & 73.22 (10.92) & 67.06 (9.99) \\ 
-  & 100  & 0.47 (0.09) & 0.53 (0.09) & 0.47 (0.09) & 0.49 (0.04) & 0.51 (0.04) & 0.49 (0.04) & 92.78 (12) & 73.61 (11.81) & 78.33 (10.92) & 74.37 (11.63) \\[.3cm] 
- \multirow{5}{*}{100} & 5  & 0.5 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.49 (0.05) & 0.48 (0.04) & 0.47 (0.05) & 125.13 (15.27) & 104.01 (14.95) & 100.33 (13.71) & 105.4 (14.95) \\ 
-    & 10  & 0.4 (0.09) & 0.4 (0.09) & 0.37 (0.09) & 0.49 (0.03) & 0.51 (0.05) & 0.51 (0.04) & 106.46 (14.76) & 101.82 (14.64) & 110.6 (14.95) & 98.85 (14.69) \\ 
-  & 25  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.49 (0.04) & 0.48 (0.04) & 0.51 (0.04) & 142.91 (16.43) & 132.29 (18.34) & 146.26 (17.96) & 132.06 (18.25) \\ 
-  & 50  & 0.57 (0.09) & 0.57 (0.09) & 0.57 (0.09) & 0.5 (0.05) & 0.5 (0.05) & 0.49 (0.04) & 114.36 (15.46) & 93 (16.26) & 95.41 (15.89) & 91.92 (15.98) \\ 
-    & 100  & 0.33 (0.09) & 0.3 (0.09) & 0.3 (0.09) & 0.49 (0.05) & 0.49 (0.05) & 0.48 (0.05) & 150.5 (20.71) & 148.07 (17.57) & 151.26 (17.18) & 148.96 (17.71) \\ 
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.97 (0.01) & 0.95 (0.02) & 48.84 (3.4) & 15.72 (1.93) & 15.32 (1.94) & 15.72 (1.93) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.94 (0.02) & 0.92 (0.03) & 49.54 (3.73) & 17.07 (2.01) & 16.08 (2.16) & 17.12 (1.99) \\ 
+    & 25  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.77 (0.02) & 0.81 (0.03) & 0.77 (0.03) & 51.78 (5.22) & 24.78 (2.57) & 26.12 (2.49) & 24.62 (2.54) \\ 
+    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.61 (0.04) & 0.59 (0.05) & 58.62 (7.74) & 40.09 (4.7) & 47.09 (4.09) & 39.85 (4.58) \\ 
+    & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.73 (0.08) & 0.5 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 82.66 (12.19) & 72.83 (9.75) & 89.03 (9.15) & 72.31 (9.5) \\[.3cm] 
+   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
+    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
+    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
+   \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.04) & 0.76 (0.03) & 0.7 (0.04) & 50.09 (8.27) & 38.1 (5.75) & 37.98 (5.5) & 38.44 (5.76) \\ 
+    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.69 (0.04) & 0.74 (0.03) & 0.69 (0.04) & 50.82 (8.15) & 37.63 (5.61) & 36.33 (5.64) & 37.99 (5.61) \\ 
+    & 25  & 0.9 (0.06) & 0.9 (0.06) & 0.9 (0.06) & 0.62 (0.04) & 0.64 (0.04) & 0.61 (0.04) & 53.01 (8.22) & 38.78 (5.29) & 36.82 (5.76) & 38.88 (5.31) \\ 
+    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.53 (0.04) & 58.9 (9.12) & 46.77 (5.54) & 50.61 (5.71) & 46.6 (5.51) \\ 
+    & 100  & 0.7 (0.09) & 0.9 (0.06) & 0.67 (0.09) & 0.51 (0.03) & 0.56 (0.04) & 0.5 (0.03) & 79.64 (12.21) & 72.76 (8.79) & 89.48 (7.98) & 72.17 (8.59) \\[.3cm] 
+   \multirow{5}{*}{50} & 5  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.04) & 0.59 (0.04) & 71.22 (13) & 70.31 (10.4) & 72.3 (9.26) & 70.79 (10.45) \\ 
+    & 10  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.05) & 0.6 (0.05) & 70.85 (12.91) & 69.43 (10.22) & 70.65 (9.29) & 69.94 (10.26) \\ 
+    & 25  & 0.7 (0.09) & 0.73 (0.08) & 0.7 (0.09) & 0.54 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 70.32 (12.81) & 67.61 (9.86) & 67 (9.58) & 68.06 (9.89) \\ 
+    & 50  & 0.67 (0.09) & 0.7 (0.09) & 0.67 (0.09) & 0.51 (0.05) & 0.51 (0.04) & 0.51 (0.05) & 74.01 (12.66) & 68.69 (9.63) & 67.9 (10.21) & 68.91 (9.64) \\ 
+    & 100  & 0.5 (0.09) & 0.6 (0.09) & 0.47 (0.09) & 0.47 (0.05) & 0.49 (0.04) & 0.45 (0.05) & 92.71 (13.06) & 83.66 (10.79) & 94.53 (11.2) & 83.56 (10.63)\\[.3cm] 
+   \multirow{5}{*}{100} & 5  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.06) & 0.57 (0.05) & 0.49 (0.06) & 130.47 (22.59) & 135.16 (19.73) & 141.42 (16.98) & 136.3 (19.72) \\ 
+    & 10  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.05) & 0.53 (0.05) & 0.51 (0.06) & 129.49 (22.49) & 134.09 (19.52) & 139.69 (16.96) & 135.26 (19.51) \\ 
+    & 25  & 0.47 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.53 (0.06) & 0.57 (0.05) & 0.51 (0.06) & 127.17 (22.22) & 131.43 (18.97) & 134.47 (17.22) & 132.42 (18.99) \\ 
+    & 50  & 0.5 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.48 (0.06) & 0.56 (0.04) & 0.48 (0.05) & 125.72 (21.8) & 129.27 (18.16) & 129.59 (17.59) & 130.27 (18.15) \\ 
+    & 100  & 0.47 (0.09) & 0.47 (0.09) & 0.43 (0.09) & 0.43 (0.06) & 0.57 (0.04) & 0.47 (0.06) & 128.38 (21.86) & 130.05 (18.05) & 131.83 (19.08) & 130.33 (18.06) \\
 \end{tabular}}
@@
 
+Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented. See Table \ref{table3} and Table \ref{table4} for results. Comparing Table \ref{table1}
+ and Table \ref{table2} yields that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
+For other situations, $\mc{B}_u$  and $\mc{B}_f$  are rather similar.
+It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool.
+Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
+It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$.
+However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_f$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$.
+In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is moderately small; otherwise, they are similar.
+%See more discussions for differences between $\mc{B}_u$ and $\mc{B}_f$ in Section \ref{discussion}.
+
+ Simulation results corresponding to model $\mc{M}_1$ are listed in Section 3 in Supplementary Materials.
+Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$, except for the difference among estimators.
+The results show that (1) the performance of $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are nearly the same and (2) in many situations, $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are  better than $\hat{\alpha}_{\rm wadj}$; in other situations, they are mostly the same.
+Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
+Therefore, similarity weighting may not be informative when the model for $\alpha_i$ is identified wrongly.
+Under $\mc{M}_1$, simple averaging, aimed for a reduction of variance, or inverse-variance weighting, targeting on reducing negative effects from varying time lengths, may work better.
+
 \begin{table}[H]
@@
   \hline
-  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.9 (0.02) & 0.89 (0.02) & 51.92 (4.04) & 19.23 (2.55) & 20.64 (2.76) & 19.36 (2.52) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.89 (0.02) & 0.89 (0.02) & 52.58 (4.35) & 21.57 (2.58) & 23.38 (2.86) & 21.72 (2.5) \\ 
-  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.78 (0.03) & 0.83 (0.02) & 0.79 (0.03) & 55.01 (5.84) & 30.3 (3.59) & 31.98 (4.36) & 30.2 (3.5) \\ 
-  & 50  & 0.9 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.66 (0.04) & 0.65 (0.04) & 0.65 (0.04) & 64.42 (8.11) & 50 (5.78) & 52.56 (6.92) & 49.55 (5.7) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.8 (0.07) & 0.57 (0.04) & 0.53 (0.04) & 0.57 (0.04) & 91.51 (13.2) & 94.26 (10.41) & 97.26 (12.57) & 93.61 (10.27) \\[.3cm] 
-  \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.92 (0.02) & 0.91 (0.02) & 52.34 (4) & 17.23 (2.96) & 18.54 (2.83) & 17.39 (2.95) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.89 (0.02) & 0.89 (0.02) & 52.59 (4.04) & 19.02 (3.24) & 20.95 (3.13) & 19.23 (3.24) \\ 
-  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.75 (0.03) & 0.78 (0.03) & 0.77 (0.03) & 54.07 (4.97) & 27.66 (4.55) & 31.79 (4.47) & 27.84 (4.61) \\ 
-  & 50  & 0.83 (0.07) & 1 (0) & 0.8 (0.07) & 0.59 (0.04) & 0.63 (0.04) & 0.59 (0.04) & 60.32 (7.53) & 47.7 (7.04) & 52.97 (7.54) & 47.78 (7.17) \\ 
-  & 100  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.47 (0.04) & 0.51 (0.04) & 0.46 (0.04) & 85.6 (12.99) & 89.85 (12.82) & 100.74 (13.61) & 90.4 (12.91) \\[.3cm] 
-  \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.93 (0.02) & 0.91 (0.02) & 49.85 (4.01) & 18.07 (2.88) & 18.38 (2.71) & 18.04 (2.88) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.02) & 0.89 (0.02) & 0.87 (0.02) & 48.73 (4.3) & 19.45 (2.97) & 19.35 (2.86) & 19.32 (2.99) \\ 
-  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.75 (0.03) & 0.78 (0.03) & 0.76 (0.03) & 47.06 (5.13) & 26.16 (3.31) & 26.81 (3.13) & 26.23 (3.33) \\ 
-  & 50  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.61 (0.04) & 0.69 (0.03) & 0.64 (0.04) & 48.75 (6.86) & 40.27 (4.43) & 42.09 (4.49) & 40.77 (4.38) \\ 
-  & 100  & 0.67 (0.09) & 1 (0) & 0.63 (0.09) & 0.55 (0.04) & 0.51 (0.04) & 0.55 (0.04) & 64.29 (11.11) & 68.85 (8.27) & 74.08 (8.72) & 69.91 (8.14) \\[.3cm] 
-  \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.94 (0.02) & 0.95 (0.02) & 57.6 (6.94) & 21.58 (5.9) & 20 (5.86) & 21.58 (5.9) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.91 (0.02) & 0.93 (0.02) & 56.8 (7.01) & 22.2 (5.97) & 20.47 (5.89) & 22.22 (5.97) \\ 
-  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.78 (0.04) & 0.79 (0.04) & 0.77 (0.04) & 56.58 (7.49) & 28.96 (6.49) & 27.06 (6.19) & 29.03 (6.48) \\ 
- & 50  & 0.9 (0.06) & 1 (0) & 0.9 (0.06) & 0.57 (0.04) & 0.6 (0.04) & 0.58 (0.04) & 64.33 (8.75) & 47.16 (8.28) & 46.3 (7.26) & 47.35 (8.25) \\ 
-     & 100  & 0.83 (0.07) & 1 (0) & 0.8 (0.07) & 0.49 (0.04) & 0.48 (0.04) & 0.5 (0.04) & 95.61 (13.02) & 90.1 (13.29) & 86.81 (11.75) & 90.55 (13.23) \\
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.92 (0.02) & 0.89 (0.03) & 48.52 (3.93) & 15.74 (2.34) & 15.76 (2.34) & 15.16 (2.24) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.91 (0.02) & 0.89 (0.02) & 47.7 (4.35) & 18.26 (2.37) & 18.97 (2.42) & 17.68 (2.28) \\ 
+  & 25  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.79 (0.03) & 0.81 (0.03) & 0.77 (0.03) & 46.95 (6.11) & 27.35 (3.81) & 30.88 (3.84) & 26.58 (3.83) \\ 
+  & 50  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.62 (0.03) & 0.65 (0.03) & 0.63 (0.03) & 56.85 (8.64) & 46.96 (7.02) & 52.92 (7.45) & 45.95 (7.17) \\ 
+  & 100  & 0.73 (0.08) & 1 (0) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.55 (0.04) & 99.22 (12.84) & 93.4 (12.97) & 103.82 (14.1) & 91.95 (13.34) \\[.3cm]  
+ \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
+  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
+  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29) \\[.3cm] 
+ \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.92 (0.03) & 0.95 (0.02) & 52.1 (2.96) & 14.04 (1.78) & 13.36 (2.07) & 14.11 (1.76) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.9 (0.03) & 0.93 (0.02) & 52.25 (3.3) & 15.12 (1.93) & 14.24 (2.29) & 15.18 (1.9) \\ 
+    & 25  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.8 (0.03) & 0.8 (0.03) & 0.8 (0.03) & 52.71 (5.28) & 22.98 (2.9) & 22.6 (3.42) & 22.95 (2.88) \\ 
+    & 50  & 0.7 (0.09) & 0.9 (0.06) & 0.7 (0.09) & 0.65 (0.03) & 0.65 (0.03) & 0.65 (0.04) & 58.65 (8.48) & 39.51 (5.65) & 40.8 (6.3) & 39.35 (5.63) \\ 
+    & 100  & 0.6 (0.09) & 0.87 (0.06) & 0.6 (0.09) & 0.47 (0.05) & 0.45 (0.04) & 0.45 (0.05) & 88.76 (13.66) & 75.93 (11.52) & 81.89 (12.19) & 75.94 (11.41) \\[.3cm] 
+   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.55 (2.9) & 12.13 (1.77) & 14.22 (1.96) & 12.09 (1.77) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.95 (0.02) & 0.93 (0.02) & 49.13 (3.31) & 14.78 (1.85) & 18.21 (2) & 14.75 (1.85) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.02) & 0.85 (0.02) & 0.83 (0.03) & 47.38 (5.13) & 26.85 (3.33) & 32.95 (3.59) & 26.81 (3.32) \\ 
+    & 50  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.61 (0.04) & 0.71 (0.04) & 0.62 (0.04) & 56.73 (7.93) & 50.96 (6.63) & 60.62 (7.21) & 50.88 (6.59) \\ 
+    & 100  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.49 (0.05) & 0.51 (0.04) & 0.49 (0.05) & 93.79 (14.67) & 102.05 (13.37) & 116.45 (15.19) & 101.55 (13.38) \\
 \end{tabular}}
@@
   \hline
-  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.99 (0.01) & 0.99 (0.01) & 0.99 (0.01) & 53.27 (2.59) & 10.91 (1.7) & 11.77 (1.55) & 10.8 (1.69) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.95 (0.02) & 0.92 (0.02) & 50.86 (3.83) & 18.06 (2.18) & 17.26 (2.17) & 18.25 (2.17) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.83 (0.03) & 0.89 (0.02) & 0.83 (0.03) & 60.52 (3.97) & 16.09 (2.4) & 19.83 (3.05) & 15.87 (2.38) \\ 
-  & 50  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.67 (0.04) & 0.69 (0.03) & 0.67 (0.04) & 54.65 (6.95) & 51.79 (6.87) & 53.83 (7.26) & 52.6 (6.91) \\ 
-  & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.77 (0.08) & 0.52 (0.04) & 0.51 (0.04) & 0.51 (0.05) & 104.73 (13) & 88.31 (12.16) & 88.88 (12.63) & 86.72 (12.35) \\[.3cm] 
-  \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.93 (0.02) & 0.93 (0.02) & 58.17 (4.18) & 18.17 (2.61) & 16.59 (2.39) & 18.09 (2.63) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 52.81 (4.07) & 19.05 (2.49) & 19.67 (2.66) & 18.95 (2.53) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.78 (0.03) & 0.82 (0.03) & 0.79 (0.03) & 61.53 (5.69) & 28.55 (4.07) & 31.82 (4.27) & 28.76 (4.07) \\ 
-  & 50  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.66 (0.04) & 0.67 (0.04) & 0.66 (0.04) & 56.31 (8.03) & 47.33 (4.89) & 41.44 (4.39) & 46.86 (4.79) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.54 (0.05) & 0.54 (0.04) & 0.55 (0.04) & 84.38 (11.62) & 82.91 (11.77) & 84.5 (12.39) & 84.3 (11.93) \\[.3cm] 
-  \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 1 (0) & 0.78 (0.03) & 0.77 (0.03) & 0.79 (0.03) & 56.35 (6.1) & 25.54 (4.06) & 30.49 (4.61) & 25.94 (4.02) \\ 
-   & 10  & 1 (0) & 1 (0) & 1 (0) & 0.81 (0.03) & 0.79 (0.03) & 0.81 (0.03) & 49.8 (5.24) & 25.04 (4.38) & 26.74 (3.64) & 24.86 (4.38) \\ 
-  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.72 (0.03) & 0.77 (0.03) & 0.71 (0.03) & 54.21 (6.51) & 44.17 (6.66) & 43.41 (6.95) & 43.89 (6.63) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.57 (0.04) & 0.52 (0.04) & 66.51 (7.86) & 46.19 (8.04) & 44.83 (9.31) & 46.54 (8.27) \\ 
-  & 100  & 0.9 (0.06) & 1 (0) & 0.87 (0.06) & 0.54 (0.04) & 0.54 (0.04) & 0.56 (0.04) & 109.21 (13.29) & 78.47 (12.45) & 83.99 (12) & 78.57 (12.75)\\[.3cm] 
-  \multirow{5}{*}{50} & 5  & 0.83 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.54 (0.04) & 0.57 (0.04) & 0.55 (0.04) & 75.29 (10.75) & 63.51 (8.3) & 64.25 (8.88) & 63.32 (8.4) \\ 
-  & 10  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.53 (0.04) & 0.55 (0.05) & 0.53 (0.04) & 57.59 (6) & 48.51 (8.32) & 50.58 (8.63) & 48.08 (8.36) \\ 
-  & 25  & 0.73 (0.08) & 0.8 (0.07) & 0.73 (0.08) & 0.58 (0.04) & 0.58 (0.04) & 0.57 (0.04) & 77.21 (12.03) & 54.73 (9.47) & 54.76 (10.24) & 54.2 (9.62) \\ 
-  & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.04) & 0.53 (0.04) & 0.6 (0.04) & 90.48 (10.21) & 68.88 (9.2) & 68.28 (10.48) & 68.8 (9.28) \\ 
-  & 100  & 0.5 (0.09) & 0.73 (0.08) & 0.53 (0.09) & 0.51 (0.05) & 0.48 (0.05) & 0.51 (0.05) & 111.09 (17.54) & 102.47 (16.68) & 110.15 (15.87) & 101.53 (16.52) \\[.3cm] 
-  \multirow{5}{*}{100} & 5  & 0.43 (0.09) & 0.37 (0.09) & 0.43 (0.09) & 0.47 (0.04) & 0.47 (0.04) & 0.47 (0.04) & 214.07 (67.4) & 195.46 (67.65) & 197.51 (68.45) & 196.58 (67.51) \\ 
-  & 10  & 0.63 (0.09) & 0.6 (0.09) & 0.67 (0.09) & 0.51 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 120.85 (15.39) & 114.79 (15.51) & 119.19 (15.75) & 114.02 (15.74) \\ 
-  & 25  & 0.57 (0.09) & 0.6 (0.09) & 0.57 (0.09) & 0.51 (0.04) & 0.53 (0.04) & 0.49 (0.04) & 97.84 (13.75) & 95.02 (14.88) & 100.04 (16.94) & 96.23 (14.71) \\ 
-  & 50  & 0.53 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.47 (0.04) & 0.49 (0.05) & 0.49 (0.05) & 141.22 (24.51) & 136.11 (25.73) & 150.62 (27.62) & 135.26 (25.39) \\ 
-  & 100  & 0.63 (0.09) & 0.63 (0.09) & 0.63 (0.09) & 0.43 (0.04) & 0.41 (0.04) & 0.45 (0.04) & 95.53 (12.8) & 103.01 (14.12) & 103.31 (16.27) & 105.79 (14.32) \\
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.04 (3.65) & 21.75 (4.34) & 22.68 (4.41) & 21.83 (4.34) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.92 (0.02) & 0.93 (0.02) & 49.93 (4.11) & 24.3 (4.44) & 25.72 (4.58) & 24.4 (4.45) \\ 
+  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.73 (0.04) & 0.8 (0.03) & 0.73 (0.04) & 51.29 (5.39) & 32.8 (5.25) & 35.39 (5.78) & 33.11 (5.21) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.49 (0.04) & 0.44 (0.05) & 0.47 (0.04) & 82.55 (11.61) & 84.26 (12.7) & 98.66 (13.96) & 84.62 (12.59) \\[.3cm] 
+ \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
+  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
+  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29)\\[.3cm] 
+ \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.03) & 0.73 (0.03) & 0.71 (0.04) & 57.87 (8.76) & 50.31 (7.58) & 57.25 (7.75) & 50.53 (7.64) \\ 
+  & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.68 (0.04) & 0.69 (0.04) & 0.69 (0.04) & 58.41 (9.11) & 51.62 (7.91) & 58.61 (8.28) & 51.85 (7.98) \\ 
+  & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.63 (0.04) & 0.68 (0.04) & 0.63 (0.04) & 62.02 (10.02) & 59.08 (8.53) & 65.55 (9.64) & 59.68 (8.53) \\ 
+  & 50  & 0.87 (0.06) & 0.9 (0.06) & 0.87 (0.06) & 0.54 (0.04) & 0.59 (0.04) & 0.52 (0.04) & 71.01 (11.73) & 73.52 (10.18) & 81.81 (11.98) & 74.51 (10.09) \\ 
+  & 100  & 0.73 (0.08) & 0.87 (0.06) & 0.73 (0.08) & 0.47 (0.05) & 0.45 (0.04) & 0.5 (0.05) & 95.93 (15.59) & 104.49 (15.12) & 119.38 (17.62) & 105.72 (14.97) \\[.3cm] 
+ \multirow{5}{*}{50} & 5  & 0.8 (0.07) & 0.77 (0.08) & 0.8 (0.07) & 0.52 (0.04) & 0.49 (0.05) & 0.52 (0.04) & 85.95 (14.57) & 90.02 (13.45) & 103.03 (13.91) & 90.08 (13.64) \\ 
+  & 10  & 0.8 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.55 (0.05) & 0.5 (0.04) & 0.53 (0.05) & 86.44 (14.95) & 90.89 (13.79) & 104.62 (14.28) & 91.03 (13.98) \\ 
+  & 25  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.53 (0.04) & 0.46 (0.04) & 0.53 (0.04) & 90.26 (15.82) & 95.36 (14.69) & 109.53 (15.69) & 95.79 (14.83) \\ 
+  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.48 (0.05) & 0.45 (0.05) & 0.45 (0.05) & 99.52 (17.26) & 106.52 (16.17) & 120.99 (18.13) & 107.55 (16.19) \\ 
+  & 100  & 0.57 (0.09) & 0.77 (0.08) & 0.63 (0.09) & 0.41 (0.04) & 0.45 (0.03) & 0.41 (0.04) & 123.11 (20.61) & 135.24 (19.74) & 151.62 (23.42) & 137.21 (19.55) \\[.3cm] 
+ \multirow{5}{*}{100} & 5  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.48 (0.05) & 0.48 (0.03) & 0.47 (0.05) & 156.82 (26.36) & 170.06 (25.92) & 196.4 (26.55) & 170.13 (26.27) \\ 
+  & 10  & 0.63 (0.09) & 0.57 (0.09) & 0.67 (0.09) & 0.46 (0.05) & 0.47 (0.03) & 0.47 (0.05) & 157.3 (26.76) & 170.93 (26.21) & 197.96 (26.87) & 171.07 (26.56) \\ 
+  & 25  & 0.67 (0.09) & 0.63 (0.09) & 0.67 (0.09) & 0.44 (0.04) & 0.5 (0.03) & 0.45 (0.04) & 160.32 (27.73) & 173.66 (27.22) & 202.61 (28.01) & 174.28 (27.48) \\ 
+  & 50  & 0.67 (0.09) & 0.67 (0.09) & 0.67 (0.09) & 0.39 (0.04) & 0.43 (0.03) & 0.38 (0.04) & 166.98 (29.35) & 182.83 (28.37) & 210.38 (30.48) & 183.67 (28.61) \\ 
+  & 100  & 0.6 (0.09) & 0.67 (0.09) & 0.53 (0.09) & 0.4 (0.04) & 0.45 (0.04) & 0.41 (0.05) & 188.29 (32.07) & 203.7 (31.63) & 233.44 (35.31) & 205.4 (31.72) \\
 \end{tabular}}
@@
 \end{table}
-
-Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented. See Table \ref{table3} and Table \ref{table4} for results. Comparing Table \ref{table1}
- and Table \ref{table2} yields that when $n$ is small ($n = 5$ or $n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
-For other situations, $\mc{B}_u$  and $\mc{B}_f$  are rather similar.
-It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool.
-Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
-It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$.
-However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_f$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$.
-In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is small; otherwise, they are similar.
-%See more discussions for differences between $\mc{B}_u$ and $\mc{B}_f$ in Section \ref{discussion}.
-
- Simulation results corresponding to model $\mc{M}_1$ are listed in Section 3 in Supplementary Materials.
-Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$, except for the difference among estimators.
-The results show that (1) the performance of $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are nearly the same and (2) in many situations, $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are  better than $\hat{\alpha}_{\rm wadj}$; in other situations, they are mostly the same.
-Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
-Therefore, similarity weighting may not be informative when the model for $\alpha_i$ is identified wrongly.
-Under $\mc{M}_1$, simple averaging, aimed for a reduction of variance, or inverse-variance weighting, targeting on reducing negative effects from varying time lengths, may work better.
 

### 2020-08-09 Rcode/comp.R

@@ -3,7 +3,7 @@ require('tikzDevice')
 # set seed
 set.seed(2020)
 # parameter setup
-n = 40; T = 250; mu.alpha = 5; sigma.alpha = 1; sigma.X = 1; sigma = 1
+n = 40; T = 250; mu.alpha = 10; sigma.alpha = 1; sigma.X = 1; sigma = 1
 
 # T* is the shock time point
 Tstar <- floor(T / 2)
@@ -121,17 +121,17 @@ segments(x0 = Tstar + 1, y0 = min(mu.alpha.hat, Y), y1 = max(c(Ypred.adjusted, m
          col = 'deepskyblue', lty = 2, lwd = 2)
 points(x = rep(Tstar, n), y = mu.alpha.hat, col = 'magenta')
 # add arrows
-arrows(x0 = Tstar + 7, y0 = Ypred.original[Tstar + 1], col = 'magenta',
+arrows(x0 = Tstar + 5, y0 = Ypred.original[Tstar + 1], col = 'magenta',
        y1 = Ypred.adjusted[Tstar + 1],  code = 3, length = 0.07)
-arrows(x0 = Tstar + 4, y0 = Y[Tstar + 2] - alpha[1],
-       y1 = Y[Tstar + 2],  code = 3, length = 0.07)
 # \hat{\alpha}
-text(x = 150, y = mean(c(Ypred.original[Tstar + 1], max(Ypred.adjusted[Tstar + 1]))),
+text(x = 148, y = mean(c(Ypred.original[Tstar + 1], max(Ypred.adjusted[Tstar + 1]))),
      col = 'magenta',
-     labels = paste0('$\\displaystyle \\hat{\\alpha} = \\frac{1}{n}\\sum_{i=1}^{n} \\hat{\\alpha}_i= \\;$',
+     paste0('$\\displaystyle \\hat{\\alpha} = \\frac{1}{n}\\sum_{i=1}^{n} \\hat{\\alpha}_i= \\;$',
                      round(alpha.hat, digits = 2)))
-text(x = 142, y = mean(Y[Tstar + 2] - alpha[1], Y[Tstar + 2]) +1, col = 'black',
-     labels = paste0('$\\alpha = ', round(alpha[1], digits = 2), '$'))
+arrows(x1 =  Tstar + 2, x0 = 140, y0 = Ypred.original[Tstar + 1], 
+       col = 'black', code = 2, length = 0.07)
[…]

### 2020-08-09 Rcode/dataanalysis.R

@@ -127,7 +127,7 @@ lrindcov <- function(cov, cols, v){
 # not significant => Independence
 lrindcov(vcov(m_COP_Sept_08)[3:5, 3:5], cols = list(1, 2, 3), v = df.residual(m_COP_Sept_08))
 
-xtable(vcov(m_COP_Sept_08)[3:5, 3:5])
+xtable(vcov(m_COP_Sept_08)[3:5, 3:5], digits = 3)
 
 #### Thursday, November 27, 2014
 

### 2020-08-09 Rcode/sim.study.R

@@ -436,7 +436,6 @@ sim.study.normal.gammaX <- function(mu.gamma.delta = 1, mu.alpha, sigma,
   if (model == 2) {
     # construction of design matrix and shock effects
     delta <- c()
-    gamma <- c()
     for (i in 1:(n + 1)) {
       Ti <- T[i]
       Tstari <- Tstar[i]
@@ -919,7 +918,7 @@ xtable(riskprop)
 xtable(pred)
 
 
-
+############################################ true start for simulation 2
 
 # MC
 library("parallel")
@@ -953,7 +952,7 @@ system.time(
                                        mu.alpha = 2, sigma = 10, 
                                        sigma.alpha = sigma.alpha,
                                        sigma.delta.gamma = 0.5, 
-                                       p = 13, B = 200, k = 5, scale = 2, 
+                                       p = 25, B = 200, k = 5, scale = 2, 
                                        n = n, np = TRUE)
       return(study)
     }
@@ -980,20 +979,17 @@ for (i in 1:nrow(sim_params)) {
   sds <- apply(table, 2, function(x) sd(x))
   result.i <- c()
   for (j in 1:20) {
-    result.i <- cbind(result.i, paste0(round(means[j], digits = 3), 
-                                       ' (', round(sds[j] / sqrt(30), 
-                                                   digits = 3), ')'))
+    result.i <- cbind(result.i, paste0(round(means[j], digits = 2), 
+                                       ' (', round(sds[j] / sqrt(nsim), 
+                                                   digits = 2), ')'))
   }
   result <- rbind(result, result.i)
 }
 result <- cbind(sim_params[, c(2,1)], result)
 # results
-riskprop <- result[, c(1:2, 8:10, 19:22)]
-pred <- result[, -c(3:4, 8:14, 19:22)]
+report <- result[, c(1:2, 8:10, 19:21, 15:18)]
 require('xtable')
-xtable(riskprop)
-xtable(pred)
-
+xtable(report)
 
 
 
@@ -1029,8 +1025,8 @@ system.time(
                                        mu.alpha = 2, sigma = sigma, 
                                        sigma.alpha = sigma.alpha,
                                        sigma.delta.gamma = 0.5, 
-                                       p = 13, B = 200, k = 5, scale = 2, 
-                                       n = 10, np = FALSE)
+                                       p = 25, B = 200, k = 5, scale = 2, 
[…]

### 2020-08-17 manuscript/manuscript.tex
minor edits; we are almost done

@@
 \begin{abstract}
-    We developed a forecasting methodology for providing credible forecasts for the time series data that have undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded.
-Three shock effects estimators were constructed for minimizing average forecast risk.
-We proposed risk-reduction propositions providing conditions when our methodology works.
+    We develop a forecasting methodology for providing credible forecasts for time series that have recently undergone a shock.
+We achieve this by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded.
+Three shock effect estimators are motivated with the aim of minimizing average forecast risk.
+We propose risk-reduction propositions that provide conditions that establish when our methodology works.
 Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential prospective success of post-shock forecasts.
-%The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well.
 Leave-one-out cross validation is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality.
@@
 
-We provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock in real-time.
-Standard forecasting methods may not allow users to explore the consequences that structural shocks have on baseline forecasts \citep{baumeister2014real}.
+We provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
+We focus on the specific setting in which a structural shock has occurred and one desires a prediction for the post-shock response at the next time point.
+Standard forecasting methods may not yield accurate predictions in the presence of such structural shocks \citep{baumeister2014real}.
 This is a general problem that has many real life applications.
@@
 On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects are all thought to arise from a similar data generating process.
-For further differences of assumptions on shocks, our methodology allows for \emph{unprecedented} shocks and no observation of past shocks.
+For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks.
 
@@
 We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast.
-The involved parameters in the risk-reduction propositions and risk-reduction quantities can be estimated by a residual bootstrap procedure that we develop within.
-%These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed.
+The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop.
 We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators.
@@
 Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection.
-%$y_1, y_2, \ldots$.  
-%Given each time point $t \geq 1$, let $\x_{1,t}$ be a vector of covariates 
-%revealed prior to the observation of $y_{1,t}$.
-
 We will suppose that specific interest is in forecasting the response after the occurrence of a structural shock.
-To gauge the performance of forecasts, we consider forecast risk in the form of mean squared error (MSE),
+To gauge the performance of forecasts, we consider forecast risk in the form of MSE,
 $$
@@
 and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.
-Specific emphasis will be given to post-shock prediction where forecasts methods only differ at one future time point.
-In this setting we will consider the magnitude $|\E{\hat y_{1,t} - y_{1,t}}|$.
+In this article, we focus on post-shock prediction where forecasts methods only differ at the next future time point.
+Thus the MSE reduces to the magnitude $|\E{\hat y_{1,t} - y_{1,t}}|$.
 
@@
 
-Let $I(\cdot)$ be an indicator function, $T_i$ be the time length of the time series $i$ for $i = 1, \ldots, n+1$, and $T_i^*$ be the time point just before the one when the shock is \emph{known} to occur, with $T_i^* < T_i$.
+Let $I(\cdot)$ be an indicator function, $T_i$ be the time length of the time series $i$ for $i = 1, \ldots, n+1$, and $T_i^*$ be the time point just before the one when the shock is known to occur, with $T_i^* < T_i$.
 For $t= 1, \ldots, T_i$ and $i = 1, \ldots, n+1$, the model $\mc{M}_1$ is defined as
@@
 \end{align*} 
-%and $\delta_i$ and $\gamma_i$ will be discussed shortly. 
 We further define 
@@
 circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-Improvement will be  measured by \emph{risk-reduction quantity}, which is the difference between the risk of Forecast 1 and Forecast 2.
-We will return to the theoretical details of risk-reduction quantity in Section \ref{properties}.
+Improvement will be measured by assessing the reduction in risk that Forecast 2 offers over Forecast 1.
+We will return to the theoretical details of risk-reduction in Section \ref{properties}.
 
@@
 Second, we introduce the candidate estimators for $\alpha_1$. Define the 
-\emph{adjustment estimator} for time series $i=1$ by
+adjustment estimator for time series $i=1$ by
 \begin{equation} \label{adjusted}
@@
 
-We also consider the \emph{inverse-variance weighted estimator} 
+We also consider the inverse-variance weighted estimator 
 in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i=2, \ldots, n+1$. 
@@
 
-%More importantly, we introduce the backgrounds and procedures of constructing \emph{weighted-adjustment estimator} as follows. 
-We now motivate a \emph{weighted-adjustment estimator} for model $\mc{M}_{21}$ 
+We now motivate a weighted-adjustment estimator for model $\mc{M}_{21}$ 
 and $\mc{M}_{22}$. Our weighted-adjustment estimator is inspired by the 
@@
 
-Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple risk-reduction conditions, and more importantly motivates a bootstrap estimation for evaluation of these conditions.
+Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation for evaluation of these conditions.
 % for $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm wadj}$ to reduce risk, and make it more clear with respect to when one is better than the other.
@@
 This term exists because of the inclusion of the random lagged response in our auto regressive model formulation.
-Under $\mc{M}_{22}$, the expression for $\var{\alpha_i}$ is not of closed form because $\gamma_i$ and $\delta_i$ may be dependent when they are placed in a random-effects model.
+Under $\mc{M}_{22}$, the expression for $\var{\alpha_i}$ is not of closed form because $\delta_i$ may be dependent when they are placed in a random-effects model.
 
@@
 %The reason is that if the estimator of $\alpha_1$ turns out to be an unbiased estimator of $\E{\alpha_1}$, the conditions get  simplified.
+For an adjustment estimator $\hat{\alpha}$, we will write the risk-reduction as $\Delta(\hat{\alpha})=R_{T_1^*+1,1}-R_{T_1^*+1,2}$ where $R_{T_1^*+1,2}$ is the risk of Forecast 2 calculated using the adjustment estimator $\hat{\alpha}$.
 
@@
 \begin{enumerate}[label = (\roman*)]
-  \item  $R_{T_1^*+1, 2} < R_{T_1^*+1, 1}$ when 
+  \item $\Delta(\hat\alpha_{\rm adj}) > 0$  when 
 $\Var(\hat{\alpha}_{\rm adj}) < \mu_{\alpha}^2$.
-  \item if $\mbf{W}^*$ satisfies (\ref{SCM}), $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm wadj}}<\mu_{\alpha}^2$. 
+  \item if $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<\mu_{\alpha}^2$. 
 \end{enumerate}
@@
 
-Proposition \ref{proprisk} tells that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties.
-Recalling from variance expression at the beginning of Section \ref{properties}, Proposition \ref{proprisk} shows that the risk-reduction condition is
+Proposition \ref{proprisk} says that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties.
+In this setting, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$.
+% from Proposition \ref{proprisk}.
+From Proposition \ref{proprisk}, we obtain a risk-reduction condition
 \begin{align}
@@
 
-For the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$, if  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}.
+If  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}.
 From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
@@
 In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.
-However, the above criteria are generally difficult to evaluate in practice due to the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.
-
-In fact, we can extend checking risk-reduction conditions to verifying the sign of risk-reduction quantities for generalization.
-For an adjustment estimator $\hat{\alpha}$, the risk-reduction quantity is defined as  $\Delta(\hat{\alpha})=R_{T_1^*+1,1}-R_{T_1^*+1,2}$.
-If $\Delta(\hat{\alpha})>0$, $\hat{\alpha}$ will improve the Forecast 1.
-In this context, according to Proposition \ref{proprisk}, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$.
-Sections \ref{varbootstrap} and \ref{loocv} will provide a detailed treatment about how to checking the sign  in practice.
+However, the above criteria are generally difficult to evaluate in practice.
+Sections \ref{varbootstrap} and \ref{loocv} will provide detailed treatment on how to estimate the sign of $\Delta(\hat\alpha)$ in practice.
 
@@
 %It is a more reasonable and general model since it is often the case that shock effects differ by means among disparate time series in practice.
-$\mc{M}_{22}$  further adds the random effect structure of $\delta$ and $\gamma$ to  $\mc{M}_{21}$ for generalization.
+$\mc{M}_{22}$  further adds the random effect structure of $\delta$ to  $\mc{M}_{21}$ for generalization.
 However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
@@
 \begin{prop}
-\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}), under $\mc{M}_{21}$ and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$. 
+\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}) then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$  under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
 \end{prop}
@@
 We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$.
-That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
+That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
 Therefore, using the generalization mentioned in Section \ref{conditionsmodel1}, under $\mc{M}_2$, it can be shown that the risk-reduction quantities are
@@
 \end{align*}
-where we estimate $\Delta(\hat{\alpha})$  using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
+where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
 
@@
 In this section we provide justification for our methods based on Monte Carlo simulation.
-We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
+We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
 We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}.
@@
 Additionally, we generated the covariates from $\text{Gamma}(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
-Last, we set $\gamma_i, \delta_i\simiid  \normal{1}{0.5}$ and $\theta_i \sim \normal{0}{1}$.
+Last, we set $\delta_i\simiid  \normal{1}{0.5}$ and $\theta_i \sim \normal{0}{1}$.
 We will consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
@@
 Our adjustment estimators will be evaluated by multiple criteria.
-We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the \emph{guess}, with 1 indicating that $\hat{\alpha}$ provides risk-reduction over the simple no-adjustment forecast, and 0 indicates the converse.
+We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the guess, with 1 indicating that $\hat{\alpha}$ provides risk-reduction over the simple no-adjustment forecast, and 0 indicates the converse.
 We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
@@
 This is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
-The reasons can be outlined as below.
-Recall in Section \ref{conditionsm2122}, the conditions of risk-reduction propositions involve $(\E{\alpha_1})^2 > \var{\hat{\alpha}} + (\E{\hat{\alpha}}-\E{\alpha_1})^2$ for $\hat{\alpha}\in \mc{A}$, where we note that those parameters are \emph{true} ones but not estimated ones.
+The reasons are outlined as follows: Recall in Section \ref{conditionsm2122}, the conditions of risk-reduction propositions involve $(\E{\alpha_1})^2 > \var{\hat{\alpha}} + (\E{\hat{\alpha}}-\E{\alpha_1})^2$ for $\hat{\alpha}\in \mc{A}$.
 Notice that $\var{\hat{\alpha}}$ is an increasing function of $\sigma$ since $\hat{\alpha}$ is estimated by OLS.
@@
 The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.136$, $2.421$, and $0.818$ dollars, respectively.
-These additive adjustment estimators do extremely well.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects only, respectively, miss the post-shock Conoco Philips share price by $1.136$, $2.421$, and $0.818$ dollars.
+These additive adjustment estimators do extremely well in this additive shock setting.
 %There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.
@@
 %This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock effects in the donor pool.
-%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.
+%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 6$.
 %This generalization was adopted in Section \ref{forecasting}.
@@
 An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.
-Although our work is developed for  time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated \emph{unbiasedly}, and an additive shock-effect structure.
+Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, and an additive shock-effect structure.
 
@@
 \end{align}
-Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \gamma_i \indep \varepsilon_{i,t}$, we have
+Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \varepsilon_{i,t}$, we have
  \begin{align*}

### 2020-08-19 manuscript/comp.tex
edits to typos and unclear points, major edits to Section 3.2 and Section 5

@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (498.49,111.84) {$\hat{y}^{1}_{T_1^*+1} = 0.46$};
+\node[text=drawCo sep=0pt, outer sep=0pt, scale=  1.00] at (470.08,425.61) {$\alpha = 4.21$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 70.86) {shock time point $T^*_1 + 1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81,372.18) {shock time point $T^*_1 + 1$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,179.57) {$y_{T_1^*+1}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,472.53) {$y_{T_1^*+1}$};
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,205.47) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,513.81) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,207.97) -- (427.48,207.97);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,516.31) -- (427.48,516.31);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,205.44) --
-	(427.48,207.97) --
-	(423.10,210.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,513.78) --
+	(427.48,516.31) --
+	(423.10,518.84);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,182.07) -- (427.48,182.07);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,475.03) -- (427.48,475.03);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,179.54) --
-	(427.48,182.07) --
-	(423.10,184.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,472.50) --
+	(427.48,475.03) --
+	(423.10,477.56);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,207.97) rectangle (212.08,171.97);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,516.31) rectangle (212.08,480.31);
 \definecolor{drawColor}{RGB}{255,106,106}
 
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,195.97) -- ( 93.75,195.97);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,504.31) -- ( 93.75,504.31);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,183.97) -- ( 93.75,183.97);
+\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,492.31) -- ( 93.75,492.31);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,192.53) {$\hat{y}_{t}^{1}$ without shock effects};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,500.87) {$\hat{y}_{t}^{1}$ without shock effects};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,180.53) {$\hat{y}_{t}^{2}$ with shock effects};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,488.87) {$\hat{y}_{t}^{2}$ with shock effects};
 \end{scope}
@@
 \end{document}
+}
+\end{tikzpicture}
+
+\end{document}

### 2020-08-19 manuscript/fig2.tex
edits to typos and unclear points, major edits to Section 3.2 and Section 5

--- 2020-06-28 manuscript/fig2.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-06-28 18:03:01
+% Created by tikzDevice version 0.12.3.1 on 2020-08-19 16:49:26
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.25) --
-	(481.73, 86.67) --
-	(476.44, 86.67) --
-	(479.09, 91.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 99.95) --
+	(481.73, 95.38) --
+	(476.44, 95.38) --
+	(479.09, 99.95);
 \definecolor{drawColor}{RGB}{0,191,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 88.07) -- (481.86, 88.07);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31,101.69) -- (481.86,101.69);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.29) -- (479.09, 90.84);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 98.92) -- (479.09,104.47);
 \definecolor{drawColor}{RGB}{238,99,99}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 81.21) -- (481.05, 85.13);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 95.61) -- (481.05, 99.53);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 85.13) -- (481.05, 81.21);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 99.53) -- (481.05, 95.61);
 \definecolor{drawColor}{RGB}{238,130,238}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (479.09,141.49) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (479.09,144.69) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.76,313.70) --
-	( 80.50,313.67) --
-	( 94.25,302.10) --
-	(107.99,304.27) --
-	(121.74,297.06) --
-	(135.48,299.42) --
-	(149.23,290.97) --
-	(162.97,283.99) --
-	(176.71,258.33) --
-	(190.46,290.13) --
-	(204.20,281.01) --
-	(217.95,276.50) --
-	(231.69,274.52) --
-	(245.43,289.86) --
-	(259.18,300.87) --
-	(272.92,286.25) --
-	(286.67,282.81) --
-	(300.41,276.99) --
-	(314.16,288.22) --
-	(327.90,280.06) --
-	(341.64,273.21) --
-	(355.39,252.42) --
-	(369.13,229.35) --
-	(382.88,199.60) --
-	(396.62,163.01) --
-	(410.37,175.15) --
-	(424.11,190.38) --
-	(437.85,181.33) --
-	(451.60,180.97) --
-	(465.34,175.47) --
-	(479.09,141.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.76,323.78) --
+	( 80.50,312.48) --
+	( 94.25,297.05) --
+	(107.99,301.43) --
+	(121.74,296.20) --
+	(135.48,301.14) --
+	(149.23,292.29) --
+	(162.97,286.87) --
+	(176.71,273.08) --
+	(190.46,289.26) --
+	(204.20,285.58) --
+	(217.95,276.06) --
+	(231.69,276.86) --
+	(245.43,287.14) --
+	(259.18,290.90) --
+	(272.92,284.54) --
+	(286.67,282.37) --
+	(300.41,275.05) --
+	(314.16,282.80) --
+	(327.90,275.49) --
+	(341.64,276.64) --
+	(355.39,253.30) --
+	(369.13,224.73) --
+	(382.88,201.68) --
+	(396.62,172.73) --
+	(410.37,172.62) --
+	(424.11,200.63) --
+	(437.85,172.58) --
+	(451.60,180.66) --
+	(465.34,165.66) --
+	(479.09,144.69);
 \definecolor{drawColor}{RGB}{0,0,0}

### 2020-08-19 manuscript/manuscript.tex
edits to typos and unclear points, major edits to Section 3.2 and Section 5

@@
 Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential prospective success of post-shock forecasts.
-Leave-one-out cross validation is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality.
+Leave-one-out cross validation with $k$ random draws is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality.
 Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
@@
 Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}.
-On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects are all thought to arise from a similar data generating process.
+On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects from outside data sources are all thought to arise from a  data generating process similar to that of the shock under study.
 For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks.
@@
 Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
-The context in \cite{clements2019measuring} allowed for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
+The context in \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
 In our context, the yet to observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the disparate time series.
@@
 
-In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure.
+In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure.
 Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
@@
 The considered adjustment strategies all target the mean of the shock effect distribution.
-However, such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean.
+Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean.
 We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast.
 The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop.
-We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators.
+We also motivate a simple leave-one-out cross validation with $k$ random draws procedure which can prospectively assess the performance of our shock effect adjustment estimators.
 This prospective assessment does not require the observation of the post-shock response.
@@
 We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020.
-We show that our proposed adjustment estimators yield much better results than no adjustment in this setting.
+We will show that our proposed adjustment estimators yield much better results than no adjustment in this setting.
 We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts.
@@
   \end{center}
-     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 4.21$.
+     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$.
 (a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given $n=40$ disparate time series.
@@
 
-We will suppose that a researcher has time series data ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
+We will suppose that a researcher has time series data ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$, where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
 Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection.
@@
 In this article, we focus on post-shock prediction where forecasts methods only differ at the next future time point.
-Thus the MSE reduces to the magnitude $|\E{\hat y_{1,t} - y_{1,t}}|$.
+Thus the MSE reduces to the magnitude $\E{\hat y_{1,t} - y_{1,t}}^2$.
 
 %The forecast consists of three steps: (1) pick a model, (2) selection of covariates, (3) choices of donor pool.
-Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$.
+Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
 In this article, we consider a dynamic panel data model with autoregressive structure similar to that in \citet{blundell1998initial}.
@@
 In this example, the mean of the estimated shock effects is taken as a shock effect estimator for the time series under study.
-Forecasts are then made by adding this shock effect estimator to the estimated response values obtained from the process that ignores the shock.
+Forecasts are then made by adding this shock effect estimator to the estimated response values obtained from the estimation procedure that ignores the shock.
 It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock effect.
@@
 $y_{1,T_1^*+1}$. Throughout the rest of this article we show that the collection of 
-disparate time series $\{y_{i,t}, t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$ has 
-the potential to improve the forecasts for $y_{1, t}$ when $t > T_1^*$ under different 
+disparate time series $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$ has 
+the potential to improve the forecasts for $y_{1, T_1^*+1}$ under  different 
 circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
@@
 
-We now construct the aggregate estimators of the shock effects that appear in 
+We now construct the aggregated estimators of the shock effects that appear in 
 Forecast 2 (see Section \ref{forecast}). We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.  %Notice that the shock effect 
@@
 \end{equation}
-where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of all of 
+where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of  
 the $\alpha_i$s for $i = 2, \ldots, n+1$.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
@@
 From a Bayesian perspective, if we assign a prior $\pi$ to $\alpha_1$, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as the Bayes rules with respect to $\pi$ under different loss functions.
-If the sampling distribution of the data and $\pi$ are known, it is possible to compute the Bayes risks of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ with respect to $\pi$, and thus enable comparisons among them.
+If the sampling distribution of the data and $\pi$ are known, it is possible to compute the Bayes risks of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ with respect to $\pi$,  thus enabling comparisons among them.
 Additionally, from Theorem 2.4 in Chapter 5 of \cite{lehmann2006theory}, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are admissible if they are unique with probability one.
@@
 Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$
-because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.
-This term exists because of the inclusion of the random lagged response in our auto regressive model formulation.
-Under $\mc{M}_{22}$, the expression for $\var{\alpha_i}$ is not of closed form because $\delta_i$ may be dependent when they are placed in a random-effects model.
+because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our auto regressive model formulation.
 
@@
 These conditions involve variances and expectations which may be difficult to compute in practice.
-To make use of those properties in practice, estimation is required.
-Sections \ref{varbootstrap} and \ref{loocv} introduce  parametric bootstrap and leave-one-out cross validation procedures which prospectively estimate the conditions necessary for risk-reduction without observation of the post-shock response for the time series under study.
-Our simulations test these procedures.
+To make use of those conditions in practice, estimation is required.
+Sections \ref{varbootstrap} introduce parametric bootstrap, which estimates the involved parameters in those conditions and thus motivates prospective decision-making  about whether $\hat{\alpha}_i$ reduces the risk.
+Section
+ \ref{loocv} describes  leave-one-out cross validation with $k$ random draws procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study.
+Our simulations verify these procedures.
 
@@
 However, the above criteria are generally difficult to evaluate in practice.
-Sections \ref{varbootstrap} and \ref{loocv} will provide detailed treatment on how to estimate the sign of $\Delta(\hat\alpha)$ in practice.
+Sections \ref{varbootstrap} and \ref{loocv}  provide detailed treatments on how to estimate the sign of $\Delta(\hat\alpha)$ in practice.
 
@@
 \begin{prop}
-\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}) then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$  under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
+\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$  under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
 \end{prop}
@@
 That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
-Therefore, using the generalization mentioned in Section \ref{conditionsmodel1}, under $\mc{M}_2$, it can be shown that the risk-reduction quantities are
+In fact, more generally, using similar proof of Lemma \ref{risklemma}, it can be shown that under $\mc{M}_2$, the risk-reduction quantities are
 \begin{align*}
   \Delta(\hat{\alpha}_{\rm adj}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2\\
+  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2,\\
   \Delta(\hat{\alpha}_{\rm IVW}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2\\
+  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2 ,\\
   \Delta(\hat{\alpha}_{\rm wadj}) 
@@
 \end{align*}
-where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
+where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using the bootstrap and leave-one-out cross validation with $k$ random draws techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
 
@@
 At iteration $b$, first resample the indices $I = \{2, \ldots, n+1\}$ of the donor pool with replacement to form $I^{(b)}$ with cardinality $n$, where we note that the elements of $I^{(b)}$ may not be unique in terms of their  indices in the donor pool.
-Initialize $y_{i,0}$ for all $i \in I^{(b)}$.
-Then, resample the residuals under models $\mc{M}_1$, $\mc{M}_{21}$, or $\mc{M}_{22}$ and obtain shock effect estimators for each of the disparate time series for all $i \in I^{(b)}$.
+Initialize $y_{i,0}^{(b)}=y_{i,0}$ for all $i \in I^{(b)}$.
+Then, resample the residuals under models $\mc{M}_1$ or $\mc{M}_{2}$, compute the bootstrapped response  $y_{i,t}^{(b)}$ for   $t \in \{1, \ldots, T_i\}$ using the model estimated by original data,  and obtain shock effect estimators for each of the disparate time series for all $i \in I^{(b)}$.
 These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
@@
 We will explicitly use these bootstrapped samples of shock effect estimators to check the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
-Recall that  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ from Proposition \ref{unbiased}.
+Recall that $\hat{\alpha}_{\rm adj}$,  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ under $\mc{M}_1$ and $\mc{M}_2$ from Proposition \ref{unbiased}.
 Our bootstrap procedure estimates the variance of our adjustment estimators.
@@
 
-We stress that the our bootstrap approximations cannot alleviate the inherent bias of using our adjustment estimators as surrogates for $\alpha_1$.
+We stress that  our bootstrap approximations cannot alleviate the inherent bias of using our adjustment estimators as surrogates for $\alpha_1$.
 We caution that the bootstrapping residuals in OLS estimation may not provide valid inference in moderate or high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}; see alternatives for residual bootstrapping in linear models in \citet{el2018can}.
+
 Recall that $\mathbf{W}^*$  may not be unique if the conditions in Proposition \ref{uniqueness} are not satisfied.
-Under the setup of our model, non-uniqueness of $\mathbf{W}^*$ would not be a problem for inferential purposes.
+Non-uniqueness might be a concern theoretically.
+It is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$'s all targeting on the same $\alpha_1$.
+For example, consider the case where the size of  donor pool to be 2, $\var{\hat{\alpha}_2}=1$, $\var{\hat{\alpha}_3}=2$, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
+In this scenario, the weighted adjustment estimator induced by $\mathbf{W}^*_1$ has variance 1 whereas the one by $\mathbf{W}^*_2$ has variance 2.
+Nevertheless, even if $\hat{\alpha}_i$ has the same variance across $i = 2, \ldots, n+1$, the same issue would occur if there were infinitely many $\mbf{W}^*$ with different norms.
+It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}).
+However, non-uniqueness of $\mathbf{W}^*$ would not be a problem for inferential purposes.
 This is because all risk-reduction propositions and other properties established will still hold.
-However, non-uniqueness may not be desirable in other model setups.
-For example, consider the model where $\alpha_i$ is assumed to be not identically distributed, the size of  donor pool to be 2, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$ with $\var{\alpha_2}\neq \var{\alpha_3}$.
-In this scenario, the procedure of trying to recover $\alpha_1$ will fail since the resulting $\alpha_1$ will be different with different variances for $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
-If the non-uniqueness is of concern, users may select the weight that optimizes some objective function.
-For instance, in the example just discussed, users may select the weight that minimizes the estimated variance of $\hat{\alpha}_{\rm wadj}$.
-%There are some issues in using $\mc{B}_u$ when $\mathbf{W}^*$ falls in the boundary of the parameter space. See detailed discussions in Section \ref{discussion}.
-
-\subsection{Leave-one-out cross validation}
+Simulation examples listed in the Section 4 of the Supplementary Materials verify this point.
+
+\subsection{Leave-one-out cross validation with $k$ random draws}
 \label{loocv}
@@
 Let $\mc{A}$ be the set of adjustment estimators.
-For each $\hat{\alpha} \in \mc{A}$, let $\delta_{\hat{\alpha}} = I(\hat\Delta(\hat{\alpha})>0)$ be a decision rule where $I(\cdot)$ is the indicator function and a $1$ corresponds to the decision to use adjustment estimator $\hat\alpha$.
-If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported 1 (0, respectively) so that it make the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be incorrect.
-If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported 0 (1, respectively) so that it make the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be correct.
+For each $\hat{\alpha} \in \mc{A}$, let $\delta_{\hat{\alpha}} = I(\hat\Delta(\hat{\alpha})>0)$ be a decision rule where $I(\cdot)$ is the indicator function and a $1$ corresponds to the decision to use  estimator $\hat\alpha$.
+If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported 1 (0, respectively) so that it makes the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be incorrect.
+If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported 0 (1, respectively) so that it makes the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be correct.
 These situations are depicted in the following table: \vspace*{0.3cm}
@@
 Our LOOCV procedure will consider $k=5$ random draws.
-Recall in Section \ref{loocv} that $k$ times of bootstrap are nested in a LOOCV with $k$ random draws.
+Recall in Section \ref{loocv} that $B$ times of bootstrap are nested in a LOOCV with $k$ random draws.
 It implies that $B(k+1)$ times of bootstrap replications are required for each Monte Carlo simulation.
@@
 Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.
-Results are displayed in Table~\ref{table2}.
+Results are  in Table~\ref{table2}.
 
@@
 Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
-However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the decision rule $\delta_{\hat{\alpha}}$  becomes unreliable for $\hat{\alpha}\in \mc{A}$.
+However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is large), the decision rule $\delta_{\hat{\alpha}}$  becomes unreliable for $\hat{\alpha}\in \mc{A}$.
 It is to be expected since the bootstrap estimates become more biased.
@@
 All the parameters are estimated using OLS.
-\item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
+\item[(2)] {\bf Selection of covariates}.
+We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$.
+The model of $\alpha_i$ incorporates daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange (CBOE) volatility index.
+In contrast, the model of $y_{i,t}$ disregards CBOE volatility index.
+It is because CBOE volatity index is a metric for capturing market risk and  sentiment, which can be highly related to the shock effect that results from investor behavior.
+It is not favorable in the model of $y_{i,t}$ since it may hinder  the estimation of $\alpha_i$.
 \item[(3)] {\bf Construction of donor pool}.
@@
 Note that there are three shock effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials.
+The estimated shock-effects for $\alpha_i$ are $-0.922, -7.063, -5.777, -6.395, -4.207$ for $i = 2, \ldots, 6$, respectively.
 Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
+Note that non-uniqueness problems will not occur in this analysis since the conditions of Proposition \ref{uniqueness} are satisfied.
+To avoid the effect of  unit differences on weighting, we center and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
 For $\hat{\alpha}_{\rm wadj}$, we observe that
 $
-  \mathbf{W}^*= (0.000,0.000, 0.000, 0.000, 1.000)
+  \mathbf{W}^*= (0.000,0.000, 0.000, 0.273, 0.727)
 $
@@
 $
-  \norm{\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)}_{2} = 900.13.
+  \Vert\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\Vert_2 = 3.440.
 $
-Note that the norm is computed using the $k$-dimensional Euclidean metric. The solution $\mathbf{W}^*$ suggests that the shock effect of interest is replicated by the November 27, 2014 shock effect.
+Note that the norm is computed using the $k$-dimensional Euclidean metric.
+The solution $\mathbf{W}^*$ suggests that the shock effect of interest is very similar to the September 25, 2008 shock effect and  the November 27, 2014 shock effect.
 
@@
 
-The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-5.348$, $\hat{\alpha}_{\rm wadj}= -5.761$, and $\hat{\alpha}_{\rm IVW}=-5.290$.
+The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-4.872$, $\hat{\alpha}_{\rm wadj}= -4.805$, and $\hat{\alpha}_{\rm IVW}=-4.384$.
 Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}.
-The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.567, 0.499, and 1.006, respectively.
+The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.419, 0.559, and 0.667, respectively.
 %Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $32.452$, $32.690$, and $31.960$, respectively.
@@
 The unadjusted forecast misses the post-shock response by 9.870 dollars whereas 
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $4.522$, $4.109$, and $3.581$ dollars, respectively. 
+the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively. 
 %Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
@@
 The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects only, respectively, miss the post-shock Conoco Philips share price by $1.136$, $2.421$, and $0.818$ dollars.
+The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects only, respectively, miss the post-shock Conoco Philips share price by $0.951$, $0.405$, and $1.460$ dollars.
 These additive adjustment estimators do extremely well in this additive shock setting.
@@
 
+There have been several other recent  methods developed for forecasting COVID-19 cases.
+For example, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries.
+A similar setup may be appropriate for post-shock forecasting but may be too dependent upon model specification for the shock distribution.
+\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach.
+However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
+\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
+They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
+Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
+
 \section{Discussion}
@@
 
-We developed methodology for forecasting post-shock response values after the occurrence of a structural shock.
+We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock.
 Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
@@
 Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
-As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
+As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
 But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
@@
 An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.
-Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, and an additive shock-effect structure.
+Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.
 
@@
 
-We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.
+We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population in the simulation examples.
 Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
-However, in applications, it is possible that $\mathbf{W}^*$ may take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-Moreover, when $p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$.
+In this scenario, $\mathbf{W}^*$ will take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
+When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$.
 However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
-Nevertheless, it does not seriously compromise the inference according to our simulation results in Section 4 in the Supplementary Materials.
+But it does not seriously compromise the inference according to our simulation results in Section 4 in the Supplementary Materials.
 
@@
 
-There have been several recent time series pooling methods developed for forecasting COVID-19 cases.
-\citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries.
-A similar setup may be appropriate for post-shock forecasting but may be too dependent upon model specification for the shock distribution.
-\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach.
-However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
-\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
-They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
-Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
-
 \section{Appendix}
@@
 \end{align*}
-where we used the fact that $\sum_{i=2}^{n+1} w_i=1$.
+where we used the fact that $\sum_{i=2}^{n+1} w^*_i=1$.
 

### 2020-08-19 Rcode/dataanalysis.R

@@ -8,6 +8,9 @@ library('msos')
 library('tikzDevice')
 library('xtable')
 
+# set working directory
+setwd("/Users/mac/Desktop/Research/Post-Shock Prediction/")
+
 ## Conoco Phillips
 getSymbols('COP', from = "2000-01-01")
 COP <- as.data.frame(COP)
@@ -26,8 +29,31 @@ Brent_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/brent-daily
 WTI_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/wti-daily_csv/data/c414c9d375ec3c8f9d7c276d866fb2a4/wti-daily_csv.csv") %>%
   rename(WTI_Close = Price)
 
+## Gold Price
+getSymbols('GC=F', from = "2000-01-01")
+gold <- as.data.frame(`GC=F`)
+gold <- na.omit(gold)
+gold <- gold %>% mutate(Date = rownames(gold))
+
+## Dollar Index
+getSymbols('DX-Y.NYB', from = "2000-01-01")
+USD <- as.data.frame(`DX-Y.NYB`)
+USD <- na.omit(USD)
+USD <- USD %>% mutate(Date = rownames(USD))
+
+## 13-Week T-Bill
+TB <- read.csv('^IRX.csv', na.strings = 'null')
+TB <- na.omit(TB)
+
+## Volatility Index
+getSymbols('^VIX', from = "2000-01-01")
+VIX <- as.data.frame(VIX)
+VIX <- na.omit(VIX)
+VIX <- VIX %>% mutate(Date = rownames(VIX))
+
+
 ## inflation adjustment
-getSymbols("CPIAUCSL", src='FRED')
+getSymbols("CPIAUCSL", src = 'FRED')
 avg.cpi <- apply.yearly(CPIAUCSL, mean)
 inflation_adj <- as.numeric(avg.cpi['2020'])/avg.cpi
 inflation_adj <- as.data.frame(inflation_adj)
@@ -38,21 +64,21 @@ inflation_adj <- inflation_adj %>% mutate(year = 1947:2020)
 # Data Preparation
 COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% rename(COP_Close = COP.Close)
 GSPC_close <- GSPC %>% dplyr::select(GSPC.Close, Date) %>% rename(GSPC_Close = GSPC.Close)
-COP_close <- merge(COP_close, GSPC_close)
-COP_close <- merge(COP_close, WTI_Crude)
[…]

### 2020-08-20 manuscript/manuscript.tex
minor edits to manuscript; we are almost done!

@@
     We develop a forecasting methodology for providing credible forecasts for time series that have recently undergone a shock.
-We achieve this by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded.
+We achieve this by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcomes are observed.
 Three shock effect estimators are motivated with the aim of minimizing average forecast risk.
 We propose risk-reduction propositions that provide conditions that establish when our methodology works.
-Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential prospective success of post-shock forecasts.
-Leave-one-out cross validation with $k$ random draws is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality.
+Bootstrap and leave-one-out cross validation procedures are provided to prospectively assess the performance of our methodology.
 Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
@@
 The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop.
-We also motivate a simple leave-one-out cross validation with $k$ random draws procedure which can prospectively assess the performance of our shock effect adjustment estimators.
+We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators.
 This prospective assessment does not require the observation of the post-shock response.
@@
     \item Under $\mc{M}_{21}$, 
-    \begin{align*}
+    $
       \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1}
-      \quad \text{ and } \quad 
+    $
+    and
+    $
        \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} .
-    \end{align*}
+    $
     \item Under $\mc{M}_{22}$,
-    \begin{align*}
+    $
       \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1}
-      \quad \text{ and } \quad 
+    $
+    and
+    $
        \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} .
-    \end{align*}
+    $
   \end{enumerate}
@@
 Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$.
-Notice that under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$ (see distributional details of $\alpha_1$ in Section \ref{modelsetup}).
+However, under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$.
 Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$.
-Thus, we collect these results  as the following proposition.
+We collect these results in the following proposition.
 
@@
 Section
- \ref{loocv} describes  leave-one-out cross validation with $k$ random draws procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study.
+ \ref{loocv} describes our leave-one-out cross validation procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study.
 Our simulations verify these procedures.
@@
 \end{align*}
-where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using the bootstrap and leave-one-out cross validation with $k$ random draws techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
+where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using bootstrap and leave-one-out cross validation procedures developed in Sections \ref{varbootstrap} and \ref{loocv}.
 
@@
 
+There are some philosophical distinctions between $\mc{B}_u$ and $\mc{B}_f$.
+$\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
+In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
+A double bootstrap procedure with similar steps can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
+The double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, can check whether a bootstrap percentile interval of resampled estimates of $\Delta(\hat{\alpha})$ contain 0 at a desired error threshold.
+We investigated such a double bootstrap procedure and found that it produced inferences that were similar to those produced using the bootstrap techniques developed in the main text.
+
 We stress that our bootstrap approximations cannot alleviate the inherent bias of using our adjustment estimators as surrogates for $\alpha_1$.
@@
 Non-uniqueness might be a concern theoretically.
-It is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$'s all targeting on the same $\alpha_1$.
+This is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$'s all targeting on the same $\alpha_1$.
 For example, consider the case where the size of  donor pool to be 2, $\var{\hat{\alpha}_2}=1$, $\var{\hat{\alpha}_3}=2$, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
@@
 It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}).
-However, non-uniqueness of $\mathbf{W}^*$ would not be a problem for inferential purposes.
-This is because all risk-reduction propositions and other properties established will still hold.
-Simulation examples listed in the Section 4 of the Supplementary Materials verify this point.
+Simulations in the Section 4 of the Supplementary Materials provide some evidence that non-uniqueness of $\mathbf{W}^*$ is not problematic for inferences.
 
@@
 
+We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population in these simulations.
+Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
+In this scenario, $\mathbf{W}^*$ will take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
+When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$.
+However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
+Moreover, simulations in Section 4 of the Supplementary Materials show that non-uniqueness does not seriously compromise the inference.
+
 \section{Forecasting Conoco Phillips stock in the presence of shocks}
@@
 We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$.
-The model of $\alpha_i$ incorporates daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange (CBOE) volatility index.
-In contrast, the model of $y_{i,t}$ disregards CBOE volatility index.
-It is because CBOE volatity index is a metric for capturing market risk and  sentiment, which can be highly related to the shock effect that results from investor behavior.
-It is not favorable in the model of $y_{i,t}$ since it may hinder  the estimation of $\alpha_i$.
+The model of $\alpha_i$ incorporates daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX).
+The model for $y_{i,t}$ disregards VIX.
+This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
 \item[(3)] {\bf Construction of donor pool}.
@@
 
-We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, and they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
+We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well.
+Our estimation framework misses the yet to be observed pot-shock response, however they perform much better than unadjusted forecasts that do not account for shock effects.
 The unadjusted forecast misses the post-shock response by 9.870 dollars whereas
@@
 
-There have been several other recent  methods developed for forecasting COVID-19 cases.
+\section{Discussion}
+\label{discussion}
+
+We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock.
+Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
+There have been several other recent similar methods developed for forecasting COVID-19 cases.
 For example, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries.
@@
 \citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
-They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
+They also provided useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
 Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
 
-\section{Discussion}
-\label{discussion}
-
-We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock.
-Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
 We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings.
@@
 Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
-%for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.
-
 Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
@@
 
-We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population in the simulation examples.
-Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
-In this scenario, $\mathbf{W}^*$ will take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$.
-However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
-But it does not seriously compromise the inference according to our simulation results in Section 4 in the Supplementary Materials.
-
-Note that there are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_f$.
-$\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
-
-%Double bootstrap can also be employed as an alternative to the bootstrap procedure proposed in Section \ref{varbootstrap}. 
-A double bootstrap procedure with similar steps to the bootstrap technique in Section~\ref{varbootstrap} can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
-The double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, can check whether a bootstrap percentile interval of resampled estimates of $\Delta(\hat{\alpha})$ contain 0 at a desired error threshold.
-We investigated such a double bootstrap procedure and found that it produced inferences that were similar to those produced using the bootstrap techniques developed in the main text.
-
 \section{Appendix}

### 2020-08-20 Rcode/comp.R
removal of slashes in the histogram

@@ -153,7 +153,7 @@ tikz('alphahist.tex', standAlone = TRUE, width = 8, height = 3.5)
 # plot
 par(mar = c(4, 4, 1, 2))
 # Histogram
-hist(mu.alpha.hat, breaks = 15, col = 'deepskyblue', 
+hist(mu.alpha.hat, breaks = 15, col = 'white', border = 'deepskyblue', 
      xlab = '$\\hat{\\alpha}_i$', plot = TRUE,
      density = TRUE, main = '')
 abline(v = alpha.hat, col = 'magenta')
@@ -164,4 +164,8 @@ text(x = 11.6, y = 6.7,
      labels = paste0('$\\displaystyle \\hat{\\alpha} = \\frac{1}{n}\\sum_{i=1}^{n} \\hat{\\alpha}_i= \\;$',
                      round(alpha.hat, digits = 2)))
 dev.off()
+
+
+hist(mu.alpha.hat, breaks = 15, plot = TRUE, col = 'white', border = 'deepskyblue', angle = 0)
+
 

### 2020-08-25 manuscript/manuscript.tex
revisions to comments; see major revision in the last paragraph of discussion and model setup

@@
 \usepackage[linesnumbered, ruled,vlined]{algorithm2e}
+\usepackage{pdflscape}
 % margin setup
@@
 We assume that the disparate time series are independent from the time series under study before the timing of the shock.
-We also assume that the shock effects for each disparate time series are independent realizations from some unknown distribution with existing first and second moments.
+Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing first and second moments.
 
@@
 
-In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure.
+In this article, we will assume a simple autoregressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure.
 Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
@@
 The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-Our auto regressive model will consider present day covariates to better motivate similarity weighting.
+Our autoregressive model will consider present day covariates to better motivate similarity weighting.
 The considered adjustment strategies all target the mean of the shock effect distribution.
@@
 \begin{align*}
-  \eta_i &\simiid  \; \E{\eta_i} = 0, \var{\eta_i} = \sigma^2_{\eta}\\
-  \phi_i &\simiid \; |\phi_i|<1, \\
-   \theta_i &\simiid  \; \E{\theta_i}=\mu_{\theta}, \var{\theta_i}=\Sigma_{\theta}^2 \\
-\alpha_i &\simiid \; \E{\alpha_i}=\mu_{\alpha}, \var{\alpha_i}=\sigma_{\alpha}^2, \\
-\varepsilon_{i,t} &\simiid \; \E{\varepsilon_{i,t}} =0, \var{\varepsilon_{i,t}}=\sigma^2 \where \sigma > 0 ,  \\
+  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}\\
+  \phi_i &\simiid \mrm{Uniform}(-1,1), \\
+   \theta_i &\simiid \mc{F}_{\theta} \text{ with }  \; \mrm{E}_{\mc{F}_{\theta}}(\theta_i) = \mu_{\theta}, \mrm{Var}_{\mc{F}_{\theta}}(\theta_i)  = \Sigma^2_{\theta} \\
+\alpha_i &\simiid \mc{F}_{\alpha} \text{ with }  \; \mrm{E}_{\mc{F}_{\alpha}}(\alpha_i) = \mu_{\alpha}, \mrm{Var}_{\mc{F}_{\alpha}}(\alpha_i)  = \sigma^2_{\alpha}  \\
+\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t})  = \sigma^2 \where \sigma > 0 ,  \\
 \eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t}.
@@
 \begin{align*}
-\t{\varepsilon}_{i} &\simiid  \E{\t{\varepsilon}}=0, \var{\t{\varepsilon}}=\sigma^2_{\alpha} \where \sigma_{\alpha}>0\\
+\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha} \where \sigma_{\alpha}>0\\
 \eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
@@
 \begin{align*}
-\delta_i \overset{iid}{\sim}\;  \mrm{E}(\delta) = \mu_\delta, \var{\delta} = \Sigma_\delta
+\delta_i\simiid  \mc{F}_{\delta} \text{ with }\mrm{E}_{\mc{F}_{\delta}}(\delta_i)=\mu_{\delta}, \mrm{Var}_{\mc{F}_{\delta}}(\delta_i)=\Sigma_\delta 
    \quad \text{ with } \quad  \delta_i  \indep \t{\varepsilon}_{i}.
@@
 $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
-Conditional on all regression parameters, previous responses, and covariates, 
-the response variable $y_{i,t}$ in $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ 
-has distribution 
-$$
-  y_{i,t} 
-    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
-      , \sigma^2).
-$$
 For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares 
@@
 % Though in Section \ref{modelsetup} we assume $\mbf{x}_{i,t}\in \reals^p$ and bases construction for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$  on this fact, we will shortly show that the covariates need not be of the same dimension across disparate time series.
-In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
+\label{remark1}In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
  % We can insert $\mathbf{0}$ into the covariates of disparate time series for the parts that they do not share.
@@
 Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$
-because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our auto regressive model formulation.
+because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
 
@@
 In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.
-Results are displayed in Table~\ref{table1}.
+Results are displayed in Table~\ref{table1} in the Appendix \ref{tablesappendix}.
 
@@
 Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.
-Results are  in Table~\ref{table2}.
-
-\begin{table}[h]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table1}
-\begin{center}
-\resizebox{\textwidth-1.2cm}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.91 (0.02) & 0.9 (0.03) & 53.23 (4.1) & 15.88 (2.1) & 16.78 (2.37) & 15.82 (2.07) \\ 
-    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.89 (0.03) & 0.9 (0.03) & 0.89 (0.03) & 53.01 (4.47) & 17.83 (2.38) & 19.56 (2.56) & 17.61 (2.36) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.74 (0.04) & 0.81 (0.04) & 0.75 (0.04) & 53.38 (5.92) & 26.44 (3.8) & 29.06 (4) & 26.11 (3.75) \\ 
-    & 50  & 0.83 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.64 (0.05) & 0.59 (0.05) & 61.68 (7.73) & 46 (6.31) & 47.3 (7.14) & 45.25 (6.32) \\ 
-    & 100  & 0.7 (0.09) & 0.87 (0.06) & 0.7 (0.09) & 0.53 (0.05) & 0.54 (0.05) & 0.53 (0.06) & 85.68 (12.95) & 87.25 (11.86) & 87.07 (13.63) & 85.65 (12.02)\\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
-    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
-   \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 51.11 (3.05) & 14.94 (2.36) & 14.09 (2.37) & 15.09 (2.35) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.91 (0.02) & 52.34 (3.19) & 15.64 (2.73) & 15.29 (2.74) & 15.89 (2.68) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.73 (0.04) & 0.76 (0.04) & 0.73 (0.04) & 56.03 (5.2) & 25.49 (3.85) & 27.38 (3.87) & 25.27 (3.84) \\ 
-    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.56 (0.04) & 0.6 (0.04) & 0.57 (0.04) & 71.37 (7.76) & 47.25 (6.42) & 52.06 (6.57) & 46.41 (6.43) \\ 
-    & 100  & 0.63 (0.09) & 0.67 (0.09) & 0.63 (0.09) & 0.52 (0.04) & 0.42 (0.04) & 0.53 (0.04) & 111.91 (13.83) & 92.95 (12.34) & 103.13 (12.74) & 91.07 (12.37) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.94 (0.02) & 0.93 (0.02) & 47.79 (2.93) & 14.83 (1.72) & 14.83 (2.04) & 14.76 (1.72) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.91 (0.02) & 0.89 (0.03) & 47.93 (3.25) & 16.55 (1.89) & 17.55 (2.12) & 16.53 (1.88) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.82 (0.03) & 0.83 (0.03) & 49.78 (5.01) & 26.42 (3.38) & 29.11 (3.4) & 26.45 (3.35) \\ 
-    & 50  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.64 (0.05) & 0.63 (0.05) & 0.64 (0.05) & 62.64 (7.4) & 48.84 (6.4) & 52.67 (6.28) & 48.8 (6.35) \\ 
-    & 100  & 0.83 (0.07) & 0.8 (0.07) & 0.83 (0.07) & 0.57 (0.05) & 0.59 (0.05) & 0.59 (0.05) & 103.37 (12.23) & 97.81 (12.52) & 102.4 (12.49) & 97.63 (12.45) \\
-\end{tabular}}
-   \end{center}
-      \vspace{-.5cm}
-\end{table}
+Results are  in Table~\ref{table2} in the Appendix \ref{tablesappendix}.
 
@@
 
-\begin{table}[H]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table2}
-\begin{center}
-\resizebox{\textwidth-1.2cm}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.97 (0.01) & 0.95 (0.02) & 48.84 (3.4) & 15.72 (1.93) & 15.32 (1.94) & 15.72 (1.93) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.94 (0.02) & 0.92 (0.03) & 49.54 (3.73) & 17.07 (2.01) & 16.08 (2.16) & 17.12 (1.99) \\ 
-    & 25  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.77 (0.02) & 0.81 (0.03) & 0.77 (0.03) & 51.78 (5.22) & 24.78 (2.57) & 26.12 (2.49) & 24.62 (2.54) \\ 
-    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.61 (0.04) & 0.59 (0.05) & 58.62 (7.74) & 40.09 (4.7) & 47.09 (4.09) & 39.85 (4.58) \\ 
-    & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.73 (0.08) & 0.5 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 82.66 (12.19) & 72.83 (9.75) & 89.03 (9.15) & 72.31 (9.5) \\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
-    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.04) & 0.76 (0.03) & 0.7 (0.04) & 50.09 (8.27) & 38.1 (5.75) & 37.98 (5.5) & 38.44 (5.76) \\ 
-    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.69 (0.04) & 0.74 (0.03) & 0.69 (0.04) & 50.82 (8.15) & 37.63 (5.61) & 36.33 (5.64) & 37.99 (5.61) \\ 
-    & 25  & 0.9 (0.06) & 0.9 (0.06) & 0.9 (0.06) & 0.62 (0.04) & 0.64 (0.04) & 0.61 (0.04) & 53.01 (8.22) & 38.78 (5.29) & 36.82 (5.76) & 38.88 (5.31) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.53 (0.04) & 58.9 (9.12) & 46.77 (5.54) & 50.61 (5.71) & 46.6 (5.51) \\ 
-    & 100  & 0.7 (0.09) & 0.9 (0.06) & 0.67 (0.09) & 0.51 (0.03) & 0.56 (0.04) & 0.5 (0.03) & 79.64 (12.21) & 72.76 (8.79) & 89.48 (7.98) & 72.17 (8.59) \\[.3cm] 
-   \multirow{5}{*}{50} & 5  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.04) & 0.59 (0.04) & 71.22 (13) & 70.31 (10.4) & 72.3 (9.26) & 70.79 (10.45) \\ 
-    & 10  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.05) & 0.6 (0.05) & 70.85 (12.91) & 69.43 (10.22) & 70.65 (9.29) & 69.94 (10.26) \\ 
-    & 25  & 0.7 (0.09) & 0.73 (0.08) & 0.7 (0.09) & 0.54 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 70.32 (12.81) & 67.61 (9.86) & 67 (9.58) & 68.06 (9.89) \\ 
-    & 50  & 0.67 (0.09) & 0.7 (0.09) & 0.67 (0.09) & 0.51 (0.05) & 0.51 (0.04) & 0.51 (0.05) & 74.01 (12.66) & 68.69 (9.63) & 67.9 (10.21) & 68.91 (9.64) \\ 
-    & 100  & 0.5 (0.09) & 0.6 (0.09) & 0.47 (0.09) & 0.47 (0.05) & 0.49 (0.04) & 0.45 (0.05) & 92.71 (13.06) & 83.66 (10.79) & 94.53 (11.2) & 83.56 (10.63)\\[.3cm] 
-   \multirow{5}{*}{100} & 5  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.06) & 0.57 (0.05) & 0.49 (0.06) & 130.47 (22.59) & 135.16 (19.73) & 141.42 (16.98) & 136.3 (19.72) \\ 
-    & 10  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.05) & 0.53 (0.05) & 0.51 (0.06) & 129.49 (22.49) & 134.09 (19.52) & 139.69 (16.96) & 135.26 (19.51) \\ 
-    & 25  & 0.47 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.53 (0.06) & 0.57 (0.05) & 0.51 (0.06) & 127.17 (22.22) & 131.43 (18.97) & 134.47 (17.22) & 132.42 (18.99) \\ 
-    & 50  & 0.5 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.48 (0.06) & 0.56 (0.04) & 0.48 (0.05) & 125.72 (21.8) & 129.27 (18.16) & 129.59 (17.59) & 130.27 (18.15) \\ 
-    & 100  & 0.47 (0.09) & 0.47 (0.09) & 0.43 (0.09) & 0.43 (0.06) & 0.57 (0.04) & 0.47 (0.06) & 128.38 (21.86) & 130.05 (18.05) & 131.83 (19.08) & 130.33 (18.06) \\
-\end{tabular}}
-   \end{center}
-      \vspace{-.5cm}
-\end{table}
-
 From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$   decreases, which is a pattern similar to the one shown in the first experiment.
@@
 
-Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented. See Table \ref{table3} and Table \ref{table4} for results. Comparing Table \ref{table1}
+Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented.
+See Table \ref{table3} and Table \ref{table4} for results in the Appendix \ref{tablesappendix}.
+Comparing Table \ref{table1}
  and Table \ref{table2} yields that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
@@
 Under $\mc{M}_1$, simple averaging, aimed for a reduction of variance, or inverse-variance weighting, targeting on reducing negative effects from varying time lengths, may work better.
-
-\begin{table}[H]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table3}
-\begin{center}
-\resizebox{\textwidth-1.2cm}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}} $  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.92 (0.02) & 0.89 (0.03) & 48.52 (3.93) & 15.74 (2.34) & 15.76 (2.34) & 15.16 (2.24) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.91 (0.02) & 0.89 (0.02) & 47.7 (4.35) & 18.26 (2.37) & 18.97 (2.42) & 17.68 (2.28) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.79 (0.03) & 0.81 (0.03) & 0.77 (0.03) & 46.95 (6.11) & 27.35 (3.81) & 30.88 (3.84) & 26.58 (3.83) \\ 
-  & 50  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.62 (0.03) & 0.65 (0.03) & 0.63 (0.03) & 56.85 (8.64) & 46.96 (7.02) & 52.92 (7.45) & 45.95 (7.17) \\ 
-  & 100  & 0.73 (0.08) & 1 (0) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.55 (0.04) & 99.22 (12.84) & 93.4 (12.97) & 103.82 (14.1) & 91.95 (13.34) \\[.3cm]  
- \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
-  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29) \\[.3cm] 
- \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.92 (0.03) & 0.95 (0.02) & 52.1 (2.96) & 14.04 (1.78) & 13.36 (2.07) & 14.11 (1.76) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.9 (0.03) & 0.93 (0.02) & 52.25 (3.3) & 15.12 (1.93) & 14.24 (2.29) & 15.18 (1.9) \\ 
-    & 25  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.8 (0.03) & 0.8 (0.03) & 0.8 (0.03) & 52.71 (5.28) & 22.98 (2.9) & 22.6 (3.42) & 22.95 (2.88) \\ 
-    & 50  & 0.7 (0.09) & 0.9 (0.06) & 0.7 (0.09) & 0.65 (0.03) & 0.65 (0.03) & 0.65 (0.04) & 58.65 (8.48) & 39.51 (5.65) & 40.8 (6.3) & 39.35 (5.63) \\ 
-    & 100  & 0.6 (0.09) & 0.87 (0.06) & 0.6 (0.09) & 0.47 (0.05) & 0.45 (0.04) & 0.45 (0.05) & 88.76 (13.66) & 75.93 (11.52) & 81.89 (12.19) & 75.94 (11.41) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.55 (2.9) & 12.13 (1.77) & 14.22 (1.96) & 12.09 (1.77) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.95 (0.02) & 0.93 (0.02) & 49.13 (3.31) & 14.78 (1.85) & 18.21 (2) & 14.75 (1.85) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.02) & 0.85 (0.02) & 0.83 (0.03) & 47.38 (5.13) & 26.85 (3.33) & 32.95 (3.59) & 26.81 (3.32) \\ 
-    & 50  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.61 (0.04) & 0.71 (0.04) & 0.62 (0.04) & 56.73 (7.93) & 50.96 (6.63) & 60.62 (7.21) & 50.88 (6.59) \\ 
-    & 100  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.49 (0.05) & 0.51 (0.04) & 0.49 (0.05) & 93.79 (14.67) & 102.05 (13.37) & 116.45 (15.19) & 101.55 (13.38) \\
-\end{tabular}}
-   \end{center}
-      \vspace{-.5cm}
-\end{table}
-
-\begin{table}[H]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table4}
-\begin{center}
-\resizebox{\textwidth-1.2cm}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.04 (3.65) & 21.75 (4.34) & 22.68 (4.41) & 21.83 (4.34) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.92 (0.02) & 0.93 (0.02) & 49.93 (4.11) & 24.3 (4.44) & 25.72 (4.58) & 24.4 (4.45) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.73 (0.04) & 0.8 (0.03) & 0.73 (0.04) & 51.29 (5.39) & 32.8 (5.25) & 35.39 (5.78) & 33.11 (5.21) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.49 (0.04) & 0.44 (0.05) & 0.47 (0.04) & 82.55 (11.61) & 84.26 (12.7) & 98.66 (13.96) & 84.62 (12.59) \\[.3cm] 
- \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
-  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29)\\[.3cm] 
- \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.03) & 0.73 (0.03) & 0.71 (0.04) & 57.87 (8.76) & 50.31 (7.58) & 57.25 (7.75) & 50.53 (7.64) \\ 
-  & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.68 (0.04) & 0.69 (0.04) & 0.69 (0.04) & 58.41 (9.11) & 51.62 (7.91) & 58.61 (8.28) & 51.85 (7.98) \\ 
-  & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.63 (0.04) & 0.68 (0.04) & 0.63 (0.04) & 62.02 (10.02) & 59.08 (8.53) & 65.55 (9.64) & 59.68 (8.53) \\ 
-  & 50  & 0.87 (0.06) & 0.9 (0.06) & 0.87 (0.06) & 0.54 (0.04) & 0.59 (0.04) & 0.52 (0.04) & 71.01 (11.73) & 73.52 (10.18) & 81.81 (11.98) & 74.51 (10.09) \\ 
-  & 100  & 0.73 (0.08) & 0.87 (0.06) & 0.73 (0.08) & 0.47 (0.05) & 0.45 (0.04) & 0.5 (0.05) & 95.93 (15.59) & 104.49 (15.12) & 119.38 (17.62) & 105.72 (14.97) \\[.3cm] 
- \multirow{5}{*}{50} & 5  & 0.8 (0.07) & 0.77 (0.08) & 0.8 (0.07) & 0.52 (0.04) & 0.49 (0.05) & 0.52 (0.04) & 85.95 (14.57) & 90.02 (13.45) & 103.03 (13.91) & 90.08 (13.64) \\ 
-  & 10  & 0.8 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.55 (0.05) & 0.5 (0.04) & 0.53 (0.05) & 86.44 (14.95) & 90.89 (13.79) & 104.62 (14.28) & 91.03 (13.98) \\ 
-  & 25  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.53 (0.04) & 0.46 (0.04) & 0.53 (0.04) & 90.26 (15.82) & 95.36 (14.69) & 109.53 (15.69) & 95.79 (14.83) \\ 
-  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.48 (0.05) & 0.45 (0.05) & 0.45 (0.05) & 99.52 (17.26) & 106.52 (16.17) & 120.99 (18.13) & 107.55 (16.19) \\ 
-  & 100  & 0.57 (0.09) & 0.77 (0.08) & 0.63 (0.09) & 0.41 (0.04) & 0.45 (0.03) & 0.41 (0.04) & 123.11 (20.61) & 135.24 (19.74) & 151.62 (23.42) & 137.21 (19.55) \\[.3cm] 
- \multirow{5}{*}{100} & 5  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.48 (0.05) & 0.48 (0.03) & 0.47 (0.05) & 156.82 (26.36) & 170.06 (25.92) & 196.4 (26.55) & 170.13 (26.27) \\ 
-  & 10  & 0.63 (0.09) & 0.57 (0.09) & 0.67 (0.09) & 0.46 (0.05) & 0.47 (0.03) & 0.47 (0.05) & 157.3 (26.76) & 170.93 (26.21) & 197.96 (26.87) & 171.07 (26.56) \\ 
-  & 25  & 0.67 (0.09) & 0.63 (0.09) & 0.67 (0.09) & 0.44 (0.04) & 0.5 (0.03) & 0.45 (0.04) & 160.32 (27.73) & 173.66 (27.22) & 202.61 (28.01) & 174.28 (27.48) \\ 
-  & 50  & 0.67 (0.09) & 0.67 (0.09) & 0.67 (0.09) & 0.39 (0.04) & 0.43 (0.03) & 0.38 (0.04) & 166.98 (29.35) & 182.83 (28.37) & 210.38 (30.48) & 183.67 (28.61) \\ 
-  & 100  & 0.6 (0.09) & 0.67 (0.09) & 0.53 (0.09) & 0.4 (0.04) & 0.45 (0.04) & 0.41 (0.05) & 188.29 (32.07) & 203.7 (31.63) & 233.44 (35.31) & 205.4 (31.72) \\
-\end{tabular}}
-   \end{center}
-      \vspace{-.5cm}
-\end{table}
 
@@
 From another perspective, it is possible that the stock of Conoco Phillips actually experienced multiple shocks on 2020 March 9th.
-For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector auto regressive model.
+For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector autoregressive model.
 Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.
@@
 The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
+Additionally, $\alpha_i$ can be heteroskedastic; i.e.,  they can have different variances.
+In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply.
 We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts.
@@
 
+Construction of donor pool is a critical step that directly matters in prediction.
+In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for  varying variances and  varying means that are linear functions of common covariates.
+Remark \ref{remark1} shows that common covariates are not restrictive with structural zero in coefficients.
+However, it is difficult to verify such assumption or structure in practice.
+In principle, one should select identities that come from a common population, which is also the one  the identity under study come from, as candidates in donor pool.
+This selection criterion is often adopted in the literature of comparative case studies.
+For example, \citet{card1990impact} used a set of cities in southern U.S.
+to estimate the effect of 1980 Mariel Boatlift on the Miami labor market.
+\citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country.
+To estimate the effect of Proposition 99, a large tabacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period.
+Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.
+
 \section{Appendix}
@@
 
+\subsection{Tables for Section \ref{simulation}}
+\label{tablesappendix}
+\newpage
+
+\begin{landscape}
+\begin{table}[b]
+\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table1}
+\begin{center}
+\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
+ $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
+  \hline
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.91 (0.02) & 0.9 (0.03) & 53.23 (4.1) & 15.88 (2.1) & 16.78 (2.37) & 15.82 (2.07) \\ 
+    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.89 (0.03) & 0.9 (0.03) & 0.89 (0.03) & 53.01 (4.47) & 17.83 (2.38) & 19.56 (2.56) & 17.61 (2.36) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.74 (0.04) & 0.81 (0.04) & 0.75 (0.04) & 53.38 (5.92) & 26.44 (3.8) & 29.06 (4) & 26.11 (3.75) \\ 
+    & 50  & 0.83 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.64 (0.05) & 0.59 (0.05) & 61.68 (7.73) & 46 (6.31) & 47.3 (7.14) & 45.25 (6.32) \\ 
+    & 100  & 0.7 (0.09) & 0.87 (0.06) & 0.7 (0.09) & 0.53 (0.05) & 0.54 (0.05) & 0.53 (0.06) & 85.68 (12.95) & 87.25 (11.86) & 87.07 (13.63) & 85.65 (12.02)\\[.3cm] 
+   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
+    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
+    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
+   \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 51.11 (3.05) & 14.94 (2.36) & 14.09 (2.37) & 15.09 (2.35) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.91 (0.02) & 52.34 (3.19) & 15.64 (2.73) & 15.29 (2.74) & 15.89 (2.68) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.73 (0.04) & 0.76 (0.04) & 0.73 (0.04) & 56.03 (5.2) & 25.49 (3.85) & 27.38 (3.87) & 25.27 (3.84) \\ 
+    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.56 (0.04) & 0.6 (0.04) & 0.57 (0.04) & 71.37 (7.76) & 47.25 (6.42) & 52.06 (6.57) & 46.41 (6.43) \\ 
+    & 100  & 0.63 (0.09) & 0.67 (0.09) & 0.63 (0.09) & 0.52 (0.04) & 0.42 (0.04) & 0.53 (0.04) & 111.91 (13.83) & 92.95 (12.34) & 103.13 (12.74) & 91.07 (12.37) \\[.3cm] 
+   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.94 (0.02) & 0.93 (0.02) & 47.79 (2.93) & 14.83 (1.72) & 14.83 (2.04) & 14.76 (1.72) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.91 (0.02) & 0.89 (0.03) & 47.93 (3.25) & 16.55 (1.89) & 17.55 (2.12) & 16.53 (1.88) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.82 (0.03) & 0.83 (0.03) & 49.78 (5.01) & 26.42 (3.38) & 29.11 (3.4) & 26.45 (3.35) \\ 
+    & 50  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.64 (0.05) & 0.63 (0.05) & 0.64 (0.05) & 62.64 (7.4) & 48.84 (6.4) & 52.67 (6.28) & 48.8 (6.35) \\ 
+    & 100  & 0.83 (0.07) & 0.8 (0.07) & 0.83 (0.07) & 0.57 (0.05) & 0.59 (0.05) & 0.59 (0.05) & 103.37 (12.23) & 97.81 (12.52) & 102.4 (12.49) & 97.63 (12.45) \\
+\end{tabular}}
+   \end{center}
+\end{table}
+\end{landscape}
+
+\begin{landscape}
+\begin{table}[b]
+\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table2}
+\begin{center}
+\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
+ $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
+  \hline
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.97 (0.01) & 0.95 (0.02) & 48.84 (3.4) & 15.72 (1.93) & 15.32 (1.94) & 15.72 (1.93) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.94 (0.02) & 0.92 (0.03) & 49.54 (3.73) & 17.07 (2.01) & 16.08 (2.16) & 17.12 (1.99) \\ 
+    & 25  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.77 (0.02) & 0.81 (0.03) & 0.77 (0.03) & 51.78 (5.22) & 24.78 (2.57) & 26.12 (2.49) & 24.62 (2.54) \\ 
+    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.61 (0.04) & 0.59 (0.05) & 58.62 (7.74) & 40.09 (4.7) & 47.09 (4.09) & 39.85 (4.58) \\ 
+    & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.73 (0.08) & 0.5 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 82.66 (12.19) & 72.83 (9.75) & 89.03 (9.15) & 72.31 (9.5) \\[.3cm] 
+   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
+    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
+    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
+    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
+   \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.04) & 0.76 (0.03) & 0.7 (0.04) & 50.09 (8.27) & 38.1 (5.75) & 37.98 (5.5) & 38.44 (5.76) \\ 
+    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.69 (0.04) & 0.74 (0.03) & 0.69 (0.04) & 50.82 (8.15) & 37.63 (5.61) & 36.33 (5.64) & 37.99 (5.61) \\ 
+    & 25  & 0.9 (0.06) & 0.9 (0.06) & 0.9 (0.06) & 0.62 (0.04) & 0.64 (0.04) & 0.61 (0.04) & 53.01 (8.22) & 38.78 (5.29) & 36.82 (5.76) & 38.88 (5.31) \\ 
+    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.53 (0.04) & 58.9 (9.12) & 46.77 (5.54) & 50.61 (5.71) & 46.6 (5.51) \\ 
+    & 100  & 0.7 (0.09) & 0.9 (0.06) & 0.67 (0.09) & 0.51 (0.03) & 0.56 (0.04) & 0.5 (0.03) & 79.64 (12.21) & 72.76 (8.79) & 89.48 (7.98) & 72.17 (8.59) \\[.3cm] 
+   \multirow{5}{*}{50} & 5  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.04) & 0.59 (0.04) & 71.22 (13) & 70.31 (10.4) & 72.3 (9.26) & 70.79 (10.45) \\ 
+    & 10  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.05) & 0.6 (0.05) & 70.85 (12.91) & 69.43 (10.22) & 70.65 (9.29) & 69.94 (10.26) \\ 
+    & 25  & 0.7 (0.09) & 0.73 (0.08) & 0.7 (0.09) & 0.54 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 70.32 (12.81) & 67.61 (9.86) & 67 (9.58) & 68.06 (9.89) \\ 
+    & 50  & 0.67 (0.09) & 0.7 (0.09) & 0.67 (0.09) & 0.51 (0.05) & 0.51 (0.04) & 0.51 (0.05) & 74.01 (12.66) & 68.69 (9.63) & 67.9 (10.21) & 68.91 (9.64) \\ 
+    & 100  & 0.5 (0.09) & 0.6 (0.09) & 0.47 (0.09) & 0.47 (0.05) & 0.49 (0.04) & 0.45 (0.05) & 92.71 (13.06) & 83.66 (10.79) & 94.53 (11.2) & 83.56 (10.63)\\[.3cm] 
+   \multirow{5}{*}{100} & 5  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.06) & 0.57 (0.05) & 0.49 (0.06) & 130.47 (22.59) & 135.16 (19.73) & 141.42 (16.98) & 136.3 (19.72) \\ 
+    & 10  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.05) & 0.53 (0.05) & 0.51 (0.06) & 129.49 (22.49) & 134.09 (19.52) & 139.69 (16.96) & 135.26 (19.51) \\ 
+    & 25  & 0.47 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.53 (0.06) & 0.57 (0.05) & 0.51 (0.06) & 127.17 (22.22) & 131.43 (18.97) & 134.47 (17.22) & 132.42 (18.99) \\ 
+    & 50  & 0.5 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.48 (0.06) & 0.56 (0.04) & 0.48 (0.05) & 125.72 (21.8) & 129.27 (18.16) & 129.59 (17.59) & 130.27 (18.15) \\ 
+    & 100  & 0.47 (0.09) & 0.47 (0.09) & 0.43 (0.09) & 0.43 (0.06) & 0.57 (0.04) & 0.47 (0.06) & 128.38 (21.86) & 130.05 (18.05) & 131.83 (19.08) & 130.33 (18.06) \\
+\end{tabular}}
+   \end{center}
+\end{table}
+\end{landscape}
+
+\begin{landscape}
+\begin{table}[b]
+\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table3}
+\begin{center}
+\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
+ $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}} $  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
+  \hline
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.92 (0.02) & 0.89 (0.03) & 48.52 (3.93) & 15.74 (2.34) & 15.76 (2.34) & 15.16 (2.24) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.91 (0.02) & 0.89 (0.02) & 47.7 (4.35) & 18.26 (2.37) & 18.97 (2.42) & 17.68 (2.28) \\ 
+  & 25  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.79 (0.03) & 0.81 (0.03) & 0.77 (0.03) & 46.95 (6.11) & 27.35 (3.81) & 30.88 (3.84) & 26.58 (3.83) \\ 
+  & 50  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.62 (0.03) & 0.65 (0.03) & 0.63 (0.03) & 56.85 (8.64) & 46.96 (7.02) & 52.92 (7.45) & 45.95 (7.17) \\ 
+  & 100  & 0.73 (0.08) & 1 (0) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.55 (0.04) & 99.22 (12.84) & 93.4 (12.97) & 103.82 (14.1) & 91.95 (13.34) \\[.3cm]  
+ \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
+  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
+  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29) \\[.3cm] 
+ \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.92 (0.03) & 0.95 (0.02) & 52.1 (2.96) & 14.04 (1.78) & 13.36 (2.07) & 14.11 (1.76) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.9 (0.03) & 0.93 (0.02) & 52.25 (3.3) & 15.12 (1.93) & 14.24 (2.29) & 15.18 (1.9) \\ 
+    & 25  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.8 (0.03) & 0.8 (0.03) & 0.8 (0.03) & 52.71 (5.28) & 22.98 (2.9) & 22.6 (3.42) & 22.95 (2.88) \\ 
+    & 50  & 0.7 (0.09) & 0.9 (0.06) & 0.7 (0.09) & 0.65 (0.03) & 0.65 (0.03) & 0.65 (0.04) & 58.65 (8.48) & 39.51 (5.65) & 40.8 (6.3) & 39.35 (5.63) \\ 
+    & 100  & 0.6 (0.09) & 0.87 (0.06) & 0.6 (0.09) & 0.47 (0.05) & 0.45 (0.04) & 0.45 (0.05) & 88.76 (13.66) & 75.93 (11.52) & 81.89 (12.19) & 75.94 (11.41) \\[.3cm] 
+   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.55 (2.9) & 12.13 (1.77) & 14.22 (1.96) & 12.09 (1.77) \\ 
+    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.95 (0.02) & 0.93 (0.02) & 49.13 (3.31) & 14.78 (1.85) & 18.21 (2) & 14.75 (1.85) \\ 
+    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.02) & 0.85 (0.02) & 0.83 (0.03) & 47.38 (5.13) & 26.85 (3.33) & 32.95 (3.59) & 26.81 (3.32) \\ 
+    & 50  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.61 (0.04) & 0.71 (0.04) & 0.62 (0.04) & 56.73 (7.93) & 50.96 (6.63) & 60.62 (7.21) & 50.88 (6.59) \\ 
+    & 100  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.49 (0.05) & 0.51 (0.04) & 0.49 (0.05) & 93.79 (14.67) & 102.05 (13.37) & 116.45 (15.19) & 101.55 (13.38) \\
+\end{tabular}}
+   \end{center}
+      \vspace{-.5cm}
+\end{table}
+\end{landscape}
+
+\begin{landscape}
+\begin{table}[b]
+\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table4}
+\begin{center}
+\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
+ $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
+  \hline
+ \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.04 (3.65) & 21.75 (4.34) & 22.68 (4.41) & 21.83 (4.34) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.92 (0.02) & 0.93 (0.02) & 49.93 (4.11) & 24.3 (4.44) & 25.72 (4.58) & 24.4 (4.45) \\ 
+  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.73 (0.04) & 0.8 (0.03) & 0.73 (0.04) & 51.29 (5.39) & 32.8 (5.25) & 35.39 (5.78) & 33.11 (5.21) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.49 (0.04) & 0.44 (0.05) & 0.47 (0.04) & 82.55 (11.61) & 84.26 (12.7) & 98.66 (13.96) & 84.62 (12.59) \\[.3cm] 
+ \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
+  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
+  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
+  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
+  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29)\\[.3cm] 
+ \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.03) & 0.73 (0.03) & 0.71 (0.04) & 57.87 (8.76) & 50.31 (7.58) & 57.25 (7.75) & 50.53 (7.64) \\ 
+  & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.68 (0.04) & 0.69 (0.04) & 0.69 (0.04) & 58.41 (9.11) & 51.62 (7.91) & 58.61 (8.28) & 51.85 (7.98) \\ 
+  & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.63 (0.04) & 0.68 (0.04) & 0.63 (0.04) & 62.02 (10.02) & 59.08 (8.53) & 65.55 (9.64) & 59.68 (8.53) \\ 
+  & 50  & 0.87 (0.06) & 0.9 (0.06) & 0.87 (0.06) & 0.54 (0.04) & 0.59 (0.04) & 0.52 (0.04) & 71.01 (11.73) & 73.52 (10.18) & 81.81 (11.98) & 74.51 (10.09) \\ 
+  & 100  & 0.73 (0.08) & 0.87 (0.06) & 0.73 (0.08) & 0.47 (0.05) & 0.45 (0.04) & 0.5 (0.05) & 95.93 (15.59) & 104.49 (15.12) & 119.38 (17.62) & 105.72 (14.97) \\[.3cm] 
+ \multirow{5}{*}{50} & 5  & 0.8 (0.07) & 0.77 (0.08) & 0.8 (0.07) & 0.52 (0.04) & 0.49 (0.05) & 0.52 (0.04) & 85.95 (14.57) & 90.02 (13.45) & 103.03 (13.91) & 90.08 (13.64) \\ 
+  & 10  & 0.8 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.55 (0.05) & 0.5 (0.04) & 0.53 (0.05) & 86.44 (14.95) & 90.89 (13.79) & 104.62 (14.28) & 91.03 (13.98) \\ 
+  & 25  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.53 (0.04) & 0.46 (0.04) & 0.53 (0.04) & 90.26 (15.82) & 95.36 (14.69) & 109.53 (15.69) & 95.79 (14.83) \\ 
+  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.48 (0.05) & 0.45 (0.05) & 0.45 (0.05) & 99.52 (17.26) & 106.52 (16.17) & 120.99 (18.13) & 107.55 (16.19) \\ 
+  & 100  & 0.57 (0.09) & 0.77 (0.08) & 0.63 (0.09) & 0.41 (0.04) & 0.45 (0.03) & 0.41 (0.04) & 123.11 (20.61) & 135.24 (19.74) & 151.62 (23.42) & 137.21 (19.55) \\[.3cm] 
+ \multirow{5}{*}{100} & 5  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.48 (0.05) & 0.48 (0.03) & 0.47 (0.05) & 156.82 (26.36) & 170.06 (25.92) & 196.4 (26.55) & 170.13 (26.27) \\ 
+  & 10  & 0.63 (0.09) & 0.57 (0.09) & 0.67 (0.09) & 0.46 (0.05) & 0.47 (0.03) & 0.47 (0.05) & 157.3 (26.76) & 170.93 (26.21) & 197.96 (26.87) & 171.07 (26.56) \\ 
+  & 25  & 0.67 (0.09) & 0.63 (0.09) & 0.67 (0.09) & 0.44 (0.04) & 0.5 (0.03) & 0.45 (0.04) & 160.32 (27.73) & 173.66 (27.22) & 202.61 (28.01) & 174.28 (27.48) \\ 
+  & 50  & 0.67 (0.09) & 0.67 (0.09) & 0.67 (0.09) & 0.39 (0.04) & 0.43 (0.03) & 0.38 (0.04) & 166.98 (29.35) & 182.83 (28.37) & 210.38 (30.48) & 183.67 (28.61) \\ 
+  & 100  & 0.6 (0.09) & 0.67 (0.09) & 0.53 (0.09) & 0.4 (0.04) & 0.45 (0.04) & 0.41 (0.05) & 188.29 (32.07) & 203.7 (31.63) & 233.44 (35.31) & 205.4 (31.72) \\
+\end{tabular}}
+   \end{center}
+\end{table}
+\end{landscape}
+
 \bibliographystyle{plainnat}

### 2020-08-26 manuscript/manuscript.tex
edits to presentation

@@
 % title
-\title{Minimizing post-shock forecasting error using disparate information}
+\title{Minimizing post-shock forecasting error through aggregation of borrowed information}
 \author{Jilei Lin\thanks{jileil2@ilinois.edu} }
@@
     We develop a forecasting methodology for providing credible forecasts for time series that have recently undergone a shock.
-We achieve this by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcomes are observed.
+We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
 Three shock effect estimators are motivated with the aim of minimizing average forecast risk.
@@
 Companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis, but they only have recent sales data for which the company is operating well.
-All is not lost in this setting, one may be able to supplement the present forecast with past data borrowed from disparate time series which contain similar structural shocks.
-The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from disparate time series, and then incorporate the aggregated shock effect estimator into the present forecast.
-Our method of combining disparate shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
+All is not lost in this setting, one may be able to supplement the present forecast with past data borrowed from other time series which contain similar structural shocks.
+The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
+Our method of combining shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
 
@@
 
-In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past.
+In our methodological framework, the researcher creates a synthetic panel of time series which have undergone similar structural shocks in the past.
 Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
-As in SCM, care is needed when forming the donor pool of disparate time series.
+As in SCM, care is needed when forming the donor pool of time series.
 However, there are key differences between our framework and SCM.
-We assume that the disparate time series are independent from the time series under study before the timing of the shock.
+We assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock.
 Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing first and second moments.
 
-We estimate the shock effects that are present in the disparate time series for which post-shock responses are observed.
+We estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed.
 We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest.
@@
 The context in \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
-In our context, the yet to observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the disparate time series.
+In our context, the yet to be observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the time series forming the donor pool.
 
@@
 However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method.
-%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point.
 We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting.
@@
      \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$.
-(a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given $n=40$ disparate time series.
+(a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series.
 (b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.
-The magenta dots represent $\hat{\alpha}_i$ from disparate time series.
+The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool.
 The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=10.22$.
@@
 This figure depicts a time series that experienced a shock at time point $T_1^*+1 = 126$.
-It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded.
+It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations from a donor pool of forty time series that have previously undergone a similar shock for which post-shock responses are recorded.
 Similarity in this context means that the shock effects are random variables that from a common distribution.
-%As we can see, the purple line provides a better prediction than the red line in this particular example.
-But we will justify later that consideration of estimated shock effects will improve the prediction under certain conditions.
 In this example, the mean of the estimated shock effects is taken as a shock effect estimator for the time series under study.
@@
 Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
-for $i = 1, \ldots, n+1$.  %Although synthesizing information from disparate time series assumes similarities of shock effects, shock effects may differ in terms of their means in practice. 
+for $i = 1, \ldots, n+1$.
 We also consider a model where the shock effects are linear functions of covariates with an additional additive mean-zero error.
-%Additionally, $\mc{M}_1$ can be further improved in the sense that the shock effects may depend on the covariates around the shock time points, i.e., $T_i^*$ for $i = 1, \ldots, n+1$. 
-%$\mc{M}_2$ can be constructed to accommodate those issues by imposing additional structures on the means of $\alpha_i$ as in (\ref{model2}) for $i = 1, \ldots, n+1$.
 For $i = 1, \ldots, n+1$, the random effects structure for this model (model $\mc{M}_2$) is:
@@
 $y_{1,t}$, $t = 1,\ldots T_1^*$. Instead, they only differ in predicting 
-$y_{1,T_1^*+1}$. Throughout the rest of this article we show that the collection of 
-disparate time series $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$ has 
+$y_{1,T_1^*+1}$. Throughout the rest of this article we show that the donor pool of time series $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$ has 
 the potential to improve the forecasts for $y_{1, T_1^*+1}$ under  different 
@@
 
-We now construct the aggregated estimators of the shock effects that appear in 
-Forecast 2 (see Section \ref{forecast}). We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.  %Notice that the shock effect 
-%for time series $1$ is typically unobserved. But we can gather knowledge from 
-%disparate time series to construct some sort of estimators that may be helpful for 
-%estimating $\E{\alpha_1}$. 
-First, we introduce the procedures of parameter estimation for 
-$\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
-For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares 
-(OLS) using historical data of $t = 1, \ldots, T_i$.
+We now construct the aggregated estimators of the shock effects that appear in Forecast 2 (see Section \ref{forecast}).
+We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.
+First, we introduce the procedures of parameter estimation for $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}).
+For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares (OLS) using historical data of $t = 1, \ldots, T_i$.
 For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$.
-In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate
-of $\alpha_i$.  Note that parameter estimation 
-for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
-We emphasize that $\alpha_i$s are random variables but the OLS estimation is conditioned on the their realizations from some distribution.
+In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate of $\alpha_i$.
+Note that parameter estimation for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
+We emphasize that $\alpha_i$s are random variables, but the OLS estimation is conditioned on the realizations from some distribution.
 
@@
 Our objective is in predicting a post-shock response $y_{1,T_1^*+1}$ that is not yet 
-observed using disparate time series whose post-shock responses are observed.
+observed using other time series whose post-shock responses are observed.
 %However, the idea of merging information from  similar events (i.e., time series in our 
@@
 %should be similar to the time series of interest. 
-Our weighted-adjustment estimator will therefore perform well when the pool of 
-disparate time series posses similar covariates to the time series for which 
-no post-shock responses are observed. We compute $\mbf{W}^*$ as
+Our weighted-adjustment estimator will therefore perform well when the pool of time series posses similar covariates to the time series for which no post-shock responses are observed.
+We compute $\mbf{W}^*$ as
 \begin{align}
@@
 Initialize $y_{i,0}^{(b)}=y_{i,0}$ for all $i \in I^{(b)}$.
-Then, resample the residuals under models $\mc{M}_1$ or $\mc{M}_{2}$, compute the bootstrapped response  $y_{i,t}^{(b)}$ for   $t \in \{1, \ldots, T_i\}$ using the model estimated by original data,  and obtain shock effect estimators for each of the disparate time series for all $i \in I^{(b)}$.
+Then, resample the residuals under models $\mc{M}_1$ or $\mc{M}_{2}$, compute the bootstrapped response  $y_{i,t}^{(b)}$ for   $t \in \{1, \ldots, T_i\}$ using the model estimated by original data,  and obtain shock effect estimators for each of the time series in the donor pool for all $i \in I^{(b)}$.
 These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
@@
 In this analysis we make the following design considerations:
-
-%In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession.
-Specific interest is in predictions made after March 6, 2020, the Friday before the stock market crash on March 9, 2020.
-We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustments for the shock.
-%Section \ref{background} provides the justification for the first three steps.
-Section \ref{results} discusses the result of our forecast.
 
@@
 We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock.
-Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
+Our methodology is as follows: construct a synthetic panel of time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
 There have been several other recent similar methods developed for forecasting COVID-19 cases.

### 2020-08-26 manuscript/manuscript.tex
minor edits; will post on ArXiv now

@@
   \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}\\
-  \phi_i &\simiid \mrm{Uniform}(-1,1), \\
+  \phi_i &\simiid \mc{F}_{\phi} \text{ where } |\mc{F}_{\phi}| < 1, \\
    \theta_i &\simiid \mc{F}_{\theta} \text{ with }  \; \mrm{E}_{\mc{F}_{\theta}}(\theta_i) = \mu_{\theta}, \mrm{Var}_{\mc{F}_{\theta}}(\theta_i)  = \Sigma^2_{\theta} \\
@@
 
-We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response. It is important to note that in general $\hat{\alpha}$ 
-is not a consistent estimator of the unobserved $\alpha_1$ nor does it converge 
-to $\alpha_1$.  Despite these inferential shortcomings, adjustment of the forecast 
-for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has 
-the potential to lower forecast risk under several conditions corresponding to 
-different estimators of $\alpha_1$. % which will be discussed shortly.
+We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response.
+It is important to note that in general $\hat{\alpha}$ does not converge to $\alpha_1$ in any sense.
+Despite this shortcoming, adjustment of the forecast for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has the potential to lower forecast risk under several conditions corresponding to different estimators of $\alpha_1$.
+% which will be discussed shortly.
 
@@
 To make use of those conditions in practice, estimation is required.
-Sections \ref{varbootstrap} introduce parametric bootstrap, which estimates the involved parameters in those conditions and thus motivates prospective decision-making  about whether $\hat{\alpha}_i$ reduces the risk.
-Section
- \ref{loocv} describes our leave-one-out cross validation procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study.
+Sections \ref{varbootstrap} introduce a residual bootstrap procedure which estimates the involved parameters in those conditions and thus motivates prospective decision-making about whether $\hat{\alpha}_i$ reduces the risk.
+Section \ref{loocv} describes our leave-one-out cross validation procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study.
 Our simulations verify these procedures.
@@
 
-There are some philosophical distinctions between $\mc{B}_u$ and $\mc{B}_f$.
+We reiterate the philosophical distinction between $\mc{B}_u$ and $\mc{B}_f$.
 $\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
+In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness arises from parameters and idiosyncratic error.
 A double bootstrap procedure with similar steps can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
@@
 
-\subsection{Leave-one-out cross validation with $k$ random draws}
+\subsection{Leave-one-out cross validation}
 \label{loocv}
@@
 However, if we assume the mutual  independence structure, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
-In other words, mutual independence assumption is not related to  $\E{\mc{C}(\delta_{\hat{\alpha}})}$ (i.e., the intrinsic correctness) but its estimation.
+%In other words, mutual independence assumption is not related to  $\E{\mc{C}(\delta_{\hat{\alpha}})}$ (i.e., the intrinsic correctness) but its estimation.
 \end{remark}
@@
 In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.
-Results are displayed in Table~\ref{table1} in the Appendix \ref{tablesappendix}.
+Results are displayed in Table~\ref{table1} in the Appendix, Section \ref{tablesappendix}.
 
@@
 Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.
-Results are  in Table~\ref{table2} in the Appendix \ref{tablesappendix}.
+Results are  in Table~\ref{table2} in the Appendix, Section \ref{tablesappendix}.
 
@@
 Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented.
-See Table \ref{table3} and Table \ref{table4} for results in the Appendix \ref{tablesappendix}.
+See Table \ref{table3} and Table \ref{table4} for results in the Appendix, Section \ref{tablesappendix}.
 Comparing Table \ref{table1}
@@
 Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.
-Motivated by his study, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
+Motivated by \citet{kilian2009not}, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
 The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
@@
 As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
-But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
+But we note that consistency estimates from LOOCV may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
 %This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock effects in the donor pool.
@@
 If serial correlation exists in the data, various block bootstrapping procedures \citep{kunsch1989jackknife, liu1992moving} can be possible reasonable alternatives.
-Note that the pseudo time series generated by our proposed parametric bootstrap are not stationary.
-If stationarity is of concern, one can be referred to the stationary bootstrap invented by \citet{politis1994stationary} for stationary and weakly dependent time series.
+Note that the pseudo time series generated by our proposed residual bootstrap are not stationary.
+If stationarity is of concern, one can be referred to the stationary bootstrap in \citet{politis1994stationary} for stationary and weakly dependent time series.
 Nevertheless, it was shown that approximation accuracy might be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.
@@
 Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.
+
+\vspace*{0.5cm}\noindent{\bf Acknowledgements}: We are grateful to Forrest W. Crawford, Karl Oskar Ekvall, Soheil Eshghi, Lutz Kilian, Ziyu Liu, Dootika Vats, and Dave Zhao for helpful comments.
 

### 2020-08-27 Submission/letter.tex
addition of letter

\documentclass[11pt]{article}

\usepackage{tikz}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{color}
\usepackage[export]{adjustbox}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\usepackage{geometry}
\geometry{margin=1in}

\renewcommand*\arraystretch{1.05}

\begin{document}

\footnotesize
%\color{lightblue}
\begin{tikzpicture}
  \node at (0,0) {\includegraphics[height=1.1in, keepaspectratio = true]{UI.png}};
  \node at (13.4, -0.05) {\vspace{1cm}\begin{tabular}{l}
      \\ \sc Jilei Lin \\
       \it Graduate Student \\
       \it Department of Statistics \\
       University of Illinois \\
       Daniels Hall, Room 0506A \\
	   1010 W. Green St \\
	   Urbana, IL 61820 \\
       \texttt{jileil2@illinois.edu} \\ 
       \end{tabular} };
\end{tikzpicture}

\normalsize

Dear editor,

We are excited to submit our manuscript ``Minimizing post-shock forecasting error through aggregation of outside information'' for possible publication at the  International Journal of Forecasting.

In this manuscript, we  develop a forecasting methodology for providing credible forecasts for time series that are known to  experience a shock in the future. It is a general methodology that has various potential real-life applications in forecasting during  \emph{unprecedented} time. We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed. We construct three shock effect estimators  with the aim of minimizing average forecast risk. We propose risk-reduction propositions that provide conditions that establish when our methodology works. Bootstrap and leave-one-out cross validation procedures are provided to prospectively evaluate those conditions and estimate corresponding correctness. We use a real data example of forecasting Conoco Phillips stock price during the time  of   oil price control and COVID-19 pandemicto verify  our methodology.

We confirm that this manuscript is only under consideration at the International Journal of Forecasting. Thank you for your consideration.

Sincerely,

Jilei Lin \\
Daniel J. Eck

\end{document}

### 2020-08-28 Submission/letter.tex
updated letter to the editor; forgot to compile the pdf file, can you do that, sorry

@@
 
-In this manuscript, we  develop a forecasting methodology for providing credible forecasts for time series that are known to  experience a shock in the future.
-It is a general methodology that has various potential real-life applications in forecasting during  \emph{unprecedented} time.
-We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
-We construct three shock effect estimators  with the aim of minimizing average forecast risk.
+In this manuscript, we  develop forecasting methodology for providing credible forecasts for time series that are known to have undergone a recent shock for which no post-shock data is observed.
+Our methodology has various potential real-life applications in many forecasting settings.
+
+We construct credible forecasts by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
 We propose risk-reduction propositions that provide conditions that establish when our methodology works.
-Bootstrap and leave-one-out cross validation procedures are provided to prospectively evaluate those conditions and estimate corresponding correctness.
-We use a real data example of forecasting Conoco Phillips stock price during the time  of   oil price control and COVID-19 pandemicto verify  our methodology.
+Bootstrap and leave-one-out cross validation procedures are provided to prospectively evaluate the performance of our methodology.
+
+We demonstrate the utility of our methodology with a real data analysis involving the forecasting of Conoco Phillips stock price during a time period of massive oil price volatility and increasing COVID-19 panic.
+We also provide several numerical examples that demonstrate the effectiveness of our prospective evaluation procedures.
 

### 2020-08-28 Submission/manuscript.tex
addition of manuscript

--- 2020-08-26 manuscript/manuscript.tex
@@
-\documentclass[11pt]{article}
-
-% use packages
+\documentclass[final,5p, twocolumn, authoryear]{elsarticle}
+
 \usepackage[utf8]{inputenc}
@@
 \usepackage{enumitem}
-\usepackage{url}
-\usepackage{authblk}
 \usepackage{bm}
 \usepackage[usenames]{color}
-\usepackage{hyperref}
-\usepackage{geometry}
 \usepackage{caption}
@@
 \usepackage{pdflscape}
-% margin setup
-\geometry{margin=0.8in}
+\PassOptionsToPackage{hyphens}{url}
+\usepackage{hyperref}
 
@@
 
-\allowdisplaybreaks
-
-% title
-\title{Minimizing post-shock forecasting error through aggregation of borrowed information}
-\author{Jilei Lin\thanks{jileil2@ilinois.edu} }
-\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
-\affil{Department of Statistics, University of Illinois at Urbana-Champaign}
-
-%%% New version of \caption puts things in smaller type, single-spaced 
-%%% and indents them to set them off more from the text.
-\makeatletter
-\long\def\@makecaption#1#2{
-  \vskip 0.8ex
-  \setbox\@tempboxa\hbox{\small {\bf #1:} #2}
-  \parindent 1.5em  %% How can we use the global value of this???
-  \dimen0=\hsize
-  \advance\dimen0 by -3em
-  \ifdim \wd\@tempboxa >\dimen0
-  \hbox to \hsize{
-    \parindent 0em
-    \hfil 
-    \parbox{\dimen0}{\def\baselinestretch{0.96}\small
-      {\bf #1.} #2
-      %%\unhbox\@tempboxa
-    } 
-    \hfil}
-  \else \hbox to \hsize{\hfil \box\@tempboxa \hfil}
-  \fi
-}
-\makeatother
+\journal{International Journal of Forecasting}
 
@@
 
-\maketitle
+\begin{frontmatter}
+
+\title{Minimizing post-shock forecasting error through aggregation of outside information}
+
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{}
+%% \address[label1]{}
+%% \address[label2]{}
+
+\author{Jilei Lin\corref{cor1}}
+
+\cortext[cor1]{Corresponding author.}
+
+\ead{jileil2@illinois.edu }
+
+\author{Daniels J. Eck \corref{}}
+
+\ead{dje13@illinois.edu}
+
+\address{Department of Statistics, University of Illinois, Champaign-Urbana, IL, United States}
+
 \begin{abstract}
@@
 \end{abstract}
+
+\begin{keyword}
+  Data Integration \sep 
+ Prospective forecasting \sep 
+ Risk reduction \sep 
+Residual bootstrap \sep 
+Cross validation 
+%% keywords here, in the form: keyword \sep keyword
+
+%% PACS codes here, in the form: \PACS code \sep code
+
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+
+\end{keyword}
+
+\end{frontmatter}
 
@@
 
-\begin{figure}[H]
+\begin{figure*}[t!]
   \begin{center}
-    \subfloat{\includegraphics[height = 7cm]{comp.pdf}}\\
-     \subfloat{\includegraphics[height = 7cm]{alphahist.pdf}}
+    \subfloat{\includegraphics[height = 5.5cm]{comp.pdf}}\\
+     \subfloat{\includegraphics[height = 5.5cm]{alphahist.pdf}}
   \end{center}
@@
 It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
-\end{figure}
+\end{figure*}
 
@@
 \alpha_i &\simiid \mc{F}_{\alpha} \text{ with }  \; \mrm{E}_{\mc{F}_{\alpha}}(\alpha_i) = \mu_{\alpha}, \mrm{Var}_{\mc{F}_{\alpha}}(\alpha_i)  = \sigma^2_{\alpha}  \\
-\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t})  = \sigma^2 \where \sigma > 0 ,  \\
-\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t}.
-\end{align*}
-Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
+\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t})  = \sigma^2  ,  \\
+\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t},
+\end{align*}
+where $\sigma > 0$. Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
 for $i = 1, \ldots, n+1$.
@@
 \begin{align*}
-\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha} \where \sigma_{\alpha}>0\\
+\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha}\\
 \eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
 \end{align*} 
-We further define 
+where $\sigma_a > 0$. We further define 
 $\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}$. 
@@
 where $\delta$ is a  fixed unknown parameter.
-We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects 
-structure for $\delta_i$:
-\begin{align*}
-\delta_i\simiid  \mc{F}_{\delta} \text{ with }\mrm{E}_{\mc{F}_{\delta}}(\delta_i)=\mu_{\delta}, \mrm{Var}_{\mc{F}_{\delta}}(\delta_i)=\Sigma_\delta 
-   \quad \text{ with } \quad  \delta_i  \indep \t{\varepsilon}_{i}.
+We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects :
+\begin{align*}
+&\delta_i\simiid  \mc{F}_{\delta} \text{ with }\mrm{E}_{\mc{F}_{\delta}}(\delta_i)=\mu_{\delta}, \mrm{Var}_{\mc{F}_{\delta}}(\delta_i)=\Sigma_\delta \\
+   & \delta_i  \indep \t{\varepsilon}_{i}.
 \end{align*}
@@
 \begin{align}
-  \begin{array}{lll}
-     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
-    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
-  \end{array}
+ \Theta &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon \label{parameter} \\
+ & \qquad  t= 1, \ldots, T_i, i = 2, \ldots, n +1\}, \nonumber \\
+    \Theta_1 &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon  \nonumber \\
+   & \qquad t= 1, \ldots, T_i, i = 1\}, \nonumber
 \end{align}
@@
 \begin{align*}
- \mbf{X}_1 = \mbf{x}_{1, T_1^*+1}',
+ \mbf{X}_1 &= \mbf{x}_{1, T_1^*+1}',
   \quad  
@@
     \mbf{x}_{n+1, T_{n+1}^*+1}'
-  \end{pmatrix},
-  \quad \text{and} \quad 
+  \end{pmatrix}, \\ 
   \hat{\mbf{X}}_1(\mbf{W}) 
-    = \mbf{W}'\mbf{X},
+   & = \mbf{W}'\mbf{X},
 \end{align*}
@@
 \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
+  &  \quad +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
-  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
+  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
+  &\quad + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
 \end{align*}
 \end{enumerate}
-Formal justification for these results can be found in Appendix.
+Formal justification for these results can be found in Appendix \ref{proofs}.
 Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$
@@
 From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
-\begin{equation} \label{varwadj}
+\begin{align} \label{varwadj}
 \var{\hat{\alpha}_{\rm wadj}}
- = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
-\end{equation}
+ &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 \nonumber \\
+ &< \mu_{\alpha}^2.
+\end{align}
 In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.
@@
 \var{\hat{\alpha}_{\rm wadj}}
- = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}) < (\E{\alpha_1})^2,
+& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} \\
+ &+ \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})  \\
+ &< (\E{\alpha_1})^2,
 \end{align*}
@@
 \begin{align*}
- \E{\alpha_1^2}= \var{\alpha_1}+(\E{\alpha_1})^2
+ \E{\alpha_1^2} &= \var{\alpha_1}+(\E{\alpha_1})^2\\
  &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
@@
 For example, Russia and OPEC began a battle for global oil price control on Sunday, March 8th \citep{sukhankin2020russian}, and several US states began declaring state of emergencies in response to the evolving coronavirus pandemic \citep{nygov, alonso2020state}.
-In this analysis we make the following design considerations:
-
-%\subsection{Background}
-%\label{background}
-
-%Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo}. %and with a relatively recent initial public offering \citep{conocohist}. 
-%Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control on the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}.
-Furthermore, fear and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
-Major events include the SXSW festival being cancelled as trading closed on March 6th \citep{wang2020impact}.
-New York declared a state of emergency on March 7th \citep{nygov}, and by Sunday, March 8th, eight states have declared a state of emergency \citep{alonso2020state} while Italy placed 16 million people in quarantine \citep{sjodin2020only}.
-
-%Economic indicators forecasted our recession before the coronavirus pandemic began.
-The current recession followed an inversion of the yield curve that first happened back in March, 2019 \citep{tokic2019yield}.
-An inversion of the yield curve is an event that signals likely recessions \citep{andolfatto2018yield, bauer2018economic}.
-In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
-We also consider previous OPEC oil supply shocks \citep{mensi2014opec}.
-We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models.
-Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}.
+
+We collect our data through the use of \texttt{quantmod} package \citep{ryan2017quantmod} in R. In this analysis we make the following design considerations:
 
@@
 
-\begin{figure}
+\begin{figure*}[t!]
   \begin{center}
@@
   \vspace{-.6cm}
-\end{figure}
+\end{figure*}
 
@@
 
-\vspace*{0.5cm}\noindent{\bf Acknowledgements}: We are grateful to Forrest W. Crawford, Karl Oskar Ekvall, Soheil Eshghi, Lutz Kilian, Ziyu Liu, Dootika Vats, and Dave Zhao for helpful comments.
+\section{Acknowledgement}
+
+This work was supported by the National Institutes of Health [NICHD DP2 HD091799-01].
+We are grateful to Forrest W.
+Crawford, Karl Oskar Ekvall, Soheil Eshghi, Lutz Kilian, Ziyu Liu, Dootika Vats, and Dave Zhao for helpful comments.
 
@@
 \begin{align*}
-\E{\hat{\alpha}_{\rm adj}} =\frac{1}{n}  \sum_{i=2}^{n+1} \E{\E{\hat{\alpha}_i|\Theta}} = \mu_{\alpha} 
-\quad \text{ and } \quad \E{\hat{\alpha}_{\rm wadj}}&= \sum_{i=2}^{n+1} w_i^* \E{\E{\hat{\alpha}_i|\Theta}}= \sum_{i=2}^{n+1} w_i^*\mu_{\alpha}= \mu_{\alpha}.
+\E{\hat{\alpha}_{\rm adj}} &=\frac{1}{n}  \sum_{i=2}^{n+1} \E{\E{\hat{\alpha}_i|\Theta}} = \mu_{\alpha} \\
+ \E{\hat{\alpha}_{\rm wadj}}&= \sum_{i=2}^{n+1} w_i^* \E{\E{\hat{\alpha}_i|\Theta}}= \sum_{i=2}^{n+1} w_i^*\mu_{\alpha}= \mu_{\alpha}.
 \end{align*}
@@
   \begin{align*}
-   \E{\hat{\alpha}_{\rm wadj}}= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}
+   \E{\hat{\alpha}_{\rm wadj}}
+   &= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}\\
    &= \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right)\\
@@
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
-  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
+  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
+ & \quad  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
 \end{align*}
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
+  & \quad  +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
 \end{align*}
@@
   \begin{align*}
-    C(\Theta_1) =\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} -(\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}),
+    C(\Theta_1) &=\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} \\
+    & \quad -(\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}),
   \end{align*}
@@
   \begin{align*}
-    R_{T_1^*+1,1}= \mrm{E}\big\{\big(C(\Theta_1)-\alpha_1\big)^2\big\}
-    \qquad \text{ and } 
-    \qquad  R_{T_1^*+1,2}= \mrm{E}\big\{\big(C(\Theta_1)+\hat{\alpha}-\alpha_1\big)^2\big\}.
+    R_{T_1^*+1,1}
+    &= \mrm{E}\big\{\big(C(\Theta_1)-\alpha_1\big)^2\big\}\\
+     R_{T_1^*+1,2} &=  \mrm{E}\big\{\big(C(\Theta_1)+\hat{\alpha}-\alpha_1\big)^2\big\}.
   \end{align*}
@@
 
+\section*{References}
 \bibliographystyle{plainnat}

### 2020-08-29 Submission/manuscript.tex
addition of codes and mentions in manuscript

@@
 
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
 \author{Jilei Lin\corref{cor1}}
@@
 Cross validation 
-%% keywords here, in the form: keyword \sep keyword
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
 \end{keyword}
@@
 In our context, the yet to be observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the time series forming the donor pool.
-
-%Therefore the traditional forecast combination framework may not be of any help.  
-%The Bayesian hierarchical approach of \citet{lee2020estimation} may be too sensitive to prior and the hierarchical parametric model setup.
-Overall, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock.
 
@@
 
-% Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock effect of the time series under study.
-
-%The question is then how to estimate the shock effects and improve the 
-%prediction?
-This paper proposes three estimators, the adjustment estimator, weighted adjustment estimator, and inverse-variance weighted estimators.
-Section (to be updated) discusses properties of those estimators.
-Section (to be updated) compares the  interplay between prediction risk and different shock effects estimators.
-Section (to be updated) conducts simulation to justify our claims and certain properties that cannot be found analytically.
-
 \begin{figure*}[t!]
@@
 
-%The forecast consists of three steps: (1) pick a model, (2) selection of covariates, (3) choices of donor pool.
 Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
@@
 
-%Section \ref{properties} will provide a more detailed treatment about when our proposed estimators in Section \ref{constructionofestimators} will improve the prediction under various model setups in Section \ref{modelsetup}.
-More examples will be provided using Monte Carlo simulations in Section \ref{simulation}.
-
-\subsection{Model Setup}
+\subsection{Model setup}
 
@@
 forecasts that do not account for the shock effect.
-%The interest of this study lies in comparing how consideration of shock effects 
-%improves the prediction. 
+
 More formally, we will consider the following candidate forecasts: 
@@
 incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study.
-%Under $\mc{M}_1$ (Section \ref{modelsetup}), $\E{\alpha_1} = \mu_{\alpha}$.
 
@@
 Despite this shortcoming, adjustment of the forecast for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has the potential to lower forecast risk under several conditions corresponding to different estimators of $\alpha_1$.
-% which will be discussed shortly.
 
@@
 is required and the numerator and denominator terms are dependent in general.
-%It is hard to evaluate its expectation and variance. 
-%But it is clear 
-%that $\hat{\alpha}_{\rm IVW}$ will generally not be unbiased. 
+
 However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in 
-practical settings. %when the change 
-%point is not symmetric and/or there are some series with small or large number 
-%of time points recorded. We will then investigate the performance of this 
-%estimator in simulation (Section \ref{simulation}).
+practical settings.
 We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ 
@@
 in \cite{abadie2010synthetic}. 
-%we intend to construct a weighted adjustment estimator by using similar but 
-%different methods. 
 However, our weighted-adjustment estimator is not a causal estimator and 
 our estimation premise is a reversal of that in SCM. 
-%The case study of \citet{abadie2010synthetic} in essence observes the data and 
-%estimates the effect of policy. 
 Our objective is in predicting a post-shock response $y_{1,T_1^*+1}$ that is not yet 
 observed using other time series whose post-shock responses are observed.
-%However, the idea of merging information from  similar events (i.e., time series in our 
-%study) to improve the solutions for the problem of interest should be the same.
 
@@
  \end{align*}
-%It is a reasonable assumption that the pool of time series that we are considering 
-%should be similar to the time series of interest. 
 Our weighted-adjustment estimator will therefore perform well when the pool of time series posses similar covariates to the time series for which no post-shock responses are observed.
@@
 \end{align}
-%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
 \cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
-so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
-%still hold approximately 
+so that (\ref{SCM}) holds approximately 
 and that weighted-adjustment estimation techniques of this form are not 
@@
 Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
-is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
-%we are mainly interested in constructing the following adjustment estimator:
+is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist.
 Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
@@
   \end{align*}
- %Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model.
-To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock.
-This model somehow accounts for the impact of past information on the shock effects.
  We further define
@@
 \begin{remark}
-% Though in Section \ref{modelsetup} we assume $\mbf{x}_{i,t}\in \reals^p$ and bases construction for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$  on this fact, we will shortly show that the covariates need not be of the same dimension across disparate time series.
 \label{remark1}In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
- % We can insert $\mathbf{0}$ into the covariates of disparate time series for the parts that they do not share.
-For example, suppose $\mathbf{x}_{2, t}, \mathbf{x}_{2, t-1}\in \reals^{p-1}$ and $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}\in \reals^p$ are the covariates for time series 2 and 3.
-Assume that the $p$th column of $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}$ is the part they do not share.
-In this case, we can let $\mathbf{x}^{adj}_{2, t}=(\mathbf{x}_{2, t}, \mathbf{0})$, $\mathbf{x}^{adj}_{2, t-1}=(\mathbf{x}_{2, t-1}, \mathbf{0})$ to satisfy the $p$-dimension requirement.
 However, it is not necessary that the all $p$ covariates are important for every time series under study.
 The regression coefficients $\theta_i$ are nuisance parameters that are not of primary importance.
-% In this regard, OLS estimations in software can reparameterize the design matrix.
-Of course, the column space of the design matrix does not change compared to the one in original dimension.
-Thus, the least squares estimators do not change.
-In other words, OLS estimation need no adjustment.
-The generalization may only apply to the construction of weighted-adjustment  estimator $\hat{\alpha}_{\rm wadj}$.
 It will be understood that structural 0s in $\theta_i$ correspond to variables that are unimportant. 
@@
 Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation for evaluation of these conditions.
-% for $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm wadj}$ to reduce risk, and make it more clear with respect to when one is better than the other.
 These conditions and bootstrap will be discussed in Section \ref{conditions} and \ref{varbootstrap}, respectively.
@@
 \end{enumerate}
-Formal justification for these results can be found in Appendix \ref{proofs}.
-Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$
+Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
 because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
@@
 In this section we will discuss the conditions for risk reduction for individual shock effects estimators under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-%The reason is that if the estimator of $\alpha_1$ turns out to be an unbiased estimator of $\E{\alpha_1}$, the conditions get  simplified.
 For an adjustment estimator $\hat{\alpha}$, we will write the risk-reduction as $\Delta(\hat{\alpha})=R_{T_1^*+1,1}-R_{T_1^*+1,2}$ where $R_{T_1^*+1,2}$ is the risk of Forecast 2 calculated using the adjustment estimator $\hat{\alpha}$.
@@
 In this setting, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$.
-% from Proposition \ref{proprisk}.
 From Proposition \ref{proprisk}, we obtain a risk-reduction condition
@@
 Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$ (see Forecast in Section \ref{forecast}); (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
-%This result is also intuitive.
-For example, if  $\mu_{\alpha}$ is large, Forecast 1 will definitely work poor because large  $\mu_{\alpha}$ implies shock effects that cannot be ignored.
-See Section \ref{forecast} for forecast formulation for details.
 
@@
 The shock effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$. 
-%It is a more reasonable and general model since it is often the case that shock effects differ by means among disparate time series in practice.
-$\mc{M}_{22}$  further adds the random effect structure of $\delta$ to  $\mc{M}_{21}$ for generalization.
 However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$. 
-%From Proposition \ref{varprop}, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$  will be as in Proposition \ref{propriskwadj2}.
 We now state conditions for risk-reduction.
@@
 \end{equation}
-
-%A simple mean-squares decomposition produces the following inequality for assessing the favorability of $\hat{\alpha}_{\rm wadj}$ to $\hat{\alpha}_{\rm adj}$ under models $\mc{M}_{21}$ and $\mc{M}_{22}$,
-% \begin{align*}
-%  \var{\hat{\alpha}_{\rm adj}} 
-%  -\var{\hat{\alpha}_{\rm wadj}} + \big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2> 0.
-%\end{align*}
-
-%If it turns out to be fact that the variance of the weighted-adjustment estimator is greater than that of adjustment estimator, we should be aware that  the compromise for variance because of using $\hat{\alpha}_{\rm wadj}$ shouldn't exceed the squared bias, i.e., $\big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2$.
 
@@
 where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using bootstrap and leave-one-out cross validation procedures developed in Sections \ref{varbootstrap} and \ref{loocv}.
-
-%%%%%%%%%%% Commenting out Section 3.2 %%%%%%%%%%%%
-%\subsection{Comparisons among estimators}
-%\label{comparisons}
-
-%In comparing  shock effects estimators, we would assume that the risk-reduction conditions are satisfied as in Section \ref{conditions}.
-
-%Denote the risk-reduction quantities for adjustment estimators as $\Delta_{\rm adj}$, $\Delta_{\rm IVW}$, and $\Delta_{\rm wadj}$, respectively for standard adjustment, inverse-variance weighted estimator, and weighted-adjustment estimato.
-%%%As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration.
-For example, if we find that $\Delta_{\rm wadj}>\Delta_{\rm adj}$ and $\Delta_{\rm wadj}>\Delta_{\rm IVW}$, the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ is the most favorable.
-%According to  discussion in Section \ref{conditionsm2122}, we know that under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, the risk-reduction quantity for $\hat{\alpha}_{\rm IVW}$ is
-%\begin{align*}
-%  \Delta_{\rm IVW} = (\E{\alpha_1})^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2.
-%\end{align*}
-%From discussions in Section \ref{conditions}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ differ across models, we will discuss in different cases accordingly.
-
-%\subsubsection{Under $\mc{M}_{1}$}
-
-%From Proposition \ref{proprisk}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
-%\begin{align*}
-%  \Delta_{\rm adj} 
-%  = \mu_{\alpha}^2 -\var{\hat{\alpha}_{\rm adj}}
-%\quad   \text{ and } \quad 
-%  \Delta_{\rm wadj} 
-%  = \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}.
-%\end{align*}
-%Under the framework of $\mc{M}_1$, the risk-reduction quantity  for $\hat{\alpha}_{\rm IVW}$ is
-%\begin{align*}
-%  \Delta_{\rm IVW} = \mu_{\alpha}^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2.
-%\end{align*}
-%In other words, when $\var{\hat{\alpha}_{\rm wadj}}<\var{\hat{\alpha}_{\rm adj}}$ and $\hat{\alpha}_{\rm wadj} < \var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2$, we would prefer $\hat{\alpha}_{\rm wadj}$ as the best estimator.
-Other conditions for voting the other estimators as the best one follow similarly.
-
-%\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}
-%\label{section322}
-
-%According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
-%\begin{align*}
-%  \Delta(\hat{\alpha}_{\rm adj})
-%  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
-%\quad   \text{ and } \quad 
-%  \Delta(\hat{\alpha}_{\rm wadj})
-%  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
-%\end{align*}
-%In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
-%\begin{align*}
-% \Delta(\hat{\alpha}_{\rm IVW})
-%  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
-%\end{align*}
-
-% These are some analytical results for comparison studies among estimators of $\alpha_1$.
-Next, we will detail a framework for estimation of risk-reduction  quantities using a parametric bootstrap routine.
-Therefore, the above inequalities can be analyzed numerically and risk-reduction quantities can be estimated using plug-in estimators in practice.
-
-%\begin{remark}
-%  In Section \ref{constructionofestimators}, we noted that $\mathbf{W}^*$ may not be unique if $2p < n$.
-However, Proposition \ref{proprisk} and \ref{propriskwadj2} will hold for  every $\hat{\alpha}_{\rm wadj}$ using  $\mathbf{W}^*$ that satisfies (\ref{SCM}).
-%\end{remark}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{align*}
-%  \Delta(\hat{\alpha}_{\rm adj})
-  %&= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
   \hat{\Delta}(\hat{\alpha}_{\rm adj}) & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
@@
 where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance estimator for $\Var(\hat{\alpha}_{\rm adj})$.
-
-%Suppose we have a pool of shock effect estimators, $\mc{A}$, e.g., $\mc{A}= \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ in our study.
-We can determine which one is the best shock effect estimator.
-Suppose the $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ and $\hat{\Delta}(\hat{\alpha}_{\rm IVW})$ are estimators for $\Delta(\hat{\alpha}_{\rm wadj}) $ and $\Delta(\hat{\alpha}_{\rm IVW})$, respectively.
-Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}(\hat{\alpha})>0$ for $\hat{\alpha}\in \mc{A}$.
-Besides, we can also select the best shock effect estimator accordingly.
-Define
-%\begin{align}
-%	\hat{\alpha}_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \hat{\Delta}(\hat{\alpha}) \quad \text{ and } \quad  \alpha_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \Delta(\hat{\alpha}).
-\label{best}
-%\end{align}
-%That is, the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities whereas $\alpha_{\rm best}$ is the true best shock effect estimator given observed post-shock response.
-See more discussions in Section \ref{loocv}.
 
@@
 \end{center} 
-%Similar definitions can be adapted to the best shock effect estimators. 
 \vspace*{0.3cm}
@@
 	= I(\delta_{\hat{\alpha}} \text{ is correct})
- %\quad \text{ and } \quad  	
- %\mc{C}(\mc{A}) 
-%	= I(\hat{\alpha}_{\rm best} = \alpha_{\rm best})
 $
@@
 However, it is possible to estimate $\E{\mc{C}(\delta_{\hat{\alpha}})}$ using LOOCV.
-%For each $\hat{\alpha}\in \mc{A}$ we can compute the consistency as $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ using the estimation procedures in Section \ref{varbootstrap}.
 The LOOCV estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$ are
@@
 \end{equation}
-where $\mc{J}$ is the set of the $k$ randomly sampled indicies.
-%Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively.
-The estimation bias should decrease as $k \to n$.
+where $\mc{J}$ is the set of the $k$ randomly sampled indices.
 
@@
 However, if we assume the mutual  independence structure, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
-%In other words, mutual independence assumption is not related to  $\E{\mc{C}(\delta_{\hat{\alpha}})}$ (i.e., the intrinsic correctness) but its estimation.
 \end{remark}
 
-\section{Numerical Examples}
+\section{Numerical examples}
 \label{simulation}
@@
 In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is moderately small; otherwise, they are similar.
-%See more discussions for differences between $\mc{B}_u$ and $\mc{B}_f$ in Section \ref{discussion}.
 
@@
 The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}.
-%The reasons for those three shocks are.
-%  \begin{enumerate}
-%  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities.
-On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank.
-The day of the announcement, the stocks of other major Wall Street firms tumbled (including Conoco Phillips).
-These concerns then spilled over into the broader universe of stocks \citep{shorter2008bear}.
-%In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
-%  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets.
-The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}.
-Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
-%  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}.
-During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors.
-During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}.
-%  \end{enumerate}
 \end{enumerate}
@@
 
-%\begin{table}[H]
-%  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table5}
-%  \begin{center}
-%    \begin{tabular}{lrrr}
-%      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
- %     \hline 
- %   Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
- %   \end{tabular}
- % \end{center}  
-%\end{table}
-%\vspace{-.5cm}
-
 The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-4.872$, $\hat{\alpha}_{\rm wadj}= -4.805$, and $\hat{\alpha}_{\rm IVW}=-4.384$.
@@
 The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.419, 0.559, and 0.667, respectively.
-%Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $32.452$, $32.690$, and $31.960$, respectively.
 We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
@@
 the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively.
-%Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
-Moreover, the risk-reduction quantities are consistent with the reality as well.
+
 The true shock effect is not fully recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$.
@@
 These additive adjustment estimators do extremely well in this additive shock setting.
-%There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.
-%This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.
 
@@
 But we note that consistency estimates from LOOCV may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
-%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock effects in the donor pool.
-%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 6$.
-%This generalization was adopted in Section \ref{forecasting}.
-In this case, the variance expressions proposed in Section \ref{properties} will not work.
-However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
+
 Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its first and second moments exist.
@@
 It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.
-
-% \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
-This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$ where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$; for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$.
-The sampling stops when $N$ observations are reached.
-Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d.
-discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d.
-geometric random variables with parameter $p$.
-However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}.
-Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$.
-This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.
 
@@
 Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.
+
+\section{Supplementary material}
+
+Supplementary material includes the results of  likelihood ratio test for  independence among nested shock effects in Section \ref{forecasting}, the algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$, simulation results for $\mc{M}_1$, and simulation results for an example of the boundary case $p < n$.
 

### 2020-08-29 Submission/dataanalysis.R

@@ -1,0 +1,678 @@
+# load packages
+library("data.table")
+library("tidyverse")
+library("tseries")
+library("quantmod")
+library('Rsolnp')
+library('msos')
+library('tikzDevice')
+library('xtable')
+
+# set working directory
+setwd("/Users/mac/Desktop/Research/Post-Shock Prediction/")
+
+## Conoco Phillips
+getSymbols('COP', from = "2000-01-01")
+COP <- as.data.frame(COP)
+COP <- COP %>% mutate(Date = rownames(COP))
+
+## S&P 500
+getSymbols('^GSPC', from = "1970-01-01")
+GSPC <- as.data.frame(GSPC)
+GSPC <- GSPC %>% mutate(Date = rownames(GSPC))
+
+## Brent Crude prices
+Brent_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/brent-daily_csv/data/d93216330ab2c27aae3d177b2f0f0921/brent-daily_csv.csv") %>%
+  rename(Oil_Close = Price)
+
+## WTI Crude prices
+WTI_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/wti-daily_csv/data/c414c9d375ec3c8f9d7c276d866fb2a4/wti-daily_csv.csv") %>%
+  rename(WTI_Close = Price)
+
+## Gold Price
+getSymbols('GC=F', from = "2000-01-01")
+gold <- as.data.frame(`GC=F`)
+gold <- na.omit(gold)
+gold <- gold %>% mutate(Date = rownames(gold))
+
+## Dollar Index
+getSymbols('DX-Y.NYB', from = "2000-01-01")
+USD <- as.data.frame(`DX-Y.NYB`)
+USD <- na.omit(USD)
+USD <- USD %>% mutate(Date = rownames(USD))
+
+## 13-Week T-Bill
+TB <- read.csv('^IRX.csv', na.strings = 'null')
+TB <- na.omit(TB)
+
+## Volatility Index
+getSymbols('^VIX', from = "2000-01-01")
+VIX <- as.data.frame(VIX)
+VIX <- na.omit(VIX)
+VIX <- VIX %>% mutate(Date = rownames(VIX))
+
+
+## inflation adjustment
+getSymbols("CPIAUCSL", src = 'FRED')
+avg.cpi <- apply.yearly(CPIAUCSL, mean)
[…]

### 2020-08-29 Submission/simulation.R

@@ -1,0 +1,1473 @@
+# OLS
+# this function returns the W^* estimated by synthetic control method (SCM)
+scm <- function(X, Tstar) {
+  # X is a list of covariates for disparate time series
+  # X[[1]] should be the covariate of the time series to predict
+  # X[[p]] for p = 2,...,n+1 are covariates for time series pool
+  
+  # T^* is a vector of shock-effects time points
+  # shock effect point must be > 2
+  
+  # package for constrained optiminization
+  require('Rsolnp')
+  
+  # number of time series for pool
+  n <- length(X) - 1
+  
+  # covariate for time series for prediction
+  X1 <- X[[1]][Tstar[1] + 1, , drop = FALSE]
+  
+  # covariates for time series pool
+  X0 <- c()
+  for (i in 1:n) {
+    X0[[i]] <- X[[i + 1]][Tstar[i + 1] + 1, , drop = FALSE]
+  }
+  
+  # objective function
+  weightedX0 <- function(W) {
+    # W is a vector of weight of the same length of X0
+    n <- length(W)
+    p <- ncol(X1)
+    XW <- matrix(0, nrow = 1, ncol = p)
+    for (i in 1:n) {
+      XW <- XW + W[i] * X0[[i]]
+    }
+    norm <- as.numeric(crossprod(matrix(X1 - XW)))
+    return(norm)
+  }
+  
+  # constraint for W
+  Wcons <- function(W) sum(W) - 1
+  
+  
+  # optimization
+  solnp(par = rep(1/n, n), fun = weightedX0, eqfun = Wcons, eqB = 0, 
+        LB = rep(0, n), UB = rep(1, n), control = list(trace = 0))
+}
+
+ols.est.alphahat <- function(Tstar, Y, X) {
+  
+  n <- length(Y) - 1
+  T <- c()
+  for (i in 1:(n + 1)) {
+    T <- c(T, length(Y[[i]]) - 1)
+  }
+  
+  # empty
+  alphahat <- c()
+  se <- c()
+  res <- c()
+  lmod <- c()
+  
+  
+  for (i in 2:(n + 1)) {
+    
+    # set up
+    Ti <- T[i]
[…]

### 2020-08-29 Submission/manuscript.tex
addition of codes and mentions in manuscript

@@
 
-Supplementary material includes the results of  likelihood ratio test for  independence among nested shock effects in Section \ref{forecasting}, the algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$, simulation results for $\mc{M}_1$, and simulation results for an example of the boundary case $p < n$.
+Supplementary material includes the results of  likelihood ratio test for  independence among nested shock effects in Section \ref{forecasting}, the algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$, simulation results for $\mc{M}_1$, simulation results for an example of the boundary case $p < n$, and R codes for corresponding simulations and data analysis.
 

### 2020-09-06 Submission/manuscript.tex
correction of names
double blind mode
addition of other submission materials

@@
-\documentclass[final,5p, twocolumn, authoryear]{elsarticle}
-
+\documentclass[11pt,3p,review,authoryear]{elsarticle}
 \usepackage[utf8]{inputenc}
@@
 
+\bibliographystyle{model5-names}
+\biboptions{longnamesfirst}
+
 \begin{document}
@@
 \title{Minimizing post-shock forecasting error through aggregation of outside information}
-
-\author{Jilei Lin\corref{cor1}}
-
-\cortext[cor1]{Corresponding author.}
-
-\ead{jileil2@illinois.edu }
-
-\author{Daniels J. Eck \corref{}}
-
-\ead{dje13@illinois.edu}
-
-\address{Department of Statistics, University of Illinois, Champaign-Urbana, IL, United States}
 
@@
   \begin{center}
-    \subfloat{\includegraphics[height = 5.5cm]{comp.pdf}}\\
-     \subfloat{\includegraphics[height = 5.5cm]{alphahist.pdf}}
+    \subfloat{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
+     \subfloat{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
   \end{center}
@@
   \begin{center}
-    \includegraphics[height = 9cm]{fig2.pdf}
+    \includegraphics[height = 9cm]{FIG2.pdf}
     \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price.}
@@
 
-\section{Acknowledgement}
-
-This work was supported by the National Institutes of Health [NICHD DP2 HD091799-01].
-We are grateful to Forrest W.
-Crawford, Karl Oskar Ekvall, Soheil Eshghi, Lutz Kilian, Ziyu Liu, Dootika Vats, and Dave Zhao for helpful comments.
-
 \section{Appendix}
@@
 \begin{center}
-\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
+\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
    &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
@@
 \section*{References}
-\bibliographystyle{plainnat}
 \bibliography{synthetic-prediction-notes}

### 2020-09-06 Submission/title.tex
addition of other submission materials

--- 2020-09-06 Submission/manuscript.tex
@@
+% Template for articles submitted to the International Journal of Forecasting
+% Further instructions are available at www.ctan.org/pkg/elsarticle
+% You only need to submit the pdf file, not the source files.
+% If your article is accepted for publication, you will be asked for the source files.
+
 \documentclass[11pt,3p,review,authoryear]{elsarticle}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amsfonts}
-%\usepackage{amscd}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{mathtools}
-\usepackage{natbib}
-\usepackage{enumitem}
-\usepackage{bm}
-\usepackage[usenames]{color}
-\usepackage{caption}
-\usepackage{float}
-\usepackage[caption = false]{subfig}
-\usepackage{tikz}
-\usepackage{multirow}
-\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
-\usepackage{pdflscape}
-\PassOptionsToPackage{hyphens}{url}
-\usepackage{hyperref}
-
-% function definition
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\w}{\textbf{w}}
-\newcommand{\x}{\textbf{x}}
-\newcommand{\X}{\textbf{X}}
-\newcommand{\Y}{\textbf{Y}}
-\newcommand{\Hist}{\mathcal{H}}
-\def\mbf#1{\mathbf{#1}} % bold but not italic
-\def\ind#1{\mathrm{1}(#1)} % indicator function
-\newcommand{\simiid}{\stackrel{iid}{\sim}} %[] IID 
-\def\where{\text{ where }} % where
-\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
-\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
-\def\mrm#1{\mathrm{#1}} % remove math
-\newcommand{\reals}{\mathbb{R}} % Real number symbol
-\def\t#1{\tilde{#1}} % tilde
-\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
-\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
-\def\v#1{\mbi{#1}} % Vector notation
-\def\mc#1{\mathcal{#1}} % mathical
-\DeclareMathOperator*{\argmax}{arg\,max} % arg max
-\DeclareMathOperator*{\argmin}{arg\,min} % arg min
-\def\E#1{\mathrm{E}(#1)} % Expectation symbol
-\def\var#1{\mathrm{Var}(#1)} % Variance symbol
-\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
-\newcommand\red[1]{{\color{red}#1}}
-
-\newcommand{\norm}[1]{\left\lVert#1\right\rVert} % A norm with 1 argument
-\DeclareMathOperator{\Var}{Var} % Variance symbol
-
-\newtheorem{cor}{Corollary}
-\newtheorem{lem}{Lemma}
-\newtheorem{thm}{Theorem}
-\newtheorem{defn}{Definition}
-\newtheorem{prop}{Proposition}
-\theoremstyle{definition}
-\newtheorem{remark}{Remark}
-\hypersetup{
-  linkcolor  = blue,
-  citecolor  = blue,
-  urlcolor   = blue,
-  colorlinks = true,
-} % color setup
-
-% proof to proposition 
-\newenvironment{proof-of-proposition}[1][{}]{\noindent{\bf
-    Proof of Proposition {#1}}
-  \hspace*{.5em}}{\qed\bigskip\\}
-% general proof of corollary
-  \newenvironment{proof-of-corollary}[1][{}]{\noindent{\bf
-    Proof of Corollary {#1}}
-  \hspace*{.5em}}{\qed\bigskip\\}
-% general proof of lemma
-  \newenvironment{proof-of-lemma}[1][{}]{\noindent{\bf
-    Proof of Lemma {#1}}
-  \hspace*{.5em}}{\qed\bigskip\\}
 
 \journal{International Journal of Forecasting}
-
 \bibliographystyle{model5-names}
 \biboptions{longnamesfirst}
+% Please use \citet and \citep for citations.
 
@@
 \title{Minimizing post-shock forecasting error through aggregation of outside information}
+
+  \author[uiuc]{Jilei Lin\corref{cor}}
+   \ead{jileil2@illinois.edu}
+
+ \author[uiuc]{Daniel J Eck}
+ \address[uiuc]{Department of Statistics, University of Illinois at Urbana-Champaign\\
+ 725 S. Wright St., Champaign, IL, 61820, U.S.}
+ \ead{dje13@illinois.edu}
+  \cortext[cor]{Corresponding author}
 
@@
 
-\section{Introduction}
-
-We provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
-We focus on the specific setting in which a structural shock has occurred and one desires a prediction for the post-shock response at the next time point.
-Standard forecasting methods may not yield accurate predictions in the presence of such structural shocks \citep{baumeister2014real}.
-This is a general problem that has many real life applications.
-For example, one may be interested in forecasting the stock price of a company tomorrow after hearing terrible or great news about the company  after hours trading.
-Companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis, but they only have recent sales data for which the company is operating well.
-All is not lost in this setting, one may be able to supplement the present forecast with past data borrowed from other time series which contain similar structural shocks.
-The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
-Our method of combining shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
-
-We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models.
-In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
-In this setting, the additive shock effect is a random effect that is parameterized in the autoregressive model.
-The shock effect is then estimated using ordinary least squares (OLS).
-The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}.
-One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}.
-Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}.
-On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects from outside data sources are all thought to arise from a  data generating process similar to that of the shock under study.
-For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks.
-
-In our methodological framework, the researcher creates a synthetic panel of time series which have undergone similar structural shocks in the past.
-Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
-As in SCM, care is needed when forming the donor pool of time series.
-However, there are key differences between our framework and SCM.
-We assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock.
-Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing first and second moments.
-
-We estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed.
-We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest.
-This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest.
-Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
-The context in \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
-In our context, the yet to be observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the time series forming the donor pool.
-
-In this article, we will assume a simple autoregressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure.
-Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
-However, our model formulation is more general than \cite{ramaswamy1993empirical}.
-In our model, the donor pool can consist of dependent time series but time series within the donor pool should be independent of the time series of interest.
-However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method.
-We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting.
-The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-Our autoregressive model will consider present day covariates to better motivate similarity weighting.
-The considered adjustment strategies all target the mean of the shock effect distribution.
-Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean.
-We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast.
-The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop.
-We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators.
-This prospective assessment does not require the observation of the post-shock response.
-Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.
-We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020.
-We will show that our proposed adjustment estimators yield much better results than no adjustment in this setting.
-We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts.
-We now motivate our framework for post-shock forecasting.
-
-\begin{figure*}[t!]
-  \begin{center}
-    \subfloat{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
-     \subfloat{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
-  \end{center}
-     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$.
-(a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series.
-(b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.
-The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool.
-The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=10.22$.
-It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
-\end{figure*}
-
-\section{Setting}
-\label{setting}
-
-We will suppose that a researcher has time series data ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$, where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
-Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection.
-We will suppose that specific interest is in forecasting the response after the occurrence of a structural shock.
-To gauge the performance of forecasts, we consider forecast risk in the form of MSE,
-$$
-  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2,
-$$
-and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.
-In this article, we focus on post-shock prediction where forecasts methods only differ at the next future time point.
-Thus the MSE reduces to the magnitude $\E{\hat y_{1,t} - y_{1,t}}^2$.
-
-Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
-In this article, we consider a dynamic panel data model with autoregressive structure similar to that in \citet{blundell1998initial}.
-Our dynamic panel model includes an additional shock effect whose presence or absence is given by the binary variable $D_{i,t}$, and we will assume that the donor pool time series are independent of the time series under study.
-The details of this model are in the next section.
-
-Figure \ref{figure1} provides a simple intuition of the practical usefulness of our proposed methodology.
-This figure depicts a time series that experienced a shock at time point $T_1^*+1 = 126$.
-It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations from a donor pool of forty time series that have previously undergone a similar shock for which post-shock responses are recorded.
-Similarity in this context means that the shock effects are random variables that from a common distribution.
-In this example, the mean of the estimated shock effects is taken as a shock effect estimator for the time series under study.
-Forecasts are then made by adding this shock effect estimator to the estimated response values obtained from the estimation procedure that ignores the shock.
-It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock effect.
-We evaluate the performance of this post-shock forecasting methodology throughout this article; we outline situations for when it is expected to work and when it is not.
-
-\subsection{Model setup}
-
-\label{modelsetup}
-
-In this section, we will describe the assumed dynamic panel models for which 
-post-shock aggregated estimators are provided. The basic structures of these models 
-are the same for all time-series in the analysis, the differences between them lie in the setup of the shock effect distribution.
-
-Let $I(\cdot)$ be an indicator function, $T_i$ be the time length of the time series $i$ for $i = 1, \ldots, n+1$, and $T_i^*$ be the time point just before the one when the shock is known to occur, with $T_i^* < T_i$.
-For $t= 1, \ldots, T_i$ and $i = 1, \ldots, n+1$, the model $\mc{M}_1$ is defined as
-\begin{align}
-\mc{M}_1 \colon y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\label{equation1}
-\end{align}
- where $D_{i,t} = I(t = T_i^* + 1)$ 
-and $\x_{i,t} \in \R^{p}$ with $p \geq 1$.  We assume that the 
-$\mbf{x}_{i,t}$'s are fixed. Let $|x|$ denote the absolute value of $x$ for $x\in \reals$. For $i = 1, \ldots, n+1$ and $t=1, \ldots, T_i$, the random effects structure for $\mc{M}_1$ is:
-\begin{align*}
-  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}\\
-  \phi_i &\simiid \mc{F}_{\phi} \text{ where } |\mc{F}_{\phi}| < 1, \\
-   \theta_i &\simiid \mc{F}_{\theta} \text{ with }  \; \mrm{E}_{\mc{F}_{\theta}}(\theta_i) = \mu_{\theta}, \mrm{Var}_{\mc{F}_{\theta}}(\theta_i)  = \Sigma^2_{\theta} \\
-\alpha_i &\simiid \mc{F}_{\alpha} \text{ with }  \; \mrm{E}_{\mc{F}_{\alpha}}(\alpha_i) = \mu_{\alpha}, \mrm{Var}_{\mc{F}_{\alpha}}(\alpha_i)  = \sigma^2_{\alpha}  \\
-\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t})  = \sigma^2  ,  \\
-\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t},
-\end{align*}
-where $\sigma > 0$. Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
-for $i = 1, \ldots, n+1$.
-We also consider a model where the shock effects are linear functions of covariates with an additional additive mean-zero error.
-For $i = 1, \ldots, n+1$, the random effects structure for this model (model $\mc{M}_2$) is:
-\begin{align}
-\mc{M}_2 \colon \begin{array}{l}
-  y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
-  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+ \t{\varepsilon}_{i},
-\end{array}\label{model2}
-\end{align}
- where the added random effects are
-\begin{align*}
-\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha}\\
-\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
-\end{align*} 
-where $\sigma_a > 0$. We further define 
-$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}$. 
-We will investigate the post-shock aggregated estimators in $\mc{M}_2$ 
-in settings where $\delta_i$ is either fixed or random. 
-We let $\mc{M}_{21}$ denote model $\mc{M}_{2}$ with $\delta_i = \delta$ for $i= 1, \ldots, n+1$, 
-where $\delta$ is a  fixed unknown parameter.
-We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects :
-\begin{align*}
-&\delta_i\simiid  \mc{F}_{\delta} \text{ with }\mrm{E}_{\mc{F}_{\delta}}(\delta_i)=\mu_{\delta}, \mrm{Var}_{\mc{F}_{\delta}}(\delta_i)=\Sigma_\delta \\
-   & \delta_i  \indep \t{\varepsilon}_{i}.
-\end{align*}
-We further define the parameter sets
-\begin{align}
- \Theta &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon \label{parameter} \\
- & \qquad  t= 1, \ldots, T_i, i = 2, \ldots, n +1\}, \nonumber \\
-    \Theta_1 &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon  \nonumber \\
-   & \qquad t= 1, \ldots, T_i, i = 1\}, \nonumber
-\end{align}
-where $\Theta$ and $\Theta_1$ can adapt to $\mc{M}_1$ by dropping $\delta_i$. We assume this for notational simplicity.
-
-\subsection{Forecast}
-\label{forecast}
-In this section we show how post-shock aggregate estimators improve upon standard 
-forecasts that do not account for the shock effect.
-
-More formally, we will consider the following candidate forecasts: 
-\begin{align*}
-  &\text{Forecast 1}: \hat y_{1,T_1^*+1}^1 = \hat\eta_1 
-    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
-    , \\
-  &\text{Forecast 2}: \hat y_{1,T_1^*+1}^2 = \hat\eta_1 
-    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
-    + \hat{\alpha},
-\end{align*}
-where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all OLS estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
-The first forecast ignores the presence of $\alpha_1$ while the second forecast 
-incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study.
-
-Note that the two forecasts do not differ in their predictions for 
-$y_{1,t}$, $t = 1,\ldots T_1^*$. Instead, they only differ in predicting 
-$y_{1,T_1^*+1}$. Throughout the rest of this article we show that the donor pool of time series $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$ has 
-the potential to improve the forecasts for $y_{1, T_1^*+1}$ under  different 
-circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-Improvement will be measured by assessing the reduction in risk that Forecast 2 offers over Forecast 1.
-We will return to the theoretical details of risk-reduction in Section \ref{properties}.
-
-We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response.
-It is important to note that in general $\hat{\alpha}$ does not converge to $\alpha_1$ in any sense.
-Despite this shortcoming, adjustment of the forecast for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has the potential to lower forecast risk under several conditions corresponding to different estimators of $\alpha_1$.
-
-\subsection{Construction of shock effects estimators}
-\label{constructionofestimators}
-
-We now construct the aggregated estimators of the shock effects that appear in Forecast 2 (see Section \ref{forecast}).
-We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.
-First, we introduce the procedures of parameter estimation for $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}).
-For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares (OLS) using historical data of $t = 1, \ldots, T_i$.
-For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$.
-In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate of $\alpha_i$.
-Note that parameter estimation for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
-We emphasize that $\alpha_i$s are random variables, but the OLS estimation is conditioned on the realizations from some distribution.
-
-Second, we introduce the candidate estimators for $\alpha_1$. Define the 
-adjustment estimator for time series $i=1$ by
-\begin{equation} \label{adjusted}
-  \hat{\alpha}_{\text{adj}} = \frac{1}{n}\sum_{i=2}^{n+1}\hat{\alpha}_i,
-\end{equation}
-where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of  
-the $\alpha_i$s for $i = 2, \ldots, n+1$.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
-the unknown $\alpha_1$ term for which no meaningful estimation information 
-otherwise exists. It is intuitive that $\hat{\alpha}_{\rm adj}$ should perform 
-well under $\mc{M}_1$ where we assume that $\alpha_i$'s share the same mean 
-for $i= 1, \ldots, n+1$. However, it can also be shown that 
-$\hat{\alpha}_{\rm adj}$ may be less favorable in $\mc{M}_{21}$ 
-and $\mc{M}_{22}$, which will be discussed in detail in Section \ref{properties}.
-
-We also consider the inverse-variance weighted estimator 
-in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i=2, \ldots, n+1$. 
-The inverse-variance weighted estimator is defined as 
-\begin{align*}
-  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
-  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{U}_i)_{22}^{-1},
-\end{align*}
-where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
-$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
-and $\mbf{U}_i$ is the design matrix for OLS with respect to time series 
-for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
-is required and the numerator and denominator terms are dependent in general.
-
-However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in 
-practical settings.
-We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ 
-and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of 
-$\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation 
-(see Section \ref{simulation}).
-
-We now motivate a weighted-adjustment estimator for model $\mc{M}_{21}$ 
-and $\mc{M}_{22}$. Our weighted-adjustment estimator is inspired by the 
-weighting techniques in synthetic control methodology (SCM) developed 
-in \cite{abadie2010synthetic}. 
-However, our weighted-adjustment estimator is not a causal estimator and 
-our estimation premise is a reversal of that in SCM. 
-Our objective is in predicting a post-shock response $y_{1,T_1^*+1}$ that is not yet 
-observed using other time series whose post-shock responses are observed.
-
-We use similar notation as that in \cite{abadie2010synthetic} to motivate our weighted-adjustment estimator. Consider a $\mbf{W} \in \R^n$ weight vector 
-$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 
-$i = 2, \ldots, n+1$. Construct
-\begin{align*}
- \mbf{X}_1 &= \mbf{x}_{1, T_1^*+1}',
-  \quad  
-  \mbf{X} = \begin{pmatrix}
-    \mbf{x}_{2, T_2^*+1}' \\
-    \vdots \\
-    \mbf{x}_{n+1, T_{n+1}^*+1}'
-  \end{pmatrix}, \\ 
-  \hat{\mbf{X}}_1(\mbf{W}) 
-   & = \mbf{W}'\mbf{X},
-\end{align*}
-where $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{1 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 
-Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
-$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that
-\begin{align}
- \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
-\end{align}
-Note that (\ref{SCM}) tries to find $\mbf{W}^*$ such that $\mbf{x}_{1, T_1^*+1}$ is a convex combination of $\mbf{x}_{i, T_i^*+1}$ for $i = 2, \ldots, n+1$ with weights $\mbf{W}^*$.
-Therefore, $\mbf{W}^*$ should exist as long as $\mbf{X}_1$ falls in the convex hull of
- \begin{align*}
-   \left\{ \mbf{x}_{2, T_2^*+1}', \ldots, \mbf{x}_{n+1, T_{n+1}^*+1}' \right\}.
- \end{align*}
-Our weighted-adjustment estimator will therefore perform well when the pool of time series posses similar covariates to the time series for which no post-shock responses are observed.
-We compute $\mbf{W}^*$ as
-\begin{align}
-  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})}_{p}. 
-  \label{W}
-\end{align}
-\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
-so that (\ref{SCM}) holds approximately 
-and that weighted-adjustment estimation techniques of this form are not 
-appropriate when the fit is poor. 
-Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
-is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist.
-Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
-  \begin{align*}
-    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
-    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
-      w^*_2 & \cdots & w^*_{n+1}
-    \end{pmatrix}'.
-  \end{align*}
- We further define
-\begin{align*}
-  \mathbf{V} = (\mathbf{x}_{2, T_2^*+1}, \ldots,\mathbf{x}_{n+1, T_{n+1}^*+1}).
-\end{align*}
-\begin{prop}
-  \label{uniqueness} If $\mathbf{V}$ has full rank and it exists some $\mathbf{W}$ satisfies (\ref{SCM}), the solution to  (\ref{W}) is unique.
-\end{prop} 
-Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.
-Note that $\mathbf{V}$ is $p \times n$.
-Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $p \geq n$.
-However, when $p < n$, $\mathbf{W}^*$ may not be unique.
-If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $p < n$, there are infinitely many solutions to (\ref{SCM}).
-The issue of non-uniqueness is further discussed in Section \ref{varbootstrap}.
-
-\begin{remark}
-\label{remark1}In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
-However, it is not necessary that the all $p$ covariates are important for every time series under study.
-The regression coefficients $\theta_i$ are nuisance parameters that are not of primary importance.
-It will be understood that structural 0s in $\theta_i$ correspond to variables that are unimportant. 
-\end{remark}
-
-\begin{remark}
-  Our forecasting premise and estimation construction shares similarities with Bayesian viewpoints.
-From a Bayesian perspective, if we assign a prior $\pi$ to $\alpha_1$, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as the Bayes rules with respect to $\pi$ under different loss functions.
-If the sampling distribution of the data and $\pi$ are known, it is possible to compute the Bayes risks of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ with respect to $\pi$,  thus enabling comparisons among them.
-Additionally, from Theorem 2.4 in Chapter 5 of \cite{lehmann2006theory}, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are admissible if they are unique with probability one.
-\end{remark}
-
-\section{Forecast risk and properties of shock effects estimators}
-\label{properties}
-
-In this section, we discuss the properties that are related to forecast-risk reduction.
-In discussion of risk, it is useful to derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.
-The expressions for the expectations are as follow,
-
- \begin{enumerate}[label = (\roman*)]
-    \item Under $\mc{M}_{1}$, $\E{\hat{\alpha}_{\rm adj}}=\E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha}$.
-    \item Under $\mc{M}_{21}$, 
-    $
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1}
-    $
-    and
-    $
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} .
-    $
-    \item Under $\mc{M}_{22}$,
-    $
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1}
-    $
-    and
-    $
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} .
-    $
-  \end{enumerate}
-Formal justification for these results can be found in Appendix.
-Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$.
-However, under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$.
-Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$.
-We collect these results in the following proposition.
-
-\begin{prop}
-\label{unbiased} 
-\quad 
-\begin{enumerate}[label = (\roman*)]
-  \item Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$.
-Under $\mc{M}_{21}$ and $\mc{M}_{22}$, $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ in general.
-  \item Suppose that $\mbf{W}^*$ satisfies (\ref{SCM}). Under $\mc{M}_{1}$, $\mc{M}_{21}$ and $\mc{M}_{22}$, $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
-\end{enumerate}
-\end{prop}
-
-Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation for evaluation of these conditions.
-These conditions and bootstrap will be discussed in Section \ref{conditions} and \ref{varbootstrap}, respectively.
-Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below.
-
-\begin{enumerate}[label = (\roman*)]
-  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
-\begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
-\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
-\end{align*}
-\item Under $\mc{M}_{22}$, 
-\begin{align*}
-\var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
-  &  \quad +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
-  &\quad + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
-\end{align*}
-\end{enumerate}
-Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
-because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
-
-Section \ref{conditions} details conditions needed for risk-reduction and comparisons of adjustment estimators.
-These conditions involve variances and expectations which may be difficult to compute in practice.
-To make use of those conditions in practice, estimation is required.
-Sections \ref{varbootstrap} introduce a residual bootstrap procedure which estimates the involved parameters in those conditions and thus motivates prospective decision-making about whether $\hat{\alpha}_i$ reduces the risk.
-Section \ref{loocv} describes our leave-one-out cross validation procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study.
-Our simulations verify these procedures.
-
-\subsection{Risk-reduction conditions for shock effects estimators}
-\label{conditions}
-
-In this section we will discuss the conditions for risk reduction for individual shock effects estimators under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-For an adjustment estimator $\hat{\alpha}$, we will write the risk-reduction as $\Delta(\hat{\alpha})=R_{T_1^*+1,1}-R_{T_1^*+1,2}$ where $R_{T_1^*+1,2}$ is the risk of Forecast 2 calculated using the adjustment estimator $\hat{\alpha}$.
-
-\subsubsection{Conditions under $\mc{M}_1$}
- \label{conditionsmodel1}
-
-Recall that Proposition \ref{unbiased} implies that the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ are unbiased for $\E{\alpha_1}$ under $\mc{M}_1$.
-With this result, we will have  the following propositions that specify the conditions that are necessary for risk reduction.
-
-\begin{prop}
-\label{proprisk}Under $\mc{M}_1$,
-\begin{enumerate}[label = (\roman*)]
-  \item $\Delta(\hat\alpha_{\rm adj}) > 0$  when 
-$\Var(\hat{\alpha}_{\rm adj}) < \mu_{\alpha}^2$.
-  \item if $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<\mu_{\alpha}^2$. 
-\end{enumerate}
-\end{prop}
-
-Proposition \ref{proprisk} says that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties.
-In this setting, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$.
-From Proposition \ref{proprisk}, we obtain a risk-reduction condition
-\begin{align}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
-\end{align}
-
-Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$ (see Forecast in Section \ref{forecast}); (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
-
-If  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}.
-From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
-\begin{align} \label{varwadj}
-\var{\hat{\alpha}_{\rm wadj}}
- &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 \nonumber \\
- &< \mu_{\alpha}^2.
-\end{align}
-In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.
-However, the above criteria are generally difficult to evaluate in practice.
-Sections \ref{varbootstrap} and \ref{loocv}  provide detailed treatments on how to estimate the sign of $\Delta(\hat\alpha)$ in practice.
-
-\subsubsection{Conditions under $\mc{M}_{21}$ and $\mc{M}_{22}$}
-\label{conditionsm2122}
-
-The shock effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$. 
-However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$. 
-We now state conditions for risk-reduction.
-
-\begin{prop}
-\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$  under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
-\end{prop}
-Under Proposition \ref{propriskwadj2}, we can obtain a risk-reduction inequality that is similar to \eqref{varwadj},
-\begin{align*}
-\var{\hat{\alpha}_{\rm wadj}}
-& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} \\
- &+ \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})  \\
- &< (\E{\alpha_1})^2,
-\end{align*}
-where $\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$.
-The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.
-Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally.
-Hence, Proposition \ref{proprisk} no longer holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.
-
-As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting.
-By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
-\begin{align*}
- \E{\alpha_1^2} &= \var{\alpha_1}+(\E{\alpha_1})^2\\
- &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
-  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
-  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
-\end{align*}
-The above inequality simplifies to 
-\begin{equation} \label{ineq}
- (\E{\alpha_1})^2 >\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
-\end{equation}
-
-As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$.
-We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$.
-That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
-In fact, more generally, using similar proof of Lemma \ref{risklemma}, it can be shown that under $\mc{M}_2$, the risk-reduction quantities are
-\begin{align*}
-  \Delta(\hat{\alpha}_{\rm adj}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2,\\
-  \Delta(\hat{\alpha}_{\rm IVW}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2 ,\\
-  \Delta(\hat{\alpha}_{\rm wadj}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}},
-\end{align*}
-where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using bootstrap and leave-one-out cross validation procedures developed in Sections \ref{varbootstrap} and \ref{loocv}.
-
-\subsection{Bootstrap for risk-reduction evaluation problems}
-\label{varbootstrap}
-
-In this section, we present bootstrap procedures that approximate the distribution of our shock effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction quantity using plug-in approach in practice.
-Our procedure involves the resampling of residuals in the separate OLS fits.
-This procedure has its origins in Section 6 of \citet{efron1986bootstrap} and Chapter 12 of \cite{kilian2017structural}.
-Our procedure involves the resampling of the residuals which are assumed to be the realizations of an iid process.
-
-Our first bootstrap procedure is as follows: Let $B$ be the bootstrap sample size.
-At iteration $b$, first resample the indices $I = \{2, \ldots, n+1\}$ of the donor pool with replacement to form $I^{(b)}$ with cardinality $n$, where we note that the elements of $I^{(b)}$ may not be unique in terms of their  indices in the donor pool.
-Initialize $y_{i,0}^{(b)}=y_{i,0}$ for all $i \in I^{(b)}$.
-Then, resample the residuals under models $\mc{M}_1$ or $\mc{M}_{2}$, compute the bootstrapped response  $y_{i,t}^{(b)}$ for   $t \in \{1, \ldots, T_i\}$ using the model estimated by original data,  and obtain shock effect estimators for each of the time series in the donor pool for all $i \in I^{(b)}$.
-These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-We can then estimate distributional quantities of our shock effect estimators under our considered models with the bootstrap samples $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-We denote this procedure by $\mc{B}_u$.
-We motivate a second bootstrap procedure $\mc{B}_f$ which treats the the donor pool as fixed, and not a realization from an infinite super-population.
-Therefore, there is no resampling of the donor pool in $\mc{B}_f$, it is otherwise similar to $\mc{B}_u$.
-An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in Section 2 in the Supplementary Materials.
-
-We will explicitly use these bootstrapped samples of shock effect estimators to check the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
-Recall that $\hat{\alpha}_{\rm adj}$,  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ under $\mc{M}_1$ and $\mc{M}_2$ from Proposition \ref{unbiased}.
-Our bootstrap procedure estimates the variance of our adjustment estimators.
-We can then estimate the risk-reduction propositions and inequalities.
-For example, we can estimate $\Delta(\hat{\alpha}_{\rm adj})$ under model $\mc{M}_{21}$ or $\mc{M}_{22}$ with
-\begin{align*}
-  \hat{\Delta}(\hat{\alpha}_{\rm adj}) & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
-\end{align*}
-where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance estimator for $\Var(\hat{\alpha}_{\rm adj})$.
-
-We reiterate the philosophical distinction between $\mc{B}_u$ and $\mc{B}_f$.
-$\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness arises from parameters and idiosyncratic error.
-A double bootstrap procedure with similar steps can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
-The double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, can check whether a bootstrap percentile interval of resampled estimates of $\Delta(\hat{\alpha})$ contain 0 at a desired error threshold.
-We investigated such a double bootstrap procedure and found that it produced inferences that were similar to those produced using the bootstrap techniques developed in the main text.
-
-We stress that our bootstrap approximations cannot alleviate the inherent bias of using our adjustment estimators as surrogates for $\alpha_1$.
-We caution that the bootstrapping residuals in OLS estimation may not provide valid inference in moderate or high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}; see alternatives for residual bootstrapping in linear models in \citet{el2018can}.
-
-Recall that $\mathbf{W}^*$  may not be unique if the conditions in Proposition \ref{uniqueness} are not satisfied.
-Non-uniqueness might be a concern theoretically.
-This is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$'s all targeting on the same $\alpha_1$.
-For example, consider the case where the size of  donor pool to be 2, $\var{\hat{\alpha}_2}=1$, $\var{\hat{\alpha}_3}=2$, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
-In this scenario, the weighted adjustment estimator induced by $\mathbf{W}^*_1$ has variance 1 whereas the one by $\mathbf{W}^*_2$ has variance 2.
-Nevertheless, even if $\hat{\alpha}_i$ has the same variance across $i = 2, \ldots, n+1$, the same issue would occur if there were infinitely many $\mbf{W}^*$ with different norms.
-It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}).
-Simulations in the Section 4 of the Supplementary Materials provide some evidence that non-uniqueness of $\mathbf{W}^*$ is not problematic for inferences.
-
-\subsection{Leave-one-out cross validation}
-\label{loocv}
-
-In this section, we adapt leave-one-out cross validation (LOOCV) to our estimation context in order to provide prospective evaluations of our adjustment techniques.
-Our proposed LOOCV procedure has its roots in Section 7.10 of \citet{hastie2009elements}.
-Recall in Section \ref{modelsetup} that we are given the data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining observations form the donor pool.
-For iteration $m \in \{1,\ldots,n\}$ of our LOOCV procedure, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}_m, t = 1, \ldots, T_{i}\}$, where $\mc{I}_m=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, we can evaluate the performance of our adjustment estimators and the original forecast made without adjustment (i.e., Forecast 1 in Section \ref{forecast}).
-
-LOOCV can be very computationally intensive when $n$ is large, especially when combined with bootstrapping.
-To alleviate these concerns we can perform LOOCV with a random subset of $k \leq n$ iterations selected without replacement.
-In this setting, we let $\mc{J}$ be the randomly sampled indices.
-For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Based on the new donor pool, we estimate relevant parameters using bootstrap procedures outlined in Section \ref{varbootstrap}.
-In other words, $k$ times of bootstrapping are nested in a LOOCV procedure.
-We find that $k=5$ or $k=10$ iterations of LOOCV performs well.
-
-We now outline how LOOCV can be used to prospectively assess the performance of adjustment estimators.
-Let $\mc{A}$ be the set of adjustment estimators.
-For each $\hat{\alpha} \in \mc{A}$, let $\delta_{\hat{\alpha}} = I(\hat\Delta(\hat{\alpha})>0)$ be a decision rule where $I(\cdot)$ is the indicator function and a $1$ corresponds to the decision to use  estimator $\hat\alpha$.
-If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported 1 (0, respectively) so that it makes the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be incorrect.
-If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported 0 (1, respectively) so that it makes the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be correct.
-These situations are depicted in the following table: \vspace*{0.3cm}
-
-\begin{center}
-  \begin{center}
-      \begin{tabular}{cc|c|c}
-        \hline
-        & & \multicolumn{2}{c}{Decision} \\
-        & & $\delta_{\hat{\alpha}} = 1$ & $\delta_{\hat{\alpha}} = 0$ \\ 
-                \hline
-     \multirow{2}{*}{Truth}  & $\Delta(\hat{\alpha})>0$ & Correct & Incorrect \\
-      \cline{3-4}
-      & $\Delta(\hat{\alpha})<0$  & Incorrect & Correct \\
-      \hline
-      \end{tabular}
-  \end{center}
-\end{center} 
-\vspace*{0.3cm}
-
-We will use 
-$
-	\mc{C}(\delta_{\hat\alpha}) 
-	= I(\delta_{\hat{\alpha}} \text{ is correct})
-$
-as a metric that evaluates the performance of forecasts made with the adjustment estimator $\hat\alpha$.
-If $\E{\mc{C}(\delta_{\hat{\alpha}})} > 0.5$, we claim that $\delta_{\hat{\alpha}}$ is better than random guessing.
-Note that $\mc{C}(\delta_{\hat{\alpha}})$ can generally be computed only when the post-shock response is observed.
-However, it is possible to estimate $\E{\mc{C}(\delta_{\hat{\alpha}})}$ using LOOCV.
-The LOOCV estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$ are
-\begin{equation} \label{loocvm}
-	 \bar{\mc{C}}(\delta_{\hat{\alpha}})= \frac{1}{n} \sum_{m = 1}^n \mc{C}^{(-m)}(\delta_{\hat{\alpha}}),
-	\end{equation}
-where $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ is computed with respect to donor pool with index set $\mc{I}_m$ and the $m+1$ time series is treated as the time series of interest.
-The LOOCV with $k$ random draws estimates $\E{\mc{C}(\delta_{\hat{\alpha}})}$ as
-\begin{equation} \label{loocvk}
-	 \bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})	,
-\end{equation}
-where $\mc{J}$ is the set of the $k$ randomly sampled indices.
-
-\begin{remark}
-  Note that we allow the time series within the donor pool to be dependent but donor pool should be independent of the time series of interest.
-However, if we assume the mutual  independence structure, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
-\end{remark}
-
-\section{Numerical examples}
-\label{simulation}
-
-\subsection{Modeling setup}
-
-In this section we provide justification for our methods based on Monte Carlo simulation.
-We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
-We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}.
-Parameter setup of our simulations is detailed as follows: the $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
-We sampled $T_i$'s independently from  $\text{Gamma}(15, 10)$ that are further rounded to integers, where the minimum allowable value of $T_i$ is fixed to be 90.
-We will randomly draw $T_i^*$ from $\{p + 4, \ldots, T_i-1\}$.
-The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
-Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
-Additionally, we generated the covariates from $\text{Gamma}(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
-Last, we set $\delta_i\simiid  \normal{1}{0.5}$ and $\theta_i \sim \normal{0}{1}$.
-We will consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
-We choose a Monte Carlo sample size of $30$ replications and a bootstrap sample size of $B = 200$ for computation.
-Means and standard errors for estimated quantities will be recorded.
-Our LOOCV procedure will consider $k=5$ random draws.
-Recall in Section \ref{loocv} that $B$ times of bootstrap are nested in a LOOCV with $k$ random draws.
-It implies that $B(k+1)$ times of bootstrap replications are required for each Monte Carlo simulation.
-
-\subsection{Performance metrics}
-
-Our adjustment estimators will be evaluated by multiple criteria.
-We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the guess, with 1 indicating that $\hat{\alpha}$ provides risk-reduction over the simple no-adjustment forecast, and 0 indicates the converse.
-We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
-We will also consider the Euclidean distance between the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ and the realized post-shock response $y_{1,T_1^*+1}$.
-The first two metrics can combine to assess our forecasting methodology prospectively while the latter requires the realization of the post-shock response $y_{1,T_1^*+1}$.
-
-\subsection{Monte Carlo results}
-\label{parametricbootstrapsimulation}
-
-In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities.
-We mainly discuss simulations under $\mc{M}_2$ (see Section \ref{modelsetup}) for $\mc{B}_u$ and $\mc{B}_f$ (see Section \ref{varbootstrap}) with comparisons to those under $\mc{M}_1$ whose results are listed in Section 3 in the Supplementary Materials.
-Two simulation setups are investigated.
-
-In the first simulation setup, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$.
-Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates.
-In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.
-Results are displayed in Table~\ref{table1} in the Appendix, Section \ref{tablesappendix}.
-
-In the second simulation setup, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n=10$.
-Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.
-Results are  in Table~\ref{table2} in the Appendix, Section \ref{tablesappendix}.
-
-First, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we  observe from Table \ref{table1} that the decision making of $\delta_{\hat{\alpha}}$ is nearly correct  for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small  from Table \ref{table1}.
-The reasons can be explained as follows.
-When $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal according to construction of $\hat{\alpha}_{\rm wadj}$ in Section \ref{constructionofestimators}.
-Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
-However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is large), the decision rule $\delta_{\hat{\alpha}}$  becomes unreliable for $\hat{\alpha}\in \mc{A}$.
-It is to be expected since the bootstrap estimates become more biased.
-However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$.
-Second, fixing $\sigma_{\alpha}$, we can observe that the correctness of $\delta_{\hat{\alpha}}$ increases when $n$ increases.
-It is due to the robustness gain in estimation when $n$ increases.
-
-Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down, though they  follow similar patterns.
-Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$.
-But it is not present for $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ since we applied the fact  $\hat{\alpha}_{\rm wadj}$ is unbiased for $\E{\alpha_1}$ from Proposition \ref{unbiased} in plugging it in with replacing $\E{\alpha_1}$.
-Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative.
-Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of correctness between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
-For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.83 \times 0.59 = 0.490$ from Table \ref{table1}.
-In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.
-
-From columns related to distance to $y_{1, T_1^*+1}$ in Table \ref{table1}, as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
-When $\sigma_{\alpha}= 5, 10, 25$, forecasts using $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are always better than the original forecast significantly.
-But it does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
-It is reasonable in that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
-Nevertheless, no statistical evidence has been found to support the claim that $n$ matters in prediction.
-In other words, the size of the donor pool matters for producing reliable decision-making of $\delta_{\hat{\alpha}}$ rather than reliable prediction.
-
-From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$   decreases, which is a pattern similar to the one shown in the first experiment.
-Furthermore, as $\sigma$ increases fixing $\sigma_{\alpha}$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases as well.
-Note that the correctness  hinges on the estimation of the parameters.
-Since $\hat{\alpha}_{\rm wadj}$  is a linear combination of OLS estimates, as $\sigma$ increases, $\var{\hat{\alpha}_{\rm wadj}}$ increases as well.
-Therefore, $\hat{\alpha}_{\rm wadj}$ become more volatile and its estimation of $\E{\alpha_1}$ can be less reliable.
-Those reasons can explain  why an increase of $\sigma_{\alpha}$ contributes to a decrease of  $\bar{\mc{C}}(\delta_{\hat{\alpha}})$.
-We observe similar patterns for distance to $y_{1, T_1^*+1}$ as well.
-When $\sigma$ increases with fixing $\sigma_{\alpha}$, it is likely that the degree of variation of $y_{1,t}$ exceeds the extent of adjustment improvement $\hat{\alpha}$ can contribute to for $\hat{\alpha}\in \mc{A}$.
-
-With respect to averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases.
-This is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
-The reasons are outlined as follows: Recall in Section \ref{conditionsm2122}, the conditions of risk-reduction propositions involve $(\E{\alpha_1})^2 > \var{\hat{\alpha}} + (\E{\hat{\alpha}}-\E{\alpha_1})^2$ for $\hat{\alpha}\in \mc{A}$.
-Notice that $\var{\hat{\alpha}}$ is an increasing function of $\sigma$ since $\hat{\alpha}$ is estimated by OLS.
-Therefore, it explains the reason why the increase of $\sigma$ would result in a decrease of averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ since the inequality is not likely to hold when  $\var{\hat{\alpha}}$ increases.
-
-Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented.
-See Table \ref{table3} and Table \ref{table4} for results in the Appendix, Section \ref{tablesappendix}.
-Comparing Table \ref{table1}
- and Table \ref{table2} yields that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
-For other situations, $\mc{B}_u$  and $\mc{B}_f$  are rather similar.
-It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool.
-Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
-It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$.
-However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_f$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$.
-In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is moderately small; otherwise, they are similar.
-
- Simulation results corresponding to model $\mc{M}_1$ are listed in Section 3 in Supplementary Materials.
-Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$, except for the difference among estimators.
-The results show that (1) the performance of $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are nearly the same and (2) in many situations, $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are  better than $\hat{\alpha}_{\rm wadj}$; in other situations, they are mostly the same.
-Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
-Therefore, similarity weighting may not be informative when the model for $\alpha_i$ is identified wrongly.
-Under $\mc{M}_1$, simple averaging, aimed for a reduction of variance, or inverse-variance weighting, targeting on reducing negative effects from varying time lengths, may work better.
-
-We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population in these simulations.
-Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
-In this scenario, $\mathbf{W}^*$ will take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$.
-However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
-Moreover, simulations in Section 4 of the Supplementary Materials show that non-uniqueness does not seriously compromise the inference.
-
-\section{Forecasting Conoco Phillips stock in the presence of shocks}
-\label{forecasting}
-
-We demonstrate our post-shock forecasting methodology on a time series of Conoco Phillips share prices after the occurrence of a structural shock.
-Conoco Phillips is a large oil and gas resources company \citep{conocowhatwedo}.
-The particular post-shock response that we predict happened after trading ended on Friday March 6th, 2020 and before trading began on Monday March 9th, 2020.
-It is reasonable that the timing of this shock is known, several events occurred over the trading weekend which had an impact on stock markets and the oil markets.
-For example, Russia and OPEC began a battle for global oil price control on Sunday, March 8th \citep{sukhankin2020russian}, and several US states began declaring state of emergencies in response to the evolving coronavirus pandemic \citep{nygov, alonso2020state}.
-
-We collect our data through the use of \texttt{quantmod} package \citep{ryan2017quantmod} in R. In this analysis we make the following design considerations:
-
-\begin{enumerate}
-\item[(1)] {\bf Selection of model}.
-We will use an AR(1) model to forecast Conoco Phillips stock price.
-This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.
-For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect.
-All estimates will be adjusted for inflation.
-The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects.
-All the parameters are estimated using OLS.
-\item[(2)] {\bf Selection of covariates}.
-We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$.
-The model of $\alpha_i$ incorporates daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX).
-The model for $y_{i,t}$ disregards VIX.
-This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
-\item[(3)] {\bf Construction of donor pool}.
-Our donor pool consists of Conoco Phillips shock effects observed in the past.
-We consider shock effects which occurred on March 14, 2008, several days in September, 2008, and November 27, 2014.
-The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession.
-In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}.
-These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Mac in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}.
-The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}.
-\end{enumerate}
-
-We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020.
-The covariates and response of time series in the donor pool are adjusted for inflation.
-Note that there are three shock effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials.
-The estimated shock-effects for $\alpha_i$ are $-0.922, -7.063, -5.777, -6.395, -4.207$ for $i = 2, \ldots, 6$, respectively.
-Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
-Note that non-uniqueness problems will not occur in this analysis since the conditions of Proposition \ref{uniqueness} are satisfied.
-To avoid the effect of  unit differences on weighting, we center and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
-For $\hat{\alpha}_{\rm wadj}$, we observe that
-$
-  \mathbf{W}^*= (0.000,0.000, 0.000, 0.273, 0.727)
-$
-and 
-$
-  \Vert\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\Vert_2 = 3.440.
-$
-Note that the norm is computed using the $k$-dimensional Euclidean metric.
-The solution $\mathbf{W}^*$ suggests that the shock effect of interest is very similar to the September 25, 2008 shock effect and  the November 27, 2014 shock effect.
-
-The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-4.872$, $\hat{\alpha}_{\rm wadj}= -4.805$, and $\hat{\alpha}_{\rm IVW}=-4.384$.
-Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}.
-The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.419, 0.559, and 0.667, respectively.
-We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
-
-\begin{figure*}[t!]
-  \begin{center}
-    \includegraphics[height = 9cm]{FIG2.pdf}
-    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price.}
-    \label{Fig:CP}
-  \end{center}  
-  \vspace{-.6cm}
-\end{figure*}
-
-We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well.
-Our estimation framework misses the yet to be observed pot-shock response, however they perform much better than unadjusted forecasts that do not account for shock effects.
-The unadjusted forecast misses the post-shock response by 9.870 dollars whereas
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively.
-
-The true shock effect is not fully recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$.
-This may be a result of a poorly constructed donor pool.
-The shock on March 9th, 2020 is in the midst of the COVID-19 pandemic and oil production volatility.
-It is difficult to find available stock market time series data that were generated under a similar setting.
-In any event, the shock on March 9th, 2020 was the largest price shock to Conoco Phillips shares by a wide margin, even after adjusting for inflation.
-
-From another perspective, it is possible that the stock of Conoco Phillips actually experienced multiple shocks on 2020 March 9th.
-For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector autoregressive model.
-Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.
-Motivated by \citet{kilian2009not}, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
-The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects only, respectively, miss the post-shock Conoco Philips share price by $0.951$, $0.405$, and $1.460$ dollars.
-These additive adjustment estimators do extremely well in this additive shock setting.
-
-\section{Discussion}
-\label{discussion}
-
-We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock.
-Our methodology is as follows: construct a synthetic panel of time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
-There have been several other recent similar methods developed for forecasting COVID-19 cases.
-For example, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries.
-A similar setup may be appropriate for post-shock forecasting but may be too dependent upon model specification for the shock distribution.
-\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach.
-However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
-\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
-They also provided useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
-Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
-
-We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings.
-The model, under which we verify these claims, is a simple AR(1) model.
-Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
-Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
-As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
-But we note that consistency estimates from LOOCV may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
-
-Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its first and second moments exist.
-The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
-Additionally, $\alpha_i$ can be heteroskedastic; i.e.,  they can have different variances.
-In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply.
-We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts.
-An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.
-Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.
-
-Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series.
-If the data are subject to heteroskedasticity of unknown form, bootstrapping tuples of regressands and regressors proposed by \citet{freedman1981bootstrapping} is robust in this situation with asymptotic validity in autoregressive models established by \citet{gonccalves2004bootstrapping}.
-If serial correlation exists in the data, various block bootstrapping procedures \citep{kunsch1989jackknife, liu1992moving} can be possible reasonable alternatives.
-Note that the pseudo time series generated by our proposed residual bootstrap are not stationary.
-If stationarity is of concern, one can be referred to the stationary bootstrap in \citet{politis1994stationary} for stationary and weakly dependent time series.
-Nevertheless, it was shown that approximation accuracy might be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.
-More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, \citet{berkowitz2000recent}, and Chapter 12 in \citet{kilian2017structural}.
-It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.
-
-Construction of donor pool is a critical step that directly matters in prediction.
-In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for  varying variances and  varying means that are linear functions of common covariates.
-Remark \ref{remark1} shows that common covariates are not restrictive with structural zero in coefficients.
-However, it is difficult to verify such assumption or structure in practice.
-In principle, one should select identities that come from a common population, which is also the one  the identity under study come from, as candidates in donor pool.
-This selection criterion is often adopted in the literature of comparative case studies.
-For example, \citet{card1990impact} used a set of cities in southern U.S.
-to estimate the effect of 1980 Mariel Boatlift on the Miami labor market.
-\citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country.
-To estimate the effect of Proposition 99, a large tabacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period.
-Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.
-
-\section{Supplementary material}
-
-Supplementary material includes the results of  likelihood ratio test for  independence among nested shock effects in Section \ref{forecasting}, the algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$, simulation results for $\mc{M}_1$, simulation results for an example of the boundary case $p < n$, and R codes for corresponding simulations and data analysis.
-
-\section{Appendix}
-\label{proofs}
-
-\subsection{Justification of Expectation of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
-\label{exp}
-
-The building block for the following proof is the fact that least squares is conditionally unbiased conditioned on $\Theta$.
-
-\noindent \textbf{Case I: under $\mc{M}_{1}$:} It follows that  under $\mc{M}_{1}$ (see Section \ref{modelsetup}),
-\begin{align*}
-\E{\hat{\alpha}_{\rm adj}} &=\frac{1}{n}  \sum_{i=2}^{n+1} \E{\E{\hat{\alpha}_i|\Theta}} = \mu_{\alpha} \\
- \E{\hat{\alpha}_{\rm wadj}}&= \sum_{i=2}^{n+1} w_i^* \E{\E{\hat{\alpha}_i|\Theta}}= \sum_{i=2}^{n+1} w_i^*\mu_{\alpha}= \mu_{\alpha}.
-\end{align*}
-where we used the fact that $\sum_{i=2}^{n+1} w^*_i=1$.
-
-\noindent \textbf{Case II: under $\mc{M}_{21}$ and $\mc{M}_{22}$:} Since $\E{\tilde{\varepsilon}_{i, T_i}}=0$, $\E{\hat{\tilde{\alpha}}_{i}}=\E{\tilde{\alpha}_{i}}=\E{\alpha_{i}}$, it follows that
-  \begin{align*}
-   \E{\hat{\alpha}_{\rm wadj}}
-   &= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}\\
-   &= \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right)\\
-   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}\right]\bigg\}\\
-   &=\mu_{\alpha}+ \mu_{\delta}' \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}\tag{$\mbf{W}\in \mc{W}$}
-   \\
-   &=\mu_{\alpha}+  \mu_{\delta}'\mbf{x}_{1, T_1^*+1}. \tag{from (\ref{SCM})}
-   \end{align*}
-Similarly,
-  \begin{align*}
-   \E{\hat{\alpha}_{\rm adj}}
-   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \mu_{\delta}'  \mbf{x}_{i, T_i^*+1}.
-   \end{align*}
-
-\subsection{Justification of Variance of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
-\label{var}
-
-Notice that under the setting of OLS, the design matrix for $\mc{M}_2$ is the same as the one for $\mc{M}_1$. Therefore, it follows that
-  \begin{align*}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \E{\var{\hat{\alpha}_{\rm wadj}|\Theta}} + \var{\E{\hat{\alpha}_{\rm wadj}|\Theta}} \\
-  &=\mrm{E} \left\{\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\} +\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
-\end{align*}
-Under $\mc{M}_{21}$ where $\delta_i=\delta$ are fixed unknown parameters,  we will have
-  \begin{align}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma^2(\mbf{U}'_i\mbf{U}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
-\end{align}
-Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \varepsilon_{i,t}$, we have
- \begin{align*}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
- & \quad  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
-\end{align*}
-For the adjustment estimator, we simply replace $\mbf{W}^*$ with $1/n\mbf{1}_n$. Thus, under $\mc{M}_{21}$ we have 
- \begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
-\end{align*}
-Under $\mc{M}_{22}$, we shall have
- \begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
-  & \quad  +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
-\end{align*}
-Notice that $\mc{M}_{1}$ differs from $\mc{M}_{21}$ only by its mean parameterization of $\alpha$ (see Section \ref{modelsetup}).
-In other words, the variances of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ under $\mc{M}_1$ are the same for those under $\mc{M}_{21}$.
-
-\subsection{Proofs for lemmas and propositions}
-
-\begin{proof-of-proposition}[\ref{uniqueness}]
-  The proof of \citet{li2019statistical} in Appendix A.2 and A.3 adapts easily to Proposition \ref{uniqueness}.
-\end{proof-of-proposition}
-
-\begin{proof-of-proposition}[\ref{unbiased}] The proof for unbiasedness follows immediately from discussions related to expectation in Section \ref{properties}.
-For the biasedness of  $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$, we write the bias term for $\hat{\alpha}_{\rm adj}$ as below.
-\begin{align*}
-  \mrm{Bias}(\hat{\alpha}_{\rm adj}) = 
-  \begin{cases}
-       \frac{1}{n} \sum_{i=2}^{n+1} \delta'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1})  & \text{ for } \mc{M}_{21}\\
-    \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1})  & \text{ for }\mc{M}_{22}
-  \end{cases}.
-\end{align*}
-But it may be unbiased in some special circumstances when the above bias turns out to be 0. \end{proof-of-proposition}
-
-\begin{lem}
-  \label{risklemma} The forecast risk reduction is $R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2$ for all estimators of $\alpha_1$ that are independent of $\Theta_1$ (see Section \ref{modelsetup}).
-\end{lem}
-
-\begin{proof-of-lemma}[\ref{risklemma}]
-  Define 
-  \begin{align*}
-    C(\Theta_1) &=\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} \\
-    & \quad -(\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}),
-  \end{align*}
-  where $\Theta_1$ is as defined in (\ref{parameter}). Notice that
-  \begin{align*}
-    R_{T_1^*+1,1}
-    &= \mrm{E}\big\{\big(C(\Theta_1)-\alpha_1\big)^2\big\}\\
-     R_{T_1^*+1,2} &=  \mrm{E}\big\{\big(C(\Theta_1)+\hat{\alpha}-\alpha_1\big)^2\big\}.
-  \end{align*}
-  It follows that
-  \begin{align*}
-    R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-2\E{C(\Theta_1)\hat{\alpha}}-\E{\hat{\alpha}-\alpha_1}^2.
-  \end{align*}
-  Assuming $\mbf{S}=(\mbf{1}_n, \mbf{y}_{1,t-1}, \mbf{x}_{1})$ has full rank, under OLS setting, $\hat{\eta}_1$, $\hat{\phi}_1$, and $\hat{\theta}_1$ are unbiased estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively under conditioning of $\Theta_1$.
-Since we assume $\hat{\alpha}$ is independent of $\Theta_1$, through the method of iterated expectation,
-  \begin{align*}
-    \E{C(\Theta_1)\hat{\alpha}}=\mrm{E}\big\{\hat{\alpha}\cdot \E{C(\Theta_1)\mid \Theta_1}\}=0.
-  \end{align*}
-  It follows that
-  \begin{align*}
-    R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2,
-  \end{align*}
-  which finishes the proof.
-\end{proof-of-lemma}
-
-\begin{proof-of-proposition}[\ref{proprisk}] The proofs are arranged into two separate parts as below.
-
- \textbf{Proof for statement (i):} Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$ because
-  \begin{align*}
-   \mrm{E}\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
-   = \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}
-   &= \frac{1}{n}\sum_{i=2}^{n+1}\E{\E{\hat{\alpha}_i\mid \Theta}}\\
-   &=  \frac{1}{n}\sum_{i=2}^{n+1}\E{\alpha_i}
-   = \mu_{\alpha}=\E{\alpha_1},
-  \end{align*}
-  where we used the fact that OLS estimator is unbiased when the design matrix $\mbf{U}_i$ is of full rank for all $i = 2, \ldots, n+1$.
-Because $\alpha_1\indep \varepsilon_{i,t}$, $\E{\hat{\alpha}_{\rm adj}\alpha_1}=\E{\hat{\alpha}_{\rm adj}}\E{\alpha_1}=(\E{\hat{\alpha}_{\rm adj}})^2$.
-By Lemma \ref{risklemma},
-    \begin{align*}
-    R_{T_1^*+1,1}-R_{T_1^*+1,2}
-    &=\E{\alpha_1^2}-\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
-   & =\E{\alpha_1^2}-\E{\alpha_1^2}- \E{\hat{\alpha}_{\rm adj}^2}+2\E{\hat{\alpha}_{\rm adj}\alpha_1} \\
-   &= \mu_{\alpha}^2 - \var{\hat{\alpha}_{\rm adj}} 
-  \end{align*}
-  Therefore, as long as we have $\var{\hat{\alpha}_{\rm adj}}<\mu_{\alpha}^2$, we will achieve the risk reduction.
-
- \textbf{Proof for statement (ii):} By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\mu_{\alpha}$ holds for $\mc{M}_{1}$.
-The remainder of the proof follows a similar argument to the proof of statement (i).
-\end{proof-of-proposition}
-
-\begin{proof-of-proposition}[\ref{propriskwadj2}]
-  By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ holds for $\mc{M}_{21}$ and $\mc{M}_{22}$.
-The remainder of the proof follows a similar argument to the proof of Proposition \ref{proprisk}.
-\end{proof-of-proposition}
-
-\subsection{Tables for Section \ref{simulation}}
-\label{tablesappendix}
-\newpage
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table1}
-\begin{center}
-\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.91 (0.02) & 0.9 (0.03) & 53.23 (4.1) & 15.88 (2.1) & 16.78 (2.37) & 15.82 (2.07) \\ 
-    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.89 (0.03) & 0.9 (0.03) & 0.89 (0.03) & 53.01 (4.47) & 17.83 (2.38) & 19.56 (2.56) & 17.61 (2.36) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.74 (0.04) & 0.81 (0.04) & 0.75 (0.04) & 53.38 (5.92) & 26.44 (3.8) & 29.06 (4) & 26.11 (3.75) \\ 
-    & 50  & 0.83 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.64 (0.05) & 0.59 (0.05) & 61.68 (7.73) & 46 (6.31) & 47.3 (7.14) & 45.25 (6.32) \\ 
-    & 100  & 0.7 (0.09) & 0.87 (0.06) & 0.7 (0.09) & 0.53 (0.05) & 0.54 (0.05) & 0.53 (0.06) & 85.68 (12.95) & 87.25 (11.86) & 87.07 (13.63) & 85.65 (12.02)\\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
-    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
-   \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 51.11 (3.05) & 14.94 (2.36) & 14.09 (2.37) & 15.09 (2.35) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.91 (0.02) & 52.34 (3.19) & 15.64 (2.73) & 15.29 (2.74) & 15.89 (2.68) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.73 (0.04) & 0.76 (0.04) & 0.73 (0.04) & 56.03 (5.2) & 25.49 (3.85) & 27.38 (3.87) & 25.27 (3.84) \\ 
-    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.56 (0.04) & 0.6 (0.04) & 0.57 (0.04) & 71.37 (7.76) & 47.25 (6.42) & 52.06 (6.57) & 46.41 (6.43) \\ 
-    & 100  & 0.63 (0.09) & 0.67 (0.09) & 0.63 (0.09) & 0.52 (0.04) & 0.42 (0.04) & 0.53 (0.04) & 111.91 (13.83) & 92.95 (12.34) & 103.13 (12.74) & 91.07 (12.37) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.94 (0.02) & 0.93 (0.02) & 47.79 (2.93) & 14.83 (1.72) & 14.83 (2.04) & 14.76 (1.72) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.91 (0.02) & 0.89 (0.03) & 47.93 (3.25) & 16.55 (1.89) & 17.55 (2.12) & 16.53 (1.88) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.82 (0.03) & 0.83 (0.03) & 49.78 (5.01) & 26.42 (3.38) & 29.11 (3.4) & 26.45 (3.35) \\ 
-    & 50  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.64 (0.05) & 0.63 (0.05) & 0.64 (0.05) & 62.64 (7.4) & 48.84 (6.4) & 52.67 (6.28) & 48.8 (6.35) \\ 
-    & 100  & 0.83 (0.07) & 0.8 (0.07) & 0.83 (0.07) & 0.57 (0.05) & 0.59 (0.05) & 0.59 (0.05) & 103.37 (12.23) & 97.81 (12.52) & 102.4 (12.49) & 97.63 (12.45) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table2}
-\begin{center}
-\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.97 (0.01) & 0.95 (0.02) & 48.84 (3.4) & 15.72 (1.93) & 15.32 (1.94) & 15.72 (1.93) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.94 (0.02) & 0.92 (0.03) & 49.54 (3.73) & 17.07 (2.01) & 16.08 (2.16) & 17.12 (1.99) \\ 
-    & 25  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.77 (0.02) & 0.81 (0.03) & 0.77 (0.03) & 51.78 (5.22) & 24.78 (2.57) & 26.12 (2.49) & 24.62 (2.54) \\ 
-    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.61 (0.04) & 0.59 (0.05) & 58.62 (7.74) & 40.09 (4.7) & 47.09 (4.09) & 39.85 (4.58) \\ 
-    & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.73 (0.08) & 0.5 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 82.66 (12.19) & 72.83 (9.75) & 89.03 (9.15) & 72.31 (9.5) \\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
-    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.04) & 0.76 (0.03) & 0.7 (0.04) & 50.09 (8.27) & 38.1 (5.75) & 37.98 (5.5) & 38.44 (5.76) \\ 
-    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.69 (0.04) & 0.74 (0.03) & 0.69 (0.04) & 50.82 (8.15) & 37.63 (5.61) & 36.33 (5.64) & 37.99 (5.61) \\ 
-    & 25  & 0.9 (0.06) & 0.9 (0.06) & 0.9 (0.06) & 0.62 (0.04) & 0.64 (0.04) & 0.61 (0.04) & 53.01 (8.22) & 38.78 (5.29) & 36.82 (5.76) & 38.88 (5.31) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.53 (0.04) & 58.9 (9.12) & 46.77 (5.54) & 50.61 (5.71) & 46.6 (5.51) \\ 
-    & 100  & 0.7 (0.09) & 0.9 (0.06) & 0.67 (0.09) & 0.51 (0.03) & 0.56 (0.04) & 0.5 (0.03) & 79.64 (12.21) & 72.76 (8.79) & 89.48 (7.98) & 72.17 (8.59) \\[.3cm] 
-   \multirow{5}{*}{50} & 5  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.04) & 0.59 (0.04) & 71.22 (13) & 70.31 (10.4) & 72.3 (9.26) & 70.79 (10.45) \\ 
-    & 10  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.05) & 0.6 (0.05) & 70.85 (12.91) & 69.43 (10.22) & 70.65 (9.29) & 69.94 (10.26) \\ 
-    & 25  & 0.7 (0.09) & 0.73 (0.08) & 0.7 (0.09) & 0.54 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 70.32 (12.81) & 67.61 (9.86) & 67 (9.58) & 68.06 (9.89) \\ 
-    & 50  & 0.67 (0.09) & 0.7 (0.09) & 0.67 (0.09) & 0.51 (0.05) & 0.51 (0.04) & 0.51 (0.05) & 74.01 (12.66) & 68.69 (9.63) & 67.9 (10.21) & 68.91 (9.64) \\ 
-    & 100  & 0.5 (0.09) & 0.6 (0.09) & 0.47 (0.09) & 0.47 (0.05) & 0.49 (0.04) & 0.45 (0.05) & 92.71 (13.06) & 83.66 (10.79) & 94.53 (11.2) & 83.56 (10.63)\\[.3cm] 
-   \multirow{5}{*}{100} & 5  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.06) & 0.57 (0.05) & 0.49 (0.06) & 130.47 (22.59) & 135.16 (19.73) & 141.42 (16.98) & 136.3 (19.72) \\ 
-    & 10  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.05) & 0.53 (0.05) & 0.51 (0.06) & 129.49 (22.49) & 134.09 (19.52) & 139.69 (16.96) & 135.26 (19.51) \\ 
-    & 25  & 0.47 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.53 (0.06) & 0.57 (0.05) & 0.51 (0.06) & 127.17 (22.22) & 131.43 (18.97) & 134.47 (17.22) & 132.42 (18.99) \\ 
-    & 50  & 0.5 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.48 (0.06) & 0.56 (0.04) & 0.48 (0.05) & 125.72 (21.8) & 129.27 (18.16) & 129.59 (17.59) & 130.27 (18.15) \\ 
-    & 100  & 0.47 (0.09) & 0.47 (0.09) & 0.43 (0.09) & 0.43 (0.06) & 0.57 (0.04) & 0.47 (0.06) & 128.38 (21.86) & 130.05 (18.05) & 131.83 (19.08) & 130.33 (18.06) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table3}
-\begin{center}
-\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}} $  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.92 (0.02) & 0.89 (0.03) & 48.52 (3.93) & 15.74 (2.34) & 15.76 (2.34) & 15.16 (2.24) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.91 (0.02) & 0.89 (0.02) & 47.7 (4.35) & 18.26 (2.37) & 18.97 (2.42) & 17.68 (2.28) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.79 (0.03) & 0.81 (0.03) & 0.77 (0.03) & 46.95 (6.11) & 27.35 (3.81) & 30.88 (3.84) & 26.58 (3.83) \\ 
-  & 50  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.62 (0.03) & 0.65 (0.03) & 0.63 (0.03) & 56.85 (8.64) & 46.96 (7.02) & 52.92 (7.45) & 45.95 (7.17) \\ 
-  & 100  & 0.73 (0.08) & 1 (0) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.55 (0.04) & 99.22 (12.84) & 93.4 (12.97) & 103.82 (14.1) & 91.95 (13.34) \\[.3cm]  
- \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
-  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29) \\[.3cm] 
- \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.92 (0.03) & 0.95 (0.02) & 52.1 (2.96) & 14.04 (1.78) & 13.36 (2.07) & 14.11 (1.76) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.9 (0.03) & 0.93 (0.02) & 52.25 (3.3) & 15.12 (1.93) & 14.24 (2.29) & 15.18 (1.9) \\ 
-    & 25  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.8 (0.03) & 0.8 (0.03) & 0.8 (0.03) & 52.71 (5.28) & 22.98 (2.9) & 22.6 (3.42) & 22.95 (2.88) \\ 
-    & 50  & 0.7 (0.09) & 0.9 (0.06) & 0.7 (0.09) & 0.65 (0.03) & 0.65 (0.03) & 0.65 (0.04) & 58.65 (8.48) & 39.51 (5.65) & 40.8 (6.3) & 39.35 (5.63) \\ 
-    & 100  & 0.6 (0.09) & 0.87 (0.06) & 0.6 (0.09) & 0.47 (0.05) & 0.45 (0.04) & 0.45 (0.05) & 88.76 (13.66) & 75.93 (11.52) & 81.89 (12.19) & 75.94 (11.41) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.55 (2.9) & 12.13 (1.77) & 14.22 (1.96) & 12.09 (1.77) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.95 (0.02) & 0.93 (0.02) & 49.13 (3.31) & 14.78 (1.85) & 18.21 (2) & 14.75 (1.85) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.02) & 0.85 (0.02) & 0.83 (0.03) & 47.38 (5.13) & 26.85 (3.33) & 32.95 (3.59) & 26.81 (3.32) \\ 
-    & 50  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.61 (0.04) & 0.71 (0.04) & 0.62 (0.04) & 56.73 (7.93) & 50.96 (6.63) & 60.62 (7.21) & 50.88 (6.59) \\ 
-    & 100  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.49 (0.05) & 0.51 (0.04) & 0.49 (0.05) & 93.79 (14.67) & 102.05 (13.37) & 116.45 (15.19) & 101.55 (13.38) \\
-\end{tabular}}
-   \end{center}
-      \vspace{-.5cm}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table4}
-\begin{center}
-\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.04 (3.65) & 21.75 (4.34) & 22.68 (4.41) & 21.83 (4.34) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.92 (0.02) & 0.93 (0.02) & 49.93 (4.11) & 24.3 (4.44) & 25.72 (4.58) & 24.4 (4.45) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.73 (0.04) & 0.8 (0.03) & 0.73 (0.04) & 51.29 (5.39) & 32.8 (5.25) & 35.39 (5.78) & 33.11 (5.21) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.49 (0.04) & 0.44 (0.05) & 0.47 (0.04) & 82.55 (11.61) & 84.26 (12.7) & 98.66 (13.96) & 84.62 (12.59) \\[.3cm] 
- \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
-  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29)\\[.3cm] 
- \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.03) & 0.73 (0.03) & 0.71 (0.04) & 57.87 (8.76) & 50.31 (7.58) & 57.25 (7.75) & 50.53 (7.64) \\ 
-  & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.68 (0.04) & 0.69 (0.04) & 0.69 (0.04) & 58.41 (9.11) & 51.62 (7.91) & 58.61 (8.28) & 51.85 (7.98) \\ 
-  & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.63 (0.04) & 0.68 (0.04) & 0.63 (0.04) & 62.02 (10.02) & 59.08 (8.53) & 65.55 (9.64) & 59.68 (8.53) \\ 
-  & 50  & 0.87 (0.06) & 0.9 (0.06) & 0.87 (0.06) & 0.54 (0.04) & 0.59 (0.04) & 0.52 (0.04) & 71.01 (11.73) & 73.52 (10.18) & 81.81 (11.98) & 74.51 (10.09) \\ 
-  & 100  & 0.73 (0.08) & 0.87 (0.06) & 0.73 (0.08) & 0.47 (0.05) & 0.45 (0.04) & 0.5 (0.05) & 95.93 (15.59) & 104.49 (15.12) & 119.38 (17.62) & 105.72 (14.97) \\[.3cm] 
- \multirow{5}{*}{50} & 5  & 0.8 (0.07) & 0.77 (0.08) & 0.8 (0.07) & 0.52 (0.04) & 0.49 (0.05) & 0.52 (0.04) & 85.95 (14.57) & 90.02 (13.45) & 103.03 (13.91) & 90.08 (13.64) \\ 
-  & 10  & 0.8 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.55 (0.05) & 0.5 (0.04) & 0.53 (0.05) & 86.44 (14.95) & 90.89 (13.79) & 104.62 (14.28) & 91.03 (13.98) \\ 
-  & 25  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.53 (0.04) & 0.46 (0.04) & 0.53 (0.04) & 90.26 (15.82) & 95.36 (14.69) & 109.53 (15.69) & 95.79 (14.83) \\ 
-  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.48 (0.05) & 0.45 (0.05) & 0.45 (0.05) & 99.52 (17.26) & 106.52 (16.17) & 120.99 (18.13) & 107.55 (16.19) \\ 
-  & 100  & 0.57 (0.09) & 0.77 (0.08) & 0.63 (0.09) & 0.41 (0.04) & 0.45 (0.03) & 0.41 (0.04) & 123.11 (20.61) & 135.24 (19.74) & 151.62 (23.42) & 137.21 (19.55) \\[.3cm] 
- \multirow{5}{*}{100} & 5  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.48 (0.05) & 0.48 (0.03) & 0.47 (0.05) & 156.82 (26.36) & 170.06 (25.92) & 196.4 (26.55) & 170.13 (26.27) \\ 
-  & 10  & 0.63 (0.09) & 0.57 (0.09) & 0.67 (0.09) & 0.46 (0.05) & 0.47 (0.03) & 0.47 (0.05) & 157.3 (26.76) & 170.93 (26.21) & 197.96 (26.87) & 171.07 (26.56) \\ 
-  & 25  & 0.67 (0.09) & 0.63 (0.09) & 0.67 (0.09) & 0.44 (0.04) & 0.5 (0.03) & 0.45 (0.04) & 160.32 (27.73) & 173.66 (27.22) & 202.61 (28.01) & 174.28 (27.48) \\ 
-  & 50  & 0.67 (0.09) & 0.67 (0.09) & 0.67 (0.09) & 0.39 (0.04) & 0.43 (0.03) & 0.38 (0.04) & 166.98 (29.35) & 182.83 (28.37) & 210.38 (30.48) & 183.67 (28.61) \\ 
-  & 100  & 0.6 (0.09) & 0.67 (0.09) & 0.53 (0.09) & 0.4 (0.04) & 0.45 (0.04) & 0.41 (0.05) & 188.29 (32.07) & 203.7 (31.63) & 233.44 (35.31) & 205.4 (31.72) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
-
-\section*{References}
-\bibliography{synthetic-prediction-notes}
-
 \end{document}

### 2020-10-18 problem_setup/Notes_on_synthetic_prediction_empBayes.tex
added nonparametric problem setup

--- 2020-08-26 manuscript/manuscript.tex
@@
 
-% title
-\title{Minimizing post-shock forecasting error through aggregation of borrowed information}
-\author{Jilei Lin\thanks{jileil2@ilinois.edu} }
-\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
-\affil{Department of Statistics, University of Illinois at Urbana-Champaign}
-
-%%% New version of \caption puts things in smaller type, single-spaced 
-%%% and indents them to set them off more from the text.
-\makeatletter
-\long\def\@makecaption#1#2{
-  \vskip 0.8ex
-  \setbox\@tempboxa\hbox{\small {\bf #1:} #2}
-  \parindent 1.5em  %% How can we use the global value of this???
-  \dimen0=\hsize
-  \advance\dimen0 by -3em
-  \ifdim \wd\@tempboxa >\dimen0
-  \hbox to \hsize{
-    \parindent 0em
-    \hfil 
-    \parbox{\dimen0}{\def\baselinestretch{0.96}\small
-      {\bf #1.} #2
-      %%\unhbox\@tempboxa
-    } 
-    \hfil}
-  \else \hbox to \hsize{\hfil \box\@tempboxa \hfil}
-  \fi
-}
-\makeatother
+\title{Synthetic prediction methods for minimizing post shock forecasting error}
+\author{Daniel J. Eck and Jilei Lin and Dave Zhao}
+\date{May 2019}
 
@@
 \begin{abstract}
-    We develop a forecasting methodology for providing credible forecasts for time series that have recently undergone a shock.
-We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
-Three shock effect estimators are motivated with the aim of minimizing average forecast risk.
-We propose risk-reduction propositions that provide conditions that establish when our methodology works.
-Bootstrap and leave-one-out cross validation procedures are provided to prospectively assess the performance of our methodology.
-Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
+    We seek to develop a forecasting methodology for time series data that is 
+    thought to have undergone a shock which has origins that have not been 
+    previously observed.  We still can provide credible forecasts for a time 
+    series in the presence of such systematic shocks by drawing from disparate 
+    time series that have undergone similar shocks for which post-shock 
+    outcome data is recorded.  These disparate time series are assumed to have 
+    mechanistic similarities to the time series under study but are otherwise 
+    independent.  The inferential goal of our forecasting 
+    methodology is to supplement observed time series data with post-shock 
+    data from the disparate time series in order to minimize average forecast 
+    risk. 
 \end{abstract}
-
-\section{Introduction}
-
-We provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
-We focus on the specific setting in which a structural shock has occurred and one desires a prediction for the post-shock response at the next time point.
-Standard forecasting methods may not yield accurate predictions in the presence of such structural shocks \citep{baumeister2014real}.
-This is a general problem that has many real life applications.
-For example, one may be interested in forecasting the stock price of a company tomorrow after hearing terrible or great news about the company  after hours trading.
-Companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis, but they only have recent sales data for which the company is operating well.
-All is not lost in this setting, one may be able to supplement the present forecast with past data borrowed from other time series which contain similar structural shocks.
-The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
-Our method of combining shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
-
-We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models.
-In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
-In this setting, the additive shock effect is a random effect that is parameterized in the autoregressive model.
-The shock effect is then estimated using ordinary least squares (OLS).
-The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}.
-One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}.
-Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}.
-On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects from outside data sources are all thought to arise from a  data generating process similar to that of the shock under study.
-For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks.
-
-In our methodological framework, the researcher creates a synthetic panel of time series which have undergone similar structural shocks in the past.
-Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
-As in SCM, care is needed when forming the donor pool of time series.
-However, there are key differences between our framework and SCM.
-We assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock.
-Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing first and second moments.
-
-We estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed.
-We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest.
-This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest.
-Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
-The context in \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
-In our context, the yet to be observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the time series forming the donor pool.
-
-%Therefore the traditional forecast combination framework may not be of any help.  
-%The Bayesian hierarchical approach of \citet{lee2020estimation} may be too sensitive to prior and the hierarchical parametric model setup.
-Overall, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock.
-
-In this article, we will assume a simple autoregressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure.
-Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
-However, our model formulation is more general than \cite{ramaswamy1993empirical}.
-In our model, the donor pool can consist of dependent time series but time series within the donor pool should be independent of the time series of interest.
-However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method.
-We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting.
-The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-Our autoregressive model will consider present day covariates to better motivate similarity weighting.
-The considered adjustment strategies all target the mean of the shock effect distribution.
-Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean.
-We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast.
-The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop.
-We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators.
-This prospective assessment does not require the observation of the post-shock response.
-Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.
-We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020.
-We will show that our proposed adjustment estimators yield much better results than no adjustment in this setting.
-We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts.
-We now motivate our framework for post-shock forecasting.
-
-% Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock effect of the time series under study.
-
-%The question is then how to estimate the shock effects and improve the 
-%prediction?
-This paper proposes three estimators, the adjustment estimator, weighted adjustment estimator, and inverse-variance weighted estimators.
-Section (to be updated) discusses properties of those estimators.
-Section (to be updated) compares the  interplay between prediction risk and different shock effects estimators.
-Section (to be updated) conducts simulation to justify our claims and certain properties that cannot be found analytically.
-
-\begin{figure}[H]
-  \begin{center}
-    \subfloat{\includegraphics[height = 7cm]{comp.pdf}}\\
-     \subfloat{\includegraphics[height = 7cm]{alphahist.pdf}}
-  \end{center}
-     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$.
-(a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series.
-(b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.
-The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool.
-The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=10.22$.
-It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
-\end{figure}
 
@@
 Thus the MSE reduces to the magnitude $\E{\hat y_{1,t} - y_{1,t}}^2$.
-
-%The forecast consists of three steps: (1) pick a model, (2) selection of covariates, (3) choices of donor pool.
-Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
-In this article, we consider a dynamic panel data model with autoregressive structure similar to that in \citet{blundell1998initial}.
-Our dynamic panel model includes an additional shock effect whose presence or absence is given by the binary variable $D_{i,t}$, and we will assume that the donor pool time series are independent of the time series under study.
-The details of this model are in the next section.
-
-Figure \ref{figure1} provides a simple intuition of the practical usefulness of our proposed methodology.
-This figure depicts a time series that experienced a shock at time point $T_1^*+1 = 126$.
-It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations from a donor pool of forty time series that have previously undergone a similar shock for which post-shock responses are recorded.
-Similarity in this context means that the shock effects are random variables that from a common distribution.
-In this example, the mean of the estimated shock effects is taken as a shock effect estimator for the time series under study.
-Forecasts are then made by adding this shock effect estimator to the estimated response values obtained from the estimation procedure that ignores the shock.
-It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock effect.
-We evaluate the performance of this post-shock forecasting methodology throughout this article; we outline situations for when it is expected to work and when it is not.
-
-%Section \ref{properties} will provide a more detailed treatment about when our proposed estimators in Section \ref{constructionofestimators} will improve the prediction under various model setups in Section \ref{modelsetup}.
-More examples will be provided using Monte Carlo simulations in Section \ref{simulation}.
 
@@
 \begin{align*}
-  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}\\
-  \phi_i &\simiid \mrm{Uniform}(-1,1), \\
-   \theta_i &\simiid \mc{F}_{\theta} \text{ with }  \; \mrm{E}_{\mc{F}_{\theta}}(\theta_i) = \mu_{\theta}, \mrm{Var}_{\mc{F}_{\theta}}(\theta_i)  = \Sigma^2_{\theta} \\
-\alpha_i &\simiid \mc{F}_{\alpha} \text{ with }  \; \mrm{E}_{\mc{F}_{\alpha}}(\alpha_i) = \mu_{\alpha}, \mrm{Var}_{\mc{F}_{\alpha}}(\alpha_i)  = \sigma^2_{\alpha}  \\
-\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t})  = \sigma^2 \where \sigma > 0 ,  \\
+  \eta_i &\simiid \mc{F}_{\eta} \\ %\text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}\\
+  \phi_i &\simiid \mc{F}_{\phi} \text{ where } |\mc{F}_{\phi}| < 1, \\
+   \theta_i &\simiid \mc{F}_{\theta} \\%\text{ with }  \; \mrm{E}_{\mc{F}_{\theta}}(\theta_i) = \mu_{\theta}, \mrm{Var}_{\mc{F}_{\theta}}(\theta_i)  = \Sigma^2_{\theta} \\
+\alpha_i &\simiid \mc{F}_{\alpha} \\ %\text{ with }  \; \mrm{E}_{\mc{F}_{\alpha}}(\alpha_i) = \mu_{\alpha}, \mrm{Var}_{\mc{F}_{\alpha}}(\alpha_i)  = \sigma^2_{\alpha}  \\
+\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon} \\ %\text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t})  = \sigma^2 \where \sigma > 0 ,  \\
 \eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t}.
 \end{align*}
-Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
-for $i = 1, \ldots, n+1$.
-We also consider a model where the shock effects are linear functions of covariates with an additional additive mean-zero error.
-For $i = 1, \ldots, n+1$, the random effects structure for this model (model $\mc{M}_2$) is:
-\begin{align}
-\mc{M}_2 \colon \begin{array}{l}
-  y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
-  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+ \t{\varepsilon}_{i},
-\end{array}\label{model2}
-\end{align}
- where the added random effects are
-\begin{align*}
-\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha} \where \sigma_{\alpha}>0\\
-\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
-\end{align*} 
-We further define 
-$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}$. 
-We will investigate the post-shock aggregated estimators in $\mc{M}_2$ 
-in settings where $\delta_i$ is either fixed or random. 
-We let $\mc{M}_{21}$ denote model $\mc{M}_{2}$ with $\delta_i = \delta$ for $i= 1, \ldots, n+1$, 
-where $\delta$ is a  fixed unknown parameter.
-We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects 
-structure for $\delta_i$:
-\begin{align*}
-\delta_i\simiid  \mc{F}_{\delta} \text{ with }\mrm{E}_{\mc{F}_{\delta}}(\delta_i)=\mu_{\delta}, \mrm{Var}_{\mc{F}_{\delta}}(\delta_i)=\Sigma_\delta 
-   \quad \text{ with } \quad  \delta_i  \indep \t{\varepsilon}_{i}.
-\end{align*}
-We further define the parameter sets
-\begin{align}
-  \begin{array}{lll}
-     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
-    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
-  \end{array}
-\end{align}
-where $\Theta$ and $\Theta_1$ can adapt to $\mc{M}_1$ by dropping $\delta_i$. We assume this for notational simplicity.
 
-\subsection{Forecast}
-\label{forecast}
-In this section we show how post-shock aggregate estimators improve upon standard 
-forecasts that do not account for the shock effect.
-%The interest of this study lies in comparing how consideration of shock effects 
-%improves the prediction. 
-More formally, we will consider the following candidate forecasts: 
-\begin{align*}
-  &\text{Forecast 1}: \hat y_{1,T_1^*+1}^1 = \hat\eta_1 
-    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
-    , \\
-  &\text{Forecast 2}: \hat y_{1,T_1^*+1}^2 = \hat\eta_1 
-    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
-    + \hat{\alpha},
-\end{align*}
-where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all OLS estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
-The first forecast ignores the presence of $\alpha_1$ while the second forecast 
-incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study. 
-%Under $\mc{M}_1$ (Section \ref{modelsetup}), $\E{\alpha_1} = \mu_{\alpha}$.
+\section{What comes next}
 
-Note that the two forecasts do not differ in their predictions for 
-$y_{1,t}$, $t = 1,\ldots T_1^*$. Instead, they only differ in predicting 
-$y_{1,T_1^*+1}$. Throughout the rest of this article we show that the donor pool of time series $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$ has 
-the potential to improve the forecasts for $y_{1, T_1^*+1}$ under  different 
-circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-Improvement will be measured by assessing the reduction in risk that Forecast 2 offers over Forecast 1.
-We will return to the theoretical details of risk-reduction in Section \ref{properties}.
+We want to consider decision rules that are nonparametric in nature.
+For example, suppose that we posit a classical linear regression model for \eqref{equation1} (then $\varepsilon_{i,t} \sim N(0, \sigma_i^2)$).
 
-We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response. It is important to note that in general $\hat{\alpha}$ 
-is not a consistent estimator of the unobserved $\alpha_1$ nor does it converge 
-to $\alpha_1$.  Despite these inferential shortcomings, adjustment of the forecast 
-for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has 
-the potential to lower forecast risk under several conditions corresponding to 
-different estimators of $\alpha_1$. % which will be discussed shortly.
+\vspace*{0.5cm}\noindent 1.
+We can estimate all $\alpha$'s using OLS, and provided that $T_i$ is large enough, then $\hat\alpha_i|\alpha_i \approx N(0,\sigma^2_i)$.
+We could then consider estimating the distribution function of the $\alpha$'s using the noisy observations $\hat\alpha_i$, $i=2,\ldots, n$.
+Dave suggested that we may consider deconvolution in order to handle the fact that $\alpha = \hat\alpha + \varepsilon$, where $\varepsilon \approx N(0, \sigma^2_i)$ and $\sigma^2_i$ is either known or estimated very well.
+Then we can use a two step approach to first estimate the distribution $\mc{F}_{\alpha}$ using a nonparametric MLE approach and then second obtain quantiles from this estimated distribution.
+Perhaps a one step approach exists, but we didn't think of one in the meeting (development of such an approach is advantageous and should be thought about).
 
-\subsection{Construction of shock effects estimators}
-\label{constructionofestimators}
+\vspace*{0.5cm}\noindent 2.
+We also discussed extreme-value distributions to handle tail events that are unlikely but potentially disastrous (think ``COVID before COVID'').
+There are approaches that exist which ``tack on'' an extreme-value distribution to the tail of some data-generating process where the bulk of the data is fit by some other methodology.
 
-We now construct the aggregated estimators of the shock effects that appear in Forecast 2 (see Section \ref{forecast}).
-We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.
-First, we introduce the procedures of parameter estimation for $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}).
-For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares (OLS) using historical data of $t = 1, \ldots, T_i$.
-For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$.
-In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate of $\alpha_i$.
-Note that parameter estimation for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
-We emphasize that $\alpha_i$s are random variables, but the OLS estimation is conditioned on the realizations from some distribution.
+\vspace*{0.5cm}\noindent 3.
+We could also consider frameworks which allow for outcome models to be selected, we do not necessary need a linear regression model but we do need to have the ability to estimate a ``shock effect.''
 
-Second, we introduce the candidate estimators for $\alpha_1$. Define the 
-adjustment estimator for time series $i=1$ by
-\begin{equation} \label{adjusted}
-  \hat{\alpha}_{\text{adj}} = \frac{1}{n}\sum_{i=2}^{n+1}\hat{\alpha}_i,
-\end{equation}
-where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of  
-the $\alpha_i$s for $i = 2, \ldots, n+1$.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
-the unknown $\alpha_1$ term for which no meaningful estimation information 
-otherwise exists. It is intuitive that $\hat{\alpha}_{\rm adj}$ should perform 
-well under $\mc{M}_1$ where we assume that $\alpha_i$'s share the same mean 
-for $i= 1, \ldots, n+1$. However, it can also be shown that 
-$\hat{\alpha}_{\rm adj}$ may be less favorable in $\mc{M}_{21}$ 
-and $\mc{M}_{22}$, which will be discussed in detail in Section \ref{properties}.
-
-We also consider the inverse-variance weighted estimator 
-in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i=2, \ldots, n+1$. 
-The inverse-variance weighted estimator is defined as 
-\begin{align*}
-  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
-  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{U}_i)_{22}^{-1},
-\end{align*}
-where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
-$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
-and $\mbf{U}_i$ is the design matrix for OLS with respect to time series 
-for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
-is required and the numerator and denominator terms are dependent in general. 
-%It is hard to evaluate its expectation and variance. 
-%But it is clear 
-%that $\hat{\alpha}_{\rm IVW}$ will generally not be unbiased. 
-However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in 
-practical settings. %when the change 
-%point is not symmetric and/or there are some series with small or large number 
-%of time points recorded. We will then investigate the performance of this 
-%estimator in simulation (Section \ref{simulation}).
-We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ 
-and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of 
-$\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation 
-(see Section \ref{simulation}).
-
-We now motivate a weighted-adjustment estimator for model $\mc{M}_{21}$ 
-and $\mc{M}_{22}$. Our weighted-adjustment estimator is inspired by the 
-weighting techniques in synthetic control methodology (SCM) developed 
-in \cite{abadie2010synthetic}. 
-%we intend to construct a weighted adjustment estimator by using similar but 
-%different methods. 
-However, our weighted-adjustment estimator is not a causal estimator and 
-our estimation premise is a reversal of that in SCM. 
-%The case study of \citet{abadie2010synthetic} in essence observes the data and 
-%estimates the effect of policy. 
-Our objective is in predicting a post-shock response $y_{1,T_1^*+1}$ that is not yet 
-observed using other time series whose post-shock responses are observed.
-%However, the idea of merging information from  similar events (i.e., time series in our 
-%study) to improve the solutions for the problem of interest should be the same.
-
-We use similar notation as that in \cite{abadie2010synthetic} to motivate our weighted-adjustment estimator. Consider a $\mbf{W} \in \R^n$ weight vector 
-$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 
-$i = 2, \ldots, n+1$. Construct
-\begin{align*}
- \mbf{X}_1 = \mbf{x}_{1, T_1^*+1}',
-  \quad  
-  \mbf{X} = \begin{pmatrix}
-    \mbf{x}_{2, T_2^*+1}' \\
-    \vdots \\
-    \mbf{x}_{n+1, T_{n+1}^*+1}'
-  \end{pmatrix},
-  \quad \text{and} \quad 
-  \hat{\mbf{X}}_1(\mbf{W}) 
-    = \mbf{W}'\mbf{X},
-\end{align*}
-where $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{1 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 
-Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
-$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that
-\begin{align}
- \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
-\end{align}
-Note that (\ref{SCM}) tries to find $\mbf{W}^*$ such that $\mbf{x}_{1, T_1^*+1}$ is a convex combination of $\mbf{x}_{i, T_i^*+1}$ for $i = 2, \ldots, n+1$ with weights $\mbf{W}^*$.
-Therefore, $\mbf{W}^*$ should exist as long as $\mbf{X}_1$ falls in the convex hull of
- \begin{align*}
-   \left\{ \mbf{x}_{2, T_2^*+1}', \ldots, \mbf{x}_{n+1, T_{n+1}^*+1}' \right\}.
- \end{align*}
-%It is a reasonable assumption that the pool of time series that we are considering 
-%should be similar to the time series of interest. 
-Our weighted-adjustment estimator will therefore perform well when the pool of time series posses similar covariates to the time series for which no post-shock responses are observed.
-We compute $\mbf{W}^*$ as
-\begin{align}
-  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})}_{p}. 
-  \label{W}
-\end{align}
-%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
-\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
-so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
-%still hold approximately 
-and that weighted-adjustment estimation techniques of this form are not 
-appropriate when the fit is poor. 
-Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
-is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
-%we are mainly interested in constructing the following adjustment estimator:
-Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
-  \begin{align*}
-    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
-    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
-      w^*_2 & \cdots & w^*_{n+1}
-    \end{pmatrix}'.
-  \end{align*}
- %Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model.
-To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock.
-This model somehow accounts for the impact of past information on the shock effects.
- We further define
-\begin{align*}
-  \mathbf{V} = (\mathbf{x}_{2, T_2^*+1}, \ldots,\mathbf{x}_{n+1, T_{n+1}^*+1}).
-\end{align*}
-\begin{prop}
-  \label{uniqueness} If $\mathbf{V}$ has full rank and it exists some $\mathbf{W}$ satisfies (\ref{SCM}), the solution to  (\ref{W}) is unique.
-\end{prop} 
-Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.
-Note that $\mathbf{V}$ is $p \times n$.
-Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $p \geq n$.
-However, when $p < n$, $\mathbf{W}^*$ may not be unique.
-If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $p < n$, there are infinitely many solutions to (\ref{SCM}).
-The issue of non-uniqueness is further discussed in Section \ref{varbootstrap}.
-
-\begin{remark}
-% Though in Section \ref{modelsetup} we assume $\mbf{x}_{i,t}\in \reals^p$ and bases construction for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$  on this fact, we will shortly show that the covariates need not be of the same dimension across disparate time series.
-\label{remark1}In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
- % We can insert $\mathbf{0}$ into the covariates of disparate time series for the parts that they do not share.
-For example, suppose $\mathbf{x}_{2, t}, \mathbf{x}_{2, t-1}\in \reals^{p-1}$ and $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}\in \reals^p$ are the covariates for time series 2 and 3.
-Assume that the $p$th column of $\mathbf{x}_{3, t}, \mathbf{x}_{3, t-1}$ is the part they do not share.
-In this case, we can let $\mathbf{x}^{adj}_{2, t}=(\mathbf{x}_{2, t}, \mathbf{0})$, $\mathbf{x}^{adj}_{2, t-1}=(\mathbf{x}_{2, t-1}, \mathbf{0})$ to satisfy the $p$-dimension requirement.
-However, it is not necessary that the all $p$ covariates are important for every time series under study.
-The regression coefficients $\theta_i$ are nuisance parameters that are not of primary importance.
-% In this regard, OLS estimations in software can reparameterize the design matrix.
-Of course, the column space of the design matrix does not change compared to the one in original dimension.
-Thus, the least squares estimators do not change.
-In other words, OLS estimation need no adjustment.
-The generalization may only apply to the construction of weighted-adjustment  estimator $\hat{\alpha}_{\rm wadj}$.
-It will be understood that structural 0s in $\theta_i$ correspond to variables that are unimportant. 
-\end{remark}
-
-\begin{remark}
-  Our forecasting premise and estimation construction shares similarities with Bayesian viewpoints.
-From a Bayesian perspective, if we assign a prior $\pi$ to $\alpha_1$, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as the Bayes rules with respect to $\pi$ under different loss functions.
-If the sampling distribution of the data and $\pi$ are known, it is possible to compute the Bayes risks of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ with respect to $\pi$,  thus enabling comparisons among them.
-Additionally, from Theorem 2.4 in Chapter 5 of \cite{lehmann2006theory}, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are admissible if they are unique with probability one.
-\end{remark}
-
-\section{Forecast risk and properties of shock effects estimators}
-\label{properties}
-
-In this section, we discuss the properties that are related to forecast-risk reduction.
-In discussion of risk, it is useful to derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.
-The expressions for the expectations are as follow,
-
- \begin{enumerate}[label = (\roman*)]
-    \item Under $\mc{M}_{1}$, $\E{\hat{\alpha}_{\rm adj}}=\E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha}$.
-    \item Under $\mc{M}_{21}$, 
-    $
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1}
-    $
-    and
-    $
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} .
-    $
-    \item Under $\mc{M}_{22}$,
-    $
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1}
-    $
-    and
-    $
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} .
-    $
-  \end{enumerate}
-Formal justification for these results can be found in Appendix.
-Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$.
-However, under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$.
-Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$.
-We collect these results in the following proposition.
-
-\begin{prop}
-\label{unbiased} 
-\quad 
-\begin{enumerate}[label = (\roman*)]
-  \item Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$.
-Under $\mc{M}_{21}$ and $\mc{M}_{22}$, $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ in general.
-  \item Suppose that $\mbf{W}^*$ satisfies (\ref{SCM}). Under $\mc{M}_{1}$, $\mc{M}_{21}$ and $\mc{M}_{22}$, $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
-\end{enumerate}
-\end{prop}
-
-Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation for evaluation of these conditions.
-% for $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm wadj}$ to reduce risk, and make it more clear with respect to when one is better than the other.
-These conditions and bootstrap will be discussed in Section \ref{conditions} and \ref{varbootstrap}, respectively.
-Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below.
-
-\begin{enumerate}[label = (\roman*)]
-  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
-\begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
-\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
-\end{align*}
-\item Under $\mc{M}_{22}$, 
-\begin{align*}
-\var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
-  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
-\end{align*}
-\end{enumerate}
-Formal justification for these results can be found in Appendix.
-Note that the variances are not comparable in closed-form %we shall see that it is difficult to compare variances between $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$
-because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
-
-Section \ref{conditions} details conditions needed for risk-reduction and comparisons of adjustment estimators.
-These conditions involve variances and expectations which may be difficult to compute in practice.
-To make use of those conditions in practice, estimation is required.
-Sections \ref{varbootstrap} introduce parametric bootstrap, which estimates the involved parameters in those conditions and thus motivates prospective decision-making  about whether $\hat{\alpha}_i$ reduces the risk.
-Section
- \ref{loocv} describes our leave-one-out cross validation procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study.
-Our simulations verify these procedures.
-
-\subsection{Risk-reduction conditions for shock effects estimators}
-\label{conditions}
-
-In this section we will discuss the conditions for risk reduction for individual shock effects estimators under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-%The reason is that if the estimator of $\alpha_1$ turns out to be an unbiased estimator of $\E{\alpha_1}$, the conditions get  simplified.
-For an adjustment estimator $\hat{\alpha}$, we will write the risk-reduction as $\Delta(\hat{\alpha})=R_{T_1^*+1,1}-R_{T_1^*+1,2}$ where $R_{T_1^*+1,2}$ is the risk of Forecast 2 calculated using the adjustment estimator $\hat{\alpha}$.
-
-\subsubsection{Conditions under $\mc{M}_1$}
- \label{conditionsmodel1}
-
-Recall that Proposition \ref{unbiased} implies that the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ are unbiased for $\E{\alpha_1}$ under $\mc{M}_1$.
-With this result, we will have  the following propositions that specify the conditions that are necessary for risk reduction.
-
-\begin{prop}
-\label{proprisk}Under $\mc{M}_1$,
-\begin{enumerate}[label = (\roman*)]
-  \item $\Delta(\hat\alpha_{\rm adj}) > 0$  when 
-$\Var(\hat{\alpha}_{\rm adj}) < \mu_{\alpha}^2$.
-  \item if $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<\mu_{\alpha}^2$. 
-\end{enumerate}
-\end{prop}
-
-Proposition \ref{proprisk} says that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties.
-In this setting, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$.
-% from Proposition \ref{proprisk}.
-From Proposition \ref{proprisk}, we obtain a risk-reduction condition
-\begin{align}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
-\end{align}
-
-Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$ (see Forecast in Section \ref{forecast}); (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
-%This result is also intuitive.
-For example, if  $\mu_{\alpha}$ is large, Forecast 1 will definitely work poor because large  $\mu_{\alpha}$ implies shock effects that cannot be ignored.
-See Section \ref{forecast} for forecast formulation for details.
-
-If  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}.
-From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
-\begin{equation} \label{varwadj}
-\var{\hat{\alpha}_{\rm wadj}}
- = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
-\end{equation}
-In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.
-However, the above criteria are generally difficult to evaluate in practice.
-Sections \ref{varbootstrap} and \ref{loocv}  provide detailed treatments on how to estimate the sign of $\Delta(\hat\alpha)$ in practice.
-
-\subsubsection{Conditions under $\mc{M}_{21}$ and $\mc{M}_{22}$}
-\label{conditionsm2122}
-
-The shock effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
-%It is a more reasonable and general model since it is often the case that shock effects differ by means among disparate time series in practice.
-$\mc{M}_{22}$  further adds the random effect structure of $\delta$ to  $\mc{M}_{21}$ for generalization.
-However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
-%From Proposition \ref{varprop}, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$  will be as in Proposition \ref{propriskwadj2}.
-We now state conditions for risk-reduction.
-
-\begin{prop}
-\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$  under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
-\end{prop}
-Under Proposition \ref{propriskwadj2}, we can obtain a risk-reduction inequality that is similar to \eqref{varwadj},
-\begin{align*}
-\var{\hat{\alpha}_{\rm wadj}}
- = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}) < (\E{\alpha_1})^2,
-\end{align*}
-where $\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$.
-The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.
-Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally.
-Hence, Proposition \ref{proprisk} no longer holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.
-
-As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting.
-By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
-\begin{align*}
- \E{\alpha_1^2}= \var{\alpha_1}+(\E{\alpha_1})^2
- &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
-  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
-  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
-\end{align*}
-The above inequality simplifies to 
-\begin{equation} \label{ineq}
- (\E{\alpha_1})^2 >\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
-\end{equation}
-
-%A simple mean-squares decomposition produces the following inequality for assessing the favorability of $\hat{\alpha}_{\rm wadj}$ to $\hat{\alpha}_{\rm adj}$ under models $\mc{M}_{21}$ and $\mc{M}_{22}$,
-% \begin{align*}
-%  \var{\hat{\alpha}_{\rm adj}} 
-%  -\var{\hat{\alpha}_{\rm wadj}} + \big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2> 0.
-%\end{align*}
-
-%If it turns out to be fact that the variance of the weighted-adjustment estimator is greater than that of adjustment estimator, we should be aware that  the compromise for variance because of using $\hat{\alpha}_{\rm wadj}$ shouldn't exceed the squared bias, i.e., $\big(\E{\hat{\alpha}_{\rm adj}}-\mrm{E}(\alpha_1)\big)^2$.
-
-As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$.
-We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$.
-That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
-In fact, more generally, using similar proof of Lemma \ref{risklemma}, it can be shown that under $\mc{M}_2$, the risk-reduction quantities are
-\begin{align*}
-  \Delta(\hat{\alpha}_{\rm adj}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2,\\
-  \Delta(\hat{\alpha}_{\rm IVW}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2 ,\\
-  \Delta(\hat{\alpha}_{\rm wadj}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}},
-\end{align*}
-where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using bootstrap and leave-one-out cross validation procedures developed in Sections \ref{varbootstrap} and \ref{loocv}.
-
-%%%%%%%%%%% Commenting out Section 3.2 %%%%%%%%%%%%
-%\subsection{Comparisons among estimators}
-%\label{comparisons}
-
-%In comparing  shock effects estimators, we would assume that the risk-reduction conditions are satisfied as in Section \ref{conditions}.
-
-%Denote the risk-reduction quantities for adjustment estimators as $\Delta_{\rm adj}$, $\Delta_{\rm IVW}$, and $\Delta_{\rm wadj}$, respectively for standard adjustment, inverse-variance weighted estimator, and weighted-adjustment estimato.
-%%%As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration.
-For example, if we find that $\Delta_{\rm wadj}>\Delta_{\rm adj}$ and $\Delta_{\rm wadj}>\Delta_{\rm IVW}$, the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ is the most favorable.
-%According to  discussion in Section \ref{conditionsm2122}, we know that under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, the risk-reduction quantity for $\hat{\alpha}_{\rm IVW}$ is
-%\begin{align*}
-%  \Delta_{\rm IVW} = (\E{\alpha_1})^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2.
-%\end{align*}
-%From discussions in Section \ref{conditions}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ differ across models, we will discuss in different cases accordingly.
-
-%\subsubsection{Under $\mc{M}_{1}$}
-
-%From Proposition \ref{proprisk}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
-%\begin{align*}
-%  \Delta_{\rm adj} 
-%  = \mu_{\alpha}^2 -\var{\hat{\alpha}_{\rm adj}}
-%\quad   \text{ and } \quad 
-%  \Delta_{\rm wadj} 
-%  = \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}.
-%\end{align*}
-%Under the framework of $\mc{M}_1$, the risk-reduction quantity  for $\hat{\alpha}_{\rm IVW}$ is
-%\begin{align*}
-%  \Delta_{\rm IVW} = \mu_{\alpha}^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2.
-%\end{align*}
-%In other words, when $\var{\hat{\alpha}_{\rm wadj}}<\var{\hat{\alpha}_{\rm adj}}$ and $\hat{\alpha}_{\rm wadj} < \var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\mu_{\alpha})^2$, we would prefer $\hat{\alpha}_{\rm wadj}$ as the best estimator.
-Other conditions for voting the other estimators as the best one follow similarly.
-
-%\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}
-%\label{section322}
-
-%According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
-%\begin{align*}
-%  \Delta(\hat{\alpha}_{\rm adj})
-%  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
-%\quad   \text{ and } \quad 
-%  \Delta(\hat{\alpha}_{\rm wadj})
-%  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
-%\end{align*}
-%In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
-%\begin{align*}
-% \Delta(\hat{\alpha}_{\rm IVW})
-%  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
-%\end{align*}
-
-% These are some analytical results for comparison studies among estimators of $\alpha_1$.
-Next, we will detail a framework for estimation of risk-reduction  quantities using a parametric bootstrap routine.
-Therefore, the above inequalities can be analyzed numerically and risk-reduction quantities can be estimated using plug-in estimators in practice.
-
-%\begin{remark}
-%  In Section \ref{constructionofestimators}, we noted that $\mathbf{W}^*$ may not be unique if $2p < n$.
-However, Proposition \ref{proprisk} and \ref{propriskwadj2} will hold for  every $\hat{\alpha}_{\rm wadj}$ using  $\mathbf{W}^*$ that satisfies (\ref{SCM}).
-%\end{remark}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Bootstrap for risk-reduction evaluation problems}
-\label{varbootstrap}
-
-In this section, we present bootstrap procedures that approximate the distribution of our shock effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction quantity using plug-in approach in practice.
-Our procedure involves the resampling of residuals in the separate OLS fits.
-This procedure has its origins in Section 6 of \citet{efron1986bootstrap} and Chapter 12 of \cite{kilian2017structural}.
-Our procedure involves the resampling of the residuals which are assumed to be the realizations of an iid process.
-
-Our first bootstrap procedure is as follows: Let $B$ be the bootstrap sample size.
-At iteration $b$, first resample the indices $I = \{2, \ldots, n+1\}$ of the donor pool with replacement to form $I^{(b)}$ with cardinality $n$, where we note that the elements of $I^{(b)}$ may not be unique in terms of their  indices in the donor pool.
-Initialize $y_{i,0}^{(b)}=y_{i,0}$ for all $i \in I^{(b)}$.
-Then, resample the residuals under models $\mc{M}_1$ or $\mc{M}_{2}$, compute the bootstrapped response  $y_{i,t}^{(b)}$ for   $t \in \{1, \ldots, T_i\}$ using the model estimated by original data,  and obtain shock effect estimators for each of the time series in the donor pool for all $i \in I^{(b)}$.
-These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-We can then estimate distributional quantities of our shock effect estimators under our considered models with the bootstrap samples $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-We denote this procedure by $\mc{B}_u$.
-We motivate a second bootstrap procedure $\mc{B}_f$ which treats the the donor pool as fixed, and not a realization from an infinite super-population.
-Therefore, there is no resampling of the donor pool in $\mc{B}_f$, it is otherwise similar to $\mc{B}_u$.
-An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in Section 2 in the Supplementary Materials.
-
-We will explicitly use these bootstrapped samples of shock effect estimators to check the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
-Recall that $\hat{\alpha}_{\rm adj}$,  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ under $\mc{M}_1$ and $\mc{M}_2$ from Proposition \ref{unbiased}.
-Our bootstrap procedure estimates the variance of our adjustment estimators.
-We can then estimate the risk-reduction propositions and inequalities.
-For example, we can estimate $\Delta(\hat{\alpha}_{\rm adj})$ under model $\mc{M}_{21}$ or $\mc{M}_{22}$ with
-\begin{align*}
-%  \Delta(\hat{\alpha}_{\rm adj})
-  %&= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
-  \hat{\Delta}(\hat{\alpha}_{\rm adj}) & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
-\end{align*}
-where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance estimator for $\Var(\hat{\alpha}_{\rm adj})$.
-
-%Suppose we have a pool of shock effect estimators, $\mc{A}$, e.g., $\mc{A}= \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ in our study.
-We can determine which one is the best shock effect estimator.
-Suppose the $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ and $\hat{\Delta}(\hat{\alpha}_{\rm IVW})$ are estimators for $\Delta(\hat{\alpha}_{\rm wadj}) $ and $\Delta(\hat{\alpha}_{\rm IVW})$, respectively.
-Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}(\hat{\alpha})>0$ for $\hat{\alpha}\in \mc{A}$.
-Besides, we can also select the best shock effect estimator accordingly.
-Define
-%\begin{align}
-%	\hat{\alpha}_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \hat{\Delta}(\hat{\alpha}) \quad \text{ and } \quad  \alpha_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \Delta(\hat{\alpha}).
-\label{best}
-%\end{align}
-%That is, the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities whereas $\alpha_{\rm best}$ is the true best shock effect estimator given observed post-shock response.
-See more discussions in Section \ref{loocv}.
-
-There are some philosophical distinctions between $\mc{B}_u$ and $\mc{B}_f$.
-$\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.
-A double bootstrap procedure with similar steps can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
-The double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, can check whether a bootstrap percentile interval of resampled estimates of $\Delta(\hat{\alpha})$ contain 0 at a desired error threshold.
-We investigated such a double bootstrap procedure and found that it produced inferences that were similar to those produced using the bootstrap techniques developed in the main text.
-
-We stress that our bootstrap approximations cannot alleviate the inherent bias of using our adjustment estimators as surrogates for $\alpha_1$.
-We caution that the bootstrapping residuals in OLS estimation may not provide valid inference in moderate or high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}; see alternatives for residual bootstrapping in linear models in \citet{el2018can}.
-
-Recall that $\mathbf{W}^*$  may not be unique if the conditions in Proposition \ref{uniqueness} are not satisfied.
-Non-uniqueness might be a concern theoretically.
-This is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$'s all targeting on the same $\alpha_1$.
-For example, consider the case where the size of  donor pool to be 2, $\var{\hat{\alpha}_2}=1$, $\var{\hat{\alpha}_3}=2$, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
-In this scenario, the weighted adjustment estimator induced by $\mathbf{W}^*_1$ has variance 1 whereas the one by $\mathbf{W}^*_2$ has variance 2.
-Nevertheless, even if $\hat{\alpha}_i$ has the same variance across $i = 2, \ldots, n+1$, the same issue would occur if there were infinitely many $\mbf{W}^*$ with different norms.
-It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}).
-Simulations in the Section 4 of the Supplementary Materials provide some evidence that non-uniqueness of $\mathbf{W}^*$ is not problematic for inferences.
-
-\subsection{Leave-one-out cross validation with $k$ random draws}
-\label{loocv}
-
-In this section, we adapt leave-one-out cross validation (LOOCV) to our estimation context in order to provide prospective evaluations of our adjustment techniques.
-Our proposed LOOCV procedure has its roots in Section 7.10 of \citet{hastie2009elements}.
-Recall in Section \ref{modelsetup} that we are given the data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining observations form the donor pool.
-For iteration $m \in \{1,\ldots,n\}$ of our LOOCV procedure, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}_m, t = 1, \ldots, T_{i}\}$, where $\mc{I}_m=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, we can evaluate the performance of our adjustment estimators and the original forecast made without adjustment (i.e., Forecast 1 in Section \ref{forecast}).
-
-LOOCV can be very computationally intensive when $n$ is large, especially when combined with bootstrapping.
-To alleviate these concerns we can perform LOOCV with a random subset of $k \leq n$ iterations selected without replacement.
-In this setting, we let $\mc{J}$ be the randomly sampled indices.
-For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Based on the new donor pool, we estimate relevant parameters using bootstrap procedures outlined in Section \ref{varbootstrap}.
-In other words, $k$ times of bootstrapping are nested in a LOOCV procedure.
-We find that $k=5$ or $k=10$ iterations of LOOCV performs well.
-
-We now outline how LOOCV can be used to prospectively assess the performance of adjustment estimators.
-Let $\mc{A}$ be the set of adjustment estimators.
-For each $\hat{\alpha} \in \mc{A}$, let $\delta_{\hat{\alpha}} = I(\hat\Delta(\hat{\alpha})>0)$ be a decision rule where $I(\cdot)$ is the indicator function and a $1$ corresponds to the decision to use  estimator $\hat\alpha$.
-If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported 1 (0, respectively) so that it makes the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be incorrect.
-If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported 0 (1, respectively) so that it makes the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be correct.
-These situations are depicted in the following table: \vspace*{0.3cm}
-
-\begin{center}
-  \begin{center}
-      \begin{tabular}{cc|c|c}
-        \hline
-        & & \multicolumn{2}{c}{Decision} \\
-        & & $\delta_{\hat{\alpha}} = 1$ & $\delta_{\hat{\alpha}} = 0$ \\ 
-                \hline
-     \multirow{2}{*}{Truth}  & $\Delta(\hat{\alpha})>0$ & Correct & Incorrect \\
-      \cline{3-4}
-      & $\Delta(\hat{\alpha})<0$  & Incorrect & Correct \\
-      \hline
-      \end{tabular}
-  \end{center}
-\end{center}
-%Similar definitions can be adapted to the best shock effect estimators. 
-\vspace*{0.3cm}
-
-We will use 
-$
-	\mc{C}(\delta_{\hat\alpha}) 
-	= I(\delta_{\hat{\alpha}} \text{ is correct})
- %\quad \text{ and } \quad  	
- %\mc{C}(\mc{A}) 
-%	= I(\hat{\alpha}_{\rm best} = \alpha_{\rm best})
-$
-as a metric that evaluates the performance of forecasts made with the adjustment estimator $\hat\alpha$.
-If $\E{\mc{C}(\delta_{\hat{\alpha}})} > 0.5$, we claim that $\delta_{\hat{\alpha}}$ is better than random guessing.
-Note that $\mc{C}(\delta_{\hat{\alpha}})$ can generally be computed only when the post-shock response is observed.
-However, it is possible to estimate $\E{\mc{C}(\delta_{\hat{\alpha}})}$ using LOOCV.
-%For each $\hat{\alpha}\in \mc{A}$ we can compute the consistency as $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ using the estimation procedures in Section \ref{varbootstrap}.
-The LOOCV estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$ are
-\begin{equation} \label{loocvm}
-	 \bar{\mc{C}}(\delta_{\hat{\alpha}})= \frac{1}{n} \sum_{m = 1}^n \mc{C}^{(-m)}(\delta_{\hat{\alpha}}),
-	\end{equation}
-where $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ is computed with respect to donor pool with index set $\mc{I}_m$ and the $m+1$ time series is treated as the time series of interest.
-The LOOCV with $k$ random draws estimates $\E{\mc{C}(\delta_{\hat{\alpha}})}$ as
-\begin{equation} \label{loocvk}
-	 \bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})	,
-\end{equation}
-where $\mc{J}$ is the set of the $k$ randomly sampled indicies.
-%Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively.
-The estimation bias should decrease as $k \to n$.
-
-\begin{remark}
-  Note that we allow the time series within the donor pool to be dependent but donor pool should be independent of the time series of interest.
-However, if we assume the mutual  independence structure, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
-In other words, mutual independence assumption is not related to  $\E{\mc{C}(\delta_{\hat{\alpha}})}$ (i.e., the intrinsic correctness) but its estimation.
-\end{remark}
-
-\section{Numerical Examples}
-\label{simulation}
-
-\subsection{Modeling setup}
-
-In this section we provide justification for our methods based on Monte Carlo simulation.
-We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
-We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}.
-Parameter setup of our simulations is detailed as follows: the $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
-We sampled $T_i$'s independently from  $\text{Gamma}(15, 10)$ that are further rounded to integers, where the minimum allowable value of $T_i$ is fixed to be 90.
-We will randomly draw $T_i^*$ from $\{p + 4, \ldots, T_i-1\}$.
-The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
-Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
-Additionally, we generated the covariates from $\text{Gamma}(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
-Last, we set $\delta_i\simiid  \normal{1}{0.5}$ and $\theta_i \sim \normal{0}{1}$.
-We will consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
-We choose a Monte Carlo sample size of $30$ replications and a bootstrap sample size of $B = 200$ for computation.
-Means and standard errors for estimated quantities will be recorded.
-Our LOOCV procedure will consider $k=5$ random draws.
-Recall in Section \ref{loocv} that $B$ times of bootstrap are nested in a LOOCV with $k$ random draws.
-It implies that $B(k+1)$ times of bootstrap replications are required for each Monte Carlo simulation.
-
-\subsection{Performance metrics}
-
-Our adjustment estimators will be evaluated by multiple criteria.
-We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the guess, with 1 indicating that $\hat{\alpha}$ provides risk-reduction over the simple no-adjustment forecast, and 0 indicates the converse.
-We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
-We will also consider the Euclidean distance between the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ and the realized post-shock response $y_{1,T_1^*+1}$.
-The first two metrics can combine to assess our forecasting methodology prospectively while the latter requires the realization of the post-shock response $y_{1,T_1^*+1}$.
-
-\subsection{Monte Carlo results}
-\label{parametricbootstrapsimulation}
-
-In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities.
-We mainly discuss simulations under $\mc{M}_2$ (see Section \ref{modelsetup}) for $\mc{B}_u$ and $\mc{B}_f$ (see Section \ref{varbootstrap}) with comparisons to those under $\mc{M}_1$ whose results are listed in Section 3 in the Supplementary Materials.
-Two simulation setups are investigated.
-
-In the first simulation setup, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$.
-Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates.
-In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.
-Results are displayed in Table~\ref{table1} in the Appendix \ref{tablesappendix}.
-
-In the second simulation setup, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n=10$.
-Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.
-Results are  in Table~\ref{table2} in the Appendix \ref{tablesappendix}.
-
-First, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we  observe from Table \ref{table1} that the decision making of $\delta_{\hat{\alpha}}$ is nearly correct  for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small  from Table \ref{table1}.
-The reasons can be explained as follows.
-When $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal according to construction of $\hat{\alpha}_{\rm wadj}$ in Section \ref{constructionofestimators}.
-Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
-However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is large), the decision rule $\delta_{\hat{\alpha}}$  becomes unreliable for $\hat{\alpha}\in \mc{A}$.
-It is to be expected since the bootstrap estimates become more biased.
-However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$.
-Second, fixing $\sigma_{\alpha}$, we can observe that the correctness of $\delta_{\hat{\alpha}}$ increases when $n$ increases.
-It is due to the robustness gain in estimation when $n$ increases.
-
-Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down, though they  follow similar patterns.
-Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$.
-But it is not present for $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ since we applied the fact  $\hat{\alpha}_{\rm wadj}$ is unbiased for $\E{\alpha_1}$ from Proposition \ref{unbiased} in plugging it in with replacing $\E{\alpha_1}$.
-Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative.
-Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of correctness between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
-For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.83 \times 0.59 = 0.490$ from Table \ref{table1}.
-In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.
-
-From columns related to distance to $y_{1, T_1^*+1}$ in Table \ref{table1}, as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
-When $\sigma_{\alpha}= 5, 10, 25$, forecasts using $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are always better than the original forecast significantly.
-But it does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
-It is reasonable in that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
-Nevertheless, no statistical evidence has been found to support the claim that $n$ matters in prediction.
-In other words, the size of the donor pool matters for producing reliable decision-making of $\delta_{\hat{\alpha}}$ rather than reliable prediction.
-
-From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$   decreases, which is a pattern similar to the one shown in the first experiment.
-Furthermore, as $\sigma$ increases fixing $\sigma_{\alpha}$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases as well.
-Note that the correctness  hinges on the estimation of the parameters.
-Since $\hat{\alpha}_{\rm wadj}$  is a linear combination of OLS estimates, as $\sigma$ increases, $\var{\hat{\alpha}_{\rm wadj}}$ increases as well.
-Therefore, $\hat{\alpha}_{\rm wadj}$ become more volatile and its estimation of $\E{\alpha_1}$ can be less reliable.
-Those reasons can explain  why an increase of $\sigma_{\alpha}$ contributes to a decrease of  $\bar{\mc{C}}(\delta_{\hat{\alpha}})$.
-We observe similar patterns for distance to $y_{1, T_1^*+1}$ as well.
-When $\sigma$ increases with fixing $\sigma_{\alpha}$, it is likely that the degree of variation of $y_{1,t}$ exceeds the extent of adjustment improvement $\hat{\alpha}$ can contribute to for $\hat{\alpha}\in \mc{A}$.
-
-With respect to averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases.
-This is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
-The reasons are outlined as follows: Recall in Section \ref{conditionsm2122}, the conditions of risk-reduction propositions involve $(\E{\alpha_1})^2 > \var{\hat{\alpha}} + (\E{\hat{\alpha}}-\E{\alpha_1})^2$ for $\hat{\alpha}\in \mc{A}$.
-Notice that $\var{\hat{\alpha}}$ is an increasing function of $\sigma$ since $\hat{\alpha}$ is estimated by OLS.
-Therefore, it explains the reason why the increase of $\sigma$ would result in a decrease of averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ since the inequality is not likely to hold when  $\var{\hat{\alpha}}$ increases.
-
-Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented.
-See Table \ref{table3} and Table \ref{table4} for results in the Appendix \ref{tablesappendix}.
-Comparing Table \ref{table1}
- and Table \ref{table2} yields that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
-For other situations, $\mc{B}_u$  and $\mc{B}_f$  are rather similar.
-It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool.
-Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
-It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$.
-However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_f$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$.
-In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is moderately small; otherwise, they are similar.
-%See more discussions for differences between $\mc{B}_u$ and $\mc{B}_f$ in Section \ref{discussion}.
-
- Simulation results corresponding to model $\mc{M}_1$ are listed in Section 3 in Supplementary Materials.
-Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$, except for the difference among estimators.
-The results show that (1) the performance of $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are nearly the same and (2) in many situations, $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are  better than $\hat{\alpha}_{\rm wadj}$; in other situations, they are mostly the same.
-Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
-Therefore, similarity weighting may not be informative when the model for $\alpha_i$ is identified wrongly.
-Under $\mc{M}_1$, simple averaging, aimed for a reduction of variance, or inverse-variance weighting, targeting on reducing negative effects from varying time lengths, may work better.
-
-We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population in these simulations.
-Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
-In this scenario, $\mathbf{W}^*$ will take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$.
-However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
-Moreover, simulations in Section 4 of the Supplementary Materials show that non-uniqueness does not seriously compromise the inference.
-
-\section{Forecasting Conoco Phillips stock in the presence of shocks}
-\label{forecasting}
-
-We demonstrate our post-shock forecasting methodology on a time series of Conoco Phillips share prices after the occurrence of a structural shock.
-Conoco Phillips is a large oil and gas resources company \citep{conocowhatwedo}.
-The particular post-shock response that we predict happened after trading ended on Friday March 6th, 2020 and before trading began on Monday March 9th, 2020.
-It is reasonable that the timing of this shock is known, several events occurred over the trading weekend which had an impact on stock markets and the oil markets.
-For example, Russia and OPEC began a battle for global oil price control on Sunday, March 8th \citep{sukhankin2020russian}, and several US states began declaring state of emergencies in response to the evolving coronavirus pandemic \citep{nygov, alonso2020state}.
-In this analysis we make the following design considerations:
-
-%\subsection{Background}
-%\label{background}
-
-%Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo}. %and with a relatively recent initial public offering \citep{conocohist}. 
-%Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control on the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}.
-Furthermore, fear and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th.
-Major events include the SXSW festival being cancelled as trading closed on March 6th \citep{wang2020impact}.
-New York declared a state of emergency on March 7th \citep{nygov}, and by Sunday, March 8th, eight states have declared a state of emergency \citep{alonso2020state} while Italy placed 16 million people in quarantine \citep{sjodin2020only}.
-
-%Economic indicators forecasted our recession before the coronavirus pandemic began.
-The current recession followed an inversion of the yield curve that first happened back in March, 2019 \citep{tokic2019yield}.
-An inversion of the yield curve is an event that signals likely recessions \citep{andolfatto2018yield, bauer2018economic}.
-In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock.
-We also consider previous OPEC oil supply shocks \citep{mensi2014opec}.
-We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models.
-Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}.
-
-\begin{enumerate}
-\item[(1)] {\bf Selection of model}.
-We will use an AR(1) model to forecast Conoco Phillips stock price.
-This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.
-For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect.
-All estimates will be adjusted for inflation.
-The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects.
-All the parameters are estimated using OLS.
-\item[(2)] {\bf Selection of covariates}.
-We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$.
-The model of $\alpha_i$ incorporates daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX).
-The model for $y_{i,t}$ disregards VIX.
-This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
-\item[(3)] {\bf Construction of donor pool}.
-Our donor pool consists of Conoco Phillips shock effects observed in the past.
-We consider shock effects which occurred on March 14, 2008, several days in September, 2008, and November 27, 2014.
-The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession.
-In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}.
-These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Mac in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}.
-The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}.
-%The reasons for those three shocks are.
-%  \begin{enumerate}
-%  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities.
-On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank.
-The day of the announcement, the stocks of other major Wall Street firms tumbled (including Conoco Phillips).
-These concerns then spilled over into the broader universe of stocks \citep{shorter2008bear}.
-%In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
-%  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets.
-The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}.
-Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
-%  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}.
-During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors.
-During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}.
-%  \end{enumerate}
-\end{enumerate}
-
-We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020.
-The covariates and response of time series in the donor pool are adjusted for inflation.
-Note that there are three shock effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials.
-The estimated shock-effects for $\alpha_i$ are $-0.922, -7.063, -5.777, -6.395, -4.207$ for $i = 2, \ldots, 6$, respectively.
-Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
-Note that non-uniqueness problems will not occur in this analysis since the conditions of Proposition \ref{uniqueness} are satisfied.
-To avoid the effect of  unit differences on weighting, we center and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
-For $\hat{\alpha}_{\rm wadj}$, we observe that
-$
-  \mathbf{W}^*= (0.000,0.000, 0.000, 0.273, 0.727)
-$
-and 
-$
-  \Vert\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\Vert_2 = 3.440.
-$
-Note that the norm is computed using the $k$-dimensional Euclidean metric.
-The solution $\mathbf{W}^*$ suggests that the shock effect of interest is very similar to the September 25, 2008 shock effect and  the November 27, 2014 shock effect.
-
-%\begin{table}[H]
-%  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table5}
-%  \begin{center}
-%    \begin{tabular}{lrrr}
-%      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
- %     \hline 
- %   Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
- %   \end{tabular}
- % \end{center}  
-%\end{table}
-%\vspace{-.5cm}
-
-The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-4.872$, $\hat{\alpha}_{\rm wadj}= -4.805$, and $\hat{\alpha}_{\rm IVW}=-4.384$.
-Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}.
-The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.419, 0.559, and 0.667, respectively.
-%Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $32.452$, $32.690$, and $31.960$, respectively.
-We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[height = 9cm]{fig2.pdf}
-    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price.}
-    \label{Fig:CP}
-  \end{center}  
-  \vspace{-.6cm}
-\end{figure}
-
-We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well.
-Our estimation framework misses the yet to be observed pot-shock response, however they perform much better than unadjusted forecasts that do not account for shock effects.
-The unadjusted forecast misses the post-shock response by 9.870 dollars whereas
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively. 
-%Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without.
-Moreover, the risk-reduction quantities are consistent with the reality as well.
-The true shock effect is not fully recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$.
-This may be a result of a poorly constructed donor pool.
-The shock on March 9th, 2020 is in the midst of the COVID-19 pandemic and oil production volatility.
-It is difficult to find available stock market time series data that were generated under a similar setting.
-In any event, the shock on March 9th, 2020 was the largest price shock to Conoco Phillips shares by a wide margin, even after adjusting for inflation.
-
-From another perspective, it is possible that the stock of Conoco Phillips actually experienced multiple shocks on 2020 March 9th.
-For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector autoregressive model.
-Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.
-Motivated by his study, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
-The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects only, respectively, miss the post-shock Conoco Philips share price by $0.951$, $0.405$, and $1.460$ dollars.
-These additive adjustment estimators do extremely well in this additive shock setting.
-%There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.
-%This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.
-
-\section{Discussion}
-\label{discussion}
-
-We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock.
-Our methodology is as follows: construct a synthetic panel of time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
-There have been several other recent similar methods developed for forecasting COVID-19 cases.
-For example, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries.
-A similar setup may be appropriate for post-shock forecasting but may be too dependent upon model specification for the shock distribution.
-\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach.
-However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
-\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
-They also provided useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
-Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
-
-We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings.
-The model, under which we verify these claims, is a simple AR(1) model.
-Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
-Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
-As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
-But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
-%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock effects in the donor pool.
-%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 6$.
-%This generalization was adopted in Section \ref{forecasting}.
-In this case, the variance expressions proposed in Section \ref{properties} will not work.
-However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock effects (not necessarily mutually independent) in the donor pool are independent of the one of interest.
-Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its first and second moments exist.
-The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
-Additionally, $\alpha_i$ can be heteroskedastic; i.e.,  they can have different variances.
-In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply.
-We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts.
-An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.
-Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.
-
-Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series.
-If the data are subject to heteroskedasticity of unknown form, bootstrapping tuples of regressands and regressors proposed by \citet{freedman1981bootstrapping} is robust in this situation with asymptotic validity in autoregressive models established by \citet{gonccalves2004bootstrapping}.
-If serial correlation exists in the data, various block bootstrapping procedures \citep{kunsch1989jackknife, liu1992moving} can be possible reasonable alternatives.
-Note that the pseudo time series generated by our proposed parametric bootstrap are not stationary.
-If stationarity is of concern, one can be referred to the stationary bootstrap invented by \citet{politis1994stationary} for stationary and weakly dependent time series.
-Nevertheless, it was shown that approximation accuracy might be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.
-More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, \citet{berkowitz2000recent}, and Chapter 12 in \citet{kilian2017structural}.
-It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.
-
-% \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$.
-This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$ where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$; for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$.
-The sampling stops when $N$ observations are reached.
-Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d.
-discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d.
-geometric random variables with parameter $p$.
-However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}.
-Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$.
-This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.
-
-Construction of donor pool is a critical step that directly matters in prediction.
-In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for  varying variances and  varying means that are linear functions of common covariates.
-Remark \ref{remark1} shows that common covariates are not restrictive with structural zero in coefficients.
-However, it is difficult to verify such assumption or structure in practice.
-In principle, one should select identities that come from a common population, which is also the one  the identity under study come from, as candidates in donor pool.
-This selection criterion is often adopted in the literature of comparative case studies.
-For example, \citet{card1990impact} used a set of cities in southern U.S.
-to estimate the effect of 1980 Mariel Boatlift on the Miami labor market.
-\citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country.
-To estimate the effect of Proposition 99, a large tabacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period.
-Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.
-
-\section{Appendix}
-\label{proofs}
-
-\subsection{Justification of Expectation of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
-\label{exp}
-
-The building block for the following proof is the fact that least squares is conditionally unbiased conditioned on $\Theta$.
-
-\noindent \textbf{Case I: under $\mc{M}_{1}$:} It follows that  under $\mc{M}_{1}$ (see Section \ref{modelsetup}),
-\begin{align*}
-\E{\hat{\alpha}_{\rm adj}} =\frac{1}{n}  \sum_{i=2}^{n+1} \E{\E{\hat{\alpha}_i|\Theta}} = \mu_{\alpha} 
-\quad \text{ and } \quad \E{\hat{\alpha}_{\rm wadj}}&= \sum_{i=2}^{n+1} w_i^* \E{\E{\hat{\alpha}_i|\Theta}}= \sum_{i=2}^{n+1} w_i^*\mu_{\alpha}= \mu_{\alpha}.
-\end{align*}
-where we used the fact that $\sum_{i=2}^{n+1} w^*_i=1$.
-
-\noindent \textbf{Case II: under $\mc{M}_{21}$ and $\mc{M}_{22}$:} Since $\E{\tilde{\varepsilon}_{i, T_i}}=0$, $\E{\hat{\tilde{\alpha}}_{i}}=\E{\tilde{\alpha}_{i}}=\E{\alpha_{i}}$, it follows that
-  \begin{align*}
-   \E{\hat{\alpha}_{\rm wadj}}= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}
-   &= \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right)\\
-   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}\right]\bigg\}\\
-   &=\mu_{\alpha}+ \mu_{\delta}' \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}\tag{$\mbf{W}\in \mc{W}$}
-   \\
-   &=\mu_{\alpha}+  \mu_{\delta}'\mbf{x}_{1, T_1^*+1}. \tag{from (\ref{SCM})}
-   \end{align*}
-Similarly,
-  \begin{align*}
-   \E{\hat{\alpha}_{\rm adj}}
-   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \mu_{\delta}'  \mbf{x}_{i, T_i^*+1}.
-   \end{align*}
-
-\subsection{Justification of Variance of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
-\label{var}
-
-Notice that under the setting of OLS, the design matrix for $\mc{M}_2$ is the same as the one for $\mc{M}_1$. Therefore, it follows that
-  \begin{align*}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \E{\var{\hat{\alpha}_{\rm wadj}|\Theta}} + \var{\E{\hat{\alpha}_{\rm wadj}|\Theta}} \\
-  &=\mrm{E} \left\{\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\} +\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
-\end{align*}
-Under $\mc{M}_{21}$ where $\delta_i=\delta$ are fixed unknown parameters,  we will have
-  \begin{align}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma^2(\mbf{U}'_i\mbf{U}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
-\end{align}
-Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \varepsilon_{i,t}$, we have
- \begin{align*}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}
-  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
-\end{align*}
-For the adjustment estimator, we simply replace $\mbf{W}^*$ with $1/n\mbf{1}_n$. Thus, under $\mc{M}_{21}$ we have 
- \begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
-\end{align*}
-Under $\mc{M}_{22}$, we shall have
- \begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
-\end{align*}
-Notice that $\mc{M}_{1}$ differs from $\mc{M}_{21}$ only by its mean parameterization of $\alpha$ (see Section \ref{modelsetup}).
-In other words, the variances of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ under $\mc{M}_1$ are the same for those under $\mc{M}_{21}$.
-
-\subsection{Proofs for lemmas and propositions}
-
-\begin{proof-of-proposition}[\ref{uniqueness}]
-  The proof of \citet{li2019statistical} in Appendix A.2 and A.3 adapts easily to Proposition \ref{uniqueness}.
-\end{proof-of-proposition}
-
-\begin{proof-of-proposition}[\ref{unbiased}] The proof for unbiasedness follows immediately from discussions related to expectation in Section \ref{properties}.
-For the biasedness of  $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$, we write the bias term for $\hat{\alpha}_{\rm adj}$ as below.
-\begin{align*}
-  \mrm{Bias}(\hat{\alpha}_{\rm adj}) = 
-  \begin{cases}
-       \frac{1}{n} \sum_{i=2}^{n+1} \delta'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1})  & \text{ for } \mc{M}_{21}\\
-    \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1})  & \text{ for }\mc{M}_{22}
-  \end{cases}.
-\end{align*}
-But it may be unbiased in some special circumstances when the above bias turns out to be 0. \end{proof-of-proposition}
-
-\begin{lem}
-  \label{risklemma} The forecast risk reduction is $R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2$ for all estimators of $\alpha_1$ that are independent of $\Theta_1$ (see Section \ref{modelsetup}).
-\end{lem}
-
-\begin{proof-of-lemma}[\ref{risklemma}]
-  Define 
-  \begin{align*}
-    C(\Theta_1) =\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} -(\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}),
-  \end{align*}
-  where $\Theta_1$ is as defined in (\ref{parameter}). Notice that
-  \begin{align*}
-    R_{T_1^*+1,1}= \mrm{E}\big\{\big(C(\Theta_1)-\alpha_1\big)^2\big\}
-    \qquad \text{ and } 
-    \qquad  R_{T_1^*+1,2}= \mrm{E}\big\{\big(C(\Theta_1)+\hat{\alpha}-\alpha_1\big)^2\big\}.
-  \end{align*}
-  It follows that
-  \begin{align*}
-    R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-2\E{C(\Theta_1)\hat{\alpha}}-\E{\hat{\alpha}-\alpha_1}^2.
-  \end{align*}
-  Assuming $\mbf{S}=(\mbf{1}_n, \mbf{y}_{1,t-1}, \mbf{x}_{1})$ has full rank, under OLS setting, $\hat{\eta}_1$, $\hat{\phi}_1$, and $\hat{\theta}_1$ are unbiased estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively under conditioning of $\Theta_1$.
-Since we assume $\hat{\alpha}$ is independent of $\Theta_1$, through the method of iterated expectation,
-  \begin{align*}
-    \E{C(\Theta_1)\hat{\alpha}}=\mrm{E}\big\{\hat{\alpha}\cdot \E{C(\Theta_1)\mid \Theta_1}\}=0.
-  \end{align*}
-  It follows that
-  \begin{align*}
-    R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2,
-  \end{align*}
-  which finishes the proof.
-\end{proof-of-lemma}
-
-\begin{proof-of-proposition}[\ref{proprisk}] The proofs are arranged into two separate parts as below.
-
- \textbf{Proof for statement (i):} Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$ because
-  \begin{align*}
-   \mrm{E}\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
-   = \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}
-   &= \frac{1}{n}\sum_{i=2}^{n+1}\E{\E{\hat{\alpha}_i\mid \Theta}}\\
-   &=  \frac{1}{n}\sum_{i=2}^{n+1}\E{\alpha_i}
-   = \mu_{\alpha}=\E{\alpha_1},
-  \end{align*}
-  where we used the fact that OLS estimator is unbiased when the design matrix $\mbf{U}_i$ is of full rank for all $i = 2, \ldots, n+1$.
-Because $\alpha_1\indep \varepsilon_{i,t}$, $\E{\hat{\alpha}_{\rm adj}\alpha_1}=\E{\hat{\alpha}_{\rm adj}}\E{\alpha_1}=(\E{\hat{\alpha}_{\rm adj}})^2$.
-By Lemma \ref{risklemma},
-    \begin{align*}
-    R_{T_1^*+1,1}-R_{T_1^*+1,2}
-    &=\E{\alpha_1^2}-\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
-   & =\E{\alpha_1^2}-\E{\alpha_1^2}- \E{\hat{\alpha}_{\rm adj}^2}+2\E{\hat{\alpha}_{\rm adj}\alpha_1} \\
-   &= \mu_{\alpha}^2 - \var{\hat{\alpha}_{\rm adj}} 
-  \end{align*}
-  Therefore, as long as we have $\var{\hat{\alpha}_{\rm adj}}<\mu_{\alpha}^2$, we will achieve the risk reduction.
-
- \textbf{Proof for statement (ii):} By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\mu_{\alpha}$ holds for $\mc{M}_{1}$.
-The remainder of the proof follows a similar argument to the proof of statement (i).
-\end{proof-of-proposition}
-
-\begin{proof-of-proposition}[\ref{propriskwadj2}]
-  By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ holds for $\mc{M}_{21}$ and $\mc{M}_{22}$.
-The remainder of the proof follows a similar argument to the proof of Proposition \ref{proprisk}.
-\end{proof-of-proposition}
-
-\subsection{Tables for Section \ref{simulation}}
-\label{tablesappendix}
-\newpage
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table1}
-\begin{center}
-\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.91 (0.02) & 0.9 (0.03) & 53.23 (4.1) & 15.88 (2.1) & 16.78 (2.37) & 15.82 (2.07) \\ 
-    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.89 (0.03) & 0.9 (0.03) & 0.89 (0.03) & 53.01 (4.47) & 17.83 (2.38) & 19.56 (2.56) & 17.61 (2.36) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.74 (0.04) & 0.81 (0.04) & 0.75 (0.04) & 53.38 (5.92) & 26.44 (3.8) & 29.06 (4) & 26.11 (3.75) \\ 
-    & 50  & 0.83 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.64 (0.05) & 0.59 (0.05) & 61.68 (7.73) & 46 (6.31) & 47.3 (7.14) & 45.25 (6.32) \\ 
-    & 100  & 0.7 (0.09) & 0.87 (0.06) & 0.7 (0.09) & 0.53 (0.05) & 0.54 (0.05) & 0.53 (0.06) & 85.68 (12.95) & 87.25 (11.86) & 87.07 (13.63) & 85.65 (12.02)\\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
-    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
-   \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 51.11 (3.05) & 14.94 (2.36) & 14.09 (2.37) & 15.09 (2.35) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.91 (0.02) & 52.34 (3.19) & 15.64 (2.73) & 15.29 (2.74) & 15.89 (2.68) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.73 (0.04) & 0.76 (0.04) & 0.73 (0.04) & 56.03 (5.2) & 25.49 (3.85) & 27.38 (3.87) & 25.27 (3.84) \\ 
-    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.56 (0.04) & 0.6 (0.04) & 0.57 (0.04) & 71.37 (7.76) & 47.25 (6.42) & 52.06 (6.57) & 46.41 (6.43) \\ 
-    & 100  & 0.63 (0.09) & 0.67 (0.09) & 0.63 (0.09) & 0.52 (0.04) & 0.42 (0.04) & 0.53 (0.04) & 111.91 (13.83) & 92.95 (12.34) & 103.13 (12.74) & 91.07 (12.37) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.94 (0.02) & 0.93 (0.02) & 47.79 (2.93) & 14.83 (1.72) & 14.83 (2.04) & 14.76 (1.72) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.91 (0.02) & 0.89 (0.03) & 47.93 (3.25) & 16.55 (1.89) & 17.55 (2.12) & 16.53 (1.88) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.82 (0.03) & 0.83 (0.03) & 49.78 (5.01) & 26.42 (3.38) & 29.11 (3.4) & 26.45 (3.35) \\ 
-    & 50  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.64 (0.05) & 0.63 (0.05) & 0.64 (0.05) & 62.64 (7.4) & 48.84 (6.4) & 52.67 (6.28) & 48.8 (6.35) \\ 
-    & 100  & 0.83 (0.07) & 0.8 (0.07) & 0.83 (0.07) & 0.57 (0.05) & 0.59 (0.05) & 0.59 (0.05) & 103.37 (12.23) & 97.81 (12.52) & 102.4 (12.49) & 97.63 (12.45) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table2}
-\begin{center}
-\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.97 (0.01) & 0.95 (0.02) & 48.84 (3.4) & 15.72 (1.93) & 15.32 (1.94) & 15.72 (1.93) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.94 (0.02) & 0.92 (0.03) & 49.54 (3.73) & 17.07 (2.01) & 16.08 (2.16) & 17.12 (1.99) \\ 
-    & 25  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.77 (0.02) & 0.81 (0.03) & 0.77 (0.03) & 51.78 (5.22) & 24.78 (2.57) & 26.12 (2.49) & 24.62 (2.54) \\ 
-    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.61 (0.04) & 0.59 (0.05) & 58.62 (7.74) & 40.09 (4.7) & 47.09 (4.09) & 39.85 (4.58) \\ 
-    & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.73 (0.08) & 0.5 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 82.66 (12.19) & 72.83 (9.75) & 89.03 (9.15) & 72.31 (9.5) \\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
-    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.04) & 0.76 (0.03) & 0.7 (0.04) & 50.09 (8.27) & 38.1 (5.75) & 37.98 (5.5) & 38.44 (5.76) \\ 
-    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.69 (0.04) & 0.74 (0.03) & 0.69 (0.04) & 50.82 (8.15) & 37.63 (5.61) & 36.33 (5.64) & 37.99 (5.61) \\ 
-    & 25  & 0.9 (0.06) & 0.9 (0.06) & 0.9 (0.06) & 0.62 (0.04) & 0.64 (0.04) & 0.61 (0.04) & 53.01 (8.22) & 38.78 (5.29) & 36.82 (5.76) & 38.88 (5.31) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.53 (0.04) & 58.9 (9.12) & 46.77 (5.54) & 50.61 (5.71) & 46.6 (5.51) \\ 
-    & 100  & 0.7 (0.09) & 0.9 (0.06) & 0.67 (0.09) & 0.51 (0.03) & 0.56 (0.04) & 0.5 (0.03) & 79.64 (12.21) & 72.76 (8.79) & 89.48 (7.98) & 72.17 (8.59) \\[.3cm] 
-   \multirow{5}{*}{50} & 5  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.04) & 0.59 (0.04) & 71.22 (13) & 70.31 (10.4) & 72.3 (9.26) & 70.79 (10.45) \\ 
-    & 10  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.05) & 0.6 (0.05) & 70.85 (12.91) & 69.43 (10.22) & 70.65 (9.29) & 69.94 (10.26) \\ 
-    & 25  & 0.7 (0.09) & 0.73 (0.08) & 0.7 (0.09) & 0.54 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 70.32 (12.81) & 67.61 (9.86) & 67 (9.58) & 68.06 (9.89) \\ 
-    & 50  & 0.67 (0.09) & 0.7 (0.09) & 0.67 (0.09) & 0.51 (0.05) & 0.51 (0.04) & 0.51 (0.05) & 74.01 (12.66) & 68.69 (9.63) & 67.9 (10.21) & 68.91 (9.64) \\ 
-    & 100  & 0.5 (0.09) & 0.6 (0.09) & 0.47 (0.09) & 0.47 (0.05) & 0.49 (0.04) & 0.45 (0.05) & 92.71 (13.06) & 83.66 (10.79) & 94.53 (11.2) & 83.56 (10.63)\\[.3cm] 
-   \multirow{5}{*}{100} & 5  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.06) & 0.57 (0.05) & 0.49 (0.06) & 130.47 (22.59) & 135.16 (19.73) & 141.42 (16.98) & 136.3 (19.72) \\ 
-    & 10  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.05) & 0.53 (0.05) & 0.51 (0.06) & 129.49 (22.49) & 134.09 (19.52) & 139.69 (16.96) & 135.26 (19.51) \\ 
-    & 25  & 0.47 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.53 (0.06) & 0.57 (0.05) & 0.51 (0.06) & 127.17 (22.22) & 131.43 (18.97) & 134.47 (17.22) & 132.42 (18.99) \\ 
-    & 50  & 0.5 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.48 (0.06) & 0.56 (0.04) & 0.48 (0.05) & 125.72 (21.8) & 129.27 (18.16) & 129.59 (17.59) & 130.27 (18.15) \\ 
-    & 100  & 0.47 (0.09) & 0.47 (0.09) & 0.43 (0.09) & 0.43 (0.06) & 0.57 (0.04) & 0.47 (0.06) & 128.38 (21.86) & 130.05 (18.05) & 131.83 (19.08) & 130.33 (18.06) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table3}
-\begin{center}
-\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}} $  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.92 (0.02) & 0.89 (0.03) & 48.52 (3.93) & 15.74 (2.34) & 15.76 (2.34) & 15.16 (2.24) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.91 (0.02) & 0.89 (0.02) & 47.7 (4.35) & 18.26 (2.37) & 18.97 (2.42) & 17.68 (2.28) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.79 (0.03) & 0.81 (0.03) & 0.77 (0.03) & 46.95 (6.11) & 27.35 (3.81) & 30.88 (3.84) & 26.58 (3.83) \\ 
-  & 50  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.62 (0.03) & 0.65 (0.03) & 0.63 (0.03) & 56.85 (8.64) & 46.96 (7.02) & 52.92 (7.45) & 45.95 (7.17) \\ 
-  & 100  & 0.73 (0.08) & 1 (0) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.55 (0.04) & 99.22 (12.84) & 93.4 (12.97) & 103.82 (14.1) & 91.95 (13.34) \\[.3cm]  
- \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
-  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29) \\[.3cm] 
- \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.92 (0.03) & 0.95 (0.02) & 52.1 (2.96) & 14.04 (1.78) & 13.36 (2.07) & 14.11 (1.76) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.9 (0.03) & 0.93 (0.02) & 52.25 (3.3) & 15.12 (1.93) & 14.24 (2.29) & 15.18 (1.9) \\ 
-    & 25  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.8 (0.03) & 0.8 (0.03) & 0.8 (0.03) & 52.71 (5.28) & 22.98 (2.9) & 22.6 (3.42) & 22.95 (2.88) \\ 
-    & 50  & 0.7 (0.09) & 0.9 (0.06) & 0.7 (0.09) & 0.65 (0.03) & 0.65 (0.03) & 0.65 (0.04) & 58.65 (8.48) & 39.51 (5.65) & 40.8 (6.3) & 39.35 (5.63) \\ 
-    & 100  & 0.6 (0.09) & 0.87 (0.06) & 0.6 (0.09) & 0.47 (0.05) & 0.45 (0.04) & 0.45 (0.05) & 88.76 (13.66) & 75.93 (11.52) & 81.89 (12.19) & 75.94 (11.41) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.55 (2.9) & 12.13 (1.77) & 14.22 (1.96) & 12.09 (1.77) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.95 (0.02) & 0.93 (0.02) & 49.13 (3.31) & 14.78 (1.85) & 18.21 (2) & 14.75 (1.85) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.02) & 0.85 (0.02) & 0.83 (0.03) & 47.38 (5.13) & 26.85 (3.33) & 32.95 (3.59) & 26.81 (3.32) \\ 
-    & 50  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.61 (0.04) & 0.71 (0.04) & 0.62 (0.04) & 56.73 (7.93) & 50.96 (6.63) & 60.62 (7.21) & 50.88 (6.59) \\ 
-    & 100  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.49 (0.05) & 0.51 (0.04) & 0.49 (0.05) & 93.79 (14.67) & 102.05 (13.37) & 116.45 (15.19) & 101.55 (13.38) \\
-\end{tabular}}
-   \end{center}
-      \vspace{-.5cm}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table4}
-\begin{center}
-\resizebox{1.4\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.04 (3.65) & 21.75 (4.34) & 22.68 (4.41) & 21.83 (4.34) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.92 (0.02) & 0.93 (0.02) & 49.93 (4.11) & 24.3 (4.44) & 25.72 (4.58) & 24.4 (4.45) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.73 (0.04) & 0.8 (0.03) & 0.73 (0.04) & 51.29 (5.39) & 32.8 (5.25) & 35.39 (5.78) & 33.11 (5.21) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.49 (0.04) & 0.44 (0.05) & 0.47 (0.04) & 82.55 (11.61) & 84.26 (12.7) & 98.66 (13.96) & 84.62 (12.59) \\[.3cm] 
- \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
-  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29)\\[.3cm] 
- \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.03) & 0.73 (0.03) & 0.71 (0.04) & 57.87 (8.76) & 50.31 (7.58) & 57.25 (7.75) & 50.53 (7.64) \\ 
-  & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.68 (0.04) & 0.69 (0.04) & 0.69 (0.04) & 58.41 (9.11) & 51.62 (7.91) & 58.61 (8.28) & 51.85 (7.98) \\ 
-  & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.63 (0.04) & 0.68 (0.04) & 0.63 (0.04) & 62.02 (10.02) & 59.08 (8.53) & 65.55 (9.64) & 59.68 (8.53) \\ 
-  & 50  & 0.87 (0.06) & 0.9 (0.06) & 0.87 (0.06) & 0.54 (0.04) & 0.59 (0.04) & 0.52 (0.04) & 71.01 (11.73) & 73.52 (10.18) & 81.81 (11.98) & 74.51 (10.09) \\ 
-  & 100  & 0.73 (0.08) & 0.87 (0.06) & 0.73 (0.08) & 0.47 (0.05) & 0.45 (0.04) & 0.5 (0.05) & 95.93 (15.59) & 104.49 (15.12) & 119.38 (17.62) & 105.72 (14.97) \\[.3cm] 
- \multirow{5}{*}{50} & 5  & 0.8 (0.07) & 0.77 (0.08) & 0.8 (0.07) & 0.52 (0.04) & 0.49 (0.05) & 0.52 (0.04) & 85.95 (14.57) & 90.02 (13.45) & 103.03 (13.91) & 90.08 (13.64) \\ 
-  & 10  & 0.8 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.55 (0.05) & 0.5 (0.04) & 0.53 (0.05) & 86.44 (14.95) & 90.89 (13.79) & 104.62 (14.28) & 91.03 (13.98) \\ 
-  & 25  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.53 (0.04) & 0.46 (0.04) & 0.53 (0.04) & 90.26 (15.82) & 95.36 (14.69) & 109.53 (15.69) & 95.79 (14.83) \\ 
-  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.48 (0.05) & 0.45 (0.05) & 0.45 (0.05) & 99.52 (17.26) & 106.52 (16.17) & 120.99 (18.13) & 107.55 (16.19) \\ 
-  & 100  & 0.57 (0.09) & 0.77 (0.08) & 0.63 (0.09) & 0.41 (0.04) & 0.45 (0.03) & 0.41 (0.04) & 123.11 (20.61) & 135.24 (19.74) & 151.62 (23.42) & 137.21 (19.55) \\[.3cm] 
- \multirow{5}{*}{100} & 5  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.48 (0.05) & 0.48 (0.03) & 0.47 (0.05) & 156.82 (26.36) & 170.06 (25.92) & 196.4 (26.55) & 170.13 (26.27) \\ 
-  & 10  & 0.63 (0.09) & 0.57 (0.09) & 0.67 (0.09) & 0.46 (0.05) & 0.47 (0.03) & 0.47 (0.05) & 157.3 (26.76) & 170.93 (26.21) & 197.96 (26.87) & 171.07 (26.56) \\ 
-  & 25  & 0.67 (0.09) & 0.63 (0.09) & 0.67 (0.09) & 0.44 (0.04) & 0.5 (0.03) & 0.45 (0.04) & 160.32 (27.73) & 173.66 (27.22) & 202.61 (28.01) & 174.28 (27.48) \\ 
-  & 50  & 0.67 (0.09) & 0.67 (0.09) & 0.67 (0.09) & 0.39 (0.04) & 0.43 (0.03) & 0.38 (0.04) & 166.98 (29.35) & 182.83 (28.37) & 210.38 (30.48) & 183.67 (28.61) \\ 
-  & 100  & 0.6 (0.09) & 0.67 (0.09) & 0.53 (0.09) & 0.4 (0.04) & 0.45 (0.04) & 0.41 (0.05) & 188.29 (32.07) & 203.7 (31.63) & 233.44 (35.31) & 205.4 (31.72) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
+%\vspace*{0.5cm}\noindent We could also consider problems of the form 
+%$$
+%  \min_{\mc{F}_{\alpha} \in \mc{F}}\left(y_{1,T_i^*+1} - \hat y_{1,T_i^*+1}(\mc{F}_{\alpha})\right)^2
+%$$
+%where $\mc{F}$ is a function class.
 

### 2020-12-10 Revision/list.tex
revision comments for the first reviewer added

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{graphicx,times}
\usepackage{mathtools}
\usepackage{url}
%\usepackage{setspacing}
\usepackage{fullpage}
\usepackage{palatino}
\usepackage{mathpazo}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{xifthen} % Allows us to put in optional arguments to questions
\usepackage{color}
\usepackage{manfnt}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{nicefrac,mathtools}
\usepackage[top=2.2cm,bottom=2.2cm,right=2.1cm,left=2.1cm]{geometry}
\usepackage{color}   %May be necessary if you want to color links
\usepackage{hyperref}
\usepackage{float}
\usepackage{showexpl}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{chngcntr}
\usepackage{xparse}
\usepackage{etoolbox}
\usepackage{blkarray}
\usepackage{cprotect}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}

\newcommand{\R}{\mathbb{R}}
\newcommand{\ds}{\displaystyle}
\newcommand{\mustar}{\mu^{\textstyle{*}}}
\newcommand{\betastar}{\hat{\beta}^{\textstyle{*}}}
\newcommand{\betahat}{\hat{\beta}}
\newcommand{\betaw}{\hat{\beta}_w}
\newcommand{\betastarT}{\hat{\beta}^{\textstyle{*}^T}}
\newcommand{\betabar}{\bar{\beta}^{\textstyle{*}}}
\newcommand{\bstar}{b^{\textstyle{*}}}
\newcommand{\vstar}{v^{\textstyle{*}}}
\newcommand{\Bstar}{B^{\textstyle{*}}}
\newcommand{\wstar}{w^{\textstyle{*}}}
\newcommand{\BICstar}{\textsc{bic}^{\textstyle{*}}}
\newcommand{\minBICstar}{\min_{s=1,...,r}\left\{\BIC^{\textstyle{*}}(s)\right\}}
\newcommand{\sstar}{s_m^{\textstyle{*}}}
\newcommand{\epstar}{\varepsilon^{\textstyle{*}}}
\newcommand{\epstarT}{\varepsilon^{{\textstyle{*}^T}}}
\newcommand{\epresstar}{\widehat{\varepsilon}^{\textstyle{*}}}
\newcommand{\epresstarT}{\widehat{\varepsilon}^{\textstyle{*}^T}}
\newcommand{\residstar}{\widehat{\varepsilon}^{\textstyle{*}}}
\newcommand{\Ystar}{Y^{\textstyle{*}}}
\newcommand{\Xstar}{X^{\textstyle{*}}}
\newcommand{\Wstar}{W^{\textstyle{*}}}
\newcommand{\Wstarinv}{W^{{\textstyle{*}^{-1}}}}
\newcommand{\Zstar}{Z^{\textstyle{*}}}
\newcommand{\YstarT}{Y^{{\textstyle{*}^T}}}
\newcommand{\XstarT}{X^{\textstyle{*}^T}}
\newcommand{\Sigstar}{\widehat{\Sigma}^{\textstyle{*}}}
\newcommand{\Sigstarhalf}{\widehat{\Sigma}^{\textstyle{*}^{1/2}}}
\newcommand{\Sigstarhalfinv}{\widehat{\Sigma}^{\textstyle{*}^{-1/2}}}
\newcommand{\lstar}{l^{\textstyle{*}}}

\newcommand{\Astar}{A^{\textstyle{*}}}
\newcommand{\Gostar}{\widehat{G}_o^{\textstyle{*}}}
\newcommand{\GostarT}{\widehat{G}_o^{\textstyle{*}^T}}
\newcommand{\Gohat}{\widehat{G}_o}
\newcommand{\GohatT}{\widehat{G}_o^T}
\newcommand{\Sigresstar}{\widehat{\Sigma}^{\textstyle{*}}}

\newcommand{\B}{\mathcal{B}}
\newcommand{\Lnorm}{\mathcal{L}}
\newcommand{\Sub}{\mathcal{S}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\Proj}{\mathcal{P}}
\newcommand{\Env}{\mathcal{E}}
\newcommand{\Envspace}{\Env_{\Sigma}(\B)}
\newcommand{\utrue}{u_{\text{true}}}
\newcommand{\BIC}{\textsc{bic}}
\newcommand{\dimEnv}{\text{dim}\{\Envspace\}}
\newcommand{\minBIC}{\min_{s=1,...,r}\left(\BIC(s)\right)}
\newcommand{\nboot}{n_{\text{boot}}}

\newcommand{\X}{\mathbb{X}}
\newcommand{\Y}{\mathbb{Y}}
\newcommand{\Ymatstar}{\Y^{\textstyle{*}}}
\newcommand{\YmatstarT}{\Y^{\textstyle{*}^T}}
\newcommand{\Xmatstar}{\X^{\textstyle{*}}}
\newcommand{\XmatstarT}{\X^{\textstyle{*}^T}}

\newcommand{\Sigres}{\widehat{\Sigma}}
\newcommand{\SigY}{\widehat{\Sigma}_{Y}}
\newcommand{\SigX}{\widehat{\Sigma}_{X}}
\newcommand{\Pu}{\widehat{\Proj}_{\Env_u}}
\newcommand{\Pj}{\widehat{\Proj}_{\Env_j}}
\newcommand{\Qu}{\widehat{\Q}_{\Env_u}}
\newcommand{\Qj}{\widehat{\Q}_{\Env_j}}
\newcommand{\PD}{\widehat{\Proj}_{D}}
\newcommand{\betau}{\hat{\beta}_u}
\newcommand{\betaj}{\hat{\beta}_j}
\newcommand{\res}{\widehat{\varepsilon}}

\newcommand{\sestar}{\text{se}^{\textstyle{*}}\{\text{vec}(\hat{\beta})\}}
\newcommand{\setrue}{\text{se}_{\text{true}}\{\text{vec}(\hat{\beta})\}}

\newcommand{\vecop}[1]{\text{vec}\left( #1 \right)}
\newcommand{\vechop}[1]{\text{vech}\left( #1 \right)}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}

\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Var}{var}

\newtheorem{lem}{Lemma} 
\newtheorem{thm}{Theorem} 
\allowdisplaybreaks

\setlength{\parindent}{0cm}

\newcommand{\response}[1]{\noindent \textcolor{blue}{\emph{Response:} #1}}
\cMakeRobust\response

\title{Referee report checklist}
\author{Jilei Lin and Daniel J. Eck}
\date{}

\bibliographystyle{plainnat}

\begin{document}

\maketitle

Thank you for the opportunity to resubmit at \emph{International Journal of Forecasting}. Thank you to the reviewers for comments that led to an improved version of this manuscript. We address all of the reviewers' comments below. An outlines of each change made or a rebuttal is provided for all of the reviewer's comments.

\newpage
\section*{Reviewer 1: \texttt{Cover letter for authors.pdf}}

Thank you very much for taking the time to provide a thoughtful review of our manuscript. We think that these comments will go a long way to improve the exposition of our manuscript. \\

%% addressed
{\bf  Comment 1:} How could the method be applied to forecast two or more period after a shock? \\

\response{The method can be extended to forecast two or more periods after a shock. There are two situations.  \\

First, suppose that there is no additional shock after $T_1^* + 1$. From equation (1) in the manuscript, the forecast at time point $T_1^*+2$ is
\begin{align*}
 \hat{y}_{i, T_i^* + 2} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+1}^{2} + \hat{\theta}_i'\mathbf{x}_{1, T_1^*+2}, \tag{*}
\end{align*}
where $\hat{y}_{1, T_1^*+1}^{2}=\hat{y}_{1, T_1^*+1}^{1} + \hat{\alpha}_{T_1^* + 1}$, where $\hat{y}_{1, T_1^*+1}^{1}$ is the forecast without adjustment, and  $\hat{\alpha}_{T_1^* + 1}$ is the shock-effect estimator for the shock at $T_1^*+1$. The forecast for $d>2$ more periods is
\begin{align*}
 \hat{y}_{i, T_i^* + d} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+d-1}+ \hat{\theta}_i'\mathbf{x}_{1, T_1^*+d},
\end{align*}
where $\hat{y}_{1, T_1^*+d-1}$ can be also computed recursively using the above formula and we  emphasize  $ \hat{y}_{i, T_i^* + 1}=\hat{y}_{1, T_1^*+1}^{2}$. Since we use AR(1) model, $|\phi_1 |< 1$ is assumed.  As one can expect, the impact of the shock  $\alpha_1$ will diminish as $d$ increases. Similar logic can apply for AR($p$). \\

Second, suppose that  there is one more shock effect after $T_1^*+1$, say, $\alpha_{T_1^* + d^*}$ for some $d^* > 1$. Without loss of generality, assume $d^* = 2$. Under our framework, users may want to construct another set of donor pool with time series that experienced shock effects similar to $\alpha_{T_1^* + 2}$. Next,  apply our proposed method to compute $\hat{\alpha}_{T_1^* + 2}$, the estimator for the shock effect at $T_1^* +2$. The forecast at the point $T_1^* + 2$ will be,  
\begin{align*}
 \hat{y}_{i, T_i^* + 2} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+1}^{2} + \hat{\theta}_i'\mathbf{x}_{1, T_1^*+2} + \hat{\alpha}_{T_1^* + 2}.
\end{align*}
These two cases can be further combined to generalize forecasting for two or more periods. \\
}

{\bf Comment 2:} Page 3, line 30: \citet{blundell1998initial} model is a fixed effect dynamic panel and estimate the parameters using the panel analysis. It would be nice if you clarify in what sense your work is similar to them. \\

\response{The model of \citet{blundell1998initial} is
\begin{align*}
  y_{it} = \alpha y_{i, t-1} + \beta_1'x_{it} + \beta_2'x_{it-1} + \eta_i + v_{it}, \quad i = 1, \ldots, N, \quad t = 2, \ldots, T.
\end{align*}
where $|\alpha|<1$. In contrast, our model is
\begin{align*}
 y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t},
\end{align*}
where $|\phi_i| < 1$. Our model is similar to the one of \citet{blundell1998initial}  in the sense that we have the fixed-effect decomposition of the error term $\eta_i +\varepsilon_{i,t}$ and the autoregressive structure. However, our model allows for $\eta_i$ as random effects, different time lengths for each time series, different autoregressive parameters, and a shock component.}\\

{\bf Comment 3:} Page 4, line 50: Your paper considers forecasting a time-series model. It is confusing for readers to read your sentence ”In this article, we consider a dynamic panel data model...''.\\

\response{Sorry for the confusion. We will correct that in the revised version.}\\

{\bf  Comment 4:} Figures on page 5: Figure labels, (a) and (b), are missing. What does the black line in the top graph represent? Is it the realized observations?\\

\response{Thanks for pointing it out. The labels (a) and (b) are now added in the revised manuscript.   The \textcolor{black}{black} line stands for the realized observations whereas the \textcolor{magenta}{magenta} line stands for the fitted values.} \\

{\bf Comment 5:} Page 7, line 52: Are these time series estimates or panel data estimates? If panel estimators are used, then OLS estimators in this model results in inconsistency of the estimators. In that case, how wouldn't this inconsistency affect the results in section 3 about the unbiasedness? \\

\response{Sorry for not making it clear. They are time series estimates or the ordinary least squares (OLS) estimates but not panel data estimates. In fact, our method can be generalized to any model whose parameter can be estimated in an unbiased fashion. In the second paragraph of Section 6, we wrote \\

\begin{tcolorbox}
``Although our work is developed for time-series or AR($p$) models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated \emph{\textcolor{red}{unbiasedly}}, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.''
\end{tcolorbox}

\vspace{0.4cm}In other words, if the estimator used in panel data is unbiased, our method can adapt to this scenario by weighting the shock effects estimated by panel data estimation procedure. In this case, the propositions in Section 3 still hold though the exact variance expressions will change since we are not using OLS estimators.}\\

{\bf Comment 6:} Page 8, line 46: It is not clear to met how you estimate $\alpha_i$'s by OLS. Could you give the expressions for $\hat{\alpha}_i$? Also, how can you identify $\alpha_i$ from $\eta_i$? Isn't $\hat{\alpha}_{\rm adj}$ an estimator of $E(\alpha_1)$? \\

\response{Sorry for not making it clear. The estimation procedures can be explained in detail as follows. Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series and $\mathbf{D}_{i}=(D_{i,t})_{t=1}^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$. We define $\mathbf{U}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$. Then the expression for $\hat{\alpha}_i$ is
\begin{align*}
  \hat{\alpha}_i = [(\mathbf{U}'_i\mathbf{U}_i)^{-1}\mathbf{U}_i'\mathbf{Y}_{i}]_{2}, \quad 
  \text{ where }\quad \mathbf{Y}_{i}=(y_{i,t})_{t=1}^{T_i} 
 \quad  \text{ for } i = 2, \ldots, n+1.
\end{align*}
Note that $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Recall that our model is
\begin{align*}
  y_{i,t} = \eta_i + \alpha_i D_{i,t} + \phi_i y_{i,t-1} + \theta_i'\mathbf{x}_{i,t} + \varepsilon_{i,t}, 
  \quad i = 1, \ldots, n+1.
\end{align*}
$\eta_i$ represents the effect of the intercept. Thus, we cannot identify $\alpha_i$ from $\eta_i$. As defined in (4) in the manuscript, through averaging, $\hat{\alpha}_{\rm adj}$ is an estimator  of $E(\alpha_1)$.} \\

{\bf Comment 7:} Page 9, line 10: It is not clear to me what $\mathbf{U}_i$'s are. An example could help understanding that better. \\

\response{Thanks for pointing it out. We will clarify it in the revised version. $\mathbf{U}_i$'s represent the design matrix for the OLS estimation at the $i$th time series. For example, suppose the sample size for $i$th time series in the donor pool (i.e., $i\geq 2$) is 4; we have one covariate consisting of $x_1, \ldots, x_4$; and the shock occurs at $t = 4$. In this case, $\mathbf{U}_i$ is 
\begin{align*}
  \mathbf{U}_i = \begin{pmatrix}
    1 & 0 & x_1 \\
    1 & 0 & x_2 \\
    1 & 0 & x_3 \\
    1 & 1 & x_4
  \end{pmatrix}.
\end{align*}
Suppose the sample size for the time series of interest is also 4, and we have a covariate $k_1, \ldots, k_4$. Note that the design matrix of the time series of interest will not contain $D_{1,t}$ since $D_{1,t}= I(t=T_1^*+1)=0$ due to we do not observe the shock. In this case, 
\begin{align*}
  \mathbf{U}_1 = \begin{pmatrix}
    1 &  k_1 \\
    1 &  k_2 \\
    1 &  k_3 \\
    1 &  k_4
  \end{pmatrix}.
\end{align*}} \\

{\bf Comment 8:} Page 9, line 15: Why the closed form expressions for $E(\hat{\alpha}_{\rm IVW})$ and $Var(\hat{\alpha}_{\rm IVW})$ are not provided? \\

\response{Recall that in page 8, we wrote \\
\begin{tcolorbox}
''The inverse-variance weighted estimator is defined as 
\begin{align*}
  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mathbf{U}_i)_{22}^{-1},
\end{align*}
where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
and $\mathbf{U}_i$ is the design matrix for OLS with respect to time series 
for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
is required and the numerator and denominator terms are dependent in general.''
\end{tcolorbox} \\
To be more specific, $\hat{\sigma}_{i\alpha}$ depends on $\hat{\alpha}_i$. As a result, the numerator and denominator of $ \hat{\alpha}_{\rm IVW}$ are dependent. Without making distributional assumptions, it is impossible to evaluate $E(\hat{\alpha}_{\rm IVW})$ and $Var(\hat{\alpha}_{\rm IVW})$ in a closed form.}\\

{\bf Comment 9:} Page 13, line 14: $\mu_{\alpha}$ is unknown, and in practice we have to estimate it. Would the results hold if one replaces $\mu_{\alpha}$ with its estimate? \\

\response{We go for a plug-in approach. If we can estimate $\mu_{\alpha}$ well, the results should hold with high probability. Section 3.2 is dedicated to this estimation problem. Using plug-in approaches, we get a decision rule to determine whether the scalar adjustment will be beneficial with correctness probability $p$. Section 3.3 details the leave-one-out cross validation procedures, which are tailored to our setup, to estimate $p$. As a result, users can be informed about the credibility of our methods} \\

{\bf Comment 10:} Page 14, line 7: Shouldn’t $E(\alpha_1)$ be $\mu_{\alpha}$? Previously $\mu_{\alpha}$ was used.\\

\response{In the line 7 at Page 14, $E(\alpha_1)$ is taken under $\mathcal{M}_{21}$ or $\mathcal{M}_{22}$. In contrast, $\mu_{\alpha}$ is used under $\mathcal{M}_{1}$. Recall that in Section 2.1,
\begin{align*}
  &\alpha_i \sim \mathcal{F}_{\alpha} 
 \quad  \text{ with }\quad  E_{\mathcal{F}_{\alpha}}(\alpha_i) =\mu_{\alpha}, Var_{\mathcal{F}_{\alpha}}(\alpha_i)=\sigma^2_{\alpha},\quad   \text{iid under } \mathcal{M}_1\\
 & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{iid under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
\end{align*}
In other words,  $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ is an extended version of $\mathcal{M}_{1}$ by allowing it to depend on some covariates. However, in general, $E(\alpha_1)\neq \mu_{\alpha}$ under   $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ due to the presence of $\delta_i'\mathbf{x}_{i, T_i^*+1}$.} \\

{\bf Comment 11:} Page 18, numerical example: The model setup does not contain the individual effects (intercepts) similar to the models in equations (1)-(2) on page 6. How would the result change if you include them with different variances? \\

\response{The result wouldn't change. In fact, in our proof listed in the Appendix, we do not make use of the assumption that $\eta_i$ follows the same distribution. In other words, the results  still hold when the individual effects have different variances.}\\

{\bf Comment 12:} Page 23, construction of donor pool: Your model assumes that the shocks have the same distribution. Given that these shocks are from different sources and happened because of various reasons, how could one justify them? Practically, there are many previous shocks. How can someone choose from them?\\

\response{It is a good question. To clarify, $\mathcal{M}_1$ assumes that the shocks have the same distribution. However, $\mathcal{M}_{21}$ assumes the shocks have the same variance but have different conditional means with allowing covariates to play a role. Moreover, $\mathcal{M}_{22}$ assumes they have different conditional means and conditional variances by allowing $\delta_i$ to be random. But the shock effects are assumed to follow a general family of  unknown distribution with possible different means and variances.\\

$\mathcal{M}_{21}$ and $\mathcal{M}_{22}$ are constructed for generalization. In practice, it is hard to verify those assumptions. It leaves the discretion for users to construct donor pool by gathering time series experiencing similar events to the one the time series of interest experienced. \\

Theoretically, it is possible to verify the assumptions of $\mathcal{M}_{1}$ using empirical Bayes methods to some degree. First, we need a  pool of shock effects that users believe they are realizations from a common distribution, say, $\mathcal{F}_{\alpha}$. Using empirical Bayes methods, we can estimate $\mathcal{F}_{\alpha}$ to have $\hat{\mathcal{F}}_{\alpha}$. To verify whether the remaining shock effects are from $\mathcal{F}_{\alpha}$, we can check the quantile of $\hat{\mathcal{F}}_{\alpha}$ to judge whether they are extreme in $\hat{\mathcal{F}}_{\alpha}$. However, the theoretical justification for this approach is left for future research. \\

In practice, someone can select the shocks that are similar to the one of interest. For example, they can be similar in causes, scale, and characteristics. Using our data analysis example, on March 9th 2020, Conoco Phillips experienced a shock during COVID-19 pandemic and oil supply shock. During COVID-19 pandemic, the US economy is in a situation that resembles the one in financial crisis. As a result, we select the shocks in the past that are related to financial crisis and oil supply shock.} \\

{\bf Comment 13:} Figure 2 on Page 24: Are the black dots the real data? What does the line represent?\\

\response{Thanks for pointing it out. We will clarify this in the revised version. The black dots represent the real data. The line in \textcolor{magenta}{magenta} color represents the fitted line of our model.}

\bibliography{synthetic-prediction-notes}

\end{document}

### 2020-12-19 Revision/list.tex
response to the second reviewer and editor but partial response to the associate editor

@@
 
+\hypersetup{
+  linkcolor  = blue,
+  citecolor  = blue,
+  urlcolor   = blue,
+  colorlinks = true,
+} % color setup
+
 \title{Referee report checklist}
@@
 
+\section*{Editors}
+
+---------------------------------------------------------------------------------------------------------------------------
+
+We have now received feedback on your manuscript from two reviewers as well as an Associate Editor.
+The reviewers' reports are attached to this message, while the AE's comments are included below this letter.
+
+Both reviewers and the AE agree that you address a relevant and interesting topic, and that your paper has the potential to provide a valuable addition to the forecaster's toolkit.
+That being said, the current version of the manuscript does not meet the publication standards of the IJF.
+A number of important points are raised by the reviewers that are either unclear or unresolved, and these need to be addressed.
+In addition, the Associate Editor provides some useful comments and suggestions, also pointing out that quite a substantial revision is required.
+
+In sum, I have decided to give you the opportunity to revise and resubmit your manuscript.
+Please do note that this is a "major revision".
+This means that, while we feel that the work presented in the manuscript might be of interest for the journal, re-submitting your manuscript does not necessarily mean it will be accepted, eventually.
+
+---------------------------------------------------------------------------------------------------------------------------
+
+\response{Thank you for the opportunity to submit a revision. We include a point by point response for the comments and concerns raised by the reviwers.}
+
+\section*{Associate Editor}
+
+{\bf Comment:} Firstly, this contribution seems to me to be related to two exisiting strands of literature, neither of which is cited.
+Describing the contribution relative to these literatures might help some readers better appreciate the achievements.
+These are the literatures on "ad hoc" model adjustments for breaks, see e.g.,  \cite{clements1996intercept} for an early contribution, and \cite{castle2015robust} for a more recent example.
+The second is to do with outliers (innovation, additive and level shifts) in ARMA models, see e.g., \cite{tsay1986time}.
+Comparing/contrasting the approach in the paper with these literatures may be illuminating.
+\\
+
+{\bf Comment 2:} Secondly, a single empirical example is presented. I would like to see the results for a range of series - this would generate confidence in the proposed approach. \\
+
+\textbf{Summary of \cite{clements1996intercept}:} \cite{clements1996intercept} proposes three intercept correction for $m$-ahead forecasts of VECM.
+They are constant adjustment throughout the $m$ periods, a one-off adjustment, simple adjustment, and tailing-off forecast.
+In their setup, let $\hat{\boldsymbol{\varepsilon}}_{T}$ be the residual of VECM at $t= T$ and we are interested in  $m$-ahead forecasts.
+Denote the $m$-ahead forecasts by $\hat{y}_{ T+ m}$ and the adjusted forecasts by $\hat{\boldsymbol{y}}_{T+m}^*$.
+The \emph{constant adjustment}  considers $\hat{\boldsymbol{y}}_{T+m}^*= \hat{\boldsymbol{y}}_{ T+ m} + \hat{\boldsymbol{\varepsilon}}_{T}$.
+The \emph{one-off} adjustment considers $\hat{\boldsymbol{y}}_{T+1}^*= \hat{\boldsymbol{y}}_{ T+ 1} + \hat{\boldsymbol{\varepsilon}}_{T}$ and compute $m$-ahead forecasts using $\hat{\boldsymbol{y}}_{T+1}^*$; i.e., they only adjust once.
+The \emph{simple adjustment} considers only $\hat{\boldsymbol{y}}_{T+m}^*= \hat{\boldsymbol{y}}_{ T+ m} + \hat{\boldsymbol{\varepsilon}}_{T}$.
+The \emph{tailing-off} adjustment considers
+\begin{align*}
+  \hat{\boldsymbol{y}}_{T+m}^*
+  &=\hat{\boldsymbol{y}}_{T+m} + \sum_{i=0}^m \mathbf{\Pi}^i \mathbf{H}^{m-1-i}  \hat{\boldsymbol{\varepsilon}}_T,
+\end{align*}
+where $\mathbf{\Pi}$ is the parameter matrix of  the error correction term. It is shown that the forecast bias is reduced  when the long-run relationship of VECM changes. \\
+
+It is important to note that their method uses $\hat{\boldsymbol{\varepsilon}}_{T}$.
+In other words, the hope of reducing forecast risk depends on whether a large deviation is observed at $t=T$.
+That is, the method is not immune to unprecedented and unobserved shock.
+
+\textbf{Summary of \cite{castle2015robust}:} \cite{castle2015robust} proposed a number of robust forecasting in contrast to equilibrium-correction models.
+However, their proposed methods would depend on whether past data contain future shock signal to adjust for the forecast.
+As a result, similar to \cite{clements1996intercept}, it is not robust to unprecedented and unobserved shock.
+\\
+
+\textbf{Summary of \cite{tsay1986time}:} \cite{tsay1986time} specifies a general generating  mechanism of outliers and corresponding outlier detection methods for ARMA model.
+The two types of his proposed outlier generating mechanism are innovational outlier and additive outlier.
+The additive outlier only affects observation at $t= T_0$ for some $T_0 \in \{ 1, \ldots, T\}$.
+In contrast, the innovational outlier introduces a disturbance on the white noise so that it influences the entire process and impacts future values.
+In our study, in our AR(1) example,  the unprecedented shock is similar to innovational outlier in the sense that the contaminated response will impact future values through autoregressive structure.
+However, the difference is that the shock is an additive effect.
+
 \newpage
@@
 
-\response{The method can be extended to forecast two or more periods after a shock. There are two situations.  \\
+\response{Thanks for pointing it out. The method can be extended to forecast two or more periods after a shock. There are two situations.  \\
 
@@
 \begin{align*}
- \hat{y}_{i, T_i^* + 2} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+1}^{2} + \hat{\theta}_i'\mathbf{x}_{1, T_1^*+2} + \hat{\alpha}_{T_1^* + 2}.
+ \hat{y}_{i, T_i^* + 2} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+1}^{2} + \hat{\theta}_1'\mathbf{x}_{1, T_1^*+2} + \hat{\alpha}_{T_1^* + 2}.
 \end{align*}
-These two cases can be further combined to generalize forecasting for two or more periods. \\
+These two cases can be further combined to generalize forecasting for two or more periods. It is added to Section 6.\\
 }
@@
 \begin{align*}
- y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t},
+ y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mathbf{x}_{i,t} + \varepsilon_{i,t},
 \end{align*}
@@
 Our model is similar to the one of \citet{blundell1998initial}  in the sense that we have the fixed-effect decomposition of the error term $\eta_i +\varepsilon_{i,t}$ and the autoregressive structure.
-However, our model allows for $\eta_i$ as random effects, different time lengths for each time series, different autoregressive parameters, and a shock component.}\\
+However, our model allows for $\eta_i$ as random effects, different time lengths for each time series, different autoregressive parameters, and a shock component.
+To avoid confusion, we  remove this reference in the revised manuscript.}\\
 
@@
 
-\response{Sorry for the confusion. We will correct that in the revised version.}\\
+\response{Sorry for the confusion. It is corrected  in the revised version.}\\
 
@@
 Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series and $\mathbf{D}_{i}=(D_{i,t})_{t=1}^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$.
-We define $\mathbf{U}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$.
+We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$.
 Then the expression for $\hat{\alpha}_i$ is
 \begin{align*}
-  \hat{\alpha}_i = [(\mathbf{U}'_i\mathbf{U}_i)^{-1}\mathbf{U}_i'\mathbf{Y}_{i}]_{2}, \quad 
+  \hat{\alpha}_i = [(\mathbf{M}'_i\mathbf{M}_i)^{-1}\mathbf{M}_i'\mathbf{Y}_{i}]_{2}, \quad 
   \text{ where }\quad \mathbf{Y}_{i}=(y_{i,t})_{t=1}^{T_i} 
@@
 \end{align*}
-Note that $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Recall that our model is
+Note that $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Our model is
 \begin{align*}
@@
 \response{Thanks for pointing it out.
-We will clarify it in the revised version.
-$\mathbf{U}_i$'s represent the design matrix for the OLS estimation at the $i$th time series.
+We  clarify it in the revised version, and change the notation to be $\mathbf{M}_i$, which represents the design matrix of the model used in OLS estimation at the $i$th time series.
 For example, suppose the sample size for $i$th time series in the donor pool (i.e., $i\geq 2$) is 4; we have one covariate consisting of $x_1, \ldots, x_4$; and the shock occurs at $t = 4$.
@@
 \begin{align*}
-  \mathbf{U}_i = \begin{pmatrix}
+  \mathbf{M}_i = \begin{pmatrix}
     1 & 0 & x_1 \\
@@
 \begin{align*}
-  \mathbf{U}_1 = \begin{pmatrix}
+  \mathbf{M}_1 = \begin{pmatrix}
     1 &  k_1 \\
@@
 
-\response{Recall that in page 8, we wrote \\
+\response{In page 8, we wrote \\
 \begin{tcolorbox}
@@
   \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
-  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mathbf{U}_i)_{22}^{-1},
+  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{M}_i'\mathbf{M}_i)_{22}^{-1},
 \end{align*}
@@
 $\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
-and $\mathbf{U}_i$ is the design matrix for OLS with respect to time series 
+and $\mathbf{M}_i$ is the design matrix for OLS with respect to time series 
 for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
 is required and the numerator and denominator terms are dependent in general.''
-\end{tcolorbox} \\
+\end{tcolorbox}
 To be more specific, $\hat{\sigma}_{i\alpha}$ depends on $\hat{\alpha}_i$.
@@
 
-\response{In the line 7 at Page 14, $E(\alpha_1)$ is taken under $\mathcal{M}_{21}$ or $\mathcal{M}_{22}$. In contrast, $\mu_{\alpha}$ is used under $\mathcal{M}_{1}$. Recall that in Section 2.1,
+\response{In the line 7 at Page 14, $E(\alpha_1)$ is taken under $\mathcal{M}_{21}$ or $\mathcal{M}_{22}$.
+In contrast, $\mu_{\alpha}$ is used under $\mathcal{M}_{1}$.
+In Section 2.1, we define the distribution of $\alpha_i$ as
 \begin{align*}
@@
 \response{Thanks for pointing it out.
-We will clarify this in the revised version.
+We  clarify this in the revised version.
 The black dots represent the real data.
 The line in \textcolor{magenta}{magenta} color represents the fitted line of our model.}
+
+\newpage
+
+\section*{Reviewer 2:  \texttt{MinimizingPostShockForestError\_IJF\_pdf}}
+
+{\bf Comment 1:} The method hinges on the assumption that the time series forming the donor pool are independent from the time series under study prior to the shock.
+This seems to be a very restrictive assumption.
+The shocks that the donor pool have undergone in the past must be representative of the shock that the time series of interest is experiencing, but the series are independent.
+Given this restrictive assumption what practical applications are ruled out?
+\\
+
+\response{Yes.
+It could be a restrictive assumption in a number of situations.
+For example, if time series in a donor pool are observed in almost concurrent time as the one under study (or, the time differences are not large enough), the independence assumption may not hold.
+As a result, application in panel data should be ruled out.
+However, if the time differences are large, the dependence should diminish as time passes.} \\
+
+{\bf Comment 2:} It would be helpful to the reader to be very explicit about the timing of when information is realized.
+Is it correct that the researcher knows at $T_1^*$ that there will be a shock at $T_1^* + 1$, and they know the type of shock that it will be in order to identify the relevant donor pool shocks, but they do not know the magnitude?
+This is quite an informational advantage over unanticipated shocks.
+In many situations one could imagine that the shock was unanticipated.
+Therefore, at $T_1^* + 1$  there is a large forecast error (your model 1) but now information is available about the type of shock, so the proposed methodology of the shock effect estimator is applied at $T_1^* + 2$, yielding gains over the unadjusted forecast.
+The timing of information is crucial, but the methodology proposed in the paper seems to be applicable in many different timing scenarios.
+\\
+
+\response{It is correct that the researcher knows at $T_1^*$ that there will be a shock at $T_1^* + 1$.
+In practice, it usually happens to the case that when we realize that the shock is about to occur, we  know the \emph{general type}  or \emph{general cause} of the shock.
+The magnitude is not known.
+\\
+
+For example, in the Conoco Phillips stock example, when we knew the outbreak of COVID-19 was about to come, past shocks related to financial crisis may be helpful.
+Or, near the outbreak of COVID-19, suppose that a department in a university realized that it would be faced with declining applications.
+It could make use of the information about the decline of its admitted students in the past or that of other departments when similar situations (i.e., the number of applications suddenly decreases) happened.\\
+
+We admit it is quite an informational advantage over unanticipated shocks.
+However, in practice, if a shock is unanticipated, we may not even be able to construct such a post-shock analysis since we do not know it is about to happen.\\
+
+You are right about the timing.
+It can be applicable in many different timing scenarios.
+Generally, suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$ and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$.
+It is possible to generalize our method to this situation.
+\\
+
+Thank you for your remark on the timing scenarios. It is very helpful for improving our manuscript.} \\
+
+{\bf Comment 3:} Related to the point above, the model applied is an AR(1) with contemporaneous regressors.
+This structure requires the covariates to be known in the future for \emph{ex ante} forecasts, or for them to be forecast.
+The set-up assumes θ1 to be well behaved and the covariates are not subject to shocks if they need to be forecast.
+Empirically, we could also think of cases where the mean shift $D_{i,t}$ interacted with the covariates which would give an additional forecast error via $\mathbf{x}_{1, T_1^* + 1}$.
+The theoretical results seem to hinge on known $\mathbf{x}_{1,t}$ entering contemporaneously to derive unbiasedness.
+What are the implications of the covariates needing to be forecast?
+\\
+
+\response{It is a very good point.
+Thanks for pointing it out.
+Indeed, our method assumes $\mathbf{x}_{1, T_1^* + 1}$ to be given.
+If it is to be forecasted with errors, it will possibly result in a biased estimation of $E(\alpha_1)$ with $\hat{\alpha}_{\rm wadj}$ such that the evaluation of the proposition may not be reliable.
+\\
+
+In fact, the situation when  covariates are forecasted with errors is similar to the one when the variance of the shock effect is large.
+In both situations, the signal from covariates is weak.
+Our simulation discusses this situation by increasing $\sigma_{\alpha}$.
+It shows that a slightly weak signal will not compromise the correctness of our evaluated propositions a lot.
+However, if the forecast for the covariates is seriously bad (i.e., the signal from covariates is really weak), our result shows that the risk-reduction evaluation may be only as good as a random guess.} \\
+
+{\bf Comment 4:} Given the dynamic structure, what happens after $T_1^*+1$?
+Couldn't you use the donor pool shocks to estimate the shock transition (e.g.
+apply the shock effect estimator to the m periods following the shock), and produce an intercept correction dummy for the next $m$ periods?
+It would be interesting empirically to see if the shock is anticipated to be permanent or transitory.
+I wonder if the theoretical statements of when forecast risk is minimized may be adapted to assess when transitory shocks die out such that the unadjusted forecast is preferable again?
+\\
+
+\response{The shock transition idea you raised is interesting. We will respond to your questions one by one as follows. \\
+
+\begin{tcolorbox}
+  Given the dynamic structure, what happens after $T_1^*+1$?
+\end{tcolorbox}
+
+In our setup, we only model the time series under study up to $t = 1, \ldots, T_1^*+1$.
+We do not know what happened  after $T_1^*+1$.
+Under our setup, there are two possible situations.
+First, there is no shock after $T_1^*+1$.
+Second, there are $k$ shocks after $T_1^*$, say, at $T_1^*+d_1, \ldots, T_1^* + d_k$.
+\\
+
+\begin{tcolorbox}
+  Couldn't you use the donor pool shocks to estimate the shock transition (e.g.
+apply the shock effect estimator to the m periods following the shock), and produce an intercept correction dummy for the next $m$ periods?
+\end{tcolorbox}
+
+As we talked above, there are two situations.
+When there is no shock after $T_1^*+1$, we can simply use standard forecast for $m$-ahead  prediction in time series methodologies.
+When there are $k$ shocks after $T_1^*$, in our method, one should construct  $k$ additional donor pools to estimate the $k$ arriving shock effects.
+The details are provided in the Discussion Section in the revised manuscript.
+\\
+
+Suppose that  the existing donor pool has time series that experience $k$ shocks, each of which is similar to the one the time series under study are going to.
+Then, we can readily apply the above stated method to estimate the \emph{shock transition} and adjust for the forecasts.\\
+
+\begin{tcolorbox}
+  It would be interesting empirically to see if the shock is anticipated to be permanent or transitory.
+\end{tcolorbox}
+
+In fact, it is more of a modeling assumption. If we assume an AR model, the impact of any shock will diminish as time passes by. However, if we assume an additive model, the impact will be permanent.
+
+\begin{tcolorbox}
+ I wonder if the theoretical statements of when forecast risk is minimized may be adapted to assess when transitory shocks die out such that the unadjusted forecast is preferable again?
+\end{tcolorbox}
+
+To our best knowledge, our theoretical results are not related to when the transitory shocks die out.
+In our proposition, the risk reduction does not depend on the autoregressive parameter $\phi_1$, which controls the rate how the impact of the shock dies out.
+Our proposition is related to the adjustment at time point $T_1^*+1$ but not in a dynamic fashion.
+} \\
+
+{\bf Comment 5:} While the simulations were useful, I found the discussion in section 4 quite impenetrable.
+There are so many decisions that a researcher would need to make, including which weighting method and all the bootstrapping and leave-one-out decisions.
+It would be very helpful to the reader if you could give a summary of all your results stating your preferred user decisions for generic specifications.
+\\
+
+\response{There are mainly three decisions to make for an user: to choose 
+  \begin{itemize}
+    \item among  $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, and $\hat{\alpha}_{\rm wadj}$ 
+    \item between $\mathcal{B}_f$ and $\mathcal{B}_u$ (see detailed definition in Section 3.2)
+    \item bootstrap replication $B$ and $k$ in $k$ random draws in LOOCV
+  \end{itemize}
+  First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution.
+Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool.
+Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.
+\\
+
+  The selection between $\mathcal{B}_f$ and $\mathcal{B}_u$ is more of a philosophical question. In Section 3.2,  we noted
+
+  \begin{tcolorbox}
+  $\mathcal{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
+In contrast, $\mathcal{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness arises from parameters and idiosyncratic error.
+  \end{tcolorbox}
+
+In Section 4.3, we found that $\mathcal{B}_u$ is better than $\mathcal{B}_f$ when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is large.
+Otherwise, they are nearly the same.
+\\
+
+At the end of Section 4.3, we noted that when $p < n$, there are infinitely many solutions to $\mathbf{W}^*$ such that $\mathbf{W}^*$ will take values on the boundary of $\mathcal{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\rm wadj}$ \citep{andrews2000inconsistency}.
+$\mathcal{B}_f$  is immune to this issue.
+However, our simulation results in the Supplementary Materials show that the non-uniqueness does not seriously compromise the inference.
+\\
+
+In summary, $\mathcal{B}_u$ is preferred when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is \emph{believed} to be large.
+If $p < n$ and non-uniqueness problem is of concern due to theoretical reasons,  $\mathcal{B}_f$ is preferred.
+In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.
+\\
+
+Lastly,  greater number of bootstrap replication $B$ is preferred.
+Usually, $B = 200$ is sufficient.
+Ideally, $k=n$ is preferred.
+However, if the data size is large such that $k=n$ is computationally expensive, we found that $k = 5$ or $k = 10$ works well.
+In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool.
+} \\
+
+{\bf Comment 6:} Section 2 is hard to read without defining the terms that come in the second para- graph of section 2.1 (lines 19-23 of p.6). I'd suggest moving this to the beginning of section 2. \\
+
+\response{Sorry for not making it clear.
+The terms not defined in the caption of Figure 1 are now defined in the revised manuscript.
+For other parts, we find there are no terms that are not defined.
+The beginning parts of Section 2 are intended to give a general picture to the reader that our method is in fact general whereas the setup we investigate in Section 2.1 is a special case.
+}
 

### 2020-12-19 Revision/manuscript.tex
revision comments for the first reviewer added
response to the second reviewer and editor but partial response to the associate editor

--- 2020-09-06 Submission/manuscript.tex
@@
   \begin{center}
-    \subfloat{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
-     \subfloat{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
+    \subfloat[]{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
+     \subfloat[]{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
   \end{center}
@@
 The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool.
-The prediction of $\hat{y}^{2}_{T_1^*+1}$ and $\hat{y}^{1}_{T_1^*+1}$ differs only by an adjustment $\hat{\alpha}=10.22$.
-It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
+\textcolor{red}{$\hat{y}^{1}_{T_1^*+1}$ is the prediction without scalar adjustment of $\hat{\alpha}$ whereas $\hat{y}^{2}_{T_1^*+1}$ is the one with.
+In this example,
+    they differ only by an adjustment $\hat{\alpha}=10.22$.} It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
 \end{figure*}
@@
 Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
-In this article, we consider a dynamic panel data model with autoregressive structure similar to that in \citet{blundell1998initial}.
-Our dynamic panel model includes an additional shock effect whose presence or absence is given by the binary variable $D_{i,t}$, and we will assume that the donor pool time series are independent of the time series under study.
-The details of this model are in the next section.
+\textcolor{red}{In this article, we consider a  special case that the model includes random effects for the covariates, autoregressive structure, and an additional shock effect, whose presence or absence is given by the indicator variable $D_{i,t}$.
+We will assume that the donor pool time series are independent of the time series under study.
+The details of this model are in the next section.}
 
@@
   \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
-  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{U}_i)_{22}^{-1},
+  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{M}_i)_{22}^{-1},
 \end{align*}
@@
 $\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
-and $\mbf{U}_i$ is the design matrix for OLS with respect to time series 
+and $\mbf{M}_i$ is the design matrix for OLS with respect to time series 
 for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
-\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
+\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
 \end{align*}
@@
 \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
   &  \quad +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
+  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
   &\quad + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
@@
 Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
-because of the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.  This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
+because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, \textcolor{red}{where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}}.
+This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
 
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
 \end{align}
@@
 \var{\hat{\alpha}_{\rm wadj}}
- &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 \nonumber \\
+ &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 \nonumber \\
  &< \mu_{\alpha}^2.
@@
 \var{\hat{\alpha}_{\rm wadj}}
-& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} \\
+& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} \\
  &+ \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})  \\
@@
     \includegraphics[height = 9cm]{FIG2.pdf}
-    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price.}
+    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. \textcolor{red}{Black dots and magenta line represent real data and fitted line, respectively.}}
     \label{Fig:CP}
@@
 Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.
+
+\textcolor{red}{We can extend the proposed nowcasting to forecast  the response for $m$ periods, where $m\geq 2$.
+Without loss of generality, we assume $m = 2$.
+There are two cases.
+First, suppose that there is no additional shock after $T_1^*+1$.
+Then, the forecast boils down to standard $m$-ahead forecast in time series.
+Second, assume that the time series under study will experience a shock at $T_1^* + 2$, say $\alpha_1^{(2)}$.
+Under our framework, users may want to construct another set of donor pool with time series that experience shock similar to  $\alpha_1^{(2)}$.
+Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(2)}$.
+The forecast at $t = T_1^* + 2$ is
+\begin{align*}
+  \hat{y}^2_{1, T_1^*+2}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +2} + \hat{\alpha}_1^{(2)},
+\end{align*} 
+where $\hat{y}_{1, T_1^* + 1}^2$ is defined as in Section \ref{forecast}.
+These two cases can be generalized to  forecasting $m\geq 2$ more periods.
+The scenarios for forecasting in AR($p$), or other general models are analogous.}
+
+\textcolor{red}{In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$.
+The methodology can be extended to more general timing scenarios.
+Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$.
+We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.}
 
@@
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma^2(\mbf{U}'_i\mbf{U}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
+  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma^2(\mbf{M}'_i\mbf{M}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
+  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
 \end{align}
@@
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
+  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  & \quad  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
 \end{align*}
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}\\
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
   & \quad  +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
@@
   \end{align*}
-  where we used the fact that OLS estimator is unbiased when the design matrix $\mbf{U}_i$ is of full rank for all $i = 2, \ldots, n+1$.
+  where we used the fact that OLS estimator is unbiased when the design matrix $\mbf{M}_i$ is of full rank for all $i = 2, \ldots, n+1$.
 Because $\alpha_1\indep \varepsilon_{i,t}$, $\E{\hat{\alpha}_{\rm adj}\alpha_1}=\E{\hat{\alpha}_{\rm adj}}\E{\alpha_1}=(\E{\hat{\alpha}_{\rm adj}})^2$.

### 2020-12-31 Revision/list.tex
revised comments and manuscript with addition of Section 5.2 for apple example

@@
 
+\response{Thanks for pointing it out. The discussion of those papers is included in the introduction section of the revised manuscript.}\\
+
 {\bf Comment 2:} Secondly, a single empirical example is presented. I would like to see the results for a range of series - this would generate confidence in the proposed approach. \\
 
-\textbf{Summary of \cite{clements1996intercept}:} \cite{clements1996intercept} proposes three intercept correction for $m$-ahead forecasts of VECM.
-They are constant adjustment throughout the $m$ periods, a one-off adjustment, simple adjustment, and tailing-off forecast.
-In their setup, let $\hat{\boldsymbol{\varepsilon}}_{T}$ be the residual of VECM at $t= T$ and we are interested in  $m$-ahead forecasts.
-Denote the $m$-ahead forecasts by $\hat{y}_{ T+ m}$ and the adjusted forecasts by $\hat{\boldsymbol{y}}_{T+m}^*$.
-The \emph{constant adjustment}  considers $\hat{\boldsymbol{y}}_{T+m}^*= \hat{\boldsymbol{y}}_{ T+ m} + \hat{\boldsymbol{\varepsilon}}_{T}$.
-The \emph{one-off} adjustment considers $\hat{\boldsymbol{y}}_{T+1}^*= \hat{\boldsymbol{y}}_{ T+ 1} + \hat{\boldsymbol{\varepsilon}}_{T}$ and compute $m$-ahead forecasts using $\hat{\boldsymbol{y}}_{T+1}^*$; i.e., they only adjust once.
-The \emph{simple adjustment} considers only $\hat{\boldsymbol{y}}_{T+m}^*= \hat{\boldsymbol{y}}_{ T+ m} + \hat{\boldsymbol{\varepsilon}}_{T}$.
-The \emph{tailing-off} adjustment considers
-\begin{align*}
-  \hat{\boldsymbol{y}}_{T+m}^*
-  &=\hat{\boldsymbol{y}}_{T+m} + \sum_{i=0}^m \mathbf{\Pi}^i \mathbf{H}^{m-1-i}  \hat{\boldsymbol{\varepsilon}}_T,
-\end{align*}
-where $\mathbf{\Pi}$ is the parameter matrix of  the error correction term. It is shown that the forecast bias is reduced  when the long-run relationship of VECM changes. \\
-
-It is important to note that their method uses $\hat{\boldsymbol{\varepsilon}}_{T}$.
-In other words, the hope of reducing forecast risk depends on whether a large deviation is observed at $t=T$.
-That is, the method is not immune to unprecedented and unobserved shock.
-
-\textbf{Summary of \cite{castle2015robust}:} \cite{castle2015robust} proposed a number of robust forecasting in contrast to equilibrium-correction models.
-However, their proposed methods would depend on whether past data contain future shock signal to adjust for the forecast.
-As a result, similar to \cite{clements1996intercept}, it is not robust to unprecedented and unobserved shock.
-\\
-
-\textbf{Summary of \cite{tsay1986time}:} \cite{tsay1986time} specifies a general generating  mechanism of outliers and corresponding outlier detection methods for ARMA model.
-The two types of his proposed outlier generating mechanism are innovational outlier and additive outlier.
-The additive outlier only affects observation at $t= T_0$ for some $T_0 \in \{ 1, \ldots, T\}$.
-In contrast, the innovational outlier introduces a disturbance on the white noise so that it influences the entire process and impacts future values.
-In our study, in our AR(1) example,  the unprecedented shock is similar to innovational outlier in the sense that the contaminated response will impact future values through autoregressive structure.
-However, the difference is that the shock is an additive effect.
+\response{The simulation presents the results  for a range of series.
+To generate confidence of our proposed approach, we will include another data example of forecasting the stock price of Apple Inc.
+during MacBook release to illustrate our methods.}
 
@@
 
+Thank you for your appreciation of the potential of our methods, and for your valuable detailed comments.  We think these comments will help a lot in improving our manuscript.\\
+
 {\bf Comment 1:} The method hinges on the assumption that the time series forming the donor pool are independent from the time series under study prior to the shock.
@@
 First, there is no shock after $T_1^*+1$.
+If we assume an AR structure, the impact of the shock should decade along time.
+If we assume an additive structure without autoregressive component, the shock will be permanent.
 Second, there are $k$ shocks after $T_1^*$, say, at $T_1^*+d_1, \ldots, T_1^* + d_k$.
@@
 
-As we talked above, there are two situations.
-When there is no shock after $T_1^*+1$, we can simply use standard forecast for $m$-ahead  prediction in time series methodologies.
-When there are $k$ shocks after $T_1^*$, in our method, one should construct  $k$ additional donor pools to estimate the $k$ arriving shock effects.
-The details are provided in the Discussion Section in the revised manuscript.
+It is theoretically possible but the theoretical justification is left for future research. We will illustrate the idea as follows. \\
+
+Suppose that we are interested in estimating shock transition of the time series of interest for $d$ periods for time points, say, $T_1^* +1, \ldots, T_1^*+d$.
+Assume also that $T_i^* + d \leq T_i$ for $i = 2, \ldots, n+1$.
+We can use existing change-point detection methods to identify multiple change-points such that we can generate a change-point vector $\mathbf{D}_i = (D_{i, T_i^*+1}, \ldots, D_{i, T_i^*+d})^{T}$, where $D_{i, T_i^*+j}=1$ if there is a change-point (i.e., a shock) occurring at $t=T_i^*+j$.
+Or, $\mathbf{D}_i$ can be given by the user simply.
+Next, we can  estimate the shock effect using OLS at which $D_{i, T_i^*+j}=1$ for $j = 1, \ldots, d$.
+Then, we can obtain $\hat{\mathbf{S}}_i$ that is a vector with $j$th entries being $0$ if there is no shock at $T_i ^ * + j$ but being the estimated shock effect  if there is.
 \\
 
-Suppose that  the existing donor pool has time series that experience $k$ shocks, each of which is similar to the one the time series under study are going to.
-Then, we can readily apply the above stated method to estimate the \emph{shock transition} and adjust for the forecasts.\\
+Suppose we have covariates of the time series of interest up to $T_1^* +d$.
+Then, we can construct similar synthetic control weights  $\mathbf{W}^*$ as illustrated in the manuscript.
+Or, a more careful construction of synthetic control weighting is needed since we usually do not have the covariates up to $T_1^*+d$ in practice for $d$ being large.
+We leave it for future research.
+Then, we compute
+\begin{align*}
+  \hat{\mathbf{S}}_1 = \sum_{i=2}^{n+1} w_i^* \hat{\mathbf{S}}_i 
+\end{align*}
+as the estimated shock transition.
+However, it cannot be a simple intercept correction dummy because shock effects in $\hat{\mathbf{S}}_1$ should be considered in the $m$-ahead forecasts if we are interested in time series forecasts.
+For example, in computing $\hat{y}_{1, T_1^*+2}$ when there is no shock effect at $T_1^*+2$, we need to consider the adjusted forecast  $\hat{y}^2_{1, T_1^*+1}=\hat{y}^1_{1, T_1^*+1} + \hat{\alpha}_1$.
+\\
 
@@
 
-In fact, it is more of a modeling assumption. If we assume an AR model, the impact of any shock will diminish as time passes by. However, if we assume an additive model, the impact will be permanent.
+If all the time series in the donor pool experience more than one shock, it would be hard to judge whether the shock is anticipated to be permanent or transitory.
+It is because more than two sources of shocks exist.\\
+
+If all the time series in the donor pool experience  only experience one shock, it is possible to do such anticipation. We will illustrate the idea as below. \\
+
+Consider the model
+\begin{align*}
+  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i, t} + \beta_i I( t\leq T_i^*)+ \varepsilon_{i,t}.
+\end{align*}
+Note that we consider a general model  but not AR($p$) because the shock in AR($p$)  must be transitory due to weakly stationarity assumption.
+If we assume $\varepsilon_{i,t} \sim N(0,1)$ i.i.d., we can estimate $\beta_i$ using OLS.
+Using the weights $\mathbf{W}^*$ from previous procedure, we can  compute
+\begin{align*}
+  \hat{\beta}_1 = \sum_{i=2}^{n+1} w_i^* \hat{\beta}_i
+\end{align*}
+If $\hat{\beta}_1$ is close to 0, the shock is anticipated to be transitory.
+Otherwise, it is anticipated to be permanent.
+However, a threshold is needed.
+One can use bootstrap to estimate the distribution of   $\hat{\beta}_1$ and conduct hypothesis testing to test $H_0: E(\hat{\beta}_1)=0$ versus $H_1: E(\hat{\beta}_1)\neq 0$.
+\\
 
@@
 
-To our best knowledge, our theoretical results are not related to when the transitory shocks die out.
-In our proposition, the risk reduction does not depend on the autoregressive parameter $\phi_1$, which controls the rate how the impact of the shock dies out.
-Our proposition is related to the adjustment at time point $T_1^*+1$ but not in a dynamic fashion.
-} \\
+To our best knowledge, we haven't established the rigor of the above idea and do not know whether the theoretical statements can adapt to when transitory shocks die  out.} \\
 
@@
 In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool.
-} \\
+\\
+
+We include these comments at the end of Section 3 and Section 4 of the revised manuscript.} \\
 

### 2020-12-31 Revision/manuscript.tex
revised comments and manuscript with addition of Section 5.2 for apple example

@@
 For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks.
+\textcolor{red}{Our shock effect setting is also similar to the data generating mechanism of  \cite{tsay1986time} studied for ARMA model.
+\cite{tsay1986time} studied additive outliers that contaminates on the data at only one or multiple specific points but not others, and innovational outliers that impact the subsequent responses.
+Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}
 
@@
 This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest.
+\textcolor{red}{Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts.
+However, the approach of \cite{clements1996intercept} is not robust to unprecedented and unobserved shock since the shock signal is not embedded in the data.
+\textcolor{red}{Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust approaches for forecasting vector equilibrium-correction models but their forecast requires  conditioning on  the past data that contain shock signal, and thus not robust under our setting.}}
+
 Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
@@
 The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool.
-\textcolor{red}{$\hat{y}^{1}_{T_1^*+1}$ is the prediction without scalar adjustment of $\hat{\alpha}$ whereas $\hat{y}^{2}_{T_1^*+1}$ is the one with.
+$\hat{y}^{1}_{T_1^*+1}$ is the prediction without scalar adjustment of $\hat{\alpha}$ whereas $\hat{y}^{2}_{T_1^*+1}$ is the one with.
 In this example,
-    they differ only by an adjustment $\hat{\alpha}=10.22$.} It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
+    they differ only by an adjustment $\hat{\alpha}=10.22$. It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
 \end{figure*}
@@
 Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
-\textcolor{red}{In this article, we consider a  special case that the model includes random effects for the covariates, autoregressive structure, and an additional shock effect, whose presence or absence is given by the indicator variable $D_{i,t}$.
+In this article, we consider a  special case that the model includes random effects for the covariates, autoregressive structure, and an additional shock effect, whose presence or absence is given by the indicator variable $D_{i,t}$.
 We will assume that the donor pool time series are independent of the time series under study.
-The details of this model are in the next section.}
+The details of this model are in the next section.
 
@@
 \end{remark}
+
+\textcolor{red}{At the end, we provide some preferred user decisions for usage of shock-effect estimators.
+First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution.
+Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool.
+Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.}
 
@@
 Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
-because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, \textcolor{red}{where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}}.
+because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}.
 This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
@@
 
-\section{Forecasting Conoco Phillips stock in the presence of shocks}
+\textcolor{red}{In summary, $\mathcal{B}_u$ is preferred when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is believed to be large.
+If $p < n$ and non-uniqueness problem is of concern due to theoretical reasons,  $\mathcal{B}_f$ is preferred.
+In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.}
+
+\section{Empirical examples}
+
+\textcolor{red}{In this section, we discuss two data examples of post-shock prediction.
+Section \ref{forecasting} discusses the prediction of Conoco Phillips stock under the oil supply shock and financial crisis shock.
+Complementary to Section \ref{forecasting}, we further apply our proposed method to forecasting Apple stock price with shock source from releasing MacBook series product.}
+
+\subsection{Forecasting Conoco Phillips stock in the presence of shocks}
 \label{forecasting}
@@
     \includegraphics[height = 9cm]{FIG2.pdf}
-    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. \textcolor{red}{Black dots and magenta line represent real data and fitted line, respectively.}}
+    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. Black dots and magenta line represent real data and fitted line, respectively.}
     \label{Fig:CP}
@@
 These additive adjustment estimators do extremely well in this additive shock setting.
+
+\subsection{Forecasting Apple stock in the presence of shocks}
+
+Apple Inc.
+is an American technology company that develops a range of electronics and software with typical products, such as, iPhone, iPad, Mac, and Apple Watch.
+Every year, Apple Inc.
+releases a new series of MacBook computers to the public.
+Typically, after the release, the stock price of Apple Inc.
+is expected to experience a shock since Mac sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced.
+For example, the sales of Mac account for 9.8\% of its revenue \citep{applemac}.
+In this example, we are interested in forecasting the stock price of Apple Inc.
+near the release of MacBook series on November, 10th, 2020.
+In particular, in recent years, we observe that it usually takes two or more than two days for the shock to take effect on the stock price in the case of Apple Inc.
+Therefore, different from Section \ref{forecasting}, we are interested in the stock price of Apple Inc.
+on the day after the release date, i.e., on November 11th, 2020.
+The detailed considerations of our analysis are outlined as below.
+
+\begin{enumerate}[label = (\arabic*)]
+  \item \textbf{Selection of model.} Similar to Section \ref{forecasting}, we use an AR(1) model to forecast the stock price of Apple Inc.
+We consider 20 trading days data for the time series of interest and time series in the donor pool.
+Likewise, all the estimates will be adjusted for inflation.
+Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$ in replace of the one in Section \ref{modelsetup}.
+As a result, a generalized weighting of Section \ref{constructionofestimators} is used.
+To be specific, we mean
+  \begin{align*}
+    \mathbf{X}_1 = \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \quad \text{ and } \quad 
+    \mathbf{X}= \begin{pmatrix}
+      \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
+    \end{pmatrix},
+  \end{align*}
+  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ stands for the covariates from time $t = T_i^* +1$ to $t = T_i^*+2$. The model $\mc{M}_2$ is then generalized to 
+  \begin{align*}
+    \mc{M}_2 \colon \begin{array}{l}
+  y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
+  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}+ \t{\varepsilon}_{i},
+\end{array}
+  \end{align*}
+  where $\delta_i$ is $p \times 2$. The weighting method in Section \ref{constructionofestimators} and the corresponding properties  still follow.
+  \item \textbf{Selection of covariates.} Different to Section \ref{forecasting}, we consider only  S\&P 500 index prices and 13 Week treasury bill rates as covariates.
+In this example, the weighting method will require future covariates in computation.
+As a result, forecasting of future covariates is needed.
+We used AIC to select AR(3) for S\&P 500 index prices and AR(1)  for 13 Week treasury bill rates.
+We used Ljung-Box tests to test for model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models.
+Then, we use 2-ahead forecasts to predict the future covariates.
+  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc.
+with shock-effect date as  in the middle of 20 trading days for 2017, 2018, and 2019.
+The shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively.
+Those dates are the past dates when Apple introduced new series of MacBook products in the corresponding year.
+\end{enumerate}
+
+The covariates and response of time series in the donor pool are adjusted for inflation.
+The estimated shock effects $\alpha_i$ are $0.864, 0.905, 1.129$ for $i = 2, 3, 4$, respectively.
+Using  the same treatment of the covariates in computing $\mathbf{W}^*$ as in Section \ref{forecasting}, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
+  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.673.
+$ It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.
+
+The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 0.966$, $\hat{\alpha}_{\rm wadj}=0.950$, and $\hat{\alpha}_{\rm IVW} = 0.955$.
+The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.183$, $0.084$, and $0.085$, respectively.
+Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk.
+
+\begin{figure*}[t!]
+  \begin{center}
+    \includegraphics[height = 9cm]{FIG3.pdf}
+    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and magenta line represent real data and fitted line, respectively.}
+    \label{Fig3}
+  \end{center}  
+  \vspace{-.6cm}
+\end{figure*}
+
+As we can see from Figure \ref{Fig3}, the post-shock forecasts perform nearly perfectly.
+The unadjusted forecast misses the post-shock by 0.919 dollars.
+The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.047, 0.035, and 0.031 dollars.
+In other words, the true shock effect is nearly fully recovered by $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
+It implies that the construction of donor pool is successful.
+To explain, it appears as a trend that in recent 3 years, Apple inc.
+only updates the hardware of the MacBook series in the release of every year without much redesign, and improves the their hardware performance significantly \citep{apple2017, apple2018, apple2019} .
+It is the case for the release in 2020 as well.
+The new MacBook series consider M1 chip invented by Apple inc.
+itself in replace of chips by Intel inc.
+in the past years, and their CPU speed improves significantly; the M1 chip enables  Mac users to use the apps developed in iPhone and thus run a greater range of applications than before \citep{apple2020}.
+Therefore, in this example, our analysis is similar to \cite{baumeister2014real} in that the  forecast is conditioned on past shocks and the shock is within the range of historical experience.
 
@@
 
-\textcolor{red}{We can extend the proposed nowcasting to forecast  the response for $m$ periods, where $m\geq 2$.
+We can extend the proposed nowcasting to forecast  the response for $m$ periods, where $m\geq 2$.
 Without loss of generality, we assume $m = 2$.
@@
 These two cases can be generalized to  forecasting $m\geq 2$ more periods.
-The scenarios for forecasting in AR($p$), or other general models are analogous.}
-
-\textcolor{red}{In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$.
+The scenarios for forecasting in AR($p$), or other general models are analogous.
+
+In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$.
 The methodology can be extended to more general timing scenarios.
 Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$.
-We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.}
+We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.
 

### 2020-12-31 Revision/apple.R

@@ -1,0 +1,353 @@
+# load package
+library("quantmod")
+library('dplyr')
+library('Rsolnp')
+library('ggplot2')
+library('tikzDevice')
+# set working directory
+setwd("/Users/mac/Desktop/Research/Post-Shock Prediction/")
+
+# Apple 
+getSymbols('AAPL', from = "2000-01-01")
+AAPL <- as.data.frame(AAPL)
+AAPL <- AAPL %>% mutate(Date = rownames(AAPL))
+
+
+## S&P 500
+getSymbols('^GSPC', from = "1970-01-01")
+GSPC <- as.data.frame(GSPC)
+GSPC <- GSPC %>% mutate(Date = rownames(GSPC))
+
+## 13-Week T-Bill
+TB <- read.csv('^IRX.csv', na.strings = 'null')
+TB <- na.omit(TB)
+
+
+## inflation adjustment
+getSymbols("CPIAUCSL", src = 'FRED')
+avg.cpi <- apply.yearly(CPIAUCSL, mean)
+inflation_adj <- as.numeric(avg.cpi['2020'])/avg.cpi
+inflation_adj <- as.data.frame(inflation_adj)
+colnames(inflation_adj) <- c("dollars_2020")
+inflation_adj <- inflation_adj %>% mutate(year = 1947:2020)
+
+
+# Data Preparation
+AAPL_close <- AAPL %>% dplyr::select(AAPL.Close, Date) %>% rename(AAPL_Close = AAPL.Close)
+GSPC_close <- GSPC %>% dplyr::select(GSPC.Close, Date) %>% rename(GSPC_Close = GSPC.Close)
+TB_close <- TB %>% dplyr::select(Close, Date) %>% rename(TB_Close = Close)
+
+tom <- list(AAPL_close, GSPC_close, TB_close)
+for (i in 1:length(tom)) {
+  AAPL_close <- merge(AAPL_close, tom[[i]])
+}
+
+# response
+Y <- AAPL_close$AAPL_Close[-1]
+
+# data frame
+AAPL_close <- data.frame(AAPL_close[-nrow(AAPL_close), ], Y)
+
+
+# shock effect date
+start <- which(AAPL_close$Date %in% c("2017-06-06", "2017-06-07"))
+start_day_201706 <- as.numeric(1:nrow(AAPL_close) %in% start)
+AAPL_close <- AAPL_close %>% mutate(start_day_201706 = start_day_201706)
[…]

### 2020-12-31 Revision/manuscript.tex
revised Section 5.2

@@
 Note that non-uniqueness problems will not occur in this analysis since the conditions of Proposition \ref{uniqueness} are satisfied.
-To avoid the effect of  unit differences on weighting, we center and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
+To avoid the effect of  unit differences on weighting, we centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
 For $\hat{\alpha}_{\rm wadj}$, we observe that
@@
 Apple Inc.
-is an American technology company that develops a range of electronics and software with typical products, such as, iPhone, iPad, Mac, and Apple Watch.
+is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch.
 Every year, Apple Inc.
@@
 In particular, in recent years, we observe that it usually takes two or more than two days for the shock to take effect on the stock price in the case of Apple Inc.
-Therefore, different from Section \ref{forecasting}, we are interested in the stock price of Apple Inc.
+Therefore, we are interested in the stock price of Apple Inc.
 on the day after the release date, i.e., on November 11th, 2020.
@@
 \begin{enumerate}[label = (\arabic*)]
-  \item \textbf{Selection of model.} Similar to Section \ref{forecasting}, we use an AR(1) model to forecast the stock price of Apple Inc.
+  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc.
 We consider 20 trading days data for the time series of interest and time series in the donor pool.
-Likewise, all the estimates will be adjusted for inflation.
+All the estimates will be adjusted for inflation.
 Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$ in replace of the one in Section \ref{modelsetup}.
@@
   \begin{align*}
-    \mathbf{X}_1 = \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \quad \text{ and } \quad 
+    \mathbf{X}_1 = \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \quad \text{ and } \quad 
     \mathbf{X}= \begin{pmatrix}
-      \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
+      \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
     \end{pmatrix},
@@
   where $\delta_i$ is $p \times 2$. The weighting method in Section \ref{constructionofestimators} and the corresponding properties  still follow.
-  \item \textbf{Selection of covariates.} Different to Section \ref{forecasting}, we consider only  S\&P 500 index prices and 13 Week treasury bill rates as covariates.
-In this example, the weighting method will require future covariates in computation.
+  \item \textbf{Selection of covariates.} \textcolor{red}{We consider   S\&P 500 index prices and 13 Week treasury bill rates as covariates.} In this example, the weighting method will require future covariates in computation.
 As a result, forecasting of future covariates is needed.
 We used AIC to select AR(3) for S\&P 500 index prices and AR(1)  for 13 Week treasury bill rates.
-We used Ljung-Box tests to test for model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models.
+We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models.
 Then, we use 2-ahead forecasts to predict the future covariates.
@@
 The shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively.
-Those dates are the past dates when Apple introduced new series of MacBook products in the corresponding year.
+Those dates are the past dates when Apple Inc.
+introduced new series of MacBook computers in the corresponding year.
 \end{enumerate}
@@
 The estimated shock effects $\alpha_i$ are $0.864, 0.905, 1.129$ for $i = 2, 3, 4$, respectively.
-Using  the same treatment of the covariates in computing $\mathbf{W}^*$ as in Section \ref{forecasting}, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
+\textcolor{red}{We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.} As a result, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
   \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.673.
@@
 The unadjusted forecast misses the post-shock by 0.919 dollars.
-The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.047, 0.035, and 0.031 dollars.
+The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.047, 0.035, and 0.031 dollars, respectively.
 In other words, the true shock effect is nearly fully recovered by $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
@@
 Therefore, in this example, our analysis is similar to \cite{baumeister2014real} in that the  forecast is conditioned on past shocks and the shock is within the range of historical experience.
+\textcolor{red}{In other words, the shock in this example is not unprecedented.}
 

### 2021-01-06 Revision/list.tex
revised mansucript and response to reviewers

@@
 
-\response{The simulation presents the results  for a range of series.
-To generate confidence of our proposed approach, we will include another data example of forecasting the stock price of Apple Inc.
-during MacBook release to illustrate our methods.}
+\response{We include another example of forecasting the stock price of Apple Inc.
+during MacBook release in 2020 in Section 5.2 of the revised manuscript.
+Our method nearly perfectly recovers its stock price of the day after the release date.
+The donor pool constructed includes three time series of  Apple inc.'s stock price during MacBook release in the past three years.
+In this example, the shock is with precedent and our method works well because Apple Inc.
+is a well-established company that is not expected to reform its products a lot.
+As a result, knowledge from past shocks can bring insights into the future shocks.
+This example is representative for applying our methods to the time series that are to experience a shock that is with precedent in the past.
+In contrast, the example of Conoco Phillips is without precedent.
+In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by  pandemic.
+In this example, our method is better than the original forecast though it cannot fully recover the stock price.
+\\
+
+In summary, the Apple example and Conoco Phillips example are representative of time series that are to experience precedented and unprecedented shocks, respectively.
+We think they generate confidence in our proposed approach since they  represent a wide range of applications in the real life.
+To support, the simulation  in Section 4 also informs  users the situations when our methods will work well and will not.
+}
 
@@
 
-\response{The shock transition idea you raised is interesting. We will respond to your questions one by one as follows. \\
-
-\begin{tcolorbox}
-  Given the dynamic structure, what happens after $T_1^*+1$?
-\end{tcolorbox}
-
-In our setup, we only model the time series under study up to $t = 1, \ldots, T_1^*+1$.
+\response{In our setup, we only model the time series under study up to $t = 1, \ldots, T_1^*+1$.
 We do not know what happened  after $T_1^*+1$.
-Under our setup, there are two possible situations.
-First, there is no shock after $T_1^*+1$.
-If we assume an AR structure, the impact of the shock should decade along time.
-If we assume an additive structure without autoregressive component, the shock will be permanent.
-Second, there are $k$ shocks after $T_1^*$, say, at $T_1^*+d_1, \ldots, T_1^* + d_k$.
+It is possible that there are no shocks or additional shocks after $T_1^*+1$.
 \\
 
-\begin{tcolorbox}
-  Couldn't you use the donor pool shocks to estimate the shock transition (e.g.
-apply the shock effect estimator to the m periods following the shock), and produce an intercept correction dummy for the next $m$ periods?
-\end{tcolorbox}
-
-It is theoretically possible but the theoretical justification is left for future research. We will illustrate the idea as follows. \\
-
-Suppose that we are interested in estimating shock transition of the time series of interest for $d$ periods for time points, say, $T_1^* +1, \ldots, T_1^*+d$.
-Assume also that $T_i^* + d \leq T_i$ for $i = 2, \ldots, n+1$.
-We can use existing change-point detection methods to identify multiple change-points such that we can generate a change-point vector $\mathbf{D}_i = (D_{i, T_i^*+1}, \ldots, D_{i, T_i^*+d})^{T}$, where $D_{i, T_i^*+j}=1$ if there is a change-point (i.e., a shock) occurring at $t=T_i^*+j$.
-Or, $\mathbf{D}_i$ can be given by the user simply.
-Next, we can  estimate the shock effect using OLS at which $D_{i, T_i^*+j}=1$ for $j = 1, \ldots, d$.
-Then, we can obtain $\hat{\mathbf{S}}_i$ that is a vector with $j$th entries being $0$ if there is no shock at $T_i ^ * + j$ but being the estimated shock effect  if there is.
+It is possible to use the donor pool to estimate the shock transition,  and produce an intercept dummy for the next $m$ periods.
+Assume there are no additional shocks  after $T_1^*+1$, and $T_i^*+m \leq T_i$ for $i = 2, \ldots, n+1$.
+Consider the model
+\begin{align*}
+  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i, T_i^* + d}I(t = T_i^*+d) +\varepsilon_{i,t}
+\end{align*}
+for $i = 2, \ldots, n+1$ and $d = 1, \ldots, m$.
+Suppose we have information of the covariates up to $T_1^*+d$ either by given information or by forecasting.
+We can use our proposed synthetic control method to compute weights $\mathbf{W}^*$ and OLS to estimate $\beta_{i, T_i^*+d}$ to compute $\hat{\beta}_{1, T_1^*+d}$.
+As a result, we obtain $\hat{\boldsymbol{\beta}}_1^{(m)} = (\hat{\beta}_{1, T_1^*+d})_{d = 1}^m$.
+However, it cannot be a simple intercept dummy but instead an iterative adjustment in computing $m$-ahead forecasts.
+For example, $\hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)}+ \hat{\beta}_{1, T_1^*+2}$, where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts considering $\hat{y}_{1, T_1^*+1}^{(1)}$ in computation.
+The approach of \cite{agarwal2020two} is an alternative  to this problem though its adjustment is without theoretical guarantees.
 \\
 
-Suppose we have covariates of the time series of interest up to $T_1^* +d$.
-Then, we can construct similar synthetic control weights  $\mathbf{W}^*$ as illustrated in the manuscript.
-Or, a more careful construction of synthetic control weighting is needed since we usually do not have the covariates up to $T_1^*+d$ in practice for $d$ being large.
-We leave it for future research.
-Then, we compute
+To judge if the shock is permanent, we may go for another approach. Consider the model
 \begin{align*}
-  \hat{\mathbf{S}}_1 = \sum_{i=2}^{n+1} w_i^* \hat{\mathbf{S}}_i 
+  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i}I(T_i^*< t \leq  T_i^*+d) +\varepsilon_{i,t}.
 \end{align*}
-as the estimated shock transition.
-However, it cannot be a simple intercept correction dummy because shock effects in $\hat{\mathbf{S}}_1$ should be considered in the $m$-ahead forecasts if we are interested in time series forecasts.
-For example, in computing $\hat{y}_{1, T_1^*+2}$ when there is no shock effect at $T_1^*+2$, we need to consider the adjusted forecast  $\hat{y}^2_{1, T_1^*+1}=\hat{y}^1_{1, T_1^*+1} + \hat{\alpha}_1$.
+We can compute $\hat{\beta}_i$ from OLS and $\mathbf{W}^*$ from synthetic approach with covariates $d \times p$ (see for example of $p = 2$ in our added Apple example in Section 5.2 of revised transcript) to compute $\hat{\beta}_1$.
+Note that $\hat{\beta}_1$ is unbiased.
+We can use parametric double bootstrap to test the hypothesis that $H_0 \colon \beta_1=0$ versus $H_1 \colon \beta_1\neq 0$.
 \\
 
-\begin{tcolorbox}
-  It would be interesting empirically to see if the shock is anticipated to be permanent or transitory.
-\end{tcolorbox}
-
-If all the time series in the donor pool experience more than one shock, it would be hard to judge whether the shock is anticipated to be permanent or transitory.
-It is because more than two sources of shocks exist.\\
-
-If all the time series in the donor pool experience  only experience one shock, it is possible to do such anticipation. We will illustrate the idea as below. \\
-
-Consider the model
-\begin{align*}
-  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i, t} + \beta_i I( t\leq T_i^*)+ \varepsilon_{i,t}.
-\end{align*}
-Note that we consider a general model  but not AR($p$) because the shock in AR($p$)  must be transitory due to weakly stationarity assumption.
-If we assume $\varepsilon_{i,t} \sim N(0,1)$ i.i.d., we can estimate $\beta_i$ using OLS.
-Using the weights $\mathbf{W}^*$ from previous procedure, we can  compute
-\begin{align*}
-  \hat{\beta}_1 = \sum_{i=2}^{n+1} w_i^* \hat{\beta}_i
-\end{align*}
-If $\hat{\beta}_1$ is close to 0, the shock is anticipated to be transitory.
-Otherwise, it is anticipated to be permanent.
-However, a threshold is needed.
-One can use bootstrap to estimate the distribution of   $\hat{\beta}_1$ and conduct hypothesis testing to test $H_0: E(\hat{\beta}_1)=0$ versus $H_1: E(\hat{\beta}_1)\neq 0$.
-\\
-
-\begin{tcolorbox}
- I wonder if the theoretical statements of when forecast risk is minimized may be adapted to assess when transitory shocks die out such that the unadjusted forecast is preferable again?
-\end{tcolorbox}
-
-To our best knowledge, we haven't established the rigor of the above idea and do not know whether the theoretical statements can adapt to when transitory shocks die  out.} \\
+To our best knowledge, we don't know whether the theoretical statements of our proposed methods in the manuscript can be adapted to assess when transitory shocks die out.} \\
 

### 2021-01-06 Revision/manuscript.tex
revised mansucript and response to reviewers

@@
 For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks.
-\textcolor{red}{Our shock effect setting is also similar to the data generating mechanism of  \cite{tsay1986time} studied for ARMA model.
+Our shock effect setting is also similar to the data generating mechanism of  \cite{tsay1986time} studied for ARMA model.
 \cite{tsay1986time} studied additive outliers that contaminates on the data at only one or multiple specific points but not others, and innovational outliers that impact the subsequent responses.
-Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}
+Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.
 
@@
 This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest.
-\textcolor{red}{Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts.
+Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts.
 However, the approach of \cite{clements1996intercept} is not robust to unprecedented and unobserved shock since the shock signal is not embedded in the data.
-\textcolor{red}{Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust approaches for forecasting vector equilibrium-correction models but their forecast requires  conditioning on  the past data that contain shock signal, and thus not robust under our setting.}}
+Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust approaches for forecasting vector equilibrium-correction models but their forecast requires  conditioning on  the past data that contain shock signal, and thus not robust under our setting.
 
@@
 Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.
-We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020.
-We will show that our proposed adjustment estimators yield much better results than no adjustment in this setting.
-We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts.
-We now motivate our framework for post-shock forecasting.
+\textcolor{red}{We demonstrate the utility of our methodology in real data analyses in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020 due to oil supply shock and COVID-19 pandemic, and the stock price of Apple Inc.
+that experienced a shock due to MacBook release on November 10th, 2020.
+We will show that our proposed adjustment estimators yield much better results than no adjustment in these setting.
+The example of Conoco Phillips provides an empirical application of our methods in unprecedented shocks whereas that of Apple provides a treatment for shock with precedent.
+We now motivate our framework for post-shock forecasting.}
 
@@
 \begin{align}
- \Theta &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon \label{parameter} \\
- & \qquad  t= 1, \ldots, T_i, i = 2, \ldots, n +1\}, \nonumber \\
-    \Theta_1 &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon  \nonumber \\
-   & \qquad t= 1, \ldots, T_i, i = 1\}, \nonumber
+ \Theta &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\label{parameter} \\
+    \Theta_1 &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon  t= 1, \ldots, T_i, i = 1\}, \nonumber
 \end{align}
@@
 
-\textcolor{red}{At the end, we provide some preferred user decisions for usage of shock-effect estimators.
+\begin{remark}
+  \textcolor{red}{We also provide some recommended choices for shock-effect estimators in different situations.
 First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution.
@@
 Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.}
+\end{remark}
 
@@
 
-\textcolor{red}{In summary, $\mathcal{B}_u$ is preferred when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is believed to be large.
+In summary, $\mathcal{B}_u$ is preferred when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is believed to be large.
 If $p < n$ and non-uniqueness problem is of concern due to theoretical reasons,  $\mathcal{B}_f$ is preferred.
-In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.}
+In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.
 
@@
 \textcolor{red}{In this section, we discuss two data examples of post-shock prediction.
-Section \ref{forecasting} discusses the prediction of Conoco Phillips stock under the oil supply shock and financial crisis shock.
-Complementary to Section \ref{forecasting}, we further apply our proposed method to forecasting Apple stock price with shock source from releasing MacBook series product.}
+Section \ref{forecasting} discusses the prediction of Conoco Phillips stock under the unprecedented oil supply shock and financial crisis shock.
+Section \ref{apple} applies our proposed method to forecasting Apple stock price with precedented shock source from releasing MacBook series product.
+They provide empirical illustration for real-life applications with precedented shocks and unprecedented ones, respectively.
+The adjusted forecast in Section \ref{forecasting} performs much better than original forecast whereas the adjusted forecast in Section \ref{apple} nearly perfectly recovers the response after shock.
+The reasons are detailed in  Section \ref{forecasting} and Section \ref{apple}, respectively.}
 
@@
 \subsection{Forecasting Apple stock in the presence of shocks}
+\label{apple}
 
@@
   where $\delta_i$ is $p \times 2$. The weighting method in Section \ref{constructionofestimators} and the corresponding properties  still follow.
-  \item \textbf{Selection of covariates.} \textcolor{red}{We consider   S\&P 500 index prices and 13 Week treasury bill rates as covariates.} In this example, the weighting method will require future covariates in computation.
+  \item \textbf{Selection of covariates.} We consider   S\&P 500 index prices and 13 Week treasury bill rates as covariates.
+In this example, the weighting method will require future covariates in computation.
 As a result, forecasting of future covariates is needed.
@@
 The estimated shock effects $\alpha_i$ are $0.864, 0.905, 1.129$ for $i = 2, 3, 4$, respectively.
-\textcolor{red}{We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.} As a result, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
+We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
+As a result, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
   \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.673.
@@
 Therefore, in this example, our analysis is similar to \cite{baumeister2014real} in that the  forecast is conditioned on past shocks and the shock is within the range of historical experience.
-\textcolor{red}{In other words, the shock in this example is not unprecedented.}
+In other words, the shock in this example is not unprecedented.
 

### 2021-01-06 Revision/list.tex
I made minor changes. I will look everything over more closely tomorrow

@@
     \item between $\mathcal{B}_f$ and $\mathcal{B}_u$ (see detailed definition in Section 3.2)
-    \item bootstrap replication $B$ and $k$ in $k$ random draws in LOOCV
+    \item The $k$ in the $k$ random draws in LOOCV
   \end{itemize}
@@
 Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.
+These recommendations are included in Remark 3 at the end of Section 2.
 \\
@@
 In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.
+This explanation is added to the end of Section 4.
 \\
 
-Lastly,  greater number of bootstrap replication $B$ is preferred.
-Usually, $B = 200$ is sufficient.
+%Lastly,  greater number of bootstrap replication $B$ is preferred. Usually, $B = 200$ is sufficient. 
 Ideally, $k=n$ is preferred.
@@
 
-We include these comments at the end of Section 3 and Section 4 of the revised manuscript.} \\
+} \\
 

### 2021-01-06 Revision/manuscript.tex
I made minor changes. I will look everything over more closely tomorrow

@@
 Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.
-\textcolor{red}{We demonstrate the utility of our methodology in real data analyses in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020 due to oil supply shock and COVID-19 pandemic, and the stock price of Apple Inc.
-that experienced a shock due to MacBook release on November 10th, 2020.
+\textcolor{red}{We demonstrate the utility of our methodology with two real data analyses.
+The first of these focuses on forecasting the stock price of Conoco Phillips after March 9th, 2020, in the midst of the COVID-19 pandemic and an oil supply war.
+The second of these focuses on forecasting the stock price of Apple Inc.
+after the company releases their latest installment of the MacBook on November 10th, 2020.
 We will show that our proposed adjustment estimators yield much better results than no adjustment in these setting.
-The example of Conoco Phillips provides an empirical application of our methods in unprecedented shocks whereas that of Apple provides a treatment for shock with precedent.
-We now motivate our framework for post-shock forecasting.}
+The example of Conoco Phillips provides an empirical application of our methods in unprecedented shocks whereas the Apple example provides a case for post-shock prediction where the shock has precedent.
+We now motivate our framework for post-shock prediction.}
 
@@
 
-In this section, we present bootstrap procedures that approximate the distribution of our shock effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction quantity using plug-in approach in practice.
+We present bootstrap procedures that approximate the distribution of our shock effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction quantity using plug-in approach in practice.
 Our procedure involves the resampling of residuals in the separate OLS fits.
@@
 
-In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities.
+We discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities.
 We mainly discuss simulations under $\mc{M}_2$ (see Section \ref{modelsetup}) for $\mc{B}_u$ and $\mc{B}_f$ (see Section \ref{varbootstrap}) with comparisons to those under $\mc{M}_1$ whose results are listed in Section 3 in the Supplementary Materials.
@@
 
-\textcolor{red}{In this section, we discuss two data examples of post-shock prediction.
-Section \ref{forecasting} discusses the prediction of Conoco Phillips stock under the unprecedented oil supply shock and financial crisis shock.
-Section \ref{apple} applies our proposed method to forecasting Apple stock price with precedented shock source from releasing MacBook series product.
-They provide empirical illustration for real-life applications with precedented shocks and unprecedented ones, respectively.
-The adjusted forecast in Section \ref{forecasting} performs much better than original forecast whereas the adjusted forecast in Section \ref{apple} nearly perfectly recovers the response after shock.
-The reasons are detailed in  Section \ref{forecasting} and Section \ref{apple}, respectively.}
+\textcolor{red}{In this section, we discuss two real data examples of post-shock prediction.
+Section \ref{forecasting} discusses the prediction of Conoco Phillips stock occurring on March 9th, 2020.
+This shock relates to an oil price war and the COVID-19 pandemic.
+Section \ref{apple} applies our proposed method to the forecasting of Apple stock prices after releasing the latest version of their MacBook product.
+These examples provide empirical illustration of our methodology in settings where the shock is, respectively, unprecedented and with precedent.
+The adjusted forecast in Section \ref{forecasting} performs much better than original forecast whereas the adjusted forecast in Section \ref{apple} nearly perfectly recovers the response after shock as reasonably expected.
+}
 

### 2021-01-07 Revision/list.tex
minor change to response to the AE

@@
 In this example, our method is better than the original forecast though it cannot fully recover the stock price.
-\\
-
-In summary, the Apple example and Conoco Phillips example are representative of time series that are to experience precedented and unprecedented shocks, respectively.
-We think they generate confidence in our proposed approach since they  represent a wide range of applications in the real life.
-To support, the simulation  in Section 4 also informs  users the situations when our methods will work well and will not.
+We hope that the addition of the Apple example helps to generate confidence in our approach.
 }

### 2021-01-07 Revision/list.tex
revised mansucript and response to reviewers

@@
 We address all of the reviewers' comments below.
-An outlines of each change made or a rebuttal is provided for all of the reviewer's comments.
+An outline of each change made or a rebuttal is provided for all of the reviewers' comments.
 
@@
 during MacBook release in 2020 in Section 5.2 of the revised manuscript.
-Our method nearly perfectly recovers its stock price of the day after the release date.
-The donor pool constructed includes three time series of  Apple inc.'s stock price during MacBook release in the past three years.
+\textcolor{red}{Our forecast is very close to the stock price of the day after the release date.} The donor pool constructed includes three time series of  Apple inc.'s stock price during MacBook release in the past three years.
 In this example, the shock is with precedent and our method works well because Apple Inc.
@@
 In this example, our method is better than the original forecast though it cannot fully recover the stock price.
-We hope that the addition of the Apple example helps to generate confidence in our approach.
-}
+We hope that the addition of the Apple example helps to generate confidence in our approach.}
 
@@
 Section 3.3 details the leave-one-out cross validation procedures, which are tailored to our setup, to estimate $p$.
-As a result, users can be informed about the credibility of our methods} \\
+As a result, users can be informed about the credibility of our methods.} \\
 
@@
 In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool.
-\\
-
 } \\

### 2021-01-07 Revision/manuscript.tex
made minor edits; it looks good
revised mansucript and response to reviewers

@@
 Bootstrap and leave-one-out cross validation procedures are provided to prospectively assess the performance of our methodology.
-Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
+Several simulated data examples, and two real data examples of forecasting Conoco Phillips and Apple stock price are provided for verification and illustration.
 \end{abstract}
@@
 On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects from outside data sources are all thought to arise from a  data generating process similar to that of the shock under study.
-For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of past shocks.
+For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of  shocks in the recent past.
 Our shock effect setting is also similar to the data generating mechanism of  \cite{tsay1986time} studied for ARMA model.
@@
 
-In this article, we will assume a simple autoregressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure.
+In this article, we will assume a simple autoregressive data generating process  with a general random-effect structure.
 Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
@@
 Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.
-\textcolor{red}{We demonstrate the utility of our methodology with two real data analyses.
+We demonstrate the utility of our methodology with two real data analyses.
 The first of these focuses on forecasting the stock price of Conoco Phillips after March 9th, 2020, in the midst of the COVID-19 pandemic and an oil supply war.
@@
 The example of Conoco Phillips provides an empirical application of our methods in unprecedented shocks whereas the Apple example provides a case for post-shock prediction where the shock has precedent.
-We now motivate our framework for post-shock prediction.}
+We now motivate our framework for post-shock prediction.
 
@@
 and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.
-In this article, we focus on post-shock prediction where forecasts methods only differ at the next future time point.
+In this article, we focus on post-shock prediction where forecasting methods only differ at the next future time point.
 Thus the MSE reduces to the magnitude $\E{\hat y_{1,t} - y_{1,t}}^2$.
@@
 This figure depicts a time series that experienced a shock at time point $T_1^*+1 = 126$.
-It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations from a donor pool of forty time series that have previously undergone a similar shock for which post-shock responses are recorded.
+It is supposed that the researcher does not have any information after $T_1^*$, but does have observations from a donor pool of forty time series that have previously undergone a similar shock for which post-shock responses are recorded.
 Similarity in this context means that the shock effects are random variables that from a common distribution.
@@
 
-In this section, we will describe the assumed dynamic panel models for which 
+In this section, we will describe the assumed autoregressive models with random effects for which 
 post-shock aggregated estimators are provided. The basic structures of these models 
@@
 \begin{align}
- \Theta &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\label{parameter} \\
-    \Theta_1 &= \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon  t= 1, \ldots, T_i, i = 1\}, \nonumber
+\begin{array}{l}
+ \;\, \Theta = \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
+   \Theta_1 = \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon  t= 1, \ldots, T_i, i = 1\}
+\end{array}\label{parameter} 
 \end{align}
@@
 Note that parameter estimation for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
-We emphasize that $\alpha_i$s are random variables, but the OLS estimation is conditioned on the realizations from some distribution.
+We emphasize that $\alpha_i$'s are random variables, but the OLS estimation is conditioned on the realizations from some distribution.
 
@@
 \end{equation}
-where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of  
+where the $\hat{\alpha}_i$'s in \eqref{adjusted} are OLS estimators of  
 the $\alpha_i$s for $i = 2, \ldots, n+1$.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
@@
   \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
-  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{M}_i)_{22}^{-1},
+  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{M}_i'\mbf{M}_i)_{22}^{-1},
 \end{align*}
@@
 The regression coefficients $\theta_i$ are nuisance parameters that are not of primary importance.
-It will be understood that structural 0s in $\theta_i$ correspond to variables that are unimportant. 
+It will be understood that structural 0's in $\theta_i$ correspond to variables that are unimportant. 
 \end{remark}
@@
 \begin{remark}
-  \textcolor{red}{We also provide some recommended choices for shock-effect estimators in different situations.
+We also provide some recommended choices for shock-effect estimators in different situations.
 First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution.
 Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool.
-Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.}
+Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.
 \end{remark}
@@
 Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$.
-However, under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$.
+However, under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$.
 Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$.
@@
 \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
-  &  \quad +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
-  &\quad + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
+  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
 \end{align*}
 \end{enumerate}
-Formal justification for these results can be found in Appendix \ref{proofs}. Note that the variances are not comparable in closed-form 
+Formal justification for these results can be found in Appendix in Section \ref{proofs}. Note that the variances are not comparable in closed-form 
 because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}.
@@
 \var{\hat{\alpha}_{\rm wadj}}
- &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 \nonumber \\
- &< \mu_{\alpha}^2.
+ &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
 \end{align}
@@
 
-The shock effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$. 
+The shock effects $\alpha_i$'s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
 However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
@@
 \var{\hat{\alpha}_{\rm wadj}}
-& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} \\
- &+ \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})  \\
- &< (\E{\alpha_1})^2,
+& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}) < (\E{\alpha_1})^2,
 \end{align*}
@@
 
-\textcolor{red}{In this section, we discuss two real data examples of post-shock prediction.
+In this section, we discuss two real data examples of post-shock prediction.
 Section \ref{forecasting} discusses the prediction of Conoco Phillips stock occurring on March 9th, 2020.
@@
 These examples provide empirical illustration of our methodology in settings where the shock is, respectively, unprecedented and with precedent.
-The adjusted forecast in Section \ref{forecasting} performs much better than original forecast whereas the adjusted forecast in Section \ref{apple} nearly perfectly recovers the response after shock as reasonably expected.
-}
+\textcolor{red}{The adjusted forecast in Section \ref{forecasting} performs much better than original forecast whereas the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.}
 
@@
 We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$.
-The model of $\alpha_i$ incorporates daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX).
+The model of $\alpha_i$ incorporates lagged daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX).
 The model for $y_{i,t}$ disregards VIX.
@@
   where $\delta_i$ is $p \times 2$. The weighting method in Section \ref{constructionofestimators} and the corresponding properties  still follow.
-  \item \textbf{Selection of covariates.} We consider   S\&P 500 index prices and 13 Week treasury bill rates as covariates.
+  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates.
 In this example, the weighting method will require future covariates in computation.
@@
 We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models.
-Then, we use 2-ahead forecasts to predict the future covariates.
+Then, we use 1-ahead forecasts to predict the future covariates.
   \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc.
-with shock-effect date as  in the middle of 20 trading days for 2017, 2018, and 2019.
+with shock-effect date as  in the middle of 15 trading days for 2017, 2018, and 2019.
 The shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively.
@@
 We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
-As a result, we observe $\mathbf{W}^* = (0.674, 0.000, 0.326)$ and $
-  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.673.
+As a result, we observe $\mathbf{W}^* = (0.664, 0.000, 0.336)$ and $
+  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.674.
 $ It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.
 
-The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 0.966$, $\hat{\alpha}_{\rm wadj}=0.950$, and $\hat{\alpha}_{\rm IVW} = 0.955$.
-The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.183$, $0.084$, and $0.085$, respectively.
+The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.071$, $\hat{\alpha}_{\rm wadj}=1.066$, and $\hat{\alpha}_{\rm IVW} = 1.090$.
+The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.192$, $0.095$, and $0.091$, respectively.
 Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk.
@@
 As we can see from Figure \ref{Fig3}, the post-shock forecasts perform nearly perfectly.
-The unadjusted forecast misses the post-shock by 0.919 dollars.
-The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.047, 0.035, and 0.031 dollars, respectively.
-In other words, the true shock effect is nearly fully recovered by $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
-It implies that the construction of donor pool is successful.
+The unadjusted forecast misses the post-shock by 1.518 dollars.
+The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.447, 0.427, and 0.452 dollars, respectively.
+\textcolor{red}{In other words, the forecasts induced by $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are very close to the true response.
+Note  that the 1-ahead forecast error for the covariates contribute to some of the forecast risk.} Beyond that, it implies that the construction of donor pool is successful.
 To explain, it appears as a trend that in recent 3 years, Apple inc.

### 2021-01-07 Revision/apple.R

@@ -53,7 +53,7 @@ AAPL_close <- data.frame(AAPL_close[-nrow(AAPL_close), ], Y)
 start <- which(AAPL_close$Date %in% c("2017-06-06", "2017-06-07"))
 start_day_201706 <- as.numeric(1:nrow(AAPL_close) %in% start)
 AAPL_close <- AAPL_close %>% mutate(start_day_201706 = start_day_201706)
-TS2 <- AAPL_close[(start[1] - 10):(start[1] + 10), ]
+TS2 <- AAPL_close[(start[1] - 5):(start[1] + 10), ]
 # inflation adjustment
 TS2[, 2:5] <- TS2[, 2:5] * inflation_adj$dollars_2020[inflation_adj$year == 2017] 
 m_AAPL_201706 <- lm(Y ~ AAPL_Close + start_day_201706 + GSPC_Close + TB_Close, 
@@ -67,7 +67,7 @@ alpha_201706
 start <- which(AAPL_close$Date %in% c("2018-10-29", "2018-10-30"))
 start_day_201810 <- as.numeric(1:nrow(AAPL_close) %in% start)
 AAPL_close <- AAPL_close %>% mutate(start_day_201810 = start_day_201810)
-TS3 <- AAPL_close[(start[1] - 10):(start[1] + 10), ]
+TS3 <- AAPL_close[(start[1] - 5):(start[1] + 10), ]
 # inflation adjustment
 TS3[, 2:5] <- TS3[, 2:5] * inflation_adj$dollars_2020[inflation_adj$year == 2018] 
 m_AAPL_201810 <- lm(Y ~ AAPL_Close + start_day_201810 + GSPC_Close + TB_Close, 
@@ -80,7 +80,7 @@ alpha_201810
 start <- which(AAPL_close$Date %in% c("2019-06-03", "2019-06-04"))
 start_day_201906 <- as.numeric(1:nrow(AAPL_close) %in% start)
 AAPL_close <- AAPL_close %>% mutate(start_day_201906 = start_day_201906)
-TS4 <- AAPL_close[(start[1] - 10):(start[1] + 10), ]
+TS4 <- AAPL_close[(start[1] - 5):(start[1] + 10), ]
 # inflation adjustment
 TS4[, 2:5] <- TS4[, 2:5] * inflation_adj$dollars_2020[inflation_adj$year == 2019] 
[…]

### 2021-01-08 Revision/manuscript.tex
making a round of edits; not done yet

@@
 This is a general problem that has many real life applications.
-For example, one may be interested in forecasting the stock price of a company tomorrow after hearing terrible or great news about the company  after hours trading.
+For example, one may be interested in forecasting the stock price of a company tomorrow after hearing terrible or great news about the company after trading has concluded for the day.
 Companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis, but they only have recent sales data for which the company is operating well.
-All is not lost in this setting, one may be able to supplement the present forecast with past data borrowed from other time series which contain similar structural shocks.
+All is not lost in this forecasting setting, one may be able to supplement the present forecast with past data borrowed from other time series which contain similar structural shocks.
 The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
@@
 In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
-In this setting, the additive shock effect is a random effect that is parameterized in the autoregressive model.
+In this setting, we treat the additive shock effect as an observed random effect, obtained from a distribution of similar shocks, that is parameterized as a conditional fixed effect within an autoregressive model.
 The shock effect is then estimated using ordinary least squares (OLS).
@@
 Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}.
-On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects from outside data sources are all thought to arise from a  data generating process similar to that of the shock under study.
-For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of  shocks in the recent past.
-Our shock effect setting is also similar to the data generating mechanism of  \cite{tsay1986time} studied for ARMA model.
-\cite{tsay1986time} studied additive outliers that contaminates on the data at only one or multiple specific points but not others, and innovational outliers that impact the subsequent responses.
-Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.
+On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting framework, provided that the shock effects from outside data sources arose from the same data generating process as the shock effect under study.
+For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of shocks from the recent past.
+Our shock effect setting is also similar to the data generating mechanism that  \cite{tsay1986time} studied for ARMA models.
+\cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses.
+\red{ I do not understand what this means, please clarify: Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}
 
@@
 We assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock.
-Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing first and second moments.
-
-We estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed.
-We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest.
-This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest.
+Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing second moments.
+
+We then estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed.
+These estimated shock effects are then aggregated and this aggregated estimator is taken to be the estimator for the shock effect in the time series of interest.
+Finally, this aggreagted estimator is then added to a forecast for the yet to be realized post-shock response of the time series of interest.
 Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts.
 However, the approach of \cite{clements1996intercept} is not robust to unprecedented and unobserved shock since the shock signal is not embedded in the data.
-Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust approaches for forecasting vector equilibrium-correction models but their forecast requires  conditioning on  the past data that contain shock signal, and thus not robust under our setting.
-
-Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}.
-The context in \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}.
-In our context, the yet to be observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the time series forming the donor pool.
+Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust general approaches for forecasting in vector equilibrium-correction models.
+However, their forecasting methodology requires conditioning on the past data that contain shock signals.
+This approach is therefore not applicable in the post-shock setting.
+
+The shock effects in our post-shock forecasting framework are similar to ``expectation shocks,'' studied in \cite{clements2019measuring}.
+\cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach, as in \cite{croushore2006data}.
+In our context, the yet to be observed shock effect of interest arises as a random effect whose assumed generative distribution can only be partially estimated.
+This partial estimation only uses shock effect estimates from the time series forming the donor pool.
 
 In this article, we will assume a simple autoregressive data generating process  with a general random-effect structure.
-Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
+These specifications are similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
 However, our model formulation is more general than \cite{ramaswamy1993empirical}.
-In our model, the donor pool can consist of dependent time series but time series within the donor pool should be independent of the time series of interest.
+In our model, the donor pool can consist of dependent time series, but the time series forming the donor pool are required to be independent from the time series of interest.
 However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method.
@@
 after the company releases their latest installment of the MacBook on November 10th, 2020.
-We will show that our proposed adjustment estimators yield much better results than no adjustment in these setting.
+We will show that our proposed adjustment estimators yield much better results than no adjustment in these settings.
 The example of Conoco Phillips provides an empirical application of our methods in unprecedented shocks whereas the Apple example provides a case for post-shock prediction where the shock has precedent.
@@
 
-In this section, we will describe the assumed autoregressive models with random effects for which 
-post-shock aggregated estimators are provided. The basic structures of these models 
-are the same for all time-series in the analysis, the differences between them lie in the setup of the shock effect distribution.
+We now describe the assumed autoregressive models with random effects for which post-shock aggregated estimators are provided.
+The basic structures of these models are the same for all time-series in the analysis, the differences between them lie in the setup of the shock effect distribution.
 
@@
 and $\x_{i,t} \in \R^{p}$ with $p \geq 1$.  We assume that the 
-$\mbf{x}_{i,t}$'s are fixed. Let $|x|$ denote the absolute value of $x$ for $x\in \reals$. For $i = 1, \ldots, n+1$ and $t=1, \ldots, T_i$, the random effects structure for $\mc{M}_1$ is:
+$\mbf{x}_{i,t}$s are fixed. Let $|x|$ denote the absolute value of $x$ for $x\in \reals$. For $i = 1, \ldots, n+1$ and $t=1, \ldots, T_i$, the random effects structure for $\mc{M}_1$ is:
 \begin{align*}
@@
 
-Note that the two forecasts do not differ in their predictions for 
-$y_{1,t}$, $t = 1,\ldots T_1^*$. Instead, they only differ in predicting 
-$y_{1,T_1^*+1}$. Throughout the rest of this article we show that the donor pool of time series $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$ has 
-the potential to improve the forecasts for $y_{1, T_1^*+1}$ under  different 
-circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
+%Note that the two forecasts do not differ in their predictions for $y_{1,t}$, $t = 1,\ldots T_1^*$. Instead, they only differ in predicting $y_{1,T_1^*+1}$. 
+Throughout the rest of this article we highlight when the information from the time series donor pool, indexed by $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$, can be used to construct a shock effect estimator $\hat\alpha$ in which Forecast 2 beats Forecast 1 and vice-versa.
+We will consider the different dynamic panel models $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
 Improvement will be measured by assessing the reduction in risk that Forecast 2 offers over Forecast 1.
-We will return to the theoretical details of risk-reduction in Section \ref{properties}.
-
+We outline the theoretical details of risk-reduction in Section \ref{properties}.
 We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response.
-It is important to note that in general $\hat{\alpha}$ does not converge to $\alpha_1$ in any sense.
-Despite this shortcoming, adjustment of the forecast for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has the potential to lower forecast risk under several conditions corresponding to different estimators of $\alpha_1$.
-
-\subsection{Construction of shock effects estimators}
+It is important to note that, in general, $\hat{\alpha}$ does not converge to $\alpha_1$ in any sense.
+Despite this shortcoming, adjustment of the forecast for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has the potential to lower forecast risk under several conditions, and for several estimation techniques.
+
+\subsection{Shock effect estimators}
 \label{constructionofestimators}
@@
 First, we introduce the procedures of parameter estimation for $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}).
-For $i = 2, \ldots, n+1$, all parameters in this model will be estimated with ordinary least squares (OLS) using historical data of $t = 1, \ldots, T_i$.
-For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$.
-In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate of $\alpha_i$.
-Note that parameter estimation for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
-We emphasize that $\alpha_i$'s are random variables, but the OLS estimation is conditioned on the realizations from some distribution.
-
-Second, we introduce the candidate estimators for $\alpha_1$. Define the 
-adjustment estimator for time series $i=1$ by
+For $i = 2, \ldots, n+1$, all parameters in this model will be estimated via ordinary least squares (OLS) using historical data indexed by $t = 1, \ldots, T_i$.
+For $i = 1$, we estimate all the parameters, excluding $\alpha_1$, using OLS for time periods indexed by $t=1, \ldots, T_1^*$.
+Let $\hat{\alpha}_i$ be the OLS estimate of $\alpha_i$, $i = 2, \ldots, n+1$.
+Note that parameter estimation under $\mc{M}_1$ is the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
+We emphasize that the $\alpha_i$s are realizations from a random effects distribution, and that the OLS estimators $\hat\alpha_i$ assumes that these realized values are conditional fixed effects in an autoregressive model, as in \eqref{equation1} and \eqref{model2}.
+
+The candidate estimators for $\alpha_1$ are now introduced. Define the adjustment estimator for time series $i=1$ by 
 \begin{equation} \label{adjusted}
@@
 \end{equation}
-where the $\hat{\alpha}_i$'s in \eqref{adjusted} are OLS estimators of  
-the $\alpha_i$s for $i = 2, \ldots, n+1$.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
+We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
 the unknown $\alpha_1$ term for which no meaningful estimation information 
 otherwise exists. It is intuitive that $\hat{\alpha}_{\rm adj}$ should perform 
-well under $\mc{M}_1$ where we assume that $\alpha_i$'s share the same mean 
+well under $\mc{M}_1$ where we assume that $\alpha_i$s share the same mean 
 for $i= 1, \ldots, n+1$. However, it can also be shown that 
@@
 We also consider the inverse-variance weighted estimator 
-in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i=2, \ldots, n+1$. 
+in practical settings where the $T_i$s and $T_i^*$s vary greatly across $i=2, \ldots, n+1$. 
 The inverse-variance weighted estimator is defined as 
@@
 \end{align*}
-where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
-$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
-and $\mbf{M}_i$ is the design matrix for OLS with respect to time series 
-for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
-is required and the numerator and denominator terms are dependent in general.
-
-However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in 
-practical settings.
-We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ 
-and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of 
-$\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation 
-(see Section \ref{simulation}).
-
-We now motivate a weighted-adjustment estimator for model $\mc{M}_{21}$ 
-and $\mc{M}_{22}$. Our weighted-adjustment estimator is inspired by the 
-weighting techniques in synthetic control methodology (SCM) developed 
-in \cite{abadie2010synthetic}. 
-However, our weighted-adjustment estimator is not a causal estimator and 
-our estimation premise is a reversal of that in SCM. 
-Our objective is in predicting a post-shock response $y_{1,T_1^*+1}$ that is not yet 
-observed using other time series whose post-shock responses are observed.
-
-We use similar notation as that in \cite{abadie2010synthetic} to motivate our weighted-adjustment estimator. Consider a $\mbf{W} \in \R^n$ weight vector 
-$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 
-$i = 2, \ldots, n+1$. Construct
+where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, $\hat{\sigma}_i$ is the residual standard error from OLS estimation, and $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$.
+Note that since $\sigma$ is unknown, estimation is required and the numerator and denominator terms are dependent in general.
+However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in practical settings, especially when the $T^*_i$s very considerably.
+We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of $\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation (see Section \ref{simulation}).
+
+We now motivate a weighted-adjustment estimator appropriate for model $\mc{M}_{21}$ and $\mc{M}_{22}$.
+Our weighted-adjustment estimator is inspired by the weighting techniques in synthetic control methodology (SCM) developed in \cite{abadie2010synthetic}.
+However, our weighted-adjustment estimator is not a pure causal estimator, and our estimation premise is a reversal of the SCM context in \cite{abadie2010synthetic}.
+In our context, we predict the unobserved post-shock response $y_{1,T_1^*+1}$ (intervention is absent) using post-shock information from other time series whose post-shock responses are all observed (intervention is present).
+
+We use similar notation as that in \cite{abadie2010synthetic} to describe our weighted-adjustment estimator.
+Consider a $\mbf{W} \in \R^n$ weight vector $\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all $i = 2, \ldots, n+1$.
+Construct
 \begin{align*}
@@
 Therefore, $\mbf{W}^*$ should exist as long as $\mbf{X}_1$ falls in the convex hull of
- \begin{align*}
+$
    \left\{ \mbf{x}_{2, T_2^*+1}', \ldots, \mbf{x}_{n+1, T_{n+1}^*+1}' \right\}.
- \end{align*}
+$
 Our weighted-adjustment estimator will therefore perform well when the pool of time series posses similar covariates to the time series for which no post-shock responses are observed.
@@
 \end{align}
-\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
-so that (\ref{SCM}) holds approximately 
-and that weighted-adjustment estimation techniques of this form are not 
-appropriate when the fit is poor. 
-Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
-is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist.
-Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
+\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ in \eqref{W} so that (\ref{SCM}) holds approximately and that weighted-adjustment estimation techniques of this form are not appropriate when the fit is poor.
+Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed.
+Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact.
+Because the objective function is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist.
+The weighted-adjustment estimator for the shock effect $\alpha_1$ obtained from the weights $\mbf{W}^*$ is defined as
   \begin{align*}
@@
       w^*_2 & \cdots & w^*_{n+1}
-    \end{pmatrix}'.
-  \end{align*}
- We further define
-\begin{align*}
-  \mathbf{V} = (\mathbf{x}_{2, T_2^*+1}, \ldots,\mathbf{x}_{n+1, T_{n+1}^*+1}).
-\end{align*}
+    \end{pmatrix}',
+  \end{align*}
+and we further define
+$
+  \mathbf{V} = (\mathbf{x}_{2, T_2^*+1}, \ldots,\mathbf{x}_{n+1, T_{n+1}^*+1}) \in \R^{p \times n}.
+$
 \begin{prop}
-  \label{uniqueness} If $\mathbf{V}$ has full rank and it exists some $\mathbf{W}$ satisfies (\ref{SCM}), the solution to  (\ref{W}) is unique.
+  \label{uniqueness} If $\mathbf{V}$ has full rank then there exists some $\mathbf{W}^*$ that solves (\ref{SCM}) and this solution is unique.
 \end{prop} 
 Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.
-Note that $\mathbf{V}$ is $p \times n$.
-Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $p \geq n$.
-However, when $p < n$, $\mathbf{W}^*$ may not be unique.
-If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $p < n$, there are infinitely many solutions to (\ref{SCM}).
-The issue of non-uniqueness is further discussed in Section \ref{varbootstrap}.
+If $\mathbf{V}$ is full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is when $p \geq n$ in our setting.
+Non-uniqueness might be a concern theoretically.
+This is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$s, all targeting $\alpha_1$.
+For example, consider the case when $n = 2$, we have $\var{\hat{\alpha}_2}=1$ and $\var{\hat{\alpha}_3}=2$, the covariates are such that $\x_1 = \x_2 = \x_3$, and we consider $\mathbf{W}^*_1=(1,0)$ and $\mathbf{W}^*_2=(0,1)$ as solutions to \eqref{W}.
+In this hypothetical, the weighted adjustment estimator constructed from $\mathbf{W}^*_1$ has variance 1 whereas the same quantity constructed from $\mathbf{W}^*_2$ has variance 2.
+It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}).
+Empirically, we find some simulation evidence that non-uniqueness of $\mathbf{W}^*$ is not problematic for inferences in our setting.
+Specifics can be seen in Section 4 of the Supplementary Materials.
+We close this Section with some remarks about our shock-effect estimators:
 
@@
 
-\section{Forecast risk and properties of shock effects estimators}
+\section{Forecast risk, risk-reduction, and properties of shock effects estimators}
 \label{properties}
 
-In this section, we discuss the properties that are related to forecast-risk reduction.
-In discussion of risk, it is useful to derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.
+In this section, we discuss the properties that are related to forecast risk-reduction.
+It is useful to first derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.
 The expressions for the expectations are as follow,
@@
 
-The shock effects $\alpha_i$'s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
+The shock effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
 However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
@@
 We caution that the bootstrapping residuals in OLS estimation may not provide valid inference in moderate or high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}; see alternatives for residual bootstrapping in linear models in \citet{el2018can}.
-
-Recall that $\mathbf{W}^*$  may not be unique if the conditions in Proposition \ref{uniqueness} are not satisfied.
-Non-uniqueness might be a concern theoretically.
-This is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$'s all targeting on the same $\alpha_1$.
-For example, consider the case where the size of  donor pool to be 2, $\var{\hat{\alpha}_2}=1$, $\var{\hat{\alpha}_3}=2$, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$.
-In this scenario, the weighted adjustment estimator induced by $\mathbf{W}^*_1$ has variance 1 whereas the one by $\mathbf{W}^*_2$ has variance 2.
-Nevertheless, even if $\hat{\alpha}_i$ has the same variance across $i = 2, \ldots, n+1$, the same issue would occur if there were infinitely many $\mbf{W}^*$ with different norms.
-It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}).
-Simulations in the Section 4 of the Supplementary Materials provide some evidence that non-uniqueness of $\mathbf{W}^*$ is not problematic for inferences.
 
@@
 We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}.
-Parameter setup of our simulations is detailed as follows: the $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.
-We sampled $T_i$'s independently from  $\text{Gamma}(15, 10)$ that are further rounded to integers, where the minimum allowable value of $T_i$ is fixed to be 90.
+Parameter setup of our simulations is detailed as follows: the $\phi_i$s are sampled independently from $\mrm{Uniform}(0,1)$.
+We sampled $T_i$s independently from  $\text{Gamma}(15, 10)$ that are further rounded to integers, where the minimum allowable value of $T_i$ is fixed to be 90.
 We will randomly draw $T_i^*$ from $\{p + 4, \ldots, T_i-1\}$.
@@
 We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population in these simulations.
-Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$.
+Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions $\mathbf{W}^*$.
 In this scenario, $\mathbf{W}^*$ will take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$.
+When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ that satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$.
 However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
-Moreover, simulations in Section 4 of the Supplementary Materials show that non-uniqueness does not seriously compromise the inference.
-
-In summary, $\mathcal{B}_u$ is preferred when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is believed to be large.
-If $p < n$ and non-uniqueness problem is of concern due to theoretical reasons,  $\mathcal{B}_f$ is preferred.
-In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.
+Empirically, simulations in Section 4 of the Supplementary Materials show that non-uniqueness does not seriously compromise inferences under $\mc{B}_u$.
+
+Our simulations provide some empirical evidence that $\mathcal{B}_u$ is preferred when the donor pool size is moderately small ($n< 10$) and the signal from the covariates is believed to be large.
+If $p < n$ and non-uniqueness problem is of concern for theoretical reasons,  $\mathcal{B}_f$ may be preferred.
+In most cases, the choice between $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to the philosophical differences between these bootstrap procedures.
 
@@
 These examples provide empirical illustration of our methodology in settings where the shock is, respectively, unprecedented and with precedent.
-\textcolor{red}{The adjusted forecast in Section \ref{forecasting} performs much better than original forecast whereas the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.}
+The adjusted forecast in Section \ref{forecasting} performs much better than the unadjusted original forecast, and the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.
 
@@
 In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}.
-These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Mac in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}.
+These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Macbook in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}.
 The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}.
@@
 Typically, after the release, the stock price of Apple Inc.
-is expected to experience a shock since Mac sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced.
-For example, the sales of Mac account for 9.8\% of its revenue \citep{applemac}.
+is expected to experience a shock since Macbook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced.
+For example, the sales of Macbooks account for 9.8\% of its revenue \citep{applemac}.
 In this example, we are interested in forecasting the stock price of Apple Inc.
-near the release of MacBook series on November, 10th, 2020.
-In particular, in recent years, we observe that it usually takes two or more than two days for the shock to take effect on the stock price in the case of Apple Inc.
+after the release of the latest MacBook on November, 10th, 2020.
+In recent years, we observe that it takes two or more days (\red{Why is it two or more days and not just two days?
+How can we be certain that we want the shock effect on November 11th instead of November 12th or some later date?}) for the shock to take effect on the stock price.
 Therefore, we are interested in the stock price of Apple Inc.
@@
 All the estimates will be adjusted for inflation.
-Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$ in replace of the one in Section \ref{modelsetup}.
-As a result, a generalized weighting of Section \ref{constructionofestimators} is used.
-To be specific, we mean
+Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$.
+As a result, we consider weighting with respect to
   \begin{align*}
@@
   \end{align*}
-  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ stands for the covariates from time $t = T_i^* +1$ to $t = T_i^*+2$. The model $\mc{M}_2$ is then generalized to 
+  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ denotes the matrix joining both covariate column vectors corresponding to time points $t = T_i^* +1$ and $t = T_i^*+2$.
+\red{You need to define the space of possible values for possible weighs in this new context, it is not immediately clear what you did.} The model $\mc{M}_2$ is then changed to
   \begin{align*}
@@
   \end{align*}
-  where $\delta_i$ is $p \times 2$. The weighting method in Section \ref{constructionofestimators} and the corresponding properties  still follow.
+  where $\delta_i \in \R^{p \times 2}$.
+\red{The above does not make sense, $\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}$ is not a scalar, and $y_{i,t}$ is not a vector, right?
+It seems that, as currently written, $\alpha_i$ should be replaced by $\alpha_{i,t}$, for $t = T^*+1, T^*+2$, where it is understood that $\alpha_{i,T^*+1}$ is close to zero.
+But I am not even sure if that is correct, why is the shock effect for the irrelevant nuisance next day response even considered at all?
+What did you actually do here?}
   \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates.
@@
 As a result, forecasting of future covariates is needed.
-We used AIC to select AR(3) for S\&P 500 index prices and AR(1)  for 13 Week treasury bill rates.
+We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates.
 We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models.
-Then, we use 1-ahead forecasts to predict the future covariates.
+We then predict the future covariates.
   \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc.
-with shock-effect date as  in the middle of 15 trading days for 2017, 2018, and 2019.
-The shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively.
-Those dates are the past dates when Apple Inc.
-introduced new series of MacBook computers in the corresponding year.
+with shock-effect date in the middle of 15 trading days for 2017, 2018, and 2019.
+The specific shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively.
+We only include the last three Macbook releases in our donor pool because those releases are similar to the current release in the sense that Apple inc.
+has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019, apple2020}.
+%The new MacBook series is built with M1 chip invented by Apple inc.
+instead of chips by Intel inc.
+that were used in past years, and their CPU speed improves significantly \citep{apple2020}.
 \end{enumerate}
@@
 We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
-As a result, we observe $\mathbf{W}^* = (0.664, 0.000, 0.336)$ and $
-  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.674.
-$ It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.
-
+As a result, we observe $\mathbf{W}^* = (0.664, 0.000, 0.336)$ \red{It is still a little confusing where this came from since it is not defined in this setting.} and $
+  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.674$.
+It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.
 The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.071$, $\hat{\alpha}_{\rm wadj}=1.066$, and $\hat{\alpha}_{\rm IVW} = 1.090$.
@@
 Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk.
+As we can see from Figure \ref{Fig3}, the post-shock forecasts perform well.
+The unadjusted forecast misses the post-shock by 1.518 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.447, 0.427, and 0.452 dollars, respectively.
+Note  that the 1-ahead forecast error for the covariates contribute to some of the forecast risk.
 
@@
 \end{figure*}
-
-As we can see from Figure \ref{Fig3}, the post-shock forecasts perform nearly perfectly.
-The unadjusted forecast misses the post-shock by 1.518 dollars.
-The use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ miss by 0.447, 0.427, and 0.452 dollars, respectively.
-\textcolor{red}{In other words, the forecasts induced by $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are very close to the true response.
-Note  that the 1-ahead forecast error for the covariates contribute to some of the forecast risk.} Beyond that, it implies that the construction of donor pool is successful.
-To explain, it appears as a trend that in recent 3 years, Apple inc.
-only updates the hardware of the MacBook series in the release of every year without much redesign, and improves the their hardware performance significantly \citep{apple2017, apple2018, apple2019} .
-It is the case for the release in 2020 as well.
-The new MacBook series consider M1 chip invented by Apple inc.
-itself in replace of chips by Intel inc.
-in the past years, and their CPU speed improves significantly; the M1 chip enables  Mac users to use the apps developed in iPhone and thus run a greater range of applications than before \citep{apple2020}.
-Therefore, in this example, our analysis is similar to \cite{baumeister2014real} in that the  forecast is conditioned on past shocks and the shock is within the range of historical experience.
-In other words, the shock in this example is not unprecedented.
 

### 2021-01-09 Revision/manuscript.tex
finished round of revisions

@@
 \cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses.
-\red{ I do not understand what this means, please clarify: Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}
+\red{ I do not understand what the following means, please clarify: Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}
 
@@
 It is useful to first derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.
-The expressions for the expectations are as follow,
+The expressions for the expectations are as follows:
 
@@
   \end{enumerate}
-Formal justification for these results can be found in Appendix.
+Formal justification for these results can be found in the Appendix.
 Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$.
 However, under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$.
-Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$.
-We collect these results in the following proposition.
+Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$.
+On the other hand, $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$.
+We collect these results in the following proposition:
 
@@
 
-Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation for evaluation of these conditions.
-These conditions and bootstrap will be discussed in Section \ref{conditions} and \ref{varbootstrap}, respectively.
-Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below.
+Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation procedure for evaluation of these conditions, discussed in Section \ref{conditions} and \ref{varbootstrap} respectively.
+Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:
 
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}\\
-\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}, \\
+\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.
 \end{align*}
@@
 \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})\\
+  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}),\\
   \var{\hat{\alpha}_{\rm wadj}} 
@@
 \end{enumerate}
-Formal justification for these results can be found in Appendix in Section \ref{proofs}. Note that the variances are not comparable in closed-form 
-because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}.
+Formal justification for these results can be found in Section \ref{proofs} of the Appendix.
+Note that the variances are not comparable in closed-form because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}.
 This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
@@
 Recall that Proposition \ref{unbiased} implies that the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ are unbiased for $\E{\alpha_1}$ under $\mc{M}_1$.
-With this result, we will have  the following propositions that specify the conditions that are necessary for risk reduction.
+With this result, we will have  the following proposition that specify the conditions that are necessary for risk reduction:
 
@@
 
-Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$ (see Forecast in Section \ref{forecast}); (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
+Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$; (2) In the finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
 
@@
 The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.
-Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally.
+Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ in general.
 Hence, Proposition \ref{proprisk} no longer holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.
 
-As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting.
-By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
+As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting. By Lemma \ref{risklemma}, we will achieve risk-reduction when
 \begin{align*}
@@
 We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$.
-That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
+We can adapt the above to derive a risk-reduction condition for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
 In fact, more generally, using similar proof of Lemma \ref{risklemma}, it can be shown that under $\mc{M}_2$, the risk-reduction quantities are
@@
   \Delta(\hat{\alpha}_{\rm wadj}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}},
-\end{align*}
-where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using bootstrap and leave-one-out cross validation procedures developed in Sections \ref{varbootstrap} and \ref{loocv}.
+  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}.
+\end{align*}
+We estimate $\Delta(\hat{\alpha})$ using bootstrap and leave-one-out cross validation procedures developed in Sections \ref{varbootstrap} and \ref{loocv}.
 
@@
 Therefore, there is no resampling of the donor pool in $\mc{B}_f$, it is otherwise similar to $\mc{B}_u$.
-An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in Section 2 in the Supplementary Materials.
+An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in Section 2 of the Supplementary Materials.
 
@@
 
-In this section, we adapt leave-one-out cross validation (LOOCV) to our estimation context in order to provide prospective evaluations of our adjustment techniques.
+In this section, we motivate a leave-one-out cross validation (LOOCV) procedure within our estimation context in order to provide prospective evaluations of our adjustment techniques.
 Our proposed LOOCV procedure has its roots in Section 7.10 of \citet{hastie2009elements}.
-Recall in Section \ref{modelsetup} that we are given the data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining observations form the donor pool.
+Recall in Section \ref{modelsetup} that we have data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining observations form the donor pool.
 For iteration $m \in \{1,\ldots,n\}$ of our LOOCV procedure, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}_m, t = 1, \ldots, T_{i}\}$, where $\mc{I}_m=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, we can evaluate the performance of our adjustment estimators and the original forecast made without adjustment (i.e., Forecast 1 in Section \ref{forecast}).
+Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, we can evaluate the performance of our adjustment estimators and the original forecast made without adjustment.
 
 LOOCV can be very computationally intensive when $n$ is large, especially when combined with bootstrapping.
-To alleviate these concerns we can perform LOOCV with a random subset of $k \leq n$ iterations selected without replacement.
+To alleviate these concerns, one can perform LOOCV with a random subset of $k \leq n$ iterations selected without replacement.
 In this setting, we let $\mc{J}$ be the randomly sampled indices.
@@
 We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}.
-Parameter setup of our simulations is detailed as follows: the $\phi_i$s are sampled independently from $\mrm{Uniform}(0,1)$.
-We sampled $T_i$s independently from  $\text{Gamma}(15, 10)$ that are further rounded to integers, where the minimum allowable value of $T_i$ is fixed to be 90.
-We will randomly draw $T_i^*$ from $\{p + 4, \ldots, T_i-1\}$.
+The parameter setup of our simulations is detailed as follows:
+\begin{align*}
+  \phi_i &\simiid U(0,1),	\\
+  \delta_i &\simiid  \normal{1}{0.5}, \\
+  \theta_i &\simiid \normal{0}{1}, \\
+  \alpha_i &\simiid \normal{\mu_\alpha}{\sigma_{\alpha}^2}, \\
+  T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
+  T_i^* &\simiid U(p+4, T_i-1), \\
+  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2}
+\end{align*}
+where the $[\cdot]$ operation in the generation of the $T_i$s corresponds to rounding the input to the nearest integer and the discrete uniform distribution is used to generate the $T_i^*$s.
 The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
 Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
-Additionally, we generated the covariates from $\text{Gamma}(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.
-Last, we set $\delta_i\simiid  \normal{1}{0.5}$ and $\theta_i \sim \normal{0}{1}$.
+Additionally, we generated all of the entries of the covariate vectors to be realizations from a $\text{Gamma}(1,2)$ distribution.
+
 We will consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
-We choose a Monte Carlo sample size of $30$ replications and a bootstrap sample size of $B = 200$ for computation.
+We choose a Monte Carlo sample size of $30$ replications and a bootstrap sample size of $B = 200$ for our computations.
 Means and standard errors for estimated quantities will be recorded.
@@
 In the second simulation setup, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n=10$.
-Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.
+Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates ranges from strong to nearly nonexistant.
 Results are  in Table~\ref{table2} in the Appendix, Section \ref{tablesappendix}.
 
-First, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we  observe from Table \ref{table1} that the decision making of $\delta_{\hat{\alpha}}$ is nearly correct  for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small  from Table \ref{table1}.
-The reasons can be explained as follows.
-When $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal according to construction of $\hat{\alpha}_{\rm wadj}$ in Section \ref{constructionofestimators}.
-Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
+First, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we  observe from Table \ref{table1} that the decision making using $\delta_{\hat{\alpha}}$ is nearly correct for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small.
+The reasons can be explained as follows: When $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal according to construction of $\hat{\alpha}_{\rm wadj}$ in Section \ref{constructionofestimators}.
+Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ and $\mc{M}_{21}$ are very similar and estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
 However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is large), the decision rule $\delta_{\hat{\alpha}}$  becomes unreliable for $\hat{\alpha}\in \mc{A}$.
-It is to be expected since the bootstrap estimates become more biased.
-However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$.
-Second, fixing $\sigma_{\alpha}$, we can observe that the correctness of $\delta_{\hat{\alpha}}$ increases when $n$ increases.
-It is due to the robustness gain in estimation when $n$ increases.
-
-Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down, though they  follow similar patterns.
+This is to be expected since the bootstrap estimates become more biased.
+However, users are warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ and they have an idea of the effectiveness of $\delta_{\hat{\alpha}}$.
+Second, fixing $\sigma_{\alpha}$, we can observe that the rate in which we make correct decisions, $\delta_{\hat{\alpha}}$, increases when $n$ increases.
+
+Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports that $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down.
 Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$.
@@
 
-From columns related to distance to $y_{1, T_1^*+1}$ in Table \ref{table1}, as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
+In the last four columns of Table~\ref{table1} we can see that as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
 When $\sigma_{\alpha}= 5, 10, 25$, forecasts using $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are always better than the original forecast significantly.
-But it does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
-It is reasonable in that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
-Nevertheless, no statistical evidence has been found to support the claim that $n$ matters in prediction.
-In other words, the size of the donor pool matters for producing reliable decision-making of $\delta_{\hat{\alpha}}$ rather than reliable prediction.
-
-From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$   decreases, which is a pattern similar to the one shown in the first experiment.
-Furthermore, as $\sigma$ increases fixing $\sigma_{\alpha}$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases as well.
-Note that the correctness  hinges on the estimation of the parameters.
+This does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
+It is reasonable that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
+Nevertheless, no Monte-Carlo evidence has been found to support the claim that $n$ plays a large role prediction.
+
+From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases with $\sigma$ fixed, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases.
+Furthermore, as $\sigma$ increases we have that $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases as well.
+Note that decision making ability hinges on the estimation of the parameters.
 Since $\hat{\alpha}_{\rm wadj}$  is a linear combination of OLS estimates, as $\sigma$ increases, $\var{\hat{\alpha}_{\rm wadj}}$ increases as well.
@@
 
-With respect to averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases.
+The averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ (i.e., the guess) starts to decrease as $\sigma$ increases.
 This is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
@@
 See Table \ref{table3} and Table \ref{table4} for results in the Appendix, Section \ref{tablesappendix}.
-Comparing Table \ref{table1}
- and Table \ref{table2} yields that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_f$ with statistical evidence.
-For other situations, $\mc{B}_u$  and $\mc{B}_f$  are rather similar.
-It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool.
+From Table \ref{table1} and Table \ref{table3} we have that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is preferable to $\mc{B}_f$.
+For other situations, $\mc{B}_u$  and $\mc{B}_f$ perform similarly.
+It is likely that the extra randomness from sampling the donor pool with replacement compensates for the possible noises from a small donor pool.
 Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
@@
 
- Simulation results corresponding to model $\mc{M}_1$ are listed in Section 3 in Supplementary Materials.
-Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$, except for the difference among estimators.
-The results show that (1) the performance of $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are nearly the same and (2) in many situations, $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are  better than $\hat{\alpha}_{\rm wadj}$; in other situations, they are mostly the same.
+ Simulation results corresponding to model $\mc{M}_1$ are listed in Section 3 in the Supplementary Materials.
+Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$.
+The results show that: (1) the performance of $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are nearly the same and (2) in many situations, $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are  better than $\hat{\alpha}_{\rm wadj}$; in other situations, they are mostly the same.
 Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
@@
 
-We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population in these simulations.
+In these simulations we have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.
 Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions $\mathbf{W}^*$.
@@
 
-Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its first and second moments exist.
+Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its second moments exist.
 The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
@@
 
-Construction of donor pool is a critical step that directly matters in prediction.
+Construction of the donor pool is a critical step that directly matters in prediction.
 In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for  varying variances and  varying means that are linear functions of common covariates.

### 2021-01-10 Revision/manuscript.tex
feedback to comments

@@
 \cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses.
-\red{ I do not understand what the following means, please clarify: Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}
+\red{Please clarify:...} \textcolor{blue}{Our shock effect of interest is similar to innovational  outliers  in the sense that it is an additive effect in the model of response only at a particular time point but it impacts the subsequent responses through an autoregressive structure.}
 
@@
 In recent years, we observe that it takes two or more days (\red{Why is it two or more days and not just two days?
-How can we be certain that we want the shock effect on November 11th instead of November 12th or some later date?}) for the shock to take effect on the stock price.
+\textcolor{blue}{It took two trading days for shock effects for 2017 and 2018 but 6 trading days for 2019.} How can we be certain that we want the shock effect on November 11th instead of November 12th or some later date?} \textcolor{blue}{We cannot know how long it took for the shock effect in 2020 to take an effect.
+From the past data (i.e., data in 2017 and 2018), I think 2 trading days are a safe guess.}) for the shock to take effect on the stock price.
 Therefore, we are interested in the stock price of Apple Inc.
@@
   where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ denotes the matrix joining both covariate column vectors corresponding to time points $t = T_i^* +1$ and $t = T_i^*+2$.
-\red{You need to define the space of possible values for possible weighs in this new context, it is not immediately clear what you did.} The model $\mc{M}_2$ is then changed to
+\red{You need to define the space of possible values for possible weighs in this new context, it is not immediately clear what you did.} \textcolor{blue}{In this case, $\mathcal{W}= \{\mathbf{W}\in [0,1]^n\colon 1_n'\mathbf{W}=1\}$ and we aim to find $\mathbf{W}^*\in \mathcal{W}$ with $\mathbf{W}^*=(w_2^*,\ldots, w_{n+1}^*)'$ such that }
+  \begin{align*}
+    \textcolor{blue}{\mathbf{x}_{i, T_i^*+1:T_i^*+2}=\sum_{i=2}^{n+1}w_i^*\mathbf{x}_{i, T_i^*+1:T_i^*+2}}.
+  \end{align*} 
+  \textcolor{blue}{and $\mathbf{W}^*$ is estimated by}
+  \begin{align*}
+ \textcolor{blue}{\mathbf{W}^*= \argmin_{\mathbf{W}\in \mathcal{W}} \left\| \mathbf{x}_{i, T_i^*+1:T_i^*+2}-\sum_{i=2}^{n+1}w_i^*\mathbf{x}_{i, T_i^*+1:T_i^*+2} \right\|_{2p}.}
+  \end{align*}
+The model $\mc{M}_2$ is then changed to 
   \begin{align*}
@@
   y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
-  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}+ \t{\varepsilon}_{i},
+  \; \textcolor{red}{\alpha_i 1_2= \mu_{\alpha}1_2+\mbf{x}_{i, T_i^*+1:T_i^*+2}'\delta_{i}+ \t{\varepsilon}_{i}1_2},
 \end{array}
   \end{align*}
-  where $\delta_i \in \R^{p \times 2}$.
+  where \textcolor{red}{$\delta_i \in \R^{p \times 1}$ is not assumed to be random}.
 \red{The above does not make sense, $\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}$ is not a scalar, and $y_{i,t}$ is not a vector, right?
@@
 But I am not even sure if that is correct, why is the shock effect for the irrelevant nuisance next day response even considered at all?
-What did you actually do here?}
+What did you actually do here?
+\textcolor{blue}{I change the model accordingly where we cannot assume $\delta_i$ is random anymore in this context and it has to be particular $\delta_i$ such that the model holds.
+It is also possible that  we can use $\alpha_{i,t}$.
+By taking it two days to take effect, I mean $\alpha_{i, T_i^*+1}$ is small but not close to zero and it should be taken into consideration together with $\alpha_{i, T_i^*+2}$.
+I personally prefer $\alpha_i$ instead of $\alpha_{i,t}$ since $\alpha_i$ is more intuitive  in that there is only one gross shock effect.
+Or, there is another possible approach.
+Recall that we can use different covariates in the model of $\alpha_i$  and in the model of $y_{i,t}$.
+So, we can only use $\mathbf{x}_{i, T_i^*+1}$ to construct the weights.
+Please let me know what you think and which model you prefer.}}
   \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates.

### 2021-01-11 Revision/manuscript.tex
made minor changes to manuscript; added to the organization of Section 4

@@
   \phi_i &\simiid U(0,1),	\\
-  \delta_i &\simiid  \normal{1}{0.5}, \\
+  \delta_i &\simiid  \normal{1}{0.5^2}, \\
   \theta_i &\simiid \normal{0}{1}, \\
@@
   T_i^* &\simiid U(p+4, T_i-1), \\
-  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2}
+  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2},
 \end{align*}
@@
 We discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities.
-We mainly discuss simulations under $\mc{M}_2$ (see Section \ref{modelsetup}) for $\mc{B}_u$ and $\mc{B}_f$ (see Section \ref{varbootstrap}) with comparisons to those under $\mc{M}_1$ whose results are listed in Section 3 in the Supplementary Materials.
-Two simulation setups are investigated.
-
-In the first simulation setup, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$.
+We mainly discuss simulations under model $\mc{M}_2$ and both bootstrap procedures, $\mc{B}_u$ and $\mc{B}_f$.
+Complementary simulations under $\mc{M}_1$ are provided in Section 3 of the Supplementary Materials.
+We now present the two simulation setups that are investigated in the main text.
+
+In the first simulation setup we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$.
 Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates.
@@
 
-Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented.
+\subsection{Additional considerations}
+\label{parametricbootstrapsimulation2}
+
+We now present results from simulations under bootstrap procedure $\mc{B}_f$ under the same two parameter setups considered above.
 See Table \ref{table3} and Table \ref{table4} for results in the Appendix, Section \ref{tablesappendix}.

### 2021-01-19 Revision/list.tex
revised manuscript and feedback to comments

@@
 The labels (a) and (b) are now added in the revised manuscript.
-The \textcolor{black}{black} line stands for the realized observations whereas the \textcolor{magenta}{magenta} line stands for the fitted values.} \\
+The \textcolor{black}{black} line stands for the realized observations whereas the violet line stands for the fitted values.} \\
 
@@
 
-\response{Thanks for pointing it out.
-We  clarify this in the revised version.
-The black dots represent the real data.
-The line in \textcolor{magenta}{magenta} color represents the fitted line of our model.}
+\response{Thanks for pointing it out. We  clarify this in the revised version. The black dots represent the real data. The line in violet color represents the fitted line of our model.}
 
@@
 It is possible to generalize our method to this situation.
-\\
+\textcolor{red}{Our new Apple example in Section 5.2 of the revised manuscript provides an example for the case $d=2$ with predicted covariates.}\\
 
@@
 
-\response{There are mainly three decisions to make for an user: to choose 
+\response{\textcolor{red}{Thank you for pointing it out.
+We repolished Section 4 for better readability in the revised manuscript.} \textcolor{red}{We  summarize  our results including preferred user decisions as below.
+}There are mainly three decisions to make for an user: to choose
   \begin{itemize}

### 2021-01-19 Revision/manuscript.tex
revised manuscript and feedback to comments

--- 2021-01-09 Revision/manuscript.tex
@@
 \cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses.
-\red{ I do not understand what the following means, please clarify: Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}
+Our shock effect of interest is similar to innovational  outliers  in the sense that it is an additive effect in the model of response only at a particular time point but it impacts the subsequent responses through an autoregressive structure.
 
@@
   T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
-  T_i^* &\simiid U(p+4, T_i-1), \\
-  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2}
-\end{align*}
-where the $[\cdot]$ operation in the generation of the $T_i$s corresponds to rounding the input to the nearest integer and the discrete uniform distribution is used to generate the $T_i^*$s.
+  T_i^* &\simiid \red{U\{p+4, T_i-1\}}, \\
+  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2},
+\end{align*}
+where the $[\cdot]$ operation in the generation of the $T_i$'s corresponds to rounding the input to the nearest integer, \red{$U(a,b)$, $U\{a,b\}$, and $\mrm{Gamma}(c,d)$  stands for a random variable from continuous uniform distribution on the closed interval from $a$ to $b$, discrete uniform distribution on the set of integers from $a$ and $b$, and Gamma distribution with shape parameter $c$ and scale parameter $d$, respectively}.
 The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
@@
 These examples provide empirical illustration of our methodology in settings where the shock is, respectively, unprecedented and with precedent.
-The adjusted forecast in Section \ref{forecasting} performs much better than the unadjusted original forecast, and the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.
+\textcolor{red}{Generalizations of our method are discussed as well.
+Section \ref{forecasting} allows the shock effect to be decomposed into separable estimable parts,  multiple shock effects to be nested in a time series, and different models for the response and the shock effects.
+Section \ref{apple} extends the forecasting adjustment at $T_1^*+1$ to $T_1^*+2$, and considers  a different model of the time series of interest  to that of   donor pool.
+In terms of the results, the adjusted forecast in Section \ref{forecasting} performs much better than the unadjusted original forecast, and the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.}
 
@@
 Our donor pool consists of Conoco Phillips shock effects observed in the past.
-We consider shock effects which occurred on March 14, 2008, several days in September, 2008, and November 27, 2014.
+We consider shock effects which occurred on March 15, 2008, several days in September, 2008, and November 27, 2014.
 The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession.
@@
     \includegraphics[height = 9cm]{FIG2.pdf}
-    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. Black dots and magenta line represent real data and fitted line, respectively.}
+    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. Black dots and violet line represent real data and fitted line, respectively.}
     \label{Fig:CP}
@@
 after the release of the latest MacBook on November, 10th, 2020.
-In recent years, we observe that it takes two or more days (\red{Why is it two or more days and not just two days?
-How can we be certain that we want the shock effect on November 11th instead of November 12th or some later date?}) for the shock to take effect on the stock price.
-Therefore, we are interested in the stock price of Apple Inc.
-on the day after the release date, i.e., on November 11th, 2020.
-The detailed considerations of our analysis are outlined as below.
+\textcolor{red}{From knowledge from our donor pool (see  (3) Construction of donor pool below), we observe that it takes two days for the shock effect to take hold.} Therefore, we are interested in the stock price of Apple Inc.
+on the day after the release date, i.e., on November 11th, 2020, \red{when we conjecture that the time series of interest would experience a shock}.
+\red{We collect our data through   \texttt{quantmod} package \citep{ryan2017quantmod} in R.} The detailed considerations of our analysis are outlined as below.
 
 \begin{enumerate}[label = (\arabic*)]
-  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc.
-We consider 20 trading days data for the time series of interest and time series in the donor pool.
+  \item \red{\textbf{Selection of model.}}  We use an AR(1) model to forecast the stock price of Apple Inc.
 All the estimates will be adjusted for inflation.
-Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$.
-As a result, we consider weighting with respect to
-  \begin{align*}
-    \mathbf{X}_1 = \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \quad \text{ and } \quad 
-    \mathbf{X}= \begin{pmatrix}
-      \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
-    \end{pmatrix},
-  \end{align*}
-  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ denotes the matrix joining both covariate column vectors corresponding to time points $t = T_i^* +1$ and $t = T_i^*+2$.
-\red{You need to define the space of possible values for possible weighs in this new context, it is not immediately clear what you did.} The model $\mc{M}_2$ is then changed to
-  \begin{align*}
-    \mc{M}_2 \colon \begin{array}{l}
-  y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
-  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}+ \t{\varepsilon}_{i},
-\end{array}
-  \end{align*}
-  where $\delta_i \in \R^{p \times 2}$.
-\red{The above does not make sense, $\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}$ is not a scalar, and $y_{i,t}$ is not a vector, right?
-It seems that, as currently written, $\alpha_i$ should be replaced by $\alpha_{i,t}$, for $t = T^*+1, T^*+2$, where it is understood that $\alpha_{i,T^*+1}$ is close to zero.
-But I am not even sure if that is correct, why is the shock effect for the irrelevant nuisance next day response even considered at all?
-What did you actually do here?}
+We consider $D_{i, t} = I(t = T_i^*+2)$.
+By observing  the data, we found a large shock effect on October 10th, 2020, two days before the release of iPhone 12, iPhone 12 Pro, MagSafe accessories, and HomePod mini.
+Denote this date by $T_{1,\#}$, and the shock effect by $\beta$.
+We account for this shock effect that is not of our interest in the model by setting
+  \begin{align*}
+    y_{1,t} &= \eta_i + \alpha_1 D_{1,t} +\phi_1y_{1, t-1}+\theta_1'\mathbf{x}_{1,t} + \beta I(t = T_{1,\#}) + \varepsilon_{i,t}.
+  \end{align*}
+  The model for $y_{i,t}$ is the same as in Section \ref{modelsetup} for $i = 2, \ldots, n+1$.   The model for the shock effect is
+  \begin{align*}
+    \alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{i,T_i^*+2}  + \tilde{\varepsilon}_{i,t}.
+  \end{align*}
+  Then, the weighting schemes introduced in Section \ref{constructionofestimators} will use  $\{\mathbf{x}_{i,T_i^*+2} \colon i = 1, \ldots, n+1\}$ for computing $\mathbf{W}^*$, where $\mathbf{x}_{1, T_1^*+2}$ will require prediction as detailed in (2) Selection of covariates.
+We used mean squared error for the response in the training data to select an appropriate time length out of 20, 25, 30, and 50 trading days.
+As a result, we consider 25 trading days data for the time series of interest and time series in the donor pool.
   \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates.
@@
   \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc.
-with shock-effect date in the middle of 15 trading days for 2017, 2018, and 2019.
-The specific shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively.
-We only include the last three Macbook releases in our donor pool because those releases are similar to the current release in the sense that Apple inc.
-has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019, apple2020}.
+with shock-effect date in the middle of \red{25} trading days for 2017, 2018, and 2019.
+The specific shock-effect dates are June 6th, 2017, October 30th, 2018, and June 3rd, 2019, respectively.
+We only include the last three Macbook releases in our donor pool because \red{we conjecture that} those releases are similar to the current release in the sense that Apple inc.
+has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019}; \red{and it is indeed consistent \citep{apple2020}}.
 %The new MacBook series is built with M1 chip invented by Apple inc.
@@
 The covariates and response of time series in the donor pool are adjusted for inflation.
-The estimated shock effects $\alpha_i$ are $0.864, 0.905, 1.129$ for $i = 2, 3, 4$, respectively.
+The estimated shock effects $\alpha_i$ are $0.686, 1.688, 1.393$ for $i = 2, 3, 4$, respectively.
 We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
-As a result, we observe $\mathbf{W}^* = (0.664, 0.000, 0.336)$ \red{It is still a little confusing where this came from since it is not defined in this setting.} and $
-  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.674$.
+As a result, we compute $\mathbf{W}^* = (0.712, 0.000, 0.288)$ and $
+  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 2.422$.
 It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.
-The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.071$, $\hat{\alpha}_{\rm wadj}=1.066$, and $\hat{\alpha}_{\rm IVW} = 1.090$.
-The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.192$, $0.095$, and $0.091$, respectively.
+The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.256$, $\hat{\alpha}_{\rm wadj}=0.889$, and $\hat{\alpha}_{\rm IVW} = 0.951$.
+The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.245$, $0.134$, and $0.133$, respectively.
 Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk.
 As we can see from Figure \ref{Fig3}, the post-shock forecasts perform well.
-The unadjusted forecast misses the post-shock by 1.518 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.447, 0.427, and 0.452 dollars, respectively.
-Note  that the 1-ahead forecast error for the covariates contribute to some of the forecast risk.
+The unadjusted forecast misses the post-shock by 0.799 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.457, 0.090, and 0.152 dollars, respectively.
+\red{It appears that covariates weighting with $\hat{\alpha}_{\rm wadj}$ is more successful.
+It is possible that $\mc{M}_2$ is a good fit for the data.
+Note  that the 1-ahead forecast error for $y_{1, T_1^*+1}$ and the covariates contribute to some of the forecast risk.}
 
@@
     \includegraphics[height = 9cm]{FIG3.pdf}
-    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and magenta line represent real data and fitted line, respectively.}
+    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and violet line represent real data and fitted line, respectively.}
     \label{Fig3}
@@
 The model, under which we verify these claims, is a simple AR(1) model.
-Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
+Similar results can be obtained for more general models \red{whose parameter can be estimated unbiasedly}.
+%such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
 Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
@@
 We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.
+\red{The Apple example illustrates the case when $d = 2$ with predicted covariates, where the prediction error for covariates and response can contribute to the post-shock forecast risk.}
 

### 2021-01-22 Revision/list.tex
finished round of revisions

@@
 
-\response{We include another example of forecasting the stock price of Apple Inc.
-during MacBook release in 2020 in Section 5.2 of the revised manuscript.
-\textcolor{red}{Our forecast is very close to the stock price of the day after the release date.} The donor pool constructed includes three time series of  Apple inc.'s stock price during MacBook release in the past three years.
-In this example, the shock is with precedent and our method works well because Apple Inc.
-is a well-established company that is not expected to reform its products a lot.
-As a result, knowledge from past shocks can bring insights into the future shocks.
-This example is representative for applying our methods to the time series that are to experience a shock that is with precedent in the past.
+\response{We include another example in which we forecast the stock price of Apple Inc.
+after the latest release of their MacBook product in 2020.
+This example is included in Section 5.2 of the revised manuscript.
+In this example, the donor pool constructed includes three past time series of  Apple inc.'s stock price surrounding previous releases of the MacBook which occurred over the past three years.
+In this example, the shock is with precedent and our method is expected to work well.
+This is because Apple Inc.
+is a well-established company that did not revolutionize the Macbook.
+Our adjusted forecast performs very well in this setting, as expected.
+This example is representative for applying our methods to the time series that are to experience a shock that is with some precedent in the past.
 In contrast, the example of Conoco Phillips is without precedent.
-In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by  pandemic.
+In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by a pandemic.
 In this example, our method is better than the original forecast though it cannot fully recover the stock price.
@@
 \end{align*}
-where $\hat{y}_{1, T_1^*+1}^{2}=\hat{y}_{1, T_1^*+1}^{1} + \hat{\alpha}_{T_1^* + 1}$, where $\hat{y}_{1, T_1^*+1}^{1}$ is the forecast without adjustment, and  $\hat{\alpha}_{T_1^* + 1}$ is the shock-effect estimator for the shock at $T_1^*+1$.
-The forecast for $d>2$ more periods is
+where $\hat{y}_{1, T_1^*+1}^{2}=\hat{y}_{1, T_1^*+1}^{1} + \hat{\alpha}_{T_1^* + 1}$, $\hat{y}_{1, T_1^*+1}^{1}$ is the forecast without adjustment, $\mathbf{x}_{1, T_1^*+2}$ is either known or forecasted, and  $\hat{\alpha}_{T_1^* + 1}$ is the shock-effect estimator for the shock at $T_1^*+1$.
+The forecast for $d>2$ more periods is similarly stated as
 \begin{align*}
@@
 \end{align*}
-where $\hat{y}_{1, T_1^*+d-1}$ can be also computed recursively using the above formula and we  emphasize  $ \hat{y}_{i, T_i^* + 1}=\hat{y}_{1, T_1^*+1}^{2}$.
-Since we use AR(1) model, $|\phi_1 |< 1$ is assumed.
-As one can expect, the impact of the shock  $\alpha_1$ will diminish as $d$ increases.
-Similar logic can apply for AR($p$).
-\\
+where $\mathbf{x}_{1, T_1^*+d}$ is either known or forecasted. \\
 
@@
 \end{align*}
-These two cases can be further combined to generalize forecasting for two or more periods. It is added to Section 6.\\
+These two cases can be further combined to generalize forecasting for two or more periods. We added aspects of this response to the Discussion.\\
 }
@@
 \begin{tcolorbox}
-``Although our work is developed for time-series or AR($p$) models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated \emph{\textcolor{red}{unbiasedly}}, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.''
+`` Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.''
 \end{tcolorbox}
 
-\vspace{0.4cm}In other words, if the estimator used in panel data is unbiased, our method can adapt to this scenario by weighting the shock effects estimated by panel data estimation procedure.
+%\vspace{0.4cm}In other words, if the estimator used in panel data is unbiased, our method can adapt to this scenario by weighting the shock effects estimated by panel data estimation procedure.
 In this case, the propositions in Section 3 still hold though the exact variance expressions will change since we are not using OLS estimators.}\\
@@
 The estimation procedures can be explained in detail as follows.
-Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series and $\mathbf{D}_{i}=(D_{i,t})_{t=1}^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$.
+Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series and $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$.
 We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$.
@@
   \hat{\alpha}_i = [(\mathbf{M}'_i\mathbf{M}_i)^{-1}\mathbf{M}_i'\mathbf{Y}_{i}]_{2}, \quad 
-  \text{ where }\quad \mathbf{Y}_{i}=(y_{i,t})_{t=1}^{T_i} 
- \quad  \text{ for } i = 2, \ldots, n+1.
+  \text{ where }\quad \mathbf{Y}_{i}=(y_{i,1},\ldots,y_{i,T_i})' 
+ \quad  \text{ for } i = 2, \ldots, n+1,
 \end{align*}
-Note that $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Our model is
+where $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Our model is
 \begin{align*}
@@
 \response{Thanks for pointing it out.
-We  clarify it in the revised version, and change the notation to be $\mathbf{M}_i$, which represents the design matrix of the model used in OLS estimation at the $i$th time series.
-For example, suppose the sample size for $i$th time series in the donor pool (i.e., $i\geq 2$) is 4; we have one covariate consisting of $x_1, \ldots, x_4$; and the shock occurs at $t = 4$.
+We  clarify it in the revised version, and change the notation to be $\mathbf{M}_i$, which represents the design matrix of the model used in OLS estimation at the $i$th time series.} \\
+
+%For example, suppose the sample size for $i$th time series in the donor pool (i.e., $i\geq 2$) is 4; we have one covariate consisting of $x_1, \ldots, x_4$; and the shock occurs at $t = 4$.
 In this case, $\mathbf{U}_i$ is
-\begin{align*}
-  \mathbf{M}_i = \begin{pmatrix}
-    1 & 0 & x_1 \\
-    1 & 0 & x_2 \\
-    1 & 0 & x_3 \\
-    1 & 1 & x_4
-  \end{pmatrix}.
-\end{align*}
-Suppose the sample size for the time series of interest is also 4, and we have a covariate $k_1, \ldots, k_4$.
+%\begin{align*}
+%  \mathbf{M}_i = \begin{pmatrix}
+%    1 & 0 & x_1 \\
+%    1 & 0 & x_2 \\
+%    1 & 0 & x_3 \\
+%    1 & 1 & x_4
+%  \end{pmatrix}.
+%\end{align*}
+%Suppose the sample size for the time series of interest is also 4, and we have a covariate $k_1, \ldots, k_4$.
 Note that the design matrix of the time series of interest will not contain $D_{1,t}$ since $D_{1,t}= I(t=T_1^*+1)=0$ due to we do not observe the shock.
 In this case,
-\begin{align*}
-  \mathbf{M}_1 = \begin{pmatrix}
-    1 &  k_1 \\
-    1 &  k_2 \\
-    1 &  k_3 \\
-    1 &  k_4
-  \end{pmatrix}.
-\end{align*}} \\
+%\begin{align*}
+%  \mathbf{M}_1 = \begin{pmatrix}
+%    1 &  k_1 \\
+%    1 &  k_2 \\
+%    1 &  k_3 \\
+%    1 &  k_4
+%  \end{pmatrix}.
+%\end{align*}} \\
 
@@
 
-\response{It is a good question.
+%It is a good question.
 To clarify, $\mathcal{M}_1$ assumes that the shocks have the same distribution.
@@
 
-$\mathcal{M}_{21}$ and $\mathcal{M}_{22}$ are constructed for generalization.
+%$\mathcal{M}_{21}$ and $\mathcal{M}_{22}$ are constructed for generalization.
 In practice, it is hard to verify those assumptions.
@@
 
-Theoretically, it is possible to verify the assumptions of $\mathcal{M}_{1}$ using empirical Bayes methods to some degree.
+%Theoretically, it is possible to verify the assumptions of $\mathcal{M}_{1}$ using empirical Bayes methods to some degree.
 First, we need a  pool of shock effects that users believe they are realizations from a common distribution, say, $\mathcal{F}_{\alpha}$.
@@
 
-In practice, someone can select the shocks that are similar to the one of interest.
-For example, they can be similar in causes, scale, and characteristics.
-Using our data analysis example, on March 9th 2020, Conoco Phillips experienced a shock during COVID-19 pandemic and oil supply shock.
-During COVID-19 pandemic, the US economy is in a situation that resembles the one in financial crisis.
-As a result, we select the shocks in the past that are related to financial crisis and oil supply shock.} \\
+\response{Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
+If this cannot be done, then the methodology may not work well.
+Practitioners can use qualitative and quantitative information to inform their decisions about which time series inform the donor pool.
+Consider our Conoco Phillips example.
+On March 9th 2020, Conoco Phillips was expected to experience a negative shock in the midst of the  COVID-19 pandemic and an oil supply shock.
+While the COVID-19 pandemic is unprecedented, several economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises.
+On the other hand, the oil supply shock had precedent.
+As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.} \\
 
@@
 The magnitude is not known.
-\\
-
-For example, in the Conoco Phillips stock example, when we knew the outbreak of COVID-19 was about to come, past shocks related to financial crisis may be helpful.
+%For example, in the Conoco Phillips stock example, when we knew the outbreak of COVID-19 was about to come, past shocks related to financial crisis may be helpful.
 Or, near the outbreak of COVID-19, suppose that a department in a university realized that it would be faced with declining applications.
 It could make use of the information about the decline of its admitted students in the past or that of other departments when similar situations (i.e., the number of applications suddenly decreases) happened.\\
-
-We admit it is quite an informational advantage over unanticipated shocks.
+We admit that it is quite an informational advantage over unanticipated shocks.
 However, in practice, if a shock is unanticipated, we may not even be able to construct such a post-shock analysis since we do not know it is about to happen.\\
@@
 It is possible to generalize our method to this situation.
-\textcolor{red}{Our new Apple example in Section 5.2 of the revised manuscript provides an example for the case $d=2$ with predicted covariates.}\\
+Our new Apple example in Section 5.2 of the revised manuscript provides an example for the case $d=2$ with predicted covariates.
+\\
 
@@
 However, it cannot be a simple intercept dummy but instead an iterative adjustment in computing $m$-ahead forecasts.
-For example, $\hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)}+ \hat{\beta}_{1, T_1^*+2}$, where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts considering $\hat{y}_{1, T_1^*+1}^{(1)}$ in computation.
-The approach of \cite{agarwal2020two} is an alternative  to this problem though its adjustment is without theoretical guarantees.
+For example, $\hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)}+ \hat{\beta}_{1, T_1^*+2}$, where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts.
+%considering $\hat{y}_{1, T_1^*+1}^{(1)}$ in computation.
+The approach of \cite{agarwal2020two} is an alternative  to this problem though its adjustment is without theoretical guarantees. \\
+
+%To judge if the shock is permanent, we may consider another approach. Consider the model
+%\begin{align*}
+%  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i}I(T_i^*< t \leq  T_i^*+d) +\varepsilon_{i,t}.
+%\end{align*}
+%We can compute $\hat{\beta}_i$ from OLS and $\mathbf{W}^*$ from synthetic approach with covariates $d \times p$ (see for example of $p = 2$ in our added Apple example in Section 5.2 of revised transcript) to compute $\hat{\beta}_1$.
+Note that $\hat{\beta}_1$ is unbiased.
+We can use parametric double bootstrap to test the hypothesis that $H_0 \colon \beta_1=0$ versus $H_1 \colon \beta_1\neq 0$ at time point $T^*_i+d$.
 \\
 
-To judge if the shock is permanent, we may go for another approach. Consider the model
-\begin{align*}
-  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i}I(T_i^*< t \leq  T_i^*+d) +\varepsilon_{i,t}.
-\end{align*}
-We can compute $\hat{\beta}_i$ from OLS and $\mathbf{W}^*$ from synthetic approach with covariates $d \times p$ (see for example of $p = 2$ in our added Apple example in Section 5.2 of revised transcript) to compute $\hat{\beta}_1$.
-Note that $\hat{\beta}_1$ is unbiased.
-We can use parametric double bootstrap to test the hypothesis that $H_0 \colon \beta_1=0$ versus $H_1 \colon \beta_1\neq 0$.
-\\
-
-To our best knowledge, we don't know whether the theoretical statements of our proposed methods in the manuscript can be adapted to assess when transitory shocks die out.} \\
+To the best of our knowledge, we don't know whether the theoretical statements of our proposed methods in the manuscript can be adapted to assess when transitory shocks die out.} \\
 
@@
 
-\response{\textcolor{red}{Thank you for pointing it out.
-We repolished Section 4 for better readability in the revised manuscript.} \textcolor{red}{We  summarize  our results including preferred user decisions as below.
-}There are mainly three decisions to make for an user: to choose
+\response{Thank you for pointing it out.
+We polished Section 4 for better readability in the revised manuscript.
+We  summarize  our results including preferred user decisions as below.
+There are mainly three decisions to make for an user: to choose
   \begin{itemize}

### 2021-01-22 Revision/manuscript.tex
finished round of revisions

@@
 Note that since $\sigma$ is unknown, estimation is required and the numerator and denominator terms are dependent in general.
-However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in practical settings, especially when the $T^*_i$s very considerably.
+However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in practical settings, especially when the $T^*_i$s vary considerably.
 We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of $\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation (see Section \ref{simulation}).
@@
   T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
-  T_i^* &\simiid \red{U\{p+4, T_i-1\}}, \\
+  T_i^* &\simiid U\{p+4, T_i-1\}, \\
   \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2},
 \end{align*}
-where the $[\cdot]$ operation in the generation of the $T_i$'s corresponds to rounding the input to the nearest integer, \red{$U(a,b)$, $U\{a,b\}$, and $\mrm{Gamma}(c,d)$  stands for a random variable from continuous uniform distribution on the closed interval from $a$ to $b$, discrete uniform distribution on the set of integers from $a$ and $b$, and Gamma distribution with shape parameter $c$ and scale parameter $d$, respectively}.
+where the $[\cdot]$ operation in the generation of the $T_i$'s corresponds to rounding the input to the nearest integer, $U(a,b)$, $U\{a,b\}$, and $\mrm{Gamma}(c,d)$, respectively,  denotes the continuous uniform distribution on the closed interval from $a$ to $b$, discrete uniform distribution on the set of integers from $a$ and $b$, and Gamma distribution with shape parameter $c$ and scale parameter $d$, respectively.
 The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
@@
 Section \ref{apple} applies our proposed method to the forecasting of Apple stock prices after releasing the latest version of their MacBook product.
-These examples provide empirical illustration of our methodology in settings where the shock is, respectively, unprecedented and with precedent.
-\textcolor{red}{Generalizations of our method are discussed as well.
+These examples provide empirical illustration of our methodology in settings where the shock has, respectively, unprecedented and precedented origins.
+%\textcolor{red}{Generalizations of our method are discussed as well.
 Section \ref{forecasting} allows the shock effect to be decomposed into separable estimable parts,  multiple shock effects to be nested in a time series, and different models for the response and the shock effects.
@@
 In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}.
-These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Macbook in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}.
+These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie MacBook in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}.
 The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}.
@@
 We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well.
-Our estimation framework misses the yet to be observed pot-shock response, however they perform much better than unadjusted forecasts that do not account for shock effects.
+Our estimation framework misses the yet to be observed post-shock response.
+However, they perform much better than unadjusted forecasts that do not account for shock effects.
 The unadjusted forecast misses the post-shock response by 9.870 dollars whereas
@@
 Typically, after the release, the stock price of Apple Inc.
-is expected to experience a shock since Macbook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced.
-For example, the sales of Macbooks account for 9.8\% of its revenue \citep{applemac}.
+is expected to experience a shock since MacBook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced.
+For example, the sales of MacBooks account for 9.8\% of its revenue \citep{applemac}.
 In this example, we are interested in forecasting the stock price of Apple Inc.
 after the release of the latest MacBook on November, 10th, 2020.
-\textcolor{red}{From knowledge from our donor pool (see  (3) Construction of donor pool below), we observe that it takes two days for the shock effect to take hold.} Therefore, we are interested in the stock price of Apple Inc.
-on the day after the release date, i.e., on November 11th, 2020, \red{when we conjecture that the time series of interest would experience a shock}.
-\red{We collect our data through   \texttt{quantmod} package \citep{ryan2017quantmod} in R.} The detailed considerations of our analysis are outlined as below.
+Our donor pool suggests that it takes two days for the shock effect to take hold.
+Therefore, we are interested in the stock price of Apple Inc.
+on the day after the release date, i.e., on November 11th, 2020.
+Our data is collected using the \texttt{quantmod} package \citep{ryan2017quantmod} in R.
+The detailed considerations of our analysis are outlined as below:
 
 \begin{enumerate}[label = (\arabic*)]
-  \item \red{\textbf{Selection of model.}}  We use an AR(1) model to forecast the stock price of Apple Inc.
+  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc.
 All the estimates will be adjusted for inflation.
@@
   \end{align*}
-  The model for $y_{i,t}$ is the same as in Section \ref{modelsetup} for $i = 2, \ldots, n+1$.   The model for the shock effect is
+  The model for the shock effect is
   \begin{align*}
@@
   \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc.
-with shock-effect date in the middle of \red{25} trading days for 2017, 2018, and 2019.
+with shock-effect date in the middle of 25 trading days for 2017, 2018, and 2019.
 The specific shock-effect dates are June 6th, 2017, October 30th, 2018, and June 3rd, 2019, respectively.
-We only include the last three Macbook releases in our donor pool because \red{we conjecture that} those releases are similar to the current release in the sense that Apple inc.
-has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019}; \red{and it is indeed consistent \citep{apple2020}}.
+We only include the last three MacBook releases in our donor pool.
+This is because these releases are similar to the current release, Apple inc.
+has only updated the hardware of the computer without much redesign of the MacBook \citep{apple2017, apple2018, apple2019}.
+The same is the case with the lastest MacBook release \citep{apple2020}.
 %The new MacBook series is built with M1 chip invented by Apple inc.
@@
 The unadjusted forecast misses the post-shock by 0.799 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.457, 0.090, and 0.152 dollars, respectively.
-\red{It appears that covariates weighting with $\hat{\alpha}_{\rm wadj}$ is more successful.
-It is possible that $\mc{M}_2$ is a good fit for the data.
-Note  that the 1-ahead forecast error for $y_{1, T_1^*+1}$ and the covariates contribute to some of the forecast risk.}
+In this example, covariates weighting to construct $\hat{\alpha}_{\rm wadj}$ is more successful than the other techniques, it is possible that model $\mc{M}_2$ fits this data well.
+Note  that the 1-ahead forecast error for $y_{1, T_1^*+1}$ and the covariates contribute to some of the forecast risk.
 
@@
 The model, under which we verify these claims, is a simple AR(1) model.
-Similar results can be obtained for more general models \red{whose parameter can be estimated unbiasedly}.
+Similar results can be obtained for more general models whose parameters can be estimated unbiasedly.
 %such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
@@
 An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.
-Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.
-
-We can extend the proposed nowcasting to forecast  the response for $m$ periods, where $m\geq 2$.
-Without loss of generality, we assume $m = 2$.
-There are two cases.
-First, suppose that there is no additional shock after $T_1^*+1$.
-Then, the forecast boils down to standard $m$-ahead forecast in time series.
-Second, assume that the time series under study will experience a shock at $T_1^* + 2$, say $\alpha_1^{(2)}$.
-Under our framework, users may want to construct another set of donor pool with time series that experience shock similar to  $\alpha_1^{(2)}$.
-Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(2)}$.
-The forecast at $t = T_1^* + 2$ is
-\begin{align*}
-  \hat{y}^2_{1, T_1^*+2}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +2} + \hat{\alpha}_1^{(2)},
-\end{align*} 
-where $\hat{y}_{1, T_1^* + 1}^2$ is defined as in Section \ref{forecast}.
-These two cases can be generalized to  forecasting $m\geq 2$ more periods.
-The scenarios for forecasting in AR($p$), or other general models are analogous.
-
-In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$.
-The methodology can be extended to more general timing scenarios.
+Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.
+
+In our setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$.
+The methodology can be amended to accommodate different timing scenarios.
 Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$.
 We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.
-\red{The Apple example illustrates the case when $d = 2$ with predicted covariates, where the prediction error for covariates and response can contribute to the post-shock forecast risk.}
+The Apple example illustrates the case when $d = 2$ with predicted covariates, where the prediction error for covariates and response can contribute to the post-shock forecast risk.
+
+We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead. %We present one possible generalization under the specification that $m = 2$. 
+In this setting, there are two cases.
+In the first case, we suppose that there is no additional shock after $T_1^*+1$.
+Then, the forecast boils down to standard $m$-ahead forecast in time series.
+In the second case, we assume that the time series under study will experience an additional additive shock at $T_1^* + m$, say $\alpha_1^{(m)}$.
+Users now construct the donor pool to consist of time series that experience shocks similar to  $\alpha_1^{(m)}$.
+Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(m)}$.
+The adjusted forecast at $t = T_1^* + m$ is
+$
+  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}.
+$
 

### 2021-01-25 Revision/manuscript.tex
revised manuscript

@@
 This figure depicts a time series that experienced a shock at time point $T_1^*+1 = 126$.
-It is supposed that the researcher does not have any information after $T_1^*$, but does have observations from a donor pool of forty time series that have previously undergone a similar shock for which post-shock responses are recorded.
+It is supposed that the researcher does not have any information after $T_1^*$, but does have observations from a donor pool of forty time series that have previously undergone similar shocks for which post-shock responses are recorded.
 Similarity in this context means that the shock effects are random variables that from a common distribution.
@@
 \alpha_i &\simiid \mc{F}_{\alpha} \text{ with }  \; \mrm{E}_{\mc{F}_{\alpha}}(\alpha_i) = \mu_{\alpha}, \mrm{Var}_{\mc{F}_{\alpha}}(\alpha_i)  = \sigma^2_{\alpha}  \\
-\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon}}(\varepsilon_{i,t})  = \sigma^2  ,  \\
+\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i  ,  \\
 \eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t},
 \end{align*}
-where $\sigma > 0$. Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
+where $\sigma > 0$  \red{ and $\indep $ stands for independence operator}. Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
 for $i = 1, \ldots, n+1$.
@@
 Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation procedure for evaluation of these conditions, discussed in Section \ref{conditions} and \ref{varbootstrap} respectively.
-Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:
+\red{Throughout this section, we will assume that the time series within the donor pool are independent for exact variance expressions.
+However, the theory developed later allows for dependence within the donor pool.} Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:
 
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}, \\
-\var{\hat{\alpha}_{\rm wadj}}  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.
+  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma^2_i\, \mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}, \\
+\var{\hat{\alpha}_{\rm wadj}}  &= \sum_{i=2}^{n+1}(\sigma_iw_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.
 \end{align*}
@@
 \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}),\\
+  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\, \mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}),\\
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
+  &=\sum_{i=2}^{n+1}(\sigma_iw_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
 \end{align*}
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
+  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\, \mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
 \end{align}
@@
 \var{\hat{\alpha}_{\rm wadj}}
- &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
+ &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
 \end{align}
@@
 \var{\hat{\alpha}_{\rm wadj}}
-& = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}) < (\E{\alpha_1})^2,
+& =\sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}) < (\E{\alpha_1})^2,
 \end{align*}
@@
 We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the guess, with 1 indicating that $\hat{\alpha}$ provides risk-reduction over the simple no-adjustment forecast, and 0 indicates the converse.
-We will consider the LOOCV estimators \eqref{loocvm} and \eqref{loocvk} to assess correct decision making.
-We will also consider the Euclidean distance between the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ and the realized post-shock response $y_{1,T_1^*+1}$.
+\red{We will consider the LOOCV estimators with $k$ random draws \eqref{loocvk} to assess correct decision making.} We will also consider the Euclidean distance between the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ and the realized post-shock response $y_{1,T_1^*+1}$.
 The first two metrics can combine to assess our forecasting methodology prospectively while the latter requires the realization of the post-shock response $y_{1,T_1^*+1}$.
@@
   \begin{center}
-    \includegraphics[height = 9cm]{FIG3.pdf}
+    \includegraphics[height = 7cm, width = 16.8cm]{FIG3.pdf}
     \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and violet line represent real data and fitted line, respectively.}
@@
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma^2(\mbf{M}'_i\mbf{M}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
+  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma_i^2(\mbf{M}'_i\mbf{M}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
+  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
 \end{align}
@@
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
+  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  & \quad  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
+  &=\frac{1}{n^2}\sum_{i=2}^{n+1} \sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
 \end{align*}
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
+  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
   & \quad  +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).

### 2021-01-25 Revision/apple.R

@@ -4,6 +4,7 @@ library('dplyr')
 library('Rsolnp')
 library('ggplot2')
 library('tikzDevice')
+library('ggpubr')
 # set working directory
 setwd("/Users/mac/Desktop/Research/Post-Shock Prediction/")
 
@@ -50,24 +51,24 @@ AAPL_close <- data.frame(AAPL_close[-nrow(AAPL_close), ], Y)
 
 
 # shock effect date
-start <- which(AAPL_close$Date %in% c("2017-06-06", "2017-06-07"))
+start <- which(AAPL_close$Date == "2017-06-06")
 start_day_201706 <- as.numeric(1:nrow(AAPL_close) %in% start)
 AAPL_close <- AAPL_close %>% mutate(start_day_201706 = start_day_201706)
-TS2 <- AAPL_close[(start[1] - 5):(start[1] + 10), ]
+TS2 <- AAPL_close[(start[1] - 12):(start[1] + 12), ]
 # inflation adjustment
 TS2[, 2:5] <- TS2[, 2:5] * inflation_adj$dollars_2020[inflation_adj$year == 2017] 
 m_AAPL_201706 <- lm(Y ~ AAPL_Close + start_day_201706 + GSPC_Close + TB_Close, 
-                 data = TS2)
+                    data = TS2)
 alpha_201706 <- summary(m_AAPL_201706)$coef[3,1:2] 
 # shock-effects
 alpha_201706
 
 
 # shock effect date
-start <- which(AAPL_close$Date %in% c("2018-10-29", "2018-10-30"))
-start_day_201810 <- as.numeric(1:nrow(AAPL_close) %in% start)
+start <- which(AAPL_close$Date == "2018-10-30")
+start_day_201810 <- as.numeric(1:nrow(AAPL_close) == start)
 AAPL_close <- AAPL_close %>% mutate(start_day_201810 = start_day_201810)
-TS3 <- AAPL_close[(start[1] - 5):(start[1] + 10), ]
+TS3 <- AAPL_close[(start[1] - 12):(start[1] + 12), ]
 # inflation adjustment
 TS3[, 2:5] <- TS3[, 2:5] * inflation_adj$dollars_2020[inflation_adj$year == 2018] 
 m_AAPL_201810 <- lm(Y ~ AAPL_Close + start_day_201810 + GSPC_Close + TB_Close, 
@@ -77,10 +78,10 @@ alpha_201810 <- summary(m_AAPL_201810)$coef[3,1:2]
 alpha_201810
 
 # shock effect date
[…]

### 2021-01-25 Revision/list.tex
updated referee report

@@
 This example is included in Section 5.2 of the revised manuscript.
-In this example, the donor pool constructed includes three past time series of  Apple inc.'s stock price surrounding previous releases of the MacBook which occurred over the past three years.
+In this example, the donor pool includes three past time series of  Apple inc.'s stock price surrounding previous releases of the MacBook.
 In this example, the shock is with precedent and our method is expected to work well.
 This is because Apple Inc.
-is a well-established company that did not revolutionize the Macbook.
+is a well-established company that did not revolutionize the MacBook product in their last three releases.
+Apple Inc.
+mostly focused on upgrading the hardware in the MacBook, this same is true for the latest release.
 Our adjusted forecast performs very well in this setting, as expected.
-This example is representative for applying our methods to the time series that are to experience a shock that is with some precedent in the past.
+This example is representative for a class of problems involving shocks that are very similar to those in the past.
 In contrast, the example of Conoco Phillips is without precedent.
-In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by a pandemic.
-In this example, our method is better than the original forecast though it cannot fully recover the stock price.
+In the past, Conoco Phillips  did not experience a financial crisis shock caused by a pandemic supplemented with an oil price shock.
+In the Conoco Phillips example, our method is better than the original forecast, although we do not fully recover the yet to be observed stock price.
 We hope that the addition of the Apple example helps to generate confidence in our approach.}
@@
 If this cannot be done, then the methodology may not work well.
-Practitioners can use qualitative and quantitative information to inform their decisions about which time series inform the donor pool.
+Practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool.
 Consider our Conoco Phillips example.

### 2021-01-25 Revision/manuscript.tex
updated referee report

@@
 However, it is difficult to verify such assumption or structure in practice.
-In principle, one should select identities that come from a common population, which is also the one  the identity under study come from, as candidates in donor pool.
+In principle, one should select individuals that come from a common population, the same populationas the individual under study, to form the donor pool.
 This selection criterion is often adopted in the literature of comparative case studies.
@@
 \citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country.
-To estimate the effect of Proposition 99, a large tabacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period.
+To estimate the effect of Proposition 99, a large tobacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period.
 Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.

### 2021-01-25 Revision/list.tex
made minor updates to manuscript and referee report; need to better address Comment 12 from reviewer 1

@@
 It could be a restrictive assumption in a number of situations.
-For example, if time series in a donor pool are observed in almost concurrent time as the one under study (or, the time differences are not large enough), the independence assumption may not hold.
-As a result, application in panel data should be ruled out.
-However, if the time differences are large, the dependence should diminish as time passes.} \\
+Panel data applications are ruled out.
+Additionally, if time series in a donor pool are observed in almost concurrent time as the one under study (or, the time differences are not large enough), the independence assumption may not hold.
+However, if the time differences between the time series under study and those forming the donor pool are large enough, then the dependence should be negligible.
+This is the case in our Conoco Phillips and Apple examples.} \\
 
@@
 You are right about the timing.
-It can be applicable in many different timing scenarios.
+Our methodology can be applicable in many different timing scenarios.
 Generally, suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$ and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$.
@@
 It shows that a slightly weak signal will not compromise the correctness of our evaluated propositions a lot.
-However, if the forecast for the covariates is seriously bad (i.e., the signal from covariates is really weak), our result shows that the risk-reduction evaluation may be only as good as a random guess.} \\
+However, if the forecast for the covariates is seriously bad (i.e., the signal from covariates is really weak), our result shows that the risk-reduction evaluation may be only as good as a random guess.
+\\
+
+In the event that the mean shift $D_{i,t}$ interacts with the covariates, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions.
+In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed.
+A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid.
+This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid.
+} \\
 
@@
 
-To the best of our knowledge, we don't know whether the theoretical statements of our proposed methods in the manuscript can be adapted to assess when transitory shocks die out.} \\
+To the best of our knowledge, we don't know whether the theoretical statements of our proposed methods in the manuscript can be adapted to assess when transitory shocks die out.
+This is beyond the scope of our current paper.} \\
 

### 2021-01-25 Revision/manuscript.tex
made minor updates to manuscript and referee report; need to better address Comment 12 from reviewer 1

@@
 \end{align*}
-where $\sigma > 0$  \red{ and $\indep $ stands for independence operator}. Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
+where $\indep $ denotes the independence operator. Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
 for $i = 1, \ldots, n+1$.
@@
 \end{align*} 
-where $\sigma_a > 0$. We further define 
+We further define 
 $\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}$. 
@@
 Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation procedure for evaluation of these conditions, discussed in Section \ref{conditions} and \ref{varbootstrap} respectively.
-\red{Throughout this section, we will assume that the time series within the donor pool are independent for exact variance expressions.
-However, the theory developed later allows for dependence within the donor pool.} Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:
+Throughout this section, we will assume that the time series within the donor pool are independent.
+This is needed for exact variance expressions.
+However, the theory developed later allows for dependence within the donor pool \red{be specific of when independence is required and when it is not}.
+Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:
 
@@
 We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the guess, with 1 indicating that $\hat{\alpha}$ provides risk-reduction over the simple no-adjustment forecast, and 0 indicates the converse.
-\red{We will consider the LOOCV estimators with $k$ random draws \eqref{loocvk} to assess correct decision making.} We will also consider the Euclidean distance between the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ and the realized post-shock response $y_{1,T_1^*+1}$.
+We will consider the LOOCV estimators with $k$ random draws \eqref{loocvk} to assess correct decision making.
+We will also consider the Euclidean distance between the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ and the realized post-shock response $y_{1,T_1^*+1}$.
 The first two metrics can combine to assess our forecasting methodology prospectively while the latter requires the realization of the post-shock response $y_{1,T_1^*+1}$.

### 2021-01-26 Revision/list.tex
revised manuscript and list with changes in red

@@
 The labels (a) and (b) are now added in the revised manuscript.
-The \textcolor{black}{black} line stands for the realized observations whereas the violet line stands for the fitted values.} \\
+The black line stands for the realized observations whereas the violet line stands for the fitted values.} \\
 
@@
 \begin{tcolorbox}
-`` Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.''
-\end{tcolorbox}
+``Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.''
+\end{tcolorbox}} \\
 
@@
 The estimation procedures can be explained in detail as follows.
-Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series and $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$.
-We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$.
+Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \textcolor{red}{\mathbf{Y}_i^{(1)}}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series, $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$, \textcolor{red}{and  $\mathbf{Y}_i^{(1)}$ is the lagged response $\mathbf{Y}_{i}=(y_{i,1},\ldots,y_{i,T_i})'$}.
+We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \textcolor{red}{\mathbf{Y}_i^{(1)}}, \mathbf{X}_{i})$.
 Then the expression for $\hat{\alpha}_i$ is
 \begin{align*}
-  \hat{\alpha}_i = [(\mathbf{M}'_i\mathbf{M}_i)^{-1}\mathbf{M}_i'\mathbf{Y}_{i}]_{2}, \quad 
-  \text{ where }\quad \mathbf{Y}_{i}=(y_{i,1},\ldots,y_{i,T_i})' 
+  \hat{\alpha}_i = [(\mathbf{M}'_i\mathbf{M}_i)^{-1}\mathbf{M}_i'\mathbf{Y}_{i}]_{2}, 
  \quad  \text{ for } i = 2, \ldots, n+1,
@@
 In other words,  $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ is an extended version of $\mathcal{M}_{1}$ by allowing it to depend on some covariates.
-However, in general, $E(\alpha_1)\neq \mu_{\alpha}$ under   $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ due to the presence of $\delta_i'\mathbf{x}_{i, T_i^*+1}$.} \\
+However, in general, $E(\alpha_1)\neq \mu_{\alpha}$ under   $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ due to the presence of $\delta_i'\mathbf{x}_{i, T_i^*+1}$.}\\
 
@@
 
-\response{Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
+\response{\textcolor{red}{To our best knowledge, it is impossible to justify this assumption.} % Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
 If this cannot be done, then the methodology may not work well.
-Practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool.
+\textcolor{red}{In real-life applications,} practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool.
 Consider our Conoco Phillips example.
@@
 
-You are right about the timing.
+\textcolor{red}{Our proposed methodology is applied at $T_1^*+1$, yielding gains over the unadjusted forecast.} You are right about the timing.
 Our methodology can be applicable in many different timing scenarios.
@@
 This structure requires the covariates to be known in the future for \emph{ex ante} forecasts, or for them to be forecast.
-The set-up assumes θ1 to be well behaved and the covariates are not subject to shocks if they need to be forecast.
+The set-up assumes $\theta_1$ to be well behaved and the covariates are not subject to shocks if they need to be forecast.
 Empirically, we could also think of cases where the mean shift $D_{i,t}$ interacted with the covariates which would give an additional forecast error via $\mathbf{x}_{1, T_1^* + 1}$.
@@
 This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid.
-} \\
+\textcolor{red}{This  gives users a sense of variability of post-shock predictions due to forecast error from covariates.}} \\
 
@@
 %considering $\hat{y}_{1, T_1^*+1}^{(1)}$ in computation.
-The approach of \cite{agarwal2020two} is an alternative  to this problem though its adjustment is without theoretical guarantees. \\
+\textcolor{red}{One can then use $\hat{\boldsymbol{\beta}}_1^{(m)}$ to judge whether the shock is transitory  or permanent.} The approach of \cite{agarwal2020two} is an alternative  to \textcolor{red}{intercept correction dummy} problem though its adjustment is without theoretical guarantees.
+\\
 

### 2021-01-27 Revision/list.tex
made what I am hoping is the last or second to last round of edits. Please look over carefully.

@@
 The estimation procedures can be explained in detail as follows.
-Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \textcolor{red}{\mathbf{Y}_i^{(1)}}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series, $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$, \textcolor{red}{and  $\mathbf{Y}_i^{(1)}$ is the lagged response $\mathbf{Y}_{i}=(y_{i,1},\ldots,y_{i,T_i})'$}.
-We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \textcolor{red}{\mathbf{Y}_i^{(1)}}, \mathbf{X}_{i})$.
+Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{Y}_i^{(1)}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series, $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$, and $\mathbf{Y}_i^{(1)}$ is the lagged response $(y_{i,1},\ldots,y_{i,T_i})'$.
+We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{Y}_i^{(1)}, \mathbf{X}_{i})$.
 Then the expression for $\hat{\alpha}_i$ is
@@
 \end{align*}
-$\eta_i$ represents the effect of the intercept.
+the intercept is denoted as $\eta_i$.
 Thus, we cannot identify $\alpha_i$ from $\eta_i$.
@@
 \response{Thanks for pointing it out.
-We  clarify it in the revised version, and change the notation to be $\mathbf{M}_i$, which represents the design matrix of the model used in OLS estimation at the $i$th time series.} \\
+This quantity is the model (design) matrix corresponding to the $i$th time series.
+We clarify this quantity the revised version, and we change the notation to be $\mathbf{M}_i$.
+Our previous response describes $\mathbf{M}_i$ in more detail.} \\
 
@@
 
-\response{\textcolor{red}{To our best knowledge, it is impossible to justify this assumption.} % Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
-If this cannot be done, then the methodology may not work well.
-\textcolor{red}{In real-life applications,} practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool.
+ Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
+If this cannot be done, then the methodology may fail.
+In real-life applications, practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool.
 Consider our Conoco Phillips example.
 On March 9th 2020, Conoco Phillips was expected to experience a negative shock in the midst of the  COVID-19 pandemic and an oil supply shock.
-While the COVID-19 pandemic is unprecedented, several economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises.
+While the COVID-19 pandemic is unprecedented, several, although not all, economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises.
 On the other hand, the oil supply shock had precedent.
-As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.} \\
+As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.
+\\
 
@@
 However, if the time differences between the time series under study and those forming the donor pool are large enough, then the dependence should be negligible.
-This is the case in our Conoco Phillips and Apple examples.} \\
+This is the case in our Conoco Phillips and Apple examples.
+We include this discussion in the Introduction.
+Thank you for this comment.} \\
 
@@
 
-\textcolor{red}{Our proposed methodology is applied at $T_1^*+1$, yielding gains over the unadjusted forecast.} You are right about the timing.
+Our proposed methodology is applied at $T_1^*+1$.
+You are right about the timing.
 Our methodology can be applicable in many different timing scenarios.
@@
 
-Thank you for your remark on the timing scenarios. It is very helpful for improving our manuscript.} \\
+Thank you for your remark on timing scenarios, it led to an improved manuscript.} \\
 
@@
 
-\response{It is a very good point.
-Thanks for pointing it out.
+\response{Good point, thank you.
 Indeed, our method assumes $\mathbf{x}_{1, T_1^* + 1}$ to be given.
@@
 
-In fact, the situation when  covariates are forecasted with errors is similar to the one when the variance of the shock effect is large.
+The situation when covariates are forecasted with errors is similar to the one when the variance of the shock effect is large.
 In both situations, the signal from covariates is weak.
 Our simulation discusses this situation by increasing $\sigma_{\alpha}$.
-It shows that a slightly weak signal will not compromise the correctness of our evaluated propositions a lot.
+It shows that a slightly weak signal will not strongly compromise the correctness of our prospective methods.
 However, if the forecast for the covariates is seriously bad (i.e., the signal from covariates is really weak), our result shows that the risk-reduction evaluation may be only as good as a random guess.
@@
 This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid.
-\textcolor{red}{This  gives users a sense of variability of post-shock predictions due to forecast error from covariates.}} \\
+This may gives users a sense of the variability of post-shock predictions due to forecast error from covariates that are also affected from the shock.
+We included this response to the Discussion, thank you again.} \\
 
@@
 \begin{align*}
-  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i, T_i^* + d}I(t = T_i^*+d) +\varepsilon_{i,t}
+  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i, T_i^* + d}I(t = T_i^*+d) +\varepsilon_{i,t},
 \end{align*}
@@
 However, it cannot be a simple intercept dummy but instead an iterative adjustment in computing $m$-ahead forecasts.
-For example, $\hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)}+ \hat{\beta}_{1, T_1^*+2}$, where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts.
-%considering $\hat{y}_{1, T_1^*+1}^{(1)}$ in computation.
-\textcolor{red}{One can then use $\hat{\boldsymbol{\beta}}_1^{(m)}$ to judge whether the shock is transitory  or permanent.} The approach of \cite{agarwal2020two} is an alternative  to \textcolor{red}{intercept correction dummy} problem though its adjustment is without theoretical guarantees.
+For example,
+$$
+  \hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)} + \hat{\beta}_{1, T_1^*+2}, 
+$$
+where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts.
+One then may be able to use $\hat{\boldsymbol{\beta}}_1^{(d)}$ to judge whether the shock is transitory or permanent.
+We speculate that the transitory shock effect can be theoretically justified using similar arguments as those that appear in our manuscript, but we view this extension as outside the scope of our current paper.
+The SCM based approach of \cite{agarwal2020two} is an alternative that may also be able to assess whether or not a shock is transitory, although this adjustment is without any theoretical guarantees.
 \\
@@
 \\
-
-To the best of our knowledge, we don't know whether the theoretical statements of our proposed methods in the manuscript can be adapted to assess when transitory shocks die out.
-This is beyond the scope of our current paper.} \\
+} \\
 

### 2021-01-27 Revision/manuscript.tex
revised manuscript and list with changes in red
made what I am hoping is the last or second to last round of edits. Please look over carefully.

@@
 
-In our methodological framework, the researcher creates a synthetic panel of time series which have undergone similar structural shocks in the past.
-Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
+\red{Check out this paragraph.} In our methodological framework, the researcher first creates a donor pool of time series which have undergone similar structural shocks in the past.
+Similarity in this context refers to the shock effects as arising from a common distribution with existing second moments.
+The unobserved shock effect in the time series of interest is assumed to arise from the same distribution.
+Construction of the donor pool and the desired aims of the donor pool has precedent in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
 As in SCM, care is needed when forming the donor pool of time series.
-However, there are key differences between our framework and SCM.
-We assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock.
-Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing second moments.
-
-We then estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed.
-These estimated shock effects are then aggregated and this aggregated estimator is taken to be the estimator for the shock effect in the time series of interest.
-Finally, this aggreagted estimator is then added to a forecast for the yet to be realized post-shock response of the time series of interest.
+However, there are several key differences between our framework and SCM.
+Unlike in SCM, we are not trying to estimate the causal effect of an intervention.
+Also, we assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock.
+This rules out panel data applications where the time series of interest and those forming the donor pool evolve in tandem.
+When there are large time differences between the time series under study and those forming the donor pool, then the dependence will be negligible in practice.
+This is the case in the Conoco Phillips and Apple stock forecasting examples.
+
+We then estimate the shock effects that are present in the time series forming the donor pool for which the post-shock responses are observed.
+These estimated shock effects are then aggregated.
+Finally, this aggregated estimator is added to the forecast for the yet to be realized post-shock response of the time series of interest.
 Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts.
@@
 This approach is therefore not applicable in the post-shock setting.
-
 The shock effects in our post-shock forecasting framework are similar to ``expectation shocks,'' studied in \cite{clements2019measuring}.
@@
 We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting.
-The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.
-Our autoregressive model will consider present day covariates to better motivate similarity weighting.
+The latter technique is similar to the weighting in SCM \citep{abadie2010synthetic}.
 The considered adjustment strategies all target the mean of the shock effect distribution.
@@
 after the company releases their latest installment of the MacBook on November 10th, 2020.
-We will show that our proposed adjustment estimators yield much better results than no adjustment in these settings.
-The example of Conoco Phillips provides an empirical application of our methods in unprecedented shocks whereas the Apple example provides a case for post-shock prediction where the shock has precedent.
-We now motivate our framework for post-shock prediction.
+We will show that our proposed adjustment estimators yield much better results than no adjustment in these examples.
+The Conoco Phillips example provides an empirical application of our methods when the shock is unprecedented in nature, arising from a global pandemic and an oil supply shock.
+The Apple example provides a case for post-shock prediction when the shock has precedent, Apple just released the latest version of their MacBook product.
+We now elaborate our framework for post-shock prediction.
 
@@
 Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation procedure for evaluation of these conditions, discussed in Section \ref{conditions} and \ref{varbootstrap} respectively.
-Throughout this section, we will assume that the time series within the donor pool are independent.
+Throughout this section, we have specified that the time series within the donor pool are independent.
 This is needed for exact variance expressions.
-However, the theory developed later allows for dependence within the donor pool \red{be specific of when independence is required and when it is not}.
+However, the theory developed later allows for dependence within the donor pool.
 Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:
@@
 Therefore, we are interested in the stock price of Apple Inc.
-on the day after the release date, i.e., on November 11th, 2020.
+on the day after the release date, November 11th, 2020.
 Our data is collected using the \texttt{quantmod} package \citep{ryan2017quantmod} in R.
@@
 with shock-effect date in the middle of 25 trading days for 2017, 2018, and 2019.
-The specific shock-effect dates are June 6th, 2017, October 30th, 2018, and June 3rd, 2019, respectively.
+The specific shock-effect dates are June 7th, 2017, October 31st, 2018, and June 4th, 2019, respectively.
 We only include the last three MacBook releases in our donor pool.
@@
 has only updated the hardware of the computer without much redesign of the MacBook \citep{apple2017, apple2018, apple2019}.
-The same is the case with the lastest MacBook release \citep{apple2020}.
+The same is the case with the latest MacBook release \citep{apple2020}.
 %The new MacBook series is built with M1 chip invented by Apple inc.
@@
 The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
-Additionally, $\alpha_i$ can be heteroskedastic; i.e.,  they can have different variances.
+Additionally, $\alpha_i$ can be heteroskedastic.
 In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply.
@@
 
-We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead. %We present one possible generalization under the specification that $m = 2$. 
+We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead.
 In this setting, there are two cases.
@@
 $
-  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}.
-$
+  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}
+$
+where the future covariates are themselves forecasted. The additional forecasting variability may  render such an adjustment approach useless.
+
+In our framework we have assumed the covariates to be known.
+However, it may be the case that the shock effects the covariates as well as the response.
+If so, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions.
+In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed.
+A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid.
+This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid.
+This may gives users a sense of the variability of post-shock predictions due to forecast error from covariates that are also affected from the shock.
 
@@
 
-Construction of the donor pool is a critical step that directly matters in prediction.
+Construction of the donor pool is a critical step in our post-shock prediction framework.
 In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for varying variances and  varying means that are linear functions of common covariates.
-Remark \ref{remark1} shows that common covariates are not restrictive with structural zero in coefficients.
-However, it is difficult to verify such assumption or structure in practice.
-In principle, one should select individuals that come from a common population, the same populationas the individual under study, to form the donor pool.
+However, it may be difficult to confirm such an assumption or modeling structure in practice.
+Also note that we assume that the time series under study is independent of those forming the donor pool, independence being practically satisfied when the time series of interest is separated from the donor pool in time.
+In principle, one should select time series that come from a common population, the same population as the individual under study, to form the donor pool.
 This selection criterion is often adopted in the literature of comparative case studies.
@@
 
+%\section{Acknowledgements}
+
 \section{Appendix}
@@
    \E{\hat{\alpha}_{\rm wadj}}
-   &= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}\\
-   &= \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right)\\
-   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}\right]\bigg\}\\
+   &= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}
+   = \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
+   = \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}\right]\bigg\} \\
    &=\mu_{\alpha}+ \mu_{\delta}' \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}\tag{$\mbf{W}\in \mc{W}$}
@@
 Similarly,
-  \begin{align*}
+$
    \E{\hat{\alpha}_{\rm adj}}
-   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \mu_{\delta}'  \mbf{x}_{i, T_i^*+1}.
-   \end{align*}
+   =\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \mu_{\delta}'  \mbf{x}_{i, T_i^*+1}.
+$
 
@@
   \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
- & \quad  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
+  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
 \end{align*}
@@
   \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
-  & \quad  +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
+  =\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}
+   +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
 \end{align*}
@@
   \begin{align*}
-    C(\Theta_1) &=\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} \\
-    & \quad -(\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}),
+    C(\Theta_1) =\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} 
+    &- (\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}),
   \end{align*}
@@
   \begin{align*}
-    \E{C(\Theta_1)\hat{\alpha}}=\mrm{E}\big\{\hat{\alpha}\cdot \E{C(\Theta_1)\mid \Theta_1}\}=0.
+    \E{C(\Theta_1)\hat{\alpha}}=\mrm{E}\big\{\hat{\alpha}\E{C(\Theta_1)\mid \Theta_1}\}=0.
   \end{align*}
@@
    \mrm{E}\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
-   = \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}
-   &= \frac{1}{n}\sum_{i=2}^{n+1}\E{\E{\hat{\alpha}_i\mid \Theta}}\\
+   &= \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}
+   = \frac{1}{n}\sum_{i=2}^{n+1}\E{\E{\hat{\alpha}_i\mid \Theta}}\\
    &=  \frac{1}{n}\sum_{i=2}^{n+1}\E{\alpha_i}
@@
   R_{T_1^*+1,1}-R_{T_1^*+1,2}
-    &=\E{\alpha_1^2}-\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
-   & =\E{\alpha_1^2}-\E{\alpha_1^2}- \E{\hat{\alpha}_{\rm adj}^2}+2\E{\hat{\alpha}_{\rm adj}\alpha_1} \\
+    &=\E{\alpha_1^2}-\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2 \\
+    &=\E{\alpha_1^2}-\E{\alpha_1^2}- \E{\hat{\alpha}_{\rm adj}^2}+2\E{\hat{\alpha}_{\rm adj}\alpha_1} \\
     &= \mu_{\alpha}^2 - \var{\hat{\alpha}_{\rm adj}} 
@@
 \label{tablesappendix}
-\newpage
 

### 2021-01-28 Revision/manuscript.tex
revised manuscript and list with changes in red, and created separate checklist

@@
 
-\red{Check out this paragraph.} In our methodological framework, the researcher first creates a donor pool of time series which have undergone similar structural shocks in the past.
-Similarity in this context refers to the shock effects as arising from a common distribution with existing second moments.
-The unobserved shock effect in the time series of interest is assumed to arise from the same distribution.
+In our methodological framework, the researcher first creates a donor pool of time series which have undergone similar structural shocks in the past.
+\red{Similarity in this context refers to the shock effects as arising from a common distribution that has existing second moments and allows for varying variances and varying means that are linear functions of common covariates.} The unobserved shock effect in the time series of interest is assumed to arise from the same distribution.
 Construction of the donor pool and the desired aims of the donor pool has precedent in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
@@
 The Conoco Phillips example provides an empirical application of our methods when the shock is unprecedented in nature, arising from a global pandemic and an oil supply shock.
-The Apple example provides a case for post-shock prediction when the shock has precedent, Apple just released the latest version of their MacBook product.
-We now elaborate our framework for post-shock prediction.
+\red{The Apple example is about annual release of their MacBook products, and provides a case for post-shock prediction when the shock has precedent.} We now elaborate our framework for post-shock prediction.
 
@@
 In our framework we have assumed the covariates to be known.
-However, it may be the case that the shock effects the covariates as well as the response.
+However, it may be the case that the shock \red{affects} the covariates as well as the response.
 If so, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions.
@@
 Construction of the donor pool is a critical step in our post-shock prediction framework.
-In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for varying variances and  varying means that are linear functions of common covariates.
+In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from \red{the same distribution that allows} for varying variances and  varying means that are linear functions of common covariates.
 However, it may be difficult to confirm such an assumption or modeling structure in practice.

### 2021-01-28 Revision/responsetoAE.tex
revised manuscript and list with changes in red, and created separate checklist

--- 2021-01-25 Revision/list.tex
@@
 
-\title{Referee report checklist}
+\title{Response to Associate Editor's Comments}
 \author{Jilei Lin and Daniel J. Eck}
@@
 
-Thank you for the opportunity to resubmit at \emph{International Journal of Forecasting}.
-Thank you to the reviewers for comments that led to an improved version of this manuscript.
-We address all of the reviewers' comments below.
-An outline of each change made or a rebuttal is provided for all of the reviewers' comments.
+\textcolor{red}{Thank you for your helpful comments for our literature review and data analysis. We think they will help improve the quality of our manuscript a lot.}\\
 
-\section*{Editors}
-
----------------------------------------------------------------------------------------------------------------------------
-
-We have now received feedback on your manuscript from two reviewers as well as an Associate Editor.
-The reviewers' reports are attached to this message, while the AE's comments are included below this letter.
-
-Both reviewers and the AE agree that you address a relevant and interesting topic, and that your paper has the potential to provide a valuable addition to the forecaster's toolkit.
-That being said, the current version of the manuscript does not meet the publication standards of the IJF.
-A number of important points are raised by the reviewers that are either unclear or unresolved, and these need to be addressed.
-In addition, the Associate Editor provides some useful comments and suggestions, also pointing out that quite a substantial revision is required.
-
-In sum, I have decided to give you the opportunity to revise and resubmit your manuscript.
-Please do note that this is a "major revision".
-This means that, while we feel that the work presented in the manuscript might be of interest for the journal, re-submitting your manuscript does not necessarily mean it will be accepted, eventually.
-
----------------------------------------------------------------------------------------------------------------------------
-
-\response{Thank you for the opportunity to submit a revision. We include a point by point response for the comments and concerns raised by the reviwers.}
-
-\section*{Associate Editor}
-
-{\bf Comment:} Firstly, this contribution seems to me to be related to two exisiting strands of literature, neither of which is cited.
+{\bf Comment 1:} Firstly, this contribution seems to me to be related to two exisiting strands of literature, neither of which is cited.
 Describing the contribution relative to these literatures might help some readers better appreciate the achievements.
@@
 
-\newpage
-\section*{Reviewer 1: \texttt{Cover letter for authors.pdf}}
-
-Thank you very much for taking the time to provide a thoughtful review of our manuscript. We think that these comments will go a long way to improve the exposition of our manuscript. \\
-
-%% addressed
-{\bf  Comment 1:} How could the method be applied to forecast two or more period after a shock? \\
-
-\response{Thanks for pointing it out. The method can be extended to forecast two or more periods after a shock. There are two situations.  \\
-
-First, suppose that there is no additional shock after $T_1^* + 1$. From equation (1) in the manuscript, the forecast at time point $T_1^*+2$ is
-\begin{align*}
- \hat{y}_{i, T_i^* + 2} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+1}^{2} + \hat{\theta}_i'\mathbf{x}_{1, T_1^*+2}, \tag{*}
-\end{align*}
-where $\hat{y}_{1, T_1^*+1}^{2}=\hat{y}_{1, T_1^*+1}^{1} + \hat{\alpha}_{T_1^* + 1}$, $\hat{y}_{1, T_1^*+1}^{1}$ is the forecast without adjustment, $\mathbf{x}_{1, T_1^*+2}$ is either known or forecasted, and  $\hat{\alpha}_{T_1^* + 1}$ is the shock-effect estimator for the shock at $T_1^*+1$.
-The forecast for $d>2$ more periods is similarly stated as
-\begin{align*}
- \hat{y}_{i, T_i^* + d} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+d-1}+ \hat{\theta}_i'\mathbf{x}_{1, T_1^*+d},
-\end{align*}
-where $\mathbf{x}_{1, T_1^*+d}$ is either known or forecasted. \\
-
-Second, suppose that  there is one more shock effect after $T_1^*+1$, say, $\alpha_{T_1^* + d^*}$ for some $d^* > 1$.
-Without loss of generality, assume $d^* = 2$.
-Under our framework, users may want to construct another set of donor pool with time series that experienced shock effects similar to $\alpha_{T_1^* + 2}$.
-Next,  apply our proposed method to compute $\hat{\alpha}_{T_1^* + 2}$, the estimator for the shock effect at $T_1^* +2$.
-The forecast at the point $T_1^* + 2$ will be,
-\begin{align*}
- \hat{y}_{i, T_i^* + 2} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+1}^{2} + \hat{\theta}_1'\mathbf{x}_{1, T_1^*+2} + \hat{\alpha}_{T_1^* + 2}.
-\end{align*}
-These two cases can be further combined to generalize forecasting for two or more periods. We added aspects of this response to the Discussion.\\
-}
-
-{\bf Comment 2:} Page 3, line 30: \citet{blundell1998initial} model is a fixed effect dynamic panel and estimate the parameters using the panel analysis.
-It would be nice if you clarify in what sense your work is similar to them.
-\\
-
-\response{The model of \citet{blundell1998initial} is
-\begin{align*}
-  y_{it} = \alpha y_{i, t-1} + \beta_1'x_{it} + \beta_2'x_{it-1} + \eta_i + v_{it}, \quad i = 1, \ldots, N, \quad t = 2, \ldots, T.
-\end{align*}
-where $|\alpha|<1$. In contrast, our model is
-\begin{align*}
- y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mathbf{x}_{i,t} + \varepsilon_{i,t},
-\end{align*}
-where $|\phi_i| < 1$.
-Our model is similar to the one of \citet{blundell1998initial}  in the sense that we have the fixed-effect decomposition of the error term $\eta_i +\varepsilon_{i,t}$ and the autoregressive structure.
-However, our model allows for $\eta_i$ as random effects, different time lengths for each time series, different autoregressive parameters, and a shock component.
-To avoid confusion, we  remove this reference in the revised manuscript.}\\
-
-{\bf Comment 3:} Page 4, line 50: Your paper considers forecasting a time-series model.
-It is confusing for readers to read your sentence ”In this article, we consider a dynamic panel data model...''.\\
-
-\response{Sorry for the confusion. It is corrected  in the revised version.}\\
-
-{\bf  Comment 4:} Figures on page 5: Figure labels, (a) and (b), are missing. What does the black line in the top graph represent? Is it the realized observations?\\
-
-\response{Thanks for pointing it out.
-The labels (a) and (b) are now added in the revised manuscript.
-The \textcolor{black}{black} line stands for the realized observations whereas the violet line stands for the fitted values.} \\
-
-{\bf Comment 5:} Page 7, line 52: Are these time series estimates or panel data estimates?
-If panel estimators are used, then OLS estimators in this model results in inconsistency of the estimators.
-In that case, how wouldn't this inconsistency affect the results in section 3 about the unbiasedness?
-\\
-
-\response{Sorry for not making it clear.
-They are time series estimates or the ordinary least squares (OLS) estimates but not panel data estimates.
-In fact, our method can be generalized to any model whose parameter can be estimated in an unbiased fashion.
-In the second paragraph of Section 6, we wrote \\
-
-\begin{tcolorbox}
-`` Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.''
-\end{tcolorbox}
-
-%\vspace{0.4cm}In other words, if the estimator used in panel data is unbiased, our method can adapt to this scenario by weighting the shock effects estimated by panel data estimation procedure.
-In this case, the propositions in Section 3 still hold though the exact variance expressions will change since we are not using OLS estimators.}\\
-
-{\bf Comment 6:} Page 8, line 46: It is not clear to met how you estimate $\alpha_i$'s by OLS.
-Could you give the expressions for $\hat{\alpha}_i$?
-Also, how can you identify $\alpha_i$ from $\eta_i$?
-Isn't $\hat{\alpha}_{\rm adj}$ an estimator of $E(\alpha_1)$?
-\\
-
-\response{Sorry for not making it clear.
-The estimation procedures can be explained in detail as follows.
-Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series and $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$.
-We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{X}_{i})$.
-Then the expression for $\hat{\alpha}_i$ is
-\begin{align*}
-  \hat{\alpha}_i = [(\mathbf{M}'_i\mathbf{M}_i)^{-1}\mathbf{M}_i'\mathbf{Y}_{i}]_{2}, \quad 
-  \text{ where }\quad \mathbf{Y}_{i}=(y_{i,1},\ldots,y_{i,T_i})' 
- \quad  \text{ for } i = 2, \ldots, n+1,
-\end{align*}
-where $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Our model is
-\begin{align*}
-  y_{i,t} = \eta_i + \alpha_i D_{i,t} + \phi_i y_{i,t-1} + \theta_i'\mathbf{x}_{i,t} + \varepsilon_{i,t}, 
-  \quad i = 1, \ldots, n+1.
-\end{align*}
-$\eta_i$ represents the effect of the intercept.
-Thus, we cannot identify $\alpha_i$ from $\eta_i$.
-As defined in (4) in the manuscript, through averaging, $\hat{\alpha}_{\rm adj}$ is an estimator  of $E(\alpha_1)$.} \\
-
-{\bf Comment 7:} Page 9, line 10: It is not clear to me what $\mathbf{U}_i$'s are. An example could help understanding that better. \\
-
-\response{Thanks for pointing it out.
-We  clarify it in the revised version, and change the notation to be $\mathbf{M}_i$, which represents the design matrix of the model used in OLS estimation at the $i$th time series.} \\
-
-%For example, suppose the sample size for $i$th time series in the donor pool (i.e., $i\geq 2$) is 4; we have one covariate consisting of $x_1, \ldots, x_4$; and the shock occurs at $t = 4$.
-In this case, $\mathbf{U}_i$ is
-%\begin{align*}
-%  \mathbf{M}_i = \begin{pmatrix}
-%    1 & 0 & x_1 \\
-%    1 & 0 & x_2 \\
-%    1 & 0 & x_3 \\
-%    1 & 1 & x_4
-%  \end{pmatrix}.
-%\end{align*}
-%Suppose the sample size for the time series of interest is also 4, and we have a covariate $k_1, \ldots, k_4$.
-Note that the design matrix of the time series of interest will not contain $D_{1,t}$ since $D_{1,t}= I(t=T_1^*+1)=0$ due to we do not observe the shock.
-In this case,
-%\begin{align*}
-%  \mathbf{M}_1 = \begin{pmatrix}
-%    1 &  k_1 \\
-%    1 &  k_2 \\
-%    1 &  k_3 \\
-%    1 &  k_4
-%  \end{pmatrix}.
-%\end{align*}} \\
-
-{\bf Comment 8:} Page 9, line 15: Why the closed form expressions for $E(\hat{\alpha}_{\rm IVW})$ and $Var(\hat{\alpha}_{\rm IVW})$ are not provided? \\
-
-\response{In page 8, we wrote \\
-\begin{tcolorbox}
-''The inverse-variance weighted estimator is defined as 
-\begin{align*}
-  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
-  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{M}_i'\mathbf{M}_i)_{22}^{-1},
-\end{align*}
-where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
-$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
-and $\mathbf{M}_i$ is the design matrix for OLS with respect to time series 
-for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
-is required and the numerator and denominator terms are dependent in general.''
-\end{tcolorbox}
-To be more specific, $\hat{\sigma}_{i\alpha}$ depends on $\hat{\alpha}_i$.
-As a result, the numerator and denominator of $ \hat{\alpha}_{\rm IVW}$ are dependent.
-Without making distributional assumptions, it is impossible to evaluate $E(\hat{\alpha}_{\rm IVW})$ and $Var(\hat{\alpha}_{\rm IVW})$ in a closed form.}\\
-
-{\bf Comment 9:} Page 13, line 14: $\mu_{\alpha}$ is unknown, and in practice we have to estimate it. Would the results hold if one replaces $\mu_{\alpha}$ with its estimate? \\
-
-\response{We go for a plug-in approach.
-If we can estimate $\mu_{\alpha}$ well, the results should hold with high probability.
-Section 3.2 is dedicated to this estimation problem.
-Using plug-in approaches, we get a decision rule to determine whether the scalar adjustment will be beneficial with correctness probability $p$.
-Section 3.3 details the leave-one-out cross validation procedures, which are tailored to our setup, to estimate $p$.
-As a result, users can be informed about the credibility of our methods.} \\
-
-{\bf Comment 10:} Page 14, line 7: Shouldn’t $E(\alpha_1)$ be $\mu_{\alpha}$? Previously $\mu_{\alpha}$ was used.\\
-
-\response{In the line 7 at Page 14, $E(\alpha_1)$ is taken under $\mathcal{M}_{21}$ or $\mathcal{M}_{22}$.
-In contrast, $\mu_{\alpha}$ is used under $\mathcal{M}_{1}$.
-In Section 2.1, we define the distribution of $\alpha_i$ as
-\begin{align*}
-  &\alpha_i \sim \mathcal{F}_{\alpha} 
- \quad  \text{ with }\quad  E_{\mathcal{F}_{\alpha}}(\alpha_i) =\mu_{\alpha}, Var_{\mathcal{F}_{\alpha}}(\alpha_i)=\sigma^2_{\alpha},\quad   \text{iid under } \mathcal{M}_1\\
- & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{iid under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
-\end{align*}
-In other words,  $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ is an extended version of $\mathcal{M}_{1}$ by allowing it to depend on some covariates.
-However, in general, $E(\alpha_1)\neq \mu_{\alpha}$ under   $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ due to the presence of $\delta_i'\mathbf{x}_{i, T_i^*+1}$.} \\
-
-{\bf Comment 11:} Page 18, numerical example: The model setup does not contain the individual effects (intercepts) similar to the models in equations (1)-(2) on page 6.
-How would the result change if you include them with different variances?
-\\
-
-\response{The result wouldn't change.
-In fact, in our proof listed in the Appendix, we do not make use of the assumption that $\eta_i$ follows the same distribution.
-In other words, the results  still hold when the individual effects have different variances.}\\
-
-{\bf Comment 12:} Page 23, construction of donor pool: Your model assumes that the shocks have the same distribution.
-Given that these shocks are from different sources and happened because of various reasons, how could one justify them?
-Practically, there are many previous shocks.
-How can someone choose from them?\\
-
-%It is a good question.
-To clarify, $\mathcal{M}_1$ assumes that the shocks have the same distribution.
-However, $\mathcal{M}_{21}$ assumes the shocks have the same variance but have different conditional means with allowing covariates to play a role.
-Moreover, $\mathcal{M}_{22}$ assumes they have different conditional means and conditional variances by allowing $\delta_i$ to be random.
-But the shock effects are assumed to follow a general family of  unknown distribution with possible different means and variances.\\
-
-%$\mathcal{M}_{21}$ and $\mathcal{M}_{22}$ are constructed for generalization.
-In practice, it is hard to verify those assumptions.
-It leaves the discretion for users to construct donor pool by gathering time series experiencing similar events to the one the time series of interest experienced.
-\\
-
-%Theoretically, it is possible to verify the assumptions of $\mathcal{M}_{1}$ using empirical Bayes methods to some degree.
-First, we need a  pool of shock effects that users believe they are realizations from a common distribution, say, $\mathcal{F}_{\alpha}$.
-Using empirical Bayes methods, we can estimate $\mathcal{F}_{\alpha}$ to have $\hat{\mathcal{F}}_{\alpha}$.
-To verify whether the remaining shock effects are from $\mathcal{F}_{\alpha}$, we can check the quantile of $\hat{\mathcal{F}}_{\alpha}$ to judge whether they are extreme in $\hat{\mathcal{F}}_{\alpha}$.
-However, the theoretical justification for this approach is left for future research.
-\\
-
-\response{Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
-If this cannot be done, then the methodology may not work well.
-Practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool.
-Consider our Conoco Phillips example.
-On March 9th 2020, Conoco Phillips was expected to experience a negative shock in the midst of the  COVID-19 pandemic and an oil supply shock.
-While the COVID-19 pandemic is unprecedented, several economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises.
-On the other hand, the oil supply shock had precedent.
-As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.} \\
-
-{\bf Comment 13:} Figure 2 on Page 24: Are the black dots the real data? What does the line represent?\\
-
-\response{Thanks for pointing it out. We  clarify this in the revised version. The black dots represent the real data. The line in violet color represents the fitted line of our model.}
-
-\newpage
-
-\section*{Reviewer 2:  \texttt{MinimizingPostShockForestError\_IJF\_pdf}}
-
-Thank you for your appreciation of the potential of our methods, and for your valuable detailed comments.  We think these comments will help a lot in improving our manuscript.\\
-
-{\bf Comment 1:} The method hinges on the assumption that the time series forming the donor pool are independent from the time series under study prior to the shock.
-This seems to be a very restrictive assumption.
-The shocks that the donor pool have undergone in the past must be representative of the shock that the time series of interest is experiencing, but the series are independent.
-Given this restrictive assumption what practical applications are ruled out?
-\\
-
-\response{Yes.
-It could be a restrictive assumption in a number of situations.
-Panel data applications are ruled out.
-Additionally, if time series in a donor pool are observed in almost concurrent time as the one under study (or, the time differences are not large enough), the independence assumption may not hold.
-However, if the time differences between the time series under study and those forming the donor pool are large enough, then the dependence should be negligible.
-This is the case in our Conoco Phillips and Apple examples.} \\
-
-{\bf Comment 2:} It would be helpful to the reader to be very explicit about the timing of when information is realized.
-Is it correct that the researcher knows at $T_1^*$ that there will be a shock at $T_1^* + 1$, and they know the type of shock that it will be in order to identify the relevant donor pool shocks, but they do not know the magnitude?
-This is quite an informational advantage over unanticipated shocks.
-In many situations one could imagine that the shock was unanticipated.
-Therefore, at $T_1^* + 1$  there is a large forecast error (your model 1) but now information is available about the type of shock, so the proposed methodology of the shock effect estimator is applied at $T_1^* + 2$, yielding gains over the unadjusted forecast.
-The timing of information is crucial, but the methodology proposed in the paper seems to be applicable in many different timing scenarios.
-\\
-
-\response{It is correct that the researcher knows at $T_1^*$ that there will be a shock at $T_1^* + 1$.
-In practice, it usually happens to the case that when we realize that the shock is about to occur, we  know the \emph{general type}  or \emph{general cause} of the shock.
-The magnitude is not known.
-%For example, in the Conoco Phillips stock example, when we knew the outbreak of COVID-19 was about to come, past shocks related to financial crisis may be helpful.
-Or, near the outbreak of COVID-19, suppose that a department in a university realized that it would be faced with declining applications.
-It could make use of the information about the decline of its admitted students in the past or that of other departments when similar situations (i.e., the number of applications suddenly decreases) happened.\\
-We admit that it is quite an informational advantage over unanticipated shocks.
-However, in practice, if a shock is unanticipated, we may not even be able to construct such a post-shock analysis since we do not know it is about to happen.\\
-
-You are right about the timing.
-Our methodology can be applicable in many different timing scenarios.
-Generally, suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$ and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$.
-It is possible to generalize our method to this situation.
-Our new Apple example in Section 5.2 of the revised manuscript provides an example for the case $d=2$ with predicted covariates.
-\\
-
-Thank you for your remark on the timing scenarios. It is very helpful for improving our manuscript.} \\
-
-{\bf Comment 3:} Related to the point above, the model applied is an AR(1) with contemporaneous regressors.
-This structure requires the covariates to be known in the future for \emph{ex ante} forecasts, or for them to be forecast.
-The set-up assumes θ1 to be well behaved and the covariates are not subject to shocks if they need to be forecast.
-Empirically, we could also think of cases where the mean shift $D_{i,t}$ interacted with the covariates which would give an additional forecast error via $\mathbf{x}_{1, T_1^* + 1}$.
-The theoretical results seem to hinge on known $\mathbf{x}_{1,t}$ entering contemporaneously to derive unbiasedness.
-What are the implications of the covariates needing to be forecast?
-\\
-
-\response{It is a very good point.
-Thanks for pointing it out.
-Indeed, our method assumes $\mathbf{x}_{1, T_1^* + 1}$ to be given.
-If it is to be forecasted with errors, it will possibly result in a biased estimation of $E(\alpha_1)$ with $\hat{\alpha}_{\rm wadj}$ such that the evaluation of the proposition may not be reliable.
-\\
-
-In fact, the situation when  covariates are forecasted with errors is similar to the one when the variance of the shock effect is large.
-In both situations, the signal from covariates is weak.
-Our simulation discusses this situation by increasing $\sigma_{\alpha}$.
-It shows that a slightly weak signal will not compromise the correctness of our evaluated propositions a lot.
-However, if the forecast for the covariates is seriously bad (i.e., the signal from covariates is really weak), our result shows that the risk-reduction evaluation may be only as good as a random guess.
-\\
-
-In the event that the mean shift $D_{i,t}$ interacts with the covariates, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions.
-In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed.
-A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid.
-This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid.
-} \\
-
-{\bf Comment 4:} Given the dynamic structure, what happens after $T_1^*+1$?
-Couldn't you use the donor pool shocks to estimate the shock transition (e.g.
-apply the shock effect estimator to the m periods following the shock), and produce an intercept correction dummy for the next $m$ periods?
-It would be interesting empirically to see if the shock is anticipated to be permanent or transitory.
-I wonder if the theoretical statements of when forecast risk is minimized may be adapted to assess when transitory shocks die out such that the unadjusted forecast is preferable again?
-\\
-
-\response{In our setup, we only model the time series under study up to $t = 1, \ldots, T_1^*+1$.
-We do not know what happened  after $T_1^*+1$.
-It is possible that there are no shocks or additional shocks after $T_1^*+1$.
-\\
-
-It is possible to use the donor pool to estimate the shock transition,  and produce an intercept dummy for the next $m$ periods.
-Assume there are no additional shocks  after $T_1^*+1$, and $T_i^*+m \leq T_i$ for $i = 2, \ldots, n+1$.
-Consider the model
-\begin{align*}
-  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i, T_i^* + d}I(t = T_i^*+d) +\varepsilon_{i,t}
-\end{align*}
-for $i = 2, \ldots, n+1$ and $d = 1, \ldots, m$.
-Suppose we have information of the covariates up to $T_1^*+d$ either by given information or by forecasting.
-We can use our proposed synthetic control method to compute weights $\mathbf{W}^*$ and OLS to estimate $\beta_{i, T_i^*+d}$ to compute $\hat{\beta}_{1, T_1^*+d}$.
-As a result, we obtain $\hat{\boldsymbol{\beta}}_1^{(m)} = (\hat{\beta}_{1, T_1^*+d})_{d = 1}^m$.
-However, it cannot be a simple intercept dummy but instead an iterative adjustment in computing $m$-ahead forecasts.
-For example, $\hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)}+ \hat{\beta}_{1, T_1^*+2}$, where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts.
-%considering $\hat{y}_{1, T_1^*+1}^{(1)}$ in computation.
-The approach of \cite{agarwal2020two} is an alternative  to this problem though its adjustment is without theoretical guarantees. \\
-
-%To judge if the shock is permanent, we may consider another approach. Consider the model
-%\begin{align*}
-%  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i}I(T_i^*< t \leq  T_i^*+d) +\varepsilon_{i,t}.
-%\end{align*}
-%We can compute $\hat{\beta}_i$ from OLS and $\mathbf{W}^*$ from synthetic approach with covariates $d \times p$ (see for example of $p = 2$ in our added Apple example in Section 5.2 of revised transcript) to compute $\hat{\beta}_1$.
-Note that $\hat{\beta}_1$ is unbiased.
-We can use parametric double bootstrap to test the hypothesis that $H_0 \colon \beta_1=0$ versus $H_1 \colon \beta_1\neq 0$ at time point $T^*_i+d$.
-\\
-
-To the best of our knowledge, we don't know whether the theoretical statements of our proposed methods in the manuscript can be adapted to assess when transitory shocks die out.
-This is beyond the scope of our current paper.} \\
-
-{\bf Comment 5:} While the simulations were useful, I found the discussion in section 4 quite impenetrable.
-There are so many decisions that a researcher would need to make, including which weighting method and all the bootstrapping and leave-one-out decisions.
-It would be very helpful to the reader if you could give a summary of all your results stating your preferred user decisions for generic specifications.
-\\
-
-\response{Thank you for pointing it out.
-We polished Section 4 for better readability in the revised manuscript.
-We  summarize  our results including preferred user decisions as below.
-There are mainly three decisions to make for an user: to choose
-  \begin{itemize}
-    \item among  $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, and $\hat{\alpha}_{\rm wadj}$ 
-    \item between $\mathcal{B}_f$ and $\mathcal{B}_u$ (see detailed definition in Section 3.2)
-    \item The $k$ in the $k$ random draws in LOOCV
-  \end{itemize}
-  First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution.
-Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool.
-Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.
-These recommendations are included in Remark 3 at the end of Section 2.
-\\
-
-  The selection between $\mathcal{B}_f$ and $\mathcal{B}_u$ is more of a philosophical question. In Section 3.2,  we noted
-
-  \begin{tcolorbox}
-  $\mathcal{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast, $\mathcal{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness arises from parameters and idiosyncratic error.
-  \end{tcolorbox}
-
-In Section 4.3, we found that $\mathcal{B}_u$ is better than $\mathcal{B}_f$ when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is large.
-Otherwise, they are nearly the same.
-\\
-
-At the end of Section 4.3, we noted that when $p < n$, there are infinitely many solutions to $\mathbf{W}^*$ such that $\mathbf{W}^*$ will take values on the boundary of $\mathcal{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\rm wadj}$ \citep{andrews2000inconsistency}.
-$\mathcal{B}_f$  is immune to this issue.
-However, our simulation results in the Supplementary Materials show that the non-uniqueness does not seriously compromise the inference.
-\\
-
-In summary, $\mathcal{B}_u$ is preferred when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is \emph{believed} to be large.
-If $p < n$ and non-uniqueness problem is of concern due to theoretical reasons,  $\mathcal{B}_f$ is preferred.
-In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.
-This explanation is added to the end of Section 4.
-\\
-
-%Lastly,  greater number of bootstrap replication $B$ is preferred. Usually, $B = 200$ is sufficient. 
-Ideally, $k=n$ is preferred.
-However, if the data size is large such that $k=n$ is computationally expensive, we found that $k = 5$ or $k = 10$ works well.
-In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool.
-} \\
-
-{\bf Comment 6:} Section 2 is hard to read without defining the terms that come in the second para- graph of section 2.1 (lines 19-23 of p.6). I'd suggest moving this to the beginning of section 2. \\
-
-\response{Sorry for not making it clear.
-The terms not defined in the caption of Figure 1 are now defined in the revised manuscript.
-For other parts, we find there are no terms that are not defined.
-The beginning parts of Section 2 are intended to give a general picture to the reader that our method is in fact general whereas the setup we investigate in Section 2.1 is a special case.
-}
-
 \bibliography{synthetic-prediction-notes}

### 2021-01-28 Revision/responsetoMinimizingPostShockForestErrorIJF.tex
revised manuscript and list with changes in red, and created separate checklist

--- 2021-01-27 Revision/list.tex
@@
 
-\title{Referee report checklist}
+\title{Response to Reviewer 2:  \texttt{MinimizingPostShockForestError\_IJF\_pdf}}
 \author{Jilei Lin and Daniel J. Eck}
@@
 \maketitle
-
-Thank you for the opportunity to resubmit at \emph{International Journal of Forecasting}.
-Thank you to the reviewers for comments that led to an improved version of this manuscript.
-We address all of the reviewers' comments below.
-An outline of each change made or a rebuttal is provided for all of the reviewers' comments.
-
-\section*{Editors}
-
----------------------------------------------------------------------------------------------------------------------------
-
-We have now received feedback on your manuscript from two reviewers as well as an Associate Editor.
-The reviewers' reports are attached to this message, while the AE's comments are included below this letter.
-
-Both reviewers and the AE agree that you address a relevant and interesting topic, and that your paper has the potential to provide a valuable addition to the forecaster's toolkit.
-That being said, the current version of the manuscript does not meet the publication standards of the IJF.
-A number of important points are raised by the reviewers that are either unclear or unresolved, and these need to be addressed.
-In addition, the Associate Editor provides some useful comments and suggestions, also pointing out that quite a substantial revision is required.
-
-In sum, I have decided to give you the opportunity to revise and resubmit your manuscript.
-Please do note that this is a "major revision".
-This means that, while we feel that the work presented in the manuscript might be of interest for the journal, re-submitting your manuscript does not necessarily mean it will be accepted, eventually.
-
----------------------------------------------------------------------------------------------------------------------------
-
-\response{Thank you for the opportunity to submit a revision. We include a point by point response for the comments and concerns raised by the reviwers.}
-
-\section*{Associate Editor}
-
-{\bf Comment:} Firstly, this contribution seems to me to be related to two exisiting strands of literature, neither of which is cited.
-Describing the contribution relative to these literatures might help some readers better appreciate the achievements.
-These are the literatures on "ad hoc" model adjustments for breaks, see e.g.,  \cite{clements1996intercept} for an early contribution, and \cite{castle2015robust} for a more recent example.
-The second is to do with outliers (innovation, additive and level shifts) in ARMA models, see e.g., \cite{tsay1986time}.
-Comparing/contrasting the approach in the paper with these literatures may be illuminating.
-\\
-
-\response{Thanks for pointing it out. The discussion of those papers is included in the introduction section of the revised manuscript.}\\
-
-{\bf Comment 2:} Secondly, a single empirical example is presented. I would like to see the results for a range of series - this would generate confidence in the proposed approach. \\
-
-\response{We include another example in which we forecast the stock price of Apple Inc.
-after the latest release of their MacBook product in 2020.
-This example is included in Section 5.2 of the revised manuscript.
-In this example, the donor pool includes three past time series of  Apple inc.'s stock price surrounding previous releases of the MacBook.
-In this example, the shock is with precedent and our method is expected to work well.
-This is because Apple Inc.
-is a well-established company that did not revolutionize the MacBook product in their last three releases.
-Apple Inc.
-mostly focused on upgrading the hardware in the MacBook, this same is true for the latest release.
-Our adjusted forecast performs very well in this setting, as expected.
-This example is representative for a class of problems involving shocks that are very similar to those in the past.
-In contrast, the example of Conoco Phillips is without precedent.
-In the past, Conoco Phillips  did not experience a financial crisis shock caused by a pandemic supplemented with an oil price shock.
-In the Conoco Phillips example, our method is better than the original forecast, although we do not fully recover the yet to be observed stock price.
-We hope that the addition of the Apple example helps to generate confidence in our approach.}
-
-\newpage
-\section*{Reviewer 1: \texttt{Cover letter for authors.pdf}}
-
-Thank you very much for taking the time to provide a thoughtful review of our manuscript. We think that these comments will go a long way to improve the exposition of our manuscript. \\
-
-%% addressed
-{\bf  Comment 1:} How could the method be applied to forecast two or more period after a shock? \\
-
-\response{Thanks for pointing it out. The method can be extended to forecast two or more periods after a shock. There are two situations.  \\
-
-First, suppose that there is no additional shock after $T_1^* + 1$. From equation (1) in the manuscript, the forecast at time point $T_1^*+2$ is
-\begin{align*}
- \hat{y}_{i, T_i^* + 2} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+1}^{2} + \hat{\theta}_i'\mathbf{x}_{1, T_1^*+2}, \tag{*}
-\end{align*}
-where $\hat{y}_{1, T_1^*+1}^{2}=\hat{y}_{1, T_1^*+1}^{1} + \hat{\alpha}_{T_1^* + 1}$, $\hat{y}_{1, T_1^*+1}^{1}$ is the forecast without adjustment, $\mathbf{x}_{1, T_1^*+2}$ is either known or forecasted, and  $\hat{\alpha}_{T_1^* + 1}$ is the shock-effect estimator for the shock at $T_1^*+1$.
-The forecast for $d>2$ more periods is similarly stated as
-\begin{align*}
- \hat{y}_{i, T_i^* + d} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+d-1}+ \hat{\theta}_i'\mathbf{x}_{1, T_1^*+d},
-\end{align*}
-where $\mathbf{x}_{1, T_1^*+d}$ is either known or forecasted. \\
-
-Second, suppose that  there is one more shock effect after $T_1^*+1$, say, $\alpha_{T_1^* + d^*}$ for some $d^* > 1$.
-Without loss of generality, assume $d^* = 2$.
-Under our framework, users may want to construct another set of donor pool with time series that experienced shock effects similar to $\alpha_{T_1^* + 2}$.
-Next,  apply our proposed method to compute $\hat{\alpha}_{T_1^* + 2}$, the estimator for the shock effect at $T_1^* +2$.
-The forecast at the point $T_1^* + 2$ will be,
-\begin{align*}
- \hat{y}_{i, T_i^* + 2} = \hat{\eta}_1 + \hat{\phi}_i \hat{y}_{1, T_1^*+1}^{2} + \hat{\theta}_1'\mathbf{x}_{1, T_1^*+2} + \hat{\alpha}_{T_1^* + 2}.
-\end{align*}
-These two cases can be further combined to generalize forecasting for two or more periods. We added aspects of this response to the Discussion.\\
-}
-
-{\bf Comment 2:} Page 3, line 30: \citet{blundell1998initial} model is a fixed effect dynamic panel and estimate the parameters using the panel analysis.
-It would be nice if you clarify in what sense your work is similar to them.
-\\
-
-\response{The model of \citet{blundell1998initial} is
-\begin{align*}
-  y_{it} = \alpha y_{i, t-1} + \beta_1'x_{it} + \beta_2'x_{it-1} + \eta_i + v_{it}, \quad i = 1, \ldots, N, \quad t = 2, \ldots, T.
-\end{align*}
-where $|\alpha|<1$. In contrast, our model is
-\begin{align*}
- y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mathbf{x}_{i,t} + \varepsilon_{i,t},
-\end{align*}
-where $|\phi_i| < 1$.
-Our model is similar to the one of \citet{blundell1998initial}  in the sense that we have the fixed-effect decomposition of the error term $\eta_i +\varepsilon_{i,t}$ and the autoregressive structure.
-However, our model allows for $\eta_i$ as random effects, different time lengths for each time series, different autoregressive parameters, and a shock component.
-To avoid confusion, we  remove this reference in the revised manuscript.}\\
-
-{\bf Comment 3:} Page 4, line 50: Your paper considers forecasting a time-series model.
-It is confusing for readers to read your sentence ”In this article, we consider a dynamic panel data model...''.\\
-
-\response{Sorry for the confusion. It is corrected  in the revised version.}\\
-
-{\bf  Comment 4:} Figures on page 5: Figure labels, (a) and (b), are missing. What does the black line in the top graph represent? Is it the realized observations?\\
-
-\response{Thanks for pointing it out.
-The labels (a) and (b) are now added in the revised manuscript.
-The black line stands for the realized observations whereas the violet line stands for the fitted values.} \\
-
-{\bf Comment 5:} Page 7, line 52: Are these time series estimates or panel data estimates?
-If panel estimators are used, then OLS estimators in this model results in inconsistency of the estimators.
-In that case, how wouldn't this inconsistency affect the results in section 3 about the unbiasedness?
-\\
-
-\response{Sorry for not making it clear.
-They are time series estimates or the ordinary least squares (OLS) estimates but not panel data estimates.
-In fact, our method can be generalized to any model whose parameter can be estimated in an unbiased fashion.
-In the second paragraph of Section 6, we wrote \\
-
-\begin{tcolorbox}
-``Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.''
-\end{tcolorbox}} \\
-
-%\vspace{0.4cm}In other words, if the estimator used in panel data is unbiased, our method can adapt to this scenario by weighting the shock effects estimated by panel data estimation procedure.
-In this case, the propositions in Section 3 still hold though the exact variance expressions will change since we are not using OLS estimators.}\\
-
-{\bf Comment 6:} Page 8, line 46: It is not clear to met how you estimate $\alpha_i$'s by OLS.
-Could you give the expressions for $\hat{\alpha}_i$?
-Also, how can you identify $\alpha_i$ from $\eta_i$?
-Isn't $\hat{\alpha}_{\rm adj}$ an estimator of $E(\alpha_1)$?
-\\
-
-\response{Sorry for not making it clear.
-The estimation procedures can be explained in detail as follows.
-Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{Y}_i^{(1)}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series, $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$, and $\mathbf{Y}_i^{(1)}$ is the lagged response $(y_{i,1},\ldots,y_{i,T_i})'$.
-We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{Y}_i^{(1)}, \mathbf{X}_{i})$.
-Then the expression for $\hat{\alpha}_i$ is
-\begin{align*}
-  \hat{\alpha}_i = [(\mathbf{M}'_i\mathbf{M}_i)^{-1}\mathbf{M}_i'\mathbf{Y}_{i}]_{2}, 
- \quad  \text{ for } i = 2, \ldots, n+1,
-\end{align*}
-where $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Our model is
-\begin{align*}
-  y_{i,t} = \eta_i + \alpha_i D_{i,t} + \phi_i y_{i,t-1} + \theta_i'\mathbf{x}_{i,t} + \varepsilon_{i,t}, 
-  \quad i = 1, \ldots, n+1.
-\end{align*}
-the intercept is denoted as $\eta_i$.
-Thus, we cannot identify $\alpha_i$ from $\eta_i$.
-As defined in (4) in the manuscript, through averaging, $\hat{\alpha}_{\rm adj}$ is an estimator  of $E(\alpha_1)$.} \\
-
-{\bf Comment 7:} Page 9, line 10: It is not clear to me what $\mathbf{U}_i$'s are. An example could help understanding that better. \\
-
-\response{Thanks for pointing it out.
-This quantity is the model (design) matrix corresponding to the $i$th time series.
-We clarify this quantity the revised version, and we change the notation to be $\mathbf{M}_i$.
-Our previous response describes $\mathbf{M}_i$ in more detail.} \\
-
-%For example, suppose the sample size for $i$th time series in the donor pool (i.e., $i\geq 2$) is 4; we have one covariate consisting of $x_1, \ldots, x_4$; and the shock occurs at $t = 4$.
-In this case, $\mathbf{U}_i$ is
-%\begin{align*}
-%  \mathbf{M}_i = \begin{pmatrix}
-%    1 & 0 & x_1 \\
-%    1 & 0 & x_2 \\
-%    1 & 0 & x_3 \\
-%    1 & 1 & x_4
-%  \end{pmatrix}.
-%\end{align*}
-%Suppose the sample size for the time series of interest is also 4, and we have a covariate $k_1, \ldots, k_4$.
-Note that the design matrix of the time series of interest will not contain $D_{1,t}$ since $D_{1,t}= I(t=T_1^*+1)=0$ due to we do not observe the shock.
-In this case,
-%\begin{align*}
-%  \mathbf{M}_1 = \begin{pmatrix}
-%    1 &  k_1 \\
-%    1 &  k_2 \\
-%    1 &  k_3 \\
-%    1 &  k_4
-%  \end{pmatrix}.
-%\end{align*}} \\
-
-{\bf Comment 8:} Page 9, line 15: Why the closed form expressions for $E(\hat{\alpha}_{\rm IVW})$ and $Var(\hat{\alpha}_{\rm IVW})$ are not provided? \\
-
-\response{In page 8, we wrote \\
-\begin{tcolorbox}
-''The inverse-variance weighted estimator is defined as 
-\begin{align*}
-  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
-  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{M}_i'\mathbf{M}_i)_{22}^{-1},
-\end{align*}
-where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
-$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
-and $\mathbf{M}_i$ is the design matrix for OLS with respect to time series 
-for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
-is required and the numerator and denominator terms are dependent in general.''
-\end{tcolorbox}
-To be more specific, $\hat{\sigma}_{i\alpha}$ depends on $\hat{\alpha}_i$.
-As a result, the numerator and denominator of $ \hat{\alpha}_{\rm IVW}$ are dependent.
-Without making distributional assumptions, it is impossible to evaluate $E(\hat{\alpha}_{\rm IVW})$ and $Var(\hat{\alpha}_{\rm IVW})$ in a closed form.}\\
-
-{\bf Comment 9:} Page 13, line 14: $\mu_{\alpha}$ is unknown, and in practice we have to estimate it. Would the results hold if one replaces $\mu_{\alpha}$ with its estimate? \\
-
-\response{We go for a plug-in approach.
-If we can estimate $\mu_{\alpha}$ well, the results should hold with high probability.
-Section 3.2 is dedicated to this estimation problem.
-Using plug-in approaches, we get a decision rule to determine whether the scalar adjustment will be beneficial with correctness probability $p$.
-Section 3.3 details the leave-one-out cross validation procedures, which are tailored to our setup, to estimate $p$.
-As a result, users can be informed about the credibility of our methods.} \\
-
-{\bf Comment 10:} Page 14, line 7: Shouldn’t $E(\alpha_1)$ be $\mu_{\alpha}$? Previously $\mu_{\alpha}$ was used.\\
-
-\response{In the line 7 at Page 14, $E(\alpha_1)$ is taken under $\mathcal{M}_{21}$ or $\mathcal{M}_{22}$.
-In contrast, $\mu_{\alpha}$ is used under $\mathcal{M}_{1}$.
-In Section 2.1, we define the distribution of $\alpha_i$ as
-\begin{align*}
-  &\alpha_i \sim \mathcal{F}_{\alpha} 
- \quad  \text{ with }\quad  E_{\mathcal{F}_{\alpha}}(\alpha_i) =\mu_{\alpha}, Var_{\mathcal{F}_{\alpha}}(\alpha_i)=\sigma^2_{\alpha},\quad   \text{iid under } \mathcal{M}_1\\
- & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{iid under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
-\end{align*}
-In other words,  $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ is an extended version of $\mathcal{M}_{1}$ by allowing it to depend on some covariates.
-However, in general, $E(\alpha_1)\neq \mu_{\alpha}$ under   $\mathcal{M}_{21}$  or $\mathcal{M}_{22}$ due to the presence of $\delta_i'\mathbf{x}_{i, T_i^*+1}$.}\\
-
-{\bf Comment 11:} Page 18, numerical example: The model setup does not contain the individual effects (intercepts) similar to the models in equations (1)-(2) on page 6.
-How would the result change if you include them with different variances?
-\\
-
-\response{The result wouldn't change.
-In fact, in our proof listed in the Appendix, we do not make use of the assumption that $\eta_i$ follows the same distribution.
-In other words, the results  still hold when the individual effects have different variances.}\\
-
-{\bf Comment 12:} Page 23, construction of donor pool: Your model assumes that the shocks have the same distribution.
-Given that these shocks are from different sources and happened because of various reasons, how could one justify them?
-Practically, there are many previous shocks.
-How can someone choose from them?\\
-
-%It is a good question.
-To clarify, $\mathcal{M}_1$ assumes that the shocks have the same distribution.
-However, $\mathcal{M}_{21}$ assumes the shocks have the same variance but have different conditional means with allowing covariates to play a role.
-Moreover, $\mathcal{M}_{22}$ assumes they have different conditional means and conditional variances by allowing $\delta_i$ to be random.
-But the shock effects are assumed to follow a general family of  unknown distribution with possible different means and variances.\\
-
-%$\mathcal{M}_{21}$ and $\mathcal{M}_{22}$ are constructed for generalization.
-In practice, it is hard to verify those assumptions.
-It leaves the discretion for users to construct donor pool by gathering time series experiencing similar events to the one the time series of interest experienced.
-\\
-
-%Theoretically, it is possible to verify the assumptions of $\mathcal{M}_{1}$ using empirical Bayes methods to some degree.
-First, we need a  pool of shock effects that users believe they are realizations from a common distribution, say, $\mathcal{F}_{\alpha}$.
-Using empirical Bayes methods, we can estimate $\mathcal{F}_{\alpha}$ to have $\hat{\mathcal{F}}_{\alpha}$.
-To verify whether the remaining shock effects are from $\mathcal{F}_{\alpha}$, we can check the quantile of $\hat{\mathcal{F}}_{\alpha}$ to judge whether they are extreme in $\hat{\mathcal{F}}_{\alpha}$.
-However, the theoretical justification for this approach is left for future research.
-\\
-
- Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
-If this cannot be done, then the methodology may fail.
-In real-life applications, practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool.
-Consider our Conoco Phillips example.
-On March 9th 2020, Conoco Phillips was expected to experience a negative shock in the midst of the  COVID-19 pandemic and an oil supply shock.
-While the COVID-19 pandemic is unprecedented, several, although not all, economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises.
-On the other hand, the oil supply shock had precedent.
-As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.
-\\
-
-{\bf Comment 13:} Figure 2 on Page 24: Are the black dots the real data? What does the line represent?\\
-
-\response{Thanks for pointing it out. We  clarify this in the revised version. The black dots represent the real data. The line in violet color represents the fitted line of our model.}
-
-\newpage
-
-\section*{Reviewer 2:  \texttt{MinimizingPostShockForestError\_IJF\_pdf}}
 
@@
 If it is to be forecasted with errors, it will possibly result in a biased estimation of $E(\alpha_1)$ with $\hat{\alpha}_{\rm wadj}$ such that the evaluation of the proposition may not be reliable.
-\\
+\textcolor{red}{Moreover, the forecast error from covariates contributes to more error in the unadjusted forecast, and thus in the post-shock one.}\\
 
@@
 We  summarize  our results including preferred user decisions as below.
-There are mainly three decisions to make for an user: to choose
+There are mainly three decisions to make for an user to choose
   \begin{itemize}
@@
     \item between $\mathcal{B}_f$ and $\mathcal{B}_u$ (see detailed definition in Section 3.2)
-    \item The $k$ in the $k$ random draws in LOOCV
+    \item the $k$ in the $k$ random draws in LOOCV
   \end{itemize}

### 2021-01-28 Revision/responsetocoverletterforautor.tex
revised manuscript and list with changes in red, and created separate checklist

--- 2021-01-27 Revision/list.tex
@@
 
-\title{Referee report checklist}
+\title{Response to Reviewer 1: \texttt{Cover letter for authors.pdf}}
 \author{Jilei Lin and Daniel J. Eck}
@@
 \maketitle
-
-Thank you for the opportunity to resubmit at \emph{International Journal of Forecasting}.
-Thank you to the reviewers for comments that led to an improved version of this manuscript.
-We address all of the reviewers' comments below.
-An outline of each change made or a rebuttal is provided for all of the reviewers' comments.
-
-\section*{Editors}
-
----------------------------------------------------------------------------------------------------------------------------
-
-We have now received feedback on your manuscript from two reviewers as well as an Associate Editor.
-The reviewers' reports are attached to this message, while the AE's comments are included below this letter.
-
-Both reviewers and the AE agree that you address a relevant and interesting topic, and that your paper has the potential to provide a valuable addition to the forecaster's toolkit.
-That being said, the current version of the manuscript does not meet the publication standards of the IJF.
-A number of important points are raised by the reviewers that are either unclear or unresolved, and these need to be addressed.
-In addition, the Associate Editor provides some useful comments and suggestions, also pointing out that quite a substantial revision is required.
-
-In sum, I have decided to give you the opportunity to revise and resubmit your manuscript.
-Please do note that this is a "major revision".
-This means that, while we feel that the work presented in the manuscript might be of interest for the journal, re-submitting your manuscript does not necessarily mean it will be accepted, eventually.
-
----------------------------------------------------------------------------------------------------------------------------
-
-\response{Thank you for the opportunity to submit a revision. We include a point by point response for the comments and concerns raised by the reviwers.}
-
-\section*{Associate Editor}
-
-{\bf Comment:} Firstly, this contribution seems to me to be related to two exisiting strands of literature, neither of which is cited.
-Describing the contribution relative to these literatures might help some readers better appreciate the achievements.
-These are the literatures on "ad hoc" model adjustments for breaks, see e.g.,  \cite{clements1996intercept} for an early contribution, and \cite{castle2015robust} for a more recent example.
-The second is to do with outliers (innovation, additive and level shifts) in ARMA models, see e.g., \cite{tsay1986time}.
-Comparing/contrasting the approach in the paper with these literatures may be illuminating.
-\\
-
-\response{Thanks for pointing it out. The discussion of those papers is included in the introduction section of the revised manuscript.}\\
-
-{\bf Comment 2:} Secondly, a single empirical example is presented. I would like to see the results for a range of series - this would generate confidence in the proposed approach. \\
-
-\response{We include another example in which we forecast the stock price of Apple Inc.
-after the latest release of their MacBook product in 2020.
-This example is included in Section 5.2 of the revised manuscript.
-In this example, the donor pool includes three past time series of  Apple inc.'s stock price surrounding previous releases of the MacBook.
-In this example, the shock is with precedent and our method is expected to work well.
-This is because Apple Inc.
-is a well-established company that did not revolutionize the MacBook product in their last three releases.
-Apple Inc.
-mostly focused on upgrading the hardware in the MacBook, this same is true for the latest release.
-Our adjusted forecast performs very well in this setting, as expected.
-This example is representative for a class of problems involving shocks that are very similar to those in the past.
-In contrast, the example of Conoco Phillips is without precedent.
-In the past, Conoco Phillips  did not experience a financial crisis shock caused by a pandemic supplemented with an oil price shock.
-In the Conoco Phillips example, our method is better than the original forecast, although we do not fully recover the yet to be observed stock price.
-We hope that the addition of the Apple example helps to generate confidence in our approach.}
-
-\newpage
-\section*{Reviewer 1: \texttt{Cover letter for authors.pdf}}
 
@@
  \quad  \text{ with }\quad  E_{\mathcal{F}_{\alpha}}(\alpha_i) =\mu_{\alpha}, Var_{\mathcal{F}_{\alpha}}(\alpha_i)=\sigma^2_{\alpha},\quad   \text{iid under } \mathcal{M}_1\\
- & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{iid under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
+ & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{\textcolor{red}{independent} under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
 \end{align*}
@@
 
- Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
+ \response{Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects.
 If this cannot be done, then the methodology may fail.
@@
 As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.
-\\
+}\\
 
@@
 
-\newpage
-
-\section*{Reviewer 2:  \texttt{MinimizingPostShockForestError\_IJF\_pdf}}
-
-Thank you for your appreciation of the potential of our methods, and for your valuable detailed comments.  We think these comments will help a lot in improving our manuscript.\\
-
-{\bf Comment 1:} The method hinges on the assumption that the time series forming the donor pool are independent from the time series under study prior to the shock.
-This seems to be a very restrictive assumption.
-The shocks that the donor pool have undergone in the past must be representative of the shock that the time series of interest is experiencing, but the series are independent.
-Given this restrictive assumption what practical applications are ruled out?
-\\
-
-\response{Yes.
-It could be a restrictive assumption in a number of situations.
-Panel data applications are ruled out.
-Additionally, if time series in a donor pool are observed in almost concurrent time as the one under study (or, the time differences are not large enough), the independence assumption may not hold.
-However, if the time differences between the time series under study and those forming the donor pool are large enough, then the dependence should be negligible.
-This is the case in our Conoco Phillips and Apple examples.
-We include this discussion in the Introduction.
-Thank you for this comment.} \\
-
-{\bf Comment 2:} It would be helpful to the reader to be very explicit about the timing of when information is realized.
-Is it correct that the researcher knows at $T_1^*$ that there will be a shock at $T_1^* + 1$, and they know the type of shock that it will be in order to identify the relevant donor pool shocks, but they do not know the magnitude?
-This is quite an informational advantage over unanticipated shocks.
-In many situations one could imagine that the shock was unanticipated.
-Therefore, at $T_1^* + 1$  there is a large forecast error (your model 1) but now information is available about the type of shock, so the proposed methodology of the shock effect estimator is applied at $T_1^* + 2$, yielding gains over the unadjusted forecast.
-The timing of information is crucial, but the methodology proposed in the paper seems to be applicable in many different timing scenarios.
-\\
-
-\response{It is correct that the researcher knows at $T_1^*$ that there will be a shock at $T_1^* + 1$.
-In practice, it usually happens to the case that when we realize that the shock is about to occur, we  know the \emph{general type}  or \emph{general cause} of the shock.
-The magnitude is not known.
-%For example, in the Conoco Phillips stock example, when we knew the outbreak of COVID-19 was about to come, past shocks related to financial crisis may be helpful.
-Or, near the outbreak of COVID-19, suppose that a department in a university realized that it would be faced with declining applications.
-It could make use of the information about the decline of its admitted students in the past or that of other departments when similar situations (i.e., the number of applications suddenly decreases) happened.\\
-We admit that it is quite an informational advantage over unanticipated shocks.
-However, in practice, if a shock is unanticipated, we may not even be able to construct such a post-shock analysis since we do not know it is about to happen.\\
-
-Our proposed methodology is applied at $T_1^*+1$.
-You are right about the timing.
-Our methodology can be applicable in many different timing scenarios.
-Generally, suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$ and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$.
-It is possible to generalize our method to this situation.
-Our new Apple example in Section 5.2 of the revised manuscript provides an example for the case $d=2$ with predicted covariates.
-\\
-
-Thank you for your remark on timing scenarios, it led to an improved manuscript.} \\
-
-{\bf Comment 3:} Related to the point above, the model applied is an AR(1) with contemporaneous regressors.
-This structure requires the covariates to be known in the future for \emph{ex ante} forecasts, or for them to be forecast.
-The set-up assumes $\theta_1$ to be well behaved and the covariates are not subject to shocks if they need to be forecast.
-Empirically, we could also think of cases where the mean shift $D_{i,t}$ interacted with the covariates which would give an additional forecast error via $\mathbf{x}_{1, T_1^* + 1}$.
-The theoretical results seem to hinge on known $\mathbf{x}_{1,t}$ entering contemporaneously to derive unbiasedness.
-What are the implications of the covariates needing to be forecast?
-\\
-
-\response{Good point, thank you.
-Indeed, our method assumes $\mathbf{x}_{1, T_1^* + 1}$ to be given.
-If it is to be forecasted with errors, it will possibly result in a biased estimation of $E(\alpha_1)$ with $\hat{\alpha}_{\rm wadj}$ such that the evaluation of the proposition may not be reliable.
-\\
-
-The situation when covariates are forecasted with errors is similar to the one when the variance of the shock effect is large.
-In both situations, the signal from covariates is weak.
-Our simulation discusses this situation by increasing $\sigma_{\alpha}$.
-It shows that a slightly weak signal will not strongly compromise the correctness of our prospective methods.
-However, if the forecast for the covariates is seriously bad (i.e., the signal from covariates is really weak), our result shows that the risk-reduction evaluation may be only as good as a random guess.
-\\
-
-In the event that the mean shift $D_{i,t}$ interacts with the covariates, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions.
-In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed.
-A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid.
-This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid.
-This may gives users a sense of the variability of post-shock predictions due to forecast error from covariates that are also affected from the shock.
-We included this response to the Discussion, thank you again.} \\
-
-{\bf Comment 4:} Given the dynamic structure, what happens after $T_1^*+1$?
-Couldn't you use the donor pool shocks to estimate the shock transition (e.g.
-apply the shock effect estimator to the m periods following the shock), and produce an intercept correction dummy for the next $m$ periods?
-It would be interesting empirically to see if the shock is anticipated to be permanent or transitory.
-I wonder if the theoretical statements of when forecast risk is minimized may be adapted to assess when transitory shocks die out such that the unadjusted forecast is preferable again?
-\\
-
-\response{In our setup, we only model the time series under study up to $t = 1, \ldots, T_1^*+1$.
-We do not know what happened  after $T_1^*+1$.
-It is possible that there are no shocks or additional shocks after $T_1^*+1$.
-\\
-
-It is possible to use the donor pool to estimate the shock transition,  and produce an intercept dummy for the next $m$ periods.
-Assume there are no additional shocks  after $T_1^*+1$, and $T_i^*+m \leq T_i$ for $i = 2, \ldots, n+1$.
-Consider the model
-\begin{align*}
-  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i, T_i^* + d}I(t = T_i^*+d) +\varepsilon_{i,t},
-\end{align*}
-for $i = 2, \ldots, n+1$ and $d = 1, \ldots, m$.
-Suppose we have information of the covariates up to $T_1^*+d$ either by given information or by forecasting.
-We can use our proposed synthetic control method to compute weights $\mathbf{W}^*$ and OLS to estimate $\beta_{i, T_i^*+d}$ to compute $\hat{\beta}_{1, T_1^*+d}$.
-As a result, we obtain $\hat{\boldsymbol{\beta}}_1^{(m)} = (\hat{\beta}_{1, T_1^*+d})_{d = 1}^m$.
-However, it cannot be a simple intercept dummy but instead an iterative adjustment in computing $m$-ahead forecasts.
-For example,
-$$
-  \hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)} + \hat{\beta}_{1, T_1^*+2}, 
-$$
-where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts.
-One then may be able to use $\hat{\boldsymbol{\beta}}_1^{(d)}$ to judge whether the shock is transitory or permanent.
-We speculate that the transitory shock effect can be theoretically justified using similar arguments as those that appear in our manuscript, but we view this extension as outside the scope of our current paper.
-The SCM based approach of \cite{agarwal2020two} is an alternative that may also be able to assess whether or not a shock is transitory, although this adjustment is without any theoretical guarantees.
-\\
-
-%To judge if the shock is permanent, we may consider another approach. Consider the model
-%\begin{align*}
-%  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i}I(T_i^*< t \leq  T_i^*+d) +\varepsilon_{i,t}.
-%\end{align*}
-%We can compute $\hat{\beta}_i$ from OLS and $\mathbf{W}^*$ from synthetic approach with covariates $d \times p$ (see for example of $p = 2$ in our added Apple example in Section 5.2 of revised transcript) to compute $\hat{\beta}_1$.
-Note that $\hat{\beta}_1$ is unbiased.
-We can use parametric double bootstrap to test the hypothesis that $H_0 \colon \beta_1=0$ versus $H_1 \colon \beta_1\neq 0$ at time point $T^*_i+d$.
-\\
-} \\
-
-{\bf Comment 5:} While the simulations were useful, I found the discussion in section 4 quite impenetrable.
-There are so many decisions that a researcher would need to make, including which weighting method and all the bootstrapping and leave-one-out decisions.
-It would be very helpful to the reader if you could give a summary of all your results stating your preferred user decisions for generic specifications.
-\\
-
-\response{Thank you for pointing it out.
-We polished Section 4 for better readability in the revised manuscript.
-We  summarize  our results including preferred user decisions as below.
-There are mainly three decisions to make for an user: to choose
-  \begin{itemize}
-    \item among  $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, and $\hat{\alpha}_{\rm wadj}$ 
-    \item between $\mathcal{B}_f$ and $\mathcal{B}_u$ (see detailed definition in Section 3.2)
-    \item The $k$ in the $k$ random draws in LOOCV
-  \end{itemize}
-  First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution.
-Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool.
-Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.
-These recommendations are included in Remark 3 at the end of Section 2.
-\\
-
-  The selection between $\mathcal{B}_f$ and $\mathcal{B}_u$ is more of a philosophical question. In Section 3.2,  we noted
-
-  \begin{tcolorbox}
-  $\mathcal{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast, $\mathcal{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness arises from parameters and idiosyncratic error.
-  \end{tcolorbox}
-
-In Section 4.3, we found that $\mathcal{B}_u$ is better than $\mathcal{B}_f$ when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is large.
-Otherwise, they are nearly the same.
-\\
-
-At the end of Section 4.3, we noted that when $p < n$, there are infinitely many solutions to $\mathbf{W}^*$ such that $\mathbf{W}^*$ will take values on the boundary of $\mathcal{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\rm wadj}$ \citep{andrews2000inconsistency}.
-$\mathcal{B}_f$  is immune to this issue.
-However, our simulation results in the Supplementary Materials show that the non-uniqueness does not seriously compromise the inference.
-\\
-
-In summary, $\mathcal{B}_u$ is preferred when  the donor pool size is moderately small ($n< 10$) and the signal from the covariates is \emph{believed} to be large.
-If $p < n$ and non-uniqueness problem is of concern due to theoretical reasons,  $\mathcal{B}_f$ is preferred.
-In other cases, the choice between  $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to philosophical differences mentioned above.
-This explanation is added to the end of Section 4.
-\\
-
-%Lastly,  greater number of bootstrap replication $B$ is preferred. Usually, $B = 200$ is sufficient. 
-Ideally, $k=n$ is preferred.
-However, if the data size is large such that $k=n$ is computationally expensive, we found that $k = 5$ or $k = 10$ works well.
-In practice, $(k+1) B$ number of bootstrap replications are implemented to complete the evaluation, where $k B$ is from LOOCV to estimate the correctness parameter $p$ and $B$ is from ordinary bootstrap using the whole donor pool.
-} \\
-
-{\bf Comment 6:} Section 2 is hard to read without defining the terms that come in the second para- graph of section 2.1 (lines 19-23 of p.6). I'd suggest moving this to the beginning of section 2. \\
-
-\response{Sorry for not making it clear.
-The terms not defined in the caption of Figure 1 are now defined in the revised manuscript.
-For other parts, we find there are no terms that are not defined.
-The beginning parts of Section 2 are intended to give a general picture to the reader that our method is in fact general whereas the setup we investigate in Section 2.1 is a special case.
-}
-
 \bibliography{synthetic-prediction-notes}

### 2021-01-28 Revision/revisionEJoSchecklist.tex
revised manuscript and list with changes in red, and created separate checklist

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{graphicx,times}
\usepackage{mathtools}
\usepackage{url}
%\usepackage{setspacing}
\usepackage{fullpage}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}

\newcommand{\R}{\mathbb{R}}
\newcommand{\ds}{\displaystyle}
\newcommand{\mustar}{\mu^{\textstyle{*}}}
\newcommand{\betastar}{\hat{\beta}^{\textstyle{*}}}
\newcommand{\betahat}{\hat{\beta}}
\newcommand{\betaw}{\hat{\beta}_w}
\newcommand{\betastarT}{\hat{\beta}^{\textstyle{*}^T}}
\newcommand{\betabar}{\bar{\beta}^{\textstyle{*}}}
\newcommand{\bstar}{b^{\textstyle{*}}}
\newcommand{\vstar}{v^{\textstyle{*}}}
\newcommand{\Bstar}{B^{\textstyle{*}}}
\newcommand{\wstar}{w^{\textstyle{*}}}
\newcommand{\BICstar}{\textsc{bic}^{\textstyle{*}}}
\newcommand{\minBICstar}{\min_{s=1,...,r}\left\{\BIC^{\textstyle{*}}(s)\right\}}
\newcommand{\sstar}{s_m^{\textstyle{*}}}
\newcommand{\epstar}{\varepsilon^{\textstyle{*}}}
\newcommand{\epstarT}{\varepsilon^{{\textstyle{*}^T}}}
\newcommand{\epresstar}{\widehat{\varepsilon}^{\textstyle{*}}}
\newcommand{\epresstarT}{\widehat{\varepsilon}^{\textstyle{*}^T}}
\newcommand{\residstar}{\widehat{\varepsilon}^{\textstyle{*}}}
\newcommand{\Ystar}{Y^{\textstyle{*}}}
\newcommand{\Xstar}{X^{\textstyle{*}}}
\newcommand{\Wstar}{W^{\textstyle{*}}}
\newcommand{\Wstarinv}{W^{{\textstyle{*}^{-1}}}}
\newcommand{\Zstar}{Z^{\textstyle{*}}}
\newcommand{\YstarT}{Y^{{\textstyle{*}^T}}}
\newcommand{\XstarT}{X^{\textstyle{*}^T}}
\newcommand{\Sigstar}{\widehat{\Sigma}^{\textstyle{*}}}
\newcommand{\Sigstarhalf}{\widehat{\Sigma}^{\textstyle{*}^{1/2}}}
\newcommand{\Sigstarhalfinv}{\widehat{\Sigma}^{\textstyle{*}^{-1/2}}}
\newcommand{\lstar}{l^{\textstyle{*}}}

\newcommand{\Astar}{A^{\textstyle{*}}}
\newcommand{\Gostar}{\widehat{G}_o^{\textstyle{*}}}
\newcommand{\GostarT}{\widehat{G}_o^{\textstyle{*}^T}}
\newcommand{\Gohat}{\widehat{G}_o}
\newcommand{\GohatT}{\widehat{G}_o^T}
\newcommand{\Sigresstar}{\widehat{\Sigma}^{\textstyle{*}}}

\newcommand{\B}{\mathcal{B}}
\newcommand{\Lnorm}{\mathcal{L}}
\newcommand{\Sub}{\mathcal{S}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\Proj}{\mathcal{P}}
\newcommand{\Env}{\mathcal{E}}
\newcommand{\Envspace}{\Env_{\Sigma}(\B)}
\newcommand{\utrue}{u_{\text{true}}}
\newcommand{\BIC}{\textsc{bic}}
\newcommand{\dimEnv}{\text{dim}\{\Envspace\}}
\newcommand{\minBIC}{\min_{s=1,...,r}\left(\BIC(s)\right)}
\newcommand{\nboot}{n_{\text{boot}}}

\newcommand{\X}{\mathbb{X}}
\newcommand{\Y}{\mathbb{Y}}
\newcommand{\Ymatstar}{\Y^{\textstyle{*}}}
\newcommand{\YmatstarT}{\Y^{\textstyle{*}^T}}
\newcommand{\Xmatstar}{\X^{\textstyle{*}}}
\newcommand{\XmatstarT}{\X^{\textstyle{*}^T}}

\newcommand{\Sigres}{\widehat{\Sigma}}
\newcommand{\SigY}{\widehat{\Sigma}_{Y}}
\newcommand{\SigX}{\widehat{\Sigma}_{X}}
\newcommand{\Pu}{\widehat{\Proj}_{\Env_u}}
\newcommand{\Pj}{\widehat{\Proj}_{\Env_j}}
\newcommand{\Qu}{\widehat{\Q}_{\Env_u}}
\newcommand{\Qj}{\widehat{\Q}_{\Env_j}}
\newcommand{\PD}{\widehat{\Proj}_{D}}
\newcommand{\betau}{\hat{\beta}_u}
\newcommand{\betaj}{\hat{\beta}_j}
\newcommand{\res}{\widehat{\varepsilon}}

\newcommand{\sestar}{\text{se}^{\textstyle{*}}\{\text{vec}(\hat{\beta})\}}
\newcommand{\setrue}{\text{se}_{\text{true}}\{\text{vec}(\hat{\beta})\}}

\newcommand{\vecop}[1]{\text{vec}\left( #1 \right)}
\newcommand{\vechop}[1]{\text{vech}\left( #1 \right)}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}

\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Var}{var}

\newtheorem{lem}{Lemma} 
\newtheorem{thm}{Theorem} 
\allowdisplaybreaks

\setlength{\parindent}{0cm}

\title{Referee report checklist}
\author{Daniel J. Eck}
\date{}

\begin{document}

\maketitle

Thank you for the opportunity to resubmit at Electronic Journal of Statistics. Thank you to the reviewers for comments that led to an improved version of this manuscript. We address all of the reviewers' comments below. An outlines of each change made or a rebuttal is provided for all of the reviewer's comments.

\section*{Editors}

------------------------------------------------------------------------------------------------------------------------
Both referees like aspects of the paper, but make several suggestions that would improve the paper. The exposition needs to improve --- and both referees have provided several pointers in that regard. I have also gotten some comments from another expert on this topic, who is less enthusiastic about the paper. I mention his relevant comments below: \\

"The authors claim they are providing CIs for certain scalar parameters (e.g., cell means or cell probabilities). It is not clear to me what kind of coverage guarantees these CIs have, because they appear to be defined in terms of a data-dependent distribution (dependent on the MLE in the completion of the family). Explicitly: what is the reference distribution for computing the coverage? Is the coverage marginal, or is it conditional? And if it is conditional, what exactly is the conditioning event (I assume that the sufficient statistic is on the boundary of the support, but this is not spelled out)? Not only should the authors clarify this point but they should also verify coverage, both theoretically and in simulations." \\

I like many aspects of the paper --- and even though the theoretical underpinnings of the results presented in this paper was developed in the PhD thesis of the second author almost 30 years ago --- it is both elegant and of good technical quality, and is worth publishing now. \\

Hence I recommend a major revision where the authors address all the concerns of the reviewers and prepare a point-by-point response to their comments.\\
----------------------------------------------------------------------------------------------------------------------

I concur with the position of the AE, and I have a further minor point myself: EJS is electronic, so supplementary files do not make much sense. On the other hand, we do not want to publish a paper which is 70 pages long - so I suggest to enclose proofs and discussion in the paper as an appendix, and to leave the codes in a file on your website or on the arXiv. \\

{\bf Response to the editors:} Thank you for the opportunity to submit a revision. We include a point by point response for the comments and concerns raised by the reviewers. We also relegate the code and thorough analysis to arXiv. \\

{\bf Response to third reviewer's comments in the AE's report:} %The conditioning event is indeed that the sufficient statistic is on the boundary. As the first referee pointed out, this point was laid out in a free-flowing manner. We have since added a definition for the limiting conditional model as suggested by that referee with the hope that this clarifies the point. 
We do admit that our intervals are not a complete confidence interval recipe, because they only say what to do when the MLE does not exist in the conventional sense (only exists in the Barndorff-Nielsen completion).  And, of course, it is only a complete confidence interval recipe (that says what to do for all possible data) that can have a coverage probability.  So our proposal has to be considered only as a fix-up of some other confidence interval recipe.  For example: do Wald intervals when the MLE exists in the conventional sense (MLE mean values not on the boundary) and do our intervals when the MLE does not exist in the conventional sense (MLE mean values on the boundary). Or the same with score or likelihood or variance stabilizing or something else substituted for Wald. The web page \url{http://www.stat.umn.edu/geyer/5102/examp/coverage.html} shows how these modified intervals work combining, our proposal with various other confidence interval recipes.  They clearly fix up all bad behavior near the boundaries.  In light of this we do not think adding simulations will help.  We could add this web page to the supplementary material if the editors think that would be helpful. And, of course, we could make similar plots for other distributions.

\newpage
\section*{Reviewer 1}

Thank you very much for taking the time to provide a thoughtful review of our manuscript. We think that these comments will go a long way to improve the exposition of our manuscript. \\

%% addressed
{\bf Major Comment 1:} I feel part of the introduction requires some rewriting. In particular, it would be appreciated if the contributions of this paper is elaborated further. Currently, the paragraph starting with ‘In this paper, ·’ is meant to serve this purpose. However, if the authors can structure this a bit more (through bullet points, maybe?) and elaborate more on the contributions of this manuscript, distinguishing them from Geyer (2009) in particular (and other relevant literature), that would significantly improve this part of the exposition. \\

{\bf Response:} We now better outline the contributions made in this paper using bullet points.  \\

%% addressed
{\bf Major Comment 2:} Defining the completion before Section 2 would make things easier to follow. \\

{\bf Response:} We agree that the completion needs to be defined, thank you for pointing this out. We now provide an informal definition in the Introduction and a formal definition in Section 4. \\

%% addressed
{\bf Major Comment 3:} What do the authors mean by ‘apparent MLE’ in Pg. 3? The sentence containing this is unclear to me. \\

{\bf Response:} The word `apparent' should not be there and has been removed. Thank you for catching this. \\

%% addressed
{\bf Major Comment 4:} Having sentences like ‘To find the MLE ... has been identified’ in Pg. 4 can be confusing to some readers at this stage. If LCM were defined already that would be once again, easier to follow.\\

{\bf Response:} Thank you for reading this closely. We want to first present the utility of methodology to the reader before explaining the LCM. So we removed mentions to the LCM and the buildup to the LCM from this Section. We provide a formal definition of the LCM in Section 4. \\

%% addressed
{\bf Major Comment 5:} Generally there is a lot of references to quantities and concepts in [3]. This may make things hard to follow for readers without a thorough understanding of [3]. In my opinion, it would be better to include a short summary of preliminaries from [3]. I would further recommend altering the exposition throughout, with appropriate references to this summary. \\

{\bf Response:} Thank you for alerting us that this may be confusing.  We better separate the developments in this manuscript from the concepts in [3] without including a summary of preliminaries. We better elaborate the contributions in this paper as suggested. We provide definitions of key quantities as suggested, for example the LCM is now defined within our framework. We also remove references to technical terms in the motivating example which we hope gives the reader a conceptual basis for understanding both the problem of interest and how we plan on providing a solution with the methodology in this paper. \\

%% addressed
{\bf Major Comment 6:} Several things are deferred to the supplement, without appropriate pointers. I would recommend including proper references to section numbers, etc. in the supplement. \\

{\bf Response:} Thank you for pointing this out, we now provide much more pointed references to quantities in the Appendix. The R code is now relegated to ArXiv. \\

%% addressed
{\bf Major Comment 7:} In Section 4, I would recommend including a summary of the authors’ method in an algorithm format. \\

{\bf Response:} We now include a summary of our method in a simple algorithmic format. \\

%% addressed
{\bf Major Comment 8:} Quite some material is presented in Section 4 in a free-flowing manner. However, providing key concepts and conclusions within definition and result (theorem, lemma, etc) environments respectively, would be very useful. E.g definition of LCM; having Eqn 6 as a separate result, so it is easy to find, etc. \\

{\bf Response:} Thanks for your commentary on our exposition. We add a definition of LCM and the closure of the exponential family.  \\

%% addressed
{\bf Major Comment 9:} Kindly elaborate on the point ‘However, ...it has’ before Equation (8). \\

{\bf Response:} We expanded on the point about computational stability by mentioning issues overflow and underflow.  We also defer to the Appendix for more details on careful coding. \\

%% addressed
{\bf Major Comment 10:} In Section 5.3, the running time is mentioned without specific details regarding the computational resources. Therefore, it is hard to calibrate the real computational speed of the proposed method. \\

{\bf Response:} Thank you for pointing this out, we added information on the computational resources. \\

%% addressed
{\bf Major Comment 11:} Generally, many definitions are presented in a free-flowing manner, and I feel, collecting them in one place would be very useful. \\

{\bf Response:} We added definitions within Section 4 to the free-flowing presentation of ideas. \\

%% addressed
{\bf Major Comment 12:} The counterexample in the supplementary is very interesting. I would recommend describing the counterexample in the main manuscript, with some intuitions, deferring details to the supplementary. \\

{\bf Response:} Thank you for pointing this out, we reference the purpose of this counterexample with more emphasis in the remarks to Theorem 6. \\

%% addressed
{\bf Major Comment 13:} Remark 1 after Theorem 6 is extremely dense, and hard to follow. I would suggest de-densifying it. \\

{\bf Response:} Remark 1 has been de-densified. We also add a remark that serves as a roadmap. \\

%% addressed
{\bf Major Comment 14:} Are there are any geometric interpretation of assumption 16? If this is purely a proof artefact, I would recommend providing some intuition regarding why and how this this shows up. \\

{\bf Response:} We now provide some intuition for assumption (16) and why it arises as a proof artefact.  \\

%% addressed
{\bf Major Comment 15:} I would recommend providing a short summary of key technical contributions of the proofs in the main manuscript.
 \\

{\bf Response:} Some technical contributions of the proof are now provided in the Introduction. \\

%% addressed
{\bf Major Comment 16:} There are some citations at the beginning, however, this problem has been extremely well-studied. The authors make an important contribution, and therefore, situating the problem better in the context of relevant literature would be recommended. In particular, the current citation misses several important works, (e.g. [1, 5, 6]). I would recommend citing related works more broadly with appropriate categorizations of the works, in the way the authors have currently presented. \\

{\bf Response:} We add these references as suggested. \\

%% addressed
{\bf Major Comment 17:} Along similar lines as above, the discussion and connections to [2] seems more appropriate for the introduction, rather than deferring to the discussion. \\

{\bf Response:} We moved the discussion and connections to [2] to the Introduction as suggested. \\

%% addressed
{\bf Major Comment 18:} The sentence ‘Moreover, ...solutions’ seems a bit misplaced. It is technically true if one still wishes to provide MLE-based inference. But it misses the crucial fact that there are currently other available options. For instance, one could provide valid inference based on the debiased lasso [7, 8, 4], under appropriate sparsity conditions. In my opinion, the authors could still make arguments in their favor. For instance, practitioners may be more comfortable using traditional estimation/inference schemes—the ones they have been more familiar with for ages, rather than switching to a whole different estimator—and therefore, it is still crucial to make MLE- based inference pipelines more suited for contemporary datasets. This is setting aside the additional fact that debiased lasso requires sparsity assumptions that may be quite hard to check in practice. \\

{\bf Response:} There are, of course, a huge variety of methods that have been placed in
the literature for analyzing regression data.  Debiased LASSO seems only
one of many of these.  Moreover, the debiased LASSO was originally developed
for linear models which are already Barndorff-Nielsen complete and exhibit
none of the phenomena this paper is about, and \citet{xia-nan-li} say that 
when extended to generalized linear models (GLM) the debiased LASSO does
not work, so it seems irrelevant to the concerns of this paper. \\

\begin{sloppypar}
No regularization or shrinkage method, including Bayesian methods,
take seriously the possibility that
the true unknown model is near or on the boundary of the parameter space.
Only methods for inference in the Barndorff-Nielsen completion can do that.
So, as the discussion of \citet{geyer-gdor} says,
our methods are competitors of the conventional methods for high-dimensional
data, even though that is not a concern of this paper, and we have not
developed this theme.
\end{sloppypar}

%We do not add references to the debiased lasso as suggested here for similar reasons to those given in the Discussion of Geyer (2009). Specifically, Geyer (2009) says:
%\begin{quote}
%	Bayesian inference does not avoid the issues treated in this article unless one is a subjective Bayesian and the prior truly represents someone’s prior opinion. In complicated examples like our contingency table example (Section 2.3), such subjective priors seem difficult if not impossible. For exponential families satisfying the conditions of Brown [3], flat improper priors on natural parameters lead to proper posteriors if and only if the MLE exists in the conventional sense, that is, if and only if the conditions of Theorem 4 hold. When the MLE does not exist in the conventional sense, priors that are ``diffuse,'' ``vague,'' or ``objective'' make no sense.

%Nonparametric inference, both older (smoothing) and newer (machine learn- ing) behave weirdly when the MLE does not exist in the conventional sense. Consider our logistic regression example (Section 2.2) from the nonparametric point of view. Let us take a simple nonparametric approach of fitting a polynomial of arbitrary degree. Traditionally, we need some sort of model selection criterion such as cross-validation to choose the degree. Here the quadratic model fits the data perfectly so no model of higher degree can fit better. All the non-parametricness collapses when solutions ``at infinity'' are considered. Wavelets do not work well here; neither does smoothing of any form; neither does regularization such as LASSO or SVM [14, Section 4.4.4 and Chapters 5, 6, and 12]. All make a simple situation needlessly complicated. This paragraph and the preceding one raise issues but provide no answers, which must await another paper and perhaps another author.
%\end{quote}

\vspace*{0.5cm} If requested we will add references to the debiased lasso into the Discussion of the present paper. \\

%% addressed
{\bf Minor Comments:} ‘a likelihood maximizing sequences’ in abstract;
There are some repeats, such as ‘when when’ in first line. Similar repeats are seen in multiple places; ‘is origins’ on Pg. 2. \\

{\bf Response:} Thank you for pointing out these typos, they are now fixed. We scanned for and fixed other typos.

\newpage
\section*{Reviewer 2}

Thank you for your positive feedback of our current paper.  We will shed some light on the comments raised in \texttt{EJS2001-007R1R2.pdf} about the methodology in  Likelihood Inference in Exponential Families and Directions of Recession which we will refer to as Geyer (2009). 
\begin{itemize}
\item Nonuniqueness is not the issue.  The geometry of Theorem~6
    in \citet{geyer-gdor} makes every generic direction of recession 
    (GDOR) of the original model (OM) a direction of constancy of the LCM.
    It follows that the constancy space of the LCM contains the normal
    cone (the set of all directions of recession,
    \citealp[Theorem~3]{geyer-gdor}).  It follows that the confidence
    region defined by (23) in \citet{geyer-gdor} is uniquely defined
    as the discussion following that equation indicates.
    So these confidence intervals are well defined.
\item Conditional is not the issue.  What \citet{geyer-gdor} calls the
    limiting conditional model (LCM) is both a family of limit distributions
    and a family of conditional distributions.  Think of it as a family
    of limit distributions, and it is clear that conditioning is irrelevant.
    The hypothesis tests are not conditional, and neither are the
    confidence intervals that come from inverting them.
\item We do admit that our intervals are not a complete confidence interval recipe, because they only say what to do when the MLE does not exist in the conventional sense (only exists in the Barndorff-Nielsen completion).  And, of course, it is only a complete confidence interval recipe (that says what to do for all possible data) that can have a coverage probability.  So our proposal has to be considered only as a fix-up of some other confidence interval recipe.  For example: do Wald intervals when the MLE exists in the conventional sense (MLE mean values not on the boundary) and do our intervals when the MLE does not exist in the conventional sense (MLE mean values on the boundary). %Or the same with score or likelihood or variance stabilizing or something else substituted for Wald. The web page \url{http://www.stat.umn.edu/geyer/5102/examp/coverage.html} shows how these modified intervals work combining, our proposal with various other confidence interval recipes.  They clearly fix up all bad behavior near the boundaries.  In light of this we do not think adding simulations will help.  We could add this web page to the supplementary material if the editors think that would be helpful. And, of course, we could make similar plots for other distributions.
\end{itemize}

%{\bf Comment:} $s$ is not an estimate, how to understand the confidence interval of $s$. \\

%{\bf Response:} $s$ is understood to be on the canonical parameter parameterization, the one-sided confidence intervals on the mean-value parameterization appearing in the figures of Geyer (2009) are obtained from mapping $\hat\theta + \gamma + s\delta$,$s \in [\hat s, \infty)$, to the mean-value parameterization. Nonuniqueness of $\gamma$ is covered in Section 3.16.2 of Geyer (2009). Nonuniqueness of $\delta$ is also not an issus.  The geometry of Theorem~6 in \citet{geyer-gdor} makes every generic direction of recession (GDOR) of the original model (OM) a direction of constancy of the LCM. It follows that the constancy space of the LCM contains the normal cone (the set of all directions of recession,\citealp[Theorem~3]{geyer-gdor}).  It follows that the confidence region defined by (23) in \citet{geyer-gdor} is uniquely defined as the discussion following that equation indicates. So these confidence intervals are well defined. \\

%{\bf Comment:} The probability of the event of sufficient statistic $Y$ belongs to the boundary of convex set of the exponential family distributions is not the p-value of the null hypothesis. Actually, what is the null hypothesis in this situation is not well defined ... My conclusion of this story is that the interval of parameters gives us a set of distributions $p_{\hat\theta + \gamma + s\delta}$, $s \in [\hat s, \infty)$ such that the probability of sufficient statistic lies on the boundary is no less than $\alpha$ but I cannot think it as the confidence interval of the parameters. \\

%{\bf Response:} We hope to clarify the meaning of the hypothesis test and confidence intervals issues raised in this comment.
%\begin{itemize}
%\item Conditional is not the issue.  What \citet{geyer-gdor} calls the limiting conditional model (LCM) is both a family of limit distributions and a family of conditional distributions.  Think of it as a family of limit distributions, and it is clear that conditioning is irrelevant.  The hypothesis tests are not conditional, and neither are the confidence intervals that come from inverting them.
%\item Nonuniqueness is not the issue.  The geometry of Theorem~6 in \citet{geyer-gdor} makes every generic direction of recession (GDOR) of the original model (OM) a direction of constancy of the LCM. It follows that the constancy space of the LCM contains the normal cone (the set of all directions of recession, \citealp[Theorem~3]{geyer-gdor}).  It follows that the confidence region defined by (23) in \citet{geyer-gdor} is uniquely defined as the discussion following that equation indicates.  So these confidence intervals are well defined.
%\end{itemize}

\begin{thebibliography}{0}

\bibitem[Barndorff-Nielsen(1970)]{barndorff-nielsen-notes}
Barndorff-Nielsen, O. (1970).
\newblock \emph{Exponential Families: Exact Theory}.
\newblock Various Publications Series, Number 19, Matematisk Institut,
    Aarhus Universitet.

\bibitem[Barndorff-Nielsen(1978)]{barndorff-nielsen}
Barndorff-Nielsen, O. (1978).
\newblock \emph{Information and Exponential Families}.
\newblock Wiley, Chichester.

\bibitem[Brown(1986)]{brown}
Brown, L.~D. (1986).
\newblock \emph{Fundamentals of Statistical Exponential Families: with
    Applications in Statistical Decision Theory}.
\newblock Institute of Mathematical Statistics, Hayward, CA.

\bibitem[Csisz\'{a}r and Mat\'{u}\v{s}(2005)]{csiszar-matus}
Csisz\'{a}r, I. and Mat\'{u}\v{s}, F. (2005).
\newblock Closure of exponential families.
\newblock \emph{Annals of Probability}, \textbf{33}, 582--600.

\bibitem[Geyer(1990)]{geyer-thesis}
Geyer, C.~J. (1990).
\newblock \emph{Likelihood and Exponential Families}.
\newblock PhD thesis, University of Washington.
\newblock \url{http://purl.umn.edu/56330}.

\bibitem[Geyer(2009)]{geyer-gdor}
Geyer, C.~J. (2009).
\newblock Likelihood inference in exponential families and directions
    of recession.
\newblock \emph{Electronic Journal of Statistics}, \textbf{3}, 259--289.

\bibitem[Xia, et al.(2020)Xia, Nan and Li]{xia-nan-li}
Xia, L., Nan, B., and Li, Yi (2020).
\newblock A Revisit to De-biased Lasso for Generalized Linear Models.
\newblock \url{https://arxiv.org/abs/2006.12778}.

\end{thebibliography}

\end{document}

### 2021-01-28 Revision/dataanalysis.R

@@ -1,0 +1,679 @@
+# load packages
+library("data.table")
+library("tidyverse")
+library("tseries")
+library("quantmod")
+library('Rsolnp')
+library('msos')
+library('tikzDevice')
+library('xtable')
+
+# set working directory
+setwd("/Users/mac/Desktop/Research/Post-Shock Prediction/")
+
+## Conoco Phillips
+getSymbols('COP', from = "2000-01-01")
+COP <- as.data.frame(COP)
+COP <- COP %>% mutate(Date = rownames(COP))
+
+## S&P 500
+getSymbols('^GSPC', from = "1970-01-01")
+GSPC <- as.data.frame(GSPC)
+GSPC <- GSPC %>% mutate(Date = rownames(GSPC))
+
+## Brent Crude prices
+Brent_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/brent-daily_csv/data/d93216330ab2c27aae3d177b2f0f0921/brent-daily_csv.csv") %>%
+  rename(Oil_Close = Price)
+
+## WTI Crude prices
+WTI_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/wti-daily_csv/data/c414c9d375ec3c8f9d7c276d866fb2a4/wti-daily_csv.csv") %>%
+  rename(WTI_Close = Price)
+
+## Gold Price
+getSymbols('GC=F', from = "2000-01-01")
+gold <- as.data.frame(`GC=F`)
+gold <- na.omit(gold)
+gold <- gold %>% mutate(Date = rownames(gold))
+
+## Dollar Index
+getSymbols('DX-Y.NYB', from = "2000-01-01")
+USD <- as.data.frame(`DX-Y.NYB`)
+USD <- na.omit(USD)
+USD <- USD %>% mutate(Date = rownames(USD))
+
+## 13-Week T-Bill
+TB <- read.csv('^IRX.csv', na.strings = 'null')
+TB <- na.omit(TB)
+
+## Volatility Index
+getSymbols('^VIX', from = "2000-01-01")
+VIX <- as.data.frame(VIX)
+VIX <- na.omit(VIX)
+VIX <- VIX %>% mutate(Date = rownames(VIX))
+
+
+## inflation adjustment
+getSymbols("CPIAUCSL", src = 'FRED')
+avg.cpi <- apply.yearly(CPIAUCSL, mean)
[…]

### 2021-02-02 Revision/list.tex
updated materials

@@
 
-\response{Thank you for the opportunity to submit a revision. We include a point by point response for the comments and concerns raised by the reviwers.}
+\response{Thank you for the opportunity to submit a revision. We include a point by point response for the comments and concerns raised by the reviewers.}
 
@@
 
-{\bf Comment:} Firstly, this contribution seems to me to be related to two exisiting strands of literature, neither of which is cited.
+Thank you for your helpful comments for our literature review and data analysis. We think they will help improve the quality of our manuscript. \\
+
+{\bf Comment 1:} Firstly, this contribution seems to me to be related to two exisiting strands of literature, neither of which is cited.
 Describing the contribution relative to these literatures might help some readers better appreciate the achievements.
@@
  \quad  \text{ with }\quad  E_{\mathcal{F}_{\alpha}}(\alpha_i) =\mu_{\alpha}, Var_{\mathcal{F}_{\alpha}}(\alpha_i)=\sigma^2_{\alpha},\quad   \text{iid under } \mathcal{M}_1\\
- & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{iid under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
+ & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{independent under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
 \end{align*}
@@
 On the other hand, the oil supply shock had precedent.
-As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.
-\\
+As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock to form our donor pool.
+Adjustment with respect to this donor pool led to much better forecasts than doing nothing.}\\
 
@@
 If it is to be forecasted with errors, it will possibly result in a biased estimation of $E(\alpha_1)$ with $\hat{\alpha}_{\rm wadj}$ such that the evaluation of the proposition may not be reliable.
+Moreover, the forecast error from covariates contributes to more error in the unadjusted forecast, and the post-shock forecast.
 \\
@@
 \response{Sorry for not making it clear.
-The terms not defined in the caption of Figure 1 are now defined in the revised manuscript.
+The terms were not defined in the caption of Figure 1 are now defined in the revised manuscript.
 For other parts, we find there are no terms that are not defined.
-The beginning parts of Section 2 are intended to give a general picture to the reader that our method is in fact general whereas the setup we investigate in Section 2.1 is a special case.
+The beginning parts of Section 2 are intended to give the reader a depiction of the logic of our method before we proceed into the technicals of our method.
 }

### 2021-02-02 Revision/manuscript.tex
updated materials

@@
 In our methodological framework, the researcher first creates a donor pool of time series which have undergone similar structural shocks in the past.
-\red{Similarity in this context refers to the shock effects as arising from a common distribution that has existing second moments and allows for varying variances and varying means that are linear functions of common covariates.} The unobserved shock effect in the time series of interest is assumed to arise from the same distribution.
+Similarity in this context refers to the shock effects as arising from a distribution that has existing second moments, with extensions to variances and means that are linear functions of common covariates.
+The unobserved shock effect in the time series of interest is assumed to arise from the same distribution.
 Construction of the donor pool and the desired aims of the donor pool has precedent in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
@@
 We will show that our proposed adjustment estimators yield much better results than no adjustment in these examples.
-The Conoco Phillips example provides an empirical application of our methods when the shock is unprecedented in nature, arising from a global pandemic and an oil supply shock.
-\red{The Apple example is about annual release of their MacBook products, and provides a case for post-shock prediction when the shock has precedent.} We now elaborate our framework for post-shock prediction.
+The Conoco Phillips example provides an empirical application of our methods when the shock is anticipated yet unprecedented in nature, arising from a global pandemic and an oil supply shock.
+The Apple example provides a case for post-shock prediction when the shock has precedent, we forecast the stock price after the latest release of the MacBook.
+We now elaborate our framework for post-shock prediction, we start with an illustration.
 
@@
 It is supposed that the researcher does not have any information after $T_1^*$, but does have observations from a donor pool of forty time series that have previously undergone similar shocks for which post-shock responses are recorded.
-Similarity in this context means that the shock effects are random variables that from a common distribution.
+Similarity in this context means that the shock effects are random realizations from a common distribution.
 In this example, the mean of the estimated shock effects is taken as a shock effect estimator for the time series under study.
@@
 In our framework we have assumed the covariates to be known.
-However, it may be the case that the shock \red{affects} the covariates as well as the response.
+However, it may be the case that the shock affects the covariates as well as the response.
 If so, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions.
@@
 Construction of the donor pool is a critical step in our post-shock prediction framework.
-In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from \red{the same distribution that allows} for varying variances and  varying means that are linear functions of common covariates.
+In our model, shocks estimated from candidate time series in the donor pool, together with the shock in the time series of interest, should come from the same generative process.
 However, it may be difficult to confirm such an assumption or modeling structure in practice.

### 2021-02-02 Revision/responsetoMinimizingPostShockForestErrorIJF.tex
updated materials

@@
 If it is to be forecasted with errors, it will possibly result in a biased estimation of $E(\alpha_1)$ with $\hat{\alpha}_{\rm wadj}$ such that the evaluation of the proposition may not be reliable.
-\textcolor{red}{Moreover, the forecast error from covariates contributes to more error in the unadjusted forecast, and thus in the post-shock one.}\\
+Moreover, the forecast error from covariates contributes to more error in the unadjusted forecast, and the post-shock forecast.
+\\
 

### 2021-02-02 Revision/responsetocoverletterforautor.tex
updated materials

@@
  \quad  \text{ with }\quad  E_{\mathcal{F}_{\alpha}}(\alpha_i) =\mu_{\alpha}, Var_{\mathcal{F}_{\alpha}}(\alpha_i)=\sigma^2_{\alpha},\quad   \text{iid under } \mathcal{M}_1\\
- & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{\textcolor{red}{independent} under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
+ & \alpha_i = \mu_{\alpha} +\delta_i'\mathbf{x}_{i, T_i^*+1} + \tilde{\varepsilon}_i\quad  \text{independent under } \mathcal{M}_{21} \text{ or } \mathcal{M}_{22}.
 \end{align*}
@@
 On the other hand, the oil supply shock had precedent.
-As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.
-}\\
+As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock to form our donor pool.
+Adjustment with respect to this donor pool led to much better forecasts than doing nothing.}\\
 

### 2021-02-02 Revision/manuscript.tex
made minor updates to manuscript

@@
 The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool.
-$\hat{y}^{1}_{T_1^*+1}$ is the prediction without scalar adjustment of $\hat{\alpha}$ whereas $\hat{y}^{2}_{T_1^*+1}$ is the one with.
-In this example,
-    they differ only by an adjustment $\hat{\alpha}=10.22$. It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
+$\hat{y}^{1}_{T_1^*+1}$ is the prediction without any adjustment, and $\hat{y}^{2}_{T_1^*+1}$ is the forecast with additive adjustment of $\hat{\alpha} = n^{-1}\sum_{i=2}^{n+1}\hat\alpha_i$.
+In this example, theses forecasts differ by $\hat{\alpha}=10.22$.
+It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
 \end{figure*}

### 2021-02-04 Revision/manuscript.tex
revised manuscript for figure 3 and a minor change in discussions

@@
     \includegraphics[height = 7cm, width = 16.8cm]{FIG3.pdf}
-    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and violet line represent real data and fitted line, respectively.}
+    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc.
+Black dots and violet line represent real data and fitted line, respectively.
+\textcolor{red}{We did not include forecast at $t=T_1^*+1$ for better visualization of post-shock forecast at $t=T_1^*+2$.
+The dotted line connects the unadjusted forecast at $t=T_1^*$ with the one at $t=T_1^*+2$.}}
     \label{Fig3}
@@
 $
-  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}
+ \textcolor{red}{ \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^1 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}}
 $

### 2021-02-04 Revision/responsetoAE.tex
revised manuscript for figure 3 and a minor change in discussions

@@
 
-\textcolor{red}{Thank you for your helpful comments for our literature review and data analysis. We think they will help improve the quality of our manuscript a lot.}\\
+Thank you for your helpful comments for our literature review and data analysis. We think they will help improve the quality of our manuscript. \\
 

### 2021-02-04 Revision/apple.R

@@ -318,6 +318,8 @@ mat <- cbind(TS1$id[nrow(TS1)], c(Yhat_adj))
 colnames(mat) <- c("id", "Yhat_adj")
 dat <- as.data.frame(mat)
 colnames(Yhat_nothing) <- "y"
+dat2 <- data.frame(id = c(25, 27), pred = c(m_AAPL_2020_11$fitted.values[25], 
+                                            Yhat_nothing))
 # set working directory
 setwd('/Users/mac/Desktop/Research/Post-Shock Prediction/')
 # plot setting
@@ -332,8 +334,9 @@ p1 <- ggplot(TS1, mapping = aes(x = id, y = AAPL_Close)) +
              pch = 2:4, cex = 2, width = 0.65) + 
   geom_point(data = data.frame(x = unique(dat$id), y = Yhat_nothing), 
              aes(x = x, y = y), col = "violet", cex = 2) + 
-  geom_line(aes(x = id, y = c(m_AAPL_2020_11$fitted.values, y1, Yhat_nothing)), 
-            col = "violet") + 
+  geom_line(aes(x = id, y = c(m_AAPL_2020_11$fitted.values)), 
+            col = "violet", TS1[1:25,]) + 
+  geom_line(aes(x = id, y = pred), dat2, col = 'violet', linetype = "dotted", size = 2) + 
   annotate("text", x = 1, y = seq(from = 110, to = 104, length.out = 4), 
            label = c("$\\hat{y}_{1, T_1^* + 2}^{1}$",
                      "$\\hat{y}_{1, T_1^* + 2}^{1} + \\hat{\\alpha}_{\\rm adj}$",
@@ -366,8 +369,8 @@ p2 <- ggplot(tail(TS1, 4), mapping = aes(x = id, y = AAPL_Close)) +
               pch = 2:4, cex = 3, width = 0.15, height = 0.15) + 
   geom_point(data = data.frame(x = unique(dat$id), y = Yhat_nothing), 
              aes(x = x, y = y), col = "violet", cex = 2) + 
-  geom_line(aes(x = id, y = c(tail(m_AAPL_2020_11$fitted.values, 2), y1, Yhat_nothing)), 
-            col = "violet") + 
+  geom_line(aes(x = id, y = c(m_AAPL_2020_11$fitted.values[24:25])), col = "violet", TS1[24:25,]) +
[…]

### 2021-02-04 Revision/manuscript.tex
everything looks good

--- 2021-02-02 Revision/manuscript.tex
@@
     \includegraphics[height = 7cm, width = 16.8cm]{FIG3.pdf}
-    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and violet line represent real data and fitted line, respectively.}
+    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc.
+Black dots and violet line represent real data and fitted line, respectively.
+We did not include forecast at $t=T_1^*+1$ for better visualization of post-shock forecast at $t=T_1^*+2$.
+The dotted line connects the unadjusted forecast at $t=T_1^*$ with the forecast at $t=T_1^*+2$.
+Our donor pool suggested that the shock effect take place at $t=T_1^*+2$ in this example.}
     \label{Fig3}
@@
 In the second case, we assume that the time series under study will experience an additional additive shock at $T_1^* + m$, say $\alpha_1^{(m)}$.
-Users now construct the donor pool to consist of time series that experience shocks similar to  $\alpha_1^{(m)}$.
+Users now construct the donor pool to include time series that experienced shocks similar to  $\alpha_1^{(m)}$.
 Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(m)}$.
@@
 $
-  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}
+ \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^1 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}
 $

### 2021-02-06 Revision/letter.tex
added letter

--- 2020-08-27 Submission/letter.tex
@@
 	   1010 W. Green St \\
-	   Urbana, IL 61820 \\
+	   Urbana, IL 61801 \\
        \texttt{jileil2@illinois.edu} \\ 
@@
 
-We are excited to submit our manuscript ``Minimizing post-shock forecasting error through aggregation of outside information'' for possible publication at the  International Journal of Forecasting.
+We are grateful to submit a revision for our manuscript ``Minimizing post-shock forecasting error through aggregation of outside information'' at International Journal of Forecasting.
+The responses to all of the comments are included in the resubmission files.
 
-In this manuscript, we  develop a forecasting methodology for providing credible forecasts for time series that are known to  experience a shock in the future.
-It is a general methodology that has various potential real-life applications in forecasting during  \emph{unprecedented} time.
-We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
-We construct three shock effect estimators  with the aim of minimizing average forecast risk.
-We propose risk-reduction propositions that provide conditions that establish when our methodology works.
-Bootstrap and leave-one-out cross validation procedures are provided to prospectively evaluate those conditions and estimate corresponding correctness.
-We use a real data example of forecasting Conoco Phillips stock price during the time  of   oil price control and COVID-19 pandemicto verify  our methodology.
-
-We confirm that this manuscript is only under consideration at the International Journal of Forecasting. Thank you for your consideration.
+Thank you for your reconsideration.
 

### 2021-03-07 problem statement.tex
addition of problem statement

% document class
\documentclass[12pt]{article}

% use package
\usepackage{scribe}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{graphicx,times}
\usepackage{mathtools}
\usepackage{url}
%\usepackage{setspacing}
\usepackage{fullpage}
\usepackage{palatino}
\usepackage{mathpazo}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{xifthen} % Allows us to put in optional arguments to questions
\usepackage{color}
\usepackage{manfnt}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{nicefrac,mathtools}
\usepackage{float}
\usepackage{showexpl}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{chngcntr}
\usepackage{xparse}
\usepackage{etoolbox}
\usepackage{blkarray}
\usepackage{cprotect}
\usepackage{authblk}

\bibliographystyle{plainnat}

\title{Post-Shock Transition Estimation}
\author{Jilei Lin\thanks{jileil2@ilinois.edu} }
\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
\affil{Department of Statistics, University of Illinois at Urbana-Champaign}

% start document
\begin{document}

\maketitle

\section{Introduction}

Suppose that an individual, given time series $\{(\mathbf{x}_{1, t},y_{1,t})\colon t=1, \ldots, T_1\}$, is interested in predicting $y_{1, T_1+k}$ for some $k \in \naturals$. However,  he knows that the time series is about experience a shock at $T_1+k$, whose signal is not embedded in the data. In this case,   statistical methodologies that rely on capturing signal from training data to predict are not expected to perform well.

Based on the synthetic control theory \cite{abadie2010synthetic}, \citet{lin2020minimizing} proposes a post-shock prediction method that borrows information from other similar  time series experiencing analogous shocks by constructing a donor pool $\{(\mathbf{x}_{i, t},y_{i,t})\colon i = 2, \ldots, n +1, t = 1, \ldots, T_i\}$, and uses synthetic control method to weight the shock effects $\hat{\alpha}_i$ estimated from the donor pool for $i = 2, \ldots, n+1$ to provide a scalar adjustment to the naive time series forecast $\hat{y}_{1, T_1+k}$. \citet{lin2020minimizing} provides conditions when  optimality of minimizing mean squared forecast error is attained.

However, the work of \citet{lin2020minimizing} is limited to the nowcasting problem. Moreover, it provides no information about how the shock will affect the time series afterwards, let alone whether it will die out.  In practice, it is natural to think of applications where we are interested in the dynamics of the shock, whether and how the shock will die out. For example, when a company knows it is going to experience a disastrous shock, managers will be interested in  whether the shock will be persistent, how it affects future sales for a number of months, and thus how to adjust cost and production to combat such crisis.

In this paper, we are interested in extending the work of \citet{lin2020minimizing} to estimate the shock transition after the time series of interest experience a shock, i.e., $\{\hat{y}_{1, T_1+k+j}\colon j = 1, \ldots, d\}$, extend its optimality propositions of nowcasting to prediction for a period, and develop a hypothesis testing procedure to judge whether the shock is permanent or transitory.

\section{Methods}

Suppose at $t=T_i^*$, one knows the shock is about to occur at $t=T_i^*+1$. Consider the following model
\begin{align*}
  \mc{M} \colon 
  \begin{array}{l}
    y_{i,t} = \eta_i +  \alpha_{i,t}I(t > T_i^*)+ \phi_i y_{i,t-1} + \mathbf{x}_{i,t}\bs{\theta}_i + \varepsilon_{i,t}\\[.3cm]
    \alpha_{i,t} = \mu_{\alpha} + \mbf{x}_{i, t}\boldsymbol{\delta}_i + \tilde{\varepsilon}_i
  \end{array},
\end{align*}
where $D_{i,t}= I(t= T_i^* +t)$, $I(\cdot)$ is an indicator function, and $\mbf{x}_{i,t}, \boldsymbol{\theta}_{i}\in \reals^p$ with $p\geq 1$. The random effects structure is oragnized as below.
\begin{align*}
  \tilde{\varepsilon}_i &\simiid \mc{F}_{\tilde{\varepsilon}} \text{ with } \E_{\mc{F}_{\tilde{\varepsilon}}}, \Var_{\mc{F}_{\tilde{\varepsilon}}}(\tilde{\varepsilon}_i)= \sigma^2_{\alpha}  >0 \\
  \eta_i & \indep \alpha_{i,t} \indep \phi_i \indep \boldsymbol{\theta}_i \indep \varepsilon_{i,t} \indep \tilde{\varepsilon}_i.
\end{align*}
The candidate forecasts are
\begin{align*}
  &\text{Forecast 1}: \hat{y}_{1,T_1^*+k + j}^{(1)} = \hat\eta_1 
    + \hat\phi_1 y_{1,T_1^*+k+j-1} + \hat\theta_1'\mbf{x}_{1,T_1^*+k+j-1} 
    , \\
  &\text{Forecast 2}: \hat{y}_{1,T_1^*+k+j}^{(2)} = \hat\eta_1 
    + \hat\phi_1 y_{1,T_1^*+k+j-1} + \hat{\theta}_1'\mbf{x}_{1,T_1^*+k+j-1} 
    + \hat{\alpha}^{(j)},
\end{align*}
where $\hat{\alpha}^{(j)}$ is an estimate of the shock effect occurring in the model of $y_{1,T_1^*+k+j}$, and other parameters are estimated in an unbiased fashion, e.g., OLS. Define
\begin{align}
  \begin{array}{lll}
     \Theta &= &\{(\eta_i, \phi_i, \bs{\theta}_i, \alpha_{i,t}, \mbf{x}_{i,t}, y_{i,t-1}, \bs{\delta}_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
    \Theta_1 &= &\{(\eta_i, \phi_i, \bs{\theta}_i, \alpha_{i,t}, \mbf{x}_{i,t}, y_{i,t-1}, \bs{\delta}_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
  \end{array}
\end{align}

For simplicity, assume $k=0$. Given the post-shock estimated transition, $\{\hat{y}_{1, t}^2\colon t= T_1 +1, \ldots, T_1+d\}$, to gauge the forecast performance, we consider the forecast risk in the form of MSE as below
\begin{align*}
  R_k 
  &= \frac{1}{d} \sum_{j=1}^d \E [(\hat{y}_{1,T_1+j}^{(k)}-y_{1, T_1+j})^2] ,
  \quad k = 1, 2.
\end{align*}
By generalizing Lemma 1 from \citet{lin2020minimizing}, we get the risk-reduction quantities as
 \begin{align*}
     R_1-R_2 =\frac{1}{d} \sum_{j=1}^d  \Big\{ \E (\alpha_{1, T_1^*+j}^2) - \E [(\hat{\alpha}^{(j)}-\alpha_{1, T_1^*+j})^2]\Big\},
  \end{align*}
for all  $\hat{\bs{\alpha}}$ independent of $\Theta_1$.

\subsection{Challenges}

\begin{challenges}
  How to define a proper null hypothesis that captures whether the shock transition is  transitory or permanent?   Define $ \hat{\boldsymbol{\alpha}} = (\hat{\alpha}^{(j)})_{j=1}^d$ and $\bs{\alpha}_1= (\alpha_{T_1^*+j})_{j=1}^d$. One possible hypothesis is
  \begin{align*}
    H_0 \colon \bs{\alpha}_1=\bs{0} 
    \quad \text{ versus } \quad 
    H_1 \colon \bs{\alpha}_1 \neq \bs{0} 
  \end{align*}
  In any cases, it is important to find an unbiased estimator of $\bs{\alpha}_1$. $\hat{\alpha}_{\rm wadj}$ in \citep{lin2020minimizing} might be possible. 
\end{challenges}

\begin{challenges}
  How to generalize to $\hat{\alpha}_{\rm wadj}$? In \citep{lin2020minimizing}, the weighting is with respect to  $\mbf{x}_{i, T_i^*+1}$ for $i = 1, \ldots, n+1$. However, in this case, we have $\mbf{x}_{i, T_i^*+j}$ for $i = 1, \ldots, n+1$ and $j = 1, \ldots, d$. Perhaps, we may want to do $d$ times of weighting such that the unbiased  property still holds. However, a lot of forecast error for $\mbf{x}_{T_i^*+j}$ when $d$ is large may be of concern in constructing such estimator.
\end{challenges}

\bibliography{synthetic-prediction-notes}

\end{document}

### 2021-03-07 problem statement.tex
addition of problem statement

@@
   &\text{Forecast 1}: \hat{y}_{1,T_1^*+k + j}^{(1)} = \hat\eta_1 
-    + \hat\phi_1 y_{1,T_1^*+k+j-1} + \hat\theta_1'\mbf{x}_{1,T_1^*+k+j-1} 
+    + \hat\phi_1 \hat{y}^{(1)}_{1,T_1^*+k+j-1} + \mbf{x}_{1,T_1^*+k+j-1} \hat{\bs{\theta}}_1
     , \\
   &\text{Forecast 2}: \hat{y}_{1,T_1^*+k+j}^{(2)} = \hat\eta_1 
-    + \hat\phi_1 y_{1,T_1^*+k+j-1} + \hat{\theta}_1'\mbf{x}_{1,T_1^*+k+j-1} 
+    + \hat\phi_1 \hat{y}^{(2)}_{1,T_1^*+k+j-1} + \mbf{x}_{1,T_1^*+k+j-1} \hat{\bs{\theta}}_1
     + \hat{\alpha}^{(j)},
 \end{align*}
-where $\hat{\alpha}^{(j)}$ is an estimate of the shock effect occurring in the model of $y_{1,T_1^*+k+j}$, and other parameters are estimated in an unbiased fashion, e.g., OLS. Define
+where $\hat{y}_{1, T_1^*}^{(1)}=\hat{y}_{1, T_1^*}^{(2)}=y_{1,T_1^*}$, $\hat{\alpha}^{(j)}$ is an estimate of the shock effect occurring in the model of $y_{1,T_1^*+k+j}$, and other parameters are estimated in an unbiased fashion, e.g., OLS.
+Define
 \begin{align}
@@
   R_k 
-  &= \frac{1}{d} \sum_{j=1}^d \E [(\hat{y}_{1,T_1+j}^{(k)}-y_{1, T_1+j})^2] ,
+  &= \frac{1}{d} \sum_{j=1}^d \E [(\hat{y}_{1,T_1^*+j}^{(k)}-y_{1, T_1+j})^2] ,
   \quad k = 1, 2.
 \end{align*}
-By generalizing Lemma 1 from \citet{lin2020minimizing}, we get the risk-reduction quantities as
+
+\begin{proposition}
+  Suppose that $\hat{\alpha}^{(j)}$ estimates $\alpha_{1, T_1^*+j}$ unbiasedly and that  $\hat{\alpha}^{(j)}$ is independent of $\Theta_1$. Then, $R_1 > R_2$ when
+\end{proposition}
+\begin{proof}
+  Define
 \begin{align*}
-     R_1-R_2 =\frac{1}{d} \sum_{j=1}^d  \Big\{ \E (\alpha_{1, T_1^*+j}^2) - \E [(\hat{\alpha}^{(j)}-\alpha_{1, T_1^*+j})^2]\Big\},
+  C(\Theta_1, j) = \hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^*+j-1}^{(2)} + \mbf{x}_{1, T_1^*+j}\hat{\bs{\theta}}_1 - (\eta_1 + \phi_1 y_{1, T_1^* + j-1} + \mbf{x}_{1, T_1^*+j} \bs{\theta}_1 +\varepsilon_{1, T_1^*+j}) .
 \end{align*}
-for all  $\hat{\bs{\alpha}}$ independent of $\Theta_1$.
+We first consider a simple case when $d=2$. By Lemma 1 in \cite{lin2020minimizing},
+\begin{align*}
+  & \E [(\hat{y}_{1,T_1+1}^{(1)}-y_{1, T_1+1})^2] -  \E [(\hat{y}_{1,T_1+1}^{(2)}-y_{1, T_1+1})^2]\\
+= \quad   & \E(\alpha_{1, T_1^*+1}^2) - \E[(\hat{\alpha}^{(1)}-\alpha_{1, T_1^*+1})^2] \\
+= \quad & - \E[ (\hat{\alpha}^{(1)})^2]+2 \E(\hat{\alpha}^{(1)} \alpha_{1, T_1^*+1}) \\
+= \quad &  - \E[ (\hat{\alpha}^{(1)})^2]+2 \E[\alpha_{1, T_1^*+1} \cdot \E(\hat{\alpha}^{(1)} \mid  \alpha_{1, T_1^*+1})] \\
+= \quad & 2 \E[ \alpha_{1, T_1^*+2}^2]- \E[(\hat{\alpha}^{(1)})^2] \\
+= \quad & \E[ \alpha_{1, T_1^*+2}^2]- \Var(\hat{\alpha}^{(1)}).
+\end{align*}
+Next,
+\begin{align*}
+ & \E [(\hat{y}_{1,T_1+2}^{(1)}-y_{1, T_1+2})^2] -  \E [(\hat{y}_{1,T_1+2}^{(2)}-y_{1, T_1+2})^2]  \\
+= \quad  & \E \Big\{ (C(\Theta_1, 2) - \hat{\phi}_1\hat{\alpha}^{(2)}-\alpha_{1, T_1^*+2})^2\Big\}- \E \Big\{ (C(\Theta_1, 2) -\alpha_{1, T_1^*+2})^2\Big\} \\
+= \quad & -\E (\alpha_{1, T_1^*+2}^2)  + 2 \E (C(\Theta_1, 2)\alpha_{1, T_1^*+2}) - 2 \E [C(\Theta_1, 2) (\hat{\phi}_1\hat{\alpha}^{(2)}+\alpha_{1, T_1^*+2})] + \E[(\hat{\phi}_1\hat{\alpha}^{(2)}+\alpha_{1, T_1^*+2})^2] \\
+= \quad & \E[(\hat{\phi}_1\hat{\alpha}^{(2)})^2] + 2 \E [\hat{\phi}_1 \hat{\alpha}^{(2)} \alpha_{1, T_1^*+2}] -2 \E[C(\Theta_1, 2) \hat{\phi}_{1}\hat{\alpha}^{(2)}]
+\end{align*}
+By assumption, $\hat{\alpha}^{(2)}$ is independent  of $\Theta_1$.
+Moreover, $\alpha_{1, T_1^*+2}$ is also independent  of $\Theta_1$ by construction.
+Since OLS estimators are unbiased and $\hat{\alpha}^{(2)}$ estimates $\alpha_{1, T_1^*+2}$ unbiasedly,
+\begin{align*}
+  \E [\hat{\phi}_1 \hat{\alpha}^{(2)} \alpha_{1, T_1^*+2}] &= \phi_1 [\E (\hat{\alpha}^{(2)})]^2\\
+  \E [C(\Theta_1, 2)\hat{\phi}_1 \hat{\alpha}^{(2)}] &=  \E[C(\Theta_1, 2) \hat{\phi}_1 ] \cdot \E(\hat{\alpha}^{(2)})
+\end{align*}
+Thus,
+\begin{align*}
+ & \E [(\hat{y}_{1,T_1+2}^{(1)}-y_{1, T_1+2})^2] -  \E [(\hat{y}_{1,T_1+2}^{(2)}-y_{1, T_1+2})^2] \\
+= \quad & \E[(\hat{\phi}_1\hat{\alpha}^{(2)})^2] + 2 \phi_1 \cdot [\E (\hat{\alpha}^{(2)})]^2 -2 \E[C(\Theta_1, 2) \hat{\phi}_1 ] \cdot \E(\hat{\alpha}^{(2)}) \\
+= \quad & \E[(\hat{\phi}_1\hat{\alpha}^{(2)})^2]  + 2\cdot \E(\hat{\alpha}^{(2)}) \cdot  \Big\{\phi_1 \E (\hat{\alpha}^{(2)}) - \E[C(\Theta_1, 2) \hat{\phi}_1] \Big\}
+\end{align*}
+\textcolor{red}{Challenges: How to evaluate $\E[C(\Theta_1, 2) \hat{\phi}_1]$.}
+\end{proof}
 

### 2021-03-16 problem_statement.tex
made comments to problem statement

--- 2021-03-07 problem statement.tex
@@
 
-\bibliographystyle{plainnat}
+\newenvironment{commentline}[1]{
+\noindent{\color{red} \rule{\linewidth}{0.5mm}}
+\textbf{Comment}: #1
+
+\noindent{\color{red} \rule{\linewidth}{0.5mm}}
+}
 
@@
 
+\commentline{Do not use `he', use something like `the researcher'.}
+
 Based on the synthetic control theory \cite{abadie2010synthetic}, \citet{lin2020minimizing} proposes a post-shock prediction method that borrows information from other similar  time series experiencing analogous shocks by constructing a donor pool $\{(\mathbf{x}_{i, t},y_{i,t})\colon i = 2, \ldots, n +1, t = 1, \ldots, T_i\}$, and uses synthetic control method to weight the shock effects $\hat{\alpha}_i$ estimated from the donor pool for $i = 2, \ldots, n+1$ to provide a scalar adjustment to the naive time series forecast $\hat{y}_{1, T_1+k}$.
 \citet{lin2020minimizing} provides conditions when  optimality of minimizing mean squared forecast error is attained.
+
+\commentline{Our method is not synthetic control, it's a weighted-adjustment estimator that is inspired by synthetic control.}
 
@@
 \end{align*}
-where $D_{i,t}= I(t= T_i^* +t)$, $I(\cdot)$ is an indicator function, and $\mbf{x}_{i,t}, \boldsymbol{\theta}_{i}\in \reals^p$ with $p\geq 1$. The random effects structure is oragnized as below.
+where $D_{i,t}= I(t= T_i^* +t)$, $I(\cdot)$ is an indicator function, and $\mbf{x}_{i,t}, \boldsymbol{\theta}_{i}\in \reals^p$ with $p\geq 1$. The random effects structure is organized as below.
 \begin{align*}
-  \tilde{\varepsilon}_i &\simiid \mc{F}_{\tilde{\varepsilon}} \text{ with } \E_{\mc{F}_{\tilde{\varepsilon}}}, \Var_{\mc{F}_{\tilde{\varepsilon}}}(\tilde{\varepsilon}_i)= \sigma^2_{\alpha}  >0 \\
+  \tilde{\varepsilon}_i &\simiid \mc{F}_{\tilde{\varepsilon}} \text{ with } \E_{\mc{F}_{\tilde{\varepsilon}}} = 0, \Var_{\mc{F}_{\tilde{\varepsilon}}}(\tilde{\varepsilon}_i)= \sigma^2_{\alpha}  >0, \\
   \eta_i & \indep \alpha_{i,t} \indep \phi_i \indep \boldsymbol{\theta}_i \indep \varepsilon_{i,t} \indep \tilde{\varepsilon}_i.
@@
 where $\hat{y}_{1, T_1^*}^{(1)}=\hat{y}_{1, T_1^*}^{(2)}=y_{1,T_1^*}$, $\hat{\alpha}^{(j)}$ is an estimate of the shock effect occurring in the model of $y_{1,T_1^*+k+j}$, and other parameters are estimated in an unbiased fashion, e.g., OLS.
+
+\commentline{There is also the h-ahead forecast model, see: \url{https://www.ssc.wisc.edu/~bhansen/papers/hstep.pdf} Perhaps their framework is more appropriate.
+See a more authoritative presentation in \cite{clements1996multi}.}
+
 Define
@@
 
+\commentline{We could consider an $h$-ahead forecasting procedure at each value over some window $h = 1,\ldots,H$.
+We can then consider the adjusted and unadjusted responses at every $h$, and then develop a test of the differences between these two quantities for each $h$.
+Alternatively, we could consider if the shock effect washes out in each series in the donor pool for each $h$.
+Both of these procedures would require a multiple testing framework.
+All of this may depend on the forecast horizon $H$.
+}
+
 \begin{challenges}
@@
 
+\commentline{The $h$ ahead framework does not involve $x$ values beyond the range of data collection. We could do something with forecasting, but that seems shaky.}
+
+\bibliographystyle{plainnat}
 \bibliography{synthetic-prediction-notes}

### 2021-05-30 transience-prediction.tex
addition of draft ideas

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{caption}
\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
\usepackage{pdflscape}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{palatino}
\usepackage{mathpazo}
\usepackage[top=2.4cm,bottom=2.4cm,right=2.4cm,left=2.4cm]{geometry}

% function definition
\def\naturals{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\Hist}{\mathcal{H}}
\def\mbf#1{\mathbf{#1}} % bold but not italic
\def\ind#1{\mathrm{1}(#1)} % indicator function
\newcommand{\simiid}{\stackrel{iid}{\sim}} %[] IID 
\def\where{\text{ where }} % where
\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
\def\mrm#1{\mathrm{#1}} % remove math
\newcommand{\reals}{\mathbb{R}} % Real number symbol
\def\t#1{\tilde{#1}} % tilde
\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
\def\v#1{\mbi{#1}} % Vector notation
\def\mc#1{\mathcal{#1}} % mathical
\DeclareMathOperator*{\argmax}{arg\,max} % arg max
\DeclareMathOperator*{\argmin}{arg\,min} % arg min
\def\E{\mathbb{E}} % Expectation symbol
\def\mc#1{\mathcal{#1}}
\def\var#1{\mathrm{Var}(#1)} % Variance symbol
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
\newcommand\red[1]{{\color{red}#1}}
\def\bs#1{\boldsymbol{#1}}
\def\P{\mathbb{P}}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert} % A norm with 1 argument
\DeclareMathOperator{\Var}{Var} % Variance symbol

\newtheorem{cor}{Corollary}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{prop}{Proposition}
\theoremstyle{definition}
\newtheorem{remark}{Remark}
\hypersetup{
  linkcolor  = blue,
  citecolor  = blue,
  urlcolor   = blue,
  colorlinks = true,
} % color setup

% proof to proposition 
\newenvironment{proof-of-proposition}[1][{}]{\noindent{\bf
    Proof of Proposition {#1}}
  \hspace*{.5em}}{\qed\bigskip\\}
% general proof of corollary
  \newenvironment{proof-of-corollary}[1][{}]{\noindent{\bf
    Proof of Corollary {#1}}
  \hspace*{.5em}}{\qed\bigskip\\}
% general proof of lemma
  \newenvironment{proof-of-lemma}[1][{}]{\noindent{\bf
    Proof of Lemma {#1}}
  \hspace*{.5em}}{\qed\bigskip\\}
\theoremstyle{definition}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}

\title{Transience prediction}

\begin{document}

\maketitle

\section{Ideas}

In time series literature, under a squared loss $L(\cdot)$, the conditional forecast, which turns out to be the frequently used standard  multiple horizon forecast, is the best point forecast that minimizes the loss if the model is specified correctly. In other words, if the time series does experience a shock but the shock is transient, as $D_i\equiv T_i-T_i^*+1\to \infty$, the mean squared loss of the conditional forecast for $D_i$ horizons should converge to the minimum of mean squared loss that  any $D_i$-horizon forecast can achieve.  On the other hand, if the time series do experience a shock but the shock is permanent and large, $D_i$-horizon conditional forecast adjusted by additive shock should enjoy a better loss than the unadjusted conditional forecast obtained from the training data that do not experience a shock. Essentially, the problem of judging whether a shock is permanent or transient boils down into comparing  the losses of adjusted $D_i$-horizon conditional forecast and the unadjusted one.

\cite{quaedvlieg2021multi} proposes  a test to jointly compare $1$ to $H$-ahead forecasts 
 for a  sequence of models such that users can get a sense of the overall quality of the model. \textcolor{red}{Note that $D_i$ and $H$ need not be equal. $D_i$ is the horizon while $H$ proxies the maximum requirements of the model predictive ability.} In our case, this method can be applied to a paired comparison of adjusted $D_i$-horizon conditional forecast and unadjusted one. The methodology of \cite{quaedvlieg2021multi} involves a specification of a loss function $L(\cdot)$ that is used to compare the losses between two models. Moreover, the proposed test statistic is a function of those losses. In other words, it requires information of the responses that are to be forecasted. Therefore, a naive application of this method to compare adjusted $D_i$-horizon conditional forecast and the unadjusted one would fail. It is because from the perspective of practitioners, a retrospective comparison is not as useful as a prospective comparison that can predict whether the shock is transient or permanent without observing the shock and future series.

To deal with this problem, motivated by \cite{abadie2010synthetic} and \cite{lin2020minimizing}, it is possible to approximate the probability that the shock is transient using the donor pool  under suitable assumptions. Then, we illustrate the idea as below. Let the donor pool size be $n$. For $i = 1, \ldots, n +1$ and $t = 1, \ldots, T_i$, we assume
\begin{align*}
  y_{i,t} &= K(\mc{F}_{i, t-1}) + \mathbf{x}_{i,t}\boldsymbol{\beta}  + \alpha_{i,t} I(t > T_i^*)+\varepsilon_{i,t},\\
         \alpha_{i,t} &= \mu_{t}^{\alpha} + \mbf{z}_{i,t}\bs{\gamma}_{i} + \tilde{\varepsilon}_{i,t}
\end{align*}
where $\mc{F}_{i, t-1}$  denotes the information  before $t-1$ of time series $i$, $K(\cdot)$ is a general real-valued function, $\mathbf{x}_{i,t},\bs{\beta}\in \reals^{p}$, $\bs{z}_{i,t}, \bs{\gamma}_{i}\in \reals^q$, $\tilde{\varepsilon}_{i,t}$ and $\varepsilon_{i,t}$ follow some well-defined distribution with existing first and second moments, and $T_i^*$ is the time point that the user knows a shock is about to come at $t = T_{i}^*+1$. We further assume, $\tilde{\varepsilon}_{i,t}$ and $\varepsilon_{i,t}$ are  independent. This implies that $\alpha_{i,t}$ and $\varepsilon_{i,t}$ are independent.

Note that $\|{(\alpha_{i,t})_{t=T_i^*+1}^{t=T_i}}\|_2$ should be close to zero if the shock is transient. Also, more general than \cite{lin2020minimizing}, $\mbf{z}_{i,t}$ is a vector of known covariates for the shock effects. \textcolor{red}{Note that the model for $\alpha_{i,t}$ may need revision since specification of covariates for $H$ time points in practice may be difficult, and involve large uncertainty and estimation error.}

Let $\bs{d}_i^h=(d_{i,t}^h)_{t=1}^{T_i}$ be the loss differences of adjusted and unadjusted forecast for $i = 2, \ldots, n+1$ at the $h$-ahead forecast. Define $\E(d_{i,t}^h)=\mu_{i,t}^h$ and
\begin{align*}
  \mu_{i}^h = \lim_{T_i \to \infty} \frac{1}{T_i} \sum_{t=1}^{T_i} \mu_{i,t}^h.
\end{align*}
Note that in the case of post-shock prediction, before the shock time point, the adjusted forecast and unadjusted forecast are essentially the same. It implies
\begin{align*}
  \mu_{i}^h = \lim_{T_i \to \infty} \frac{1}{T_i} \sum_{t=T_i^*+1}^{T_i} \mu_{i,t}^h.
\end{align*}
In other words, \textcolor{red}{in order not make the test trivial, we have to make sure $T_i=O(T_i-T_i^*+1)$, i.e., $T_i-T_i^*+1$is not negligible compared to $T_i$.} Otherwise, $\mu_i^h$ will be always zero and there is no need for testing. Also,

\cite{quaedvlieg2021multi}  proposes two tests for testing the following two hypotheses respectively,
\begin{align*}
  H_{0,1}\colon \mu^{(\rm Avg)}_i \equiv  \sum_{h=1}^H a_h \mu^h\leq 0 
  \quad &\text{ versus }
  \quad H_{1,1}\colon \mu^{(\rm Avg)}_i > 0\\
  H_{0,2}\colon \mu^{(\rm Unif)}_i \equiv  \min_{h=1, \ldots, H} \mu^h_i  > 0 
  \quad &\text{ versus }
  \quad H_{1,2}\colon \mu^{(\rm Unif)}_i  \leq  0,
\end{align*}
where $\sum_{h=1}^H a_h =1$ and $a_h$ is typically selected to be $1/H$. The first hypothesis is for testing average predictive superiority whereas the second is for uniform superiority. From the definition, apparently, the second test is more stringent and more powerful but it is less likely to reject. It rejects only when the adjusted forecast is significantly better than the unadjusted one. Also, \textcolor{red}{\cite{quaedvlieg2021multi} note that if $H$ is large, the power of the test may decrease.}

Consider a hypothesis test $\mc{T}_i$ that considers testing one of the two hypotheses.  \cite{quaedvlieg2021multi} shows that his test is powerful as $T_i \to \infty$. So, we may define the permanence of the shock as
\begin{align*}
  S_i = I(\mc{T}_i \text{ rejects }H_0)= I(\bs{\alpha}_i \text{ is permanent}).
\end{align*}
We further assume that for $i = 1, \ldots, n+1$,
\begin{align*}
  \E (S_i) = \P(\bs{\alpha}_i \text{ is permanent})=s
\text{ for some } s\in [0,1].
\end{align*}
Suppose we can obtain a weighting $\mathbf{W} = (w_2, \ldots, w_{n+1})$. As a result, we can find an unbiased estimate for $ \P(\bs{\alpha}_1 \text{ is permanent})$ with
\begin{align*}
\hat{ \P}(\bs{\alpha}_1 \text{ is permanent})
  &= \sum_{i=2}^{n+1} w_i \cdot S_i \\
 \E ( \hat{ \P}(\bs{\alpha}_1 \text{ is permanent}))
 &= 
 \sum_{i=2}^{n+1} w_i\cdot  \E (S_i)= \sum_{i=2}^{n+1} w_i \cdot  s = s.
\end{align*}
We may construct the weighting using synthetic control method as below. 
For $i=1, \ldots, n+2$, define  
\begin{align*}
  \mathbf{Z}_{i} 
  = \begin{pmatrix}
    \mbf{z}_{i, T_i^*+1} \\ 
    \vdots \\
    \mbf{z}_{i, T_i^*+H}
  \end{pmatrix}
  \quad 
  \text{ and } \quad 
  \mc{W}=\{\mathbf{W}\in [0,1]^n \colon \mathbf{1}_n'\mathbf{W}=1\}
\end{align*}
Suppose there exists $\mathbf{W}^*\in \mc{W}$ with $\mathbf{W}^* = (w_{2}^*, \ldots, w_{n+1}^*)$ such that
\begin{align*}
  \mathbf{Z}_1 = \sum_{i=2}^{n+1} w_i^* \mathbf{Z}_{i}.
\end{align*}
We may estimate $\mathbf{W}^*$ as
\begin{align*}
  \mathbf{W}^* 
  = \argmin_{\mathbf{W}\in \mc{W}}
  \|  \mathbf{Z}_1-\sum_{i=2}^{n+1} w_i^* \mathbf{Z}_{i} \|_2.
\end{align*}

\section{Definitions}

\subsection{stochastic process and dynamic system}

\begin{definition}[stochastic process]
  A stochastic process $\{Y_t\}_{t\in T}$ is a collection of random variables $Y_t$, taking values in a common measurable space $(\Xi, \mc{X})$, indexed by a set $T$
\end{definition}

\begin{definition}[one-parameter process]
  A  process whose index set $T$ has one dimension is a one-parameter process.
\end{definition}

\begin{definition}[dynamical system]
  A dynamical system  consists of a measurable space $\Xi$, a $\sigma$-algebra $\mc{X}$ on $\Xi$, a probability measure $\mu$ defined on $\mc{X}$, and a mapping $T\colon \Xi \mapsto \Xi$ which is $(\mc{X},\mc{X})$-measurable
\end{definition}

\subsection{mixing}

\begin{definition}[mixing]
  A dynamical system $(\Xi, \mc{X}, \mu, T)$ is mixing when, for any $A,B \in \mc{X}$,
  \begin{align*}
    \lim_{t\to \infty} |\mu(A\cap T^{-t}(B))-\mu(A)\mu(T^{-t}(B))|=0,
  \end{align*}
  where $T^{-t}(A)=T^{-1}(T^{-t+1}(A))$.
  For stochastic process, ``mixing'' means ``asymptotically independent'', which means the statistical dependence between $Y(t_1)$ and $Y(t_2)$ goes to zero as $|t_1-t_2|$ increases.
\end{definition}

\begin{definition}[near epoch dependence]
\label{ned}  $\{Y_t\}$ is a near epoch dependent (NED) on a mixing process $\{V_t\}$ if $\E (Y_t^2) < \infty$ and $v_k= \sup_t \norm{Y_t-\E_{t-k}^{t+k}(Y_t)}_2 \to 0$ as $k \to \infty$, where $\norm{\cdot}_p$ is the $L_p$ norm and $\E_{t-k}^{t+k}(\cdot) \equiv \E (\cdot | \mc{F}_{t-k}^{t+k})$, where $\mc{F}_{t-k}^{t+k}\equiv \sigma(V_{t-k}, \ldots, V_{t+k})$ is the $\sigma$-algebra generated by $V_{t-k}, \ldots, V_{t+k}$.
\end{definition}

\begin{definition}
  If $v_k= O(k^{-a-\delta})$ in Definition \ref{ned} for some $\delta > 0$, we say $\{Y_t\}$ is NED of size $-a$.
\end{definition}

\begin{definition}[conditional stationarity]
  A one-parameter process $\{Y_t\}$ is conditionally stationary if for all $n\in \naturals$ and every set of $n+1$ indices $t_1, \ldots, t_{n+1}\in T$, $t_i < t_{i+1}$, and every shift $\tau$,
  \begin{align*}
    \mc{L}(Y_{t_{n+1}}|Y_{t_1}, Y_{t_2}, \ldots, Y_{t_n})
    = \mc{L}(Y_{t_{n+1}+\tau}|Y_{t_1+\tau }, Y_{t_2+\tau }, \ldots, Y_{t_n+\tau })
    \quad a.s.,
  \end{align*}
  where $\mc{L}(Y|X)$ is the distribution function of a $Y$ conditional on $X$.
\end{definition}

\begin{definition}[$\alpha$-mixing]
  For a stochastic process $Y_t$, the $\alpha$-mixing coefficient is 
  \begin{align*}
    \alpha(t_1, t_2) = \sup \{
    |\P(A\cap B)-\P(A)\P(B)|\colon A\in \sigma(Y_{t_1}^{-}), B\in \sigma(Y_{t_2}^{+})\},
  \end{align*}
  where $Y^{+}=\max\{Y, 0\}$ and $Y^{-}=\max\{-Y, 0\}$. 
  If the system is conditionally stationary, $\alpha(t_1, t_2)=\alpha(t_2, t_1)=\alpha(|t_1-t_2|)\equiv \alpha(\tau)$. If $\alpha(\tau)\to 0$ as $\tau \to \infty$, the process is $\alpha$-mixing.
\end{definition}

\bibliographystyle{plainnat}
\bibliography{synthetic-prediction-notes}

\end{document}

### 2021-07-01 transience-prediction.tex
addition of simulation codes and setup

@@
 \def\P{\mathbb{P}}
+
+\newcommand{\ceil}[1]{\lceil #1 \rceil}
 
@@
 \begin{align*}
-  y_{i,t} &= K(\mc{F}_{i, t-1}) + \mathbf{x}_{i,t}\boldsymbol{\beta}  + \alpha_{i,t} I(t > T_i^*)+\varepsilon_{i,t},\\
-         \alpha_{i,t} &= \mu_{t}^{\alpha} + \mbf{z}_{i,t}\bs{\gamma}_{i} + \tilde{\varepsilon}_{i,t}
+  y_{i,t} &= K(\mc{F}_{i, t-1}) + \mathbf{x}_{i,t}\boldsymbol{\beta}  +  \textcolor{red}{\alpha_{i} I(t > T_i^*)}+\varepsilon_{i,t},\\
+         \alpha_{i} &= \mu_{\alpha} + \mbf{x}_{i,T_i^*+1}\bs{\gamma}_{i} + \tilde{\varepsilon}_{i}
 \end{align*}
@@
 
+\newpage
+
+\section{Simulation Setup}
+
+Let $n$ denote the donor pool size, $p$ denote the number of covariates used, $H$ denote the number of horizon used, $T_i$ denote the length of time series to be evaluated for time series $i$, $K_i$ denote the training sample size used for each  forecasting  time series $i$, $T_i^*$ denote the time point just before the realization of the shock for time series $i$ for $i = 1, \ldots, n+1$.
+
+$n$, $p$, and $H$ are pre-determined.
+$T_i, K_i \sim \mrm{Gamma}(15, 10)$.
+The total sample size for $i$th time series is $T_i + K_i + H$.
+$T_i^*$ is randomly sampled from $\ceil{\frac{1}{4}T_i}+1$ to $\ceil{\frac{3}{4} T_i} + K_i+ H$.
+If $T_i, K_i < 90$, we force them to be 90.
+The adopted model for the data is as below:
+\begin{align*}
+  y_{i,t} &= \eta_i + \phi_i y_{i,t-1} + \mbf{x}_{i,t} \bs{\beta}_i + \alpha_i I(t > T_i^*) + \varepsilon_{i,t},\\
+  \alpha_i &= \mu_{\alpha} + \mbf{x}_{i,T_i^*+1}\bs{\gamma}_i + \tilde{\varepsilon}_{i},
+\end{align*}
+where
+\begin{align*}
+  \phi_i & \sim \text{ indep. }  U(0,1) \\
+  \eta_i & \sim \text{ indep. }  \mc{N}(0,1) \\
+  \varepsilon_{i,t} & \sim \text{ indep. } \mc{N}(0, \sigma^2)\\
+  \tilde{\varepsilon}_i & \sim \text{ indep. } \mc{N}(0, \sigma_{\alpha}^2)
+  \\
+  \bs{\gamma}_i & \sim \text{ indep. } \mc{N}(\mu_{\gamma}\bs{1}_p, \sigma_{\gamma}^2 \mbf{I}_p) \\
+  \bs{\beta}_i & \sim \text{ indep. }  \mc{N}(\bs{0}_p, \mbf{I}_p).
+\end{align*}
+Moreover, the elements of $\mathbf{x}_{i,t}$ are independently distributed as $\mrm{Gamma}(1,\delta)$.
+
 \bibliographystyle{plainnat}

### 2021-07-01 simu.R

@@ -1,0 +1,313 @@
+# load packages
+require('forecast')
+
+# this function returns the W^* estimated by synthetic control method (SCM)
+scm <- function(X, Tstar) {
+  # X is a list of covariates for disparate time series
+  # X[[1]] should be the covariate of the time series to predict
+  # X[[p]] for p = 2,...,n+1 are covariates for time series pool
+  
+  # T^* is a vector of shock-effects time points
+  # shock effect point must be > 2
+  
+  # package for constrained optiminization
+  require('Rsolnp')
+  
+  # number of time series for pool
+  n <- length(X) - 1
+  
+  # covariate for time series for prediction
+  X1 <- X[[1]][Tstar[1] + 1, , drop = FALSE]
+  
+  # covariates for time series pool
+  X0 <- c()
+  for (i in 1:n) {
+    X0[[i]] <- X[[i + 1]][Tstar[i + 1] + 1, , drop = FALSE]
+  }
+  
+  # objective function
+  weightedX0 <- function(W) {
+    # W is a vector of weight of the same length of X0
+    n <- length(W)
+    p <- ncol(X1)
+    XW <- matrix(0, nrow = 1, ncol = p)
+    for (i in 1:n) {
+      XW <- XW + W[i] * X0[[i]]
+    }
+    norm <- as.numeric(crossprod(matrix(X1 - XW)))
+    return(norm)
+  }
+  
+  # constraint for W
+  Wcons <- function(W) sum(W) - 1
+  
+  
+  # optimization
+  solnp(par = rep(1/n, n), fun = weightedX0, eqfun = Wcons, eqB = 0, 
+        LB = rep(0, n), UB = rep(1, n), control = list(trace = 0))
+}
+
+# squared error loss
+sel <- function(yhat, y) {
+  (y - yhat) ^ 2
+}
+
+# taSPA test for comparison of two models
+taSPA.mhfc <- function(ell, d, B, bw = 4) {
+  # ell is the block length
+  # d is the matrix of loss differential
+  # B is the bootstrap size
+  # bw is the bandwidth parameter for computing HAC estimator
+  
+  # compute dbar
[…]

### 2021-07-01 simu.R
addition of simulation codes and setup

@@ -231,19 +231,20 @@ sim.normal.gammaX <- function(mu.gamma.delta = 1, mu.alpha, sigma,
   }
   
   # estimates
-  ps <- ps.indic.W(Tstar = Tstar, Y = Y, X = X, K = K, H = H, Ts = Ts, ell = ell, B = B, bw = bw)$ps
-  W <- ps.indic.W(Tstar = Tstar, Y = Y, X = X, K = K, H = H, Ts = Ts, ell = ell, B = B, bw = bw)$W
-  Is <- ps.indic.W(Tstar = Tstar, Y = Y, X = X, K = K, H = H, Ts = Ts, ell = ell, B = B, bw = bw)$Is
+  est <- ps.indic.W(Tstar = Tstar, Y = Y, X = X, K = K, H = H, Ts = Ts, ell = ell, B = B, bw = bw)
+  ps <- est$ps
+  W <- est$W
+  Is <- est$Is
   # compute forecasts
-  phat <- sum(ps[-1] * W)
-  Ihat <- sum(ps[-1] * Is)
+  phat <- sum(W * ps[-1])
+  Ihat <- sum(W * Is[-1])
   p.diff <- abs(phat - ps[1])
   I.diff <- abs(Ihat - Is[1])
   return(c(p.diff = p.diff, I.diff = I.diff))
 }
 
-result <- sim.normal.gammaX(mu.alpha = 0, mu.gamma.delta = 0, sigma = 1, sigma.alpha = 1, p = 4,
-                            B = 500, n = 5, H = 12, scale = 5, ell = 3)
+system.time(result <- sim.normal.gammaX(mu.alpha = 0, mu.gamma.delta = 0, sigma = 1, sigma.alpha = 1, p = 4,
+                            B = 20, n = 5, H = 12, scale = 5, ell = 3))
 
 
 # MC

### 2021-07-01 prevalence_testing/postshocktest2021draft.tex
reorganized repository

--- 2021-02-02 Revision/manuscript.tex
@@
-\documentclass[11pt,3p,review,authoryear]{elsarticle}
+\documentclass[11pt]{article}
+
+% use packages
 \usepackage[utf8]{inputenc}
@@
 \usepackage{enumitem}
+\usepackage{url}
+\usepackage{authblk}
 \usepackage{bm}
 \usepackage[usenames]{color}
+\usepackage{hyperref}
+\usepackage{geometry}
 \usepackage{caption}
@@
 \usepackage{pdflscape}
-\PassOptionsToPackage{hyphens}{url}
-\usepackage{hyperref}
+% margin setup
+\geometry{margin=0.8in}
 
@@
 
-\journal{International Journal of Forecasting}
+\allowdisplaybreaks
 
-\bibliographystyle{model5-names}
-\biboptions{longnamesfirst}
+\title{Testing for the prevalence or transience of a shock effect in the post-shock setting}
+\author{}
+\date{}
 
@@
 
-\begin{frontmatter}
-
-\title{Minimizing post-shock forecasting error through aggregation of outside information}
-
+\maketitle
 \begin{abstract}
-    We develop a forecasting methodology for providing credible forecasts for time series that have recently undergone a shock.
-We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
-Three shock effect estimators are motivated with the aim of minimizing average forecast risk.
-We propose risk-reduction propositions that provide conditions that establish when our methodology works.
-Bootstrap and leave-one-out cross validation procedures are provided to prospectively assess the performance of our methodology.
-Several simulated data examples, and two real data examples of forecasting Conoco Phillips and Apple stock price are provided for verification and illustration.
+ We provide a hypothesis test for the existence or transience of a shock in the post-shock setting of \cite{lin2021minimizing}.
 \end{abstract}
 
-\begin{keyword}
-  Data Integration \sep 
- Prospective forecasting \sep 
- Risk reduction \sep 
-Residual bootstrap \sep 
-Cross validation 
-\end{keyword}
-
-\end{frontmatter}
-
-\section{Introduction}
-
-We provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
-We focus on the specific setting in which a structural shock has occurred and one desires a prediction for the post-shock response at the next time point.
-Standard forecasting methods may not yield accurate predictions in the presence of such structural shocks \citep{baumeister2014real}.
-This is a general problem that has many real life applications.
-For example, one may be interested in forecasting the stock price of a company tomorrow after hearing terrible or great news about the company after trading has concluded for the day.
-Companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis, but they only have recent sales data for which the company is operating well.
-All is not lost in this forecasting setting, one may be able to supplement the present forecast with past data borrowed from other time series which contain similar structural shocks.
-The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
-Our method of combining shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
-
-We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models.
-In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed.
-In this setting, we treat the additive shock effect as an observed random effect, obtained from a distribution of similar shocks, that is parameterized as a conditional fixed effect within an autoregressive model.
-The shock effect is then estimated using ordinary least squares (OLS).
-The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}.
-One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}.
-Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}.
-On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting framework, provided that the shock effects from outside data sources arose from the same data generating process as the shock effect under study.
-For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of shocks from the recent past.
-Our shock effect setting is also similar to the data generating mechanism that  \cite{tsay1986time} studied for ARMA models.
-\cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses.
-Our shock effect of interest is similar to innovational  outliers  in the sense that it is an additive effect in the model of response only at a particular time point but it impacts the subsequent responses through an autoregressive structure.
-
-In our methodological framework, the researcher first creates a donor pool of time series which have undergone similar structural shocks in the past.
-Similarity in this context refers to the shock effects as arising from a distribution that has existing second moments, with extensions to variances and means that are linear functions of common covariates.
-The unobserved shock effect in the time series of interest is assumed to arise from the same distribution.
-Construction of the donor pool and the desired aims of the donor pool has precedent in synthetic control methodology (SCM) \citep{abadie2010synthetic}.
-As in SCM, care is needed when forming the donor pool of time series.
-However, there are several key differences between our framework and SCM.
-Unlike in SCM, we are not trying to estimate the causal effect of an intervention.
-Also, we assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock.
-This rules out panel data applications where the time series of interest and those forming the donor pool evolve in tandem.
-When there are large time differences between the time series under study and those forming the donor pool, then the dependence will be negligible in practice.
-This is the case in the Conoco Phillips and Apple stock forecasting examples.
-
-We then estimate the shock effects that are present in the time series forming the donor pool for which the post-shock responses are observed.
-These estimated shock effects are then aggregated.
-Finally, this aggregated estimator is added to the forecast for the yet to be realized post-shock response of the time series of interest.
-Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts.
-However, the approach of \cite{clements1996intercept} is not robust to unprecedented and unobserved shock since the shock signal is not embedded in the data.
-Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust general approaches for forecasting in vector equilibrium-correction models.
-However, their forecasting methodology requires conditioning on the past data that contain shock signals.
-This approach is therefore not applicable in the post-shock setting.
-The shock effects in our post-shock forecasting framework are similar to ``expectation shocks,'' studied in \cite{clements2019measuring}.
-\cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach, as in \cite{croushore2006data}.
-In our context, the yet to be observed shock effect of interest arises as a random effect whose assumed generative distribution can only be partially estimated.
-This partial estimation only uses shock effect estimates from the time series forming the donor pool.
-
-In this article, we will assume a simple autoregressive data generating process  with a general random-effect structure.
-These specifications are similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}.
-However, our model formulation is more general than \cite{ramaswamy1993empirical}.
-In our model, the donor pool can consist of dependent time series, but the time series forming the donor pool are required to be independent from the time series of interest.
-However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method.
-We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting.
-The latter technique is similar to the weighting in SCM \citep{abadie2010synthetic}.
-The considered adjustment strategies all target the mean of the shock effect distribution.
-Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean.
-We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast.
-The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop.
-We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators.
-This prospective assessment does not require the observation of the post-shock response.
-Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.
-We demonstrate the utility of our methodology with two real data analyses.
-The first of these focuses on forecasting the stock price of Conoco Phillips after March 9th, 2020, in the midst of the COVID-19 pandemic and an oil supply war.
-The second of these focuses on forecasting the stock price of Apple Inc.
-after the company releases their latest installment of the MacBook on November 10th, 2020.
-We will show that our proposed adjustment estimators yield much better results than no adjustment in these examples.
-The Conoco Phillips example provides an empirical application of our methods when the shock is anticipated yet unprecedented in nature, arising from a global pandemic and an oil supply shock.
-The Apple example provides a case for post-shock prediction when the shock has precedent, we forecast the stock price after the latest release of the MacBook.
-We now elaborate our framework for post-shock prediction, we start with an illustration.
-
-\begin{figure*}[t!]
-  \begin{center}
-    \subfloat[]{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
-     \subfloat[]{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
-  \end{center}
-     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$.
-(a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series.
-(b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.
-The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool.
-$\hat{y}^{1}_{T_1^*+1}$ is the prediction without any adjustment, and $\hat{y}^{2}_{T_1^*+1}$ is the forecast with additive adjustment of $\hat{\alpha} = n^{-1}\sum_{i=2}^{n+1}\hat\alpha_i$.
-In this example, theses forecasts differ by $\hat{\alpha}=10.22$.
-It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
-\end{figure*}
-
 \section{Setting}
-\label{setting}
-
-We will suppose that a researcher has time series data ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$, where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
-Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection.
-We will suppose that specific interest is in forecasting the response after the occurrence of a structural shock.
-To gauge the performance of forecasts, we consider forecast risk in the form of MSE,
-$$
-  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2,
-$$
-and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.
-In this article, we focus on post-shock prediction where forecasting methods only differ at the next future time point.
-Thus the MSE reduces to the magnitude $\E{\hat y_{1,t} - y_{1,t}}^2$.
-
-Our post-shock forecasting methodology will consist of selecting covariates $\x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), for $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
-In this article, we consider a  special case that the model includes random effects for the covariates, autoregressive structure, and an additional shock effect, whose presence or absence is given by the indicator variable $D_{i,t}$.
-We will assume that the donor pool time series are independent of the time series under study.
-The details of this model are in the next section.
-
-Figure \ref{figure1} provides a simple intuition of the practical usefulness of our proposed methodology.
-This figure depicts a time series that experienced a shock at time point $T_1^*+1 = 126$.
-It is supposed that the researcher does not have any information after $T_1^*$, but does have observations from a donor pool of forty time series that have previously undergone similar shocks for which post-shock responses are recorded.
-Similarity in this context means that the shock effects are random realizations from a common distribution.
-In this example, the mean of the estimated shock effects is taken as a shock effect estimator for the time series under study.
-Forecasts are then made by adding this shock effect estimator to the estimated response values obtained from the estimation procedure that ignores the shock.
-It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock effect.
-We evaluate the performance of this post-shock forecasting methodology throughout this article; we outline situations for when it is expected to work and when it is not.
 
@@
 
-We now describe the assumed autoregressive models with random effects for which post-shock aggregated estimators are provided.
-The basic structures of these models are the same for all time-series in the analysis, the differences between them lie in the setup of the shock effect distribution.
-
+The assumed autoregressive models considered are that in \cite{lin2021minimizing}, we describe details here.
 Let $I(\cdot)$ be an indicator function, $T_i$ be the time length of the time series $i$ for $i = 1, \ldots, n+1$, and $T_i^*$ be the time point just before the one when the shock is known to occur, with $T_i^* < T_i$.
@@
 \end{align*}
-where $\indep $ denotes the independence operator. Notice that $\mc{M}_1$ assumes that $\alpha_i$ are iid with $\E{\alpha_i}=\mu_{\alpha}$ 
-for $i = 1, \ldots, n+1$.
-We also consider a model where the shock effects are linear functions of covariates with an additional additive mean-zero error.
+where $\indep $ denotes the independence operator.
+We also consider a modeling framework where the shock effects are linear functions of covariates with an additional additive mean-zero error.
 For $i = 1, \ldots, n+1$, the random effects structure for this model (model $\mc{M}_2$) is:
@@
 \label{forecast}
-In this section we show how post-shock aggregate estimators improve upon standard 
-forecasts that do not account for the shock effect.
 
-More formally, we will consider the following candidate forecasts: 
+In our post-shock setting we consider the following candidate forecasts: 
 \begin{align*}
@@
 where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all OLS estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
-The first forecast ignores the presence of $\alpha_1$ while the second forecast 
-incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study.
+%The first forecast ignores the presence of $\alpha_1$ while the second forecast incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study.
 
-%Note that the two forecasts do not differ in their predictions for $y_{1,t}$, $t = 1,\ldots T_1^*$. Instead, they only differ in predicting $y_{1,T_1^*+1}$. 
 Throughout the rest of this article we highlight when the information from the time series donor pool, indexed by $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$, can be used to construct a shock effect estimator $\hat\alpha$ in which Forecast 2 beats Forecast 1 and vice-versa.
 We will consider the different dynamic panel models $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-Improvement will be measured by assessing the reduction in risk that Forecast 2 offers over Forecast 1.
+%Improvement will be measured by assessing the reduction in risk that Forecast 2 offers over Forecast 1.
 We outline the theoretical details of risk-reduction in Section \ref{properties}.
@@
 Despite this shortcoming, adjustment of the forecast for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has the potential to lower forecast risk under several conditions, and for several estimation techniques.
+We want to determine which forecast is appropriate over a horizon while the methods in \cite{lin2021minimizing} were only appropriate in the nowcasting setting in which prediction was only focused on the response immediately following the shock.
 
-\subsection{Shock effect estimators}
-\label{constructionofestimators}
+\subsection{Multi-horizon forecast evaluation}
 
-We now construct the aggregated estimators of the shock effects that appear in Forecast 2 (see Section \ref{forecast}).
-We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.
-First, we introduce the procedures of parameter estimation for $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}).
-For $i = 2, \ldots, n+1$, all parameters in this model will be estimated via ordinary least squares (OLS) using historical data indexed by $t = 1, \ldots, T_i$.
-For $i = 1$, we estimate all the parameters, excluding $\alpha_1$, using OLS for time periods indexed by $t=1, \ldots, T_1^*$.
-Let $\hat{\alpha}_i$ be the OLS estimate of $\alpha_i$, $i = 2, \ldots, n+1$.
-Note that parameter estimation under $\mc{M}_1$ is the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.
-We emphasize that the $\alpha_i$s are realizations from a random effects distribution, and that the OLS estimators $\hat\alpha_i$ assumes that these realized values are conditional fixed effects in an autoregressive model, as in \eqref{equation1} and \eqref{model2}.
+We now consider an approach for comparing the forecasts over a specified time horizon after a shock has occurred by borrowing information across similar forecasts.
 
-The candidate estimators for $\alpha_1$ are now introduced. Define the adjustment estimator for time series $i=1$ by 
-\begin{equation} \label{adjusted}
-  \hat{\alpha}_{\text{adj}} = \frac{1}{n}\sum_{i=2}^{n+1}\hat{\alpha}_i,
-\end{equation}
-We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
-the unknown $\alpha_1$ term for which no meaningful estimation information 
-otherwise exists. It is intuitive that $\hat{\alpha}_{\rm adj}$ should perform 
-well under $\mc{M}_1$ where we assume that $\alpha_i$s share the same mean 
-for $i= 1, \ldots, n+1$. However, it can also be shown that 
-$\hat{\alpha}_{\rm adj}$ may be less favorable in $\mc{M}_{21}$ 
-and $\mc{M}_{22}$, which will be discussed in detail in Section \ref{properties}.
+\cite{quaedvlieg2021multi} provided a methodology for comparing forecasts jointly across all horizons of a forecast path, $h = 1,\ldots, H$.
+In our post-shock setting, we want to compare the forecasts
+$$
+  \hat y^{1,h}_{1,t} \; \text{and} \; \hat y^{2,h}_{1,t}
+$$
+where $y^{1,h}_{1,t}$ is the forecast for $y_t$ that accounts for the yet-to-be observed structural shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{1,t}$ is defined similarly for the forecast that does not include any shock effect information.
+We will compare these forecasts in terms of their loss differential
+$$
+  d_t = L_{1,t} - L_{2,t},
+$$
+where $L_{j,t} = L(y_t,\hat y_{j,t})$, $j = 1,2$, and $L$ is a loss function.
+Hypothesis tests in \cite{quaedvlieg2021multi} are with respect to $E(d_t) = \mu_t$.
+Conditions for these tests require conditions of \cite{giacomini2006tests}.
 
-We also consider the inverse-variance weighted estimator 
-in practical settings where the $T_i$s and $T_i^*$s vary greatly across $i=2, \ldots, n+1$. 
-The inverse-variance weighted estimator is defined as 
-\begin{align*}
-  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
-  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{M}_i'\mbf{M}_i)_{22}^{-1},
-\end{align*}
-where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, $\hat{\sigma}_i$ is the residual standard error from OLS estimation, and $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$.
-Note that since $\sigma$ is unknown, estimation is required and the numerator and denominator terms are dependent in general.
-However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in practical settings, especially when the $T^*_i$s vary considerably.
-We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of $\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation (see Section \ref{simulation}).
+\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$.
+We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock.
+Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool.
 
-We now motivate a weighted-adjustment estimator appropriate for model $\mc{M}_{21}$ and $\mc{M}_{22}$.
-Our weighted-adjustment estimator is inspired by the weighting techniques in synthetic control methodology (SCM) developed in \cite{abadie2010synthetic}.
-However, our weighted-adjustment estimator is not a pure causal estimator, and our estimation premise is a reversal of the SCM context in \cite{abadie2010synthetic}.
-In our context, we predict the unobserved post-shock response $y_{1,T_1^*+1}$ (intervention is absent) using post-shock information from other time series whose post-shock responses are all observed (intervention is present).
+We will consider the average superior predictive ability (aSPA) to assess whether or not a shock is permanent or transitory.
+The aSPA investigates forecast comparisons based on their weighted average loss difference
+$$
+  \mu^{(AVG)} = \textbf{w}^T\mathbf{\mu} = \sum_{h=1}^H w_h \mu^h
+$$
+with weights $\textbf{w}$ that sum to one.
+Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1.
 
-We use similar notation as that in \cite{abadie2010synthetic} to describe our weighted-adjustment estimator.
-Consider a $\mbf{W} \in \R^n$ weight vector $\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all $i = 2, \ldots, n+1$.
-Construct
-\begin{align*}
- \mbf{X}_1 &= \mbf{x}_{1, T_1^*+1}',
-  \quad  
-  \mbf{X} = \begin{pmatrix}
-    \mbf{x}_{2, T_2^*+1}' \\
-    \vdots \\
-    \mbf{x}_{n+1, T_{n+1}^*+1}'
-  \end{pmatrix}, \\ 
-  \hat{\mbf{X}}_1(\mbf{W}) 
-   & = \mbf{W}'\mbf{X},
-\end{align*}
-where $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{1 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 
-Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
-$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that
-\begin{align}
- \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
-\end{align}
-Note that (\ref{SCM}) tries to find $\mbf{W}^*$ such that $\mbf{x}_{1, T_1^*+1}$ is a convex combination of $\mbf{x}_{i, T_i^*+1}$ for $i = 2, \ldots, n+1$ with weights $\mbf{W}^*$.
-Therefore, $\mbf{W}^*$ should exist as long as $\mbf{X}_1$ falls in the convex hull of
-$
-   \left\{ \mbf{x}_{2, T_2^*+1}', \ldots, \mbf{x}_{n+1, T_{n+1}^*+1}' \right\}.
-$
-Our weighted-adjustment estimator will therefore perform well when the pool of time series posses similar covariates to the time series for which no post-shock responses are observed.
-We compute $\mbf{W}^*$ as
-\begin{align}
-  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})}_{p}. 
-  \label{W}
-\end{align}
-\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ in \eqref{W} so that (\ref{SCM}) holds approximately and that weighted-adjustment estimation techniques of this form are not appropriate when the fit is poor.
-Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed.
-Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact.
-Because the objective function is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist.
-The weighted-adjustment estimator for the shock effect $\alpha_1$ obtained from the weights $\mbf{W}^*$ is defined as
-  \begin{align*}
-    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
-    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
-      w^*_2 & \cdots & w^*_{n+1}
-    \end{pmatrix}',
-  \end{align*}
-and we further define
-$
-  \mathbf{V} = (\mathbf{x}_{2, T_2^*+1}, \ldots,\mathbf{x}_{n+1, T_{n+1}^*+1}) \in \R^{p \times n}.
-$
-\begin{prop}
-  \label{uniqueness} If $\mathbf{V}$ has full rank then there exists some $\mathbf{W}^*$ that solves (\ref{SCM}) and this solution is unique.
-\end{prop} 
-Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.
-If $\mathbf{V}$ is full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is when $p \geq n$ in our setting.
-Non-uniqueness might be a concern theoretically.
-This is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$s, all targeting $\alpha_1$.
-For example, consider the case when $n = 2$, we have $\var{\hat{\alpha}_2}=1$ and $\var{\hat{\alpha}_3}=2$, the covariates are such that $\x_1 = \x_2 = \x_3$, and we consider $\mathbf{W}^*_1=(1,0)$ and $\mathbf{W}^*_2=(0,1)$ as solutions to \eqref{W}.
-In this hypothetical, the weighted adjustment estimator constructed from $\mathbf{W}^*_1$ has variance 1 whereas the same quantity constructed from $\mathbf{W}^*_2$ has variance 2.
-It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}).
-Empirically, we find some simulation evidence that non-uniqueness of $\mathbf{W}^*$ is not problematic for inferences in our setting.
-Specifics can be seen in Section 4 of the Supplementary Materials.
-We close this Section with some remarks about our shock-effect estimators:
-
-\begin{remark}
-\label{remark1}In Section \ref{modelsetup} we specify that $\mbf{x}_{i,t}, \theta_i \in \reals^p$. 
-However, it is not necessary that the all $p$ covariates are important for every time series under study.
-The regression coefficients $\theta_i$ are nuisance parameters that are not of primary importance.
-It will be understood that structural 0's in $\theta_i$ correspond to variables that are unimportant. 
-\end{remark}
-
-\begin{remark}
-  Our forecasting premise and estimation construction shares similarities with Bayesian viewpoints.
-From a Bayesian perspective, if we assign a prior $\pi$ to $\alpha_1$, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as the Bayes rules with respect to $\pi$ under different loss functions.
-If the sampling distribution of the data and $\pi$ are known, it is possible to compute the Bayes risks of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ with respect to $\pi$,  thus enabling comparisons among them.
-Additionally, from Theorem 2.4 in Chapter 5 of \cite{lehmann2006theory}, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are admissible if they are unique with probability one.
-\end{remark}
-
-\begin{remark}
-We also provide some recommended choices for shock-effect estimators in different situations.
-First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution.
-Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool.
-Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates.
-\end{remark}
-
-\section{Forecast risk, risk-reduction, and properties of shock effects estimators}
-\label{properties}
-
-In this section, we discuss the properties that are related to forecast risk-reduction.
-It is useful to first derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.
-The expressions for the expectations are as follows:
-
- \begin{enumerate}[label = (\roman*)]
-    \item Under $\mc{M}_{1}$, $\E{\hat{\alpha}_{\rm adj}}=\E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha}$.
-    \item Under $\mc{M}_{21}$, 
-    $
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1}
-    $
-    and
-    $
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} .
-    $
-    \item Under $\mc{M}_{22}$,
-    $
-      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1}
-    $
-    and
-    $
-       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} .
-    $
-  \end{enumerate}
-Formal justification for these results can be found in the Appendix.
-Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$.
-However, under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$.
-Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$.
-On the other hand, $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$.
-We collect these results in the following proposition:
-
-\begin{prop}
-\label{unbiased} 
-\quad 
-\begin{enumerate}[label = (\roman*)]
-  \item Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$.
-Under $\mc{M}_{21}$ and $\mc{M}_{22}$, $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ in general.
-  \item Suppose that $\mbf{W}^*$ satisfies (\ref{SCM}). Under $\mc{M}_{1}$, $\mc{M}_{21}$ and $\mc{M}_{22}$, $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
-\end{enumerate}
-\end{prop}
-
-Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation procedure for evaluation of these conditions, discussed in Section \ref{conditions} and \ref{varbootstrap} respectively.
-Throughout this section, we have specified that the time series within the donor pool are independent.
-This is needed for exact variance expressions.
-However, the theory developed later allows for dependence within the donor pool.
-Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:
-
-\begin{enumerate}[label = (\roman*)]
-  \item Under $\mc{M}_1$ and $\mc{M}_{21}$,  
-\begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma^2_i\, \mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}, \\
-\var{\hat{\alpha}_{\rm wadj}}  &= \sum_{i=2}^{n+1}(\sigma_iw_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.
-\end{align*}
-\item Under $\mc{M}_{22}$, 
-\begin{align*}
-\var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\, \mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}),\\
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &=\sum_{i=2}^{n+1}(\sigma_iw_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
-\end{align*}
-\end{enumerate}
-Formal justification for these results can be found in Section \ref{proofs} of the Appendix.
-Note that the variances are not comparable in closed-form because of the term $\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}$, where  $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$ from Section \ref{constructionofestimators}.
-This term exists because of the inclusion of the random lagged response in our autoregressive model formulation.
-
-Section \ref{conditions} details conditions needed for risk-reduction and comparisons of adjustment estimators.
-These conditions involve variances and expectations which may be difficult to compute in practice.
-To make use of those conditions in practice, estimation is required.
-Sections \ref{varbootstrap} introduce a residual bootstrap procedure which estimates the involved parameters in those conditions and thus motivates prospective decision-making about whether $\hat{\alpha}_i$ reduces the risk.
-Section \ref{loocv} describes our leave-one-out cross validation procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study.
-Our simulations verify these procedures.
-
-\subsection{Risk-reduction conditions for shock effects estimators}
-\label{conditions}
-
-In this section we will discuss the conditions for risk reduction for individual shock effects estimators under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-For an adjustment estimator $\hat{\alpha}$, we will write the risk-reduction as $\Delta(\hat{\alpha})=R_{T_1^*+1,1}-R_{T_1^*+1,2}$ where $R_{T_1^*+1,2}$ is the risk of Forecast 2 calculated using the adjustment estimator $\hat{\alpha}$.
-
-\subsubsection{Conditions under $\mc{M}_1$}
- \label{conditionsmodel1}
-
-Recall that Proposition \ref{unbiased} implies that the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ are unbiased for $\E{\alpha_1}$ under $\mc{M}_1$.
-With this result, we will have  the following proposition that specify the conditions that are necessary for risk reduction:
-
-\begin{prop}
-\label{proprisk}Under $\mc{M}_1$,
-\begin{enumerate}[label = (\roman*)]
-  \item $\Delta(\hat\alpha_{\rm adj}) > 0$  when 
-$\Var(\hat{\alpha}_{\rm adj}) < \mu_{\alpha}^2$.
-  \item if $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<\mu_{\alpha}^2$. 
-\end{enumerate}
-\end{prop}
-
-Proposition \ref{proprisk} says that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties.
-In this setting, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$.
-From Proposition \ref{proprisk}, we obtain a risk-reduction condition
-\begin{align}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\, \mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
-\end{align}
-
-Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$; (2) In the finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.
-
-If  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}.
-From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
-\begin{align} \label{varwadj}
-\var{\hat{\alpha}_{\rm wadj}}
- &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
-\end{align}
-In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.
-However, the above criteria are generally difficult to evaluate in practice.
-Sections \ref{varbootstrap} and \ref{loocv}  provide detailed treatments on how to estimate the sign of $\Delta(\hat\alpha)$ in practice.
-
-\subsubsection{Conditions under $\mc{M}_{21}$ and $\mc{M}_{22}$}
-\label{conditionsm2122}
-
-The shock effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$.
-However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$.
-We now state conditions for risk-reduction.
-
-\begin{prop}
-\label{propriskwadj2} If $\mbf{W}^*$ satisfies (\ref{SCM}), then $\Delta(\hat\alpha_{\rm wadj}) > 0$ when $\var{\hat{\alpha}_{\rm wadj}}<(\E{\alpha_1})^2$  under $\mc{M}_{21}$ and $\mc{M}_{22}$. 
-\end{prop}
-Under Proposition \ref{propriskwadj2}, we can obtain a risk-reduction inequality that is similar to \eqref{varwadj},
-\begin{align*}
-\var{\hat{\alpha}_{\rm wadj}}
-& =\sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}) < (\E{\alpha_1})^2,
-\end{align*}
-where $\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$.
-The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.
-Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ in general.
-Hence, Proposition \ref{proprisk} no longer holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.
-
-As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting. By Lemma \ref{risklemma}, we will achieve risk-reduction when
-\begin{align*}
- \E{\alpha_1^2} &= \var{\alpha_1}+(\E{\alpha_1})^2\\
- &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
-  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
-  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
-\end{align*}
-The above inequality simplifies to 
-\begin{equation} \label{ineq}
- (\E{\alpha_1})^2 >\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
-\end{equation}
-
-As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$.
-We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$.
-We can adapt the above to derive a risk-reduction condition for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
-In fact, more generally, using similar proof of Lemma \ref{risklemma}, it can be shown that under $\mc{M}_2$, the risk-reduction quantities are
-\begin{align*}
-  \Delta(\hat{\alpha}_{\rm adj}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2,\\
-  \Delta(\hat{\alpha}_{\rm IVW}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2 ,\\
-  \Delta(\hat{\alpha}_{\rm wadj}) 
-  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}.
-\end{align*}
-We estimate $\Delta(\hat{\alpha})$ using bootstrap and leave-one-out cross validation procedures developed in Sections \ref{varbootstrap} and \ref{loocv}.
-
-\subsection{Bootstrap for risk-reduction evaluation problems}
-\label{varbootstrap}
-
-We present bootstrap procedures that approximate the distribution of our shock effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction quantity using plug-in approach in practice.
-Our procedure involves the resampling of residuals in the separate OLS fits.
-This procedure has its origins in Section 6 of \citet{efron1986bootstrap} and Chapter 12 of \cite{kilian2017structural}.
-Our procedure involves the resampling of the residuals which are assumed to be the realizations of an iid process.
-
-Our first bootstrap procedure is as follows: Let $B$ be the bootstrap sample size.
-At iteration $b$, first resample the indices $I = \{2, \ldots, n+1\}$ of the donor pool with replacement to form $I^{(b)}$ with cardinality $n$, where we note that the elements of $I^{(b)}$ may not be unique in terms of their  indices in the donor pool.
-Initialize $y_{i,0}^{(b)}=y_{i,0}$ for all $i \in I^{(b)}$.
-Then, resample the residuals under models $\mc{M}_1$ or $\mc{M}_{2}$, compute the bootstrapped response  $y_{i,t}^{(b)}$ for   $t \in \{1, \ldots, T_i\}$ using the model estimated by original data,  and obtain shock effect estimators for each of the time series in the donor pool for all $i \in I^{(b)}$.
-These shock effect estimators are then used to construct any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-We can then estimate distributional quantities of our shock effect estimators under our considered models with the bootstrap samples $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
-We denote this procedure by $\mc{B}_u$.
-We motivate a second bootstrap procedure $\mc{B}_f$ which treats the the donor pool as fixed, and not a realization from an infinite super-population.
-Therefore, there is no resampling of the donor pool in $\mc{B}_f$, it is otherwise similar to $\mc{B}_u$.
-An algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$  are outlined in Section 2 of the Supplementary Materials.
-
-We will explicitly use these bootstrapped samples of shock effect estimators to check the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.
-Recall that $\hat{\alpha}_{\rm adj}$,  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ under $\mc{M}_1$ and $\mc{M}_2$ from Proposition \ref{unbiased}.
-Our bootstrap procedure estimates the variance of our adjustment estimators.
-We can then estimate the risk-reduction propositions and inequalities.
-For example, we can estimate $\Delta(\hat{\alpha}_{\rm adj})$ under model $\mc{M}_{21}$ or $\mc{M}_{22}$ with
-\begin{align*}
-  \hat{\Delta}(\hat{\alpha}_{\rm adj}) & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
-\end{align*}
-where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance estimator for $\Var(\hat{\alpha}_{\rm adj})$.
-
-We reiterate the philosophical distinction between $\mc{B}_u$ and $\mc{B}_f$.
-$\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors.
-In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness arises from parameters and idiosyncratic error.
-A double bootstrap procedure with similar steps can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$.
-The double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, can check whether a bootstrap percentile interval of resampled estimates of $\Delta(\hat{\alpha})$ contain 0 at a desired error threshold.
-We investigated such a double bootstrap procedure and found that it produced inferences that were similar to those produced using the bootstrap techniques developed in the main text.
-
-We stress that our bootstrap approximations cannot alleviate the inherent bias of using our adjustment estimators as surrogates for $\alpha_1$.
-We caution that the bootstrapping residuals in OLS estimation may not provide valid inference in moderate or high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}; see alternatives for residual bootstrapping in linear models in \citet{el2018can}.
-
-\subsection{Leave-one-out cross validation}
-\label{loocv}
-
-In this section, we motivate a leave-one-out cross validation (LOOCV) procedure within our estimation context in order to provide prospective evaluations of our adjustment techniques.
-Our proposed LOOCV procedure has its roots in Section 7.10 of \citet{hastie2009elements}.
-Recall in Section \ref{modelsetup} that we have data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining observations form the donor pool.
-For iteration $m \in \{1,\ldots,n\}$ of our LOOCV procedure, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}_m, t = 1, \ldots, T_{i}\}$, where $\mc{I}_m=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, we can evaluate the performance of our adjustment estimators and the original forecast made without adjustment.
-
-LOOCV can be very computationally intensive when $n$ is large, especially when combined with bootstrapping.
-To alleviate these concerns, one can perform LOOCV with a random subset of $k \leq n$ iterations selected without replacement.
-In this setting, we let $\mc{J}$ be the randomly sampled indices.
-For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$.
-Based on the new donor pool, we estimate relevant parameters using bootstrap procedures outlined in Section \ref{varbootstrap}.
-In other words, $k$ times of bootstrapping are nested in a LOOCV procedure.
-We find that $k=5$ or $k=10$ iterations of LOOCV performs well.
-
-We now outline how LOOCV can be used to prospectively assess the performance of adjustment estimators.
-Let $\mc{A}$ be the set of adjustment estimators.
-For each $\hat{\alpha} \in \mc{A}$, let $\delta_{\hat{\alpha}} = I(\hat\Delta(\hat{\alpha})>0)$ be a decision rule where $I(\cdot)$ is the indicator function and a $1$ corresponds to the decision to use  estimator $\hat\alpha$.
-If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported 1 (0, respectively) so that it makes the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be incorrect.
-If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported 0 (1, respectively) so that it makes the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be correct.
-These situations are depicted in the following table: \vspace*{0.3cm}
-
-\begin{center}
-  \begin{center}
-      \begin{tabular}{cc|c|c}
-        \hline
-        & & \multicolumn{2}{c}{Decision} \\
-        & & $\delta_{\hat{\alpha}} = 1$ & $\delta_{\hat{\alpha}} = 0$ \\ 
-                \hline
-     \multirow{2}{*}{Truth}  & $\Delta(\hat{\alpha})>0$ & Correct & Incorrect \\
-      \cline{3-4}
-      & $\Delta(\hat{\alpha})<0$  & Incorrect & Correct \\
-      \hline
-      \end{tabular}
-  \end{center}
-\end{center} 
-\vspace*{0.3cm}
-
-We will use 
-$
-	\mc{C}(\delta_{\hat\alpha}) 
-	= I(\delta_{\hat{\alpha}} \text{ is correct})
-$
-as a metric that evaluates the performance of forecasts made with the adjustment estimator $\hat\alpha$.
-If $\E{\mc{C}(\delta_{\hat{\alpha}})} > 0.5$, we claim that $\delta_{\hat{\alpha}}$ is better than random guessing.
-Note that $\mc{C}(\delta_{\hat{\alpha}})$ can generally be computed only when the post-shock response is observed.
-However, it is possible to estimate $\E{\mc{C}(\delta_{\hat{\alpha}})}$ using LOOCV.
-The LOOCV estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$ are
-\begin{equation} \label{loocvm}
-	 \bar{\mc{C}}(\delta_{\hat{\alpha}})= \frac{1}{n} \sum_{m = 1}^n \mc{C}^{(-m)}(\delta_{\hat{\alpha}}),
-	\end{equation}
-where $\mc{C}^{(-m)}(\delta_{\hat{\alpha}})$ is computed with respect to donor pool with index set $\mc{I}_m$ and the $m+1$ time series is treated as the time series of interest.
-The LOOCV with $k$ random draws estimates $\E{\mc{C}(\delta_{\hat{\alpha}})}$ as
-\begin{equation} \label{loocvk}
-	 \bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})	,
-\end{equation}
-where $\mc{J}$ is the set of the $k$ randomly sampled indices.
-
-\begin{remark}
-  Note that we allow the time series within the donor pool to be dependent but donor pool should be independent of the time series of interest.
-However, if we assume the mutual  independence structure, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ will be an almost unbiased estimator of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ \citep[Page 222]{msos}.
-\end{remark}
-
-\section{Numerical examples}
-\label{simulation}
-
-\subsection{Modeling setup}
-
-In this section we provide justification for our methods based on Monte Carlo simulation.
-We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.
-We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}.
-The parameter setup of our simulations is detailed as follows:
-\begin{align*}
-  \phi_i &\simiid U(0,1),	\\
-  \delta_i &\simiid  \normal{1}{0.5^2}, \\
-  \theta_i &\simiid \normal{0}{1}, \\
-  \alpha_i &\simiid \normal{\mu_\alpha}{\sigma_{\alpha}^2}, \\
-  T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
-  T_i^* &\simiid U\{p+4, T_i-1\}, \\
-  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2},
-\end{align*}
-where the $[\cdot]$ operation in the generation of the $T_i$'s corresponds to rounding the input to the nearest integer, $U(a,b)$, $U\{a,b\}$, and $\mrm{Gamma}(c,d)$, respectively,  denotes the continuous uniform distribution on the closed interval from $a$ to $b$, discrete uniform distribution on the set of integers from $a$ and $b$, and Gamma distribution with shape parameter $c$ and scale parameter $d$, respectively.
-The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank.
-Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths.
-Additionally, we generated all of the entries of the covariate vectors to be realizations from a $\text{Gamma}(1,2)$ distribution.
-
-We will consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$.
-We choose a Monte Carlo sample size of $30$ replications and a bootstrap sample size of $B = 200$ for our computations.
-Means and standard errors for estimated quantities will be recorded.
-Our LOOCV procedure will consider $k=5$ random draws.
-Recall in Section \ref{loocv} that $B$ times of bootstrap are nested in a LOOCV with $k$ random draws.
-It implies that $B(k+1)$ times of bootstrap replications are required for each Monte Carlo simulation.
-
-\subsection{Performance metrics}
-
-Our adjustment estimators will be evaluated by multiple criteria.
-We interpret $\delta_{\hat{\alpha}}= I(\hat{\Delta}(\hat{\alpha})>0)$ for $\hat{\alpha}\in \mc{A}$ as the guess, with 1 indicating that $\hat{\alpha}$ provides risk-reduction over the simple no-adjustment forecast, and 0 indicates the converse.
-We will consider the LOOCV estimators with $k$ random draws \eqref{loocvk} to assess correct decision making.
-We will also consider the Euclidean distance between the post-shock forecasts $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$ and the realized post-shock response $y_{1,T_1^*+1}$.
-The first two metrics can combine to assess our forecasting methodology prospectively while the latter requires the realization of the post-shock response $y_{1,T_1^*+1}$.
-
-\subsection{Monte Carlo results}
-\label{parametricbootstrapsimulation}
-
-We discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities.
-We mainly discuss simulations under model $\mc{M}_2$ and both bootstrap procedures, $\mc{B}_u$ and $\mc{B}_f$.
-Complementary simulations under $\mc{M}_1$ are provided in Section 3 of the Supplementary Materials.
-We now present the two simulation setups that are investigated in the main text.
-
-In the first simulation setup we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$.
-Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates.
-In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.
-Results are displayed in Table~\ref{table1} in the Appendix, Section \ref{tablesappendix}.
-
-In the second simulation setup, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n=10$.
-Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates ranges from strong to nearly nonexistant.
-Results are  in Table~\ref{table2} in the Appendix, Section \ref{tablesappendix}.
-
-First, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we  observe from Table \ref{table1} that the decision making using $\delta_{\hat{\alpha}}$ is nearly correct for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small.
-The reasons can be explained as follows: When $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal according to construction of $\hat{\alpha}_{\rm wadj}$ in Section \ref{constructionofestimators}.
-Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ and $\mc{M}_{21}$ are very similar and estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}.
-However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is large), the decision rule $\delta_{\hat{\alpha}}$  becomes unreliable for $\hat{\alpha}\in \mc{A}$.
-This is to be expected since the bootstrap estimates become more biased.
-However, users are warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ and they have an idea of the effectiveness of $\delta_{\hat{\alpha}}$.
-Second, fixing $\sigma_{\alpha}$, we can observe that the rate in which we make correct decisions, $\delta_{\hat{\alpha}}$, increases when $n$ increases.
-
-Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports that $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down.
-Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$.
-But it is not present for $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ since we applied the fact  $\hat{\alpha}_{\rm wadj}$ is unbiased for $\E{\alpha_1}$ from Proposition \ref{unbiased} in plugging it in with replacing $\E{\alpha_1}$.
-Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative.
-Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of correctness between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$.
-For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.83 \times 0.59 = 0.490$ from Table \ref{table1}.
-In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.
-
-In the last four columns of Table~\ref{table1} we can see that as $\sigma_{\alpha}$ increases, the prediction appears to be poorer.
-When $\sigma_{\alpha}= 5, 10, 25$, forecasts using $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are always better than the original forecast significantly.
-This does not hold generally for the case when $\sigma_{\alpha}=50, 100$.
-It is reasonable that when the $\sigma_{\alpha}$ is large, it is difficult to find a reliable estimate of $\alpha_1$.
-Nevertheless, no Monte-Carlo evidence has been found to support the claim that $n$ plays a large role prediction.
-
-From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases with $\sigma$ fixed, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases.
-Furthermore, as $\sigma$ increases we have that $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ decreases as well.
-Note that decision making ability hinges on the estimation of the parameters.
-Since $\hat{\alpha}_{\rm wadj}$  is a linear combination of OLS estimates, as $\sigma$ increases, $\var{\hat{\alpha}_{\rm wadj}}$ increases as well.
-Therefore, $\hat{\alpha}_{\rm wadj}$ become more volatile and its estimation of $\E{\alpha_1}$ can be less reliable.
-Those reasons can explain  why an increase of $\sigma_{\alpha}$ contributes to a decrease of  $\bar{\mc{C}}(\delta_{\hat{\alpha}})$.
-We observe similar patterns for distance to $y_{1, T_1^*+1}$ as well.
-When $\sigma$ increases with fixing $\sigma_{\alpha}$, it is likely that the degree of variation of $y_{1,t}$ exceeds the extent of adjustment improvement $\hat{\alpha}$ can contribute to for $\hat{\alpha}\in \mc{A}$.
-
-The averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ (i.e., the guess) starts to decrease as $\sigma$ increases.
-This is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$.
-The reasons are outlined as follows: Recall in Section \ref{conditionsm2122}, the conditions of risk-reduction propositions involve $(\E{\alpha_1})^2 > \var{\hat{\alpha}} + (\E{\hat{\alpha}}-\E{\alpha_1})^2$ for $\hat{\alpha}\in \mc{A}$.
-Notice that $\var{\hat{\alpha}}$ is an increasing function of $\sigma$ since $\hat{\alpha}$ is estimated by OLS.
-Therefore, it explains the reason why the increase of $\sigma$ would result in a decrease of averaged $I(\hat{\Delta}(\hat{\alpha})>0)$ since the inequality is not likely to hold when  $\var{\hat{\alpha}}$ increases.
-
-\subsection{Additional considerations}
-\label{parametricbootstrapsimulation2}
-
-We now present results from simulations under bootstrap procedure $\mc{B}_f$ under the same two parameter setups considered above.
-See Table \ref{table3} and Table \ref{table4} for results in the Appendix, Section \ref{tablesappendix}.
-From Table \ref{table1} and Table \ref{table3} we have that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is preferable to $\mc{B}_f$.
-For other situations, $\mc{B}_u$  and $\mc{B}_f$ perform similarly.
-It is likely that the extra randomness from sampling the donor pool with replacement compensates for the possible noises from a small donor pool.
-Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases.
-It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$.
-However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_f$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$.
-In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is moderately small; otherwise, they are similar.
-
- Simulation results corresponding to model $\mc{M}_1$ are listed in Section 3 in the Supplementary Materials.
-Results under model $\mc{M}_1$ are very similar to those of $\mc{M}_2$.
-The results show that: (1) the performance of $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are nearly the same and (2) in many situations, $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm IVW}$ are  better than $\hat{\alpha}_{\rm wadj}$; in other situations, they are mostly the same.
-Recall that in $\mc{M}_1$, the models for $\alpha_1$ do not involve the covariates.
-Therefore, similarity weighting may not be informative when the model for $\alpha_i$ is identified wrongly.
-Under $\mc{M}_1$, simple averaging, aimed for a reduction of variance, or inverse-variance weighting, targeting on reducing negative effects from varying time lengths, may work better.
-
-In these simulations we have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.
-Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions $\mathbf{W}^*$.
-In this scenario, $\mathbf{W}^*$ will take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.
-When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ that satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$.
-However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$.
-Empirically, simulations in Section 4 of the Supplementary Materials show that non-uniqueness does not seriously compromise inferences under $\mc{B}_u$.
-
-Our simulations provide some empirical evidence that $\mathcal{B}_u$ is preferred when the donor pool size is moderately small ($n< 10$) and the signal from the covariates is believed to be large.
-If $p < n$ and non-uniqueness problem is of concern for theoretical reasons,  $\mathcal{B}_f$ may be preferred.
-In most cases, the choice between $\mathcal{B}_u$  and  $\mathcal{B}_f$ would be up to personal preferences related to the philosophical differences between these bootstrap procedures.
-
-\section{Empirical examples}
-
-In this section, we discuss two real data examples of post-shock prediction.
-Section \ref{forecasting} discusses the prediction of Conoco Phillips stock occurring on March 9th, 2020.
-This shock relates to an oil price war and the COVID-19 pandemic.
-Section \ref{apple} applies our proposed method to the forecasting of Apple stock prices after releasing the latest version of their MacBook product.
-These examples provide empirical illustration of our methodology in settings where the shock has, respectively, unprecedented and precedented origins.
-%\textcolor{red}{Generalizations of our method are discussed as well.
-Section \ref{forecasting} allows the shock effect to be decomposed into separable estimable parts,  multiple shock effects to be nested in a time series, and different models for the response and the shock effects.
-Section \ref{apple} extends the forecasting adjustment at $T_1^*+1$ to $T_1^*+2$, and considers  a different model of the time series of interest  to that of   donor pool.
-In terms of the results, the adjusted forecast in Section \ref{forecasting} performs much better than the unadjusted original forecast, and the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.}
-
-\subsection{Forecasting Conoco Phillips stock in the presence of shocks}
-\label{forecasting}
-
-We demonstrate our post-shock forecasting methodology on a time series of Conoco Phillips share prices after the occurrence of a structural shock.
-Conoco Phillips is a large oil and gas resources company \citep{conocowhatwedo}.
-The particular post-shock response that we predict happened after trading ended on Friday March 6th, 2020 and before trading began on Monday March 9th, 2020.
-It is reasonable that the timing of this shock is known, several events occurred over the trading weekend which had an impact on stock markets and the oil markets.
-For example, Russia and OPEC began a battle for global oil price control on Sunday, March 8th \citep{sukhankin2020russian}, and several US states began declaring state of emergencies in response to the evolving coronavirus pandemic \citep{nygov, alonso2020state}.
-
-We collect our data through the use of \texttt{quantmod} package \citep{ryan2017quantmod} in R. In this analysis we make the following design considerations:
-
-\begin{enumerate}
-\item[(1)] {\bf Selection of model}.
-We will use an AR(1) model to forecast Conoco Phillips stock price.
-This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.
-For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect.
-All estimates will be adjusted for inflation.
-The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects.
-All the parameters are estimated using OLS.
-\item[(2)] {\bf Selection of covariates}.
-We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$.
-The model of $\alpha_i$ incorporates lagged daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX).
-The model for $y_{i,t}$ disregards VIX.
-This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
-\item[(3)] {\bf Construction of donor pool}.
-Our donor pool consists of Conoco Phillips shock effects observed in the past.
-We consider shock effects which occurred on March 15, 2008, several days in September, 2008, and November 27, 2014.
-The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession.
-In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}.
-These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie MacBook in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}.
-The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}.
-\end{enumerate}
-
-We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020.
-The covariates and response of time series in the donor pool are adjusted for inflation.
-Note that there are three shock effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Section 1 in the Supplementary Materials.
-The estimated shock-effects for $\alpha_i$ are $-0.922, -7.063, -5.777, -6.395, -4.207$ for $i = 2, \ldots, 6$, respectively.
-Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
-Note that non-uniqueness problems will not occur in this analysis since the conditions of Proposition \ref{uniqueness} are satisfied.
-To avoid the effect of  unit differences on weighting, we centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
-For $\hat{\alpha}_{\rm wadj}$, we observe that
-$
-  \mathbf{W}^*= (0.000,0.000, 0.000, 0.273, 0.727)
-$
-and 
-$
-  \Vert\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\Vert_2 = 3.440.
-$
-Note that the norm is computed using the $k$-dimensional Euclidean metric.
-The solution $\mathbf{W}^*$ suggests that the shock effect of interest is very similar to the September 25, 2008 shock effect and  the November 27, 2014 shock effect.
-
-The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-4.872$, $\hat{\alpha}_{\rm wadj}= -4.805$, and $\hat{\alpha}_{\rm IVW}=-4.384$.
-Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}.
-The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.419, 0.559, and 0.667, respectively.
-We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
-
-\begin{figure*}[t!]
-  \begin{center}
-    \includegraphics[height = 9cm]{FIG2.pdf}
-    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. Black dots and violet line represent real data and fitted line, respectively.}
-    \label{Fig:CP}
-  \end{center}  
-  \vspace{-.6cm}
-\end{figure*}
-
-We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well.
-Our estimation framework misses the yet to be observed post-shock response.
-However, they perform much better than unadjusted forecasts that do not account for shock effects.
-The unadjusted forecast misses the post-shock response by 9.870 dollars whereas
-the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively.
-
-The true shock effect is not fully recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$.
-This may be a result of a poorly constructed donor pool.
-The shock on March 9th, 2020 is in the midst of the COVID-19 pandemic and oil production volatility.
-It is difficult to find available stock market time series data that were generated under a similar setting.
-In any event, the shock on March 9th, 2020 was the largest price shock to Conoco Phillips shares by a wide margin, even after adjusting for inflation.
-
-From another perspective, it is possible that the stock of Conoco Phillips actually experienced multiple shocks on 2020 March 9th.
-For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector autoregressive model.
-Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context.
-Motivated by \citet{kilian2009not}, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect.
-The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects.
-The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects only, respectively, miss the post-shock Conoco Philips share price by $0.951$, $0.405$, and $1.460$ dollars.
-These additive adjustment estimators do extremely well in this additive shock setting.
-
-\subsection{Forecasting Apple stock in the presence of shocks}
-\label{apple}
-
-Apple Inc.
-is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch.
-Every year, Apple Inc.
-releases a new series of MacBook computers to the public.
-Typically, after the release, the stock price of Apple Inc.
-is expected to experience a shock since MacBook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced.
-For example, the sales of MacBooks account for 9.8\% of its revenue \citep{applemac}.
-In this example, we are interested in forecasting the stock price of Apple Inc.
-after the release of the latest MacBook on November, 10th, 2020.
-Our donor pool suggests that it takes two days for the shock effect to take hold.
-Therefore, we are interested in the stock price of Apple Inc.
-on the day after the release date, November 11th, 2020.
-Our data is collected using the \texttt{quantmod} package \citep{ryan2017quantmod} in R.
-The detailed considerations of our analysis are outlined as below:
-
-\begin{enumerate}[label = (\arabic*)]
-  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc.
-All the estimates will be adjusted for inflation.
-We consider $D_{i, t} = I(t = T_i^*+2)$.
-By observing  the data, we found a large shock effect on October 10th, 2020, two days before the release of iPhone 12, iPhone 12 Pro, MagSafe accessories, and HomePod mini.
-Denote this date by $T_{1,\#}$, and the shock effect by $\beta$.
-We account for this shock effect that is not of our interest in the model by setting
-  \begin{align*}
-    y_{1,t} &= \eta_i + \alpha_1 D_{1,t} +\phi_1y_{1, t-1}+\theta_1'\mathbf{x}_{1,t} + \beta I(t = T_{1,\#}) + \varepsilon_{i,t}.
-  \end{align*}
-  The model for the shock effect is
-  \begin{align*}
-    \alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{i,T_i^*+2}  + \tilde{\varepsilon}_{i,t}.
-  \end{align*}
-  Then, the weighting schemes introduced in Section \ref{constructionofestimators} will use  $\{\mathbf{x}_{i,T_i^*+2} \colon i = 1, \ldots, n+1\}$ for computing $\mathbf{W}^*$, where $\mathbf{x}_{1, T_1^*+2}$ will require prediction as detailed in (2) Selection of covariates.
-We used mean squared error for the response in the training data to select an appropriate time length out of 20, 25, 30, and 50 trading days.
-As a result, we consider 25 trading days data for the time series of interest and time series in the donor pool.
-  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates.
-In this example, the weighting method will require future covariates in computation.
-As a result, forecasting of future covariates is needed.
-We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates.
-We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models.
-We then predict the future covariates.
-  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc.
-with shock-effect date in the middle of 25 trading days for 2017, 2018, and 2019.
-The specific shock-effect dates are June 7th, 2017, October 31st, 2018, and June 4th, 2019, respectively.
-We only include the last three MacBook releases in our donor pool.
-This is because these releases are similar to the current release, Apple inc.
-has only updated the hardware of the computer without much redesign of the MacBook \citep{apple2017, apple2018, apple2019}.
-The same is the case with the latest MacBook release \citep{apple2020}.
-%The new MacBook series is built with M1 chip invented by Apple inc.
-instead of chips by Intel inc.
-that were used in past years, and their CPU speed improves significantly \citep{apple2020}.
-\end{enumerate}
-
-The covariates and response of time series in the donor pool are adjusted for inflation.
-The estimated shock effects $\alpha_i$ are $0.686, 1.688, 1.393$ for $i = 2, 3, 4$, respectively.
-We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$.
-As a result, we compute $\mathbf{W}^* = (0.712, 0.000, 0.288)$ and $
-  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 2.422$.
-It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects.
-The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.256$, $\hat{\alpha}_{\rm wadj}=0.889$, and $\hat{\alpha}_{\rm IVW} = 0.951$.
-The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.245$, $0.134$, and $0.133$, respectively.
-Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk.
-As we can see from Figure \ref{Fig3}, the post-shock forecasts perform well.
-The unadjusted forecast misses the post-shock by 0.799 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.457, 0.090, and 0.152 dollars, respectively.
-In this example, covariates weighting to construct $\hat{\alpha}_{\rm wadj}$ is more successful than the other techniques, it is possible that model $\mc{M}_2$ fits this data well.
-Note  that the 1-ahead forecast error for $y_{1, T_1^*+1}$ and the covariates contribute to some of the forecast risk.
-
-\begin{figure*}[t!]
-  \begin{center}
-    \includegraphics[height = 7cm, width = 16.8cm]{FIG3.pdf}
-    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and violet line represent real data and fitted line, respectively.}
-    \label{Fig3}
-  \end{center}  
-  \vspace{-.6cm}
-\end{figure*}
-
-\section{Discussion}
-\label{discussion}
-
-We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock.
-Our methodology is as follows: construct a synthetic panel of time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast.
-There have been several other recent similar methods developed for forecasting COVID-19 cases.
-For example, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries.
-A similar setup may be appropriate for post-shock forecasting but may be too dependent upon model specification for the shock distribution.
-\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach.
-However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool.
-\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.
-They also provided useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.
-Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
-
-We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings.
-The model, under which we verify these claims, is a simple AR(1) model.
-Similar results can be obtained for more general models whose parameters can be estimated unbiasedly.
-%such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models.
-Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent.
-As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock.
-But we note that consistency estimates from LOOCV may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
-
-Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its second moments exist.
-The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.
-Additionally, $\alpha_i$ can be heteroskedastic.
-In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply.
-We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts.
-An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.
-Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.
-
-In our setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$.
-The methodology can be amended to accommodate different timing scenarios.
-Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$.
-We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.
-The Apple example illustrates the case when $d = 2$ with predicted covariates, where the prediction error for covariates and response can contribute to the post-shock forecast risk.
-
-We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead.
-In this setting, there are two cases.
-In the first case, we suppose that there is no additional shock after $T_1^*+1$.
-Then, the forecast boils down to standard $m$-ahead forecast in time series.
-In the second case, we assume that the time series under study will experience an additional additive shock at $T_1^* + m$, say $\alpha_1^{(m)}$.
-Users now construct the donor pool to consist of time series that experience shocks similar to  $\alpha_1^{(m)}$.
-Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(m)}$.
-The adjusted forecast at $t = T_1^* + m$ is
-$
-  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}
-$
-where the future covariates are themselves forecasted. The additional forecasting variability may  render such an adjustment approach useless.
-
-In our framework we have assumed the covariates to be known.
-However, it may be the case that the shock affects the covariates as well as the response.
-If so, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions.
-In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed.
-A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid.
-This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid.
-This may gives users a sense of the variability of post-shock predictions due to forecast error from covariates that are also affected from the shock.
-
-Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series.
-If the data are subject to heteroskedasticity of unknown form, bootstrapping tuples of regressands and regressors proposed by \citet{freedman1981bootstrapping} is robust in this situation with asymptotic validity in autoregressive models established by \citet{gonccalves2004bootstrapping}.
-If serial correlation exists in the data, various block bootstrapping procedures \citep{kunsch1989jackknife, liu1992moving} can be possible reasonable alternatives.
-Note that the pseudo time series generated by our proposed residual bootstrap are not stationary.
-If stationarity is of concern, one can be referred to the stationary bootstrap in \citet{politis1994stationary} for stationary and weakly dependent time series.
-Nevertheless, it was shown that approximation accuracy might be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.
-More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, \citet{berkowitz2000recent}, and Chapter 12 in \citet{kilian2017structural}.
-It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.
-
-Construction of the donor pool is a critical step in our post-shock prediction framework.
-In our model, shocks estimated from candidate time series in the donor pool, together with the shock in the time series of interest, should come from the same generative process.
-However, it may be difficult to confirm such an assumption or modeling structure in practice.
-Also note that we assume that the time series under study is independent of those forming the donor pool, independence being practically satisfied when the time series of interest is separated from the donor pool in time.
-In principle, one should select time series that come from a common population, the same population as the individual under study, to form the donor pool.
-This selection criterion is often adopted in the literature of comparative case studies.
-For example, \citet{card1990impact} used a set of cities in southern U.S.
-to estimate the effect of 1980 Mariel Boatlift on the Miami labor market.
-\citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country.
-To estimate the effect of Proposition 99, a large tobacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period.
-Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.
-
-\section{Supplementary material}
-
-Supplementary material includes the results of  likelihood ratio test for independence among nested shock effects in Section \ref{forecasting}, the algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$, simulation results for $\mc{M}_1$, simulation results for an example of the boundary case $p < n$, and R codes for corresponding simulations and data analysis.
-
-%\section{Acknowledgements}
-
-\section{Appendix}
-\label{proofs}
-
-\subsection{Justification of Expectation of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
-\label{exp}
-
-The building block for the following proof is the fact that least squares is conditionally unbiased conditioned on $\Theta$.
-
-\noindent \textbf{Case I: under $\mc{M}_{1}$:} It follows that  under $\mc{M}_{1}$ (see Section \ref{modelsetup}),
-\begin{align*}
-\E{\hat{\alpha}_{\rm adj}} &=\frac{1}{n}  \sum_{i=2}^{n+1} \E{\E{\hat{\alpha}_i|\Theta}} = \mu_{\alpha} \\
- \E{\hat{\alpha}_{\rm wadj}}&= \sum_{i=2}^{n+1} w_i^* \E{\E{\hat{\alpha}_i|\Theta}}= \sum_{i=2}^{n+1} w_i^*\mu_{\alpha}= \mu_{\alpha}.
-\end{align*}
-where we used the fact that $\sum_{i=2}^{n+1} w^*_i=1$.
-
-\noindent \textbf{Case II: under $\mc{M}_{21}$ and $\mc{M}_{22}$:} Since $\E{\tilde{\varepsilon}_{i, T_i}}=0$, $\E{\hat{\tilde{\alpha}}_{i}}=\E{\tilde{\alpha}_{i}}=\E{\alpha_{i}}$, it follows that
-  \begin{align*}
-   \E{\hat{\alpha}_{\rm wadj}}
-   &= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}
-   = \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
-   = \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}\right]\bigg\} \\
-   &=\mu_{\alpha}+ \mu_{\delta}' \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}\tag{$\mbf{W}\in \mc{W}$}
-   \\
-   &=\mu_{\alpha}+  \mu_{\delta}'\mbf{x}_{1, T_1^*+1}. \tag{from (\ref{SCM})}
-   \end{align*}
-Similarly,
-$
-   \E{\hat{\alpha}_{\rm adj}}
-   =\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \mu_{\delta}'  \mbf{x}_{i, T_i^*+1}.
-$
-
-\subsection{Justification of Variance of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$}
-\label{var}
-
-Notice that under the setting of OLS, the design matrix for $\mc{M}_2$ is the same as the one for $\mc{M}_1$. Therefore, it follows that
-  \begin{align*}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \E{\var{\hat{\alpha}_{\rm wadj}|\Theta}} + \var{\E{\hat{\alpha}_{\rm wadj}|\Theta}} \\
-  &=\mrm{E} \left\{\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\} +\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
-\end{align*}
-Under $\mc{M}_{21}$ where $\delta_i=\delta$ are fixed unknown parameters,  we will have
-  \begin{align}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma_i^2(\mbf{M}'_i\mbf{M}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
-  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
-\end{align}
-Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \varepsilon_{i,t}$, we have
- \begin{align*}
-  \var{\hat{\alpha}_{\rm wadj}} 
-  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
-\end{align*}
-For the adjustment estimator, we simply replace $\mbf{W}^*$ with $1/n\mbf{1}_n$. Thus, under $\mc{M}_{21}$ we have 
- \begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  &=\frac{1}{n^2}\sum_{i=2}^{n+1} \sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
-\end{align*}
-Under $\mc{M}_{22}$, we shall have
- \begin{align*}
-  \var{\hat{\alpha}_{\rm adj}} 
-  =\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}
-   +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
-\end{align*}
-Notice that $\mc{M}_{1}$ differs from $\mc{M}_{21}$ only by its mean parameterization of $\alpha$ (see Section \ref{modelsetup}).
-In other words, the variances of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ under $\mc{M}_1$ are the same for those under $\mc{M}_{21}$.
-
-\subsection{Proofs for lemmas and propositions}
-
-\begin{proof-of-proposition}[\ref{uniqueness}]
-  The proof of \citet{li2019statistical} in Appendix A.2 and A.3 adapts easily to Proposition \ref{uniqueness}.
-\end{proof-of-proposition}
-
-\begin{proof-of-proposition}[\ref{unbiased}] The proof for unbiasedness follows immediately from discussions related to expectation in Section \ref{properties}.
-For the biasedness of  $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$, we write the bias term for $\hat{\alpha}_{\rm adj}$ as below.
-\begin{align*}
-  \mrm{Bias}(\hat{\alpha}_{\rm adj}) = 
-  \begin{cases}
-       \frac{1}{n} \sum_{i=2}^{n+1} \delta'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1})  & \text{ for } \mc{M}_{21}\\
-    \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}'(\mbf{x}_{i, T_i^*+1}-n\mbf{x}_{1, T_1^*+1})  & \text{ for }\mc{M}_{22}
-  \end{cases}.
-\end{align*}
-But it may be unbiased in some special circumstances when the above bias turns out to be 0. \end{proof-of-proposition}
-
-\begin{lem}
-  \label{risklemma} The forecast risk reduction is $R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2$ for all estimators of $\alpha_1$ that are independent of $\Theta_1$ (see Section \ref{modelsetup}).
-\end{lem}
-
-\begin{proof-of-lemma}[\ref{risklemma}]
-  Define 
-  \begin{align*}
-    C(\Theta_1) =\hat{\eta}_1 +\hat{\phi}_1 y_{1, T_1^*}+\hat{\theta}_1'\mbf{x}_{1, T_1^*+1} 
-    &- (\eta_1 +\phi_1y_{1,T_1^*}+\theta_1'\mbf{x}_{1,T_1^*+1}),
-  \end{align*}
-  where $\Theta_1$ is as defined in (\ref{parameter}). Notice that
-  \begin{align*}
-    R_{T_1^*+1,1}
-    &= \mrm{E}\big\{\big(C(\Theta_1)-\alpha_1\big)^2\big\}\\
-     R_{T_1^*+1,2} &=  \mrm{E}\big\{\big(C(\Theta_1)+\hat{\alpha}-\alpha_1\big)^2\big\}.
-  \end{align*}
-  It follows that
-  \begin{align*}
-    R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-2\E{C(\Theta_1)\hat{\alpha}}-\E{\hat{\alpha}-\alpha_1}^2.
-  \end{align*}
-  Assuming $\mbf{S}=(\mbf{1}_n, \mbf{y}_{1,t-1}, \mbf{x}_{1})$ has full rank, under OLS setting, $\hat{\eta}_1$, $\hat{\phi}_1$, and $\hat{\theta}_1$ are unbiased estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively under conditioning of $\Theta_1$.
-Since we assume $\hat{\alpha}$ is independent of $\Theta_1$, through the method of iterated expectation,
-  \begin{align*}
-    \E{C(\Theta_1)\hat{\alpha}}=\mrm{E}\big\{\hat{\alpha}\E{C(\Theta_1)\mid \Theta_1}\}=0.
-  \end{align*}
-  It follows that
-  \begin{align*}
-    R_{T_1^*+1,1}-R_{T_1^*+1,2}=\E{\alpha_1^2}-\E{\hat{\alpha}-\alpha_1}^2,
-  \end{align*}
-  which finishes the proof.
-\end{proof-of-lemma}
-
-\begin{proof-of-proposition}[\ref{proprisk}] The proofs are arranged into two separate parts as below.
-
- \textbf{Proof for statement (i):} Under $\mc{M}_1$, $\hat{\alpha}_{\rm adj}$ is an unbiased estimator of $\E{\alpha_1}$ because
-\begin{align*}
-   \mrm{E}\left( \frac{1}{n}\sum_{i=2}^{n+1} \hat{\alpha}_i\right)
-   &= \frac{1}{n}\sum_{i=2}^{n+1}\E{\hat{\alpha}_i}
-   = \frac{1}{n}\sum_{i=2}^{n+1}\E{\E{\hat{\alpha}_i\mid \Theta}}\\
-   &=  \frac{1}{n}\sum_{i=2}^{n+1}\E{\alpha_i}
-   = \mu_{\alpha}=\E{\alpha_1},
-\end{align*}
-  where we used the fact that OLS estimator is unbiased when the design matrix $\mbf{M}_i$ is of full rank for all $i = 2, \ldots, n+1$.
-Because $\alpha_1\indep \varepsilon_{i,t}$, $\E{\hat{\alpha}_{\rm adj}\alpha_1}=\E{\hat{\alpha}_{\rm adj}}\E{\alpha_1}=(\E{\hat{\alpha}_{\rm adj}})^2$.
-By Lemma \ref{risklemma},
-\begin{align*}
-  R_{T_1^*+1,1}-R_{T_1^*+1,2}
-    &=\E{\alpha_1^2}-\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2 \\
-    &=\E{\alpha_1^2}-\E{\alpha_1^2}- \E{\hat{\alpha}_{\rm adj}^2}+2\E{\hat{\alpha}_{\rm adj}\alpha_1} \\
-    &= \mu_{\alpha}^2 - \var{\hat{\alpha}_{\rm adj}} 
-\end{align*}
-  Therefore, as long as we have $\var{\hat{\alpha}_{\rm adj}}<\mu_{\alpha}^2$, we will achieve the risk reduction.
-
- \textbf{Proof for statement (ii):} By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\mu_{\alpha}$ holds for $\mc{M}_{1}$.
-The remainder of the proof follows a similar argument to the proof of statement (i).
-\end{proof-of-proposition}
-
-\begin{proof-of-proposition}[\ref{propriskwadj2}]
-  By Proposition \ref{unbiased}, the property that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ holds for $\mc{M}_{21}$ and $\mc{M}_{22}$.
-The remainder of the proof follows a similar argument to the proof of Proposition \ref{proprisk}.
-\end{proof-of-proposition}
-
-\subsection{Tables for Section \ref{simulation}}
-\label{tablesappendix}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table1}
-\begin{center}
-\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.91 (0.02) & 0.9 (0.03) & 53.23 (4.1) & 15.88 (2.1) & 16.78 (2.37) & 15.82 (2.07) \\ 
-    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.89 (0.03) & 0.9 (0.03) & 0.89 (0.03) & 53.01 (4.47) & 17.83 (2.38) & 19.56 (2.56) & 17.61 (2.36) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.74 (0.04) & 0.81 (0.04) & 0.75 (0.04) & 53.38 (5.92) & 26.44 (3.8) & 29.06 (4) & 26.11 (3.75) \\ 
-    & 50  & 0.83 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.64 (0.05) & 0.59 (0.05) & 61.68 (7.73) & 46 (6.31) & 47.3 (7.14) & 45.25 (6.32) \\ 
-    & 100  & 0.7 (0.09) & 0.87 (0.06) & 0.7 (0.09) & 0.53 (0.05) & 0.54 (0.05) & 0.53 (0.06) & 85.68 (12.95) & 87.25 (11.86) & 87.07 (13.63) & 85.65 (12.02)\\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
-    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
-   \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 51.11 (3.05) & 14.94 (2.36) & 14.09 (2.37) & 15.09 (2.35) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.91 (0.02) & 0.91 (0.02) & 52.34 (3.19) & 15.64 (2.73) & 15.29 (2.74) & 15.89 (2.68) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.93 (0.05) & 0.73 (0.04) & 0.76 (0.04) & 0.73 (0.04) & 56.03 (5.2) & 25.49 (3.85) & 27.38 (3.87) & 25.27 (3.84) \\ 
-    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.56 (0.04) & 0.6 (0.04) & 0.57 (0.04) & 71.37 (7.76) & 47.25 (6.42) & 52.06 (6.57) & 46.41 (6.43) \\ 
-    & 100  & 0.63 (0.09) & 0.67 (0.09) & 0.63 (0.09) & 0.52 (0.04) & 0.42 (0.04) & 0.53 (0.04) & 111.91 (13.83) & 92.95 (12.34) & 103.13 (12.74) & 91.07 (12.37) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.94 (0.02) & 0.93 (0.02) & 47.79 (2.93) & 14.83 (1.72) & 14.83 (2.04) & 14.76 (1.72) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.91 (0.02) & 0.89 (0.03) & 47.93 (3.25) & 16.55 (1.89) & 17.55 (2.12) & 16.53 (1.88) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.03) & 0.82 (0.03) & 0.83 (0.03) & 49.78 (5.01) & 26.42 (3.38) & 29.11 (3.4) & 26.45 (3.35) \\ 
-    & 50  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.64 (0.05) & 0.63 (0.05) & 0.64 (0.05) & 62.64 (7.4) & 48.84 (6.4) & 52.67 (6.28) & 48.8 (6.35) \\ 
-    & 100  & 0.83 (0.07) & 0.8 (0.07) & 0.83 (0.07) & 0.57 (0.05) & 0.59 (0.05) & 0.59 (0.05) & 103.37 (12.23) & 97.81 (12.52) & 102.4 (12.49) & 97.63 (12.45) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_u$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table2}
-\begin{center}
-\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.97 (0.01) & 0.95 (0.02) & 48.84 (3.4) & 15.72 (1.93) & 15.32 (1.94) & 15.72 (1.93) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.03) & 0.94 (0.02) & 0.92 (0.03) & 49.54 (3.73) & 17.07 (2.01) & 16.08 (2.16) & 17.12 (1.99) \\ 
-    & 25  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.77 (0.02) & 0.81 (0.03) & 0.77 (0.03) & 51.78 (5.22) & 24.78 (2.57) & 26.12 (2.49) & 24.62 (2.54) \\ 
-    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.05) & 0.61 (0.04) & 0.59 (0.05) & 58.62 (7.74) & 40.09 (4.7) & 47.09 (4.09) & 39.85 (4.58) \\ 
-    & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.73 (0.08) & 0.5 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 82.66 (12.19) & 72.83 (9.75) & 89.03 (9.15) & 72.31 (9.5) \\[.3cm] 
-   \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.03) & 0.92 (0.02) & 0.91 (0.03) & 48.18 (4.59) & 20.47 (2.71) & 19.13 (2.97) & 20.53 (2.73) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 48.93 (4.71) & 21.27 (2.6) & 19.24 (3.03) & 21.31 (2.61) \\ 
-    & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.74 (0.03) & 0.77 (0.03) & 0.74 (0.03) & 51.18 (5.7) & 26.68 (2.78) & 27.17 (3) & 26.53 (2.77) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.57 (0.04) & 0.61 (0.04) & 0.57 (0.04) & 57.82 (7.81) & 40.51 (4.37) & 46.85 (4.02) & 40.19 (4.27) \\ 
-    & 100  & 0.73 (0.08) & 0.93 (0.05) & 0.7 (0.09) & 0.51 (0.04) & 0.51 (0.04) & 0.5 (0.04) & 79.3 (12.44) & 72.33 (9.12) & 88.81 (8.46) & 71.83 (8.85) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.04) & 0.76 (0.03) & 0.7 (0.04) & 50.09 (8.27) & 38.1 (5.75) & 37.98 (5.5) & 38.44 (5.76) \\ 
-    & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.69 (0.04) & 0.74 (0.03) & 0.69 (0.04) & 50.82 (8.15) & 37.63 (5.61) & 36.33 (5.64) & 37.99 (5.61) \\ 
-    & 25  & 0.9 (0.06) & 0.9 (0.06) & 0.9 (0.06) & 0.62 (0.04) & 0.64 (0.04) & 0.61 (0.04) & 53.01 (8.22) & 38.78 (5.29) & 36.82 (5.76) & 38.88 (5.31) \\ 
-    & 50  & 0.8 (0.07) & 0.8 (0.07) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.53 (0.04) & 58.9 (9.12) & 46.77 (5.54) & 50.61 (5.71) & 46.6 (5.51) \\ 
-    & 100  & 0.7 (0.09) & 0.9 (0.06) & 0.67 (0.09) & 0.51 (0.03) & 0.56 (0.04) & 0.5 (0.03) & 79.64 (12.21) & 72.76 (8.79) & 89.48 (7.98) & 72.17 (8.59) \\[.3cm] 
-   \multirow{5}{*}{50} & 5  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.04) & 0.59 (0.04) & 71.22 (13) & 70.31 (10.4) & 72.3 (9.26) & 70.79 (10.45) \\ 
-    & 10  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.6 (0.05) & 0.63 (0.05) & 0.6 (0.05) & 70.85 (12.91) & 69.43 (10.22) & 70.65 (9.29) & 69.94 (10.26) \\ 
-    & 25  & 0.7 (0.09) & 0.73 (0.08) & 0.7 (0.09) & 0.54 (0.05) & 0.56 (0.05) & 0.55 (0.05) & 70.32 (12.81) & 67.61 (9.86) & 67 (9.58) & 68.06 (9.89) \\ 
-    & 50  & 0.67 (0.09) & 0.7 (0.09) & 0.67 (0.09) & 0.51 (0.05) & 0.51 (0.04) & 0.51 (0.05) & 74.01 (12.66) & 68.69 (9.63) & 67.9 (10.21) & 68.91 (9.64) \\ 
-    & 100  & 0.5 (0.09) & 0.6 (0.09) & 0.47 (0.09) & 0.47 (0.05) & 0.49 (0.04) & 0.45 (0.05) & 92.71 (13.06) & 83.66 (10.79) & 94.53 (11.2) & 83.56 (10.63)\\[.3cm] 
-   \multirow{5}{*}{100} & 5  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.06) & 0.57 (0.05) & 0.49 (0.06) & 130.47 (22.59) & 135.16 (19.73) & 141.42 (16.98) & 136.3 (19.72) \\ 
-    & 10  & 0.47 (0.09) & 0.47 (0.09) & 0.47 (0.09) & 0.51 (0.05) & 0.53 (0.05) & 0.51 (0.06) & 129.49 (22.49) & 134.09 (19.52) & 139.69 (16.96) & 135.26 (19.51) \\ 
-    & 25  & 0.47 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.53 (0.06) & 0.57 (0.05) & 0.51 (0.06) & 127.17 (22.22) & 131.43 (18.97) & 134.47 (17.22) & 132.42 (18.99) \\ 
-    & 50  & 0.5 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.48 (0.06) & 0.56 (0.04) & 0.48 (0.05) & 125.72 (21.8) & 129.27 (18.16) & 129.59 (17.59) & 130.27 (18.15) \\ 
-    & 100  & 0.47 (0.09) & 0.47 (0.09) & 0.43 (0.09) & 0.43 (0.06) & 0.57 (0.04) & 0.47 (0.06) & 128.38 (21.86) & 130.05 (18.05) & 131.83 (19.08) & 130.33 (18.06) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $n$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table3}
-\begin{center}
-\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $n$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}} $  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.92 (0.02) & 0.89 (0.03) & 48.52 (3.93) & 15.74 (2.34) & 15.76 (2.34) & 15.16 (2.24) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.91 (0.02) & 0.89 (0.02) & 47.7 (4.35) & 18.26 (2.37) & 18.97 (2.42) & 17.68 (2.28) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.93 (0.05) & 0.79 (0.03) & 0.81 (0.03) & 0.77 (0.03) & 46.95 (6.11) & 27.35 (3.81) & 30.88 (3.84) & 26.58 (3.83) \\ 
-  & 50  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.62 (0.03) & 0.65 (0.03) & 0.63 (0.03) & 56.85 (8.64) & 46.96 (7.02) & 52.92 (7.45) & 45.95 (7.17) \\ 
-  & 100  & 0.73 (0.08) & 1 (0) & 0.8 (0.07) & 0.53 (0.04) & 0.53 (0.04) & 0.55 (0.04) & 99.22 (12.84) & 93.4 (12.97) & 103.82 (14.1) & 91.95 (13.34) \\[.3cm]  
- \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
-  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29) \\[.3cm] 
- \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.92 (0.03) & 0.95 (0.02) & 52.1 (2.96) & 14.04 (1.78) & 13.36 (2.07) & 14.11 (1.76) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.92 (0.02) & 0.9 (0.03) & 0.93 (0.02) & 52.25 (3.3) & 15.12 (1.93) & 14.24 (2.29) & 15.18 (1.9) \\ 
-    & 25  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.8 (0.03) & 0.8 (0.03) & 0.8 (0.03) & 52.71 (5.28) & 22.98 (2.9) & 22.6 (3.42) & 22.95 (2.88) \\ 
-    & 50  & 0.7 (0.09) & 0.9 (0.06) & 0.7 (0.09) & 0.65 (0.03) & 0.65 (0.03) & 0.65 (0.04) & 58.65 (8.48) & 39.51 (5.65) & 40.8 (6.3) & 39.35 (5.63) \\ 
-    & 100  & 0.6 (0.09) & 0.87 (0.06) & 0.6 (0.09) & 0.47 (0.05) & 0.45 (0.04) & 0.45 (0.05) & 88.76 (13.66) & 75.93 (11.52) & 81.89 (12.19) & 75.94 (11.41) \\[.3cm] 
-   \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.55 (2.9) & 12.13 (1.77) & 14.22 (1.96) & 12.09 (1.77) \\ 
-    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.95 (0.02) & 0.93 (0.02) & 49.13 (3.31) & 14.78 (1.85) & 18.21 (2) & 14.75 (1.85) \\ 
-    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.83 (0.02) & 0.85 (0.02) & 0.83 (0.03) & 47.38 (5.13) & 26.85 (3.33) & 32.95 (3.59) & 26.81 (3.32) \\ 
-    & 50  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.61 (0.04) & 0.71 (0.04) & 0.62 (0.04) & 56.73 (7.93) & 50.96 (6.63) & 60.62 (7.21) & 50.88 (6.59) \\ 
-    & 100  & 0.8 (0.07) & 0.93 (0.05) & 0.8 (0.07) & 0.49 (0.05) & 0.51 (0.04) & 0.49 (0.05) & 93.79 (14.67) & 102.05 (13.37) & 116.45 (15.19) & 101.55 (13.38) \\
-\end{tabular}}
-   \end{center}
-      \vspace{-.5cm}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[b]
-\caption{30 Monte Carlo simulations of $\mc{M}_2$ for $\mc{B}_f$ with varying $\sigma$ and $\sigma_{\alpha}$} \vspace{.3cm} \label{table4}
-\begin{center}
-\resizebox{1.2\textwidth}{!}{\begin{tabular}{cc|ccc|ccc|cccc|}
-   &   & \multicolumn{3}{|c|}{Guess} & \multicolumn{3}{|c|}{LOOCV with $k$ random draws} &  \multicolumn{4}{|c|}{Distance to $y_{1, T_1^*+1}$} \\ 
- $\sigma$   & $\sigma_{\alpha}$ &  $\delta_{\hat{\alpha}_{\rm adj}}$  & $\delta_{\hat{\alpha}_{\rm wadj}}$ & $\delta_{\hat{\alpha}_{\rm IVW}}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.15cm]
-  \hline
- \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.94 (0.02) & 0.95 (0.02) & 0.94 (0.02) & 50.04 (3.65) & 21.75 (4.34) & 22.68 (4.41) & 21.83 (4.34) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.92 (0.02) & 0.93 (0.02) & 49.93 (4.11) & 24.3 (4.44) & 25.72 (4.58) & 24.4 (4.45) \\ 
-  & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.73 (0.04) & 0.8 (0.03) & 0.73 (0.04) & 51.29 (5.39) & 32.8 (5.25) & 35.39 (5.78) & 33.11 (5.21) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.49 (0.04) & 0.44 (0.05) & 0.47 (0.04) & 82.55 (11.61) & 84.26 (12.7) & 98.66 (13.96) & 84.62 (12.59) \\[.3cm] 
- \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.88 (0.02) & 0.86 (0.03) & 50.59 (5.24) & 29.19 (5.2) & 31.4 (5.28) & 29.29 (5.22) \\ 
-  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.82 (0.03) & 0.84 (0.03) & 0.82 (0.03) & 51.17 (5.49) & 31.55 (5.33) & 33.91 (5.56) & 31.7 (5.35) \\ 
-  & 25  & 0.93 (0.05) & 1 (0) & 0.93 (0.05) & 0.72 (0.04) & 0.75 (0.04) & 0.71 (0.04) & 53.53 (6.58) & 40.05 (6.03) & 43.5 (6.66) & 40.43 (6) \\ 
-  & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.58 (0.05) & 0.55 (0.05) & 62.45 (8.25) & 55.56 (8.11) & 62.15 (9.19) & 56.12 (8.04) \\ 
-  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.73 (0.08) & 0.49 (0.05) & 0.44 (0.05) & 0.46 (0.05) & 85.72 (12.73) & 89.5 (13.37) & 103.25 (15.07) & 89.92 (13.29)\\[.3cm] 
- \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.7 (0.03) & 0.73 (0.03) & 0.71 (0.04) & 57.87 (8.76) & 50.31 (7.58) & 57.25 (7.75) & 50.53 (7.64) \\ 
-  & 10  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.68 (0.04) & 0.69 (0.04) & 0.69 (0.04) & 58.41 (9.11) & 51.62 (7.91) & 58.61 (8.28) & 51.85 (7.98) \\ 
-  & 25  & 0.93 (0.05) & 0.97 (0.03) & 0.9 (0.06) & 0.63 (0.04) & 0.68 (0.04) & 0.63 (0.04) & 62.02 (10.02) & 59.08 (8.53) & 65.55 (9.64) & 59.68 (8.53) \\ 
-  & 50  & 0.87 (0.06) & 0.9 (0.06) & 0.87 (0.06) & 0.54 (0.04) & 0.59 (0.04) & 0.52 (0.04) & 71.01 (11.73) & 73.52 (10.18) & 81.81 (11.98) & 74.51 (10.09) \\ 
-  & 100  & 0.73 (0.08) & 0.87 (0.06) & 0.73 (0.08) & 0.47 (0.05) & 0.45 (0.04) & 0.5 (0.05) & 95.93 (15.59) & 104.49 (15.12) & 119.38 (17.62) & 105.72 (14.97) \\[.3cm] 
- \multirow{5}{*}{50} & 5  & 0.8 (0.07) & 0.77 (0.08) & 0.8 (0.07) & 0.52 (0.04) & 0.49 (0.05) & 0.52 (0.04) & 85.95 (14.57) & 90.02 (13.45) & 103.03 (13.91) & 90.08 (13.64) \\ 
-  & 10  & 0.8 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.55 (0.05) & 0.5 (0.04) & 0.53 (0.05) & 86.44 (14.95) & 90.89 (13.79) & 104.62 (14.28) & 91.03 (13.98) \\ 
-  & 25  & 0.77 (0.08) & 0.77 (0.08) & 0.77 (0.08) & 0.53 (0.04) & 0.46 (0.04) & 0.53 (0.04) & 90.26 (15.82) & 95.36 (14.69) & 109.53 (15.69) & 95.79 (14.83) \\ 
-  & 50  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.48 (0.05) & 0.45 (0.05) & 0.45 (0.05) & 99.52 (17.26) & 106.52 (16.17) & 120.99 (18.13) & 107.55 (16.19) \\ 
-  & 100  & 0.57 (0.09) & 0.77 (0.08) & 0.63 (0.09) & 0.41 (0.04) & 0.45 (0.03) & 0.41 (0.04) & 123.11 (20.61) & 135.24 (19.74) & 151.62 (23.42) & 137.21 (19.55) \\[.3cm] 
- \multirow{5}{*}{100} & 5  & 0.63 (0.09) & 0.57 (0.09) & 0.63 (0.09) & 0.48 (0.05) & 0.48 (0.03) & 0.47 (0.05) & 156.82 (26.36) & 170.06 (25.92) & 196.4 (26.55) & 170.13 (26.27) \\ 
-  & 10  & 0.63 (0.09) & 0.57 (0.09) & 0.67 (0.09) & 0.46 (0.05) & 0.47 (0.03) & 0.47 (0.05) & 157.3 (26.76) & 170.93 (26.21) & 197.96 (26.87) & 171.07 (26.56) \\ 
-  & 25  & 0.67 (0.09) & 0.63 (0.09) & 0.67 (0.09) & 0.44 (0.04) & 0.5 (0.03) & 0.45 (0.04) & 160.32 (27.73) & 173.66 (27.22) & 202.61 (28.01) & 174.28 (27.48) \\ 
-  & 50  & 0.67 (0.09) & 0.67 (0.09) & 0.67 (0.09) & 0.39 (0.04) & 0.43 (0.03) & 0.38 (0.04) & 166.98 (29.35) & 182.83 (28.37) & 210.38 (30.48) & 183.67 (28.61) \\ 
-  & 100  & 0.6 (0.09) & 0.67 (0.09) & 0.53 (0.09) & 0.4 (0.04) & 0.45 (0.04) & 0.41 (0.05) & 188.29 (32.07) & 203.7 (31.63) & 233.44 (35.31) & 205.4 (31.72) \\
-\end{tabular}}
-   \end{center}
-\end{table}
-\end{landscape}
-
-\section*{References}
-\bibliography{synthetic-prediction-notes}
+\bibliographystyle{plainnat}
+\bibliography{../synthetic-prediction-notes}
 

### 2021-07-01 prevalence_testing/numerical_studies/simu.R
added UIUC cluster scripts; waiting for results!

@@ -244,7 +244,7 @@ sim.normal.gammaX <- function(mu.gamma.delta = 1, mu.alpha, sigma,
 }
 
 system.time(result <- sim.normal.gammaX(mu.alpha = 0, mu.gamma.delta = 0, sigma = 1, sigma.alpha = 1, p = 4,
-                            B = 20, n = 5, H = 12, scale = 5, ell = 3))
+                            B = 200, n = 5, H = 12, scale = 5, ell = 3))
 
 
 # MC
@@ -264,6 +264,8 @@ nsim <- 50
 ns <- c(5, 10, 15, 25)
 sigma.alphas <- c(1, 5, 10, 25, 100)
 sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
+
+
 
 # simulation time
 system.time(
@@ -304,7 +306,7 @@ for (i in 1:nrow(sim_params)) {
   result.i <- c()
   for (j in 1:16) {
     result.i <- cbind(result.i, paste0(round(means[j], digits = 3), 
-                                       ' (', round(sds[j] / sqrt(50), 
+                                       ' (', round(sds[j] / sqrt(nsim), 
                                                    digits = 3), ')'))
   }
   result <- rbind(result, result.i)

### 2021-07-01 prevalence_testing/numerical_studies/simu_cluster_ns10.R

@@ -1,0 +1,48 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+#ncores <- detectCores() - 1
+registerDoParallel(cores = ncores)
+set.seed(14)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 100
+
+# parameter setup
+ns <- 10
+sigma.alphas <- c(1, 5, 10, 25, 100)
+sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
+
+
+
+# simulation time
+system.time(
+	output_ns5 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		sigma.alpha <- sim_params[j, 1]
+		n <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX(mu.gamma.delta = 2, 
+																 mu.alpha = 10, sigma = 1, 
+																 sigma.alpha = sigma.alpha, 
+																 sigma.delta.gamma = 1, 
+																 p = 13, B = 200, scale = 10, 
+																 n = n, H = 12, ell = 3)
+			return(study)
+		}
+		# return results
+		out
+	})
+)
+
+save(output_ns10, file = "output_ns10.RData")
+
+

### 2021-07-01 prevalence_testing/numerical_studies/simu_cluster_ns15.R

@@ -1,0 +1,48 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+#ncores <- detectCores() - 1
+registerDoParallel(cores = ncores)
+set.seed(15)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 100
+
+# parameter setup
+ns <- 15
+sigma.alphas <- c(1, 5, 10, 25, 100)
+sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
+
+
+
+# simulation time
+system.time(
+	output_ns5 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		sigma.alpha <- sim_params[j, 1]
+		n <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX(mu.gamma.delta = 2, 
+																 mu.alpha = 10, sigma = 1, 
+																 sigma.alpha = sigma.alpha, 
+																 sigma.delta.gamma = 1, 
+																 p = 13, B = 200, scale = 10, 
+																 n = n, H = 12, ell = 3)
+			return(study)
+		}
+		# return results
+		out
+	})
+)
+
+save(output_ns15, file = "output_ns15.RData")
+
+

### 2021-07-01 prevalence_testing/numerical_studies/simu_cluster_ns25.R

@@ -1,0 +1,48 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+#ncores <- detectCores() - 1
+registerDoParallel(cores = ncores)
+set.seed(16)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 100
+
+# parameter setup
+ns <- 25
+sigma.alphas <- c(1, 5, 10, 25, 100)
+sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
+
+
+
+# simulation time
+system.time(
+	output_ns5 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		sigma.alpha <- sim_params[j, 1]
+		n <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX(mu.gamma.delta = 2, 
+																 mu.alpha = 10, sigma = 1, 
+																 sigma.alpha = sigma.alpha, 
+																 sigma.delta.gamma = 1, 
+																 p = 13, B = 200, scale = 10, 
+																 n = n, H = 12, ell = 3)
+			return(study)
+		}
+		# return results
+		out
+	})
+)
+
+save(output_ns25, file = "output_ns25.RData")
+
+

### 2021-07-01 prevalence_testing/numerical_studies/simu_cluster_ns5.R

@@ -1,0 +1,48 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+#ncores <- detectCores() - 1
+registerDoParallel(cores = ncores)
+set.seed(13)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 100
+
+# parameter setup
+ns <- 5
+sigma.alphas <- c(1, 5, 10, 25, 100)
+sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
+
+
+
+# simulation time
+system.time(
+	output_ns5 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		sigma.alpha <- sim_params[j, 1]
+		n <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX(mu.gamma.delta = 2, 
+																 mu.alpha = 10, sigma = 1, 
+																 sigma.alpha = sigma.alpha, 
+																 sigma.delta.gamma = 1, 
+																 p = 13, B = 200, scale = 10, 
+																 n = n, H = 12, ell = 3)
+			return(study)
+		}
+		# return results
+		out
+	})
+)
+
+save(output_ns5, file = "output_ns5.RData")
+
+

### 2021-07-01 prevalence_testing/numerical_studies/simu_source.R

@@ -1,0 +1,246 @@
+# load packages
+require('forecast')
+ncores <- 20
+
+
+# this function returns the W^* estimated by synthetic control method (SCM)
+scm <- function(X, Tstar) {
+	# X is a list of covariates for disparate time series
+	# X[[1]] should be the covariate of the time series to predict
+	# X[[p]] for p = 2,...,n+1 are covariates for time series pool
+	
+	# T^* is a vector of shock-effects time points
+	# shock effect point must be > 2
+	
+	# package for constrained optimization
+	require('Rsolnp')
+	
+	# number of time series for pool
+	n <- length(X) - 1
+	
+	# covariate for time series for prediction
+	X1 <- X[[1]][Tstar[1] + 1, , drop = FALSE]
+	
+	# covariates for time series pool
+	X0 <- c()
+	for (i in 1:n) {
+		X0[[i]] <- X[[i + 1]][Tstar[i + 1] + 1, , drop = FALSE]
+	}
+	
+	# objective function
+	weightedX0 <- function(W) {
+		# W is a vector of weight of the same length of X0
+		n <- length(W)
+		p <- ncol(X1)
+		XW <- matrix(0, nrow = 1, ncol = p)
+		for (i in 1:n) {
+			XW <- XW + W[i] * X0[[i]]
+		}
+		norm <- as.numeric(crossprod(matrix(X1 - XW)))
+		return(norm)
+	}
+	
+	# constraint for W
+	Wcons <- function(W) sum(W) - 1
+	
+	
+	# optimization
+	solnp(par = rep(1/n, n), fun = weightedX0, eqfun = Wcons, eqB = 0, 
+				LB = rep(0, n), UB = rep(1, n), control = list(trace = 0))
+}
+
+# squared error loss
+sel <- function(yhat, y) {
+	(y - yhat) ^ 2
+}
+
+# taSPA test for comparison of two models
+taSPA.mhfc <- function(ell, d, B, bw = 4) {
+	# ell is the block length
+	# d is the matrix of loss differential
+	# B is the bootstrap size
[…]

### 2021-07-09 prevalence_testing/numerical_studies/simu_cluster_aggregation.R
adding updates to my script; adding supplement material to Jileis simulations ran on the campus cluster

@@ -1,0 +1,42 @@
+
+
+rm(list = ls())
+
+## load in output
+load("output_ns5.RData")
+load("output_ns10.RData")
+load("output_ns15.RData")
+load("output_ns25.RData")
+
+output <- c(output_ns5, output_ns10, output_ns15, 
+						output_ns25)
+
+## create simulation parameters
+ns <- c(5, 10, 15, 25)
+sigma.alphas <- c(1, 5, 10, 25, 100)
+sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
+nsim <- 100
+
+# store results
+# load packages
+require('readxl')
+require('writexl')
+write_xlsx(lapply(output, as.data.frame), 'trial.xlsx')
+
+result <- c()
+for (i in 1:nrow(sim_params)) {
+	table <- output[[i]]
+	# means and sds
+	means <- apply(table, 2, function(x) mean(x))
+	sds <- apply(table, 2, function(x) sd(x))
+	result.i <- c()
+	for (j in 1:2) {
+		result.i <- cbind(result.i, paste0(round(means[j], digits = 3), 
+																			 ' (', round(sds[j] / sqrt(nsim), 
+																			 						digits = 3), ')'))
+	}
+	result <- rbind(result, result.i)
+}
+result <- cbind(sim_params[, c(2,1)], result)
+require('xtable')
+xtable(result)

### 2021-07-09 prevalence_testing/numerical_studies/simu_cluster_ns10.R

@@ -21,7 +21,7 @@ sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
 
 # simulation time
 system.time(
-	output_ns5 <- lapply(1:nrow(sim_params), FUN = function(j) {
+	output_ns10 <- lapply(1:nrow(sim_params), FUN = function(j) {
 		# parameters
 		sigma.alpha <- sim_params[j, 1]
 		n <- sim_params[j, 2]

### 2021-07-09 prevalence_testing/numerical_studies/simu_cluster_ns15.R

@@ -21,7 +21,7 @@ sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
 
 # simulation time
 system.time(
-	output_ns5 <- lapply(1:nrow(sim_params), FUN = function(j) {
+	output_ns15 <- lapply(1:nrow(sim_params), FUN = function(j) {
 		# parameters
 		sigma.alpha <- sim_params[j, 1]
 		n <- sim_params[j, 2]

### 2021-07-09 prevalence_testing/numerical_studies/simu_cluster_ns25.R

@@ -21,7 +21,7 @@ sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
 
 # simulation time
 system.time(
-	output_ns5 <- lapply(1:nrow(sim_params), FUN = function(j) {
+	output_ns25 <- lapply(1:nrow(sim_params), FUN = function(j) {
 		# parameters
 		sigma.alpha <- sim_params[j, 1]
 		n <- sim_params[j, 2]

### 2021-07-09 prevalence_testing/numerical_studies/sustained_shock.R

@@ -1,0 +1,133 @@
+
+
+
+library(data.table) 
+
+
+# squared error loss
+sel <- function(yhat, y) {
+	(y - yhat) ^ 2
+}
+
+
+data_setup <- function(T, n, H, lag, shock, ar){
+
+	y <- arima.sim(n = n + H + T, 
+								 model = list(order = c(lag, 0, 0), 
+								 						 ar = rep(ar, lag)))
+	
+	shift <- rep(0, length(y))
+	shift[1:(T+n+H) > (T+n)/2] <- shock
+	y <- y + shift
+	
+	df <- data.frame(t=y)
+	setDT(df)[, paste("t", 1:lag, sep = "") := shift(t, 1:lag)]
+	df$shock <- as.factor(as.numeric(1:nrow(df) > (T+n)/2))
+  
+	output = list(df = df, shift = shift)
+	output
+
+}
+
+
+
+diff <- function(dat, T, H, lag){
+	df <- dat$df
+	shift <- dat$shift
+	
+	m <- lm(t ~ ., data = df)
+	shock_hat <- coef(m)[lag + 2]
+	shift_hat <- rep(0, nrow(df))
+	shift_hat[1:(T+n+H) > (T+n)/2] <- shock_hat
+	
+	m1.L <- matrix(NA, nrow = T, ncol = H)
+	m2.L <- matrix(NA, nrow = T, ncol = H)
+	
+	# compute losses
+	y <- df$t
+	for (h in 1:H) {
+		for (t in 1:T) {
+			# AR(lag) with shift removed
+			m1.t.h <- arima(y[(t + H - h + 1):(t + n + H - h)] - 
+												shift[(t + H - h + 1):(t + n + H - h)], 
+											order = c(lag, 0, 0))
+			# AR(lag)
+			m2.t.h <- arima(y[(t + H - h + 1):(t + n + H - h)], 
+											order = c(lag, 0, 0))
+			m1.L[t, h] <- sel(y = y[t + n + H], yhat = predict(m1.t.h, h)$pred[h])
+			m2.L[t, h] <- sel(y = y[t + n + H], yhat = predict(m2.t.h, h)$pred[h])
+		}
+	}
+	d <- m1.L - m2.L
+	d
+	
+}
+
+
+
+# taSPA test for comparison of two models
+taSPA.mhfc <- function(ell, d, B, bw = 4) {
+	# ell is the block length
+	# d is the matrix of loss differential
[…]

### 2021-07-27 transience-prediction.tex
addition of conditions

@@
 
+\begin{align*}
+  y_{i,t} &= \eta_i + \phi_i y_{i,t-1} + \mbf{x}_{i,t} \bs{\beta}_i + \xi_i\cdot  I(t > T_i^*) + \varepsilon_{i,t},\\
+  \xi_i &= \alpha_i \cdot e^{-(t-T_i^*-1)} \\
+  \alpha_i &= \mu_{\alpha} + \mbf{x}_{i,T_i^*+1}\bs{\gamma}_i + \tilde{\varepsilon}_{i},
+\end{align*}
+
+\begin{table}[H]
+\caption{50 MC simulations  with varying $n$ and $\sigma_{\alpha}$ ($B = 200$, $H = 12$, $\ell = 3$, $\mu_{\alpha}=10$) \\ MC mean and standard errors for absolute differences between $p_1$ and estimated $p_1$.} \vspace{-.5cm}
+\begin{center}
+  \begin{tabular}{cccc}
+  $n$ & $\sigma_{\alpha}$ & $|\hat{p}-p_1|$ & $|\hat{I}- I_1|$ \\ 
+  \hline
+\multirow{5}{*}{5} & 1  & 0.083 (0.028) & 0.084 (0.028) \\ 
+    & 5  & 0.083 (0.028) & 0.084 (0.028) \\ 
+    & 10  & 0.083 (0.028) & 0.084 (0.028) \\ 
+    & 25  & 0.074 (0.027) & 0.074 (0.027) \\ 
+    & 100  & 0.053 (0.019) & 0.053 (0.019) \\[.15cm] 
+    \hline 
+   \multirow{5}{*}{10} & 1  & 0.063 (0.03) & 0.063 (0.03) \\ 
+   & 5  & 0.063 (0.03) & 0.063 (0.03) \\ 
+   & 10  & 0.063 (0.03) & 0.063 (0.03) \\ 
+   & 25  & 0.063 (0.03) & 0.063 (0.03) \\ 
+    & 100  & 0.052 (0.025) & 0.052 (0.025) \\[.15cm] 
+     \hline 
+  \multirow{5}{*}{15} & 1  & 0.065 (0.026) & 0.066 (0.026) \\ 
+   & 5  & 0.065 (0.026) & 0.066 (0.026) \\ 
+    & 10  & 0.065 (0.026) & 0.066 (0.026) \\ 
+   & 25  & 0.065 (0.026) & 0.066 (0.026) \\ 
+    & 100  & 0.087 (0.029) & 0.087 (0.029) \\[.15cm]  
+     \hline 
+   \multirow{5}{*}{25}& 1  & 0.044 (0.021) & 0.044 (0.021) \\ 
+    & 5  & 0.043 (0.021) & 0.044 (0.021) \\ 
+    & 10  & 0.05 (0.022) & 0.05 (0.022) \\ 
+    & 25  & 0.05 (0.022) & 0.05 (0.022) \\ 
+    & 100  & 0.048 (0.022) & 0.049 (0.022) \\   
+  \end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}
+\caption{100 MC simulations  with varying $\sigma$ and $\sigma_{\alpha}$ ($B = 200$, $H = 12$, $\ell = 3$, $n=10$) \\ MC mean and standard errors for absolute differences between $p_1$ and estimated $p_1$.}
+  \begin{center}
+    \begin{tabular}{ccccc}
+     $\sigma$ & $\sigma_{\alpha}$ &  $|\hat{p}-p_1|$ & $|\hat{I}- I_1|$ \\[.15cm]  
+     \hline 
+   \multirow{5}{*}{5}  & 5  & 0.039 (0.016) & 0.04 (0.016) \\ 
+     & 10  & 0.039 (0.016) & 0.04 (0.016) \\ 
+     & 25  & 0.054 (0.019) & 0.054 (0.019) \\ 
+     & 50  & 0.059 (0.019) & 0.059 (0.019) \\ 
+     & 100  & 0.098 (0.026) & 0.098 (0.026) \\[.15cm]  
+      \hline 
+    \multirow{5}{*}{10}  & 5  & 0.044 (0.016) & 0.044 (0.016) \\ 
+     & 10  & 0.044 (0.016) & 0.044 (0.016) \\ 
+     & 25  & 0.042 (0.016) & 0.042 (0.016) \\ 
+     & 50  & 0.065 (0.019) & 0.065 (0.019) \\ 
+     & 100  & 0.101 (0.026) & 0.101 (0.026) \\[.15cm]  
+      \hline 
+    \multirow{5}{*}{25}  & 5  & 0.045 (0.018) & 0.046 (0.018) \\ 
+     & 10  & 0.058 (0.02) & 0.059 (0.02) \\ 
+     & 25  & 0.06 (0.02) & 0.061 (0.02) \\ 
+     & 50  & 0.105 (0.026) & 0.106 (0.026) \\ 
+     & 100  & 0.122 (0.027) & 0.122 (0.027) \\[.15cm]  
+      \hline 
+    \multirow{5}{*}{50}  & 5  & 0.075 (0.023) & 0.076 (0.023) \\ 
+     & 10  & 0.085 (0.025) & 0.086 (0.025) \\ 
+     & 25  & 0.08 (0.023) & 0.08 (0.023) \\ 
+     & 50  & 0.14 (0.029) & 0.14 (0.029) \\ 
+     & 100  & 0.148 (0.027) & 0.148 (0.027) \\[.15cm]  
+      \hline 
+    \multirow{5}{*}{100}  & 5  & 0.148 (0.029) & 0.149 (0.029) \\ 
+    & 10  & 0.151 (0.029) & 0.151 (0.029) \\ 
+     & 25  & 0.162 (0.029) & 0.162 (0.029) \\ 
+     & 50  & 0.229 (0.034) & 0.229 (0.034) \\ 
+     & 100  & 0.272 (0.034) & 0.272 (0.034) \\
+    \end{tabular}
+  \end{center}  
+\end{table}
+
+\begin{table}[H]
+\caption{100 MC simulations for decaying shock effects with varying $\mu_{\alpha}$ and $H$  ($B = 200$, $\mu_{\gamma}=2$, $\ell = 3$, $n=10$)} 
+\begin{center}
+\begin{tabular}{rrrccc}
+  \hline
+ $\mu_{\alpha}$ & $H$ & $|\hat{p}-p_1|$ & $|\hat{I}- I_1|$ & Mean of $p$-values in the donor pool \\ 
+  \hline
+ 0 & 2 & 0.11 (0.023) & 0.114 (0.023) & 0.08 (0.009) \\ 
+ 5 & 2 & 0.1 (0.021) & 0.1 (0.021) & 0.079 (0.009) \\ 
+ 50 & 2 & 0.075 (0.018) & 0.075 (0.018) & 0.062 (0.008) \\ 
+   100 & 2 & 0.064 (0.017) & 0.064 (0.017) & 0.048 (0.007)  \\[.15cm]  
+    \hline 
+   0 & 4 & 0.12 (0.025) & 0.124 (0.025) & 0.069 (0.007) \\ 
+   5 & 4 & 0.12 (0.025) & 0.12 (0.025) & 0.064 (0.007) \\ 
+   50 & 4 & 0.087 (0.022) & 0.094 (0.023) & 0.046 (0.007) \\ 
+   100 & 4 & 0.049 (0.016) & 0.049 (0.017) & 0.033 (0.006)  \\[.15cm]  
+    \hline 
+   0 & 8 & 0.184 (0.031) & 0.192 (0.032) & 0.07 (0.008) \\ 
+   5 & 8 & 0.181 (0.032) & 0.191 (0.033) & 0.067 (0.008) \\ 
+   50 & 8 & 0.139 (0.029) & 0.139 (0.029) & 0.05 (0.007) \\ 
+   100 & 8 & 0.102 (0.024) & 0.103 (0.024) & 0.04 (0.007)  \\[.15cm]   
+    \hline 
+   0  & 16  & 0.202 (0.031) & 0.202 (0.031) & 0.097 (0.008) \\ 
+   5 & 16 & 0.202 (0.031) & 0.202 (0.031) & 0.095 (0.008) \\ 
+   50 & 16 & 0.168 (0.031) & 0.168 (0.031) & 0.064 (0.008) \\ 
+   100 & 16 & 0.125 (0.029) & 0.125 (0.029) & 0.044 (0.006) \\ 
+   \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\caption{100 MC simulations for decaying shock effects with varying $\ell$ and $H$  ($B = 200$, $\mu_{\gamma}=2$, $\mu_{\alpha}=5$, $n=10$)} 
+\begin{center}
+\begin{tabular}{rrrccc}
+  \hline
+  $\ell$ & $H$ &  $|\hat{p}-p_1|$ & $|\hat{I}- I_1|$ & Mean of $p$-values in the donor pool  \\ 
+  \hline
+ 2  &  \multirow{4}{*}{2}  & 0.107 (0.026) & 0.12 (0.028) & 0.064 (0.008) \\ 
+   4  &  & 0.108 (0.022) & 0.118 (0.023) & 0.077 (0.008) \\ 
+   8  &   & 0.105 (0.024) & 0.107 (0.024) & 0.067 (0.009) \\ 
+   16  &   & 0.12 (0.025) & 0.124 (0.026) & 0.07 (0.009) \\[.15cm] 
+    \hline  
+   2  & \multirow{4}{*}{4}  & 0.162 (0.032) & 0.172 (0.033) & 0.061 (0.008) \\ 
+   4  &  & 0.089 (0.017) & 0.097 (0.019) & 0.08 (0.008) \\ 
+   8  &   & 0.135 (0.027) & 0.135 (0.027) & 0.08 (0.009) \\
+   16  &   & 0.156 (0.031) & 0.158 (0.031) & 0.063 (0.007) \\[.15cm]  
+   \hline  
+   2  & \multirow{4}{*}{8}  & 0.108 (0.025) & 0.112 (0.025) & 0.079 (0.009) \\ 
+   4  &   & 0.134 (0.029) & 0.136 (0.029) & 0.071 (0.008) \\ 
+   8  &   & 0.186 (0.033) & 0.186 (0.032) & 0.075 (0.008) \\ 
+   16  &   & 0.125 (0.026) & 0.125 (0.026) & 0.071 (0.008) \\[.15cm] 
+    \hline  
+   2  & \multirow{4}{*}{16}  & 0.222 (0.033) & 0.225 (0.033) & 0.094 (0.01) \\ 
+   4  &   & 0.124 (0.024) & 0.126 (0.024) & 0.081 (0.008) \\ 
+   8  &   & 0.14 (0.028) & 0.14 (0.028) & 0.075 (0.008) \\ 
+   16  &   & 0.162 (0.032) & 0.162 (0.032) & 0.068 (0.009) \\ 
+   \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+\newpage
+
+\section{Conditions}
+
+\begin{enumerate}
+  \item Donor pool sample size $n \to \infty$
+  \item $\|\alpha_1 - \hat{\alpha}_{w} \|_2 \to 0$ as $n\to \infty$ (this can be realized by setting $\sigma_{\alpha}$ small enough and $\Var(\bs{\gamma} )$ small enough)
+  \item The set of weights that are positive is fixed and finite asymptotically 
+  \item Conditions of Quaedvlieg and $B \to \infty$
+  \item $T_i \to \infty$ for $i = 2,\ldots, n+1$ and $T_i^* =o(T_i)$.
+\end{enumerate}
+
+If all those conditions hold, $\| p_1-\hat{p}\| \to 0$.
+
 \bibliographystyle{plainnat}

### 2021-07-29 transience-prediction.tex
addition of codes for ideal case

@@
 
+Note that $K_i$ is training sample size for time series $i$. Consider
+\begin{align*}
+  K_i & \sim \ceil{\mrm{Gamma}(a_{K}, b_K)}\\
+   T_i & \sim \ceil{\mrm{Gamma}(a_{T}, b_T)} \\
+  T_i^* &\equiv \ceil{0.5 \cdot T_i},
+\end{align*}
+ Then, we consider the following simulation setup
+\begin{verbatim}
+  ns <- c(5, 10, 20, 40)
+  Tscale <- Kscale <- 1 / 2 # b_T, b_K 
+  K.T.shape <- c(200, 400, 800, 1600) # for K_i and T_i
+  mu.gamma.delta <- 2 # mean for parameter vector of shock
+  sigma.delta.gamma <- 0.1 # sd for parameter vector of shock
+  sigma.alpha <- 0.1 # sd for shock noise  
+  sigma <- 0.1 # sd for response noise
+  mu.alpha <- 50 # intercept for shock (relatively large)
+  H <- 8 
+  ell <- 4
+  scale <- 2 # scale for covariates that follow Gamma distribution
+\end{verbatim}
+
 \begin{align*}

### 2021-07-29 simu_decay.R

@@ -176,16 +176,13 @@ ps.indic.W.decay <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05) 
 
 # simulation study normal for decaying shock effects
 sim.normal.gammaX.decay <- function(mu.gamma.delta = 1, mu.alpha, sigma, 
-                              sigma.alpha, sigma.delta.gamma = 0.5, 
-                              p, B, n, H, scale, ell = ell, bw = 4) {
-  K <- round(rgamma(n = n + 1, shape = 15, scale = 10)) # training sample size
-  Ts <- round(rgamma(n = n + 1, shape = 15, scale = 10)) # Time Length
-  Ts[which(Ts < 90)] <- 90
-  K[which(K < 90)] <- 90
-  Tstar <- c() # Shock Time Points
-  for (i in 1:(n + 1)) {
-    Tstar <- c(Tstar, sample((ceiling(1 / 4 * Ts[i]) + 1):(ceiling(3 / 4 * Ts[i]) + K[i] + H), size = 1))
-  }
+                              sigma.alpha, sigma.delta.gamma = 0.1, 
+                              p, B, n, H, scale, ell = ell, bw = 4,
+                              Kscale = 1 / 2, Tscale = 1 / 2, 
+                              Kshape, Tshape) {
+  K <- ceiling(rgamma(n + 1, scale = Kscale, shape = Kshape)) # training sample size
+  Ts <- ceiling(rgamma(n + 1, scale = Tscale, shape = Tshape)) # Time Length
+  Tstar <- ceiling(0.5 * Ts)
   phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters
   
   X <- c()
@@ -240,14 +237,19 @@ sim.normal.gammaX.decay <- function(mu.gamma.delta = 1, mu.alpha, sigma,
   Is <- est$Is
   # compute forecasts
   phat <- sum(W * ps[-1])
-  Ihat <- sum(W * Is[-1])
   p.diff <- abs(phat - ps[1])
-  I.diff <- abs(Ihat - Is[1])
-  return(c(p.diff = p.diff, I.diff = I.diff))
+  p.mean <- mean(ps[-1])
+  p.mean.diff <- abs(p.mean - ps[1])
+  return(c(p.diff = p.diff, p.mean = p.mean, p.mean.diff = p.mean.diff))
 }
 
[…]

### 2021-07-29 transience-prediction.tex
addition of codes for ideal case

--- 2021-07-27 transience-prediction.tex
@@
 
+Note that $K_i$ is training sample size for time series $i$. Consider
+\begin{align*}
+  K_i & \sim \ceil{\mrm{Gamma}(a_{K}, b_K)}\\
+   T_i & \sim \ceil{\mrm{Gamma}(a_{T}, b_T)} \\
+  T_i^* &\equiv \ceil{0.5 \cdot T_i},
+\end{align*}
+ Then, we consider the following simulation setup
+\begin{verbatim}
+  ns <- c(5, 10, 20, 40)
+  Tscale <- Kscale <- 1 / 2 # b_T, b_K 
+  K.T.shape <- c(200, 400, 800, 1600) # for K_i and T_i
+  mu.gamma.delta <- 2 # mean for parameter vector of shock
+  sigma.delta.gamma <- 0.1 # sd for parameter vector of shock
+  sigma.alpha <- 0.05 # sd for shock noise  
+  sigma <- 0.1 # sd for response noise
+  mu.alpha <- 50 # intercept for shock (relatively large)
+  H <- 8 
+  ell <- 4
+  scale <- 2 # scale for covariates that follow Gamma distribution
+\end{verbatim}
+
 \begin{align*}

### 2021-07-29 simu_decay.R

@@ -284,7 +284,7 @@ system.time(
                                        sigma.alpha = 0.05, 
                                        sigma.delta.gamma = 0.1, 
                                        p = 13, B = 200, scale = 2, 
-                                       n = 10, H = 8, ell = 4,
+                                       n = n, H = 8, ell = 4,
                                        Kshape = shape.K.T, Tshape = shape.K.T)
       return(study)
     }

### 2021-07-29 simu_decay.R
addition of codes for ideal case

@@ -182,7 +182,7 @@ sim.normal.gammaX.decay <- function(mu.gamma.delta = 1, mu.alpha, sigma,
                               Kshape, Tshape) {
   K <- ceiling(rgamma(n + 1, scale = Kscale, shape = Kshape)) # training sample size
   Ts <- ceiling(rgamma(n + 1, scale = Tscale, shape = Tshape)) # Time Length
-  Tstar <- ceiling(0.5 * Ts)
+  Tstar <- ceiling(1.5 * Ts)
   phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters
   
   X <- c()

### 2021-07-29 simu_decay.R
addition of codes for ideal case

@@ -182,7 +182,10 @@ sim.normal.gammaX.decay <- function(mu.gamma.delta = 1, mu.alpha, sigma,
                               Kshape, Tshape) {
   K <- ceiling(rgamma(n + 1, scale = Kscale, shape = Kshape)) # training sample size
   Ts <- ceiling(rgamma(n + 1, scale = Tscale, shape = Tshape)) # Time Length
-  Tstar <- ceiling(1.5 * Ts)
+  Tstar <- c()
+  for (i in 1:(n + 1)) {
+    Tstar <- c(Tstar,  max(Ts[i] + 1, ceiling(0.5 * (Ts[i] + K[i] + H))))
+  }
   phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters
   
   X <- c()

### 2021-08-25 prevalence_testing/numerical_studies/COP.R
updating repo

@@ -1,0 +1,411 @@
+# load packages
+library("data.table")
+library("dplyr")
+library("tseries")
+library("quantmod")
+library('Rsolnp')
+library('msos')
+library('tikzDevice')
+library('xtable')
+
+# load packages
+require('forecast')
+
+# this function returns the W^* estimated by synthetic control method (SCM)
+scm <- function(X, Tstar) {
+  # X is a list of covariates for disparate time series
+  # X[[1]] should be the covariate of the time series to predict
+  # X[[p]] for p = 2,...,n+1 are covariates for time series pool
+  
+  # T^* is a vector of shock-effects time points
+  # shock effect point must be > 2
+  
+  # package for constrained optiminization
+  require('Rsolnp')
+  
+  # number of time series for pool
+  n <- length(X) - 1
+  
+  # covariate for time series for prediction
+  X1 <- X[[1]][Tstar[1] + 1, , drop = FALSE]
+  
+  # covariates for time series pool
+  X0 <- c()
+  for (i in 1:n) {
+    X0[[i]] <- X[[i + 1]][Tstar[i + 1] + 1, , drop = FALSE]
+  }
+  
+  # objective function
+  weightedX0 <- function(W) {
+    # W is a vector of weight of the same length of X0
+    n <- length(W)
+    p <- ncol(X1)
+    XW <- matrix(0, nrow = 1, ncol = p)
+    for (i in 1:n) {
+      XW <- XW + W[i] * X0[[i]]
+    }
+    norm <- as.numeric(crossprod(matrix(X1 - XW)))
+    return(norm)
+  }
+  
+  # constraint for W
+  Wcons <- function(W) sum(W) - 1
+  
+  
+  # optimization
+  solnp(par = rep(1/n, n), fun = weightedX0, eqfun = Wcons, eqB = 0, 
+        LB = rep(0, n), UB = rep(1, n), control = list(trace = 0))
+}
+
+# squared error loss
+sel <- function(yhat, y) {
+  (y - yhat) ^ 2
+}
+
+# taSPA test for comparison of two models
+taSPA.mhfc <- function(ell, d, B, bw = 4) {
[…]

### 2021-08-25 prevalence_testing/numerical_studies/simu_cluster_ns10.R

@@ -10,7 +10,7 @@ source("simu_source.R")
 registerDoParallel(cores = ncores)
 set.seed(14)
 RNGkind("L'Ecuyer-CMRG")
-nsim <- 100
+nsim <- 150
 
 # parameter setup
 ns <- 10
@@ -34,7 +34,7 @@ system.time(
 																 mu.alpha = 10, sigma = 1, 
 																 sigma.alpha = sigma.alpha, 
 																 sigma.delta.gamma = 1, 
-																 p = 13, B = 200, scale = 10, 
+																 p = 13, B = 2000, scale = 10, 
 																 n = n, H = 12, ell = 3)
 			return(study)
 		}

### 2021-08-25 prevalence_testing/numerical_studies/simu_cluster_ns15.R

@@ -10,7 +10,7 @@ source("simu_source.R")
 registerDoParallel(cores = ncores)
 set.seed(15)
 RNGkind("L'Ecuyer-CMRG")
-nsim <- 100
+nsim <- 150
 
 # parameter setup
 ns <- 15
@@ -34,7 +34,7 @@ system.time(
 																 mu.alpha = 10, sigma = 1, 
 																 sigma.alpha = sigma.alpha, 
 																 sigma.delta.gamma = 1, 
-																 p = 13, B = 200, scale = 10, 
+																 p = 13, B = 2000, scale = 10, 
 																 n = n, H = 12, ell = 3)
 			return(study)
 		}

### 2021-08-25 prevalence_testing/numerical_studies/simu_cluster_ns5.R

@@ -10,7 +10,7 @@ source("simu_source.R")
 registerDoParallel(cores = ncores)
 set.seed(13)
 RNGkind("L'Ecuyer-CMRG")
-nsim <- 100
+nsim <- 150
 
 # parameter setup
 ns <- 5
@@ -34,7 +34,7 @@ system.time(
 																 mu.alpha = 10, sigma = 1, 
 																 sigma.alpha = sigma.alpha, 
 																 sigma.delta.gamma = 1, 
-																 p = 13, B = 200, scale = 10, 
+																 p = 13, B = 2000, scale = 10, 
 																 n = n, H = 12, ell = 3)
 			return(study)
 		}

### 2021-08-25 prevalence_testing/numerical_studies/simu_cluster_trial_aggregation.R

@@ -3,17 +3,17 @@
 rm(list = ls())
 
 ## load in output
-load("output_ns5.RData")
-load("output_ns10.RData")
-load("output_ns15.RData")
-load("output_ns25.RData")
+load("output_trial_ns5.RData")
+load("output_trial_ns10.RData")
+load("output_trial_ns15.RData")
+load("output_trial_ns25.RData")
 
 output <- c(output_ns5, output_ns10, output_ns15, 
 						output_ns25)
 
 ## create simulation parameters
 ns <- c(5, 10, 15, 25)
-sigma.alphas <- c(1, 5, 10, 25, 100)
+sigma.alphas <- c(1, 2, 3, 4, 5) / 10
 sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
 nsim <- 150
 

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay.R

@@ -98,8 +98,29 @@ taSPA.mhfc <- function(ell, d, B, bw = 4) {
   return(p)
 }
 
-# functions that return alpha.hat and synthetic weights
-ps.indic.W <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05) {
+vote <- function(ps, sig = 0.05) {
+  indic.p <- ifelse(ps < 0.05, yes = 1, no = 0)
+  mean <- mean(indic.p)
+  if (mean > 0.5) output <- 1
+  else if (mean == 0.5) output <- sample(c(1, 0), size = 1)
+  else output <- 0
+  return(output)
+}
+
+Wp <- function(ps, W, type = c('Fisher', 'Pearson')) {
+  if (type == 'Fisher') {
+    Mis <- -log(ps + 1e-10)
+  } else if (type == 'Pearson') {
+    Mis <- -log(1 - ps + 1e-10)
+  }
+  M <- Mis * W
+  p <- 1 - pgamma(2 * M, shape = 1 / (sum(W ^ 2)), scale = 2)
+  return(p)
+}
+
+
+# functions that return alpha.hat and synthetic weights for decaying shock effects
+ps.indic.W.decay <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05) {
   
   n <- length(Y) - 1
   
@@ -126,9 +147,11 @@ ps.indic.W <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05) {
         # lag
         yilag <- Y[[i]][-(Ti + 1)][(t + H - h + 1):(t + Ki + H - h)]
         
+        # decay
+        decay <- exp(- ((t + H - h + 1):(t + Ki + H - h) - Tstari - 1)) * ifelse((t + H - h + 1):(t + Ki + H - h) >= Tstari + 1, yes = 1, no = 0)
+        
         # OLS
-        lmodi.adj <- lm(yi ~ 1 + ifelse((t + H - h + 1):(t + Ki + H - h) >= Tstari + 1, yes = 1, no = 0) + 
-                          yilag + xi)
+        lmodi.adj <- lm(yi ~ 1 + decay + yilag + xi)
         lmodi.unadj <- lm(yi ~ 1 + yilag + xi)
         
         # beta.hat
[…]

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_H16.R

@@ -1,0 +1,76 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+registerDoParallel(cores = ncores)
+set.seed(16)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 150
+
+
+# parameter setup
+#Hs <- c(2, 4, 8, 16)
+Hs <- 16
+mu.alphas <- c(-1, 0, 1, 2)
+
+sim_params <- expand.grid(list(mu.alphas = mu.alphas, Hs = Hs))
+
+# simulation time
+system.time(suppressMessages(
+	output_mu_H16 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		mu.alpha <- sim_params[j, 1]
+		H <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 0, 
+																			 mu.alpha = mu.alpha, sigma = 1, 
+																			 sigma.alpha = 1, 
+																			 sigma.delta.gamma = 1, 
+																			 p = 13, B = 2000, scale = 4, 
+																			 n = 10, H = H, ell = 3)
+			return(study)
+		}
+		# return results
+		out
+	})
+))
+
+
+# parameter setup
+ells <- c(2, 4, 8, 16)
+sim_params <- expand.grid(list(ells = ells, Hs = Hs))
+
+# simulation time
+system.time(suppressMessages(
+	output_ell_H16 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		ell <- sim_params[j, 1]
+		H <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 0, 
+																			 mu.alpha = 2, sigma = 1, 
+																			 sigma.alpha = 1, 
+																			 sigma.delta.gamma = 1, 
+																			 p = 13, B = 2000, scale = 4, 
+																			 n = 10, H = H, ell = ell)
+			return(study)
+		}
+		# return results
[…]

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_H2.R

@@ -1,0 +1,76 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+registerDoParallel(cores = ncores)
+set.seed(13)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 150
+
+
+# parameter setup
+#Hs <- c(2, 4, 8, 16)
+Hs <- 2
+mu.alphas <- c(-1, 0, 1, 2)
+
+sim_params <- expand.grid(list(mu.alphas = mu.alphas, Hs = Hs))
+
+# simulation time
+system.time(suppressMessages(
+	output_mu_H2 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		mu.alpha <- sim_params[j, 1]
+		H <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 0, 
+																			 mu.alpha = mu.alpha, sigma = 1, 
+																			 sigma.alpha = 1, 
+																			 sigma.delta.gamma = 1, 
+																			 p = 13, B = 2000, scale = 4, 
+																			 n = 10, H = H, ell = 3)
+			return(study)
+		}
+		# return results
+		out
+	})
+))
+
+
+# parameter setup
+ells <- c(2, 4, 8, 16)
+sim_params <- expand.grid(list(ells = ells, Hs = Hs))
+
+# simulation time
+system.time(suppressMessages(
+	output_ell_H2 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		ell <- sim_params[j, 1]
+		H <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 0, 
+																			 mu.alpha = 2, sigma = 1, 
+																			 sigma.alpha = 1, 
+																			 sigma.delta.gamma = 1, 
+																			 p = 13, B = 2000, scale = 4, 
+																			 n = 10, H = H, ell = ell)
+			return(study)
+		}
[…]

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_H4.R

@@ -1,0 +1,76 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+registerDoParallel(cores = ncores)
+set.seed(14)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 150
+
+
+# parameter setup
+#Hs <- c(2, 4, 8, 16)
+Hs <- 4
+mu.alphas <- c(-1, 0, 1, 2)
+
+sim_params <- expand.grid(list(mu.alphas = mu.alphas, Hs = Hs))
+
+# simulation time
+system.time(suppressMessages(
+	output_mu_H4 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		mu.alpha <- sim_params[j, 1]
+		H <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 0, 
+																			 mu.alpha = mu.alpha, sigma = 1, 
+																			 sigma.alpha = 1, 
+																			 sigma.delta.gamma = 1, 
+																			 p = 13, B = 2000, scale = 4, 
+																			 n = 10, H = H, ell = 3)
+			return(study)
+		}
+		# return results
+		out
+	})
+))
+
+
+# parameter setup
+ells <- c(2, 4, 8, 16)
+sim_params <- expand.grid(list(ells = ells, Hs = Hs))
+
+# simulation time
+system.time(suppressMessages(
+	output_ell_H4 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		ell <- sim_params[j, 1]
+		H <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 0, 
+																			 mu.alpha = 2, sigma = 1, 
+																			 sigma.alpha = 1, 
+																			 sigma.delta.gamma = 1, 
+																			 p = 13, B = 2000, scale = 4, 
+																			 n = 10, H = H, ell = ell)
+			return(study)
+		}
[…]

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_H8.R

@@ -1,0 +1,76 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+registerDoParallel(cores = ncores)
+set.seed(15)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 150
+
+
+# parameter setup
+#Hs <- c(2, 4, 8, 16)
+Hs <- 8
+mu.alphas <- c(-1, 0, 1, 2)
+
+sim_params <- expand.grid(list(mu.alphas = mu.alphas, Hs = Hs))
+
+# simulation time
+system.time(suppressMessages(
+	output_mu_H8 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		mu.alpha <- sim_params[j, 1]
+		H <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 0, 
+																			 mu.alpha = mu.alpha, sigma = 1, 
+																			 sigma.alpha = 1, 
+																			 sigma.delta.gamma = 1, 
+																			 p = 13, B = 2000, scale = 4, 
+																			 n = 10, H = H, ell = 3)
+			return(study)
+		}
+		# return results
+		out
+	})
+))
+
+
+# parameter setup
+ells <- c(2, 4, 8, 16)
+sim_params <- expand.grid(list(ells = ells, Hs = Hs))
+
+# simulation time
+system.time(suppressMessages(
+	output_ell_H8 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		ell <- sim_params[j, 1]
+		H <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 0, 
+																			 mu.alpha = 2, sigma = 1, 
+																			 sigma.alpha = 1, 
+																			 sigma.delta.gamma = 1, 
+																			 p = 13, B = 2000, scale = 4, 
+																			 n = 10, H = H, ell = ell)
+			return(study)
+		}
[…]

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_T_100.R

@@ -1,0 +1,47 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+registerDoParallel(cores = ncores)
+set.seed(13)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 200
+
+
+# parameter setup
+#shape.K.Ts <- c(200, 400, 600, 800)
+shape.K.Ts <- 100
+ns <- c(50, 100, 200, 300)
+sim_params <- expand.grid(list(shape.K.Ts = shape.K.Ts, ns = ns))
+
+# simulation time
+system.time(
+	output_T_100 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		shape.K.T <- sim_params[j, 1]
+		n <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 2, 
+																			 mu.alpha = 10, sigma = 0.1, 
+																			 sigma.alpha = 0.05, 
+																			 sigma.delta.gamma = 0.1, 
+																			 p = 13, B = 1000, scale = 2, 
+																			 n = n, H = 8, ell = 4,
+																			 Kshape = shape.K.T, Tshape = shape.K.T)
+			return(study)
+		}
+		# return results
+		out
+	})
+)
+
+
+save(output_T_100, file = "output_decay_T_100.RData")

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_T_200.R

@@ -1,0 +1,47 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+registerDoParallel(cores = ncores)
+set.seed(13)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 200
+
+
+# parameter setup
+#shape.K.Ts <- c(200, 400, 600, 800)
+shape.K.Ts <- 200
+ns <- c(50, 100, 200, 300)
+sim_params <- expand.grid(list(shape.K.Ts = shape.K.Ts, ns = ns))
+
+# simulation time
+system.time(
+	output_T_200 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		shape.K.T <- sim_params[j, 1]
+		n <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 2, 
+																			 mu.alpha = 10, sigma = 0.1, 
+																			 sigma.alpha = 0.05, 
+																			 sigma.delta.gamma = 0.1, 
+																			 p = 13, B = 1000, scale = 2, 
+																			 n = n, H = 8, ell = 4,
+																			 Kshape = shape.K.T, Tshape = shape.K.T)
+			return(study)
+		}
+		# return results
+		out
+	})
+)
+
+
+save(output_T_200, file = "output_decay_T_200.RData")

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_T_300.R

@@ -1,0 +1,47 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+registerDoParallel(cores = ncores)
+set.seed(13)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 200
+
+
+# parameter setup
+#shape.K.Ts <- c(200, 400, 600, 800)
+shape.K.Ts <- 300
+ns <- c(50, 100, 200, 300)
+sim_params <- expand.grid(list(shape.K.Ts = shape.K.Ts, ns = ns))
+
+# simulation time
+system.time(
+	output_T_300 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		shape.K.T <- sim_params[j, 1]
+		n <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 2, 
+																			 mu.alpha = 10, sigma = 0.1, 
+																			 sigma.alpha = 0.05, 
+																			 sigma.delta.gamma = 0.1, 
+																			 p = 13, B = 1000, scale = 2, 
+																			 n = n, H = 8, ell = 4,
+																			 Kshape = shape.K.T, Tshape = shape.K.T)
+			return(study)
+		}
+		# return results
+		out
+	})
+)
+
+
+save(output_T_300, file = "output_decay_T_300.RData")

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_T_400.R

@@ -1,0 +1,47 @@
+
+
+# MC
+library("parallel")
+library("doParallel")
+library("foreach")
+source("simu_source.R")
+
+registerDoParallel(cores = ncores)
+set.seed(13)
+RNGkind("L'Ecuyer-CMRG")
+nsim <- 200
+
+
+# parameter setup
+#shape.K.Ts <- c(200, 400, 600, 800)
+shape.K.Ts <- 400
+ns <- c(50, 100, 200, 300)
+sim_params <- expand.grid(list(shape.K.Ts = shape.K.Ts, ns = ns))
+
+# simulation time
+system.time(
+	output_T_400 <- lapply(1:nrow(sim_params), FUN = function(j) {
+		# parameters
+		shape.K.T <- sim_params[j, 1]
+		n <- sim_params[j, 2]
+		# %do% evaluates sequentially
+		# %dopar% evaluates in parallel
+		# .combine results
+		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+			# result
+			study <- sim.normal.gammaX.decay(mu.gamma.delta = 2, 
+																			 mu.alpha = 10, sigma = 0.1, 
+																			 sigma.alpha = 0.05, 
+																			 sigma.delta.gamma = 0.1, 
+																			 p = 13, B = 1000, scale = 2, 
+																			 n = n, H = 8, ell = 4,
+																			 Kshape = shape.K.T, Tshape = shape.K.T)
+			return(study)
+		}
+		# return results
+		out
+	})
+)
+
+
+save(output_T_400, file = "output_decay_T_400.RData")

### 2021-08-25 prevalence_testing/numerical_studies/simu_decay_T_aggregation.R

@@ -1,0 +1,44 @@
+
+rm(list = ls())
+
+## load in output
+load("output_decay_T_100.RData")
+load("output_decay_T_200.RData")
+load("output_decay_T_300.RData")
+load("output_decay_T_400.RData")
+
+output <- c(output_T_100, output_T_200, output_T_300, 
+						output_T_400)
+
+## create simulation parameters
+shape.K.Ts <- c(100, 200, 300, 400)
+ns <- c(50, 100, 200, 300)
+
+sim_params <- expand.grid(list(shape.K.Ts = shape.K.Ts, ns = ns))
+sim_params <- expand.grid(list(ns = ns, shape.K.Ts = shape.K.Ts))
+nsim <- 200
+
+# store results
+# load packages
+require('readxl')
+require('writexl')
+write_xlsx(lapply(output, as.data.frame), 'ntrial.xlsx')
+
+result <- c()
+for (i in 1:nrow(sim_params)) {
+	table <- output[[i]]
+	# means and sds
+	means <- apply(table, 2, function(x) mean(x))
+	sds <- apply(table, 2, function(x) sd(x))
+	result.i <- c()
+	for (j in 1:7) {
+		result.i <- cbind(result.i, paste0(round(means[j], digits = 3), 
+																			 ' (', round(sds[j] / sqrt(nsim), 
+																			 						digits = 3), ')'))
+	}
+	result <- rbind(result, result.i)
+}
+result <- cbind(sim_params[, c(1,2)], result)
+require('xtable')
+xtable(result, digits = c(0,0,0,3,3,3,3,3,3,3))
+

### 2021-08-25 prevalence_testing/numerical_studies/simu_source.R

@@ -242,5 +242,185 @@ sim.normal.gammaX <- function(mu.gamma.delta = 1, mu.alpha, sigma,
 	Ihat <- sum(W * Is[-1])
 	p.diff <- abs(phat - ps[1])
 	I.diff <- abs(Ihat - Is[1])
-	return(c(p.diff = p.diff, I.diff = I.diff))
+	return(c(p.diff = p.diff, I.diff = I.diff, ps = ps, W = W))
 }
+
+
+
+##########################
+# Decay functions
+##########################
+
+
+# functions that return alpha.hat and synthetic weights for decaying shock effects
+ps.indic.W.decay <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05) {
+	
+	n <- length(Y) - 1
+	
+	# empty
+	ps <- c()
+	
+	for (i in 1:(n + 1)) {
+		
+		# set up
+		Ti <- Ts[i]
+		Ki <- K[i]
+		Tstari <- Tstar[i]
+		
+		m1.L.i <- matrix(NA, nrow = Ti, ncol = H)
+		m2.L.i <- matrix(NA, nrow = Ti, ncol = H)
+		
+		# compute losses
+		for (h in 1:H) {
+			for (t in 1:Ti) {
+				
+				yi <- Y[[i]][-1][(t + H - h + 1):(t + Ki + H - h)]
+				xi <- X[[i]][-1, ][(t + H - h + 1):(t + Ki + H - h),]
+				
+				# lag
+				yilag <- Y[[i]][-(Ti + 1)][(t + H - h + 1):(t + Ki + H - h)]
+				
+				# decay
+				decay <- exp(- ((t + H - h + 1):(t + Ki + H - h) - Tstari - 1)) * ifelse((t + H - h + 1):(t + Ki + H - h) >= Tstari + 1, yes = 1, no = 0)
+				
+				# OLS
+				lmodi.adj <- lm(yi ~ 1 + decay + yilag + xi)
+				lmodi.unadj <- lm(yi ~ 1 + yilag + xi)
+				
+				# beta.hat
+				beta.hat.adj <- matrix(coef(lmodi.adj), nrow = 1)
+				beta.hat.adj[which(is.na(beta.hat.adj) == TRUE)] <- 0
+				beta.hat.unadj <- matrix(coef(lmodi.unadj), nrow = 1)
+				
+				yhat.adj <- tail(yi, 1)
[…]

### 2021-08-25 prevalence_testing/numerical_studies/simu_trial_cluster_ns10.R

@@ -8,20 +8,20 @@ source("simu_source.R")
 
 #ncores <- detectCores() - 1
 registerDoParallel(cores = ncores)
-set.seed(16)
+set.seed(14)
 RNGkind("L'Ecuyer-CMRG")
 nsim <- 150
 
 # parameter setup
-ns <- 25
-sigma.alphas <- c(1, 5, 10, 25, 100)
+ns <- 10
+sigma.alphas <- c(1, 2, 3, 4, 5) / 10
 sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
 
 
 
 # simulation time
 system.time(
-	output_ns25 <- lapply(1:nrow(sim_params), FUN = function(j) {
+	output_ns10 <- lapply(1:nrow(sim_params), FUN = function(j) {
 		# parameters
 		sigma.alpha <- sim_params[j, 1]
 		n <- sim_params[j, 2]
@@ -30,10 +30,10 @@ system.time(
 		# .combine results
 		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
 			# result
-			study <- sim.normal.gammaX(mu.gamma.delta = 2, 
-																 mu.alpha = 10, sigma = 1, 
+			study <- sim.normal.gammaX(mu.gamma.delta = 1, 
+																 mu.alpha = 2, sigma = 1, 
 																 sigma.alpha = sigma.alpha, 
-																 sigma.delta.gamma = 1, 
+																 sigma.delta.gamma = 0.10, 
 																 p = 13, B = 2000, scale = 10, 
 																 n = n, H = 12, ell = 3)
 			return(study)
@@ -43,6 +43,6 @@ system.time(
 	})
 )
 
-save(output_ns25, file = "output_ns25.RData")
+save(output_ns10, file = "output_ns10.RData")
 
 

### 2021-08-25 prevalence_testing/numerical_studies/simu_trial_cluster_ns15.R

@@ -8,20 +8,20 @@ source("simu_source.R")
 
 #ncores <- detectCores() - 1
 registerDoParallel(cores = ncores)
-set.seed(16)
+set.seed(15)
 RNGkind("L'Ecuyer-CMRG")
 nsim <- 150
 
 # parameter setup
-ns <- 25
-sigma.alphas <- c(1, 5, 10, 25, 100)
+ns <- 15
+sigma.alphas <- c(1, 2, 3, 4, 5) / 10
 sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
 
 
 
 # simulation time
 system.time(
-	output_ns25 <- lapply(1:nrow(sim_params), FUN = function(j) {
+	output_ns15 <- lapply(1:nrow(sim_params), FUN = function(j) {
 		# parameters
 		sigma.alpha <- sim_params[j, 1]
 		n <- sim_params[j, 2]
@@ -30,10 +30,10 @@ system.time(
 		# .combine results
 		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
 			# result
-			study <- sim.normal.gammaX(mu.gamma.delta = 2, 
-																 mu.alpha = 10, sigma = 1, 
+			study <- sim.normal.gammaX(mu.gamma.delta = 1, 
+																 mu.alpha = 2, sigma = 1, 
 																 sigma.alpha = sigma.alpha, 
-																 sigma.delta.gamma = 1, 
+																 sigma.delta.gamma = 0.10, 
 																 p = 13, B = 2000, scale = 10, 
 																 n = n, H = 12, ell = 3)
 			return(study)
@@ -43,6 +43,7 @@ system.time(
 	})
 )
 
-save(output_ns25, file = "output_ns25.RData")
+save(output_ns15, file = "output_ns15.RData")
+
 
 

### 2021-08-25 prevalence_testing/numerical_studies/simu_trial_cluster_ns25.R

@@ -14,7 +14,7 @@ nsim <- 150
 
 # parameter setup
 ns <- 25
-sigma.alphas <- c(1, 5, 10, 25, 100)
+sigma.alphas <- c(1, 2, 3, 4, 5) / 10
 sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
 
 
@@ -30,10 +30,10 @@ system.time(
 		# .combine results
 		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
 			# result
-			study <- sim.normal.gammaX(mu.gamma.delta = 2, 
-																 mu.alpha = 10, sigma = 1, 
+			study <- sim.normal.gammaX(mu.gamma.delta = 1, 
+																 mu.alpha = 2, sigma = 1, 
 																 sigma.alpha = sigma.alpha, 
-																 sigma.delta.gamma = 1, 
+																 sigma.delta.gamma = 0.10, 
 																 p = 13, B = 2000, scale = 10, 
 																 n = n, H = 12, ell = 3)
 			return(study)
@@ -44,5 +44,6 @@ system.time(
 )
 
 save(output_ns25, file = "output_ns25.RData")
+
 
 

### 2021-08-25 prevalence_testing/numerical_studies/simu_trial_cluster_ns5.R

@@ -8,20 +8,20 @@ source("simu_source.R")
 
 #ncores <- detectCores() - 1
 registerDoParallel(cores = ncores)
-set.seed(16)
+set.seed(13)
 RNGkind("L'Ecuyer-CMRG")
 nsim <- 150
 
 # parameter setup
-ns <- 25
-sigma.alphas <- c(1, 5, 10, 25, 100)
+ns <- 5
+sigma.alphas <- c(1, 2, 3, 4, 5) / 10
 sim_params <- expand.grid(list(sigma.alphas = sigma.alphas, ns = ns))
 
 
 
 # simulation time
 system.time(
-	output_ns25 <- lapply(1:nrow(sim_params), FUN = function(j) {
+	output_ns5 <- lapply(1:nrow(sim_params), FUN = function(j) {
 		# parameters
 		sigma.alpha <- sim_params[j, 1]
 		n <- sim_params[j, 2]
@@ -30,10 +30,10 @@ system.time(
 		# .combine results
 		out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
 			# result
-			study <- sim.normal.gammaX(mu.gamma.delta = 2, 
-																 mu.alpha = 10, sigma = 1, 
+			study <- sim.normal.gammaX(mu.gamma.delta = 1, 
+																 mu.alpha = 2, sigma = 1, 
 																 sigma.alpha = sigma.alpha, 
-																 sigma.delta.gamma = 1, 
+																 sigma.delta.gamma = 0.10, 
 																 p = 13, B = 2000, scale = 10, 
 																 n = n, H = 12, ell = 3)
 			return(study)
@@ -43,6 +43,6 @@ system.time(
 	})
 )
 
-save(output_ns25, file = "output_ns25.RData")
+save(output_ns5, file = "output_ns5.RData")
 
 

### 2021-08-25 prevalence_testing/numerical_studies/sustained_shock.R

@@ -124,7 +124,7 @@ T <- 150
 n <- 50
 H <- 20
 lag <- 5
-shock <- 1
+shock <- 2
 ar <- 0.10
 
 dat <- data_setup(T = T, n = n, H = H, lag = lag, shock = shock, ar = ar)

### 2021-08-25 prevalence_testing/postshocktest2021draft.tex
moved stuff to pravlence_testing directory

@@
 \newcommand{\x}{\textbf{x}}
+\newcommand{\dbf}{\textbf{d}}
+\newcommand{\y}{\textbf{y}}
 \newcommand{\X}{\textbf{X}}
 \newcommand{\Y}{\textbf{Y}}
+\newcommand{\L}{\textbf{L}}
 \newcommand{\Hist}{\mathcal{H}}
@@
 \DeclareMathOperator*{\argmin}{arg\,min} % arg min
-\def\E#1{\mathrm{E}(#1)} % Expectation symbol
+\def\E{\mathbb{E}} % Expectation symbol
+\def\mc#1{\mathcal{#1}}
 \def\var#1{\mathrm{Var}(#1)} % Variance symbol
@@
 \newcommand\red[1]{{\color{red}#1}}
+\def\bs#1{\boldsymbol{#1}}
+\def\P{\mathbb{P}}
 
+\newcommand{\ceil}[1]{\lceil #1 \rceil}
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert} % A norm with 1 argument
@@
 
-\title{Testing for the prevalence or transience of a shock effect in the post-shock setting}
+\title{Prospective testing for the prevalence or transience of a shock effect before it occurs}
 \author{}
@@
 \maketitle
+
+%We develop a forecasting methodology for providing credible forecasts for time series that have recently undergone a shock.
+We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
+Three shock effect estimators are motivated with the aim of minimizing average forecast risk.
+We propose risk-reduction propositions that provide conditions that establish when our methodology works.
+Bootstrap and leave-one-out cross validation procedures are provided to prospectively assess the performance of our methodology.
+Several simulated data examples, and two real data examples of forecasting Conoco Phillips and Apple stock price are provided for verification and illustration
+
 \begin{abstract}
- We provide a hypothesis test for the existence or transience of a shock in the post-shock setting of \cite{lin2021minimizing}.
+We develop a hypothesis testing procedure to prospectively test whether an anticipated shock is likely to be transient or permanent over a time horizon.
+We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
+These additional time series form a donor pool.
+For each of the time series in the donor pool we calculate a p-value corresponding to a hypothesis test on the relevance of the inclusion of shock-effect information in predicting the response over the time horizon.
+These p-values are then combined to form an aggregated p-value which guides one decision in determining whether the shock effect for the time series under study is expected to be prevalent or transient.
+This p-value can be computed before the shock-effect is observed in the time series under study provided one can form a suitable donor pool.
+Several simulated data examples, and two real data examples of forecasting Conoco Phillips stock price and ....
+are provided for verification and illustration.
 \end{abstract}
+
+\section{Introduction}
+
+%We provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
+We provide forecasting methodology for assessing the lingering effect of an anticipated structural shock to a time series under study.
+We focus on the setting in which a structural shock has occurred and one desires a prediction for the post-shock response over a set time horizon $H$.
+Specific interest is in determining whether the shock is expected to be permanent or transient over $H$.
+Standard forecasting methods may not yield any guidance on the post-shock trajectories \citep{baumeister2014real}.
+This is a general problem that has many real life applications.
+For example, one may acquire terrible or great news about a company and desire to determine whether that news is bound to impact the stock price of that company over a relevant time period.
+Companies may be interested in forecasting the demand of their products after they were involved in a brand crisis, but they only have recent sales data from pre-crises times.
+%Policy makers, economists, and citizens alike may be interested in determining whether inflation will dissipate or persist for the foreseeable future
+All is not lost in this forecasting setting, one may be able to supplement the present forecast with past data borrowed from other time series which contain post-shock trajectories arising from materially similar structural shocks.
+
+The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
+
+Our testing method embraces ideas from 
+forecast aggregation in the post-shock setting \citep{lin2021minimizing}, 
+forecast comparison \citep{diebold1995comparing, quaedvlieg2021multi}, 
+p-value combination, 
+conditional forecasting \citep{baumeister2014real, kilian2017structural}, 
+time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting},
+forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, 
+synthetic control methodology \citep{abadie2010synthetic, agarwal2020two},  
+expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
 
@@
 
+We will suppose that a researcher has multivariate time series data $\y_{i,t}$, $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
+We let $\y_{i,t} = (y_{i,t}$, $\x_{i,t}$) where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
+Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection.
+We will suppose that each time series $\y_{i,t}$ undergoes a shock at time $T^*_i \leq T_i + 1$.
+To define an interesting setting, we will suppose that $T^*_1 = T_1 + 1$, and $1 < T^*_i < T_i + 1$ for $i \geq 2$.
+We will suppose that $\x_{i,t=T^*_i}$ is observed before the shock takes effect on $y_{i,t=T^*_i}$.
+
+We are interested in point forecasts $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ with the aim of determining whether the shock has an effect on $y_{i,t}^h$.
+\cite{quaedvlieg2021multi} provided a methodology for comparing forecasts jointly across all horizons of a forecast path, $h = 1,\ldots, H$.
+In our post-shock setting, we want to compare the forecasts
+$$
+  \hat y^{i,h}_{1,t} \; \text{and} \; \hat y^{2,h}_{i,t}
+$$
+where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed structural shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.
+We will compare these forecasts in terms of their loss differential
+$$
+  \dbf_{i,t} = \L_{i,t,1} - \L_{i,t,2},
+$$
+where $L_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{h,j})$, $j = 1,2$, and $L$ is a loss function.
+Hypothesis tests in \cite{quaedvlieg2021multi} are with respect to $E(\dbf_{i,t}) = \mbf\mu_{i,t}$.
+Conditions for these tests require conditions of \cite{giacomini2006tests}.
+
+We will be interested in $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
+
+\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$.
+We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock.
+Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool.
+\vspace*{0.5cm}
+
+We will consider the average superior predictive ability (aSPA) to assess whether or not a shock is permanent or transitory.
+The aSPA investigates forecast comparisons based on their weighted average loss difference
+$$
+  \mu^{(AVG)} = \textbf{w}^T\mathbf{\mu} = \sum_{h=1}^H w_h \mu^h
+$$
+with weights $\textbf{w}$ that sum to one.
+Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1.
+
 \subsection{Model setup}
+\label{modelsetup}
 
-\label{modelsetup}
+\noindent\textbf{Note}: We need to update the modeling setup. We should present a general modeling class which includes both the decay model and the permanent shift model.
+\vspace*{0.5cm}
 
@@
 
+\noindent\textbf{Note}: Our forecast needs to be written with respect to our general model. Specifics can be given when we conduct our numerical examples.
+\vspace*{0.5cm}
+
 In our post-shock setting we consider the following candidate forecasts: 
@@
 
-\subsection{Multi-horizon forecast evaluation}
+\section{Simulation Setup}
+\label{simulation}
 
-We now consider an approach for comparing the forecasts over a specified time horizon after a shock has occurred by borrowing information across similar forecasts.
+Let $n$ denote the donor pool size, $p$ denote the number of covariates used, $H$ denote the number of horizon used, $T_i$ denote the length of time series to be evaluated for time series $i$, $K_i$ denote the training sample size used for each  forecasting  time series $i$, $T_i^*$ denote the time point just before the realization of the shock for time series $i$ for $i = 1, \ldots, n+1$.
 
-\cite{quaedvlieg2021multi} provided a methodology for comparing forecasts jointly across all horizons of a forecast path, $h = 1,\ldots, H$.
-In our post-shock setting, we want to compare the forecasts
-$$
-  \hat y^{1,h}_{1,t} \; \text{and} \; \hat y^{2,h}_{1,t}
-$$
-where $y^{1,h}_{1,t}$ is the forecast for $y_t$ that accounts for the yet-to-be observed structural shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{1,t}$ is defined similarly for the forecast that does not include any shock effect information.
-We will compare these forecasts in terms of their loss differential
-$$
-  d_t = L_{1,t} - L_{2,t},
-$$
-where $L_{j,t} = L(y_t,\hat y_{j,t})$, $j = 1,2$, and $L$ is a loss function.
-Hypothesis tests in \cite{quaedvlieg2021multi} are with respect to $E(d_t) = \mu_t$.
-Conditions for these tests require conditions of \cite{giacomini2006tests}.
+In this setting $n$, $p$, and $H$ are pre-determined.
+$T_i, K_i \sim \mrm{Gamma}(15, 10)$.
+The total sample size for $i$th time series is $T_i + K_i + H$.
+$T_i^*$ is randomly sampled from $\ceil{\frac{1}{4}T_i}+1$ to $\ceil{\frac{3}{4} T_i} + K_i+ H$.
+If $T_i, K_i < 90$, we force them to be 90.
+The adopted model for the data is as below:
+\begin{align*}
+  y_{i,t} &= \eta_i + \phi_i y_{i,t-1} + \mbf{x}_{i,t} \bs{\beta}_i + \alpha_i I(t > T_i^*) + \varepsilon_{i,t},\\
+  \alpha_i &= \mu_{\alpha} + \mbf{x}_{i,T_i^*+1}\bs{\gamma}_i + \tilde{\varepsilon}_{i},
+\end{align*}
+where
+\begin{align*}
+  \phi_i & \sim \text{ indep. }  U(0,1) \\
+  \eta_i & \sim \text{ indep. }  \mc{N}(0,1) \\
+  \varepsilon_{i,t} & \sim \text{ indep. } \mc{N}(0, \sigma^2)\\
+  \tilde{\varepsilon}_i & \sim \text{ indep. } \mc{N}(0, \sigma_{\alpha}^2)
+  \\
+  \bs{\gamma}_i & \sim \text{ indep. } \mc{N}(\mu_{\gamma}\bs{1}_p, \sigma_{\gamma}^2 \mbf{I}_p) \\
+  \bs{\beta}_i & \sim \text{ indep. }  \mc{N}(\bs{0}_p, \mbf{I}_p).
+\end{align*}
+Moreover, the elements of $\mathbf{x}_{i,t}$ are independently distributed as $\mrm{Gamma}(1,\delta)$.
 
-\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$.
-We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock.
-Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool.
+Note that $K_i$ is training sample size for time series $i$. Consider
+\begin{align*}
+  K_i & \sim \ceil{\mrm{Gamma}(a_{K}, b_K)}\\
+   T_i & \sim \ceil{\mrm{Gamma}(a_{T}, b_T)} \\
+  T_i^* &\equiv \max\{T_i+1, \ceil{0.5 \cdot(T_i+K_i+H)}\},
+\end{align*}
 
-We will consider the average superior predictive ability (aSPA) to assess whether or not a shock is permanent or transitory.
-The aSPA investigates forecast comparisons based on their weighted average loss difference
-$$
-  \mu^{(AVG)} = \textbf{w}^T\mathbf{\mu} = \sum_{h=1}^H w_h \mu^h
-$$
-with weights $\textbf{w}$ that sum to one.
-Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1.
+$K_i+H+T_i^* > T_i+K_i+H$
+
+ Then, we consider the following simulation setup
+\begin{verbatim}
+  ns <- c(5, 10, 20, 40)
+  Tscale <- Kscale <- 1 / 2 # b_T, b_K 
+  K.T.shape <- c(200, 400, 800, 1600) # for K_i and T_i
+  mu.gamma.delta <- 2 # mean for parameter vector of shock
+  sigma.delta.gamma <- 0.1 # sd for parameter vector of shock
+  sigma.alpha <- 0.05 # sd for shock noise  
+  sigma <- 0.1 # sd for response noise
+  mu.alpha <- 50 # intercept for shock (relatively large)
+  H <- 8 
+  ell <- 4
+  scale <- 2 # scale for covariates that follow Gamma distribution
+\end{verbatim}
+
+\begin{align*}
+  y_{i,t} &= \eta_i + \phi_i y_{i,t-1} + \mbf{x}_{i,t} \bs{\beta}_i + \xi_i\cdot  I(t > T_i^*) + \varepsilon_{i,t},\\
+  \xi_i &= \alpha_i \cdot e^{-(t-T_i^*-1)} \\
+  \alpha_i &= \mu_{\alpha} + \mbf{x}_{i,T_i^*+1}\bs{\gamma}_i + \tilde{\varepsilon}_{i},
+\end{align*}
 

### 2021-08-27 prevalence_testing/postshocktest2021draft.tex
edited manuscript draft

@@
 \usepackage{amsfonts}
-%\usepackage{amscd}
+\usepackage{amscd}
 \usepackage{amssymb}
+\usepackage{natbib}
+\usepackage{url}
+
 \usepackage{graphicx}
-\usepackage{mathtools}
-\usepackage{natbib}
+%\usepackage{mathtools}
 \usepackage{enumitem}
-\usepackage{url}
 \usepackage{authblk}
@@
 \usepackage{hyperref}
-\usepackage{geometry}
+
 \usepackage{caption}
@@
 \usepackage{pdflscape}
+
 % margin setup
+\usepackage{geometry}
 \geometry{margin=0.8in}
@@
 \noindent\textbf{Note}: We need to update the modeling setup. We should present a general modeling class which includes both the decay model and the permanent shift model.
-\vspace*{0.5cm}
 
-The assumed autoregressive models considered are that in \cite{lin2021minimizing}, we describe details here.
-Let $I(\cdot)$ be an indicator function, $T_i$ be the time length of the time series $i$ for $i = 1, \ldots, n+1$, and $T_i^*$ be the time point just before the one when the shock is known to occur, with $T_i^* < T_i$.
-For $t= 1, \ldots, T_i$ and $i = 1, \ldots, n+1$, the model $\mc{M}_1$ is defined as
+\vspace{0.5cm}\noindent\textbf{Possible modeling approach}
+
+\vspace{0.5cm} We now describe the assumed autoregressive models with random effects for which post-shock aggregated estimators are provided. The model $\mc{M}$ is defined as
 \begin{align}
-\mc{M}_1 \colon y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\label{equation1}
+\mc{M} \colon \begin{array}{l}
+  y_{i,t} =\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j} + f(\mc{F}_{i,t-1},\x_{i,t-1},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
+  \; f(\mc{F}_{i,t-1},\x_{i,t-1},\alpha_i) = \alpha_i g(t) + \sum_{j=1}^{q_3}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_4-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
+  \; \alpha_i = \mu_{\alpha}+ \sum_{j=1}^{q_5}\delta_{i,j}'\mbf{x}_{i, T_i^*+j}+ \t{\varepsilon}_{i}, 
+\end{array}\label{model}
 \end{align}
- where $D_{i,t} = I(t = T_i^* + 1)$ 
-and $\x_{i,t} \in \R^{p}$ with $p \geq 1$.  We assume that the 
-$\mbf{x}_{i,t}$s are fixed. Let $|x|$ denote the absolute value of $x$ for $x\in \reals$. For $i = 1, \ldots, n+1$ and $t=1, \ldots, T_i$, the random effects structure for $\mc{M}_1$ is:
+where $D_{i,t} = I(t \geq T_i^* + 1)$, $I(\cdot)$ is the indicator function, $\x_{i,t} \in \R^{p}$ are fixed with $p \geq 1$, $g(t)$ is a bounded continuous function which does not cross zero and $\lim_{t\to\infty}g(t) = a \in \R$.
+Let
+$\mathbf{\phi}_i = (\phi_{i,1},\ldots,\phi_{i,q_1})'$, 
+$\mathbf{\theta}_i = (\theta_{i,1},\ldots,\theta_{i,q_2})'$, 
+$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_3})'$, 
+$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i,q_4})'$, 
+$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,q_5})'$, 
+and suppose that the regression coefficients in \eqref{model} have the following random effects structure:
 \begin{align*}
-  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}\\
-  \phi_i &\simiid \mc{F}_{\phi} \text{ where } |\mc{F}_{\phi}| < 1, \\
-   \theta_i &\simiid \mc{F}_{\theta} \text{ with }  \; \mrm{E}_{\mc{F}_{\theta}}(\theta_i) = \mu_{\theta}, \mrm{Var}_{\mc{F}_{\theta}}(\theta_i)  = \Sigma^2_{\theta} \\
-\alpha_i &\simiid \mc{F}_{\alpha} \text{ with }  \; \mrm{E}_{\mc{F}_{\alpha}}(\alpha_i) = \mu_{\alpha}, \mrm{Var}_{\mc{F}_{\alpha}}(\alpha_i)  = \sigma^2_{\alpha}  \\
-\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i  ,  \\
-\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t},
+  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
+  \mathbf{\phi}_i &\simiid \mc{F}_{\mathbf{\phi}} \text{ where } |\phi_{i,j}| < 1, \\
+  \mathbf{\theta}_i &\simiid \mc{F}_{\mathbf{\theta}} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}}}(\theta_i) = \mu_{\mathbf{\theta}}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}}}(\mathbf{\theta}_i)  = \Sigma^2_{\mathbf{\theta}}, \\
+  \tilde{\mathbf{\phi}}_i &\simiid \mc{F}_{\tilde{\mathbf{\phi}}} \text{ where } |\t\phi_{i,j}| < 1, \\
+  \tilde{\mathbf{\theta}}_i &\simiid \mc{F}_{\tilde{\mathbf{\theta}}} \text{ with }  \; \mrm{E}_{\mc{F}_{\tilde{\mathbf{\theta}}}}(\theta_i) = \mu_{\tilde{\mathbf{\theta}}}, \mrm{Var}_{\mc{F}_{\tilde{\mathbf{\theta}}}}(\tilde{\mathbf{\theta}}_i)  = \Sigma^2_{\tilde{\mathbf{\theta}}}, \\
+  \mathbf{\delta}_i &\simiid  \mc{F}_{\mathbf{\delta}} \text{ with } \mrm{E}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\mu_{\mathbf{\delta}}, \mrm{Var}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\Sigma_{\mathbf{\delta}}, \\
+\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i,  \\
+\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha}, \\
+&\eta_i \indep \mathbf{\phi}_i \indep \mathbf{\theta}_i \indep 
+\tilde{\mathbf{\phi}}_i \indep \tilde{\mathbf{\theta}}_i \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t}.
 \end{align*}
-where $\indep $ denotes the independence operator.
-We also consider a modeling framework where the shock effects are linear functions of covariates with an additional additive mean-zero error.
-For $i = 1, \ldots, n+1$, the random effects structure for this model (model $\mc{M}_2$) is:
-\begin{align}
-\mc{M}_2 \colon \begin{array}{l}
-  y_{i,t} =\eta_i +\alpha_i D_{i,t} + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
-  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}+ \t{\varepsilon}_{i},
-\end{array}\label{model2}
-\end{align}
- where the added random effects are
-\begin{align*}
-\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha}\\
-\eta_i &\indep  \alpha_i \indep \phi_i \indep \theta_i \indep \varepsilon_{i,t} \indep \t{\varepsilon}_{i}.
-\end{align*} 
-We further define 
-$\tilde{\alpha}_i=\mu_{\alpha}+\delta_i'\mbf{x}_{i, T_i^*+1}$. 
-We will investigate the post-shock aggregated estimators in $\mc{M}_2$ 
-in settings where $\delta_i$ is either fixed or random. 
-We let $\mc{M}_{21}$ denote model $\mc{M}_{2}$ with $\delta_i = \delta$ for $i= 1, \ldots, n+1$, 
-where $\delta$ is a  fixed unknown parameter.
-We let $\mc{M}_{22}$ denote model $\mc{M}_{2}$ with the following random effects :
-\begin{align*}
-&\delta_i\simiid  \mc{F}_{\delta} \text{ with }\mrm{E}_{\mc{F}_{\delta}}(\delta_i)=\mu_{\delta}, \mrm{Var}_{\mc{F}_{\delta}}(\delta_i)=\Sigma_\delta \\
-   & \delta_i  \indep \t{\varepsilon}_{i}.
-\end{align*}
+The model \eqref{model} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}. \textbf{Need to carefully show}.
+
 We further define the parameter sets
@@
 \begin{array}{l}
- \;\, \Theta = \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
-   \Theta_1 = \{(\eta_i, \phi_i, \theta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i)\colon  t= 1, \ldots, T_i, i = 1\}
+ \;\, \Theta = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \tilde{\mathbf{\phi}}_i, \tilde{\mathbf{\theta}}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
+   \Theta_1 = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \tilde{\mathbf{\phi}}_i, \tilde{\mathbf{\theta}}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon  t= 1, \ldots, T_i, i = 1\}
 \end{array}\label{parameter} 
 \end{align}
-where $\Theta$ and $\Theta_1$ can adapt to $\mc{M}_1$ by dropping $\delta_i$. We assume this for notational simplicity.
 
-\subsection{Forecast}
+\subsection{Forecasting and testing for shock persistence}
 \label{forecast}
@@
 \begin{align*}
-  &\text{Forecast 1}: \hat y_{1,T_1^*+1}^1 = \hat\eta_1 
-    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
-    , \\
-  &\text{Forecast 2}: \hat y_{1,T_1^*+1}^2 = \hat\eta_1 
-    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
-    + \hat{\alpha},
+  &\text{Forecast 1}: \\
+  &\text{Forecast 2}: 
 \end{align*}
-where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all OLS estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$.
-%The first forecast ignores the presence of $\alpha_1$ while the second forecast incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study.
-
-Throughout the rest of this article we highlight when the information from the time series donor pool, indexed by $\{y_{i,t} \colon t = 1,\ldots,T_i, i = 2,\ldots,n+1\}$, can be used to construct a shock effect estimator $\hat\alpha$ in which Forecast 2 beats Forecast 1 and vice-versa.
-We will consider the different dynamic panel models $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$.
-%Improvement will be measured by assessing the reduction in risk that Forecast 2 offers over Forecast 1.
-We outline the theoretical details of risk-reduction in Section \ref{properties}.
-We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response.
-It is important to note that, in general, $\hat{\alpha}$ does not converge to $\alpha_1$ in any sense.
-Despite this shortcoming, adjustment of the forecast for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has the potential to lower forecast risk under several conditions, and for several estimation techniques.
 We want to determine which forecast is appropriate over a horizon while the methods in \cite{lin2021minimizing} were only appropriate in the nowcasting setting in which prediction was only focused on the response immediately following the shock.

### 2021-08-30 prevalence_testing/postshocktest2021draft.tex
add sbatch files to repo; updated model formulation

@@
 \mc{M} \colon \begin{array}{l}
-  y_{i,t} =\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j} + f(\mc{F}_{i,t-1},\x_{i,t-1},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
-  \; f(\mc{F}_{i,t-1},\x_{i,t-1},\alpha_i) = \alpha_i g(t) + \sum_{j=1}^{q_3}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_4-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
-  \; \alpha_i = \mu_{\alpha}+ \sum_{j=1}^{q_5}\delta_{i,j}'\mbf{x}_{i, T_i^*+j}+ \t{\varepsilon}_{i}, 
+  y_{i,t} =\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j} + \alpha_i D_{i,t}f(t) + \varepsilon_{i,t},\\[.2cm]
+  %\; f(\mc{F}_{i,t-1},\x_{i,t-1},\alpha_i) =  \\[.2cm] %+ \sum_{j=1}^{q_3}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_4-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
+  \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \t{\varepsilon}_{i},
+  %\sum_{j=1}^{q_3}\delta_{i,j}'\mbf{x}_{i, T_i^*-j+1}+ \t{\varepsilon}_{i}, 
 \end{array}\label{model}
 \end{align}
-where $D_{i,t} = I(t \geq T_i^* + 1)$, $I(\cdot)$ is the indicator function, $\x_{i,t} \in \R^{p}$ are fixed with $p \geq 1$, $g(t)$ is a bounded continuous function which does not cross zero and $\lim_{t\to\infty}g(t) = a \in \R$.
+where $D_{i,t} = I(t \geq T_i^* + 1)$, $I(\cdot)$ is the indicator function, $\x_{i,t} \in \R^{p}$ are fixed with $p \geq 1$, $f(t)$ is a bounded continuous function which does not cross zero and $\lim_{t\to\infty}g(t) = a \in \R$.
 Let
@@
 $\mathbf{\theta}_i = (\theta_{i,1},\ldots,\theta_{i,q_2})'$, 
-$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_3})'$, 
-$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i,q_4})'$, 
-$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,q_5})'$, 
+%$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_3})'$, 
+%$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i,q_4})'$, 
+$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,q_3})'$, 
 and suppose that the regression coefficients in \eqref{model} have the following random effects structure:
@@
   \mathbf{\theta}_i &\simiid \mc{F}_{\mathbf{\theta}} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}}}(\theta_i) = \mu_{\mathbf{\theta}}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}}}(\mathbf{\theta}_i)  = \Sigma^2_{\mathbf{\theta}}, \\
-  \tilde{\mathbf{\phi}}_i &\simiid \mc{F}_{\tilde{\mathbf{\phi}}} \text{ where } |\t\phi_{i,j}| < 1, \\
-  \tilde{\mathbf{\theta}}_i &\simiid \mc{F}_{\tilde{\mathbf{\theta}}} \text{ with }  \; \mrm{E}_{\mc{F}_{\tilde{\mathbf{\theta}}}}(\theta_i) = \mu_{\tilde{\mathbf{\theta}}}, \mrm{Var}_{\mc{F}_{\tilde{\mathbf{\theta}}}}(\tilde{\mathbf{\theta}}_i)  = \Sigma^2_{\tilde{\mathbf{\theta}}}, \\
+  %\tilde{\mathbf{\phi}}_i &\simiid \mc{F}_{\tilde{\mathbf{\phi}}} \text{ where } |\t\phi_{i,j}| < 1, \\
+  %\tilde{\mathbf{\theta}}_i &\simiid \mc{F}_{\tilde{\mathbf{\theta}}} \text{ with }  \; \mrm{E}_{\mc{F}_{\tilde{\mathbf{\theta}}}}(\theta_i) = \mu_{\tilde{\mathbf{\theta}}}, \mrm{Var}_{\mc{F}_{\tilde{\mathbf{\theta}}}}(\tilde{\mathbf{\theta}}_i)  = \Sigma^2_{\tilde{\mathbf{\theta}}}, \\
   \mathbf{\delta}_i &\simiid  \mc{F}_{\mathbf{\delta}} \text{ with } \mrm{E}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\mu_{\mathbf{\delta}}, \mrm{Var}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\Sigma_{\mathbf{\delta}}, \\
@@
 &\eta_i \indep \mathbf{\phi}_i \indep \mathbf{\theta}_i \indep 
-\tilde{\mathbf{\phi}}_i \indep \tilde{\mathbf{\theta}}_i \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t}.
+%\tilde{\mathbf{\phi}}_i \indep \tilde{\mathbf{\theta}}_i \indep 
+\mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t}.
 \end{align*}
@@
 \begin{array}{l}
- \;\, \Theta = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \tilde{\mathbf{\phi}}_i, \tilde{\mathbf{\theta}}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
-   \Theta_1 = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \tilde{\mathbf{\phi}}_i, \tilde{\mathbf{\theta}}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon  t= 1, \ldots, T_i, i = 1\}
+ \;\, \Theta = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
+   \Theta_1 = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon  t= 1, \ldots, T_i, i = 1\}
 \end{array}\label{parameter} 
 \end{align}
+
+\vspace*{0.5cm}\noindent\textbf{Alternative model formulation}
+
+\vspace*{0.5cm} We now describe the assumed autoregressive models with random effects for which post-shock aggregated estimators are provided. The model $\mc{M}$ is defined as
+\begin{align}
+\mc{M} \colon \begin{array}{l}
+  y_{i,t} =\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j} + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
+  \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i g(t) +  \sum_{j=1}^{\tilde q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{\tilde q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
+  \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \t{\varepsilon}_{i},
+  %\sum_{j=1}^{q_3}\delta_{i,j}'\mbf{x}_{i, T_i^*-j+1}+ \t{\varepsilon}_{i}, 
+\end{array}\label{model-gen}
+\end{align}
+where $g(t)$ is a known or estimable bounded continuous function which does not cross zero and $\lim_{t\to\infty}g(t) = a \in \R$. Let 
+$\mathbf{\phi}_i = (\phi_{i,1},\ldots,\phi_{i,q_1})'$, 
+$\mathbf{\theta}_i = (\theta_{i,1},\ldots,\theta_{i,q_2})'$, 
+$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,\t q_{i,1}})'$, 
+$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i,\t q_{i,2}})'$, 
+$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,q_3})'$, 
+and suppose that the regression coefficients in \eqref{model-gen} have the following hierarchical random effects structure: 
+\begin{align*}
+  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
+  \mathbf{\phi}_i &\simiid \mc{F}_{\mathbf{\phi}} \text{ where } |\phi_{i,j}| < 1, \\
+  \mathbf{\theta}_i &\simiid \mc{F}_{\mathbf{\theta}} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}}}(\theta_i) = \mu_{\mathbf{\theta}}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}}}(\mathbf{\theta}_i)  = \Sigma^2_{\mathbf{\theta}}, \\
+  \mathbf{\delta}_i &\simiid  \mc{F}_{\mathbf{\delta}} \text{ with } \mrm{E}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\mu_{\mathbf{\delta}}, \mrm{Var}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\Sigma_{\mathbf{\delta}}, \\
+\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i,  \\
+\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha}, \\
+  \tilde{\mathbf{\phi}}_{i,j} &= \mu_{\tilde{\mathbf{\phi}}_j} + \lambda_{i,j}, j = 1,\ldots, \t q_{i,1}, \; \text{where} \; \lambda_{i,j} \overset{ind}{\sim} \mathcal{F}_{\lambda}(\x_{i,T_i^*}) \; \text{with} \; |\mu_{\tilde{\mathbf{\phi}}_j}| < 1 \; \text{and} \; |\mu_{\tilde{\mathbf{\phi}}_j} + \lambda_{i,j}| < 1,  \\
+  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots,\t q_{i,2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_i) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_i) = \Sigma^2_\gamma,  \\
+  \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\
+&\eta_i \indep \mathbf{\phi}_i \indep \mathbf{\theta}_i \indep 
+\tilde{\mathbf{\phi}}_i \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \t q_{i,k} \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t},
+\end{align*}
+where the distribution $\mathcal{F}_k(\x_{i,T_i^*})$ is a discrete distribution conditional on $\x_{i,T_i^*}$, $\theta_{i,j} = 0$ for any $q_1 < j \leq \t q_{i,1}$, and $\phi_{i,j} = 0$ for any $q_2 < j \leq \t q_{i,2}$.
+The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}.
+\textbf{Need to carefully show}.
+Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in
+$\mathcal{F}_k(\x_{i,T_i^*})$ and $\mathcal{F}_{\lambda}(\x_{i,T_i^*})$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\x_{i,T_i^*}$.
 

### 2021-08-31 prevalence_testing/postshocktest2021draft.tex
addition of proof

@@
 
+\begin{prop}
+  Let $p_i \sim \mc{D}$ be independent sequence of p-values for $i = 1, \ldots, n+1$ and some distribution $\mc{D}$, where $p_1$ is the p-value of the time series of interest.
+Let  $\alpha$ denote the significance level.
+If $\P(p_1 \leq \alpha) \neq 0.5$, with probability one, the expected misclassification rate for voting in prevalence testing is
+  \begin{align*}
+    \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases} .
+  \end{align*}
+\end{prop}
+
+\begin{proof}
+ Since $\P(p_1 \leq \alpha)\in \reals$, by Strong Law of Large Numbers,
+\begin{align*}
+  \frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha)  
+   \stackrel{a.s.}{\rightarrow}  \P(p_i \leq \alpha) = \P(p_1 \leq \alpha),
+\end{align*}
+which follows from the fact that $p_i$ are i.i.d. Define
+\begin{align*}
+  f \colon [0,1] \mapsto \{0,1\} 
+  \text{ with }
+  f(x) = I(x \geq 0.5).
+\end{align*}
+Let $C(f)$ denote the continuity set of $f$. Suppose that $\P(p_1 \leq  \alpha) \neq 0.5$. In this case, notice that 
+\begin{align*}
+  \P(\P(p_1 \leq  \alpha) \in C(f)) =1.
+\end{align*}
+By Slutsky's Theorem, we have
+\begin{align*}
+  I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  \stackrel{a.s.}{\rightarrow} 
+  I\{ \P(p_1 \leq  \alpha) \geq 0.5\}.
+\end{align*}
+Moreover, note that
+\begin{align*}
+\E \left\{ |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
+  - I( p_1 \leq  \alpha) |\right\}
+  & = \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases} \\
+  & \leq  0.5.
+\end{align*}
+That implies that with probability one, 
+\begin{align*}
+  \E \left\{ \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right|\right\}
+  = \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases}.
+\end{align*}
+That is, with probability one, the expected misclassification rate is as above.
+\end{proof}
+
+\begin{remark}
+  Since indicator functions are bounded in $\mc{L}^2$, by Chebyshev-Rachman Strong Law of Large Numbers, the independence assumption can be relaxed to be that those p-values are uncorrelated.
+\end{remark}
+
 \section{Simulation Setup}

### 2021-08-31 prevalence_testing/postshocktest2021draft.tex
added commentary on new model; added comment to Jileis proof

@@
 \end{align*}
-The model \eqref{model} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}. \textbf{Need to carefully show}.
+The model \eqref{model} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}.
+\textbf{Need to carefully show}.
+In this formulation $f(t)$ represents either a permanent or transient structural change to the time series that results from the shock.
 
@@
 Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in
-$\mathcal{F}_k(\x_{i,T_i^*})$ and $\mathcal{F}_{\lambda}(\x_{i,T_i^*})$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\x_{i,T_i^*}$.
+$\mathcal{F}_k(\x_{i,T_i^*})$ and $\mathcal{F}_{\lambda}(\x_{i,T_i^*})$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha +\delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively.
+
+We see that model \eqref{model-gen} with its accompanying random effects structure is flexible enough to capture changing structural dynamics as well as a mean-shift.
+These dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$.
+Two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|_2$ are expected to experience similar structural changes.
+This makes distance based weighting an attractive avenue.
 
@@
 We want to determine which forecast is appropriate over a horizon while the methods in \cite{lin2021minimizing} were only appropriate in the nowcasting setting in which prediction was only focused on the response immediately following the shock.
+
+\vspace*{0.5cm}\noindent\textbf{Note}: We need to explain what the voting method is, possibly in algorithmic format.
+Also note that the p-values that we obtain are computed using a bootstrap procedure.
+Perhaps an additional proposition that states the performance of these bootstrap p-values would further guarantee reliability.
 

### 2021-09-13 prevalence_testing/postshocktest2021draft.tex
minor changes to model formulation

@@
   y_{i,t} =\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j} + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
-  \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i g(t) +  \sum_{j=1}^{\tilde q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{\tilde q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
+  \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i +  \sum_{j=1}^{q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
   \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \t{\varepsilon}_{i},
@@
 $\mathbf{\theta}_i = (\theta_{i,1},\ldots,\theta_{i,q_2})'$, 
-$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,\t q_{i,1}})'$, 
-$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i,\t q_{i,2}})'$, 
-$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,q_3})'$, 
+$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_{1}})'$, 
+$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i, q_{2}})'$, 
+$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,p})'$, 
 and suppose that the regression coefficients in \eqref{model-gen} have the following hierarchical random effects structure: 
@@
 \t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha}, \\
-  \tilde{\mathbf{\phi}}_{i,j} &= \mu_{\tilde{\mathbf{\phi}}_j} + \lambda_{i,j}, j = 1,\ldots, \t q_{i,1}, \; \text{where} \; \lambda_{i,j} \overset{ind}{\sim} \mathcal{F}_{\lambda}(\x_{i,T_i^*}) \; \text{with} \; |\mu_{\tilde{\mathbf{\phi}}_j}| < 1 \; \text{and} \; |\mu_{\tilde{\mathbf{\phi}}_j} + \lambda_{i,j}| < 1,  \\
-  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots,\t q_{i,2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_i) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_i) = \Sigma^2_\gamma,  \\
-  \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\
+  \tilde{\mathbf{\phi}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1}) \; \text{where} \; |\tilde{\mathbf{\phi}}_{i,j}| < 1,  \\
+  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots, q_{2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_i) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_i) = \Sigma^2_\gamma,  \\
+ % \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\
 &\eta_i \indep \mathbf{\phi}_i \indep \mathbf{\theta}_i \indep 
-\tilde{\mathbf{\phi}}_i \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \t q_{i,k} \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t},
+\tilde{\mathbf{\phi}}_i \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t},
 \end{align*}
-where the distribution $\mathcal{F}_k(\x_{i,T_i^*})$ is a discrete distribution conditional on $\x_{i,T_i^*}$, $\theta_{i,j} = 0$ for any $q_1 < j \leq \t q_{i,1}$, and $\phi_{i,j} = 0$ for any $q_2 < j \leq \t q_{i,2}$.
+where the distribution $\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1})$ exists between -1 and 1 and $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{j,T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{j,T_i^*+1}\| \to 0$.
+%the distribution $\mathcal{F}_k(\x_{i,T_i^*})$ is a discrete distribution conditional on $\x_{i,T_i^*}$, $\theta_{i,j} = 0$ for any $q_1 < j \leq \t q_{i,1}$, and $\phi_{i,j} = 0$ for any $q_2 < j \leq \t q_{i,2}$.
 The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}.
 \textbf{Need to carefully show}.
-Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in
-$\mathcal{F}_k(\x_{i,T_i^*})$ and $\mathcal{F}_{\lambda}(\x_{i,T_i^*})$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha +\delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively.
+Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha + \delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively.
 

### 2021-09-20 prevalence_testing/postshocktest2021draft.tex
added some theoretical arguments; still trying some stuff out

@@
 \newcommand{\Hist}{\mathcal{H}}
+\newcommand{\Prob}{\mathbb{P}}
 \def\mbf#1{\mathbf{#1}} % bold but not italic
@@
 $$
-  \hat y^{i,h}_{1,t} \; \text{and} \; \hat y^{2,h}_{i,t}
+  \hat y^{1,h}_{i,t} \; \text{and} \; \hat y^{2,h}_{i,t}
 $$
@@
 $$
-where $L_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{h,j})$, $j = 1,2$, and $L$ is a loss function.
+where $\L_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function.
 Hypothesis tests in \cite{quaedvlieg2021multi} are with respect to $E(\dbf_{i,t}) = \mbf\mu_{i,t}$.
@@
 $$
-  \mu^{(AVG)} = \textbf{w}^T\mathbf{\mu} = \sum_{h=1}^H w_h \mu^h
+  \mu^{(\text{Avg})}_i = \textbf{w}_i'\mathbf{\mu}_i = \sum_{h=1}^H w_{i,h} \mu_i^h,
 $$
-with weights $\textbf{w}$ that sum to one.
-Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1.
+with weights $\textbf{w}_i$ that sum to one.
+Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu_i^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1.
+
+We consider a simple test for average SPA, based on the weighted-average loss differential. The associated null is
+\begin{equation} \label{test}
+	H_{i,\text{aSPA}}^0: \mu^{(\text{Avg})}_i \leq 0.
+\end{equation}
+A studentized test statistic corresponding to the null hypothesis \eqref{test} is of the form 
+\begin{equation} \label{tstat}
+	t_{i,\text{aSPA}} = \frac{\sqrt{T}_i\bar{d}_{i}}{\hat{\zeta}_{i}},
+\end{equation}
+where $\bar{d}_{i} = \textbf{w}_i'\textbf{d}_{i}$ and we choose to estimate $\zeta_{i} = \sqrt{\textbf{w}_i'\Omega_{i}\textbf{w}_i}$ directly based on $\textbf{w}_i'\textbf{d}_{i,t}$ using the HAC estimator \citep{giacomini2006tests} where $\Omega_{i} = \text{avar}\left(\sqrt{T}_i(\bar{d}_{i} - \mbf{\mu}_{i})\right)$.
 
@@
 \begin{align*}
-  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
+  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = \mu_\eta, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
   \mathbf{\phi}_i &\simiid \mc{F}_{\mathbf{\phi}} \text{ where } |\phi_{i,j}| < 1, \\
@@
 \mc{M} \colon \begin{array}{l}
-  y_{i,t} =\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j} + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
+  y_{i,t} = \left(\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j}\right)(1 - D_{i,t}) + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
   \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i +  \sum_{j=1}^{q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
-  \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \t{\varepsilon}_{i},
+  \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
   %\sum_{j=1}^{q_3}\delta_{i,j}'\mbf{x}_{i, T_i^*-j+1}+ \t{\varepsilon}_{i}, 
@@
 and suppose that the regression coefficients in \eqref{model-gen} have the following hierarchical random effects structure: 
-\begin{align*}
-  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = 0, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
-  \mathbf{\phi}_i &\simiid \mc{F}_{\mathbf{\phi}} \text{ where } |\phi_{i,j}| < 1, \\
-  \mathbf{\theta}_i &\simiid \mc{F}_{\mathbf{\theta}} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}}}(\theta_i) = \mu_{\mathbf{\theta}}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}}}(\mathbf{\theta}_i)  = \Sigma^2_{\mathbf{\theta}}, \\
+\begin{equation} \label{random-effects}
+\begin{split}
+  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = \mu_\eta, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
+  \mathbf{\phi}_{i,j} &\simiid \mc{F}_{\mathbf{\phi}_j} \text{ where } |\phi_{i,j}| < 1, \\
+  \mathbf{\theta}_{i,j} &\simiid \mc{F}_{\mathbf{\theta}_j} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}_j}}(\theta_{i,j}) = \mu_{\mathbf{\theta}_j}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}_j}}(\mathbf{\theta}_{i,j})  = \Sigma^2_{\mathbf{\theta}_j}, \\
   \mathbf{\delta}_i &\simiid  \mc{F}_{\mathbf{\delta}} \text{ with } \mrm{E}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\mu_{\mathbf{\delta}}, \mrm{Var}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\Sigma_{\mathbf{\delta}}, \\
 \varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i,  \\
-\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha}, \\
-  \tilde{\mathbf{\phi}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1}) \; \text{where} \; |\tilde{\mathbf{\phi}}_{i,j}| < 1,  \\
-  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots, q_{2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_i) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_i) = \Sigma^2_\gamma,  \\
+\varepsilon_{\alpha, i} &\simiid  \mc{F}_{\varepsilon_\alpha} \text{ with }\mrm{E}_{\mc{F}_{\varepsilon_\alpha}}(\varepsilon_{\alpha, i})=0, \mrm{Var}_{\mc{F}_{\varepsilon_{\alpha}}}(\varepsilon_{\alpha, i})=\sigma^2_{\alpha}, \\
+  \tilde{\mathbf{\phi}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\phi}_j}}(\x_{i,T_i^*+1}) \; \text{where} \; |\tilde{\mathbf{\phi}}_{i,j}| < 1,  \\
+  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots, q_{2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_{i,j}) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_{i,j}) = \Sigma^2_\gamma,  \\
  % \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\
-&\eta_i \indep \mathbf{\phi}_i \indep \mathbf{\theta}_i \indep 
-\tilde{\mathbf{\phi}}_i \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t},
-\end{align*}
-where the distribution $\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1})$ exists between -1 and 1 and $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{j,T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{j,T_i^*+1}\| \to 0$.
+&\eta_i \indep \mathbf{\phi}_{i,j} \indep \mathbf{\theta}_{i,j} \indep 
+\tilde{\mathbf{\phi}}_{i,j} \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i}, 
+\end{split}
+\end{equation}
+where the distribution $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ exists between -1 and 1 and $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{j,T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{j,T_i^*+1}\| \to 0$.
 %the distribution $\mathcal{F}_k(\x_{i,T_i^*})$ is a discrete distribution conditional on $\x_{i,T_i^*}$, $\theta_{i,j} = 0$ for any $q_1 < j \leq \t q_{i,1}$, and $\phi_{i,j} = 0$ for any $q_2 < j \leq \t q_{i,2}$.
@@
 
+\vspace*{0.5cm}\noindent\textbf{Possible theoretical approach}: \\
+
+Let $l$ be the block length of the moving block bootstrap (MBB) where we assume that $T_i = lK_i$.
+Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
+$$
+  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
+$$
+The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.
+
+\begin{equation} \label{whb}
+	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{K_i}\sum_{k=1}^{K_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
+\end{equation}
+where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
+\begin{equation} \label{boott}
+  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
+  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
+  \Big\vert \overset{P}{\longrightarrow} 0,
+\end{equation}
+as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
+$$
+  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
+$$
+The results \eqref{boott} implies that 
+\begin{equation} \label{bootp}
+  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
+\end{equation}
+    where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$.
+Therefore bootstrap inference in the donor pool is a good approximation.
+%We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.
+
+\vspace*{0.5cm}\noindent\textbf{This needs some work (ignore for now)} Now consider a case where there exists a $2 \leq i' < n + 1$ where $\x_{1,t} = \x_{i',t}$.
+Now suppose for simplicity that $T^*_{j'} = T^*_1$ and that $T_{i'} = T_1$ where $T_1 > T^*_1 + q_1 + q_2 + 2$.
+This assumes that we have data for the first time series beyond the shock point.
+We will show that when there is a covariate clone of the time series under study, then estimation in this series will approximate estimation in the time series under study provided that the underlying variability is very small relative to the signal.
+To see this, consider $t > T^*_1$, where
+\begin{align*}
+y_{1,t} &= \eta_1 + \mu_\alpha + \delta_1'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} + \sum_{j=0}^{q_2-1}(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{1} + \varepsilon_{1,t}, \\
+y_{i',t} &= \eta_{i'} + \mu_\alpha + \delta_{i'}'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} + \sum_{j=0}^{q_2-1}(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{i'} + \varepsilon_{i',t}, \\
+\hat y_{1,t} &= \hat \eta_1 + \hat{\alpha}_1(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat y_{1,t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}, \\
+\hat y_{i',t} &= \hat\eta_{i'} + \hat{\alpha}_{i'}(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat y_{i',t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j},
+\end{align*}
+where $\alpha_j(\x) = \mu_\alpha + \delta_j'\x$, and we have 
+\begin{align*}
+  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\left] \\
+  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} - (\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{1,t} \Bigg\vert \\
+  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\left] \\
+  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} - (\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{i',t} \Bigg\vert.
+\end{align*}
+\textbf{Needs finishing, but the argument is simple: estimation uncertainty declines as error variance decreases.
+And differences in the random effects decrease as variability decreases.} \vspace*{0.5cm}
+
+\vspace*{0.5cm} We now demonstrate an idealized setting in which the above logic holds.
+We first present some intermediary technical results and definitions.
+Let $\lambda_{\text{max},\theta_k}$, $\lambda_{\text{max},\theta_\delta}$, $\lambda_{\text{max},\gamma}$ respectively be the largest eigenvalues of $\Sigma_{\theta_k}$, $\Sigma_{\delta}$, and $\Sigma_{\gamma}$ for $k = 1,\ldots,q_2$.
+Define
+\begin{align*}
+  \mu_{\min} &= \min\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\min(\mu_\delta),\min(\mu_{\theta_k}),\min(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
+  \mu_{\max} &= \max\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\max(\mu_\delta),\max(\mu_{\theta_k}),\max(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
+  \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
+  \sigma^2_\max &= \max\left(\sigma^2_\eta,\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_\alpha,\sigma^2_{\tilde\phi_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right).  
+\end{align*}
+
+\begin{prop}
+	Let $\bf{y}_{i,t}$, $i = 1,\ldots,n_i$, $t = 1,\ldots, T$ be a collection of independent time series.
+Let each time series $\bf{y}_{i,t}$ be generated by model \eqref{model-gen} with accompanying random effects structure \eqref{random-effects}, where $y_{i,t}$ is a scalar response $\x_{i,t} \in \R^p$ is a fixed vector of covariates.
+Suppose that there is a common shock time $p + 2 < T^* < T - (p+2)$ where $q_1 = q_2 = 1$, $\|\x_{i,t}\| = 1$ where each entry of $\x_{i,t}$ is non-negative, $\mu_{\min} > 0$, and $y_{i,0} = 0$.
+Then for every $1 \leq t \leq T$ and every $C > 0$ we have that
+	\begin{equation} \label{signal-to-noise}
+	  \E(y_{i,t}) \geq C\Var(y_{i,t}),	
+	\end{equation}
+	provided that 
+	\begin{equation} \label{condition-1}
+	\begin{split}
+		\mu_\alpha + 3\mu_{\min} &\geq C\left(3\sigma^2_{\max} + 2\lambda_{\max}\right), \\
+		2\mu_{\min} &\geq C\left(2\sigma^2_{\max} + \lambda_{\max}\right).	
+	\end{split}
+	\end{equation}
+\end{prop}
+
+\begin{proof}
+For $t > T^* + 1$ we have 
+\begin{align*}
+  \E(y_{i,t}) &= \E\left[\E(y_{i,t}|y_{i,t-1})\right] \\ 
+    &= \E\left[\E(\eta_i + \alpha_i + \tilde\phi_i y_{i,t-1} 
+      + \tilde\theta_i'\x_{i,t}|y_{i,t-1})\right] \\
+    &= \E(\eta_i + \mu_\alpha + \delta_i'\x_{i,T^*+1} + \tilde\phi_i y_{i,t-1} + \tilde\theta_i'\x_{i,t}) \\
+    &= \mu_\eta + \mu_\alpha + \mu_\delta'\x_{i,T^*+1} + \mu_{\tilde\theta}'\x_{i,t} + \mu_{\tilde\phi}\E(y_{i,t-1}) \\
+    &\geq (\mu_\alpha + 3\mu_{\min}) + \mu_{\min}\E(y_{i,t-1}) \\
+    &\geq \sum_{j=1}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\E(y_{i,T^*}) \\
+    &= \sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(\E\left[\E(y_{i,T^*}|y_{i,T^*-1})\right]\right) \\   
+    &= \sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(\E(\eta_i + \theta_i'\x_{i,T^*} + \phi_i y_{i,T^*-1}) \right) \\
+    &\geq \sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(2\mu_{\min} + \mu_{\min} \E(y_{i,T^*-1}) \right) \\
+    &\geq \sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(\sum_{j=0}^{T^*-1}\mu_{\min}^j(2\mu_{\min}) \right), 
+\end{align*}
+and 
+\begin{align*}
+  \Var(y_{i,t})	&= \E\left[\Var(y_{i,t}|y_{i,t-1})\right] + \Var\left[\E(y_{i,t}|y_{i,t-1})\right] \\
+  &= \E\left[\Var(\eta_i + \mu_\alpha + \delta_i'\x_{i,T^*+1} + \tilde\theta_i'\x_{i,t} + \tilde\phi_i y_{i,t-1} + \varepsilon_{i,t} + \varepsilon_{\alpha,i}|y_{i,t-1})\right] \\
+  &+ \Var\left[\E(\eta_i + \mu_\alpha + \delta_i'\x_{i,T^*+1} + \tilde\theta_i'\x_{i,t} + \tilde\phi_i y_{i,t-1} + \varepsilon_{i,t} + \varepsilon_{\alpha,i}|y_{i,t-1})\right] \\
+  &\leq 3\sigma^2_{\max} + 2\lambda_{\max} + \Var\left[\E(\tilde\phi_i y_{i,t-1}|y_{i,t-1})\right] \\
+  &= 3\sigma^2_{\max} + 2\lambda_{\max} + \mu_{\tilde\phi}^2\Var(y_{i,t-1}) \\
+  &\leq \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\Var(y_{i,T^*}) \\
+  &= \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\E\left[\Var(y_{i,T^*}|y_{i,T^*-1})\right] + \Var\left[\E(y_{i,T^*}|y_{i,T^*-1})\right]\right) \\
+  &= \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\E\left[\Var(\eta_i + \theta_i'\x_{i,T^*} + \phi_iy_{i,T^*-1} + \varepsilon_{i,T^*}|y_{i,T^*-1})\right] \right.
+\\
+  &\qquad+  \left.\Var\left[\E(\eta_i + \theta_i'\x_{i,T^*} + \phi_iy_{i,T^*-1} + \varepsilon_{i,T^*}|y_{i,T^*-1})\right]\right)  \\
+  &\leq \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(2\sigma^2_{\max} + \lambda_{\max} + \mu_{\phi}^2\Var(y_{i,T^*-1}) \right) \\
+  &\leq \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right).
+\end{align*}
+Combining the above with the condition \eqref{condition-1} yields 
+\begin{align*}
+  \frac{\E(y_{i,t})}{\Var(y_{i,t})} &\geq \frac{\sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(\sum_{j=0}^{T^*-1}\mu_{\min}^j(2\mu_{\min}) \right)}{\sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right)} \\
+  &\geq \frac{C\sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + C(\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right)}{\sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right)} \\
+  &= C.
+\end{align*}
+\end{proof}
+
+%Let 
+%$$
+%  \rho_\text{min} = \min\left\{
+%    \frac{\mu_\eta}{\sigma^2_\eta}, 
+%    \frac{\|\mu_{\delta}\|}{\|\Sigma_\delta\|},
+%    \frac{\|\mu_{\theta}\|}{\|\Sigma_\theta\|},
+%    \frac{\|\mu_{\phi}\|}{\|\Sigma_\phi\|},
+%    \frac{\|\mu_{\tilde\theta}\|}{\|\Sigma_{\tilde{\theta}}\|},
+%    \frac{\|\mu_{\tilde\phi}\|}{\|\Sigma_{\tilde{\phi}}\|}             
+%  \right\},
+%$$
+%and let
+%$$
+%  \rho_\text{max} = \max\left\{
+%    \frac{\mu_\eta}{\sigma^2_\eta}, 
+%    \frac{\|\mu_{\delta}\|}{\|\Sigma_\delta\|},
+%    \frac{\|\mu_{\theta}\|}{\|\Sigma_\theta\|},
+%    \frac{\|\mu_{\phi}\|}{\|\Sigma_\phi\|},
+%    \frac{\|\mu_{\tilde\theta}\|}{\|\Sigma_{\tilde{\theta}}\|},
+%    \frac{\|\mu_{\tilde\phi}\|}{\|\Sigma_{\tilde{\phi}}\|}             
+%  \right\}.
+%$$
+
 \section{Simulation Setup}
@@
 \bibliographystyle{plainnat}
-\bibliography{../synthetic-prediction-notes}
+\bibliography{synthetic-prediction-notes}
+%\bibliography{../synthetic-prediction-notes}
 

### 2021-10-14 prevalence_testing/postshocktest2021draft.tex
small changes
updated theoretical arguments

@@
 
-\begin{prop}
+\begin{prop} \label{prop:signaltonoise}
 	Let $\bf{y}_{i,t}$, $i = 1,\ldots,n_i$, $t = 1,\ldots, T$ be a collection of independent time series.
 Let each time series $\bf{y}_{i,t}$ be generated by model \eqref{model-gen} with accompanying random effects structure \eqref{random-effects}, where $y_{i,t}$ is a scalar response $\x_{i,t} \in \R^p$ is a fixed vector of covariates.
-Suppose that there is a common shock time $p + 2 < T^* < T - (p+2)$ where $q_1 = q_2 = 1$, $\|\x_{i,t}\| = 1$ where each entry of $\x_{i,t}$ is non-negative, $\mu_{\min} > 0$, and $y_{i,0} = 0$.
-Then for every $1 \leq t \leq T$ and every $C > 0$ we have that
+Suppose that there is a common shock time $p + 2 < T^* < T - (p+2)$ where $q_1 = q_2 = 1$, $\|\x_{i,t}\| = 1$, each entry of $\x_{i,t}$ is non-negative, $\mu_{\min} > 0$, and $y_{i,0} = 0$.
+Then for every $1 \leq t \leq T$ we have that
 	\begin{equation} \label{signal-to-noise}
@@
 \end{prop}
+
+\textbf{Remarks}:
+\begin{enumerate}
+	\item The conditions \eqref{condition-1} govern the signal strength necessary in the expected behavior of the underlying random effects structure relative to variability necessary for the overall signal to noise ratio for the overall time series to be lower bounded by some positive value $C$.
+	\item The conditions of Proposition~\ref{prop:signaltonoise} state that there is an increasing trend in $y_{i,t}$ for all $i$.
+\end{enumerate}
 
@@
   &\geq \frac{C\sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + C(\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right)}{\sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right)} \\
-  &= C.
+  &= C,
+\end{align*}
+for all $i$ and $t$. A similar argument holds when $t \leq T^* + 1$.
+\end{proof}
+
+\begin{lem}[Technical Lemma 1] \label{lem1}
+	Let $a_j, b_j \in \R$, $j = 1,2$, and $C > 0$ be such that $C \leq a_j/b_j \leq 2C$, $j = 1,2$. Further suppose that 
+	$$
+	  \frac{|a_1 - a_2|}{a_1 + a_2} < \frac{\varepsilon}{2C},
+	$$
+	for some $\varepsilon > 0$. Then 
+	$$
+	  \frac{|a_1 - a_2|}{b_1 + b_2} < \varepsilon.
+	$$
+\end{lem}
+
+\begin{proof}
+Observe that 
+$$
+  |a_1 - a_2| < \frac{\varepsilon(a_1 + a_2)}{2C} 
+	  = \frac{\varepsilon(b_1(a_1/b_1) + b_2(a_2/b_2))}{2C} 
+	  \leq \frac{\varepsilon(2b_1C + 2b_2C)}{2C} 
+	  = \varepsilon(b_1 + b_2).
+$$
+The conclusion immediately follows from the above.
+\end{proof}
+
+\begin{lem}[Technical Lemma 2] \label{lem2}
+Let $a_j, b_j \in \R$, $j = 1,2$ be such that $0 < a_1,a_2 < 1$, $b_1,b_2 > 0$. Let $c_1 = \max(a_1,a_2)$, $c_2 = \min(a_1,a_2)$, $d_1 = \max(b_1,b_2)$, $d_2 = \min(b_1,b_2)$. Then, 
+$$
+  |a_1b_1 - a_2b_2| \leq |a_1 - a_2|d_1 + |b_1 - b_2|c_2.
+$$
+\end{lem}
+
+\begin{proof}
+Observe that 
+$$
+  |a_1b_1 - a_2b_2| \leq c_1d_1 - c_2d_2 = (c_1 - c_2)d_1 + (d_1 - d_2)c_2. 
+$$
+The conclusion follows by noting that $c_1 - c_2 = |a_1 - a_2|$ and $d_1 - d_2 = |b_1 - b_2|$.
+\end{proof}
+
+\begin{prop} \label{prop:signaltonoisediff}
+	Suppose the conditions of Proposition~\ref{prop:signaltonoise} where $C$ is chosen so that 
+	\begin{equation} \label{signal-to-noise2}
+	  C \leq \frac{\E(y_{i,t})}{\Var(y_{i,t})} \leq 2C,
+	\end{equation}
+	for all $i$ and $1 \leq t \leq T$. Let $2 < i' < n + 1$ be the index of a time series in the donor pool for which CONDITIONS then for some $\varepsilon > 0$ we have 
+	$$
+	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\Var(y_{i,t} - y_{i',t})} < \varepsilon
+	$$
+\end{prop}
+
+\begin{proof}
+	First suppose that we have 
+	\begin{equation} \label{prop:cond}
+	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\E(y_{i,t} + y_{i',t})} \leq \frac{\varepsilon}{2C}.		
+	\end{equation}
+	Then Lemma~\ref{lem2} combined with the assumed conditions imply the conclusion of this proposition. We now verify that \eqref{prop:cond} holds.
+
+	For $t > T^* + 1$ a similar recursion in the proof of Proposition~\ref{prop:signaltonoise} yields 
+	\begin{align*}
+		&\E(y_{i,t} - y_{i',t}) = \E\left( \delta_i'\x_{i,T^*+1} + \tilde\theta_i'\x_{i,T^*+1} + \tilde\phi_i y_{i,t-1} - (\delta_{i'}'\x_{i',T^*+1} + \tilde\theta_{i'}'\x_{i',T^*+1} + \tilde\phi_{i'} y_{i',t-1}) \right) \\
+		&\qquad= \mu_\delta'\x_{i,T^*+1} + \mu_{\tilde\theta_i}'\x_{i,T^*+1} + \mu_{\tilde\phi_i} \E(y_{i,t-1}) - (\mu_\delta'\x_{i',T^*+1} + \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1} + \mu_{\tilde\phi_{i'}}\E(y_{i',t-1})) \\
+		&\qquad= \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
+		&\qquad\qquad + \mu_{\tilde\phi_{i}}^{t - T^*}\E(y_{i,T^*}) - \mu_{\tilde\phi_{i'}}^{t - T^*}\E(y_{i',T^*}) \\
+		&\qquad= \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
+		&\qquad\qquad + \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{i}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{i}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j})\right)\mu_{\phi}^j\right].
+	\end{align*}
+Similarly, 
+\begin{align*}
+	&\E(y_{i,t} + y_{i',t}) = \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
+		&\qquad + \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{i}}^{t - T^*} + \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{i}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j}) + \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j})\right)\mu_{\phi}^j\right].
 \end{align*}

### 2021-10-21 prevalence_testing/postshocktest2021draft.tex
addition of proposition

@@
 \begin{prop}
-  Let $p_i \sim \mc{D}$ be independent sequence of p-values for $i = 1, \ldots, n+1$ and some distribution $\mc{D}$, where $p_1$ is the p-value of the time series of interest.
-Let  $\alpha$ denote the significance level.
-If $\P(p_1 \leq \alpha) \neq 0.5$, with probability one, the expected misclassification rate for voting in prevalence testing is
+
+Suppose $p_1, \ldots, p_{n+1}$ be a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest.
+If $\P(p_1 \leq \alpha) \neq 0.5$,
+\begin{align*}
+  \E \bigg\{\left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right|\bigg\}
+  \to  \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases}
+\end{align*}
+That is, as $n\to \infty$, the expected misclassification rate of voting converges to 
 \begin{align*}
@@
     \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
-  \end{cases} .
+  \end{cases}
 \end{align*}
+and the limiting misclassification rate is bounded by 0.5.
 \end{prop}
@@
 \begin{proof}
- Since $\P(p_1 \leq \alpha)\in \reals$, by Strong Law of Large Numbers,
+Notice that as $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$ and $I(p_i \leq  \alpha) $ is a Bernoulli random variable, $I(p_i \leq  \alpha)$ is identically distributed for  $i = 1, \ldots, n+1$.
+Since $p_i$ is pairwise independent and $p_i$ are identically distributed for $i = 2, \ldots, n+1$, by Weak Law of Large Numbers,
 \begin{align*}
   \frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha)  
-   \stackrel{a.s.}{\rightarrow}  \P(p_i \leq \alpha) = \P(p_1 \leq \alpha),
+   \stackrel{p}{\rightarrow}  \P(p_i \leq \alpha) = \P(p_1 \leq \alpha),
 \end{align*}
-which follows from the fact that $p_i$ are i.i.d. Define
+Define
 \begin{align*}
@@
   I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
-  \stackrel{a.s.}{\rightarrow} 
+  \stackrel{p}{\rightarrow} 
   I\{ \P(p_1 \leq  \alpha) \geq 0.5\}.
+\end{align*}
+It follows that
+\begin{align*}
+   I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}- I( p_1 \leq  \alpha) 
+  \stackrel{p}{\rightarrow} 
+  I\{ \P(p_1 \leq  \alpha) \geq 0.5\} - I( p_1 \leq  \alpha) 
+\end{align*}
+Since the function $g(x)= |x|$ is continuous in $x$,  by continuous mapping theorem, 
+\begin{align*}
+  \bigg|  I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \bigg| \stackrel{p}{\rightarrow}   |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
+  - I( p_1 \leq  \alpha) |
 \end{align*}
@@
 \end{align*}
-That implies that with probability one, 
+Due to the fact that
 \begin{align*}
-  \E \left\{ \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
-  - I( p_1 \leq  \alpha) \right|\right\}
-  = \begin{cases}
+ \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right| \leq 1
+\end{align*}
+is bounded by 1, by Dominated Convergence Theorem for the version of convergence in measure,
+\begin{align*}
+ \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right|
+  \stackrel{\mathcal{L}_1}{\rightarrow}  |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
+  - I( p_1 \leq  \alpha) |.
+\end{align*}
+That would imply that 
+\begin{align*}
+  \E \bigg\{\left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right|\bigg\}
+  \to  \begin{cases}
     1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
     \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
-  \end{cases}.
+  \end{cases}
 \end{align*}
-That is, with probability one, the expected misclassification rate is as above.
+That is, the expected misclassification rate of voting converges to 
+\begin{align*}
+  \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases}
+\end{align*}
 \end{proof}
-
-\begin{remark}
-  Since indicator functions are bounded in $\mc{L}^2$, by Chebyshev-Rachman Strong Law of Large Numbers, the independence assumption can be relaxed to be that those p-values are uncorrelated.
-\end{remark}
 

### 2021-10-28 prevalence_testing/postshocktest2021draft.tex
updated theoretical argument for boundinf of expectations

@@
 \end{align*}
-That is, as $n\to \infty$, the expected misclassification rate of voting converges to 
-\begin{align*}
-  \begin{cases}
-    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
-    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
-  \end{cases}
-\end{align*}
-and the limiting misclassification rate is bounded by 0.5.
+%That is, as $n\to \infty$, the expected misclassification rate of voting converges to 
+%\begin{align*}
+%  \begin{cases}
+%    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+%    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+%  \end{cases}
+%\end{align*}
+%and the limiting misclassification rate is bounded by 0.5.
 \end{prop}
@@
 
-\begin{lem}[Technical Lemma 1] \label{lem1}
-	Let $a_j, b_j \in \R$, $j = 1,2$, and $C > 0$ be such that $C \leq a_j/b_j \leq 2C$, $j = 1,2$. Further suppose that 
-	$$
-	  \frac{|a_1 - a_2|}{a_1 + a_2} < \frac{\varepsilon}{2C},
-	$$
-	for some $\varepsilon > 0$. Then 
-	$$
-	  \frac{|a_1 - a_2|}{b_1 + b_2} < \varepsilon.
-	$$
-\end{lem}
-
-\begin{proof}
-Observe that 
-$$
-  |a_1 - a_2| < \frac{\varepsilon(a_1 + a_2)}{2C} 
-	  = \frac{\varepsilon(b_1(a_1/b_1) + b_2(a_2/b_2))}{2C} 
-	  \leq \frac{\varepsilon(2b_1C + 2b_2C)}{2C} 
-	  = \varepsilon(b_1 + b_2).
-$$
-The conclusion immediately follows from the above.
-\end{proof}
-
-\begin{lem}[Technical Lemma 2] \label{lem2}
+\begin{lem}[Technical Lemma 1] \label{lem:absdiff}
 Let $a_j, b_j \in \R$, $j = 1,2$ be such that $0 < a_1,a_2 < 1$, $b_1,b_2 > 0$. Let $c_1 = \max(a_1,a_2)$, $c_2 = \min(a_1,a_2)$, $d_1 = \max(b_1,b_2)$, $d_2 = \min(b_1,b_2)$. Then, 
@@
 
-\begin{prop} \label{prop:signaltonoisediff}
-	Suppose the conditions of Proposition~\ref{prop:signaltonoise} where $C$ is chosen so that 
-	\begin{equation} \label{signal-to-noise2}
-	  C \leq \frac{\E(y_{i,t})}{\Var(y_{i,t})} \leq 2C,
-	\end{equation}
-	for all $i$ and $1 \leq t \leq T$. Let $2 < i' < n + 1$ be the index of a time series in the donor pool for which CONDITIONS then for some $\varepsilon > 0$ we have 
+\begin{prop}
+	Let $\bf{y}_{i,t}$, $i = 1,\ldots,n_i$, $t = 1,\ldots, T$ be a collection of independent time series.
+Let each time series $\bf{y}_{i,t}$ be generated by model \eqref{model-gen} with accompanying random effects structure \eqref{random-effects}, where $y_{i,t}$ is a scalar response $\x_{i,t} \in \R^p$ is a fixed vector of covariates.
+Suppose that there is a common shock time $p + 2 < T^* < T - (p+2)$ where $q_1 = q_2 = 1$, $\|\x_{i,t}\| = 1$, each entry of $\x_{i,t}$ is non-negative, $\mu_{\min} > 0$, and $y_{i,0} = 0$.
+Let $i' \geq 2$ be an index.
+Then, for any $\epsilon > 0$ we can choose an $\gamma > 0$ such that
 	$$
-	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\Var(y_{i,t} - y_{i',t})} < \varepsilon
+	  \left\vert\E(y_{i,t} - y_{i',t})\right\vert \leq \epsilon,
 	$$
+	provided that 
+	\begin{align*}
+  |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| &< \gamma, \\
+  |\mu_{\tilde\theta_1}'\x_{1,T^*+1} - \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1}| &< \gamma, \\
+  \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}\right\vert &< \gamma, \qquad \text{for all} \; t, \\
+  |\mu_{\tilde\phi_1}^j - \mu_{\tilde\phi_{i'}}^j| &< \gamma, \qquad \text{for all} \; j. 
+	\end{align*}
 \end{prop}
@@
 \begin{proof}
-	First suppose that we have 
-	\begin{equation} \label{prop:cond}
-	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\E(y_{i,t} + y_{i',t})} \leq \frac{\varepsilon}{2C}.		
-	\end{equation}
-	Then Lemma~\ref{lem2} combined with the assumed conditions imply the conclusion of this proposition. We now verify that \eqref{prop:cond} holds.
+A similar recursion to that seen in the proof of Proposition~\ref{prop:signaltonoise} yields
+\begin{align*}
+	&|\E(y_{1,t} - y_{i',t})| =  \left\vert \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{1}}^j(\mu_\delta'\x_{1,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{1}}^j(\mu_{\tilde\theta_{1}}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',t-j})\right]\right.
+\\
+		&\qquad\qquad\left.
++ \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j})\right)\mu_{\phi}^j\right]\right\vert \\
+	&\qquad\leq |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| 
+	  + \sum_{j=1}^{t - (T^*+1)}\left\vert\mu_{\tilde\phi_{1}}^j(\mu_\delta'\x_{1,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right\vert \\ 
+	&\qquad\qquad+ |\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}| + \sum_{j=1}^{t - (T^*+1)}\left\vert \mu_{\tilde\phi_{1}}^j(\mu_{\tilde\theta_{1}}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',t-j})\right\vert \\
+	&\qquad\qquad + \mu_\eta\sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j \\
+	&\qquad\leq |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| + |\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}| \\
+	&\qquad\qquad + \sum_{j=1}^{t - (T^*+1)}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,T^*+1},\mu_\delta'\x_{i',T^*+1}) + \left\vert\mu_\delta'\x_{1,T^*+1} -\mu_\delta'\x_{i',T^*+1}\right\vert\mu_{\tilde\phi_{1}}^j\right] \\
+	&\qquad\qquad + \sum_{j=1}^{t - (T^*+1)}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,t-j},\mu_\delta'\x_{i',t-j}) + \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t-j} - \mu_{\tilde\theta_{i'}}'\x_{i',t-j}\right\vert\mu_{\tilde\phi_{1}}^j\right] \\
+	&\qquad\qquad + \mu_\eta\sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j,
+\end{align*}
+where the second inequality follows from applications of Lemma~\ref{lem:absdiff}. Continuing from the second inequality, the conditions of this proposition imply that
+\begin{align*}
+  &|\E(y_{1,t} - y_{i',t})|	\\
+  &\qquad\leq 2\gamma + \sum_{j=1}^{\infty}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,T^*+1},\mu_\delta'\x_{i',T^*+1}) + \gamma\mu_{\tilde\phi_{1}}^j\right] \\
+  &\qquad\qquad + \sum_{j=1}^{\infty}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,t-j},\mu_\delta'\x_{i',t-j}) + \gamma\mu_{\tilde\phi_{1}}^j\right] \\
+  &\qquad\qquad + \mu_\eta\sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j  \\
+  &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} \\
+  &\qquad\qquad + \mu_\eta\sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j \\
+  &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} + \gamma\frac{\mu_{\eta}}{1 - \mu_{\phi}} + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j \\
+  &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} + \gamma\frac{\mu_{\eta}}{1 - \mu_{\phi}} + \gamma\frac{\max(\mu_\theta) + 1}{1 - \mu_\phi},
+\end{align*}  
+where the last inequality follows from Lemma~\ref{lem:absdiff}. We can choose $\gamma$ small enough so that $|\E(y_{1,t} - y_{i',t})| < \varepsilon$.
+\end{proof}
 
-	For $t > T^* + 1$ a similar recursion in the proof of Proposition~\ref{prop:signaltonoise} yields 
-	\begin{align*}
-		&\E(y_{i,t} - y_{i',t}) = \E\left( \delta_i'\x_{i,T^*+1} + \tilde\theta_i'\x_{i,T^*+1} + \tilde\phi_i y_{i,t-1} - (\delta_{i'}'\x_{i',T^*+1} + \tilde\theta_{i'}'\x_{i',T^*+1} + \tilde\phi_{i'} y_{i',t-1}) \right) \\
-		&\qquad= \mu_\delta'\x_{i,T^*+1} + \mu_{\tilde\theta_i}'\x_{i,T^*+1} + \mu_{\tilde\phi_i} \E(y_{i,t-1}) - (\mu_\delta'\x_{i',T^*+1} + \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1} + \mu_{\tilde\phi_{i'}}\E(y_{i',t-1})) \\
-		&\qquad= \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
-		&\qquad\qquad + \mu_{\tilde\phi_{i}}^{t - T^*}\E(y_{i,T^*}) - \mu_{\tilde\phi_{i'}}^{t - T^*}\E(y_{i',T^*}) \\
-		&\qquad= \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
-		&\qquad\qquad + \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{i}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{i}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j})\right)\mu_{\phi}^j\right].
-	\end{align*}
-Similarly, 
-\begin{align*}
-	&\E(y_{i,t} + y_{i',t}) = \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
-		&\qquad + \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{i}}^{t - T^*} + \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{i}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j}) + \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j})\right)\mu_{\phi}^j\right].
-\end{align*}
-\end{proof}
+%\begin{lem}[Technical Lemma 2] \label{lem1}
+%	Let $a_j, b_j \in \R$, $j = 1,2$, and $C > 0$ be such that $C \leq a_j/b_j \leq 2C$, $j = 1,2$. Further suppose that 
+%	$$
+%	  \frac{|a_1 - a_2|}{a_1 + a_2} < \frac{\varepsilon}{2C},
+%	$$
+%	for some $\varepsilon > 0$. Then 
+%	$$
+%	  \frac{|a_1 - a_2|}{b_1 + b_2} < \varepsilon.
+%	$$
+%\end{lem}
+
+%\begin{proof}
+%Observe that 
+%$$
+%  |a_1 - a_2| < \frac{\varepsilon(a_1 + a_2)}{2C} 
+%	  = \frac{\varepsilon(b_1(a_1/b_1) + b_2(a_2/b_2))}{2C} 
+%	  \leq \frac{\varepsilon(2b_1C + 2b_2C)}{2C} 
+%	  = \varepsilon(b_1 + b_2).
+%$$
+%The conclusion immediately follows from the above.
+%\end{proof}
+
+%\begin{prop} \label{prop:signaltonoisediff}
+%	Suppose the conditions of Proposition~\ref{prop:signaltonoise} where $C$ is chosen so that 
+%	\begin{equation} \label{signal-to-noise2}
+%	  C \leq \frac{\E(y_{i,t})}{\Var(y_{i,t})} \leq 2C,
+%	\end{equation}
+%	for all $i$ and $1 \leq t \leq T$. Let $2 < i' < n + 1$ be the index of a time series in the donor pool for which CONDITIONS then for some $\varepsilon > 0$ we have 
+%	$$
+%	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\Var(y_{i,t} - y_{i',t})} < \varepsilon
+%	$$
+%\end{prop}
+
+%\begin{proof}
+%	First suppose that we have 
+%	\begin{equation} \label{prop:cond}
+%	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\E(y_{i,t} + y_{i',t})} \leq \frac{\varepsilon}{2C}.		
+%	\end{equation}
+%	Then Lemma~\ref{lem:absdiff} combined with the assumed conditions imply the conclusion of this proposition. We now verify that \eqref{prop:cond} holds.
+%Suppose that:
+%\begin{align*}
+%  |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| &< \gamma \\
+%  |\mu_{\tilde\theta_1}'\x_{1,T^*+1} - \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1}| &< \gamma \\
+%  \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}\right\vert &< \gamma, \qquad \text{for all} \; t \\
+%  |\mu_{\tilde\phi_1}^j - \mu_{\tilde\phi_{i'}}^j| &< \gamma, \qquad \text{for all} \; j \\
+%  \mu_\delta'\x_{1,T^*+1} + \mu_\delta'\x_{i',T^*+1} &> D
+%\end{align*}
+%Similarly, 
+%\begin{align*}
+%	&\E(y_{i,t} + y_{i',t}) = \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
+%		&\qquad + \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{i}}^{t - T^*} + \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{i}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j}) + \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j})\right)\mu_{\phi}^j\right].
+%\end{align*}
+%\end{proof}
 

### 2021-11-01 prevalence_testing/postshocktest2021draft.tex
addition with corollary

@@
 \def\P{\mathbb{P}}
+\def\var{\mathbf{Var}}
+\def\naturals{\mathbb{N}}
+\def\cp{\overset{p}{\to}}
+\def\clt{\overset{\mathcal{L}^2}{\to}}
 
+\newtheorem{corollary}{Corollary}
 \newcommand{\ceil}[1]{\lceil #1 \rceil}
@@
 
-Suppose $p_1, \ldots, p_{n+1}$ be a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest.
+\label{votprop}Suppose $p_2, \ldots, p_{n+1}$ is  a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest.
 If $\P(p_1 \leq \alpha) \neq 0.5$,
@@
 \end{align*}
-%That is, as $n\to \infty$, the expected misclassification rate of voting converges to 
-%\begin{align*}
-%  \begin{cases}
-%    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
-%    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
-%  \end{cases}
-%\end{align*}
-%and the limiting misclassification rate is bounded by 0.5.
 \end{prop}
@@
 
+\begin{lem}
+  \label{gwlln}  For each $n\in \naturals$, let $c_{n1}, \ldots, c_{nn}$ be real numbers bounded by some $K > 0$, and let $X_{n1}, \ldots, X_{nn}$ be pairwise independent random variables defined on a probability space $(\Omega_n, \mc{F}_n, \P_n)$, and let $\E_n$ and $\var_n$ denote the corresponding expectation and variance.
+If $(b_n)$ is a sequence of positive numbers such that $b_n \uparrow \infty$ such that
+    \begin{align*}
+      \sum_{i=1}^n \P_n (|X_{ni}| > b_n) \to 0
+      \quad \text{ and } 
+      \quad \frac{1}{(b_n)^2} \sum_{i=1}^n \E_n[X_{ni}^2; |X_{ni}|\leq b_n] \to 0,
+    \end{align*}
+    then
+    \begin{align*}
+      \frac{1}{b_n} \sum_{i=1}^n c_{ni} (X_{ni} - \E_n[X_{ni}; X_{ni} \leq b_n]) \cp 0.
+    \end{align*}
+\end{lem}
+
+\begin{proof}
+  For each $n\in \naturals$ set
+    \begin{align*}
+      S_n = \sum_{i=1}^n c_{ni} X_{ni}, \quad T_n = \sum_{i=1}^n c_{ni} Y_{ni},
+      \quad Y_{ni} = X_{ni} I(|X_{ni}|\leq b_n), \quad i = 1, \ldots, n.
+    \end{align*}
+   The goal is to show that  $(S_n- \E_n[T_n])/b_n \cp 0$. For this, it suffices to show that (1) $(T_n - S_n)/b_n \cp 0$ and (2) $(T_n - \E_n[T_n])/b_n \cp 0$ because
+    \begin{align*}
+      (T_n - \E_n[T_n])/b_n -(T_n - S_n)/b_n = (S_n- \E_n[T_n])/b_n .
+    \end{align*}
+     We first prove (1). Notice that for every $\varepsilon > 0$ and $n\in \naturals$,
+    \begin{align*}
+      \{|S_n- T_n| > \varepsilon\}\subseteq \bigcup_{i=1}^n \{X_{ni}\neq Y_{ni}\}
+      = \bigcup_{i=1}^n \{|X_{ni}|>b_n\},
+    \end{align*}
+    and, as a result, by Boole's inequality we have
+    \begin{align*}
+      \P_n (|S_n - T_n|>\varepsilon) \leq \sum_{i=1}^n \P_n(|X_{ni}|>b_n) \to 0,
+    \end{align*}
+    which proves (1).
+Next, we prove (2).
+Since $\mc{L}^2$ implies convergence in probability, it suffices to show that $(T_n-\E[T_n])/b_n \clt 0$, i.e., $\var[T_n]/(b_n)^2 \to 0$.
+Since $X_{n1}, \ldots, X_{nn}$ are pairwise independent, so are $Y_{n1}, \ldots, Y_{nn}$, and consequently
+    \begin{align*}
+      \Var_n[T_n]=\sum_{i=1}^n \Var_n[Y_{ni}] \leq \sum_{i=1}^n \E_n[(c_{ni}X_{ni})^2; |X_{ni}|\leq b_n] \leq K^2\sum_{i=1}^n \E_n[(X_{ni})^2; |X_{ni}|\leq b_n].
+    \end{align*}
+    As a result,
+    \begin{align*}
+    0\leq   \frac{\Var_n[T_n]}{b_n^2}\leq K^2 \cdot  \frac{1}{b_n^2}\sum_{i=1}^n \E_n[(X_{ni})^2; |X_{ni}|\leq b_n] \to 0,
+    \end{align*}
+    which proves the result by sandwich theorem.
+\end{proof}
+
+\newpage
+\begin{corollary}
+\label{coro1}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
+\begin{align*}
+  \mc{I}_n = \{i = \in 2,\ldots, n+1\colon 0< w_i < 1\}.
+\end{align*}
+Suppose that  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$ as $n \to \infty$, and $w_i b_n\leq K$ for $i\in \mc{I}_n$ and some $K>0$, where $b_n \geq 1$ and $b_n \to \infty$ as $n\to \infty$.
+Assume for $i \in \mc{I}_n$,  $p_i$ are pairwise independent $p$-values  with
+\begin{align*}
+  \sum_{i\in \mc{I}_n}\P(p_i \leq \alpha) = \sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_{1},
+\end{align*}
+where $\kappa_i =  \P(p_i \leq \alpha)\in [0,1]$ for $i \in \mc{I}_n$, $\alpha$ is the significance level, $\kappa_1 = \P(p_1 \leq \alpha)$, and  $p_1$ is the p-value of the time series of interest.
+If $\P(p_1 \leq \alpha) \neq 0.5$,
+\begin{align*}
+  \E \bigg\{\left|I\left\{ \sum_{i\in \mc{I}_n} w_i I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right|\bigg\}
+  \to  \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases}
+\end{align*}
+\end{corollary}
+
+\begin{proof}
+  The proof is rather similar to Proposition \ref{votprop}. It suffices to show that
+  \begin{align*}
+   \sum_{i\in \mc{I}_n} w_i I(p_i \leq  \alpha) \cp \kappa_1 =  \P(p_1 \leq \alpha).
+  \end{align*}
+  and the remaining proof is the same as that of Proposition \ref{votprop} in terms of applying Dominated Convergence Theorem in the version of  convergence in probability.
+As $p_i$ are pairwise independent for $i\in \mc{I}_n$, $I(p_i\leq \alpha)$ are pairwise independent for $i \in \mc{I}_n$.
+The idea is to prove the required condition of Lemma \ref{gwlln} holds.
+As  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$, $b_n > 1$, and  $b_n \to \infty$ as $n \to \infty$,
+  \begin{align*}
+    & \sum_{i\in \mc{I}_n} \P\big( I(p_i \leq  \alpha) > b_n\big) \to 0\\
+   & \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} \E\big[ I(p_i \leq  \alpha) \,|\, I(p_i \leq  \alpha) \leq b_n\big]
+     =  \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} \P\big(p_i \leq\alpha \big)
+     = \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} w_i \kappa_i  \to 0
+  \end{align*}
+  because $ \sum_{i\in \mc{I}_n} w_i \kappa_i = O(1)$ by the assumption $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_{1}$.
+Let $c_{ni} = w_i b_n$ for $i \in \mc{I}_n$.
+Since $w_i b_n\leq K$ for some $K > 0$ and $b_n$, we have
+  \begin{align*}
+    & \frac{1}{b_n} \sum_{i\in \mc{I}_n}  c_{ni} \big(  I(p_i \leq  \alpha) - \P( I(p_i \leq  \alpha) \, |\,  I(p_i \leq  \alpha)  \leq b_n )  \big) \\
+  = \quad     &\frac{1}{b_n} \sum_{i\in \mc{I}_n}  c_{ni} \big(  I(p_i \leq  \alpha) - \P( I(p_i \leq  \alpha) \big)  \cp 0
+  \end{align*}
+  which follows from Lemma \ref{gwlln}. The above is equivalent to
+  \begin{align*}
+   \sum_{i\in \mc{I}_n}  w_i I(p_i \leq  \alpha) - \sum_{i\in \mc{I}_n} w_i  \kappa_i  \cp 0
+  \end{align*}
+  As $\sum_{i\in \mc{I}_n} w_i  \kappa_i\to \kappa_1$ as $n \to \infty$, by Slutsky's Theorem,
+  \begin{align*}
+     \sum_{i\in \mc{I}_n}  w_i I(p_i \leq  \alpha)  \cp \kappa_1,
+  \end{align*}
+  which finishes the proof.
+\end{proof}
+
 \vspace*{0.5cm}\noindent\textbf{Possible theoretical approach}: \\
@@
 \begin{align*}
-  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\left] \\
+  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\right] \\
   &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} - (\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{1,t} \Bigg\vert \\
-  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\left] \\
+  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\right] \\
   &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} - (\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{i',t} \Bigg\vert.
@@
   \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
-  \sigma^2_\max &= \max\left(\sigma^2_\eta,\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_\alpha,\sigma^2_{\tilde\phi_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right).  
+  \sigma^2_{\max} &= \max\left(\sigma^2_{\eta},\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_{\alpha},\sigma^2_{\tilde{\phi}_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right).  
 \end{align*}

### 2021-11-01 prevalence_testing/postshocktest2021draft.tex
added more detail to signal2noise arguments

@@
   |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| &< \gamma, \\
-  |\mu_{\tilde\theta_1}'\x_{1,T^*+1} - \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1}| &< \gamma, \\
+%  |\mu_{\tilde\theta_1}'\x_{1,T^*+1} - \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1}| &< \gamma, \\
   \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}\right\vert &< \gamma, \qquad \text{for all} \; t, \\
-  |\mu_{\tilde\phi_1}^j - \mu_{\tilde\phi_{i'}}^j| &< \gamma, \qquad \text{for all} \; j. 
+  |\mu_{\tilde\phi_1}^j - \mu_{\tilde\phi_{i'}}^j| &< \gamma, \qquad \text{for all} \; j, \\
+  |\x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1}| &< \gamma, \\
+  |\x_{1,t}'\Sigma_{\tilde\theta_{1}}\x_{1,t} - \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t}| &< \gamma, \qquad \text{for all} \; t.
 	\end{align*}
@@
 	&\qquad\qquad+ |\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}| + \sum_{j=1}^{t - (T^*+1)}\left\vert \mu_{\tilde\phi_{1}}^j(\mu_{\tilde\theta_{1}}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',t-j})\right\vert \\
-	&\qquad\qquad + \mu_\eta\sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j \\
+	&\qquad\qquad + \mu_\eta\sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j \\
 	&\qquad\leq |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| + |\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}| \\
@@
 	&\qquad\qquad + \sum_{j=1}^{t - (T^*+1)}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,t-j},\mu_\delta'\x_{i',t-j}) + \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t-j} - \mu_{\tilde\theta_{i'}}'\x_{i',t-j}\right\vert\mu_{\tilde\phi_{1}}^j\right] \\
-	&\qquad\qquad + \mu_\eta\sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j,
+	&\qquad\qquad + \mu_\eta\sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j,
 \end{align*}
@@
   &\qquad\qquad + \sum_{j=1}^{\infty}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,t-j},\mu_\delta'\x_{i',t-j}) + \gamma\mu_{\tilde\phi_{1}}^j\right] \\
-  &\qquad\qquad + \mu_\eta\sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j  \\
+  &\qquad\qquad + \mu_\eta\sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j  \\
   &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} \\
-  &\qquad\qquad + \mu_\eta\sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j \\
-  &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} + \gamma\frac{\mu_{\eta}}{1 - \mu_{\phi}} + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j}) \right\vert\mu_{\phi}^j \\
+  &\qquad\qquad + \mu_\eta\sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j \\
+  &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} + \gamma\frac{\mu_{\eta}}{1 - \mu_{\phi}} + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j \\
   &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} + \gamma\frac{\mu_{\eta}}{1 - \mu_{\phi}} + \gamma\frac{\max(\mu_\theta) + 1}{1 - \mu_\phi},
 \end{align*}  
-where the last inequality follows from Lemma~\ref{lem:absdiff}. We can choose $\gamma$ small enough so that $|\E(y_{1,t} - y_{i',t})| < \varepsilon$.
+where the last inequality follows from Lemma~\ref{lem:absdiff}. We can choose $\gamma$ small enough so that $|\E(y_{1,t} - y_{i',t})| < \varepsilon$. A similar recursion for the variance yields 
+\begin{align*}
+ &\left\vert \Var(y_{1,t}) - \Var(y_{i',t})\right\vert 
+   = \left\vert \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{1,t}'\Sigma_{\tilde\theta_i}\x_{1,t} -   \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t} \right.
+\\
+   &\qquad\left. + \mu_{\tilde\phi_1}^2\Var(y_{1,t-1}) - \mu_{\tilde\phi_{i'}}^2\Var(y_{i',t-1}) \right\vert \\
+   &\leq \left\vert \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{1,t}'\Sigma_{\tilde\theta_i}\x_{1,t} -   \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t}\right\vert \\
+   &\qquad + \left\vert\mu_{\tilde\phi_1}^2\Var(y_{1,t-1}) - \mu_{\tilde\phi_{i'}}^2\Var(y_{i',t-1})\right\vert \\
+   &= \left\vert \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{1,t}'\Sigma_{\tilde\theta_1}\x_{1,t} -   \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t}\right\vert \\
+   &\qquad + \left\vert \mu_{\tilde\phi_1}^2\left(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2 + \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} + \x_{1,t-1}'\Sigma_{\tilde\theta_1}\x_{1,t-1} + \mu_{\tilde\phi_1}^2\Var(y_{1,t-2})\right) \right.\\
+   &\qquad\qquad\left.- \mu_{\tilde\phi_{i'}}^2\left(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2 + \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{i',t-1}'\Sigma_{\tilde\theta_{i'}}\x_{i',t-1} + \mu_{\tilde\phi_{i'}}^2\Var(y_{i',t-2})\right) \right\vert \\
+   &\leq \left\vert \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1}\right\vert + \left\vert\x_{1,t}'\Sigma_{\tilde\theta_1}\x_{1,t} -   \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t}\right\vert \\
+   &\qquad+ \left\vert \mu_{\tilde\phi_1}^2\left(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2 + \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} + \x_{1,t-1}'\Sigma_{\tilde\theta_1}\x_{1,t-1}\right) \right.\\
+   &\qquad\qquad\left.- \mu_{\tilde\phi_{i'}}^2\left(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2 + \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{i',t-1}'\Sigma_{\tilde\theta_{i'}}\x_{i',t-1}\right) \right\vert \\
+   &\qquad + \left\vert \mu_{\tilde\phi_1}^4\Var(y_{1,t-2}) - \mu_{\tilde\phi_{i'}}^4\Var(y_{i',t-2}) \right\vert \\
+   &\leq \sum_{j=0}^{t - (T^* + 1)}\left[ \left\vert \mu_{\tilde\phi_1}^{2j}\x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \mu_{\tilde\phi_{i'}}^{2j}\x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1}\right\vert \right.
+\\
+   &\qquad\left.
++ \left\vert \mu_{\tilde\phi_1}^{2j}\x_{1,t-j}'\Sigma_{\tilde\theta_1}\x_{1,t-j} - \mu_{\tilde\phi_{i'}}^{2j}\x_{i',t-j}'\Sigma_{\tilde\theta_{i'}}\x_{i',t-j} \right\vert + \left\vert\mu_{\tilde\phi_1}^{2j} - \mu_{\tilde\phi_{i'}}^{2j}\right\vert(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2)\right] \\
+   &\qquad + \left\vert \mu_{\tilde\phi_1}^{2(t - T^*)}\Var(y_{1,t - T^*}) - \mu_{\tilde\phi_{i'}}^{2(t - T^*)}\Var(y_{i',t - T^*}) \right\vert \\
+   &\leq \sum_{j=0}^{t - (T^* + 1)}\left[ \left\vert \mu_{\tilde\phi_1}^{2j} - \mu_{\tilde\phi_{i'}}^{2j}\right\vert \lambda_{\text{max}} +  \left\vert\x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1}\right\vert\mu_{\tilde\phi_1}^{2j} \right.
+\\
+   &\qquad\left.
++ \left\vert \mu_{\tilde\phi_1}^{2j} - \mu_{\tilde\phi_{i'}}^{2j}\right\vert \lambda_{\text{max}} +  \left\vert\x_{1,t-j}'\Sigma_{\tilde\theta_1}\x_{1,t-j} - \x_{i',t-j}'\Sigma_{\tilde\theta_{i'}}\x_{i',t-j}\right\vert\mu_{\tilde\phi_1}^{2j} + \left\vert\mu_{\tilde\phi_1}^{2j} - \mu_{\tilde\phi_{i'}}^{2j}\right\vert(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2)\right] \\
+   &\qquad + \left\vert \mu_{\tilde\phi_1}^{2(t - T^*)}\sum_{j=0}^{T^*-1}\left(\sigma^2_\eta + \sigma^2 + \x_{1,T^*-j}'\Sigma_\theta\x_{1,T^*-j}\right)\mu_{\phi}^{2j} \right. \\ 
+   &\qquad\qquad\left. - \mu_{\tilde\phi_{i'}}^{2(t - T^*)}\sum_{j=0}^{T^*-1}\left(\sigma^2_\eta + \sigma^2 + \x_{i',T^*-j}'\Sigma_\theta\x_{i',T^*-j}\right)\mu_{\phi}^{2j} \right\vert \\
+   &\leq 2\gamma\frac{\lambda_{\max}}{(1 - \mu_{\tilde\phi_1}^{2})(1 - \mu_{\tilde\phi_{i'}}^{2})} + 2\gamma\frac{1}{1 - \mu_{\tilde\phi_1}^2} + \gamma\frac{\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2}{(1 - \mu_{\tilde\phi_1}^{2})(1 - \mu_{\tilde\phi_{i'}}^{2})} \\
+   &\qquad+ (\sigma^2_\eta + \sigma^2)\left\vert \mu_{\tilde\phi_1}^{2(t - T^*)} - \mu_{\tilde\phi_{i'}}^{2(t - T^*)} \right\vert\sum_{j=0}^{T^*-1}\mu_{\phi}^{2j} \\
+   &\qquad+ \sum_{j=0}^{2(t - T^*)}\left\vert \mu_{\tilde\phi_1}^{2(t - T^*)}\x_{1,T^*-j}'\Sigma_\theta\x_{1,T^*-j} - \mu_{\tilde\phi_{i'}}^{2(t - T^*)}\x_{i',T^*-j}'\Sigma_\theta\x_{i',T^*-j} \right\vert \mu_{\phi}^{2j} \\
+   &\leq 2\gamma\frac{\lambda_{\max}}{(1 - \mu_{\tilde\phi_1}^{2})(1 - \mu_{\tilde\phi_{i'}}^{2})} + 2\gamma\frac{1}{1 - \mu_{\tilde\phi_1}^2} + \gamma\frac{\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2}{(1 - \mu_{\tilde\phi_1}^{2})(1 - \mu_{\tilde\phi_{i'}}^{2})} \\
+   &\qquad + \gamma\frac{\sigma^2_\eta + \sigma^2}{1 - \mu_\phi^2} + \gamma\frac{\lambda_{\max}}{1 - \mu_\phi^2} + \gamma\frac{1}{1 - \mu_\phi^2}
+   \end{align*}
+We can choose $\gamma$ small enough so that $|\Var(y_{1,t}) - \Var(y_{i',t})| < \varepsilon$.
 \end{proof}

### 2021-11-03 prevalence_testing/postshocktest2021draft.tex
minor edits

@@
   \tilde{\mathbf{\phi}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\phi}_j}}(\x_{i,T_i^*+1}) \; \text{where} \; |\tilde{\mathbf{\phi}}_{i,j}| < 1,  \\
-  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots, q_{2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_{i,j}) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_{i,j}) = \Sigma^2_\gamma,  \\
+  \tilde{\mathbf{\theta}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\theta}_j}}(\x_{i,T_i^*+1}),  \\  
  % \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\
 &\eta_i \indep \mathbf{\phi}_{i,j} \indep \mathbf{\theta}_{i,j} \indep 
-\tilde{\mathbf{\phi}}_{i,j} \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i}, 
+\tilde{\mathbf{\phi}}_{i,j} \indep \lambda_{i,j} \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i}, 
 \end{split}
 \end{equation}
-where the distribution $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ exists between -1 and 1 and $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{j,T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{j,T_i^*+1}\| \to 0$.
+%where the distributions $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_{i'}}(\x_{i,T_i^*+1})$ are such that $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_i}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i',T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{i',T_i^*+1}\| \to 0$.
 %the distribution $\mathcal{F}_k(\x_{i,T_i^*})$ is a discrete distribution conditional on $\x_{i,T_i^*}$, $\theta_{i,j} = 0$ for any $q_1 < j \leq \t q_{i,1}$, and $\phi_{i,j} = 0$ for any $q_2 < j \leq \t q_{i,2}$.
-The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}.
+%The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}.
 \textbf{Need to carefully show}.
 Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha + \delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively.
+where the distributions $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_{i'}}(\x_{i,T_i^*+1})$ satisfy $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1}) \overset{d}{=} \mathcal{F}_{\tilde{\mathbf{\phi}}_{j}}(\x_{i',T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_j}(\x_{i,T_i^*+1}) \overset{d}{=} \mathcal{F}_{\tilde{\mathbf{\theta}}_{j}}(\x_{i',T_i^*+1})$ when $\x_{i,T_i^*+1} = \x_{i',T_i^*+1}$.
+Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}}$ must be small relative to the signal strength.
 
 We see that model \eqref{model-gen} with its accompanying random effects structure is flexible enough to capture changing structural dynamics as well as a mean-shift.
-These dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$.
-Two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|_2$ are expected to experience similar structural changes.
+These dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$, the covariates recorded right before the first post-shock response is observed.
+Under this setup any two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|_2$ are expected to experience similar structural changes.
 This makes distance based weighting an attractive avenue.

### 2021-11-10 prevalence_testing/postshocktest2021draft.tex
preliminary draft of section 2.2

@@
 \label{forecast}
+
+In this section, we motivates the relation between shock persistence testing and forecasting comparison.
+In time series literature, under a squared error loss $L(\cdot)$, the forecast using the conditional mean is the best point forecast that minimizes the expected loss if the model is specified correctly.
+That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases.
+On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information should enjoy a smaller expected loss than any conditional mean forecast without such information does.
+In other words, the problem of testing for shock persistence boils down into comparing the conditional mean forecast that is adjusted by shock information and the one that is unadjusted.
+To deal with this problem, we applied the forecast comparison procedure of  \cite{quaedvlieg2021multi} to conduct shock persistence testing.
+
+In this paper, we extend the framework of post-shock forecast \citep{lin2021minimizing}, which aggregates outside information by constructing a donor pool, to post-shock persistence testing.
+The donor pool consists of time series called  ``donors'' that are similar to the time series of interest.
+As we do not observe the future data, information from donors can aid our decision making and forecasts.
+Note that what  similarity exactly means here can be vague but the donors and the time series of interest should come from a common population in principle; see more details of how to select donors in \cite{lin2021minimizing}.
+In this paper, we also proposed several theoretical results with some detailed conditions on the donor pool, which may alleviate the difficulty of dealing with similarity when choosing donors.
+
+In this paper, we propose a new way of aggregating information from donor pool to conduct post-shock persistence testing, which is quite different from \cite{lin2021minimizing}.
+The general structure of this aggregation technique is illustrated as below.
+Suppose we are given a nonempty donor pool with size $n$ that consist of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed.
+With shock information, we are able to compute unadjusted forecast that does not incorporate shock information and adjusted forecast that does.
+The forecast comparison using methodology of \cite{quaedvlieg2021multi} for each donor yields a $p$-value, $p_{i+1}$ for $i$th donor in the donor pool.
+Given $\{p_i \colon i = 2, \ldots, n+1\}$, we propose a methodology for judging whether the shock of the time series of interest is persistent or not.
+Next, we illustrate the details of our methodology as below.
+
+For each donor $\mc{T}_i$, $i = 2, \ldots, n+1$, to compare adjusted and unadjusted forecasts,  a model needs to be specified.
+The model should describe how the shock impacts the time series.
+Note that the model needs not to be the same for every donor in the donor pool.
+However, certain conditions need to be imposed as discussed previously.
+Given a model for each donor pool, we compute the unadjusted forecast and adjusted forecast.
+For the sake of generality, unadjusted forecast and adjusted forecast are two different principles of forecast with one ignoring the shock and the other accommodating it.
+From our best knowledge, in the literature of post-shock prediction, the reliable post-shock point forecast exists only for $t=T^*+1$ when the shock occurs.
+The adjusted forecast and unadjusted forecast are the same for $t\leq  T^*$ whereas the adjusted forecast and unadjusted forecast differs by an adjustment that depends on the model chosen.
+
+\newpage
 

### 2021-11-11 prevalence_testing/postshocktest2021draft.tex
preliminary draft of section 2.2

@@
 
+\label{section2}
+
 We will suppose that a researcher has multivariate time series data $\y_{i,t}$, $t = 1, \ldots,  T_i$ and $i = 1, \ldots, n+1$.
@@
 In time series literature, under a squared error loss $L(\cdot)$, the forecast using the conditional mean is the best point forecast that minimizes the expected loss if the model is specified correctly.
-That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases.
-On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information should enjoy a smaller expected loss than any conditional mean forecast without such information does.
+That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional mean forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases.
+On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information and makes good use of it should enjoy a smaller expected loss than any conditional mean forecast without such information does.
 In other words, the problem of testing for shock persistence boils down into comparing the conditional mean forecast that is adjusted by shock information and the one that is unadjusted.
@@
 The general structure of this aggregation technique is illustrated as below.
-Suppose we are given a nonempty donor pool with size $n$ that consist of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed.
+Suppose we are given a nonempty donor pool with size $n$ that consists of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed.
 With shock information, we are able to compute unadjusted forecast that does not incorporate shock information and adjusted forecast that does.
@@
 For each donor $\mc{T}_i$, $i = 2, \ldots, n+1$, to compare adjusted and unadjusted forecasts,  a model needs to be specified.
-The model should describe how the shock impacts the time series.
+The model should describe how the shock impacts the time series at and after a certain time point $t= T_i^* + 1$.
+For clarity, we refers the unadjusted forecast to the conditional mean forecast based on the part of the model that ignores shock effect; and the adjusted forecast refers to the conditional mean forecast based on the full model.
 Note that the model needs not to be the same for every donor in the donor pool.
 However, certain conditions need to be imposed as discussed previously.
-Given a model for each donor pool, we compute the unadjusted forecast and adjusted forecast.
-For the sake of generality, unadjusted forecast and adjusted forecast are two different principles of forecast with one ignoring the shock and the other accommodating it.
-From our best knowledge, in the literature of post-shock prediction, the reliable post-shock point forecast exists only for $t=T^*+1$ when the shock occurs.
-The adjusted forecast and unadjusted forecast are the same for $t\leq  T^*$ whereas the adjusted forecast and unadjusted forecast differs by an adjustment that depends on the model chosen.
+
+ Given a model for each donor pool, we compute the unadjusted conditional mean forecast and adjusted conditional mean forecast in the framework of \cite{quaedvlieg2021multi}.
+As introduced in the beginning of Section \ref{section2}, for a given horizon $h$, to forecast $y_{i, t}$, we compute the two forecasts based on the information set $\mathcal{F}_{i, t-h}$ of each donor pool (i.e., the data before $t-h$) for $i = 2, \ldots, n+1$.
+Note that in practice, a training sample size $K_i$ should be specified for $i = 2, \ldots, n+1$ such that we use the information set $\mathcal{F}_{i, t-h-K_i + 1:t-h}$.
+
+ Even if the data contain shock information for each donor, it is impossible to compute the adjusted conditional mean forecast based on $\mathcal{F}_{i, t-h}$ when $t -h \leq T_i^*$, i.e., we only have training data that do no have any shock information.
+Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information.
+In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an unbiased estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate.
+However, the unbiased estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.
+To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear.
+However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.
 

### 2021-11-12 prevalence_testing/postshocktest2021draft.tex
some reorganization and an additional lemma

@@
 
+We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
+Let $l$ be the block length of the MBB where we assume that $T_i = lK_i$.
+Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
+$$
+  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
+$$
+The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.
+
+\begin{equation} \label{whb}
+	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{K_i}\sum_{k=1}^{K_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
+\end{equation}
+where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
+\begin{equation} \label{boott}
+  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
+  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
+  \Big\vert \overset{P}{\longrightarrow} 0,
+\end{equation}
+as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
+$$
+  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
+$$
+The results \eqref{boott} implies that 
+\begin{equation} \label{bootp}
+  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
+\end{equation}
+    where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$.
+Therefore bootstrap inference in the donor pool is a good approximation.
+%We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.
+
 \subsection{Model setup}
@@
 
-\noindent\textbf{Note}: We need to update the modeling setup. We should present a general modeling class which includes both the decay model and the permanent shift model.
-
-\vspace{0.5cm}\noindent\textbf{Possible modeling approach}
-
-\vspace{0.5cm} We now describe the assumed autoregressive models with random effects for which post-shock aggregated estimators are provided. The model $\mc{M}$ is defined as
-\begin{align}
-\mc{M} \colon \begin{array}{l}
-  y_{i,t} =\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j} + \alpha_i D_{i,t}f(t) + \varepsilon_{i,t},\\[.2cm]
-  %\; f(\mc{F}_{i,t-1},\x_{i,t-1},\alpha_i) =  \\[.2cm] %+ \sum_{j=1}^{q_3}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_4-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
-  \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \t{\varepsilon}_{i},
-  %\sum_{j=1}^{q_3}\delta_{i,j}'\mbf{x}_{i, T_i^*-j+1}+ \t{\varepsilon}_{i}, 
-\end{array}\label{model}
-\end{align}
-where $D_{i,t} = I(t \geq T_i^* + 1)$, $I(\cdot)$ is the indicator function, $\x_{i,t} \in \R^{p}$ are fixed with $p \geq 1$, $f(t)$ is a bounded continuous function which does not cross zero and $\lim_{t\to\infty}g(t) = a \in \R$.
-Let
-$\mathbf{\phi}_i = (\phi_{i,1},\ldots,\phi_{i,q_1})'$, 
-$\mathbf{\theta}_i = (\theta_{i,1},\ldots,\theta_{i,q_2})'$, 
-%$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_3})'$, 
-%$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i,q_4})'$, 
-$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,q_3})'$, 
-and suppose that the regression coefficients in \eqref{model} have the following random effects structure:
-\begin{align*}
-  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = \mu_\eta, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
-  \mathbf{\phi}_i &\simiid \mc{F}_{\mathbf{\phi}} \text{ where } |\phi_{i,j}| < 1, \\
-  \mathbf{\theta}_i &\simiid \mc{F}_{\mathbf{\theta}} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}}}(\theta_i) = \mu_{\mathbf{\theta}}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}}}(\mathbf{\theta}_i)  = \Sigma^2_{\mathbf{\theta}}, \\
-  %\tilde{\mathbf{\phi}}_i &\simiid \mc{F}_{\tilde{\mathbf{\phi}}} \text{ where } |\t\phi_{i,j}| < 1, \\
-  %\tilde{\mathbf{\theta}}_i &\simiid \mc{F}_{\tilde{\mathbf{\theta}}} \text{ with }  \; \mrm{E}_{\mc{F}_{\tilde{\mathbf{\theta}}}}(\theta_i) = \mu_{\tilde{\mathbf{\theta}}}, \mrm{Var}_{\mc{F}_{\tilde{\mathbf{\theta}}}}(\tilde{\mathbf{\theta}}_i)  = \Sigma^2_{\tilde{\mathbf{\theta}}}, \\
-  \mathbf{\delta}_i &\simiid  \mc{F}_{\mathbf{\delta}} \text{ with } \mrm{E}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\mu_{\mathbf{\delta}}, \mrm{Var}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\Sigma_{\mathbf{\delta}}, \\
-\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i,  \\
-\t{\varepsilon}_{i} &\simiid  \mc{F}_{\t{\varepsilon}} \text{ with }\mrm{E}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=0, \mrm{Var}_{\mc{F}_{\t{\varepsilon}}}(\t{\varepsilon}_{i})=\sigma^2_{\alpha}, \\
-&\eta_i \indep \mathbf{\phi}_i \indep \mathbf{\theta}_i \indep 
-%\tilde{\mathbf{\phi}}_i \indep \tilde{\mathbf{\theta}}_i \indep 
-\mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t}.
-\end{align*}
-The model \eqref{model} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}.
-\textbf{Need to carefully show}.
-In this formulation $f(t)$ represents either a permanent or transient structural change to the time series that results from the shock.
-
-We further define the parameter sets
-\begin{align}
-\begin{array}{l}
- \;\, \Theta = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
-   \Theta_1 = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon  t= 1, \ldots, T_i, i = 1\}
-\end{array}\label{parameter} 
-\end{align}
-
-\vspace*{0.5cm}\noindent\textbf{Alternative model formulation}
-
-\vspace*{0.5cm} We now describe the assumed autoregressive models with random effects for which post-shock aggregated estimators are provided. The model $\mc{M}$ is defined as
+We now describe the assumed autoregressive models with random effects for which post-shock aggregated estimators are provided. The model $\mc{M}$ is defined as
 \begin{align}
@@
 \end{align}
-where $g(t)$ is a known or estimable bounded continuous function which does not cross zero and $\lim_{t\to\infty}g(t) = a \in \R$. Let 
+where $D_{i,t} = I(t \geq T_i^* + 1)$, $I(\cdot)$ is the indicator function, $\x_{i,t} \in \R^{p}$ are fixed with $p \geq 1$. Let 
 $\mathbf{\phi}_i = (\phi_{i,1},\ldots,\phi_{i,q_1})'$, 
@@
 \end{equation}
-%where the distributions $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_{i'}}(\x_{i,T_i^*+1})$ are such that $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_i}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i',T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{i',T_i^*+1}\| \to 0$.
-%the distribution $\mathcal{F}_k(\x_{i,T_i^*})$ is a discrete distribution conditional on $\x_{i,T_i^*}$, $\theta_{i,j} = 0$ for any $q_1 < j \leq \t q_{i,1}$, and $\phi_{i,j} = 0$ for any $q_2 < j \leq \t q_{i,2}$.
-%The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}.
-\textbf{Need to carefully show}.
-Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha + \delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively.
 where the distributions $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_{i'}}(\x_{i,T_i^*+1})$ satisfy $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1}) \overset{d}{=} \mathcal{F}_{\tilde{\mathbf{\phi}}_{j}}(\x_{i',T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_j}(\x_{i,T_i^*+1}) \overset{d}{=} \mathcal{F}_{\tilde{\mathbf{\theta}}_{j}}(\x_{i',T_i^*+1})$ when $\x_{i,T_i^*+1} = \x_{i',T_i^*+1}$.
@@
 
-We see that model \eqref{model-gen} with its accompanying random effects structure is flexible enough to capture changing structural dynamics as well as a mean-shift.
-These dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$, the covariates recorded right before the first post-shock response is observed.
+We see that model \eqref{model-gen} with its accompanying random effects structure \eqref{random-effects} is flexible enough to capture changing structural dynamics as well as a mean-shift, and is a generalization of the model in \cite{lin2021minimizing}.
+Note that the flexibility of allowing for changing structural dynamics is useful for fitting purposes, but it does not necessarily reflect the state of the world in the post-shock setting.
+It is of course possible that there is no shock or a simple mean-shift.
+
+The post-shock dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$, the covariates recorded right before the first post-shock response is observed.
 Under this setup any two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|_2$ are expected to experience similar structural changes.
 This makes distance based weighting an attractive avenue.
+
+%We further define the parameter sets
+%\begin{align}
+%\begin{array}{l}
+% \;\, \Theta = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
+%   \Theta_1 = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon  t= 1, \ldots, T_i, i = 1\}
+%\end{array}\label{parameter} 
+%\end{align}
 
@@
 
-\newpage
+\vspace*{0.5cm}
 
@@
 
-\vspace*{0.5cm}\noindent\textbf{Note}: We need to explain what the voting method is, possibly in algorithmic format.
+\newpage
+
+\noindent\textbf{Note}: We need to explain what the voting method is, possibly in algorithmic format.
 Also note that the p-values that we obtain are computed using a bootstrap procedure.
@@
 
-\newpage
 \begin{corollary}
@@
 
-\vspace*{0.5cm}\noindent\textbf{Possible theoretical approach}: \\
+\newpage
 
-Let $l$ be the block length of the moving block bootstrap (MBB) where we assume that $T_i = lK_i$.
-Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
-$$
-  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
-$$
-The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.
-
-\begin{equation} \label{whb}
-	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{K_i}\sum_{k=1}^{K_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
-\end{equation}
-where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
-\begin{equation} \label{boott}
-  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
-  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
-  \Big\vert \overset{P}{\longrightarrow} 0,
-\end{equation}
-as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
-$$
-  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
-$$
-The results \eqref{boott} implies that 
-\begin{equation} \label{bootp}
-  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
-\end{equation}
-    where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$.
-Therefore bootstrap inference in the donor pool is a good approximation.
-%We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.
-
-\vspace*{0.5cm}\noindent\textbf{This needs some work (ignore for now)} Now consider a case where there exists a $2 \leq i' < n + 1$ where $\x_{1,t} = \x_{i',t}$.
-Now suppose for simplicity that $T^*_{j'} = T^*_1$ and that $T_{i'} = T_1$ where $T_1 > T^*_1 + q_1 + q_2 + 2$.
-This assumes that we have data for the first time series beyond the shock point.
-We will show that when there is a covariate clone of the time series under study, then estimation in this series will approximate estimation in the time series under study provided that the underlying variability is very small relative to the signal.
-To see this, consider $t > T^*_1$, where
-\begin{align*}
-y_{1,t} &= \eta_1 + \mu_\alpha + \delta_1'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} + \sum_{j=0}^{q_2-1}(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{1} + \varepsilon_{1,t}, \\
-y_{i',t} &= \eta_{i'} + \mu_\alpha + \delta_{i'}'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} + \sum_{j=0}^{q_2-1}(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{i'} + \varepsilon_{i',t}, \\
-\hat y_{1,t} &= \hat \eta_1 + \hat{\alpha}_1(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat y_{1,t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}, \\
-\hat y_{i',t} &= \hat\eta_{i'} + \hat{\alpha}_{i'}(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat y_{i',t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j},
-\end{align*}
-where $\alpha_j(\x) = \mu_\alpha + \delta_j'\x$, and we have 
-\begin{align*}
-  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\right] \\
-  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} - (\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{1,t} \Bigg\vert \\
-  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\right] \\
-  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} - (\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{i',t} \Bigg\vert.
-\end{align*}
-\textbf{Needs finishing, but the argument is simple: estimation uncertainty declines as error variance decreases.
-And differences in the random effects decrease as variability decreases.} \vspace*{0.5cm}
-
-\vspace*{0.5cm} We now demonstrate an idealized setting in which the above logic holds.
+\vspace*{0.5cm} We now demonstrate an idealized theoretical setting for which our post-shock testing methodology involving a distance based weighted average of p-values works well.
+The idea is that inferences based on distance based weighted nearly recovers the time series under study when there exists a time series in the donor pool, indexed by $i'$, such that $\x_{1,t} \approx \x_{i',t}$ and the signal strength in our modeling setup \eqref{model-gen} and \eqref{random-effects} is large relative to variation.
 We first present some intermediary technical results and definitions.
@@
 	\item The conditions \eqref{condition-1} govern the signal strength necessary in the expected behavior of the underlying random effects structure relative to variability necessary for the overall signal to noise ratio for the overall time series to be lower bounded by some positive value $C$.
-	\item The conditions of Proposition~\ref{prop:signaltonoise} state that there is an increasing trend in $y_{i,t}$ for all $i$.
+	\item The conditions of Proposition~\ref{prop:signaltonoise} state that there is an increasing trend in $y_{i,t}$ for all $i$. This can be relaxed, but a fully general argument is cumbersome.
 \end{enumerate}
@@
 	$$
-	  \left\vert\E(y_{i,t} - y_{i',t})\right\vert \leq \epsilon,
+	  \left\vert\E(y_{i,t} - y_{i',t})\right\vert \leq \epsilon, \qquad |\Var(y_{1,t}) - \Var(y_{i',t})| < \varepsilon,
 	$$
@@
 \end{proof}
+
+\begin{lem}[Technical Lemma 2] \label{lem:diffsig2noise}
+Let $a_j, b_j \in \R$, $j = 1,2$. Suppose that $b_j > b > 0$ for $j = 1,2$. Then for any $\varepsilon > 0$ we have 
+$$
+  \left\vert\frac{a_1}{b_1} - \frac{a_2}{b_2}\right\vert \leq \varepsilon,
+$$
+provided that $|a_1-a_2|$,$|b_1-b_2| < \delta$ for some chosen $\delta > 0$.
+\end{lem}
+
+\begin{proof}
+\begin{align*}
+  \left\vert\frac{a_1}{b_1} - \frac{a_2}{b_2}\right\vert 
+    &= \left\vert\frac{a_1b_2 - a_2b_1}{b_1b_2}\right\vert 
+    = \left\vert\frac{(a_1 - a_2 + a_2)(b_2 - b_1 + b_1) - a_2b_1}{b_1b_2}\right\vert \\
+    &= \left\vert \frac{a_1(b_2 - b_1) + a_2b_1 + (a_1 - a_2)b_1 - a_2b_1}{b_1b_2} \right\vert \leq \frac{2\delta}{b^2} \\
+    &\leq \frac{|a_1|\delta + |b_1|\delta}{b^2} \leq \varepsilon, 
+\end{align*}
+where $\delta \leq \varepsilon b^2/(|a_1| + |b_1|)$.
+\end{proof}
+
+\noindent\textbf{This needs some work (ignore for now)} Now consider a case where there exists a $2 \leq i' < n + 1$ where $\x_{1,t} = \x_{i',t}$.
+Now suppose for simplicity that $T^*_{j'} = T^*_1$ and that $T_{i'} = T_1$ where $T_1 > T^*_1 + q_1 + q_2 + 2$.
+This assumes that we have data for the first time series beyond the shock point.
+We will show that when there is a covariate clone of the time series under study, then estimation in this series will approximate estimation in the time series under study provided that the underlying variability is very small relative to the signal.
+To see this, consider $t > T^*_1$, where
+\begin{align*}
+y_{1,t} &= \eta_1 + \mu_\alpha + \delta_1'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} + \sum_{j=0}^{q_2-1}(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{1} + \varepsilon_{1,t}, \\
+y_{i',t} &= \eta_{i'} + \mu_\alpha + \delta_{i'}'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} + \sum_{j=0}^{q_2-1}(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{i'} + \varepsilon_{i',t}, \\
+\hat y_{1,t} &= \hat \eta_1 + \hat{\alpha}_1(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat y_{1,t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}, \\
+\hat y_{i',t} &= \hat\eta_{i'} + \hat{\alpha}_{i'}(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat y_{i',t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j},
+\end{align*}
+where $\alpha_j(\x) = \mu_\alpha + \delta_j'\x$, and we have 
+\begin{align*}
+  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\right] \\
+  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} - (\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{1,t} \Bigg\vert \\
+  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\right] \\
+  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} - (\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{i',t} \Bigg\vert.
+\end{align*}
+\textbf{Needs finishing, but the argument is simple: estimation uncertainty declines as error variance decreases.
+And differences in the random effects decrease as variability decreases.} \vspace*{0.5cm}
 

### 2021-11-16 prevalence_testing/manual.tex
addition of manual and edits to manuscript

\documentclass[12pt]{article}

\usepackage{scribe}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{apacite}
\usepackage{palatino}
\usepackage{mathpazo}

\bibliographystyle{apacite}

\title{User manual for R functions used in Post-Shock Persistence Testing}

\begin{document}

\maketitle

This document describes the functions that are used in the post-shock persistence testing.

\tableofcontents

\section{\texttt{scm} function}

\texttt{scm(X,Tstar)} is  a core function in post-shock prediction methodology that is used to compute the synthetic weights $\mathbf{W}^*$ in \citeA{lin2021minimizing}. It computes the weights to minimize the Euclidean distance between the convex combination of the covariates in the donor pool and the covariates of the time series of interest. The optimization is based on  nonlinear optimization using the \texttt{solnp} in the  R package \texttt{Rsolnp} \cite{ghalanos2012package}.

Suppose the donor pool size is $n$. \texttt{scm(X,Tstar)} takes \texttt{X} and \texttt{Tstar} as inputs and outputs a vector of weights $\mathbf{W}^*$ and other convergence details related to \texttt{solnp}, where
\begin{itemize}
	\item \texttt{X} is a list of covariates with length $n+1$, where the first element of the list should be the covariates of the time series of interest and the remaining elements of the list are the covariates of the donors. The covariates should be in the class of \texttt{matrix} with size $T_i\times p$ for $i = 1, \ldots, n+1$.
	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+1$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$.
\end{itemize}

\emph{Examples:}

\begin{verbatim}
p <- 2; n <- 10;
T <- round(rgamma(n = n + 1, shape = 15, scale = 10)) # Time Length
Tstar <- c() # Shock Time Points
for (t in T) {
  Tstar <- c(Tstar, sample((p + 3 + 1):(t - 1), size = 1))
}
phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters
# construction of design matrix
X <- c()
for (i in 1:(n + 1)) {
  Ti <- T[i]
  Tstari <- Tstar[i]
  X[[i]] <- matrix(rgamma(n = p * (Ti + 1), shape = 1, scale = 1),
                   ncol = p, byrow = T) 
}
scm(X, Tstar)
\end{verbatim}

\section{\texttt{sel} function}

\texttt{sel(yhat,y)} function is a function that computes the squared error loss between   $\hat{\bs{y}}$ and  $\bs{y}$, where 
\begin{itemize}
	\item \texttt{yhat} is either a vector or a scalar
	\item \texttt{y} is either a vector or a scalar
\end{itemize}
\texttt{yhat} and \texttt{y} must have equal length. The output of \texttt{sel(yhat,y)} is the squared error loss. It may be a vector or scalar.

\emph{Examples:}
\begin{verbatim}
sel(rnorm(10), rep(0,10))
\end{verbatim}

\section{\texttt{taSPA.mhfc} function}

\texttt{taSPA.mhfc(ell,d,B,bw)} is a core function that implements the hypothesis test of \citeA{quaedvlieg2021multi} that compares two  forecasts  in terms of average superior predictive ability (aSPA) for multiple horizons. See the theoretical and algorithmic details of the hypotheses in \citeA{quaedvlieg2021multi}. Let $H$ be the maximum horizon number for the forecasts and $T$ be the sample size. The test statistic is
\begin{align*}
	t_{aSPA, ij} = \frac{\sqrt{T}\bar{d}_{ij}}{\hat{\xi}_{ij}}, 
\end{align*}
where $\bs{d}_{ij, t}$ ($H\times 1$) is the loss differential between forecasts $i$ and $j$ at time $t$, $\bar{\bs{d}}_{ij}$ is the average across $t = 1, \ldots, T$, $\bar{d}_{ij}=\bs{w}'\bar{\bs{d}}_{ij}$,  $\xi_{ij}= \sqrt{\bs{w}'\bs{\Omega}_{ij}\bs{w}}$ is estimated by HAC estimator, $\bs{\Omega}_{ij}$ is the asymptotic variance of $\bar{\bs{d}}_{ij}$. $\bs{w}=\bs{1}_H/H$ is taken as default. The computation of HAC estimator requires specification of a bandwidth parameter \texttt{bw}. Provided with a loss differential matrix \texttt{d}, this test uses moving-block bootstrap to approximate the distribution of the test statistic. Note that
\begin{itemize}
	\item \texttt{ell} is the block length of the moving block bootstrap. Theory of \citeA{quaedvlieg2021multi} requires $\texttt{ell} = o(T^{1/2})$.
	\item \texttt{d} is the loss differential matrix of size $T \times H$. It must be of \texttt{matrix} class. The element in $t$th row and $h$th column should be the loss differential between two $h$-step forecasts for $t$th observation.
	\item \texttt{B} is the bootstrap sample size.
	\item \texttt{bw} is the bandwidth of computation for HAC estimator. HAC estimation is based on \texttt{HAC} from \citeA{tsapppackage} using quadratic spectral kernel.
\end{itemize}

The output of \texttt{taSPA.mhfc(ell,d,B,bw)}  is the $p$-value of the test, which is a scalar.
 Importantly, \texttt{taSPA.mhfc(ell,d,B,bw)} tests a \emph{one-sided} hypothesis. Thus it is necessary to check whether the way about how the loss differential \texttt{d} is computed matches the hypothesis that is tested. See more details of the hypothesis that is tested in \citeA{quaedvlieg2021multi}.

 \emph{Examples:}
\begin{verbatim}
y <- arima.sim(list(2,0,0), n = 100)

T <- 50; H <- 10; K <- 40

m1.L.i <- matrix(NA, nrow = T, ncol = H)
m2.L.i <- matrix(NA, nrow = T, ncol = H)
for (h in 1:H) {
  for (t in 1:T) {
    y.t <- y[(t + H - h + 1):(t + K + H - h)]

    m1 <- arima(y.t, order = c(1, 0, 0))
    m2 <- arima(y.t, order = c(2, 0, 0))

    y.t.hat.1 <- predict(m1, h)$pred[h]
    y.t.hat.2 <- predict(m1, h)$pred[h]

    m1.L.i[t, h] <- sel(y = y[t + K + H], yhat = y.t.hat.1)
    m2.L.i[t, h] <- sel(y = y[t + K + H], yhat = y.t.hat.2)
  }
}
d <- m2.L.i - m1.L.i

taSPA.mhfc(ell = 2, d = d, B = 200, bw = 4)
\end{verbatim}

 \section{\texttt{vote} function}

 \texttt{vote(ps,sig)} is a function that yields the significance voting from a vector of $p$-values given a significance level. To be specific, if over 50\% of the tests, each of which corresponds to a $p$-value in the donor pool,   are significant according to the given significance level, the output of  \texttt{vote(ps,sig)} would be 1. It is 0 otherwise. Note that
 \begin{itemize}
 	\item \texttt{ps} is a vector of $p$-values with values in $[0,1]$.
 	\item \texttt{sig} is the significance level. It is 0.05 in default. It should be a scalar.
 \end{itemize}

 \emph{Examples:}

 \begin{verbatim}
 vote(runif(10), .05)
 \end{verbatim}

 \section{\texttt{ols.est.alphahat} function}

 \texttt{ols.est.alphahat(Tstar,Y,X)} is the core function in \citeA{lin2021minimizing} that is used to compute the weighted adjusted shock effect estimate $\hat{\alpha}_{\rm wadj}$ that aggregates information in the donor pool. Suppose the donor pool size is $n$. Given the shock time points, it performs $n$ OLS regressions across the donor pool to estimate the shock effect of each donor. The regression is based on the $\textbf{AR}(1)$ model with covariates as specified in Section 2.1 of \citeA{lin2021minimizing}.  The function internally uses \texttt{scm} function to compute the weights $\mbf{W}^*$ and weight the donors' shock effects to compute $\hat{\alpha}_{\rm wadj}$. It also computes the $\hat{\alpha}_{\rm IVW}$ estimate and $\hat{\alpha}_{\rm adj}$ estimate. See more details of these two estimates in \citeA{lin2021minimizing}. Note that
\begin{itemize}
	\item \texttt{X} is a list of covariates with length $n+1$, where the first element of the list should be the covariates of the time series of interest and the remaining elements of the list are the covariates of the donors. The covariates should be in the class of \texttt{matrix} with size $T_i\times p$ for $i = 1, \ldots, n+1$.
	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+1$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$.
	\item \texttt{Y} is a list of responses with length $n +1$,  where the first element of the list should be the response of the time series of interest and the remaining elements of the list are the responses of the donors. It should be a vector.
\end{itemize}

 This function outputs
 \begin{itemize}
 	\item \texttt{alphahat} is a vector of $n$ length and contains the OLS shock effect estimates for the donors.
 	\item \texttt{est} is a vector of three shock effect estimates, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$.
 	\item \texttt{Tstar} is the same as the one in the input.
 	\item \texttt{X} is the same as the one in the input.
 	\item \texttt{Y} is the same as the one in the input.
 	\item \texttt{lmod} is a list of $n$ \texttt{lm} objects that were fitted by OLS for each donor. The ordering is the same as how the donor is ordered in \texttt{X}, \texttt{Y}, and \texttt{Tstar}.
 	\item \texttt{res} is a list of $n$ residual objects corresponding to each element of  \texttt{lmod}.
 	\item \texttt{Wstar} is the synthetic weights, as defined in the output of \texttt{scm}.
 	\item \texttt{se} is a vector of length $n$ and each element is the OLS standard error for the OLS shock effect estimate for each donor.
 \end{itemize}

 \emph{Examples:}

 \begin{verbatim}
n <- 10; p <- 2
Ts <- ceiling(rgamma(n + 1, scale = 10, shape = 10)) # Time Length
Tstar <- c() # Shock Time Points
for (t in T) {
  Tstar <- c(Tstar, sample((p + 3 + 1):(t - 1), size = 1))
}
phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters

X <- c()
alpha <- c()
# construction of design matrix and shock effects
gamma <- c()
for (i in 1:(n + 1)) {
  Ti <- Ts[i]
  Tstari <- Tstar[i]
  Ki <- K[i]
  X[[i]] <- matrix(rgamma(n = p * (Ti + Ki + H + 1),
                          shape = 1, scale = 1), ncol = p, byrow = TRUE) 
  gamma[[i]] <- matrix(rnorm(p, mean = 1, sd = 1), nrow = 1)
  epsilontildei <- rnorm(n = 1, sd = 1)
  alpha <- c(alpha, 1 + gamma[[i]] %*% X[[i]][Tstari + 1, ] +
               epsilontildei)
}

# generation of yit
Y <- c()
for (i in 1:(n + 1)) {
  yi0 <- rnorm(1)
  Tstari <- Tstar[i]
  alphai <- alpha[i]
  phii <- phi[i]
  xi <- X[[i]]
  yi <- yi0
  thetai <- matrix(rnorm(p), nrow = 1)
  etai <- rnorm(1)
  for (t in 2:(Ts[i] + 1)) {
    epsilonit <- rnorm(n = 1, sd = 1)
    yi <- c(yi, etai + alphai * ifelse(t >= Tstari + 2, 
                                       yes = 1, no = 0) +
              phii * yi[t - 1] + thetai %*% xi[t, ] + epsilonit)
  }
  Y[[i]] <- yi
}
ols.est.alphahat(Tstar,Y,X)
 \end{verbatim}

 \section{\texttt{ps.indic.W.permanent}}

 \texttt{ps.indic.W.permanent(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} is a core function that produces the synthetic weights from \texttt{scm}, a sequence of $p$-values and corresponding rejection/acceptance decisions for each donor in the donor pool based on a give significance level and the test  function \texttt{taSPA.mhfc}. The assumed model for this function is
 \begin{align*}
 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \alpha_i I(t > T_i^*+1) + \varepsilon_{i,t},\\
 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
 \end{align*}
 where $T_i^*+1$ is the time point when the shock occurs for $i = 2, \ldots, n+1$, $\bs{x}_{i,t}$ is the covariate, and $\eta_i$ is the intercept. Note that only $\bs{\theta}$, $\eta_i$, and $\alpha_i$ are estimable. The above model is called permanent model due to the presence of a persistent shock term. For each donor, this function computes the adjusted forecast and unadjusted forecast, construct the corresponding loss differential matrix, and perform the forecast comparison test.  Suppose the donor pool size is $n$. The input for this function is
\begin{itemize}
	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+1$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$.
	\item \texttt{Y} is a list of responses with length $n +1$,  where the first element of the list should be the response of the time series of interest and the remaining elements of the list are the responses of the donors. It should be a vector.
	\item \texttt{X} is a list of covariates with length $n+1$, where the first element of the list should be the covariates of the time series of interest and the remaining elements of the list are the covariates of the donors. The covariates should be in the class of \texttt{matrix} with size $T_i\times p$ for $i = 1, \ldots, n+1$. Note that the sample size of each element  in \texttt{X} should be  $T_i+ K_i + H$, where $K_i$ is the training sample size and $T_i$ is the length of the donor time series that are wished to be considered as the data used in forecast comparison. $H$ is the maximum horizon.
	\item \texttt{K} is a vector of training sample sizes that are used to compute $h$-step forecast for each data point. \texttt{K} has a length of $n+1$. The first element of \texttt{K} can be \texttt{NA} as forecast comparison is not available for the time series of interest.
	\item \texttt{H} is the maximum $h$ that an $h$-step forecast that is wished to be considered in the multi-horizon forecast comparison testing procedure in \citeA{quaedvlieg2021multi}.
	\item \texttt{Ts} is a vector of length $n+1$, and it specifies the length of the time series (ordered from the time series of interest to donors).
	\item \texttt{ell} is the block length of the moving block bootstrap. See details in \texttt{taSPA.mhfc}.
	\item \texttt{B} is the bootstrap sample size. See details in \texttt{taSPA.mhfc}.
	\item \texttt{bw} is the bandwidth of computation for HAC estimator. See details in \texttt{taSPA.mhfc}.
	\item \texttt{sig.levl} is the significance level for the test. It is 0.05 in default.
\end{itemize}

 The output of this function is
 \begin{itemize}
 	\item \texttt{ps} is a sequence of $p$-values from forecast comparison test of \citeA{quaedvlieg2021multi}  for the donors. It is of length $n$.
 	\item \texttt{W} is a vector of synthetic weights and is of length $n$.
 	\item  \texttt{Is} is a sequence of rejection/acceptance decisions from forecast comparison for the donors, where 1 stands for rejection and 0 for acceptance. It is of length $n$.
 \end{itemize}

 \emph{Examples:}

 \begin{verbatim}
n <- 10; p <- 2
K <- ceiling(rgamma(n + 1, scale = 5, shape = 10)) # training sample size
Ts <- ceiling(rgamma(n + 1, scale = 10, shape = 10)) # Time Length
Tstar <- c()
for (i in 1:(n + 1)) {
  Tstar <- c(Tstar,  max(Ts[i] + 1, ceiling(0.5 * (Ts[i] + K[i] + H))))
}
phi <- round(runif(n + 1, 0, 1), 3) # autoregressive parameters

X <- c()
alpha <- c()
# construction of design matrix and shock effects
gamma <- c()
for (i in 1:(n + 1)) {
  Ti <- Ts[i]
  Tstari <- Tstar[i]
  Ki <- K[i]
  X[[i]] <- matrix(rgamma(n = p * (Ti + Ki + H + 1),
                          shape = 1, scale = 1), ncol = p, byrow = TRUE) 
  gamma[[i]] <- matrix(rnorm(p, mean = 1, sd = 1), nrow = 1)
  epsilontildei <- rnorm(n = 1, sd = 1)
  alpha <- c(alpha, 1 + gamma[[i]] %*% X[[i]][Tstari + 1, ] +
               epsilontildei)
}

# generation of yit
Y <- c()
for (i in 1:(n + 1)) {
  yi0 <- rnorm(1)
  Tstari <- Tstar[i]
  alphai <- alpha[i]
  phii <- phi[i]
  xi <- X[[i]]
  yi <- yi0
  thetai <- matrix(rnorm(p), nrow = 1)
  etai <- rnorm(1)
  for (t in 2:(K[i] + Ts[i] + H + 1)) {
    epsilonit <- rnorm(n = 1, sd = 1)
    yi <- c(yi, etai + alphai * ifelse(t >= Tstari + 2, 
                                       yes = 1, no = 0) +
              phii * yi[t - 1] + thetai %*% xi[t, ] + epsilonit)
  }
  Y[[i]] <- yi
}

est <- ps.indic.W.permanent(Tstar = Tstar, Y = Y, X = X, K = K, 
                            H = 10, Ts = Ts, ell = 4, B = 200, bw = 4)
 \end{verbatim}

 \section{\texttt{ps.indic.W.complicate}}

 \texttt{ps.indic.W.complicate(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
 \begin{align*}
 	y_{i,t}
 	&= \left(\eta_i + \sum_{j=1}^{q_2} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
 	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i}
 \end{align*}
 where $D_{i,t}=I(t > T_i^*+1)$. Note that only $\eta_i, \alpha_i - \eta_i, \phi_{i,j}, \bs{\theta}_{i, j+1}, \tilde{\phi}_{i,j}-\phi_{i,j}, \tilde{\bs{\theta}}_{i,j+1}-\bs{\theta}_{i, j+1}$ are estimable.
The role of the shock in this model is that the dynamics of $y_{i,t}$ change after the shock.

Examples are similar to those for \texttt{ps.indic.W.permanent}.

\section{\texttt{ps.indic.W.decay}}

 \texttt{ps.indic.W.decay(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
 \begin{align*}
 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \xi_i D_{i,t} + \varepsilon_{i,t},\\
 	\xi_i &= \alpha_i \cdot e^{-(t-T_i^*-1)} \\
 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
 \end{align*}
 where $D_{i,t}=I(t > T_i^*+1)$. Note that only $\eta_i, \phi_i, \alpha_i, \bs{\theta}$ are estimable. This model captures the type of the shock that has exponential decay.

 Examples are similar to those for \texttt{ps.indic.W.permanent}.

 \section{\texttt{ps.indic.W.decay.nls}}

 \texttt{ps.indic.W.decay.nls(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
 \begin{align*}
 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \xi_i D_{i,t} + \varepsilon_{i,t},\\
 	\xi_i &= \alpha_i \cdot e^{-c(t-T_i^*-1)} \\
 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
 \end{align*}
 where $D_{i,t}=I(t > T_i^*+1)$. Note that only $\eta_i, \phi_i, \alpha_i, \bs{\theta},c$ are estimable. This model  is more general than \texttt{ps.indic.W.decay} with enabling estimability of the speed of the exponential decay, $c$. The estimation is based on \texttt{nls} function. Note that singularity problems may occur for this model when applied to complicate or large dataset.

 Examples are similar to those for \texttt{ps.indic.W.permanent}.

\bibliography{synthetic-prediction-notes.bib}
\end{document}

### 2021-11-16 prevalence_testing/postshocktest2021draft.tex
addition of manual and edits to manuscript

@@
 Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information.
-In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an unbiased estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate.
-However, the unbiased estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.
+In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an consistent estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate.
+However, the consistent estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.
 To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear.
 However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.
+
+ With the presence of autoregressive parameters in some models, unbiased estimation with OLS  is not feasible but the bias is $O(T^{-1})$, where $T$ is the time series length \citep{shaman1988bias}.
+In this paper, we use the OLS estimates to approximate the adjusted conditional mean forecast and unadjusted one.
+The bias decades away as $T\to \infty$.
 

### 2021-11-18 prevalence_testing/manual.tex
edits to manual and COP.R

@@
 The covariates should be in the class of \texttt{matrix} with size $T_i\times p$ for $i = 1, \ldots, n+1$.
-	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+1$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$.
+	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+2$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$. 
 	\item \texttt{Y} is a list of responses with length $n +1$,  where the first element of the list should be the response of the time series of interest and the remaining elements of the list are the responses of the donors.
 It should be a vector.
+Note  that to compute the lag, the effective sample size used is $T_i - 1$, where $T_i$ is the time series length of $i$th time series.
 \end{itemize}
@@
 Tstar <- c() # Shock Time Points
-for (t in T) {
+for (t in Ts) {
   Tstar <- c(Tstar, sample((p + 3 + 1):(t - 1), size = 1))
@@
   Tstari <- Tstar[i]
-  Ki <- K[i]
-  X[[i]] <- matrix(rgamma(n = p * (Ti + Ki + H + 1),
+  X[[i]] <- matrix(rgamma(n = p * (Ti + 1),
                           shape = 1, scale = 1), ncol = p, byrow = TRUE) 
@@
 Suppose the donor pool size is $n$.
+\emph{It is important to note that the ordering of the donors should be with respect to the timing when those time series occur, from the earliest to the latest.}
+
  The input for this function is
 \begin{itemize}
-	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+1$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$.
+	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+2$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$. 
 	\item \texttt{Y} is a list of responses with length $n +1$,  where the first element of the list should be the response of the time series of interest and the remaining elements of the list are the responses of the donors.
 It should be a vector.
+Note  that to compute the lag, the effective sample size used is $T_i - 1$, where $T_i$ is the time series length of $i$th time series.
 	\item \texttt{X} is a list of covariates with length $n+1$, where the first element of the list should be the covariates of the time series of interest and the remaining elements of the list are the covariates of the donors.
@@
 \texttt{K} has a length of $n+1$.
-The first element of \texttt{K} can be \texttt{NA} as forecast comparison is not available for the time series of interest.
+If \texttt{retro = FALSE}, \texttt{K[1]} can be \texttt{NA}.
 	\item \texttt{H} is the maximum $h$ that an $h$-step forecast that is wished to be considered in the multi-horizon forecast comparison testing procedure in \citeA{quaedvlieg2021multi}.
@@
 	\item \texttt{sig.levl} is the significance level for the test. It is 0.05 in default.
+	\item \texttt{retro} is a logical value indicating \texttt{TRUE} or \texttt{FALSE}.
+If  \texttt{TRUE}, the $p$-value for the time series of interest will be computed.
+If  \texttt{FALSE}, only the $p$-values of donors will be computed.
+This argument is intended for retrospective data analysis where the $p$-value of the time series of interest is needed.
 \end{itemize}
@@
 
- \texttt{ps.indic.W.complicate(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
+ \texttt{ps.indic.W.complicate(Tstar,Y,X,K,H,Ts,q1,q2,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
  \begin{align*}
  	y_{i,t}
- 	&= \left(\eta_i + \sum_{j=1}^{q_2} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
+ 	&= \left(\eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
  	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
@@
 The role of the shock in this model is that the dynamics of $y_{i,t}$ change after the shock.
+Note that to prepare the lagged response and covariates, the effective sample size is $T_i-\max\{q_1, q_2-1\}$.
+Note that current code only allows for $q_2\leq q_1 + 1$.
 

### 2021-11-18 prevalence_testing/numerical_studies/COP.R

@@ -108,32 +108,98 @@ taSPA.mhfc <- function(ell, d, B, bw = 4) {
   return(p)
 }
 
+ols.est.alphahat <- function(Tstar, Y, X) {
+  
+  n <- length(Y) - 1
+  T <- c()
+  for (i in 1:(n + 1)) {
+    T <- c(T, length(Y[[i]]) - 1)
+  }
+  
+  # empty
+  alphahat <- c()
+  se <- c()
+  res <- c()
+  lmod <- c()
+  
+  
+  for (i in 2:(n + 1)) {
+    
+    # set up
+    Ti <- T[i]
+    Tstari <- Tstar[i]
+    yi <- Y[[i]][-1]
+    xi <- X[[i]][-1, ]
+    
+    # lag
+    yilag <- Y[[i]][-Ti]
+    
+    # OLS
+    lmodi <- lm(yi ~ 1 + ifelse(1:(Ti-1) == Tstari + 1, yes = 1, no = 0) + 
+                  yilag + xi)
+    
+    # find estimates
+    alphahat <- c(alphahat, coef(lmodi)[2])
+    se <- c(se, summary(lmodi)$coef[2, 2])
+    res[[i - 1]] <- residuals(lmodi)
+    lmod[[i - 1]] <- lmodi
+  }
+  
+  # uname
+  names(alphahat) <- names(se) <- NULL
+  
+  # adjustment estimator
+  alphahat.adj <- mean(alphahat)
+  
+  # weighted adjustment estimator
+  if (is.matrix(X[[1]]) == FALSE) {
+    for (i in 1:(n + 1)) {
+      X[[i]] <- as.matrix(X[[i]])
+    }
+  }
+  # Weights
+  W <- round(scm(X = X, Tstar = Tstar)$par, digits = 3)
+  # Computation
+  alphahat.wadj <- as.numeric(crossprod(W, alphahat))
+  
+  # Inverse-Variance Estimator
+  alphahat.IVW <- sum(alphahat / se ^ 2) /  (sum(1 / se ^ 2))
+  
+  est <- c(alphahat.adj, alphahat.wadj, alphahat.IVW)
+  names(est) <- c('adj', 'wadj', 'IVW')
+  
+  # output
+  return(list(alphahat = alphahat, est = est, Tstar = Tstar, X = X, Y = Y, 
+              lmod = lmod, res = res, Wstar = W, se = se))
+  
+}
+
[…]

### 2021-11-18 prevalence_testing/postshocktest2021draft.tex

@@
 
-\begin{prop}
+\begin{prop} \label{prop:donor}
 	Let $\bf{y}_{i,t}$, $i = 1,\ldots,n_i$, $t = 1,\ldots, T$ be a collection of independent time series.
@@
 
-\noindent\textbf{This needs some work (ignore for now)} Now consider a case where there exists a $2 \leq i' < n + 1$ where $\x_{1,t} = \x_{i',t}$.
-Now suppose for simplicity that $T^*_{j'} = T^*_1$ and that $T_{i'} = T_1$ where $T_1 > T^*_1 + q_1 + q_2 + 2$.
-This assumes that we have data for the first time series beyond the shock point.
-We will show that when there is a covariate clone of the time series under study, then estimation in this series will approximate estimation in the time series under study provided that the underlying variability is very small relative to the signal.
-To see this, consider $t > T^*_1$, where
+\begin{cor} \label{cor:differences}
+	Let $\bf{y}_{i,t}$, $i = 1,\ldots,n_i$, $t = 1,\ldots, T$ be a collection of independent time series.
+Let each time series $\bf{y}_{i,t}$ be generated by model \eqref{model-gen} with accompanying random effects structure \eqref{random-effects}, where $y_{i,t}$ is a scalar response $\x_{i,t} \in \R^p$ is a fixed vector of covariates.
+Suppose that there is a common shock time $p + 2 < T^* < T - (p+2)$ where $q_1 = q_2 = 1$, $\|\x_{i,t}\| = 1$, each entry of $\x_{i,t}$ is non-negative, $\mu_{\min} > 0$, and $y_{i,0} = 0$.
+Let $i' \geq 2$ be an index.
+Assume that $\Var(y_{1,t})$, $\Var(y_{i',t}) \geq b$ for all $t$.
+Assume the conditions of Proposition~\ref{prop:donor}.
+Then we can choose an $\varepsilon > 0$ such that
+	$$
+	  \left\vert \frac{\E(y_{1,t})}{\Var(y_{1,t})} - \frac{\E(y_{i',t})}{\Var(y_{i',t})} \right\vert \leq \varepsilon,
+	$$
+	for all $1 \leq t \leq T$.
+\end{cor}
+
+\begin{proof}
+	From Proposition~\ref{prop:donor} we can pick an arbitrary number $\delta > 0$ such that $\left\vert\E(y_{i,t} - y_{i',t})\right\vert \leq \delta$ and $|\Var(y_{1,t}) - \Var(y_{i',t})| < \delta$ for all $t = 1,\ldots,T$.
+The conclusion follows from Lemma~\ref{lem:diffsig2noise}.
+\end{proof}
+
+This is some justification for the idea that one may be able to make inferences about the time series of interest using a time series from the donor pool.
+
+\vspace*{0.5cm}
+
+\noindent \textbf{Doodles}:
 \begin{align*}
-y_{1,t} &= \eta_1 + \mu_\alpha + \delta_1'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} + \sum_{j=0}^{q_2-1}(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{1} + \varepsilon_{1,t}, \\
-y_{i',t} &= \eta_{i'} + \mu_\alpha + \delta_{i'}'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} + \sum_{j=0}^{q_2-1}(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{i'} + \varepsilon_{i',t}, \\
-\hat y_{1,t} &= \hat \eta_1 + \hat{\alpha}_1(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat y_{1,t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}, \\
-\hat y_{i',t} &= \hat\eta_{i'} + \hat{\alpha}_{i'}(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat y_{i',t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j},
+  &\Prob\left(\left\vert |y_{1,t} - \E(y_{1,t})| - |y_{i',t} - \E(y_{i',t})| \right\vert \leq \varepsilon_1\right) 
+  \geq \Prob\left(|y_{1,t} - \E(y_{1,t})| \leq \varepsilon_1/2,  |y_{i',t} - \E(y_{i',t})| \leq \varepsilon_1/2\right) \\
+  &\qquad = \Prob\left(|y_{1,t} - \E(y_{1,t})| \leq \varepsilon_1/2\right) \Prob\left(|y_{i',t} - \E(y_{i',t})| \leq \varepsilon_1/2\right) \\
+  &\qquad \geq \left(1 - \frac{4\Var(y_{1,t})}{\varepsilon_1^2}\right)\left(1 - \frac{4\Var(y_{i',t})}{\varepsilon_1^2}\right) \\
+  &\qquad \geq \left(1 - \frac{4\E(y_{1,t})}{\varepsilon_1^2C}\right)\left(1 - \frac{4\E(y_{i',t})}{\varepsilon_1^2C}\right),
+  %&\qquad = 1 - \frac{4\E(y_{1,t})}{\varepsilon^2C} - \frac{4\E(y_{i',t})}{\varepsilon^2C} + \frac{16\E(y_{1,t})\E(y_{i',t})}{\varepsilon^4C^2},
 \end{align*}
-where $\alpha_j(\x) = \mu_\alpha + \delta_j'\x$, and we have 
+for all $t = 1,\ldots,T$ where the second inequality follows from Chebyshev's inequality and the last inequality follows from Proposition~\ref{prop:signaltonoise}.
+
+\vspace*{0.5cm}
+The above argument implies that a $C$ can be chosen so that 
 \begin{align*}
-  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\right] \\
-  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} - (\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{1,t} \Bigg\vert \\
-  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\right] \\
-  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} - (\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{i',t} \Bigg\vert.
+  &|y_{1,t} - y_{i',t}| = |y_{1,t} - y_{i',t} \pm \E(y_{1,t}) \pm \E(y_{i',t})| \\
+  &\qquad = |(y_{1,t} - \E(y_{1,t})) - (y_{i',t} - \E(y_{i',t})) + (\E(y_{1,t}) - \E(y_{i',t}))| \\
+  &\qquad \leq |y_{1,t} - \E(y_{1,t})| + |y_{i',t} - \E(y_{i',t})| + |\E(y_{1,t}) - \E(y_{i',t})| \\
+  &\qquad \leq \varepsilon_2,
 \end{align*}
-\textbf{Needs finishing, but the argument is simple: estimation uncertainty declines as error variance decreases.
-And differences in the random effects decrease as variability decreases.} \vspace*{0.5cm}
+holds with high probability for all $t = 1,\ldots,T$ by Proposition~\ref{prop:donor}.
 
-%\begin{lem}[Technical Lemma 2] \label{lem1}
-%	Let $a_j, b_j \in \R$, $j = 1,2$, and $C > 0$ be such that $C \leq a_j/b_j \leq 2C$, $j = 1,2$. Further suppose that 
-%	$$
-%	  \frac{|a_1 - a_2|}{a_1 + a_2} < \frac{\varepsilon}{2C},
-%	$$
-%	for some $\varepsilon > 0$. Then 
-%	$$
-%	  \frac{|a_1 - a_2|}{b_1 + b_2} < \varepsilon.
-%	$$
-%\end{lem}
-
-%\begin{proof}
-%Observe that 
-%$$
-%  |a_1 - a_2| < \frac{\varepsilon(a_1 + a_2)}{2C} 
-%	  = \frac{\varepsilon(b_1(a_1/b_1) + b_2(a_2/b_2))}{2C} 
-%	  \leq \frac{\varepsilon(2b_1C + 2b_2C)}{2C} 
-%	  = \varepsilon(b_1 + b_2).
-%$$
-%The conclusion immediately follows from the above.
-%\end{proof}
-
-%\begin{prop} \label{prop:signaltonoisediff}
-%	Suppose the conditions of Proposition~\ref{prop:signaltonoise} where $C$ is chosen so that 
-%	\begin{equation} \label{signal-to-noise2}
-%	  C \leq \frac{\E(y_{i,t})}{\Var(y_{i,t})} \leq 2C,
-%	\end{equation}
-%	for all $i$ and $1 \leq t \leq T$. Let $2 < i' < n + 1$ be the index of a time series in the donor pool for which CONDITIONS then for some $\varepsilon > 0$ we have 
-%	$$
-%	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\Var(y_{i,t} - y_{i',t})} < \varepsilon
-%	$$
-%\end{prop}
-
-%\begin{proof}
-%	First suppose that we have 
-%	\begin{equation} \label{prop:cond}
-%	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\E(y_{i,t} + y_{i',t})} \leq \frac{\varepsilon}{2C}.		
-%	\end{equation}
-%	Then Lemma~\ref{lem:absdiff} combined with the assumed conditions imply the conclusion of this proposition. We now verify that \eqref{prop:cond} holds.
-%Suppose that:
-%\begin{align*}
-%  |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| &< \gamma \\
-%  |\mu_{\tilde\theta_1}'\x_{1,T^*+1} - \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1}| &< \gamma \\
-%  \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}\right\vert &< \gamma, \qquad \text{for all} \; t \\
-%  |\mu_{\tilde\phi_1}^j - \mu_{\tilde\phi_{i'}}^j| &< \gamma, \qquad \text{for all} \; j \\
-%  \mu_\delta'\x_{1,T^*+1} + \mu_\delta'\x_{i',T^*+1} &> D
-%\end{align*}
-%Similarly, 
-%\begin{align*}
-%	&\E(y_{i,t} + y_{i',t}) = \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
-%		&\qquad + \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{i}}^{t - T^*} + \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{i}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j}) + \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j})\right)\mu_{\phi}^j\right].
-%\end{align*}
-%\end{proof}
-
-%Let 
-%$$
-%  \rho_\text{min} = \min\left\{
-%    \frac{\mu_\eta}{\sigma^2_\eta}, 
-%    \frac{\|\mu_{\delta}\|}{\|\Sigma_\delta\|},
-%    \frac{\|\mu_{\theta}\|}{\|\Sigma_\theta\|},
-%    \frac{\|\mu_{\phi}\|}{\|\Sigma_\phi\|},
-%    \frac{\|\mu_{\tilde\theta}\|}{\|\Sigma_{\tilde{\theta}}\|},
-%    \frac{\|\mu_{\tilde\phi}\|}{\|\Sigma_{\tilde{\phi}}\|}             
-%  \right\},
-%$$
-%and let
-%$$
-%  \rho_\text{max} = \max\left\{
-%    \frac{\mu_\eta}{\sigma^2_\eta}, 
-%    \frac{\|\mu_{\delta}\|}{\|\Sigma_\delta\|},
-%    \frac{\|\mu_{\theta}\|}{\|\Sigma_\theta\|},
-%    \frac{\|\mu_{\phi}\|}{\|\Sigma_\phi\|},
-%    \frac{\|\mu_{\tilde\theta}\|}{\|\Sigma_{\tilde{\theta}}\|},
-%    \frac{\|\mu_{\tilde\phi}\|}{\|\Sigma_{\tilde{\phi}}\|}             
-%  \right\}.
-%$$
+\vspace*{0.5cm}
+Add condition that $\text{argmax}_t\|\x_{1,t} - \x_{i',t}\| < \delta$. Then the OLS estimates satisfy 
+$$
+  \|(\hat\eta_1,\hat\phi_1,\hat\theta_1',\hat\alpha_1)' - 
+    (\hat\eta_{i'},\hat\phi_{i'},\hat\theta_{i'}',\hat\alpha_{i'})'\| < \varepsilon_3
+$$
+with high probability, and therefore $\left\vert|y_{1,t} - \hat y_{i,t}| - |y_{i',t} - \hat y_{i',t}|\right\vert < \varepsilon_4$ with high probability for all $t = 1,\ldots,T$.
 

### 2021-12-05 prevalence_testing/postshocktest2021draft.tex
new codes for functions and data analysis and some addition to manuscript

--- 2021-11-16 prevalence_testing/postshocktest2021draft.tex
@@
 \begin{align*}
-  \mc{I}_n = \{i = \in 2,\ldots, n+1\colon 0< w_i < 1\}.
+  \mc{I}_n = \{i =  2,\ldots, n+1\colon 0< w_i < 1\}.
 \end{align*}
@@
 \end{proof}
+
+Note that asymptotic approximation for the misclassification error does not work when the weight is concentrated, i.e., $\mc{I}_n$ is finite even if $n\to \infty$, where $\mc{I}_n = \{i =  2,\ldots, n+1\colon 0< w_i < 1\}$.
+The intuition is that  it is impossible to find a weight to constrain the random behavior of the Bernoulli random variables $I(p_i\leq \alpha)$ for $i \in \mc{I}_n$ such that the weak law of large number can apply.
+Nevertheless, in this case, if $\kappa_i = \P(p_i\leq \alpha)$ for $i\in \mc{I}_n$ is small, the approximation for the misclassification in Corollary \ref{coro1} is favorable.
+This situation occurs very frequently in practice.
+It can be shown as below.
+
+Note that the mean squared error of estimating $\P(p_1\leq \alpha)=\kappa_1$ is
+\begin{align*}
+	\E\bigg\{ \Big\{ \sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)-\kappa_1 \Big\}^2 \bigg\}
+	&= \Big\{ \sum_{i\in \mc{I}_n} w_i \kappa_i -\kappa_1 \Big\}^2 + \var 
+	\Big\{\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha) \Big\}\\
+	&= \Big\{ \sum_{i\in \mc{I}_n} w_i \kappa_i -\kappa_1 \Big\}^2  + \sum_{i\in \mc{I}_n} w_i^2 \kappa_i (1-\kappa_i) \\
+	& \overset{n\to \infty }{\to} \sum_{i\in \mc{I}_n} w_i^2 \kappa_i (1-\kappa_i) ,
+\end{align*}
+where the last second step assumes that $\{I(p_i\leq \alpha)\colon i\in \mc{I}_n\}$ are independent and the last step uses the condition $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_1$ as $n\to \infty$, which is used in Corollary \ref{coro1}.
+Notice that if $\kappa_i$ is very small, the mean squared error of $\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)$ turns out to be small such that by the rationale of the proof of Proposition \ref{votprop}, the asymptotic approximation for the misclassification error in  Corollary \ref{coro1} should be acceptable.
 
@@
 
+\section{Numerical Examples}
+
+\begin{table}[H]
+	\begin{center}
+		\begin{tabular}{cccccc}
+  \hline
+ & null & Permanent & Decay without scale & Decay with scale & Complicate \\ 
+  \hline
+TS2 & 239.71 & 241.70 & 241.71 & 242.91 & 236.17 \\ 
+  TS3 & 276.52 & 277.73 & 272.63 & 275.79 & 274.25 \\ 
+  TS4 & 215.67 & 212.55 & 214.45 & 211.37 & 198.31 \\ 
+  Mean & 243.97 & 244.00 & 242.93 & 243.36 & 236.24 \\ 
+  TS1 & 262.59 & 260.58 & 239.07 & 266.03 & 206.03 \\ 
+   \hline
+\end{tabular}
+	\end{center}	
+\end{table}
+
+\begin{table}
+\begin{center}
+  \begin{tabular}{cccccccccr}
+     $L$ ($T_i-T^*_i$) & Model & $p_1$ & $\mathbf{W}^*=(0,0,1)$ & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
+     \hline 
+     7 & Permanent & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $212.554$ \\
+     7 & Decaying & 0 && $0.395$ &  0 (incorrect)  & 0 (incorrect) & $214.447$ \\
+      7 & Complicate & 1 && $0.090$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 198.307 \\[.2cm]
+     15 & Permanent & 1 &  & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 249.637 \\
+     15 & Decaying & 0 & & 0 & \textcolor{red}{0} & \textcolor{red}{0}   & $250.107$  \\
+     15 & Complicate & 1 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  & $232.084$\\[.2cm]
+     30 & Permanent & 1 &  & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  302.089 \\
+     30 & Decaying & 0 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  &  $302.432$ \\
+     30 & Complicate & 1 & & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 298.345
+  \end{tabular}
+\end{center}	
+\end{table}
+
 \bibliographystyle{plainnat}

### 2021-12-05 prevalence_testing/numerical_studies/COP.R

@@ -135,7 +135,7 @@ ols.est.alphahat <- function(Tstar, Y, X) {
     yilag <- Y[[i]][-Ti]
     
     # OLS
-    lmodi <- lm(yi ~ 1 + ifelse(1:(Ti-1) == Tstari + 1, yes = 1, no = 0) + 
+    lmodi <- lm(yi ~ 1 + ifelse(1:Ti == Tstari + 1, yes = 1, no = 0) + 
                   yilag + xi)
     
     # find estimates
@@ -191,16 +191,17 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .
     Ki <- K[i]
     Tstari <- Tstar[i]
     
-    sym <- ols.est.alphahat(Tstar = Tstar[c(i, 2:(i - 1))], X = X[c(i, 2:(i - 1))], Y = Y[c(i, 2:(i - 1))])
+    if (i > 2) {
+      sym <- ols.est.alphahat(Tstar = Tstar[c(i, 2:(i - 1))], X = X[c(i, 2:(i - 1))], Y = Y[c(i, 2:(i - 1))])
+      alpha.wadj <- sym$est[2]
+    }
     
-    alpha.wadj <- sym$est[2]
-    
-    m1.L.i <- matrix(NA, nrow = Ti, ncol = H)
-    m2.L.i <- matrix(NA, nrow = Ti, ncol = H)
+    m1.L.i <- matrix(NA, nrow = Ti - Ki - H, ncol = H)
+    m2.L.i <- matrix(NA, nrow = Ti - Ki - H, ncol = H)
     
     # compute losses
     for (h in 1:H) {
-      for (t in 1:Ti) {
+      for (t in 1:(Ti - Ki - H)) {
         
         yi <- Y[[i]][-1][(t + H - h + 1):(t + Ki + H - h)]
         xi <- X[[i]][-1, ][(t + H - h + 1):(t + Ki + H - h),]
@@ -221,19 +222,17 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .
         yhat.adj <- tail(yi, 1)
         yhat.unadj <- tail(yi, 1)
         
-        
-        if (t + Ki + H - h <= Tstari + 1 & i >= 3) {
-          
-          
-        }
-        
         for (j in 1:h) {
[…]

### 2021-12-05 prevalence_testing/postshocktest2021draft.tex
new codes for functions and data analysis and some addition to manuscript

@@
 \begin{table}[H]
-	\begin{center}
-		\begin{tabular}{cccccc}
-  \hline
- & null & Permanent & Decay without scale & Decay with scale & Complicate \\ 
-  \hline
-TS2 & 239.71 & 241.70 & 241.71 & 242.91 & 236.17 \\ 
-  TS3 & 276.52 & 277.73 & 272.63 & 275.79 & 274.25 \\ 
-  TS4 & 215.67 & 212.55 & 214.45 & 211.37 & 198.31 \\ 
-  Mean & 243.97 & 244.00 & 242.93 & 243.36 & 236.24 \\ 
-  TS1 & 262.59 & 260.58 & 239.07 & 266.03 & 206.03 \\ 
-   \hline
-\end{tabular}
-	\end{center}	
-\end{table}
-
-\begin{table}
+	\caption{Results for Cocono Philips}
 \begin{center}
@@
      15 & Permanent & 1 &  & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 249.637 \\
-     15 & Decaying & 0 & & 0 & \textcolor{red}{0} & \textcolor{red}{0}   & $250.107$  \\
-     15 & Complicate & 1 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  & $232.084$\\[.2cm]
+     15 & Decaying & 0 & & 0 & \textcolor{red}{1} & \textcolor{red}{1}   & $250.107$  \\
+     15 & Complicate & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $232.084$\\[.2cm]
      30 & Permanent & 1 &  & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  302.089 \\

### 2021-12-05 prevalence_testing/numerical_studies/COP.R

@@ -196,12 +196,12 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .
       alpha.wadj <- sym$est[2]
     }
     
-    m1.L.i <- matrix(NA, nrow = Ti - Ki - H, ncol = H)
-    m2.L.i <- matrix(NA, nrow = Ti - Ki - H, ncol = H)
+    m1.L.i <- matrix(NA, nrow = Ti - Ki - H - 1, ncol = H)
+    m2.L.i <- matrix(NA, nrow = Ti - Ki - H - 1, ncol = H)
     
     # compute losses
     for (h in 1:H) {
-      for (t in 1:(Ti - Ki - H)) {
+      for (t in 1:(Ti - Ki - H - 1)) {
         
         yi <- Y[[i]][-1][(t + H - h + 1):(t + Ki + H - h)]
         xi <- X[[i]][-1, ][(t + H - h + 1):(t + Ki + H - h),]
@@ -261,7 +261,7 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .
   return(list(ps = ps, W = W, Is = Is, AIC = AIC, BIC = BIC))
 }
 
-ps.indic.W.decay <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05) {
+ps.indic.W.decay <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05, retro = TRUE) {
   
   n <- length(Y) - 1
   
@@ -283,12 +283,12 @@ ps.indic.W.decay <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05) 
     }
     
     
-    m1.L.i <- matrix(NA, nrow = Ti - Ki - H, ncol = H)
-    m2.L.i <- matrix(NA, nrow = Ti - Ki - H, ncol = H)
+    m1.L.i <- matrix(NA, nrow = Ti - Ki - H - 1, ncol = H)
+    m2.L.i <- matrix(NA, nrow = Ti - Ki - H - 1, ncol = H)
     
     # compute losses
     for (h in 1:H) {
-      for (t in 1:(Ti - Ki - H)) {
+      for (t in 1:(Ti - Ki - H - 1)) {
         
         yi <- Y[[i]][-1][(t + H - h + 1):(t + Ki + H - h)]
[…]

### 2021-12-07 prevalence_testing/manual.tex
new codes for functions and data analysis and some addition to manuscript
change of complicate to dynamic

@@
 	\item \texttt{Ts} is a vector of length $n+1$, and it specifies the length of the time series (ordered from the time series of interest to donors).
+Note that for each element of \texttt{Ts}, it should be at least greater than or equal to $K_i + H + 2$.
 	\item \texttt{ell} is the block length of the moving block bootstrap. See details in \texttt{taSPA.mhfc}.
@@
 
- \section{\texttt{ps.indic.W.complicate}}
+ \section{\texttt{ps.indic.W.dynamic}}
 
- \texttt{ps.indic.W.complicate(Tstar,Y,X,K,H,Ts,q1,q2,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
+ \texttt{ps.indic.W.dynamic(Tstar,Y,X,K,H,Ts,q1,q2,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
  \begin{align*}
@@
 Note that to prepare the lagged response and covariates, the effective sample size is $T_i-\max\{q_1, q_2-1\}$.
-Note that current code only allows for $q_2\leq q_1 + 1$.
+Note that for each element of \texttt{Ts}, it should be at least greater than or equal to $K_i + H + \max\{q_1, q_2-1\}+1$.
 

### 2021-12-07 prevalence_testing/postshocktest2021draft.tex
change of complicate to dynamic

@@
      7 & Decaying & 0 && $0.395$ &  0 (incorrect)  & 0 (incorrect) & $214.447$ \\
-      7 & Complicate & 1 && $0.090$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 198.307 \\[.2cm]
+      7 & Dynamic & 1 && $0.090$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 198.307 \\[.2cm]
      15 & Permanent & 1 &  & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 249.637 \\
      15 & Decaying & 0 & & 0 & \textcolor{red}{1} & \textcolor{red}{1}   & $250.107$  \\
-     15 & Complicate & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $232.084$\\[.2cm]
+     15 & Dynamic & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $232.084$\\[.2cm]
      30 & Permanent & 1 &  & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  302.089 \\
      30 & Decaying & 0 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  &  $302.432$ \\
-     30 & Complicate & 1 & & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 298.345
+     30 & Dynamic & 1 & & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 298.345
   \end{tabular}

### 2021-12-07 prevalence_testing/numerical_studies/COP.R

@@ -352,7 +352,7 @@ ps.indic.W.decay <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05, 
 }
 
 # functions that return alpha.hat and synthetic weights for decaying shock effects
-ps.indic.W.complicate <- function(Tstar, Y, X, K, H, Ts,
+ps.indic.W.dynamic <- function(Tstar, Y, X, K, H, Ts,
                                   q1, q2, 
                                   ell, B, bw, sig.levl = .05, retro = TRUE) {
   
@@ -698,18 +698,18 @@ for (d in 1:nrow(TS2)) {
 }
 co.D <- as.matrix(co.D)
 
-m_COP.complicate <- lm(TS2$Y ~ as.matrix(TS2[, c(2:7, 9:14)]) + co.D + TS2$start_day_20080317)
+m_COP.dynamic <- lm(TS2$Y ~ as.matrix(TS2[, c(2:7, 9:14)]) + co.D + TS2$start_day_20080317)
 
 # AICs
 AIC.20080314.null <- AIC(m_COP_3_17.null)
 AIC.20080314.permanent <- AIC(m_COP_3_17)
 AIC.20080314.decay1 <- AIC(m_COP.exp)
 AIC.20080314.decay2 <- AIC(m_COP.decay)
-AIC.20080314.complicate <- AIC(m_COP.complicate)
+AIC.20080314.dynamic <- AIC(m_COP.dynamic)
 
 AIC.20080314 <- c(AIC.20080314.null, AIC.20080314.permanent, 
                   AIC.20080314.decay1, AIC.20080314.decay2,
-                  AIC.20080314.complicate)
+                  AIC.20080314.dynamic)
 
 #### 2008 shock effects
 
@@ -739,7 +739,7 @@ for (d in 1:nrow(TS3)) {
 }
 co.D <- as.matrix(co.D)
 
-m_COP.complicate <- lm(TS3$Y ~ as.matrix(TS3[, c(2:7, 9:14)]) + co.D + TS3$start_day_20080908)
+m_COP.dynamic <- lm(TS3$Y ~ as.matrix(TS3[, c(2:7, 9:14)]) + co.D + TS3$start_day_20080908)
 
 
 # AICs
@@ -747,11 +747,11 @@ AIC.20080908.null <- AIC(m_COP_null)
 AIC.20080908.permanent <- AIC(m_COP_Sept_08) 
[…]

### 2021-12-18 prevalence_testing/manual.tex
revision to the codes and addition of results

@@
 	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+1$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$.
+	\item The default for \texttt{scale} is \texttt{scale = FALSE}.
+If \texttt{scale = TRUE}, the function  collects $\mc{Q}=\{\mathbf{x}_{i, T_i^*+1}\colon i = 1, \ldots, n+1\}$ and scale and center within $\mc{Q}$, i.e., center by the sample mean of $\{x_{i, j, T_i^*+1} \colon i = 1, \ldots, n+1\}$, where $j$ index stands for the $j$th variable.
 \end{itemize}
@@
 This argument is intended for retrospective data analysis where the $p$-value of the time series of interest is needed.
+	\item \texttt{scale} option can allow users to compute weights based on scaled covariates or not. See details in \texttt{scm}.
 \end{itemize}
@@
 
- \texttt{ps.indic.W.dynamic(Tstar,Y,X,K,H,Ts,q1,q2,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
+ \texttt{ps.indic.W.dynamic(Tstar,Y,X,K,H,Ts,q1,q2,ell,B,bw,sig.levl)} performs the similar functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
  \begin{align*}
@@
 
-Examples are similar to those for \texttt{ps.indic.W.permanent}.
-
-\section{\texttt{ps.indic.W.decay}}
-
- \texttt{ps.indic.W.decay(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
- \begin{align*}
- 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \xi_i D_{i,t} + \varepsilon_{i,t},\\
- 	\xi_i &= \alpha_i \cdot e^{-(t-T_i^*-1)} \\
- 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
- \end{align*}
- where $D_{i,t}=I(t > T_i^*+1)$. Note that only $\eta_i, \phi_i, \alpha_i, \bs{\theta}$ are estimable. This model captures the type of the shock that has exponential decay.
-
- Examples are similar to those for \texttt{ps.indic.W.permanent}.
-
- \section{\texttt{ps.indic.W.decay.nls}}
-
- \texttt{ps.indic.W.decay.nls(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} performs the same functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
- \begin{align*}
- 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \xi_i D_{i,t} + \varepsilon_{i,t},\\
- 	\xi_i &= \alpha_i \cdot e^{-c(t-T_i^*-1)} \\
- 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
- \end{align*}
- where $D_{i,t}=I(t > T_i^*+1)$.
-Note that only $\eta_i, \phi_i, \alpha_i, \bs{\theta},c$ are estimable.
-This model  is more general than \texttt{ps.indic.W.decay} with enabling estimability of the speed of the exponential decay, $c$.
-The estimation is based on \texttt{nls} function.
-Note that singularity problems may occur for this model when applied to complicate or large dataset.
+Additional functionality of \texttt{ps.indic.W.dynamic} compared to \texttt{ps.indic.W.permanent} is the specification of \texttt{nolag.i.x}, which allows users to add extra covariates that are not wished to be lagged in the model of $y_{i,t}$.
+\texttt{nolag.i.x} should be a list object of length two with the first element being a vector of indices referencing to the donor.
+The second element should be a list object with elements being the added covariates (of matrix or vector type) that are not wished to be lagged.
 

### 2021-12-18 prevalence_testing/postshocktest2021draft.tex
revision to the codes and addition of results

@@
 
+\newpage
+
 \section{Numerical Examples}
@@
 \begin{table}[H]
-	\caption{Results for Cocono Philips}
+	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.221, 0, 0.779)$ from scaled covariates}
 \begin{center}
   \begin{tabular}{cccccccccr}
-     $L$ ($T_i-T^*_i$) & Model & $p_1$ & $\mathbf{W}^*=(0,0,1)$ & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
+     $L$ ($T_i-T^*_i$) & Model & $p_1$ &  $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
      \hline 
-     7 & Permanent & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $212.554$ \\
-     7 & Decaying & 0 && $0.395$ &  0 (incorrect)  & 0 (incorrect) & $214.447$ \\
-      7 & Dynamic & 1 && $0.090$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 198.307 \\[.2cm]
-     15 & Permanent & 1 &  & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 249.637 \\
-     15 & Decaying & 0 & & 0 & \textcolor{red}{1} & \textcolor{red}{1}   & $250.107$  \\
-     15 & Dynamic & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $232.084$\\[.2cm]
-     30 & Permanent & 1 &  & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  302.089 \\
-     30 & Decaying & 0 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  &  $302.432$ \\
-     30 & Dynamic & 1 & & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 298.345
+     7 & Permanent & 1  & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $289.61$ \\      7 & Dynamic & 1 & $0$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 420.86 \\[.2cm]
+     15 & Permanent & 1   & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 294.74 \\
+     15 & Dynamic & 1 & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $416.12$\\[.2cm]
+     30 & Permanent & 1   & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  303.88 \\
+     30 & Dynamic & 1  & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 435.22
+  \end{tabular}
+\end{center}	
+\end{table}
+
+\begin{table}[H]
+	\caption{Results for Conoco Philips ($n=5$), $\mbf{W}^* = (0, 0, 0, 0.363, 0.637)$ from scaled covariates}
+\begin{center}
+  \begin{tabular}{cccccccccr}
+     $L$ ($T_i-T^*_i$) & Model & $p_1$  & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
+     \hline 
+     7 & Permanent & 1  & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $236.21$ \\
+      7 & Dynamic & 1 & $0$   &  \textcolor{red}{0} & \textcolor{red}{0}  & $324.91$ \\[.2cm]
+     15 & Permanent & 1   & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 273.95 \\
+     15 & Dynamic & 1  & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $370.83$\\[.2cm]
+     30 & Permanent & 1   & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  346.17 \\
+     30 & Dynamic & 1 & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 451.16
   \end{tabular}

### 2021-12-18 prevalence_testing/numerical_studies/COP2.R

@@ -280,8 +280,8 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .
 
 # functions that return alpha.hat and synthetic weights for decaying shock effects
 ps.indic.W.dynamic <- function(Tstar, Y, X, K, H, Ts,
-                               q1, q2, 
-                               ell, B, bw, sig.levl = .05, retro = TRUE,
+                                  q1, q2, 
+                                  ell, B, bw, sig.levl = .05, retro = TRUE,
                                nolag.i.x = NA, selfW = NA, scale = FALSE) {
   
   n <- length(Y) - 1
@@ -445,7 +445,7 @@ ps.indic.W.dynamic <- function(Tstar, Y, X, K, H, Ts,
           }
         }
         
-        
+
         
         # losses
         m1.L.i[t, h] <- sel(y = Y[[i]][-1][t + Ki + H], yhat = yhat.adj[h + q1])
@@ -480,7 +480,6 @@ ps.indic.W.dynamic <- function(Tstar, Y, X, K, H, Ts,
 
 # set working directory
 setwd("~/Library/Mobile Documents/com~apple~CloudDocs/Desktop/Research/Post-Shock Prediction/")
-
 
 ## Conoco Phillips
 getSymbols('COP', from = "2000-01-01")
@@ -550,6 +549,7 @@ for (i in 1:length(tom)) {
 Y <- COP_close$COP_Close[-1]
 
 # data frame
+# important: the date of Y is the date in the dataframe plus one day
 COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
 
 COP_close <- data.frame(COP_close[-1, ], COP_close[-nrow(COP_close), -c(1,8)])
@@ -576,14 +576,12 @@ TS2 <- COP_close[(start - (1 + 15 + K + H)):(start + L),]
 # inflation adjustment
 TS2[, 2:8] <- TS2[, 2:8] * inflation_adj$dollars_2020[inflation_adj$year == 2008] 
 
-
 m_COP_3_17.null <- lm(Y ~ COP_Close + GSPC_Close + WTI_Close + 
-                   USD_Close + TB_Close, 
[…]

### 2022-01-09 prevalence_testing/postshocktest2021draft.tex
addition of data analysis of COP

--- 2021-12-07 prevalence_testing/postshocktest2021draft.tex
@@
 \label{votprop}Suppose $p_2, \ldots, p_{n+1}$ is  a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest.
-If $\P(p_1 \leq \alpha) \neq 0.5$,
+If $\P(p_1 \leq \alpha) \neq 0.5$,  as $n\to \infty$,
 \begin{align*}
@@
 where $\kappa_i =  \P(p_i \leq \alpha)\in [0,1]$ for $i \in \mc{I}_n$, $\alpha$ is the significance level, $\kappa_1 = \P(p_1 \leq \alpha)$, and  $p_1$ is the p-value of the time series of interest.
-If $\P(p_1 \leq \alpha) \neq 0.5$,
+If $\P(p_1 \leq \alpha) \neq 0.5$, as $n\to \infty$,
 \begin{align*}
@@
 
+\newpage
+
 \section{Numerical Examples}
 
+In this section, we illustrate shock prevalence testing using two real data examples.
+Section \ref{sptcop} discusses the prevalence testing of the shock that Conoco Phillips stock experienced on March 9th, 2020.
+
+\subsection{Testing shock prevalence for Conoco Phillips stock price series}
+
+\label{sptcop}
+
+Post-shock  prevalence testing is motivated by post-shock prediction  \citep{lin2021minimizing} and also an extension of it from the perspective of hypothesis testing.
+Applying our methodology  on one of the datasets demonstrated in \cite{lin2021minimizing} helps connect our work to \cite{lin2021minimizing} and spell out the differences between two methodologies.
+
+As illustrated in Section 5.1 in \cite{lin2021minimizing}, it is found that Conoco Phillips stock price experienced unprecedented shocks due to  oil supply control and COVID-19 pandemic on one single day,  March 9th, 2020.
+In this data example, we are interested in investigating whether this shock is prevalent, i.e., whether the impact of the shock on the stock price will persist over time.
+Denote the stock price of Conoco Phillips at time $t$ as $y_{i,t}$ for $i$th time series, where $i = 1, \ldots n+1$, the time series of interest is ordered as the 1st time series, and $n$ is the donor pool size.
+We used the same covariates  as \cite{lin2021minimizing} did in the model of $y_{i,t}$, which are S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, and 13-week treasury bill rates.
+
+We considered the shock effects that occurred on March 15, 2008, September 2008, and November 27, 2014, where the rationale behind this selection is discussed in Section 5.1(3) in  \cite{lin2021minimizing}.
+However, we analyzed the multiple shock effects on September (September 8th, 2008; September 16th, 2008; and September 26, 2008) differently.
+Under the  setting of our methodology, it is possible that the occurrence of  those shocks can be modeled by one persistent shock effect or explained by that the model of $y_{i,t}$ changes after September 5th, 2008.
+In other words, we analyzed the three shock effects within one time series and considered three donors in our donor pool.
+
+To analyze the dataset, we propose two models. Denote the covariate matrix at time $t$ for $i$th time series by $\bs{x}_{i,t}$.  The first model $\mc{M}_1$, called ``permanent'' model, is 
+ \begin{align*}
+ 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
+ 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
+ \end{align*}
+where $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$ and $t = 1, \ldots, T_i$.
+Note that we allow the shock effect to take effect for multiple time points instead of one time point as in  \cite{lin2021minimizing}.
+This simple model describes the setting where one additive shock effect is persistent over time.
+The second model $\mc{M}_2$, called ``dynamic'' model, is
+\begin{align*}
+ 	y_{i,t}
+ 	&= \left(\eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
+ 	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
+ 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
+ \end{align*}
+ where $q_1 = q_2=2$,  $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$, and $t = 1, \ldots, T_i$.
+We estimate $\mc{M}_1$ and $\mc{M}_2$ using ordinary least squares (OLS) estimation.
+$\mc{M}_2$ adds more flexibility to $\mc{M}_1$ by allowing that the model of $y_{i,t}$ changes after the shock, as seen from the term related to $1-D_{i,t}$,  though the model still preserves the autoregressive model form.
+In practice, $\mc{M}_2$ should make more sense than $\mc{M}_1$ as it accommodates for more complicated cases.
+However, $\mc{M}_2$  requires far more degrees of freedom for estimation and this can increase variance in estimation.
+We used weighted AIC for model selection, which is detailed as follows.
+For $i$th donor in the donor pool, we can compute its AICs for $\mc{M}_1$ and $\mc{M}_2$, say $a^1_i$ and $a^2_i$, and also its synthetic weight $W_i^*$, where $\mbf{W}^* = (w_2^*, \ldots, w_{n+1}^*)$ and its computation is detailed in the next paragraph.
+Let $A^{1*}= \sum_{i=2}^{n+1} w_i^* a^1_i$ and $A^{2*}= \sum_{i=2}^{n+1} w_i^*a^2_i$.
+We will select $\mc{M}_1$ if $A^{1*} < A^{2*}$ and vice versa.
+
+ In computing the weights, to avoid the impact of unit differences from different columns of covariates on weighting, we center and scale the covariates. The steps are detailed as below. Consider
+\begin{align*}
+	\bs{X}= \begin{pmatrix}
+		\bs{x}_{1, T_1^*+1}\\
+		\vdots  \\
+		\bs{x}_{n+1, T_{n+1}^*+1}
+	\end{pmatrix},
+\end{align*}
+where $t = T_i^*+1$ is the time point when the shock effect takes place for $i$th time series.
+For each column of $\bs{X}$, we center it by subtracting its column mean and scale the resulting column vector by dividing the standard deviation of the resulting column vector.
+Denote the resulting covariates matrix by $\bs{X}^*$.
+We compute the synthetic weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}.
+However, for the model of $y_{i,t}$, we do not conduct such centering and scaling procedure.
+
+From the definition of $D_{i,t} = I(t > T_i^*+1)$, it is evident that the number of post-shock time points, i.e., time $t$ for which $t > T_i^*+1$, affects the inference results.
+As our methodology only requires $T_i-T_i^*$ is not small compared to $T_i$, we attempted three post-shock time length for our inference, say $L = 7, 15, 30$.
+Recall that in  Section \ref{forecast}, we refer to the forecast  that incorporates shock information as adjusted forecast and the one that does not as unadjusted forecast.
+As specified in Section \ref{forecast}, post-shock prevalence testing requires specification of  the maximum number $H$ of forecast horizons and training sample size $K$, where $h$-step forecasts of adjusted forecast and unadjusted forecast are compared for $h = 1, \ldots, H$.
+We set $H = 10$, $K = 30$, and $T_i =  H + K + L+15$ for $i = 2, \ldots, 4$.
+That being said, for $t = K + H + 1, \ldots, T_i$ and $h = 1, \ldots, H$, different $h$-step adjusted and unadjusted forecasts for $y_{i,t}$ under $\mc{M}_1$ or  $\mc{M}_2$ are compared.
+
 \begin{table}[H]
-	\caption{Results for Cocono Philips}
+	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.221, 0, 0.779)$ from scaled covariates} \label{coptable}
 \begin{center}
   \begin{tabular}{cccccccccr}
-     $L$ ($T_i-T^*_i$) & Model & $p_1$ & $\mathbf{W}^*=(0,0,1)$ & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
+     $L$  & Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
      \hline 
-     7 & Permanent & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $212.554$ \\
-     7 & Decaying & 0 && $0.395$ &  0 (incorrect)  & 0 (incorrect) & $214.447$ \\
-      7 & Dynamic & 1 && $0.090$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 198.307 \\[.2cm]
-     15 & Permanent & 1 &  & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 249.637 \\
-     15 & Decaying & 0 & & 0 & \textcolor{red}{1} & \textcolor{red}{1}   & $250.107$  \\
-     15 & Dynamic & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $232.084$\\[.2cm]
-     30 & Permanent & 1 &  & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  302.089 \\
-     30 & Decaying & 0 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  &  $302.432$ \\
-     30 & Dynamic & 1 & & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 298.345
+     7 & $\mc{M}_1$  & $289.61$ & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
+     7 & $\mc{M}_2$  & 420.86 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     15 & $\mc{M}_1$ & 294.74 & 1   & 0 &0 (Yes) & 0 (Yes)     \\
+     15 &  $\mc{M}_2$ & $416.12$ & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
+     30 &  $\mc{M}_1$ & 303.88 & 1   & $0$ & 0 (Yes) &0 (Yes)   \\
+     30 &  $\mc{M}_2$ & 435.22 & 1  & 0 &0 (Yes) & 0 (Yes)  
   \end{tabular}
@@
 \end{table}
+
+We implemented our analysis of the Conoco Phillips dataset and summarized the results in Table \ref{coptable}. We discuss our finding in several parts as follows.
+
+Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.221, 0, 0.779)$.
+It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second.
+As pointed out by \cite{lin2021minimizing} in Section 5.1(3), the shocks experienced by the first and  third donor are related to recessions, and oil supply shock, respectively.
+The results are intuitive in the sense that from a retrospective perspective of a data analyst, the shock experienced by the series $\{y_{1,t}\colon t = 1, \ldots, T_1\}$ is due to oil supply shock and recessions caused by COVID-19 pandemic.
+
+Additionally, from Table \ref{coptable}, for all $L = 7, 15, 30$, $\mc{M}_1$ is preferred over $\mc{M}_2$.
+Nevertheless, the inference results of  $\mc{M}_1$  do not differ from $\mc{M}_2$, as seen from the fourth column to the seventh column of Table \ref{coptable}.
+It is possible that   $\mc{M}_2$ is also a good fit for the dataset.
+
+It is important to note that $p_1$ is the $p$-value of the forecast comparison between adjusted forecast and unadjusted forecast if we have the data $\{y_{1,t} \colon 1, \ldots, T_1\}$, where $T_1 > T_1^*$.
+In other words, it cannot be computed without observing $y_{1, t}$ for $t > T_1^*$ and we present $p_1$ only for retrospective analysis.
+Also, $\hat{p}$ is the $p$-value from weighting the $p$-values of the forecast comparison  between adjusted and unadjusted forecast for donors using $\mbf{W}^*$.
+Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and models.
+It suggests $\hat{p}$ turns out to be a good estimate of $p_1$; and the test  using $\hat{p}$ fails to reject that  the shock, which was to take effect at $t=T_1^*+1$,  is prevalent for $t > T_1^*+1$ under a significance level of 5\%.
+
+Recall from Section \ref{forecast}, voting procedure suggests shock transience (shock prevalence) if the majority of the tests  suggests shock transience (shock prevalence, respectively).
+We record 0 if the voting procedure suggests shock transience and 1 if shock prevalence.
+The weighted voting procedure weight those testing indicators using $\mbf{W}^*$; and returns shock prevalence if the output exceeds 0.5 and shock transience if the output is smaller than 0.5.
+As we observe $\{y_{1,t} \colon 1, \ldots, T_1\}$, we are able to check whether the decision of voting and weighted voting is correct.
+From the sixth and seventh columns of Table \ref{coptable}, we can see that voting and weighted voting procedures suggest shock transience and this decision is consistent across different $L$ and different models.
+As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small.
+Note that Proposition \ref{votprop} and Corollary \ref{coro1} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$.
+
+To verify our results, we plot $\{y_{1,t} \colon 1, \ldots, T_1\}$ in Figure \ref{copshocktransience}.
+Two dashed vertical lines are plotted in Figure \ref{copshocktransience}, where the left one corresponds to $t = T_1^*$ and the right one  corresponds to $t = T_1^*+1$.
+As shown by \cite{lin2021minimizing}, $y_{1,t}$ experienced a substantial shock at  $t = T_1^*+1$ and it is evident from $y_{1, T_1^*}-y_{1, T_1^*+1}$ shown in Figure 1.
+We also graphed a benchmark horizontal dashed line for comparison, which corresponds to the stock price $y_{1, T_1^*}$.
+However, notice that even if $y_{1,t}$ first experienced a considerable drop at $t = T_1^*+1$,   it started to revert back and became closer to the benchmark horizontal line as $t$ increases for $t > T_1^*$.
+This observation confirms our results as the reverting behavior implies that the impact of the shock starts to diminish as $t$ increases and that the shock is very likely to be transient.
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[height = 8cm]{COPtransience.pdf}
+		\caption{The shock transience of $\{y_{1,t} \colon 1, \ldots, T_1\}$} \label{copshocktransience}
+	\end{center}	
+\end{figure}
+
+%\begin{table}[H]
+	%\caption{Results for Conoco Philips ($n=5$), $\mbf{W}^* = (0, 0, 0, 0.363, 0.637)$ from scaled covariates}
+%\begin{center}
+  %\begin{tabular}{cccccccccr}
+     %$L$ ($T_i-T^*_i$) & Model & $p_1$  & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
+     %\hline 
+     %7 & Permanent & 1  & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $236.21$ \\
+     % 7 & Dynamic & 1 & $0$   &  \textcolor{red}{0} & \textcolor{red}{0}  & $324.91$ \\[.2cm]
+     %15 & Permanent & 1   & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 273.95 \\
+     %15 & Dynamic & 1  & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $370.83$\\[.2cm]
+     %30 & Permanent & 1   & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  346.17 \\
+     %30 & Dynamic & 1 & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 451.16
+  %\end{tabular}
+%\end{center}	
+%\end{table}
+
+\newpage
 

### 2022-01-09 prevalence_testing/numerical_studies/COP.R

@@ -754,3 +754,30 @@ rownames(AICs)[c(5, 6)] <- c('wAIC', 'TS1' )
 xtable(AICs)
 
 
+# plot shock transience
+setwd('~/Desktop/Research/synthetic prediction/')
+
+# data
+ts <- COP_close[(start - (1 + 15 + K + H)):nrow(COP_close),]
+
+# load package
+require('tikzDevice')
+# tex package specification
+options(tikzLatexPackages 
+        = c(getOption( "tikzLatexPackages" ),
+            "\\usepackage{amsmath,amsfonts,amsthm, palatino, mathpazo}"))
+# file setting
+tikz(file = 'COPtransience.tex', width = 5.5, height = 4, standAlone = TRUE)
+# plot
+plot(x = as.Date(ts$Date), y = ts$COP_Close, type = 'l',
+     xlab = 'Date $t$', ylab = 'Price $y_{1,t}$',
+     main = 'Shock transience of Conoco Phillips Stock Price $y_{1,t}$',
+     col = 'deepskyblue')
+# segments
+segments(x0 = as.Date("2020-03-09"), y0 = 30, y1 = 60, lty = 3, col = 'magenta')
+segments(x0 = as.Date("2020-03-06"), y0 = 30, y1 = 60, lty = 3, col = 'magenta')
+segments(x0 = as.Date("2020-03-06"), x1 = as.Date("2020-05-15"),
+         y0 = ts$COP_Close[which(ts$Date == as.Date("2020-03-06"))],
+         col = 'indianred1', lty = 4)
+# output
+dev.off()

### 2022-01-26 prevalence_testing/manual.tex
addition of unemployment results

@@
 	\item \texttt{scale} option can allow users to compute weights based on scaled covariates or not. See details in \texttt{scm}.
+	\item \texttt{sc.x} is a list of one vector and a list, where the ordering matters.
+The first vector should be a vector of indices referring to which time series wish to consider additional covariates that are present in the models but not considered in the weight computation.
+The second list should be a list of matrices with length equal to the length of the first vector.
+The matrices are the matrices of covariates, which are present in the models but not considered in the weight computation.
 \end{itemize}

### 2022-01-26 prevalence_testing/postshocktest2021draft.tex
addition of unemployment results

@@
 
+\section{Testing shock prevalence for persons on nonfarm payrolls}
+
+\begin{table}[H]
+	\caption{Results for persons on nonfarm payrolls ($n=4$), $\mbf{W}^* = (0, 0, 0, 1)$ from scaled covariates} \label{uemtable}
+\begin{center}
+  \begin{tabular}{ccccccccr}
+      Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
+     \hline 
+     $\mc{M}_1$  & $-655.03$ & 0  & 1 & 0 (No) &1 (No)  \\      
+      $\mc{M}_2$  & $-660.14$ & 1 & $0.19$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+  \end{tabular}
+\end{center}	
+\end{table}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[height = 8cm]{UEMtransience.pdf}
+		\caption{The shock transience of $\{y_{1,t} \colon 1, \ldots, T_1\}$} \label{uemshocktransience}
+	\end{center}	
+\end{figure}
+
 \newpage

### 2022-01-26 prevalence_testing/numerical_studies/emsda.R

@@ -1,0 +1,838 @@
+################## methodology section
+# load packages
+library("data.table")
+library("dplyr")
+library("tseries")
+library("quantmod")
+library('Rsolnp')
+library('msos')
+library('tikzDevice')
+library('xtable')
+
+# load packages
+require('forecast')
+
+# this function returns the W^* estimated by synthetic control method (SCM)
+scm <- function(X, Tstar, scale = FALSE) {
+  # X is a list of covariates for disparate time series
+  # X[[1]] should be the covariate of the time series to predict
+  # X[[p]] for p = 2,...,n+1 are covariates for time series pool
+  
+  # T^* is a vector of shock-effects time points
+  # shock effect point must be > 2
+  
+  # package for constrained optiminization
+  require('Rsolnp')
+  
+  # number of time series for pool
+  n <- length(X) - 1
+  
+  # covariate for time series for prediction
+  X1 <- X[[1]][Tstar[1] + 1, , drop = FALSE]
+  
+  # covariates for time series pool
+  X0 <- c()
+  for (i in 1:n) {
+    X0[[i]] <- X[[i + 1]][Tstar[i + 1] + 1, , drop = FALSE]
+  }
+  
+  if (scale == TRUE) {
+    dat <- rbind(X1, do.call('rbind', X0))
+    dat <- apply(dat, 2, function(x) scale(x, center = TRUE, scale = TRUE))
+    X1 <- dat[1, , drop = FALSE]
+    X0 <- c()
+    for (i in 1:n) {
+      X0[[i]] <- dat[i + 1, , drop = FALSE]
+    }
+  }
+  
+  
+  # objective function
+  weightedX0 <- function(W) {
+    # W is a vector of weight of the same length of X0
+    n <- length(W)
+    p <- ncol(X1)
+    XW <- matrix(0, nrow = 1, ncol = p)
+    for (i in 1:n) {
+      XW <- XW + W[i] * X0[[i]]
+    }
+    norm <- as.numeric(crossprod(matrix(X1 - XW)))
+    return(norm)
+  }
+  
+  # constraint for W
+  Wcons <- function(W) sum(W) - 1
+  
+  
+  # optimization
[…]

### 2022-02-12 prevalence_testing/manual.tex
edits of manuscript and COP example

--- 2021-12-18 prevalence_testing/manual.tex
@@
 
- \texttt{ps.indic.W.permanent(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} is a core function that produces the synthetic weights from \texttt{scm}, a sequence of $p$-values and corresponding rejection/acceptance decisions for each donor in the donor pool based on a give significance level and the test  function \texttt{taSPA.mhfc}.
+ \texttt{ps.indic.W.permanent(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl,retro,q1,selfW)} is a core function that produces the synthetic weights from \texttt{scm}, a sequence of $p$-values and corresponding rejection/acceptance decisions for each donor in the donor pool based on a give significance level and the test  function \texttt{taSPA.mhfc}.
 The assumed model for this function is
  \begin{align*}
- 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \alpha_i I(t > T_i^*+1) + \varepsilon_{i,t},\\
- 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
+ 	y_{i,t} &= \eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j}  +\sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1}  + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
+ 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
  \end{align*}
@@
 	\item \texttt{scale} option can allow users to compute weights based on scaled covariates or not. See details in \texttt{scm}.
+	\item \texttt{q1} specifies the number of lags for the response.
 \end{itemize}
+Note that the specification $q_2$ is not considered in this function as users can just include them in the covariates and this step does not influence the computation of the function.
 
@@
  	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
- 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i}
+ 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
  \end{align*}

### 2022-02-12 prevalence_testing/postshocktest2021draft.tex
minor edits
edits of manuscript and COP example

--- 2022-01-09 prevalence_testing/postshocktest2021draft.tex
@@
 Denote the stock price of Conoco Phillips at time $t$ as $y_{i,t}$ for $i$th time series, where $i = 1, \ldots n+1$, the time series of interest is ordered as the 1st time series, and $n$ is the donor pool size.
-We used the same covariates  as \cite{lin2021minimizing} did in the model of $y_{i,t}$, which are S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, and 13-week treasury bill rates.
+In the model of $y_{i,t}$, the covariates we consider are S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13-week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX).
 
@@
  \begin{align*}
- 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
- 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
- \end{align*}
-where $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$ and $t = 1, \ldots, T_i$.
+ 	y_{i,t} &= \eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j}  +\sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1}  + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
+ 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
+ \end{align*}
+where $q_1 = q_2=2$, $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$ and $t = 1, \ldots, T_i$.
 Note that we allow the shock effect to take effect for multiple time points instead of one time point as in  \cite{lin2021minimizing}.
@@
  	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
- 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
+ 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
  \end{align*}
@@
 	\bs{X}= \begin{pmatrix}
-		\bs{x}_{1, T_1^*+1}\\
-		\vdots  \\
-		\bs{x}_{n+1, T_{n+1}^*+1}
+		\bs{x}_{1, T_1^*+1} & \bs{x}_{1, T_1^*}\\
+		\vdots & \vdots  \\
+		\bs{x}_{n+1, T_{n+1}^*+1} & \bs{x}_{1, T_1^*}
 	\end{pmatrix},
@@
 where $t = T_i^*+1$ is the time point when the shock effect takes place for $i$th time series.
+Note that the reason for including $\bs{x}_{i, T_i^*}$ is that we consider $q_2=2$ in $\mc{M}_1$ and $\mc{M}_2$.
+In other words, the consider the 1-step lagged covariates in the model and its corresponding shock effect time point is $T_i^*$.
 For each column of $\bs{X}$, we center it by subtracting its column mean and scale the resulting column vector by dividing the standard deviation of the resulting column vector.
@@
 \begin{table}[H]
-	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.221, 0, 0.779)$ from scaled covariates} \label{coptable}
+	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.183, 0, 0.817)$ from scaled covariates} \label{coptable}
 \begin{center}
@@
      \hline 
-     7 & $\mc{M}_1$  & $289.61$ & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
-     7 & $\mc{M}_2$  & 420.86 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     15 & $\mc{M}_1$ & 294.74 & 1   & 0 &0 (Yes) & 0 (Yes)     \\
-     15 &  $\mc{M}_2$ & $416.12$ & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
-     30 &  $\mc{M}_1$ & 303.88 & 1   & $0$ & 0 (Yes) &0 (Yes)   \\
-     30 &  $\mc{M}_2$ & 435.22 & 1  & 0 &0 (Yes) & 0 (Yes)  
+     7 & $\mc{M}_1$  & $214.10$ & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
+     7 & $\mc{M}_2$  & 205.23 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     15 & $\mc{M}_1$ & 246.67 & 1   & $0.82$ & 0 (Yes) &1 (No)    \\
+     15 &  $\mc{M}_2$ & $238.24$ & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
+     30 &  $\mc{M}_1$ & 303.43 & 1   & $0.82$ & 0 (Yes) &1 (No)   \\
+     30 &  $\mc{M}_2$ & 293.38 & 1  & 0 &0 (Yes) & 0 (Yes)  
   \end{tabular}
@@
 
-Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.221, 0, 0.779)$.
+Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$.
 It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second.
@@
 
-Additionally, from Table \ref{coptable}, for all $L = 7, 15, 30$, $\mc{M}_1$ is preferred over $\mc{M}_2$.
-Nevertheless, the inference results of  $\mc{M}_1$  do not differ from $\mc{M}_2$, as seen from the fourth column to the seventh column of Table \ref{coptable}.
-It is possible that   $\mc{M}_2$ is also a good fit for the dataset.
-
-It is important to note that $p_1$ is the $p$-value of the forecast comparison between adjusted forecast and unadjusted forecast if we have the data $\{y_{1,t} \colon 1, \ldots, T_1\}$, where $T_1 > T_1^*$.
+In term of Table \ref{coptable}, it is important to note that $p_1$ is the $p$-value of the forecast comparison between adjusted forecast and unadjusted forecast if we have the data $\{y_{1,t} \colon 1, \ldots, T_1\}$, where $T_1 > T_1^*$.
 In other words, it cannot be computed without observing $y_{1, t}$ for $t > T_1^*$ and we present $p_1$ only for retrospective analysis.
 Also, $\hat{p}$ is the $p$-value from weighting the $p$-values of the forecast comparison  between adjusted and unadjusted forecast for donors using $\mbf{W}^*$.
-Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and models.
-It suggests $\hat{p}$ turns out to be a good estimate of $p_1$; and the test  using $\hat{p}$ fails to reject that  the shock, which was to take effect at $t=T_1^*+1$,  is prevalent for $t > T_1^*+1$ under a significance level of 5\%.
+From Table \ref{coptable}, for all $L = 7, 15, 30$, $\mc{M}_2$ is preferred over $\mc{M}_1$.
+Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and $\mc{M}_2$.
+The test  using $\hat{p}$ with $\mc{M}_2$ fails to reject that  the shock, which was to take effect at $t=T_1^*+1$,  is prevalent for $t > T_1^*+1$ under a significance level of 5\%.
+Nevertheless, the results appear to be a little different for $\mc{M}_1$.
+For $L=7$, $|\hat{p}-p_1|=0$ for $\mc{M}_1$ whereas $|\hat{p}-p_1|=0.82$ for $L = 15, 30$.
+Based on the performance of $\mc{M}_2$, it is possible that as the time window $L$ increases, the signal from changing parameters covariates is ``misunderstood'' by $\mc{M}_1$ as shock signal.
 
@@
 As we observe $\{y_{1,t} \colon 1, \ldots, T_1\}$, we are able to check whether the decision of voting and weighted voting is correct.
-From the sixth and seventh columns of Table \ref{coptable}, we can see that voting and weighted voting procedures suggest shock transience and this decision is consistent across different $L$ and different models.
+From the sixth column of Table \ref{coptable}, we can see that voting procedure suggests shock transience for $\mc{M}_1$ and $\mc{M}_2$ for different $L$.
+However, weighted voting suggests shock transience for $\mc{M}_2$ for different $L$ but shock prevalence for $\mc{M}_1$ and $L=15, 30$ and shock transience for $\mc{M}_1$ and $L = 7$.
 As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small.
 Note that Proposition \ref{votprop} and Corollary \ref{coro1} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$.
+Note that the interpretation and meaning of $p_1$ is closely connected with models.
+For example, $\mc{M}_1$ would imply a persistent shock whereas $\mc{M}_2$ is more general in suggesting changing dynamics.
+Thus, even if  this theoretical statement  may be correct, it makes practical sense only when model is identified well.
+This comment corresponds to the possibility that $\mc{M}_1$ may ``misunderstand'' the wrong signal of changing dynamics that are instead captured by $\mc{M}_2$.
 
@@
 
+\subsection{Testing shock prevalence for persons on nonfarm payrolls}
+
+\begin{table}[H]
+	\caption{Results for persons on nonfarm payrolls ($n=3$), $\mbf{W}^* = (0, 0.278, 0.722)$ from scaled covariates} \label{uemtable}
+\begin{center}
+  \begin{tabular}{ccccccccr}
+      Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
+     \hline 
+     $\mc{M}_1$  & $-687.836$ & 0  & 1 & 1 (No) &1 (No)  \\      
+      $\mc{M}_2$ ($q_1=q_2=1$)  & $-688.428$ & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+  \end{tabular}
+\end{center}	
+\end{table}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[height = 8cm]{UEMtransience.pdf}
+		\caption{The shock transience of $\{y_{1,t} \colon 1, \ldots, T_1\}$} \label{uemshocktransience}
+	\end{center}	
+\end{figure}
+
 \newpage

### 2022-02-12 prevalence_testing/numerical_studies/COP.R

@@ -186,7 +186,8 @@ ols.est.alphahat <- function(Tstar, Y, X) {
 }
 
 # functions that return alpha.hat and synthetic weights
-ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05, 
+ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, 
+                                 sig.levl = .05, q1, 
                                  retro = TRUE, selfW = NA, scale = FALSE) {
   
   n <- length(Y) - 1
@@ -208,36 +209,40 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .
       alpha.wadj <- sym$est[2]
     }
     
-    m1.L.i <- matrix(NA, nrow = Ti - Ki - H - 1, ncol = H)
-    m2.L.i <- matrix(NA, nrow = Ti - Ki - H - 1, ncol = H)
+    m1.L.i <- matrix(NA, nrow = Ti - Ki - H - q1, ncol = H)
+    m2.L.i <- matrix(NA, nrow = Ti - Ki - H - q1, ncol = H)
     
     # compute losses
     for (h in 1:H) {
-      for (t in 1:(Ti - Ki - H - 1)) {
+      for (t in 1:(Ti - Ki - H - q1)) {
+        TL <- length(Y[[i]])
+        yi <- Y[[i]][-(1:q1)][(t + H - h + 1):(t + Ki + H - h)]
+        xi <- X[[i]][-(1:q1), ][(t + H - h + 1):(t + Ki + H - h),]
         
-        yi <- Y[[i]][-1][(t + H - h + 1):(t + Ki + H - h)]
-        xi <- X[[i]][-1, ][(t + H - h + 1):(t + Ki + H - h),]
-        
-        # lag
-        yilag <- Y[[i]][-(Ti + 1)][(t + H - h + 1):(t + Ki + H - h)]
+        # yi lags
+        yilags <- c()
+        for (j in 1:q1) {
+          yijlag <- lag(Y[[i]][-(1:q1)], n = j)[(t + H - h + 1):(t + Ki + H - h)]
+          yilags <- cbind(yilags, yijlag)
+        }
         
         # OLS
[…]

### 2022-03-10 prevalence_testing/postshocktest2021draft.tex
postshocktext2021draft.tex has been updated to include a rought draft of the monthly nonfarm payrolls application

@@
 
-To analyze the dataset, we propose two models. Denote the covariate matrix at time $t$ for $i$th time series by $\bs{x}_{i,t}$.  The first model $\mc{M}_1$, called ``permanent'' model, is 
+To analyze the dataset, we propose two models. Denote the covariate vector at time $t$ for $i$th time series by $\bs{x}_{i,t}$.  The first model $\mc{M}_1$, called ``permanent'' model, is 
  \begin{align*}
@@
 
-\subsection{Testing shock prevalence for persons on nonfarm payrolls}
+\subsection{Testing shock prevalence for Month-on-Month Change in Log Nonfarm Payrolls (Seasonally Adjusted)}
+
+Arguably the most watched macroeconomic indicator for the US economy is the monthly release of the total nonfarm payrolls, which relects the gains or losses of persons employed.
+The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
+This decline exceeds all other monthly declines by many orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
+However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution.
+Instead, what is needed is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study.
+
+To that end, we assemble a donor pool of US recessions induced by large shocks in the last three decades: the recessions of 1981-82, 2001-2003, and 2007-2009.
+We employ a suite of monthly macroeconomic indicators as covariates for the linear model as for arriving at a optimal weighting of the donor pool.
+These indicators are all transformed to their month-on-month change in log values, so as to be consistent with the time series under study and to capture the signal inherent in changes, not raw levels, of macroeconomic variables.
+These indicators are the US unemployment insurance tranfers, real personal income, personal consumption expenditures, industrial production, consumer price index, Federal Reserve funds rate, and the count of black americans age 20 and over on US nonfarm payrolls.
+
+In table 2, we observe that weighted AIC prefers $\mc{M}_2$, and thus we turn our interest to that model.
+Since $p_{1}$ is far above the rejection threshold, we lack the evidence to reject the null of a transient shock in the time series under study, the month-on-month change in log employment in the span 2019-2022.
+The weighted pvalue, $\hat p $, misses the ground truth p-value by .146 in absolute value, yet renders the correct decision.
+
+\textbf{Questions to answer and points to hit}
+\begin{enumerate}
+\item Why did I choose the donors I chose? X 
+\item Why did I use the columns I did in OLS? X
+\item Why did I use the columns I did in the estimation of the points on the simplex?
+\item Discuss the two models, M1, M2
+\item Weighted AIC just as in previous example?
+\item By weighted AIC, M2 is the preferred model
+\item We can see that $p_{1}$ is far larger than the rejection threshold, indicating that we lack the evidence to reject the null of a transiet shock
+\item The weighted pvalue, $\hat p $, misses the ground truth p-value by .146 in absolute value
+\item The method of voting renders the correct decision
+\item The method of weighted voting renders the correct decision
+\item Ask Jilei to correct y-axis
+\item Ask Jilei whether AIC was used in the same way as first example
+\item Ask Jilei whether covariate set $\textbf{X}$ is same as simplex optimization $\textbf{X}$
+\item Ask Jilei to drop RPI as a covariate in OLS (but not necessarily for optimization)
+\item Ask Jilei to include chart with data stopping at March 2020 to better visualize how payrolls change by month
+
+\end{enumerate}
 
 \begin{table}[H]
-	\caption{Results for persons on nonfarm payrolls ($n=3$), $\mbf{W}^* = (0, 0.278, 0.722)$ from scaled covariates} \label{uemtable}
+	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0, 0.278, 0.722)$ from scaled covariates} \label{uemtable}
 \begin{center}

### 2022-03-11 Revision/manuscript.tex
minor changes

@@
 \begin{align*}
-\var{\hat{\alpha}_{\rm wadj}}
+\text{Var}(\hat{\alpha}_{\rm wadj})
 & =\sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}) < (\E{\alpha_1})^2,
@@
 \begin{align*}
- \E{\alpha_1^2} &= \var{\alpha_1}+(\E{\alpha_1})^2\\
+ \E{\alpha_1^2} &= \text{Var}(\hat{\alpha}_{1})+(\E{\alpha_1})^2\\
  &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
-  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
-  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
+  &=\text{Var}(\hat{\alpha}_{\rm adj}) +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
+  &=\text{Var}(\hat{\alpha}_{\rm adj}) +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
 \end{align*}
@@
 \begin{equation} \label{ineq}
- (\E{\alpha_1})^2 >\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
+ (\E{\alpha_1})^2 >\text{Var}(\hat{\alpha}_{\rm adj}) + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
 \end{equation}
@@
 We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$.
-We can adapt the above to derive a risk-reduction condition for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
+We can adapt the above to derive a risk-reduction condition for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\text{Var}(\hat{\alpha}_{\rm IVW}) +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.
 In fact, more generally, using similar proof of Lemma \ref{risklemma}, it can be shown that under $\mc{M}_2$, the risk-reduction quantities are

### 2022-03-11 prevalence_testing/postshocktest2021draft.tex
minor changes

@@
 \newcommand{\Y}{\textbf{Y}}
-\newcommand{\L}{\textbf{L}}
+\newcommand{\Llet}{\textbf{L}}
 \newcommand{\Hist}{\mathcal{H}}
@@
 
-\title{Prospective testing for the prevalence or transience of a shock effect before it occurs}
+\title{Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs}
 \author{}
@@
 \begin{abstract}
-We develop a hypothesis testing procedure to prospectively test whether an anticipated shock is likely to be transient or permanent over a time horizon.
+We develop a hypothesis testing procedure to prospectively test whether an anticipated shock is likely to be transient or permanent over a set time horizon.
 We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed.
 These additional time series form a donor pool.
-For each of the time series in the donor pool we calculate a p-value corresponding to a hypothesis test on the relevance of the inclusion of shock-effect information in predicting the response over the time horizon.
+For each time series in the donor pool we calculate a p-value corresponding to a hypothesis test on the relevance of the inclusion of shock-effect information in predicting the response over the time horizon.
 These p-values are then combined to form an aggregated p-value which guides one decision in determining whether the shock effect for the time series under study is expected to be prevalent or transient.
 This p-value can be computed before the shock-effect is observed in the time series under study provided one can form a suitable donor pool.
-Several simulated data examples, and two real data examples of forecasting Conoco Phillips stock price and ....
-are provided for verification and illustration.
+Two real data examples for forecasting daily Conoco Phillips stock prices and monthly employment data as well as several simulations are provided for verification and illustration.
 \end{abstract}
@@
 %We provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock.
-We provide forecasting methodology for assessing the lingering effect of an anticipated structural shock to a time series under study.
-We focus on the setting in which a structural shock has occurred and one desires a prediction for the post-shock response over a set time horizon $H$.
+In this article we provide forecasting methodology for assessing the transient or permanent behavior of an anticipated structural shock that has yet to have a measured impact on a time series under study.
+We focus on the setting in which a structural shock has occurred and one desires predictions to be made before post-shock responses are observed over a set time horizon $H$.
 Specific interest is in determining whether the shock is expected to be permanent or transient over $H$.
-Standard forecasting methods may not yield any guidance on the post-shock trajectories \citep{baumeister2014real}.
-This is a general problem that has many real life applications.
+
+This is a general problem facing many real life applications.
 For example, one may acquire terrible or great news about a company and desire to determine whether that news is bound to impact the stock price of that company over a relevant time period.
 Companies may be interested in forecasting the demand of their products after they were involved in a brand crisis, but they only have recent sales data from pre-crises times.
+Policy makers, economists, and citizens alike may be interested in the expected future behavior of the unemployment rate in the upcoming quarter or year.
 %Policy makers, economists, and citizens alike may be interested in determining whether inflation will dissipate or persist for the foreseeable future
-All is not lost in this forecasting setting, one may be able to supplement the present forecast with past data borrowed from other time series which contain post-shock trajectories arising from materially similar structural shocks.
-
-The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
-
+Standard forecasting methods may not yield any guidance on the post-shock trajectories \citep{baumeister2014real}.
+That being said, one may be able to construct credible forecasts in this setting \citep{lin2021minimizing}.
+The procedure of \cite{lin2021minimizing} works by supplementing the present forecast with past data borrowed from other time series which contain post-shock trajectories arising from materially similar structural shocks.
+
+The method of \cite{lin2021minimizing} showed success in the nowcasting setting in which one is interested in predicting the value of the first post-shock response.
+As it currently stands this method is not appropriate for more nuanced forecasts involving $h$-ahead time points.
+In this article we develop a  hypothesis testing procedure motivated by the methodology of \cite{lin2021minimizing} and the multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi} in order to test whether or not time series which incorporate shock information exhibit superior predictive performance over forecasts which do not over a set time horizon.
+This effectively tests whether a shock is transient or permanent over a set time horizon.
+
+\textcolor{red}{This needs work} The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
 Our testing method embraces ideas from
@@
 forecast comparison \citep{diebold1995comparing, quaedvlieg2021multi}, 
-p-value combination, 
+and p-value combination. 
+It also has similarities with 
 conditional forecasting \citep{baumeister2014real, kilian2017structural}, 
@@
 
+\vspace*{0.5cm}\noindent\textcolor{red}{Need more pointed references on similar methods.
+Need to discuss how this method extends \cite{lin2021minimizing} and is an application of \cite{quaedvlieg2021multi}.}
+
 \section{Setting}
@@
 We let $\y_{i,t} = (y_{i,t}$, $\x_{i,t}$) where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.
-Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection.
-We will suppose that each time series $\y_{i,t}$ undergoes a shock at time $T^*_i \leq T_i + 1$.
-To define an interesting setting, we will suppose that $T^*_1 = T_1 + 1$, and $1 < T^*_i < T_i + 1$ for $i \geq 2$.
-We will suppose that $\x_{i,t=T^*_i}$ is observed before the shock takes effect on $y_{i,t=T^*_i}$.
+We will suppose that the analyst in interesting in forecasts over a time horizon $H$ where $H > 1$ to define an interesting problem that differs from \cite{lin2021minimizing}.
+%Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection. 
+We will suppose that each time series $\y_{i,t}$ undergoes a shock at time $T^*_i \leq T_i + H$, and we will suppose that $T^*_1 = T_1 + 1$ and $1 < T^*_i < T_i + H$ for $i \geq 2$. 
+We will specify that $\x_{i,t=T^*_i}$ is observed before the shock takes effect on $y_{i,t=T^*_i}$.
 
@@
 $$
-  \dbf_{i,t} = \L_{i,t,1} - \L_{i,t,2},
-$$
-where $\L_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function.
+  \dbf_{i,t} = \Llet_{i,t,1} - \Llet_{i,t,2},
+$$
+where $\Llet_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function.
 Hypothesis tests in \cite{quaedvlieg2021multi} are with respect to $E(\dbf_{i,t}) = \mbf\mu_{i,t}$.
@@
 
-\section{Simulation Setup}
-\label{simulation}
-
-Let $n$ denote the donor pool size, $p$ denote the number of covariates used, $H$ denote the number of horizon used, $T_i$ denote the length of time series to be evaluated for time series $i$, $K_i$ denote the training sample size used for each  forecasting  time series $i$, $T_i^*$ denote the time point just before the realization of the shock for time series $i$ for $i = 1, \ldots, n+1$.
-
-In this setting $n$, $p$, and $H$ are pre-determined.
-$T_i, K_i \sim \mrm{Gamma}(15, 10)$.
-The total sample size for $i$th time series is $T_i + K_i + H$.
-$T_i^*$ is randomly sampled from $\ceil{\frac{1}{4}T_i}+1$ to $\ceil{\frac{3}{4} T_i} + K_i+ H$.
-If $T_i, K_i < 90$, we force them to be 90.
-The adopted model for the data is as below:
-\begin{align*}
-  y_{i,t} &= \eta_i + \phi_i y_{i,t-1} + \mbf{x}_{i,t} \bs{\beta}_i + \alpha_i I(t > T_i^*) + \varepsilon_{i,t},\\
-  \alpha_i &= \mu_{\alpha} + \mbf{x}_{i,T_i^*+1}\bs{\gamma}_i + \tilde{\varepsilon}_{i},
-\end{align*}
-where
-\begin{align*}
-  \phi_i & \sim \text{ indep. }  U(0,1) \\
-  \eta_i & \sim \text{ indep. }  \mc{N}(0,1) \\
-  \varepsilon_{i,t} & \sim \text{ indep. } \mc{N}(0, \sigma^2)\\
-  \tilde{\varepsilon}_i & \sim \text{ indep. } \mc{N}(0, \sigma_{\alpha}^2)
-  \\
-  \bs{\gamma}_i & \sim \text{ indep. } \mc{N}(\mu_{\gamma}\bs{1}_p, \sigma_{\gamma}^2 \mbf{I}_p) \\
-  \bs{\beta}_i & \sim \text{ indep. }  \mc{N}(\bs{0}_p, \mbf{I}_p).
-\end{align*}
-Moreover, the elements of $\mathbf{x}_{i,t}$ are independently distributed as $\mrm{Gamma}(1,\delta)$.
-
-Note that $K_i$ is training sample size for time series $i$. Consider
-\begin{align*}
-  K_i & \sim \ceil{\mrm{Gamma}(a_{K}, b_K)}\\
-   T_i & \sim \ceil{\mrm{Gamma}(a_{T}, b_T)} \\
-  T_i^* &\equiv \max\{T_i+1, \ceil{0.5 \cdot(T_i+K_i+H)}\},
-\end{align*}
-
-$K_i+H+T_i^* > T_i+K_i+H$
-
- Then, we consider the following simulation setup
-\begin{verbatim}
-  ns <- c(5, 10, 20, 40)
-  Tscale <- Kscale <- 1 / 2 # b_T, b_K 
-  K.T.shape <- c(200, 400, 800, 1600) # for K_i and T_i
-  mu.gamma.delta <- 2 # mean for parameter vector of shock
-  sigma.delta.gamma <- 0.1 # sd for parameter vector of shock
-  sigma.alpha <- 0.05 # sd for shock noise  
-  sigma <- 0.1 # sd for response noise
-  mu.alpha <- 50 # intercept for shock (relatively large)
-  H <- 8 
-  ell <- 4
-  scale <- 2 # scale for covariates that follow Gamma distribution
-\end{verbatim}
-
-\begin{align*}
-  y_{i,t} &= \eta_i + \phi_i y_{i,t-1} + \mbf{x}_{i,t} \bs{\beta}_i + \xi_i\cdot  I(t > T_i^*) + \varepsilon_{i,t},\\
-  \xi_i &= \alpha_i \cdot e^{-(t-T_i^*-1)} \\
-  \alpha_i &= \mu_{\alpha} + \mbf{x}_{i,T_i^*+1}\bs{\gamma}_i + \tilde{\varepsilon}_{i},
-\end{align*}
-
-\newpage
-
 \section{Numerical Examples}
@@
 Section \ref{sptcop} discusses the prevalence testing of the shock that Conoco Phillips stock experienced on March 9th, 2020.
+Section \ref{sptuem} discusses the prevalence testing of the shock that seasonally adjusted log nonfarm payrolls experienced in April, 2020.
 
@@
 
-Arguably the most watched macroeconomic indicator for the US economy is the monthly release of the total nonfarm payrolls, which relects the gains or losses of persons employed.
+\label{sptuem}
+
+Arguably the most watched macroeconomic indicator for the US economy is the monthly release of the total nonfarm payrolls, which reflects the gains or losses of persons employed.
 The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
 This decline exceeds all other monthly declines by many orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
-However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution.
+However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution (\textcolor{red}{Think about this}).
 Instead, what is needed is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study.
 
-To that end, we assemble a donor pool of US recessions induced by large shocks in the last three decades: the recessions of 1981-82, 2001-2003, and 2007-2009.
-We employ a suite of monthly macroeconomic indicators as covariates for the linear model as for arriving at a optimal weighting of the donor pool.
+To that end, we assemble a donor pool of US recessions induced by large shocks in the last three decades: the recessions of 1981-82, 2001-2003, and 2007-2009 (\textcolor{red}{Justification needed for these shocks; the March 2020 lockdown was an unprecedented halting of economic activity}).
+We employ a suite of monthly macroeconomic indicators as covariates for the linear model as for arriving at an optimal weighting of the donor pool.
 These indicators are all transformed to their month-on-month change in log values, so as to be consistent with the time series under study and to capture the signal inherent in changes, not raw levels, of macroeconomic variables.
-These indicators are the US unemployment insurance tranfers, real personal income, personal consumption expenditures, industrial production, consumer price index, Federal Reserve funds rate, and the count of black americans age 20 and over on US nonfarm payrolls.
+These indicators are the US unemployment insurance transfers, real personal income, personal consumption expenditures, industrial production, consumer price index, Federal Reserve funds rate, and the count of black Americans age 20 and over on US nonfarm payrolls.
 
@@
 Since $p_{1}$ is far above the rejection threshold, we lack the evidence to reject the null of a transient shock in the time series under study, the month-on-month change in log employment in the span 2019-2022.
-The weighted pvalue, $\hat p $, misses the ground truth p-value by .146 in absolute value, yet renders the correct decision.
+The weighted p-value, $\hat p $, misses the ground truth p-value by .146 in absolute value, yet renders the correct decision.
 
@@
 \item Why did I use the columns I did in OLS? X
-\item Why did I use the columns I did in the estimation of the points on the simplex?
-\item Discuss the two models, M1, M2
-\item Weighted AIC just as in previous example?
-\item By weighted AIC, M2 is the preferred model
+\item Why did I use the columns I did in the estimation of the points on the simplex? X
+\item Discuss the two models, M1, M2 X
+\item Weighted AIC just as in previous example?  X
+\item By weighted AIC, M2 is the preferred model Yes
 \item We can see that $p_{1}$ is far larger than the rejection threshold, indicating that we lack the evidence to reject the null of a transiet shock
@@
 \item The method of weighted voting renders the correct decision
-\item Ask Jilei to correct y-axis
-\item Ask Jilei whether AIC was used in the same way as first example
+\item Ask Jilei to correct y-axis X
+\item Ask Jilei whether AIC was used in the same way as first example X
 \item Ask Jilei whether covariate set $\textbf{X}$ is same as simplex optimization $\textbf{X}$ 
-\item Ask Jilei to drop RPI as a covariate in OLS (but not necessarily for optimization)
-\item Ask Jilei to include chart with data stopping at March 2020 to better visualize how payrolls change by month
+\item Ask Jilei to drop RPI as a covariate in OLS (but not necessarily for optimization) (needs checking)
+\item Ask Jilei to include chart with data stopping at March 2020 to better visualize how payrolls change by month X
 
@@
 
-\newpage
+\subsection{Simulations}
+\label{simulation}
+
+\section{Discussion}
+
+Talk about post-shock forecasting as parameterizing exogeniety and using hindsight in the donor pool to explicitly estimate exogeneity apriori.
 

### 2022-03-11 prevalence_testing/postshocktest2021draft.tex
changes of plot and addition for the steps of variable selection

@@
 
+The variable selection steps are outlined as follows.
+At first, we have the same set of covariates $\{\mc{X}_1, \ldots, \mc{X}_p\}$ for each donor, where $\mc{X}_1$ corresponds to the name of the covariate.
+Next, for each donor, we conduct stepwise variable selection based on AIC so that for each donor, we end up with a model with covariates that may differ across  donors, say $\{\mc{X}_j \colon j\in \mc{I}_i\}$ for $i = 2, \ldots, n+1$, where $\mc{I}_j$ is the collection of the indices corresponding to which covariate is selected.
+Next, we  take the union $\cup_{i=2}^{n+1}\{\mc{X}_j \colon j\in \mc{I}_i\}$ to obtain the final set of covariates that are present in the model of every donor and the time series of interest.
+
 \textbf{Questions to answer and points to hit}

### 2022-03-11 prevalence_testing/numerical_studies/emsda.R

@@ -619,7 +619,7 @@ difflog_df <- data.frame(diff(as.matrix(log(df))))
 # We create lags of the covariates
 # https://stackoverflow.com/questions/38119225/debugging-function-to-create-multiple-lags-for-multiple-columns-dplyr
 
-difflog_df.lag <- shift(difflog_df, n=1:2, give.names = T)  ##column indexes of columns to be lagged as "[,startcol:endcol]", "n=1:3" specifies the number of lags (lag1, lag2 and lag3 in this case)
+difflog_df.lag <- shift(difflog_df, n=1:1, give.names = T)  ##column indexes of columns to be lagged as "[,startcol:endcol]", "n=1:3" specifies the number of lags (lag1, lag2 and lag3 in this case)
 
 # We we combine and original series and the lags
 merged <- bind_cols(difflog_df, difflog_df.lag)
@@ -657,7 +657,8 @@ paste('This is a dataset of dimension', dim(no_NA_cols_merged)[1], 'by', dim(no_
 # want 5 donors with fewer covariates, or fewer donors with more covariates.
 
 
-dat <- no_NA_cols_merged
+dat <- complete_cases_merged
+dat <- dat[, c(1, 3, 2, 4, 6, 8, 10)]
 date <- rownames(dat)
 # setup
 H <- 12
@@ -665,112 +666,83 @@ K <- 24
 L <- 12
 
 # Time Series 2
-shock.t2 <- which(date == '1958-08-01') + 1
-shock.adj <- which(date == '1957-04-01') + 1
+shock.t2 <- which(date == '1980-03-01') + 1
 TS2 <- dat[(shock.t2 - (1 + 12 + K + H)):(shock.t2 + L),]
 TS2$shock.t2 <- as.numeric((shock.t2 - (1 + 12 + K + H)):(shock.t2 + L) %in% shock.t2:(shock.t2 + L))
-TS2$shock.adj <- as.numeric((shock.t2 - (1 + 12 + K + H)):(shock.t2 + L) == shock.adj)
[…]

### 2022-03-12 prevalence_testing/postshocktest2021draft.tex
addition of statements related to weighted AIC

@@
 where the last second step assumes that $\{I(p_i\leq \alpha)\colon i\in \mc{I}_n\}$ are independent and the last step uses the condition $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_1$ as $n\to \infty$, which is used in Corollary \ref{coro1}.
-Notice that if $\kappa_i$ is very small, the mean squared error of $\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)$ turns out to be small such that by the rationale of the proof of Proposition \ref{votprop}, the asymptotic approximation for the misclassification error in  Corollary \ref{coro1} should be acceptable.
+Notice that if $\kappa_i$ is very small, the mean squared error of $\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)$ turns out to be small such that by the rationale of the proof of Proposition \ref{votprop}, the asymptotic approximation for the misclassification error in  Corollary \ref{coro1} should be acceptable.\\
+
+\newpage
+
+Suppose we are interested in comparing two models $\mc{M}_1$ and $\mc{M}_2$ using AIC for forecasting the response in the time series of interest.
+However, direct comparison is not feasible as the data are not observed.
+Instead, we can conduct such inference based on the donor pool.
+Let the AIC of $\mc{M}_j$ for $i$th time series be $a_i^j$ for $i = 1, \ldots, n+1$ and $j = 1, 2$.
+Let $\xi_i = \P(a_i^1 > a_i^2)$.
+Note that if the data generating process is based on $\mc{M}_1$ and is true for all the donors and time series of interest, $\xi_i$ is expected to be high.
+Additionally, it is reasonable to assume $\xi_i =\xi $ for $\xi \in [0,1]$ and $i = 1, \ldots, n+1$.
+Notice that this setup is similar to the setup of weighted voting or voting we discussed before.
+So, under similar arguments, we propose the following corollary for synthetic pairwise model selection.
+
+\begin{corollary}[Synthetic pairwise model selection]
+\label{coro1}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
+\begin{align*}
+  \mc{I}_n = \{i =  2,\ldots, n+1\colon 0< w_i < 1\}.
+\end{align*}
+Suppose that  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$ as $n \to \infty$, and $w_i b_n\leq K$ for $i\in \mc{I}_n$ and some $K>0$, where $b_n \geq 1$ and $b_n \to \infty$ as $n\to \infty$.
+Assume for $i \in \mc{I}_n$,  $\{a_i^1, a_i^2\}$ are pairwise independent AICs of $\mc{M}_1$ and  $\mc{M}_2$ for $i$th time series  with
+\begin{align*}
+  \sum_{i\in \mc{I}_n}\P(a_i^1 > a_i^2) = \sum_{i\in \mc{I}_n} w_i \xi_i \to \xi_{1},
+\end{align*}
+where $\xi_i =  \P(a_i^1 > a_i^2)\in [0,1]$ for $i \in \mc{I}_n$. If $\xi  \neq 0.5$, as $n\to \infty$, 
+\begin{align*}
+  \E \bigg\{\left|I\left\{ \sum_{i\in \mc{I}_n} w_i I(a_i^1 > a_i^2) \geq 0.5\right\}
+  - I( a_1^1 > a_1^2) \right|\bigg\}
+  \to  \begin{cases}
+    1- \xi_1 & \text{ if } \xi_1 > 0.5 \\
+   \xi_1 & \text{ if } \xi_1 < 0.5 
+  \end{cases}
+\end{align*}
+\end{corollary}
 

### 2022-03-12 prevalence_testing/postshocktest2021draft.tex
addition of statements related to weighted AIC
added new procedures for weighted AIC in the code and manuscript

@@
 \usepackage{url}
+\usepackage{multirow}
 
@@
 Let the AIC of $\mc{M}_j$ for $i$th time series be $a_i^j$ for $i = 1, \ldots, n+1$ and $j = 1, 2$.
-Let $\xi_i = \P(a_i^1 > a_i^2)$.
+Let $\xi_i = \P(a_i^1 < a_i^2)$.
 Note that if the data generating process is based on $\mc{M}_1$ and is true for all the donors and time series of interest, $\xi_i$ is expected to be high.
@@
 \begin{corollary}[Synthetic pairwise model selection]
-\label{coro1}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
+\label{coro2}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
 \begin{align*}
@@
 Suppose that  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$ as $n \to \infty$, and $w_i b_n\leq K$ for $i\in \mc{I}_n$ and some $K>0$, where $b_n \geq 1$ and $b_n \to \infty$ as $n\to \infty$.
-Assume for $i \in \mc{I}_n$,  $\{a_i^1, a_i^2\}$ are pairwise independent AICs of $\mc{M}_1$ and  $\mc{M}_2$ for $i$th time series  with
-\begin{align*}
-  \sum_{i\in \mc{I}_n}\P(a_i^1 > a_i^2) = \sum_{i\in \mc{I}_n} w_i \xi_i \to \xi_{1},
-\end{align*}
-where $\xi_i =  \P(a_i^1 > a_i^2)\in [0,1]$ for $i \in \mc{I}_n$. If $\xi  \neq 0.5$, as $n\to \infty$, 
-\begin{align*}
-  \E \bigg\{\left|I\left\{ \sum_{i\in \mc{I}_n} w_i I(a_i^1 > a_i^2) \geq 0.5\right\}
-  - I( a_1^1 > a_1^2) \right|\bigg\}
+Assume for $i \in \mc{I}_n$,  $\{a_i^1, a_i^2\}$ are AICs of $\mc{M}_1$ and  $\mc{M}_2$ for $i$th time series, which are pairwise independent of $\{a_j^1, a_j^2\}$ for $j \neq i$ and that
+\begin{align*}
+  \sum_{i\in \mc{I}_n}\P(a_i^1 < a_i^2) = \sum_{i\in \mc{I}_n} w_i \xi_i \to \xi_{1},
+\end{align*}
+where $\xi_i =  \P(a_i^1 < a_i^2)\in [0,1]$ for $i \in \mc{I}_n$. If $\xi  \neq 0.5$, as $n\to \infty$, 
+\begin{align*}
+  \E \bigg\{\left|I\left\{ \sum_{i\in \mc{I}_n} w_i I(a_i^1 < a_i^2) \geq 0.5\right\}
+  - I( a_1^1 < a_1^2) \right|\bigg\}
   \to  \begin{cases}
@@
 \end{corollary}
+
+Note that Corollary \ref{coro2} gives an asymptotic upper bound for the misclassification rate of synthetic pairwise model selection, which is small if $\xi_1$ is large.
 
@@
 However, $\mc{M}_2$  requires far more degrees of freedom for estimation and this can increase variance in estimation.
-We used weighted AIC for model selection, which is detailed as follows.
-For $i$th donor in the donor pool, we can compute its AICs for $\mc{M}_1$ and $\mc{M}_2$, say $a^1_i$ and $a^2_i$, and also its synthetic weight $W_i^*$, where $\mbf{W}^* = (w_2^*, \ldots, w_{n+1}^*)$ and its computation is detailed in the next paragraph.
-Let $A^{1*}= \sum_{i=2}^{n+1} w_i^* a^1_i$ and $A^{2*}= \sum_{i=2}^{n+1} w_i^*a^2_i$.
-We will select $\mc{M}_1$ if $A^{1*} < A^{2*}$ and vice versa.
+For this purpose, the synthetic pairwise model selection proposed in the Corollary \ref{coro2} can be used to select between $\mc{M}_1$ and $\mc{M}_2$.
 
@@
   \begin{tabular}{cccccccccr}
-     $L$  & Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
+     $L$  & Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$ & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
      \hline 
-     7 & $\mc{M}_1$  & $214.10$ & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
-     7 & $\mc{M}_2$  & 205.23 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     15 & $\mc{M}_1$ & 246.67 & 1   & $0.82$ & 0 (Yes) &1 (No)    \\
-     15 &  $\mc{M}_2$ & $238.24$ & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
-     30 &  $\mc{M}_1$ & 303.43 & 1   & $0.82$ & 0 (Yes) &1 (No)   \\
-     30 &  $\mc{M}_2$ & 293.38 & 1  & 0 &0 (Yes) & 0 (Yes)  
+     7 & $\mc{M}_1$  & \multirow{2}{*}{$0.817$} & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
+     7 & $\mc{M}_2$  &  & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     15 & $\mc{M}_1$ & \multirow{2}{*}{$0.817$}  & 1   & $0.82$ & 0 (Yes) &1 (No)    \\
+     15 &  $\mc{M}_2$ & & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
+     30 &  $\mc{M}_1$ & \multirow{2}{*}{$1$}  & 1   & $0.82$ & 0 (Yes) &1 (No)   \\
+     30 &  $\mc{M}_2$ &  & 1  & 0 &0 (Yes) & 0 (Yes)  
   \end{tabular}
@@
 Also, $\hat{p}$ is the $p$-value from weighting the $p$-values of the forecast comparison  between adjusted and unadjusted forecast for donors using $\mbf{W}^*$.
-From Table \ref{coptable}, for all $L = 7, 15, 30$, $\mc{M}_2$ is preferred over $\mc{M}_1$.
+
+Let $a_i^1$ and $a_i^2$ denote the AICs of $\mc{M}_1$ and $\mc{M}_2$ for $i$th time series, respectively.
+Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, as  $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)>0.5$ for $L = 7, 15, 30$, we conclude that $\mc{M}_2$ is preferred over $\mc{M}_1$.
 Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and $\mc{M}_2$.
@@
 
-In table 2, we observe that weighted AIC prefers $\mc{M}_2$, and thus we turn our interest to that model.
-Since $p_{1}$ is far above the rejection threshold, we lack the evidence to reject the null of a transient shock in the time series under study, the month-on-month change in log employment in the span 2019-2022.
-The weighted p-value, $\hat p $, misses the ground truth p-value by .146 in absolute value, yet renders the correct decision.
-
 The variable selection steps are outlined as follows.
@@
 Next, we  take the union $\cup_{i=2}^{n+1}\{\mc{X}_j \colon j\in \mc{I}_i\}$ to obtain the final set of covariates that are present in the model of every donor and the time series of interest.
+
+In Table 2, using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, because $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)>0.5$,  we conclude that  $\mc{M}_2$ is preferred.
+Thus, we turn our interest to that model.
+Since $p_{1}$ is far above the rejection threshold, we lack the evidence to reject the null of a transient shock in the time series under study, the month-on-month change in log employment in the span 2019-2022.
+The weighted p-value, $\hat p $, misses the ground truth p-value by .146 in absolute value, yet renders the correct decision.
 
@@
   \begin{tabular}{ccccccccr}
-      Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
+      Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$  & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
      \hline 
-     $\mc{M}_1$  & $-687.836$ & 0  & 1 & 1 (No) &1 (No)  \\      
-      $\mc{M}_2$ ($q_1=q_2=1$)  & $-688.428$ & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     $\mc{M}_1$  & \multirow{2}{*}{0.722}& 0  & 1 & 1 (No) &1 (No)  \\      
+      $\mc{M}_2$ ($q_1=q_2=1$)  & & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
   \end{tabular}

### 2022-03-12 prevalence_testing/numerical_studies/COP.R

@@ -566,7 +566,7 @@ H <- 10
 # training sample size
 K <- 30
 # number of days after shock date
-L <- 7
+L <- 30
 
 #### Monday, March 17th, 2008
 
@@ -605,6 +605,7 @@ AIC.20080314.dynamic <- AIC(m_COP.dynamic)
 
 AIC.20080314 <- c(AIC.20080314.null, AIC.20080314.permanent, 
                   AIC.20080314.dynamic)
+I.AIC.2 <- ifelse(AIC(m_COP_3_17) > AIC(m_COP.dynamic), yes = 1, no = 0)
 
 #### 2008 shock effects
 
@@ -641,7 +642,7 @@ AIC.20080908.dynamic <- AIC(m_COP.dynamic)
 
 AIC.20080908 <- c(AIC.20080908.null, AIC.20080908.permanent,
                   AIC.20080908.dynamic)
-
+I.AIC.3 <- ifelse(AIC(m_COP_Sept_08) > AIC(m_COP.dynamic), yes = 1, no = 0)
 
 #### Thursday, November 27, 2014
 
@@ -677,7 +678,7 @@ AIC.20141127.dynamic <- AIC(m_COP.dynamic)
 AIC.20141127 <- c(AIC.20141127.null, AIC.20141127.permanent, 
                   AIC.20141127.dynamic)
 
-
+I.AIC.4 <- ifelse(AIC(m_COP_11_27_14) > AIC(m_COP.dynamic), yes = 1, no = 0)
 #### The March 9th, 2020 shock effect:
 
 # shock effect date
@@ -743,6 +744,7 @@ sum(res2$ps[-1] * res2$W)
 sum(res2$Is[-1] * res2$W)
 
 AICs <- rbind(AIC.20080314, AIC.20080908,  AIC.20141127)
+
 rownames(AICs) <- c('TS2', 'TS3', 'TS4')
 colnames(AICs) <- c('null', 'Permanent',  'dynamic')
 
@@ -760,6 +762,9 @@ AICs <- rbind(AICs, wAICs, AIC.20200309)
 rownames(AICs)[c(5, 6)] <- c('wAIC', 'TS1' )
 xtable(AICs)
 
+# weighted comparison
+I.AICs <- c(I.AIC.2, I.AIC.3, I.AIC.4)
+matrix(res1$W, nrow = 1) %*% I.AICs
 
 # plot shock transience
 setwd('~/Desktop/Research/synthetic prediction/')

### 2022-03-12 prevalence_testing/numerical_studies/emsda.R

@@ -684,7 +684,7 @@ co.D <- as.matrix(co.D)
 mod.t2.dynamic <- lm(TS2$PAYEMS ~ as.matrix(TS2[, 2:7]) + co.D + TS2$shock.t2)
 # AICs
 AICs.19800301 <- c(AIC(mod.t2.null), AIC(mod.t2.permanent), AIC(mod.t2.dynamic))
-
+I.AIC.2 <- ifelse(AIC(mod.t2.permanent) > AIC(mod.t2.dynamic), yes = 1, no = 0)
 
 # Time Series 3
 shock.t3 <- which(date == '2001-09-01') + 1
@@ -705,6 +705,7 @@ co.D <- as.matrix(co.D)
 mod.t3.dynamic <- lm(TS3$PAYEMS ~ as.matrix(TS3[, 2:7]) + co.D + TS3$shock.t3)
 # AICs
 AICs.20010901 <- c(AIC(mod.t3.null), AIC(mod.t3.permanent), AIC(mod.t3.dynamic))
+I.AIC.3 <- ifelse(AIC(mod.t3.permanent) > AIC(mod.t3.dynamic), yes = 1, no = 0)
 
 # Time Series 4
 shock.t4 <- which(date == '2008-03-01') + 1
@@ -725,6 +726,7 @@ co.D <- as.matrix(co.D)
 mod.t4.dynamic <- lm(TS4$PAYEMS ~ as.matrix(TS4[, 2:7]) + co.D + TS4$shock.t4)
 # AICs
 AICs.20080301 <- c(AIC(mod.t4.null), AIC(mod.t4.permanent), AIC(mod.t4.dynamic))
+I.AIC.4 <- ifelse(AIC(mod.t4.permanent) > AIC(mod.t4.dynamic), yes = 1, no = 0)
 
 # Time Series 1
 shock.t1 <- which(date == '2020-03-01') + 1
@@ -775,8 +777,9 @@ Wstar <- res1$W
 
 
 AICs <- rbind(AICs.19800301, AICs.20010901, AICs.20080301)
-
+I.AICs <- c(I.AIC.2, I.AIC.3, I.AIC.4)
 matrix(Wstar, nrow = 1) %*% AICs
+matrix(Wstar, nrow = 1) %*% I.AICs
 
 # plot shock transience
 setwd('~/Desktop/Research/synthetic prediction/')

### 2022-03-21 prevalence_testing/postshocktest2022draft.tex
saving edits; there is a lot more to do

--- 2022-03-12 prevalence_testing/postshocktest2021draft.tex
@@
 \section{Setting}
-
 \label{section2}
+
+\textcolor{red}{We should make a picture and/or create an algorithm that communicates how our method works in a simple setting} \vspace*{0.5cm}
 
@@
 %Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection. 
-We will suppose that each time series $\y_{i,t}$ undergoes a shock at time $T^*_i \leq T_i + H$, and we will suppose that $T^*_1 = T_1 + 1$ and $1 < T^*_i < T_i + H$ for $i \geq 2$. 
-We will specify that $\x_{i,t=T^*_i}$ is observed before the shock takes effect on $y_{i,t=T^*_i}$.
-
-We are interested in point forecasts $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ with the aim of determining whether the shock has an effect on $y_{i,t}^h$.
-\cite{quaedvlieg2021multi} provided a methodology for comparing forecasts jointly across all horizons of a forecast path, $h = 1,\ldots, H$.
+We will suppose that each time series $\y_{i,t}$ undergoes a shock at time $T^*_i \leq T_i + H$ for $i \geq 2$, and we will suppose that $T^*_1 = T_1 + 1$. 
+We will specify that $\x_{i,t=T^*_i}$ is observed before the shock takes effect on $y_{i,t=T^*_i}$ for all $i$. Under this setup there is no post-shock information for the series $y_{1,t}$.
+
+In this article our goal will be to leverage the post-shock information in the donor pool of series $y_{i,t}$, $i = 2,\ldots,n+1$ to test whether the anticipated shock is expected to be transient or persistent over the time horizon $H$ for the time series under study indexed by $i=1$.
+The methodology developed within will focus on the comparison of two forecasts for $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ where one forecast incorporates the shock effect and the other does not.
+We define these forecasts for each $i = 1,\ldots,n+1$, $t = 1,\ldots,T_i$ and $h = 1,\ldots,H$ as
+$$
+  \hat y^{1,h}_{i,t} \; \text{and} \; \hat y^{2,h}_{i,t},
+$$
+where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed shock and is based on the information set $\mathcal{F}_{t-h}$ (\textcolor{red}{need to define}), and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.
+%We are interested in point forecasts $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ with the aim of determining whether the shock has an effect on $y_{i,t}^h$.
+%\cite{quaedvlieg2021multi} provided a methodology for comparing forecasts jointly across all horizons of a forecast path, $h = 1,\ldots, H$.
 In our post-shock setting, we want to compare the forecasts
-$$
-  \hat y^{1,h}_{i,t} \; \text{and} \; \hat y^{2,h}_{i,t}
-$$
-where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed structural shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.
-We will compare these forecasts in terms of their loss differential
+%$$
+%  \hat y^{1,h}_{i,t} \; \text{and} \; \hat y^{2,h}_{i,t}
+%$$
+%where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed structural shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.
+
+Our methodology involves first comparing the performance of $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ for each time series in the donor pool ($i = 2,\ldots,n+1$).
+We then aggregate the decisions made in the donor pool by the similarity of the underlying time series to the time series under study.
+The first step in the process employs the recent multi-horizon forecast comparison methodology of \cite{quaedvlieg2021multi} for comparing the predictive abilitiy of forecasts jointly across all horizons of a forecast path, $h = 1,\ldots, H$.
+The second steps involves aggregation techniques motivated by the supposed data-generating process.
+These aggregation strategies are motivated by the post-shock aggregation techniques in \cite{lin2021minimizing}.
+We then report whether an anticipated shock is expected to be transient over the horizon $H$ by using an aggregated decision from the donor pool.
+
+(\textcolor{red}{this needs work}) In Section \ref{sec:multhor} we discuss the background in \cite{quaedvlieg2021multi} that is necessary for our post-shock testing procedure.
+In Section \ref{modelsetup} we motivate time series models that we consider.
+In Section \ref{sec:aggmeth} we present aggregation strategies that we consider which inform our decision about the expected shock behavior.
+
+\section{Methodological details}
+
+\subsection{Multi-horizon forecasting procedure}
+\label{sec:multhor}
+
+In this section we discuss the background of the multi-horizon forecasting procedure \citep{quaedvlieg2021multi} that is necessary for the investigation of shock behavior in our anticipated post-shock setting.
+The initial building blocks in the assessment of predictive ability of forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ will make use of a loss differential
 $$
@@
 where $\Llet_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function.
-Hypothesis tests in \cite{quaedvlieg2021multi} are with respect to $E(\dbf_{i,t}) = \mbf\mu_{i,t}$.
-Conditions for these tests require conditions of \cite{giacomini2006tests}.
-
-We will be interested in $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
-
-\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$.
+Define the expected loss differential as  $E(\dbf_{i,t}) = \mbf\mu_{i,t}$ and let the average expected loss differential be defined as $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
+%Hypothesis tests in \cite{quaedvlieg2021multi} are then constructed with respect to estimates of the expected loss differentials $E(\dbf_{i,t}) = \mbf\mu_{i,t}$, %Conditions for these tests require conditions of \cite{giacomini2006tests}.
+%where specific interest is in the average expected loss differential $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
+%%%\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$.
 We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock.
 Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool.
-\vspace*{0.5cm}
-
-We will consider the average superior predictive ability (aSPA) to assess whether or not a shock is permanent or transitory.
+%%%\vspace*{0.5cm}
+We will then judge forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ based on the average superior predictive ability (aSPA) \citep{quaedvlieg2021multi}.
 The aSPA investigates forecast comparisons based on their weighted average loss difference
@@
 Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu_i^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1.
+With this caveat in mind we will use $w_{i,h} = 1/H$, and we will consider different time horizons $H$ in some of our examples.
 
@@
 
-We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
-Let $l$ be the block length of the MBB where we assume that $T_i = lK_i$.
-Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
+A p-value corresponding to the hypothesis test \eqref{test} is computed using a moving block bootstrap (MBB). \textcolor{red}{Need more clarity on this process}
+%We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
+Let $l$ be the block length of the MBB where we assume that $T_i = lK_i$. Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array 
 $$
@@
 It is of course possible that there is no shock or a simple mean-shift.
+In fact, the simple mean shift model can be fit and one can test whether the additional flexibility of model \eqref{model-gen} is warranted for series in the donor pool.
+A general testing procedure is discussed in Section \ref{sec:aggmeth} (\textcolor{red}{need to discuss that model selection is aggregated, the primary goal concerns the series under study}).
 
@@
 
-%We further define the parameter sets
-%\begin{align}
-%\begin{array}{l}
-% \;\, \Theta = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
-%   \Theta_1 = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon  t= 1, \ldots, T_i, i = 1\}
-%\end{array}\label{parameter} 
-%\end{align}
-
-\subsection{Forecasting and testing for shock persistence}
-\label{forecast}
-
-In this section, we motivates the relation between shock persistence testing and forecasting comparison.
-In time series literature, under a squared error loss $L(\cdot)$, the forecast using the conditional mean is the best point forecast that minimizes the expected loss if the model is specified correctly.
-That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional mean forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases.
-On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information and makes good use of it should enjoy a smaller expected loss than any conditional mean forecast without such information does.
-In other words, the problem of testing for shock persistence boils down into comparing the conditional mean forecast that is adjusted by shock information and the one that is unadjusted.
-To deal with this problem, we applied the forecast comparison procedure of  \cite{quaedvlieg2021multi} to conduct shock persistence testing.
-
-In this paper, we extend the framework of post-shock forecast \citep{lin2021minimizing}, which aggregates outside information by constructing a donor pool, to post-shock persistence testing.
-The donor pool consists of time series called  ``donors'' that are similar to the time series of interest.
-As we do not observe the future data, information from donors can aid our decision making and forecasts.
-Note that what  similarity exactly means here can be vague but the donors and the time series of interest should come from a common population in principle; see more details of how to select donors in \cite{lin2021minimizing}.
-In this paper, we also proposed several theoretical results with some detailed conditions on the donor pool, which may alleviate the difficulty of dealing with similarity when choosing donors.
-
-In this paper, we propose a new way of aggregating information from donor pool to conduct post-shock persistence testing, which is quite different from \cite{lin2021minimizing}.
-The general structure of this aggregation technique is illustrated as below.
-Suppose we are given a nonempty donor pool with size $n$ that consists of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed.
-With shock information, we are able to compute unadjusted forecast that does not incorporate shock information and adjusted forecast that does.
-The forecast comparison using methodology of \cite{quaedvlieg2021multi} for each donor yields a $p$-value, $p_{i+1}$ for $i$th donor in the donor pool.
-Given $\{p_i \colon i = 2, \ldots, n+1\}$, we propose a methodology for judging whether the shock of the time series of interest is persistent or not.
-Next, we illustrate the details of our methodology as below.
-
-For each donor $\mc{T}_i$, $i = 2, \ldots, n+1$, to compare adjusted and unadjusted forecasts,  a model needs to be specified.
-The model should describe how the shock impacts the time series at and after a certain time point $t= T_i^* + 1$.
-For clarity, we refers the unadjusted forecast to the conditional mean forecast based on the part of the model that ignores shock effect; and the adjusted forecast refers to the conditional mean forecast based on the full model.
-Note that the model needs not to be the same for every donor in the donor pool.
-However, certain conditions need to be imposed as discussed previously.
-
- Given a model for each donor pool, we compute the unadjusted conditional mean forecast and adjusted conditional mean forecast in the framework of \cite{quaedvlieg2021multi}.
-As introduced in the beginning of Section \ref{section2}, for a given horizon $h$, to forecast $y_{i, t}$, we compute the two forecasts based on the information set $\mathcal{F}_{i, t-h}$ of each donor pool (i.e., the data before $t-h$) for $i = 2, \ldots, n+1$.
-Note that in practice, a training sample size $K_i$ should be specified for $i = 2, \ldots, n+1$ such that we use the information set $\mathcal{F}_{i, t-h-K_i + 1:t-h}$.
-
- Even if the data contain shock information for each donor, it is impossible to compute the adjusted conditional mean forecast based on $\mathcal{F}_{i, t-h}$ when $t -h \leq T_i^*$, i.e., we only have training data that do no have any shock information.
-Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information.
-In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an consistent estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate.
-However, the consistent estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.
-To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear.
-However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.
-
- With the presence of autoregressive parameters in some models, unbiased estimation with OLS  is not feasible but the bias is $O(T^{-1})$, where $T$ is the time series length \citep{shaman1988bias}.
-In this paper, we use the OLS estimates to approximate the adjusted conditional mean forecast and unadjusted one.
-The bias decades away as $T\to \infty$.
-
-\vspace*{0.5cm}
-
-\noindent\textbf{Note}: Our forecast needs to be written with respect to our general model. Specifics can be given when we conduct our numerical examples.
-\vspace*{0.5cm}
-
-In our post-shock setting we consider the following candidate forecasts: 
-\begin{align*}
-  &\text{Forecast 1}: \\
-  &\text{Forecast 2}: 
-\end{align*}
-We want to determine which forecast is appropriate over a horizon while the methods in \cite{lin2021minimizing} were only appropriate in the nowcasting setting in which prediction was only focused on the response immediately following the shock.
-
-\newpage
+\vspace*{0.5cm}\noindent\textcolor{red}{Explain h-ahead forecasts here}
+
+\subsection{Aggregation methods}
+\label{sec:aggmeth}
+
+\noindent\textcolor{red}{Much more is needed here}
 
@@
 
-\begin{proof}
-Notice that as $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$ and $I(p_i \leq  \alpha) $ is a Bernoulli random variable, $I(p_i \leq  \alpha)$ is identically distributed for  $i = 1, \ldots, n+1$.
-Since $p_i$ is pairwise independent and $p_i$ are identically distributed for $i = 2, \ldots, n+1$, by Weak Law of Large Numbers,
-\begin{align*}
-  \frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha)  
-   \stackrel{p}{\rightarrow}  \P(p_i \leq \alpha) = \P(p_1 \leq \alpha),
-\end{align*}
-Define
-\begin{align*}
-  f \colon [0,1] \mapsto \{0,1\} 
-  \text{ with }
-  f(x) = I(x \geq 0.5).
-\end{align*}
-Let $C(f)$ denote the continuity set of $f$. Suppose that $\P(p_1 \leq  \alpha) \neq 0.5$. In this case, notice that 
-\begin{align*}
-  \P(\P(p_1 \leq  \alpha) \in C(f)) =1.
-\end{align*}
-By Slutsky's Theorem, we have
-\begin{align*}
-  I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
-  \stackrel{p}{\rightarrow} 
-  I\{ \P(p_1 \leq  \alpha) \geq 0.5\}.
-\end{align*}
-It follows that
-\begin{align*}
-   I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}- I( p_1 \leq  \alpha) 
-  \stackrel{p}{\rightarrow} 
-  I\{ \P(p_1 \leq  \alpha) \geq 0.5\} - I( p_1 \leq  \alpha) 
-\end{align*}
-Since the function $g(x)= |x|$ is continuous in $x$,  by continuous mapping theorem, 
-\begin{align*}
-  \bigg|  I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
-  - I( p_1 \leq  \alpha) \bigg| \stackrel{p}{\rightarrow}   |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
-  - I( p_1 \leq  \alpha) |
-\end{align*}
-Moreover, note that
-\begin{align*}
-\E \left\{ |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
-  - I( p_1 \leq  \alpha) |\right\}
-  & = \begin{cases}
-    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
-    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
-  \end{cases} \\
-  & \leq  0.5.
-\end{align*}
-Due to the fact that
-\begin{align*}
- \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
-  - I( p_1 \leq  \alpha) \right| \leq 1
-\end{align*}
-is bounded by 1, by Dominated Convergence Theorem for the version of convergence in measure,
-\begin{align*}
- \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
-  - I( p_1 \leq  \alpha) \right|
-  \stackrel{\mathcal{L}_1}{\rightarrow}  |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
-  - I( p_1 \leq  \alpha) |.
-\end{align*}
-That would imply that 
-\begin{align*}
-  \E \bigg\{\left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
-  - I( p_1 \leq  \alpha) \right|\bigg\}
-  \to  \begin{cases}
-    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
-    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
-  \end{cases}
-\end{align*}
-That is, the expected misclassification rate of voting converges to 
-\begin{align*}
-  \begin{cases}
-    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
-    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
-  \end{cases}
-\end{align*}
-\end{proof}
-
-\begin{lem}
-  \label{gwlln}  For each $n\in \naturals$, let $c_{n1}, \ldots, c_{nn}$ be real numbers bounded by some $K > 0$, and let $X_{n1}, \ldots, X_{nn}$ be pairwise independent random variables defined on a probability space $(\Omega_n, \mc{F}_n, \P_n)$, and let $\E_n$ and $\var_n$ denote the corresponding expectation and variance.
-If $(b_n)$ is a sequence of positive numbers such that $b_n \uparrow \infty$ such that
-    \begin{align*}
-      \sum_{i=1}^n \P_n (|X_{ni}| > b_n) \to 0
-      \quad \text{ and } 
-      \quad \frac{1}{(b_n)^2} \sum_{i=1}^n \E_n[X_{ni}^2; |X_{ni}|\leq b_n] \to 0,
-    \end{align*}
-    then
-    \begin{align*}
-      \frac{1}{b_n} \sum_{i=1}^n c_{ni} (X_{ni} - \E_n[X_{ni}; X_{ni} \leq b_n]) \cp 0.
-    \end{align*}
-\end{lem}
-
-\begin{proof}
-  For each $n\in \naturals$ set
-    \begin{align*}
-      S_n = \sum_{i=1}^n c_{ni} X_{ni}, \quad T_n = \sum_{i=1}^n c_{ni} Y_{ni},
-      \quad Y_{ni} = X_{ni} I(|X_{ni}|\leq b_n), \quad i = 1, \ldots, n.
-    \end{align*}
-   The goal is to show that  $(S_n- \E_n[T_n])/b_n \cp 0$. For this, it suffices to show that (1) $(T_n - S_n)/b_n \cp 0$ and (2) $(T_n - \E_n[T_n])/b_n \cp 0$ because
-    \begin{align*}
-      (T_n - \E_n[T_n])/b_n -(T_n - S_n)/b_n = (S_n- \E_n[T_n])/b_n .
-    \end{align*}
-     We first prove (1). Notice that for every $\varepsilon > 0$ and $n\in \naturals$,
-    \begin{align*}
-      \{|S_n- T_n| > \varepsilon\}\subseteq \bigcup_{i=1}^n \{X_{ni}\neq Y_{ni}\}
-      = \bigcup_{i=1}^n \{|X_{ni}|>b_n\},
-    \end{align*}
-    and, as a result, by Boole's inequality we have
-    \begin{align*}
-      \P_n (|S_n - T_n|>\varepsilon) \leq \sum_{i=1}^n \P_n(|X_{ni}|>b_n) \to 0,
-    \end{align*}
-    which proves (1).
-Next, we prove (2).
-Since $\mc{L}^2$ implies convergence in probability, it suffices to show that $(T_n-\E[T_n])/b_n \clt 0$, i.e., $\var[T_n]/(b_n)^2 \to 0$.
-Since $X_{n1}, \ldots, X_{nn}$ are pairwise independent, so are $Y_{n1}, \ldots, Y_{nn}$, and consequently
-    \begin{align*}
-      \Var_n[T_n]=\sum_{i=1}^n \Var_n[Y_{ni}] \leq \sum_{i=1}^n \E_n[(c_{ni}X_{ni})^2; |X_{ni}|\leq b_n] \leq K^2\sum_{i=1}^n \E_n[(X_{ni})^2; |X_{ni}|\leq b_n].
-    \end{align*}
-    As a result,
-    \begin{align*}
-    0\leq   \frac{\Var_n[T_n]}{b_n^2}\leq K^2 \cdot  \frac{1}{b_n^2}\sum_{i=1}^n \E_n[(X_{ni})^2; |X_{ni}|\leq b_n] \to 0,
-    \end{align*}
-    which proves the result by sandwich theorem.
-\end{proof}
-
-\begin{corollary}
-\label{coro1}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
+\begin{prop}
+\label{votprop2}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
 \begin{align*}
@@
 \end{align*}
-\end{corollary}
-
-\begin{proof}
-  The proof is rather similar to Proposition \ref{votprop}. It suffices to show that
-  \begin{align*}
-   \sum_{i\in \mc{I}_n} w_i I(p_i \leq  \alpha) \cp \kappa_1 =  \P(p_1 \leq \alpha).
-  \end{align*}
-  and the remaining proof is the same as that of Proposition \ref{votprop} in terms of applying Dominated Convergence Theorem in the version of  convergence in probability.
-As $p_i$ are pairwise independent for $i\in \mc{I}_n$, $I(p_i\leq \alpha)$ are pairwise independent for $i \in \mc{I}_n$.
-The idea is to prove the required condition of Lemma \ref{gwlln} holds.
-As  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$, $b_n > 1$, and  $b_n \to \infty$ as $n \to \infty$,
-  \begin{align*}
-    & \sum_{i\in \mc{I}_n} \P\big( I(p_i \leq  \alpha) > b_n\big) \to 0\\
-   & \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} \E\big[ I(p_i \leq  \alpha) \,|\, I(p_i \leq  \alpha) \leq b_n\big]
-     =  \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} \P\big(p_i \leq\alpha \big)
-     = \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} w_i \kappa_i  \to 0
-  \end{align*}
-  because $ \sum_{i\in \mc{I}_n} w_i \kappa_i = O(1)$ by the assumption $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_{1}$.
-Let $c_{ni} = w_i b_n$ for $i \in \mc{I}_n$.
-Since $w_i b_n\leq K$ for some $K > 0$ and $b_n$, we have
-  \begin{align*}
-    & \frac{1}{b_n} \sum_{i\in \mc{I}_n}  c_{ni} \big(  I(p_i \leq  \alpha) - \P( I(p_i \leq  \alpha) \, |\,  I(p_i \leq  \alpha)  \leq b_n )  \big) \\
-  = \quad     &\frac{1}{b_n} \sum_{i\in \mc{I}_n}  c_{ni} \big(  I(p_i \leq  \alpha) - \P( I(p_i \leq  \alpha) \big)  \cp 0
-  \end{align*}
-  which follows from Lemma \ref{gwlln}. The above is equivalent to
-  \begin{align*}
-   \sum_{i\in \mc{I}_n}  w_i I(p_i \leq  \alpha) - \sum_{i\in \mc{I}_n} w_i  \kappa_i  \cp 0
-  \end{align*}
-  As $\sum_{i\in \mc{I}_n} w_i  \kappa_i\to \kappa_1$ as $n \to \infty$, by Slutsky's Theorem,
-  \begin{align*}
-     \sum_{i\in \mc{I}_n}  w_i I(p_i \leq  \alpha)  \cp \kappa_1,
-  \end{align*}
-  which finishes the proof.
-\end{proof}
+\end{prop}
 
@@
 The intuition is that  it is impossible to find a weight to constrain the random behavior of the Bernoulli random variables $I(p_i\leq \alpha)$ for $i \in \mc{I}_n$ such that the weak law of large number can apply.
-Nevertheless, in this case, if $\kappa_i = \P(p_i\leq \alpha)$ for $i\in \mc{I}_n$ is small, the approximation for the misclassification in Corollary \ref{coro1} is favorable.
+Nevertheless, in this case, if $\kappa_i = \P(p_i\leq \alpha)$ for $i\in \mc{I}_n$ is small, the approximation for the misclassification in Proposition \ref{votprop2} is favorable.
 This situation occurs very frequently in practice.
@@
 \end{align*}
-where the last second step assumes that $\{I(p_i\leq \alpha)\colon i\in \mc{I}_n\}$ are independent and the last step uses the condition $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_1$ as $n\to \infty$, which is used in Corollary \ref{coro1}.
-Notice that if $\kappa_i$ is very small, the mean squared error of $\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)$ turns out to be small such that by the rationale of the proof of Proposition \ref{votprop}, the asymptotic approximation for the misclassification error in  Corollary \ref{coro1} should be acceptable.\\
-
-\newpage
+where the last second step assumes that $\{I(p_i\leq \alpha)\colon i\in \mc{I}_n\}$ are independent and the last step uses the condition $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_1$ as $n\to \infty$, which is used in Proposition \ref{votprop2}.
+Notice that if $\kappa_i$ is very small, the mean squared error of $\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)$ turns out to be small such that by the rationale of the proof of Proposition \ref{votprop}, the asymptotic approximation for the misclassification error in  Proposition \ref{votprop2} should be acceptable.
+
+We now motivate a model selection framework for comparing different models in the donor pool with a goal of inferring which model is most appropriate for the time series under study.
 
@@
 Note that Corollary \ref{coro2} gives an asymptotic upper bound for the misclassification rate of synthetic pairwise model selection, which is small if $\xi_1$ is large.
+
+%We further define the parameter sets
+%\begin{align}
+%\begin{array}{l}
+% \;\, \Theta = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
+%   \Theta_1 = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon  t= 1, \ldots, T_i, i = 1\}
+%\end{array}\label{parameter} 
+%\end{align}
+
+\subsection{Forecasting and testing for shock persistence}
+\label{forecast}
+
+In this section, we motivates the relation between shock persistence testing and forecasting comparison.
+In time series literature, under a squared error loss $L(\cdot)$, the forecast using the conditional mean is the best point forecast that minimizes the expected loss if the model is specified correctly.
+That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional mean forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases.
+On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information and makes good use of it should enjoy a smaller expected loss than any conditional mean forecast without such information does.
+In other words, the problem of testing for shock persistence boils down into comparing the conditional mean forecast that is adjusted by shock information and the one that is unadjusted.
+To deal with this problem, we applied the forecast comparison procedure of  \cite{quaedvlieg2021multi} to conduct shock persistence testing.
+
+In this paper, we extend the framework of post-shock forecast \citep{lin2021minimizing}, which aggregates outside information by constructing a donor pool, to post-shock persistence testing.
+The donor pool consists of time series called  ``donors'' that are similar to the time series of interest.
+As we do not observe the future data, information from donors can aid our decision making and forecasts.
+Note that what  similarity exactly means here can be vague but the donors and the time series of interest should come from a common population in principle; see more details of how to select donors in \cite{lin2021minimizing}.
+In this paper, we also proposed several theoretical results with some detailed conditions on the donor pool, which may alleviate the difficulty of dealing with similarity when choosing donors.
+
+In this paper, we propose a new way of aggregating information from donor pool to conduct post-shock persistence testing, which is quite different from \cite{lin2021minimizing}.
+The general structure of this aggregation technique is illustrated as below.
+Suppose we are given a nonempty donor pool with size $n$ that consists of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed.
+With shock information, we are able to compute unadjusted forecast that does not incorporate shock information and adjusted forecast that does.
+The forecast comparison using methodology of \cite{quaedvlieg2021multi} for each donor yields a $p$-value, $p_{i+1}$ for $i$th donor in the donor pool.
+Given $\{p_i \colon i = 2, \ldots, n+1\}$, we propose a methodology for judging whether the shock of the time series of interest is persistent or not.
+Next, we illustrate the details of our methodology as below.
+
+For each donor $\mc{T}_i$, $i = 2, \ldots, n+1$, to compare adjusted and unadjusted forecasts,  a model needs to be specified.
+The model should describe how the shock impacts the time series at and after a certain time point $t= T_i^* + 1$.
+For clarity, we refers the unadjusted forecast to the conditional mean forecast based on the part of the model that ignores shock effect; and the adjusted forecast refers to the conditional mean forecast based on the full model.
+Note that the model needs not to be the same for every donor in the donor pool.
+However, certain conditions need to be imposed as discussed previously.
+
+ Given a model for each donor pool, we compute the unadjusted conditional mean forecast and adjusted conditional mean forecast in the framework of \cite{quaedvlieg2021multi}.
+As introduced in the beginning of Section \ref{section2}, for a given horizon $h$, to forecast $y_{i, t}$, we compute the two forecasts based on the information set $\mathcal{F}_{i, t-h}$ of each donor pool (i.e., the data before $t-h$) for $i = 2, \ldots, n+1$.
+Note that in practice, a training sample size $K_i$ should be specified for $i = 2, \ldots, n+1$ such that we use the information set $\mathcal{F}_{i, t-h-K_i + 1:t-h}$.
+
+ Even if the data contain shock information for each donor, it is impossible to compute the adjusted conditional mean forecast based on $\mathcal{F}_{i, t-h}$ when $t -h \leq T_i^*$, i.e., we only have training data that do no have any shock information.
+Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information.
+In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an consistent estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate.
+However, the consistent estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.
+To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear.
+However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.
+
+ With the presence of autoregressive parameters in some models, unbiased estimation with OLS  is not feasible but the bias is $O(T^{-1})$, where $T$ is the time series length \citep{shaman1988bias}.
+In this paper, we use the OLS estimates to approximate the adjusted conditional mean forecast and unadjusted one.
+The bias decades away as $T\to \infty$.
+
+\vspace*{0.5cm}
+
+\noindent\textbf{Note}: Our forecast needs to be written with respect to our general model. Specifics can be given when we conduct our numerical examples.
+\vspace*{0.5cm}
+
+In our post-shock setting we consider the following candidate forecasts: 
+\begin{align*}
+  &\text{Forecast 1}: \\
+  &\text{Forecast 2}: 
+\end{align*}
+We want to determine which forecast is appropriate over a horizon while the methods in \cite{lin2021minimizing} were only appropriate in the nowcasting setting in which prediction was only focused on the response immediately following the shock.
+
+\newpage
 
@@
 
+\textcolor{red}{A lot is needed here.
+We need to say that we are assuming that government lockdowns are temporary or rather that the effect of government lockdowns will be temporary.
+We need to mention that none of the time series in the donor pool involve lockdowns.
+We should consider a few time horizons.
+Something like 2, 3, or 4 months ahead might be interesting (we may need to consider a less complex dynamic model for fitting purposes).
+I would guess that a shorter window may exhibit disagreement between the donor pool and the series under study or may show different decisions being reported.
+}
+
 Arguably the most watched macroeconomic indicator for the US economy is the monthly release of the total nonfarm payrolls, which reflects the gains or losses of persons employed.
@@
 
+\section{Mathematical Appendix}
+
+Proof of Proposition~\ref{votprop}:
+
+\begin{proof}
+Notice that as $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$ and $I(p_i \leq  \alpha) $ is a Bernoulli random variable, $I(p_i \leq  \alpha)$ is identically distributed for  $i = 1, \ldots, n+1$.
+Since $p_i$ is pairwise independent and $p_i$ are identically distributed for $i = 2, \ldots, n+1$, by Weak Law of Large Numbers,
+\begin{align*}
+  \frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha)  
+   \stackrel{p}{\rightarrow}  \P(p_i \leq \alpha) = \P(p_1 \leq \alpha),
+\end{align*}
+Define
+\begin{align*}
+  f \colon [0,1] \mapsto \{0,1\} 
+  \text{ with }
+  f(x) = I(x \geq 0.5).
+\end{align*}
+Let $C(f)$ denote the continuity set of $f$. Suppose that $\P(p_1 \leq  \alpha) \neq 0.5$. In this case, notice that 
+\begin{align*}
+  \P(\P(p_1 \leq  \alpha) \in C(f)) =1.
+\end{align*}
+By Slutsky's Theorem, we have
+\begin{align*}
+  I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  \stackrel{p}{\rightarrow} 
+  I\{ \P(p_1 \leq  \alpha) \geq 0.5\}.
+\end{align*}
+It follows that
+\begin{align*}
+   I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}- I( p_1 \leq  \alpha) 
+  \stackrel{p}{\rightarrow} 
+  I\{ \P(p_1 \leq  \alpha) \geq 0.5\} - I( p_1 \leq  \alpha) 
+\end{align*}
+Since the function $g(x)= |x|$ is continuous in $x$,  by continuous mapping theorem, 
+\begin{align*}
+  \bigg|  I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \bigg| \stackrel{p}{\rightarrow}   |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
+  - I( p_1 \leq  \alpha) |
+\end{align*}
+Moreover, note that
+\begin{align*}
+\E \left\{ |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
+  - I( p_1 \leq  \alpha) |\right\}
+  & = \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases} \\
+  & \leq  0.5.
+\end{align*}
+Due to the fact that
+\begin{align*}
+ \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right| \leq 1
+\end{align*}
+is bounded by 1, by Dominated Convergence Theorem for the version of convergence in measure,
+\begin{align*}
+ \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right|
+  \stackrel{\mathcal{L}_1}{\rightarrow}  |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
+  - I( p_1 \leq  \alpha) |.
+\end{align*}
+That would imply that 
+\begin{align*}
+  \E \bigg\{\left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
+  - I( p_1 \leq  \alpha) \right|\bigg\}
+  \to  \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases}
+\end{align*}
+That is, the expected misclassification rate of voting converges to 
+\begin{align*}
+  \begin{cases}
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+  \end{cases}
+\end{align*}
+\end{proof}
+
+We now provide a proof for Proposition~\ref{votprop2}. This proof requires a lemma from probability theory whose proof we include for completeness.
+
+\begin{lem}
+  \label{gwlln}  For each $n\in \naturals$, let $c_{n1}, \ldots, c_{nn}$ be real numbers bounded by some $K > 0$, and let $X_{n1}, \ldots, X_{nn}$ be pairwise independent random variables defined on a probability space $(\Omega_n, \mc{F}_n, \P_n)$, and let $\E_n$ and $\var_n$ denote the corresponding expectation and variance.
+If $(b_n)$ is a sequence of positive numbers such that $b_n \uparrow \infty$ such that
+    \begin{align*}
+      \sum_{i=1}^n \P_n (|X_{ni}| > b_n) \to 0
+      \quad \text{ and } 
+      \quad \frac{1}{(b_n)^2} \sum_{i=1}^n \E_n[X_{ni}^2; |X_{ni}|\leq b_n] \to 0,
+    \end{align*}
+    then
+    \begin{align*}
+      \frac{1}{b_n} \sum_{i=1}^n c_{ni} (X_{ni} - \E_n[X_{ni}; X_{ni} \leq b_n]) \cp 0.
+    \end{align*}
+\end{lem}
+
+\begin{proof}
+  For each $n\in \naturals$ set
+    \begin{align*}
+      S_n = \sum_{i=1}^n c_{ni} X_{ni}, \quad T_n = \sum_{i=1}^n c_{ni} Y_{ni},
+      \quad Y_{ni} = X_{ni} I(|X_{ni}|\leq b_n), \quad i = 1, \ldots, n.
+    \end{align*}
+   The goal is to show that  $(S_n- \E_n[T_n])/b_n \cp 0$. For this, it suffices to show that (1) $(T_n - S_n)/b_n \cp 0$ and (2) $(T_n - \E_n[T_n])/b_n \cp 0$ because
+    \begin{align*}
+      (T_n - \E_n[T_n])/b_n -(T_n - S_n)/b_n = (S_n- \E_n[T_n])/b_n .
+    \end{align*}
+     We first prove (1). Notice that for every $\varepsilon > 0$ and $n\in \naturals$,
+    \begin{align*}
+      \{|S_n- T_n| > \varepsilon\}\subseteq \bigcup_{i=1}^n \{X_{ni}\neq Y_{ni}\}
+      = \bigcup_{i=1}^n \{|X_{ni}|>b_n\},
+    \end{align*}
+    and, as a result, by Boole's inequality we have
+    \begin{align*}
+      \P_n (|S_n - T_n|>\varepsilon) \leq \sum_{i=1}^n \P_n(|X_{ni}|>b_n) \to 0,
+    \end{align*}
+    which proves (1).
+Next, we prove (2).
+Since $\mc{L}^2$ implies convergence in probability, it suffices to show that $(T_n-\E[T_n])/b_n \clt 0$, i.e., $\var[T_n]/(b_n)^2 \to 0$.
+Since $X_{n1}, \ldots, X_{nn}$ are pairwise independent, so are $Y_{n1}, \ldots, Y_{nn}$, and consequently
+    \begin{align*}
+      \Var_n[T_n]=\sum_{i=1}^n \Var_n[Y_{ni}] \leq \sum_{i=1}^n \E_n[(c_{ni}X_{ni})^2; |X_{ni}|\leq b_n] \leq K^2\sum_{i=1}^n \E_n[(X_{ni})^2; |X_{ni}|\leq b_n].
+    \end{align*}
+    As a result,
+    \begin{align*}
+    0\leq   \frac{\Var_n[T_n]}{b_n^2}\leq K^2 \cdot  \frac{1}{b_n^2}\sum_{i=1}^n \E_n[(X_{ni})^2; |X_{ni}|\leq b_n] \to 0,
+    \end{align*}
+    which proves the result by sandwich theorem.
+\end{proof}
+
+We now have enough to prove Proposition \ref{votprop2}:
+
+\begin{proof}
+  The proof is rather similar to Proposition \ref{votprop}. It suffices to show that
+  \begin{align*}
+   \sum_{i\in \mc{I}_n} w_i I(p_i \leq  \alpha) \cp \kappa_1 =  \P(p_1 \leq \alpha).
+  \end{align*}
+  and the remaining proof is the same as that of Proposition \ref{votprop} in terms of applying Dominated Convergence Theorem in the version of  convergence in probability.
+As $p_i$ are pairwise independent for $i\in \mc{I}_n$, $I(p_i\leq \alpha)$ are pairwise independent for $i \in \mc{I}_n$.
+The idea is to prove the required condition of Lemma \ref{gwlln} holds.
+As  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$, $b_n > 1$, and  $b_n \to \infty$ as $n \to \infty$,
+  \begin{align*}
+    & \sum_{i\in \mc{I}_n} \P\big( I(p_i \leq  \alpha) > b_n\big) \to 0\\
+   & \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} \E\big[ I(p_i \leq  \alpha) \,|\, I(p_i \leq  \alpha) \leq b_n\big]
+     =  \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} \P\big(p_i \leq\alpha \big)
+     = \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} w_i \kappa_i  \to 0
+  \end{align*}
+  because $ \sum_{i\in \mc{I}_n} w_i \kappa_i = O(1)$ by the assumption $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_{1}$.
+Let $c_{ni} = w_i b_n$ for $i \in \mc{I}_n$.
+Since $w_i b_n\leq K$ for some $K > 0$ and $b_n$, we have
+  \begin{align*}
+    & \frac{1}{b_n} \sum_{i\in \mc{I}_n}  c_{ni} \big(  I(p_i \leq  \alpha) - \P( I(p_i \leq  \alpha) \, |\,  I(p_i \leq  \alpha)  \leq b_n )  \big) \\
+  = \quad     &\frac{1}{b_n} \sum_{i\in \mc{I}_n}  c_{ni} \big(  I(p_i \leq  \alpha) - \P( I(p_i \leq  \alpha) \big)  \cp 0
+  \end{align*}
+  which follows from Lemma \ref{gwlln}. The above is equivalent to
+  \begin{align*}
+   \sum_{i\in \mc{I}_n}  w_i I(p_i \leq  \alpha) - \sum_{i\in \mc{I}_n} w_i  \kappa_i  \cp 0
+  \end{align*}
+  As $\sum_{i\in \mc{I}_n} w_i  \kappa_i\to \kappa_1$ as $n \to \infty$, by Slutsky's Theorem,
+  \begin{align*}
+     \sum_{i\in \mc{I}_n}  w_i I(p_i \leq  \alpha)  \cp \kappa_1,
+  \end{align*}
+  which finishes the proof.
+\end{proof}
+
 \bibliographystyle{plainnat}

### 2022-03-23 prevalence_testing/postshocktest2022draft.tex
more updates; more to do; starting to take shape

@@
 as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
-$$
+\begin{equation} \label{bootp}
   \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
-$$
+\end{equation}
 The results \eqref{boott} implies that 
-\begin{equation} \label{bootp}
+$$
   |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
-\end{equation}
+$$
 where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$.
@@
 \end{equation}
-where the distributions $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_{i'}}(\x_{i,T_i^*+1})$ satisfy $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1}) \overset{d}{=} \mathcal{F}_{\tilde{\mathbf{\phi}}_{j}}(\x_{i',T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_j}(\x_{i,T_i^*+1}) \overset{d}{=} \mathcal{F}_{\tilde{\mathbf{\theta}}_{j}}(\x_{i',T_i^*+1})$ when $\x_{i,T_i^*+1} = \x_{i',T_i^*+1}$.
-Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}}$ must be small relative to the signal strength.
-
-We see that model \eqref{model-gen} with its accompanying random effects structure \eqref{random-effects} is flexible enough to capture changing structural dynamics as well as a mean-shift, and is a generalization of the model in \cite{lin2021minimizing}.
+where the distributions $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_{i'}}(\x_{i,T_i^*+1})$ satisfy 
+$\|\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1}) - \mathcal{F}_{\tilde{\mathbf{\phi}}_{j}}(\x_{i',T_i^*+1})\|_p \to 0$ and $\|\mathcal{F}_{\tilde{\mathbf{\theta}}_j}(\x_{i,T_i^*+1}) - \mathcal{F}_{\tilde{\mathbf{\theta}}_{j}}(\x_{i',T_i^*+1})\|_p \to 0$ as $\|\x_{i,T_i^*+1} - \x_{i',T_i^*+1}\| \to 0$ where $\|\cdot\|_p$ is a distance metric for distributions and $\|\cdot\|$ is a norm for elements in Euclidean space.
+Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}}$ must be small relative to the signal strength which is captured in $\x_{i,T^*_i+1}$.
+
+We see that model \eqref{model-gen} with its accompanying random effects structure \eqref{random-effects} is flexible enough to capture changing structural dynamics as well as a mean-shift, and is a generalization of the models mentioned in \cite{lin2021minimizing}.
 Note that the flexibility of allowing for changing structural dynamics is useful for fitting purposes, but it does not necessarily reflect the state of the world in the post-shock setting.
@@
 
-\vspace*{0.5cm}\noindent\textcolor{red}{Explain h-ahead forecasts here}
+\vspace*{0.5cm}\noindent\textcolor{red}{Jilei, explain how the h-ahead forecasts are computed here}
 
@@
 
-\noindent\textcolor{red}{Much more is needed here}
-
-\noindent\textbf{Note}: We need to explain what the voting method is, possibly in algorithmic format.
-Also note that the p-values that we obtain are computed using a bootstrap procedure.
-Perhaps an additional proposition that states the performance of these bootstrap p-values would further guarantee reliability.
+In this section we discuss aggregation techniques for combining the multi-horizon forecast p-values in Section \ref{sec:multhor} computed from forecasts from models in Section \ref{modelsetup} to illicit a decision about the transient or persistence of a structural shock.
+
+The post-shock dynamics in model~\eqref{model-gen} with random effect structure~\eqref{random-effects} are explicitly constructed so that series with similar covariates at time $T^*_i + 1$ have similar post-shock dynamics.
+This facilitates the use of simple p-value combination methods provided that there exists donors $i$ in the donor pool which have $\x_{i,T^*_i+1}$ close to $\x_{1,T^*_1+1}$.
+We will motivate two such p-value combination approaches.
+
+The first approach is a weighted average of the p-values computed in the donor pool which are calculated as in Section \ref{sec:multhor}.
+The weights reflect the similarity between $\x_{i,T^*_i+1}$ and $\x_{1,T^*_1+1}$, and are similar to the weights computed in \cite{lin2021minimizing}.
+We now discuss the details.
+Let
+\begin{align*}
+	\bs{X}= \begin{pmatrix}
+		\bs{x}_{1, T_1^*+1} & \cdots & \bs{x}_{1, T_1^*-q_2+1}\\
+		\vdots &  \ddots & \vdots  \\
+		\bs{x}_{n+1, T_{n+1}^*+1} & \cdots & \bs{x}_{1, T_1^*-q_2+1}
+	\end{pmatrix}.
+\end{align*}
+The reason for including $\bs{x}_{i, T_i^*-q_2+1}$ is that the dynamic model \eqref{model-gen} considers lagged covariate values in its shock construction.
+Let $\mbf{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1.
+We compute the weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}.
+Note that the modeling part for the response $y_{i,t}$ does not necessarily involve scaled covariates.
+From this construction we obtain the weighted average p-value
+\begin{equation} \label{wpval}
+ \hat{p}_1 = \sum_{i=2}^{n+1} w_i^* \hat{p}_i^B,	
+\end{equation}
+where $\hat{p}_i^B$ is given as \eqref{bootp} and $w_i^*$ is the weight corresponding to the similarity between the first and $(i+1)$th row of $\mbf{X}^*$.
+
+We now motivate a voting method based on the p-values computed in the donor pool.
+\textcolor{red}{Jilei, you need to explain what the voting method is, possibly in algorithmic format.}
 
 \begin{prop}
-
 \label{votprop}Suppose $p_2, \ldots, p_{n+1}$ is  a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest.
@@
   \to  \begin{cases}
-    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
-    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
+    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5, \\
+    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5. 
   \end{cases}
@@
 
-Suppose we are interested in comparing two models $\mc{M}_1$ and $\mc{M}_2$ using AIC for forecasting the response in the time series of interest.
+Suppose we are interested in comparing two models $\mc{M}_0$ and $\mc{M}$ using AIC for forecasting the response in the time series of interest.
 However, direct comparison is not feasible as the data are not observed.
@@
 Let $\xi_i = \P(a_i^1 < a_i^2)$.
-Note that if the data generating process is based on $\mc{M}_1$ and is true for all the donors and time series of interest, $\xi_i$ is expected to be high.
+Note that if the data generating process is based on $\mc{M}_0$ and is true for all the donors and time series of interest, $\xi_i$ is expected to be high.
 Additionally, it is reasonable to assume $\xi_i =\xi $ for $\xi \in [0,1]$ and $i = 1, \ldots, n+1$.
@@
 Suppose that  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$ as $n \to \infty$, and $w_i b_n\leq K$ for $i\in \mc{I}_n$ and some $K>0$, where $b_n \geq 1$ and $b_n \to \infty$ as $n\to \infty$.
-Assume for $i \in \mc{I}_n$,  $\{a_i^1, a_i^2\}$ are AICs of $\mc{M}_1$ and  $\mc{M}_2$ for $i$th time series, which are pairwise independent of $\{a_j^1, a_j^2\}$ for $j \neq i$ and that
+Assume for $i \in \mc{I}_n$,  $\{a_i^1, a_i^2\}$ are AICs of $\mc{M}_0$ and  $\mc{M}$ for $i$th time series, which are pairwise independent of $\{a_j^1, a_j^2\}$ for $j \neq i$ and that
 \begin{align*}
@@
 The bias decades away as $T\to \infty$.
-
-\vspace*{0.5cm}
-
-\noindent\textbf{Note}: Our forecast needs to be written with respect to our general model. Specifics can be given when we conduct our numerical examples.
-\vspace*{0.5cm}
-
-In our post-shock setting we consider the following candidate forecasts: 
-\begin{align*}
-  &\text{Forecast 1}: \\
-  &\text{Forecast 2}: 
-\end{align*}
-We want to determine which forecast is appropriate over a horizon while the methods in \cite{lin2021minimizing} were only appropriate in the nowcasting setting in which prediction was only focused on the response immediately following the shock.
-
-\newpage
 
@@
 
+We will consider two models to analyze these datasets.
+The first model $\mc{M}_0$ is a simplification of the model~\eqref{model-gen} involving no changes to the post-shock dynamics.
+This model is explicitly written as,
+ \begin{align*}
+ 	y_{i,t} &= \eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j}  +\sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1}  + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
+ 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
+ \end{align*}
+where $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$ and $t = 1, \ldots, T_i$.
+Model $\mc{M}_0$ describes the setting where one additive shock effect is permanent (persistent) over time, and we will refer to it as the ``permanent" model (\textcolor{red}{should be ``persistent"?}).
+The second model under consideration is  the ``dynamic'' model \eqref{model-gen} which is denoted $\mc{M}$ .
+Both models will specify that $q_1=q_2$.
+%\begin{align*}
+ %	y_{i,t}
+% 	&= \left(\eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
+% 	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
+% 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
+% \end{align*}
+ %where $q_1 = q_2=2$,  $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$, and $t = 1, \ldots, T_i$.
+We estimate $\mc{M}_0$ and $\mc{M}$ using ordinary least squares (OLS) estimation.
+$\mc{M}$ adds more flexibility to $\mc{M}_0$ by allowing that the model of $y_{i,t}$ changes after the shock, as seen from the term related to $1-D_{i,t}$,  though the model still preserves the autoregressive model form.
+In practice, $\mc{M}$ should make more sense than $\mc{M}_0$ as it accommodates for more complicated cases.
+However, $\mc{M}$  requires far more degrees of freedom for estimation and this can increase variance in estimation.
+For this purpose, the synthetic pairwise model selection proposed in the Corollary \ref{coro2} can be used to select between $\mc{M}_0$ and $\mc{M}$.
+
 \subsection{Testing shock prevalence for Conoco Phillips stock price series}
@@
 
-Post-shock  prevalence testing is motivated by post-shock prediction  \citep{lin2021minimizing} and also an extension of it from the perspective of hypothesis testing.
+%Post-shock  prevalence testing is motivated by post-shock prediction  \citep{lin2021minimizing} and also an extension of it from the perspective of hypothesis testing.
 Applying our methodology  on one of the datasets demonstrated in \cite{lin2021minimizing} helps connect our work to \cite{lin2021minimizing} and spell out the differences between two methodologies.
 
-As illustrated in Section 5.1 in \cite{lin2021minimizing}, it is found that Conoco Phillips stock price experienced unprecedented shocks due to  oil supply control and COVID-19 pandemic on one single day,  March 9th, 2020.
-In this data example, we are interested in investigating whether this shock is prevalent, i.e., whether the impact of the shock on the stock price will persist over time.
+As illustrated in Section 5.1 in \cite{lin2021minimizing}, it is found that Conoco Phillips stock price experienced unprecedented shocks due to a Russia-OPEC oil supply control battle and increasing COVID-19 pandemic fear which were simultaneously realized on Monday, March 9th, 2020.
+In this data example, we are interested in investigating whether the shock studied in \cite{lin2021minimizing} is transient or prevalent.
 Denote the stock price of Conoco Phillips at time $t$ as $y_{i,t}$ for $i$th time series, where $i = 1, \ldots n+1$, the time series of interest is ordered as the 1st time series, and $n$ is the donor pool size.
@@
 In other words, we analyzed the three shock effects within one time series and considered three donors in our donor pool.
-
-To analyze the dataset, we propose two models. Denote the covariate vector at time $t$ for $i$th time series by $\bs{x}_{i,t}$.  The first model $\mc{M}_1$, called ``permanent'' model, is 
- \begin{align*}
- 	y_{i,t} &= \eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j}  +\sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1}  + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
- 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
- \end{align*}
-where $q_1 = q_2=2$, $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$ and $t = 1, \ldots, T_i$.
-Note that we allow the shock effect to take effect for multiple time points instead of one time point as in  \cite{lin2021minimizing}.
-This simple model describes the setting where one additive shock effect is persistent over time.
-The second model $\mc{M}_2$, called ``dynamic'' model, is
-\begin{align*}
- 	y_{i,t}
- 	&= \left(\eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
- 	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
- 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
- \end{align*}
- where $q_1 = q_2=2$,  $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$, and $t = 1, \ldots, T_i$.
-We estimate $\mc{M}_1$ and $\mc{M}_2$ using ordinary least squares (OLS) estimation.
-$\mc{M}_2$ adds more flexibility to $\mc{M}_1$ by allowing that the model of $y_{i,t}$ changes after the shock, as seen from the term related to $1-D_{i,t}$,  though the model still preserves the autoregressive model form.
-In practice, $\mc{M}_2$ should make more sense than $\mc{M}_1$ as it accommodates for more complicated cases.
-However, $\mc{M}_2$  requires far more degrees of freedom for estimation and this can increase variance in estimation.
-For this purpose, the synthetic pairwise model selection proposed in the Corollary \ref{coro2} can be used to select between $\mc{M}_1$ and $\mc{M}_2$.
-
- In computing the weights, to avoid the impact of unit differences from different columns of covariates on weighting, we center and scale the covariates. The steps are detailed as below. Consider
-\begin{align*}
-	\bs{X}= \begin{pmatrix}
-		\bs{x}_{1, T_1^*+1} & \bs{x}_{1, T_1^*}\\
-		\vdots & \vdots  \\
-		\bs{x}_{n+1, T_{n+1}^*+1} & \bs{x}_{1, T_1^*}
-	\end{pmatrix},
-\end{align*}
-where $t = T_i^*+1$ is the time point when the shock effect takes place for $i$th time series.
-Note that the reason for including $\bs{x}_{i, T_i^*}$ is that we consider $q_2=2$ in $\mc{M}_1$ and $\mc{M}_2$.
-In other words, the consider the 1-step lagged covariates in the model and its corresponding shock effect time point is $T_i^*$.
-For each column of $\bs{X}$, we center it by subtracting its column mean and scale the resulting column vector by dividing the standard deviation of the resulting column vector.
-Denote the resulting covariates matrix by $\bs{X}^*$.
-We compute the synthetic weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}.
-However, for the model of $y_{i,t}$, we do not conduct such centering and scaling procedure.
 
@@
 We set $H = 10$, $K = 30$, and $T_i =  H + K + L+15$ for $i = 2, \ldots, 4$.
-That being said, for $t = K + H + 1, \ldots, T_i$ and $h = 1, \ldots, H$, different $h$-step adjusted and unadjusted forecasts for $y_{i,t}$ under $\mc{M}_1$ or  $\mc{M}_2$ are compared.
+That being said, for $t = K + H + 1, \ldots, T_i$ and $h = 1, \ldots, H$, different $h$-step adjusted and unadjusted forecasts for $y_{i,t}$ under $\mc{M}_0$ or  $\mc{M}$ are compared.
 
@@
      \hline 
-     7 & $\mc{M}_1$  & \multirow{2}{*}{$0.817$} & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
-     7 & $\mc{M}_2$  &  & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     15 & $\mc{M}_1$ & \multirow{2}{*}{$0.817$}  & 1   & $0.82$ & 0 (Yes) &1 (No)    \\
-     15 &  $\mc{M}_2$ & & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
-     30 &  $\mc{M}_1$ & \multirow{2}{*}{$1$}  & 1   & $0.82$ & 0 (Yes) &1 (No)   \\
-     30 &  $\mc{M}_2$ &  & 1  & 0 &0 (Yes) & 0 (Yes)  
+     7 & $\mc{M}_0$  & \multirow{2}{*}{$0.817$} & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
+     7 & $\mc{M}$  &  & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     15 & $\mc{M}_0$ & \multirow{2}{*}{$0.817$}  & 1   & $0.82$ & 0 (Yes) &1 (No)    \\
+     15 &  $\mc{M}$ & & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
+     30 &  $\mc{M}_0$ & \multirow{2}{*}{$1$}  & 1   & $0.82$ & 0 (Yes) &1 (No)   \\
+     30 &  $\mc{M}$ &  & 1  & 0 &0 (Yes) & 0 (Yes)  
   \end{tabular}
@@
 
-Let $a_i^1$ and $a_i^2$ denote the AICs of $\mc{M}_1$ and $\mc{M}_2$ for $i$th time series, respectively.
-Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, as  $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)>0.5$ for $L = 7, 15, 30$, we conclude that $\mc{M}_2$ is preferred over $\mc{M}_1$.
-Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and $\mc{M}_2$.
-The test  using $\hat{p}$ with $\mc{M}_2$ fails to reject that  the shock, which was to take effect at $t=T_1^*+1$,  is prevalent for $t > T_1^*+1$ under a significance level of 5\%.
-Nevertheless, the results appear to be a little different for $\mc{M}_1$.
-For $L=7$, $|\hat{p}-p_1|=0$ for $\mc{M}_1$ whereas $|\hat{p}-p_1|=0.82$ for $L = 15, 30$.
-Based on the performance of $\mc{M}_2$, it is possible that as the time window $L$ increases, the signal from changing parameters covariates is ``misunderstood'' by $\mc{M}_1$ as shock signal.
+Let $a_i^1$ and $a_i^2$ denote the AICs of $\mc{M}_0$ and $\mc{M}$ for $i$th time series, respectively.
+Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, as  $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)>0.5$ for $L = 7, 15, 30$, we conclude that $\mc{M}$ is preferred over $\mc{M}_0$.
+Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and $\mc{M}$.
+The test  using $\hat{p}$ with $\mc{M}$ fails to reject that  the shock, which was to take effect at $t=T_1^*+1$,  is prevalent for $t > T_1^*+1$ under a significance level of 5\%.
+Nevertheless, the results appear to be a little different for $\mc{M}_0$.
+For $L=7$, $|\hat{p}-p_1|=0$ for $\mc{M}_0$ whereas $|\hat{p}-p_1|=0.82$ for $L = 15, 30$.
+Based on the performance of $\mc{M}$, it is possible that as the time window $L$ increases, the signal from changing parameters covariates is ``misunderstood'' by $\mc{M}_0$ as shock signal.
 
@@
 As we observe $\{y_{1,t} \colon 1, \ldots, T_1\}$, we are able to check whether the decision of voting and weighted voting is correct.
-From the sixth column of Table \ref{coptable}, we can see that voting procedure suggests shock transience for $\mc{M}_1$ and $\mc{M}_2$ for different $L$.
-However, weighted voting suggests shock transience for $\mc{M}_2$ for different $L$ but shock prevalence for $\mc{M}_1$ and $L=15, 30$ and shock transience for $\mc{M}_1$ and $L = 7$.
+From the sixth column of Table \ref{coptable}, we can see that voting procedure suggests shock transience for $\mc{M}_0$ and $\mc{M}$ for different $L$.
+However, weighted voting suggests shock transience for $\mc{M}$ for different $L$ but shock prevalence for $\mc{M}_0$ and $L=15, 30$ and shock transience for $\mc{M}_0$ and $L = 7$.
 As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small.
@@
 Note that the interpretation and meaning of $p_1$ is closely connected with models.
-For example, $\mc{M}_1$ would imply a persistent shock whereas $\mc{M}_2$ is more general in suggesting changing dynamics.
+For example, $\mc{M}_0$ would imply a persistent shock whereas $\mc{M}$ is more general in suggesting changing dynamics.
 Thus, even if  this theoretical statement  may be correct, it makes practical sense only when model is identified well.
-This comment corresponds to the possibility that $\mc{M}_1$ may ``misunderstand'' the wrong signal of changing dynamics that are instead captured by $\mc{M}_2$.
+This comment corresponds to the possibility that $\mc{M}_0$ may ``misunderstand'' the wrong signal of changing dynamics that are instead captured by $\mc{M}$.
 
@@
 
-In Table 2, using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, because $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)>0.5$,  we conclude that  $\mc{M}_2$ is preferred.
+In Table 2, using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, because $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)>0.5$,  we conclude that  $\mc{M}$ is preferred.
 Thus, we turn our interest to that model.
@@
      \hline 
-     $\mc{M}_1$  & \multirow{2}{*}{0.722}& 0  & 1 & 1 (No) &1 (No)  \\      
-      $\mc{M}_2$ ($q_1=q_2=1$)  & & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     $\mc{M}_0$  & \multirow{2}{*}{0.722}& 0  & 1 & 1 (No) &1 (No)  \\      
+      $\mc{M}$ ($q_1=q_2=1$)  & & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
   \end{tabular}
@@
 Talk about post-shock forecasting as parameterizing exogeniety and using hindsight in the donor pool to explicitly estimate exogeneity apriori.
+This framing has its limits, we are not able to perform post-shock forecasts when we are temporarily removed from the known shock time.
+For example, in the Conoco Philips analysis it is hard to imagine a successful post-shock forecast being made in the days prior to the weekend preceding Monday, March 9th 2020 as the OPEC-Russia oil supply increases and Covid-19 fears had not yet taken shape.
+
+The post-shock forecasting methodology presented here and in \cite{lin2021minimizing} is heavily dependent on the construction of a suitable donor pool which will exhibit a degree of subjectivity.
+This is a limitation of our approach, but we argue that this limitation is not a deal breaker.
 

### 2022-03-30 prevalence_testing/postshocktest2022draft.tex
revision to the manuscript and some revisions of codes

@@
 \usepackage{pdflscape}
+\usepackage{algorithm2e}
 
@@
 
-\vspace*{0.5cm}\noindent\textcolor{red}{Jilei, explain how the h-ahead forecasts are computed here}
+\textcolor{red}{Next, we define the $h$-step forecast for $\mc{M}$, which plays an essential role in the framework of \citet{quaedvlieg2021multi}.
+Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^h$.
+Let the OLS estimate for
+\begin{align*}
+	\{(\eta_i, \alpha_i, \phi_{i,j_1}, \bs{\theta}_{i,j_2}, \tilde{\phi}_{i,j_1}, \tilde{\bs{\theta}}_{i,j_2}) \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}
+\end{align*}
+ be 
+ \begin{align*}
+ 	\{(\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_{i,j_1}, \hat{\bs{\theta}}_{i,j_2}, \hat{\tilde{\phi}}_{i,j_1}, \hat{\tilde{\bs{\theta}}}_{i,j_2}) \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}.
+ \end{align*}
+Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^h$ is defined as
+ \begin{align*}
+ 	\hat{y}_{i,t}^h &= \left(\hat{\eta}_i + \sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
+  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\tilde{\bs{\theta}}}_{i,j+1},
+ \end{align*}
+ where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$.
+This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature.}
 
@@
 
-We now motivate a voting method based on the p-values computed in the donor pool.
-\textcolor{red}{Jilei, you need to explain what the voting method is, possibly in algorithmic format.}
+We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool and \textcolor{red}{the algorithms are described in Algorithm \ref{voting}.
+There are a couple of details that are worth noting.
+First, for $t = T_i+1$ and $i \geq 2$, we used to the methodology of \cite{lin2021minimizing} to compute point forecast for $\hat{y}_{i,t}^{2,h}$.
+Note that for $t = T_i+1$, using ordinary least square conditional forecast yields $\hat{y}_{i,t}^{2,h}=  \hat{y}_{i,t}^{1,h}$ as those two forecast just differ by shock information, which is not available at this time point.
+We make such adjustment for the reason that  the method of  \cite{lin2021minimizing} is generally more likely to perform better than the ordinary forecast under certain conditions.
+Second, notice that we evaluate forecast comparison for $t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$ with time length smaller than $T_i$.
+It is because the framework of \cite{quaedvlieg2021multi} needs training sample, which implicitly requires users to feed the algorithm with moderately large dataset for a more credible analysis.
+}
+
+\vspace{.5cm}
+\begin{algorithm}[H]
+\SetAlgoLined \label{voting}
+
+\SetKwInOut{Input}{Input}
+\Input{$B, \ell $ --  bootstrap sample size, the  block size,   \\ 
+$\gamma$ -- bandwidth parameter in heteroskedasticity and autocorrelation  consistent covariance \\ 
+	\quad \quad matrix  estimation.\\ 
+$\alpha$ -- significance level\\$\{(y_{i,t}, \mbf{x}_{i,t})\colon i = 2,\ldots, n+1, t = 0, \ldots, T_i\}$ -- the data\\ $\{T_i^* \colon i = 1, \ldots, n+1\}$ -- the time point just before the shock\\
+$\{K_i \colon i = 2, \ldots, n+1\}$  -- training sample size for $h$-step forecast for different time series \\
+$q_1, q_2$ -- user-specified parameters in $\mc{M}$ \\
+$H$ -- maximum horizon 
+}
+
+\KwResult{(1) synthetic weights $\mbf{W}^*$, (2)  $\hat{p}_1$, and (3) decision based on voting and weighted voting}
+
+  \For{$i = 2:(n+1)$}{
+  	\If{$i > 2$}{
+  	Compute $\hat{\alpha}_{\rm wadj}$ based on \cite{lin2021minimizing} with $\{T_j^* \colon j = 2, \ldots, i-1\}$ and $\{(y_{j,t}, \mbf{x}_{j,t})\colon j= 2,\ldots, i-1, t = 0, \ldots, T_j\}$
+  	}
+
+ 	\For{$h = 1, \ldots, H$}{
+ 		\For{$t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$}{
+ 		Compute $\hat{y}_{i,t}^{1, h}$ and $\hat{y}_{i,t}^{2, h}$ based on OLS estimation of $\mc{M}$ with $\{T_i^* \colon i = 1, \ldots, n+1\}$ and   training data $\{(y_{i,t}, \mbf{x}_{i,t})\colon  t =  t-h- K_i +1, \ldots, t-h\}$, where we further need the set of lagged response $\{y_{i,t}\colon t = t-h-K_i- \max\{q_1, q_2-1\}+1, t-h-K_i\}$.
+
+ 		\If{$t-h = T_i^*$, $i\geq 3$, and $h =1$}{
+ 		$\hat{y}_{i,t}^{2, h}= \hat{y}_{i,t}^{2, h} + \hat{\alpha}_{\rm wadj}$
+ 		}
+ 		Compute the squared error loss $l_{t,h}^1$ based on $y_{i, t}$
+ 		 and $\hat{y}_{i,t}^{1, h}$\\
+ 		 Compute the squared error loss $l_{t,h}^2$ based on $y_{i, t}$
+ 		 and $\hat{y}_{i,t}^{2, h}$
+ 		}
+ 	}
+ 	Construct the loss differential matrix with element $l_{t,h}^2-l_{t,h}^1$ at $t$th row and $h$th column \\
+ 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix $\{l_{t,h}^2-l_{t,h}^1\}_{t,h}$ with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i$\\
+  }
+
+ 	Compute synthetic weights $\mbf{W}^*= (w_2^*, \ldots, w_{n+1}^*)$ based on $\{\mbf{x}_{i, T_i^*+1}\colon i = 1, \ldots, n+1\}$ \\
+ 	Compute the vote $V= I\Big\{n^{-1}\sum_{i=2}^{n+1}I(\hat{p}_i \leq  \alpha) \geq 0.5\Big\}$ \\
+ 	Compute the weighted vote $V^*= I\Big\{ \sum_{i=2}^{n+1}w_i^*I(\hat{p}_i \leq  \alpha) \geq 0.5\Big\}$
+
+ \caption{Algorithm for computing $\hat{p}_1$, weighted voting, and $\mbf{W}^*$}\label{Bu}
+\end{algorithm}
 
@@
      7 & $\mc{M}$  &  & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     15 & $\mc{M}_0$ & \multirow{2}{*}{$0.817$}  & 1   & $0.82$ & 0 (Yes) &1 (No)    \\
+     15 & $\mc{M}_0$ & \multirow{2}{*}{$0.817$}  & 1   & $0.817$ & 0 (Yes) &1 (No)    \\
      15 &  $\mc{M}$ & & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
-     30 &  $\mc{M}_0$ & \multirow{2}{*}{$1$}  & 1   & $0.82$ & 0 (Yes) &1 (No)   \\
+     30 &  $\mc{M}_0$ & \multirow{2}{*}{$1$}  & 1   & $0.817$ & 0 (Yes) &1 (No)   \\
      30 &  $\mc{M}$ &  & 1  & 0 &0 (Yes) & 0 (Yes)  
@@
 \begin{center}
-  \begin{tabular}{ccccccccr}
-      Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$  & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
+  \begin{tabular}{cccccccccr}
+   $L$  &  Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$  & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
      \hline 
-     $\mc{M}_0$  & \multirow{2}{*}{0.722}& 0  & 1 & 1 (No) &1 (No)  \\      
-      $\mc{M}$ ($q_1=q_2=1$)  & & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     \multirow{2}{*}{ $3$} &  $\mc{M}_0$  & \multirow{2}{*}{ 0}& 1  & 0 & 0 (Yes) &0 (Yes)  \\      
+      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.070 & $0.179$   & 0 (Yes) &1 (No)   \\[.2cm]
+     \multirow{2}{*}{ $6$} &  $\mc{M}_0$  & \multirow{2}{*}{ 0}& 1  & 0 & 0 (Yes) &0 (Yes)  \\      
+      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.265 & $0.498$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+  \multirow{2}{*}{ $12$} &  $\mc{M}_0$  & \multirow{2}{*}{0.722}& 0  & 1 & 1 (No) &1 (No)  \\      
+      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+       \multirow{2}{*}{ $18$} &  $\mc{M}_0$  & \multirow{2}{*}{0}& 0.670  & 0.330 & 0 (Yes) & 0 (Yes)  \\      
+      & $\mc{M}$ ($q_1=q_2=1$)  & & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
   \end{tabular}

### 2022-03-30 prevalence_testing/numerical_studies/COP.R

@@ -253,8 +253,8 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw,
         }
         
         # losses
-        m1.L.i[t, h] <- sel(y = Y[[i]][-1][t + Ki + H], yhat = yhat.adj[h + q1])
-        m2.L.i[t, h] <- sel(y = Y[[i]][-1][t + Ki + H], yhat = yhat.unadj[h + q1])
+        m1.L.i[t, h] <- sel(y = Y[[i]][-(1:q1)][t + Ki + H], yhat = yhat.adj[h + q1])
+        m2.L.i[t, h] <- sel(y = Y[[i]][-(1:q1)][t + Ki + H], yhat = yhat.unadj[h + q1])
       }
     }
     # loss differential
@@ -452,8 +452,8 @@ ps.indic.W.dynamic <- function(Tstar, Y, X, K, H, Ts,
         
         
         # losses
-        m1.L.i[t, h] <- sel(y = Y[[i]][-1][t + Ki + H], yhat = yhat.adj[h + q1])
-        m2.L.i[t, h] <- sel(y = Y[[i]][-1][t + Ki + H], yhat = yhat.unadj[h + q1])
+        m1.L.i[t, h] <- sel(y = Y[[i]][-(1:max(q1, q2 - 1))][t + Ki + H], yhat = yhat.adj[h + q1])
+        m2.L.i[t, h] <- sel(y = Y[[i]][-(1:max(q1, q2 - 1))][t + Ki + H], yhat = yhat.unadj[h + q1])
       }
     }
     # loss differential
@@ -566,7 +566,7 @@ H <- 10
 # training sample size
 K <- 30
 # number of days after shock date
-L <- 30
+L <- 7
 
 #### Monday, March 17th, 2008
 

### 2022-03-30 prevalence_testing/numerical_studies/emsda.R

@@ -187,8 +187,8 @@ ols.est.alphahat <- function(Tstar, Y, X) {
 }
 
 # functions that return alpha.hat and synthetic weights
-ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .05, 
-                                 sc.x = NA,
+ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, 
+                                 sig.levl = .05, q1, 
                                  retro = TRUE, selfW = NA, scale = FALSE) {
   
   n <- length(Y) - 1
@@ -210,94 +210,52 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, sig.levl = .
       alpha.wadj <- sym$est[2]
     }
     
-    m1.L.i <- matrix(NA, nrow = Ti - Ki - H - 1, ncol = H)
-    m2.L.i <- matrix(NA, nrow = Ti - Ki - H - 1, ncol = H)
+    m1.L.i <- matrix(NA, nrow = Ti - Ki - H - q1, ncol = H)
+    m2.L.i <- matrix(NA, nrow = Ti - Ki - H - q1, ncol = H)
     
     # compute losses
     for (h in 1:H) {
-      for (t in 1:(Ti - Ki - H - 1)) {
+      for (t in 1:(Ti - Ki - H - q1)) {
+        TL <- length(Y[[i]])
+        yi <- Y[[i]][-(1:q1)][(t + H - h + 1):(t + Ki + H - h)]
+        xi <- X[[i]][-(1:q1), ][(t + H - h + 1):(t + Ki + H - h),]
         
-        yi <- Y[[i]][-1][(t + H - h + 1):(t + Ki + H - h)]
-        xi <- X[[i]][-1, ][(t + H - h + 1):(t + Ki + H - h),]
-        
-        # lag
-        yilag <- Y[[i]][-(Ti + 1)][(t + H - h + 1):(t + Ki + H - h)]
-        
-        # special case that needs covariates without lags
-        sc <- c()
-        
-        if (length(sc.x) == 1) {
-          sc <- 0
-        } else {
-          if (i %in% sc.x[[1]]) {
-            sc <- 1
-          } else {
-            sc <- 0
-          }
+        # yi lags
+        yilags <- c()
+        for (j in 1:q1) {
[…]

### 2022-04-06 prevalence_testing/postshocktest2022draft.tex
updated unemployment

@@
 
+Arguably the most watched macroeconomic indicator for the US economy is the monthly release of the total nonfarm payrolls, which reflects the gains or losses of persons employed.
+However, its reputation as a lagging indicator of macroeconomic health constrains its usefulness.
+This makes it ripe for forecasting under the method herein.
+To this end, we examine the March 2020 lockdown measures as a shock to the US economy and labor market, enlisting previous macroeconomic shocks to the US economy as donors.
+The donor pool assembled notably contains no cases of lockdowns or even pandemics or epidemics.
+Instead, the common thread running through the time series under study and the donors is the element of a sudden and considerable surprise visited upon the economy from source previously judged to be marginal.
+
 \textcolor{red}{A lot is needed here.
@@
 I would guess that a shorter window may exhibit disagreement between the donor pool and the series under study or may show different decisions being reported.
-}
+However, don't we want to match the time series under study with donors based on only pre-shock features, data, variables, etc?
+It might be good to think of donor selection as a two-stage matching procedure: first, a donor is judged worthy based on some qualitative or quantitative analysis (the latter of which can be simply the correlation of their covariate vectors at $T^{*}$); second, the matches are aggregated using distanced-based weighting.}
 

### 2022-04-06 prevalence_testing/postshocktest2022draft.tex
added sketch of new mathematical argument; removed old mathematical argument; made small spot edits

@@
 
-A p-value corresponding to the hypothesis test \eqref{test} is computed using a moving block bootstrap (MBB). \textcolor{red}{Need more clarity on this process}
+A p-value corresponding to the hypothesis test \eqref{test} is computed using a moving block bootstrap (MBB) of of \cite{kunsch1989jackknife} and \cite{liu1992moving}.
+In the moving block bootstrap (MBB), a pseudo time-series is constructed by resampling blocks of length $\ell$ from the original data.
+
 %We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
-Let $l$ be the block length of the MBB where we assume that $T_i = lK_i$. Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array 
+Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = lK_i$.
+Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
 $$
@@
 \SetKwInOut{Input}{Input}
-\Input{$B, \ell $ --  bootstrap sample size, the  block size,   \\ 
+\Input{$B, \ell $ --  bootstrap sample size, the  block size \textcolor{red}{Where is bootstrapping used in this algorithm?},   \\ 
 $\gamma$ -- bandwidth parameter in heteroskedasticity and autocorrelation  consistent covariance \\ 
@@
  	Construct the loss differential matrix with element $l_{t,h}^2-l_{t,h}^1$ at $t$th row and $h$th column \\
- 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix $\{l_{t,h}^2-l_{t,h}^1\}_{t,h}$ with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i$\\
+ 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix $\{l_{t,h}^2-l_{t,h}^1\}_{t,h}$ \textcolor{red}{please confirm that this is the same notation as before.} with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i$\\
   }
@@
 \newpage
-
-\vspace*{0.5cm} We now demonstrate an idealized theoretical setting for which our post-shock testing methodology involving a distance based weighted average of p-values works well.
+\textbf{Repeating for reference}:
+\begin{align}
+\mc{M} \colon \begin{array}{l}
+  y_{i,t} = \left(\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j}\right)(1 - D_{i,t}) + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
+  \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i +  \sum_{j=1}^{q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
+  \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
+  %\sum_{j=1}^{q_3}\delta_{i,j}'\mbf{x}_{i, T_i^*-j+1}+ \t{\varepsilon}_{i}, 
+\end{array}\label{model-gen2}
+\end{align}
+where $D_{i,t} = I(t \geq T_i^* + 1)$, $I(\cdot)$ is the indicator function, $\x_{i,t} \in \R^{p}$ are fixed with $p \geq 1$. Let 
+$\mathbf{\phi}_i = (\phi_{i,1},\ldots,\phi_{i,q_1})'$, 
+$\mathbf{\theta}_i = (\theta_{i,1},\ldots,\theta_{i,q_2})'$, 
+$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_{1}})'$, 
+$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i, q_{2}})'$, 
+$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,p})'$, 
+and suppose that the regression coefficients in \eqref{model-gen2} have the following hierarchical random effects structure: 
+\begin{equation} \label{random-effects2}
+\begin{split}
+  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = \mu_\eta, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
+  \mathbf{\phi}_{i,j} &\simiid \mc{F}_{\mathbf{\phi}_j} \text{ where } |\phi_{i,j}| < 1, \\
+  \mathbf{\theta}_{i,j} &\simiid \mc{F}_{\mathbf{\theta}_j} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}_j}}(\theta_{i,j}) = \mu_{\mathbf{\theta}_j}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}_j}}(\mathbf{\theta}_{i,j})  = \Sigma^2_{\mathbf{\theta}_j}, \\
+  \mathbf{\delta}_i &\simiid  \mc{F}_{\mathbf{\delta}} \text{ with } \mrm{E}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\mu_{\mathbf{\delta}}, \mrm{Var}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\Sigma_{\mathbf{\delta}}, \\
+\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i,  \\
+\varepsilon_{\alpha, i} &\simiid  \mc{F}_{\varepsilon_\alpha} \text{ with }\mrm{E}_{\mc{F}_{\varepsilon_\alpha}}(\varepsilon_{\alpha, i})=0, \mrm{Var}_{\mc{F}_{\varepsilon_{\alpha}}}(\varepsilon_{\alpha, i})=\sigma^2_{\alpha}, \\
+  \tilde{\mathbf{\phi}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\phi}_j}}(\x_{i,T_i^*+1}) \; \text{where} \; |\tilde{\mathbf{\phi}}_{i,j}| < 1,  \\
+  \tilde{\mathbf{\theta}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\theta}_j}}(\x_{i,T_i^*+1}),  \\  
+ % \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\
+&\eta_i \indep \mathbf{\phi}_{i,j} \indep \mathbf{\theta}_{i,j} \indep 
+\tilde{\mathbf{\phi}}_{i,j} \indep \lambda_{i,j} \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i}, 
+\end{split}
+\end{equation}
+
+We now demonstrate an idealized theoretical setting for which our post-shock testing methodology involving a distance based weighted average of p-values works well.
 The idea is that inferences based on distance based weighted nearly recovers the time series under study when there exists a time series in the donor pool, indexed by $i'$, such that $\x_{1,t} \approx \x_{i',t}$ and the signal strength in our modeling setup \eqref{model-gen} and \eqref{random-effects} is large relative to variation.
+
 We first present some intermediary technical results and definitions.
@@
   \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
-  \sigma^2_{\max} &= \max\left(\sigma^2_{\eta},\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_{\alpha},\sigma^2_{\tilde{\phi}_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right).  
-\end{align*}
-
-\begin{prop} \label{prop:signaltonoise}
-	Let $\bf{y}_{i,t}$, $i = 1,\ldots,n_i$, $t = 1,\ldots, T$ be a collection of independent time series.
-Let each time series $\bf{y}_{i,t}$ be generated by model \eqref{model-gen} with accompanying random effects structure \eqref{random-effects}, where $y_{i,t}$ is a scalar response $\x_{i,t} \in \R^p$ is a fixed vector of covariates.
-Suppose that there is a common shock time $p + 2 < T^* < T - (p+2)$ where $q_1 = q_2 = 1$, $\|\x_{i,t}\| = 1$, each entry of $\x_{i,t}$ is non-negative, $\mu_{\min} > 0$, and $y_{i,0} = 0$.
-Then for every $1 \leq t \leq T$ we have that
-	\begin{equation} \label{signal-to-noise}
-	  \E(y_{i,t}) \geq C\Var(y_{i,t}),	
-	\end{equation}
-	provided that 
-	\begin{equation} \label{condition-1}
-	\begin{split}
-		\mu_\alpha + 3\mu_{\min} &\geq C\left(3\sigma^2_{\max} + 2\lambda_{\max}\right), \\
-		2\mu_{\min} &\geq C\left(2\sigma^2_{\max} + \lambda_{\max}\right).	
-	\end{split}
-	\end{equation}
-\end{prop}
-
-\textbf{Remarks}:
-\begin{enumerate}
-	\item The conditions \eqref{condition-1} govern the signal strength necessary in the expected behavior of the underlying random effects structure relative to variability necessary for the overall signal to noise ratio for the overall time series to be lower bounded by some positive value $C$.
-	\item The conditions of Proposition~\ref{prop:signaltonoise} state that there is an increasing trend in $y_{i,t}$ for all $i$. This can be relaxed, but a fully general argument is cumbersome.
-\end{enumerate}
-
-\begin{proof}
-For $t > T^* + 1$ we have 
-\begin{align*}
-  \E(y_{i,t}) &= \E\left[\E(y_{i,t}|y_{i,t-1})\right] \\ 
-    &= \E\left[\E(\eta_i + \alpha_i + \tilde\phi_i y_{i,t-1} 
-      + \tilde\theta_i'\x_{i,t}|y_{i,t-1})\right] \\
-    &= \E(\eta_i + \mu_\alpha + \delta_i'\x_{i,T^*+1} + \tilde\phi_i y_{i,t-1} + \tilde\theta_i'\x_{i,t}) \\
-    &= \mu_\eta + \mu_\alpha + \mu_\delta'\x_{i,T^*+1} + \mu_{\tilde\theta}'\x_{i,t} + \mu_{\tilde\phi}\E(y_{i,t-1}) \\
-    &\geq (\mu_\alpha + 3\mu_{\min}) + \mu_{\min}\E(y_{i,t-1}) \\
-    &\geq \sum_{j=1}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\E(y_{i,T^*}) \\
-    &= \sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(\E\left[\E(y_{i,T^*}|y_{i,T^*-1})\right]\right) \\   
-    &= \sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(\E(\eta_i + \theta_i'\x_{i,T^*} + \phi_i y_{i,T^*-1}) \right) \\
-    &\geq \sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(2\mu_{\min} + \mu_{\min} \E(y_{i,T^*-1}) \right) \\
-    &\geq \sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(\sum_{j=0}^{T^*-1}\mu_{\min}^j(2\mu_{\min}) \right), 
-\end{align*}
-and 
-\begin{align*}
-  \Var(y_{i,t})	&= \E\left[\Var(y_{i,t}|y_{i,t-1})\right] + \Var\left[\E(y_{i,t}|y_{i,t-1})\right] \\
-  &= \E\left[\Var(\eta_i + \mu_\alpha + \delta_i'\x_{i,T^*+1} + \tilde\theta_i'\x_{i,t} + \tilde\phi_i y_{i,t-1} + \varepsilon_{i,t} + \varepsilon_{\alpha,i}|y_{i,t-1})\right] \\
-  &+ \Var\left[\E(\eta_i + \mu_\alpha + \delta_i'\x_{i,T^*+1} + \tilde\theta_i'\x_{i,t} + \tilde\phi_i y_{i,t-1} + \varepsilon_{i,t} + \varepsilon_{\alpha,i}|y_{i,t-1})\right] \\
-  &\leq 3\sigma^2_{\max} + 2\lambda_{\max} + \Var\left[\E(\tilde\phi_i y_{i,t-1}|y_{i,t-1})\right] \\
-  &= 3\sigma^2_{\max} + 2\lambda_{\max} + \mu_{\tilde\phi}^2\Var(y_{i,t-1}) \\
-  &\leq \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\Var(y_{i,T^*}) \\
-  &= \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\E\left[\Var(y_{i,T^*}|y_{i,T^*-1})\right] + \Var\left[\E(y_{i,T^*}|y_{i,T^*-1})\right]\right) \\
-  &= \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\E\left[\Var(\eta_i + \theta_i'\x_{i,T^*} + \phi_iy_{i,T^*-1} + \varepsilon_{i,T^*}|y_{i,T^*-1})\right] \right.
+  \sigma^2_{\max} &= \max\left(\sigma^2_{\eta},\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_{\alpha},\sigma^2_{\tilde{\phi}_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right),
+\end{align*}
+and let $\sigma^2 = \max(\lambda_{\max}, \sigma^2_{\max})$.
+Now arbitrarily choose $\varepsilon > 0$ and fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$ for all $t$ where $\varepsilon_1$ will be selected later.
+Pick some large $M > 0$.
+Fix $T = T_1 = T_{i'}$ and $T^* = T^*_1 = T^*_{i'}$.
+Define the events
+\begin{align*}
+  E_1 := &\left\{\max\left(|\eta_1 - \eta_{i'}|,|\phi_{1,j}-\phi_{i',j}|,\|\theta_{1,k} - \theta_{i',k}\|,\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \varepsilon_1:\right.
 \\
-  &\qquad+  \left.\Var\left[\E(\eta_i + \theta_i'\x_{i,T^*} + \phi_iy_{i,T^*-1} + \varepsilon_{i,T^*}|y_{i,T^*-1})\right]\right)  \\
-  &\leq \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(2\sigma^2_{\max} + \lambda_{\max} + \mu_{\phi}^2\Var(y_{i,T^*-1}) \right) \\
-  &\leq \sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right).
-\end{align*}
-Combining the above with the condition \eqref{condition-1} yields 
-\begin{align*}
-  \frac{\E(y_{i,t})}{\Var(y_{i,t})} &\geq \frac{\sum_{j=0}^{t - (T^* + 1)} \mu_{\min}^j(\mu_{\alpha} + 3\mu_{\min}) + \mu_{\min}^{t-T^*}\left(\sum_{j=0}^{T^*-1}\mu_{\min}^j(2\mu_{\min}) \right)}{\sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right)} \\
-  &\geq \frac{C\sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + C(\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right)}{\sum_{j=0}^{t - (T^*+1)} (\mu_{\tilde\phi}^2)^j\left(3\sigma^2_{\max} + 2\lambda_{\max}\right) + (\mu_{\tilde\phi}^2)^{t - T^*}\left(\sum_{j=0}^{T^*-1}\left(\mu_{\phi}^2\right)^{j}(2\sigma^2_{\max} + \lambda_{\max})\right)} \\
-  &= C,
-\end{align*}
-for all $i$ and $t$. A similar argument holds when $t \leq T^* + 1$.
-\end{proof}
-
-\begin{lem}[Technical Lemma 1] \label{lem:absdiff}
-Let $a_j, b_j \in \R$, $j = 1,2$ be such that $0 < a_1,a_2 < 1$, $b_1,b_2 > 0$. Let $c_1 = \max(a_1,a_2)$, $c_2 = \min(a_1,a_2)$, $d_1 = \max(b_1,b_2)$, $d_2 = \min(b_1,b_2)$. Then, 
-$$
-  |a_1b_1 - a_2b_2| \leq |a_1 - a_2|d_1 + |b_1 - b_2|c_2.
-$$
-\end{lem}
-
-\begin{proof}
-Observe that 
-$$
-  |a_1b_1 - a_2b_2| \leq c_1d_1 - c_2d_2 = (c_1 - c_2)d_1 + (d_1 - d_2)c_2. 
-$$
-The conclusion follows by noting that $c_1 - c_2 = |a_1 - a_2|$ and $d_1 - d_2 = |b_1 - b_2|$.
-\end{proof}
-
-\begin{prop}
-	Let $\bf{y}_{i,t}$, $i = 1,\ldots,n_i$, $t = 1,\ldots, T$ be a collection of independent time series.
-Let each time series $\bf{y}_{i,t}$ be generated by model \eqref{model-gen} with accompanying random effects structure \eqref{random-effects}, where $y_{i,t}$ is a scalar response $\x_{i,t} \in \R^p$ is a fixed vector of covariates.
-Suppose that there is a common shock time $p + 2 < T^* < T - (p+2)$ where $q_1 = q_2 = 1$, $\|\x_{i,t}\| = 1$, each entry of $\x_{i,t}$ is non-negative, $\mu_{\min} > 0$, and $y_{i,0} = 0$.
-Let $i' \geq 2$ be an index.
-Then, for any $\epsilon > 0$ we can choose an $\gamma > 0$ such that
-	$$
-	  \left\vert\E(y_{i,t} - y_{i',t})\right\vert \leq \epsilon, \qquad |\Var(y_{1,t}) - \Var(y_{i',t})| < \varepsilon,
-	$$
-	provided that 
-	\begin{align*}
-  |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| &< \gamma, \\
-%  |\mu_{\tilde\theta_1}'\x_{1,T^*+1} - \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1}| &< \gamma, \\
-  \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}\right\vert &< \gamma, \qquad \text{for all} \; t, \\
-  |\mu_{\tilde\phi_1}^j - \mu_{\tilde\phi_{i'}}^j| &< \gamma, \qquad \text{for all} \; j, \\
-  |\x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1}| &< \gamma, \\
-  |\x_{1,t}'\Sigma_{\tilde\theta_{1}}\x_{1,t} - \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t}| &< \gamma, \qquad \text{for all} \; t.
-	\end{align*}
-\end{prop}
-
-\begin{proof}
-A similar recursion to that seen in the proof of Proposition~\ref{prop:signaltonoise} yields
-\begin{align*}
-	&|\E(y_{1,t} - y_{i',t})| =  \left\vert \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{1}}^j(\mu_\delta'\x_{1,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{1}}^j(\mu_{\tilde\theta_{1}}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',t-j})\right]\right.
-\\
-		&\qquad\qquad\left.
-+ \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',t-j})\right)\mu_{\phi}^j\right]\right\vert \\
-	&\qquad\leq |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| 
-	  + \sum_{j=1}^{t - (T^*+1)}\left\vert\mu_{\tilde\phi_{1}}^j(\mu_\delta'\x_{1,T^*+1}) - \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right\vert \\ 
-	&\qquad\qquad+ |\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}| + \sum_{j=1}^{t - (T^*+1)}\left\vert \mu_{\tilde\phi_{1}}^j(\mu_{\tilde\theta_{1}}'\x_{1,t-j}) - \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',t-j})\right\vert \\
-	&\qquad\qquad + \mu_\eta\sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j \\
-	&\qquad\leq |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| + |\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}| \\
-	&\qquad\qquad + \sum_{j=1}^{t - (T^*+1)}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,T^*+1},\mu_\delta'\x_{i',T^*+1}) + \left\vert\mu_\delta'\x_{1,T^*+1} -\mu_\delta'\x_{i',T^*+1}\right\vert\mu_{\tilde\phi_{1}}^j\right] \\
-	&\qquad\qquad + \sum_{j=1}^{t - (T^*+1)}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,t-j},\mu_\delta'\x_{i',t-j}) + \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t-j} - \mu_{\tilde\theta_{i'}}'\x_{i',t-j}\right\vert\mu_{\tilde\phi_{1}}^j\right] \\
-	&\qquad\qquad + \mu_\eta\sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{T^*-1}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j,
-\end{align*}
-where the second inequality follows from applications of Lemma~\ref{lem:absdiff}. Continuing from the second inequality, the conditions of this proposition imply that
-\begin{align*}
-  &|\E(y_{1,t} - y_{i',t})|	\\
-  &\qquad\leq 2\gamma + \sum_{j=1}^{\infty}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,T^*+1},\mu_\delta'\x_{i',T^*+1}) + \gamma\mu_{\tilde\phi_{1}}^j\right] \\
-  &\qquad\qquad + \sum_{j=1}^{\infty}\left[\vert\mu_{\tilde\phi_{1}}^j - \mu_{\tilde\phi_{i'}}^j\vert\max(\mu_\delta'\x_{1,t-j},\mu_\delta'\x_{i',t-j}) + \gamma\mu_{\tilde\phi_{1}}^j\right] \\
-  &\qquad\qquad + \mu_\eta\sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j  \\
-  &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} \\
-  &\qquad\qquad + \mu_\eta\sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*} - \mu_{\tilde\phi_{i'}}^{t - T^*}\right\vert\mu_{\phi}^j + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j \\
-  &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} + \gamma\frac{\mu_{\eta}}{1 - \mu_{\phi}} + \sum_{j=0}^{\infty}\left\vert \mu_{\tilde\phi_{1}}^{t - T^*}(\mu_{\theta}'\x_{1,T^*-j}) - \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i',T^*-j}) \right\vert\mu_{\phi}^j \\
-  &\qquad\leq 2\gamma + 2\gamma\frac{\max(\mu_\delta)}{(1 - \mu_{\tilde\phi_{1}})(1 - \mu_{\tilde\phi_{i'}})} + \gamma\frac{\mu_{\eta}}{1 - \mu_{\phi}} + \gamma\frac{\max(\mu_\theta) + 1}{1 - \mu_\phi},
-\end{align*}  
-where the last inequality follows from Lemma~\ref{lem:absdiff}. We can choose $\gamma$ small enough so that $|\E(y_{1,t} - y_{i',t})| < \varepsilon$. A similar recursion for the variance yields 
-\begin{align*}
- &\left\vert \Var(y_{1,t}) - \Var(y_{i',t})\right\vert 
-   = \left\vert \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{1,t}'\Sigma_{\tilde\theta_i}\x_{1,t} -   \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t} \right.
-\\
-   &\qquad\left. + \mu_{\tilde\phi_1}^2\Var(y_{1,t-1}) - \mu_{\tilde\phi_{i'}}^2\Var(y_{i',t-1}) \right\vert \\
-   &\leq \left\vert \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{1,t}'\Sigma_{\tilde\theta_i}\x_{1,t} -   \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t}\right\vert \\
-   &\qquad + \left\vert\mu_{\tilde\phi_1}^2\Var(y_{1,t-1}) - \mu_{\tilde\phi_{i'}}^2\Var(y_{i',t-1})\right\vert \\
-   &= \left\vert \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{1,t}'\Sigma_{\tilde\theta_1}\x_{1,t} -   \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t}\right\vert \\
-   &\qquad + \left\vert \mu_{\tilde\phi_1}^2\left(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2 + \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} + \x_{1,t-1}'\Sigma_{\tilde\theta_1}\x_{1,t-1} + \mu_{\tilde\phi_1}^2\Var(y_{1,t-2})\right) \right.\\
-   &\qquad\qquad\left.- \mu_{\tilde\phi_{i'}}^2\left(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2 + \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{i',t-1}'\Sigma_{\tilde\theta_{i'}}\x_{i',t-1} + \mu_{\tilde\phi_{i'}}^2\Var(y_{i',t-2})\right) \right\vert \\
-   &\leq \left\vert \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1}\right\vert + \left\vert\x_{1,t}'\Sigma_{\tilde\theta_1}\x_{1,t} -   \x_{i',t}'\Sigma_{\tilde\theta_{i'}}\x_{i',t}\right\vert \\
-   &\qquad+ \left\vert \mu_{\tilde\phi_1}^2\left(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2 + \x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} + \x_{1,t-1}'\Sigma_{\tilde\theta_1}\x_{1,t-1}\right) \right.\\
-   &\qquad\qquad\left.- \mu_{\tilde\phi_{i'}}^2\left(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2 + \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1} + \x_{i',t-1}'\Sigma_{\tilde\theta_{i'}}\x_{i',t-1}\right) \right\vert \\
-   &\qquad + \left\vert \mu_{\tilde\phi_1}^4\Var(y_{1,t-2}) - \mu_{\tilde\phi_{i'}}^4\Var(y_{i',t-2}) \right\vert \\
-   &\leq \sum_{j=0}^{t - (T^* + 1)}\left[ \left\vert \mu_{\tilde\phi_1}^{2j}\x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \mu_{\tilde\phi_{i'}}^{2j}\x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1}\right\vert \right.
-\\
-   &\qquad\left.
-+ \left\vert \mu_{\tilde\phi_1}^{2j}\x_{1,t-j}'\Sigma_{\tilde\theta_1}\x_{1,t-j} - \mu_{\tilde\phi_{i'}}^{2j}\x_{i',t-j}'\Sigma_{\tilde\theta_{i'}}\x_{i',t-j} \right\vert + \left\vert\mu_{\tilde\phi_1}^{2j} - \mu_{\tilde\phi_{i'}}^{2j}\right\vert(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2)\right] \\
-   &\qquad + \left\vert \mu_{\tilde\phi_1}^{2(t - T^*)}\Var(y_{1,t - T^*}) - \mu_{\tilde\phi_{i'}}^{2(t - T^*)}\Var(y_{i',t - T^*}) \right\vert \\
-   &\leq \sum_{j=0}^{t - (T^* + 1)}\left[ \left\vert \mu_{\tilde\phi_1}^{2j} - \mu_{\tilde\phi_{i'}}^{2j}\right\vert \lambda_{\text{max}} +  \left\vert\x_{1,T^*+1}'\Sigma_\delta\x_{1,T^*+1} - \x_{i',T^*+1}'\Sigma_\delta\x_{i',T^*+1}\right\vert\mu_{\tilde\phi_1}^{2j} \right.
-\\
-   &\qquad\left.
-+ \left\vert \mu_{\tilde\phi_1}^{2j} - \mu_{\tilde\phi_{i'}}^{2j}\right\vert \lambda_{\text{max}} +  \left\vert\x_{1,t-j}'\Sigma_{\tilde\theta_1}\x_{1,t-j} - \x_{i',t-j}'\Sigma_{\tilde\theta_{i'}}\x_{i',t-j}\right\vert\mu_{\tilde\phi_1}^{2j} + \left\vert\mu_{\tilde\phi_1}^{2j} - \mu_{\tilde\phi_{i'}}^{2j}\right\vert(\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2)\right] \\
-   &\qquad + \left\vert \mu_{\tilde\phi_1}^{2(t - T^*)}\sum_{j=0}^{T^*-1}\left(\sigma^2_\eta + \sigma^2 + \x_{1,T^*-j}'\Sigma_\theta\x_{1,T^*-j}\right)\mu_{\phi}^{2j} \right. \\ 
-   &\qquad\qquad\left. - \mu_{\tilde\phi_{i'}}^{2(t - T^*)}\sum_{j=0}^{T^*-1}\left(\sigma^2_\eta + \sigma^2 + \x_{i',T^*-j}'\Sigma_\theta\x_{i',T^*-j}\right)\mu_{\phi}^{2j} \right\vert \\
-   &\leq 2\gamma\frac{\lambda_{\max}}{(1 - \mu_{\tilde\phi_1}^{2})(1 - \mu_{\tilde\phi_{i'}}^{2})} + 2\gamma\frac{1}{1 - \mu_{\tilde\phi_1}^2} + \gamma\frac{\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2}{(1 - \mu_{\tilde\phi_1}^{2})(1 - \mu_{\tilde\phi_{i'}}^{2})} \\
-   &\qquad+ (\sigma^2_\eta + \sigma^2)\left\vert \mu_{\tilde\phi_1}^{2(t - T^*)} - \mu_{\tilde\phi_{i'}}^{2(t - T^*)} \right\vert\sum_{j=0}^{T^*-1}\mu_{\phi}^{2j} \\
-   &\qquad+ \sum_{j=0}^{2(t - T^*)}\left\vert \mu_{\tilde\phi_1}^{2(t - T^*)}\x_{1,T^*-j}'\Sigma_\theta\x_{1,T^*-j} - \mu_{\tilde\phi_{i'}}^{2(t - T^*)}\x_{i',T^*-j}'\Sigma_\theta\x_{i',T^*-j} \right\vert \mu_{\phi}^{2j} \\
-   &\leq 2\gamma\frac{\lambda_{\max}}{(1 - \mu_{\tilde\phi_1}^{2})(1 - \mu_{\tilde\phi_{i'}}^{2})} + 2\gamma\frac{1}{1 - \mu_{\tilde\phi_1}^2} + \gamma\frac{\sigma^2_\eta + \sigma^2_{\alpha}+ \sigma^2}{(1 - \mu_{\tilde\phi_1}^{2})(1 - \mu_{\tilde\phi_{i'}}^{2})} \\
-   &\qquad + \gamma\frac{\sigma^2_\eta + \sigma^2}{1 - \mu_\phi^2} + \gamma\frac{\lambda_{\max}}{1 - \mu_\phi^2} + \gamma\frac{1}{1 - \mu_\phi^2}
-   \end{align*}
-We can choose $\gamma$ small enough so that $|\Var(y_{1,t}) - \Var(y_{i',t})| < \varepsilon$.
-\end{proof}
-
-\begin{lem}[Technical Lemma 2] \label{lem:diffsig2noise}
-Let $a_j, b_j \in \R$, $j = 1,2$. Suppose that $b_j > b > 0$ for $j = 1,2$. Then for any $\varepsilon > 0$ we have 
-$$
-  \left\vert\frac{a_1}{b_1} - \frac{a_2}{b_2}\right\vert \leq \varepsilon,
-$$
-provided that $|a_1-a_2|$,$|b_1-b_2| < \delta$ for some chosen $\delta > 0$.
-\end{lem}
-
-\begin{proof}
-\begin{align*}
-  \left\vert\frac{a_1}{b_1} - \frac{a_2}{b_2}\right\vert 
-    &= \left\vert\frac{a_1b_2 - a_2b_1}{b_1b_2}\right\vert 
-    = \left\vert\frac{(a_1 - a_2 + a_2)(b_2 - b_1 + b_1) - a_2b_1}{b_1b_2}\right\vert \\
-    &= \left\vert \frac{a_1(b_2 - b_1) + a_2b_1 + (a_1 - a_2)b_1 - a_2b_1}{b_1b_2} \right\vert \leq \frac{2\delta}{b^2} \\
-    &\leq \frac{|a_1|\delta + |b_1|\delta}{b^2} \leq \varepsilon, 
-\end{align*}
-where $\delta \leq \varepsilon b^2/(|a_1| + |b_1|)$.
-\end{proof}
-
-\noindent\textbf{This needs some work (ignore for now)} Now consider a case where there exists a $2 \leq i' < n + 1$ where $\x_{1,t} = \x_{i',t}$.
-Now suppose for simplicity that $T^*_{j'} = T^*_1$ and that $T_{i'} = T_1$ where $T_1 > T^*_1 + q_1 + q_2 + 2$.
-This assumes that we have data for the first time series beyond the shock point.
-We will show that when there is a covariate clone of the time series under study, then estimation in this series will approximate estimation in the time series under study provided that the underlying variability is very small relative to the signal.
-To see this, consider $t > T^*_1$, where
-\begin{align*}
-y_{1,t} &= \eta_1 + \mu_\alpha + \delta_1'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} + \sum_{j=0}^{q_2-1}(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{1} + \varepsilon_{1,t}, \\
-y_{i',t} &= \eta_{i'} + \mu_\alpha + \delta_{i'}'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} + \sum_{j=0}^{q_2-1}(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{i'} + \varepsilon_{i',t}, \\
-\hat y_{1,t} &= \hat \eta_1 + \hat{\alpha}_1(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat y_{1,t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}, \\
-\hat y_{i',t} &= \hat\eta_{i'} + \hat{\alpha}_{i'}(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat y_{i',t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j},
-\end{align*}
-where $\alpha_j(\x) = \mu_\alpha + \delta_j'\x$, and we have 
-\begin{align*}
-  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\right] \\
-  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} - (\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{1,t} \Bigg\vert \\
-  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\right] \\
-  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} - (\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{i',t} \Bigg\vert.
-\end{align*}
-\textbf{Needs finishing, but the argument is simple: estimation uncertainty declines as error variance decreases.
-And differences in the random effects decrease as variability decreases.} \vspace*{0.5cm}
-
-%\begin{lem}[Technical Lemma 2] \label{lem1}
-%	Let $a_j, b_j \in \R$, $j = 1,2$, and $C > 0$ be such that $C \leq a_j/b_j \leq 2C$, $j = 1,2$. Further suppose that 
-%	$$
-%	  \frac{|a_1 - a_2|}{a_1 + a_2} < \frac{\varepsilon}{2C},
-%	$$
-%	for some $\varepsilon > 0$. Then 
-%	$$
-%	  \frac{|a_1 - a_2|}{b_1 + b_2} < \varepsilon.
-%	$$
-%\end{lem}
-
-%\begin{proof}
-%Observe that 
-%$$
-%  |a_1 - a_2| < \frac{\varepsilon(a_1 + a_2)}{2C} 
-%	  = \frac{\varepsilon(b_1(a_1/b_1) + b_2(a_2/b_2))}{2C} 
-%	  \leq \frac{\varepsilon(2b_1C + 2b_2C)}{2C} 
-%	  = \varepsilon(b_1 + b_2).
-%$$
-%The conclusion immediately follows from the above.
-%\end{proof}
-
-%\begin{prop} \label{prop:signaltonoisediff}
-%	Suppose the conditions of Proposition~\ref{prop:signaltonoise} where $C$ is chosen so that 
-%	\begin{equation} \label{signal-to-noise2}
-%	  C \leq \frac{\E(y_{i,t})}{\Var(y_{i,t})} \leq 2C,
-%	\end{equation}
-%	for all $i$ and $1 \leq t \leq T$. Let $2 < i' < n + 1$ be the index of a time series in the donor pool for which CONDITIONS then for some $\varepsilon > 0$ we have 
-%	$$
-%	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\Var(y_{i,t} - y_{i',t})} < \varepsilon
-%	$$
-%\end{prop}
-
-%\begin{proof}
-%	First suppose that we have 
-%	\begin{equation} \label{prop:cond}
-%	  \frac{\left|\E(y_{i,t} - y_{i',t})\right|}{\E(y_{i,t} + y_{i',t})} \leq \frac{\varepsilon}{2C}.		
-%	\end{equation}
-%	Then Lemma~\ref{lem:absdiff} combined with the assumed conditions imply the conclusion of this proposition. We now verify that \eqref{prop:cond} holds.
-%Suppose that:
+  &\qquad j = 1,\ldots,q_1, k = 1,\ldots,q_2, t = 1,\ldots,T \left.\right\}, \\
+  E_2 := &\{\|(\bm{\eta}',\bm{\phi}',\bm{\theta}',\bm{\delta}',\tilde{\bm{\phi}}',\tilde{\bm{\theta}}')\|_\infty < M\},
+\end{align*}
+where $\tilde\varepsilon_t = \varepsilon_{1,t} - \varepsilon_{i',t} + D_{i,t}(\varepsilon_{\alpha,1} - \varepsilon_{\alpha,i'})$ and $\bm{\eta},\bm{\phi},\bm{\theta},\bm{\delta},\tilde{\bm{\phi}}$, and $\tilde{\bm{\theta}}$ are vectors containing the random effects in \eqref{random-effects} for indices $1$ and $i'$, and we take $\|\bm{a}\|_\infty = \max_j(|a_j|)$ .
+We will also suppose that $\|\x_{j,t}\|_\infty < M$ for $j \in \{1,i'\}$ and all $t = 1,\ldots,T$.
+Note that both $\Prob(E_1^C) \to 0$ and $\Prob(E_2^C) \to 0$  as $\sigma^2 \to 0$ with $T$ and $n$ fixed.
+For simplicity we will set $q_1 = q_2 = 1$.
+
+Conditional on $E = E_1 \cup E_2$, we first consider the recursion of $|y_{1,t} - y_{i',t}|$ for $t > T^*$,
+\begin{align*}
+	&|y_{1,t} - y_{i',t}| 
+		= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1})
+		+ (\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}y_{i',t-1}) 
+		+ (\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t}) + \tilde\varepsilon_t| \\
+	&\qquad \leq |\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}|
+		+ |\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}y_{i',t-1}| 
+		+ |\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t})| 
+		+ \varepsilon_1 \\
+	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - y_{i',t-1}| \\
+	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| \\ 
+	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - y_{i',t-2}|\right\} \\
+	&\qquad= \varepsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|y_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - y_{i',t-2}| \\
+	&\qquad \leq \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|y_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - y_{i',T^*}|.
+\end{align*}
+%Similarly, on $E$, we have 
 %\begin{align*}
-%  |\mu_\delta'\x_{1,T^*+1} - \mu_\delta'\x_{i',T^*+1}| &< \gamma \\
-%  |\mu_{\tilde\theta_1}'\x_{1,T^*+1} - \mu_{\tilde\theta_{i'}}'\x_{i',T^*+1}| &< \gamma \\
-%  \left\vert\mu_{\tilde\theta_{1}}'\x_{1,t} - \mu_{\tilde\theta_{i'}}'\x_{i',t}\right\vert &< \gamma, \qquad \text{for all} \; t \\
-%  |\mu_{\tilde\phi_1}^j - \mu_{\tilde\phi_{i'}}^j| &< \gamma, \qquad \text{for all} \; j \\
-%  \mu_\delta'\x_{1,T^*+1} + \mu_\delta'\x_{i',T^*+1} &> D
+%	|y_{1,T^*} - y_{i',T^*}| &= |()|
 %\end{align*}
-%Similarly, 
-%\begin{align*}
-%	&\E(y_{i,t} + y_{i',t}) = \sum_{j=0}^{t - (T^*+1)}\left[\left(\mu_{\tilde\phi_{i}}^j(\mu_\delta'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_\delta'\x_{i',T^*+1})\right) + \mu_{\tilde\phi_{i}}^j(\mu_{\tilde\theta_{i}}'\x_{i,T^*+1}) + \mu_{\tilde\phi_{i'}}^j(\mu_{\tilde\theta_{i'}}'\x_{i',T^*+1})\right] \\
-%		&\qquad + \sum_{j=0}^{T^* - 1}\left[\mu_\eta(\mu_{\tilde\phi_{i}}^{t - T^*} + \mu_{\tilde\phi_{i'}}^{t - T^*})\mu_{\phi}^j + \left(\mu_{\tilde\phi_{i}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j}) + \mu_{\tilde\phi_{i'}}^{t - T^*}(\mu_{\theta}'\x_{i,t-j})\right)\mu_{\phi}^j\right].
-%\end{align*}
-%\end{proof}
-
-%Let 
-%$$
-%  \rho_\text{min} = \min\left\{
-%    \frac{\mu_\eta}{\sigma^2_\eta}, 
-%    \frac{\|\mu_{\delta}\|}{\|\Sigma_\delta\|},
-%    \frac{\|\mu_{\theta}\|}{\|\Sigma_\theta\|},
-%    \frac{\|\mu_{\phi}\|}{\|\Sigma_\phi\|},
-%    \frac{\|\mu_{\tilde\theta}\|}{\|\Sigma_{\tilde{\theta}}\|},
-%    \frac{\|\mu_{\tilde\phi}\|}{\|\Sigma_{\tilde{\phi}}\|}             
-%  \right\},
-%$$
-%and let
-%$$
-%  \rho_\text{max} = \max\left\{
-%    \frac{\mu_\eta}{\sigma^2_\eta}, 
-%    \frac{\|\mu_{\delta}\|}{\|\Sigma_\delta\|},
-%    \frac{\|\mu_{\theta}\|}{\|\Sigma_\theta\|},
-%    \frac{\|\mu_{\phi}\|}{\|\Sigma_\phi\|},
-%    \frac{\|\mu_{\tilde\theta}\|}{\|\Sigma_{\tilde{\theta}}\|},
-%    \frac{\|\mu_{\tilde\phi}\|}{\|\Sigma_{\tilde{\phi}}\|}             
-%  \right\}.
-%$$
+\textcolor{red}{We should consider differencing, then the difference $|y_{1,t} - y_{1,t-1}|$ should be close to the difference $|y_{i',t} - y_{i',t-1}|$ for all $t > T^*$}
+
+\vspace*{0.5cm}\noindent Get: $|y_{1,t} - y_{i',t}| < \varepsilon_1$ where we have $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$
+
+\vspace*{0.5cm}\noindent Next: OLS solution for post-shock dynamics $(X_{i'}'X_{i'})^{-1}X_{i'}'Y_{i'}$ is just a perturbation of OLS solution for post-shock dynamics $(X_1'X_1)^{-1}X_1'Y_1$
+
+\vspace*{0.5cm}\noindent Next: $|\hat{y}_{1,t}^h - \hat{y}_{i',t}^h|$ should be small for $t > T^*$
+
+\vspace*{0.5cm}\noindent Next: loss differential $\|\dbf_{1,t} - \dbf_{i',t}\|$ should be small for $t > T^*$.
+
+\vspace*{0.5cm}\noindent Finally: bootstrapping $\dbf_{i',t}$ in place of $\dbf_{1,t}$ should yield the same conclusions. \\
+
+\textbf{Notes}:
+$$
+\begin{pmatrix}
+	0 & t & T^* + (t-T^*) \\
+	1 & t-1 & T^* + (t-T^*-1) \\
+	2 & t-2 & T^* + (t-T^*-2) \\
+	 \vdots & \vdots \\
+	t-T^*-1 & t- (t-T^*-1) = T^*+1 & T^* + (t-T^*- (t-T^*-1) )	\\ 
+	t-T^* & t- (t-T^*) = T^* & T^* + (t-T^*- (t-T^*) )
+\end{pmatrix}
+$$
+
+$$
+D_{t} = I(t \geq T^*+1)
+$$
+
+\begin{align*}
+	&|(y_{1,t+1} - y_{1,t}) - (y_{i',t+1} - y_{i',t})| \\ 
+	&= |(\delta_1'\x_{1,T^*+1} + \tilde\phi_1 y_{1,t} + \tilde\theta'\x_{1,t+1} - y_{1,t} + \varepsilon_{1,t+1}) - (\delta_{i'}'\x_{i',T^*+1} + \tilde\phi_{i'} y_{i',t} + \tilde\theta'\x_{i',t+1} - y_{i',t} + \varepsilon_{i',t+1})| \\
+	&= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}) 
+	  + (\tilde\theta'\x_{1,t+1} - \tilde\theta'\x_{i',t+1}) 
+	  + (\varepsilon_{1,t+1} - \varepsilon_{i',t+1}) + ((\tilde\phi_1 - 1) y_{1,t} - (\tilde\phi_{i'} - 1) y_{i',t})|
+\end{align*}
+
+\begin{align*}
+	&|(y_{1,t+1} - y_{1,t}) - (y_{1,t} - y_{1,t-1})| \\ 
+	&= |(\delta_1'\x_{1,T^*+1} + \tilde\phi_1 y_{1,t} + \tilde\theta'\x_{1,t+1} - y_{1,t} + \varepsilon_{1,t+1}) - (\delta_{i'}'\x_{i',T^*+1} + \tilde\phi_{i'} y_{i',t} + \tilde\theta'\x_{i',t+1} - y_{i',t} + \varepsilon_{i',t+1})| \\
+	&= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}) 
+	  + (\tilde\theta'\x_{1,t+1} - \tilde\theta'\x_{i',t+1}) 
+	  + (\varepsilon_{1,t+1} - \varepsilon_{i',t+1}) + ((\tilde\phi_1 - 1) y_{1,t} - (\tilde\phi_{i'} - 1) y_{i',t})|
+\end{align*}
 

### 2022-04-20 prevalence_testing/postshocktest2022draft.tex
updated math argument; still need to bound differences and show how bootstrapping argument works

@@
 \mc{M} \colon \begin{array}{l}
-  y_{i,t} = \left(\eta_i + \sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j}\right)(1 - D_{i,t}) + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
+  y_{i,t} = \eta_i + \left(\sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j}\right)(1 - D_{i,t}) + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
   \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i +  \sum_{j=1}^{q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
@@
 Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^h$.
-Let the OLS estimate for
+Let the ordinary least squares (OLS) estimate for
 \begin{align*}
@@
 and let $\sigma^2 = \max(\lambda_{\max}, \sigma^2_{\max})$.
-Now arbitrarily choose $\varepsilon > 0$ and fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$ for all $t$ where $\varepsilon_1$ will be selected later.
+Now fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$ for all $t$ and some choice of $\varepsilon_1$.
 Pick some large $M > 0$.
@@
 \begin{align*}
-  E_1 := &\left\{\max\left(|\eta_1 - \eta_{i'}|,|\phi_{1,j}-\phi_{i',j}|,\|\theta_{1,k} - \theta_{i',k}\|,\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \varepsilon_1:\right.
-\\
+  E_1 := &\left\{\max\left(|\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \varepsilon_1:\right. \\
   &\qquad j = 1,\ldots,q_1, k = 1,\ldots,q_2, t = 1,\ldots,T \left.\right\}, \\
@@
 
-Conditional on $E = E_1 \cup E_2$, we first consider the recursion of $|y_{1,t} - y_{i',t}|$ for $t > T^*$,
-\begin{align*}
-	&|y_{1,t} - y_{i',t}| 
+For all $t > T^*$ let $\tilde y_{i',t}$ possess the same dynamics as $y_{i',t}$ except that this process is shifted in a manner to reflect how $y_{i,t}$ changes for all $t > T^*$.
+More formally, we will let
+$$
+  \tilde y_{i',t} = \left\{\begin{array}{cc}
+  y_{i,t} & \text{when} \; t < T^*+1; \\ 
+  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}y_{1,t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t = T^* + 1; \\
+  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}\tilde y_{i',t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t > T^* + 1.
+\end{array}\right.	
+$$
+The purpose of $\tilde y_{i',t}$ is to place the post-shock responses at the same starting point which allows us to avoid strong parametric specifications on the pre-shock dynamics.
+This series also contains terms which are estimable from the data.
+Define the event
+$$
+  E_3 := \{\max\left(y_{1,t},\tilde y_{i',t}\right) < M : t = 1,\ldots,T\}, 
+$$
+where $M$ is chosen large enough so that $\Prob(E_3^c) \to 0$ as $\sigma^2 \to 0$.
+We now consider the recursion of $|y_{1,t} - \tilde{y}_{i',t}|$ for $t > T^*$ conditional on $E = E_1 \cup E_2 \cup E_3$,
+\begin{align*}
+	&|y_{1,t} - \tilde{y}_{i',t}| 
 		= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1})
-		+ (\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}y_{i',t-1}) 
+		+ (\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}) 
 		+ (\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t}) + \tilde\varepsilon_t| \\
 	&\qquad \leq |\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}|
-		+ |\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}y_{i',t-1}| 
+		+ |\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}| 
 		+ |\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t})| 
 		+ \varepsilon_1 \\
-	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - y_{i',t-1}| \\
+	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - \tilde{y}_{i',t-1}| \\
 	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| \\ 
-	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - y_{i',t-2}|\right\} \\
-	&\qquad= \varepsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|y_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - y_{i',t-2}| \\
-	&\qquad \leq \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|y_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - y_{i',T^*}|.
-\end{align*}
-%Similarly, on $E$, we have 
-%\begin{align*}
-%	|y_{1,T^*} - y_{i',T^*}| &= |()|
-%\end{align*}
-\textcolor{red}{We should consider differencing, then the difference $|y_{1,t} - y_{1,t-1}|$ should be close to the difference $|y_{i',t} - y_{i',t-1}|$ for all $t > T^*$}
-
-\vspace*{0.5cm}\noindent Get: $|y_{1,t} - y_{i',t}| < \varepsilon_1$ where we have $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$
-
-\vspace*{0.5cm}\noindent Next: OLS solution for post-shock dynamics $(X_{i'}'X_{i'})^{-1}X_{i'}'Y_{i'}$ is just a perturbation of OLS solution for post-shock dynamics $(X_1'X_1)^{-1}X_1'Y_1$
-
-\vspace*{0.5cm}\noindent Next: $|\hat{y}_{1,t}^h - \hat{y}_{i',t}^h|$ should be small for $t > T^*$
+	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||\tilde{y}_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - \tilde{y}_{i',t-2}|\right\} \\
+	&\qquad= \varepsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|\tilde{y}_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - \tilde{y}_{i',t-2}| \\
+	&\qquad \leq \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - \tilde{y}_{i',T^*}| \\
+	&\qquad = \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}|.
+\end{align*}
+With $T$ set, we can choose $\varepsilon_1$ small enough so that 
+$
+  |y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_2
+$
+for all $T^* < t \leq T $.
+
+Now let $\varepsilon_3 = \max(\varepsilon_1,\varepsilon_2)$ so that $|y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_3$ and $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_3$.
+Let $\tilde{\beta}$ be the OLS solution of model parameters with respect to the $\tilde{y}_{i',t}$ series, and let $\hat{\beta}$ be the OLS solution of model parameters with respect to the $y_{1,t}$ series.
+On $E$, these estimates will be very close to each other.
+We use Theorem 2.7.2 in \cite{golub1996matrix} to construct an explicit bound on $\|\tilde{\beta} - \hat{\beta}\|$.
+Following the notation of Section 2.7 in \cite{golub1996matrix} we will let $A$ be the design matrix with respect to the $y_{1,t}$ series so that $A\hat{\beta} = \mathbf{y}_1$ where $\mathbf{y}_1 = (y_{1,1}, \ldots, y_{1,T})'$, $\kappa(A) = \|A\|\|A^{-1}\|$ be the condition number of $A$ where $\|\cdot\|$ is a matrix norm, and we will specify that $r = \varepsilon_4 \kappa(A)$ where $\varepsilon_4$ can be chosen so that $r < 1$.
+We will also specify that $\varepsilon_3$ is chosen so that $\|\Delta A\| \leq \varepsilon_4\|A\|$ where $\Delta A = \widetilde{A} - A$ and $\widetilde{A}$ is the design matrix with respect to the $\tilde{y}_{i',t}$ series.
+Theorem 2.7.2 in \cite{golub1996matrix} states that
+\begin{equation}\label{OLSbound}
+  \|\tilde{\beta} - \hat{\beta}\| \leq \frac{2\varepsilon_4}{1-r}\kappa(A)\|\hat{\beta}\|.	
+\end{equation}
+We can bound $\kappa(A)$ and $\hat{\beta}$ on $E$ which allows one to choose $\varepsilon_5$ so that \eqref{OLSbound} is $\|\tilde{\beta} - \hat{\beta}\| < \varepsilon_5$.
+
+We now show that we can bound $|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}|$ for $t+h > T^*$.
+We restrict attention to the case where $t+h > T^*$ because when $t+h \leq T^*$ the two competing forecasts $\hat{y}_{i,t}^{1,h}$ and $\hat{y}_{i,t}^{2,h}$ are the same in our setting for all $i$.
+Let $t+h > T^*$, then
+\begin{align*}
+  &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| = |(\hat\eta_1 - \hat{\eta}_{i'}) + (\hat\alpha_1 - \hat\alpha_{i'}) + (\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}) + (\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t})| \\
+  &\qquad \leq 2\varepsilon_5 + |\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t}| + |\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}| \\
+  &\qquad \leq 2\varepsilon_5 + \|\x_{1,t}\|\|\hat{\tilde{\theta}}_1 - \hat{\tilde{\theta}}_{i'}\| + \|\hat{\tilde{\theta}}_{i'}\| \|\x_{1,t} - \x_{i',t}\| + \|\hat{y}_{1,t-1}^{1,h-1}\| |\hat{\tilde{\phi}}_1 - \hat{\tilde{\phi}}_{i'}\| + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} | \\
+  &\qquad \leq 2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + \|\hat{y}_{1,t-1}^{1,h-1}\|\varepsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} |.
+\end{align*}
+On $E$ we can bound $|\hat{y}_{1,t-1}^{1,h-1}|$ for all $h=1,\ldots,H$ and $t=1,\ldots,T$, call this bound $M_1$.
+Let $\varepsilon_6 = (2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + M_1\varepsilon_5)$.
+Then,
+\begin{align*}
+  &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| \leq 2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + |\hat{y}_{1,t-1}^{1,h-1}|\varepsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
+  &\qquad \leq (2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + M_1\varepsilon_5) + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
+  &\qquad \leq \varepsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
+  &\qquad \leq \varepsilon_6 + |\hat{\tilde{\phi}}_{i'}|\left(\varepsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}|\right) \\
+  &\qquad \leq \varepsilon_6(1 + |\hat{\tilde{\phi}}_{i'}|) + |\hat{\tilde{\phi}}_{i'}|^2|\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}| \\  
+  &\qquad \leq \varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h|\hat{y}_{1,t-h} - \hat{y}_{i',t-h}| \\
+  &\qquad \leq \varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\varepsilon_3.  
+\end{align*}
+Let $\varepsilon_7 = \max_{h = 1,\ldots,H}\left(\varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\varepsilon_3\right)$ 
+and conclude that 
+\begin{equation} \label{forecastbounds}
+  |\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| < \varepsilon_7	
+\end{equation}
+for all $t = 1,\ldots,T$ and all $h=1,\ldots,H$ such that $t+h > T^*$ on the event $E$.
+A similar argument with similar bounding choices can be made so that $|\hat{y}_{1,t}^{2,h} - \hat{\tilde{y}}_{i',t}^{2,h}| < \varepsilon_7$.
+
+\vspace*{0.5cm}\textcolor{red}{Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^h$ is defined as
+ \begin{align*}
+ 	\hat{y}_{i,t}^h &= \left(\hat{\eta}_i + \sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
+  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\tilde{\bs{\theta}}}_{i,j+1},
+ \end{align*}
+ where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$.
+This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature.}
 
@@
 $$
-
-$$
-D_{t} = I(t \geq T^*+1)
-$$
-
-\begin{align*}
-	&|(y_{1,t+1} - y_{1,t}) - (y_{i',t+1} - y_{i',t})| \\ 
-	&= |(\delta_1'\x_{1,T^*+1} + \tilde\phi_1 y_{1,t} + \tilde\theta'\x_{1,t+1} - y_{1,t} + \varepsilon_{1,t+1}) - (\delta_{i'}'\x_{i',T^*+1} + \tilde\phi_{i'} y_{i',t} + \tilde\theta'\x_{i',t+1} - y_{i',t} + \varepsilon_{i',t+1})| \\
-	&= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}) 
-	  + (\tilde\theta'\x_{1,t+1} - \tilde\theta'\x_{i',t+1}) 
-	  + (\varepsilon_{1,t+1} - \varepsilon_{i',t+1}) + ((\tilde\phi_1 - 1) y_{1,t} - (\tilde\phi_{i'} - 1) y_{i',t})|
-\end{align*}
-
-\begin{align*}
-	&|(y_{1,t+1} - y_{1,t}) - (y_{1,t} - y_{1,t-1})| \\ 
-	&= |(\delta_1'\x_{1,T^*+1} + \tilde\phi_1 y_{1,t} + \tilde\theta'\x_{1,t+1} - y_{1,t} + \varepsilon_{1,t+1}) - (\delta_{i'}'\x_{i',T^*+1} + \tilde\phi_{i'} y_{i',t} + \tilde\theta'\x_{i',t+1} - y_{i',t} + \varepsilon_{i',t+1})| \\
-	&= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}) 
-	  + (\tilde\theta'\x_{1,t+1} - \tilde\theta'\x_{i',t+1}) 
-	  + (\varepsilon_{1,t+1} - \varepsilon_{i',t+1}) + ((\tilde\phi_1 - 1) y_{1,t} - (\tilde\phi_{i'} - 1) y_{i',t})|
-\end{align*}
 

### 2022-04-20 prevalence_testing/postshocktest2022draft.tex
added a bit; still need to finish bootstrap argument

@@
 
-\textcolor{red}{Next, we define the $h$-step forecast for $\mc{M}$, which plays an essential role in the framework of \citet{quaedvlieg2021multi}.
+Next, we define the $h$-step forecast for $\mc{M}$, which plays an essential role in the framework of \citet{quaedvlieg2021multi}.
 Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^h$.
@@
  where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$.
-This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature.}
+This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature (\textcolor{red}{either provide a citation or remove this sentence}).
 
@@
 
-Now let $\varepsilon_3 = \max(\varepsilon_1,\varepsilon_2)$ so that $|y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_3$ and $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_3$.
+Now let $\varepsilon_3 = \max(\varepsilon_1,\varepsilon_2)$ so that 
+\begin{equation} \label{bounds}
+	|y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_3, \; \text{and} \; \|\x_{1,t} - \x_{i',t}\| < \varepsilon_3.
+\end{equation}
+
 Let $\tilde{\beta}$ be the OLS solution of model parameters with respect to the $\tilde{y}_{i',t}$ series, and let $\hat{\beta}$ be the OLS solution of model parameters with respect to the $y_{1,t}$ series.
@@
 We restrict attention to the case where $t+h > T^*$ because when $t+h \leq T^*$ the two competing forecasts $\hat{y}_{i,t}^{1,h}$ and $\hat{y}_{i,t}^{2,h}$ are the same in our setting for all $i$.
-Let $t+h > T^*$, then
+Let $t+h > T^*$, then, when $t > T^*$,
 \begin{align*}
@@
 \begin{equation} \label{forecastbounds}
-  |\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| < \varepsilon_7	
+  |\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| < \varepsilon_7,	
 \end{equation}
 for all $t = 1,\ldots,T$ and all $h=1,\ldots,H$ such that $t+h > T^*$ on the event $E$.
-A similar argument with similar bounding choices can be made so that $|\hat{y}_{1,t}^{2,h} - \hat{\tilde{y}}_{i',t}^{2,h}| < \varepsilon_7$.
-
-\vspace*{0.5cm}\textcolor{red}{Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^h$ is defined as
- \begin{align*}
- 	\hat{y}_{i,t}^h &= \left(\hat{\eta}_i + \sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
-  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\tilde{\bs{\theta}}}_{i,j+1},
- \end{align*}
- where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$.
-This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature.}
-
-\vspace*{0.5cm}\noindent Next: loss differential $\|\dbf_{1,t} - \dbf_{i',t}\|$ should be small for $t > T^*$.
+A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made when $t+h > T^*$ and $t \leq T^*$.
+A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made so that $|\hat{y}_{1,t}^{2,h} - \hat{\tilde{y}}_{i',t}^{2,h}| < \varepsilon_7$.
+
+We now bound the difference in loss differential vectors $\|\dbf_{1,t} - \dbf_{i',t}\|$ for $t > T^*$ when we specify the loss $L(a,b) = |a-b|$.
+The loss differential vector $\dbf_{1,t} \in \R^H$ has elements $|y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}|$.
+What we have showed so far in \eqref{bounds} and \eqref{forecastbounds} allows us to write
+$$
+  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{i',h}_{1,t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{1,t}| + 2(\varepsilon_3 + \varepsilon_7).
+$$
+Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$.
 
@@
 
-\textbf{Notes}:
-$$
-\begin{pmatrix}
-	0 & t & T^* + (t-T^*) \\
-	1 & t-1 & T^* + (t-T^*-1) \\
-	2 & t-2 & T^* + (t-T^*-2) \\
-	 \vdots & \vdots \\
-	t-T^*-1 & t- (t-T^*-1) = T^*+1 & T^* + (t-T^*- (t-T^*-1) )	\\ 
-	t-T^* & t- (t-T^*) = T^* & T^* + (t-T^*- (t-T^*) )
-\end{pmatrix}
-$$
+%\textbf{Notes}:
+%$$
+%\begin{pmatrix}
+%	0 & t & T^* + (t-T^*) \\
+%	1 & t-1 & T^* + (t-T^*-1) \\
+%	2 & t-2 & T^* + (t-T^*-2) \\
+%	 \vdots & \vdots \\
+%	t-T^*-1 & t- (t-T^*-1) = T^*+1 & T^* + (t-T^*- (t-T^*-1) )	\\ 
+%	t-T^* & t- (t-T^*) = T^* & T^* + (t-T^*- (t-T^*) )
+%\end{pmatrix}
+%$$
 

### 2022-04-26 prevalence_testing/postshocktest2022draft.tex
minor edits; still need to finish argument

@@
 
-(\textcolor{red}{this needs work}) In Section \ref{sec:multhor} we discuss the background in \cite{quaedvlieg2021multi} that is necessary for our post-shock testing procedure.
-In Section \ref{modelsetup} we motivate time series models that we consider.
+(\textcolor{red}{this needs work}) In Section \ref{modelsetup} we motivate time series models that we consider.
+In Section \ref{sec:multhor} we discuss the background in \cite{quaedvlieg2021multi} that is necessary for our post-shock testing procedure.
 In Section \ref{sec:aggmeth} we present aggregation strategies that we consider which inform our decision about the expected shock behavior.
@@
 \section{Methodological details}
-
-\subsection{Multi-horizon forecasting procedure}
-\label{sec:multhor}
-
-In this section we discuss the background of the multi-horizon forecasting procedure \citep{quaedvlieg2021multi} that is necessary for the investigation of shock behavior in our anticipated post-shock setting.
-The initial building blocks in the assessment of predictive ability of forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ will make use of a loss differential
-$$
-  \dbf_{i,t} = \Llet_{i,t,1} - \Llet_{i,t,2},
-$$
-where $\Llet_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function.
-Define the expected loss differential as  $E(\dbf_{i,t}) = \mbf\mu_{i,t}$ and let the average expected loss differential be defined as $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
-%Hypothesis tests in \cite{quaedvlieg2021multi} are then constructed with respect to estimates of the expected loss differentials $E(\dbf_{i,t}) = \mbf\mu_{i,t}$, %Conditions for these tests require conditions of \cite{giacomini2006tests}.
-%where specific interest is in the average expected loss differential $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
-%%%\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$.
-We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock.
-Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool.
-%%%\vspace*{0.5cm}
-We will then judge forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ based on the average superior predictive ability (aSPA) \citep{quaedvlieg2021multi}.
-The aSPA investigates forecast comparisons based on their weighted average loss difference
-$$
-  \mu^{(\text{Avg})}_i = \textbf{w}_i'\mathbf{\mu}_i = \sum_{h=1}^H w_{i,h} \mu_i^h,
-$$
-with weights $\textbf{w}_i$ that sum to one.
-Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu_i^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1.
-With this caveat in mind we will use $w_{i,h} = 1/H$, and we will consider different time horizons $H$ in some of our examples.
-
-We consider a simple test for average SPA, based on the weighted-average loss differential. The associated null is
-\begin{equation} \label{test}
-	H_{i,\text{aSPA}}^0: \mu^{(\text{Avg})}_i \leq 0.
-\end{equation}
-A studentized test statistic corresponding to the null hypothesis \eqref{test} is of the form 
-\begin{equation} \label{tstat}
-	t_{i,\text{aSPA}} = \frac{\sqrt{T}_i\bar{d}_{i}}{\hat{\zeta}_{i}},
-\end{equation}
-where $\bar{d}_{i} = \textbf{w}_i'\textbf{d}_{i}$ and we choose to estimate $\zeta_{i} = \sqrt{\textbf{w}_i'\Omega_{i}\textbf{w}_i}$ directly based on $\textbf{w}_i'\textbf{d}_{i,t}$ using the HAC estimator \citep{giacomini2006tests} where $\Omega_{i} = \text{avar}\left(\sqrt{T}_i(\bar{d}_{i} - \mbf{\mu}_{i})\right)$.
-
-A p-value corresponding to the hypothesis test \eqref{test} is computed using a moving block bootstrap (MBB) of of \cite{kunsch1989jackknife} and \cite{liu1992moving}.
-In the moving block bootstrap (MBB), a pseudo time-series is constructed by resampling blocks of length $\ell$ from the original data.
-
-%We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
-Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = lK_i$.
-Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
-$$
-  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
-$$
-The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.
-
-\begin{equation} \label{whb}
-	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{K_i}\sum_{k=1}^{K_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
-\end{equation}
-where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
-\begin{equation} \label{boott}
-  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
-  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
-  \Big\vert \overset{P}{\longrightarrow} 0,
-\end{equation}
-as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
-\begin{equation} \label{bootp}
-  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
-\end{equation}
-The results \eqref{boott} implies that 
-$$
-  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
-$$
-where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$.
-Therefore bootstrap inference in the donor pool is a good approximation.
-%We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.
 
@@
 The post-shock dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$, the covariates recorded right before the first post-shock response is observed.
-Under this setup any two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|_2$ are expected to experience similar structural changes.
+Under this setup any two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|$ are expected to experience similar structural changes.
 This makes distance based weighting an attractive avenue.
 
-Next, we define the $h$-step forecast for $\mc{M}$, which plays an essential role in the framework of \citet{quaedvlieg2021multi}.
-Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^h$.
+Next, we define the $h$-step forecast for $\mc{M}$ which plays an essential role in the framework of \citet{quaedvlieg2021multi}.
+Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^{1,h}$.
 Let the ordinary least squares (OLS) estimate for
 \begin{align*}
-	\{(\eta_i, \alpha_i, \phi_{i,j_1}, \bs{\theta}_{i,j_2}, \tilde{\phi}_{i,j_1}, \tilde{\bs{\theta}}_{i,j_2}) \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}
+	\{(\eta_i, \alpha_i, \phi_{i,j_1}, \bs{\theta}_{i,j_2}', \tilde{\phi}_{i,j_1}, \tilde{\bs{\theta}}_{i,j_2}')' \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}
 \end{align*}
@@
  \begin{align*}
- 	\{(\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_{i,j_1}, \hat{\bs{\theta}}_{i,j_2}, \hat{\tilde{\phi}}_{i,j_1}, \hat{\tilde{\bs{\theta}}}_{i,j_2}) \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}.
- \end{align*}
-Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^h$ is defined as
- \begin{align*}
- 	\hat{y}_{i,t}^h &= \left(\hat{\eta}_i + \sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
-  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\tilde{\bs{\theta}}}_{i,j+1},
+ 	\{(\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_{i,j_1}, \hat{\bs{\theta}}_{i,j_2}', \hat{\tilde{\phi}}_{i,j_1}, \hat{\tilde{\bs{\theta}}}_{i,j_2}')' \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}.
+ \end{align*}
+Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^{1,h}$ is defined as
+ \begin{align*}
+ 	\hat{y}_{i,t}^{1,h} &= \hat{\eta}_i + \left(\sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{1,h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
+  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{1,h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\tilde{\bs{\theta}}}_{i,j+1},
  \end{align*}
@@
 This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature (\textcolor{red}{either provide a citation or remove this sentence}).
+The $h$-step forecast corresponding to the model that does include any post-shock changes $\hat{y}_{i,t}^{2,h}$ is defined similarly,
+\begin{equation*}
+ 	\hat{y}_{i,t}^{2,h} = \hat{\eta}_i + \left(\sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{2,h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\bs{\theta}}_{i,j+1}\right).
+\end{equation*}
+
+\subsection{Multi-horizon forecasting procedure}
+\label{sec:multhor}
+
+In this section we discuss the background of the multi-horizon forecasting procedure \citep{quaedvlieg2021multi} that is necessary for the investigation of shock behavior in our anticipated post-shock setting.
+The initial building blocks in the assessment of predictive ability of forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ will make use of a loss differential
+$$
+  \dbf_{i,t} = \Llet_{i,t,1} - \Llet_{i,t,2},
+$$
+where $\Llet_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function.
+Define the expected loss differential as  $E(\dbf_{i,t}) = \mbf\mu_{i,t}$ and let the average expected loss differential be defined as $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
+%Hypothesis tests in \cite{quaedvlieg2021multi} are then constructed with respect to estimates of the expected loss differentials $E(\dbf_{i,t}) = \mbf\mu_{i,t}$, %Conditions for these tests require conditions of \cite{giacomini2006tests}.
+%where specific interest is in the average expected loss differential $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
+%%%\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$.
+We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock.
+Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool.
+%%%\vspace*{0.5cm}
+We will then judge forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ based on the average superior predictive ability (aSPA) \citep{quaedvlieg2021multi}.
+The aSPA investigates forecast comparisons based on their weighted average loss difference
+$$
+  \mu^{(\text{Avg})}_i = \textbf{w}_i'\mathbf{\mu}_i = \sum_{h=1}^H w_{i,h} \mu_i^h,
+$$
+with weights $\textbf{w}_i$ that sum to one.
+Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu_i^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1.
+With this caveat in mind we will use $w_{i,h} = 1/H$, and we will consider different time horizons $H$ in some of our examples.
+
+We consider a simple test for average SPA, based on the weighted-average loss differential. The associated null is
+\begin{equation} \label{test}
+	H_{i,\text{aSPA}}^0: \mu^{(\text{Avg})}_i \leq 0.
+\end{equation}
+A studentized test statistic corresponding to the null hypothesis \eqref{test} is of the form 
+\begin{equation} \label{tstat}
+	t_{i,\text{aSPA}} = \frac{\sqrt{T}_i\bar{d}_{i}}{\hat{\zeta}_{i}},
+\end{equation}
+where $\bar{d}_{i} = \textbf{w}_i'\textbf{d}_{i}$ and we choose to estimate $\zeta_{i} = \sqrt{\textbf{w}_i'\Omega_{i}\textbf{w}_i}$ directly based on $\textbf{w}_i'\textbf{d}_{i,t}$ using the HAC estimator \citep{giacomini2006tests} where $\Omega_{i} = \text{avar}\left(\sqrt{T}_i(\bar{d}_{i} - \mbf{\mu}_{i})\right)$.
+
+A p-value corresponding to the hypothesis test \eqref{test} is computed using a moving block bootstrap (MBB) of of \cite{kunsch1989jackknife} and \cite{liu1992moving}.
+In the moving block bootstrap (MBB), a pseudo time-series is constructed by resampling blocks of length $\ell$ from the original data.
+
+%We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
+Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = lK_i$.
+Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
+$$
+  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
+$$
+The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.
+
+\begin{equation} \label{whb}
+	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{K_i}\sum_{k=1}^{K_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
+\end{equation}
+where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
+\begin{equation} \label{boott}
+  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
+  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
+  \Big\vert \overset{P}{\longrightarrow} 0,
+\end{equation}
+as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
+\begin{equation} \label{bootp}
+  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
+\end{equation}
+The results \eqref{boott} implies that 
+$$
+  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
+$$
+where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$.
+Therefore bootstrap inference in the donor pool is a good approximation.
+%We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.
 
@@
 \newpage
-\textbf{Repeating for reference}:
-\begin{align}
-\mc{M} \colon \begin{array}{l}
-  y_{i,t} = \eta_i + \left(\sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j}\right)(1 - D_{i,t}) + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
-  \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i +  \sum_{j=1}^{q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
-  \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
-  %\sum_{j=1}^{q_3}\delta_{i,j}'\mbf{x}_{i, T_i^*-j+1}+ \t{\varepsilon}_{i}, 
-\end{array}\label{model-gen2}
-\end{align}
-where $D_{i,t} = I(t \geq T_i^* + 1)$, $I(\cdot)$ is the indicator function, $\x_{i,t} \in \R^{p}$ are fixed with $p \geq 1$. Let 
-$\mathbf{\phi}_i = (\phi_{i,1},\ldots,\phi_{i,q_1})'$, 
-$\mathbf{\theta}_i = (\theta_{i,1},\ldots,\theta_{i,q_2})'$, 
-$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_{1}})'$, 
-$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i, q_{2}})'$, 
-$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,p})'$, 
-and suppose that the regression coefficients in \eqref{model-gen2} have the following hierarchical random effects structure: 
-\begin{equation} \label{random-effects2}
-\begin{split}
-  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = \mu_\eta, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
-  \mathbf{\phi}_{i,j} &\simiid \mc{F}_{\mathbf{\phi}_j} \text{ where } |\phi_{i,j}| < 1, \\
-  \mathbf{\theta}_{i,j} &\simiid \mc{F}_{\mathbf{\theta}_j} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}_j}}(\theta_{i,j}) = \mu_{\mathbf{\theta}_j}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}_j}}(\mathbf{\theta}_{i,j})  = \Sigma^2_{\mathbf{\theta}_j}, \\
-  \mathbf{\delta}_i &\simiid  \mc{F}_{\mathbf{\delta}} \text{ with } \mrm{E}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\mu_{\mathbf{\delta}}, \mrm{Var}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\Sigma_{\mathbf{\delta}}, \\
-\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i,  \\
-\varepsilon_{\alpha, i} &\simiid  \mc{F}_{\varepsilon_\alpha} \text{ with }\mrm{E}_{\mc{F}_{\varepsilon_\alpha}}(\varepsilon_{\alpha, i})=0, \mrm{Var}_{\mc{F}_{\varepsilon_{\alpha}}}(\varepsilon_{\alpha, i})=\sigma^2_{\alpha}, \\
-  \tilde{\mathbf{\phi}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\phi}_j}}(\x_{i,T_i^*+1}) \; \text{where} \; |\tilde{\mathbf{\phi}}_{i,j}| < 1,  \\
-  \tilde{\mathbf{\theta}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\theta}_j}}(\x_{i,T_i^*+1}),  \\  
- % \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\
-&\eta_i \indep \mathbf{\phi}_{i,j} \indep \mathbf{\theta}_{i,j} \indep 
-\tilde{\mathbf{\phi}}_{i,j} \indep \lambda_{i,j} \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i}, 
-\end{split}
-\end{equation}
 
@@
   &\qquad j = 1,\ldots,q_1, k = 1,\ldots,q_2, t = 1,\ldots,T \left.\right\}, \\
-  E_2 := &\{\|(\bm{\eta}',\bm{\phi}',\bm{\theta}',\bm{\delta}',\tilde{\bm{\phi}}',\tilde{\bm{\theta}}')\|_\infty < M\},  
+  E_2 := &\{\|(\bm{\eta}',\bm{\phi}',\bm{\theta}',\bm{\delta}',\tilde{\bm{\phi}}',\tilde{\bm{\theta}}')'\|_\infty < M_1\},  
 \end{align*}
 where $\tilde\varepsilon_t = \varepsilon_{1,t} - \varepsilon_{i',t} + D_{i,t}(\varepsilon_{\alpha,1} - \varepsilon_{\alpha,i'})$ and $\bm{\eta},\bm{\phi},\bm{\theta},\bm{\delta},\tilde{\bm{\phi}}$, and $\tilde{\bm{\theta}}$ are vectors containing the random effects in \eqref{random-effects} for indices $1$ and $i'$, and we take $\|\bm{a}\|_\infty = \max_j(|a_j|)$ .
-We will also suppose that $\|\x_{j,t}\|_\infty < M$ for $j \in \{1,i'\}$ and all $t = 1,\ldots,T$.
+We will also suppose that $\|\x_{j,t}\|_\infty < M_1$ for $j \in \{1,i'\}$ and all $t = 1,\ldots,T$.
 Note that both $\Prob(E_1^C) \to 0$ and $\Prob(E_2^C) \to 0$  as $\sigma^2 \to 0$ with $T$ and $n$ fixed.
@@
 $$
-  E_3 := \{\max\left(y_{1,t},\tilde y_{i',t}\right) < M : t = 1,\ldots,T\}, 
-$$
-where $M$ is chosen large enough so that $\Prob(E_3^c) \to 0$ as $\sigma^2 \to 0$.
-We now consider the recursion of $|y_{1,t} - \tilde{y}_{i',t}|$ for $t > T^*$ conditional on $E = E_1 \cup E_2 \cup E_3$,
+  E_3 := \{\max\left(y_{1,t},\tilde y_{i',t}\right) < M_2 : t = 1,\ldots,T\}, 
+$$
+where $M_2$ is chosen large enough so that $\Prob(E_3^c) \to 0$ as $\sigma^2 \to 0$.
+Let $M = \max(M_1,M_2).$ We now consider the recursion of $|y_{1,t} - \tilde{y}_{i',t}|$ for $t > T^*$ conditional on $E = E_1 \cup E_2 \cup E_3$,
 \begin{align*}
@@
 $$
-Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$.
+Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.
 
@@
 As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small.
-Note that Proposition \ref{votprop} and Corollary \ref{coro1} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$.
+Note that Proposition \ref{votprop} and Corollary \ref{coro2} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$.
 Note that the interpretation and meaning of $p_1$ is closely connected with models.

### 2022-04-28 prevalence_testing/postshocktest2022draft.tex
edits to Intro and Discussion; Intro is starting to look good; Discussion needs work

@@
 As it currently stands this method is not appropriate for more nuanced forecasts involving $h$-ahead time points.
-In this article we develop a  hypothesis testing procedure motivated by the methodology of \cite{lin2021minimizing} and the multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi} in order to test whether or not time series which incorporate shock information exhibit superior predictive performance over forecasts which do not over a set time horizon.
+In this article we develop a  hypothesis testing procedure for determining whether or not time series which incorporate shock information exhibit superior predictive performance over forecasts which do not incorporate such information over a set time horizon.
 This effectively tests whether a shock is transient or permanent over a set time horizon.
 
-\textcolor{red}{This needs work} The core idea of our methodology is to sensibly aggregate similar past realized shock effects which arose from other time series, and then incorporate the aggregated shock effect estimator into the present forecast.
-Our testing method embraces ideas from
-forecast aggregation in the post-shock setting \citep{lin2021minimizing}, 
-forecast comparison \citep{diebold1995comparing, quaedvlieg2021multi}, 
-and p-value combination. 
-It also has similarities with 
+\textcolor{red}{This needs work} The core idea of our methodology is to first form a donor pool of time series that have undergone similar shocks, then perform the multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi}  with respect to each of these donors to determine whether the shock is prevalent or transient, and then aggregate the decisions from the donors to make a final decision of transience or prevalence for the time series under study for which no post-shock observations are observed.
+The multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi} is a natural  extension of \cite{diebold1995comparing}.
+The post-shock setting follows similar logic as that in \cite{lin2021minimizing}.
+%Our testing method embraces ideas from forecast aggregation in the post-shock setting \citep{lin2021minimizing}, forecast comparison \citep{diebold1995comparing, quaedvlieg2021multi}, and p-value combination.
+Our procedure has conceptual similarities with 
 conditional forecasting \citep{baumeister2014real, kilian2017structural}, 
@@
 forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, 
-synthetic control methodology \citep{abadie2010synthetic, agarwal2020two},  
-expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
-
-\vspace*{0.5cm}\noindent\textcolor{red}{Need more pointed references on similar methods.
+synthetic control methodology \citep{abadie2010synthetic}, 
+synthetic interventions \citep{agarwal2020synthetic, agarwal2020two}, 
+and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}.
+The synthetic intervention approach in \cite{agarwal2020two} is particularly relevant to our method.
+These authors construct a panel of countries undergoing a variety of interventions and use it to estimate what COVID case trajectories for a particular country would have looked like under different chosen courses of action.
+They then demonstrate that the method well replicates the observed trajectories of countries under the chosen intervention.
+This method works well because there are multiple countries undergoing similar interventions in response to a common shock which occurs at a similar past time for each country.
+In our setting, we do not specify that the time series in the donor pool be temporally similar to the time series under study, but we require that the shocks to those time series be similar to the shock of the time series under study.
+In \cite{lin2021minimizing} this similarity was stated in the form of a shock-effect distribution.
+In the present work, we parameterize similarity into post-shock dynamics for an autoregressive process.
+
+As alluded to above, the success of our approach hinges on the construction of a suitable donor pool that possess similar post-shock dynamics to the time series under study.
+We develop a pragmatic parametric time series model which parameterizes such a structure.
+Without such a parameterization there is no avenue for connecting decisions made regarding the post-shock information in the donor pool with the yet-to-be observed post-shock information corresponding to the time series under study.
+The parameterization that we use states that the post-shock dynamics are determined in part by observed covariates collected right before the first post-shock response is observed.
+Such a parameterization will not be known in practice.
+That being said, one can demonstrate the effectiveness and appropriateness of such a parameterization via a leave one out cross validation approach applied to the donor pool in which all post-shock information is observed \textcolor{red}{need LOOCV approach}.
+A similar prospective approach was discussed in \cite{lin2021minimizing}.
+We demonstrate the utility of our prevalence testing approach on two real data examples forecasting daily Conoco Phillips stock prices and monthly employment data as well as several simulation examples.
+Our simulation examples show settings in which our method is expected to work well and demonstrate that the appropriateness of the method decreases as the parametric specifications break down.
+In the real data examples, we show that the decisions obtained from the donor pool match those that would be observed in the future.
+
+%\vspace*{0.5cm}\noindent\textcolor{red}{Need more pointed references on similar methods.
 Need to discuss how this method extends \cite{lin2021minimizing} and is an application of \cite{quaedvlieg2021multi}.}
+
+%\subsection{Forecasting and testing for shock persistence}
+%\label{forecast}
+
+%In this section, we motivates the relation between shock persistence testing and forecasting comparison.
+In time series literature, under a squared error loss $L(\cdot)$, the forecast using the conditional mean is the best point forecast that minimizes the expected loss if the model is specified correctly.
+That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional mean forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases.
+On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information and makes good use of it should enjoy a smaller expected loss than any conditional mean forecast without such information does.
+In other words, the problem of testing for shock persistence boils down into comparing the conditional mean forecast that is adjusted by shock information and the one that is unadjusted.
+To deal with this problem, we applied the forecast comparison procedure of  \cite{quaedvlieg2021multi} to conduct shock persistence testing.
+
+%In this paper, we extend the framework of post-shock forecast \citep{lin2021minimizing}, which aggregates outside information by constructing a donor pool, to post-shock persistence testing.
+The donor pool consists of time series called  ``donors'' that are similar to the time series of interest.
+As we do not observe the future data, information from donors can aid our decision making and forecasts.
+Note that what  similarity exactly means here can be vague but the donors and the time series of interest should come from a common population in principle; see more details of how to select donors in \cite{lin2021minimizing}.
+In this paper, we also proposed several theoretical results with some detailed conditions on the donor pool, which may alleviate the difficulty of dealing with similarity when choosing donors.
+
+%In this paper, we propose a new way of aggregating information from donor pool to conduct post-shock persistence testing, which is quite different from \cite{lin2021minimizing}.
+The general structure of this aggregation technique is illustrated as below.
+Suppose we are given a nonempty donor pool with size $n$ that consists of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed.
+With shock information, we are able to compute unadjusted forecast that does not incorporate shock information and adjusted forecast that does.
+The forecast comparison using methodology of \cite{quaedvlieg2021multi} for each donor yields a $p$-value, $p_{i+1}$ for $i$th donor in the donor pool.
+Given $\{p_i \colon i = 2, \ldots, n+1\}$, we propose a methodology for judging whether the shock of the time series of interest is persistent or not.
+Next, we illustrate the details of our methodology as below.
+
+%For each donor $\mc{T}_i$, $i = 2, \ldots, n+1$, to compare adjusted and unadjusted forecasts,  a model needs to be specified.
+The model should describe how the shock impacts the time series at and after a certain time point $t= T_i^* + 1$.
+For clarity, we refers the unadjusted forecast to the conditional mean forecast based on the part of the model that ignores shock effect; and the adjusted forecast refers to the conditional mean forecast based on the full model.
+Note that the model needs not to be the same for every donor in the donor pool.
+However, certain conditions need to be imposed as discussed previously.
+
+% Given a model for each donor pool, we compute the unadjusted conditional mean forecast and adjusted conditional mean forecast in the framework of \cite{quaedvlieg2021multi}.
+As introduced in the beginning of Section \ref{section2}, for a given horizon $h$, to forecast $y_{i, t}$, we compute the two forecasts based on the information set $\mathcal{F}_{i, t-h}$ of each donor pool (i.e., the data before $t-h$) for $i = 2, \ldots, n+1$.
+Note that in practice, a training sample size $K_i$ should be specified for $i = 2, \ldots, n+1$ such that we use the information set $\mathcal{F}_{i, t-h-K_i + 1:t-h}$.
+
+% Even if the data contain shock information for each donor, it is impossible to compute the adjusted conditional mean forecast based on $\mathcal{F}_{i, t-h}$ when $t -h \leq T_i^*$, i.e., we only have training data that do no have any shock information.
+Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information.
+In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an consistent estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate.
+However, the consistent estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.
+To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear.
+However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.
+
+% With the presence of autoregressive parameters in some models, unbiased estimation with OLS is not feasible but the bias is $O(T^{-1})$, where $T$ is the time series length \citep{shaman1988bias}.
+In this paper, we use the OLS estimates to approximate the adjusted conditional mean forecast and unadjusted one.
+The bias decades away as $T\to \infty$.
 
@@
 In Section \ref{sec:aggmeth} we present aggregation strategies that we consider which inform our decision about the expected shock behavior.
+In Section \ref{mathdemo} we provide a heuristic setting that demonstrates when our proposed procedure is expected to work well.
 
@@
 
-We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool and \textcolor{red}{the algorithms are described in Algorithm \ref{voting}.
+We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool. \\
+
+\textcolor{red}{Jilei, I want you to just describe what the voting method is in plain writing as I have done above with the weighted average p-value. The propositions can then follow.} \\
+
+\textcolor{red}{Jilei, the algorithm needs to make explicit that a moving block bootstrap is performed.} \\
+
+\textcolor{red}{the algorithms are described in Algorithm \ref{voting}.
 There are a couple of details that are worth noting.
@@
 \vspace{.5cm}
-\begin{algorithm}[H]
+\begin{algorithm}
 \SetAlgoLined \label{voting}
@@
 We now motivate a model selection framework for comparing different models in the donor pool with a goal of inferring which model is most appropriate for the time series under study.
-
 Suppose we are interested in comparing two models $\mc{M}_0$ and $\mc{M}$ using AIC for forecasting the response in the time series of interest.
@@
 
-\subsection{Forecasting and testing for shock persistence}
-\label{forecast}
-
-In this section, we motivates the relation between shock persistence testing and forecasting comparison.
-In time series literature, under a squared error loss $L(\cdot)$, the forecast using the conditional mean is the best point forecast that minimizes the expected loss if the model is specified correctly.
-That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional mean forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases.
-On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information and makes good use of it should enjoy a smaller expected loss than any conditional mean forecast without such information does.
-In other words, the problem of testing for shock persistence boils down into comparing the conditional mean forecast that is adjusted by shock information and the one that is unadjusted.
-To deal with this problem, we applied the forecast comparison procedure of  \cite{quaedvlieg2021multi} to conduct shock persistence testing.
-
-In this paper, we extend the framework of post-shock forecast \citep{lin2021minimizing}, which aggregates outside information by constructing a donor pool, to post-shock persistence testing.
-The donor pool consists of time series called  ``donors'' that are similar to the time series of interest.
-As we do not observe the future data, information from donors can aid our decision making and forecasts.
-Note that what  similarity exactly means here can be vague but the donors and the time series of interest should come from a common population in principle; see more details of how to select donors in \cite{lin2021minimizing}.
-In this paper, we also proposed several theoretical results with some detailed conditions on the donor pool, which may alleviate the difficulty of dealing with similarity when choosing donors.
-
-In this paper, we propose a new way of aggregating information from donor pool to conduct post-shock persistence testing, which is quite different from \cite{lin2021minimizing}.
-The general structure of this aggregation technique is illustrated as below.
-Suppose we are given a nonempty donor pool with size $n$ that consists of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed.
-With shock information, we are able to compute unadjusted forecast that does not incorporate shock information and adjusted forecast that does.
-The forecast comparison using methodology of \cite{quaedvlieg2021multi} for each donor yields a $p$-value, $p_{i+1}$ for $i$th donor in the donor pool.
-Given $\{p_i \colon i = 2, \ldots, n+1\}$, we propose a methodology for judging whether the shock of the time series of interest is persistent or not.
-Next, we illustrate the details of our methodology as below.
-
-For each donor $\mc{T}_i$, $i = 2, \ldots, n+1$, to compare adjusted and unadjusted forecasts,  a model needs to be specified.
-The model should describe how the shock impacts the time series at and after a certain time point $t= T_i^* + 1$.
-For clarity, we refers the unadjusted forecast to the conditional mean forecast based on the part of the model that ignores shock effect; and the adjusted forecast refers to the conditional mean forecast based on the full model.
-Note that the model needs not to be the same for every donor in the donor pool.
-However, certain conditions need to be imposed as discussed previously.
-
- Given a model for each donor pool, we compute the unadjusted conditional mean forecast and adjusted conditional mean forecast in the framework of \cite{quaedvlieg2021multi}.
-As introduced in the beginning of Section \ref{section2}, for a given horizon $h$, to forecast $y_{i, t}$, we compute the two forecasts based on the information set $\mathcal{F}_{i, t-h}$ of each donor pool (i.e., the data before $t-h$) for $i = 2, \ldots, n+1$.
-Note that in practice, a training sample size $K_i$ should be specified for $i = 2, \ldots, n+1$ such that we use the information set $\mathcal{F}_{i, t-h-K_i + 1:t-h}$.
-
- Even if the data contain shock information for each donor, it is impossible to compute the adjusted conditional mean forecast based on $\mathcal{F}_{i, t-h}$ when $t -h \leq T_i^*$, i.e., we only have training data that do no have any shock information.
-Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information.
-In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an consistent estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate.
-However, the consistent estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.
-To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear.
-However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.
-
- With the presence of autoregressive parameters in some models, unbiased estimation with OLS is not feasible but the bias is $O(T^{-1})$, where $T$ is the time series length \citep{shaman1988bias}.
-In this paper, we use the OLS estimates to approximate the adjusted conditional mean forecast and unadjusted one.
-The bias decades away as $T\to \infty$.
-
-\newpage
+\subsection{Heuristic setting demonstrating when prevalence testing works well}
+\label{mathdemo}
 
@@
 Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.
-
-\vspace*{0.5cm}\noindent Finally: bootstrapping $\dbf_{i',t}$ in place of $\dbf_{1,t}$ should yield the same conclusions. \\
+Putting this all together, we can pick $\varepsilon_8$ small enough so that for some fixed $\varepsilon > 0$,
+\begin{equation} \label{testbounds}
+   \left|\sqrt{T}\frac{\textbf{w}_1'\bar{\dbf}_1^b - \textbf{w}_1'\bar{\dbf}_1}{\hat{\zeta}^b_1} - \sqrt{T}\frac{\textbf{w}_{i'}'\bar{\dbf}_{i'}^b - \textbf{w}_{i'}'\bar{\dbf}_{i'}}{\hat{\zeta}^b_{i'}}\right| < \varepsilon
+\end{equation}
+on the set $E$ where we specify that $\textbf{w}_1 = \textbf{w}_{i'}$ and that the MBB procedures samples the same indices of blocks from $\dbf_{1,t}$ and $\dbf_{i',t}$, $t = T^*+1,\ldots, T$ when forming the test statistics in \eqref{testbounds}.
+Thus for any fixed small $\varepsilon < 0$ there exists a choice of $\sigma^2$ and $\varepsilon_1$ such that inferences involving the $i'$ series for which post-shock behavior is observed can be substituted in place of the $i = 1$ series under study with high probability of a correspondence in inferences.
 
@@
 
-Talk about post-shock forecasting as parameterizing exogeniety and using hindsight in the donor pool to explicitly estimate exogeneity apriori.
+\textcolor{red}{needs work} Talk about post-shock forecasting as parameterizing exogeniety and using hindsight in the donor pool to explicitly estimate exogeneity apriori.
 This framing has its limits, we are not able to perform post-shock forecasts when we are temporarily removed from the known shock time.
@@
 
-The post-shock forecasting methodology presented here and in \cite{lin2021minimizing} is heavily dependent on the construction of a suitable donor pool which will exhibit a degree of subjectivity.
-This is a limitation of our approach, but we argue that this limitation is not a deal breaker.
+\textcolor{red}{needs work} The post-shock forecasting methodology presented here and in \cite{lin2021minimizing} is heavily dependent on the construction of a suitable donor pool which will exhibit a degree of subjectivity.
+This is a limitation of our approach, but we argue that this limitation is far from a deal breaker and has its virtues.
+Our approach allows for subject matter experts to obtain answers in a tractable manner from donor pool to model to answers.
+Subject matter experts can therefore investigate and debate the appropriateness and effect that particular donors have on the conclusions which are obtained from the method.
+This invites a robustness possibility in which the inclusion/exclusion of specific donors do not materially effect the decision that are obtained.
+
+\textcolor{red}{needs work} One hand, \cite{agarwal2020two} do not require such a parametric specification.
+On the other hand, the success of their approach is retrospective and its success is demonstrated in panel settings in which multiple donors are needed to inform hypothetical trajectories concerning the exact same shock.
 

### 2022-05-06 prevalence_testing/postshocktest2022draft.tex
minor edits; modified the math argument to include general loss functions

@@
 
-We now bound the difference in loss differential vectors $\|\dbf_{1,t} - \dbf_{i',t}\|$ for $t > T^*$ when we specify the loss $L(a,b) = |a-b|$.
+We now bound the difference in loss differential vectors $\|\dbf_{1,t} - \dbf_{i',t}\|$ for $t > T^*$. What we have showed so far in \eqref{bounds} and \eqref{forecastbounds} allows us to write
+\begin{equation} \label{L1bound}
+  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{1,h}_{i',t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{i',t}| + 2(\varepsilon_3 + \varepsilon_7).
+\end{equation}
+We conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$ where $\varepsilon_8$ is chosen so that \eqref{L1bound} holds when $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.
+%when we specify the loss $L(a,b) = |a-b|$.
 The loss differential vector $\dbf_{1,t} \in \R^H$ has elements $|y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}|$.
 What we have showed so far in \eqref{bounds} and \eqref{forecastbounds} allows us to write
-$$
-  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{i',h}_{1,t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{1,t}| + 2(\varepsilon_3 + \varepsilon_7).
-$$
-Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.
+%$$
+%  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{1,h}_{i',t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{i',t}| + 2(\varepsilon_3 + \varepsilon_7).
+%$$
+%Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.
 Putting this all together, we can pick $\varepsilon_8$ small enough so that for some fixed $\varepsilon > 0$,
@@
 As our methodology only requires $T_i-T_i^*$ is not small compared to $T_i$, we attempted three post-shock time length for our inference, say $L = 7, 15, 30$.
-Recall that in  Section \ref{forecast}, we refer to the forecast  that incorporates shock information as adjusted forecast and the one that does not as unadjusted forecast.
-As specified in Section \ref{forecast}, post-shock prevalence testing requires specification of  the maximum number $H$ of forecast horizons and training sample size $K$, where $h$-step forecasts of adjusted forecast and unadjusted forecast are compared for $h = 1, \ldots, H$.
+Recall that in  Section \ref{section2}, we refer to the forecast  that incorporates shock information as adjusted forecast and the one that does not as unadjusted forecast.
+As specified in Section \ref{section2}, post-shock prevalence testing requires specification of  the maximum number $H$ of forecast horizons and training sample size $K$, where $h$-step forecasts of adjusted forecast and unadjusted forecast are compared for $h = 1, \ldots, H$.
 We set $H = 10$, $K = 30$, and $T_i =  H + K + L+15$ for $i = 2, \ldots, 4$.
@@
 
-Recall from Section \ref{forecast}, voting procedure suggests shock transience (shock prevalence) if the majority of the tests  suggests shock transience (shock prevalence, respectively).
+Recall from Section \ref{section2}, voting procedure suggests shock transience (shock prevalence) if the majority of the tests  suggests shock transience (shock prevalence, respectively).
 We record 0 if the voting procedure suggests shock transience and 1 if shock prevalence.
@@
 %\end{table}
+
+\textcolor{red}{We now introduce a forecast scenarios \citep{baumeister2014real} approach to our prevalent testing framework.
+In \cite{lin2021minimizing} it was mentioned that Conoco Phillips possibly underwent a dual shock, which retrospectively, seems likely to be the case \citep{sharif2020covid}.
+In \cite{lin2021minimizing} the financial shocks and oil supply shocks were separated to form their own donor pools, the additive shock methodology was applied to each of these donor pools, and the results were added together.
+This approach did very well, almost perfectly recovering the yet-to-be post-shock response.
+We motivate a similar approach within our prevalence testing framework.
+The idea is to again separate out the financial and oil supply time series and add these series together.....
+}
 

### 2022-05-30 prevalence_testing/postshocktest2022draft.tex
changes to manuscript

@@
 $$
-where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed shock and is based on the information set $\mathcal{F}_{t-h}$ (\textcolor{red}{need to define}), and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.
+where $y^{1,h}_{i,t}$ is the forecast for $y_{i,t}$ that accounts for the yet-to-be observed shock and is based on the information set $\mathcal{F}_{t-h}$, and $\hat y^{2,h}_{i,t}$ is defined similarly for the forecast that does not include any shock effect information.
 %We are interested in point forecasts $y_{i,t}^h$ at multiple horizons, $h = 1, \ldots, H$ with the aim of determining whether the shock has an effect on $y_{i,t}^h$.
@@
  where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$.
-This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature (\textcolor{red}{either provide a citation or remove this sentence}).
 The $h$-step forecast corresponding to the model that does include any post-shock changes $\hat{y}_{i,t}^{2,h}$ is defined similarly,
@@
 $$
-  \dbf_{i,t} = \Llet_{i,t,1} - \Llet_{i,t,2},
+  \dbf_{i,t} =  \textcolor{red}{\Llet_{i,t,2} - \Llet_{i,t,1}},
 $$
@@
 
+\textcolor{red}{Define $\mbf{D}_i = (\mbf{d}_{i, T^*_i+H+1}', \ldots, \mbf{d}_{i, T_i}')$, which is the loss differential matrix of $i$th time series.
+Note that $\mbf{D}_i$ is of dimension $T_i-T^*_i - H$.
+$\mbf{D}_i$ compares $h$-step forecasts of $y_{i, t}$ for $t = T^* + H + 1$ to $t = T$ and $h= 1, \ldots, H$.
+In this design, adjusted and unadjusted forecasts are different with probability one such that elements of $\mbf{D}_i$ are different from zero with probability one.
+This prevents excessive zeroes to affect our inference results if $t = H+K +1,  \ldots, T$, where $K$ is the training sample size for parameter estimation of $h$-step forecasts.}
+
 We consider a simple test for average SPA, based on the weighted-average loss differential. The associated null is
@@
 %We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
-Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = lK_i$.
+Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = l\textcolor{red}{U_i}$.
 Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
@@
 \begin{equation} \label{whb}
-	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{K_i}\sum_{k=1}^{K_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
+	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{\textcolor{red}{U_i}}\sum_{k=1}^{\textcolor{red}{U_i}}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
 \end{equation}
@@
 	\bs{X}= \begin{pmatrix}
-		\bs{x}_{1, T_1^*+1} & \cdots & \bs{x}_{1, T_1^*-q_2+1}\\
-		\vdots &  \ddots & \vdots  \\
-		\bs{x}_{n+1, T_{n+1}^*+1} & \cdots & \bs{x}_{1, T_1^*-q_2+1}
+		\bs{x}_{1, T_1^*+1}  \\
+		\vdots   \\
+		\bs{x}_{n+1, T_{n+1}^*+1} 
 	\end{pmatrix}.
 \end{align*}
-The reason for including $\bs{x}_{i, T_i^*-q_2+1}$ is that the dynamic model \eqref{model-gen} considers lagged covariate values in its shock construction.
-Let $\mbf{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1.
+\textcolor{red}{In this paper, we consider this simple form of $\bs{X}$ for illustrative purpose.
+However,  more general $\bs{X}$'s are allowable.
+For example, $\bs{X}$ can also include $\bs{x}_{i, T_i^*-j+1}$ for $j = 2, \ldots, q_2$, which considers the lagged covariates in the dynamic model \eqref{model-gen}.} Let $\bs{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1.
 We compute the weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}.
@@
 
-We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool. \\
-
-\textcolor{red}{Jilei, I want you to just describe what the voting method is in plain writing as I have done above with the weighted average p-value. The propositions can then follow.} \\
-
-\textcolor{red}{Jilei, the algorithm needs to make explicit that a moving block bootstrap is performed.} \\
-
-\textcolor{red}{the algorithms are described in Algorithm \ref{voting}.
+We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool.
+\textcolor{red}{Given a significance level $\alpha$ and estimates $\{\hat{p}_i^B \colon i = 2, \ldots, n+1\}$, we compute the vote}
+\begin{align*}
+	V = I\Big\{\frac{1}{n} \sum_{i=2}^{n+1} I (\hat{p}_i^B\leq \alpha) \geq 0.5\Big\},
+\end{align*}
+\textcolor{red}{where $I(\cdot)$ is an indicator function.
+The idea of voting is very intuitive in the sense that donors vote for the shock persistence or transience  using a hypothesis testing approach and the one receiving more votes is returned.
+Second, the weighted voting generalizes this idea by making using of  the similarity weights $\mbf{W}^*$.
+It is defined as }
+\begin{align*}
+	V^* = I\Big\{ \sum_{i=2}^{n+1} w_i^* I (\hat{p}_i^B\leq \alpha) \geq 0.5\Big\}.
+\end{align*}
+
+\textcolor{red}{Algorithm \ref{Bu} describes the mechanics of computing $\mbf{W}^*, \hat{p}_1, V, V^*$ in more detail.
 There are a couple of details that are worth noting.
@@
 \begin{algorithm}
-\SetAlgoLined \label{voting}
+\SetAlgoLined
 
 \SetKwInOut{Input}{Input}
-\Input{$B, \ell $ --  bootstrap sample size, the  block size \textcolor{red}{Where is bootstrapping used in this algorithm?},   \\ 
+\Input{$B, \ell $ --  bootstrap sample size, the  block size  \\ 
 $\gamma$ -- bandwidth parameter in heteroskedasticity and autocorrelation  consistent covariance \\ 
@@
  		}
- 		Compute the squared error loss $l_{t,h}^1$ based on $y_{i, t}$
+ 		Compute the squared error loss \textcolor{red}{$l_{i,t,h, 1}$} based on $y_{i, t}$
  		 and $\hat{y}_{i,t}^{1, h}$\\
- 		 Compute the squared error loss $l_{t,h}^2$ based on $y_{i, t}$
+ 		 Compute the squared error loss \textcolor{red}{$l_{i,t,h, 2}$} based on $y_{i, t}$
  		 and $\hat{y}_{i,t}^{2, h}$
@@
  	}
- 	Construct the loss differential matrix with element $l_{t,h}^2-l_{t,h}^1$ at $t$th row and $h$th column \\
- 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix $\{l_{t,h}^2-l_{t,h}^1\}_{t,h}$ \textcolor{red}{please confirm that this is the same notation as before.} with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i$\\
+ 	Construct the loss differential matrix   with element \textcolor{red}{$l_{i,t,h, 2}-l_{i,t,h, 1}$} at $t$th row and $h$th column \\
+ 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix \textcolor{red}{$\{l_{i,t,h,2}-l_{i,t,h,1}\}_{t,h}$} with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i^B$, \textcolor{red}{where the test uses moving block bootstrap   with $B$ and $\gamma$.}\\
   }
@@
 
+\label{sec::ne}
+
 In this section, we illustrate shock prevalence testing using two real data examples.
@@
 where $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$ and $t = 1, \ldots, T_i$.
-Model $\mc{M}_0$ describes the setting where one additive shock effect is permanent (persistent) over time, and we will refer to it as the ``permanent" model (\textcolor{red}{should be ``persistent"?}).
+Model $\mc{M}_0$ describes the setting where one additive shock effect is permanent (persistent) over time, and we will refer to it as the ``persistent" model.
 The second model under consideration is  the ``dynamic'' model \eqref{model-gen} which is denoted $\mc{M}$ .
@@
 
-From the definition of $D_{i,t} = I(t > T_i^*+1)$, it is evident that the number of post-shock time points, i.e., time $t$ for which $t > T_i^*+1$, affects the inference results.
-As our methodology only requires $T_i-T_i^*$ is not small compared to $T_i$, we attempted three post-shock time length for our inference, say $L = 7, 15, 30$.
-Recall that in  Section \ref{section2}, we refer to the forecast  that incorporates shock information as adjusted forecast and the one that does not as unadjusted forecast.
-As specified in Section \ref{section2}, post-shock prevalence testing requires specification of  the maximum number $H$ of forecast horizons and training sample size $K$, where $h$-step forecasts of adjusted forecast and unadjusted forecast are compared for $h = 1, \ldots, H$.
-We set $H = 10$, $K = 30$, and $T_i =  H + K + L+15$ for $i = 2, \ldots, 4$.
-That being said, for $t = K + H + 1, \ldots, T_i$ and $h = 1, \ldots, H$, different $h$-step adjusted and unadjusted forecasts for $y_{i,t}$ under $\mc{M}_0$ or  $\mc{M}$ are compared.
+\textcolor{red}{Regarding the hyper-parameters, in this data example, we set $T_i- T_i^* = 30$ and $K = 30$.
+Note that $K = 30$ is a sensible  training sample size, see discussions for example in  \cite{lin2021minimizing}.
+Also, $T_i-T_i^*-H$ corresponds to the post-shock time length that analysts are interested in predicting whether the impact of the shock persists.
+We set $T_i- T_i^* = 30$  in order to make the post-shock time length moderately large and also for illustration purpose.
+For sensitivity analysis, we implemented the analysis for different  $H= 2, 4, 6, 8$.}
+
+\textcolor{red}{We summarize our numerical results in Table \ref{coptable}.
+In the Table \ref{coptable}, $p_1$ stands for the forecast comparison test of \cite{quaedvlieg2021multi} applied for adjusted and unadjusted forecasts on the time series of interest.
+Note that in practice, it cannot be computed because  $y_{1, t}$ for $t > T_1^*$ is not observed.
+It is provided   for retrospective  analysis.
+Second, $\hat{p}_1$ is the  estimate for $p_1$ using $\mbf{W}^*$.
+We recorded the voting and weighted voting results in the form of indicators with one being voting for persistence and zero for transience.
+See the methodological details for $\hat{p}_1$, voting, and weighted voting in Section \ref{sec:multhor}.
+In companion with the voting, the correctness of the voting is evaluated and provided  in the brackets.
+For example, ``0 (Yes)'' implies  that the procedure votes for transience and this decision is correct whereas ``1 (No)'' votes for persistence and it is incorrect.
+}
 
@@
   \begin{tabular}{cccccccccr}
-     $L$  & Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$ & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
+     $H$  & Model &   $p_1$ & $\hat{p}_1$ & $|\hat{p}_1-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
      \hline 
-     7 & $\mc{M}_0$  & \multirow{2}{*}{$0.817$} & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
-     7 & $\mc{M}$  &  & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     15 & $\mc{M}_0$ & \multirow{2}{*}{$0.817$}  & 1   & $0.817$ & 0 (Yes) &1 (No)    \\
-     15 &  $\mc{M}$ & & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
-     30 &  $\mc{M}_0$ & \multirow{2}{*}{$1$}  & 1   & $0.817$ & 0 (Yes) &1 (No)   \\
-     30 &  $\mc{M}$ &  & 1  & 0 &0 (Yes) & 0 (Yes)  
+     \multirow{2}{*}{2} & $\mc{M}_0$  &   1 & 0.183  & 0.817 & 0 (Yes) & 1 (No)  \\      
+      & $\mc{M}$  & 1 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     \multirow{2}{*}{4} & $\mc{M}_0$ &   0 & 0.519  & $0.519$ & 0 (No) &1 (No)    \\
+      &  $\mc{M}$ & 1& 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
+     \multirow{2}{*}{6} &  $\mc{M}_0$ &   0   & $0.817$ & 0.817 & 0 (No) &1 (No)   \\
+      &  $\mc{M}$ & 1 & 1  & 0 &0 (Yes) & 0 (Yes) \\[.2cm]
+     \multirow{2}{*}{8} & $\mc{M}_0$ & 0  & 0.817 & 0.817 & 0 (No) & 0 (No)\\
+     & $\mc{M}$ & 1 & 1 & 0 & 0 (Yes) & 0 (Yes)
   \end{tabular}
@@
 
-We implemented our analysis of the Conoco Phillips dataset and summarized the results in Table \ref{coptable}. We discuss our finding in several parts as follows.
-
-Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$.
+\textcolor{red}{Next, we discuss our numerical results.} Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$.
 It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second.
@@
 
-In term of Table \ref{coptable}, it is important to note that $p_1$ is the $p$-value of the forecast comparison between adjusted forecast and unadjusted forecast if we have the data $\{y_{1,t} \colon 1, \ldots, T_1\}$, where $T_1 > T_1^*$.
-In other words, it cannot be computed without observing $y_{1, t}$ for $t > T_1^*$ and we present $p_1$ only for retrospective analysis.
-Also, $\hat{p}$ is the $p$-value from weighting the $p$-values of the forecast comparison  between adjusted and unadjusted forecast for donors using $\mbf{W}^*$.
-
 Let $a_i^1$ and $a_i^2$ denote the AICs of $\mc{M}_0$ and $\mc{M}$ for $i$th time series, respectively.
-Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, as  $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)>0.5$ for $L = 7, 15, 30$, we conclude that $\mc{M}$ is preferred over $\mc{M}_0$.
-Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and $\mc{M}$.
-The test  using $\hat{p}$ with $\mc{M}$ fails to reject that  the shock, which was to take effect at $t=T_1^*+1$,  is prevalent for $t > T_1^*+1$ under a significance level of 5\%.
-Nevertheless, the results appear to be a little different for $\mc{M}_0$.
-For $L=7$, $|\hat{p}-p_1|=0$ for $\mc{M}_0$ whereas $|\hat{p}-p_1|=0.82$ for $L = 15, 30$.
-Based on the performance of $\mc{M}$, it is possible that as the time window $L$ increases, the signal from changing parameters covariates is ``misunderstood'' by $\mc{M}_0$ as shock signal.
-
-Recall from Section \ref{section2}, voting procedure suggests shock transience (shock prevalence) if the majority of the tests  suggests shock transience (shock prevalence, respectively).
-We record 0 if the voting procedure suggests shock transience and 1 if shock prevalence.
-The weighted voting procedure weight those testing indicators using $\mbf{W}^*$; and returns shock prevalence if the output exceeds 0.5 and shock transience if the output is smaller than 0.5.
-As we observe $\{y_{1,t} \colon 1, \ldots, T_1\}$, we are able to check whether the decision of voting and weighted voting is correct.
-From the sixth column of Table \ref{coptable}, we can see that voting procedure suggests shock transience for $\mc{M}_0$ and $\mc{M}$ for different $L$.
-However, weighted voting suggests shock transience for $\mc{M}$ for different $L$ but shock prevalence for $\mc{M}_0$ and $L=15, 30$ and shock transience for $\mc{M}_0$ and $L = 7$.
-As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small.
-Note that Proposition \ref{votprop} and Corollary \ref{coro2} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$.
-Note that the interpretation and meaning of $p_1$ is closely connected with models.
-For example, $\mc{M}_0$ would imply a persistent shock whereas $\mc{M}$ is more general in suggesting changing dynamics.
-Thus, even if  this theoretical statement  may be correct, it makes practical sense only when model is identified well.
-This comment corresponds to the possibility that $\mc{M}_0$ may ``misunderstand'' the wrong signal of changing dynamics that are instead captured by $\mc{M}$.
-
-To verify our results, we plot $\{y_{1,t} \colon 1, \ldots, T_1\}$ in Figure \ref{copshocktransience}.
+\textcolor{red}{Based on \ref{model-gen}, which describes $\mc{M}$ and the description of $\mc{M}$ in the beginning of Section \ref{sec::ne}, it may be inferred that $\mc{M}$ captures the post-shock dynamic change whereas $\mc{M}_0$ suggests a persistent post-shock additive location shift.} Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, \textcolor{red}{it turns out that $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=1 >0.5$.
+Using this aggregated model selection approach, we prefer $\mc{M}$ over $\mc{M}_0$.}
+
+\textcolor{red}{From Table \ref{coptable}, we can see that $p_1$ for $\mc{M}$ is not sensitive to the changes of $H$ and is uniformly 1.
+Under any reasonable significance level, based on the features of $\mc{M}$, we infer that post-shock dynamics do not differ from the pre-shock one and the shock is not persistent.
+In contrast, $p_1$ of $\mc{M}_0$ equals 1 for $H = 2$ whereas equals 0 for $H = 4, 6, 8$.
+It is possible that $\mc{M}_0$ does not fit the data well.
+In practice, a simple additive post-shock location-shift is rare and more complicated structures cannot be explained using this.
+To support this claim, we plotted $\{y_{1,t} \colon 1, \ldots, T_1\}$ in Figure \ref{copshocktransience}.}
+
 Two dashed vertical lines are plotted in Figure \ref{copshocktransience}, where the left one corresponds to $t = T_1^*$ and the right one  corresponds to $t = T_1^*+1$.
@@
 However, notice that even if $y_{1,t}$ first experienced a considerable drop at $t = T_1^*+1$,   it started to revert back and became closer to the benchmark horizontal line as $t$ increases for $t > T_1^*$.
-This observation confirms our results as the reverting behavior implies that the impact of the shock starts to diminish as $t$ increases and that the shock is very likely to be transient.
+\textcolor{red}{Note that this observation confirms our model selection and what $\mc{M}$ suggests for shock transience.
+It is also important to re-emphasize that  the test compares the forecasts from $t = T_1^* + H+1$ to $t=T_1$.
+In other words, the beginning dramatic drop as seen from Figure \ref{copshocktransience} around March is not considered in the forecast comparison.
+It is reasonable to our objective as we are interested in long-term persistence rather-than short-term substantial changes.
+It is   possible that the significance of $\mc{M}_0$ for $H = 2$ takes into account the short-term percussions of the substantial shock.
+It is because (1) for small $H$, the loss differential matrix   incorporates some large loss differential elements corresponding to $t$ close to $T^*_1+1$ and (2) $\mc{M}_0$ can be very sensitive to substantial additive location shift around $t = T^*_1+1$.
+And this phenomenon disappears as $H$ increases.}
 
@@
 \end{figure}
+
+\textcolor{red}{Next, we discuss the performance of $\hat{p}_1$, voting and weighted voting.
+From Table \ref{coptable},  we can observe that $|\hat{p}_1-p_1|$ equals zero uniformly for $\mc{M}$ and $H = 2, 4, 6, 8$.
+It suggests that $\hat{p}_1$ under $\mc{M}$ serves as a favorable proxy for $p_1$ under $\mc{M}$.
+In contrast, $|\hat{p}_1-p_1|$ is quite large for $\mc{M}_0$ and different $H$.
+It is possible that $\mc{M}_0$  does not fit the data properly or the donors are not representative of the time series of interest in the context of $\mc{M}_0$.
+Here, it is important to note that  the comparability between donors and the time series of interest is model-dependent.}
+
+\textcolor{red}{According to the last two columns of \ref{coptable}, the decisions yielded by voting and weighted voting are correct for $\mc{M}$ and $H = 2, 4, 6, 8$.
+However, the decisions for voting and weighted voting are incorrect for $\mc{M}_0$ and $H=2, 4, 6, 8$ except for voting for $\mc{M}_0$ at $H = 2$.
+The interpretations for this are similar to those when we analyze $|\hat{p}_1-p_1|$.
+Note that the decisions using $\hat{p}_1$ and weighted voting are similar.
+It is reasonable as they are functions of $\mbf{W}^*$.
+Because $p_1$ is uniformly 1 for $\mc{M}$, it is reasonable to expect $\P(p_1\leq .05)$ be small.
+Note that Proposition \ref{votprop} and Corollary \ref{coro2} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$.}
 
@@
   \begin{tabular}{cccccccccr}
-   $L$  &  Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$  & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
+     $H$  & Model &   $p_1$ & $\hat{p}_1$ & $|\hat{p}_1-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
      \hline 
-     \multirow{2}{*}{ $3$} &  $\mc{M}_0$  & \multirow{2}{*}{ 0}& 1  & 0 & 0 (Yes) &0 (Yes)  \\      
-      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.070 & $0.179$   & 0 (Yes) &1 (No)   \\[.2cm]
-     \multirow{2}{*}{ $6$} &  $\mc{M}_0$  & \multirow{2}{*}{ 0}& 1  & 0 & 0 (Yes) &0 (Yes)  \\      
-      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.265 & $0.498$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-  \multirow{2}{*}{ $12$} &  $\mc{M}_0$  & \multirow{2}{*}{0.722}& 0  & 1 & 1 (No) &1 (No)  \\      
-      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-       \multirow{2}{*}{ $18$} &  $\mc{M}_0$  & \multirow{2}{*}{0}& 0.670  & 0.330 & 0 (Yes) & 0 (Yes)  \\      
-      & $\mc{M}$ ($q_1=q_2=1$)  & & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     \multirow{2}{*}{2} & $\mc{M}_0$  &   0.190 & 0.436  & 0.246 & 0 (Yes) & 0 (Yes)\\      
+      & $\mc{M}$  & 0.520 & 0.556 & $0.036$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     \multirow{2}{*}{3} & $\mc{M}_0$ &   0.140 & 0.413  & $0.273$ & 0 (Yes) & 0 (Yes)    \\
+      &  $\mc{M}$ & 0.495 & 0.656 & 0.161 & 0 (Yes) & 0 (Yes)  \\[.2cm]
+     \multirow{2}{*}{4} &  $\mc{M}_0$ &   0.275   & $0.464$ & 0.189 & 0 (Yes) & 0 (Yes)  \\
+      &  $\mc{M}$ & 0.350 & 0.559  & 0.209 & 0 (Yes) & 0 (Yes) \\[.2cm]
+     \multirow{2}{*}{5} & $\mc{M}_0$ & 0.380  & 0.275 & 0.105 & 0 (Yes) & 0 (Yes)\\
+     & $\mc{M}$ & 0.665 & 0.763 & 0.098 & 0 (Yes) & 0 (Yes)
   \end{tabular}
@@
 \end{table}
+
+$\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=0.722$
 
@@
 \label{simulation}
+
+\begin{align*}
+	\phi_{i,j}, \theta_{i,j}  & \simiid U(0,1) \\ 
+	\delta_{i,j} & \simiid N(1,0.5^2) \\
+	\alpha_i & \simiid N(10, 2) \\
+	T_i^* & \simiid \min\Big(90, \big[Gamma(15,10)\big]\Big) \\
+	\varepsilon_{i,t} & \simiid N(0,1)\\
+	X_{i,j} & \simiid Gamma(1,2) \\
+	\tilde{\theta}_{i,j},\tilde{\phi}_{i,j} & \simiid Beta(\|\mbf{x}_{i,T_i^*+1}\|,1)
+\end{align*}
+Vary $L = 14, 30, 45,60$.
 

### 2022-05-30 prevalence_testing/numerical_studies/emsda.R

@@ -188,7 +188,7 @@ ols.est.alphahat <- function(Tstar, Y, X) {
 
 # functions that return alpha.hat and synthetic weights
 ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, 
-                                 sig.levl = .05, q1, 
+                                 sig.levl = .05, q1, subset = FALSE, 
                                  retro = TRUE, selfW = NA, scale = FALSE) {
   
   n <- length(Y) - 1
@@ -241,8 +241,8 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw,
         yhat.unadj <- Y[[i]][(t + Ki + H - h + 1 - q1):(t + Ki + H - h)]
         
         for (j in 1:h) {
-          yhat.adj.h <- matrix(c(1, ifelse(t + Ki + H - h + j >= Tstari + 1, yes = 1, no = 0),
-                                 yhat.adj[j:(j + q1 - 1)], X[[i]][-(1:q1), ][t + Ki + H - h + j, ]))
+          yhat.adj.h <- beta.hat.adj %*% matrix(c(1, ifelse(t + Ki + H - h + j >= Tstari + 1, yes = 1, no = 0),
+                                                  yhat.adj[j:(j + q1 - 1)], X[[i]][-(1:q1), ][t + Ki + H - h + j, ]))
           yhat.unadj.h <- beta.hat.unadj %*% matrix(c(1, yhat.adj[j:(j + q1 - 1)], X[[i]][-(1:q1), ][t + Ki + H - h + j, ]))
           
           if (t + Ki + H - h == Tstari & i >= 3 & h == 1) {
@@ -260,7 +260,13 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw,
     }
     # loss differential
     d <- m2.L.i - m1.L.i
-    ps[i] <- taSPA.mhfc(ell = ell, d = d, B = B, bw = bw)
+    if (subset == FALSE) {
+      ps[i] <- taSPA.mhfc(ell = ell, d = d, B = B, bw = bw) 
+    } else {
+      sub.index <- (Ti - Ki - q1 - (Ti - Tstari) + H + 1):(Ti - Ki - H - q1)
+      d.subset <- d[sub.index,  ]
[…]

### 2022-05-31 prevalence_testing/postshocktest2022draft.tex
edited manuscript

@@
 
-\textcolor{red}{This needs work} The core idea of our methodology is to first form a donor pool of time series that have undergone similar shocks, then perform the multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi}  with respect to each of these donors to determine whether the shock is prevalent or transient, and then aggregate the decisions from the donors to make a final decision of transience or prevalence for the time series under study for which no post-shock observations are observed.
+The core idea of our methodology is to first form a donor pool of time series that have undergone similar shocks, then perform the multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi}  with respect to each of these donors to determine whether the shock is prevalent or transient, and then aggregate the decisions from the donors to make a final decision of transience or prevalence for the time series under study for which no post-shock observations are observed.
 The multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi} is a natural  extension of \cite{diebold1995comparing}.
@@
 The parameterization that we use states that the post-shock dynamics are determined in part by observed covariates collected right before the first post-shock response is observed.
-Such a parameterization will not be known in practice.
+%Such a parameterization will not be known in practice.
 That being said, one can demonstrate the effectiveness and appropriateness of such a parameterization via a leave one out cross validation approach applied to the donor pool in which all post-shock information is observed \textcolor{red}{need LOOCV approach}.
@@
 $$
-  \dbf_{i,t} =  \textcolor{red}{\Llet_{i,t,2} - \Llet_{i,t,1}},
+  \dbf_{i,t} =  \Llet_{i,t,2} - \Llet_{i,t,1},
 $$
@@
 
-\textcolor{red}{Define $\mbf{D}_i = (\mbf{d}_{i, T^*_i+H+1}', \ldots, \mbf{d}_{i, T_i}')$, which is the loss differential matrix of $i$th time series.
+Define $\mbf{D}_i = (\mbf{d}_{i, T^*_i+H+1}', \ldots, \mbf{d}_{i, T_i}')$, which is the loss differential matrix of $i$th time series.
 Note that $\mbf{D}_i$ is of dimension $T_i-T^*_i - H$.
@@
 In this design, adjusted and unadjusted forecasts are different with probability one such that elements of $\mbf{D}_i$ are different from zero with probability one.
-This prevents excessive zeroes to affect our inference results if $t = H+K +1,  \ldots, T$, where $K$ is the training sample size for parameter estimation of $h$-step forecasts.}
+This prevents excessive zeroes to affect our inference results if $t = H+K +1,  \ldots, T$, where $K$ is the training sample size for parameter estimation of $h$-step forecasts.
 
@@
 %We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
-Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = l\textcolor{red}{U_i}$.
+Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = lU_i$.
 Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array
@@
 \begin{equation} \label{whb}
-	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{\textcolor{red}{U_i}}\sum_{k=1}^{\textcolor{red}{U_i}}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
+	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{U_i}\sum_{k=1}^{U_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
 \end{equation}
@@
 	\bs{X}= \begin{pmatrix}
-		\bs{x}_{1, T_1^*+1}  \\
+		\bs{x}_{2, T_2^*+1}'  \\
 		\vdots   \\
-		\bs{x}_{n+1, T_{n+1}^*+1} 
+		\bs{x}_{n+1, T_{n+1}^*+1}' 
 	\end{pmatrix}.
 \end{align*}
-\textcolor{red}{In this paper, we consider this simple form of $\bs{X}$ for illustrative purpose.
+In this paper, we consider this simple form of $\bs{X}$ for illustrative purpose.
 However,  more general $\bs{X}$'s are allowable.
-For example, $\bs{X}$ can also include $\bs{x}_{i, T_i^*-j+1}$ for $j = 2, \ldots, q_2$, which considers the lagged covariates in the dynamic model \eqref{model-gen}.} Let $\bs{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1.
+For example, $\bs{X}$ can also include $\bs{x}_{i, T_i^*-j+1}$ for $j = 2, \ldots, q_2$, which considers the lagged covariates in the dynamic model \eqref{model-gen}.
+Let $\bs{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1.
 We compute the weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}.
@@
 
-We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool.
-\textcolor{red}{Given a significance level $\alpha$ and estimates $\{\hat{p}_i^B \colon i = 2, \ldots, n+1\}$, we compute the vote}
+\textcolor{red}{Need to make a decision about voting and weighted voting; not sure if it is more robust or efficient than the weighted p-value approach.
+If it is not superior than the weighted approach in any way then we should remove it.} We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool.
+Given a significance level $\alpha$ and estimates $\{\hat{p}_i^B \colon i = 2, \ldots, n+1\}$, we compute the vote
 \begin{align*}
@@
 \end{align*}
-\textcolor{red}{where $I(\cdot)$ is an indicator function.
+where $I(\cdot)$ is an indicator function.
 The idea of voting is very intuitive in the sense that donors vote for the shock persistence or transience  using a hypothesis testing approach and the one receiving more votes is returned.
 Second, the weighted voting generalizes this idea by making using of  the similarity weights $\mbf{W}^*$.
-It is defined as }
+It is defined as
 \begin{align*}
@@
 
-\textcolor{red}{Algorithm \ref{Bu} describes the mechanics of computing $\mbf{W}^*, \hat{p}_1, V, V^*$ in more detail.
+Algorithm \ref{Bu} describes the mechanics of computing $\mbf{W}^*, \hat{p}_1, V, V^*$ in more detail.
 There are a couple of details that are worth noting.
@@
 It is because the framework of \cite{quaedvlieg2021multi} needs training sample, which implicitly requires users to feed the algorithm with moderately large dataset for a more credible analysis.
-}
 
@@
  		}
- 		Compute the squared error loss \textcolor{red}{$l_{i,t,h, 1}$} based on $y_{i, t}$
+ 		Compute the squared error loss $l_{i,t,h, 1}$ based on $y_{i, t}$
  		 and $\hat{y}_{i,t}^{1, h}$\\
- 		 Compute the squared error loss \textcolor{red}{$l_{i,t,h, 2}$} based on $y_{i, t}$
+ 		 Compute the squared error loss $l_{i,t,h, 2}$ based on $y_{i, t}$
  		 and $\hat{y}_{i,t}^{2, h}$
@@
  	}
- 	Construct the loss differential matrix   with element \textcolor{red}{$l_{i,t,h, 2}-l_{i,t,h, 1}$} at $t$th row and $h$th column \\
- 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix \textcolor{red}{$\{l_{i,t,h,2}-l_{i,t,h,1}\}_{t,h}$} with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i^B$, \textcolor{red}{where the test uses moving block bootstrap   with $B$ and $\gamma$.}\\
+ 	Construct the loss differential matrix   with element $l_{i,t,h, 2}-l_{i,t,h, 1}$ at $t$th row and $h$th column \\
+ 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix $\{l_{i,t,h,2}-l_{i,t,h,1}\}_{t,h}$ with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i^B$, where the test uses moving block bootstrap   with $B$ and $\gamma$.\\
   }
@@
 
-\textcolor{red}{Regarding the hyper-parameters, in this data example, we set $T_i- T_i^* = 30$ and $K = 30$.
+In this data example we set $T_i- T_i^* = 30$ and $K = 30$.
 Note that $K = 30$ is a sensible  training sample size, see discussions for example in  \cite{lin2021minimizing}.
-Also, $T_i-T_i^*-H$ corresponds to the post-shock time length that analysts are interested in predicting whether the impact of the shock persists.
+The quantity $T_i-T_i^*-H$ corresponds to the post-shock time length that analysts are interested in predicting whether the impact of the shock persists.
 We set $T_i- T_i^* = 30$  in order to make the post-shock time length moderately large and also for illustration purpose.
-For sensitivity analysis, we implemented the analysis for different  $H= 2, 4, 6, 8$.}
-
-\textcolor{red}{We summarize our numerical results in Table \ref{coptable}.
+For sensitivity analysis, we implemented the analysis for different  $H= 2, 4, 6, 8$.
+
+We summarize our numerical results in Table \ref{coptable}.
 In the Table \ref{coptable}, $p_1$ stands for the forecast comparison test of \cite{quaedvlieg2021multi} applied for adjusted and unadjusted forecasts on the time series of interest.
@@
 For example, ``0 (Yes)'' implies  that the procedure votes for transience and this decision is correct whereas ``1 (No)'' votes for persistence and it is incorrect.
-}
 
@@
 
-\textcolor{red}{Next, we discuss our numerical results.} Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$.
+We now discuss the numerical results.
+Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$.
 It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second.
@@
 Let $a_i^1$ and $a_i^2$ denote the AICs of $\mc{M}_0$ and $\mc{M}$ for $i$th time series, respectively.
-\textcolor{red}{Based on \ref{model-gen}, which describes $\mc{M}$ and the description of $\mc{M}$ in the beginning of Section \ref{sec::ne}, it may be inferred that $\mc{M}$ captures the post-shock dynamic change whereas $\mc{M}_0$ suggests a persistent post-shock additive location shift.} Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, \textcolor{red}{it turns out that $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=1 >0.5$.
-Using this aggregated model selection approach, we prefer $\mc{M}$ over $\mc{M}_0$.}
-
-\textcolor{red}{From Table \ref{coptable}, we can see that $p_1$ for $\mc{M}$ is not sensitive to the changes of $H$ and is uniformly 1.
+Based on \eqref{model-gen}, which describes $\mc{M}$ and the description of $\mc{M}$ in the beginning of Section \ref{sec::ne}, it may be inferred that $\mc{M}$ captures the post-shock dynamic change whereas $\mc{M}_0$ suggests a persistent post-shock additive location shift.
+Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, it turns out that $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=1 >0.5$.
+Using this aggregated model selection approach, we prefer $\mc{M}$ over $\mc{M}_0$.
+\textcolor{red}{Add column for AIC results}
+
+From Table \ref{coptable}, we can see that $p_1$ for $\mc{M}$ is not sensitive to the changes of $H$ and is uniformly 1.
 Under any reasonable significance level, based on the features of $\mc{M}$, we infer that post-shock dynamics do not differ from the pre-shock one and the shock is not persistent.
@@
 In practice, a simple additive post-shock location-shift is rare and more complicated structures cannot be explained using this.
-To support this claim, we plotted $\{y_{1,t} \colon 1, \ldots, T_1\}$ in Figure \ref{copshocktransience}.}
+To support this claim, we plotted $\{y_{1,t} \colon 1, \ldots, T_1\}$ in Figure \ref{copshocktransience}.
 
@@
 However, notice that even if $y_{1,t}$ first experienced a considerable drop at $t = T_1^*+1$,   it started to revert back and became closer to the benchmark horizontal line as $t$ increases for $t > T_1^*$.
-\textcolor{red}{Note that this observation confirms our model selection and what $\mc{M}$ suggests for shock transience.
+Note that this observation confirms our model selection and what $\mc{M}$ suggests for shock transience.
 It is also important to re-emphasize that  the test compares the forecasts from $t = T_1^* + H+1$ to $t=T_1$.
@@
 It is because (1) for small $H$, the loss differential matrix incorporates some large loss differential elements corresponding to $t$ close to $T^*_1+1$ and (2) $\mc{M}_0$ can be very sensitive to substantial additive location shift around $t = T^*_1+1$.
-And this phenomenon disappears as $H$ increases.}
+And this phenomenon disappears as $H$ increases.
 
@@
 
-\textcolor{red}{Next, we discuss the performance of $\hat{p}_1$, voting and weighted voting.
+Next, we discuss the performance of $\hat{p}_1$, voting and weighted voting.
 From Table \ref{coptable},  we can observe that $|\hat{p}_1-p_1|$ equals zero uniformly for $\mc{M}$ and $H = 2, 4, 6, 8$.
@@
 It is possible that $\mc{M}_0$  does not fit the data properly or the donors are not representative of the time series of interest in the context of $\mc{M}_0$.
-Here, it is important to note that  the comparability between donors and the time series of interest is model-dependent.}
-
-\textcolor{red}{According to the last two columns of \ref{coptable}, the decisions yielded by voting and weighted voting are correct for $\mc{M}$ and $H = 2, 4, 6, 8$.
+Here, it is important to note that  the comparability between donors and the time series of interest is model-dependent.
+
+\textcolor{red}{According to the last two columns of Table \ref{coptable}, the decisions yielded by voting and weighted voting are correct for $\mc{M}$ and $H = 2, 4, 6, 8$.
 However, the decisions for voting and weighted voting are incorrect for $\mc{M}_0$ and $H=2, 4, 6, 8$ except for voting for $\mc{M}_0$ at $H = 2$.

### 2022-06-03 prevalence_testing/postshocktest2022draft.tex
added dual shock model

@@
 
+\vspace*{0.5cm}\noindent\textbf{Note}\vspace*{0.5cm}
+
 \textcolor{red}{We now introduce a forecast scenarios \citep{baumeister2014real} approach to our prevalent testing framework.
 In \cite{lin2021minimizing} it was mentioned that Conoco Phillips possibly underwent a dual shock, which retrospectively, seems likely to be the case \citep{sharif2020covid}.
-In \cite{lin2021minimizing} the financial shocks and oil supply shocks were separated to form their own donor pools, the additive shock methodology was applied to each of these donor pools, and the results were added together.
-This approach did very well, almost perfectly recovering the yet-to-be post-shock response.
-We motivate a similar approach within our prevalence testing framework.
-The idea is to again separate out the financial and oil supply time series and add these series together.....
-}
+There were also rumblings of a dual shock in real time \citep{fitch2020oil, stevens2020oil, westbrook2020forex}.
+In \cite{lin2021minimizing} a dual shock formulation was provided in which supposed financial shocks and oil supply shocks were separated to form their own donor pools, the additive shock methodology was applied to each of these donor pools, and the results were added together.
+This approach did very well, almost perfectly recovering the yet-to-be post-shock response.}
+
+\textcolor{red}{We motivate a similar approach within our prevalence testing framework.
+The idea is to again separate out the financial and oil supply time series and add these series together which will create a new donor pool consisting of series which incorporate a dual shock whose behavior can be assessed with our methodology.
+As in \cite{lin2021minimizing} the oil supply shock donor pool consists of the single November 27, 2014 series; and the financial shock donor pool consists of the remaining two series.
+These added series which account for a potential dual shock take the following form where the subscript $o$ refers to the single November 27, 2014, the subscript $j$ indexes the other series, and $T_o = T_j$ and $T^*_o = T^*_j$}
+\begin{equation} \label{eq:dualshock}
+\begin{split}
+  z_{j,t} &= y_{o,t} + y_{j,t} \\
+  	&= \bar{\eta}_j + (\phi_o y_{o,t-1} +\theta_{o,t-1}'\x_{o,t-1} + \phi_j y_{j,t-1} +\theta_{j,t-1}'\x_{j,t-1})(1 - \bar{D}_t) \\
+  	&\qquad + (\bar{\alpha}_j + \tilde{\phi}_o y_{o,t-1} + \tilde{\theta}_{o,t-1}'\x_{o,t-1} + \tilde{\phi}_j y_{j,t-1} + \tilde{\theta}_{j,t-1}'\x_{j,t-1})\bar{D}_t + \bar{\varepsilon}_t,
+\end{split}
+\end{equation}
+where $\bar{\eta}_j = \eta_o + \eta_j$, $\bar{\alpha}_j = \alpha_o + \alpha_j$, $D_t = D_{0,t} = D_{j,t}$, and $\bar{\varepsilon}_t = \varepsilon_{0,t} + \varepsilon_{j,t} + D_t(\varepsilon_{\alpha,o} + \varepsilon_{\alpha,j})$.
+The model \eqref{eq:dualshock} is then a regression model with a heterogeneous error structure, the error distribution post-shock differs from the error distribution pre-shock.
+All model parameters are estimable in \eqref{eq:dualshock}.
+However, aggregation strategies are slightly different for this model since covariates are included for two separate series.
+
+We now examine distance-based weighting for model \eqref{eq:dualshock}.
+Consider a weight vector $\textbf{W}^d \in \R^{n-1}$ with elements $w_i \in [0,1]$ that satisfy $\sum_i w_i = 1$.
+Construct $\X_1^d = (\x_{1,T^*_1+1}', \; \x_{1,T^*_1+1}')$, $\X^d \in \R^{n-1 \times 2p}$ with rows $(\x_{o,T^*_o+1}', \; \x_{j,T^*_j+1}')$, and $\hat{\X}_1^d(\textbf{W}) = \textbf{W}^{d'}\X^d$.
+Then the optimal weights satisfy
+$$
+  \textbf{W}^{d*} = \text{arg min}_{\textbf{W} \in \mathcal{W}} \|\X_1^d - \hat{\X}_1^d(\textbf{W})\|_{2p}
+$$
+where $\mathcal{W}$ is the set of all allowable weight vectors.
 

### 2022-06-11 prevalence_testing/postshocktest2022draft.tex
revision to numerical results

@@
 \begin{table}[H]
-	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.183, 0, 0.817)$ from scaled covariates} \label{coptable}
+	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.221, 0, 0.779)$ from scaled covariates} \label{coptable}
 \begin{center}
@@
      \hline 
-     \multirow{2}{*}{2} & $\mc{M}_0$  &   1 & 0.183  & 0.817 & 0 (Yes) & 1 (No)  \\      
+     \multirow{2}{*}{2} & $\mc{M}_0$  &   1 & 0.225  & 0.775 & 0 (Yes) & 1 (No)  \\      
       & $\mc{M}$  & 1 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     \multirow{2}{*}{4} & $\mc{M}_0$ &   0 & 0.519  & $0.519$ & 0 (No) &1 (No)    \\
+     \multirow{2}{*}{4} & $\mc{M}_0$ &   0 & 0.953  & $0.953$ & 0 (No) &0 (No)    \\
       &  $\mc{M}$ & 1& 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
-     \multirow{2}{*}{6} &  $\mc{M}_0$ &   0   & $0.817$ & 0.817 & 0 (No) &1 (No)   \\
+     \multirow{2}{*}{6} &  $\mc{M}_0$ &   0   & $1$ & 1 & 0 (No) &0 (No)   \\
       &  $\mc{M}$ & 1 & 1  & 0 &0 (Yes) & 0 (Yes) \\[.2cm]
-     \multirow{2}{*}{8} & $\mc{M}_0$ & 0  & 0.817 & 0.817 & 0 (No) & 0 (No)\\
+     \multirow{2}{*}{8} & $\mc{M}_0$ & 0  & 1 & 1 & 0 (No) & 0 (No)\\
      & $\mc{M}$ & 1 & 1 & 0 & 0 (Yes) & 0 (Yes)
@@
 We now discuss the numerical results.
-Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$.
+Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.221, 0, 0.779)$.
 It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second.
@@
 Using this aggregated model selection approach, we prefer $\mc{M}$ over $\mc{M}_0$.
-\textcolor{red}{Add column for AIC results}
+\textcolor{red}{For reference, the AICs for $\mc{M}_0$ in the donors are $(297.410, 413.357, 295.174)$ whereas those for $\mc{M}$ in the donors are $(302.835, 409.544, 280.609)$.
+}
 
@@
 In practice, a simple additive post-shock location-shift is rare and more complicated structures cannot be explained using this.
-To support this claim, we plotted $\{y_{1,t} \colon 1, \ldots, T_1\}$ in Figure \ref{copshocktransience}.
 
@@
 It is reasonable to our objective as we are interested in long-term persistence rather-than short-term substantial changes.
-It is   possible that the significance of $\mc{M}_0$ for $H = 2$ takes into account the short-term percussions of the substantial shock.
-It is because (1) for small $H$, the loss differential matrix incorporates some large loss differential elements corresponding to $t$ close to $T^*_1+1$ and (2) $\mc{M}_0$ can be very sensitive to substantial additive location shift around $t = T^*_1+1$.
-And this phenomenon disappears as $H$ increases.
 
@@
   z_{j,t} &= y_{o,t} + y_{j,t} \\
-  	&= \bar{\eta}_j + (\phi_o y_{o,t-1} +\theta_{o,t-1}'\x_{o,t-1} + \phi_j y_{j,t-1} +\theta_{j,t-1}'\x_{j,t-1})(1 - \bar{D}_t) \\
-  	&\qquad + (\bar{\alpha}_j + \tilde{\phi}_o y_{o,t-1} + \tilde{\theta}_{o,t-1}'\x_{o,t-1} + \tilde{\phi}_j y_{j,t-1} + \tilde{\theta}_{j,t-1}'\x_{j,t-1})\bar{D}_t + \bar{\varepsilon}_t,
+  	&= \bar{\eta}_j + (\phi z_{j,t-1} +\theta_{o,t-1}'\x_{o,t-1} +\theta_{j,t-1}'\x_{j,t-1})(1 - \bar{D}_t) \\
+  	&\qquad + (\bar{\alpha}_j + \tilde{\phi} z_{j,t-1} + \tilde{\theta}_{o,t-1}'\x_{o,t-1}   + \tilde{\theta}_{j,t-1}'\x_{j,t-1})\bar{D}_t + \bar{\varepsilon}_t,
 \end{split}
@@
 where $\mathcal{W}$ is the set of all allowable weight vectors.
+
+\begin{table}[H]
+	\caption{Results for Conoco Philips dual shock ($n=2$), $\mbf{W}^* = (0.756, 0.244)$ from scaled covariates} \label{coptable}
+\begin{center}
+  \begin{tabular}{cccccccccr}
+     $H$   &  $\hat{p}_1$ &   Vote (Correct?) & weighted Vote (Correct?)   \\
+     \hline 
+     2  & 1    & 0 (Yes) &0 (Yes)   \\ 
+     4  & 1 & 0(Yes)  &0 (Yes)  \\ 
+     6   & 1  &0 (Yes) & 0 (Yes) \\ 
+     8   & 1  & 0 (Yes) & 0 (Yes)
+  \end{tabular}
+\end{center}	
+\end{table}
 
@@
 \begin{table}[H]
-	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0, 0.278, 0.722)$ from scaled covariates}   \label{uemtable}
+	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0.196, 0.804, 0.000)$ from scaled covariates}   \label{uemtable}
 \begin{center}
@@
      \hline 
-     \multirow{2}{*}{2} & $\mc{M}_0$  &   0.190 & 0.436  & 0.246 & 0 (Yes) & 0 (Yes)\\      
-      & $\mc{M}$  & 0.520 & 0.556 & $0.036$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     \multirow{2}{*}{3} & $\mc{M}_0$ &   0.140 & 0.413  & $0.273$ & 0 (Yes) & 0 (Yes)    \\
-      &  $\mc{M}$ & 0.495 & 0.656 & 0.161 & 0 (Yes) & 0 (Yes)  \\[.2cm]
-     \multirow{2}{*}{4} &  $\mc{M}_0$ &   0.275   & $0.464$ & 0.189 & 0 (Yes) & 0 (Yes)  \\
-      &  $\mc{M}$ & 0.350 & 0.559  & 0.209 & 0 (Yes) & 0 (Yes) \\[.2cm]
-     \multirow{2}{*}{5} & $\mc{M}_0$ & 0.380  & 0.275 & 0.105 & 0 (Yes) & 0 (Yes)\\
-     & $\mc{M}$ & 0.665 & 0.763 & 0.098 & 0 (Yes) & 0 (Yes)
+     \multirow{2}{*}{2} & $\mc{M}_0$  &   0.450 & 0.511  & 0.061 & 0 (Yes) & 0 (Yes)\\      
+      & $\mc{M}$  & 0.240 & 0.583 & $0.343$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     \multirow{2}{*}{3} & $\mc{M}_0$ &   0.500 & 0.469  & $0.031$ & 0 (Yes) & 0 (Yes)    \\
+      &  $\mc{M}$ & 1 & 0.576 & 0.424 & 0 (Yes) & 0 (Yes)  \\[.2cm]
+     \multirow{2}{*}{4} &  $\mc{M}_0$ &   0.660   & $0.443$ & 0.217 & 0 (Yes) & 0 (Yes)  \\
+      &  $\mc{M}$ & 1.000 & 0.494  & 0.506 & 0 (Yes) & 0 (Yes) \\[.2cm]
+     \multirow{2}{*}{5} & $\mc{M}_0$ & 0.700  & 0.556 & 0.144 & 0 (Yes) & 0 (Yes)\\
+     & $\mc{M}$ & 0.470 & 1.000 & 0.530 & 0 (Yes) & 0 (Yes)
   \end{tabular}
@@
 
-$\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=0.722$
+$\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=0$.
+
+AICs for $\mc{M}_0$ in the donor pool are $(-609.173, -657.146,-678.949)$
+
+AICs for $\mc{M}$ in the donor pool are $(-601.743,-649.484,-684.147)$
 

### 2022-06-11 prevalence_testing/numerical_studies/COP.R

@@ -185,9 +185,8 @@ ols.est.alphahat <- function(Tstar, Y, X) {
   
 }
 
-# functions that return alpha.hat and synthetic weights
 ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw, 
-                                 sig.levl = .05, q1, 
+                                 sig.levl = .05, q1, subset = FALSE, 
                                  retro = TRUE, selfW = NA, scale = FALSE) {
   
   n <- length(Y) - 1
@@ -240,8 +239,8 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw,
         yhat.unadj <- Y[[i]][(t + Ki + H - h + 1 - q1):(t + Ki + H - h)]
         
         for (j in 1:h) {
-          yhat.adj.h <- matrix(c(1, ifelse(t + Ki + H - h + j >= Tstari + 1, yes = 1, no = 0),
-                                 yhat.adj[j:(j + q1 - 1)], X[[i]][-(1:q1), ][t + Ki + H - h + j, ]))
+          yhat.adj.h <- beta.hat.adj %*% matrix(c(1, ifelse(t + Ki + H - h + j >= Tstari + 1, yes = 1, no = 0),
+                                                  yhat.adj[j:(j + q1 - 1)], X[[i]][-(1:q1), ][t + Ki + H - h + j, ]))
           yhat.unadj.h <- beta.hat.unadj %*% matrix(c(1, yhat.adj[j:(j + q1 - 1)], X[[i]][-(1:q1), ][t + Ki + H - h + j, ]))
           
           if (t + Ki + H - h == Tstari & i >= 3 & h == 1) {
@@ -259,7 +258,13 @@ ps.indic.W.permanent <- function(Tstar, Y, X, K, H, Ts, ell, B, bw,
     }
     # loss differential
     d <- m2.L.i - m1.L.i
-    ps[i] <- taSPA.mhfc(ell = ell, d = d, B = B, bw = bw)
+    if (subset == FALSE) {
+      ps[i] <- taSPA.mhfc(ell = ell, d = d, B = B, bw = bw) 
+    } else {
+      sub.index <- (Ti - Ki - q1 - (Ti - Tstari) + 1):(Ti - Ki - H - q1)
+      d.subset <- d[sub.index,  ]
[…]

### 2022-06-11 prevalence_testing/numerical_studies/dualshock.R

@@ -1,0 +1,439 @@
+# load packages
+library("data.table")
+library("dplyr")
+library("tseries")
+library("quantmod")
+library('Rsolnp')
+library('msos')
+library('tikzDevice')
+library('xtable')
+
+# load packages
+require('forecast')
+
+# this function returns the W^* estimated by synthetic control method (SCM)
+scm <- function(X, Tstar, scale = FALSE) {
+  # X is a list of covariates for disparate time series
+  # X[[1]] should be the covariate of the time series to predict
+  # X[[p]] for p = 2,...,n+1 are covariates for time series pool
+  
+  # T^* is a vector of shock-effects time points
+  # shock effect point must be > 2
+  
+  # package for constrained optiminization
+  require('Rsolnp')
+  
+  # number of time series for pool
+  n <- length(X) - 1
+  
+  # covariate for time series for prediction
+  X1 <- X[[1]][Tstar[1] + 1, , drop = FALSE]
+  
+  # covariates for time series pool
+  X0 <- c()
+  for (i in 1:n) {
+    X0[[i]] <- X[[i + 1]][Tstar[i + 1] + 1, , drop = FALSE]
+  }
+  
+  if (scale == TRUE) {
+    dat <- rbind(X1, do.call('rbind', X0))
+    dat <- apply(dat, 2, function(x) scale(x, center = TRUE, scale = TRUE))
+    X1 <- dat[1, , drop = FALSE]
+    X0 <- c()
+    for (i in 1:n) {
+      X0[[i]] <- dat[i + 1, , drop = FALSE]
+    }
+  }
+  
+  
+  # objective function
+  weightedX0 <- function(W) {
+    # W is a vector of weight of the same length of X0
+    n <- length(W)
+    p <- ncol(X1)
+    XW <- matrix(0, nrow = 1, ncol = p)
+    for (i in 1:n) {
+      XW <- XW + W[i] * X0[[i]]
+    }
+    norm <- as.numeric(crossprod(matrix(X1 - XW)))
+    return(norm)
+  }
+  
+  # constraint for W
+  Wcons <- function(W) sum(W) - 1
+  
+  
+  # optimization
[…]

### 2022-06-14 prevalence_testing/postshocktest2022draft.tex
addition of dual shock analysis

@@
 
-\vspace*{0.5cm}\noindent\textbf{Note}\vspace*{0.5cm}
+\subsubsection{Dual shock prevalence testing}
 
@@
 All model parameters are estimable in \eqref{eq:dualshock}.
+\textcolor{red}{Shock prevalence testing for $z_{j,t}$ is still conducted by comparing forecasts between adjusted and unadjusted conditional mean forecasts as illustrated in Section \ref{sec:multhor}}.
 However, aggregation strategies are slightly different for this model since covariates are included for two separate series.
@@
 where $\mathcal{W}$ is the set of all allowable weight vectors.
+\textcolor{red}{Note that if the model is correctly specified,   inference under this dual shock setup should work well if $\{y_{o,t}\colon t= 1, \ldots, T_0\}$ and $\{y_{j, t} \colon j = 2, \ldots, n, t = 1, \ldots, T_j\}$ are independent.
+We assume this is approximately satisfied because these time series are sufficiently separated out in time as introduced in the beginning of this section.
+We provide corresponding numerical results   in Table \ref{dualshock}.}
+
+\textcolor{red}{Under the dual shock setup, the donor pool size of this dataset is $n=2$.
+The fitted synthetic weight vector $\mbf{W}^*$ turns out to be $(0.756, 0.244)$.
+It implies that the March 15, 2008 time series is more similar to the time series of interest than the September 2008 time series.
+Similarly, we conducted sensitivity analysis using   $H = 2, 4, 6, 8$; and the results appear insensitive to $H$ from Table \ref{dualshock}.
+Based on Table \ref{dualshock}, $\hat{p}_1$ is uniformly 1 so that we fail to detect shock persistence.
+The results of voting and weighted voting are consistent to this with both voting for shock transience.}
 
 \begin{table}[H]
-	\caption{Results for Conoco Philips dual shock ($n=2$), $\mbf{W}^* = (0.756, 0.244)$ from scaled covariates} \label{coptable}
+	\caption{Results for Conoco Philips dual shock ($n=2$), $\mbf{W}^* = (0.756, 0.244)$ from scaled covariates} \label{dualshock}
 \begin{center}
   \begin{tabular}{cccccccccr}
-     $H$   &  $\hat{p}_1$ &   Vote (Correct?) & weighted Vote (Correct?)   \\
+     $H$   &  $\hat{p}_1$ &   Vote   & weighted Vote  \\
      \hline 
-     2  & 1    & 0 (Yes) &0 (Yes)   \\ 
-     4  & 1 & 0(Yes)  &0 (Yes)  \\ 
-     6   & 1  &0 (Yes) & 0 (Yes) \\ 
-     8   & 1  & 0 (Yes) & 0 (Yes)
+     2  & 1    & 0  &0   \\ 
+     4  & 1 & 0   &0   \\ 
+     6   & 1  &0  & 0  \\ 
+     8   & 1  & 0   & 0  
   \end{tabular}
@@
 \end{table}
+
+\textcolor{red}{ Unlike the results presented Table \ref{coptable}, we cannot know  the underlying $p_1$ and evaluate whether the voting and weighted voting are correct.
+This is due to the fact that the time series of interest experience financial and oil shocks at the same time.
+As a result,   the model is unidentifiable given the available  data.
+Nevertheless, the shock transience evident in Figure \ref{copshocktransience} provides a reference and supports our claim.
+This result confirms what we obtained in Section \ref{sptcop} and sucessfully generalizes the dual shock in post-shock prediction \citep{lin2021minimizing} to prevalence testing.}
 

### 2022-07-02 prevalence_testing/postshocktest2022draft.tex
added to discussion of unemployment application

@@
 
+\textbf{What I'm trying to hit here}
+\begin{enumerate}
+\item Why did I choose the donors I chose? 
+\item Why did I use the columns I did in OLS? 
+\item Why did I use the columns I did in the estimation of the points on the simplex? 
+\item Discuss the two models, M1, M2 
+\item Weighted AIC just as in previous example?  
+\item By weighted AIC, M1 is the preferred model 
+\end{enumerate}
+
 Arguably the most watched macroeconomic indicator for the US economy is the monthly release of the total nonfarm payrolls, which reflects the gains or losses of persons employed.
@@
 The donor pool assembled notably contains no cases of lockdowns or even pandemics or epidemics.
-Instead, the common thread running through the time series under study and the donors is the element of a sudden and considerable surprise visited upon the economy from source previously judged to be marginal.
+Instead, the common thread running through the time series under study and the donors is the element of a sudden and considerable negative surprise visited upon the economy from a source previously judged to be marginal.
+
+The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
+This decline exceeds all other monthly declines by many orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
+However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution (\textcolor{red}{Think about this}).
+Instead, what is needed is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics (?).
+
+We assemble a donor pool of substantial shocks to the US economy in the last four decades: the recessions of 1981-82, 2001-2003, and 2007-2009.
+The recession of 1981-82 resulted from Fed Chairman Volcker's unprecedented and controversial bid to halt persistently high inflation that had reigned for more than decade in the US.
+The economic shock that followed the September 11th terrorist both damaged consumer confidence and accelerated a contraction already in progress owing to the dot-com bubble.
+Third and finally, the spring 2008 collapse of the investment bank Bear Stearns dealt a serious blow to confidence in the US financial system, which at the time was predicted by many to withstand the unprecedented declines in major US metro real estate markets.
+These events bear similarity to the broad, seismic shock dealt to the US economy in March 2020 -- and the labor market in particular --  not only due to their unprecedented nature but also because of their potential to cause deep and lasting damage.
+
+We employ a suite of monthly macroeconomic indicators as covariates for the linear model as for arriving at an optimal weighting of the donor pool.
+These indicators are all transformed to their month-on-month change in log values, so as to be consistent with the time series under study and to capture the signal inherent in changes, not raw levels, of macroeconomic variables.
+These indicators are the US unemployment insurance transfers, real personal income, personal consumption expenditures, industrial production, consumer price index, Federal Reserve funds rate, and the count of black Americans age 20 and over on US nonfarm payrolls.
 
@@
 
-Arguably the most watched macroeconomic indicator for the US economy is the monthly release of the total nonfarm payrolls, which reflects the gains or losses of persons employed.
-The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
-This decline exceeds all other monthly declines by many orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
-However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution (\textcolor{red}{Think about this}).
-Instead, what is needed is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study.
-
-To that end, we assemble a donor pool of US recessions induced by large shocks in the last three decades: the recessions of 1981-82, 2001-2003, and 2007-2009 (\textcolor{red}{Justification needed for these shocks; the March 2020 lockdown was an unprecedented halting of economic activity}).
-We employ a suite of monthly macroeconomic indicators as covariates for the linear model as for arriving at an optimal weighting of the donor pool.
-These indicators are all transformed to their month-on-month change in log values, so as to be consistent with the time series under study and to capture the signal inherent in changes, not raw levels, of macroeconomic variables.
-These indicators are the US unemployment insurance transfers, real personal income, personal consumption expenditures, industrial production, consumer price index, Federal Reserve funds rate, and the count of black Americans age 20 and over on US nonfarm payrolls.
-
-The variable selection steps are outlined as follows.
+\textcolor{red}{If the selection technique is the same as in the case of ConocoPhillips, then we can cut this.} The variable selection steps are outlined as follows.
 At first, we have the same set of covariates $\{\mc{X}_1, \ldots, \mc{X}_p\}$ for each donor, where $\mc{X}_1$ corresponds to the name of the covariate.
@@
 
-In Table 2, using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, because $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)>0.5$,  we conclude that  $\mc{M}$ is preferred.
+In Table 3, using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, because $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2) = 0$,  we conclude that  $\mc{M}_{0}$ is preferred.
 Thus, we turn our interest to that model.
-Since $p_{1}$ is far above the rejection threshold, we lack the evidence to reject the null of a transient shock in the time series under study, the month-on-month change in log employment in the span 2019-2022.
-The weighted p-value, $\hat p $, misses the ground truth p-value by .146 in absolute value, yet renders the correct decision.
-
-\textbf{Questions to answer and points to hit}
-\begin{enumerate}
-\item Why did I choose the donors I chose? X 
-\item Why did I use the columns I did in OLS? X
-\item Why did I use the columns I did in the estimation of the points on the simplex? X
-\item Discuss the two models, M1, M2 X
-\item Weighted AIC just as in previous example?  X
-\item By weighted AIC, M2 is the preferred model Yes
-\item We can see that $p_{1}$ is far larger than the rejection threshold, indicating that we lack the evidence to reject the null of a transiet shock
-\item The weighted pvalue, $\hat p $, misses the ground truth p-value by .146 in absolute value
-\item The method of voting renders the correct decision
-\item The method of weighted voting renders the correct decision
-\item Ask Jilei to correct y-axis X
-\item Ask Jilei whether AIC was used in the same way as first example X
-\item Ask Jilei whether covariate set $\textbf{X}$ is same as simplex optimization $\textbf{X}$ 
-\item Ask Jilei to drop RPI as a covariate in OLS (but not necessarily for optimization) (needs checking)
-\item Ask Jilei to include chart with data stopping at March 2020 to better visualize how payrolls change by month X
-
-\end{enumerate}
+Since $p_{1}$ is far above the rejection threshold for horizons H=1,2,3,4, we lack the evidence to reject the null of a transient shock in the time series under study at any horizon.
+The weighted p-value, $\hat p $, misses the ground truth p-value by no more than a modest amount at almost all horizons, and at some horizons is impressively close to the ground truth.
+Last, it is worth remarking the for the preferred model $\mc{M}_{0}$, we observe a monotone increasing sequence of ground-truth p-values as H increases.
+Such a phenomenon can be taken as evidence that as more data is harnessed, the decision is stable.
+The estimated p-value $\hat p_{1}$ do an adequate job at tracking this phenomenon as H increases.
 

### 2022-07-26 prevalence_testing/postshocktest2022draft.tex
minor changes
changed epsilon notation

@@
 and let $\sigma^2 = \max(\lambda_{\max}, \sigma^2_{\max})$.
-Now fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$ for all $t$ and some choice of $\varepsilon_1$.
+Now fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \epsilon_1$ for all $t$ and some choice of $\epsilon_1$.
 Pick some large $M > 0$.
@@
 \begin{align*}
-  E_1 := &\left\{\max\left(|\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \varepsilon_1:\right. \\
+  E_1 := &\left\{\max\left(|\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \epsilon_1:\right. \\
   &\qquad j = 1,\ldots,q_1, k = 1,\ldots,q_2, t = 1,\ldots,T \left.\right\}, \\
@@
 		+ |\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t})| 
-		+ \varepsilon_1 \\
-	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - \tilde{y}_{i',t-1}| \\
-	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| \\ 
-	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||\tilde{y}_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - \tilde{y}_{i',t-2}|\right\} \\
-	&\qquad= \varepsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|\tilde{y}_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - \tilde{y}_{i',t-2}| \\
-	&\qquad \leq \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - \tilde{y}_{i',T^*}| \\
-	&\qquad = \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}|.
-\end{align*}
-With $T$ set, we can choose $\varepsilon_1$ small enough so that 
+		+ \epsilon_1 \\
+	&\qquad\leq (8M + 1)\epsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - \tilde{y}_{i',t-1}| \\
+	&\qquad\leq (8M + 1)\epsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| \\ 
+	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\epsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||\tilde{y}_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - \tilde{y}_{i',t-2}|\right\} \\
+	&\qquad= \epsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|\tilde{y}_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - \tilde{y}_{i',t-2}| \\
+	&\qquad \leq \epsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - \tilde{y}_{i',T^*}| \\
+	&\qquad = \epsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}|.
+\end{align*}
+With $T$ set, we can choose $\epsilon_1$ small enough so that 
 $
-  |y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_2
+  |y_{1,t} - \tilde{y}_{i',t}| < \epsilon_2
 $
@@
 
-Now let $\varepsilon_3 = \max(\varepsilon_1,\varepsilon_2)$ so that 
+Now let $\epsilon_3 = \max(\epsilon_1,\epsilon_2)$ so that 
 \begin{equation} \label{bounds}
-	|y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_3, \; \text{and} \; \|\x_{1,t} - \x_{i',t}\| < \varepsilon_3.
+	|y_{1,t} - \tilde{y}_{i',t}| < \epsilon_3, \; \text{and} \; \|\x_{1,t} - \x_{i',t}\| < \epsilon_3.
 \end{equation}
@@
 We use Theorem 2.7.2 in \cite{golub1996matrix} to construct an explicit bound on $\|\tilde{\beta} - \hat{\beta}\|$.
-Following the notation of Section 2.7 in \cite{golub1996matrix} we will let $A$ be the design matrix with respect to the $y_{1,t}$ series so that $A\hat{\beta} = \mathbf{y}_1$ where $\mathbf{y}_1 = (y_{1,1}, \ldots, y_{1,T})'$, $\kappa(A) = \|A\|\|A^{-1}\|$ be the condition number of $A$ where $\|\cdot\|$ is a matrix norm, and we will specify that $r = \varepsilon_4 \kappa(A)$ where $\varepsilon_4$ can be chosen so that $r < 1$.
-We will also specify that $\varepsilon_3$ is chosen so that $\|\Delta A\| \leq \varepsilon_4\|A\|$ where $\Delta A = \widetilde{A} - A$ and $\widetilde{A}$ is the design matrix with respect to the $\tilde{y}_{i',t}$ series.
+Following the notation of Section 2.7 in \cite{golub1996matrix} we will let $A$ be the design matrix with respect to the $y_{1,t}$ series so that $A\hat{\beta} = \mathbf{y}_1$ where $\mathbf{y}_1 = (y_{1,1}, \ldots, y_{1,T})'$, $\kappa(A) = \|A\|\|A^{-1}\|$ be the condition number of $A$ where $\|\cdot\|$ is a matrix norm, and we will specify that $r = \epsilon_4 \kappa(A)$ where $\epsilon_4$ can be chosen so that $r < 1$.
+We will also specify that $\epsilon_3$ is chosen so that $\|\Delta A\| \leq \epsilon_4\|A\|$ where $\Delta A = \widetilde{A} - A$ and $\widetilde{A}$ is the design matrix with respect to the $\tilde{y}_{i',t}$ series.
 Theorem 2.7.2 in \cite{golub1996matrix} states that
 \begin{equation}\label{OLSbound}
-  \|\tilde{\beta} - \hat{\beta}\| \leq \frac{2\varepsilon_4}{1-r}\kappa(A)\|\hat{\beta}\|.	
+  \|\tilde{\beta} - \hat{\beta}\| \leq \frac{2\epsilon_4}{1-r}\kappa(A)\|\hat{\beta}\|.	
 \end{equation}
-We can bound $\kappa(A)$ and $\hat{\beta}$ on $E$ which allows one to choose $\varepsilon_5$ so that \eqref{OLSbound} is $\|\tilde{\beta} - \hat{\beta}\| < \varepsilon_5$.
+We can bound $\kappa(A)$ and $\hat{\beta}$ on $E$ which allows one to choose $\epsilon_5$ so that \eqref{OLSbound} is $\|\tilde{\beta} - \hat{\beta}\| < \epsilon_5$.
 
@@
   &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| = |(\hat\eta_1 - \hat{\eta}_{i'}) + (\hat\alpha_1 - \hat\alpha_{i'}) + (\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}) + (\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t})| \\
-  &\qquad \leq 2\varepsilon_5 + |\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t}| + |\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}| \\
-  &\qquad \leq 2\varepsilon_5 + \|\x_{1,t}\|\|\hat{\tilde{\theta}}_1 - \hat{\tilde{\theta}}_{i'}\| + \|\hat{\tilde{\theta}}_{i'}\| \|\x_{1,t} - \x_{i',t}\| + \|\hat{y}_{1,t-1}^{1,h-1}\| |\hat{\tilde{\phi}}_1 - \hat{\tilde{\phi}}_{i'}\| + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} | \\
-  &\qquad \leq 2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + \|\hat{y}_{1,t-1}^{1,h-1}\|\varepsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} |.
-\end{align*}
-On $E$ we can bound $|\hat{y}_{1,t-1}^{1,h-1}|$ for all $h=1,\ldots,H$ and $t=1,\ldots,T$, call this bound $M_1$.
-Let $\varepsilon_6 = (2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + M_1\varepsilon_5)$.
-Then,
-\begin{align*}
-  &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| \leq 2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + |\hat{y}_{1,t-1}^{1,h-1}|\varepsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
-  &\qquad \leq (2\varepsilon_5 + M\varepsilon_5 + \varepsilon_3 + M_1\varepsilon_5) + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
-  &\qquad \leq \varepsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
-  &\qquad \leq \varepsilon_6 + |\hat{\tilde{\phi}}_{i'}|\left(\varepsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}|\right) \\
-  &\qquad \leq \varepsilon_6(1 + |\hat{\tilde{\phi}}_{i'}|) + |\hat{\tilde{\phi}}_{i'}|^2|\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}| \\  
-  &\qquad \leq \varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h|\hat{y}_{1,t-h} - \hat{y}_{i',t-h}| \\
-  &\qquad \leq \varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\varepsilon_3.  
-\end{align*}
-Let $\varepsilon_7 = \max_{h = 1,\ldots,H}\left(\varepsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\varepsilon_3\right)$ 
+  &\qquad \leq 2\epsilon_5 + |\hat{\tilde{\theta}}_1' \x_{1,t} - \hat{\tilde{\theta}}_{i'}' \x_{i',t}| + |\hat{\tilde{\phi}}_1 \hat{y}_{1,t-1}^{1,h-1} -  \hat{\tilde{\phi}}_{i'} \hat{y}_{i',t-1}^{1,h-1}| \\
+  &\qquad \leq 2\epsilon_5 + \|\x_{1,t}\|\|\hat{\tilde{\theta}}_1 - \hat{\tilde{\theta}}_{i'}\| + \|\hat{\tilde{\theta}}_{i'}\| \|\x_{1,t} - \x_{i',t}\| + \|\hat{y}_{1,t-1}^{1,h-1}\| |\hat{\tilde{\phi}}_1 - \hat{\tilde{\phi}}_{i'}\| + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} | \\
+  &\qquad \leq 2\epsilon_5 + M\epsilon_5 + \epsilon_3 + \|\hat{y}_{1,t-1}^{1,h-1}\|\epsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1} |.
+\end{align*}
+On $E$ we can bound $|\hat{y}_{1,t-1}^{1,h-1}|$ for all $h=1,\ldots,H$ and $t=1,\ldots,T$, call this bound $M_1$. Let $\epsilon_6 = (2\epsilon_5 + M\epsilon_5 + \epsilon_3 + M_1\epsilon_5)$. Then,
+\begin{align*}
+  &|\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| \leq 2\epsilon_5 + M\epsilon_5 + \epsilon_3 + |\hat{y}_{1,t-1}^{1,h-1}|\epsilon_5 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
+  &\qquad \leq (2\epsilon_5 + M\epsilon_5 + \epsilon_3 + M_1\epsilon_5) + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
+  &\qquad \leq \epsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-1}^{1,h-1} - \hat{y}_{i',t-1}^{1,h-1}| \\
+  &\qquad \leq \epsilon_6 + |\hat{\tilde{\phi}}_{i'}|\left(\epsilon_6 + |\hat{\tilde{\phi}}_{i'}| |\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}|\right) \\
+  &\qquad \leq \epsilon_6(1 + |\hat{\tilde{\phi}}_{i'}|) + |\hat{\tilde{\phi}}_{i'}|^2|\hat{y}_{1,t-2}^{1,h-2} - \hat{y}_{i',t-2}^{1,h-2}| \\  
+  &\qquad \leq \epsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h|\hat{y}_{1,t-h} - \hat{y}_{i',t-h}| \\
+  &\qquad \leq \epsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\epsilon_3.  
+\end{align*}
+Let $\epsilon_7 = \max_{h = 1,\ldots,H}\left(\epsilon_6 \sum_{j=0}^h |\hat{\tilde{\phi}}_{i'}|^j + |\hat{\tilde{\phi}}_{i'}|^h\epsilon_3\right)$ 
 and conclude that 
 \begin{equation} \label{forecastbounds}
-  |\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| < \varepsilon_7,	
+  |\hat{y}_{1,t}^{1,h} - \hat{\tilde{y}}_{i',t}^{1,h}| < \epsilon_7,	
 \end{equation}
@@
 A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made when $t+h > T^*$ and $t \leq T^*$.
-A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made so that $|\hat{y}_{1,t}^{2,h} - \hat{\tilde{y}}_{i',t}^{2,h}| < \varepsilon_7$.
+A similar argument with similar bounding choices to those which yielded \eqref{forecastbounds} can be made so that $|\hat{y}_{1,t}^{2,h} - \hat{\tilde{y}}_{i',t}^{2,h}| < \epsilon_7$.
 
@@
 \begin{equation} \label{L1bound}
-  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{1,h}_{i',t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{i',t}| + 2(\varepsilon_3 + \varepsilon_7).
+  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{1,h}_{i',t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{i',t}| + 2(\epsilon_3 + \epsilon_7).
 \end{equation}
-We conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$ where $\varepsilon_8$ is chosen so that \eqref{L1bound} holds when $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.
+We conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \epsilon_8$ on $E$ for all $t > T^*$ where $\epsilon_8$ is chosen so that \eqref{L1bound} holds when $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \epsilon_8$ on $E$ for all $t > T^*$.
 %when we specify the loss $L(a,b) = |a-b|$.
@@
 %Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.
-Putting this all together, we can pick $\varepsilon_8$ small enough so that for some fixed $\varepsilon > 0$,
+Putting this all together, we can pick $\epsilon_8$ small enough so that for some fixed $\epsilon > 0$,
 \begin{equation} \label{testbounds}
-   \left|\sqrt{T}\frac{\textbf{w}_1'\bar{\dbf}_1^b - \textbf{w}_1'\bar{\dbf}_1}{\hat{\zeta}^b_1} - \sqrt{T}\frac{\textbf{w}_{i'}'\bar{\dbf}_{i'}^b - \textbf{w}_{i'}'\bar{\dbf}_{i'}}{\hat{\zeta}^b_{i'}}\right| < \varepsilon
+   \left|\sqrt{T}\frac{\textbf{w}_1'\bar{\dbf}_1^b - \textbf{w}_1'\bar{\dbf}_1}{\hat{\zeta}^b_1} - \sqrt{T}\frac{\textbf{w}_{i'}'\bar{\dbf}_{i'}^b - \textbf{w}_{i'}'\bar{\dbf}_{i'}}{\hat{\zeta}^b_{i'}}\right| < \epsilon
 \end{equation}
 on the set $E$ where we specify that $\textbf{w}_1 = \textbf{w}_{i'}$ and that the MBB procedures samples the same indices of blocks from $\dbf_{1,t}$ and $\dbf_{i',t}$, $t = T^*+1,\ldots, T$ when forming the test statistics in \eqref{testbounds}.
-Thus for any fixed small $\varepsilon < 0$ there exists a choice of $\sigma^2$ and $\varepsilon_1$ such that inferences involving the $i'$ series for which post-shock behavior is observed can be substituted in place of the $i = 1$ series under study with high probability of a correspondence in inferences.
+Thus for any fixed small $\epsilon < 0$ there exists a choice of $\sigma^2$ and $\epsilon_1$ such that inferences involving the $i'$ series for which post-shock behavior is observed can be substituted in place of the $i = 1$ series under study with high probability of a correspondence in inferences.
 
@@
 We assemble a donor pool of substantial shocks to the US economy in the last four decades: the recessions of 1981-82, 2001-2003, and 2007-2009.
+These events bear similarity to the broad, seismic shock dealt to the US economy in March 2020 -- and the labor market in particular --  not only due to their unprecedented nature but also because of their potential to cause deep and lasting damage.
 The recession of 1981-82 resulted from Fed Chairman Volcker's unprecedented and controversial bid to halt persistently high inflation that had reigned for more than decade in the US.
@@
 Third and finally, the spring 2008 collapse of the investment bank Bear Stearns dealt a serious blow to confidence in the US financial system, which at the time was predicted by many to withstand the unprecedented declines in major US metro real estate markets.
-These events bear similarity to the broad, seismic shock dealt to the US economy in March 2020 -- and the labor market in particular --  not only due to their unprecedented nature but also because of their potential to cause deep and lasting damage.
-
-We employ a suite of monthly macroeconomic indicators as covariates for the linear model as for arriving at an optimal weighting of the donor pool.
+
+We used several monthly macroeconomic indicators as covariates for the linear model as for arriving at an optimal weighting of the donor pool.
 These indicators are all transformed to their month-on-month change in log values, so as to be consistent with the time series under study and to capture the signal inherent in changes, not raw levels, of macroeconomic variables.

### 2022-07-26 prevalence_testing/numerical_studies/simu_dynamic.R

@@ -450,22 +450,25 @@ nsim <- 200
 paras <- c(1 / 5 ^ 2, 1 / 5, 1, 5, 5 ^ 2)
 
 # simulation time
-system.time(
-  output <- lapply(1:length(paras), FUN = function(j) {
-    # %do% evaluates sequentially
-    # %dopar% evaluates in parallel
-    # .combine results
-    lambda2.j <- paras[j]
-    out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
-      # result
-      study <- sim(mu.delta = 1, mu.alpha = 10, sigma = 1, 
-                   sigma.alpha = 2, sigma.delta = 0.05, 
-                   p = 4, B = 200, H = 10, ell = 4, bw = 4,
-                   q1 = 2, q2 = 2, c = 2, lambda1 = 50, lambda2 = lambda2.j,
-                   L = 30, n = 10, tshape = 15, tscale = 10)
-      return(study)
-    }
-    # return results
-    out
-  })
-)
+suppressMessages({
+  system.time(
+    output <- lapply(1:length(paras), FUN = function(j) {
+      # %do% evaluates sequentially
+      # %dopar% evaluates in parallel
+      # .combine results
+      lambda2.j <- paras[j]
+      out <- foreach(k = 1:nsim, .combine = rbind) %dopar% {
+        # result
+        study <- sim(mu.delta = 1, mu.alpha = 10, sigma = 1, 
+                     sigma.alpha = 2, sigma.delta = 0.05, 
+                     p = 4, B = 200, H = 10, ell = 4, bw = 4,
+                     q1 = 2, q2 = 2, c = 2, lambda1 = 50, lambda2 = lambda2.j,
+                     L = 30, n = 10, tshape = 15, tscale = 10)
+        return(study)
+      }
+      # return results
+      out
+    })
+  )  
+})
+traceback()

### 2022-07-30 prevalence_testing/postshocktest2022draft.tex
adjustments to employment series

@@
 The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
-This decline exceeds all other monthly declines by many orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
+This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
 However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution (\textcolor{red}{Think about this}).
@@
 These events bear similarity to the broad, seismic shock dealt to the US economy in March 2020 -- and the labor market in particular --  not only due to their unprecedented nature but also because of their potential to cause deep and lasting damage.
-The recession of 1981-82 resulted from Fed Chairman Volcker's unprecedented and controversial bid to halt persistently high inflation that had reigned for more than decade in the US.
-The economic shock that followed the September 11th terrorist both damaged consumer confidence and accelerated a contraction already in progress owing to the dot-com bubble.
-Third and finally, the spring 2008 collapse of the investment bank Bear Stearns dealt a serious blow to confidence in the US financial system, which at the time was predicted by many to withstand the unprecedented declines in major US metro real estate markets.
-
-We used several monthly macroeconomic indicators as covariates for the linear model as for arriving at an optimal weighting of the donor pool.
+The recession of 1981-82 resulted from Fed Chairman Volcker's unprecedented and controversial bid to halt persistently high inflation that had reigned for more than decade in the US \citep{sablik_2013}.
+The economic shock that followed the September 11th terrorist both damaged consumer confidence and accelerated a contraction already in progress owing to the dot-com bubble \citep{kliesen_2003}.
+Third and finally, the spring 2008 collapse of the investment bank Bear Stearns dealt a serious blow to confidence in the US financial system.
+Prior to that, financial markets had withstood the unprecedented declines in major US metro real estate markets that followed the peak of the market in 2006.
+
+We used several monthly macroeconomic indicators as covariates for the linear model to arrive at an optimal weighting of the donor pool.
 These indicators are all transformed to their month-on-month change in log values, so as to be consistent with the time series under study and to capture the signal inherent in changes, not raw levels, of macroeconomic variables.
@@
 The estimated p-value $\hat p_{1}$ do an adequate job at tracking this phenomenon as H increases.
+The performance of method is in spite of the unusual path that the pre-lockdown US economy took, where weeks of restrictions on human assocation and movement gave way to relaxation of controls and an economic boom.
 
@@
 
-\textcolor{red}{needs work} Talk about post-shock forecasting as parameterizing exogeniety and using hindsight in the donor pool to explicitly estimate exogeneity apriori.
+\textcolor{red}{needs work} Talk about post-shock forecasting as parameterizing exogeneity and using hindsight in the donor pool to explicitly estimate exogeneity apriori.
 This framing has its limits, we are not able to perform post-shock forecasts when we are temporarily removed from the known shock time.

### 2022-07-30 prevalence_testing/postshocktest2022draft.tex
minor edits

@@
 
-The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
-This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
-However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution (\textcolor{red}{Think about this}).
-Instead, what is needed is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics (?).
-
 We assemble a donor pool of substantial shocks to the US economy in the last four decades: the recessions of 1981-82, 2001-2003, and 2007-2009.
@@
 
-\textcolor{red}{A lot is needed here.
-We need to say that we are assuming that government lockdowns are temporary or rather that the effect of government lockdowns will be temporary.
-We need to mention that none of the time series in the donor pool involve lockdowns.
-We should consider a few time horizons.
-Something like 2, 3, or 4 months ahead might be interesting (we may need to consider a less complex dynamic model for fitting purposes).
-I would guess that a shorter window may exhibit disagreement between the donor pool and the series under study or may show different decisions being reported.
-However, don't we want to match the time series under study with donors based on only pre-shock features, data, variables, etc?
-It might be good to think of donor selection as a two-stage matching procedure: first, a donor is judged worthy based on some qualitative or quantitative analysis (the latter of which can be simply the correlation of their covariate vectors at $T^{*}$); second, the matches are aggregated using distanced-based weighting.}
-
-\textcolor{red}{If the selection technique is the same as in the case of ConocoPhillips, then we can cut this.} The variable selection steps are outlined as follows.
+The variable selection steps are outlined as follows.
 At first, we have the same set of covariates $\{\mc{X}_1, \ldots, \mc{X}_p\}$ for each donor, where $\mc{X}_1$ corresponds to the name of the covariate.
@@
 
+The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
+This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
+However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution (\textcolor{red}{Think about this}).
+Instead, what is needed is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics (?).
+
 \subsection{Simulations}

### 2022-07-30 prevalence_testing/postshocktest2022draft.tex
small change to discussion of employment

@@
 The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
-This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.
-However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution (\textcolor{red}{Think about this}).
-Instead, what is needed is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics (?).
+This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not reasonably hope to recover the full shock effect.
+However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution.
+What is potentially as important or more important is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics.
+It is therefore the latter that may best explain the performance of the decision-making method developed here.
 

### 2022-07-31 prevalence_testing/postshocktest2022draft.tex
changes to unemployment example

@@
 The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.
-This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not reasonably hope to recover the full shock effect.
-However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution.
+This decline exceeds all other monthly declines by orders of magnitude.
+The distance-based weighting  in \citep{lin2021minimizing}, employing a convex combination of donor shocks, is known to be unable to extrapolate and thus recover the full shock effect.
+However, the procedure developed herein does not rely as heavily upon the full or partial recovery of the shock effect.
 What is potentially as important or more important is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics.

### 2022-08-06 prevalence_testing/postshocktest2022draft.tex
addition of revised results

@@
 
-In this data example we set $T_i- T_i^* = 30$ and $K = 30$.
+In this data example we set $T_i- T_i^* = 50$ and $K = 30$.
 Note that $K = 30$ is a sensible  training sample size, see discussions for example in  \cite{lin2021minimizing}.
-The quantity $T_i-T_i^*-H$ corresponds to the post-shock time length that analysts are interested in predicting whether the impact of the shock persists.
-We set $T_i- T_i^* = 30$  in order to make the post-shock time length moderately large and also for illustration purpose.
+The quantity $T_i-T_i^*-\ceil{1.5 \cdot \sqrt{T_i-T_i^*}}$ corresponds to the post-shock time length that analysts are interested in predicting whether the impact of the shock persists.
+We set $T_i- T_i^* = 50$  in order to make the post-shock time length moderately large and also for illustration purpose.
 For sensitivity analysis, we implemented the analysis for different  $H= 2, 4, 6, 8$.
@@
      \hline 
-     \multirow{2}{*}{2} & $\mc{M}_0$  &   1 & 0.225  & 0.775 & 0 (Yes) & 1 (No)  \\      
+     \multirow{2}{*}{2} & $\mc{M}_0$  &   1 & 0.023  & 0.977 & 0 (Yes) & 1 (No)  \\      
       & $\mc{M}$  & 1 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     \multirow{2}{*}{4} & $\mc{M}_0$ &   0 & 0.953  & $0.953$ & 0 (No) &0 (No)    \\
+     \multirow{2}{*}{4} & $\mc{M}_0$ &   1 & 0.125 & $0.875$ & 0 (Yes) &1 (No)    \\
       &  $\mc{M}$ & 1& 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
-     \multirow{2}{*}{6} &  $\mc{M}_0$ &   0   & $1$ & 1 & 0 (No) &0 (No)   \\
+     \multirow{2}{*}{6} &  $\mc{M}_0$ &   0   & $0.999$ & 0.999 & 0 (No) &0 (No)   \\
       &  $\mc{M}$ & 1 & 1  & 0 &0 (Yes) & 0 (Yes) \\[.2cm]
@@
 Based on \eqref{model-gen}, which describes $\mc{M}$ and the description of $\mc{M}$ in the beginning of Section \ref{sec::ne}, it may be inferred that $\mc{M}$ captures the post-shock dynamic change whereas $\mc{M}_0$ suggests a persistent post-shock additive location shift.
-Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, it turns out that $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=1 >0.5$.
+Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, it turns out that $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=0.779 >0.5$.
 Using this aggregated model selection approach, we prefer $\mc{M}$ over $\mc{M}_0$.
-\textcolor{red}{For reference, the AICs for $\mc{M}_0$ in the donors are $(297.410, 413.357, 295.174)$ whereas those for $\mc{M}$ in the donors are $(302.835, 409.544, 280.609)$.
+\textcolor{red}{For reference, the AICs for $\mc{M}_0$ in the donors are $(348.261, 504.887, 377.073)$ whereas those for $\mc{M}$ in the donors are $(349.784, 505.012, 364.108)$.
 }
@@
 Under any reasonable significance level, based on the features of $\mc{M}$, we infer that post-shock dynamics do not differ from the pre-shock one and the shock is not persistent.
-In contrast, $p_1$ of $\mc{M}_0$ equals 1 for $H = 2$ whereas equals 0 for $H = 4, 6, 8$.
+In contrast, $p_1$ of $\mc{M}_0$ equals 1 for $H = 2, 4$ whereas equals 0 for $H = 6, 8$.
 It is possible that $\mc{M}_0$ does not fit the data well.
@@
 Note that this observation confirms our model selection and what $\mc{M}$ suggests for shock transience.
-It is also important to re-emphasize that  the test compares the forecasts from $t = T_1^* + H+1$ to $t=T_1$.
+It is also important to re-emphasize that  the test compares the forecasts from $t = T_1^* + H+\ceil{1.5 \cdot \sqrt{T_1-T_1^*}}$ to $t=T_1$.
 In other words, the beginning dramatic drop as seen from Figure \ref{copshocktransience} around March is not considered in the forecast comparison.
@@
 \textcolor{red}{According to the last two columns of Table \ref{coptable}, the decisions yielded by voting and weighted voting are correct for $\mc{M}$ and $H = 2, 4, 6, 8$.
-However, the decisions for voting and weighted voting are incorrect for $\mc{M}_0$ and $H=2, 4, 6, 8$ except for voting for $\mc{M}_0$ at $H = 2$.
-The interpretations for this are similar to those when we analyze $|\hat{p}_1-p_1|$.
+However, the decisions for voting and weighted voting are incorrect for $\mc{M}_0$ and $H=2, 4, 6, 8$ except for voting for $\mc{M}_0$ at $H = 2,4$.
+Here, it is worth noting that weighted voting and voting may differ due to $\mbf{W}^*$.
+Such difference may be valuable if the weight is concentrated in one donor that does not tell a consistent story to that of time series of interest.
+Next, the interpretations for these results are similar to those when we analyze $|\hat{p}_1-p_1|$.
 Note that the decisions using $\hat{p}_1$ and weighted voting are similar.
@@
      \hline 
-     \multirow{2}{*}{2} & $\mc{M}_0$  &   0.450 & 0.511  & 0.061 & 0 (Yes) & 0 (Yes)\\      
-      & $\mc{M}$  & 0.240 & 0.583 & $0.343$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     \multirow{2}{*}{3} & $\mc{M}_0$ &   0.500 & 0.469  & $0.031$ & 0 (Yes) & 0 (Yes)    \\
-      &  $\mc{M}$ & 1 & 0.576 & 0.424 & 0 (Yes) & 0 (Yes)  \\[.2cm]
-     \multirow{2}{*}{4} &  $\mc{M}_0$ &   0.660   & $0.443$ & 0.217 & 0 (Yes) & 0 (Yes)  \\
-      &  $\mc{M}$ & 1.000 & 0.494  & 0.506 & 0 (Yes) & 0 (Yes) \\[.2cm]
-     \multirow{2}{*}{5} & $\mc{M}_0$ & 0.700  & 0.556 & 0.144 & 0 (Yes) & 0 (Yes)\\
-     & $\mc{M}$ & 0.470 & 1.000 & 0.530 & 0 (Yes) & 0 (Yes)
+     \multirow{2}{*}{2} & $\mc{M}_0$  &   0.300 & 0.443  & 0.143 & 0 (Yes) & 0 (Yes)\\      
+      & $\mc{M}$  & 0.775 & 0.591 & $0.184$   & 0 (Yes) &0 (Yes)   \\[.2cm]
+     \multirow{2}{*}{3} & $\mc{M}_0$ &   0.215 & 0.477 & $0.262$ & 0 (Yes) & 0 (Yes)    \\
+      &  $\mc{M}$ & 0.740 & 0.600 & 0.140 & 0 (Yes) & 0 (Yes)  \\[.2cm]
+     \multirow{2}{*}{4} &  $\mc{M}_0$ &   0.615   & $0.343$ & 0.272 & 0 (Yes) & 0 (Yes)  \\
+      &  $\mc{M}$ & 0.780 & 0.464  & 0.316 & 0 (Yes) & 0 (Yes) \\[.2cm]
+     \multirow{2}{*}{5} & $\mc{M}_0$ & 0.030 & 0.377 & 0.347 & 0 (No) & 0 (No)\\
+     & $\mc{M}$ & 0.940 & 0.293 & 0.647 & 0 (Yes) & 0 (Yes)
   \end{tabular}
@@
 \begin{align*}
-	\phi_{i,j}, \theta_{i,j}  & \simiid U(0,1) \\ 
+	\phi_{i,j}, \theta_{i,j}  & \simiid U(-0.4,0.4) \\ 
 	\delta_{i,j} & \simiid N(1,0.5^2) \\
@@
 	\varepsilon_{i,t} & \simiid N(0,1)\\
-	X_{i,j} & \simiid Gamma(1,2) \\
-	\tilde{\theta}_{i,j},\tilde{\phi}_{i,j} & \simiid Beta(\|\mbf{x}_{i,T_i^*+1}\|,1)
-\end{align*}
-Vary $L = 14, 30, 45,60$.
+	X_{i,j} & \simiid Gamma(1,c) \\
+	e_{i,j} & \simiid beta(\alpha, \beta) \\
+	\tilde{\theta}_{i,j}&= \theta_{i,j} + \frac{1}{5}\cdot \Big(e_{ij}-\frac{1}{2}\Big)
+\end{align*}
 

### 2022-08-06 prevalence_testing/numerical_studies/COP.R

@@ -73,6 +73,53 @@ sel <- function(yhat, y) {
   (y - yhat) ^ 2
 }
 
+# tuSPA test for comparison of two models
+tuSPA.mhfc <- function(ell, d, B, bw = 4) {
+  # ell is the block length
+  # d is the matrix of loss differential
+  # B is the bootstrap size
+  # bw is the bandwidth parameter for computing HAC estimator
+  
+  # compute dbar
+  d.bar <- matrix(apply(d, 2, mean))
+  
+  # moving-block bootstrap
+  Tt <- nrow(d); H <- ncol(d)
+  # T = ell * K
+  K <- Tt / ell
+  # Bootstrap replication
+  t.uSPA.B <- c()
+  for (b in 1:B) { 
+    # uniform draw from 1,...,T - ell +1
+    Iks <- sample(1:(Tt - ell + 1), K, replace = TRUE)
+    tau <- matrix(sapply(Iks, function(x) x:(x + ell - 1)))
+    tau <- as.numeric(tau)
+    t.uSPA.b.H <- c()
+    for (h in 1:H) { 
+      # moving-block bootstrap
+      d.b.h <- d[tau, h]
+      d.b.bar.h <- mean(d.b.h)
+      # compute moving block bootstrap standard error
+      xi.b.h <- 0
+      for (k in 1:K) {
+        xi.b.h <- xi.b.h + (sum(d.b.h[(k - 1) * ell + 1:ell] - d.b.bar.h)) ^ 2 / ell
+      }
+      xi.b.h <- xi.b.h / K
+      # compute t.uSPA statistic
+      t.uSPA.b.H[h] <- sqrt(Tt) * (d.b.bar.h - d.bar[h]) / sqrt(xi.b.h)
+    }
+    t.uSPA.B[b] <- min(t.uSPA.b.H)
+  }
+  # compute t.aSPA statistic
+  ## compute Heteroskedasticity and autocorrelation Consistent (HAC) estimator
+  require('tsapp')
+  Omega <- HAC(d, method = 'Quadratic Spectral', bw = bw)
+  t.uSPA <- min(as.numeric(sqrt(Tt) * d.bar / sqrt(diag(Omega))))
+  p <- mean(t.uSPA < t.uSPA.B)
+  # return output
+  return(p)
+}
+
 # taSPA test for comparison of two models
 taSPA.mhfc <- function(ell, d, B, bw = 4) {
   # ell is the block length
[…]

### 2022-08-06 prevalence_testing/numerical_studies/emsda.R

@@ -74,6 +74,53 @@ sel <- function(yhat, y) {
   (y - yhat) ^ 2
 }
 
+# tuSPA test for comparison of two models
+tuSPA.mhfc <- function(ell, d, B, bw = 4) {
+  # ell is the block length
+  # d is the matrix of loss differential
+  # B is the bootstrap size
+  # bw is the bandwidth parameter for computing HAC estimator
+  
+  # compute dbar
+  d.bar <- matrix(apply(d, 2, mean))
+  
+  # moving-block bootstrap
+  Tt <- nrow(d); H <- ncol(d)
+  # T = ell * K
+  K <- Tt / ell
+  # Bootstrap replication
+  t.uSPA.B <- c()
+  for (b in 1:B) { 
+    # uniform draw from 1,...,T - ell +1
+    Iks <- sample(1:(Tt - ell + 1), K, replace = TRUE)
+    tau <- matrix(sapply(Iks, function(x) x:(x + ell - 1)))
+    tau <- as.numeric(tau)
+    t.uSPA.b.H <- c()
+    for (h in 1:H) { 
+      # moving-block bootstrap
+      d.b.h <- d[tau, h]
+      d.b.bar.h <- mean(d.b.h)
+      # compute moving block bootstrap standard error
+      xi.b.h <- 0
+      for (k in 1:K) {
+        xi.b.h <- xi.b.h + (sum(d.b.h[(k - 1) * ell + 1:ell] - d.b.bar.h)) ^ 2 / ell
+      }
+      xi.b.h <- xi.b.h / K
+      # compute t.uSPA statistic
+      t.uSPA.b.H[h] <- sqrt(Tt) * (d.b.bar.h - d.bar[h]) / sqrt(xi.b.h)
+    }
+    t.uSPA.B[b] <- min(t.uSPA.b.H)
+  }
+  # compute t.aSPA statistic
+  ## compute Heteroskedasticity and autocorrelation Consistent (HAC) estimator
+  require('tsapp')
+  Omega <- HAC(d, method = 'Quadratic Spectral', bw = bw)
+  t.uSPA <- min(as.numeric(sqrt(Tt) * d.bar / sqrt(diag(Omega))))
+  p <- mean(t.uSPA < t.uSPA.B)
+  # return output
+  return(p)
+}
+
 # taSPA test for comparison of two models
 taSPA.mhfc <- function(ell, d, B, bw = 4) {
   # ell is the block length
[…]

### 2022-08-17 prevalence_testing/postshocktest2022draft.tex
reconciled Quaedvlieg results within the context of the unemployment example

@@
 
+\vspace*{0.5cm}\textcolor{red}{A naive test for the presence of a mean-shift shock effect predictably decays very quickly as more and more post-shock data is added for fitting purposes when, in truth, the shock is transient.
+However, the Quaedvlieg method runs $h = 1,...,H$ ahead forecasts that will not necessarily indicate a quickly decaying shock due to the training data for the model including post-shock responses that have yet to decay.
+Thus the unadjusted and adjusted forecasts can deviate sharply when their underlying models are fit to a small amount of post-shock data.
+When $H$ is small, there is a lot of post-shock data under consideration, and the shock decays quickly, the initial shock   may not be detected by the Quaedvlieg method due to a loss-difference matrix evaluating several differences that are negligible far away from the initial shock.
+The same can be true when $H$ is large.
+However, for medium size $H$, the influence of fitting the initial post-shock data may not yet accommodate the sharply decayed shock.
+The result of this is that the Quaedvlieg method can indicate a shifted significant difference between the adjusted and un-adjusted forecasts.
+(loss-difference matrix has dimensions $(T - T^* - \max(\lceil1.5\sqrt{T - T^*}\rceil, H))  \times H$) When we have limited sample size, we should not consider large $H$.}
+
 \subsection{Simulations}

### 2022-08-26 prevalence_testing/postshocktest2022draft.tex
addition with tables and comments

@@
 \begin{table}[H]
-	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0.196, 0.804, 0.000)$ from scaled covariates}   \label{uemtable}
+	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls for $\mc{M}_0$ (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0.196, 0.804, 0.000)$ from scaled covariates}   \label{uemtable}
 \begin{center}
   \begin{tabular}{cccccccccr}
-     $H$  & Model &   $p_1$ & $\hat{p}_1$ & $|\hat{p}_1-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
+     $H$   &   $p_1$ & $\hat{p}_1$ & $|\hat{p}_1-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
      \hline 
-     \multirow{2}{*}{2} & $\mc{M}_0$  &   0.300 & 0.443  & 0.143 & 0 (Yes) & 0 (Yes)\\      
-      & $\mc{M}$  & 0.775 & 0.591 & $0.184$   & 0 (Yes) &0 (Yes)   \\[.2cm]
-     \multirow{2}{*}{3} & $\mc{M}_0$ &   0.215 & 0.477 & $0.262$ & 0 (Yes) & 0 (Yes)    \\
-      &  $\mc{M}$ & 0.740 & 0.600 & 0.140 & 0 (Yes) & 0 (Yes)  \\[.2cm]
-     \multirow{2}{*}{4} &  $\mc{M}_0$ &   0.615   & $0.343$ & 0.272 & 0 (Yes) & 0 (Yes)  \\
-      &  $\mc{M}$ & 0.780 & 0.464  & 0.316 & 0 (Yes) & 0 (Yes) \\[.2cm]
-     \multirow{2}{*}{5} & $\mc{M}_0$ & 0.030 & 0.377 & 0.347 & 0 (No) & 0 (No)\\
-     & $\mc{M}$ & 0.940 & 0.293 & 0.647 & 0 (Yes) & 0 (Yes)
+ 2   & 0.33 & 0.21 & 0.12 & 0 (Yes) & 0 (Yes) \\ 
+   3   & 0.11 & 0.51 & 0.40 & 0 (Yes) & 0 (Yes) \\ 
+   4   & 0.43 & 0.52 & 0.09 & 0 (Yes) & 0 (Yes) \\ 
+   5   & 0.02 & 0.36 & 0.34 & 0 (No) & 0 (No) \\  
+   6   & 0.04 & 0.62 & 0.58 & 0 (No) & 0 (No) \\ 
+   7   & 0.03 & 0.40 & 0.37 & 0 (No) & 0 (No) \\ 
+   8  & 0.27 & 0.46 & 0.19 & 0 (Yes) & 0 (Yes) \\ 
+   9   & 0.49 & 0.27 & 0.22 & 0 (Yes) & 0 (Yes) \\ 
+   10  & 0.76 & 0.67 & 0.10 & 0 (Yes) & 0 (Yes) \\ 
   \end{tabular}
@@
 
-\vspace*{0.5cm}\textcolor{red}{A naive test for the presence of a mean-shift shock effect predictably decays very quickly as more and more post-shock data is added for fitting purposes when, in truth, the shock is transient.
+\textcolor{red}{From Table \ref{uemtable}, $p_1$ is insignificant for $H = 2, 3, 4$ and $H = 8, 9, 10$ but is significant for $H = 5, 6, 7$.
+Notice that weighted voting, vote, and $\hat{p}_1$ also does not perform well for $H = 5, 6, 7$.
+This implies something undetected and unique  to the time series of interest occur.
+For this reason, we investigated the point estimates of the shock effects using data from $t = T_1^*+r-37$ to $t = T_1^* + r$.
+Note that for different $r$, the training sample size is fixed and thus prevents training sample size to affect inference results.
+The results are presented in Table \ref{pesr} with point estimates of the shock effects denoted by $\hat{\alpha}_{1, r}$ and corresponding standard error and $p$-value from $t$-test.
+Note that the $t$-test is significant for $r = 1, 2, 3, 4$ but insignificant for $r\geq 5$.}
+
+\vspace*{0.5cm}\textcolor{red}{ This naive test implies that  the presence of a mean-shift shock effect predictably decays very quickly as more and more post-shock data is added for fitting purposes when, in truth, the shock is transient.
 However, the Quaedvlieg method runs $h = 1,...,H$ ahead forecasts that will not necessarily indicate a quickly decaying shock due to the training data for the model including post-shock responses that have yet to decay.
@@
 (loss-difference matrix has dimensions $(T - T^* - \max(\lceil1.5\sqrt{T - T^*}\rceil, H))  \times H$) When we have limited sample size, we should not consider large $H$.}
+
+\begin{table}[H]
+	\caption{Point estimates of shock effects under $\mc{M}_0$ using data from $t = T_1^* + r-37$ to $T^*_1 + r$} \label{pesr}
+	\begin{center}
+		\begin{tabular}{rrcr} 
+ $r$& $\hat{\alpha}_{1,r}$ & $\sqrt{\hat{\mathbf{Var}}(\hat{\alpha}_{1,r})}$ & $p$-value \\ 
+  \hline
+ 1 & $-$0.1344 & 0.0134 & 0.0000 \\ 
+  2 & $-$0.1379 & 0.0138 & 0.0000 \\ 
+  3 & $-$0.1921 & 0.0469 & 0.0002 \\ 
+  4 & $-$0.0055 & 0.0065 & 0.4056 \\ 
+  5 & 0.0054 & 0.0041 & 0.1950 \\ 
+  6 & $-$0.0013 & 0.0025 & 0.6213 \\ 
+  7 & $-$0.0042 & 0.0025 & 0.1003 \\ 
+  8 & $-$0.0028 & 0.0022 & 0.2109 \\ 
+  9 & $-$0.0010 & 0.0020 & 0.6203 \\ 
+  10 & 0.0005 & 0.0019 & 0.7788 \\ 
+  11 & 0.0006 & 0.0018 & 0.7636 \\ 
+  12 & 0.0029 & 0.0019 & 0.1368 \\ 
+  13 & 0.0024 & 0.0022 & 0.2823 \\ 
+  14 & 0.0025 & 0.0021 & 0.2442 \\ 
+  15 & 0.0015 & 0.0021 & 0.4883 \\ 
+  16 & 0.0008 & 0.0023 & 0.7245 \\ 
+  17 & 0.0013 & 0.0022 & 0.5693 \\ 
+  18 & 0.0015 & 0.0022 & 0.4907 \\ 
+   \hline
+\end{tabular}
+	\end{center}	
+\end{table}
 

### 2022-08-26 prevalence_testing/numerical_studies/emsda.R

@@ -626,10 +626,10 @@ date <- rownames(dat)
 # setup
 K <- 24
 # number of horizons
-Hs <- c(2, 3, 4, 5)
+Hs <- c(2, 3, 4, 5, 6, 7, 8, 9, 10)
 # tab
 tab <- data.frame()
-L <- 18
+L <- 15
 
 # result
 for (H in Hs) {
@@ -697,6 +697,7 @@ mod.t4.dynamic <- lm(TS4$PAYEMS ~ as.matrix(TS4[, 2:7]) + co.D + TS4$shock.t4)
 AICs.20080301 <- c(AIC(mod.t4.null), AIC(mod.t4.permanent), AIC(mod.t4.dynamic))
 I.AIC.4 <- ifelse(AIC(mod.t4.permanent) > AIC(mod.t4.dynamic), yes = 1, no = 0)
 
+
 # Time Series 1
 shock.t1 <- which(date == '2020-03-01') + 1
 TS1 <- dat[(shock.t1 - (1 + 12 + K + H)):(shock.t1 + L),]
@@ -718,7 +719,7 @@ mod.t1.dynamic <- lm(TS1$PAYEMS ~ as.matrix(TS1[, 2:7]) + co.D + TS1$shock.t1)
 AICs.20200301 <- c(AIC(mod.t1.null), AIC(mod.t1.permanent), AIC(mod.t1.dynamic))
 
 # Ti
-Ts <- rep(58, 5)
+Ts <- rep(nrow(TS1), 5)
 # Tstar
 Tstar <- rep(39, 5)
 # Y
@@ -734,12 +735,12 @@ for (i in 1:4) {
 # testing 
 res1 <- ps.indic.W.permanent(Tstar = Tstar, q1 = 1, q2 = 1, subset = TRUE, 
                              Y = Y, X = X, K = rep(K, 4), H = H,
-                             Ts = Ts, ell = 4, B = 200, bw = 4, 
+                             Ts = Ts, ell = 4, B = 500, bw = 4, 
                              scale = TRUE)
 
 res2 <- ps.indic.W.dynamic(Tstar = Tstar, Y = Y, X = X, K = rep(K, 4), 
                            q1 = 1, q2 = 1, subset = TRUE,  
-                           H = H, Ts = Ts, ell = 4, B = 200, bw = 4,
+                           H = H, Ts = Ts, ell = 4, B = 500, bw = 4,
                            scale = TRUE)
 
 # p-values
[…]

### 2022-09-19 prevalence_testing/postshocktest2022draft.tex
addition of simulation results

@@
 
+In this section, we propose  several simulation setups to illustrate the performance of our methods and find when they work well and when do not. The parameter setup is shown as follows.
 \begin{align*}
@@
 	\delta_{i,j} & \simiid N(1,0.5^2) \\
-	\alpha_i & \simiid N(10, 2) \\
+	\varepsilon_{\alpha, i} & \simiid N(0, 2) \\
 	T_i^* & \simiid \min\Big(90, \big[Gamma(15,10)\big]\Big) \\
-	\varepsilon_{i,t} & \simiid N(0,1)\\
-	X_{i,j} & \simiid Gamma(1,c) \\
-	e_{i,j} & \simiid beta(\alpha, \beta) \\
-	\tilde{\theta}_{i,j}&= \theta_{i,j} + \frac{1}{5}\cdot \Big(e_{ij}-\frac{1}{2}\Big)
-\end{align*}
+	\varepsilon_{i,t} & \simiid N(0,\sigma)\\
+	X_{i,j} & \simiid Gamma(1,2) \\
+	e_{i,j}, e_{i,j}^* & \simiid beta(\alpha_i^*, \beta_i^*) \\
+	\alpha_i^* &= a_1 \|\mbf{x}_{i, T_i^*+1}\|+b_1 \\
+	\beta_i^* &= a_2 \|\mbf{x}_{i, T_i^*+1}\|+b_2 \\
+	\tilde{\theta}_{i,j}&= \theta_{i,j} + \frac{1}{5}\cdot \Big(e_{ij}-\frac{1}{2}\Big)\\
+	\tilde{\phi}_{i,j}&= \phi_{i,j} + \frac{1}{5}\cdot \Big(e_{ij}^*-\frac{1}{2}\Big)
+\end{align*}
+Note that  $\phi_{i,j}, \theta_{i,j} \simiid U(-0.4,0.4)$ are designed to prevent non-stationarity.
+The reason for the design of $T_i^*$ is similar to that in Section 4 of \cite{lin2021minimizing}.
+In particular, we focus on varying $\mu_{\alpha}$, $\sigma$, and $a_1$ under the design of $\mc{M}$ as specified in Section \ref{modelsetup}.
+Note that $\mu_{\alpha}$ controls the signal of the shock whereas $\sigma$ manages the noise of the response.
+$a_1, a_2$ is related to the magnitude of $\alpha_i^*$, which depends also on $\|\mbf{x}_{i, T_i^*+1}\|$.
+This simulation design allows for the situations when the post-shock dynamics depends on the covariates at the time points the shock occur.
+For simplicity, we set $a_2=0$ and fix $b_1=b_2=1$.
+By varying $a_1$, we know how our methods perform as $\E(e_{i,j})$ ranges from 0 to 1.
+
+For illustration purpose, we keep other parameters simple and friendly for easier computation with bootstrap sample size $B=200$, maximum horizon $H=10$, autoregressive parameter order $q_1=q_2=2$,  donor pool sample size $n=10$, and covariate dimension $p=2$.
+Note that we set the block size in the moving block bootstrap to be $\ell=4$ and the bandwidth for HAC estimator of the covariance matrix  to be 4 (see Section \ref{sec:multhor}).
+
+In the first simulation, we vary $\mu_{\alpha}$ and $a_1$ with results presented in Table \ref{tablemualpha}.
+First, fixing $a_1$, we see that the  $\hat{\E}(\hat{p})$ and the misclassification rate (MCR) of voting and weighted voting get improved as $\mu_{\alpha}$ increases.
+When $\mu_{\alpha}=0$, the misclassification rates are close to 0.5.
+It makes sense by Proposition \ref{votprop} and \ref{votprop2} since $\hat{\E}(p_1)$ is close to 0.5 in this scenario.
+Under this design, the shock signal is neither strong enough or weak enough for the method to classify it as being persistent or transient so that the results may be poor.
+However, as $\mu_{\alpha}$ increases, the shock signal strength gets large.
+Table \ref{tablemualpha} shows that the results appear satisfactory when $\mu_{\alpha}=100$.
+
+Second, fixing $\mu_{\alpha}$, varying $a_1$ lead to a better fitting results though the improvement is marginal and does not hold for some combinations of $\mu_{\alpha}$ and $a_1$.
+Note that as $a_1$ increases from $10^{-3}$ to $10^3$, $\E(e_{ij})$ tends from 0 to $\infty$.
+According to $\mc{M}$ (see Section \ref{modelsetup}), this change make the post-shock dynamics more different than the pre-shock dynamics so that the shock signal strength gets larger.
+
+\begin{table}[H]
+	\caption{Monte Carlo Simulation of $\mc{M}$ with varying $\mu_{\alpha}$ and $a_1$ } \label{tablemualpha}
+	\begin{center}
+\begin{tabular}{rrrccccc}
+  \hline
+  $\mu_{\alpha}$ & $a_1$ & $\hat{\E}(\hat{p})$ & $\hat{\E}(p_1)$ & $\hat{\E}\big(|\hat{p}-p_1|\big)$ & MCR of voting & MCR of weighted voting \\ 
+  \hline
+ 0 & \multirow{3}{*}{$10^{-3}$} & 0.458 (0.025) & 0.420 (0.033) & 0.420 (0.024) & 0.495 (0.035) & 0.440 (0.035) \\ 
+   10 &   & 0.206 (0.022) & 0.195 (0.027) & 0.278 (0.025) & 0.250 (0.031) & 0.345 (0.034) \\ 
+   100 &  & 0.037 (0.010) & 0.010 (0.007) & 0.047 (0.012) & 0.010 (0.007) & 0.035 (0.013) \\[.2cm] 
+   \hline
+   0 & \multirow{3}{*}{$1$} & 0.382 (0.025) & 0.343 (0.031) & 0.423 (0.025) & 0.470 (0.035) & 0.520 (0.035) \\ 
+   10 &   & 0.185 (0.020) & 0.141 (0.024) & 0.267 (0.025) & 0.175 (0.027) & 0.285 (0.032) \\ 
+   100 &  & 0.014 (0.006) & 0.025 (0.011) & 0.039 (0.013) & 0.025 (0.011) & 0.035 (0.013) \\[.2cm] 
+   \hline
+   0 & \multirow{3}{*}{$10^3$} & 0.365 (0.024) & 0.268 (0.029) & 0.401 (0.023) & 0.430 (0.035) & 0.450 (0.035) \\ 
+   10 &  & 0.130 (0.017) & 0.139 (0.024) & 0.235 (0.024) & 0.160 (0.026) & 0.250 (0.031) \\ 
+   100 &   & 0.022 (0.007) & 0.010 (0.007) & 0.032 (0.010) & 0.010 (0.007) & 0.030 (0.012) \\ 
+   \hline
+\end{tabular}
+	\end{center}	
+\end{table}
+
+\begin{table}[H]
+\caption{Monte Carlo Simulation with varying $\sigma$ and $a_1$ ($B = 200$, $\mu_{\alpha}=20$, $H = 10$, $\ell=4$, bandwidth 4, $q_1=q_2=2$, $b_1=b_2=1$, $a_2=0$,   $n = 10$, $p= 2$, $\sigma_{\alpha}=2$, $\sigma_{\delta}=0.05$, $\mu_{\delta}=1$)} \label{tablesigma}
+	\begin{center}
+		\begin{tabular}{rrcccccc}
+  \hline
+  $\sigma$ & $a_1$ & $\hat{\E}(\hat{p})$ & $\hat{\E}(p_1)$ & $\hat{\E}\big(|\hat{p}-p_1|\big)$ & MCR of voting & MCR of weighted voting \\ 
+  \hline
+ 0.01 & \multirow{5}{*}{$10^{-3}$} & 0 (0) & 0 (0) & 0 (0) & 0 (0) & 0 (0) \\ 
+   1 &   & 0.116 (0.016) & 0.117 (0.022) & 0.191 (0.023) & 0.120 (0.023) & 0.170 (0.027) \\ 
+   5 &   & 0.545 (0.026) & 0.581 (0.034) & 0.471 (0.026) & 0.440 (0.035) & 0.475 (0.035) \\ 
+   10 & & 0.685 (0.023) & 0.713 (0.031) & 0.431 (0.026) & 0.330 (0.033) & 0.415 (0.035) \\ 
+   50 &  & 0.935 (0.013) & 0.935 (0.017) & 0.119 (0.020) & 0.065 (0.017) & 0.095 (0.021) \\[.2cm] 
+   \hline
+   0.01 & \multirow{5}{*}{$1$} & 0 (0) & 0 (0) & 0 (0) & 0 (0) & 0 (0) \\ 
+   1 &   & 0.112 (0.016) & 0.090 (0.020) & 0.192 (0.023) & 0.105 (0.022) & 0.195 (0.028) \\ 
+   5 &   & 0.493 (0.026) & 0.424 (0.034) & 0.499 (0.025) & 0.460 (0.035) & 0.520 (0.035) \\ 
+   10 &   & 0.626 (0.025) & 0.610 (0.034) & 0.430 (0.026) & 0.400 (0.035) & 0.380 (0.034) \\ 
+   50 &   & 0.961 (0.009) & 0.891 (0.022) & 0.136 (0.022) & 0.105 (0.022) & 0.125 (0.023) \\[.2cm]
+   \hline
+   0.01 & \multirow{5}{*}{$10^3$} & 0 (0) & 0 (0) & 0 (0) & 0 (0) & 0 (0) \\ 
+   1 &  & 0.078 (0.013) & 0.085 (0.020) & 0.149 (0.021) & 0.090 (0.020) & 0.145 (0.025) \\ 
+   5 &  & 0.461 (0.025) & 0.481 (0.035) & 0.530 (0.025) & 0.480 (0.035) & 0.570 (0.035) \\ 
+   10 &  & 0.684 (0.023) & 0.546 (0.035) & 0.473 (0.026) & 0.430 (0.035) & 0.480 (0.035) \\ 
+   50 &   & 0.921 (0.014) & 0.894 (0.022) & 0.172 (0.023) & 0.105 (0.022) & 0.155 (0.026) \\ 
+   \hline
+\end{tabular}
+	\end{center}	
+\end{table}
+
+In the second simulation, we fix $\mu_{\alpha}$ to be 20 and try to vary $\sigma$ and $a_1$.
+The results are presented in Table \ref{tablesigma}.
+Fixing $a_1$, we can observe that the results become worse and then better as $\sigma$ increases.
+Notably, when $\sigma=0.01$, which is almost close to zero as compared to $\mu_{\alpha}=20$, $\hat{\E}\big(|\hat{p}-p_1|\big)$ and misclassification rates of voting and weighted voting are almost zero.
+This implies that when the donors are nearly replicates of the time series of interest, our method is almost perfect.
+When $\sigma$ is small, the shock signal from $\mu_{\alpha}$ is relatively large and can be easily captured as a persistent shock.
+In contrast, when $\sigma$ is large, as $\mu_{\alpha}$ is fixed, the shock signal is relatively small so that it is understood as a transient shock.
+In terms of the $U$ shaped performance of our results, we posit that when $\sigma$ is moderately large, the shock signal can be easily understood as persistent or transient because under this configuration, it is very possible that the response $y_{i,t}$ can attain a magnitude greater than the shock $\alpha_{i,t}$ or smaller.
+
+In Table \ref{tablesigma}, fixing $\sigma$, we do not observe a clear trend about how $a_1$ interacts with $\hat{\E}\big(|\hat{p}-p_1|\big)$ and the misclassification rates of voting and weighted voting.
+Note that $a_1$ controls  the mean and variance of the noise for  the post-shock autoregressive parameters of $\tilde{\theta}_{i,j}, \tilde{\phi}_{i,j}$.
+It appears that $a_1$ does not affect the results, suggesting that our method is not sensitive to the noise of the unobserved parameter distribution.
+
+In conclusion, via the simulation, we find that our method works well when the shock signal is either very strong or weak compared to the noise of the response.
+However, the signal may mislead our method when the shock signal strength is similar to that of the noise.
+Note that both $\tilde{\theta}_{i,j}, \tilde{\phi}_{i,j}$ and $\mu_{\alpha}$ play a role in the post-shock dynamics but  $\tilde{\theta}_{i,j}, \tilde{\phi}_{i,j}$ controls the structure.
+Based on our results, we find that our method is not sensitive to the change of structure but instead the mean shift due to $\mu_{\alpha}$.
 

### 2022-09-22 prevalence_testing/postshocktest2022draft.tex
minor updates

@@
 Under this setup any two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|$ are expected to experience similar structural changes.
-This makes distance based weighting an attractive avenue.
+This makes distance-based weighting an attractive avenue.
 
@@
 
-A p-value corresponding to the hypothesis test \eqref{test} is computed using a moving block bootstrap (MBB) of of \cite{kunsch1989jackknife} and \cite{liu1992moving}.
+A p-value corresponding to the hypothesis test \eqref{test} is computed using a moving block bootstrap (MBB) of \cite{kunsch1989jackknife} and \cite{liu1992moving}.
 In the moving block bootstrap (MBB), a pseudo time-series is constructed by resampling blocks of length $\ell$ from the original data.
@@
 
-We now demonstrate an idealized theoretical setting for which our post-shock testing methodology involving a distance based weighted average of p-values works well.
-The idea is that inferences based on distance based weighted nearly recovers the time series under study when there exists a time series in the donor pool, indexed by $i'$, such that $\x_{1,t} \approx \x_{i',t}$ and the signal strength in our modeling setup \eqref{model-gen} and \eqref{random-effects} is large relative to variation.
+We now demonstrate an idealized theoretical setting for which our post-shock testing methodology involving a distance-based weighted average of p-values works well.
+The idea is that inferences based on distance-based weighted nearly recovers the time series under study when there exists a time series in the donor pool, indexed by $i'$, such that $\x_{1,t} \approx \x_{i',t}$ and the signal strength in our modeling setup \eqref{model-gen} and \eqref{random-effects} is large relative to variation.
 

### 2022-09-22 prevalence_testing/postshocktest2022draft.tex
revision to the algorithms

@@
 We make such adjustment for the reason that  the method of  \cite{lin2021minimizing} is generally more likely to perform better than the ordinary forecast under certain conditions.
-Second, notice that we evaluate forecast comparison for $t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$ with time length smaller than $T_i$.
+Second, notice that we evaluate forecast comparison for $t = T_i^*+\ceil{1.5 \cdot \sqrt{T_i-T_i^*}} + 1, \ldots, T_i$ with time length smaller than $T_i$.
 It is because the framework of \cite{quaedvlieg2021multi} needs training sample, which implicitly requires users to feed the algorithm with moderately large dataset for a more credible analysis.
@@
  	\For{$h = 1, \ldots, H$}{
- 		\For{$t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$}{
+ 		\For{$t = T_i^*+\ceil{1.5 \cdot \sqrt{T_i-T_i^*}} + 1, \ldots, T_i$}{
  		Compute $\hat{y}_{i,t}^{1, h}$ and $\hat{y}_{i,t}^{2, h}$ based on OLS estimation of $\mc{M}$ with $\{T_i^* \colon i = 1, \ldots, n+1\}$ and   training data $\{(y_{i,t}, \mbf{x}_{i,t})\colon  t =  t-h- K_i +1, \ldots, t-h\}$, where we further need the set of lagged response $\{y_{i,t}\colon t = t-h-K_i- \max\{q_1, q_2-1\}+1, t-h-K_i\}$.
 
- 		\If{$t-h = T_i^*$, $i\geq 3$, and $h =1$}{
- 		$\hat{y}_{i,t}^{2, h}= \hat{y}_{i,t}^{2, h} + \hat{\alpha}_{\rm wadj}$
- 		}
  		Compute the squared error loss $l_{i,t,h, 1}$ based on $y_{i, t}$
@@
 Note that Corollary \ref{coro2} gives an asymptotic upper bound for the misclassification rate of synthetic pairwise model selection, which is small if $\xi_1$ is large.
-
-%We further define the parameter sets
-%\begin{align}
-%\begin{array}{l}
-% \;\, \Theta = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon    t= 1, \ldots, T_i, i = 2, \ldots, n +1\} \\
-%   \Theta_1 = \{(\eta_i, \mathbf{\phi}_i, \mathbf{\theta}_i, \mathbf{\delta}_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1})\colon  t= 1, \ldots, T_i, i = 1\}
-%\end{array}\label{parameter} 
-%\end{align}
 
@@
 
-%\textbf{Notes}:
-%$$
-%\begin{pmatrix}
-%	0 & t & T^* + (t-T^*) \\
-%	1 & t-1 & T^* + (t-T^*-1) \\
-%	2 & t-2 & T^* + (t-T^*-2) \\
-%	 \vdots & \vdots \\
-%	t-T^*-1 & t- (t-T^*-1) = T^*+1 & T^* + (t-T^*- (t-T^*-1) )	\\ 
-%	t-T^* & t- (t-T^*) = T^* & T^* + (t-T^*- (t-T^*) )
-%\end{pmatrix}
-%$$
-
 \section{Numerical Examples}
@@
 
-%Post-shock  prevalence testing is motivated by post-shock prediction  \citep{lin2021minimizing} and also an extension of it from the perspective of hypothesis testing.
-Applying our methodology  on one of the datasets demonstrated in \cite{lin2021minimizing} helps connect our work to \cite{lin2021minimizing} and spell out the differences between two methodologies.
-
 As illustrated in Section 5.1 in \cite{lin2021minimizing}, it is found that Conoco Phillips stock price experienced unprecedented shocks due to a Russia-OPEC oil supply control battle and increasing COVID-19 pandemic fear which were simultaneously realized on Monday, March 9th, 2020.
@@
 Note that Proposition \ref{votprop} and Corollary \ref{coro2} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$.}
-
-%\begin{table}[H]
-	%\caption{Results for Conoco Philips ($n=5$), $\mbf{W}^* = (0, 0, 0, 0.363, 0.637)$ from scaled covariates}
-%\begin{center}
-  %\begin{tabular}{cccccccccr}
-     %$L$ ($T_i-T^*_i$) & Model & $p_1$  & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
-     %\hline 
-     %7 & Permanent & 1  & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $236.21$ \\
-     % 7 & Dynamic & 1 & $0$   &  \textcolor{red}{0} & \textcolor{red}{0}  & $324.91$ \\[.2cm]
-     %15 & Permanent & 1   & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 273.95 \\
-     %15 & Dynamic & 1  & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $370.83$\\[.2cm]
-     %30 & Permanent & 1   & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  346.17 \\
-     %30 & Dynamic & 1 & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 451.16
-  %\end{tabular}
-%\end{center}	
-%\end{table}
 

### 2022-10-06 prevalence_testing/postshocktest2022draft.tex
push minor edits

@@
 \begin{equation} \label{boott}
-  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
-  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
+  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}} \leq z\right] 
+  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}_{i}}  \leq z\right]
   \Big\vert \overset{P}{\longrightarrow} 0,
@@
 where $\hat{p}_i^B$ is given as \eqref{bootp} and $w_i^*$ is the weight corresponding to the similarity between the first and $(i+1)$th row of $\mbf{X}^*$.
-
-\textcolor{red}{Need to make a decision about voting and weighted voting; not sure if it is more robust or efficient than the weighted p-value approach.
-If it is not superior than the weighted approach in any way then we should remove it.} We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool.
+\textcolor{red}{Need to explain why (8) is a good thing.
+This can be done by a quick explanation and referencing simulation results and the heuristic reasoning below.}
+
+We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool.
 Given a significance level $\alpha$ and estimates $\{\hat{p}_i^B \colon i = 2, \ldots, n+1\}$, we compute the vote
@@
 \begin{prop}
-\label{votprop}Suppose $p_2, \ldots, p_{n+1}$ is  a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest.
+\label{votprop}Suppose $p_1, \ldots, p_{n+1}$ is  a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest.
 If $\P(p_1 \leq \alpha) \neq 0.5$,  as $n\to \infty$,
